### 2019-09-01 paper.tex
Make placeholder sections

\documentclass{article}
\usepackage{authblk}

\title{Test Title}

\author[1]{Kai-Min Chung}
\author[1]{Yi Lee}
\author[2]{Han-Hsuan Lin}
\author[3]{Xiaodi Wu}
\affil[1]{Institute of Information Science, Academia Sinica, Taipei, Taiwan}
\affil[2]{Department of Computer Science, University of Texas at Austin}
\affil[3]{
	Department of Computer Science, Institute for Advanced Computer Studies,
	and Joint Center for Quantum Information and Computer Science,
	University of Maryland, USA
}

\begin{document}

\maketitle

\begin{abstract}

This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...

\end{abstract}

\section{Introduction}

This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...

\section{Preliminaries}

This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...

\section{more stuff}

This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...

\begin{thebibliography}{9}
	\bibitem{1804.01082}
		Urmila Mahadev.
		\newblock Classical Verification of Quantum Computations, 2018;
		\newblock arXiv:1804.01082.

	\bibitem{quant-ph/0406180}
		Julia Kempe, Alexei Kitaev and Oded Regev.
		\newblock The Complexity of the Local Hamiltonian Problem, 2004,
		\newblock SIAM Journal of Computing, Vol. 35(5), p. 1070-1097 (2006),
		  conference version in Proc. 24th FSTTCS, p. 372-383 (2004);
		  \newblock arXiv:quant-ph/0406180.

\end{thebibliography}

\end{document}

### 2019-09-01 paper.tex
Use tabs instead of mixed tabs and spaces
Add another cited item
Add another reference and placeholder intro

@@
 This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
+Below is some intro of it copied from my SoP
+
+It was proven that BQP=BQIP.
+That is, if a quantum computer can efficiently solve a given decision problem, then it can also efficiently convince a classical machine of its solution.
+I'm generalizing this to arbitrary efficient quantum computations.
+The proof for decision problems involves the classical verifier reducing the problem to a local Hamiltonian instance; the quantum prover would then commit its certificate and act as the verifier’s trusted measurement device as put forth in "Classical Verification of Quantum Computations" by Mahadev.
+It isn't as trivial as it may seem.
+Repeating the scheme for each qubit loses the information carried by entanglements and throws off the joint distribution between qubits.
+Simply measuring the entire output register instead is difficult to analyze.
+For decision problems, it’s not hard to argue that a malicious prover cannot do better than sending identical copies of some pure state unentangled with each others.
+That same reasoning doesn't apply here a priori.
+I've been trying to get a grasp on the particular structure of the local Hamiltonian reduction in order to better analyze it.
 
@@
 \section{more stuff}
-
-This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
 
@@
 
+	\bibitem{1109.0795}
+	Matthew McKague.
+	\newblock On the power quantum computation over real Hilbert spaces, 2011,
+	\newblock Int. J. Quantum Inform., 11, 1350001 (2013);
+	\newblock arXiv:1109.0795.
+	\newblock DOI: 10.1142/S0219749913500019.
+
+	\bibitem{0704.1287}
+	Jacob D. Biamonte and Peter J. Love.
+	\newblock Realizable Hamiltonians for Universal Adiabatic Quantum Computers, 2007,
+	\newblock Phys. Rev. A 78, 012352 (2008).;
+	\newblock arXiv:0704.1287.
+	\newblock DOI: 10.1103/PhysRevA.78.012352.
+
 \end{thebibliography}

### 2019-09-01 paper.tex
Start the preliminaries section

@@
 \usepackage{authblk}
+\usepackage{amsmath, amssymb, amsthm}
+
+\newtheorem{theorem}{Theorem}[section]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
 
@@
 
-This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
-Below is some intro of it copied from my SoP
+Below is some intro of it copied from my SoP.
+This is unpolished and mostly a placeholder at the moment though.
 
@@
 
-This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
+\subsection{Notations}
 
-\section{more stuff}
+Let $H\in\mathbb{R}^{N\times N}$ be Hermitian.
+
+\begin{definition}
+	Let $\lambda(H)$ as the least eigenvalue of $H$.
+\end{definition}
+
+\begin{definition}
+	Let the \emph{ground state} of $H$ be the eigenvector corresponding to $\lambda(H)$.
+\end{definition}
+
+\subsection{Local Hamiltonian}
+
+The local Hamiltonian problem is defined as follows:
+
+Given $H_1, \ldots, H_n\in\mathbb{R}^{N\times N}$, where each $H_j$ is Hermitian and has nonzero entries on at most $c\in\mathbb{N}$ rows and columns.
+Given $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, decide whether $\lambda(H)<a$ or $\lambda(H)>b$..
+
+\begin{theorem}
+	Local Hamiltonian is QMA-complete.
+\end{theorem}
+
+\section{The Scheme}
+
+Here we describe the scheme between the classical client and an honest quantum server.
+
+First, we apply the transform given in \cite{1109.0795} to the desired quantum circuit.
+Everything is real numbers from here on.
+Note that this preserves the results of X/Z measurements.
+Then, we transform the circuit following the projection lemma construction described in \cite{quant-ph/0406180}.
+Additionally, we also double the size of the circuit by padding identity matrices at the end.
+We then follow the rest of \cite{quant-ph/0406180} and reduce the circuit into a 2-Local Hamiltonian instance.
+We can then turn all the Hamiltonians involved into some combinations of $X$ and $Z$ matrices following \cite{0704.1287}.
+
+We then follow \cite{1804.01082}.
+That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
+The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{quant-ph/0406180}.
+It will drop the $H_{out}$ term and simply set $H=J_{in}H_{in}+J_2H_{prop2}+J_1H_{prop1}+J_{clock}H_{clock}$.
+
+\section{Stuff}
 

### 2019-09-02 paper.tex
Write more on preliminaries

@@
 
-\title{Test Title}
+\title{Placeholder Title... Something About Delegating Quantum Computations}
 
@@
 
-Let $H\in\mathbb{R}^{N\times N}$ be Hermitian.
+Let $\mathcal{B}$ denote the Hilbert space corresponding to a qubit.
+Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian.
+
+\begin{definition}
+	Let $H\geq0$ denote $H$ is positive semidefinite.
+\end{definition}
 
@@
 
-Given $H_1, \ldots, H_n\in\mathbb{R}^{N\times N}$, where each $H_j$ is Hermitian and has nonzero entries on at most $c\in\mathbb{N}$ rows and columns.
-Given $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, decide whether $\lambda(H)<a$ or $\lambda(H)>b$..
+\begin{definition}
+	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian. Then $$H=\sum_{j=1}^nH_j$$ is called a \emph{Hamiltonian}.
+	If each $H_j$ acts on at most $k$ qubits, then $H$ is called a \emph{$k$-local Hamiltonian}.
+\end{definition}
+
+The local Hamiltonian problem is given by let $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, determine whether $\lambda(H)<a$ or $\lambda(H)>b$..
 
 \begin{theorem}
-	Local Hamiltonian is QMA-complete.
+	The Local Hamiltonian problem is QMA-complete.
 \end{theorem}
+
+\subsection{Projection Lemma}
+
+Here is a lemma that we will use, taken from \cite{quant-ph/0406180}.
+
+Let $H_1, H_2$ be Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
+Then $\exists J\in\mathbb{R}$ s.t.
+$\lambda(H_1\big|_S)-\frac{1}{8}\leq
+	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.
 
@@
 
-First, we apply the transform given in \cite{1109.0795} to the desired quantum circuit.
-Everything is real numbers from here on.
-Note that this preserves the results of X/Z measurements.
+\subsection{Preprocessing the circuit}
+
+We first take our universal
+
+\subsection{Reduction to Real Quantum Computation}
+
+The transform is found in \cite{1109.0795}. It turns the states and the unitary matrices into real numbers.
+
 Then, we transform the circuit following the projection lemma construction described in \cite{quant-ph/0406180}.
@@
 We can then turn all the Hamiltonians involved into some combinations of $X$ and $Z$ matrices following \cite{0704.1287}.
+
+Note that this preserves the results of X/Z measurements.
+
+\subsection{Reduction to 2-local Hamiltonians}
 
@@
 
-\section{Stuff}
+\subsection{Test computation}
+
+\subsection{Stuff}
 

### 2019-09-02 paper.tex
Write out a sketch of the scheme

@@
 
+\begin{definition}
+	Denote the \emph{controlled phase gate}: $C_\phi|xy\rangle=(-1)^{xy}|xy\rangle$.
+\end{definition}
+
+\begin{definition}
+	Let $H\big|_S=\prod_SH\prod_S$, where $\prod_S$ is the projection onto the subspace $S$.
+\end{definition}
+
+\begin{definition}
+	Let $|\widehat{t}\rangle$ denote $t$ represented in unary. That is, a state of the form $|11\ldots1\rangle |00\ldots0\rangle$; that is, $t$ $1$s followed by all $0$s.
+\end{definition}
+
 \subsection{Local Hamiltonian}
@@
 
-\subsection{Preprocessing the circuit}
-
-We first take our universal
-
 \subsection{Reduction to Real Quantum Computation}
@@
 
-Then, we transform the circuit following the projection lemma construction described in \cite{quant-ph/0406180}.
-Additionally, we also double the size of the circuit by padding identity matrices at the end.
+TODO: maybe describe the transform here as needed.
+Need to show that this doesn't change X/Z measurements.
+Also need to show that the result of this can still be rewritten into controlled phase gates and one-qubit gates.
+
+\subsection{Reduction to 2-local Hamiltonians}
+
+Then we reduce the circuit to an instance of 2-local Hamiltonian. This reduction is mostly based on \cite{quant-ph/0406180}.
+
+\subsection{preprocess the circuit}
+
+First, we rewrite the circuit to consist of only controlled phase gates and 1-qubit gates.
+TODO: prove that these 1-qubit gates are all real.
+We then double (TODO maybe multiply by $\gamma$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
+
+\subsection{2-local Hamiltonian construction}
+
+We then attempt to construct a 2-local Hamiltonian with ground state $$\phi=\sum_{t=0}^TU_t...U_1|x\rangle\otimes|\hat{t}\rangle$$.
+
 We then follow the rest of \cite{quant-ph/0406180} and reduce the circuit into a 2-Local Hamiltonian instance.
 We can then turn all the Hamiltonians involved into some combinations of $X$ and $Z$ matrices following \cite{0704.1287}.
+It will drop the $H_{out}$ term and simply set $H=J_{in}H_{in}+J_2H_{prop2}+J_1H_{prop1}+J_{clock}H_{clock}$.
 
-Note that this preserves the results of X/Z measurements.
+\subsection{2-local ZX Hamiltonians}
 
-\subsection{Reduction to 2-local Hamiltonians}
+We then follow \cite{0704.1287} in writing each terms of $H$ into only $Z$ and $X$ measurements...
+
+This probably involves some kind of basis arguments on the Hamiltonians and maybe some stuff that's a bit more ugly. This should not change the state. I'll have to write this out later...
+
+\subsection{Checking computation}
 
@@
 The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{quant-ph/0406180}.
-It will drop the $H_{out}$ term and simply set $H=J_{in}H_{in}+J_2H_{prop2}+J_1H_{prop1}+J_{clock}H_{clock}$.
 
-\subsection{Test computation}
-
-\subsection{Stuff}
+\subsection{Getting the Output}
 

### 2019-09-02 paper.tex
Copy over info from the 2local slides

@@
 Here we describe the scheme between the classical client and an honest quantum server.
+Let $x$ be the client's input, and $U_T...U_1$ be the circuit to evaluate.
 
@@
 TODO: prove that these 1-qubit gates are all real.
-We then double (TODO maybe multiply by $\gamma$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
+We ensure that each $C_\phi$s are preceded and followed by two $Z$ gates.
+That is, if the $C_\phi$ acts on the qubits $f_t$ and $s_t$, then the circuit would look like $Z_{f_t}Z_{s_t}C_\phi Z_{s_t}Z_{f_t}$ around each $C_\phi$.
+We then pad the circuit so that the $C_\phi$s are applied at $t\in T_2=\{L, 2L, 3L, \ldots\}$ for some $L\in\mathbb{N}$.
+Let $T_1=[T]\setminus T_2$ be time steps corresponding to 1-qubit gates.
 
-\subsection{2-local Hamiltonian construction}
+We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
+
+\subsection{Constructing the 2-local Hamiltonian instance}
 
 We then attempt to construct a 2-local Hamiltonian with ground state $$\phi=\sum_{t=0}^TU_t...U_1|x\rangle\otimes|\hat{t}\rangle$$.
+We do so by causing states perpendicular to this to have high eigenvalues.
 
-We then follow the rest of \cite{quant-ph/0406180} and reduce the circuit into a 2-Local Hamiltonian instance.
-We can then turn all the Hamiltonians involved into some combinations of $X$ and $Z$ matrices following \cite{0704.1287}.
-It will drop the $H_{out}$ term and simply set $H=J_{in}H_{in}+J_2H_{prop2}+J_1H_{prop1}+J_{clock}H_{clock}$.
+First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes |01\rangle\langle01|_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
+We note that when stricted to $S_{legal}$, 
+\begin{itemize}
+	\item $|10\rangle\langle10|_{t,t+1}
+		=|\widehat{t}\rangle\langle\widehat{t}|$ 
+	\item $|1\rangle\langle0|_{t+1}
+		=|\widehat{t+1}\rangle\langle\widehat{t}|$
+	\item $|11\rangle\langle00|_{t,t+1}
+		=|\widehat{t+2}\rangle\langle\widehat{t}|$
+\end{itemize}
+
+Then, we ensure that 1-qubit gates are propagated properly. To do so, we set
+	$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
+	$$H_{prop,t}=I\otimes|\widehat{t}\rangle\langle\widehat{t}|
+		+I\otimes|\widehat{t-1}\rangle\langle\widehat{t-1}|
+		-U_t\otimes|\widehat{t}\rangle\langle\widehat{t-1}|
+		-U_t^\dagger\otimes|\widehat{t-1}\rangle\langle\widehat{t}|$$
+
+I probably need to explain why this works but I'll leave it for another day.
+
+Let $S_{prop1}=\ker H_{prop1}$.
+Then, $S_{prop1}$ has the following as basis:
+\begin{itemize}
+	\item $|00\rangle_{f_t,s_t}|\xi_{00}\rangle\otimes
+		(|\widehat{t}\rangle+|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)$
+	\item $|01\rangle_{f_t,s_t}|\xi_{01}\rangle\otimes
+		(|\widehat{t}\rangle+|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)$
+	\item $|10\rangle_{f_t,s_t}|\xi_{10}\rangle\otimes
+		(|\widehat{t}\rangle-|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)$
+	\item $|11\rangle_{f_t,s_t}|\xi_{11}\rangle\otimes
+		(|\widehat{t}\rangle-|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)$
+\end{itemize}
+
+Also, if $t\in T_2$, that is, $t$ corresponds to a time step where $C_\phi$ is applied, then the following are true due to $C_\phi$ being surrounded by $Z$ gates:
+\begin{itemize}
+	\item $|0\rangle\langle0|_{f_t}\otimes
+		|\widehat{t}\rangle\langle\widehat{t}|
+		=(|\widehat{t}\rangle+|\widehat{t+1}\rangle)
+		(\langle\widehat{t}|+\langle\widehat{t+1}|)$
+	\item $|1\rangle\langle1|_{f_t}\otimes
+		|\widehat{t}\rangle\langle\widehat{t}|
+		=(|\widehat{t}\rangle-|\widehat{t+1}\rangle)
+		(\langle\widehat{t}|-\langle\widehat{t+1}|)$
+	\item $|0\rangle\langle0|_{s_t}\otimes
+		|\widehat{t}\rangle\langle\widehat{t}|
+		=(|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)
+		(\langle\widehat{t+1}|+\langle\widehat{t+2}|)$
+	\item $|1\rangle\langle1|_{s_t}\otimes
+		|\widehat{t}\rangle\langle\widehat{t}|
+		=(|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)
+		(\langle\widehat{t+1}|-\langle\widehat{t+2}|)$
+	\item $(|00\rangle\langle00|_{f_t,s_t}
+		+|11\rangle\langle11|_{f_t,s_t})\otimes
+		|\widehat{t}\rangle\langle\widehat{t}|
+		=(|\widehat{t}\rangle+|\widehat{t+2}\rangle)
+		(\langle\widehat{t}|+\langle\widehat{t+2}|)$
+	\item $(|01\rangle\langle01|_{f_t,s_t}
+		+|10\rangle\langle10|_{f_t,s_t})\otimes
+		|\widehat{t}\rangle\langle\widehat{t}|
+		=(|\widehat{t}\rangle-|\widehat{t+2}\rangle)
+		(\langle\widehat{t}|-\langle\widehat{t+2}|)$
+\end{itemize}
+
+Similarly,
+\begin{itemize}
+	\item $|0\rangle\langle0|_{f_t}\otimes
+		|\widehat{t-1}\rangle\langle\widehat{t-1}|
+		=(|\widehat{t-1}\rangle+|\widehat{t-2}\rangle)
+		(\langle\widehat{t-1}|+\langle\widehat{t-2}|)$
+	\item $|1\rangle\langle1|_{f_t}\otimes
+		|\widehat{t-1}\rangle\langle\widehat{t-1}|
+		=(|\widehat{t-1}\rangle-|\widehat{t-2}\rangle)
+		(\langle\widehat{t-1}|-\langle\widehat{t-2}|)$
+	\item $|0\rangle\langle0|_{s_t}\otimes
+		|\widehat{t-1}\rangle\langle\widehat{t-1}|
+		=(|\widehat{t-2}\rangle+|\widehat{t-3}\rangle)
+		(\langle\widehat{t-2}|+\langle\widehat{t-3}|)$
+	\item $|1\rangle\langle1|_{s_t}\otimes
+		|\widehat{t-1}\rangle\langle\widehat{t-1}|
+		=(|\widehat{t-2}\rangle-|\widehat{t-3}\rangle)
+		(\langle\widehat{t-2}|-\langle\widehat{t-3}|)$
+	\item $(|00\rangle\langle00|_{f_t,s_t}
+		+|11\rangle\langle11|_{f_t,s_t})\otimes
+		|\widehat{t-1}\rangle\langle\widehat{t-1}|
+		=(|\widehat{t-1}\rangle+|\widehat{t-3}\rangle)
+		(\langle\widehat{t-1}|+\langle\widehat{t-3}|)$
+	\item $(|01\rangle\langle01|_{f_t,s_t}
+		+|10\rangle\langle10|_{f_t,s_t})\otimes
+		|\widehat{t-1}\rangle\langle\widehat{t-1}|
+		=(|\widehat{t-1}\rangle-|\widehat{t-3}\rangle)
+		(\langle\widehat{t-1}|-\langle\widehat{t-3}|)$
+\end{itemize}
+
+Now we ensure the 1-qubit gates are applied properly. The naive way would be to set
+	$$H_t=I\otimes|\widehat t\rangle\langle\widehat t|
+		+I\otimes|\widehat{t-1}\rangle\langle\widehat{t-1}|
+		-C_\phi\otimes|\widehat t\rangle\langle\widehat{t-1}|
+		-C_\phi^\dagger\otimes|\widehat{t-1}\rangle\langle\widehat{t}|$$
+	$$H'=\sum_{t\in T_2}H_t$$
+	Equivalently, $H_t=$
+
+	$|00\rangle\langle00|_{f_t,s_t}\otimes
+		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
+		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+
+	$|01\rangle\langle01|_{f_t,s_t}\otimes
+		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
+		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+
+	$|10\rangle\langle10|_{f_t,s_t}\otimes
+		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
+		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+
+	$|11\rangle\langle11|_{f_t,s_t}\otimes
+		(|\widehat{t}\rangle+|\widehat{t-1}\rangle)
+		(\langle\widehat{t}|+\langle\widehat{t-1}|)$
+
+However, this cannot be turned into 2-local, so we change the coefficients and set 
+	$$H_{prop2}=\sum_{t\in T_2}H_{prop2,t}$$
+
+	$H_{prop2,t}=$
+
+	$|00\rangle\langle00|_{f_t,s_t}\otimes
+		4(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
+		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+
+	$|01\rangle\langle01|_{f_t,s_t}\otimes
+		2(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
+		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+
+	$|10\rangle\langle10|_{f_t,s_t}\otimes
+		2(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
+		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+
+	$|11\rangle\langle11|_{f_t,s_t}\otimes
+		(|\widehat{t}\rangle+|\widehat{t-1}\rangle)
+		(\langle\widehat{t}|+\langle\widehat{t-1}|)$
+instead.
+
+Now, if restricted to $S_{prop}$,
+
+	$H_{prop2,t}=H_{qubit,t}+H_{time,t}=$
+	$$(-2|0\rangle\langle0|_{f_t}-2|0\rangle\langle0|_{s_t}
+		+|1\rangle\langle1|_{f_t}+|1\rangle\langle1|_{s_t})\otimes$$
+	$$(|\widehat{t}\rangle\langle\widehat{t-1}|+
+		|\widehat{t-1}\rangle\langle\widehat{t}|)+$$
+	$$(2|0\rangle\langle0|_{f_t}+2|0\rangle\langle0|_{s_t}
+		+|1\rangle\langle1|_{f_t}+|1\rangle\langle1|_{s_t}
+		-2|01\rangle\langle01|_{f_t,s_t}
+		-2|10\rangle\langle10|_{f_t,s_t})\otimes$$
+	$$(|\widehat{t-1}\rangle\langle\widehat{t-1}|+
+		|\widehat{t}\rangle\langle\widehat{t}|)$$
+
+Lastly, we check if the input is right...
+	$$H_{in}=\sum_{i=m+1}^N|1\rangle\langle1|_i\otimes|0\rangle\langle0|$$
+
+Now we use the projection lemma here. This step is different now that $H_{out}$ is gone. I think $J_{in}$ gets dropped or something like that?
 

### 2019-09-02 paper.tex
Write down the steps of the scheme

@@
 
+And then, this in fact involves some probabilistic analysis shenanigans that we haven't fully figured out yet.
+
 \subsection{Getting the Output}
+
+Thanks to having padded the circuit with identity matrices at the end, if we measured $T>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation....
+
+\section{Conclusion}
+
+This is a placeholder. Lorem ipsum...
 

### 2019-09-03 paper.tex
Add placeholder comment on measuring output state

--- 2019-09-02 paper.tex
@@
 
+And then, this in fact involves some probabilistic analysis shenanigans that we haven't fully figured out yet.
+
 \subsection{Getting the Output}
+
+Thanks to having padded the circuit with identity matrices at the end, if we measured $T>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
+Now I would analyze the chances of getting this right, maybe in terms of fidelity or in terms of distance between this measured distribution and the ideal distribution...
+
+\section{Conclusion}
+
+This is a placeholder. Lorem ipsum...
 

### 2019-09-04 paper.tex
Add section 3 on delegation schemes
Add reference by Gheorghiu and Vidick
Add tentative definitions
Definitions of characteristics quantum delegation schemes might have

--- 2019-09-02 paper.tex
@@
 	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.
+
+\section{Quantum Delegation Schemes}
+
+Here we describe schemes that allows a classical client to interact with a quantum server, and various properties that such schemes can have.
+
+\begin{definition}
+	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a possibly malicious BQP prover.
+The BPP verifier has an arbitrary quantum circuit with classical input.
+Its goal is to evaluate the quantum circuit with an honest prover.
+\end{definition}
+
+\begin{definition}
+	A quantum delegation protocol has \emph{long output with error $\epsilon$} if the output can have multiple bits.
+In this case, the verifier should end with a measurement result of the output register.
+Said result's probability distribution would be within $\epsilon$ of the true distribution.
+\end{definition}
+
+\begin{definition}
+	A quantum delegation protocol is \emph{blind} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here.
+\end{definition}
+
+\begin{definition}
+	A quantum delegation protocol is \emph{verifiable} if the verifier can check if the output is correct. TODO need to be more rigorous here.
+\end{definition}
 
@@
 
+	\bibitem{1904.06320}
+	Alexandru Gheorghiu and Thomas Vidick.
+	\newblock Computationally-secure and composable remote state preparation, 2019;
+	\newblock arXiv:1904.06320.
+
 \end{thebibliography}

### 2019-09-04 paper.tex

@@
 
-Thanks to having padded the circuit with identity matrices at the end, if we measured $T>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation....
+Thanks to having padded the circuit with identity matrices at the end, if we measured $T>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
+Now I would analyze the chances of getting this right, maybe in terms of fidelity or in terms of distance between this measured distribution and the ideal distribution...
 

### 2019-09-05 paper.tex
modified a definition
make small change in a definition

@@
 \begin{definition}
-	Let $|\widehat{t}\rangle$ denote $t$ represented in unary. That is, a state of the form $|11\ldots1\rangle |00\ldots0\rangle$; that is, $t$ $1$s followed by all $0$s.
+	Let $|\widehat{t}\rangle=|11\ldots1\rangle |00\ldots0\rangle$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
 \end{definition}
@@
 \begin{definition}
-	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a possibly malicious BQP prover.
-The BPP verifier has an arbitrary quantum circuit with classical input.
-Its goal is to evaluate the quantum circuit with an honest prover.
+	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover.
+The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate with the help of the prover.
 \end{definition}

### 2019-09-05 paper.tex
Start talking about different delegation schemes
Add reference on QFHE
Need to redo this reference to reflect its acceptance to FOCS though
start describing existing schemes

@@
 
+TODO (maybe don't assume universality?)
+
 \begin{definition}
@@
 
-\section{The Scheme}
+In \cite{1804.01082}, a verifiable scheme is proposed.
+In \cite{1708.02130}, a blind scheme is proposed.
+(TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made blind.
+
+TODO check where does \cite{arXiv:1904.06320} fit in.
+
+\section{Long Output scheme}
 
 Here we describe the scheme between the classical client and an honest quantum server.
+We mostly follow the logic in \cite{1804.01082}.
+We first follow \cite{quant-ph/0406180} to reduce the problem to an instance of local Hamiltonian.
 Let $x$ be the client's input, and $U_T...U_1$ be the circuit to evaluate.
@@
 Also need to show that the result of this can still be rewritten into controlled phase gates and one-qubit gates.
-
-\subsection{Reduction to 2-local Hamiltonians}
-
-Then we reduce the circuit to an instance of 2-local Hamiltonian. This reduction is mostly based on \cite{quant-ph/0406180}.
 
@@
 
+	\bibitem{1708.02130}
+	Urmila Mahadev.
+	\newblock Classical Homomorphic Encryption for Quantum Circuits, 2017;
+	\newblock arXiv:1708.02130.
+
 \end{thebibliography}

### 2019-09-07 paper.tex
Add reference and fix a broken reference
write transform to real circuit

@@
 \usepackage{amsmath, amssymb, amsthm}
+\usepackage{braket}
 
@@
 \begin{definition}
-	Denote the \emph{controlled phase gate}: $C_\phi|xy\rangle=(-1)^{xy}|xy\rangle$.
-\end{definition}
-
-\begin{definition}
 	Let $H\big|_S=\prod_SH\prod_S$, where $\prod_S$ is the projection onto the subspace $S$.
@@
 	Let $|\widehat{t}\rangle=|11\ldots1\rangle |00\ldots0\rangle$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
+\end{definition}
+
+\begin{definition}
+	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$. $\Lambda_{f, s}(U)$ would be the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda{1, 2}(X_3)$ would be a Toffoli ((CCNOT) gate.
+\end{definition}
+
+\begin{definition}
+	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$
 \end{definition}
@@
 
-TODO check where does \cite{arXiv:1904.06320} fit in.
+TODO check where does \cite{1904.06320} fit in.
 
@@
 
+We pick our universal gate set to be Hadamard gate and controlled phase gate:
+$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
+$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
+We know this is universal from (TODO cite Kitaev). So each $U_i\in\set{H, \Lambda(P(i))}$
+
 \subsection{Reduction to Real Quantum Computation}
 
-The transform is found in \cite{1109.0795}. It turns the states and the unitary matrices into real numbers.
+Here we first reduce the circuit to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.
 
-TODO: maybe describe the transform here as needed.
-Need to show that this doesn't change X/Z measurements.
-Also need to show that the result of this can still be rewritten into controlled phase gates and one-qubit gates.
+We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re|\psi\rangle+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
+To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th.
+Note that after this transformation, the state is real.
+This transformation preserves measurement results in the standard basis.
+Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates.
+Mathematically,
+$$T\circ H_f=H_f\circ T$$
+$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
 
@@
 
+	\bibitem{quant-ph/0301040}
+	Dorit Aharonov.
+	\newblock A Simple Proof that Toffoli and Hadamard are Quantum Universal, 2003;
+	\newblock arXiv:quant-ph/0301040.
+
 \end{thebibliography}

### 2019-09-07 paper.tex
make editorial change

@@
 We first follow \cite{quant-ph/0406180} to reduce the problem to an instance of local Hamiltonian.
-Let $x$ be the client's input, and $U_T...U_1$ be the circuit to evaluate.
 
-We pick our universal gate set to be Hadamard gate and controlled phase gate:
+We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
 $$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
 $$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-We know this is universal from (TODO cite Kitaev). So each $U_i\in\set{H, \Lambda(P(i))}$
 
@@
 $$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
+We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
+After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.
 
@@
 Let $T_1=[T]\setminus T_2$ be time steps corresponding to 1-qubit gates.
-
-We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
 

### 2019-09-07 paper.tex
Switch to bibtex

@@
 
-\begin{thebibliography}{9}
-	\bibitem{1804.01082}
-	Urmila Mahadev.
-	\newblock Classical Verification of Quantum Computations, 2018;
-	\newblock arXiv:1804.01082.
-
-	\bibitem{quant-ph/0406180}
-	Julia Kempe, Alexei Kitaev and Oded Regev.
-	\newblock The Complexity of the Local Hamiltonian Problem, 2004,
-	\newblock SIAM Journal of Computing, Vol. 35(5), p. 1070-1097 (2006),
-		conference version in Proc. 24th FSTTCS, p. 372-383 (2004);
-	\newblock arXiv:quant-ph/0406180.
-
-	\bibitem{1109.0795}
-	Matthew McKague.
-	\newblock On the power quantum computation over real Hilbert spaces, 2011,
-	\newblock Int. J. Quantum Inform., 11, 1350001 (2013);
-	\newblock arXiv:1109.0795.
-	\newblock DOI: 10.1142/S0219749913500019.
-
-	\bibitem{0704.1287}
-	Jacob D. Biamonte and Peter J. Love.
-	\newblock Realizable Hamiltonians for Universal Adiabatic Quantum Computers, 2007,
-	\newblock Phys. Rev. A 78, 012352 (2008).;
-	\newblock arXiv:0704.1287.
-	\newblock DOI: 10.1103/PhysRevA.78.012352.
-
-	\bibitem{1904.06320}
-	Alexandru Gheorghiu and Thomas Vidick.
-	\newblock Computationally-secure and composable remote state preparation, 2019;
-	\newblock arXiv:1904.06320.
-
-	\bibitem{1708.02130}
-	Urmila Mahadev.
-	\newblock Classical Homomorphic Encryption for Quantum Circuits, 2017;
-	\newblock arXiv:1708.02130.
-
-	\bibitem{quant-ph/0301040}
-	Dorit Aharonov.
-	\newblock A Simple Proof that Toffoli and Hadamard are Quantum Universal, 2003;
-	\newblock arXiv:quant-ph/0301040.
-
-\end{thebibliography}
+\bibliographystyle{plain}
+\bibliography{refs}
 

### 2019-09-07 paper.tex
Fix bibtex references

@@
 
-Here is a lemma that we will use, taken from \cite{quant-ph/0406180}.
+Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.
 
@@
 
-In \cite{1804.01082}, a verifiable scheme is proposed.
-In \cite{1708.02130}, a blind scheme is proposed.
+In \cite{mahadev_delegation}, a verifiable scheme is proposed.
+In \cite{mahadev_qfhe}, a blind scheme is proposed.
 (TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made blind.
@@
 Here we describe the scheme between the classical client and an honest quantum server.
-We mostly follow the logic in \cite{1804.01082}.
-We first follow \cite{quant-ph/0406180} to reduce the problem to an instance of local Hamiltonian.
+We mostly follow the logic in \cite{mahadev_delegation}.
+We first follow \cite{kempe_kitaev_regev_2006} to reduce the problem to an instance of local Hamiltonian.
 
@@
 
-We then follow \cite{0704.1287} in writing each terms of $H$ into only $Z$ and $X$ measurements...
+We then follow \cite{biamonte_love_2008} in writing each terms of $H$ into only $Z$ and $X$ measurements...
 
@@
 
-We then follow \cite{1804.01082}.
+We then follow \cite{mahadev_delegation}.
 That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
-The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{quant-ph/0406180}.
+The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{kempe_kitaev_regev_2006}.
 

### 2019-09-07 paper.tex
Change wordings and use brakets

@@
 \begin{definition}
-	Let $|\widehat{t}\rangle=|11\ldots1\rangle |00\ldots0\rangle$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
+	Let $\ket{\widehat{t}}=\ket{11\ldots1} \ket{00\ldots0}$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
 \end{definition}
@@
 
-\subsection{Reduction to Real Quantum Computation}
+\subsection{preprocess the circuit}
 
@@
 
-We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re|\psi\rangle+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
+We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
 To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th.
@@
 $$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
+
 We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
+This is so that the final output has a higher chance to be measured in the final result in the following reduction.
+
 After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.
 
-\subsection{preprocess the circuit}
+\subsection{Constructing a local Hamiltonian instance}
 
-First, we rewrite the circuit to consist of only controlled phase gates and 1-qubit gates.
-TODO: prove that these 1-qubit gates are all real.
-We ensure that each $C_\phi$s are preceded and followed by two $Z$ gates.
-That is, if the $C_\phi$ acts on the qubits $f_t$ and $s_t$, then the circuit would look like $Z_{f_t}Z_{s_t}C_\phi Z_{s_t}Z_{f_t}$ around each $C_\phi$.
-We then pad the circuit so that the $C_\phi$s are applied at $t\in T_2=\{L, 2L, 3L, \ldots\}$ for some $L\in\mathbb{N}$.
-Let $T_1=[T]\setminus T_2$ be time steps corresponding to 1-qubit gates.
+We then attempt to construct a 2-local Hamiltonian with ground state $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$. We do so by ensuring states perpendicular to it have high eigenvalues.
 
-\subsection{Constructing the 2-local Hamiltonian instance}
-
-We then attempt to construct a 2-local Hamiltonian with ground state $$\phi=\sum_{t=0}^TU_t...U_1|x\rangle\otimes|\hat{t}\rangle$$.
-We do so by causing states perpendicular to this to have high eigenvalues.
-
-First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes |01\rangle\langle01|_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
+First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes \ket{01}\bra{01}_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
 We note that when stricted to $S_{legal}$, 
 \begin{itemize}
-	\item $|10\rangle\langle10|_{t,t+1}
-		=|\widehat{t}\rangle\langle\widehat{t}|$ 
-	\item $|1\rangle\langle0|_{t+1}
-		=|\widehat{t+1}\rangle\langle\widehat{t}|$
-	\item $|11\rangle\langle00|_{t,t+1}
-		=|\widehat{t+2}\rangle\langle\widehat{t}|$
+	\item $\ket{10}\bra{10}_{t,t+1}
+		=\ket{\widehat{t}}\bra{\widehat{t}}$ 
+	\item $\ket{1}\bra{0}_{t+1}
+		=\ket{\widehat{t+1}}\bra{\widehat{t}}$
+	\item $\ket{11}\bra{00}_{t,t+1}
+		=\ket{\widehat{t+2}}\bra{\widehat{t}}$
 \end{itemize}
@@
 	$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
-	$$H_{prop,t}=I\otimes|\widehat{t}\rangle\langle\widehat{t}|
-		+I\otimes|\widehat{t-1}\rangle\langle\widehat{t-1}|
-		-U_t\otimes|\widehat{t}\rangle\langle\widehat{t-1}|
-		-U_t^\dagger\otimes|\widehat{t-1}\rangle\langle\widehat{t}|$$
+	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
+		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+		-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
+		-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
 
@@
 \begin{itemize}
-	\item $|00\rangle_{f_t,s_t}|\xi_{00}\rangle\otimes
-		(|\widehat{t}\rangle+|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)$
-	\item $|01\rangle_{f_t,s_t}|\xi_{01}\rangle\otimes
-		(|\widehat{t}\rangle+|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)$
-	\item $|10\rangle_{f_t,s_t}|\xi_{10}\rangle\otimes
-		(|\widehat{t}\rangle-|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)$
-	\item $|11\rangle_{f_t,s_t}|\xi_{11}\rangle\otimes
-		(|\widehat{t}\rangle-|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)$
+	\item $\ket{00}_{f_t,s_t}\ket{\xi_{00}}\otimes
+		(\ket{\widehat{t}}+\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
+	\item $\ket{01}_{f_t,s_t}\ket{\xi_{01}}\otimes
+		(\ket{\widehat{t}}+\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
+	\item $\ket{10}_{f_t,s_t}\ket{\xi_{10}}\otimes
+		(\ket{\widehat{t}}-\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
+	\item $\ket{11}_{f_t,s_t}\ket{\xi_{11}}\otimes
+		(\ket{\widehat{t}}-\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
 \end{itemize}
@@
 \begin{itemize}
-	\item $|0\rangle\langle0|_{f_t}\otimes
-		|\widehat{t}\rangle\langle\widehat{t}|
-		=(|\widehat{t}\rangle+|\widehat{t+1}\rangle)
-		(\langle\widehat{t}|+\langle\widehat{t+1}|)$
-	\item $|1\rangle\langle1|_{f_t}\otimes
-		|\widehat{t}\rangle\langle\widehat{t}|
-		=(|\widehat{t}\rangle-|\widehat{t+1}\rangle)
-		(\langle\widehat{t}|-\langle\widehat{t+1}|)$
-	\item $|0\rangle\langle0|_{s_t}\otimes
-		|\widehat{t}\rangle\langle\widehat{t}|
-		=(|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)
-		(\langle\widehat{t+1}|+\langle\widehat{t+2}|)$
-	\item $|1\rangle\langle1|_{s_t}\otimes
-		|\widehat{t}\rangle\langle\widehat{t}|
-		=(|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)
-		(\langle\widehat{t+1}|-\langle\widehat{t+2}|)$
-	\item $(|00\rangle\langle00|_{f_t,s_t}
-		+|11\rangle\langle11|_{f_t,s_t})\otimes
-		|\widehat{t}\rangle\langle\widehat{t}|
-		=(|\widehat{t}\rangle+|\widehat{t+2}\rangle)
-		(\langle\widehat{t}|+\langle\widehat{t+2}|)$
-	\item $(|01\rangle\langle01|_{f_t,s_t}
-		+|10\rangle\langle10|_{f_t,s_t})\otimes
-		|\widehat{t}\rangle\langle\widehat{t}|
-		=(|\widehat{t}\rangle-|\widehat{t+2}\rangle)
-		(\langle\widehat{t}|-\langle\widehat{t+2}|)$
+	\item $\ket{0}\bra{0}_{f_t}\otimes
+		\ket{\widehat{t}}\bra{\widehat{t}}
+		=(\ket{\widehat{t}}+\ket{\widehat{t+1}})
+		(\bra{\widehat{t}}+\bra{\widehat{t+1}})$
+	\item $\ket{1}\bra{1}_{f_t}\otimes
+		\ket{\widehat{t}}\bra{\widehat{t}}
+		=(\ket{\widehat{t}}-\ket{\widehat{t+1}})
+		(\bra{\widehat{t}}-\bra{\widehat{t+1}})$
+	\item $\ket{0}\bra{0}_{s_t}\otimes
+		\ket{\widehat{t}}\bra{\widehat{t}}
+		=(\ket{\widehat{t+1}}+\ket{\widehat{t+2}})
+		(\bra{\widehat{t+1}}+\bra{\widehat{t+2}})$
+	\item $\ket{1}\bra{1}_{s_t}\otimes
+		\ket{\widehat{t}}\bra{\widehat{t}}
+		=(\ket{\widehat{t+1}}-\ket{\widehat{t+2}})
+		(\bra{\widehat{t+1}}-\bra{\widehat{t+2}})$
+	\item $(\ket{00}\bra{00}_{f_t,s_t}
+		+\ket{11}\bra{11}_{f_t,s_t})\otimes
+		\ket{\widehat{t}}\bra{\widehat{t}}
+		=(\ket{\widehat{t}}+\ket{\widehat{t+2}})
+		(\bra{\widehat{t}}+\bra{\widehat{t+2}})$
+	\item $(\ket{01}\bra{01}_{f_t,s_t}
+		+\ket{10}\bra{10}_{f_t,s_t})\otimes
+		\ket{\widehat{t}}\bra{\widehat{t}}
+		=(\ket{\widehat{t}}-\ket{\widehat{t+2}})
+		(\bra{\widehat{t}}-\bra{\widehat{t+2}})$
 \end{itemize}
@@
 \begin{itemize}
-	\item $|0\rangle\langle0|_{f_t}\otimes
-		|\widehat{t-1}\rangle\langle\widehat{t-1}|
-		=(|\widehat{t-1}\rangle+|\widehat{t-2}\rangle)
-		(\langle\widehat{t-1}|+\langle\widehat{t-2}|)$
-	\item $|1\rangle\langle1|_{f_t}\otimes
-		|\widehat{t-1}\rangle\langle\widehat{t-1}|
-		=(|\widehat{t-1}\rangle-|\widehat{t-2}\rangle)
-		(\langle\widehat{t-1}|-\langle\widehat{t-2}|)$
-	\item $|0\rangle\langle0|_{s_t}\otimes
-		|\widehat{t-1}\rangle\langle\widehat{t-1}|
-		=(|\widehat{t-2}\rangle+|\widehat{t-3}\rangle)
-		(\langle\widehat{t-2}|+\langle\widehat{t-3}|)$
-	\item $|1\rangle\langle1|_{s_t}\otimes
-		|\widehat{t-1}\rangle\langle\widehat{t-1}|
-		=(|\widehat{t-2}\rangle-|\widehat{t-3}\rangle)
-		(\langle\widehat{t-2}|-\langle\widehat{t-3}|)$
-	\item $(|00\rangle\langle00|_{f_t,s_t}
-		+|11\rangle\langle11|_{f_t,s_t})\otimes
-		|\widehat{t-1}\rangle\langle\widehat{t-1}|
-		=(|\widehat{t-1}\rangle+|\widehat{t-3}\rangle)
-		(\langle\widehat{t-1}|+\langle\widehat{t-3}|)$
-	\item $(|01\rangle\langle01|_{f_t,s_t}
-		+|10\rangle\langle10|_{f_t,s_t})\otimes
-		|\widehat{t-1}\rangle\langle\widehat{t-1}|
-		=(|\widehat{t-1}\rangle-|\widehat{t-3}\rangle)
-		(\langle\widehat{t-1}|-\langle\widehat{t-3}|)$
+	\item $\ket{0}\bra{0}_{f_t}\otimes
+		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+		=(\ket{\widehat{t-1}}+\ket{\widehat{t-2}})
+		(\bra{\widehat{t-1}}+\bra{\widehat{t-2}})$
+	\item $\ket{1}\bra{1}_{f_t}\otimes
+		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+		=(\ket{\widehat{t-1}}-\ket{\widehat{t-2}})
+		(\bra{\widehat{t-1}}-\bra{\widehat{t-2}})$
+	\item $\ket{0}\bra{0}_{s_t}\otimes
+		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+		=(\ket{\widehat{t-2}}+\ket{\widehat{t-3}})
+		(\bra{\widehat{t-2}}+\bra{\widehat{t-3}})$
+	\item $\ket{1}\bra{1}_{s_t}\otimes
+		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+		=(\ket{\widehat{t-2}}-\ket{\widehat{t-3}})
+		(\bra{\widehat{t-2}}-\bra{\widehat{t-3}})$
+	\item $(\ket{00}\bra{00}_{f_t,s_t}
+		+\ket{11}\bra{11}_{f_t,s_t})\otimes
+		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+		=(\ket{\widehat{t-1}}+\ket{\widehat{t-3}})
+		(\bra{\widehat{t-1}}+\bra{\widehat{t-3}})$
+	\item $(\ket{01}\bra{01}_{f_t,s_t}
+		+\ket{10}\bra{10}_{f_t,s_t})\otimes
+		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+		=(\ket{\widehat{t-1}}-\ket{\widehat{t-3}})
+		(\bra{\widehat{t-1}}-\bra{\widehat{t-3}})$
 \end{itemize}
@@
 Now we ensure the 1-qubit gates are applied properly. The naive way would be to set
-	$$H_t=I\otimes|\widehat t\rangle\langle\widehat t|
-		+I\otimes|\widehat{t-1}\rangle\langle\widehat{t-1}|
-		-C_\phi\otimes|\widehat t\rangle\langle\widehat{t-1}|
-		-C_\phi^\dagger\otimes|\widehat{t-1}\rangle\langle\widehat{t}|$$
+	$$H_t=I\otimes\ket{\widehat t}\bra{\widehat t}
+		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+		-C_\phi\otimes\ket{\widehat t}\bra{\widehat{t-1}}
+		-C_\phi^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
 	$$H'=\sum_{t\in T_2}H_t$$
@@
 
-	$|00\rangle\langle00|_{f_t,s_t}\otimes
-		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
-		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+	$\ket{00}\bra{00}_{f_t,s_t}\otimes
+		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
+		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
 
-	$|01\rangle\langle01|_{f_t,s_t}\otimes
-		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
-		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+	$\ket{01}\bra{01}_{f_t,s_t}\otimes
+		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
+		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
 
-	$|10\rangle\langle10|_{f_t,s_t}\otimes
-		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
-		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+	$\ket{10}\bra{10}_{f_t,s_t}\otimes
+		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
+		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
 
-	$|11\rangle\langle11|_{f_t,s_t}\otimes
-		(|\widehat{t}\rangle+|\widehat{t-1}\rangle)
-		(\langle\widehat{t}|+\langle\widehat{t-1}|)$
+	$\ket{11}\bra{11}_{f_t,s_t}\otimes
+		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
+		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
 
@@
 
-	$|00\rangle\langle00|_{f_t,s_t}\otimes
-		4(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
-		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+	$\ket{00}\bra{00}_{f_t,s_t}\otimes
+		4(\ket{\widehat{t}}-\ket{\widehat{t-1}})
+		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
 
-	$|01\rangle\langle01|_{f_t,s_t}\otimes
-		2(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
-		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+	$\ket{01}\bra{01}_{f_t,s_t}\otimes
+		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
+		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
 
-	$|10\rangle\langle10|_{f_t,s_t}\otimes
-		2(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
-		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$
+	$\ket{10}\bra{10}_{f_t,s_t}\otimes
+		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
+		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
 
-	$|11\rangle\langle11|_{f_t,s_t}\otimes
-		(|\widehat{t}\rangle+|\widehat{t-1}\rangle)
-		(\langle\widehat{t}|+\langle\widehat{t-1}|)$
+	$\ket{11}\bra{11}_{f_t,s_t}\otimes
+		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
+		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
 instead.
@@
 	$H_{prop2,t}=H_{qubit,t}+H_{time,t}=$
-	$$(-2|0\rangle\langle0|_{f_t}-2|0\rangle\langle0|_{s_t}
-		+|1\rangle\langle1|_{f_t}+|1\rangle\langle1|_{s_t})\otimes$$
-	$$(|\widehat{t}\rangle\langle\widehat{t-1}|+
-		|\widehat{t-1}\rangle\langle\widehat{t}|)+$$
-	$$(2|0\rangle\langle0|_{f_t}+2|0\rangle\langle0|_{s_t}
-		+|1\rangle\langle1|_{f_t}+|1\rangle\langle1|_{s_t}
-		-2|01\rangle\langle01|_{f_t,s_t}
-		-2|10\rangle\langle10|_{f_t,s_t})\otimes$$
-	$$(|\widehat{t-1}\rangle\langle\widehat{t-1}|+
-		|\widehat{t}\rangle\langle\widehat{t}|)$$
+	$$(-2\ket{0}\bra{0}_{f_t}-2\ket{0}\bra{0}_{s_t}
+		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t})\otimes$$
+	$$(\ket{\widehat{t}}\bra{\widehat{t-1}}+
+		\ket{\widehat{t-1}}\bra{\widehat{t}})+$$
+	$$(2\ket{0}\bra{0}_{f_t}+2\ket{0}\bra{0}_{s_t}
+		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t}
+		-2\ket{01}\bra{01}_{f_t,s_t}
+		-2\ket{10}\bra{10}_{f_t,s_t})\otimes$$
+	$$(\ket{\widehat{t-1}}\bra{\widehat{t-1}}+
+		\ket{\widehat{t}}\bra{\widehat{t}})$$
 
 Lastly, we check if the input is right...
-	$$H_{in}=\sum_{i=m+1}^N|1\rangle\langle1|_i\otimes|0\rangle\langle0|$$
+	$$H_{in}=\sum_{i=m+1}^N\ket{1}\bra{1}_i\otimes\ket{0}\bra{0}$$
 

### 2019-09-07 paper.tex
start local Hamiltonian construction

@@
 
-We then attempt to construct a 2-local Hamiltonian with ground state $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$. We do so by ensuring states perpendicular to it have high eigenvalues.
+We then attempt to construct a 2-local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
+We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biomonte_love_2008}.
 

### 2019-09-07 paper.tex
add reference on universal gate set

@@
 $$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
+This set is proven to be universal in \cite{kitaev_1997}.
 

### 2019-09-07 paper.tex
fix typo
write Hamiltonian clock check

@@
 
-We then attempt to construct a 2-local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
-We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biomonte_love_2008}.
+We then attempt to construct a local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
+We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biamonte_love_2008}.
 
-First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes \ket{01}\bra{01}_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
-We note that when stricted to $S_{legal}$, 
-\begin{itemize}
-	\item $\ket{10}\bra{10}_{t,t+1}
-		=\ket{\widehat{t}}\bra{\widehat{t}}$ 
-	\item $\ket{1}\bra{0}_{t+1}
-		=\ket{\widehat{t+1}}\bra{\widehat{t}}$
-	\item $\ket{11}\bra{00}_{t,t+1}
-		=\ket{\widehat{t+2}}\bra{\widehat{t}}$
-\end{itemize}
+First, we ensure that the invalid clock states have high eigenvalues.
+$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
+We also set $S_{legal}=\ker H_{clock}$.
+Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register.
+Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates.
+$$H_{clock}=\frac{1}{4}((T-1)I + Z_1 - Z_T - \sum_t^{T-1}Z_tZ_{t+1})$$
 

### 2019-09-07 delegations.tex
split sections into separate files

--- 2019-09-07 paper.tex
@@
-\documentclass{article}
-\usepackage{authblk}
-\usepackage{amsmath, amssymb, amsthm}
-\usepackage{braket}
-
-\newtheorem{theorem}{Theorem}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\title{Placeholder Title... Something About Delegating Quantum Computations}
-
-\author[1]{Kai-Min Chung}
-\author[1]{Yi Lee}
-\author[2]{Han-Hsuan Lin}
-\author[3]{Xiaodi Wu}
-\affil[1]{Institute of Information Science, Academia Sinica, Taipei, Taiwan}
-\affil[2]{Department of Computer Science, University of Texas at Austin}
-\affil[3]{
-	Department of Computer Science, Institute for Advanced Computer Studies,
-	and Joint Center for Quantum Information and Computer Science,
-	University of Maryland, USA
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-
-This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
-
-\end{abstract}
-
-\section{Introduction}
-
-Below is some intro of it copied from my SoP.
-This is unpolished and mostly a placeholder at the moment though.
-
-It was proven that BQP=BQIP.
-That is, if a quantum computer can efficiently solve a given decision problem, then it can also efficiently convince a classical machine of its solution.
-I'm generalizing this to arbitrary efficient quantum computations.
-The proof for decision problems involves the classical verifier reducing the problem to a local Hamiltonian instance; the quantum prover would then commit its certificate and act as the verifier’s trusted measurement device as put forth in "Classical Verification of Quantum Computations" by Mahadev.
-It isn't as trivial as it may seem.
-Repeating the scheme for each qubit loses the information carried by entanglements and throws off the joint distribution between qubits.
-Simply measuring the entire output register instead is difficult to analyze.
-For decision problems, it’s not hard to argue that a malicious prover cannot do better than sending identical copies of some pure state unentangled with each others.
-That same reasoning doesn't apply here a priori.
-I've been trying to get a grasp on the particular structure of the local Hamiltonian reduction in order to better analyze it.
-
-\section{Preliminaries}
-
-\subsection{Notations}
-
-Let $\mathcal{B}$ denote the Hilbert space corresponding to a qubit.
-Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian.
-
-\begin{definition}
-	Let $H\geq0$ denote $H$ is positive semidefinite.
-\end{definition}
-
-\begin{definition}
-	Let $\lambda(H)$ as the least eigenvalue of $H$.
-\end{definition}
-
-\begin{definition}
-	Let the \emph{ground state} of $H$ be the eigenvector corresponding to $\lambda(H)$.
-\end{definition}
-
-\begin{definition}
-	Let $H\big|_S=\prod_SH\prod_S$, where $\prod_S$ is the projection onto the subspace $S$.
-\end{definition}
-
-\begin{definition}
-	Let $\ket{\widehat{t}}=\ket{11\ldots1} \ket{00\ldots0}$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
-\end{definition}
-
-\begin{definition}
-	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$. $\Lambda_{f, s}(U)$ would be the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda{1, 2}(X_3)$ would be a Toffoli ((CCNOT) gate.
-\end{definition}
-
-\begin{definition}
-	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$
-\end{definition}
-
-\subsection{Local Hamiltonian}
-
-The local Hamiltonian problem is defined as follows:
-
-\begin{definition}
-	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian. Then $$H=\sum_{j=1}^nH_j$$ is called a \emph{Hamiltonian}.
-	If each $H_j$ acts on at most $k$ qubits, then $H$ is called a \emph{$k$-local Hamiltonian}.
-\end{definition}
-
-The local Hamiltonian problem is given by let $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, determine whether $\lambda(H)<a$ or $\lambda(H)>b$..
-
-\begin{theorem}
-	The Local Hamiltonian problem is QMA-complete.
-\end{theorem}
-
-\subsection{Projection Lemma}
-
-Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.
-
-Let $H_1, H_2$ be Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
-Then $\exists J\in\mathbb{R}$ s.t.
-$\lambda(H_1\big|_S)-\frac{1}{8}\leq
-	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.
-
 \section{Quantum Delegation Schemes}
@@
 TODO check where does \cite{1904.06320} fit in.
-
-\section{Long Output scheme}
-
-Here we describe the scheme between the classical client and an honest quantum server.
-We mostly follow the logic in \cite{mahadev_delegation}.
-We first follow \cite{kempe_kitaev_regev_2006} to reduce the problem to an instance of local Hamiltonian.
-
-We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
-$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
-$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-
-\subsection{preprocess the circuit}
-
-Here we first reduce the circuit to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.
-
-We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
-To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th.
-Note that after this transformation, the state is real.
-This transformation preserves measurement results in the standard basis.
-Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates.
-Mathematically,
-$$T\circ H_f=H_f\circ T$$
-$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
-
-We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
-This is so that the final output has a higher chance to be measured in the final result in the following reduction.
-
-After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.
-
-\subsection{Constructing a local Hamiltonian instance}
-
-We then attempt to construct a 2-local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
-We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biomonte_love_2008}.
-
-First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes \ket{01}\bra{01}_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
-We note that when stricted to $S_{legal}$, 
-\begin{itemize}
-	\item $\ket{10}\bra{10}_{t,t+1}
-		=\ket{\widehat{t}}\bra{\widehat{t}}$ 
-	\item $\ket{1}\bra{0}_{t+1}
-		=\ket{\widehat{t+1}}\bra{\widehat{t}}$
-	\item $\ket{11}\bra{00}_{t,t+1}
-		=\ket{\widehat{t+2}}\bra{\widehat{t}}$
-\end{itemize}
-
-Then, we ensure that 1-qubit gates are propagated properly. To do so, we set
-	$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
-	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
-		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
-		-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-
-I probably need to explain why this works but I'll leave it for another day.
-
-Let $S_{prop1}=\ker H_{prop1}$.
-Then, $S_{prop1}$ has the following as basis:
-\begin{itemize}
-	\item $\ket{00}_{f_t,s_t}\ket{\xi_{00}}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
-	\item $\ket{01}_{f_t,s_t}\ket{\xi_{01}}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
-	\item $\ket{10}_{f_t,s_t}\ket{\xi_{10}}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
-	\item $\ket{11}_{f_t,s_t}\ket{\xi_{11}}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
-\end{itemize}
-
-Also, if $t\in T_2$, that is, $t$ corresponds to a time step where $C_\phi$ is applied, then the following are true due to $C_\phi$ being surrounded by $Z$ gates:
-\begin{itemize}
-	\item $\ket{0}\bra{0}_{f_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}+\ket{\widehat{t+1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t+1}})$
-	\item $\ket{1}\bra{1}_{f_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}-\ket{\widehat{t+1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t+1}})$
-	\item $\ket{0}\bra{0}_{s_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t+1}}+\ket{\widehat{t+2}})
-		(\bra{\widehat{t+1}}+\bra{\widehat{t+2}})$
-	\item $\ket{1}\bra{1}_{s_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t+1}}-\ket{\widehat{t+2}})
-		(\bra{\widehat{t+1}}-\bra{\widehat{t+2}})$
-	\item $(\ket{00}\bra{00}_{f_t,s_t}
-		+\ket{11}\bra{11}_{f_t,s_t})\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}+\ket{\widehat{t+2}})
-		(\bra{\widehat{t}}+\bra{\widehat{t+2}})$
-	\item $(\ket{01}\bra{01}_{f_t,s_t}
-		+\ket{10}\bra{10}_{f_t,s_t})\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}-\ket{\widehat{t+2}})
-		(\bra{\widehat{t}}-\bra{\widehat{t+2}})$
-\end{itemize}
-
-Similarly,
-\begin{itemize}
-	\item $\ket{0}\bra{0}_{f_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}+\ket{\widehat{t-2}})
-		(\bra{\widehat{t-1}}+\bra{\widehat{t-2}})$
-	\item $\ket{1}\bra{1}_{f_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}-\ket{\widehat{t-2}})
-		(\bra{\widehat{t-1}}-\bra{\widehat{t-2}})$
-	\item $\ket{0}\bra{0}_{s_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-2}}+\ket{\widehat{t-3}})
-		(\bra{\widehat{t-2}}+\bra{\widehat{t-3}})$
-	\item $\ket{1}\bra{1}_{s_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-2}}-\ket{\widehat{t-3}})
-		(\bra{\widehat{t-2}}-\bra{\widehat{t-3}})$
-	\item $(\ket{00}\bra{00}_{f_t,s_t}
-		+\ket{11}\bra{11}_{f_t,s_t})\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}+\ket{\widehat{t-3}})
-		(\bra{\widehat{t-1}}+\bra{\widehat{t-3}})$
-	\item $(\ket{01}\bra{01}_{f_t,s_t}
-		+\ket{10}\bra{10}_{f_t,s_t})\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}-\ket{\widehat{t-3}})
-		(\bra{\widehat{t-1}}-\bra{\widehat{t-3}})$
-\end{itemize}
-
-Now we ensure the 1-qubit gates are applied properly. The naive way would be to set
-	$$H_t=I\otimes\ket{\widehat t}\bra{\widehat t}
-		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		-C_\phi\otimes\ket{\widehat t}\bra{\widehat{t-1}}
-		-C_\phi^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-	$$H'=\sum_{t\in T_2}H_t$$
-	Equivalently, $H_t=$
-
-	$\ket{00}\bra{00}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{01}\bra{01}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{10}\bra{10}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{11}\bra{11}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
-
-However, this cannot be turned into 2-local, so we change the coefficients and set 
-	$$H_{prop2}=\sum_{t\in T_2}H_{prop2,t}$$
-
-	$H_{prop2,t}=$
-
-	$\ket{00}\bra{00}_{f_t,s_t}\otimes
-		4(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{01}\bra{01}_{f_t,s_t}\otimes
-		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{10}\bra{10}_{f_t,s_t}\otimes
-		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{11}\bra{11}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
-instead.
-
-Now, if restricted to $S_{prop}$,
-
-	$H_{prop2,t}=H_{qubit,t}+H_{time,t}=$
-	$$(-2\ket{0}\bra{0}_{f_t}-2\ket{0}\bra{0}_{s_t}
-		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t})\otimes$$
-	$$(\ket{\widehat{t}}\bra{\widehat{t-1}}+
-		\ket{\widehat{t-1}}\bra{\widehat{t}})+$$
-	$$(2\ket{0}\bra{0}_{f_t}+2\ket{0}\bra{0}_{s_t}
-		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t}
-		-2\ket{01}\bra{01}_{f_t,s_t}
-		-2\ket{10}\bra{10}_{f_t,s_t})\otimes$$
-	$$(\ket{\widehat{t-1}}\bra{\widehat{t-1}}+
-		\ket{\widehat{t}}\bra{\widehat{t}})$$
-
-Lastly, we check if the input is right...
-	$$H_{in}=\sum_{i=m+1}^N\ket{1}\bra{1}_i\otimes\ket{0}\bra{0}$$
-
-Now we use the projection lemma here. This step is different now that $H_{out}$ is gone. I think $J_{in}$ gets dropped or something like that?
-
-\subsection{2-local ZX Hamiltonians}
-
-We then follow \cite{biamonte_love_2008} in writing each terms of $H$ into only $Z$ and $X$ measurements...
-
-This probably involves some kind of basis arguments on the Hamiltonians and maybe some stuff that's a bit more ugly. This should not change the state. I'll have to write this out later...
-
-\subsection{Checking computation}
-
-We then follow \cite{mahadev_delegation}.
-That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
-The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{kempe_kitaev_regev_2006}.
-
-And then, this in fact involves some probabilistic analysis shenanigans that we haven't fully figured out yet.
-
-\subsection{Getting the Output}
-
-Thanks to having padded the circuit with identity matrices at the end, if we measured $T>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
-Now I would analyze the chances of getting this right, maybe in terms of fidelity or in terms of distance between this measured distribution and the ideal distribution...
-
-\section{Conclusion}
-
-This is a placeholder. Lorem ipsum...
-
-\bibliographystyle{plain}
-\bibliography{refs}
-
-\end{document}

### 2019-09-07 introduction.tex
split sections into separate files

--- 2019-09-07 paper.tex
@@
-\documentclass{article}
-\usepackage{authblk}
-\usepackage{amsmath, amssymb, amsthm}
-\usepackage{braket}
-
-\newtheorem{theorem}{Theorem}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\title{Placeholder Title... Something About Delegating Quantum Computations}
-
-\author[1]{Kai-Min Chung}
-\author[1]{Yi Lee}
-\author[2]{Han-Hsuan Lin}
-\author[3]{Xiaodi Wu}
-\affil[1]{Institute of Information Science, Academia Sinica, Taipei, Taiwan}
-\affil[2]{Department of Computer Science, University of Texas at Austin}
-\affil[3]{
-	Department of Computer Science, Institute for Advanced Computer Studies,
-	and Joint Center for Quantum Information and Computer Science,
-	University of Maryland, USA
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-
-This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
-
-\end{abstract}
-
 \section{Introduction}
@@
 I've been trying to get a grasp on the particular structure of the local Hamiltonian reduction in order to better analyze it.
-
-\section{Preliminaries}
-
-\subsection{Notations}
-
-Let $\mathcal{B}$ denote the Hilbert space corresponding to a qubit.
-Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian.
-
-\begin{definition}
-	Let $H\geq0$ denote $H$ is positive semidefinite.
-\end{definition}
-
-\begin{definition}
-	Let $\lambda(H)$ as the least eigenvalue of $H$.
-\end{definition}
-
-\begin{definition}
-	Let the \emph{ground state} of $H$ be the eigenvector corresponding to $\lambda(H)$.
-\end{definition}
-
-\begin{definition}
-	Let $H\big|_S=\prod_SH\prod_S$, where $\prod_S$ is the projection onto the subspace $S$.
-\end{definition}
-
-\begin{definition}
-	Let $\ket{\widehat{t}}=\ket{11\ldots1} \ket{00\ldots0}$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
-\end{definition}
-
-\begin{definition}
-	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$. $\Lambda_{f, s}(U)$ would be the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda{1, 2}(X_3)$ would be a Toffoli ((CCNOT) gate.
-\end{definition}
-
-\begin{definition}
-	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$
-\end{definition}
-
-\subsection{Local Hamiltonian}
-
-The local Hamiltonian problem is defined as follows:
-
-\begin{definition}
-	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian. Then $$H=\sum_{j=1}^nH_j$$ is called a \emph{Hamiltonian}.
-	If each $H_j$ acts on at most $k$ qubits, then $H$ is called a \emph{$k$-local Hamiltonian}.
-\end{definition}
-
-The local Hamiltonian problem is given by let $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, determine whether $\lambda(H)<a$ or $\lambda(H)>b$..
-
-\begin{theorem}
-	The Local Hamiltonian problem is QMA-complete.
-\end{theorem}
-
-\subsection{Projection Lemma}
-
-Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.
-
-Let $H_1, H_2$ be Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
-Then $\exists J\in\mathbb{R}$ s.t.
-$\lambda(H_1\big|_S)-\frac{1}{8}\leq
-	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.
-
-\section{Quantum Delegation Schemes}
-
-Here we describe schemes that allows a classical client to interact with a quantum server, and various properties that such schemes can have.
-
-\begin{definition}
-	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover.
-The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate with the help of the prover.
-\end{definition}
-
-TODO (maybe don't assume universality?)
-
-\begin{definition}
-	A quantum delegation protocol has \emph{long output with error $\epsilon$} if the output can have multiple bits.
-In this case, the verifier should end with a measurement result of the output register.
-Said result's probability distribution would be within $\epsilon$ of the true distribution.
-\end{definition}
-
-\begin{definition}
-	A quantum delegation protocol is \emph{blind} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here.
-\end{definition}
-
-\begin{definition}
-	A quantum delegation protocol is \emph{verifiable} if the verifier can check if the output is correct. TODO need to be more rigorous here.
-\end{definition}
-
-In \cite{mahadev_delegation}, a verifiable scheme is proposed.
-In \cite{mahadev_qfhe}, a blind scheme is proposed.
-(TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made blind.
-
-TODO check where does \cite{1904.06320} fit in.
-
-\section{Long Output scheme}
-
-Here we describe the scheme between the classical client and an honest quantum server.
-We mostly follow the logic in \cite{mahadev_delegation}.
-We first follow \cite{kempe_kitaev_regev_2006} to reduce the problem to an instance of local Hamiltonian.
-
-We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
-$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
-$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-
-\subsection{preprocess the circuit}
-
-Here we first reduce the circuit to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.
-
-We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
-To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th.
-Note that after this transformation, the state is real.
-This transformation preserves measurement results in the standard basis.
-Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates.
-Mathematically,
-$$T\circ H_f=H_f\circ T$$
-$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
-
-We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
-This is so that the final output has a higher chance to be measured in the final result in the following reduction.
-
-After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.
-
-\subsection{Constructing a local Hamiltonian instance}
-
-We then attempt to construct a 2-local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
-We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biomonte_love_2008}.
-
-First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes \ket{01}\bra{01}_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
-We note that when stricted to $S_{legal}$, 
-\begin{itemize}
-	\item $\ket{10}\bra{10}_{t,t+1}
-		=\ket{\widehat{t}}\bra{\widehat{t}}$ 
-	\item $\ket{1}\bra{0}_{t+1}
-		=\ket{\widehat{t+1}}\bra{\widehat{t}}$
-	\item $\ket{11}\bra{00}_{t,t+1}
-		=\ket{\widehat{t+2}}\bra{\widehat{t}}$
-\end{itemize}
-
-Then, we ensure that 1-qubit gates are propagated properly. To do so, we set
-	$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
-	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
-		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
-		-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-
-I probably need to explain why this works but I'll leave it for another day.
-
-Let $S_{prop1}=\ker H_{prop1}$.
-Then, $S_{prop1}$ has the following as basis:
-\begin{itemize}
-	\item $\ket{00}_{f_t,s_t}\ket{\xi_{00}}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
-	\item $\ket{01}_{f_t,s_t}\ket{\xi_{01}}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
-	\item $\ket{10}_{f_t,s_t}\ket{\xi_{10}}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
-	\item $\ket{11}_{f_t,s_t}\ket{\xi_{11}}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
-\end{itemize}
-
-Also, if $t\in T_2$, that is, $t$ corresponds to a time step where $C_\phi$ is applied, then the following are true due to $C_\phi$ being surrounded by $Z$ gates:
-\begin{itemize}
-	\item $\ket{0}\bra{0}_{f_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}+\ket{\widehat{t+1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t+1}})$
-	\item $\ket{1}\bra{1}_{f_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}-\ket{\widehat{t+1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t+1}})$
-	\item $\ket{0}\bra{0}_{s_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t+1}}+\ket{\widehat{t+2}})
-		(\bra{\widehat{t+1}}+\bra{\widehat{t+2}})$
-	\item $\ket{1}\bra{1}_{s_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t+1}}-\ket{\widehat{t+2}})
-		(\bra{\widehat{t+1}}-\bra{\widehat{t+2}})$
-	\item $(\ket{00}\bra{00}_{f_t,s_t}
-		+\ket{11}\bra{11}_{f_t,s_t})\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}+\ket{\widehat{t+2}})
-		(\bra{\widehat{t}}+\bra{\widehat{t+2}})$
-	\item $(\ket{01}\bra{01}_{f_t,s_t}
-		+\ket{10}\bra{10}_{f_t,s_t})\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}-\ket{\widehat{t+2}})
-		(\bra{\widehat{t}}-\bra{\widehat{t+2}})$
-\end{itemize}
-
-Similarly,
-\begin{itemize}
-	\item $\ket{0}\bra{0}_{f_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}+\ket{\widehat{t-2}})
-		(\bra{\widehat{t-1}}+\bra{\widehat{t-2}})$
-	\item $\ket{1}\bra{1}_{f_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}-\ket{\widehat{t-2}})
-		(\bra{\widehat{t-1}}-\bra{\widehat{t-2}})$
-	\item $\ket{0}\bra{0}_{s_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-2}}+\ket{\widehat{t-3}})
-		(\bra{\widehat{t-2}}+\bra{\widehat{t-3}})$
-	\item $\ket{1}\bra{1}_{s_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-2}}-\ket{\widehat{t-3}})
-		(\bra{\widehat{t-2}}-\bra{\widehat{t-3}})$
-	\item $(\ket{00}\bra{00}_{f_t,s_t}
-		+\ket{11}\bra{11}_{f_t,s_t})\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}+\ket{\widehat{t-3}})
-		(\bra{\widehat{t-1}}+\bra{\widehat{t-3}})$
-	\item $(\ket{01}\bra{01}_{f_t,s_t}
-		+\ket{10}\bra{10}_{f_t,s_t})\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}-\ket{\widehat{t-3}})
-		(\bra{\widehat{t-1}}-\bra{\widehat{t-3}})$
-\end{itemize}
-
-Now we ensure the 1-qubit gates are applied properly. The naive way would be to set
-	$$H_t=I\otimes\ket{\widehat t}\bra{\widehat t}
-		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		-C_\phi\otimes\ket{\widehat t}\bra{\widehat{t-1}}
-		-C_\phi^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-	$$H'=\sum_{t\in T_2}H_t$$
-	Equivalently, $H_t=$
-
-	$\ket{00}\bra{00}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{01}\bra{01}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{10}\bra{10}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{11}\bra{11}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
-
-However, this cannot be turned into 2-local, so we change the coefficients and set 
-	$$H_{prop2}=\sum_{t\in T_2}H_{prop2,t}$$
-
-	$H_{prop2,t}=$
-
-	$\ket{00}\bra{00}_{f_t,s_t}\otimes
-		4(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{01}\bra{01}_{f_t,s_t}\otimes
-		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{10}\bra{10}_{f_t,s_t}\otimes
-		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{11}\bra{11}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
-instead.
-
-Now, if restricted to $S_{prop}$,
-
-	$H_{prop2,t}=H_{qubit,t}+H_{time,t}=$
-	$$(-2\ket{0}\bra{0}_{f_t}-2\ket{0}\bra{0}_{s_t}
-		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t})\otimes$$
-	$$(\ket{\widehat{t}}\bra{\widehat{t-1}}+
-		\ket{\widehat{t-1}}\bra{\widehat{t}})+$$
-	$$(2\ket{0}\bra{0}_{f_t}+2\ket{0}\bra{0}_{s_t}
-		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t}
-		-2\ket{01}\bra{01}_{f_t,s_t}
-		-2\ket{10}\bra{10}_{f_t,s_t})\otimes$$
-	$$(\ket{\widehat{t-1}}\bra{\widehat{t-1}}+
-		\ket{\widehat{t}}\bra{\widehat{t}})$$
-
-Lastly, we check if the input is right...
-	$$H_{in}=\sum_{i=m+1}^N\ket{1}\bra{1}_i\otimes\ket{0}\bra{0}$$
-
-Now we use the projection lemma here. This step is different now that $H_{out}$ is gone. I think $J_{in}$ gets dropped or something like that?
-
-\subsection{2-local ZX Hamiltonians}
-
-We then follow \cite{biamonte_love_2008} in writing each terms of $H$ into only $Z$ and $X$ measurements...
-
-This probably involves some kind of basis arguments on the Hamiltonians and maybe some stuff that's a bit more ugly. This should not change the state. I'll have to write this out later...
-
-\subsection{Checking computation}
-
-We then follow \cite{mahadev_delegation}.
-That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
-The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{kempe_kitaev_regev_2006}.
-
-And then, this in fact involves some probabilistic analysis shenanigans that we haven't fully figured out yet.
-
-\subsection{Getting the Output}
-
-Thanks to having padded the circuit with identity matrices at the end, if we measured $T>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
-Now I would analyze the chances of getting this right, maybe in terms of fidelity or in terms of distance between this measured distribution and the ideal distribution...
-
-\section{Conclusion}
-
-This is a placeholder. Lorem ipsum...
-
-\bibliographystyle{plain}
-\bibliography{refs}
-
-\end{document}

### 2019-09-07 longoutput.tex
split sections into separate files

--- 2019-09-07 paper.tex
@@
-\documentclass{article}
-\usepackage{authblk}
-\usepackage{amsmath, amssymb, amsthm}
-\usepackage{braket}
-
-\newtheorem{theorem}{Theorem}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\title{Placeholder Title... Something About Delegating Quantum Computations}
-
-\author[1]{Kai-Min Chung}
-\author[1]{Yi Lee}
-\author[2]{Han-Hsuan Lin}
-\author[3]{Xiaodi Wu}
-\affil[1]{Institute of Information Science, Academia Sinica, Taipei, Taiwan}
-\affil[2]{Department of Computer Science, University of Texas at Austin}
-\affil[3]{
-	Department of Computer Science, Institute for Advanced Computer Studies,
-	and Joint Center for Quantum Information and Computer Science,
-	University of Maryland, USA
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-
-This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
-
-\end{abstract}
-
-\section{Introduction}
-
-Below is some intro of it copied from my SoP.
-This is unpolished and mostly a placeholder at the moment though.
-
-It was proven that BQP=BQIP.
-That is, if a quantum computer can efficiently solve a given decision problem, then it can also efficiently convince a classical machine of its solution.
-I'm generalizing this to arbitrary efficient quantum computations.
-The proof for decision problems involves the classical verifier reducing the problem to a local Hamiltonian instance; the quantum prover would then commit its certificate and act as the verifier’s trusted measurement device as put forth in "Classical Verification of Quantum Computations" by Mahadev.
-It isn't as trivial as it may seem.
-Repeating the scheme for each qubit loses the information carried by entanglements and throws off the joint distribution between qubits.
-Simply measuring the entire output register instead is difficult to analyze.
-For decision problems, it’s not hard to argue that a malicious prover cannot do better than sending identical copies of some pure state unentangled with each others.
-That same reasoning doesn't apply here a priori.
-I've been trying to get a grasp on the particular structure of the local Hamiltonian reduction in order to better analyze it.
-
-\section{Preliminaries}
-
-\subsection{Notations}
-
-Let $\mathcal{B}$ denote the Hilbert space corresponding to a qubit.
-Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian.
-
-\begin{definition}
-	Let $H\geq0$ denote $H$ is positive semidefinite.
-\end{definition}
-
-\begin{definition}
-	Let $\lambda(H)$ as the least eigenvalue of $H$.
-\end{definition}
-
-\begin{definition}
-	Let the \emph{ground state} of $H$ be the eigenvector corresponding to $\lambda(H)$.
-\end{definition}
-
-\begin{definition}
-	Let $H\big|_S=\prod_SH\prod_S$, where $\prod_S$ is the projection onto the subspace $S$.
-\end{definition}
-
-\begin{definition}
-	Let $\ket{\widehat{t}}=\ket{11\ldots1} \ket{00\ldots0}$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
-\end{definition}
-
-\begin{definition}
-	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$. $\Lambda_{f, s}(U)$ would be the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda{1, 2}(X_3)$ would be a Toffoli ((CCNOT) gate.
-\end{definition}
-
-\begin{definition}
-	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$
-\end{definition}
-
-\subsection{Local Hamiltonian}
-
-The local Hamiltonian problem is defined as follows:
-
-\begin{definition}
-	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian. Then $$H=\sum_{j=1}^nH_j$$ is called a \emph{Hamiltonian}.
-	If each $H_j$ acts on at most $k$ qubits, then $H$ is called a \emph{$k$-local Hamiltonian}.
-\end{definition}
-
-The local Hamiltonian problem is given by let $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, determine whether $\lambda(H)<a$ or $\lambda(H)>b$..
-
-\begin{theorem}
-	The Local Hamiltonian problem is QMA-complete.
-\end{theorem}
-
-\subsection{Projection Lemma}
-
-Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.
-
-Let $H_1, H_2$ be Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
-Then $\exists J\in\mathbb{R}$ s.t.
-$\lambda(H_1\big|_S)-\frac{1}{8}\leq
-	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.
-
-\section{Quantum Delegation Schemes}
-
-Here we describe schemes that allows a classical client to interact with a quantum server, and various properties that such schemes can have.
-
-\begin{definition}
-	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover.
-The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate with the help of the prover.
-\end{definition}
-
-TODO (maybe don't assume universality?)
-
-\begin{definition}
-	A quantum delegation protocol has \emph{long output with error $\epsilon$} if the output can have multiple bits.
-In this case, the verifier should end with a measurement result of the output register.
-Said result's probability distribution would be within $\epsilon$ of the true distribution.
-\end{definition}
-
-\begin{definition}
-	A quantum delegation protocol is \emph{blind} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here.
-\end{definition}
-
-\begin{definition}
-	A quantum delegation protocol is \emph{verifiable} if the verifier can check if the output is correct. TODO need to be more rigorous here.
-\end{definition}
-
-In \cite{mahadev_delegation}, a verifiable scheme is proposed.
-In \cite{mahadev_qfhe}, a blind scheme is proposed.
-(TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made blind.
-
-TODO check where does \cite{1904.06320} fit in.
-
 \section{Long Output scheme}
@@
 Now I would analyze the chances of getting this right, maybe in terms of fidelity or in terms of distance between this measured distribution and the ideal distribution...
-
-\section{Conclusion}
-
-This is a placeholder. Lorem ipsum...
-
-\bibliographystyle{plain}
-\bibliography{refs}
-
-\end{document}

### 2019-09-07 paper.tex
split sections into separate files

--- 2019-09-07 paper.tex
@@
 
-\section{Introduction}
+\input{introduction}
 
-Below is some intro of it copied from my SoP.
-This is unpolished and mostly a placeholder at the moment though.
+\input{preliminaries}
 
-It was proven that BQP=BQIP.
-That is, if a quantum computer can efficiently solve a given decision problem, then it can also efficiently convince a classical machine of its solution.
-I'm generalizing this to arbitrary efficient quantum computations.
-The proof for decision problems involves the classical verifier reducing the problem to a local Hamiltonian instance; the quantum prover would then commit its certificate and act as the verifier’s trusted measurement device as put forth in "Classical Verification of Quantum Computations" by Mahadev.
-It isn't as trivial as it may seem.
-Repeating the scheme for each qubit loses the information carried by entanglements and throws off the joint distribution between qubits.
-Simply measuring the entire output register instead is difficult to analyze.
-For decision problems, it’s not hard to argue that a malicious prover cannot do better than sending identical copies of some pure state unentangled with each others.
-That same reasoning doesn't apply here a priori.
-I've been trying to get a grasp on the particular structure of the local Hamiltonian reduction in order to better analyze it.
+\input{delegations}
 
-\section{Preliminaries}
+\input{longoutput}
 
-\subsection{Notations}
-
-Let $\mathcal{B}$ denote the Hilbert space corresponding to a qubit.
-Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian.
-
-\begin{definition}
-	Let $H\geq0$ denote $H$ is positive semidefinite.
-\end{definition}
-
-\begin{definition}
-	Let $\lambda(H)$ as the least eigenvalue of $H$.
-\end{definition}
-
-\begin{definition}
-	Let the \emph{ground state} of $H$ be the eigenvector corresponding to $\lambda(H)$.
-\end{definition}
-
-\begin{definition}
-	Let $H\big|_S=\prod_SH\prod_S$, where $\prod_S$ is the projection onto the subspace $S$.
-\end{definition}
-
-\begin{definition}
-	Let $\ket{\widehat{t}}=\ket{11\ldots1} \ket{00\ldots0}$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
-\end{definition}
-
-\begin{definition}
-	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$. $\Lambda_{f, s}(U)$ would be the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda{1, 2}(X_3)$ would be a Toffoli ((CCNOT) gate.
-\end{definition}
-
-\begin{definition}
-	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$
-\end{definition}
-
-\subsection{Local Hamiltonian}
-
-The local Hamiltonian problem is defined as follows:
-
-\begin{definition}
-	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian. Then $$H=\sum_{j=1}^nH_j$$ is called a \emph{Hamiltonian}.
-	If each $H_j$ acts on at most $k$ qubits, then $H$ is called a \emph{$k$-local Hamiltonian}.
-\end{definition}
-
-The local Hamiltonian problem is given by let $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, determine whether $\lambda(H)<a$ or $\lambda(H)>b$..
-
-\begin{theorem}
-	The Local Hamiltonian problem is QMA-complete.
-\end{theorem}
-
-\subsection{Projection Lemma}
-
-Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.
-
-Let $H_1, H_2$ be Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
-Then $\exists J\in\mathbb{R}$ s.t.
-$\lambda(H_1\big|_S)-\frac{1}{8}\leq
-	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.
-
-\section{Quantum Delegation Schemes}
-
-Here we describe schemes that allows a classical client to interact with a quantum server, and various properties that such schemes can have.
-
-\begin{definition}
-	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover.
-The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate with the help of the prover.
-\end{definition}
-
-TODO (maybe don't assume universality?)
-
-\begin{definition}
-	A quantum delegation protocol has \emph{long output with error $\epsilon$} if the output can have multiple bits.
-In this case, the verifier should end with a measurement result of the output register.
-Said result's probability distribution would be within $\epsilon$ of the true distribution.
-\end{definition}
-
-\begin{definition}
-	A quantum delegation protocol is \emph{blind} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here.
-\end{definition}
-
-\begin{definition}
-	A quantum delegation protocol is \emph{verifiable} if the verifier can check if the output is correct. TODO need to be more rigorous here.
-\end{definition}
-
-In \cite{mahadev_delegation}, a verifiable scheme is proposed.
-In \cite{mahadev_qfhe}, a blind scheme is proposed.
-(TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made blind.
-
-TODO check where does \cite{1904.06320} fit in.
-
-\section{Long Output scheme}
-
-Here we describe the scheme between the classical client and an honest quantum server.
-We mostly follow the logic in \cite{mahadev_delegation}.
-We first follow \cite{kempe_kitaev_regev_2006} to reduce the problem to an instance of local Hamiltonian.
-
-We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
-$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
-$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-
-\subsection{preprocess the circuit}
-
-Here we first reduce the circuit to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.
-
-We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
-To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th.
-Note that after this transformation, the state is real.
-This transformation preserves measurement results in the standard basis.
-Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates.
-Mathematically,
-$$T\circ H_f=H_f\circ T$$
-$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
-
-We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
-This is so that the final output has a higher chance to be measured in the final result in the following reduction.
-
-After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.
-
-\subsection{Constructing a local Hamiltonian instance}
-
-We then attempt to construct a 2-local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
-We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biomonte_love_2008}.
-
-First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes \ket{01}\bra{01}_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
-We note that when stricted to $S_{legal}$, 
-\begin{itemize}
-	\item $\ket{10}\bra{10}_{t,t+1}
-		=\ket{\widehat{t}}\bra{\widehat{t}}$ 
-	\item $\ket{1}\bra{0}_{t+1}
-		=\ket{\widehat{t+1}}\bra{\widehat{t}}$
-	\item $\ket{11}\bra{00}_{t,t+1}
-		=\ket{\widehat{t+2}}\bra{\widehat{t}}$
-\end{itemize}
-
-Then, we ensure that 1-qubit gates are propagated properly. To do so, we set
-	$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
-	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
-		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
-		-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-
-I probably need to explain why this works but I'll leave it for another day.
-
-Let $S_{prop1}=\ker H_{prop1}$.
-Then, $S_{prop1}$ has the following as basis:
-\begin{itemize}
-	\item $\ket{00}_{f_t,s_t}\ket{\xi_{00}}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
-	\item $\ket{01}_{f_t,s_t}\ket{\xi_{01}}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
-	\item $\ket{10}_{f_t,s_t}\ket{\xi_{10}}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
-	\item $\ket{11}_{f_t,s_t}\ket{\xi_{11}}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
-\end{itemize}
-
-Also, if $t\in T_2$, that is, $t$ corresponds to a time step where $C_\phi$ is applied, then the following are true due to $C_\phi$ being surrounded by $Z$ gates:
-\begin{itemize}
-	\item $\ket{0}\bra{0}_{f_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}+\ket{\widehat{t+1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t+1}})$
-	\item $\ket{1}\bra{1}_{f_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}-\ket{\widehat{t+1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t+1}})$
-	\item $\ket{0}\bra{0}_{s_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t+1}}+\ket{\widehat{t+2}})
-		(\bra{\widehat{t+1}}+\bra{\widehat{t+2}})$
-	\item $\ket{1}\bra{1}_{s_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t+1}}-\ket{\widehat{t+2}})
-		(\bra{\widehat{t+1}}-\bra{\widehat{t+2}})$
-	\item $(\ket{00}\bra{00}_{f_t,s_t}
-		+\ket{11}\bra{11}_{f_t,s_t})\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}+\ket{\widehat{t+2}})
-		(\bra{\widehat{t}}+\bra{\widehat{t+2}})$
-	\item $(\ket{01}\bra{01}_{f_t,s_t}
-		+\ket{10}\bra{10}_{f_t,s_t})\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}-\ket{\widehat{t+2}})
-		(\bra{\widehat{t}}-\bra{\widehat{t+2}})$
-\end{itemize}
-
-Similarly,
-\begin{itemize}
-	\item $\ket{0}\bra{0}_{f_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}+\ket{\widehat{t-2}})
-		(\bra{\widehat{t-1}}+\bra{\widehat{t-2}})$
-	\item $\ket{1}\bra{1}_{f_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}-\ket{\widehat{t-2}})
-		(\bra{\widehat{t-1}}-\bra{\widehat{t-2}})$
-	\item $\ket{0}\bra{0}_{s_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-2}}+\ket{\widehat{t-3}})
-		(\bra{\widehat{t-2}}+\bra{\widehat{t-3}})$
-	\item $\ket{1}\bra{1}_{s_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-2}}-\ket{\widehat{t-3}})
-		(\bra{\widehat{t-2}}-\bra{\widehat{t-3}})$
-	\item $(\ket{00}\bra{00}_{f_t,s_t}
-		+\ket{11}\bra{11}_{f_t,s_t})\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}+\ket{\widehat{t-3}})
-		(\bra{\widehat{t-1}}+\bra{\widehat{t-3}})$
-	\item $(\ket{01}\bra{01}_{f_t,s_t}
-		+\ket{10}\bra{10}_{f_t,s_t})\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}-\ket{\widehat{t-3}})
-		(\bra{\widehat{t-1}}-\bra{\widehat{t-3}})$
-\end{itemize}
-
-Now we ensure the 1-qubit gates are applied properly. The naive way would be to set
-	$$H_t=I\otimes\ket{\widehat t}\bra{\widehat t}
-		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		-C_\phi\otimes\ket{\widehat t}\bra{\widehat{t-1}}
-		-C_\phi^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-	$$H'=\sum_{t\in T_2}H_t$$
-	Equivalently, $H_t=$
-
-	$\ket{00}\bra{00}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{01}\bra{01}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{10}\bra{10}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{11}\bra{11}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
-
-However, this cannot be turned into 2-local, so we change the coefficients and set 
-	$$H_{prop2}=\sum_{t\in T_2}H_{prop2,t}$$
-
-	$H_{prop2,t}=$
-
-	$\ket{00}\bra{00}_{f_t,s_t}\otimes
-		4(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{01}\bra{01}_{f_t,s_t}\otimes
-		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{10}\bra{10}_{f_t,s_t}\otimes
-		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{11}\bra{11}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
-instead.
-
-Now, if restricted to $S_{prop}$,
-
-	$H_{prop2,t}=H_{qubit,t}+H_{time,t}=$
-	$$(-2\ket{0}\bra{0}_{f_t}-2\ket{0}\bra{0}_{s_t}
-		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t})\otimes$$
-	$$(\ket{\widehat{t}}\bra{\widehat{t-1}}+
-		\ket{\widehat{t-1}}\bra{\widehat{t}})+$$
-	$$(2\ket{0}\bra{0}_{f_t}+2\ket{0}\bra{0}_{s_t}
-		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t}
-		-2\ket{01}\bra{01}_{f_t,s_t}
-		-2\ket{10}\bra{10}_{f_t,s_t})\otimes$$
-	$$(\ket{\widehat{t-1}}\bra{\widehat{t-1}}+
-		\ket{\widehat{t}}\bra{\widehat{t}})$$
-
-Lastly, we check if the input is right...
-	$$H_{in}=\sum_{i=m+1}^N\ket{1}\bra{1}_i\otimes\ket{0}\bra{0}$$
-
-Now we use the projection lemma here. This step is different now that $H_{out}$ is gone. I think $J_{in}$ gets dropped or something like that?
-
-\subsection{2-local ZX Hamiltonians}
-
-We then follow \cite{biamonte_love_2008} in writing each terms of $H$ into only $Z$ and $X$ measurements...
-
-This probably involves some kind of basis arguments on the Hamiltonians and maybe some stuff that's a bit more ugly. This should not change the state. I'll have to write this out later...
-
-\subsection{Checking computation}
-
-We then follow \cite{mahadev_delegation}.
-That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
-The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{kempe_kitaev_regev_2006}.
-
-And then, this in fact involves some probabilistic analysis shenanigans that we haven't fully figured out yet.
-
-\subsection{Getting the Output}
-
-Thanks to having padded the circuit with identity matrices at the end, if we measured $T>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
-Now I would analyze the chances of getting this right, maybe in terms of fidelity or in terms of distance between this measured distribution and the ideal distribution...
-
-\section{Conclusion}
-
-This is a placeholder. Lorem ipsum...
+\input{conclusion}
 

### 2019-09-07 preliminaries.tex
split sections into separate files

\section{Preliminaries}

\subsection{Notations}

Let $\mathcal{B}$ denote the Hilbert space corresponding to a qubit.
Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian.

\begin{definition}
	Let $H\geq0$ denote $H$ is positive semidefinite.
\end{definition}

\begin{definition}
	Let $\lambda(H)$ as the least eigenvalue of $H$.
\end{definition}

\begin{definition}
	Let the \emph{ground state} of $H$ be the eigenvector corresponding to $\lambda(H)$.
\end{definition}

\begin{definition}
	Let $H\big|_S=\prod_SH\prod_S$, where $\prod_S$ is the projection onto the subspace $S$.
\end{definition}

\begin{definition}
	Let $\ket{\widehat{t}}=\ket{11\ldots1} \ket{00\ldots0}$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
\end{definition}

\begin{definition}
	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$. $\Lambda_{f, s}(U)$ would be the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda{1, 2}(X_3)$ would be a Toffoli ((CCNOT) gate.
\end{definition}

\begin{definition}
	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$
\end{definition}

\subsection{Local Hamiltonian}

The local Hamiltonian problem is defined as follows:

\begin{definition}
	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian. Then $$H=\sum_{j=1}^nH_j$$ is called a \emph{Hamiltonian}.
	If each $H_j$ acts on at most $k$ qubits, then $H$ is called a \emph{$k$-local Hamiltonian}.
\end{definition}

The local Hamiltonian problem is given by let $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, determine whether $\lambda(H)<a$ or $\lambda(H)>b$..

\begin{theorem}
	The Local Hamiltonian problem is QMA-complete.
\end{theorem}

\subsection{Projection Lemma}

Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.

Let $H_1, H_2$ be Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
Then $\exists J\in\mathbb{R}$ s.t.
$\lambda(H_1\big|_S)-\frac{1}{8}\leq
	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.

### 2019-09-07 longoutput.tex
start rewriting local Hamiltonian reduction

@@
 We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
-To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th.
 Note that after this transformation, the state is real.
@@
 $$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
+Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.
 
@@
 
-We then attempt to construct a local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
-We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biamonte_love_2008}.
+We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
+We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{biamonte_love_2008}.
 
-First, we ensure that the invalid clock states have high eigenvalues.
+First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
 $$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
@@
 
-Then, we ensure that 1-qubit gates are propagated properly. To do so, we set
+Then, we ensure that the initial condition is set up correctly. Let $n$ be the number of the qubits in the circuit.
+$$H_{in}=\sum_i^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
+Where $x_i$ is the $i$th bit of $x$.
+The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$.
+Furthermore, this can be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates as
+$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$
+
+TODO define $S_{in}$ when projection lemma is used
+
+Then, we ensure that the gates are applied correctly.
 $$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
@@
 I probably need to explain why this works but I'll leave it for another day.
-
-Let $S_{prop1}=\ker H_{prop1}$.
-Then, $S_{prop1}$ has the following as basis:
-\begin{itemize}
-	\item $\ket{00}_{f_t,s_t}\ket{\xi_{00}}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
-	\item $\ket{01}_{f_t,s_t}\ket{\xi_{01}}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
-	\item $\ket{10}_{f_t,s_t}\ket{\xi_{10}}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
-	\item $\ket{11}_{f_t,s_t}\ket{\xi_{11}}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
-\end{itemize}
-
-Also, if $t\in T_2$, that is, $t$ corresponds to a time step where $C_\phi$ is applied, then the following are true due to $C_\phi$ being surrounded by $Z$ gates:
-\begin{itemize}
-	\item $\ket{0}\bra{0}_{f_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}+\ket{\widehat{t+1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t+1}})$
-	\item $\ket{1}\bra{1}_{f_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}-\ket{\widehat{t+1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t+1}})$
-	\item $\ket{0}\bra{0}_{s_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t+1}}+\ket{\widehat{t+2}})
-		(\bra{\widehat{t+1}}+\bra{\widehat{t+2}})$
-	\item $\ket{1}\bra{1}_{s_t}\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t+1}}-\ket{\widehat{t+2}})
-		(\bra{\widehat{t+1}}-\bra{\widehat{t+2}})$
-	\item $(\ket{00}\bra{00}_{f_t,s_t}
-		+\ket{11}\bra{11}_{f_t,s_t})\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}+\ket{\widehat{t+2}})
-		(\bra{\widehat{t}}+\bra{\widehat{t+2}})$
-	\item $(\ket{01}\bra{01}_{f_t,s_t}
-		+\ket{10}\bra{10}_{f_t,s_t})\otimes
-		\ket{\widehat{t}}\bra{\widehat{t}}
-		=(\ket{\widehat{t}}-\ket{\widehat{t+2}})
-		(\bra{\widehat{t}}-\bra{\widehat{t+2}})$
-\end{itemize}
-
-Similarly,
-\begin{itemize}
-	\item $\ket{0}\bra{0}_{f_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}+\ket{\widehat{t-2}})
-		(\bra{\widehat{t-1}}+\bra{\widehat{t-2}})$
-	\item $\ket{1}\bra{1}_{f_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}-\ket{\widehat{t-2}})
-		(\bra{\widehat{t-1}}-\bra{\widehat{t-2}})$
-	\item $\ket{0}\bra{0}_{s_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-2}}+\ket{\widehat{t-3}})
-		(\bra{\widehat{t-2}}+\bra{\widehat{t-3}})$
-	\item $\ket{1}\bra{1}_{s_t}\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-2}}-\ket{\widehat{t-3}})
-		(\bra{\widehat{t-2}}-\bra{\widehat{t-3}})$
-	\item $(\ket{00}\bra{00}_{f_t,s_t}
-		+\ket{11}\bra{11}_{f_t,s_t})\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}+\ket{\widehat{t-3}})
-		(\bra{\widehat{t-1}}+\bra{\widehat{t-3}})$
-	\item $(\ket{01}\bra{01}_{f_t,s_t}
-		+\ket{10}\bra{10}_{f_t,s_t})\otimes
-		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		=(\ket{\widehat{t-1}}-\ket{\widehat{t-3}})
-		(\bra{\widehat{t-1}}-\bra{\widehat{t-3}})$
-\end{itemize}
-
-Now we ensure the 1-qubit gates are applied properly. The naive way would be to set
-	$$H_t=I\otimes\ket{\widehat t}\bra{\widehat t}
-		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-		-C_\phi\otimes\ket{\widehat t}\bra{\widehat{t-1}}
-		-C_\phi^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-	$$H'=\sum_{t\in T_2}H_t$$
-	Equivalently, $H_t=$
-
-	$\ket{00}\bra{00}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{01}\bra{01}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{10}\bra{10}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{11}\bra{11}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
-
-However, this cannot be turned into 2-local, so we change the coefficients and set 
-	$$H_{prop2}=\sum_{t\in T_2}H_{prop2,t}$$
-
-	$H_{prop2,t}=$
-
-	$\ket{00}\bra{00}_{f_t,s_t}\otimes
-		4(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{01}\bra{01}_{f_t,s_t}\otimes
-		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{10}\bra{10}_{f_t,s_t}\otimes
-		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$
-
-	$\ket{11}\bra{11}_{f_t,s_t}\otimes
-		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
-		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
-instead.
-
-Now, if restricted to $S_{prop}$,
-
-	$H_{prop2,t}=H_{qubit,t}+H_{time,t}=$
-	$$(-2\ket{0}\bra{0}_{f_t}-2\ket{0}\bra{0}_{s_t}
-		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t})\otimes$$
-	$$(\ket{\widehat{t}}\bra{\widehat{t-1}}+
-		\ket{\widehat{t-1}}\bra{\widehat{t}})+$$
-	$$(2\ket{0}\bra{0}_{f_t}+2\ket{0}\bra{0}_{s_t}
-		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t}
-		-2\ket{01}\bra{01}_{f_t,s_t}
-		-2\ket{10}\bra{10}_{f_t,s_t})\otimes$$
-	$$(\ket{\widehat{t-1}}\bra{\widehat{t-1}}+
-		\ket{\widehat{t}}\bra{\widehat{t}})$$
-
-Lastly, we check if the input is right...
-	$$H_{in}=\sum_{i=m+1}^N\ket{1}\bra{1}_i\otimes\ket{0}\bra{0}$$
-
-Now we use the projection lemma here. This step is different now that $H_{out}$ is gone. I think $J_{in}$ gets dropped or something like that?
 

### 2019-09-07 longoutput.tex
Write down all Hamiltonians
Change notation for CCU gates

@@
 $$T\circ H_f=H_f\circ T$$
-$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
+$$T\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0)\Lambda^2_{f,s}(Z_0)\circ T=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ T$$
 Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.
@@
 Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates.
+TODO check if this is obvious.
+If not, explain why.
 $$H_{clock}=\frac{1}{4}((T-1)I + Z_1 - Z_T - \sum_t^{T-1}Z_tZ_{t+1})$$
@@
 
-I probably need to explain why this works but I'll leave it for another day.
+I probably need to explain why this works but TODO I'll leave it for another day.
+
+Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli.
+Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$.
+$\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
+So we can write
+$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
 

### 2019-09-07 preliminaries.tex
start rewriting local Hamiltonian reduction
Change notation for CCU gates

@@
 \begin{definition}
-	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$. $\Lambda_{f, s}(U)$ would be the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda{1, 2}(X_3)$ would be a Toffoli ((CCNOT) gate.
+	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$, $X=\begin{pmatrix}0&1\\1&0\end{pmatrix}$, $Z=\begin{pmatrix}1&0\\0&-1\end{pmatrix}$
 \end{definition}
@@
 \begin{definition}
-	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$
+	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
+I.e.
+$\Lambda^2{1, 2}(X_3)$ would be a Toffoli (CCNOT) gate.
 \end{definition}

### 2019-09-07 longoutput.tex
Simplify an expression

@@
 $$T\circ H_f=H_f\circ T$$
-$$T\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0)\Lambda^2_{f,s}(Z_0)\circ T=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ T$$
+$$T\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ T=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ T$$
 Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.

### 2019-09-07 longoutput.tex
Make obvious the real transform isn't linear

@@
 
-We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
+We consider the transform $T(\ket{\psi})=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
 Note that after this transformation, the state is real.

### 2019-09-07 longoutput.tex
Add notes on notation

@@
 After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.
+Let $x_i$ denote the $i$th bit of $x$, and $|x|$ denote the number of the qubits in the circuit.
 
@@
 
-Then, we ensure that the initial condition is set up correctly. Let $n$ be the number of the qubits in the circuit.
-$$H_{in}=\sum_i^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
-Where $x_i$ is the $i$th bit of $x$.
+Then, we ensure that the initial condition is set up correctly.
+$$H_{in}=\sum_i^{|x|}(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
 The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$.
 Furthermore, this can be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates as
-$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$
+$$H_{in}=\frac{1}{4}\sum_{i=1}^{|x|}(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$
 
@@
 
-\subsection{2-local ZX Hamiltonians}
-
-We then follow \cite{biamonte_love_2008} in writing each terms of $H$ into only $Z$ and $X$ measurements...
-
-This probably involves some kind of basis arguments on the Hamiltonians and maybe some stuff that's a bit more ugly. This should not change the state. I'll have to write this out later...
+TODO Write down the final Hamiltonian. Possibly also the eigenvalue gap.
 

### 2019-09-07 delegations.tex
Change wording

@@
 \begin{definition}
-	A quantum delegation protocol is \emph{blind} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here.
+	A quantum delegation protocol is \emph{secure} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here.
 \end{definition}
@@
 In \cite{mahadev_delegation}, a verifiable scheme is proposed.
-In \cite{mahadev_qfhe}, a blind scheme is proposed.
-(TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made blind.
+In \cite{mahadev_qfhe}, a secure scheme is proposed.
+(TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made secure.
 

### 2019-09-07 longoutput.tex
Make editorial change

@@
 $$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-This set is proven to be universal in \cite{kitaev_1997}.
+Which is proven to be universal in \cite{kitaev_1997}.
 

### 2019-09-08 longoutput.tex
Add TODO probability analysis
Add reference on checking ground state
Improve reference on Biamonte and Love
Add another reference on checking ground state
Write the ground state check

@@
 We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
-We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{biamonte_love_2008}.
+We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.
 
@@
 
-We then follow \cite{mahadev_delegation}.
-That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
-The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{kempe_kitaev_regev_2006}.
+Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevLett.120.040501} and \cite{PhysRevA.93.022326}.
+
+We write $H$ as a linear combination of tensors of $I$, $X$, and $Z$.
+$$H=\sum_S d_S S$$
+We then shift each term by an identity.
+$$H'=H+I\sum_S|d_S|$$
+$$=\sum_S|d_S|(I+\sgn(d_S)S)$$
+$$=\sum_S2|d_S|P_S$$
+Note that $P_S$ are in fact projections since $S$ all have eigenvalues $\pm1$. Now scale $H'$:
+$$H''=\frac{1}{2|d_S|}H'=\sum_S\pi_S P_S$$
+Note that $H''$ is now a weighted sum of projectors.
+We also have $0\leq\pi_S\leq1$ and $\sum_S \pi_S=1$, so we can define the corresponding probability distribution over the choice of $S$.
+Now we can write the following:
+$$\braket{\phi|H''|\phi}=\sum_S\pi_S\braket{\phi|P_S|\phi}=\E_S[\braket{\phi|P_S|\phi}]$$
+$$\braket{\phi|P_S|\phi}=\braket{\phi|\frac{1}{2}(I+\sgn(d_S)S)|\phi}=\frac{1}{2}(1+\sgn(d_S)\braket{\phi|S|\phi})$$
+Which is simple to estimate by doing the measurements corresponding to $S$.
+
+TODO so do we have perfect completeness or no?
+
+\subsection{Analysis and amplification}
+
+We then follow \cite{mahadev_delegation}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
 

### 2019-09-08 longoutput.tex
Remove another unnecessary reference

@@
 Here we describe the scheme between the classical client and an honest quantum server.
-We mostly follow the logic in \cite{mahadev_delegation}.
-We first follow \cite{kempe_kitaev_regev_2006} to reduce the problem to an instance of local Hamiltonian.
+This is similar to the underlying construction for \cite{mahadev_delegation}.
+We first preprocess the circuit using tools such as \cite{quant-ph/0301040}.
+We then follow \cite{kitaev2002classical} to reduce the problem to an instance of local Hamiltonian.
+We then analyze it using tools from \cite{PhysRevA.93.022326}.
+Then, NYI cuz we're stuck.
 
@@
 
-Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevLett.120.040501} and \cite{PhysRevA.93.022326}.
+Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevA.93.022326}.
 

### 2019-09-08 longoutput.tex
Fix typo

@@
 
-Thanks to having padded the circuit with identity matrices at the end, if we measured $T>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
+Thanks to having padded the circuit with identity matrices at the end, if we measured $t>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
 Now I would analyze the chances of getting this right, maybe in terms of fidelity or in terms of distance between this measured distribution and the ideal distribution...

### 2019-09-08 preliminaries.tex
Remove unused definitions

@@
 
-\subsection{Local Hamiltonian}
-
-The local Hamiltonian problem is defined as follows:
-
 \begin{definition}
-	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian. Then $$H=\sum_{j=1}^nH_j$$ is called a \emph{Hamiltonian}.
-	If each $H_j$ acts on at most $k$ qubits, then $H$ is called a \emph{$k$-local Hamiltonian}.
+	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitians each acting on at most $k$ qubits, then $$H=\sum_{j=1}^nH_j$$ is called a \emph{$k$-local Hamiltonian}.
 \end{definition}
-
-The local Hamiltonian problem is given by let $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, determine whether $\lambda(H)<a$ or $\lambda(H)>b$..
-
-\begin{theorem}
-	The Local Hamiltonian problem is QMA-complete.
-\end{theorem}
 
@@
 
-Let $H_1, H_2$ be Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
+Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
 Then $\exists J\in\mathbb{R}$ s.t.

### 2019-09-10 delegations.tex
Mention the possibility to achieve security
add TODO

@@
 \begin{definition}
-	A quantum delegation protocol is \emph{secure} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here.
+	A quantum delegation protocol is \emph{secure} if a malicious prover cannot learn the input or the output of the computation.
+In particular, security notions such as \emph{CPA} can be applied here.
+(TODO Just define CPA right away since there are no other security notions around here)
 \end{definition}
@@
 TODO check where does \cite{1904.06320} fit in.
+
+\subsection{Our contributions}
+
+We start by constructing a verifiable long output scheme.
+Then, we encrypt the scheme as given in \cite{mahadev_delegation} to achieve security.
+TODO Does it actually work though?
+There are multiple steps in the scheme...
+We encrypting each step separately or what?

### 2019-09-10 longoutput.tex
Fix edge case bug for gates propagation
Remove useless subscript

@@
 We then follow \cite{kitaev2002classical} to reduce the problem to an instance of local Hamiltonian.
-We then analyze it using tools from \cite{PhysRevA.93.022326}.
+Using tools from \cite{PhysRevA.93.022326}, the local Hamiltonian is written in a simple form.
 Then, NYI cuz we're stuck.
@@
 Mathematically,
-$$T\circ H_f=H_f\circ T$$
+$$T\circ H=H\circ T$$
 $$T\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ T=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ T$$
@@
 Then, we ensure that the gates are applied correctly.
-$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
+$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
 $$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
@@
 	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
+Extra care must be taken for boundary cases.
+$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
+$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
 

### 2019-09-10 longoutput.tex
Fix bug on clock Hamiltonian
Add TODO

@@
 Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates.
-TODO check if this is obvious.
-If not, explain why.
-$$H_{clock}=\frac{1}{4}((T-1)I + Z_1 - Z_T - \sum_t^{T-1}Z_tZ_{t+1})$$
+$$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
+This can be checked by fixing the first and last qubit, then doing induction on the number of switches.
 
@@
 TODO define $S_{in}$ when projection lemma is used
+
+TODO consider using the older construction with the angle between subspaces for better constants?
 

### 2019-09-10 longoutput.tex
Write more about H prop

@@
 	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-Extra care must be taken for boundary cases.
-$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
-$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
 
-I probably need to explain why this works but TODO I'll leave it for another day.
+It is easier to check that it works and is Hermitian and works as expected by a unitary change of basis.
+
+$$W=\sum_{j=0}^L U_j\ldots U_1\otimes\ket{j}\bra{j}$$
+$$W^\dagger\phi=\sum_{t=0}^T\ket{x}\otimes\ket{\hat{t}}$$
+$$W^\dagger H_{prop} W=
+\begin{pmatrix}
+	\frac{1}{2} & -\frac{1}{2} & & & &  \\
+	-\frac{1}{2} & 1 & -\frac{1}{2} & & & \\
+	& -\frac{1}{2} & 1 & \ddots & & \\
+	& & \ddots & \ddots & -\frac{1}{2} & \\
+	& & & -\frac{1}{2} & 1 & -\frac{1}{2} \\
+	& & & & -\frac{1}{2} & \frac{1}{2}
+\end{pmatrix}$$
+
+I probably need to say even more on why this works but TODO I'll leave it for another day.
+There's also a closed form to the second smallest eigenvalue above that is apparently related to random walks but I can't find the source at the moment.
 
@@
 $$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
+Extra care must be taken for boundary cases.
+$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
+$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
 

### 2019-09-10 introduction.tex
Fix typo

@@
 I'm generalizing this to arbitrary efficient quantum computations.
-The proof for decision problems involves the classical verifier reducing the problem to a local Hamiltonian instance; the quantum prover would then commit its certificate and act as the verifier’s trusted measurement device as put forth in "Classical Verification of Quantum Computations" by Mahadev.
+The proof for decision problems involves the classical verifier reducing the problem to a local Hamiltonian instance; the quantum prover would then commit its certificate and act as the verifier’s trusted measurement device as put forth in ``Classical Verification of Quantum Computations" by Mahadev.
 It isn't as trivial as it may seem.

### 2019-09-10 delegations.tex
Change wording
Remove TODO
Change definition of delegation schemes

@@
 	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover.
-The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate with the help of the prover.
+The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate and measure the result by interacting with the prover.
 \end{definition}
 
-TODO (maybe don't assume universality?)
-
 \begin{definition}
-	A quantum delegation protocol has \emph{long output with error $\epsilon$} if the output can have multiple bits.
-In this case, the verifier should end with a measurement result of the output register.
-Said result's probability distribution would be within $\epsilon$ of the true distribution.
+	A quantum delegation protocol has \emph{long output} if the output can have multiple bits. In this case, the verifier should end with a measurement result of the output register.
 \end{definition}
@@
 \begin{definition}
-	A quantum delegation protocol is \emph{verifiable} if the verifier can check if the output is correct. TODO need to be more rigorous here.
+	A quantum delegation protocol is \emph{$\delta,\epsilon$-verifiable} if the verifier's output distribution is within $\delta$ of the true distribution whenever it interacts with a prover whose probability to be accepted is greater than $\epsilon$.
 \end{definition}

### 2019-09-10 delegations.tex
Fix typo

@@
 	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover.
-The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate and measure the result by interacting with the prover.
+The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate and measure the result of by interacting with the prover.
 \end{definition}

### 2019-09-11 delegations.tex
Modify definition of verifiability

@@
 \begin{definition}
-	A quantum delegation protocol is \emph{$\delta,\epsilon$-verifiable} if the verifier's output distribution is within $\delta$ of the true distribution whenever it interacts with a prover whose probability to be accepted is greater than $\epsilon$.
+	A quantum delegation protocol is \emph{$\delta(\epsilon)$-verifiable} if the verifier's output distribution is within $\epsilon$ of the true distribution whenever it interacts with a prover whose probability to be accepted is greater than $\delta$.
 \end{definition}

### 2019-09-11 longoutput.tex
Move a TODO
Remove extra whitespace
Simplify measurement protocol

@@
 
-TODO consider using the older construction with the angle between subspaces for better constants?
-
 Then, we ensure that the gates are applied correctly.
@@
 
+TODO consider using the older construction with the angle between subspaces for better constants?
+
 \subsection{Checking computation}
@@
 We write $H$ as a linear combination of tensors of $I$, $X$, and $Z$.
-$$H=\sum_S d_S S$$
-We then shift each term by an identity.
-$$H'=H+I\sum_S|d_S|$$
-$$=\sum_S|d_S|(I+\sgn(d_S)S)$$
-$$=\sum_S2|d_S|P_S$$
-Note that $P_S$ are in fact projections since $S$ all have eigenvalues $\pm1$. Now scale $H'$:
-$$H''=\frac{1}{2|d_S|}H'=\sum_S\pi_S P_S$$
-Note that $H''$ is now a weighted sum of projectors.
-We also have $0\leq\pi_S\leq1$ and $\sum_S \pi_S=1$, so we can define the corresponding probability distribution over the choice of $S$.
-Now we can write the following:
-$$\braket{\phi|H''|\phi}=\sum_S\pi_S\braket{\phi|P_S|\phi}=\E_S[\braket{\phi|P_S|\phi}]$$
-$$\braket{\phi|P_S|\phi}=\braket{\phi|\frac{1}{2}(I+\sgn(d_S)S)|\phi}=\frac{1}{2}(1+\sgn(d_S)\braket{\phi|S|\phi})$$
+$$H=\sum_S d_S S= \sum_S |d_S|\sgn(d_S)S$$
+We then scale the Hamiltonian.
+$$D=\sum_S|d_S|$$
+$$p_S=\frac{|d_S|}{D}$$
+$$H'=\frac{H}{D}=\sum_S p_S\sgn(d_S)S$$
+
+Note that $H'$ is now a weighted sum of measurement operators. We also have $0\leq p_S\leq1$ and $\sum_S p_S=1$, so we can treat it as a probability distribution over the choice of $S$.
+$$\braket{\phi|H'|\phi}=\sum_S p_S\sgn(d_S)\braket{\phi|S|\phi}=\E_S[\sgn(d_S)\braket{\phi|S|\phi}]$$
 Which is simple to estimate by doing the measurements corresponding to $S$.
-
-TODO so do we have perfect completeness or no?
+Note that $H'=0$, but the measurement result is $\pm1$, so clearly we do not have perfect completeness.
 

### 2019-09-11 delegations.tex
Write TODO on security
Change wording

@@
 Then, we encrypt the scheme as given in \cite{mahadev_delegation} to achieve security.
-TODO Does it actually work though?
-There are multiple steps in the scheme...
-We encrypting each step separately or what?
+That is, we first encrypt the circuit.
+Then TODO it's not immediately obvious that this works.
+This isn't purely a circuit anymore, but we also have classical data and evaluation key now.

### 2019-09-11 delegations.tex
Remove unnecessary detail in definition
Change wording

@@
 \begin{definition}
-	A quantum delegation protocol has \emph{long output} if the output can have multiple bits. In this case, the verifier should end with a measurement result of the output register.
+	A quantum delegation protocol has \emph{long output} if the output register contains multiple qubits.
 \end{definition}

### 2019-09-11 delegations.tex
Make editorial change
Write about security

@@
 \begin{definition}
-	A quantum delegation protocol is \emph{secure} if a malicious prover cannot learn the input or the output of the computation.
-In particular, security notions such as \emph{CPA} can be applied here.
-(TODO Just define CPA right away since there are no other security notions around here)
+	A quantum delegation protocol is \emph{CPA-secure} if both the input and output of the circuit are CPA-secure as ciphertexts.
+In this case, the scheme should be seen as a homomorphic encryption scheme.
 \end{definition}
@@
 
-In \cite{mahadev_delegation}, a verifiable scheme is proposed.
-In \cite{mahadev_qfhe}, a secure scheme is proposed.
-(TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made secure.
+In \cite{mahadev_delegation}, a verifiable scheme is proposed. In \cite{mahadev_qfhe}, a secure scheme is proposed. (TODO just make this CPA or whatever it actually is...)
 
@@
 
+We propose a verifiable scheme with long output which can also be made secure.
 We start by constructing a verifiable long output scheme.
-Then, we encrypt the scheme as given in \cite{mahadev_delegation} to achieve security.
-That is, we first encrypt the circuit.
-Then TODO it's not immediately obvious that this works.
-This isn't purely a circuit anymore, but we also have classical data and evaluation key now.
+Then, we use \cite{mahadev_delegation} to achieve security.
+That is, we the techniques in \cite{mahadev_delegation} to encrypt the circuit and the input.
+We also tack on the evaluation key as extra input, so the entire computation can still be encoded as a single circuit.

### 2019-09-11 longoutput.tex
Fix typo
Add TODO for encrypting circuit
Fix bug
Start probability analysis

@@
-\section{Long Output scheme}
+\section{Our Long Output Scheme}
 
@@
 \subsection{preprocess the circuit}
+
+TODO Maybe encrypt things here first if needed?
 
@@
 We then follow \cite{mahadev_delegation}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
+The client would keep a single copy for output, and use the other copies to check whether the computation is done properly.
 
-And then, this in fact involves some probabilistic analysis shenanigans that we haven't fully figured out yet.
+Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=-1$ on $\ket\psi$ and $\ket\phi$ respectively, where $\phi$ is perpendicular to $\psi$.
+Obviously, $p_0=\frac{1}{2}$, and $p_1<\frac{1}{2}$...
+TODO Now what?
+Hypothesis testing...?
 

### 2019-09-12 longoutput.tex
Start rewriting preprocessing circuit

@@
 
+\subsection{preprocess the circuit}
+
 We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
@@
 
-\subsection{preprocess the circuit}
-
-TODO Maybe encrypt things here first if needed?
-
 Here we first reduce the circuit to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.
 
-We consider the transform $T(\ket{\psi})=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
+We consider the transform $\mathcal{T}(\ket{\psi})=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
 Note that after this transformation, the state is real.
@@
 Mathematically,
-$$T\circ H=H\circ T$$
-$$T\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ T=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ T$$
+$$\mathcal{T}\circ H=H\circ\mathcal{T}$$
+$$\mathcal{T}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{T}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{T}$$
 Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.

### 2019-09-12 longoutput.tex
Change notation

--- 2019-09-11 longoutput.tex
@@
 
-\subsection{preprocess the circuit}
-
-TODO Maybe encrypt things here first if needed?
-
 Here we first reduce the circuit to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.
 
-We consider the transform $T(\ket{\psi})=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
+We consider the transform $\mathcal{F}(\ket{\psi})=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
 Note that after this transformation, the state is real.
@@
 Mathematically,
-$$T\circ H=H\circ T$$
-$$T\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ T=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ T$$
+$$\mathcal{F}\circ H=H\circ\mathcal{F}$$
+$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
 Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.

### 2019-09-12 longoutput.tex
Elaborate on long output scheme

@@
 
-\subsection{preprocess the circuit}
+\subsection{Picking universal gate set}
 
@@
 
-Here we first reduce the circuit to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.
+\subsection{Creating Real Circuits}
 
-We consider the transform $\mathcal{F}(\ket{\psi})=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
+Now consider a circuit $C=U_T\ldots U_1$, where $U_i\in\set{H, \Lambda(P(i))}$.
+Its input is classical $x$ of size $n$.
+Let $\ket\psi$ denote the initial state with $N$ qubits, containing $x$ possibly followed by ancilliaries.
+
+We first reduce it to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.
+
+We consider the transform $\mathcal{F}(\ket{\phi})=\ket{0}\otimes\Re\ket{\phi}+\ket{1}\otimes\Im\ket{\phi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
 Note that after this transformation, the state is real.
 This transformation preserves measurement results in the standard basis.
-Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates.
-Mathematically,
+We apply it to $\ket\psi$.
+
+The transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
 $$\mathcal{F}\circ H=H\circ\mathcal{F}$$
 $$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
-Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.
+Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position. We modify the circuit as appropriate to obtain $C'$.
 
-We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
-This is so that the final output has a higher chance to be measured in the final result in the following reduction.
+Now $C'$ has size $T'\leq 4T$.
+The initial state is real, and all the gates are real.
+Which implies all the intermediate states as well as the output are real.
+Its input $x$ doesn't change, but the initial state $\ket{\psi'}$ is now size $N+1$.
+
+\subsection{Constructing a local Hamiltonian instance}
+
+Let $C$ undergo the above two transforms so it has the following properties
+\begin{itemize}
+	\item Initial state is real
+	\item Contains only Hadamard and Toffoli gates
+	\item The last $\gamma$ of the gates are all identity gates (can achieve easily by padding)
+\end{itemize}
 
@@
 Let $x_i$ denote the $i$th bit of $x$, and $|x|$ denote the number of the qubits in the circuit.
-
-\subsection{Constructing a local Hamiltonian instance}
 
@@
 
-TODO consider using the older construction with the angle between subspaces for better constants?
+\subsection{Measuring}
+
+Here we show that the Hamiltonians above can be written in a simple form.
+
+First, we show that Toffoli and Hadamard matrices can be written in terms of Kronecker products of $X$, $Z$, and $I$.
+$$H=X+Z$$
+$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
+$$\ket{11}\bra{11}=I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I$$
 

### 2019-09-12 longoutput.tex
Add source showing H prop is PSD
Fix wording

@@
 The transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
-$$\mathcal{F}\circ H=H\circ\mathcal{F}$$
+$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
 $$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
@@
 \begin{itemize}
-	\item Initial state is real
-	\item Contains only Hadamard and Toffoli gates
-	\item The last $\gamma$ of the gates are all identity gates (can achieve easily by padding)
+	\item All states are real (including initial, intermediate states, and output).
+	\item Consists of only Hadamard and Toffoli gates
+	\item The last $\gamma$ of the gates are all identity gates (can easily achieve by padding)
 \end{itemize}
@@
 
-TODO define $S_{in}$ when projection lemma is used
-
 Then, we ensure that the gates are applied correctly.
@@
 \end{pmatrix}$$
+
+According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks.
 

### 2019-09-12 longoutput.tex
Change a TODO
Move and work on gate set

@@
 
+\subsection{Properties of the gate set}
+
+Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli.
+Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$.
+$\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
+So we can write
+$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
+Extra care must be taken for boundary cases.
+$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
+$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
+
+To this effect, we also define $G=$... TODO define set of tensors of XZI
+
 \subsection{Constructing a local Hamiltonian instance}
@@
 
-It is easier to check that it works and is Hermitian and works as expected by a unitary change of basis.
+Next, we check that $H_{prop}\geq0$ by the following transform.
 
@@
 
-I probably need to say even more on why this works but TODO I'll leave it for another day.
-There's also a closed form to the second smallest eigenvalue above that is apparently related to random walks but I can't find the source at the moment.
-
-Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli.
-Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$.
-$\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
-So we can write
-$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
-Extra care must be taken for boundary cases.
-$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
-$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
+TODO maybe say more about this.
 

### 2019-09-12 longoutput.tex
Reorganize

@@
 
-Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli.
-Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$.
-$\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
-So we can write
-$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
-Extra care must be taken for boundary cases.
-$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
-$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
+First, we show that Toffoli and Hadamard matrices can be written in terms of Kronecker products of $X$, $Z$, and $I$.
+$$H=\frac{1}{\sqrt{2}}(X+Z)$$
+$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
+$$\ket{11}\bra{11}=I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I$$
 
@@
 $$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
-We also set $S_{legal}=\ker H_{clock}$.
-Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register.
 Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates.
@@
 
+We can also write $H$ as (TODO need to define).
+Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli.
+Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$.
+$\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
+$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
+Extra care must be taken for boundary cases.
+$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
+$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
+
 TODO maybe say more about this.
+We also set $S_{legal}=\ker H_{clock}$. Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register.
 
@@
 Here we show that the Hamiltonians above can be written in a simple form.
-
-First, we show that Toffoli and Hadamard matrices can be written in terms of Kronecker products of $X$, $Z$, and $I$.
-$$H=X+Z$$
-$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
-$$\ket{11}\bra{11}=I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I$$
 

### 2019-09-13 longoutput.tex
Change wording
Fix bug
Do more work on longoutput

@@
 $$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
-Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position. We modify the circuit as appropriate to obtain $C'$.
-
-Now $C'$ has size $T'\leq 4T$.
-The initial state is real, and all the gates are real.
+Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.
+We modify the circuit as appropriate to obtain $C'$ that has size $T'\leq 4T$.
+Its initial state is real, and all the gates are real.
 Which implies all the intermediate states as well as the output are real.
@@
 
-\subsection{Properties of the gate set}
+We prove a theorem about this circuit that we'll use later.
 
-First, we show that Toffoli and Hadamard matrices can be written in terms of Kronecker products of $X$, $Z$, and $I$.
+\begin{definition}
+	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n|U_i\in\set{I,X,Z}}$.
+\end{definition}
+
+To simplify the notation, we may only write the qubits with $X$ and $Z$ operators when talking about members of $\mathcal{G}_{XZ}$.
+
+\begin{theorem}
+	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$
+\end{theorem}
+
+\begin{proof}
 	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
 	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
-$$\ket{11}\bra{11}=I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I$$
-
-To this effect, we also define $G=$... TODO define set of tensors of XZI
+	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
+\end{proof}
 
@@
 $$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
-Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates.
+Note that $H_{clock}\in\spn\mathcal{G}_{XZ}$
 $$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
@@
 $$H_{in}=\sum_i^{|x|}(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
-The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$.
-Furthermore, this can be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates as
+The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
 $$H_{in}=\frac{1}{4}\sum_{i=1}^{|x|}(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$
@@
 
-We can also write $H$ as (TODO need to define).
+We can also write $H=\spn\mathcal{G}_{XZ}$.
 Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli.
@@
 
-TODO maybe say more about this.
-We also set $S_{legal}=\ker H_{clock}$. Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register.
+TODO
+Now we combine the three Hamiltonians defined. First consider their kernels.
+$$K_{clock}=\ker H_{clock}$$
+$$K_{in}=\ker H_{in}$$
+$$K_{prop}=\ker H_{prop}$$
 
-TODO Write down the final Hamiltonian. Possibly also the eigenvalue gap.
+It is
 
-\subsection{Measuring}
-
-Here we show that the Hamiltonians above can be written in a simple form.
-
-\subsection{Checking computation}
+\subsection{Measuring ground state}
 
@@
 
-We write $H$ as a linear combination of tensors of $I$, $X$, and $Z$.
-$$H=\sum_S d_S S= \sum_S |d_S|\sgn(d_S)S$$
+Since $H\in\spn\mathcal{G}_{XZ}$, we can write it as follows:
+$$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S= \sum_{S\in\mathcal{G}_{XZ}} |d_S|\sgn(d_S)S$$
 We then scale the Hamiltonian.
-$$D=\sum_S|d_S|$$
+$$D=\sum_{S\in\mathcal{G}_{XZ}}|d_S|$$
 $$p_S=\frac{|d_S|}{D}$$
-$$H'=\frac{H}{D}=\sum_S p_S\sgn(d_S)S$$
+$$H'=\frac{H}{D}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)S$$
 
-Note that $H'$ is now a weighted sum of measurement operators. We also have $0\leq p_S\leq1$ and $\sum_S p_S=1$, so we can treat it as a probability distribution over the choice of $S$.
-$$\braket{\phi|H'|\phi}=\sum_S p_S\sgn(d_S)\braket{\phi|S|\phi}=\E_S[\sgn(d_S)\braket{\phi|S|\phi}]$$
+Note that $H'$ is now a weighted sum of measurement operators.
+We also have $0\leq p_S\leq1$ and $\sum_{S\in\mathcal{G}_{XZ}} p_S=1$, so we can treat it as a probability distribution over the choice of $S$.
+$$\braket{\phi|H'|\phi}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}=\E_S[\sgn(d_S)\braket{\phi|S|\phi}]$$
 Which is simple to estimate by doing the measurements corresponding to $S$.

### 2019-09-13 longoutput.tex
Do more work on longoutput

@@
 
-Let $C$ undergo the above two transforms so it has the following properties
+Let $C$ undergo the above transformations so it has the following properties
 \begin{itemize}
@@
 
-We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
+We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
 We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.
@@
 $$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
-Note that $H_{clock}\in\spn\mathcal{G}_{XZ}$
+As it is a sum of projections, $H_{clock}\geq 0$. We also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
 $$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
@@
 
-TODO
 Now we combine the three Hamiltonians defined. First consider their kernels.
@@
 $$K_{prop}=\ker H_{prop}$$
-
-It is
+Notice that (TODO need proof or no?)
+$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
+We now define
+$$K=(\spn\set{\psi_{circuit}})^\bot$$
+and consider $H_{clock}\big|_K,H_{in}\big|_K,H_{prop}\big|_K$. That is, we restrict the following computations to the subspace $K$. We apply the projection lemma.
+$$\exists J_{clock},
+\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K)\geq
+\lambda(H_{in}\big|_{K\cap K_{clock}})-\frac{1}{8}$$
+$$\exists J_{prop},
+\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K+J_{prop}H_{prop}\big|_K)\geq
+\lambda(H_{in}\big|_{K\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
+$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_K)\geq\frac{3}{4}$$
+So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$. It has the following properties.
+\begin{itemize}
+	\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
+	\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
+	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$
+\end{itemize}
 
@@
 
-Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevA.93.022326}.
+Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$.
+Here we follow \cite{PhysRevA.93.022326}.
+Note that if $\phi=\psi_{circuit}$, then $\braket{\phi|H|\phi}=0$.
+If $\braket{\phi|\psi_{circuit}}=0$, then $\braket{\phi|H|\phi}>\beta>\frac{1}{\poly(T)}$.
 
@@
 
-Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=-1$ on $\ket\psi$ and $\ket\phi$ respectively, where $\phi$ is perpendicular to $\psi$.
+Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=-1$ on $\ket\psi_{circuit}$ and $\ket\phi$ respectively, where $\phi$ is perpendicular to $\psi_{circuit}$.
 Obviously, $p_0=\frac{1}{2}$, and $p_1<\frac{1}{2}$...

### 2019-09-13 longoutput.tex
Work on longoutput

@@
 
-\subsection{Picking universal gate set}
+\subsection{Preprocessing circuit}
 
@@
 
-\subsection{Creating Real Circuits}
+Now consider a circuit $C=U_T\ldots U_1$ with the following properties:
+\begin{itemize}
+	\item $U_i\in\set{H, \Lambda(P(i))}$
+	\item Has initial state $\ket\psi$ with $n$ qubits
+\end{itemize}
 
-Now consider a circuit $C=U_T\ldots U_1$, where $U_i\in\set{H, \Lambda(P(i))}$.
-Its input is classical $x$ of size $n$.
-Let $\ket\psi$ denote the initial state with $N$ qubits, containing $x$ possibly followed by ancilliaries.
+We first reduce it to use only real gates and states. The proof is taken from \cite{quant-ph/0301040}. We consider the transform
+$$\mathcal{F}(\ket{\phi})=\ket{0}\otimes\Re\ket{\phi}+\ket{1}\otimes\Im\ket{\phi}$$
+where $\Re$ and $\Im$ denote real and imaginary parts respectively. It has the following properties
 
-We first reduce it to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.
+\begin{itemize}
+	\item $\forall\ket\phi$, $\mathcal{F}(\ket\phi)$ is real.
+	\item Preserves $X$ and $Z$ measurement results
+\end{itemize}
 
-We consider the transform $\mathcal{F}(\ket{\phi})=\ket{0}\otimes\Re\ket{\phi}+\ket{1}\otimes\Im\ket{\phi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively.
-Note that after this transformation, the state is real.
-This transformation preserves measurement results in the standard basis.
-We apply it to $\ket\psi$.
+We now apply $\mathcal{F}$ to $\ket\psi$. To make the notation easier, let $\ket{\psi}$ be 1-indexed, and the $\mathcal{F}\ket{\psi}$ be 0-indexed, so corresponding qubits stay in the same position.
 
@@
 $$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
-Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.
-We modify the circuit as appropriate to obtain $C'$ that has size $T'\leq 4T$.
-Its initial state is real, and all the gates are real.
-Which implies all the intermediate states as well as the output are real.
-Its input $x$ doesn't change, but the initial state $\ket{\psi'}$ is now size $N+1$.
-
-We prove a theorem about this circuit that we'll use later.
+We modify the circuit as appropriate to obtain $C'$ that has size $T'\leq 4T$. We prove a theorem about this circuit that we'll use later.
 
@@
 
-\subsection{Constructing a local Hamiltonian instance}
-
 Let $C$ undergo the above transformations so it has the following properties
@@
 
-After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.
-Let $x_i$ denote the $i$th bit of $x$, and $|x|$ denote the number of the qubits in the circuit.
+\subsection{Constructing a local Hamiltonian instance}
 
-We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
+Let $C$ be a circuit with the above properties. Define the following quantities.
+\begin{itemize}
+	\item $C=U_T\ldots U_1$
+	\item Let $x$ be the circuit input. Which is classical.
+	\item Let $y$ denote the initial state. That is, $x$ possibly concatenated with ancillaries.
+	\item Let $y_i$ denote the $i$-th bit of $y$
+	\item Let $n=|y|$ be the number of qubits in $C$
+\end{itemize}
+
+We then attempt to construct a local Hamiltonian with the following ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
 We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.
@@
 $$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
-As it is a sum of projections, $H_{clock}\geq 0$. We also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
+As a sum of projections, clearly $H_{clock}\geq 0$. We shall also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
 $$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
@@
 Then, we ensure that the initial condition is set up correctly.
-$$H_{in}=\sum_i^{|x|}(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
+$$H_{in}=\sum_{i=1}^{|y|}(I-\ket{y_i}\bra{y_i})\otimes\ket{0}\bra{0}_1$$
 The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
-$$H_{in}=\frac{1}{4}\sum_{i=1}^{|x|}(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$
+$$H_{in}=\frac{1}{4}\sum_{i=1}^{|y|}(I-(-1)^{y_i}Z_i)\otimes(I+Z_1)$$
 

### 2019-09-13 longoutput.tex
Use projection lemma

@@
 
-According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks.
+According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks. Furthermore, the second eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.
 
@@
 We now define
-$$K=(\spn\set{\psi_{circuit}})^\bot$$
-and consider $H_{clock}\big|_K,H_{in}\big|_K,H_{prop}\big|_K$. That is, we restrict the following computations to the subspace $K$. We apply the projection lemma.
-$$\exists J_{clock},
-\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K)\geq
-\lambda(H_{in}\big|_{K\cap K_{clock}})-\frac{1}{8}$$
-$$\exists J_{prop},
-\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K+J_{prop}H_{prop}\big|_K)\geq
-\lambda(H_{in}\big|_{K\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
-$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_K)\geq\frac{3}{4}$$
+$$S=(\spn\set{\psi_{circuit}})^\bot$$
+and consider $H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$. That is, we restrict the following computations to the subspace $S$. We apply the projection lemma.
+$$\exists J_{clock}
+=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
+=O(1)$$
+$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
+\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
+$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
+=\frac{O(T)}{\Omega(T^{-2})}=O(T^3)$$
+$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
+\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
+$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
 So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$. It has the following properties.
@@
 	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$
+	\item $\norm{H_{circuit}}_{\max}=O(T^3)$
 \end{itemize}

### 2019-09-14 longoutput.tex
Start to rewrite measurement protocol
Finish 2nd draft for longoutput

--- 2019-09-13 longoutput.tex
@@
 	\item Let $y_i$ denote the $i$-th bit of $y$
-	\item Let $n=|y|$ be the number of qubits in $C$
+	\item Let $n$ be the number of qubits in $C$
 \end{itemize}
 
-We then attempt to construct a local Hamiltonian with the following ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
+We then attempt to construct a local Hamiltonian with the following ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$
 We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.
@@
 Then, we ensure that the initial condition is set up correctly.
-$$H_{in}=\sum_{i=1}^{|y|}(I-\ket{y_i}\bra{y_i})\otimes\ket{0}\bra{0}_1$$
+$$H_{in}=\sum_{i=1}^n(I-\ket{y_i}\bra{y_i})\otimes\ket{0}\bra{0}_1$$
 The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
-$$H_{in}=\frac{1}{4}\sum_{i=1}^{|y|}(I-(-1)^{y_i}Z_i)\otimes(I+Z_1)$$
+$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{y_i}Z_i)\otimes(I+Z_1)$$
 
@@
 
-Now we combine the three Hamiltonians defined. First consider their kernels.
+Now we consider the kernels of the Hamiltonians we defined. Notice the following.
 $$K_{clock}=\ker H_{clock}$$
@@
 $$K_{prop}=\ker H_{prop}$$
-Notice that (TODO need proof or no?)
 $$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
-We now define
-$$K=(\spn\set{\psi_{circuit}})^\bot$$
-and consider $H_{clock}\big|_K,H_{in}\big|_K,H_{prop}\big|_K$. That is, we restrict the following computations to the subspace $K$. We apply the projection lemma.
-$$\exists J_{clock},
-\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K)\geq
-\lambda(H_{in}\big|_{K\cap K_{clock}})-\frac{1}{8}$$
-$$\exists J_{prop},
-\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K+J_{prop}H_{prop}\big|_K)\geq
-\lambda(H_{in}\big|_{K\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
-$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_K)\geq\frac{3}{4}$$
-So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$. It has the following properties.
+We now consider the space outside the desired state.
+$$S=(\spn\set{\psi_{circuit}})^\bot$$
+$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
+To combine the Hamiltonians, we apply the projection lemma twice.
+$$\exists J_{clock}
+=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
+=O(n)=O(T)$$
+$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
+\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
+$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
+=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
+$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
+\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
+$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
+So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$ to obtain the following properties.
 \begin{itemize}
@@
 	\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
-	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$
+	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$. There are $O(T)$ nonzero components, whose coefficients are each at most $O(T^3)$.
 \end{itemize}
@@
 Note that if $\phi=\psi_{circuit}$, then $\braket{\phi|H|\phi}=0$.
-If $\braket{\phi|\psi_{circuit}}=0$, then $\braket{\phi|H|\phi}>\beta>\frac{1}{\poly(T)}$.
+If $\braket{\phi|\psi_{circuit}}=0$, then $\braket{\phi|H|\phi}>\frac{3}{4}$.
 
@@
 $$D=\sum_{S\in\mathcal{G}_{XZ}}|d_S|$$
-$$p_S=\frac{|d_S|}{D}$$
+$$p_S=\frac{|d_S|}{D}=O(T^4)$$
 $$H'=\frac{H}{D}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)S$$
@@
 
+Now let $\ket\phi$ be such that $\braket{\phi|\psi_{circuit}}=0$.
+Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=1$ on $\ket\psi_{circuit}$ and $\ket\phi$ respectively.
+$$p_0=\frac{1}{2}$$
+$$\braket{\phi|H'|\phi}=\frac{1}{O(T^4)}\braket{\phi|H|\phi}=\Omega(T^{-4})$$
+$$\Rightarrow p_1=\frac{1}{2}+\Omega(T^{-4})$$
+
 \subsection{Analysis and amplification}
@@
 The client would keep a single copy for output, and use the other copies to check whether the computation is done properly.
-
-Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=-1$ on $\ket\psi_{circuit}$ and $\ket\phi$ respectively, where $\phi$ is perpendicular to $\psi_{circuit}$.
-Obviously, $p_0=\frac{1}{2}$, and $p_1<\frac{1}{2}$...
-TODO Now what?
-Hypothesis testing...?
+TODO Now what? Hypothesis testing...?
 

### 2019-09-14 longoutput.tex
Change wording

@@
 	\item Consists of only Hadamard and Toffoli gates
-	\item The last $\gamma$ of the gates are all identity gates (can easily achieve by padding)
+	\item The last $\gamma$ of the gates are all identity gates (easily achievable by padding)
 \end{itemize}
@@
 
-According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks. Furthermore, the second eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.
+According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks. Furthermore, the last nonzero eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.
 

### 2019-09-15 longoutput.tex
Make theorem statements

@@
 
-\subsection{Preprocessing circuit}
-
 We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
@@
 Which is proven to be universal in \cite{kitaev_1997}.
+
+\subsection{Preprocessing circuit}
+
+Here we construct a transform that we will use to... TODO Editorial intro.
+
+\begin{theorem}
+	Let $C$ be a circuit that:
+	\begin{itemize}
+		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
+		\item uses $n$ qubit, including ancillaries.
+	\end{itemize}
+	Then a classical machine, given $C$ and some classical $x$, can compute a circuit $C'$ and a classical string $x'$ that:
+	\begin{itemize}
+		\item $C'$ consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
+		\item $C'$ uses $n+1$ qubits.
+		\item All states are real (including initial, intermediate states, and output).
+		\item The measurement results of $C(x)$ and the first $n$ qubits of $C'(x')$ are identically distributed.
+	\end{itemize}
+\end{theorem}
+
+\begin{proof}
 
@@
 $$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
-We modify the circuit as appropriate to obtain $C'$ that has size $T'\leq 4T$. We prove a theorem about this circuit that we'll use later.
+\end{proof}
+
+Now we also prove a theorem about the circuit after transformation that we'll use later.
 
@@
 
-Let $C$ undergo the above transformations so it has the following properties
+\subsection{Constructing a local Hamiltonian instance}
+
+Here we reduce a circuit into a local Hamiltonian instance with a few additional properties as below.
+
+\begin{theorem}
+	Let $C$ be a circuit such that:
 	\begin{itemize}
-	\item All states are real (including initial, intermediate states, and output).
-	\item Consists of only Hadamard and Toffoli gates
-	\item The last $\gamma$ of the gates are all identity gates (easily achievable by padding)
+		\item $C=U_T\ldots U_1$, where $U_i$ are either $H$ or $\Lambda^2(X)$
 	\end{itemize}
+	Let $x$ be a classical string. Then a classical machine can construct in polynomial time a local Hamiltonian instance such that:
+	\begin{itemize}
+		\item its ground state is $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$ where $y$ is $x$ possibly concatenated with ancillaries.
+		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
+		\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
+		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
+	\end{itemize}
+\end{theorem}
 
-\subsection{Constructing a local Hamiltonian instance}
+\begin{proof}
 
@@
 \begin{itemize}
-	\item $C=U_T\ldots U_1$
-	\item Let $x$ be the circuit input. Which is classical.
 	\item Let $y$ denote the initial state. That is, $x$ possibly concatenated with ancillaries.
@@
 $$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
-So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$ to obtain the following properties.
-\begin{itemize}
-	\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
-	\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
-	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$. There are $O(T)$ nonzero components, whose coefficients are each at most $O(T^3)$.
-\end{itemize}
+So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
+\end{proof}
 

### 2019-09-15 longoutput.tex
Clean up and fix bugs
Do work that was required due to creating theorems

@@
 
-Here we construct a transform that we will use to... TODO Editorial intro.
+Here we construct a way to preprocess and simplify the circuit to a form that's easy for us to work with.
 
@@
 		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
-		\item uses $n$ qubit, including ancillaries.
+		\item uses $n$ qubit, counting ancillaries.
 	\end{itemize}
-	Then a classical machine, given $C$ and some classical $x$, can compute a circuit $C'$ and a classical string $x'$ that:
+	Then a classical machine given $C$ can compute a circuit $C'$ that:
 	\begin{itemize}
-		\item $C'$ consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
-		\item $C'$ uses $n+1$ qubits.
-		\item All states are real (including initial, intermediate states, and output).
-		\item The measurement results of $C(x)$ and the first $n$ qubits of $C'(x')$ are identically distributed.
+		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
+		\item uses $n+1$ qubits, counting ancillaries.
+		\item $\forall x\in\set{0,1}^*$, the $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x)$ are identically distributed.
 	\end{itemize}
@@
 \begin{proof}
+The proof is taken from \cite{quant-ph/0301040}. We consider the transform
+	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
+where $\Re$ and $\Im$ denote real and imaginary parts respectively. It is easy to check that this preserves $X$ and $Z$ measurement results.
 
-Now consider a circuit $C=U_T\ldots U_1$ with the following properties:
-\begin{itemize}
-	\item $U_i\in\set{H, \Lambda(P(i))}$
-	\item Has initial state $\ket\psi$ with $n$ qubits
-\end{itemize}
-
-We first reduce it to use only real gates and states. The proof is taken from \cite{quant-ph/0301040}. We consider the transform
-$$\mathcal{F}(\ket{\phi})=\ket{0}\otimes\Re\ket{\phi}+\ket{1}\otimes\Im\ket{\phi}$$
-where $\Re$ and $\Im$ denote real and imaginary parts respectively. It has the following properties
-
-\begin{itemize}
-	\item $\forall\ket\phi$, $\mathcal{F}(\ket\phi)$ is real.
-	\item Preserves $X$ and $Z$ measurement results
-\end{itemize}
-
-We now apply $\mathcal{F}$ to $\ket\psi$. To make the notation easier, let $\ket{\psi}$ be 1-indexed, and the $\mathcal{F}\ket{\psi}$ be 0-indexed, so corresponding qubits stay in the same position.
-
-The transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
+This transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
 $$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
@@
 
-Now we also prove a theorem about the circuit after transformation that we'll use later.
+Now we also prove a theorem about the transformed circuit that we'll use later.
 
@@
 
-To simplify the notation, we may only write the qubits with $X$ and $Z$ operators when talking about members of $\mathcal{G}_{XZ}$.
-
 \begin{theorem}
-	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$
+	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
 \end{theorem}
@@
 
-Here we reduce a circuit into a local Hamiltonian instance with a few additional properties as below.
+Here we reduce a circuit into a local Hamiltonian instance with a few additional properties.
 
 \begin{theorem}
-	Let $C$ be a circuit such that:
+	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time a local Hamiltonian instance such that:
 	\begin{itemize}
-		\item $C=U_T\ldots U_1$, where $U_i$ are either $H$ or $\Lambda^2(X)$
-	\end{itemize}
-	Let $x$ be a classical string. Then a classical machine can construct in polynomial time a local Hamiltonian instance such that:
-	\begin{itemize}
-		\item its ground state is $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$ where $y$ is $x$ possibly concatenated with ancillaries.
+		\item its ground state is $$\ket{\psi_{circuit}}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$ where $y$ is $x$ possibly concatenated with ancillaries.
 		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
@@
 \begin{proof}
+	We construct the Hamiltonian by ensuring states perpendicular to $\ket{\psi_{circuit}}$ have high eigenvalues.
+The base construction comes from \cite{kitaev2002classical}.
+The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.
 
-Let $C$ be a circuit with the above properties. Define the following quantities.
-\begin{itemize}
-	\item Let $y$ denote the initial state. That is, $x$ possibly concatenated with ancillaries.
-	\item Let $y_i$ denote the $i$-th bit of $y$
-	\item Let $n$ be the number of qubits in $C$
-\end{itemize}
-
-We then attempt to construct a local Hamiltonian with the following ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$
-We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.
+Let $y_i$ denote the $i$-th bit of $y$, and let $n$ be the number of qubits in $C$.
 
@@
 
-Now we consider the kernels of the Hamiltonians we defined. Notice the following.
+To properly combine the three Hamiltonians defined, we consider the kernels of the Hamiltonians we defined.
 $$K_{clock}=\ker H_{clock}$$
@@
 $$K_{prop}=\ker H_{prop}$$
-$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
+Notice that
+$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$$
 We now consider the space outside the desired state.
-$$S=(\spn\set{\psi_{circuit}})^\bot$$
+$$S=(\spn\set{\ket{\psi_{circuit}}})^\bot$$
 $$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$

### 2019-09-16 longoutput.tex
Add TODO for checking ground state
Need to decide to formulate it as a theorem or corollary
Make theorem for checking ground state

@@
 
-Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$.
+Now we put the above results in term of measurement outputs.
+
+\begin{theorem}
+	Let $$H\in\spn\mathcal{G}_{XZ}$$ with ground state $\psi$ with the following properties:
+	\begin{itemize}
+		\item $\braket{\psi|H|\psi}=0$
+		\item $\forall{\ket\phi}, \braket{\psi|\phi}=0\Rightarrow\braket{\phi|H|\phi}\geq\frac{3}{4}$
+		\item has $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
+	\end{itemize}
+	Then there exists an algorithm that accepts $\ket\psi$ with probabily $\frac{1}{2}$.
+Furthermore, for $\ket\phi$ where $\braket{\psi|\phi}=0$, it accepts with probability at most $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})$.
+This algorithm doesn't apply any quantum gates, and performs only $X$ and $Z$ measurements on the input state.
+\end{theorem}
+
 Here we follow \cite{PhysRevA.93.022326}.
-Note that if $\phi=\psi_{circuit}$, then $\braket{\phi|H|\phi}=0$.
-If $\braket{\phi|\psi_{circuit}}=0$, then $\braket{\phi|H|\phi}>\frac{3}{4}$.
 
-Since $H\in\spn\mathcal{G}_{XZ}$, we can write it as follows:
-$$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S= \sum_{S\in\mathcal{G}_{XZ}} |d_S|\sgn(d_S)S$$
-We then scale the Hamiltonian.
+We scale the Hamiltonian.
 $$D=\sum_{S\in\mathcal{G}_{XZ}}|d_S|$$
@@
 Which is simple to estimate by doing the measurements corresponding to $S$.
-Note that $H'=0$, but the measurement result is $\pm1$, so clearly we do not have perfect completeness.
-
-Now let $\ket\phi$ be such that $\braket{\phi|\psi_{circuit}}=0$.
-Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=1$ on $\ket\psi_{circuit}$ and $\ket\phi$ respectively.
-$$p_0=\frac{1}{2}$$
-$$\braket{\phi|H'|\phi}=\frac{1}{O(T^4)}\braket{\phi|H|\phi}=\Omega(T^{-4})$$
-$$\Rightarrow p_1=\frac{1}{2}+\Omega(T^{-4})$$
+The measurement result is $\pm1$, so it can be modeled as a bernoulli distribution with known expected value.
+The rest is simple number crunching.
+Note that $|d_S|=O(\poly(T))$.
 

### 2019-09-16 longoutput.tex
Fix bugs

@@
 \begin{theorem}
-	Let $$H\in\spn\mathcal{G}_{XZ}$$ with ground state $\psi$ with the following properties:
+	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$
+	with ground state $\psi$ with the following properties:
 	\begin{itemize}
@@
 $$D=\sum_{S\in\mathcal{G}_{XZ}}|d_S|$$
-$$p_S=\frac{|d_S|}{D}=O(T^4)$$
+$$p_S=\frac{|d_S|}{D}=O(\poly(T))$$
 $$H'=\frac{H}{D}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)S$$
@@
 $$\braket{\phi|H'|\phi}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}=\E_S[\sgn(d_S)\braket{\phi|S|\phi}]$$
-Which is simple to estimate by doing the measurements corresponding to $S$.
-The measurement result is $\pm1$, so it can be modeled as a bernoulli distribution with known expected value.
+Which is simple to estimate by picking and doing the measurements corresponding to $S$.
+The measurement result is $\pm1$.
+It can be modeled as a Bernoulli distribution with known expected value.
 The rest is simple number crunching.
-Note that $|d_S|=O(\poly(T))$.
-
 \subsection{Analysis and amplification}

### 2019-09-19 longoutput.tex
Wrap ground state check up as proof
Add TODOs from group discussion

@@
 Here we describe the scheme between the classical client and an honest quantum server.
-This is similar to the underlying construction for \cite{mahadev_delegation}.
+This is similar to the underlying construction of \cite{mahadev_delegation}.
 We first preprocess the circuit using tools such as \cite{quant-ph/0301040}.
@@
 Then, NYI cuz we're stuck.
+\hannote{be more explicit}
 
@@
 Here we construct a way to preprocess and simplify the circuit to a form that's easy for us to work with.
+
+\KM{just use $n$ qubit input. no need to distinguish input vs ancilla at this point}
 
@@
 \begin{proof}
+\KM{prove what you claimed in the theorem.}
+
 The proof is taken from \cite{quant-ph/0301040}. We consider the transform
@@
 
+\KM{again, we don't need to make anccila explicit here}
 \begin{theorem}
-	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time a local Hamiltonian instance such that:
+	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$.
+Then a classical machine can construct in polynomial time a local Hamiltonian instance $H_{circuit}$ such that:
 	\begin{itemize}
@@
 		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
-		\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
+		\item \KM{TODO} $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
 		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
@@
 \end{theorem}
+\begin{proof}
 
@@
 The rest is simple number crunching.
+\end{proof}
+
 \subsection{Analysis and amplification}

### 2019-09-20 longoutput.tex
Start processing discussion results

@@
 
-Here we construct a way to preprocess and simplify the circuit to a form that's easy for us to work with.
-
-\KM{just use $n$ qubit input. no need to distinguish input vs ancilla at this point}
+In order to estimate the energy of a Hamiltonian using only $X$ and $Z$ measurements, the gates in the circle must be combinations of $X$ and $Z$ matrices.
+To begin, we apply a transformation to the circuit to use only real states and gates.
+This transform is taken from \cite{quant-ph/0301040}.
 
@@
 		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
-		\item uses $n$ qubit, counting ancillaries.
+		\item uses $n$ qubits
 	\end{itemize}
@@
 		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
-		\item uses $n+1$ qubits, counting ancillaries.
-		\item $\forall x\in\set{0,1}^*$, the $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x)$ are identically distributed.
+		\item uses $n+1$ qubits
+		\item Let $x\in\set{0,1}^n$, and $x||0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
+The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
 	\end{itemize}
@@
 \begin{proof}
-\KM{prove what you claimed in the theorem.}
 
-The proof is taken from \cite{quant-ph/0301040}. We consider the transform
+Consider the transform on quantum states
 	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
-where $\Re$ and $\Im$ denote real and imaginary parts respectively. It is easy to check that this preserves $X$ and $Z$ measurement results.
+where $\Re$ and $\Im$ denote real and imaginary parts respectively.
 
-This transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
+This transform commutes with Hadamard gates on the respective qubit.
+On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turn it into a combination of Hadamard and Toffoli gates.
+Mathematically,
 $$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
 $$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
+
+We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
+\begin{itemize}
+	\item $C'$ uses only Hadamard and Toffoli gates.
+	\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
+	\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple to verify that $F$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
 \end{proof}
 
-Now we also prove a theorem about the transformed circuit that we'll use later.
+We verify that our new gate set can be written as combinations of $X$ and $Z$ matrices.
 
@@
 
-\KM{again, we don't need to make anccila explicit here}
 \begin{theorem}
@@
 	\begin{itemize}
-		\item its ground state is $$\ket{\psi_{circuit}}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$ where $y$ is $x$ possibly concatenated with ancillaries.
+		\item its ground state is $$\ket{\psi_{circuit}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
 		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
-		\item \KM{TODO} $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
+		\item $\forall\ket\phi,\braket{\phi|\psi_{circuit}}=0\Rightarrow\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$
 		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
@@
 
-Let $y_i$ denote the $i$-th bit of $y$, and let $n$ be the number of qubits in $C$.
+Let $x_i$ denote the $i$-th bit of $x$, and let $n$ be the number of qubits in $C$.
 
@@
 Then, we ensure that the initial condition is set up correctly.
-$$H_{in}=\sum_{i=1}^n(I-\ket{y_i}\bra{y_i})\otimes\ket{0}\bra{0}_1$$
+$$H_{in}=\sum_{i=1}^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
 The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
-$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{y_i}Z_i)\otimes(I+Z_1)$$
+$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$
 
@@
 $$K_{prop}=\ker H_{prop}$$
-Notice that
+Notice that (TODO Need proof)
 $$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$$
@@
 \lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
+TODO Here are some steps here that need to be spelled out
 $$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
@@
 The rest is simple number crunching.
+
+TODO Above is NOT just simple number crunching. Type it out.
 \end{proof}

### 2019-09-21 longoutput.tex
Fix bug
Fix wording
Start typing ground state checking algorithm
Rewrite ground state check theorem statement

@@
 		\item uses $n+1$ qubits
-		\item Let $x\in\set{0,1}^n$, and $x||0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
+		\item Let $x\in\set{0,1}^n$.
+Let $x||0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
 The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
@@
 	\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple to verify that $F$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
+\end{itemize}
 \end{proof}
@@
 \begin{theorem}
-	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$
-	with ground state $\psi$ with the following properties:
-	\begin{itemize}
-		\item $\braket{\psi|H|\psi}=0$
-		\item $\forall{\ket\phi}, \braket{\psi|\phi}=0\Rightarrow\braket{\phi|H|\phi}\geq\frac{3}{4}$
-		\item has $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
-	\end{itemize}
-	Then there exists an algorithm that accepts $\ket\psi$ with probabily $\frac{1}{2}$.
-Furthermore, for $\ket\phi$ where $\braket{\psi|\phi}=0$, it accepts with probability at most $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})$.
-This algorithm doesn't apply any quantum gates, and performs only $X$ and $Z$ measurements on the input state.
+	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$ with  $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
+	Then there exists an algorithm that accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
+This algorithm performs only $X$ and $Z$ measurements on $\ket\phi$, and is classical otherwise.
 \end{theorem}
@@
 
-We scale the Hamiltonian.
-$$D=\sum_{S\in\mathcal{G}_{XZ}}|d_S|$$
-$$p_S=\frac{|d_S|}{D}=O(\poly(T))$$
-$$H'=\frac{H}{D}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)S$$
+\begin{algorithm}
+	\caption{Check for ground state}
+	\begin{algorithmic}[1]
+		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
+		\State $p_S=\frac{|d_S|}{D}$
+		\State $\tilde{S}\gets$ Pick weighted using $p_S$
+		\State $\lambda_{\tilde{S}}\gets$ Measure $\ket\phi$ in the $\tilde{S}$ basis
+		\If{$\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=-1$}
+			\State Accept
+		\Else
+			\State Reject
+		\EndIf
+	\end{algorithmic}
+\end{algorithm}
 
-Note that $H'$ is now a weighted sum of measurement operators.
-We also have $0\leq p_S\leq1$ and $\sum_{S\in\mathcal{G}_{XZ}} p_S=1$, so we can treat it as a probability distribution over the choice of $S$.
-$$\braket{\phi|H'|\phi}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}=\E_S[\sgn(d_S)\braket{\phi|S|\phi}]$$
-Which is simple to estimate by picking and doing the measurements corresponding to $S$.
-The measurement result is $\pm1$.
-It can be modeled as a Bernoulli distribution with known expected value.
-The rest is simple number crunching.
+\begin{align*}
+	\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
+	&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
+	&=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\E[\lambda_{\tilde{S}}]]\\
+	&=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]
+\end{align*}
 
-TODO Above is NOT just simple number crunching. Type it out.
+Note that $\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=-1$.
+
+$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]=-p+(1-p)$$
+\begin{align*}
+	\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
+	&=\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}
+\end{align*}
+
 \end{proof}

### 2019-09-21 longoutput.tex
Start lemma on intersecting kernels

@@
 $$K_{prop}=\ker H_{prop}$$
+It is clear that $K_{clock}$ consists of the states with time registers of the form $\ket{\hat{t}}$.
+
+\begin{lemma}
+	Some lemma on K clock and K prop
+\end{lemma}
+
+\begin{proof}
+	Proof of above lemma
+\end{proof}
+
 Notice that (TODO Need proof)

### 2019-09-22 longoutput.tex
Resolve TODOs on kernel intersections

@@
 \begin{definition}
-	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n|U_i\in\set{I,X,Z}}$.
+	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n\colon U_i\in\set{I,X,Z}}$.
 \end{definition}
@@
 \begin{lemma}
-	Some lemma on K clock and K prop
+	$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}\colon \ket{y}\in\mathcal{B}^{\otimes n}}$$
 \end{lemma}
@@
 \begin{proof}
-	Proof of above lemma
+	Let $\ket\phi\in K_{clock}\cap K_{prop}$.
+As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations.
+Now nonsider some $\tilde{t}$ such that $\ket\phi\bra{\tilde{t}}\ne0$.
+As $\ket\phi\in K_{prop}$, we can then say that $\ket\phi\bra{\tilde{t+1}}=U_{t+1}\ket\phi\bra{\tilde{t}}$ for $t\ne T$, and $\ket\phi\bra{\tilde{t}}=U_t\ket\phi\bra{\tilde{t-1}}$ for $t\ne0$.
+So we can obtain the required statement by induction.
 \end{proof}
 
-Notice that (TODO Need proof)
-$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$$
+\begin{corollary}
+	$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$
+\end{corollary}
+
 We now consider the space outside the desired state.
@@
 \lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
-TODO Here are some steps here that need to be spelled out
+\begin{align*}
+	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
+	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}\colon\braket{x|y}=0}
+\end{align*}
 $$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$

### 2019-09-22 longoutput.tex
Start working on amplification proof

@@
 
-We then follow \cite{mahadev_delegation}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
+A honest server can then commit copies of the ground state of the Hamiltonian for the classical client to measure.
 The client would keep a single copy for output, and use the other copies to check whether the computation is done properly.
-TODO Now what? Hypothesis testing...?
+Here we analyze what happens if the server is dishonest.
+We assume that the verifier can possess qubits and do $X$ and $Z$ measurements, but is classical otherwise.
+
+\begin{theorem}
+Let $H$ be a local Hamiltonian with the following properties:
+\begin{itemize}
+	\item Ground state...?
+	\item $\frac{3}{4}$?
+\end{itemize}
+Then, (some theorem statement)
+\end{theorem}
+\begin{proof}
+	Let $\phi_i$ be the eigenbasis of $H$.
+Then we can decomposite what the prover sends the verifier as $$\sum_I \alpha_I \ket{\phi_{i_1}}\otimes\ket{\phi_{i_2}}\otimes\ldots\otimes\ket{\phi_{i_{TODO}}}$$.
+\end{proof}
 

### 2019-09-22 longoutput.tex
Change colon typeset
Do more work on the amplification

@@
 \begin{definition}
-	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n\colon U_i\in\set{I,X,Z}}$.
+	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$.
 \end{definition}
@@
 \begin{lemma}
-	$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}\colon \ket{y}\in\mathcal{B}^{\otimes n}}$$
+	$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
 \end{lemma}
@@
 	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
-	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}\colon\braket{x|y}=0}
+	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{x|y}=0}
 \end{align*}
@@
 
-\begin{theorem}
+\begin{theorem}\label{ThmXZCheck}
 	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$ with  $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
@@
 \begin{theorem}
-Let $H$ be a local Hamiltonian with the following properties:
+Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
 \begin{itemize}
-	\item Ground state...?
-	\item $\frac{3}{4}$?
+	\item has $t$ terms
+	\item acts on $q$ qubits
+	\item Ground state $0$...?
+	\item Something something $\frac{3}{4}$?
 \end{itemize}
-Then, (some theorem statement)
+Then, the prover would send the client $n=O(\poly(t))$ copies... TODO
 \end{theorem}
 \begin{proof}
-	Let $\phi_i$ be the eigenbasis of $H$.
-Then we can decomposite what the prover sends the verifier as $$\sum_I \alpha_I \ket{\phi_{i_1}}\otimes\ket{\phi_{i_2}}\otimes\ldots\otimes\ket{\phi_{i_{TODO}}}$$.
+Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$.
+Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)}$ for $i\ne1$.
+We now decomposite what the prover sends in this basis.
+$$\sum_I \alpha_I \ket{\phi_{i_1}}\otimes\ket{\phi_{i_2}}\otimes\ldots\otimes\ket{\phi_{i_q}}$$
+We categorize the indices $I$ into three types, based on how many $1$s it contains.
+First kind contains all $1$s.
+Second contains so little $1$s that...
+something something Chernoff bound...
+And the third kind contains the rest.
+
 \end{proof}

### 2019-09-22 longoutput.tex
Add TODOs for amplification
Fix typo

@@
 	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
-	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{x|y}=0}
+	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{circuit}|y}=0}
 \end{align*}
@@
 
+$$TODO SOME STATE$$
+$$TODO SUM UP COEFFS$$
+
+Then apply \autoref{ThmXZCheck}. By the linearity of expected values, the number of accepted qubits should be around...
+
+TODO What about Chernoffs???
+
 \end{proof}

### 2019-09-23 longoutput.tex
Type up multi-indices for amplification

@@
 	\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
-	&=\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}
+	&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
 \end{align*}
@@
 \end{itemize}
-Then, the prover would send the client $n=O(\poly(t))$ copies... TODO
+Then, with the input, if honest is $n=O(\poly(t))$... TODO
 \end{theorem}
@@
 Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$.
-Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)}$ for $i\ne1$.
-We now decomposite what the prover sends in this basis.
-$$\sum_I \alpha_I \ket{\phi_{i_1}}\otimes\ket{\phi_{i_2}}\otimes\ldots\otimes\ket{\phi_{i_q}}$$
-We categorize the indices $I$ into three types, based on how many $1$s it contains.
-First kind contains all $1$s.
-Second contains so little $1$s that...
-something something Chernoff bound...
-And the third kind contains the rest.
+Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})$ for $i\ne1$.
+We now decomposite the input in this basis.
+We consider the Chernoff bound on...
+Man these variables are a pain to set up.
+Let's just say the result is $B$.
+Let $\mathcal{I}=\mathbb{Z}_q^n$ be a collection of multi-indices.
+We partition the multi-indices into three types.
+$$\mathcal{I}=\mathcal{I}_1\sqcup \mathcal{I}_2\sqcup \mathcal{I}_3$$
+$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
+$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq B}$$
 
-$$TODO SOME STATE$$
-$$TODO SUM UP COEFFS$$
+Then we can write the input (?) as follows.
+$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
+$$b=\sum_{J\in\mathcal{I}_2}\beta_J^2$$
+$$c=\sum_{J\in\mathcal{I}_3}\gamma_J^2$$
 

### 2019-09-23 longoutput.tex
Start setting up Chernoff bound

@@
 Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$.
-Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})$ for $i\ne1$.
+Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})=p'$ for $i\ne1$.
 We now decomposite the input in this basis.
-We consider the Chernoff bound on...
-Man these variables are a pain to set up.
-Let's just say the result is $B$.
-Let $\mathcal{I}=\mathbb{Z}_q^n$ be a collection of multi-indices.
+
+Fix $\frac{1}{2}<B<p'$. Consider the Chernoff bound.
+
+Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices. That is, we decomposite the input as
+$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$
+
 We partition the multi-indices into three types.
-$$\mathcal{I}=\mathcal{I}_1\sqcup \mathcal{I}_2\sqcup \mathcal{I}_3$$
 $$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
 $$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq B}$$
+$$\mathcal{I}_2=\mathcal{I}\setminus\mathcal{I}_1\setminus\mathcal{I}_3$$
 
@@
 $$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
-$$b=\sum_{J\in\mathcal{I}_2}\beta_J^2$$
-$$c=\sum_{J\in\mathcal{I}_3}\gamma_J^2$$
+	$$b=\sum_{J\in\mathcal{I}_2}\beta_J\overline{\beta_J}$$
+	$$c=\sum_{J\in\mathcal{I}_3}\gamma_J\overline{\gamma_J}$$
 

### 2019-09-23 longoutput.tex
Use auto-indent
Fix typo
Fix another typo
Fix mistake in kernel proof

@@
 
-According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks. Furthermore, the last nonzero eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.
+	According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks.
+Furthermore, the last nonzero eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.
 
@@
 As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations.
-Now nonsider some $\tilde{t}$ such that $\ket\phi\bra{\tilde{t}}\ne0$.
-As $\ket\phi\in K_{prop}$, we can then say that $\ket\phi\bra{\tilde{t+1}}=U_{t+1}\ket\phi\bra{\tilde{t}}$ for $t\ne T$, and $\ket\phi\bra{\tilde{t}}=U_t\ket\phi\bra{\tilde{t-1}}$ for $t\ne0$.
+Now consider some $\widetilde{t}$ such that $\bra{\widetilde{t}}\ket\phi\ne0$.
+As $\ket\phi\in K_{prop}$, we can then say that $\bra{\widetilde{t+1}}\ket\phi=\bra{\widetilde{t}}U_{t+1}\ket\phi$ for $t\ne T$, and $\bra{\widetilde{t}}\ket\phi=U_t\bra{\widetilde{t-1}}\ket\phi$ for $t\ne0$.
 So we can obtain the required statement by induction.
@@
 			\State $p_S=\frac{|d_S|}{D}$
-		\State $\tilde{S}\gets$ Pick weighted using $p_S$
-		\State $\lambda_{\tilde{S}}\gets$ Measure $\ket\phi$ in the $\tilde{S}$ basis
-		\If{$\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=-1$}
+			\State $\widetilde{S}\gets$ Pick weighted using $p_S$
+			\State $\lambda_{\widetilde{S}}\gets$ Measure $\ket\phi$ in the $\widetilde{S}$ basis
+			\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
 			\State Accept
@@
 		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
-	&=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\E[\lambda_{\tilde{S}}]]\\
-	&=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]
+		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
+		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
 	\end{align*}
 
-Note that $\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=-1$.
+	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
 
-$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]=-p+(1-p)$$
+	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
 	\begin{align*}
@@
 Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})=p'$ for $i\ne1$.
-We now decomposite the input in this basis.
+We now decompose the input in this basis.
 
@@
 
-Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices. That is, we decomposite the input as
+	Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices. That is, we decompose the input as
 	$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$

### 2019-09-23 longoutput.tex
Change Chernoff bound variables

@@
 	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
-
 $$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
@@
 	Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$.
-Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})=p'$ for $i\ne1$.
+Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Delta$ for $i\ne1$, where $\Delta=\Omega\left(\frac{1}{\poly(t)}\right)$.
 We now decompose the input in this basis.
-
-	Fix $\frac{1}{2}<B<p'$. Consider the Chernoff bound.
-
-	Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices. That is, we decompose the input as
+Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices.
 	$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$
-
-	We partition the multi-indices into three types.
+	Fix $\delta<2\Delta$ and partition the multi-indices into three types.
 	$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
-	$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq B}$$
+	$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq 2\delta n}$$
 	$$\mathcal{I}_2=\mathcal{I}\setminus\mathcal{I}_1\setminus\mathcal{I}_3$$
 
-	Then we can write the input (?) as follows.
+	Apply Chernoff bound to $\frac{1}{2}-\delta$. There is overwhelming probability that...
+	By Chernoff bound, there is overwhelming probability that...  Then we can write the input (?) as follows.
 	$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$

### 2019-09-23 longoutput.tex
Apply Chernoff's

@@
 
-\begin{theorem}\label{ThmXZCheck}
-	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$ with  $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
-	Then there exists an algorithm that accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
-This algorithm performs only $X$ and $Z$ measurements on $\ket\phi$, and is classical otherwise.
-\end{theorem}
-\begin{proof}
-
-	Here we follow \cite{PhysRevA.93.022326}.
-
 \begin{algorithm}
 	\caption{Check for ground state}
+	\label{AlgGroundStateCheck}
 	\begin{algorithmic}[1]
+		\Require $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$
+		\Procedure{GroundStateCheck}{$\ket\phi$}
 		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
@@
 		\EndIf
+		\EndProcedure
 	\end{algorithmic}
@@
 
+\begin{theorem}\label{ThmXZCheck}
+	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
+	Then \autoref{AlgGroundStateCheck} accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
+\end{theorem}
+\begin{proof}
+
+	Here we follow \cite{PhysRevA.93.022326}.
 	\begin{align*}
@@
 	$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$
-	Fix $\delta<2\Delta$ and partition the multi-indices into three types.
+	Fix $\delta<2\Delta$ and let $B=\frac{1}{2}-\delta$. Partition the multi-indices into three types.
 	$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
@@
 
-	Apply Chernoff bound to $\frac{1}{2}-\delta$. There is overwhelming probability that...
-	By Chernoff bound, there is overwhelming probability that...  Then we can write the input (?) as follows.
+	Apply \autoref{AlgGroundStateCheck} to every register of $\ket{\phi_1^{\otimes n}}$.
+By Chernoff bound, there is overwhelming (as $n$ grows) probability that more than $Bn$ registers are accepted.
+On the other hand, take $J\in\mathcal{I}_3$ and do the same to every register of $\ket{\phi_J}$.
+By Chernoff bound, there is overwhelming probability that less than $Bn$ registers are accepted.
+
+	Now also define the following.
 	$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
@@
 	Then apply \autoref{ThmXZCheck}. By the linearity of expected values, the number of accepted qubits should be around...
-
-	TODO What about Chernoffs???
+	TODO Does this actually work?
 

### 2019-09-23 longoutput.tex
Simplify wording
Fix logic flow

@@
 	$$\mathcal{I}_2=\mathcal{I}\setminus\mathcal{I}_1\setminus\mathcal{I}_3$$
+	We can then write the input state as follows.
+	$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
 
@@
 On the other hand, take $J\in\mathcal{I}_3$ and do the same to every register of $\ket{\phi_J}$.
-By Chernoff bound, there is overwhelming probability that less than $Bn$ registers are accepted.
+With overwhelming probability, less than $Bn$ registers are accepted.
 
 	Now also define the following.
-	$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
 	$$b=\sum_{J\in\mathcal{I}_2}\beta_J\overline{\beta_J}$$

### 2019-10-12 longoutput.tex
Clarify weights definition
Fix indentations
Fix typo in algorithm
Add work on amplification
Write down new flow of logic

--- 2019-09-23 longoutput.tex
@@
 		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
-		\State $p_S=\frac{|d_S|}{D}$
+		\State $p_S\gets\frac{|d_S|}{D}$
 		\State $\widetilde{S}\gets$ Pick weighted using $p_S$
@@
 	Then, with the input, if honest is $n=O(\poly(t))$... TODO
+
+	Client sends $N$ copies...
 \end{theorem}
 \begin{proof}
-	Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$.
-Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Delta$ for $i\ne1$, where $\Delta=\Omega\left(\frac{1}{\poly(t)}\right)$.
-We now decompose the input in this basis.
-Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices.
-	$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$
-	Fix $\delta<2\Delta$ and let $B=\frac{1}{2}-\delta$. Partition the multi-indices into three types.
-	$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
-	$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq 2\delta n}$$
-	$$\mathcal{I}_2=\mathcal{I}\setminus\mathcal{I}_1\setminus\mathcal{I}_3$$
+	Let $\set{\ket{\phi_1},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$.
+	Then $\ket{\phi_1}$ has eigenvalue $\lambda_1=0$, and $\ket{\phi_j}$ has eigenvalues $\lambda_j\geq\tilde\lambda$ for $j>1$.
 
-	Apply \autoref{AlgGroundStateCheck} to every register of $\ket{\phi_1^{\otimes n}}$.
-By Chernoff bound, there is overwhelming (as $n$ grows) probability that more than $Bn$ registers are accepted.
-On the other hand, take $J\in\mathcal{I}_3$ and do the same to every register of $\ket{\phi_J}$.
-By Chernoff bound, there is overwhelming probability that less than $Bn$ registers are accepted.
+	Consider
+	$$\sum_{j=1}^nH^j$$
+	Where $H^j$ denotes $H$ acting on the $j$th qubit. So it has eigenbasis $\ket{\phi_J}$ for some multi-index $J$ with corresponding eigenvalue
+	$$\sum_{i\in J}\lambda_i$$
 
-	Now also define the following.
-	$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
-	$$b=\sum_{J\in\mathcal{I}_2}\beta_J\overline{\beta_J}$$
-	$$c=\sum_{J\in\mathcal{I}_3}\gamma_J\overline{\gamma_J}$$
+	Now fix $\delta$ and define $n_c=\delta N$, $n_b=2n_c=2\delta N$.
+	If more than $n_b$ registers reject, then with overwhelming probability bad state...
+	Otherwise eigenvalue < $n_c$?
 
-	Then apply \autoref{ThmXZCheck}. By the linearity of expected values, the number of accepted qubits should be around...
-	TODO Does this actually work?
+	Then done?
 

### 2019-10-15 longoutput.tex
Write first draft for amplification

@@
 
-A honest server can then commit copies of the ground state of the Hamiltonian for the classical client to measure.
-The client would keep a single copy for output, and use the other copies to check whether the computation is done properly.
-Here we analyze what happens if the server is dishonest.
-We assume that the verifier can possess qubits and do $X$ and $Z$ measurements, but is classical otherwise.
+In the case for decision problems, amplifying the gap between acceptance and rejection probabilities is trivial.
+As seen in \cite{kitaev2002classical}, the prover, honest or not, cannot do better than sending $n$ identical copies of some state.
+As a result, a simple Chernoff bound would suffice.
+The same reasoning does not generalize trivially to our case, so instead we give the following proof.
+
+Suppose $\mathcal{F}$ accepts $\ket{\psi}$ with probability $\frac{1}{2}$, and any states perpendicular to it with probability $\frac{1}{2}-\Delta$.
+We start by considering simpler inputs before moving to the general case.
+
+Pick $\varepsilon>0$ as the error parameter to amplify to.
+
+Pick $n\in\mathbb{N}$ so that by Chernoff bound:
+\begin{itemize}
+	\item $\ket{\psi^{\otimes n}}$ is accepted with overwhelming probability.
+	\item If $\mathcal{F}(\ket{\phi})$ has less than $\frac{1}{2}-\varepsilon$ accept probability, then $\ket{\phi^{\otimes n}}$ is rejected with overwhelming probability.
+\end{itemize}
+
+\begin{algorithm}
+	\caption{Amplification with simple input}
+	\label{AlgAmp1}
+	\begin{algorithmic}[1]
+		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+1}}\bra{\rho_i^{\otimes n+1}}$
+		\Procedure{SimpleAmplification}{$\phi$}
+		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
+		\If{number of accepted copies $\geq \frac{1}{2}-\varepsilon$}
+			\State Output the last register
+		\Else
+			\State Reject
+		\EndIf
+		\EndProcedure
+	\end{algorithmic}
+\end{algorithm}
 
 \begin{theorem}
-	Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
-	\begin{itemize}
-		\item has $t$ terms
-		\item acts on $q$ qubits
-		\item Ground state $0$...?
-		\item Something something $\frac{3}{4}$?
-	\end{itemize}
-	Then, with the input, if honest is $n=O(\poly(t))$... TODO
-
-	Client sends $N$ copies...
+	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, its output when accepted has negligible probability to be rejected by $\mathcal{F}$.
 \end{theorem}
 \begin{proof}
-	Let $\set{\ket{\phi_1},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$.
-	Then $\ket{\phi_1}$ has eigenvalue $\lambda_1=0$, and $\ket{\phi_j}$ has eigenvalues $\lambda_j\geq\tilde\lambda$ for $j>1$.
+	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+1}}$ with $w_i$ as weights.
 
-	Consider
-	$$\sum_{j=1}^nH^j$$
-	Where $H^j$ denotes $H$ acting on the $j$th qubit. So it has eigenbasis $\ket{\phi_J}$ for some multi-index $J$ with corresponding eigenvalue
-	$$\sum_{i\in J}\lambda_i$$
+	Let $q_i$ be the accept probability of $\ket{\rho_i^{\otimes n+1}}$ under \autoref{AlgAmp1}.
 
-	Now fix $\delta$ and define $n_c=\delta N$, $n_b=2n_c=2\delta N$.
-	If more than $n_b$ registers reject, then with overwhelming probability bad state...
-	Otherwise eigenvalue < $n_c$?
+	By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+1}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.
 
-	Then done?
+	Let $J=\set{j:\mathcal{F}(\ket{\rho_j})<\frac{1}{2}-\varepsilon}$.
 
+	$\Rightarrow\forall j\in J$, $q_j$ is negligible.
+
+	$\Rightarrow\sum_{j\in J} w_j q_j$ is negligible, since $\sum_i w_i=1$.
+
+	$\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}$ is negligible, since $\sum_i w_i q_i>\delta$ is not negligible.
 \end{proof}

### 2019-10-15 paper.tex
Write the ground state check
Fix underfull hbox
Do more work on longoutput
Use projection lemma
Make references clickable
Add TODOs from group discussion
Start typing ground state checking algorithm
Start lemma on intersecting kernels
Resolve TODOs on kernel intersections
Apply Chernoff's
Write first draft for amplification
Switch affiliation to NTU

@@
 \usepackage{braket}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\newcommand{\sgn}{\operatorname{sgn}}
+\DeclareMathOperator*{\E}{\mathbb{E}}
+\DeclareMathOperator*{\spn}{\operatorname{span}}
+\DeclareMathOperator*{\poly}{\operatorname{poly}}
+\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
+\usepackage{etoolbox}
+\usepackage{hyperref}
+\newcommand{\algorithmautorefname}{Algorithm}
+\apptocmd{\thebibliography}{\raggedright}{}{}
+\usepackage{cite,color,float}
+
+\newcommand{\KM}[1]{{\footnotesize\color{cyan}[KM: #1]}}
 
@@
 \newtheorem{definition}{Definition}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{observation}[theorem]{Observation}
 
@@
 \author[1]{Kai-Min Chung}
-\author[1]{Yi Lee}
-\author[2]{Han-Hsuan Lin}
-\author[3]{Xiaodi Wu}
-\affil[1]{Institute of Information Science, Academia Sinica, Taipei, Taiwan}
-\affil[2]{Department of Computer Science, University of Texas at Austin}
-\affil[3]{
+\author[2]{Yi Lee}
+\author[3]{Han-Hsuan Lin}
+\author[4]{Xiaodi Wu}
+\affil[1]{Institute of Information Science, Academia Sinica, Taiwan}
+\affil[2]{Department of Physics, National Taiwan University, Taiwan}
+\affil[3]{Department of Computer Science, University of Texas at Austin, USA}
+\affil[4]{
 	Department of Computer Science, Institute for Advanced Computer Studies,
@@
 }
-
+\input{macros.tex}
 \begin{document}

### 2019-10-15 longoutput.tex
Add reference on de Finetti
Write a bit on de Finetti

@@
 In the case for decision problems, amplifying the gap between acceptance and rejection probabilities is trivial.
-As seen in \cite{kitaev2002classical}, the prover, honest or not, cannot do better than sending $n$ identical copies of some state.
+As seen in \cite{kitaev2002classical}, a prover, honest or not, cannot do better than sending $n$ identical copies of some state.
 As a result, a simple Chernoff bound would suffice.
-The same reasoning does not generalize trivially to our case, so instead we give the following proof.
+The same reasoning does not generalize to our case, so instead we give the following proof.
 
@@
 
+Now we consider the general case.
+We use \autoref{deFinetti}.
+Let $n=l$ and $N=k=\poly(l)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily small.
+That is, with some arbitrarily small error in measurement results, we can assume without the loss of generality that the client receives an input of the simple form above.
+Hence concludes the proof.
+
 \subsection{Getting the Output}

### 2019-10-15 preliminaries.tex
Do more work on longoutput
Use projection lemma
Write a bit on de Finetti

@@
 Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.
+\begin{theorem}
+	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$.
+	$$\exists J=\frac{\poly(\norm{H_1})}{\lambda(H_2|_{K^\bot})}$$
+	$$\lambda(H_1+JH_2)\geq\lambda(H_1\big|_K)-\frac{1}{8}$$
+\end{theorem}
 
-Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
-Then $\exists J\in\mathbb{R}$ s.t.
-$\lambda(H_1\big|_S)-\frac{1}{8}\leq
-	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.
+\subsection{Quantum de Finetti Theorem under Local Measurements}
+
+Here is a theorem taken from \cite{Brandão2017}.
+\begin{theorem}
+	\label{deFinetti}
+	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there is a measure $\nu$ on $D(A)$ such that
+	$$\max_{\Lambda_2,\ldots,\Lambda_l\in\mathcal{M}}\norm{(id\otimes\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\int \nu(d\sigma)\sigma^{\otimes l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
+\end{theorem}

### 2019-10-15 longoutput.tex
Update output subsection
Finish first draft of output subsection

@@
 	\begin{algorithmic}[1]
-		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+1}}\bra{\rho_i^{\otimes n+1}}$
+		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
 		\Procedure{SimpleAmplification}{$\phi$}
@@
 		\If{number of accepted copies $\geq \frac{1}{2}-\varepsilon$}
-			\State Output the last register
+			\State Output the last $m$ registers
 		\Else
@@
 \begin{proof}
-	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+1}}$ with $w_i$ as weights.
+	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.
 
-	Let $q_i$ be the accept probability of $\ket{\rho_i^{\otimes n+1}}$ under \autoref{AlgAmp1}.
+	Let $q_i$ be the accept probability of $\ket{\rho_i^{\otimes n+m}}$ under \autoref{AlgAmp1}.
 
-	By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+1}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.
+	By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.
 
@@
 Thanks to having padded the circuit with identity matrices at the end, if we measured $t>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
-Now I would analyze the chances of getting this right, maybe in terms of fidelity or in terms of distance between this measured distribution and the ideal distribution...
+So simply take $m$ to be high enough that it happens at least once with overwhelming probability.
+When it does, measure the entire register.
+All the errors up to this point are $O(\varepsilon)$, so will be the distance between this output distribution and the true one.

### 2019-10-15 longoutput.tex
Clean up amplification

@@
 
-Pick $\varepsilon>0$ as the error parameter to amplify to.
-
-Pick $n\in\mathbb{N}$ so that by Chernoff bound:
+Let $\varepsilon>0$, $p>0$. Pick $n\in\mathbb{N}$ so that by Chernoff bound:
 \begin{itemize}
-	\item $\ket{\psi^{\otimes n}}$ is accepted with overwhelming probability.
-	\item If $\mathcal{F}(\ket{\phi})$ has less than $\frac{1}{2}-\varepsilon$ accept probability, then $\ket{\phi^{\otimes n}}$ is rejected with overwhelming probability.
+	\item $\ket{\psi^{\otimes n}}$ is rejected with probability at most $1-p$.
+	\item If $\mathcal{F}(\ket{\phi})$ has less than $\frac{1}{2}-\varepsilon$ accept probability, then $\ket{\phi^{\otimes n}}$ is accepted with probability at most $p$.
 \end{itemize}
@@
 
+\begin{observation}
+	If the input is of the form $\ket{\phi^{\otimes n+m}}$, \autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers.
+\end{observation}
+
 \begin{theorem}
-	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, its output when accepted has negligible probability to be rejected by $\mathcal{F}$.
+	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, its output when accepted has $\frac{p}{\delta}$ to be rejected by $\mathcal{F}$.
 \end{theorem}
@@
 
-	Let $q_i$ be the accept probability of $\ket{\rho_i^{\otimes n+m}}$ under \autoref{AlgAmp1}.
-
-	By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.
+	Let $q_j$ be the accept probability of $\ket{\rho_j^{\otimes n+m}}$ under \autoref{AlgAmp1}.
+By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_j^{\otimes n+m}}$ is then $\frac{w_j q_j}{\sum_i w_i q_i}$.
 
@@
 
-	$\Rightarrow\forall j\in J$, $q_j$ is negligible.
+	$\Rightarrow\forall j\in J$, $q_j<p$.
 
-	$\Rightarrow\sum_{j\in J} w_j q_j$ is negligible, since $\sum_i w_i=1$.
+	$\Rightarrow\sum_{j\in J} w_j q_j<p$, since $\sum_i w_i=1$.
 
-	$\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}$ is negligible, since $\sum_i w_i q_i>\delta$ is not negligible.
+	$\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}<\frac{p}{\delta}$.
 \end{proof}
@@
 We use \autoref{deFinetti}.
-Let $n=l$ and $N=k=\poly(l)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily small.
+Let $n=l$ and $k=\poly(n)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily small.
 That is, with some arbitrarily small error in measurement results, we can assume without the loss of generality that the client receives an input of the simple form above.

### 2019-10-15 longoutput.tex
Fix overfull hbox
Add TODO to clarify output subsection
Change TODOs to note macros
Fix typo
Rename procedure

@@
 \begin{proof}
-	We construct the Hamiltonian by ensuring states perpendicular to $\ket{\psi_{circuit}}$ have high eigenvalues.
+	We ensure states perpendicular to $\ket{\psi_{circuit}}$ have high eigenvalues.
 The base construction comes from \cite{kitaev2002classical}.
@@
 As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations.
-Now consider some $\widetilde{t}$ such that $\bra{\widetilde{t}}\ket\phi\ne0$.
+Now consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$.
 As $\ket\phi\in K_{prop}$, we can then say that $\bra{\widetilde{t+1}}\ket\phi=\bra{\widetilde{t}}U_{t+1}\ket\phi$ for $t\ne T$, and $\bra{\widetilde{t}}\ket\phi=U_t\bra{\widetilde{t-1}}\ket\phi$ for $t\ne0$.
@@
 \begin{itemize}
-	\item $\ket{\psi^{\otimes n}}$ is rejected with probability at most $1-p$.
+	\item $\ket{\psi^{\otimes n}}$ is rejected with probability at most $p$.
 	\item If $\mathcal{F}(\ket{\phi})$ has less than $\frac{1}{2}-\varepsilon$ accept probability, then $\ket{\phi^{\otimes n}}$ is accepted with probability at most $p$.
@@
 		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
-		\Procedure{SimpleAmplification}{$\phi$}
+		\Procedure{Amplification}{$\phi$}
 		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
@@
 All the errors up to this point are $O(\varepsilon)$, so will be the distance between this output distribution and the true one.
+
+\Ethan{The above is incredibly handwavy.}

### 2019-11-13 longoutput.tex
Change wording
Fix confusing notation
Add TODO on using Mahadev's scheme
Fix wording

@@
 The same reasoning does not generalize to our case, so instead we give the following proof.
+We start by considering simpler inputs before moving on to the general case.
 
 Suppose $\mathcal{F}$ accepts $\ket{\psi}$ with probability $\frac{1}{2}$, and any states perpendicular to it with probability $\frac{1}{2}-\Delta$.
-We start by considering simpler inputs before moving to the general case.
 
@@
 \begin{observation}
-	If the input is of the form $\ket{\phi^{\otimes n+m}}$, \autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers.
+	\autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers
 \end{observation}
@@
 \begin{theorem}
-	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, its output when accepted has $\frac{p}{\delta}$ to be rejected by $\mathcal{F}$.
+	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
 \end{theorem}
@@
 
-	Let $J=\set{j:\mathcal{F}(\ket{\rho_j})<\frac{1}{2}-\varepsilon}$.
-
-	$\Rightarrow\forall j\in J$, $q_j<p$.
+	Let $J=\set{j:q_j<p}$.
 
@@
 \Ethan{The above is incredibly handwavy.}
+
+\Ethan{Now use \cite{mahadev_delegation} to turn this into a server-client thing}

### 2019-11-14 longoutput.tex
Updates from Overleaf

@@
 		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
-		\If{number of accepted copies $\geq \frac{1}{2}-\varepsilon$}
+		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
 			\State Output the last $m$ registers
@@
 \begin{observation}
-	\autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers
+	If the input is of the form $\ket{\phi^{\otimes n+m}}$, \autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers.
 \end{observation}
@@
 \begin{theorem}
-	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
+	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, its output when accepted has less than $\frac{p}{\delta}$ probability to be rejected by $\mathcal{F}$.
 \end{theorem}

### 2019-11-21 preliminaries.tex
Add TODO for de Finetti
Change TODOs to note macros
Add SampBQP

@@
 
+We define $\SampBQP$ the same way as from \cite{aaronson_2013}.
+
+\begin{definition}
+	A sampling problem $S$ is a collection of probability distributions $(D_x)$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{p(n)}$ for some fixed polynomial $p$.
+\end{definition}
+
+\begin{definition}
+	$\SampBQP$ is the class of sampling problems $S=(D_x)$ for which there exists a polynomial-time quantum algorithm that, given $x$ as input, samples from from a probability distribution $C_x$ such that $\norm{C_x-D_x}<\varepsilon$.
+\end{definition}
+
 \subsection{Projection Lemma}
@@
 \end{theorem}
+
+\Ethan{Explain the terminologies. Also check do something about the integral vs weighted sum}

### 2019-11-21 preliminaries.tex
Add QPIP

@@
 
-We define $\SampBQP$ the same way as from \cite{aaronson_2013}.
+We define $\SampBQP$ based on \cite{aaronson_2013}.
 
@@
 \begin{definition}
-	$\SampBQP$ is the class of sampling problems $S=(D_x)$ for which there exists a polynomial-time quantum algorithm that, given $x$ as input, samples from from a probability distribution $C_x$ such that $\norm{C_x-D_x}<\varepsilon$.
+	$\SampBQP$ is the class of sampling problems $S=(D_x)$ for which for all $\varepsilon$ there exists a quantum circuit constructible in time $\poly(n, \frac{1}{\varepsilon})$ that, given $x$ as input, samples from from a probability distribution $\tilde{D}_x$ such that $\norm{\tilde{D}_x-D_x}<\varepsilon$.
+\end{definition}
+
+We then define a model of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.
+
+\begin{definition}
+	A sampling problem $S=(D_x)$ is said to have a Quantum Prover Interactive Proof ($\QPIP$) with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
+	\begin{itemize}
+		\item $\bbP$ is a $\BQP$ machine.
+		\item $\bbV$ is a $\BPP$ machine.
+		\item There is a classical communication channel between $\bbP$ and $\bbV$.
+		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
+		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
+	\end{itemize}
 \end{definition}

### 2019-11-21 longoutput.tex
Work on new definitions

--- 2019-11-13 longoutput.tex
@@
 
+First, for ease of notation, we write
+
+\begin{definition}
+	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$.
+\end{definition}
+
+We define and construct an instance of Local Hamiltonian that encodes the history of the computation.
+
+\begin{definition}
+	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties: TODO
+	\begin{itemize}
+		\item can be written as...
+		\item 0 eigenvalue ground state
+		\item at least whatever eigenvalue in all other dimensions
+		\item has ground state of a particular form we like
+	\end{itemize}
+\end{definition}
+
+TODO Theorem statement for XZ LH and whatnot
+
+\subsection{Preprocessing circuit}
+
 We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
@@
 		Which is proven to be universal in \cite{kitaev_1997}.
-
-\subsection{Preprocessing circuit}
 
@@
 We verify that our new gate set can be written as combinations of $X$ and $Z$ matrices.
-
-\begin{definition}
-	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$.
-\end{definition}
 

### 2019-11-21 preliminaries.tex
Work on new definitions

@@
 	A sampling problem $S=(D_x)$ is said to have a Quantum Prover Interactive Proof ($\QPIP$) with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
+	TODO Fix/redefine this to allow $\bbV$ a single qubit and ability to ONLY measure in X/Z
 	\begin{itemize}
@@
 \end{definition}
+
+TODO Specialize above definition? Either ways make another one for purely classical $\bbV$.
 

### 2019-11-21 preliminaries.tex
Add different definitions of QPIP

--- 2019-11-21 preliminaries.tex
@@
 
-We then define a model of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.
+We then define models of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.
 
 \begin{definition}
-	A sampling problem $S=(D_x)$ is said to have a Quantum Prover Interactive Proof ($\QPIP$) with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
+	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
+	TODO Fix/redefine this to allow $\bbV$ a single qubit and ability to ONLY measure in X/Z
 	\begin{itemize}
-		\item $\bbP$ is a $\BQP$ machine.
+		\item $\bbP$ is a hybrid quantum-classical machine. Its classical part is a $BPP$ machine. Its quantum part is a register of a single qubit, on which the verifier can apply $X$ or $Z$ measurements.
 		\item $\bbV$ is a $\BPP$ machine.
+		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
 		\item There is a classical communication channel between $\bbP$ and $\bbV$.
@@
 \end{definition}
+
+\begin{definition}
+	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ defined in the same way as in $\QPIP_{XZ}$ except that $\bbV$ is fully classical and cannot receive or measure qubits.
+\end{definition}
+
+\begin{theorem}
+	$\QPIP_{XZ}=\QPIP_0$
+\end{theorem}
+\begin{proof}
+	See \cite{mahadev_delegation}.
+\end{proof}
 

### 2019-11-21 longoutput.tex
Start rewriting long output

@@
 
-Here we describe the scheme between the classical client and an honest quantum server.
-This is similar to the underlying construction of \cite{mahadev_delegation}.
-We first preprocess the circuit using tools such as \cite{quant-ph/0301040}.
-We then follow \cite{kitaev2002classical} to reduce the problem to an instance of local Hamiltonian.
-Using tools from \cite{PhysRevA.93.022326}, the local Hamiltonian is written in a simple form.
-Then, NYI cuz we're stuck.
-\hannote{be more explicit}
+Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper.
 
-First, for ease of notation, we write
+First, for ease of notation, write
 
@@
 	\begin{itemize}
-		\item can be written as...
-		\item 0 eigenvalue ground state
+		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
+		\item 0 eigenvalue ground state and has certain form TODO type it out
 		\item at least whatever eigenvalue in all other dimensions
@@
 
+TODO Combine and rewrite the following subsections
+
 Now we put the above results in term of measurement outputs.

### 2019-11-22 hamiltonian.tex
Add QPIP section

--- 2019-11-21 longoutput.tex
@@
-\section{Our Long Output Scheme}
+\section{The History XZ Local Hamiltonian}
 
@@
 \end{proof}
-
-\subsection{Analysis and amplification}
-
-In the case for decision problems, amplifying the gap between acceptance and rejection probabilities is trivial.
-As seen in \cite{kitaev2002classical}, a prover, honest or not, cannot do better than sending $n$ identical copies of some state.
-As a result, a simple Chernoff bound would suffice.
-The same reasoning does not generalize to our case, so instead we give the following proof.
-We start by considering simpler inputs before moving on to the general case.
-
-Suppose $\mathcal{F}$ accepts $\ket{\psi}$ with probability $\frac{1}{2}$, and any states perpendicular to it with probability $\frac{1}{2}-\Delta$.
-
-Let $\varepsilon>0$, $p>0$. Pick $n\in\mathbb{N}$ so that by Chernoff bound:
-\begin{itemize}
-	\item $\ket{\psi^{\otimes n}}$ is rejected with probability at most $p$.
-	\item If $\mathcal{F}(\ket{\phi})$ has less than $\frac{1}{2}-\varepsilon$ accept probability, then $\ket{\phi^{\otimes n}}$ is accepted with probability at most $p$.
-\end{itemize}
-
-\begin{algorithm}
-	\caption{Amplification with simple input}
-	\label{AlgAmp1}
-	\begin{algorithmic}[1]
-		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
-		\Procedure{Amplification}{$\phi$}
-		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
-		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
-			\State Output the last $m$ registers
-		\Else
-			\State Reject
-		\EndIf
-		\EndProcedure
-	\end{algorithmic}
-\end{algorithm}
-
-\begin{observation}
-	\autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers
-\end{observation}
-
-\begin{theorem}
-	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
-\end{theorem}
-\begin{proof}
-	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.
-
-	Let $q_j$ be the accept probability of $\ket{\rho_j^{\otimes n+m}}$ under \autoref{AlgAmp1}.
-By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_j^{\otimes n+m}}$ is then $\frac{w_j q_j}{\sum_i w_i q_i}$.
-
-	Let $J=\set{j:q_j<p}$.
-
-	$\Rightarrow\sum_{j\in J} w_j q_j<p$, since $\sum_i w_i=1$.
-
-	$\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}<\frac{p}{\delta}$.
-\end{proof}
-
-Now we consider the general case.
-We use \autoref{deFinetti}.
-Let $n=l$ and $k=\poly(n)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily small.
-That is, with some arbitrarily small error in measurement results, we can assume without the loss of generality that the client receives an input of the simple form above.
-Hence concludes the proof.
-
-\subsection{Getting the Output}
-
-Thanks to having padded the circuit with identity matrices at the end, if we measured $t>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
-So simply take $m$ to be high enough that it happens at least once with overwhelming probability.
-When it does, measure the entire register.
-All the errors up to this point are $O(\varepsilon)$, so will be the distance between this output distribution and the true one.
-
-\Ethan{The above is incredibly handwavy.}
-
-\Ethan{Now use \cite{mahadev_delegation} to turn this into a server-client thing}

### 2019-11-22 qpip.tex
Add QPIP section

--- 2019-11-21 longoutput.tex
@@
-\section{Our Long Output Scheme}
-
-Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper.
-
-First, for ease of notation, write
-
-\begin{definition}
-	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$.
-\end{definition}
-
-We define and construct an instance of Local Hamiltonian that encodes the history of the computation.
-
-\begin{definition}
-	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties: TODO
-	\begin{itemize}
-		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
-		\item 0 eigenvalue ground state and has certain form TODO type it out
-		\item at least whatever eigenvalue in all other dimensions
-		\item has ground state of a particular form we like
-	\end{itemize}
-\end{definition}
-
-TODO Theorem statement for XZ LH and whatnot
-
-\subsection{Preprocessing circuit}
-
-We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
-$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
-	$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-		Which is proven to be universal in \cite{kitaev_1997}.
-
-In order to estimate the energy of a Hamiltonian using only $X$ and $Z$ measurements, the gates in the circle must be combinations of $X$ and $Z$ matrices.
-To begin, we apply a transformation to the circuit to use only real states and gates.
-This transform is taken from \cite{quant-ph/0301040}.
-
-\begin{theorem}
-	Let $C$ be a circuit that:
-	\begin{itemize}
-		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
-		\item uses $n$ qubits
-	\end{itemize}
-	Then a classical machine given $C$ can compute a circuit $C'$ that:
-	\begin{itemize}
-		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
-		\item uses $n+1$ qubits
-		\item Let $x\in\set{0,1}^n$.
-Let $x||0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
-The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
-	\end{itemize}
-\end{theorem}
-
-\begin{proof}
-
-	Consider the transform on quantum states
-	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
-	where $\Re$ and $\Im$ denote real and imaginary parts respectively.
-
-	This transform commutes with Hadamard gates on the respective qubit.
-On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turn it into a combination of Hadamard and Toffoli gates.
-Mathematically,
-	$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
-	$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
-
-	We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
-	\begin{itemize}
-		\item $C'$ uses only Hadamard and Toffoli gates.
-		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
-		\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple to verify that $F$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
-	\end{itemize}
-\end{proof}
-
-We verify that our new gate set can be written as combinations of $X$ and $Z$ matrices.
-
-\begin{theorem}
-	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
-\end{theorem}
-
-\begin{proof}
-	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
-	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
-	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
-\end{proof}
-
-\subsection{Constructing a local Hamiltonian instance}
-
-Here we reduce a circuit into a local Hamiltonian instance with a few additional properties.
-
-\begin{theorem}
-	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$.
-Then a classical machine can construct in polynomial time a local Hamiltonian instance $H_{circuit}$ such that:
-	\begin{itemize}
-		\item its ground state is $$\ket{\psi_{circuit}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
-		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
-		\item $\forall\ket\phi,\braket{\phi|\psi_{circuit}}=0\Rightarrow\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$
-		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
-	\end{itemize}
-\end{theorem}
-
-\begin{proof}
-	We ensure states perpendicular to $\ket{\psi_{circuit}}$ have high eigenvalues.
-The base construction comes from \cite{kitaev2002classical}.
-The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.
-
-	Let $x_i$ denote the $i$-th bit of $x$, and let $n$ be the number of qubits in $C$.
-
-	First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
-	$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
-	As a sum of projections, clearly $H_{clock}\geq 0$. We shall also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
-	$$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
-	This can be checked by fixing the first and last qubit, then doing induction on the number of switches.
-
-	Then, we ensure that the initial condition is set up correctly.
-	$$H_{in}=\sum_{i=1}^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
-	The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
-	$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$
-
-	Then, we ensure that the gates are applied correctly.
-	$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
-	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
-	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
-	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-
-	Next, we check that $H_{prop}\geq0$ by the following transform.
-
-	$$W=\sum_{j=0}^L U_j\ldots U_1\otimes\ket{j}\bra{j}$$
-	$$W^\dagger\phi=\sum_{t=0}^T\ket{x}\otimes\ket{\hat{t}}$$
-	$$W^\dagger H_{prop} W=
-	\begin{pmatrix}
-		\frac{1}{2} & -\frac{1}{2} & & & &  \\
-		-\frac{1}{2} & 1 & -\frac{1}{2} & & & \\
-		& -\frac{1}{2} & 1 & \ddots & & \\
-		& & \ddots & \ddots & -\frac{1}{2} & \\
-		& & & -\frac{1}{2} & 1 & -\frac{1}{2} \\
-		& & & & -\frac{1}{2} & \frac{1}{2}
-	\end{pmatrix}$$
-
-	According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks.
-Furthermore, the last nonzero eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.
-
-	We can also write $H=\spn\mathcal{G}_{XZ}$.
-Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli.
-Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$.
-$\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
-	$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
-	Extra care must be taken for boundary cases.
-	$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
-	$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
-
-	To properly combine the three Hamiltonians defined, we consider the kernels of the Hamiltonians we defined.
-	$$K_{clock}=\ker H_{clock}$$
-	$$K_{in}=\ker H_{in}$$
-	$$K_{prop}=\ker H_{prop}$$
-	It is clear that $K_{clock}$ consists of the states with time registers of the form $\ket{\hat{t}}$.
-
-	\begin{lemma}
-		$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
-	\end{lemma}
-
-	\begin{proof}
-		Let $\ket\phi\in K_{clock}\cap K_{prop}$.
-As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations.
-Now consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$.
-As $\ket\phi\in K_{prop}$, we can then say that $\bra{\widetilde{t+1}}\ket\phi=\bra{\widetilde{t}}U_{t+1}\ket\phi$ for $t\ne T$, and $\bra{\widetilde{t}}\ket\phi=U_t\bra{\widetilde{t-1}}\ket\phi$ for $t\ne0$.
-So we can obtain the required statement by induction.
-	\end{proof}
-
-	\begin{corollary}
-		$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$
-	\end{corollary}
-
-We now consider the space outside the desired state.
-$$S=(\spn\set{\ket{\psi_{circuit}}})^\bot$$
-$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
-To combine the Hamiltonians, we apply the projection lemma twice.
-$$\exists J_{clock}
-=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
-=O(n)=O(T)$$
-$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
-\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
-$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
-=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
-$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
-\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
-\begin{align*}
-	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
-	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{circuit}|y}=0}
-\end{align*}
-$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
-So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
-\end{proof}
-
-\subsection{Measuring ground state}
-
-TODO Combine and rewrite the following subsections
-
-Now we put the above results in term of measurement outputs.
-
-\begin{algorithm}
-	\caption{Check for ground state}
-	\label{AlgGroundStateCheck}
-	\begin{algorithmic}[1]
-		\Require $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$
-		\Procedure{GroundStateCheck}{$\ket\phi$}
-		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
-		\State $p_S\gets\frac{|d_S|}{D}$
-		\State $\widetilde{S}\gets$ Pick weighted using $p_S$
-		\State $\lambda_{\widetilde{S}}\gets$ Measure $\ket\phi$ in the $\widetilde{S}$ basis
-		\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
-		\State Accept
-		\Else
-		\State Reject
-		\EndIf
-		\EndProcedure
-	\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}\label{ThmXZCheck}
-	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
-	Then \autoref{AlgGroundStateCheck} accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
-\end{theorem}
-\begin{proof}
-
-	Here we follow \cite{PhysRevA.93.022326}.
-	\begin{align*}
-		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
-		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
-		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
-		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
-	\end{align*}
-
-	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
-	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
-	\begin{align*}
-		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
-		&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
-	\end{align*}
-
-\end{proof}
-
-\subsection{Analysis and amplification}
+\section{Our QPIP Scheme}
 

### 2019-11-23 preliminaries.tex
Restructure flow and add TODOs

--- 2019-11-21 preliminaries.tex
@@
 
-We then define a model of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.
+We then define models of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.
 
 \begin{definition}
-	A sampling problem $S=(D_x)$ is said to have a Quantum Prover Interactive Proof ($\QPIP$) with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
+	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
 	\begin{itemize}
@@
 	\end{itemize}
+\end{definition}
+
+\begin{definition}
+	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ defined in the same way as in $\QPIP_{XZ}$ except that $\bbV$ is fully classical and cannot receive or measure qubits.
 \end{definition}

### 2019-11-23 qpip.tex
Restructure flow and add TODOs

@@
 
-In the case for decision problems, amplifying the gap between acceptance and rejection probabilities is trivial.
-As seen in \cite{kitaev2002classical}, a prover, honest or not, cannot do better than sending $n$ identical copies of some state.
-As a result, a simple Chernoff bound would suffice.
-The same reasoning does not generalize to our case, so instead we give the following proof.
-We start by considering simpler inputs before moving on to the general case.
+Here we create a QPIP scheme for...
+In the case for decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}.
+A prover, honest or not, couldn't do better than sending $n$ identical copies of some state.
+The same reasoning does not generalize to our case, so instead we give the following construction.
+
+We first give an alternative characterization of $\QPIP_0$.
+
+\begin{definition}
+	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$, or has a $\QPIP_{XZ}$ protocol,  with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
+	\begin{itemize}
+		\item $\bbP$ is a $\BQP$ machine.
+		\item $\bbV$ is a hybrid quantum-classical machine. Its classical part is a $BPP$ machine. Its quantum part is a single-qubit register, on which the verifier can apply only $X$ or $Z$ measurements.
+		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
+		\item There is a classical communication channel between $\bbP$ and $\bbV$.
+		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
+		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
+	\end{itemize}
+\end{definition}
+
+\begin{theorem}
+	$\QPIP_{XZ}=\QPIP_0$
+\end{theorem}
+\begin{proof}
+	See \cite{mahadev_delegation}.
+\end{proof}
+
+\begin{theorem}
+	$\SampBQP$ is in $\QPIP_{XZ}$.
+\end{theorem}
 
@@
 
+TODO Do something about this
 \begin{algorithm}
+	\floatname{algorithm}{Protocol}
 	\caption{Amplification with simple input}
@@
 	\begin{algorithmic}[1]
-		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
-		\Procedure{Amplification}{$\phi$}
-		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
+		\State The prover sends $\poly(n)$ copies of...
+		\State The verifier picks $m+n$ copies...
+		\State The verifier runs Chernoff bound on...
 		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
-			\State Output the last $m$ registers
+			\State Measure time step...
+			\State Output the...
 		\Else
@@
 		\EndIf
-		\EndProcedure
 	\end{algorithmic}
 \end{algorithm}
+TODO what's $n$?
 
-\begin{observation}
-	\autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers
-\end{observation}
+TODO Talk about de Finetti's here.
+
+Now we consider the general case.
+We use \autoref{deFinetti}.
+Let $n=l$ and $k=\poly(n)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily inverse-poly small.
+That is, with some small error in measurement results, we can assume without the loss of generality that the rest of the algorithm acts on an input of the form...
+TODO.
 
@@
 
-Now we consider the general case.
-We use \autoref{deFinetti}.
-Let $n=l$ and $k=\poly(n)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily small.
-That is, with some arbitrarily small error in measurement results, we can assume without the loss of generality that the client receives an input of the simple form above.
-Hence concludes the proof.
-
-\subsection{Getting the Output}
-
-Thanks to having padded the circuit with identity matrices at the end, if we measured $t>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
+So we pad the circuit with identity matrices at the end before constructing...
+TODO, if we measured $t>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
 So simply take $m$ to be high enough that it happens at least once with overwhelming probability.
@@
 \Ethan{The above is incredibly handwavy.}
-
-\Ethan{Now use \cite{mahadev_delegation} to turn this into a server-client thing}

### 2019-11-23 qpip.tex
Fix autoref shenanigans

@@
 
+\floatname{algorithm}{Protocol}
 TODO Do something about this
 \begin{algorithm}
-	\floatname{algorithm}{Protocol}
 	\caption{Amplification with simple input}
@@
 \begin{theorem}
-	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
+	When \hyperref[AlgAmp1]{Protocol~\ref*{AlgAmp1}} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
 \end{theorem}

### 2019-11-23 hamiltonian.tex
Restructure flow and add TODOs
Work on Hamiltonian theorem statement

@@
 Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper.
+We begin by proving that we can assume without loss of generality that the circuit is of a particular form.
+
+TODO move subsection.
 
@@
 
-We define and construct an instance of Local Hamiltonian that encodes the history of the computation.
+We define and construct an instance of Local Hamiltonian that encodes the history of the computation. TODO This only works for circuits of a particular form...
 
 \begin{definition}
-	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties: TODO
+	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties:
 	\begin{itemize}
 		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
-		\item 0 eigenvalue ground state and has certain form TODO type it out
-		\item at least whatever eigenvalue in all other dimensions
-		\item has ground state of a particular form we like
+		\item It has an eigenvector $\ket{\psi_{C(x)}}=TODO$ with eigenvalue $0$.
+		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
 	\end{itemize}
@@
 
-TODO Theorem statement for XZ LH and whatnot
+We'll prove the following theorems in this section.
+
+\begin{theorem}
+	Given $C$ and $x$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
+\end{theorem}
+
+\begin{theorem}
+	For any given circuit and input, there exists an algorithm that accepts state with probability... TODO
+\end{theorem}
+
+Before we present their proofs, first we make an observation.
+
+\begin{observation}
+	Given $C$ and $x$, one can first pad $C$ with identity matrices at the end.
+\end{observation}
+
+TODO Observation given circuit, if one pads the circuit to obtain... one can measure final state from this by padding...
 

### 2019-11-23 hamiltonian.tex
Write intro for Hamiltonian section

--- 2019-11-22 hamiltonian.tex
@@
 
-Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper.
+Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper. Here we'll only state the theorems, and prove them later in the subsections.
 
@@
 \begin{definition}
-	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$.
+	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$. TODO maybe force at most $k$ non-identity components here?
 \end{definition}
+
+Then we define a certain form of quantum circuit that is still universal.
+
+\begin{definition}
+	Let $C$ be an XZ-circuit if $C=U_T\ldots U_1$ where $U_i\in\spn\mathcal{G}_{XZ}$.
+\end{definition}
+
+\begin{theorem}
+	Given a circuit $C$ and classical input $x$, a $BPP$ machine can reduce it to an XZ-circuit $C'$ and classical input $x'$.
+\end{theorem}
 
@@
 \begin{definition}
-	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties: TODO
+	Let $C(x)$ be an XZ-circuit. Then let $H_{C(x)}$ be with the following properties:
 	\begin{itemize}
 		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
-		\item 0 eigenvalue ground state and has certain form TODO type it out
-		\item at least whatever eigenvalue in all other dimensions
-		\item has ground state of a particular form we like
+		\item It has an eigenvector $\ket{\psi_{C(x)}}=TODO$ with eigenvalue $0$.
+		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
 	\end{itemize}
@@
 
-TODO Theorem statement for XZ LH and whatnot
+\begin{theorem}
+	Given XZ-circuit $C$ and classical $x$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
+\end{theorem}
 
-\subsection{Preprocessing circuit}
+\begin{theorem}
+	Given XZ-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability... TODO that only uses $X$ and $Z$ measurements?
+\end{theorem}
+
+Lastly, before we present their proofs, we make an observation.
+
+\begin{observation}
+	Given XZ-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$.
+One can then measure the last register of $\psi_{C'(x)}$ and obtain with probabiliy $\frac{1}{2}$ the state $C(x)$.
+\end{observation}
+
+\subsection{XZ-circuits}
+
+Here we prove that XZ-circuits are universal. After this subsection, we'll be able to assume without loss of generality that all quantum circuits are XZ-circuits.
 

### 2019-11-23 preliminaries.tex
Fix typo
Remove unused definitions

@@
 I.e.
-$\Lambda^2{1, 2}(X_3)$ would be a Toffoli (CCNOT) gate.
-\end{definition}
-
-\begin{definition}
-	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitians each acting on at most $k$ qubits, then $$H=\sum_{j=1}^nH_j$$ is called a \emph{$k$-local Hamiltonian}.
+$\Lambda^2_{1, 2}(X_3)$ would be a Toffoli (CCNOT) gate.
 \end{definition}
@@
 
-\begin{definition}
-	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ defined in the same way as in $\QPIP_{XZ}$ except that $\bbV$ is fully classical and cannot receive or measure qubits.
-\end{definition}
-
 \subsection{Projection Lemma}

### 2019-11-23 hamiltonian.tex
Rename Hamiltonian and ground state label

@@
 	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$.
-Then a classical machine can construct in polynomial time a local Hamiltonian instance $H_{circuit}$ such that:
+Then a classical machine can construct in polynomial time a local Hamiltonian instance $H_{C(x)}$ such that:
 	\begin{itemize}
-		\item its ground state is $$\ket{\psi_{circuit}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
-		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
-		\item $\forall\ket\phi,\braket{\phi|\psi_{circuit}}=0\Rightarrow\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$
-		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
+		\item its ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
+		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
+		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
+		\item $H_{C(x)}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
 	\end{itemize}
@@
 \begin{proof}
-	We ensure states perpendicular to $\ket{\psi_{circuit}}$ have high eigenvalues.
+	We ensure states perpendicular to $\ket{\psi_{C(x)}}$ have high eigenvalues.
 The base construction comes from \cite{kitaev2002classical}.
@@
 	\begin{corollary}
-		$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$
+		$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$
 	\end{corollary}
@@
 We now consider the space outside the desired state.
-$$S=(\spn\set{\ket{\psi_{circuit}}})^\bot$$
+$$S=(\spn\set{\ket{\psi_{C(x)}}})^\bot$$
 $$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
@@
 	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
-	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{circuit}|y}=0}
+	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{C(x)}|y}=0}
 \end{align*}
 $$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
-So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
+So we set $H_{C(x)}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
 \end{proof}

### 2019-11-24 hamiltonian.tex
Fill in simple TODOs

@@
 
-First, for ease of notation, write
+First, fix $L\in\bbN$ and define the following that implicitly depends on $L$.
 
 \begin{definition}
-	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$. TODO maybe force at most $k$ non-identity components here?
+	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \norm{\set{i: U_i\ne I}}\leq L}$
 \end{definition}
 
-Then we define a certain form of quantum circuit that is still universal.
+$L$ can be thought of as how ``local" the Hamiltonian is. Taking $L=5$ would easily suffice for this paper.
+
+We define a certain form of quantum circuit that is still universal.
 
@@
 		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
-		\item It has an eigenvector $\ket{\psi_{C(x)}}=TODO$ with eigenvalue $0$.
+		\item It has an eigenvector $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
 		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
@@
 \begin{theorem}
-	Given XZ-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability... TODO that only uses $X$ and $Z$ measurements?
+	Given XZ-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
+Furthermore, this algorithm doesn't apply any quantum gates, and uses only $X$ and $Z$ measurements.
 \end{theorem}
 
-Lastly, before we present their proofs, we make an observation.
+Lastly, before we present proofs for the above theorems, we make an observation.
 
@@
 
-TODO Combine and rewrite the following subsections
-
 Now we put the above results in term of measurement outputs.

### 2019-11-24 hamiltonian.tex
Type out QPIP protocol

@@
 \begin{observation}
+	\label{idpadding}
 	Given XZ-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$.

### 2019-11-24 qpip.tex
Add QPIP XZ estimation for ground state
Fill in simple TODOs
Type out QPIP protocol

--- 2019-11-23 qpip.tex
@@
 		\item $\bbP$ is a $\BQP$ machine.
-		\item $\bbV$ is a hybrid quantum-classical machine. Its classical part is a $BPP$ machine. Its quantum part is a single-qubit register, on which the verifier can apply only $X$ or $Z$ measurements.
+		\item $\bbV$ is a hybrid quantum-classical machine. Its classical part is a $\BPP$ machine. Its quantum part is a single-qubit register, on which the verifier can apply only $X$ or $Z$ measurements.
 		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
@@
 \begin{theorem}
+	There is a $\QPIP_{XZ}$ protocol for \autoref{AlgGroundStateCheck}
+\end{theorem}
+\begin{proof}
+	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is obvious that any attacks on this scheme trivially maps onto an attack on the original scheme.
+\end{proof}
+
+\begin{theorem}
 	$\SampBQP$ is in $\QPIP_{XZ}$.
 \end{theorem}
+\begin{proof}
 
@@
 
-TODO Do something about this
+\floatname{algorithm}{Protocol}
 \begin{algorithm}
-	\floatname{algorithm}{Protocol}
-	\caption{Amplification with simple input}
+	\caption{Our $\QPIP_{XZ}$ protocol}
 	\label{AlgAmp1}
 	\begin{algorithmic}[1]
-		\State The prover sends $\poly(n)$ copies of...
-		\State The verifier picks $m+n$ copies...
-		\State The verifier runs Chernoff bound on...
-		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
-			\State Measure time step...
-			\State Output the...
+		\State Pick $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
+		\State Pick $n$ large enough so, $P\left[Bin(n, \frac{1}{2}-\varepsilon)<\left(\frac{1}{2}-2\varepsilon\right)n\right]$ is negligible in $\varepsilon$ by Chernoff bound
+		\State Pick $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}=O(\poly(\varepsilon))$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
+		\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
+		\State The verifier randomly picks $n+m$ copies in sequence and without replacement
+		\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
+		\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
+			\For{$i\gets 1, m$}
+				\State Measure the time register of a (supposedly) fresh copy of $\ket{\psi_{C(x)}}$ that the prover sent
+				\If{Measured $t\geq T$}
+					\State Measure and output the other registers
+				\EndIf
+			\EndFor
+			\State Reject
 		\Else
@@
 \end{algorithm}
-TODO what's $n$?
 
-TODO Talk about de Finetti's here.
+We first apply \autoref{deFinetti}. This is justified because... TODO
 
-Now we consider the general case.
-We use \autoref{deFinetti}.
-Let $n=l$ and $k=\poly(n)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily inverse-poly small.
-That is, with some small error in measurement results, we can assume without the loss of generality that the rest of the algorithm acts on an input of the form...
-TODO.
+So, with some error $O(\poly(\varepsilon))$ in measurement results, we can assume without the loss of generality that the rest of the algorithm acts on an input of the form... TODO.
 
-\begin{theorem}
-	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
-\end{theorem}
-\begin{proof}
 Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.
@@
 $\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}<\frac{p}{\delta}$.
-\end{proof}
 
@@
 
-\Ethan{The above is incredibly handwavy.}
+\end{proof}

### 2019-11-24 qpip.tex
Type out permutation invariance argument

@@
 			\For{$i\gets 1, m$}
-				\State Measure the time register of a (supposedly) fresh copy of $\ket{\psi_{C(x)}}$ that the prover sent
+				\State Measure the time register of a fresh copy from the prover
 				\If{Measured $t\geq T$}
@@
 
-We first apply \autoref{deFinetti}. This is justified because... TODO
+This clearly has completeness negligibly close to $1$. Now we analyze soundness, for a possibly cheating prover.
 
-So, with some error $O(\poly(\varepsilon))$ in measurement results, we can assume without the loss of generality that the rest of the algorithm acts on an input of the form... TODO.
+Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers. Denote the state at that point as
 
-Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.
+$$\sigma'=\frac{1}{\abs{\Sym(N)}}\sum_{\Pi\in\Sym(N)}\Pi\sigma\Pi^\dagger$$
 
-Let $q_j$ be the accept probability of $\ket{\rho_j^{\otimes n+m}}$ under \autoref{AlgAmp1}.
+Let $\tilde{\Pi}$ be some fixed permutation. Then it is easy to check that
+
+$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger=\sigma'$$
+
+So $\sigma'$ is permutation-invariant and we can apply \autoref{deFinetti}:
+
+$$\norm{\sigma'-\sum_i w_i\rho_i^{\otimes n+m}}=O(\poly(\varepsilon))$$
+
+Note that this is a classical probability distribution over inputs $\rho_i^{\otimes n+m}$ with $w_i$ as weights.
+
+Let $q_j$ be the accept probability of $\ket{\rho_j^{\otimes n+m}}$ under \hyperref[AlgAmp1]{Protocol~\ref*{AlgAmp1}}.
 By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_j^{\otimes n+m}}$ is then $\frac{w_j q_j}{\sum_i w_i q_i}$.

### 2019-11-24 preliminaries.tex
Fix typo

@@
 	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there is a measure $\nu$ on $D(A)$ such that
-	$$\max_{\Lambda_2,\ldots,\Lambda_l\in\mathcal{M}}\norm{(id\otimes\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\int \nu(d\sigma)\sigma^{\otimes l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
+	$$\max_{\Lambda_2,\ldots,\Lambda_l\in\mathcal{M}}\norm{(id\otimes\Lambda_2\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\int \nu(d\sigma)\sigma^{\otimes l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
 \end{theorem}

### 2019-11-24 qpip.tex
Auto indent
Work on qpip

@@
 			\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
-		\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
+			\If{over $(\frac{1}{2}-2\varepsilon)n$ copies accept}
 			\For{$i\gets 1, m$}
@@
 
-Let $q_j$ be the accept probability of $\ket{\rho_j^{\otimes n+m}}$ under \hyperref[AlgAmp1]{Protocol~\ref*{AlgAmp1}}.
-By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_j^{\otimes n+m}}$ is then $\frac{w_j q_j}{\sum_i w_i q_i}$.
+	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-2\varepsilon)n$ copies out of $\rho_i^{\otimes n}$ accept under \autoref[AlgGroundStateCheck].
+By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.
 

### 2019-11-24 qpip.tex
Fix typo

@@
 
-	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-2\varepsilon)n$ copies out of $\rho_i^{\otimes n}$ accept under \autoref[AlgGroundStateCheck].
+	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-2\varepsilon)n$ copies out of $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
 By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.

### 2019-11-24 qpip.tex
Fix typo

@@
 			\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
-			\If{over $(\frac{1}{2}-2\varepsilon)n$ copies accept}
+			\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
 			\For{$i\gets 1, m$}
@@
 
-	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-2\varepsilon)n$ copies out of $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
+	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies out of $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
 By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.

### 2019-11-25 qpip.tex
Start re-parameterizing qpip

@@
 \begin{theorem}
-	$\SampBQP$ is in $\QPIP_{XZ}$.
+	$\SampBQP$ is in $\QPIP_{XZ}$ with completeness negligible to perfect and soundness $1-O(T^{-c})$ for any constant $c$.
 \end{theorem}
 \begin{proof}
-
-	Suppose $\mathcal{F}$ accepts $\ket{\psi}$ with probability $\frac{1}{2}$, and any states perpendicular to it with probability $\frac{1}{2}-\Delta$.
-
-	Let $\varepsilon>0$, $p>0$. Pick $n\in\mathbb{N}$ so that by Chernoff bound:
-	\begin{itemize}
-		\item $\ket{\psi^{\otimes n}}$ is rejected with probability at most $p$.
-		\item If $\mathcal{F}(\ket{\phi})$ has less than $\frac{1}{2}-\varepsilon$ accept probability, then $\ket{\phi^{\otimes n}}$ is accepted with probability at most $p$.
-	\end{itemize}
 
@@
 		\begin{algorithmic}[1]
+			\State $\varepsilon\gets T^{-c}$
 			\State Pick $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
@@
 
-	This clearly has completeness negligibly close to $1$. Now we analyze soundness, for a possibly cheating prover.
+	This clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover.
 
@@
 
+	TODO set $\tilde{\sigma}$ and fix above to be product measure
+
 	Note that this is a classical probability distribution over inputs $\rho_i^{\otimes n+m}$ with $w_i$ as weights.
 
-	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies out of $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
-By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.
+	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
+By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.
 
-	Let $J=\set{j:q_j<p}$.
+	Define $J$ to be the set of $j$s where $q_j$ is negligible. TODO negligible shenanigans
 
-	$\Rightarrow\sum_{j\in J} w_j q_j<p$, since $\sum_i w_i=1$.
+	$$\sum_{j\in J} w_j q_j$$
 
-	$\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}<\frac{p}{\delta}$.
+	$$\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}<\frac{p}{\delta}$$
 
-	So we pad the circuit with identity matrices at the end before constructing...
-TODO, if we measured $t>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation.
-So simply take $m$ to be high enough that it happens at least once with overwhelming probability.
-When it does, measure the entire register.
-All the errors up to this point are $O(\varepsilon)$, so will be the distance between this output distribution and the true one.
+	Now let $\rho_i$ be with over probability $1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck}. So it is $O(\poly(\varepsilon))$-close to $\ket{\psi_{C(x)}}$.
+
+	So we simply measure the time register until we get a result where we can extract $C(x)$. The probability of failing to do so after all $m$ copies is $\frac{1}{2^m}$ which is negligible.
+
+	All errors up to this point is $O(\poly(\varepsilon))$.
 

### 2019-11-25 hamiltonian.tex
Fix typo
Finish another draft of QPIP analysis

@@
 \begin{theorem}
-	Given a circuit $C$ and classical input $x$, a $BPP$ machine can reduce it to an XZ-circuit $C'$ and classical input $x'$.
+	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to an XZ-circuit $C'$ and classical input $x'$.
 \end{theorem}
@@
 	\end{itemize}
+\end{definition}
+
+\begin{definition}
+	We call the first registers of $\psi_{C(x)}$ the data register, and the later registers of $\psi_{C(x)}$ the time register.
 \end{definition}

### 2019-11-25 qpip.tex
Finish another draft of QPIP analysis

@@
 
+TODO the following needs $\delta$ parameter
 \begin{theorem}
@@
 
+	Set the following variables
+	\begin{itemize}
+		\item $\varepsilon=T^{-c}$
+		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
+		\item $n$ large enough so by Chernoff bound:
+			\begin{itemize}
+				\item[$\circ$] $q'=P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
+				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
+			\end{itemize}
+		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
+	\end{itemize}
+
+	We claim that the following protocol does what is required:
 	\floatname{algorithm}{Protocol}
@@
 		\begin{algorithmic}[1]
-			\State $\varepsilon\gets T^{-c}$
-			\State Pick $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
-			\State Pick $n$ large enough so, $P\left[Bin(n, \frac{1}{2}-\varepsilon)<\left(\frac{1}{2}-2\varepsilon\right)n\right]$ is negligible in $\varepsilon$ by Chernoff bound
-			\State Pick $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}=O(\poly(\varepsilon))$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
 			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
@@
 				\If{Measured $t\geq T$}
-					\State Measure and output the other registers
+					\State Measure and output its data register
 				\EndIf
@@
 
-	This clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover.
+	This clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover. Let $\sigma$ be the state the prover sends.
 
-	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers. Denote the state at that point as
+	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers. Denote the state after the random permutation as
 
@@
 
-	$$\norm{\sigma'-\sum_i w_i\rho_i^{\otimes n+m}}=O(\poly(\varepsilon))$$
+	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+n}(\sigma'-\sum_i w_i\rho_i^{\otimes n+m})}=O(\varepsilon)$$
 
-	TODO set $\tilde{\sigma}$ and fix above to be product measure
+	Note that $\tilde\sigma=\sum_i w_i\rho_i^{\otimes n+m}$ is a classical probability distribution over inputs $\rho_i^{\otimes n+m}$ with $w_i$ as weights.
 
-	Note that this is a classical probability distribution over inputs $\rho_i^{\otimes n+m}$ with $w_i$ as weights.
+	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
+	So the accept chance of this prover is $\sum_j w_j p_j>\delta$
+	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.
 
-	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
-By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.
+	Let
+	$$J=\set{j:q_j\leq q'}$$
 
-	Define $J$ to be the set of $j$s where $q_j$ is negligible. TODO negligible shenanigans
-
+	Then the following is clearly negligible:
 	$$\sum_{j\in J} w_j q_j$$
 
-	$$\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}<\frac{p}{\delta}$$
+	And so is
+	$$\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}$$
 
-	Now let $\rho_i$ be with over probability $1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck}. So it is $O(\poly(\varepsilon))$-close to $\ket{\psi_{C(x)}}$.
+	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otime n+m}$ where $\rho_i$ has over probability $\1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck} is overwhelming.
 
-	So we simply measure the time register until we get a result where we can extract $C(x)$. The probability of failing to do so after all $m$ copies is $\frac{1}{2^m}$ which is negligible.
+	Such $\rho_i$ are $O(\poly(\varepsilon))$-close to $\ket{\psi_{C(x)}}$.
 
-	All errors up to this point is $O(\poly(\varepsilon))$.
+	So we simply measure the time register until we get measurement result $t\geq T$. The probability of failing to do so after all $m$ copies is $\frac{1}{2^m}$ which is negligible.
+
+	Once we do measure $t\geq T$, the data register is guaranteed to be $O(\poly(\varepsilon))$-close to $C(x)$.
+
+	All errors up to this point is $O(\varepsilon)$.
 

### 2019-11-25 preliminaries.tex
Add delta parameter to soundness

@@
 \begin{definition}
-	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
+	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
 	\begin{itemize}

### 2019-11-25 qpip.tex
Add delta parameter to soundness

@@
 \begin{definition}
-	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$, or has a $\QPIP_{XZ}$ protocol,  with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
+	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$, or has a $\QPIP_{XZ}$ protocol,  with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
 	\begin{itemize}
@@
 
-TODO the following needs $\delta$ parameter
 \begin{theorem}
-	$\SampBQP$ is in $\QPIP_{XZ}$ with completeness negligible to perfect and soundness $1-O(T^{-c})$ for any constant $c$.
+	$\SampBQP$ is in $\QPIP_{XZ}$ with completeness negligible to perfect and soundness $(O(T^{-c}), 1-O(T^{-c}))$ for any constant $c$.
 \end{theorem}
 \begin{proof}
-
 	Set the following variables
@@
 
-	This clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover. Let $\sigma$ be the state the prover sends.
+	This clearly has completeness negligibly close to $1$.
+Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted.
+Let $\sigma$ be the state the prover sends.
 

### 2019-11-25 qpip.tex
Fix typo

@@
 
-	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otime n+m}$ where $\rho_i$ has over probability $\1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck} is overwhelming.
+	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ where $\rho_i$ has over probability $1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck} is overwhelming.
 

### 2019-11-25 hamiltonian.tex
Make editorial change

@@
 \begin{theorem}
-	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$.
-Then a classical machine can construct in polynomial time a local Hamiltonian instance $H_{C(x)}$ such that:
+	Let $C=U_T\ldots U_1$ be a XZ-circuit, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
 	\begin{itemize}
@@
 		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
-		\item $H_{C(x)}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
+		\item Has $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
 	\end{itemize}

### 2019-11-27 hamiltonian.tex
Make editorial changes

@@
 
-In order to estimate the energy of a Hamiltonian using only $X$ and $Z$ measurements, the gates in the circle must be combinations of $X$ and $Z$ matrices.
-To begin, we apply a transformation to the circuit to use only real states and gates.
-This transform is taken from \cite{quant-ph/0301040}.
+Now we present a construction from \cite{quant-ph/0301040}.
 

### 2019-11-27 hamiltonian.tex
Rename XZ-circuit to HT-circuit

@@
 
+We will first show that $\set{H, T}$ is a universal gate set.
+
+\begin{definition}
+	Call $C$ an $HT$-circuit if it consists of only Hadamard and Toffoli gates.
+\end{definition}
+
+\begin{theorem}
+	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to an $HT$-circuit $C'$ and classical input $x'$.
+\end{theorem}
+
+We then define and construct an instance of Local Hamiltonian that encodes the history of the computation.
 First, fix $L\in\bbN$ and define the following that implicitly depends on $L$.
@@
 \begin{definition}
-	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \norm{\set{i: U_i\ne I}}\leq L}$
+	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \abs{\set{i: U_i\ne I}}\leq L}$
 \end{definition}
@@
 
-We define a certain form of quantum circuit that is still universal.
-
 \begin{definition}
-	Let $C$ be an XZ-circuit if $C=U_T\ldots U_1$ where $U_i\in\spn\mathcal{G}_{XZ}$.
-\end{definition}
-
-\begin{theorem}
-	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to an XZ-circuit $C'$ and classical input $x'$.
-\end{theorem}
-
-We define and construct an instance of Local Hamiltonian that encodes the history of the computation.
-
-\begin{definition}
-	Let $C(x)$ be an XZ-circuit. Then let $H_{C(x)}$ be with the following properties:
+	Let $C(x)$ be an $HT$-circuit. Then let $H_{C(x)}$ be with the following properties:
 	\begin{itemize}
-		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
-		\item It has an eigenvector $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
+		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
+		\item Has an eigenvector $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
 		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
@@
 \begin{theorem}
-	Given XZ-circuit $C$ and classical $x$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
+	Given $HT$-circuit $C$ and classical $x$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
 \end{theorem}
@@
 \begin{theorem}
-	Given XZ-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
+	Given $HT$-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
 Furthermore, this algorithm doesn't apply any quantum gates, and uses only $X$ and $Z$ measurements.
@@
 	\label{idpadding}
-	Given XZ-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$.
+	Given $HT$-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$.
 One can then measure the last register of $\psi_{C'(x)}$ and obtain with probabiliy $\frac{1}{2}$ the state $C(x)$.
@@
 
-\subsection{XZ-circuits}
+\subsection{$HT$-circuits}
 
-Here we prove that XZ-circuits are universal. After this subsection, we'll be able to assume without loss of generality that all quantum circuits are XZ-circuits.
+Here we prove that $HT$-circuits are universal. After this subsection, we'll be able to assume without loss of generality that all quantum circuits are $HT$-circuits.
 
@@
 
-We verify that our new gate set can be written as combinations of $X$ and $Z$ matrices.
+Note that our new gate set can be written as linear combinations of $X$ and $Z$ matrices.
 
@@
 \begin{theorem}
-	Let $C=U_T\ldots U_1$ be a XZ-circuit, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
+	Let $C=U_T\ldots U_1$ be a $HT$-circuit, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
 	\begin{itemize}
@@
 
-	We can also write $H=\spn\mathcal{G}_{XZ}$.
+	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$.
 Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli.

### 2019-11-28 preliminaries.tex

@@
 	\label{deFinetti}
-	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there is a measure $\nu$ on $D(A)$ such that
-	$$\max_{\Lambda_2,\ldots,\Lambda_l\in\mathcal{M}}\norm{(id\otimes\Lambda_2\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\int \nu(d\sigma)\sigma^{\otimes l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
+	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
+	$$\max_{\Lambda_1,\ldots,\Lambda_l}\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
 \end{theorem}
-
-\Ethan{Explain the terminologies. Also check do something about the integral vs weighted sum}

### 2019-12-23 preliminaries.tex
Implement some suggestions from Dr. Chung

@@
 
-We then define models of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.
+We then define models of interaction between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.
 
 \begin{definition}
-	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
+	A sampling problem $S=(D_x)$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
 	\begin{itemize}
-		\item $\bbP$ is a $\BQP$ machine.
-		\item $\bbV$ is a $\BPP$ machine.
-		\item There is a classical communication channel between $\bbP$ and $\bbV$.
+		\item $\bbP$ is a $\BQP$ machine, which also has access to a quantum channel which can transmit $\tau$ qubits.
+		\item $\bbV$ is a hybrid machine.
+Its classical part is a BPP machine.
+The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel which can transmit $\tau$ qubits.
+At any given time, the verifier is not allowed to possess more than $\tau$ qubits.
+The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical machine.
+		\item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially many bits at any step.
+        \item At any given step, either the verifier or the prover perform computations on their registers and send bits and qubits through the relevant channels to the other party.
 		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.

### 2019-12-23 hamiltonian.tex
Make editorial change

@@
 
-\begin{definition}
-	Call $C$ an $HT$-circuit if it consists of only Hadamard and Toffoli gates.
-\end{definition}
-
 \begin{theorem}
-	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to an $HT$-circuit $C'$ and classical input $x'$.
+	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to another circuit $C'$ and classical input $x'$, where $C'$ contains only Hadamard and Toffoli gates.
 \end{theorem}
@@
 
-$L$ can be thought of as how ``local" the Hamiltonian is. Taking $L=5$ would easily suffice for this paper.
+$L$ can be thought of as how ``local" a Hamiltonian is. Taking $L=5$ would easily suffice for this paper.
 
 \begin{definition}
-	Let $C(x)$ be an $HT$-circuit. Then let $H_{C(x)}$ be with the following properties:
+	Let $C(x)$ be a circuit consisting of Hadamard and Toffoli gates. Then let $H_{C(x)}$ be with the following properties:
 	\begin{itemize}
@@
 \begin{theorem}
-	Given $HT$-circuit $C$ and classical $x$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
+	Given circuit $C$ consisting of Hadamard and Toffoli gates, and $x\in\set{0,1}^*$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
 \end{theorem}
@@
 \begin{theorem}
-	Given $HT$-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
+	Given circuit $C$ consisting of Hadamard and Toffoli gates, and $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
 Furthermore, this algorithm doesn't apply any quantum gates, and uses only $X$ and $Z$ measurements.
@@
 	\label{idpadding}
-	Given $HT$-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$.
-One can then measure the last register of $\psi_{C'(x)}$ and obtain with probabiliy $\frac{1}{2}$ the state $C(x)$.
+	Given circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$.
+One can then measure the time register of $\ket{\psi_{C'(x)}}$ and obtain with probability $\frac{1}{2}$ the state $C(x)$.
 \end{observation}
 
-\subsection{$HT$-circuits}
+\subsection{Circuits of Toffoli and Hadamard gates}
 
-Here we prove that $HT$-circuits are universal. After this subsection, we'll be able to assume without loss of generality that all quantum circuits are $HT$-circuits.
+Here we first prove that $\set{H, T}$ is a universal gate set.
+After this subsection, we'll be able to assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates.
+After doing that, we make a further observation that we'll use later.
 
-We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
+We know that Hadamard gate and controlled phase gate is universal following \cite{quant-ph/0301040}:
 $$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
@@
 \begin{proof}
-
 	Consider the transform on quantum states
@@
 
-Here we reduce a circuit into a local Hamiltonian instance with a few additional properties.
+Here we reduce a circuit into a history XZ local Hamiltonian instance.
 
 \begin{theorem}
-	Let $C=U_T\ldots U_1$ be a $HT$-circuit, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
+	Let $C=U_T\ldots U_1$ be a circuit consisting of Hadamard and Toffoli gates, and let $x\in\set{0, 1}^*$.
+Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
 	\begin{itemize}
@@
 
-\subsection{Measuring ground state}
+\subsection{Checking for ground state}
 

### 2019-12-23 qpip.tex
Add introductory details for qpip
Add TODO for QPIP reference

@@
 
-Here we create a QPIP scheme for...
+Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state.
 In the case for decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}.
@@
 
-We first give an alternative characterization of $\QPIP_0$.
+We then extend our scheme for $\QPIP_0$, by using results from \cite{mahadev_delegation}.
 
-\begin{definition}
-	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$, or has a $\QPIP_{XZ}$ protocol,  with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
-	\begin{itemize}
-		\item $\bbP$ is a $\BQP$ machine.
-		\item $\bbV$ is a hybrid quantum-classical machine. Its classical part is a $\BPP$ machine. Its quantum part is a single-qubit register, on which the verifier can apply only $X$ or $Z$ measurements.
-		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
-		\item There is a classical communication channel between $\bbP$ and $\bbV$.
-		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
-		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
-	\end{itemize}
-\end{definition}
+\subsection{TODO 1 qubit}
 
-\begin{theorem}
-	$\QPIP_{XZ}=\QPIP_0$
-\end{theorem}
+\Ethan{Fix title}
+
+First, we make an observation.
+
+\begin{observation}
+	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
+\end{observation}
 \begin{proof}
-	See \cite{mahadev_delegation}.
+	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
 \end{proof}
@@
 \begin{theorem}
-	There is a $\QPIP_{XZ}$ protocol for \autoref{AlgGroundStateCheck}
-\end{theorem}
-\begin{proof}
-	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is obvious that any attacks on this scheme trivially maps onto an attack on the original scheme.
-\end{proof}
-
-\begin{theorem}
-	$\SampBQP$ is in $\QPIP_{XZ}$ with completeness negligible to perfect and soundness $(O(T^{-c}), 1-O(T^{-c}))$ for any constant $c$.
+	Let $L\in\SampBQP$.
+Then there exists some $\QPIP_1$ protocol for $L$ with completeness negligible to perfect and soundness $(O(T^{-c}), 1-O(T^{-c}))$ for any constant $c$.
+Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
 \end{theorem}
@@
 			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
-			\State The verifier randomly picks $n+m$ copies in sequence and without replacement
-			\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
-			\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
-			\For{$i\gets 1, m$}
-				\State Measure the time register of a fresh copy from the prover
-				\If{Measured $t\geq T$}
-					\State Measure and output its data register
+			\State The verifier randomly picks $n+m$ copies; $m$ for output and $n$ for checking
+			\State $c\gets0$
+			\For{$i\gets1, N$}
+			    \If{Register is for checking}
+			    \State The verifier runs \autoref{AlgGroundStateCheck} on the register
+			    \If{Test passes}
+			        $c\gets c+1$
+			    \EndIf
+			    \ElsIf{Register is for outputting}
+			    \State The verifier measures the clock register
+			    \If{measurement result $\geq\frac{T}{2}$}
+			        \If{$y$ isn't set}
+			            $y\gets$ Measure the data register
+                    \EndIf
+			    \EndIf
+			    \Else
+			    \State Measure the entire register in standard basis
 			    \EndIf
 			\EndFor
+			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
+			\If{$y$ is set}
+			\State output $y$
+			\Else
 			\State Reject
+			\EndIf
 			\Else
@@
 	All errors up to this point is $O(\varepsilon)$.
+\end{proof}
 
-\end{proof}
+\subsection{TODO 0 qubits}
+
+\Ethan{Fix title}

### 2019-12-23 qpip.tex
Make editorial changes

@@
 	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
+	\Ethan{Maybe give the protocol a name then?}
 \end{observation}
@@
 
-	We claim that the following protocol does what is required:
+	We claim that \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} does what is required.
 	\floatname{algorithm}{Protocol}
 	\begin{algorithm}
-		\caption{Our $\QPIP_{XZ}$ protocol}
-		\label{AlgAmp1}
+		\caption{Our $\QPIP_1$ protocol}
+		\label{ProtoQPIP1}
 		\begin{algorithmic}[1]
@@
 
-	This clearly has completeness negligibly close to $1$.
+	It clearly has completeness negligibly close to $1$.
 Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted.
@@
 
-	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers. Denote the state after the random permutation as
+	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers.
+	We can see a random permutation as a classical mix over all possible permutations of $\sigma$; mathematically, it can be written as:
 
@@
 
-	Let $\tilde{\Pi}$ be some fixed permutation. Then it is easy to check that
+	Now we verify that $\sigma'$ is indeed permutation-invariant.
+	Let $\tilde{\Pi}$ be some fixed permutation, then clearly:
 
@@
 	So we simply measure the time register until we get measurement result $t\geq T$. The probability of failing to do so after all $m$ copies is $\frac{1}{2^m}$ which is negligible.
+	\Ethan{Change this, since we changed the algorithm}
 

### 2019-12-23 qpip.tex
Make editorial changes to hybrid client protocol

--- 2019-12-23 qpip.tex
@@
 
-\subsection{TODO 1 qubit}
-
-\Ethan{Fix title}
+\subsection{Protocol for Hybrid Client}
 
@@
 \begin{observation}
+	\label{ProtoGroundStateCheck}
 	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
@@
 	Let $L\in\SampBQP$.
-Then there exists some $\QPIP_1$ protocol for $L$ with completeness negligible to perfect and soundness $(O(T^{-c}), 1-O(T^{-c}))$ for any constant $c$.
+Then there exists some $\QPIP_1$ protocol for $L$ with completeness negligible to perfect and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
 Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
@@
 		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
-		\item $n$ large enough so by Chernoff bound:
+		\item $n$ large enough so the following quantities are negligible in $\varepsilon$ by the Chernoff bound:
 			\begin{itemize}
-				\item[$\circ$] $q'=P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
-				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
+				\item[$\circ$] $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$
+				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$
 			\end{itemize}
@@
 
-	We claim that the following protocol does what is required:
+	With these parameters, we claim that \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} does what is required.
 	\floatname{algorithm}{Protocol}
 	\begin{algorithm}
-		\caption{Our $\QPIP_{XZ}$ protocol}
-		\label{AlgAmp1}
+		\caption{Our $\QPIP_1$ protocol}
+		\label{ProtoQPIP1}
 		\begin{algorithmic}[1]
 			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
-			\State The verifier randomly picks $n+m$ copies; $m$ for output and $n$ for checking
+			\State The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
 			\State $c\gets0$
+			\State $y\gets$null
 			\For{$i\gets1, N$}
-			    \If{Register is for checking}
-			    \State The verifier runs \autoref{AlgGroundStateCheck} on the register
+			    \If{Copy is for checking}
+				\State The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
 			    \If{Test passes}
@@
 			    \EndIf
-			    \ElsIf{Register is for outputting}
-			    \State The verifier measures the clock register
-			    \If{measurement result $\geq\frac{T}{2}$}
-			        \If{$y$ isn't set}
-			            $y\gets$ Measure the data register
+			    \ElsIf{Copy is for outputting}
+			    \State The verifier measures the copy in standard basis
+			    \If{measurement result of the clock register $\geq\frac{T}{2}$}
+			        \If{$y=$null}
+			            $y\gets$ measurement result of the data register
                     \EndIf
@@
 			    \Else
-			    \State Measure the entire register in standard basis
+			    \State The verifier measures the entire register in standard basis
 			    \EndIf
@@
 			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
-			\If{$y$ is set}
+			\If{$y\ne$null}
 			\State output $y$
@@
 
-	This clearly has completeness negligibly close to $1$.
+	It clearly has completeness negligibly close to $1$.
 Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted.
-Let $\sigma$ be the state the prover sends.
+Let $\sigma$ be the state the prover sends to the verifier.
 
-	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers. Denote the state after the random permutation as
+	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers.
+	A random permutation is equivalent to a classical mix over all possible permutations of $\sigma$:
 
@@
 
-	Let $\tilde{\Pi}$ be some fixed permutation. Then it is easy to check that
-
+	Now we verify that $\sigma'$ is permutation-invariant.
+	Let $\tilde{\Pi}$ be some fixed permutation, then clearly:
 	$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger=\sigma'$$
 
-	So $\sigma'$ is permutation-invariant and we can apply \autoref{deFinetti}:
-
+	So we can apply \autoref{deFinetti}. $\exists\set{w_i, \rho_i}$ such that:
 	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+n}(\sigma'-\sum_i w_i\rho_i^{\otimes n+m})}=O(\varepsilon)$$
 
-	Note that $\tilde\sigma=\sum_i w_i\rho_i^{\otimes n+m}$ is a classical probability distribution over inputs $\rho_i^{\otimes n+m}$ with $w_i$ as weights.
+	Note that $\tilde\sigma=\sum_i w_i\rho_i^{\otimes n+m}$ is a classical mix over $\rho_i^{\otimes n+m}$ with weights $w_i$.
 
@@
 	So the accept chance of this prover is $\sum_j w_j p_j>\delta$
-	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.
+	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.
 
 	Let
-	$$J=\set{j:q_j\leq q'}$$
+	$$J=\set{j:q_j\leq P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]}$$
 
-	Then the following is clearly negligible:
+	Recall that then each $q_j$ must be negligible by how we picked $n$. Hence the following is clearly negligible:
 	$$\sum_{j\in J} w_j q_j$$
@@
 	And so is
-	$$\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}$$
+	$$\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}=\frac{\sum_{j\in J} w_j q_j}{\delta}$$
 
@@
 
-	Such $\rho_i$ are $O(\poly(\varepsilon))$-close to $\ket{\psi_{C(x)}}$.
+	Such $\rho_i$ are $O(\negl(\varepsilon))$-close to $\ket{\psi_{C(x)}}$, by applying a Chernoff bound to \autoref{ThmXZCheck}.
 
-	So we simply measure the time register until we get measurement result $t\geq T$. The probability of failing to do so after all $m$ copies is $\frac{1}{2^m}$ which is negligible.
+	The probability of measuring $t\geq T$ on the clock register of $\ket{\psi_{C(x)}}$ is $\frac{1}{2}$, so the probability of failing to do so after $m$ attempts is negligible.
 
@@
 
-\subsection{TODO 0 qubits}
+\subsection{Protocol for Fully Classical Client}
 
-\Ethan{Fix title}
+\Ethan{TODO read Mahadev's?}

### 2019-12-23 qpip.tex
Change protocol section heading
Start last subsection

@@
-\section{Our QPIP Scheme}
+\section{Our Delegation Protocols}
 
@@
 
-\Ethan{TODO read Mahadev's?}
+Here we combine the above scheme with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients.
+
+We first describe the construction in \cite{mahadev_delegation}.
+
+\begin{theorem}
+	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol that...
+	\begin{itemize}
+		\item x
+		\item y
+		\item z
+	\end{itemize}
+\end{theorem}
+\begin{proof}
+	Construction given in \cite{mahadev_delegation}
+\end{proof}
+
+\Ethan{TODO}

### 2019-12-23 qpip.tex
Fix grammatical mistake
Fix typo

@@
 			        \If{$y=$null}
-			            $y\gets$ measurement result of the data register
+			            \State $y\gets$ measurement result of the data register
                     \EndIf
@@
 
-	Such $\rho_i$ are $O(\negl(\varepsilon))$-close to $\ket{\psi_{C(x)}}$, by applying a Chernoff bound to \autoref{ThmXZCheck}.
+	Such $\rho_i$ is $O(\negl(\varepsilon))$-close to $\ket{\psi_{C(x)}}$, by applying a Chernoff bound to \autoref{ThmXZCheck}.
 

### 2019-12-23 qpip.tex
Replace y=null with bot
Fix typo

@@
 			\State $c\gets0$
-			\State $y\gets$null
+			\State $y\gets\bot$
 			\For{$i\gets1, N$}
@@
 			    \If{measurement result of the clock register $\geq\frac{T}{2}$}
-			        \If{$y=$null}
+			        \If{$y=\bot$}
 			            \State $y\gets$ measurement result of the data register
@@
 			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
-			\If{$y\ne$null}
+			\If{$y\ne\bot$}
 			\State output $y$
@@
 
-	Such $\rho_i$ is $O(\negl(\varepsilon))$-close to $\ket{\psi_{C(x)}}$, by applying a Chernoff bound to \autoref{ThmXZCheck}.
+	Such $\rho_i$ is $O(\negl(\varepsilon))$-close to $\ket{\psi_{C'(x)}}$, by applying a Chernoff bound to \autoref{ThmXZCheck}.
 
-	The probability of measuring $t\geq T$ on the clock register of $\ket{\psi_{C(x)}}$ is $\frac{1}{2}$, so the probability of failing to do so after $m$ attempts is negligible.
-
-	Once we do measure $t\geq T$, the data register is guaranteed to be $O(\poly(\varepsilon))$-close to $C(x)$.
+	The probability of measuring $t\geq T$ on the clock register of $\ket{\psi_{C'(x)}}$ is $\frac{1}{2}$, so the probability of failing to do so after $m$ attempts is negligible.
+	Once we do measure $t\geq T$, the data register is $C(x)$.
 

### 2019-12-27 preliminaries.tex
Add discussion results with Han-Hsuan

--- 2019-11-28 preliminaries.tex
@@
 
-Let $\mathcal{B}$ denote the Hilbert space corresponding to a qubit.
-Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian.
+Let $\mathcal{B}$ be the Hilbert space corresponding to one qubit.
+Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian matrices.
+We use $H\geq0$ to denote $H$ being positive semidefinite.
+Let $\lambda(H)$ be the smallest eigenvalue of $H$.
+The ground states of $H$ are the eigenvectors corresponding to $\lambda(H)$.
+For matrix $H$ and subspace $S$, let $H\big|_S=\Pi_S H \Pi_S$, where $\Pi_S$ is the projector onto the subspace $S$.
+For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
+Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
+I.e.
+$\Lambda^2_{1, 2}(X_3)$ would be a Toffoli (CCNOT) gate.
 
+\iffalse
 \begin{definition}
@@
 \begin{definition}
-	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$, $X=\begin{pmatrix}0&1\\1&0\end{pmatrix}$, $Z=\begin{pmatrix}1&0\\0&-1\end{pmatrix}$
-\end{definition}
-
-\begin{definition}
 	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
@@
 \end{definition}
+\fi
 
-We define $\SampBQP$ based on \cite{aaronson_2013}.
+The phase gate and Pauli matrices are denoted as follows.
 
 \begin{definition}
+	$P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$, $X=\begin{pmatrix}0&1\\1&0\end{pmatrix}$,
+	$Y=\begin{pmatrix}0&-i\\i&0\end{pmatrix}$,
+	$Z=\begin{pmatrix}1&0\\0&-1\end{pmatrix}$
+\end{definition}
+
+We define a sampling version of $\BQP$, $\SampBQP$, based on \cite{aaronson_2013}.
+
+\begin{definition} [sampling problem]
 	A sampling problem $S$ is a collection of probability distributions $(D_x)$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{p(n)}$ for some fixed polynomial $p$.
@@
 
-\begin{definition}
-	$\SampBQP$ is the class of sampling problems $S=(D_x)$ for which for all $\varepsilon$ there exists a quantum circuit constructible in time $\poly(n, \frac{1}{\varepsilon})$ that, given $x$ as input, samples from from a probability distribution $\tilde{D}_x$ such that $\norm{\tilde{D}_x-D_x}<\varepsilon$.
+\begin{definition} [$\SampBQP$]
+	$\SampBQP$ is the class of sampling problems $S=(D_x)$ for which for all $\varepsilon$ there exists a quantum circuit constructible in time $\poly(|x|, \frac{1}{\varepsilon})$ that, given $x$ as input, samples from from a probability distribution $\tilde{D}_x$ such that $\norm{\tilde{D}_x-D_x}<\varepsilon$.
 \end{definition}
 
-We then define models of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.
+We  classify the interaction between a (almost classical) client and a quantum server for sampling problems, extending the classification by \cite{mahadev_delegation}.
 
 \begin{definition}
-	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
+	A sampling problem $S=(D_x)$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms \hannote{ protocols?} $(\bbP, \bbV)$ with the following properties with input $x$:
 	\begin{itemize}
-		\item $\bbP$ is a $\BQP$ machine.
-		\item $\bbV$ is a $\BPP$ machine.
-		\item There is a classical communication channel between $\bbP$ and $\bbV$.
+		\item $\bbP$ is run by the prover, a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
+		\item $\bbV$ is run by the verifier, which is a hybrid machine of a classical part and a limited quantum part.
+The classical part is a $\BPP$ machine.
+The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel which can transmit $\tau$ qubits.
+At any given time, the verifier is not allowed to possess more than $\tau$ qubits.
+The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
+		 \item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially\hannote{poly in what} many bits to either direction. 
+		 \item The protocol\hannote{?} is run by steps.
+At any given step, either the verifier or the prover performs computations on their registers and send bits and qubits through the relevant channels to the other party.	\hannote{redundant?}
 		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
-		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
+		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$ outputs a distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
 	\end{itemize}
@@
 
-Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.
+We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which projects the ground state of the Hamiltonian $H_1$ to the ground space of a Hamiltonian $H_2$ with a large gap.
+
+\hannote{original text?}
 \begin{theorem}
@@
 
-Here is a theorem taken from \cite{Brandão2017}.
+There are many formulations of quantum de Finetti theorems. We use the one from \cite{Brandão2017} because we need logarithmic dependence on $|A|$.
 \begin{theorem}

### 2019-12-27 hamiltonian.tex

@@
 
-Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper. Here we'll only state the theorems, and prove them later in the subsections.
+In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian problem. \hannote{proofs in later sections?}
 
-We will first show that $\set{H, T}$ is a universal gate set.
+%Here we lay our theoretical foundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper.
+\hannote{?} Here we'll only state the theorems, and prove them later in the subsections.
 
+First note that $\set{H, T}$ is a universal gate set.
+
+\hannote{citation}
 \begin{theorem}
@@
 
-We then define and construct an instance of Local Hamiltonian that encodes the history of the computation.
-First, fix $L\in\bbN$ and define the following that implicitly depends on $L$.
+%We want to define and construct an instance of Local Hamiltonian that encodes the history of the computation.
+
+ We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$.% and define the following that implicitly depends on $L$.
 
 \begin{definition}
-	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \abs{\set{i: U_i\ne I}}\leq L}$
+	$$\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \abs{\set{i: U_i\ne I}}\leq 5}$$
 \end{definition}
 
-$L$ can be thought of as how ``local" a Hamiltonian is. Taking $L=5$ would easily suffice for this paper.
+%We fix $L=5$ for this paper.For any $L\in\bbN$,
 
-\begin{definition}
-	Let $C(x)$ be a circuit consisting of Hadamard and Toffoli gates. Then let $H_{C(x)}$ be with the following properties:
+\hannote{something?}
+
+\begin{theorem}
+	Let $C$ be a circuit consisting of $T$ Hadamard or Toffoli gates. For any input string $x$,  there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
 	\begin{itemize}
 		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
-		\item Has an eigenvector $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
-		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
+		\item $H_{C(x)}$ has a unique ground state  $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
+We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
+		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
 	\end{itemize}
+\end{theorem}
+
+\iffalse
+\begin{definition}
+	We call the first registers of $\ket{\psi_{C(x)}}$ the data register, and the later registers of $\psi_{C(x)}$ the time register.
 \end{definition}
-
-\begin{definition}
-	We call the first registers of $\psi_{C(x)}$ the data register, and the later registers of $\psi_{C(x)}$ the time register.
-\end{definition}
+\fi
 
 \begin{theorem}
-	Given circuit $C$ consisting of Hadamard and Toffoli gates, and $x\in\set{0,1}^*$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
+	Given a circuit $C$ consisting of Hadamard and Toffoli gates, and an input string $x$, there ea $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
 \end{theorem}

### 2019-12-27 introduction.tex

@@
 
-It was proven that BQP=BQIP.
+It was proven that BQP=BQIP\hannote{who  when and cite}.
 That is, if a quantum computer can efficiently solve a given decision problem, then it can also efficiently convince a classical machine of its solution.
@@
 I've been trying to get a grasp on the particular structure of the local Hamiltonian reduction in order to better analyze it.
+
+\hannote{paste}
+
+We are interested in delegating quantum computations from a classical client to an untrusted quantum server.
+Under this setting, the client would send the server a quantum circuit and an initial state.
+Then, through interaction with the honest server, the client obtains a measurement result as if he measured the true output of the circuit.
+If the server attempts to deceive the client, the client should reject it.
+The case where the circuit encodes a decision problem has been well-studied, and we're now trying to generalize those results to circuits with possibly many bits of output.
+
+If the circuit encodes a decision problem, then by considering adiabatic quantum computation, there exists a reduction to local Hamiltonian.
+Local Hamiltonian is QMA-complete, so there's a certificate for every yes-instance, and no valid certificates for any no-instances.
+An introduction can be found in Kitaev, Shen, and Vyalyi's "Classical and Quantum Computation".
+Furthermore, Biamonte and Love's "Realizable Hamiltonians for Universal Adiabatic Quantum Computers" states that these local Hamiltonians have very simple forms, which in turn implies that in order to check such certificates one only requires abilities to receive qubits and perform X/Z measurements.
+Based on this observation, Mahadev constructed a protocol in "Classical Verification of Quantum Computations" which, under the LWE assumption (a widely believed conjecture in quantum cryptography), allows the prover to commit qubits and act as the verfier's trusted X/Z measurement device.
+This solves the delegation of decision problem from a fully classical client to a quantum server.
+
+To generalize delegation of quantum computations to allow long output, simply repeating the known protocol for every output qubit doesn't work.
+The joint probability distribution between qubits would be incorrect due to entanglements.
+In fact, generally the output qubits encode sampling problems rather than decision problems.
+Furthermore, for decision problems one can argue that the prover's optimal strategy is to send identical copies of a certificate, so Chernoff bound can be applied, but said argument doesn't generalize to sampling problems either.
+To overcome these challenges, we start by modifying the local Hamiltonian construction so it is compatible with long output.
+We then analyze our protocol's soundness more carefully, before using Mahadev's result as a black box to solve the long output case too for fully classical clients.
+
+A possible application for our long output protocol is to make the computation not only verifiable, but also private in the sense of homomorphic encryptions.
+That is, the input is encrypted before being sent to the server.
+The server computes on the encrypted input, obtaining an encrypted output.
+The client then receives and decrypts the output.
+Here we can combine results from Mahadev's "Classical Homomorphic Encryption for Quantum Circuits" with our long output scheme.
+The client can simply send the homomorphic evaluation circuit to the server with the encrypted input.

### 2019-12-27 introduction.tex
Add notes about intro

@@
 
-Below is some intro of it copied from my SoP.
-This is unpolished and mostly a placeholder at the moment though.
+\Ethan{This section is currently all rough draft. We'll probably rewrite almost all of it.}
+
+\Ethan{Below is my attempt to talk about it in my SoP}
 
@@
 
-\hannote{paste}
+\Ethan{Below is my attempt to talk about it in my research proposal}
 

### 2019-12-27 privacy.tex
Add section on privacy

\section{Private Delegation}

We can further generalize the protocol from last section by making the computation private. We do it by combining with \cite{mahadev_qfhe}, that is, homomorphically encrypting...

\Ethan{TODO}

### 2020-01-01 hamiltonian.tex
Add discussion results

@@
 
-In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian problem. \hannote{proofs in later sections?}
+In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian problem. \hannote{put proofs back. Adiabatic ref?}
+
+\Ethan{Adiabatic and spectral gap ref = \cite{adiabatic}}
 
@@
 	\end{itemize}
+
+	Furthermore, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
 \end{theorem}
@@
 \end{definition}
+
+\begin{theorem}
+	Given a circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x$, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
+\end{theorem}
 \fi
@@
 \begin{theorem}
-	Given a circuit $C$ consisting of Hadamard and Toffoli gates, and an input string $x$, there ea $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
-\end{theorem}
-
-\begin{theorem}
-	Given circuit $C$ consisting of Hadamard and Toffoli gates, and $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
-Furthermore, this algorithm doesn't apply any quantum gates, and uses only $X$ and $Z$ measurements.
+	Given circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
+In particular, it accepts the $\ket{psi_{C(x)}}$ with probability $\fot$.
+Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
 \end{theorem}
@@
 	\label{idpadding}
-	Given circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$.
+	Given a circuit $C$ and an input string $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtaining another circuit $C'$.
 One can then measure the time register of $\ket{\psi_{C'(x)}}$ and obtain with probability $\frac{1}{2}$ the state $C(x)$.
@@
 
-Here we first prove that $\set{H, T}$ is a universal gate set.
-After this subsection, we'll be able to assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates.
-After doing that, we make a further observation that we'll use later.
+\hannote{throw this into appendix?}
+ Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
+Because of this result, we cam assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates.
 
-We know that Hadamard gate and controlled phase gate is universal following \cite{quant-ph/0301040}:
+ %After this subsection, we'll be able to assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates.
+%After doing that, we make a further observation that we'll use later.
+
+\hannote{theorem?} We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
 $$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
 	$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-		Which is proven to be universal in \cite{kitaev_1997}.
 
-Now we present a construction from \cite{quant-ph/0301040}.
+Now we present the construction from \cite{quant-ph/0301040}.
 
@@
 	\begin{itemize}
-		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
+		\item consists of either $H$ or $\Lambda(P(i))$, and the number of gates is $T$.\hannote{confusing?}
 		\item uses $n$ qubits
@@
 	\begin{itemize}
-		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
+		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
 		\item uses $n+1$ qubits
-		\item Let $x\in\set{0,1}^n$.
-Let $x||0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
-The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
+		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
+		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
+		%The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
 	\end{itemize}
@@
 		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
-		\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple to verify that $F$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
+		\item When $x$ is classical, $\mathcal{F}(x)=x||0$.
+So $F\circ C(x)=C'(x||0)$.
+It is simple \hannote{need a little more work?}to verify that $\mathcal{F}$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
 	\end{itemize}
@@
 
-\subsection{Constructing a local Hamiltonian instance}
+\subsection{Reducing $\SampBQP$ to  local Hamiltonian }
 
-Here we reduce a circuit into a history XZ local Hamiltonian instance.
+In this section, we show how to reduce a $\SampBQP$ circuit to a  local-$XZ$-Hamiltonian.
 
 \begin{theorem}
-	Let $C=U_T\ldots U_1$ be a circuit consisting of Hadamard and Toffoli gates, and let $x\in\set{0, 1}^*$.
-Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
+	Let $C=U_T\ldots U_1$ be a circuit consisting of Hadamard and Toffoli gates, and let $x\in\set{0, 1}^n$.
+Then there exists a $\BPP$  machine which generates the  description of a $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
 	\begin{itemize}
-		\item its ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
+		\item its unique ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
 		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
 		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
-		\item Has $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
+		\item $H_{C(x)}$ has $O(T)$ nonzero terms whose coefficients are  at most $O(T^3)$.
 	\end{itemize}
@@
 \begin{proof}
-	We ensure states perpendicular to $\ket{\psi_{C(x)}}$ have high eigenvalues.
+	We need to ensure the excited states of $H_{C(x)}$ have high eigenvalues.
 The base construction comes from \cite{kitaev2002classical}.
@@
 
-	\begin{lemma}
+	\begin{lemma} \hannote{throw outside? or just merge}
 		$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
@@
 
-\subsection{Checking for ground state}
+\subsection{Checking the ground state of the local Hamiltonian}
 
-Now we put the above results in term of measurement outputs.
+%Now we put the above results in term of measurement outputs.\hannote{???}
+
+We present an algorithm that checks whether a given state is the ground state of some fixed $H_{C(x)}$ following~\cite{PhysRevA.93.022326}.
 
@@
 		\Procedure{GroundStateCheck}{$\ket\phi$}
-		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
-		\State $p_S\gets\frac{|d_S|}{D}$
-		\State $\widetilde{S}\gets$ Pick weighted using $p_S$
-		\State $\lambda_{\widetilde{S}}\gets$ Measure $\ket\phi$ in the $\widetilde{S}$ basis
+		\State Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
+		\State Set $p_S = \frac{|d_S|}{D}$
+		\State Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
+		\State  Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
 		\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}

### 2020-01-01 preliminaries.tex
Add discussion results

@@
 
+\begin{rmk}
+\hannote{sampling generalize decision blah}
+\end{rmk}
+
 \begin{definition} [$\SampBQP$]
@@
 
+\subsection{Quantum Prover Interactive Protocol (QPIP)}
 We  classify the interaction between a (almost classical) client and a quantum server for sampling problems, extending the classification by \cite{mahadev_delegation}.

### 2020-01-01 qpip.tex
Add discussion results

@@
 Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state.
-In the case for decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}.
+In the case of decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}.
 A prover, honest or not, couldn't do better than sending $n$ identical copies of some state.
-The same reasoning does not generalize to our case, so instead we give the following construction.
+The same reasoning does not work in  our case, so  we give the following construction instead.
 
-We then extend our scheme for $\QPIP_0$, by using results from \cite{mahadev_delegation}.
+We then extend our scheme for $\QPIP_0$ using results from \cite{mahadev_delegation}.
 
@@
 \end{proof}
-
+\hannote{something. pull protocol out?}
 \begin{theorem}
-	Let $L\in\SampBQP$.
-Then there exists some $\QPIP_1$ protocol for $L$ with completeness negligible to perfect and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
+    \label{QPIP1thm}
+	For any $L\in\SampBQP$,  there exists a $\QPIP_1$ protocol for $L$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
 Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
@@
 	\begin{algorithm}
-		\caption{Our $\QPIP_1$ protocol}
+		\caption{ $\QPIP_1$ protocol for $\SampBQP$}
 		\label{ProtoQPIP1}
@@
 
-Here we combine the above scheme with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients.
+Here we combine \autoref{QPIP1thm} with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients.
 
-We first describe the construction in \cite{mahadev_delegation}.
+We first restate the construction in \cite{mahadev_delegation}.
+
+Let $\rho$ be an $n$-qubit state.
+Let $h$ be an n-bits string called the \emph{basis choice}.
+That is, $h_i=0$ indicates that the $i$-th qubit of $\rho$ is to be measured in the standard basis, while $i=1$ indicates Hadamard basis measurement instead.
+Let $D_{\rho, h}$ be the distribution of the corresponding measurement results.
 
 \begin{theorem}
-	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol that...
+    \label{Mahadev_QPIP0_Protocol_Interface}
+	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
 	\begin{itemize}
-		\item x
-		\item y
-		\item z
+	    \item The protocol runs either a ``Hadamard round" or a ``test round" with probability $\fot$ each.
+	    \item With a test round, the verifier outputs nothing other than accept/reject
+	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
+	    \item (completeness) $\forall n\in\mathcal{B}^{\otimes n}, h\in\bbN$ and $h$, there is a prover with negligible reject probability.
+Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_\rho, h$
+	    \item (soundness) Fix $\bbP'$ and $h$.
+Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round.
+Then $\exists\tilde\bbP$ s.t.
+$\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t.
+$D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
 	\end{itemize}
 \end{theorem}
-\begin{proof}
-	Construction given in \cite{mahadev_delegation}
-\end{proof}
 
-\Ethan{TODO}
+\Ethan{Maybe wrap the below into a protocol?}
+
+Let $\varepsilon>0$. Pick $N$ large enough so that by geometric probability getting a 
+We pick $h$ the same way as we'd decide the measurement basis as in \Ethan{TODO ref protocol 2}.
+
+\Ethan{TODO analyze that the above actually works?}

### 2020-01-03 privacy.tex
Start combining with QFHE

@@
 
-We can further generalize the protocol from last section by making the computation private. We do it by combining with \cite{mahadev_qfhe}, that is, homomorphically encrypting...
+\Ethan{TODO Do some kinda intro to the section}
 
-\Ethan{TODO}
+\subsection{Quantum homomorphic encryption scheme}
+
+\Ethan{This subsection is copied and pasted directly from the other QMPC paper and is kinda a mess}
+
+We present the interface of quantum full homomorphic encryption (QFHE) scheme as given in \cite{mahadev_qfhe}.
+
+\begin{dfn}
+	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
+	\begin{itemize}
+		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
+			\begin{itemize}
+				\item $\lambda$: security parameter
+				\item $L$: maximum size of circuits that can be homomorphically evaluated
+			\end{itemize}
+		\item $\mathsf{HE.Enc_{pk}}(\mu)\rightarrow c$
+		\item $\mathsf{HE.Dec_{sk}}(c)\rightarrow \mu^*$
+			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
+		\item $\mathsf{HE.Eval_{evk}}(f, c_1, \ldots, c_l)\rightarrow c_f$
+			\begin{itemize}
+				\item $f$: a circuit of depth at most $L$
+				\item Satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_1),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$
+			\end{itemize}
+	\end{itemize}
+	\Ethan{Figure out what else depends on L}
+\end{dfn}
+
+We also recall the security definition for a FHE scheme.
+
+\begin{dfn}
+	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
+	$$\abs{Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
+	where $(pk, evk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
+	\Ethan{Urmila didn't specify quantum adversary here? Also dropped the $1^L$.}
+\end{dfn}
+
+\begin{thm}
+	There exists a quantum homomorphic encryption scheme $\mathsf{QHE}$ with the following additional
+	\begin{itemize}
+		\item $\mathsf{QHE.Keygen}$ additionally takes $1^L$ as parameter
+		\item There exists a classical encryption scheme $\mathsf{HE}$ such that $\mathsf{QHE}$'s ciphertexts has the form $TODO$, where $c$ encodes $(x, z)$ under $\mathsf{HE}$.
+		\item It allow finer controls of homomorphically applying a circuit on a gate-by-gate basis.
+There is, there exists a universal gate set $G$ and function $\mathsf{QHE.EvalGate}(TODO)$ that outputs ``as expected" \Ethan{huh?} as long as the corresponding \Ethan{hmm...} circuit depth isn't over $L$.
+	\end{itemize}
+\end{thm}
+
+\subsection{Generalizing our delegation protocol using QFHE}
+
+\floatname{algorithm}{Protocol}
+\begin{algorithm}
+	\caption{Verifiable, private, and constant round delegation}
+	\label{ProtoQPIP1}
+	\begin{algorithmic}[1]
+		\State $\mathsf{Keygen}\rightarrow(pk, evk, sk)$
+		\State $\mathsf{Enc}_{pk}(x)=c$
+		\State The client encrypts its input
+		\State The server and the client runs the $\QPIP_0$ protocol homomorphically on this encrypted input \Ethan{Maybe say a bit more since it's not exactly a circuit to begin with...
+Or I guess it has to be written as one}
+	\end{algorithmic}
+\end{algorithm}
+
+TODO prove semantic security (shouldn't be hard)
+
+TODO prove this still has verifiability

### 2020-01-05 qpip.tex
Updates from Overleaf
Implement one of Han-Hsuan's suggestions

@@
 \end{proof}
-\hannote{something. pull protocol out?}
-\begin{theorem}
-    \label{QPIP1thm}
-	For any $L\in\SampBQP$,  there exists a $\QPIP_1$ protocol for $L$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
-Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
-\end{theorem}
-\begin{proof}
-	Set the following variables
-	\begin{itemize}
-		\item $\varepsilon=T^{-c}$
-		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
-		\item $n$ large enough so the following quantities are negligible in $\varepsilon$ by the Chernoff bound:
-			\begin{itemize}
-				\item[$\circ$] $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$
-				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$
-			\end{itemize}
-		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
-	\end{itemize}
 
-	With these parameters, we claim that \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} does what is required.
+Now we present \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}}, a $\QPIP_1$ protocol for any $\SampBQP$ problem with inverse polynomial error in circuit size.
+
 \floatname{algorithm}{Protocol}
@@
 	\begin{algorithmic}[1]
+		\Procedure{QPIP1}{$C, x, c$}
+		\State Let $\varepsilon=T^{-c}$
+		\State Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
+		\State Let $n$ be large enough so both $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ and $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ are negligible in $\varepsilon$ by Chernoff bound
+		\State Let $N$ be large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
+
 		\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
@@
 
+\begin{theorem}
+    \label{QPIP1thm}
+	For any $L\in\SampBQP$, \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} is a protocol for $L$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
+Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
+\end{theorem}
+\begin{proof}
 	It clearly has completeness negligibly close to $1$.
@@
 
-Let $\varepsilon>0$. Pick $N$ large enough so that by geometric probability getting a 
+Let $\varepsilon>0$. Pick $N$ large enough so that by
+
 We pick $h$ the same way as we'd decide the measurement basis as in \Ethan{TODO ref protocol 2}.

### 2020-01-05 privacy.tex
Fix typo
Make some progress on combining QPIP0 with QFHE

@@
 	\begin{itemize}
-		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
+		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
 			\begin{itemize}
@@
 			\end{itemize}
-		\item $\mathsf{HE.Enc_{pk}}(\mu)\rightarrow c$
-		\item $\mathsf{HE.Dec_{sk}}(c)\rightarrow \mu^*$
+		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
+		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
 			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
-		\item $\mathsf{HE.Eval_{evk}}(f, c_1, \ldots, c_l)\rightarrow c_f$
+		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
 			\begin{itemize}
@@
 	\end{itemize}
-	\Ethan{Figure out what else depends on L}
 \end{dfn}
+
+Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.
+
+$\mathsf{Keygen}$ and $\mathsf{Enc}$ can be done classically.
+$\mathsf{Dec}$ commutes with standard basis measurement, and in the event that the result is already a measurement result, can also be done classically.
 
@@
 
-\begin{thm}
-	There exists a quantum homomorphic encryption scheme $\mathsf{QHE}$ with the following additional
-	\begin{itemize}
-		\item $\mathsf{QHE.Keygen}$ additionally takes $1^L$ as parameter
-		\item There exists a classical encryption scheme $\mathsf{HE}$ such that $\mathsf{QHE}$'s ciphertexts has the form $TODO$, where $c$ encodes $(x, z)$ under $\mathsf{HE}$.
-		\item It allow finer controls of homomorphically applying a circuit on a gate-by-gate basis.
-There is, there exists a universal gate set $G$ and function $\mathsf{QHE.EvalGate}(TODO)$ that outputs ``as expected" \Ethan{huh?} as long as the corresponding \Ethan{hmm...} circuit depth isn't over $L$.
-	\end{itemize}
-\end{thm}
+\subsection{Generalizing our delegation protocol using QFHE}
 
-\subsection{Generalizing our delegation protocol using QFHE}
+We construct a verifiable, private, and constant round $\QPIP_0$ protocol by combining our $\QPIP_0$ protocol earlier with \cite{mahadev_qfhe}.
 
@@
 	\caption{Verifiable, private, and constant round delegation}
-	\label{ProtoQPIP1}
+	\label{ProtoPrivateDelegation}
 	\begin{algorithmic}[1]
+		\Procedure{Delegation}{C, x}
 			\State $\mathsf{Keygen}\rightarrow(pk, evk, sk)$
-		\State $\mathsf{Enc}_{pk}(x)=c$
-		\State The client encrypts its input
-		\State The server and the client runs the $\QPIP_0$ protocol homomorphically on this encrypted input \Ethan{Maybe say a bit more since it's not exactly a circuit to begin with...
-Or I guess it has to be written as one}
+			\State Let $\tilde{x}=\mathsf{Enc}_{pk}(x)$
+			\State Let $\tilde{C}$ to the circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{Eval}_{evk}(C, \tilde{x})$
+			\State The client delegates $\tilde{C}(\tilde{x})$ to the server using our $\QPIP_0$ protocol.
+		\EndProcedure
 	\end{algorithmic}
@@
 
-TODO prove semantic security (shouldn't be hard)
+\begin{thm}
+	\autoref{ProtoPrivateDelegation} is IND-CPA secure.
+\end{thm}
+\begin{proof}
+	TODO
+\end{proof}
 
-TODO prove this still has verifiability
+\begin{thm}
+	\autoref{ProtoPrivateDelegation} is a $\QPIP$ scheme for... (TODO) \Ethan{Just copy from earlier and hope I don't need to rewrite too much}
+\end{thm}
+\begin{proof}
+	TODO
+\end{proof}

### 2020-01-05 privacy.tex
Fix typo

@@
 		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
-			\begin{itemize}
-				\item $\lambda$: security parameter
-				\item $L$: maximum size of circuits that can be homomorphically evaluated
-			\end{itemize}
 		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
@@
 		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
-			\begin{itemize}
-				\item $f$: a circuit of depth at most $L$
-				\item Satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_1),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$
-			\end{itemize}
 	\end{itemize}
@@
 Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.
+As this is a homomorphic encryption scheme, it satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$
 

### 2020-01-18 qpip.tex
Add parallel rep ref
Split protocol into two sections

@@
 \section{Our Delegation Protocols}
+
+\section{Delegation Protocol for Hybrid Client}
 
@@
 The same reasoning does not work in our case, so we give the following construction instead.
-
-We then extend our scheme for $\QPIP_0$ using results from \cite{mahadev_delegation}.
-
-\subsection{Protocol for Hybrid Client}
 
@@
 \end{proof}
-
-\subsection{Protocol for Fully Classical Client}
-
-Here we combine \autoref{QPIP1thm} with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients.
-
-We first restate the construction in \cite{mahadev_delegation}.
-
-Let $\rho$ be an $n$-qubit state.
-Let $h$ be an n-bits string called the \emph{basis choice}.
-That is, $h_i=0$ indicates that the $i$-th qubit of $\rho$ is to be measured in the standard basis, while $i=1$ indicates Hadamard basis measurement instead.
-Let $D_{\rho, h}$ be the distribution of the corresponding measurement results.
-
-\begin{theorem}
-    \label{Mahadev_QPIP0_Protocol_Interface}
-	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
-	\begin{itemize}
-	    \item The protocol runs either a ``Hadamard round" or a ``test round" with probability $\fot$ each.
-	    \item With a test round, the verifier outputs nothing other than accept/reject
-	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
-	    \item (completeness) $\forall n\in\mathcal{B}^{\otimes n}, h\in\bbN$ and $h$, there is a prover with negligible reject probability.
-Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_\rho, h$
-	    \item (soundness) Fix $\bbP'$ and $h$.
-Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round.
-Then $\exists\tilde\bbP$ s.t.
-$\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t.
-$D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
-	\end{itemize}
-\end{theorem}
-
-\Ethan{Maybe wrap the below into a protocol?}
-
-Let $\varepsilon>0$. Pick $N$ large enough so that by
-
-We pick $h$ the same way as we'd decide the measurement basis as in \Ethan{TODO ref protocol 2}.
-
-\Ethan{TODO analyze that the above actually works?}

### 2020-01-18 qpip0.tex
Split protocol into two sections

\section{Delegation Protocol for Fully Classical Client}

We then extend our scheme for $\QPIP_0$ using results from \cite{mahadev_delegation}.

Here we combine \autoref{QPIP1thm} with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients. Combining them will cost polynomially rounds, so we use results from \cite{parallelrep} that allows parallel repetition to construct a constant-round protocol.

We first restate the construction in \cite{mahadev_delegation}.

Let $\rho$ be an $n$-qubit state. Let $h$ be an n-bits string called the \emph{basis choice}. That is, $h_i=0$ indicates that the $i$-th qubit of $\rho$ is to be measured in the standard basis, while $i=1$ indicates Hadamard basis measurement instead. Let $D_{\rho, h}$ be the distribution of the corresponding measurement results.

\begin{theorem}
    \label{Mahadev_QPIP0_Protocol_Interface}
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
	\begin{itemize}
	    \item The protocol runs either a ``Hadamard round" or a ``test round" with probability $\fot$ each.
	    \item With a test round, the verifier outputs nothing other than accept/reject
	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
	    \item (completeness) $\forall n\in\mathcal{B}^{\otimes n}, h\in\bbN$ and $h$, there is a prover with negligible reject probability. Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_\rho, h$
	    \item (soundness) Fix $\bbP'$ and $h$. Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round. Then $\exists\tilde\bbP$ s.t. $\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t. $D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
	\end{itemize}
\end{theorem}

\Ethan{Maybe wrap the below into a protocol?}

Let $\varepsilon>0$. Pick $N$ large enough so that by

We pick $h$ the same way as we'd decide the measurement basis as in \Ethan{TODO ref protocol 2}.

\Ethan{TODO analyze that the above actually works?}

### 2020-01-18 qpip0.tex
Start typesetting parallelrep lemma

@@
 Combining them will cost polynomially rounds, so we use results from \cite{parallelrep} that allows parallel repetition to construct a constant-round protocol.
+
+\subsection{Subprotocol for Quantum Measurements}
 
@@
 	\begin{itemize}
-	    \item The protocol runs either a ``Hadamard round" or a ``test round" with probability $\fot$ each.
+	    \item The protocol runs either a ``Hadamard round" or a ``test round".
 	    \item With a test round, the verifier outputs nothing other than accept/reject
@@
 $D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
+		\item This is a 4-round protocol. The prover does not know whether it is a test or Hadamard round until the end of 3rd round.
+		\begin{enumerate}
+			\item The verifier generates $(k, td)$, ``key" and ``trapdoor". It sends the key to the prover.
+			\item The prover computes a classical ``commitment" $y$ and sends it to the verifier.
+			\item The verifier sends $c\in\set{0, 1}$, where $c=0$ corresponds to test round and $c=1$ corresponds to Hadamard round.
+			\item The prover computes and sends a classical string $a$
+		\end{enumerate}
 	\end{itemize}
@@
 
-\Ethan{Maybe wrap the below into a protocol?}
+\subsection{Parallel Repetition of the Measurement Subprotocol}
 
-Let $\varepsilon>0$. Pick $N$ large enough so that by
+Here we follow \cite{parallelrep}.
 
-We pick $h$ the same way as we'd decide the measurement basis as in \Ethan{TODO ref protocol 2}.
+We characterize a prover by two unitaries $(U_0, U)$ acting on the space $\cH_C\otimes\cH_X\otimes\cH_Z\otimes\cH_Y\otimes\cH_K$.
 
-\Ethan{TODO analyze that the above actually works?}
+\Ethan{I'll elaborate on above later, after figuring out exactly what I need or don't need}
+
+Each coordinate can be accepted and rejected separately, and the entire protocol accepts only if all coordinates accept.
+
+Let $A_{k_i, y_i}$ be the set of $a_i$s accepted by the verifier in the test round when the first and second messages are $k_i$ and $y_i$, respectively.
+
+We present a lemma from \cite{parallelrep}.
+
+\begin{lem}
+	Let $(U_0, U)$ be some prover's strategy.
+	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $i\in[m]$, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
+	Let $\gamma$ be sampled uniformly from $\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document}.
+	Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\phi}_{X, Z}$,
+
+	$$TODO-LONG-EQ$$
+
+	where $t$ is the number of qubits in the register $ph$, $z_0, z_1\in\bbC$ such that $\abs{z_0}=\abs{z_1}=1$, and $z_0$, $z_1$, $\ket{\phi_0}_{X, Z}$, $\ket{\phi_1}_{X, Z}$, $\ket{\phi_{err}}_{X, Z}$ may depend on $\gamma$.
+	Furthermore, the following properties are satisfied.
+	\begin{itemize}
+		\item property 1
+		\item property 1
+		\item property 1
+		\item property 1
+		\item property 1
+	\end{itemize}
+\end{lem}

### 2020-01-18 qpip0.tex
Typeset more of parallel rep lemma

@@
 	Let $\gamma$ be sampled uniformly from $\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document}.
-	Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\phi}_{X, Z}$,
+	Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{X, Z}$,
 
@@
 
-	where $t$ is the number of qubits in the register $ph$, $z_0, z_1\in\bbC$ such that $\abs{z_0}=\abs{z_1}=1$, and $z_0$, $z_1$, $\ket{\phi_0}_{X, Z}$, $\ket{\phi_1}_{X, Z}$, $\ket{\phi_{err}}_{X, Z}$ may depend on $\gamma$.
+	where $t$ is the number of qubits in the register $ph$ \Ethan{Where is this register defined?},
+	$z_0, z_1\in\bbC$ such that $\abs{z_0}=\abs{z_1}=1$, and $z_0$, $z_1$, $\ket{\psi_0}_{X, Z}$, $\ket{\psi_1}_{X, Z}$, $\ket{\psi_{err}}_{X, Z}$ may depend on $\gamma$.
 	Furthermore, the following properties are satisfied.
-	\begin{itemize}
-		\item property 1
-		\item property 1
-		\item property 1
-		\item property 1
-		\item property 1
-	\end{itemize}
+	\begin{enumerate}
+		\item Let $\ket{\psi_{err}}=\ket{\psi}-\ket{\psi_0}-\ket{\psi_1}$, then
+			$$\E_\gamma[\norm{\ket{\psi_{err}}}^2]\leq\frac{1}{T}+\negl(n)$$
+		\item TODO Some long property
+		\item For any fixed $\gamma$,
+			$$\E_{b\in\set{0, 1}}\left[\norm{\ket{\psi_{b}}_{X, Z}}^2\right]\leq\frac{1}{2}\norm{\ket{\psi}_{X, Z}}^2$$
+		\item For any fixed $\gamma$ and $c\in\set{0, 1}^m$ such that $c_i=0$, \Ethan{Where's this $M_{X_i}$ defined?}
+			$$\Pr\left[M_{X_i}\circ U\frac{\ket{c}_C\ket{\psi_0}_{X,Z}}{\norm{\psi_0}_{X,Z}}\in A_{k_i, y_i}\right]\leq2^{m-1}\gamma+\negl(n)$$
+		\item For any fixed $\gamma$, there exists an efficient quantum algorithm $\cE_i$ such that
+			$$\Pr\left[\cE_i\left(\frac{\ket{0^m}_C\ket{\psi_1}_{X,Z}}{\norm{\psi_1}_{X,Z}}\in A_{k_i, y_i}\right)\right]\leq1-\negl(n)$$
+	\end{enumerate}
 \end{lem}

### 2020-01-18 qpip0.tex
Add comment on parallel rep
Switch to lemma 3.6 for parallel rep

@@
 
+\iffalse
+
+\Ethan{Do we even need this lemma 3.5, or can we just use 3.6...}
+
 \begin{lem}
@@
 \end{lem}
+
+\fi
+
+\begin{lem}
+	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
+	Let $\gamma_i\xleftarrow{\$}\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document} for each $i\in[m]$.
+	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
+	$$\ket{\psi}=TODO$$
+	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
+	Furthermore, the following properties are satisfied.
+	\begin{enumerate}
+		\item stuff
+		\item stuff
+		\item stuff
+		\item stuff
+		\item stuff
+	\end{enumerate}
+\end{lem}

### 2020-01-18 qpip0.tex
Realize the need to generalize parallelrep

@@
 	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
-	$$\ket{\psi}=TODO$$
+	$$\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ket{\psi_{110}}+\ldots+\ket{\psi_{11\ldots10}}+\ket{\psi_{11\ldots11}}+\ket{\psi_{err}}$$
 	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
-	Furthermore, the following properties are satisfied.
+	Furthermore, the following properties are satisfied. \Ethan{Takes a bit of parsing to see how is our case different here since $c$ might be defined differently for us}
 	\begin{enumerate}
 		\item stuff
-		\item stuff
-		\item stuff
-		\item stuff
+		\item For any fixed $\hat\gamma$... 
+		\item For any fixed $\hat\gamma$...
+		\item For any fixed $c$,
+			$$\E_{\hat\gamma}\left[\norm{\ket{\psi_{err}}_{X,Z}}^2\right]\leq\frac{6m^2}{T}+\negl(n)$$
 		\item stuff

### 2020-01-19 preliminaries.tex
Move QFHE basics into preliminaries

@@
 \end{theorem}
+
+\subsection{Quantum Homomorphic Encryption Schemes}
+
+\begin{dfn}
+	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
+	\begin{itemize}
+		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
+		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
+		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
+			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
+		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
+	\end{itemize}
+\end{dfn}
+
+Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.
+
+As this is a homomorphic encryption scheme, it satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$
+
+We also recall the security definition for a FHE scheme.
+
+\begin{dfn}
+	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
+	$$\abs{Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
+	where $(pk, evk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
+	\Ethan{Urmila didn't specify quantum adversary here? Also dropped the $1^L$.}
+\end{dfn}
+
+Lastly, we recall the definition of a verifiable quantum FHE scheme:
+\begin{dfn}
+	TODO
+\end{dfn}

### 2020-01-19 privacy.tex
Move QFHE basics into preliminaries

@@
 
-We present the interface of quantum full homomorphic encryption (QFHE) scheme as given in \cite{mahadev_qfhe}.
-
-\begin{dfn}
-	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
+We present the interface of quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe}.
+We use this particular QFHE because it allows the use of a classical client.
+Specifically, it has the following extra properties:
 \begin{itemize}
-		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
-		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
-		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
-			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
-		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
+	\item $\mathsf{Keygen}$ can be done classically.
+	\item In the case where the plaintext is classical, $\mathsf{Enc}$ can be done classically.
+	\item $\mathsf{Dec}$ commutes with standard basis measurement. If the ciphertext is a measurement result, it can also be done classically.
 \end{itemize}
-\end{dfn}
-
-Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.
-As this is a homomorphic encryption scheme, it satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$
-
-$\mathsf{Keygen}$ and $\mathsf{Enc}$ can be done classically.
-$\mathsf{Dec}$ commutes with standard basis measurement, and in the event that the result is already a measurement result, can also be done classically.
-
-We also recall the security definition for a FHE scheme.
-
-\begin{dfn}
-	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
-	$$\abs{Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
-	where $(pk, evk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
-	\Ethan{Urmila didn't specify quantum adversary here? Also dropped the $1^L$.}
-\end{dfn}
 

### 2020-01-19 privacy.tex
Make editorial changes

@@
 
-We present the interface of quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe}.
+We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe}.
 We use this particular QFHE because it allows the use of a classical client.
@@
 \begin{itemize}
-	\item $\mathsf{Keygen}$ can be done classically.
-	\item In the case where the plaintext is classical, $\mathsf{Enc}$ can be done classically.
-	\item $\mathsf{Dec}$ commutes with standard basis measurement. If the ciphertext is a measurement result, it can also be done classically.
+	\item $\mathsf{QHE.Keygen}$ can be done classically.
+	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
+	\item $\mathsf{QHE.Dec}$ commutes with standard basis measurement. If the ciphertext is a measurement result, it can also be done classically.
 \end{itemize}
@@
 
-We construct a verifiable, private, and constant round $\QPIP_0$ protocol by combining our $\QPIP_0$ protocol earlier with \cite{mahadev_qfhe}.
-
 \floatname{algorithm}{Protocol}
 \begin{algorithm}
-	\caption{Verifiable, private, and constant round delegation}
+	\caption{Verifiable, secure, and constant round delegation}
 	\label{ProtoPrivateDelegation}
@@
 		\Procedure{Delegation}{C, x}
-			\State $\mathsf{Keygen}\rightarrow(pk, evk, sk)$
+			\State $\mathsf{QHE.Keygen}\rightarrow(pk, evk, sk)$
 			\State Let $\tilde{x}=\mathsf{Enc}_{pk}(x)$
@@
 \begin{proof}
-	TODO
+	This is... not so trivial.
 \end{proof}

### 2020-01-21 parallel/efficient_verification.tex
Updates from Overleaf

\section{Making Verifier Efficient}\label{sec:efficient}
In this section, we construct a CVQC protocol with efficient verification in the CRS+QRO model where a classical common reference string is available for both prover and verifier in addition to quantum access to QRO.
Our main theorem in this section is stated as follows:
\begin{theorem}\label{thm:Eff}
Assuming LWE assumption and existence of post-quantum iO, post-quantum FHE, and two-round CVQC protocol in the standard model, there exists a two-round CVQC protocol for $\QTIME(T)$ with verification complexity $\poly(n, \log T)$ in the CRS+QRO model.
\end{theorem}
%assuming that a standard model instantiation of the two-round protocol given in Sec.~\ref{sec:tworound} is secure.
\begin{remark}
One may think that the underlying two-round CVQC protocol can be in the QROM instead of in the standard model since we rely on the QROM anyway.
However, this is not the case since we need to use the underlying two-round CVQC in a non-black box way, which cannot be done if that is in the QROM.
Since our two-round protocol given in Sec.~\ref{sec:tworound} is only proven secure in the QROM, we do not know any two-round CVQC protocol provably secure in the standard model.
On the other hand, it is widely used heuristic in cryptography that a scheme proven secure in the QROM is also secure in the standard model if the QRO is instantiated by a well-designed cryptographic hash function such as SHA-3. 
Therefore, we believe that it is reasonable to assume that a standard model instantiation of the scheme in  Sec.~\ref{sec:tworound} with a concrete hash function is sound.  
\end{remark}
\begin{remark}
One may think we need not assume CRS in addition to QRO since CRS may be replaced with an output of QRO.
This can be done if CRS is just a uniformly random string.
However, in our construction, CRS is non-uniform and has a certain structure.
Therefore we cannot implement CRS by QRO.
\end{remark}

\subsection{Preparation}
First, we prepare a lemma that is used in our security proof.
\begin{lemma}\label{lem:adaptive_program}
For any finite sets $\calX$ and $\calY$ and two-stage oracle-aided quantum algorithm $\A=(\A_1,\A_2)$, we have
\begin{align*}
\Pr\left[1 \sample \A_2^{H}(\ket{\st_\A},z):\ket{\st_\A}\sample\A_1^{H}()\right]-\Pr\left[1 \sample \A_2^{H[z,G]}(\ket{\st_\A},z):\ket{\st_\A}\sample\A_1^{H}()\right]\leq q_12^{-\frac{\ell}{2}+1}
\end{align*}
where 
$z\sample \bit^{\ell}$,
$H\sample \func(\bit^{\ell}\times \calX,\calY)$, $G\sample \func(\calX,\calY)$, $H[z,G]$ is defined by 
\begin{align*}
H[z,G](z',x)=
\begin{cases}
G(x) &\text{~if~}z'=z \\
H(z',x) &\text{~else}
\end{cases}.    
\end{align*}
where $q_1$ denotes the maximal number of queries by $\A_1$.
\end{lemma}
This can be proven similarly to \cite[Lemma 2.2]{EC:SaiXagYam18}. 
We give a proof in Appendix~\ref{sec:proof_adaptive_program} for completeness.

\subsection{Four-Round Protocol}\label{sec:efficient-four}
First, we construct a four-round scheme with efficient verification, which is transformed into two-round protocol in the next subsection.
Our construction is based on the following building blocks:
\begin{itemize}
\item A two-round CVQC protocol $\Pi=(\pro=\pro_2,\ver=(\ver_1,\ver_\out))$ in the standard model, which works as follows: 
\begin{description}
\item[$\ver_1$:] On input the security parameter $1^\secpar$ and $x$, it generates a pair $(\key,\td)$ of a``key" and ``trapdoor", sends $\key$ to $\pro$, and keeps $\td$ as its internal state.
\item[$\pro_2$:] On input $x$ and $\key$, it generates a response $e$ and sends it to $\ver$.
\item[$\ver_\out$:] On input $x$, $\key$, $\td$, $e$, it returns $\top$ indicating acceptance or $\bot$ indicating rejection.
\end{description}

\item A post-quantum PRG $\PRG:\bit^{\ell_s}\ra \bit^{\ell_r}$ where $\ell_r$ is the length of randomness for $\ver_1$.

%\item A family $\famCRH$ of post-quantum CRH $\CRH:\bit^*\ra \bit^{\Omega(\secpar)}$.

\item An FHE scheme $\Pi_\FHE=(\fhekeygen,\fheenc,\fheeval,\fhedec)$ with post-quantum CPA security.

\item A strong output compressing randomized encoding scheme $\Pi_\RE=(\rsetup,\renc,\rdec)$ with post-quantum security. We denote the simulator for $\Pi_\RE$ by $\calS_\re$.

\item A SNARK $\Pi_{\SNARK}=(\pro_{\snark},\ver_{\snark})$ in the QROM for an $\NP$ language $\lang_{\snark}$ defined below:

We have $(x,\pk_{\fhe},\ct,\ct')\in \lang_{\snark}$
if and only if there exists $e$ such that
$\ct'= \fheeval(\pk_{\fhe},\allowbreak C[x,e],\ct)$ where $C[x,e]$ is a circuit that works as follows:
\begin{description}
\item[$C{[}x,e{]}(s)$:] Given input $s$, it computes $(k,\td)\sample \ver_1(1^\secpar,x;PRG(s))$, and returns $1$ if and only if $\ver_\out(x,k,\td,e)=\top$ and $0$ otherwise. 
\end{description}

%We have $(x,\pk_{\fhe},\ct,\ct')\in \lang_{\snark}$
%if and only if there exists $e$ such that
%$\crh(\crs_{\re})=t$,
%$k=\rdec(\crs_{\re},\Menc)$, and
%$\ct'= \fheeval(\pk_{\fhe},C[x,e],\ct)$ where $C[x,e]$ is a circuit that works as follows:
%\begin{description}
%\item[$C{[}x,e{]}(s)$:] Given input $s$, it computes $(k,\td)\sample \ver_1(1^\secpar,x;PRG(s))$, and returns $1$ if and only if $\ver_\out(x,k,\td,e)=\top$ and $0$ otherwise. 
%\end{description}
\end{itemize}

Let $\lang$ be a BPP language decided by a quantum Turing machine $\QTM$ (i.e., for any $x\in \bit^*$, $x\in \lang$ if and only if $\QTM$ accepts $x$),
and for any $T$, $\lang_T$ denotes the set consisting of $x\in \lang$ such that 
$\QTM$ accepts $x$ in $T$ steps.
Then we construct a 4-round CVQC protocol $(\setupeff,\proeff=(\proefftwo,\proefffour),\vereff=(\vereffone,\vereffthree,\vereffout))$ for $\lang_T$ in the CRS+QRO model where the verifier's efficiency only logarithmically depends on $T$.
Let $H:\bit^{2\secpar}\times \bit^{2\secpar}\ra \bit^{\secpar}$ be a quantum random oracle.

\begin{description}
\item[$\setupeff(1^\secpar)$:]
The setup algorithm takes the security parameter $1^\secpar$ as input, generates $\crs_\re \sample \bit^{\ell}$ % and $\CRH\sample \famCRH$, 
and computes $\ek_\re\sample \rsetup(1^\secpar,1^\ell,\crs_\re)$ %and $t\defeq\crh(\crs_\re)$ 
where $\ell$ is a parameter specified later.
Then it outputs a CRS for verifier $\crs_{\vereff}\defeq \ek_\re$ and a CRS for prover $\crs_{\proeff}\defeq \crs_\re$.\footnote{We note that we divide the CRS into $\crs_{\vereff}$ and $\crs_{\proeff}$ just for the verifier efficiency and soundness still holds even if a cheating prover sees $\crs_{\vereff}$.} 
\item[$\vereffone^{H}$:] 
Given $\crs_{\vereff}= \ek_\re$ and $x$, 
it generates $s\sample \bit^{\ell_s}$ and $(\pk_{\fhe},\sk_{\fhe})\sample \fhekeygen(1^\secpar)$,
computes $\ct\sample \fheenc(\pk_{\fhe},s)$
and  $\Menc\sample \renc(\ek_\re,M,s,T')$
where $M$ is a Turing machine that works as follows:
\begin{description}
\item[$M(s)$:] Given an input $s\in \bit^{\ell_s}$, it computes $(k,\td)\sample \ver_1(1^\secpar,x;PRG(s))$ and outputs $k$
\end{description}
and $T'$ is specified later.
Then it sends $(\Menc,\pk_{\fhe},\ct)$ to $\proeff$ and keeps $\sk_{\fhe}$ as its internal state.

\item[$\proefftwo^{H}$:] Given $\crs_{\proeff}=\crs_\re$, $x$ and the message  $(\Menc,\pk_{\fhe},\ct)$ from the verifier, it computes $k\la \rdec(\crs_{\re},\Menc)$, $e\sample \pro_2(x,k)$, and $\ct'\la \fheeval(\pk_{\fhe},C[x,e],\ct)$ where $C[x,e]$ is a classical circuit defined above.
Then it sends $\ct'$ to $\pro$ and keeps $(\pk_{\fhe},\ct,\ct',e)$ as its state.
\item[$\vereffthree^{H}$] Upon receiving $\ct'$, it randomly picks $z\sample \bit^{2\secpar}$ and sends $z$ to $\proeff$.
\item[$\proefffour^{H}$] Upon receiving $z$, 
it computes $\pi_\snark \sample \pro_{\snark}^{H(z,\cdot)}((x,\pk_{\fhe},\ct,\ct'),e)$
and sends $\pi_\snark$ to $\vereff$.

\item[$\vereffout^{H}$:] 
It returns $\top$ if $\ver_{\snark}^{H(z,\cdot)}((x,\pk_{\fhe},\ct,\ct'),\pi_{\snark})=\top$ and $1 \la \fhedec(\sk_{\fhe},\ct')$ and $\bot$ otherwise.
\end{description}

\paragraph{Choice of parameters.}
\begin{itemize}
\item We set $\ell$ to be an upper bound of the length of $k$ where $(k,\td)\sample \ver_1(1^\secpar,x)$ for $x\in \lang_T$. We note that we have $\ell=\poly(\secpar,T)$.
\item We set $T'$ to be an upperbound of the running time of $M$ on input $s\in \bit^{\ell_s}$ when $x\in \lang_T$. We note that we have $T'=\poly(\secpar,T)$.
\end{itemize}

\paragraph{Verification Efficiency.}
By encoding efficiency of $\Pi_{RE}$ and verification efficiency of $\Pi_{\SNARK}$, $\vereff$ runs in time $\poly(\secpar,|x|,\log T)$.

\begin{theorem}[Completeness]\label{thm:eff_completeness}
%If the protocol is run honestly on input $x\in \lang$, then $\ver$ returns $\bot$ with overwhelming probability.
For any $x\in \lang_T$, 
\begin{align*}
\Pr\left[\langle\proeff^{H}(\crs_{\proeff}),\vereff^H(\crs_{\vereff})\rangle(x)=\bot \right]=\negl(\secpar)    
\end{align*}
where $(\crs_{\proeff},\crs_{\vereff})\sample \setupeff(1^\secpar)$.
\end{theorem}
\begin{proof}
This easily follows from completeness and correctness of the underlying primitives.
\end{proof}

\begin{theorem}[Soundness]\label{thm:eff_soundness}
For any $x\notin \lang_T$ any efficient quantum cheating prover $\A$, 
\begin{align*}
\Pr\left[\langle\A^H(\crs_{\proeff},\crs_{\vereff}),\vereff^H(\crs_{\vereff})\rangle(x)=\top\right]=\negl(\secpar)    
\end{align*}
where $(\crs_{\proeff},\crs_{\vereff})\sample \setupeff(1^\secpar)$.
\end{theorem}
\begin{proof}
We fix $T$ and $x\notin \lang_T$.
Let $\A$ be a cheating prover.
First, we divides $\A$ into the first stage $\A_1$, which is given $(\crs_{\proeff},\crs_{\vereff})$ and the first message and outputs the second message $\ct'$ and its internal state $\ket{\st_{\A}}$, and the second stage $\A_2$, which is given the internal state $\ket{\st_{\A}}$ and the third message and outputs the fourth message $\pi_{\snark}$.
We consider the following sequence of games between an adversary $\A=(\A_1,\A_2)$ and a challenger. 
Let $q_1$ and $q_2$ be an upper bound of number of random oracle queries by $\A_1$ and $\A_2$, respectively.
We denote the event that the challenger returns $1$ in $\game_i$ by $\TT_i$.
\begin{description}
\item[$\game_1$:] This is the original soundness game.
Specifically, the game runs as follows:
\begin{enumerate}
    \item The challenger generates 
    $H\sample \func(\bit^{2\secpar}\times \bit^{2\secpar},\bit^{\secpar})$, 
    $\crs_\re\sample \bit^{\ell}$, %$\CRH\sample \famCRH$, 
    $s\sample \bit^{\ell_s}$, and $(\pk_{\fhe},\sk_{\fhe})\sample \fhekeygen(1^\secpar)$, and computes $\ek_\re\sample \rsetup(1^\secpar,1^\ell,\crs_\re)$,  %$t\defeq\crh(\crs_\re)$, 
    $\ct\sample \fheenc(\pk_{\fhe},s)$, and  $\Menc\sample \renc(\ek_\re,M,s,T')$.
    \item $\A_1^{H}$ is given $\crs_{\proeff}\defeq \crs_\re$, $\crs_{\vereff}\defeq \ek_\re$ and the first message $(\Menc,\pk_{\fhe},\ct)$, and outputs the second message $\ct'$ and its internal state $\ket{\st_{\A}}$.
    \item The challenger randomly picks $z\sample \bit^{2\secpar}$.
    \item $\A_2^{H}$ is given the state $\ket{\st_{\A}}$ and the third message $z$ and outputs $\pi_{\snark}$.
    \item The challenger returns $1$ if  $\ver_{\snark}^{H(z,\cdot)}((x,\pk_{\fhe},\ct,\ct'),\pi_{\snark})=\top$ and $1 \la \fhedec(\sk_{\fhe},\ct')$ and $0$ otherwise.
\end{enumerate}

\item[$\game_2$:]
This game is identical to the previous game except that the oracles given to $\A_2$ and $V_{\snark}$ are replaced with $H[z,G]$ and $G$ in Step 4 and 5 respectively where $G\sample \func(\bit^{2\secpar},\bit^{\secpar})$ and $H[z,G]$ is as defined in Lemma~\ref{lem:adaptive_program}. 
We note that the oracle given to $\A_1$ in Step 2 is unchanged from $H$.

\item[$\game_3$:]
This game is identical to the previous game except that Step 4 and 5 are modified as follows:
\begin{description}
\item[4.] The challenger runs $e \sample \ext^{\A'_2[H,\ket{\st_{\A}},z]}((x,\pk_{\fhe},\ct,\ct'),1^{q_2},1^\secpar)$ where $\A'_2[H,\st_{\A},z]$ is an oracle-aided quantum algorithm that is given an oracle $G$ and emulates $\A_2^{H[z,G]}(\ket{\st_{\A}},z)$.
\item[5.] The challenger returns $1$ if 
$e$ is a valid witness for $(x,\pk_{\fhe},\ct,\ct')\in \lang_{\snark}$ and $1 \la \fhedec(\sk_{\fhe},\ct')$ and $0$ otherwise.
\end{description}

%\item[$\game_4$:]
%This game is identical to the previous game except that Step 5 is modified as follows:
%\begin{description}
%\item[5.] The challenger returns $1$ if 
%$k'=k$ where $(k,\td)\sample \ver_1(1^\secpar,x;PRG(s))$, 
%$(\crs'_{\re},k',e)$ is a valid witness for $(x,\pk_{\fhe},\ct,\ct')\in \lang_{\snark}$ and $1 \la \fhedec(\sk_{\fhe},\ct')$ and $0$ otherwise.
%\end{description}

\item[$\game_4$:]
This game is identical to the previous game except that Step 5 is modified as follows:
\begin{description}
\item[5.] The challenger returns $1$ if 
$e$ is a valid witness for $(x,\pk_{\fhe},\ct,\ct')\in \lang_{\snark}$, and $\ver_\out(x,k,\td,e)=\top$ where $(k,\td)\sample \ver_1(1^\secpar,x;PRG(s))$ and $0$ otherwise.
\end{description}

\item[$\game_5$:]
This game is identical to the previous game except that $\ct$ is generated as $\ct\sample \fheenc(\pk_{\fhe},\allowbreak 0^{2\secpar})$ in Step 1.

\item[$\game_6$:]
This game is identical to the previous game except that $\crs_\re$, $\ek_\re$, and $\Menc$ are generated in a different way. Specifically, in Step $1$, the challenger computes
$(k,\td)\sample \ver_1(1^\secpar,x;PRG(s))$, $(\crs_\re,\Menc)\sample \calS_\re(1^\secpar,1^{|M|},1^{\ell_s},k,T^*)$, and $\ek_\re \sample \rsetup(1^\secpar,1^\ell,\crs_\re)$ where $T^*$ is the running time of $M(\inp)$.
We note that the same $(k,\td)$ generated in this step is also used in Step 5.

\item[$\game_7$:]
This game is identical to the previous game except that $PRG(s)$ used for generating $(k,\td)$ in Step 1 is replaced with a true randomness.
\end{description}

This completes the descriptions of games. 
Our goal is to prove $\Pr[\TT_1]=\negl(\secpar)$. We prove this by the following lemmas. 
Since Lemmas~\ref{lem:eff_gamehop_five}, \ref{lem:eff_gamehop_six}, and \ref{lem:eff_gamehop_seven} can be proven by straightforward reductions, we only give proofs for the rest of lemmas.

\begin{lemma}\label{lem:eff_gamehop_one}
We have $|\Pr[\TT_2]-\Pr[\TT_1]|\leq q_12^{-(\secpar+1)}$.
\end{lemma}
\begin{proof}
This lemma is obtained by applying Lemma~\ref{lem:adaptive_program} for $\B=(\B_1,\B_2)$ described below:
\begin{description}
\item[$\B_1^{O_1}$():]   It generates 
    $\crs_\re\sample \bit^{\ell}$,  $s\sample \bit^{\ell_s}$, and $(\pk_{\fhe},\sk_{\fhe})\sample \fhekeygen(1^\secpar)$, computes $\ek_\re\sample \rsetup(1^\secpar,1^\ell,\crs_\re)$,  $\ct\sample \fheenc(\pk_{\fhe},s)$, $\Menc\sample \renc(\ek_\re,M,s,T')$,  and $\ct\sample \fheenc(\pk_{\fhe},s)$, and sets $\crs_{\proeff}=\crs_\re$ and $\crs_{\vereff}\defeq \ek_\re$.
Then it runs $(\ct',\ket{\st_{\A}})\sample \A_1^{O_1}(\crs_{\proeff},\crs_{\vereff},x,(\Menc,\pk_{\fhe},\ct))$, and outputs $\ket{\st_\B}\defeq(\ket{\st_\A},x,\Menc,\ct,\ct',\sk_\fhe)$.\footnote{Classical strings are encoded as quantum states in a trivial manner.}
\item[$\B_2^{O_2}(\ket{\st_\B},z)$:] 
It runs $\pi_{\snark}\sample \A_2^{O_2}(\ket{\st_\A})$, and outputs $1$ if $\ver_{\snark}^{O_2(z,\cdot)}((x,\pk_{\fhe},\ct,\ct'),\pi_{\snark})=\top$ and $1 \la \fhedec(\sk_{\fhe},\ct')$ and $0$ otherwise.
\end{description}
\end{proof}

\begin{lemma}\label{lem:eff_gamehop_two}
If $\Pi_{\SNARK}$ satisfies the extractability and $\Pr[\TT_2]$ is non-negligible, then $\Pr[\TT_3]$ is also non-negligible.
\end{lemma}
\begin{proof}
Let $\transcript_3$ be the transcript of the protocol before the forth message is sent (i.e., $\transcript_3=(\crs_{\proeff},\crs_{\vereff},\Menc,\pk_{\fhe},\ct',z)$).
We say that $(H,\sk_\fhe,\transcript_3,\ket{\st_\A})$ is good if we randomly choose $G\sample \func(\bit^{2\secpar},\bit^{\secpar})$ and run $\pi_{\snark}\sample \A_2^{H[z,G]}(\ket{\st_\A})$ to complete the transcript, then the transcript is accepted (i.e., we have $\ver_{\snark}^{G}((x,\pk_{\fhe},\ct,\ct'),\pi_{\snark})=\top$ and $1 \la \fhedec(\sk_{\fhe},\ct')$) with non-negligible probability.
By a standard averaging argument, if $\Pr[\TT_2]$ is non-negligible, then a non-negligible fraction of $(H,\sk_\fhe,\transcript_3,\ket{\st_\A})$ is good when they are generated as in $\game_2$.
We fix good $(\transcript_3,\sk_\fhe,\ket{\st_\A})$.
Then by the extractability of $\Pi_{\SNARK}$, $\ext$ succeeds in extracting a witness for $(x,\pk_{\fhe},\ct,\ct')\in \lang_{\snark}$ with non-negligible probability. Moreover, since we assume $(H,\sk_\fhe,\transcript_3,\ket{\st_\A})$ is good, we always have $1 \la \fhedec(\sk_{\fhe},\ct')$ (since otherwise a transcript with prefix $\transcript_3$ cannot be accepted).
Therefore we can conclude that $\Pr[\TT_3]$ is non-negligible.
\end{proof}

%\begin{lemma}\label{lem:eff_gamehop_three}
%If $\famCRH$ satisfies collision-resistance, then we have $|\Pr[\TT_4]-\Pr[\TT_3]|\leq \negl(\secpar)$.
%\end{lemma}
%\begin{proof}
%If $(\crs'_{\re},k',e)$ is a valid witness for $(x,\pk_{\fhe},\ct,\ct')\in \lang_{\snark}$, then we especially have   $\crh(\crs'_{\re})=t$ and
%$k'=\rdec(\Menc,\crs'_{\re})$.
%Conditioned on this happening, by the collision resistance of $\famCRH$, we have $\crs'_\re=\crs_\re$ with overwhelming probability.
%If this happens, $k'=k$ where $(k,\td)\sample \ver_1(1^\secpar,x;PRG(s))$ by the correctness of $\Pi_{\RE}$.
%Therefore, when the challenger returns $1$ in $\game_3$, we have $k'=k$ with overwhelming probability. Thus, the lemma follows. 
%\end{proof}

\begin{lemma}\label{lem:eff_gamehop_four}
We have $\Pr[\TT_4]=\Pr[\TT_3]$.
\end{lemma}
\begin{proof}
If $e$ is a valid witness for $(x,\pk_{\fhe}, \ct,\ct')\in \lang_{\snark}$, then we especially have $\ct'= \fheeval(\pk_{\fhe},\allowbreak C[x,e],\ct)$.
By the correctness of $\Pi_\FHE$, we have $\fhedec(\sk_\fhe,\ct')=C[x,e](s)=(\ver_\out(x,k,\td,e)\overset{?}{=}\top)$ where $(k,\td)\sample \ver_1(1^\secpar,x;PRG(s))$.
Therefore, the challenger returns $1$ in $\game_4$ if and only if it returns $1$ in $\game_3$.
\end{proof}

\begin{lemma}\label{lem:eff_gamehop_five}
If $\Pi_{\FHE}$ is CPA-secure, then we have $|\Pr[\TT_5]-\Pr[\TT_4]|\leq \negl(\secpar)$.
\end{lemma}

\begin{lemma}\label{lem:eff_gamehop_six}
If $\Pi_{\RE}$ is secure, then we have
$|\Pr[\TT_6]-\Pr[\TT_5]|\leq \negl(\secpar)$.
\end{lemma}

\begin{lemma}\label{lem:eff_gamehop_seven}
If $\PRG$ is secure, then we have  $|\Pr[\TT_7]-\Pr[\TT_6]|\leq \negl(\secpar)$.
\end{lemma}

\begin{lemma}\label{lem:eff_gamehop_eight}
If $(\pro,\ver)$ satisfies soundness, then we have $\Pr[\TT_7]\leq \negl(\secpar)$.
\end{lemma}
\begin{proof}
Suppose that $\Pr[\TT_7]$ is non-negligible. Then we construct an adversary $\B$ against the underlying two-round protocol as follows:
\begin{description}
\item[$\B(k)$:] Given the first message $k$, it generates 
    $H\sample\func(\bit^{2\secpar}\times \bit^{2\secpar},\bit^{\secpar})$, $G\sample \func(\bit^{2\secpar},\allowbreak \bit^{\secpar})$, $z\sample \bit^{2\secpar}$,
    $(k,\td)\sample \ver_1(1^\secpar,x;PRG(s))$, $(\crs_\re,\Menc)\sample \calS_\re(1^\secpar,1^{|M|},1^{\ell_s},k,T^*)$, $\ek_\re \sample \rsetup(1^\secpar,1^\ell,\crs_\re)$,   and $(\pk_{\fhe},\sk_{\fhe})\sample \fhekeygen(1^\secpar)$,  computes  $\ct\sample \fheenc(\allowbreak \pk_{\fhe},0^{2\secpar})$,
    and sets $\crs_{\proeff}=\crs_\re$ and $\crs_{\vereff}\defeq \ek_\re$.
Then it runs $(\ct',\ket{\st_{\A}})\sample \A_1^{H}(\crs_{\proeff},\crs_{\vereff},\allowbreak x,(\Menc,\pk_{\fhe},\ct))$ and $e\sample \ext^{\A'_2[H,\ket{\st_{\A}},z]}((x,\pk_{\fhe},\ct,\ct'),1^{q_2},1^\secpar)$ and outputs $e$.
\end{description}
Then we can easily see that the probability that we have $\ver_\out(x,k,\td,e)$ is at least $\Pr[\TT_7]$.
Therefore, if the underlying two-round protocol is sound, then $\Pr[\TT_7]=\negl(\secpar)$.
\end{proof}

By combining Lemmas~\ref{lem:eff_gamehop_one} to~\ref{lem:eff_gamehop_seven}, we can see that if $\Pr[\TT_1]$ is non-negligible, then $\Pr[\TT_7]$ is also non-negligible, which contradicts Lemma~\ref{lem:eff_gamehop_eight}.
Therefore we conclude that $\Pr[\TT_1]=\negl(\secpar)$.
\end{proof}

%\begin{remark}[On Reducing Rounds]
%One may think that we can shrink the scheme to two-round by letting the prover send the SNARK proof as a part of the second message.
%However, we do not know how to prove the soundness of this version since Chiesa et al.~\cite{TCC:ChiManSpo19} only proved non-adaptive extractability for SNARK in the QROM where the statement should be fixed in advance.  
%If we assume adaptive extractability for SNARK, then we would be able to prove the soundness for the two-round version.
%This motivates to construct SNARK with adaptive extractability in the QROM.
%\end{remark}

\subsection{Reducing to Two-Round via Fiat-Shamir}
Here, we show that the number of rounds can be reduced to $2$ relying on another random oracle.
Namely, we observe that the third message of the scheme is just a public coin, and so we can apply the Fiat-Shamir transform similarly to Sec.\ref{sec:tworound}.
In the following, we describe the protocol for completeness.

Our two-round CVQC protocol $(\setupefffs,\proefffs,\verefffs=(\verefffsone,\verefffsout))$ for $\lang_T$ in the CRS+QRO model is described as follows.
Let $H:\bit^{2\secpar}\times \bit^{2\secpar}\ra \bit^{\secpar}$ be a quantum random oracle and $H':\bit^{\ell_{ct'}}\ra \bit^{2\secpar}$ be another quantum random oracle where $\ell_{\ct'}$ is the maximal length of $\ct'$ in the four-round scheme and $\ell$ and $T'$ be as defined in the previous section.

\begin{description}
\item[$\setupefffs(1^\secpar)$:]
The setup algorithm takes the security parameter $1^\secpar$ as input, generates $\crs_\re \sample \bit^{\ell}$ % and $\CRH\sample \famCRH$, 
and computes $\ek_\re\sample \rsetup(1^\secpar,1^\ell,\crs_\re)$. %and $t\defeq\crh(\crs_\re)$ 
Then it outputs a CRS for verifier $\crs_{\verefffs}\defeq \ek_\re$ and a CRS for prover $\crs_{\proefffs}\defeq \crs_\re$.
\item[$\verefffsone^{H,H'}$:] 
Given $\crs_{\verefffs}= \ek_\re$ and $x$, 
it generates $s\sample \bit^{\ell_s}$ and $(\pk_{\fhe},\sk_{\fhe})\sample \fhekeygen(1^\secpar)$,
computes $\ct\sample \fheenc(\pk_{\fhe},s)$
and  $\Menc\sample \renc(\ek_\re,M,s,T')$
where $M$ is a Turing machine that works as follows:
\begin{description}
\item[$M(s)$:] Given an input $s\in \bit^{\ell_s}$, it computes $(k,\td)\sample \ver_1(1^\secpar,x;PRG(s))$ and outputs $k$.
\end{description}
Then it sends $(\Menc,\pk_{\fhe},\ct)$ to $\proefffs$ and keeps $\sk_{\fhe}$ as its internal state.

\item[$\proefffstwo^{H,H'}$:] Given $\crs_{\proefffs}=\crs_\re$, $x$ and the message  $(\Menc,\pk_{\fhe},\ct)$ from the verifier, it computes $k\la \rdec(\crs_{\re},\Menc)$, $e\sample \pro_2(x,k)$, and $\ct'\la \fheeval(\pk_{\fhe},C[x,e],\ct)$ where $C[x,e]$ is a classical circuit defined above.
Then it computes $z\defeq H'(\ct')$, computes $\pi_\snark \sample \pro_{\snark}^{H(z,\cdot)}((x,\pk_{\fhe},\ct,\ct'),e)$
and sends $(\ct',\pi_\snark)$ to $\verefffs$.

\item[$\verefffsout^{H,H'}$:] 
It computes $z\defeq H'(\ct')$ and returns $\top$ if $\ver_{\snark}^{H(z,\cdot)}((x,\pk_{\fhe},\ct,\ct'),\pi_{\snark})=\top$ and $1 \la \fhedec(\sk_{\fhe},\ct')$ and $\bot$ otherwise.
\end{description}

\paragraph{Verification Efficiency.}
Clearly, the verification efficiency is preserved from the protocol in Sec.~\ref{sec:efficient-four}

\begin{theorem}[Completeness]\label{thm:efffs_completeness}
%If the protocol is run honestly on input $x\in \lang$, then $\ver$ returns $\bot$ with overwhelming probability.
For any $x\in \lang_T$, 
\begin{align*}
\Pr\left[\langle\proefffs^{H,H'}(\crs_{\proefffs}),\verefffs^{H,H'}(\crs_{\verefffs})\rangle(x)=\bot \right]=\negl(\secpar)    
\end{align*}
where $(\crs_{\proefffs},\crs_{\verefffs})\sample \setupefffs(1^\secpar)$.
\end{theorem}

\begin{theorem}[Soundness]\label{thm:efffs_soundness}
For any $x\notin \lang_T$ any efficient quantum cheating prover $\A$, 
\begin{align*}
\Pr\left[\langle\A^{H,H'}(\crs_{\proefffs},\crs_{\vereff}),\verefffs^{H,H'}(\crs_{\verefffs})\rangle(x)=\top\right]=\negl(\secpar)    
\end{align*}
where $(\crs_{\proefffs},\crs_{\verefffs})\sample \setupefffs(1^\secpar)$.
\end{theorem}
This can be reduced to Theorem~\ref{thm:eff_soundness} similarly to the proof of soundness of the protocol in Sec.~\ref{sec:tworound}.

%\begin{remark}[Making the protocol non-interactive in designated verifier setting]
%In the designated verifier setting where the verifier can hold a secret verification key (in other words, the soundness is required only if $\crs_{\verefffs}$ is hidden from a cheating prover), we can make the protocol non-interactive. Moreover, we need not use strong output-compressing randomized encoding (and thus iO) in this setting.
%In the following, we briefly describe the construction.
%First, we observe that the first message of (a standard model instantiation of) the  two-round CVQC protocol given in Sec.~\ref{sec:tworound} only depends on the size of the problem instance $x$ and does not depend on $x$ itself thanks to the similar property of the Mahadev's protocol.
%Then we can construct a non-interactive protocol as follows:
%The setup algorithm generates $s\sample \bit^\secpar$ and 
%$(\pk_{\fhe},\sk_{\fhe})\sample \fhekeygen(1^\secpar)$,
%computes 
%$(k,\td)\sample \ver_1(1^\secpar,1^{|x|};PRG(s))$
%and $\ct\sample \fheenc(\pk_{\fhe},s)$,
%and sets $(k,\pk_{\fhe},\ct)$ as a CRS and $\sk_{\fhe}$ as a secret verification key. 
%The rest of the protocol works similaly to the above scheme.
%We can prove the soundness of the scheme similarly. A caveat is that we can only prove non-adaptive soundness where the statement $x$ should be fixed before the setup since the Mahadev's protocol is only shown to satisfy non-adaptive soundness. 
%\end{remark}

### 2020-01-21 parallel/intro.tex
Updates from Overleaf

\section{Introduction}
Can we verify quantum computations by a classical computer? This problem has been a major open problem in the field until Mahadev~\cite{FOCS:Mahadev18a} finally gave an affirmative solution.
Specifically, she constructed an interactive protocol between an efficient classical verifier (a BPP machine) and an efficient quantum prover (a BQP machine) where the verifier can verify the result of the BQP computation.
(In the following, we call such a protocol a CVQC protocol.\footnote{``CVQC" stands for ``Classical Verification of Quantum Computations"}) 
Soundness of her protocol relies on a computational assumption that the learning with error (LWE) problem \cite{JACM:Regev09} is hard for an efficient quantum algorithm, which has been widely used in the field of cryptography. We refer to the extensive survey by Peikert \cite{FTTCS:Peikert16} for details about LWE and its cryptographic applications.

Though her result is a significant breakthrough, there are still several drawbacks. First, her protocol has soundness error $3/4$, which means that a cheating prover may convince the verifier even if it does not correctly computes the BQP computation with probability at most $3/4$. Though we can exponentially reduce the soundness error by sequential repetition, we need super-constant rounds to reduce the soundness error to be negligible.
If parallel repetition works to reduce the soundness error, then we need not increase the number of round.
However, parallel repetition may not reduce soundness error for computationally sound protocol in general \cite{FOCS:BelImpNao97,TCC:PieWik07}.
Thus, it is still open to construct constant round protocol with negligible soundness error.

Another issue is about verifier's efficiency. In her protocol, for verifying a computation that is done by a quantum computer in time $T$, the verifier's running time is as large as $\poly(T)$.
Considering a situation where a device with weak classical computational power outsources computations to untrusted quantum server, we may want to make the verifier's running time as small as possible.
Such a problem has been studied well in the setting where the prover is classical and we know solutions where verifier's running time only logarithmically depends on $T$~\cite{STOC:Kilian92,SIAM:Micali00,STOC:KalRazRot13,STOC:KalRazRot14,JACM:GolKalRot15,STOC:ReiRotRot16,STOC:BraHolKal17,STOC:BKKSW18,FOCS:HolRot18,STOC:CCHLRRW19,STOC:KalPanYan19}.
%\takashi{We may need not cite such a lot. I just cited all works I know.}
Hopefully, we want to obtain a CVQC protocol where the verifier runs in logarithmic time.  
%However, it is non-trivial to combine the Mahadev's protocol of verification of quantum computations and a verifiable delegation protocol in the classical setting.
%Thus,

\subsection{Our Results}
In this paper, we solve the above drawbacks of the Mahadev's protocol. 
Our contribution is divided into three parts:
\begin{itemize}
    \item We show that parallel repetition version of Mahadev's protocol has negligible soundness error. This gives the first constant round CVQC protocol with negligible soundness error.
    \item We construct a two-round CVQC protocol in the quantum random oracle model (QROM) \cite{AC:BDFLSZ11} where a cryptographic hash function is idealized to be a random function that is only accessible as a quantum oracle.
    This is obtained by applying the Fiat-Shamir transform \cite{C:FiaSha86,C:LiuZha19,C:DFMS19} to the parallel repetition version of the Mahadev's protocol.
    \item We construct a two-round CVQC protocol with logarithmic-time verifier in the CRS+QRO model where both prover and verifier can access to a (classical) common reference string generated by a trusted third party in addition to quantum access to QRO.
    For proving soundness, we assume that a standard model instantiation of our two-round protocol with a concrete hash function (say, SHA-3) is sound and the existence of post-quantum indistinguishability obfuscation \cite{JACM:BGIRSVY12,SIAM:GGH0SW16} and (post-quantum) fully homomorphic encryption (FHE) \cite{STOC:Gentry09} in addition to the quantum hardness of the LWE problem. 
\end{itemize}

\subsection{Related Works}
\paragraph{Verification of Quantum Computation.}
There are long line of researches on verification of quantum computation.
Except for solutions relying on computational assumptions, there are two type of settings where verification of quantum computation is known to be possible.
In the first setting, instead of considering purely classical verifier, we assume that a verifier can perform a certain kind of weak quantum computations \cite{FOCS:BroFitKas09,PR:FitKas17,arXiv:ABOEM17,PR:MorFit18}.
In the second setting, we assume that a prover is splitted into two remote servers that share entanglement but do not communicate \cite{Nat:RUV13}.
Though these works do not give a CVQC protocol in our sense, the advantage is that we need not assume any computational assumption for the proof of soundness, and thus they are incomparable to Mahadev's result and ours.

Subsequent to Mahadev's breakthrough result, Gheorghiu and Vidick \cite{FOCS:GheVid19} gave a CVQC protocol that also satisfies blindness, which ensures that a prover cannot learn what computation is delegated.
We note that their protocol requires polynomial number of rounds.

\paragraph{Concurrent Work.}
In a concurrent and independent work, Alagic et al. \cite{arXiv:AlaChiHun19} also shows similar results to our first and second results, parallel repetition theorem for the Madadev's protocol and a two-round CVQC protocol by the Fiat-Shamir transform.
We note that our third result, a two-round CVQC protocol with efficient verification, is unique in this paper.

### 2020-01-21 parallel/parallel.tex
Updates from Overleaf

\section{Parallel Repetition of Mahadev's Protocol}

\subsection{Overview of Mahadev's Protocol}
Here, we recall the Mahadev's protocol \cite{FOCS:Mahadev18a}. We only give a high-level description of the protocol and properties of it and omit the details since they are not needed to show our result.

The protocol is run between a quantum prover $\pro$ and a classical verifier $\ver$ on a common input $x$. The aim of the protocol is to enable a verifier to classically verify $x\in \lang$ for a BQP language $\lang$ with the help of interactions with a quantum prover.
The protocol is a 4-round protocol where the first message is sent from $\ver$ to $\pro$. 
We denote the $i$-th message generation algorithm by $\ver_i$ for $i\in\{1,3\}$ or $\pro_i$ for $i\in \{2,4\}$ and denote the verifier's final decision algorithm by $\ver_\out$.
Then a high-level description of the protocol is given below.
\begin{description}
\item[$\ver_1$:] On input the security parameter $1^\secpar$ and $x$, it generates a pair $(\key,\td)$ of a``key" and ``trapdoor", sends $\key$ to $\pro$, and keeps $\td$ as its internal state.
\item[$\pro_2$:] On input $x$ and $\key$, it generates a classical ``commitment" $\comy$ along with a quantum state $\ket{\st_\pro}$, sends $\comy$ to $\pro$, and keeps $\ket{\st_\pro}$ as its internal state.
\item[$\ver_3$:] It randomly picks $c\sample \bit$ and sends $c$ to $\pro$.\footnote{The third message is just a public-coin, and does not depend on the transcript so far or $x$.}
For a knowledgeable reader, the case of $c=0$ corresponds to the ``test round" and the case of $c=1$ corresponds to the ``Hadamard round" in the terminology in \cite{FOCS:Mahadev18a}.
\item[$\pro_4$:] On input $\ket{\st_\pro}$ and $c$, it generates a classical string $\ans$ and sends $\ans$ to $\pro$.
\item[$\ver_\out$:] On input $\key$, $\td$, $y$, $c$, and $\ans$, it returns $\top$ indicating acceptance or $\bot$ indicating rejection.
In case $c=0$, the verification can be done publicly, that is, $\ver_\out$ need not take $\td$ as input.
\end{description}

For the protocol, we have the following properties:\\
\noindent\textbf{Completeness:}
For all $x\in \lang$, we have $\Pr[\langle \pro,\ver \rangle(x)]=\bot]= \negl(\secpar)$.\\
\noindent\textbf{Soundness:}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$, we have  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot]\leq 3/4$.

We need a slightly different form of soundness implicitly shown in \cite{FOCS:Mahadev18a}, which roughly says that if a cheating prover can pass the ``test round" (i.e., the case of $c=0$) with overwhelming probability, then it can pass the ``Hadamard round" (i.e., the case of $c=1$) only with a negligible probability. 
\begin{lemma}[implicit in \cite{FOCS:Mahadev18a}]\label{lem:Mah_soundness}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$ such that  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot\mid c=0]=\negl(\secpar)$, we have $\Pr[\langle \pro^*,\ver \rangle(x)]=\top\mid c=1]=\negl(\secpar)$.
\end{lemma}

\subsection{Parallel Repetition}
Here, we prove that the parallel repetition of the Mahadev's protocol decrease the soundness bound to be negligible.
Let $\pro^m$ and $\ver^m$ be $m$-parallel repetitions of the honest prover $\pro$ and verifier $\ver$ in the Mahadev's protocol. Then we have the following:
\begin{theorem}[Completeness]\label{thm:rep_completeness}
For all $x\in \lang$ and $m= \poly(\secpar)$, we have $\Pr[\langle \pro^m,\ver^m \rangle(x)]=\bot]= \negl(\secpar)$.\\
\end{theorem}
\begin{theorem}[Soundness]\label{thm:rep_soundness}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$, we have  $\Pr[\langle \pro^*,\ver^m \rangle(x)]=\top]\leq \negl(\secpar)$ for $m=\poly(\secpar)$.
\end{theorem}

The completeness (Theorem~\ref{thm:rep_completeness}) easily follows from the completeness of the Mahadev's protocol.
In the next subsection, we prove the soundness (Theorem~\ref{thm:rep_soundness}).

\subsection{Proof of Soundness}
\noindent\textbf{Characterization of cheating prover.}
Any cheating prover can be characterized by a tuple $(U_0,\{U_c\}_{c\in \bit^n})$ of unitaries over Hilbert space $\hil_{\regX}\otimes \hil_{\regZ} \otimes \hil_{\regY}  \otimes \hil_{\regK} $. 
A prover characterized by $(U_0,\{U_{\bfc}\}_{\bfc\in \bit^n})$ works as follows.\footnote{Here, we hardwire into the cheating prover the instance $x\notin \lang$ on which it will cheat instead of giving it as an input.}
\begin{description}
\item[Second Message:] Upon receiving $k=(\key_1,...,\key_m)$, it applies $U_0$ to the state $\ket{0}\otimes\ket{0}\otimes\ket{0}\otimes  \ket{k}$, and then measures the $Y$ register to obtain $y=(\comy_1,...,\comy_m)$. Then it sends $\bfy$ to $\ver$ and keeps the resulting state $\ket{\psi_{k,y}}$ over  $\hil_{\regX,\regZ}$.
\item [Forth Message:] Upon receiving $c\in \bit^{m}$, it applies $U_c$ to $\ket{\psi}_{\pro^*}$ and then measures the $\regX$ register in computational basis to obtain $a=(a_1,...,a_m)$. We denote the designated register for $a_i$ by $\regX_i$ 
\end{description}

%Let $\ket{\psi_{k,y}}$ be the prover's state over $\hil_{\regX,\regZ}$ after sending $y=(y_1,...,y_m)$ conditioned on a fixed value of $k$ and $y$.
For $i\in[m]$ and $c_i\in \bit$, let $\Pi_{i,c_i}^{out}$ be the projection to the space spanned by states that 
contains a accepting message in $\regX_i$ w.r.t. the challenge $c_i$.
Then we have
\begin{align*}
\Pr[\langle P^*,V \rangle=accept]=\mathbb{E}_{k,y,c}[\|\Pi_{m,c_m}^{out}...\Pi_{1,c_1}^{out}U_{c}\ket{\psi_{k,y}}\|^{2}]
\end{align*}
We prove this is negligible in the following.

First, we observe that it suffices to show that for any polynomial $p$, there exists $m=O(\log(\secpar))$ such that we have 
\begin{align*}
\mathbb{E}_{k,y,c}[\|\Pi_{m,c_m}^{out}...\Pi_{1,c_1}^{out}U_{c}\ket{\psi_{k,y}}\|^{2}]\leq 1/p(\secpar).
\end{align*}
This is because if we set $m=O(\secpar)$, then we can consider the first $m'=O(\log \secpar)$ coordinates and do the same analysis ignoring the rest of coordinates.
\takashi{Is this correct?}

In the following, we fix a polynomial $p$, and set $m$ and $\epsilon$ so that 
$\epsilon=1/\poly(\secpar)$ and  $(m+1)m2^{m-1}2\epsilon+2^{-m}\leq 1/2p(\secpar)$.

%\begin{lemma}
%Let $U$ be an efficient unitary acting on registers $\regX$, $\regY$, and $\regZ$.
%Let $f:\calX \ra \bit$ be an efficiently computable function and $\Pi_f$ be a projector that projects $\regZ$ register onto the space spanned by $\{\ket{x}\}_{X\in S_f}$
%where $S_f\defeq {x\in \calX \text{~s.t.~}f(x)=1}$ (i.e., we let $\Pi\defeq \sum_{x\in S_f}I\ot I\ot\ket{x}\bra{x})$.
%Then for any $\epsilon=1/\poly(\secpar)$, there exists a decomposition of $\hil_\regX$ into two subspaces $\Sgood$ and $\Sbad$ and an efficient quantum algorithm $\ext$ such that the following is satisfied:
%\begin{enumerate}
%    \item $\ext$ outputs $x\in S_f$ with probability $1$ on any input $\ket{\psigood}\in \Sgood$.    
%    \item For any $\ket{\psibad}\in \Sbad$, we have $\|\Pi_f U\ket{\psibad}\ket{0}\ket{0}\|^2\leq \epsilon$
    %\item If there is an efficient quantum algorithm with input $z$ to generate $\ket{\psi}$ such that $\|\Pi_{\Sgood}\ket{\psi}\|$ is non-negligible where $\Pi_{\Sgood}$ denotes the projection onto $\Sgood$, then there exists an efficient quantum algorithm with input $z$ to generate $\Pi_{\Sgood}\ket{\psi}$ with overwhelming probability. 
%\end{enumerate}
%\end{lemma}

For proving the soundness, we prepare several lemmas.
\begin{lemma}\label{lem:decomp}
Let $\A_i$ be a quantum algorithm that takes a quantum state $\ket{\psi}\in \hil$, picks random $c\sample \bit^m$ such that $c_i=0$, applies a unitary $U_c$ to $\ket{\psi}$ and finally measures $\regX$ to output a classical string $a_i\in \calX$.
%Let $f_i:\calX \ra \bit$ be a function such that $f(x_i)=1$ if and only if $\ver_\out(k_i,y_i,0,x_i)=\top$. 
%Then for any $\epsilon=1/\poly(\secpar)$, 
Then there exist a decomposition of $\hil_{\regX,\regZ}$ into two subspaces $T_{i,0}$ and $T_{i,1}$ and an efficient quantum algorithm $\ext_i$ such that for any fixed $k,y$ and any state $\ket{\psi}$ the followings are satisfied: Let $\Pi_{i,b}^{in}$ be the projection to $T_{i,b}$.
\begin{enumerate}
    \item
    We have $\Pr[\ver_\out(k_i,y_i,0,a_i)=\top: a_i\sample \ext_i(\Pi_{i,0}^{in}\ket{\psi})]=1-\negl(\secpar)$.
    \item We have $\Pr[\ver_\out(k_i,y_i,0,a_i)=\top:a_i\sample \A_i(\Pi_{i,1}^{in}\ket{\psi})]\leq \epsilon$.
    \item Measurement w.r.t. $\{\Pi_{i,0}^{in}, \Pi_{i,1}^{in}\}$ can be done efficiently.
    \takashi{approximately?}
\end{enumerate}
\end{lemma}

\begin{lemma}\label{lem:decomp2}
%For any adversary's second stage strategy $\{U_c\}_{v\in\bit^{m}}$,
%we can define partition $\hil_{\regX,\regZ}$ into $T_{i,0}$ and $T_{i,1}$ for each $i\in[m]$, such that the following properties are satisfied.
For the partitions $(T_{i,0},T_{i,1})_{i\in[m]}$ as defined in Lemma~\ref{lem:decomp}, the following is satisfied:
Assuming LWE, for all $i\in[m]$ and $c\in \bit^{m}$, we have 
    \begin{align*}
     \mathbb{E}_{k,y}\left[\left\|\Pi_{i,c_i}^{out}U_c\Pi_{i,1-c_i}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|^2\right]\leq  2^{m-1}\epsilon +\negl(\secpar).
    \end{align*}
%  \item We have 
%    \begin{align*}
%     \mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}^{out}U_c\Pi_{i,1}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|\right]\leq  (2^m\epsilon)^{1/2}
%    \end{align*}

%  \item Assuming LWE, we have 
%    \begin{align*}
%     \mathbb{E}_{k,y}\left[\left\|\Pi_{i,1}^{out}U_c\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|\right]\leq  \negl(\secpar)
%    \end{align*}
\end{lemma}

\begin{proof}
%For each $i\in [m]$, we apply Lemma~\ref{lem:decomp} w.r.t $\A_i$ 
%that applies the second stage $\A$ with a random $c$ such that $c_i=0$ and then measures $\regX_i$ and $f$ that performs the verification on the $i$-th coordinate in the test round. 
%More precisely, given an input $\ket{\psi}$, it picks random $c_{-i}$, set $c_i\defeq 0$ to define $c$, applies $U_c$ to $\ket{\psi}$, measures $\regX_i$, and outputs the measurement outcome. 
%We define $f(x)=1$ if and only if $\ver_{\out}(k,y,0,x)=accept$.
%By Lemma~\ref{lem:decomp}, there exist a partition ($T_{i,0},T_{i,1}$) of $\hil_{\regX,\regZ}$ and an efficient quantum algorithm $\ext_i$ such that for any state $\ket{\psi}$, 
%\begin{itemize} 
%  \item
%    We have $\Pr[f(x)=1: x\sample \ext_i(\Pi_{i,0}^{in}\ket{\psi})]=1-\negl(\secpar)$.
%    \item We have $\Pr[f(x)=1:x\sample \A_i(\Pi_{i,1}^{in}\ket{\psi})]\leq \epsilon$.
%    \item Measurement w.r.t. $\{\Pi_{i,0}^{in}, \Pi_{i,1}^{in}\}$ can be done efficiently.
%\end{itemize}
First, we show the inequality for the case of $c_i=0$.
For any fixed $k$, $y$, the second claim of Lemma~\ref{lem:decomp} implies 
\begin{align*}
    &~~~\mathbb{E}_{c_{-i}}\left[\left\|\Pi_{i,0}^{out}U_c\Pi_{i,1}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|^2\right] \leq \epsilon,
\end{align*}
which implies 
\begin{align*}
    \left\|\Pi_{i,0}^{out}U_c\Pi_{i,1}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|^2\leq 2^{m-1}\epsilon
\end{align*}
for all $c_{-i}\in \bit^{m-1}$.
Averaging over all $(k,y)$, we obtain the inequality with the case $c_i=0$.

We move on to the proof of the case of $c_i=1$.
To prove this, we assume that 
\begin{align*}
     \mathbb{E}_{k,y}\left[\left\|\Pi_{i,1}^{out}U_c\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|^2\right]\geq 1/\poly(\secpar). 
\end{align*}
for some polynomial $\poly$, and construct an adversary $\B$ that breaks Lemma~\ref{lem:Mah_soundness}.

$\B$ is given $k_i$ as the first round message, and repeats the following procedure $\Theta(\poly(\secpar))$ times:
\begin{enumerate}
\item Pick $k_{-i}$ according to the protocol to complete $k=(k_1,...,k_m)$
\item Pick $c\sample \bit^{m}$ such that $c_i=1$.
\item Run the first stage of $\A$ to obtain $y$ along with its internal state $\ket{\psi_{k,y}}$.
\item Apply a projector $\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}$ to $\ket{\psi_{k,y}}$ by applying iterative projective measurements and unitary $U_c$. We note that these projective measurements can be implemented efficiently by the third claim of  Lemma~\ref{lem:decomp}. 
\takashi{Here, we assume perfect projection. In the actual proof, we have to think about the approximate version.}
If it fails in any of the projection, then it immediately aborts this trial and goes back to the 1st step of the loop.
Otherwise, it goes out the loop to continue the attack.
\end{enumerate}
Since we assume \begin{align*}
    \mathbb{E}_{k,y}\left[\left\|\Pi_{i,1}^{out}U_c\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|^2\right]\geq 1/\poly(\secpar),
\end{align*}
we especially have  
\begin{align*}
\mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|^2\right]\geq 1/\poly(\secpar).
\end{align*}
Therefore, in each trial in the loop, the probability that $\B$ does not abort is at least $1/\poly(\secpar)$. 
Thus, $\B$ goes out the loop within $\Theta(\poly(\secpar))$ times repetitions with overwhelming probability.
Assuming this happens, $\B$ now has $k,y$ along with the state $\ket{\psi_{\B}}\defeq\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}/\left\|\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|$.
Then it sends $y_i$ to the verifier.
Then verifier returns $c'_i$.
\begin{itemize}
\item If $c'_i=0$, $\B$ runs $\ext_i(\ket{\psi_{\B}})$ to obtain $a_i$. This is an accepting answer with probability $1-\negl(\secpar)$ by the first claim of  Lemma~\ref{lem:decomp}.
\item If $c'_i=1$, $\B$ applies $U_c$ to $\ket{\psi_{\B}}$ and then measures $\regX_i$ to obtain $a_i$. 
Let $\fail$ be the event that $\B$ fails to generate $\ket{\psi_{\B}}$ within $\Theta(\poly(\secpar))$ times of trials.
Then we have 
%The probability that $\B$ fails to generate $\ket{\psi_{\B}}$ within $\Theta(\poly(\secpar))$ times of trials and $a_i$ is accepted is 
\begin{align*}
% &~~~\mathbb{E}_{k,y}\left[\left\|\Pi_{i,1}^{out}U_c\left(\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}/\left\|\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|\right)\right\|^2\right]\\
%&\leq 
 &~~~\Pr\left[\ver_{\out}(k_i,\td,y_i,1,a_i) \mid \overline{\fail}\right]\\
 &\leq \Pr\left[\ver_{\out}(k_i,\td,y_i,1,a_i) \wedge \overline{\fail}\right]-\Pr[\fail]\\
 &\leq \mathbb{E}_{k,y}\left[\left\|\Pi_{i,1}^{out}U_c\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|^2\right]-\negl(\secpar)\\
 &\geq 1/\poly(\secpar)-\negl(\secpar).
\end{align*}
\end{itemize}
\takashi{More careful analysis needed.}

Overall, $\B$ succeeds in answering a correct answer with overwhelming probability for the case of $c_i=0$ and with non-negligible probability for the case of $c_i=1$, which contradicts Lemma~\ref{lem:Mah_soundness}.
Therefore, under the LWE assumption, we have
\begin{align*}
   \mathbb{E}_{k,y}\left[\left\|\Pi_{i,1}^{out}U_c\Pi_{i,0}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi_{k,y}}\right\|^2\right]=\negl(\secpar), 
\end{align*}
which concludes the proof of the proof of Lemma~\ref{lem:decomp2}.
\end{proof}

\begin{lemma}\label{lem:decomp3}
For any $\ket{\psi}\in \hil_{\regX,\regZ}$ %and decompositions of $\hil_{\regX,\regZ}$ into $T_{i,0}$ and $T_{i,1}$ for $i\in[m]$ 
and $c\in[m]$, we define
\begin{align*}
 \ket{\psi_i^{c}}\defeq \Pi_{i,1-c_i}^{in}\Pi_{i-1,c_{i-1}}^{in}...\Pi_{1,c_1}^{in}\ket{\psi} 
\end{align*}
and 
\begin{align*}
 \ket{\psi_{m+1}^{c}}\defeq \ket{\psi}-\sum_{i=1}^{m}\ket{\psi_{i}^{c}}.
\end{align*}
Then we have
\begin{align*}
 \mathbb{E}_{c}\left[\left\|\ket{\psi_{m+1}^{c}}\right\|^{2}\right]=2^{-m}.
\end{align*}
\end{lemma}
\begin{proof}
\takashi{easy induction?}
\end{proof}

\begin{lemma}\label{lem:parallel_soundness}
\begin{align*}
\mathbb{E}_{k,y,c}\left[\left\|\Pi_{m,c_m}...\Pi_{1,c_1}U_{c}\ket{\psi_{k,y}}\right\|^{2}\right]\leq 2^{-m} + (m+1)m 2^{m-1}\epsilon +\negl(\secpar).
\end{align*}
\end{lemma}
\begin{proof}
Fix $c$.
We decompose $\ket{\psi_{k,y}}$ as in Lemma~\ref{lem:decomp3} to write 
\begin{align*}
\ket{\psi_{k,y}}=\sum_{i=1}^{m+1}\ket{\psi_{k,y,i}^{c}}.
\end{align*}
Then we have 
\begin{align*}
&~~~\mathbb{E}_{k,y}\left[\left\|\Pi_{m,c_m}^{out}...\Pi_{1,c_1}^{out}U_{c}\ket{\psi_{k,y}}\right\|^2\right]\\
&\leq \mathbb{E}_{k,y}\left[\left(\sum_{i=1}^{m+1}\left\|\Pi_{m,c_m}^{out}...\Pi_{1,c_1}^{out}U_{c}\ket{\psi_{k,y,i}}\right\|\right)^2\right]\\
&\leq \mathbb{E}_{k,y}\left[(m+1)\sum_{i=1}^{m+1}\left\|\Pi_{m,c_m}^{out}...\Pi_{1,c_1}^{out}U_{c}\ket{\psi_{k,y,i}}\right\|^2\right]\\
&\leq (m+1)\left(\sum_{i=1}^{m}\mathbb{E}_{k,y}\left[\left\|\Pi_{i,c_i}^{out}U_{c}\ket{\psi_{k,y,i}}\right\|^2\right]+\mathbb{E}_{k,y}\left[\left\|\ket{\psi_{m+1}^{c}}\right\|^2\right]\right)\\
&\leq (m+1)m 2^{m-1}\epsilon+\negl(\secpar)+ \mathbb{E}_{k,y}\left[\left\|\ket{\psi_{m+1}^{c}}\right\|^2\right]
\end{align*}
by Lemma~\ref{lem:decomp2}.
By taking average over all $c$, we have 
\begin{align*}
&~~~\mathbb{E}_{k,y,c}\left[\left\|\Pi_{m,c_m}...\Pi_{1,c_1}U_{c}\ket{\psi_{k,y}}\right\|^2\right]\\
&\leq (m+1)m 2^{m-1}\epsilon+\negl(\secpar) +\mathbb{E}_{k,y,c}\left[\left\|\ket{\psi_{m+1}^{c}}\right\|^2\right]\\
&\leq (m+1)m 2^{m-1}\epsilon+\negl(\secpar) +2^{-m}
\end{align*}
by Lemma~\ref{lem:decomp3}.
\end{proof}

By Lemma~\ref{lem:parallel_soundness} and $(m+1)m2^{m-1}2\epsilon+2^{-m}\leq 1/2p(\secpar)$, we have 
\begin{align*}
    \mathbb{E}_{k,y,c}\left[\left\|\Pi_{m,c_m}...\Pi_{1,c_1}U_{c}\ket{\psi_{k,y}}\right\|^{2}\right]\leq 1/p(\secpar).
\end{align*}
As discussed in the beginning of this subsection, this suffices to show the soundness of the parallel repetition of the Mahadev's protocol (Theorem~\ref{thm:rep_soundness}).

\subsection{Jordan's Lemma and the Subspace Supporting Test Round}

%In this section, for each trial $i\in [m]$, we will use Jordan's lemma to partition the the Prover's space $\hil$ into $T_i$ and $T^{\bot}_i$, which satisfies the following properties. 
%\begin{itemize}
%    \item $T^{\bot}_i$ is the orthogonal complement of $T_i$ in $\hil$.  
%    \item For $\ket{s} \in T_i$, there exists an efficient quantum algorithm $U_T$, such that $U_T\ket{s}$ can pass the test round with probability $1-\frac{1}{\poly(n)}$; but there is no efficient quantum algorithm $U_H$, such that $U_H\ket{s}$ can pass the Hadamard round. 
%\end{itemize}

Let $m$ be the number of repetitions. We consider the prover's state after sending $y_1,\dots,y_m$. We let the prover's state space be $\hil_{\regX,\regZ}$, where $\regX$ is the register corresponding to the last message and $\regZ$ is the prover's working qubits. We can decompose $\regX$ into $\regX_1,\dots,\regX_m$ without loss of generality, where $\regX_i$ is corresponding to the output message of the $i$th trial.

\begin{lemma}\label{lem:test_subspace}
For $i\in [m]$, we can partition $\hil_{\regX,\regZ}$ into $T_i$, $T^{\bot}_i$, and $T^{err}_i$, such that the following properties are satisfied. 
\begin{itemize}
    \item $T^{\bot}_i$ is the orthogonal complement of $T_i$ in $\hil_{\regX,\regZ}$.
    \item For $\ket{\psi}\in T_i$, for any efficient quantum algorithm $A$ used in Hadamard round, 
    \begin{align*}
        &\Pr[V\left(A(\ket{\psi})\right)=accept]\leq \delta. 
    \end{align*} 
    \takashi{This holds only if $\ket{\psi}$ is generated efficiently.}
    \item For $\ket{\psi^{\bot}}\in T^{\bot}_i$, 
    \begin{align*}
        &\Pr[f^{-1}(y_i)=M_{\regX_i}\circ\ket{\psi^{\bot}}]\leq \epsilon,  
    \end{align*}
    where $M_{\regX_i}$ is the standard-basis measurement in the register $\regX_i$, 
\end{itemize}
\end{lemma}
\nai{Need to specify the relation between $\epsilon$ and $\delta$.}
%\nai{I want to say that $T_i$ is the subspace where the prover can pass the text round but must fail in the Hadamard round. Needs to be more formal.}

%\nai{For $T_i^{\bot}$, do we need to say it cannot pass the test round with high probability? Or, we only need to care $T_i$.}

\begin{lemma}[Jordan's lemma]~\label{lemma:Jordan}
Given any two projectors $\Pi_1$ and $\Pi_2$. There exists a decomposition of the Hilbert space into one-dimensional and two-dimensional subspaces, which satisfy the following properties: 
\begin{itemize}
    \item All subspaces are orthogonal to each other.
    \item For any two-dimensional subspace $S$, for all $\ket{s}\in S$, $\Pi_1 \ket{s} \in S$ and $\Pi_2 \ket{s} \in S$.
    \item For any two-dimensional subspace $S$, $\Pi_1$ and $\Pi_2$ are rank-one projectors, i.e., there exist two vectors $\ket{v_1}$ and $\ket{v_2}$ in $S$ such that for all $ \ket{s}\in S$,  $\Pi_1 \ket{s} = \ipro{v_1}{s}\ket{v_1}$ and $\Pi_2 |s\rangle =\ipro{v_2}{s}\ket{v_2}$. 
\end{itemize}
\end{lemma}
\begin{proof}
We defer the proof to the Appendix. 
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lem:test_subspace}]

Let $\regC$ be the register for the messages $c_1,\dots,c_m$ from the verifier. We define two projectors
\begin{align*}
    &\Pi_{in} := \opro{0}{0}_{\regC}\otimes I_{\regX,\regZ}\quad and \\
    &\Pi_{out} := H_{\regC_{-i}}U_T^{\dag}\left(I_{\regC}\otimes(\opro{f^{-1}(y_i)}{f^{-1}(y_i)})_{\regX_i}\otimes I_{\regX_{-i},\regZ}\right)U_T H_{\regC_{-i}}.  
\end{align*}
\nai{Need to clarify why we set $\regC_{-i}$ be uniform superposition.}

By Jordan's lemma, we can decompose the space $\hil_{\regC,\regX,\regZ}$ into one-dimensional and two-dimensional subspaces. Let $S_1,\dots,S_{\ell}$ be the two-dimensional subspaces from decomposition. Then, $\Pi_{in}$ on $S_1,\dots,S_{\ell}$ can be represented as $\ket{v_1},\dots,\ket{v_{\ell}}$. We can represent $\ket{v_i}$ as $\ket{0}_{\regC}\ket{v'_j}_{\regX,\regZ}$ for all $j\in [\ell]$ since $\Pi_{in}$ has register $\regC$ be all-zero state. Similarly, we represent $\Pi_{out}$ on $S_1,\dots,S_{\ell}$ as $\ket{w}_1,\dots,\ket{w}_{\ell}$.

Now, we define a basis 
\begin{align*}
    B_i := \{\ket{v'_j}_{\regX,\regZ}:\; |\ipro{v_j}{w_j}|^2\geq \epsilon\}. 
\end{align*}
We let $T_i := span(B_i)$ and $T_i^{\bot}$ be the orthogonal complement of $T_i$ in $\hil_{\regX,\regZ}$. It is obvious that $\ket{\psi^{\bot}}\in T_i^{\bot}$ accepted with probability at most $\epsilon$.

Finally, for $\ket{\psi}\in T_i$, we can use amplitude amplification to amplify the accepting probability in the test round to $1$. This implies that the prover only has negligible probability to be rejected in the test round, the probability the prover passes the test round is negligible according to Lemma~\ref{lem:Mah_soundness}. 
\nai{Make it clear how to do amplitude amplification here. We need to ``call the verifier'' to implement the projector $\Pi_{out}$ or the rotation $I-2\Pi_{out}$ since only the verifier knows $f^{-1}(y_i)$.}
\takashi{Lemma~\ref{lem:Mah_soundness} can be applied only if $\ket{\psi}$ is generated by an efficient algorithm. On the other hand, we cannot implement the projection onto $T_i$ efficiently. So here is somehow tricky to argue.}

\end{proof}

\subsection{Approximate and efficient subspace}

For $i\in [k]$, we define $T_i$, $T_i^{err}$, and $T_i^{\bot}$ on space $\hil_{X,Z,C_{-i}}$. Here, $T_i$ is the subspace where

The following procedure define a projector $G_{i\gamma}$. Let $\epsilon = 1/poly$, $T = poly$, and $T << 1/\epsilon$. 
\begin{itemize}
    \item Let $U = V_i P H_{C_{-i}}$. 
    \item $\Pi_{in} := \opro{0}{0}\otimes I_A$. 
    \item $\Pi_{out}$, $R_1$, $R_2$. 
    \item $Q = R_2R_1$. 
    \item Do phase estimation $E$ with precision $\epsilon/2$. 
    \item i.e. $Q\ket{u} = e^{i\hat{\theta}}\ket{u}$. 
    \begin{align*}
        E\ket{u}\ket{0} \rightarrow \sum_{\theta} \alpha_{\theta} \ket{u}\ket{\theta}. 
    \end{align*}
    such that 
    \begin{align*}
        \sum_{\theta\notin \hat{\theta}+\epsilon/2}|\alpha_{\theta}|^2\leq 2^{-n}. 
    \end{align*}
    \item Sample $\gamma$ from $j\epsilon$ for $j\in [T]$
    \begin{align*}
        \ket{u}\ket{\theta}\ket{0} \rightarrow \ket{u}\ket{\theta}\ket{b}
    \end{align*}
    $b=1$ iff $2\pi -(\gamma-\epsilon/2)>\theta>\gamma-\frac{\epsilon}{2}$. 
    \item Uncompute $E$. 
    \item Measure the last qubit (the index of the threshold). 
\end{itemize}

\begin{align*}
    S_{in}:= \opro{0}{0}\otimes I_A \mbox{ wrt }Q_i
\end{align*}
decompose to $\{\ket{u_j}, \theta_j\}$. Here $u_j$ is given by Jordan's Lemma.

for $\ket{\psi}\in S_{in}$
let 
\begin{align*}
    \ket{\psi} = \sum_{j} \alpha_j \ket{u_j}. 
\end{align*}
Fix $\gamma$ define 
\begin{align*}
    &\ket{\psi_0} = \sum_{j: \theta_j <\gamma-\epsilon} \alpha_j\ket{u_j} = \Pi_{\geq \gamma} \ket{\psi}\\
    &\ket{\psi_1} = \sum_{j: \theta_j >\gamma }\alpha_j\ket{u_j} = \Pi_{\leq \gamma-\epsilon} \ket{\psi} \\
    &\ket{\psi_{err}} = \sum_{j: others} \alpha_j\ket{u_j} 
\end{align*}

\begin{align*}
    G_{i,\gamma} (\ket{\psi_0} + \ket{\psi_1}) 
\end{align*}
project to $\ket{\psi_0}$ or $\ket{\psi_1}$ with small error from phase estimation.

\begin{align*}
    &G_{i,\gamma} \ket{\psi} \rightarrow \ket{\tilde{\psi}_0}\mbox{ or }\ket{\tilde{\psi}_1}.\\ 
    &\ket{\tilde{\psi}_b} = \ket{\psi_b}+G_{i,\gamma}\ket{\psi_{err}}.
\end{align*}

Need to prove the following inequality. 
\begin{align*}
    \|\ket{\tilde{\psi}_b} - \ket{\psi_b}\|<\|\ket{\psi_{err}}\|.
\end{align*}

\begin{align*}
    E[\|\ket{\psi_{err}}\|] \leq \sqrt{1/T} \mbox{ or } 1/T. 
\end{align*}

Note: 
\begin{align*}
    \ket{\tilde{\psi}_1}\mbox{ reject by Hadamard round w.h.p}. 
\end{align*}
It seems that we can just analyze $\ket{\tilde{\psi}_b}$ instead of $\ket{\psi_b}$.

\subsection{older proof}
\begin{lemma}
For $i\in [m]$, we can partition $\hil_{\regX,\regZ}$ into $T_{i}$ and $T_{i}^{\bot}$, such that the following properties are satisfied. 
For all $i\in[m]$, $c_{<i}\in \bit^{i-1}$, and efficiently implementable unitary $U$,
\begin{itemize}
    \item $T_{i}^{\bot}$ is the orthogonal complement of $T_{i}$ in $\hil_{\regX,\regZ}$.

    \item We have 
    \begin{align*}
     \mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}\right\|^2\right]\leq   \mathbb{E}_{k,y}\left[\left\|\Pi_{T_{i}}U^{\dagger}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}\right\|^{2}\right]+\left(2^{m+4}\epsilon\right)^{1/2}
    \end{align*}

     \item Assuming LWE, we have 
    \begin{align*}
     \mathbb{E}_{k,y}\left[\left\|\Pi_{i,1}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}\right\|^{2}\right]\leq   \mathbb{E}_{k,y}\left[\left\|\Pi_{T_{i}^{\bot}}U^{\dagger}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}\right\|^{2}\right]+\negl(\secpar)
    \end{align*}
\end{itemize}
\end{lemma}
\begin{proof}
In the following, we denote $\ket{\psi_{k,y,i}}\defeq U^{\dagger}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}$.
For each $i\in [m]$, we apply Lemma~\ref{lem:decomp} w.r.t $\A_i$ 
%that applies the second stage $\A$ with a random $c$ and then measures $\regX_i$. 
%More precisely, 
that, given an input $\ket{\psi}$, applies $U$ to $\ket{\psi}$, measures $\regX_i$, and outputs the measurement outcome. 
By Lemma~\ref{lem:decomp}, there exist a partition ($T_i,T_i^{\bot}$) of $\hil_{\regX,\regZ}$ and an efficient quantum algorithm $\ext_i$ such that for any state $\ket{\psi}$, 
\begin{itemize} 
  \item
    We have $\Pr[f(x)=1: x\sample \ext_i(\Pi_{T_i}\ket{\psi})]=1$.
    \item We have $\Pr[f(x)=1:x\sample \A_i(\Pi_{T_i^{\bot}}\ket{\psi})]\leq \epsilon$.
    \item Measurement w.r.t. $\{\Pi_{T_i}, \Pi_{T_i^{\bot}}\}$ can be done efficiently.
\end{itemize}
For any fixed $k$, $y$, and $c$, we have
\begin{align*}
    &~~~\left\|\Pi_{i,1}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}\right\|\\
    &=\left\|\Pi_{i,1}U\ket{\psi_{k,y,i}}\right\|\\
    &\leq \left\|\Pi_{i,1}U\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|+\left\|\Pi_{i,1}U\Pi_{T_i^\bot}\ket{\psi_{k,y,i}}\right\|\\
    &\leq  \left\|\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|+\left\|\Pi_{i,1}U\Pi_{T_i^\bot}\ket{\psi_{k,y,i}}\right\|.
\end{align*}
By squaring both sides of the inequality, we obtain
\begin{align*}
    &~~~\left\|\Pi_{i,1}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}\right\|^2\\
    &\leq  \left\|\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|^2+\left\|\Pi_{i,1}U\Pi_{T_i^\bot}\ket{\psi_{k,y,i}}\right\|^2+2\left\|\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|\left\|\Pi_{i,1}U\Pi_{T_i^\bot}\ket{\psi_{k,y,i}}\right\|.
\end{align*}

By the second property above, we have
\begin{align*}
    \mathbb{E}_{c}\left[\left\|\Pi_{i,1}U\Pi_{T_i^\bot}\ket{\psi_{k,y,i}}\right\|^{2}\right]\leq \epsilon
\end{align*}
which implies 
\begin{align*}
    \left\|\Pi_{i,1}U\Pi_{T_i^\bot}\ket{\psi_{k,y,i}}\right\|^{2}\leq 2^{m}\epsilon
\end{align*}
for all $c\in \bit^{m}$.
In addition, it is trivial that we have
\begin{align*}
    \left\|\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|\leq 1.
\end{align*}
Then we obtain
\begin{align*}
    &~~~\left\|\Pi_{i,1}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}\right\|^2\\
    &\leq  \left\|\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|^2+2^{m}\epsilon+2\left(2^{m}\epsilon\right)^{1/2}\\
    &\leq \left\|\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|^2+\left(2^{m+4}\epsilon\right)^{1/2}
\end{align*}

Summing up over all $(k,y)$, we obtain the first inequality.

We move on to the proof of the second inequality.
%First, if $\mathbb{E}_{k,y}[\|\ket{\psi_{k,y,i}}\|]=\negl(\secpar)$, then we have 
%\begin{align*}
%\mathbb{E}_{k,y}[\|\Pi_{i,1}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U_{c}\ket{\psi_{k,y}}\|]\leq \mathbb{E}_{k,y}[\|\ket{\psi_{k,y,i}}\|]=\negl(\secpar)   
%\end{align*}
%and thus the inequality trivially holds.
%In the following, we assume that $\mathbb{E}_{k,y}[\|\ket{\psi_{k,y,i}}\|]$ is non-negligible.
Similarly to the above, we have 
\begin{align*}
    &~~~~\mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}\right\|\right]\\
    &=\mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}U\ket{\psi_{k,y,i}}\right\|\right]\\
    &\leq \mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}U\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|\right]+\mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}U\Pi_{T_i^\bot}\ket{\psi_{k,y,i}}\right\|\right]\\
    &\leq \mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}U\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|\right]+\mathbb{E}_{k,y}\left[\left\|\Pi_{T_i^\bot}\ket{\psi_{k,y,i}}\right\|\right]
\end{align*}
Thus it suffices to show 
\begin{align*}
   \mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}U\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|\right]=\negl(\secpar). 
\end{align*}
To prove this, we assume that 
\begin{align*}
   \mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}U\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|\right]\geq 1/\poly(\secpar). 
\end{align*}
for some polynomial $\poly$, and construct an adversary $\B$ that breaks Lemma~\ref{lem:Mah_soundness}.

$\B$ is given $k_i$ as the first round message, and repeats the following procedure $\Theta(\poly(\secpar))$ times:
\begin{enumerate}
\item Pick $k_{-i}$ according to the protocol to complete $k=(k_1,...,k_m)$
\item Pick $c_{<i}\sample \bit^{i-1}$.
\item Run the first stage of $\A$ to obtain $y$ along with its internal state $\ket{\psi_{k,y}}$.
\item Apply $U$ to $\ket{\psi_{k,y}}$ and measures $\regX_1,..,\regX_{i-1}$ to obtain $a_{1}$,...,$a_{i-1}$.
\item If at least one of $a_1$,...,$a_{i-1}$ is not an accepting answer w.r.t. the transcript of the corresponding coordinate, then immediately abort this trial and go back to the 1st step of the loop. 
\item Apply $U^{\dagger}$ to the post-measurement state to obtain $\ket{\psi_{k,y,i}}$.
\item Apply a measurement $\{\Pi_{T_i},\Pi_{T_i^{\bot}}\}$ to $\ket{\psi_{k,y,i}}$. 
If the measurement gives  $\Pi_{T_i^{\bot}}\ket{\psi_{k,y,i}}$, then it immediately aborts this trial and goes back to the 1st step of the loop. Otherwise, it goes out the loop to continue the attack.
\end{enumerate}
Since we assume \begin{align*}
   \mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}U\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|\right]\geq 1/\poly(\secpar),
\end{align*}
we especially have 
\begin{align*}
   \mathbb{E}_{k,y}\left[\left\|\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|\right]\geq 1/\poly(\secpar).    
\end{align*}
Therefore in each trial in the loop, the probability that $\B$ does not abort is at least $1/\poly(\secpar)$. 
Thus, $\B$ goes out the loop within $\Theta(\poly(\secpar))$ times repetitions with overwhelming probability.
Assuming this happens, $\B$ now has $k,y$ along with the corresponding state $\ket{\psi_{\B}}\defeq \Pi_{T_i}\ket{\psi_{k,y,i}}/\left\|\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|$.
Then it sends $y_i$ to the verifier.
Then verifier returns $c_i$.
\begin{itemize}
\item If $c_i=0$, $\B$ runs $\ext_i(\ket{\psi_{\B}})$ to obtain $a_i$. This is an accepting answer with probability 1 by the first property above.
\item If $c_i=1$, $\B$ applies $U$ to  $\ket{\psi_{\B}}$ and then measures $\regX_i$ to obtain $a_i$. The probability that $a_i$ is accepted is 
\begin{align*}
   &~~~~\mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}U\left(\Pi_{T_i}\ket{\psi_{k,y,i}}/\|\Pi_{T_i}\ket{\psi_{k,y,i}}\|\right)\right\|\right]\\
    &\leq \mathbb{E}_{k,y}\left[\left\|\Pi_{i,0}U\Pi_{T_i}\ket{\psi_{k,y,i}}\right\|\right],
\end{align*}
which is assumed to be non-negligible.

\takashi{More careful analysis may be needed here since non-aborting probability in the loop depends on $(k,y)$.}
\end{itemize}

Overall, $\B$ succeeds in answering a correct answer with overwhelming probability for the case of $c_i=0$ and with non-negligible probability for the case of $c_i=1$, which contradicts Lemma~\ref{lem:Mah_soundness}.
Therefore, under the LWE assumption, we have
\begin{align*}
   \mathbb{E}_{k,y}[\|\Pi_{i,0}U\Pi_{T_i}\ket{\psi_{k,y,i}}\|]=\negl(\secpar), 
\end{align*}
which concludes the proof of the proof of Lemma~\ref{lem:decomp2}.

\end{proof}

\begin{theorem}
\begin{align*}
\Pr[\langle P^*,V \rangle=accept]=\mathbb{E}_{k,y,c}\left[\left\|\Pi_{m,c_m}...\Pi_{1,c_1}U_{c}\ket{\psi_{k,y}}\right\|^{2}\right]\leq 2^{-m}+(2^{m+4}\epsilon)^{1/2} +\negl(\secpar).
\end{align*}
\end{theorem}
\begin{proof}
Let $N_{k,y,i,c}\defeq \left\|\Pi_{i,c_i}...\Pi_{1,c_1}U_{c}\ket{\psi_{k,y}}\right\|^{2}$ for notational simplicity.
Summing up the two inequalities in Lemma~\ref{lem:decomp2} and dividing it by $2$, under the LWE assumption, for any $i$, $c_{<i}$, and $U$, we have 
\begin{align*}
     \mathbb{E}_{k,y,c_i}\left[\left\|\Pi_{i,c_i}\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}\right\|^{2}\right]\leq \frac{1}{2}\left(\mathbb{E}_{k,y}\left[\left\|\Pi_{i-1,c_{i-1}}...\Pi_{1,c_1}U\ket{\psi_{k,y}}\right\|^{2}\right]+\left(2^{m+4}\epsilon\right)^{1/2}+\negl(\secpar)\right).  
\end{align*}
By setting $U\defeq U_c$, for any fixed choice of $c_{-i}$, we have
\begin{align*}
\mathbb{E}_{k,y,c_{i}}\left[N_{k,y,i,c}\right]\leq \frac{1}{2}\left(\mathbb{E}_{k,y,c_i}\left[N_{k,y,i-1,c}\right]+\left(2^{m+4}\epsilon\right)^{1/2}+\negl(\secpar)\right).
\end{align*}
\takashi{Should check if $U$ can depend on $c$. I guess the current argument is wrong.}

Then we have
\begin{align*}
 &~~~~\mathbb{E}_{k,y,c}\left[N_{k,y,i,c}\right]\\
 &=  \mathbb{E}_{c_{-i}}\left[\mathbb{E}_{k,y,c_i}\left[N_{k,y,m,c}\right]\right]\\
 &\leq \mathbb{E}_{c_{-i}}\left[\frac{1}{2}\left(\mathbb{E}_{k,y,c_i}\left[N_{k,y,m-1,c}\right]+\left(2^{m+4}\epsilon\right)^{1/2}+\negl(\secpar)\right)\right]\\
 &=\frac{1}{2}\mathbb{E}_{k,y,c}\left[N_{k,y,i-1,c}\right]+\frac{1}{2}\left(\left(2^{m+4}\epsilon\right)^{1/2}+\negl(\secpar)\right)
\end{align*}

Applying this ineuqality for each $i=m,...,1$, we obtain
\begin{align*}
\mathbb{E}_{k,y,c}\left[N_{k,y,m,c}\right]\leq 2^{-m}+\left(2^{m+4}\epsilon\right)^{1/2}+\negl(\secpar).
\end{align*}
\end{proof}

### 2020-01-21 qpip0.tex
Uncomment parallelrep 3.5
Updates from Overleaf

@@
 \section{Delegation Protocol for Fully Classical Client}
+
+\hannote{In this section, we modify the construction of \cite{mahadev_delegation} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}
 
@@
 \subsection{Subprotocol for Quantum Measurements}
-
-We first restate the construction in \cite{mahadev_delegation}.
+%\hannote{what is this for?}
+As a warm-up, we  restate the construction in \cite{mahadev_delegation}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.
 
@@
 
-We present a lemma from \cite{parallelrep}.
-
-\iffalse
-
 \Ethan{Do we even need this lemma 3.5, or can we just use 3.6...}
 
+\hannote{import 3.5. didn't import the proof, too long.}
+
+First, We present a lemma from \cite{parallelrep}  that gives a decomposition of a cheating prover's state. We omit the proof here.
+
+\begin{lemma}[Lemma 3.5 of \cite{parallelrep}]\label{lem:partition}
+Let $(U_0,U)$ be any prover's strategy. Let $m=O(\log \secpar)$, $i\in[m]$, 
+$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\frac{\gamma_0}{T}=1/\poly(\secpar)$.
+Let $\gamma$ be sampled uniformly randomly from $[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}]$.
+Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{\regX,\regZ}$,
+\begin{align*}
+    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+ z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
+\end{align*}
+where $t$ is the number of qubits in the register $ph$, $z_0,z_1\in \mathbb{C}$ such that $|z_0|=|z_1|=1$, and 
+$z_0$, $z_1$, $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ may depend on $\gamma$.
+
+Furthermore, the following properties are satisfied.
+%
+\begin{enumerate}
+%\item There exist (sub-normalized) states $\ket{\psi_0}_{\regX,\regZ}$ and $\ket{\psi_1}_{\regX,\regZ}$ such that when $G_{i,\gamma}$ runs on input $\ket{\psi}_{\regX,\regZ}$, the output is  $(0,\ket{\psi_0}_{\regX,\regZ}/\|\ket{\psi_0}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_0}_{\regX,\regZ}\|^2$, $(1,\ket{\psi_1}_{\regX,\regZ}/\|\ket{\psi_1}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_1}_{\regX,\regZ}\|^2$, and $\bot$ with probability  $1-\|\ket{\psi_0}_{\regX,\regZ}\|^2- \|\ket{\psi_1}_{\regX,\regZ}\|^2$,
+    \item If we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$, then we have  $E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$.
+\item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$.
+%where $M_{ph,th,in}$ is the computational-basis measurement in the register $(ph,th,in)$.
+%and $t$ is the number of qubits in $ph$.
+This implies that if we apply the measurement $M_{ph,th,in}$ on $\frac{G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in}}{\|\ket{\psi}_{\regX,\regZ}\|}$, then the outcome is $0^tb1$ with probability $\|\ket{\psi_b}_{\regX,\regZ}\|^2$ and the resulting state in the register $(\regX,\regZ)$  is $\frac{\ket{\psi_b}_{\regX,\regZ}}{\|\ket{\psi_b}_{\regX,\regZ}\|}$ ignoring a global phase factor.
+    \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. 
+        \item 
+For any fixed $\gamma$ and $c\in \bit^m$ such that $c_i=0$, we have 
+\begin{align*}
+\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq 2^{m-1}\gamma+\negl(\secpar).
+\end{align*}
+    \item 
+For any fixed $\gamma$, there exists an efficient quantum algorithm $\ext_i$ such that 
+\begin{align*}  
+  \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
+  \end{align*}   
+\end{enumerate}
+\end{lemma}
+
+\hannote{duplicate version by ethan..}
 \begin{lem}
@@
 
-\fi
+\Ethan{Below is 3.6. Looks kinda useful but I need to think through this $c$ thing to make sure it'll be fine even if it's not randomly generated.}
+\hannote{How about include 3.6 in the theorem}
+
+\begin{theorem}
+
+ If there exists a $\QPIP_1$ protocol $(\bbV, \bbP)$ for $\SampBQP$ with soundness blah and completeness blah there exists a $\QPIP_0$ protocol $(\bbV', \bbP')$ for $\SampBQP$ with soundness blah' and completeness blah'
+
+\end{theorem}
+\begin{proof}
+We run Mahadev's 4-round protocol \ref{} and use parallel repetition to reduce the soundness error.
+\end{proof}
 
@@
 \end{lem}
+    asdf
+\begin{theorem}
+
+	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ for $\SampBQP$ with soundness blah and completeness blah
+
+\end{theorem}

### 2020-01-21 parallel/appendix.tex

\section{Proof of Lemma~\ref{lem:adaptive_program}}\label{sec:proof_adaptive_program}
Here, we give a proof of Lemma~\ref{lem:adaptive_program}.
We note that the proof is essentially the same as the proof of \cite[Lemma 2.2]{EC:SaiXagYam18}.

Before proving the lemma, we introduce another lemma, which gives a lower bound for a decisional variant of Grover's search problem.

\begin{lemma}[{\cite[Lemma C.1]{SonYun17}}] \label{lem:Decision_Grover}
Let $g_z:\bit^\ell \rightarrow \bit$ denotes a function defined as $g_{z}(z):=1$ and $g_z(z'):=0$ for all $z'\not=z$, and $g_{\bot}:\bit^\ell \rightarrow \bit$ denotes a function that returns $0$ for all inputs. Then for any quantum adversary $\B=(\B_1,\B_2)$ we have 
\[
\left|\Pr[1\sample\B_2(\ket{\st_{\B}},z) \mid \ket{\st_{\B}}\sample \B_1^{g_z}()]- \Pr[1\sample\B_2(\ket{\st_{\B}},z) \mid \ket{\st_{\B}}\sample \B_1^{g_{\bot}}()] \right|\leq q_1 \cdot2^{-\frac{\ell}{2}+1}.
\]
where $z\sample \bit^{\ell}$ and $q_1$ denotes the maximal number of queries by $\B_1$.
\end{lemma}

Then we prove Lemma~\ref{lem:adaptive_program}.

\begin{proof}(of Lemma~\ref{lem:adaptive_program}.)
We consider the following sequence of games.
We denote the event that $\game_i$ returns $1$ by $\TT_i$.
\begin{description}
\item[$\game_1$:] This game simulates the environment of the first term of LHS in the inequality in the lemma. Namely, the challenger chooses $z\sample \bit^{\ell}$, $H\sample \func(\bit^{\ell}\times \calX,\calY)$, $\A_1$ runs with oracle $H$ to generate $\ket{\st_{\A}}$, $\A_2$ runs on input $(\ket{\st_{\A}},z)$ with oracle $H$ to generate a bit $b$, and the game returns $b$.
\item[$\game_2$:] This game is identical to the previous game except that the oracle given to $\A_1$ is replaced with $H[z,G]$ where $G\sample \func(\calX,\calY)$.
\item[$\game_3$:] This game is identical to the previous game except that the oracle given to $\A_1$ is replaced with $H$ and the oracle given to $\A_2$ is replaced with $H[z,G]$.
We note that this game simulates the environment as in the second term of the LHS in the inequality in the lemma.
\end{description}
What we need to prove is $|\Pr[\TT_1]-\Pr[\TT_3]|\leq q_12^{-\frac{\ell}{2}+1}$.
First we observe that the change from $\game_2$ to $\game_3$ is just conceptual and nothing changes from the adversary's view since in both games, the oracles given to $\A_1$ and $\A_2$ are random oracles that agrees on any input $(z',x)$ such that $z'\neq z$ and independent on any input $(z,x)$.
Therefore we have $\Pr[\TT_2]=\Pr[\TT_3]$.
What is left is to prove $|\Pr[\TT_1]-\Pr[\TT_2]|\leq q_12^{-\frac{\ell}{2}+1}$.
For proving this, we construct an algorithm $\B=(\B_1,\B_2)$ that breaks Lemma~\ref{lem:adaptive_program} with the advantage $|\Pr[\TT_1]-\Pr[\TT_2]$ as follows:

\begin{description}
\item[$\B_1^{g^*}()$:] It generates $H\sample \func(\bit^{\ell}\times \calX,\calY)$ and  $G\sample \func(\calX,\calY)$, implements an oracle $O_1$ as
\begin{align*}
O_1(z',x)=
\begin{cases}
G(x) &\text{~if~}g^*(z')=1 \\
H(z',x) &\text{~else}
\end{cases},    
\end{align*}
runs $\ket{\st_{\A}}\sample\A_1^{O_1}()$ and outputs $\ket{\st_{\B}}\defeq \ket{\st_{\A}}$
\item[$\B_2(\ket{\st_{\B}}=\ket{\st_{\A}},z)$:]
It runs $b \sample \A_2^{H}(\ket{\st_{\B}},z)$ and outputs $b$.
\end{description}
It is easy to see that if $g^*=g_{\bot}$, then $\B$ perfectly simulates $\game_1$ for $\A$ and if $g^*=g_z$, then $\B$ perfectly simulates $\game_2$ for $\A$.
Therefore, we have $|\Pr[\TT_1]-\Pr[\TT_2]|\leq q_12^{-\frac{\ell}{2}+1}$ by Lemma~\ref{lem:adaptive_program}.
\end{proof}

### 2020-01-21 parallel/para_main.tex

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts,amsthm}
\usepackage{braket}
\usepackage{authblk}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true,allcolors=blue]{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{mdframed} 
\mdfdefinestyle{figstyle}{ %
  linecolor=black!7, %
  backgroundcolor=black!7, %
  innertopmargin=10pt, %
  innerleftmargin=\textwidth, %
  innerrightmargin=\textwidth, %
  innerbottommargin=5pt %
}

\usepackage{comment}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{fact}{Fact}
\newtheorem{observation}{Observation}
\newtheorem{remark}{Remark}
\newtheorem{problem}{Problem}

\input{macros.tex}

\title{Classical Verification of Quantum Computations with \\ Efficient Verifier}
\begin{document}

\author[1]{Nai-Hui Chia}
\author[2]{Kai-Min Chung}
\author[3]{Takashi Yamakawa\thanks{This work was done in part while the author was visiting Academia Sinica.}}
\affil[1]{Department of Computer Science, University of Texas at Austin}
\affil[2]{Institute of Information Science, Academia Sinica}
\affil[3]{NTT Secure Platform Laboratories}
%\author{Nai-Hui Chia \and
%Kai-Min Chung \and
%Takashi Yamakawa}
%\date{November 2019}

\maketitle
\begin{abstract}
In this paper, we extend the protocol of classical verification of quantum computations (CVQC) recently proposed by Mahadev to make the verification efficient.
Our result is obtained in the following three steps:
\begin{itemize}
    \item We show that parallel repetition of Mahadev's protocol has negligible soundness error. This gives the first constant round CVQC protocol with negligible soundness error. In this part, we only assume the quantum hardness of the learning with error (LWE) problem similarly to the Mahadev's work.
    \item We construct a two-round CVQC protocol in the quantum random oracle model (QROM) where a cryptographic hash function is idealized to be a random function.
    This is obtained by applying the Fiat-Shamir transform to the parallel repetition version of the Mahadev's protocol.
    \item We construct a two-round CVQC protocol with efficient verifier in the CRS+QRO model where both prover and verifier can access to a (classical) common reference string generated by a trusted third party in addition to quantum access to QRO.
    Specifically, the verifier can verify a $\QTIME(T)$ computation in time $\poly(\secpar,\log T)$ where $\secpar$ is the security parameter.
    For proving soundness, we assume that a standard model instantiation of our two-round protocol with a concrete hash function (say, SHA-3) is sound and the existence of post-quantum indistinguishability obfuscation and post-quantum fully homomorphic encryption in addition to the quantum hardness of the LWE problem. 
\end{itemize}
\end{abstract}
\input{intro.tex}
\input{preliminaries.tex}
%\input{parallel.tex}
%\input{parallel_2.tex}
\input{parallel_3.tex}
\input{FiatShamir.tex}
\input{efficient_verification.tex}

\bibliographystyle{alpha}
\bibliography{abbrev3,crypto,reference}

\appendix
\input{appendix.tex}
\end{document}

### 2020-01-21 parallel/parallel_3.tex

\section{Parallel Repetition of Mahadev's Protocol}

\subsection{Overview of Mahadev's Protocol}\label{sec:mahadev_overview}
Here, we recall the Mahadev's protocol \cite{FOCS:Mahadev18a}. We only give a high-level description of the protocol and properties of it and omit the details since they are not needed to show our result.

The protocol is run between a quantum prover $\pro$ and a classical verifier $\ver$ on a common input $x$. The aim of the protocol is to enable a verifier to classically verify $x\in \lang$ for a BQP language $\lang$ with the help of interactions with a quantum prover.
The protocol is a 4-round protocol where the first message is sent from $\ver$ to $\pro$. 
We denote the $i$-th message generation algorithm by $\ver_i$ for $i\in\{1,3\}$ or $\pro_i$ for $i\in \{2,4\}$ and denote the verifier's final decision algorithm by $\ver_\out$.
Then a high-level description of the protocol is given below.
\begin{description}
\item[$\ver_1$:] On input the security parameter $1^\secpar$ and $x$, it generates a pair $(\key,\td)$ of a``key" and ``trapdoor", sends $\key$ to $\pro$, and keeps $\td$ as its internal state.
\item[$\pro_2$:] On input $x$ and $\key$, it generates a classical ``commitment" $\comy$ along with a quantum state $\ket{\st_\pro}$, sends $\comy$ to $\pro$, and keeps $\ket{\st_\pro}$ as its internal state.
\item[$\ver_3$:] It randomly picks $c\sample \bit$ and sends $c$ to $\pro$.\footnote{The third message is just a public-coin, and does not depend on the transcript so far or $x$.}
Following the terminology in \cite{FOCS:Mahadev18a}, we call the case of $c=0$ the ``test round" and the case of $c=1$ the ``Hadamard round".
\item[$\pro_4$:] On input $\ket{\st_\pro}$ and $c$, it generates a classical string $\ans$ and sends $\ans$ to $\pro$.
\item[$\ver_\out$:] On input $\key$, $\td$, $y$, $c$, and $\ans$, it returns $\top$ indicating acceptance or $\bot$ indicating rejection.
In case $c=0$, the verification can be done publicly, that is, $\ver_\out$ need not take $\td$ as input.
\end{description}

For the protocol, we have the following properties:\\
\noindent\textbf{Completeness:}
For all $x\in \lang$, we have $\Pr[\langle \pro,\ver \rangle(x)]=\bot]= \negl(\secpar)$.\\
\noindent\textbf{Soundness:}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$, we have  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot]\leq 3/4$.

We need a slightly different form of soundness implicitly shown in \cite{FOCS:Mahadev18a}, which roughly says that if a cheating prover can pass the ``test round" (i.e., the case of $c=0$) with overwhelming probability, then it can pass the ``Hadamard round" (i.e., the case of $c=1$) only with a negligible probability. 
\begin{lemma}[implicit in \cite{FOCS:Mahadev18a}]\label{lem:Mah_soundness}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$ such that  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot\mid c=0]=\negl(\secpar)$, we have $\Pr[\langle \pro^*,\ver \rangle(x)]=\top\mid c=1]=\negl(\secpar)$.
\end{lemma}

We will also use the following simple fact:
\begin{fact}\label{fact:perfectly_pass_test}
There exists an efficient prover that passes the test round with probability $1$ (but passes the Hadamard round with probability $0$) even if $x\notin \lang$. 
\end{fact}

\subsection{Parallel Repetition}
Here, we prove that the parallel repetition of the Mahadev's protocol decrease the soundness bound to be negligible.
Let $\pro^m$ and $\ver^m$ be $m$-parallel repetitions of the honest prover $\pro$ and verifier $\ver$ in the Mahadev's protocol. Then we have the following:
\begin{theorem}[Completeness]\label{thm:rep_completeness}
For all $m= \Omega(\log^2(\secpar))$, for all $x\in \lang$, we have $\Pr[\langle \pro^m,\ver^m \rangle(x)]=\bot]= \negl(\secpar)$.\\
\end{theorem}
\begin{theorem}[Soundness]\label{thm:rep_soundness}
For all $m= \Omega(\log^2(\secpar))$, if the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$, we have  $\Pr[\langle \pro^*,\ver^m \rangle(x)]=\top]\leq \negl(\secpar)$.
\end{theorem}
The completeness (Theorem~\ref{thm:rep_completeness}) easily follows from the completeness of the Mahadev's protocol.
In the next subsection, we prove the soundness (Theorem~\ref{thm:rep_soundness}).

\subsection{Proof of Soundness}\label{sec:proof_of_soundness}
First, we remark that it suffices to show that for any $\mu=1/\poly(n)$, there exists $m=O(\log(n))$ such that the success probability of the cheating prover is at most $\mu$.
This is because we are considering $\omega(\log(n))$-parallel repetition, in which case the number of repetitions is larger than   any $m=O(\log(n))$ for sufficiently large $n$, and thus we can just focus on  the first $m$ coordinates ignoring the rest of the coordinates.  
Thus, we prove the above claim in this section.
%We prove the soundness by showing that for any noticeable $\mu=1/\poly(\secpar)$, there exists a number $m=O(\log \secpar)$ such that by parallelly repeating the protocol $m$ times, the soundness error can be reduced to less than $\mu$.

\noindent\textbf{Characterization of cheating prover.}
Any cheating prover can be characterized by a tuple $(U_0,U)$ of unitaries over Hilbert space $\hil_{\regC}\otimes \hil_{\regX}\otimes \hil_{\regZ} \otimes \hil_{\regY}  \otimes \hil_{\regK}$. 
A prover characterized by $(U_0,U)$ works as follows.\footnote{Here, we hardwire into the cheating prover the instance $x\notin \lang$ on which it will cheat instead of giving it as an input.}
\begin{description}
\item[Second Message:] Upon receiving $k=(\key_1,...,\key_m)$, it applies $U_0$ to the state $\ket{0}_{\regX}\otimes\ket{0}_{\regZ}\otimes\ket{0}_{\regY}\otimes  \ket{k}_{\regK}$, and then measures the $Y$ register to obtain $y=(\comy_1,...,\comy_m)$. Then it sends $\bfy$ to $\ver$ and keeps the resulting state $\ket{\psi(k,y)}_{\regX,\regZ}$ over  $\hil_{\regX,\regZ}$.
\item [Forth Message:] Upon receiving $c\in \bit^{m}$, it applies $U$ to $\ket{c}_{\regC}\ket{\psi(k,y)}_{\regX,\regZ}$ and then measures the $\regX$ register in computational basis to obtain $a=(a_1,...,a_m)$. We denote the designated register for $a_i$ by $\regX_i$. %Then, we can view the verifier's verification procedure on $i$th coordinate as a unitary $V_i$. 
\end{description}

Here, we first introduce a general lemma about two projectors that was shown by Nagaj, Wocjan, and Zhang \cite{NWZ09} by using the Jordan's lemma.
\begin{lemma}[{\cite[Appendix A]{NWZ09}}]\label{lem:decomposition}
Let $\Pi_0$ and $\Pi_1$ be projectors on an $N$-dimensional Hilbert space $\hil$ and let $R_0:= 2\Pi_0-I$, $R_1:= 2\Pi_1-I$, and $Q:=R_1R_0$. $\hil$ can be decomposed into two-dimensional subspaces $S_j$ for $j\in[\ell]$ and $N-2\ell$ one-dimensional subspaces $T_j^{(bc)}$ for $b,c\in \bit$ that satisfies the following properties:
\begin{enumerate}
\item For each two-dimensional subspace $S_j$, there exist two orthonormal bases $(\ket{\alpha_j},\ket{\alpha_j^{\bot}})$ and $(\ket{\beta_j},\ket{\beta_j^{\bot}})$ of $S_j$ such that $\ipro{\alpha_j}{\beta_j}$ is a positive real and for all $ \ket{s}\in S_j$,  $\Pi_0 \ket{s} = \ipro{\alpha_j}{s}\ket{\alpha_j}$ and $\Pi_1 |s\rangle =\ipro{\beta_j}{s}\ket{\beta_j}$.  Moreover, $Q$ is a rotation with eigenvalues $e^{\pm i\theta_j}$ in $S_j$ corresponding to eigenvectors $\ket{\phi_j^+}=\frac{1}{\sqrt{2}}(\ket{\alpha_j}+i\ket{\alpha_j^\bot})$ and $\ket{\phi_j^-}=\frac{1}{\sqrt{2}}(\ket{\alpha_j}-i\ket{\alpha_j^\bot})$
where $\theta_j=2\arccos \ipro{\alpha_j}{\beta_j}=2\arccos\sqrt{\bra{\alpha_j}\Pi_1\ket{\alpha_j}}$.
\item  Each one-dimensional subspace $T_j^{(bc)}$ is spanned by a vector $\ket{\alpha_j^{(bc)}}$ such that $\Pi_0 \ket{\alpha_j^{(bc)}}=b \ket{\alpha_j^{(bc)}}$ and $\Pi_1 \ket{\alpha_j^{(bc)}}=c \ket{\alpha_j^{(bc)}}$.
\end{enumerate}
\end{lemma}

Fix $k$ and $y$ for now (until we finish the proof of Lemma~\ref{lem:partition_further}). For $i\in [m]$, we consider two projectors 
\begin{align*}
    &\Pi_{in}:= \opro{0^m}{0^m}_{\regC}\otimes I_{\regX,\regZ}\\
    %&\Pi_{i,out} := (UH_{\regC_{-i}})^{\dag}(\sum_{b,x: f_{k}(b,x)=y}\opro{b,x}{b,x}_{\regX_i})\otimes I_{\regC,\regX_{-i},\regZ} (UH_{\regC_{-i}}),
   & \Pi_{i,out} := (UH_{\regC_{-i}})^{\dag}(\sum_{a_i\in \Acc_{k_i,y_i}}\opro{a_i}{a_i}_{\regX_i}\otimes I_{\regC,\regX_{-i},\regZ}) (UH_{\regC_{-i}}),
\end{align*}
where 
$\regX_{-i}:= \regX_1,\dots,\regX_{i-1}, \regX_{i+1},\dots, \regX_{m}$,  $H_{\regC_{-i}}$ means applying Hadamard operators to registers $\regC_1,\dots,\regC_{i-1}, \regC_{i+1},\dots, \regC_{m}$, and $\Acc_{k_i,y_i}$ denotes the set of $a_i$ such that the verifier accepts $a_i$ in the test round on the $i$-th coordinate when the first and second messages are $k_i$ and $y_i$, respectively.
Note that one can efficiently check if $a_i\in \Acc_{k_i,y_i}$ without knowing the trapdoor behind $k_i$ since verification in the test round can be done publicly as explained in Sec. \ref{sec:mahadev_overview}. 
We apply Lemma~\ref{lem:decomposition} for $\Pi_0= \Pi_{in}$ and $\Pi_1=\Pi_{i,out}$ to decompose the space  $\hil_{\regC,\regX,\regZ}$ into the two-dimensional subspaces $\{S_j\}_{j}$ and one-dimensional subspaces $\{T_{j}^{bc}\}_{j,b,c}$.
In the following, we use notations defined in Lemma~\ref{lem:decomposition} for this particular application.
We can write $\ket{\alpha_j}_{\regC,\regX,\regZ}=\ket{0}\ot \ket{\hat{\alpha}_j}_{\regX,\regZ}$  since $\Pi_{in}\ket{\alpha_j}=\ipro{\alpha_j}{\alpha_j}\ket{\alpha_j}=\ket{\alpha_j}$.
Similarly, we can write  $\ket{\alpha_j^{(10)}}_{\regC,\regX,\regZ}=\ket{0}\ot \ket{\hat{\alpha}_j^{(10)}}_{\regX,\regZ}$ 
and  $\ket{\alpha_j^{(11)}}_{\regC,\regX,\regZ}=\ket{0}\ot \ket{\hat{\alpha}_j^{(11)}}_{\regX,\regZ}$. 
Then  $\{\ket{\hat{\alpha}_j}\}_{j}$ and $\{\ket{\hat{\alpha}_{j}^{(1c)}}\}_{j,c}$ span $\hil_{\regX,\regZ}$.

First, we prove a lemma which gives a decomposition of a cheating prover's state.

\begin{lemma}\label{lem:partition}
Let $(U_0,U)$ be any prover's strategy. Let $m=O(\log \secpar)$, $i\in[m]$, 
$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\frac{\gamma_0}{T}=1/\poly(\secpar)$. Let $\gamma$ be sampled uniformly randomly from $[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}]$. Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{\regX,\regZ}$,  
\begin{align*}
    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+ z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
\end{align*}
where $t$ is the number of qubits in the register $ph$, $z_0,z_1\in \mathbb{C}$ such that $|z_0|=|z_1|=1$, and 
$z_0$, $z_1$, $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ may depend on $\gamma$.

Furthermore, the following properties are satisfied.
%
\begin{enumerate}
%\item There exist (sub-normalized) states $\ket{\psi_0}_{\regX,\regZ}$ and $\ket{\psi_1}_{\regX,\regZ}$ such that when $G_{i,\gamma}$ runs on input $\ket{\psi}_{\regX,\regZ}$, the output is  $(0,\ket{\psi_0}_{\regX,\regZ}/\|\ket{\psi_0}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_0}_{\regX,\regZ}\|^2$, $(1,\ket{\psi_1}_{\regX,\regZ}/\|\ket{\psi_1}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_1}_{\regX,\regZ}\|^2$, and $\bot$ with probability  $1-\|\ket{\psi_0}_{\regX,\regZ}\|^2- \|\ket{\psi_1}_{\regX,\regZ}\|^2$,
    \item If we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$, then we have  $E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$.
\item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$. %where $M_{ph,th,in}$ is the computational-basis measurement in the register $(ph,th,in)$. %and $t$ is the number of qubits in $ph$.   
This implies that if we apply the measurement $M_{ph,th,in}$ on $\frac{G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in}}{\|\ket{\psi}_{\regX,\regZ}\|}$, then the outcome is $0^tb1$ with probability $\|\ket{\psi_b}_{\regX,\regZ}\|^2$ and the resulting state in the register $(\regX,\regZ)$  is $\frac{\ket{\psi_b}_{\regX,\regZ}}{\|\ket{\psi_b}_{\regX,\regZ}\|}$ ignoring a global phase factor.
    \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. 
        \item 
For any fixed $\gamma$ and $c\in \bit^m$ such that $c_i=0$, we have 
\begin{align*}
\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq 2^{m-1}\gamma+\negl(\secpar).
\end{align*}
    \item 
For any fixed $\gamma$, there exists an efficient quantum algorithm $\ext_i$ such that 
\begin{align*}  
  \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
  \end{align*}   
\end{enumerate}
\end{lemma}

%\begin{remark}
%To prove Theorem~\ref{thm:rep_soundness}, we only need $m$ to be at most $\log(n)$. Hence, $\gamma_0$ and $T$ can be $1/\poly(n)$. 
%\end{remark}

\begin{proof}[Proof of Lemma~\ref{lem:partition}]
Procedure~\ref{fig:process_G} defines an efficient process $G_{i,\gamma}$, which decomposes $\ket{\psi}_{\regX,\regZ}$ into $\ket{\psi_0}_{\regX,\regZ}$ , $\ket{\psi_1}_{\regX,\regZ}$ , and $\ket{\psi_{err}}_{\regX,\regZ}$  described in Lemma~\ref{lem:partition}.    
Here, $G_{i,\gamma} := U_{in}U^{\dag}_{est}U_{th}U_{est}$ operates on register $\regC$, $\regX$, $\regZ$, and additional registers $ph$, $th$, and $in$, and we let $\delta:=\frac{\gamma_0}{3T}$.

\floatname{algorithm}{Procedure}
\begin{algorithm}[h]
    \begin{mdframed}[style=figstyle,innerleftmargin=10pt,innerrightmargin=10pt]
    \begin{enumerate}
   % \item Uniformly choose $\gamma$ from $[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}]$ 
    \item Do quantum phase estimation $U_{est}$ on $Q=(2\Pi_{in}-I)(2\Pi_{i,out}-I)$ with input state $\ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}$ and $\tau$-bit precision and failure probability $2^{-n}$ where the parameter $\tau$ will be specified later, i.e.,  
    \begin{align*}
        U_{est}\ket{u}_{\regC,\regX,\regZ}\ket{0^t}_{ph} \rightarrow \sum_{\theta\in(-\pi,\pi]} \alpha_{\theta} \ket{u}_{\regC,\regX,\regZ}\ket{\theta}_{ph}.
    \end{align*}
 such that $\sum_{\theta\notin \bar{\theta}\pm 2^{-\tau}}|\alpha_{\theta}|^2\leq 2^{-\secpar}$ for any eigenvector $\ket{u}_{\regC,\regX,\regZ}$ of $Q$ with eigenvalue $e^{i\bar{\theta}}$.
 %\item Apply $U_{cos}:\ket{u}_{\regC,\regX,\regZ}\ket{\theta'}_{ph}\ket{0}_{pr} \xrightarrow{U_{cos}} \ket{u}_{\regC,\regX,\regZ}\ket{\theta'}_{ph}\ket{\cos^2(\theta'/2)}_{pr}$. 
    \item Apply $U_{th}:\ket{u}_{\regC,\regX,\regZ}\ket{\theta}_{ph}\ket{0}_{th} \xrightarrow{U_{th}} \ket{u}_{\regC,\regX,\regZ}\ket{\theta}_{ph}\ket{b}_{th} $, 
    where $b=1$ if $\cos^2 (\theta/2)\geq \gamma-\delta$.
    %$\cos^2 \theta\in [\gamma-\delta/2, \gamma + \delta/2]$. 
    \item Apply $U_{est}^\dag$. 
   % \item Measure $ph$ and $th$ registers and let $m$ be the measurement outcome. If $m=0^{\tau}b$ for $b\in \bit$, then it returns $b$ and the quantum state in the registers $(\regX,\regZ)$, and $\bot$ otherwise where $\tau$ is the number of qubits in the $ph$ register.
   \item Apply $U_{in}: \ket{c}_{\regC}\ket{0}_{in} \xrightarrow{U_{in}}  \ket{c}_{\regC}\ket{b'}_{in}$,
    where $b'=1$ if $c= 0^m$. 
    %\item Measure the single-qubit registers $th$ and $err$. 
\end{enumerate}
    \caption{$G_{i,\gamma}$}
    \label{fig:process_G}
    \end{mdframed}
\end{algorithm}

%We can consider $U_c$ as a unitary $U$ operating on registers $\regC$, $\regX$, and $\regZ$.

%First, we remark that $\ket{\alpha_1},...,\ket{\alpha_\ell}$ and $\{\ket{\alpha_{j}^{(1c)}}\}$ spans $\ket{0^m}_{\regC}\ot \hil_{\regX,\regZ}$.

In the procedure, we choose $\tau$ so that for any $\theta$ and $\theta'$ such that $|\theta'-\theta|\leq 2^{-\tau}$, we have $|\cos^2(\theta'/2)-\cos^2(\theta/2)|\leq \delta/2$.
Since we can upper and lower bound $\cos^2(\theta'/2)-\cos^2(\theta/2)$ by polynomials in $\theta'-\theta$ by considering the Taylor series, we can set $\tau=O(-\log(\delta))$ for satisfying this property.\takashi{More explanation may be needed?}
Since phase estimation with $\tau$-bit precision and failure probability $2^{-\secpar}$ can be done in time $\poly(\secpar,2^{\tau})$ \cite{NWZ09} and $\delta=\frac{\gamma_0}{3T}=1/\poly(\secpar)$ by the assumption, the procedure runs in time $\poly(\secpar)$.

For each $j\in [\ell]$, we define $p_j:= \cos^2(\theta_j/2)=\bra{\alpha_j} \Pi_{i,out} \ket{\alpha_j}$.
We define the following projections on $\hil_{\regX,\regZ}$:
\begin{align*}
    &\Pi_{in, \leq \gamma-2\delta} := \sum_{j: p_j\leq \gamma-2\delta}\opro{\hat{\alpha}_j}{\hat{\alpha}_j}_{\regX,\regZ}+ \sum_{j} \opro{\hat{\alpha}_j^{10}}{\hat{\alpha}_j^{10}}_{\regX,\regZ},\\
     &\Pi_{in, \geq \gamma} := \sum_{j: p_j\geq  \gamma}\opro{\hat{\alpha}_j}{\hat{\alpha}_j}_{\regX,\regZ}+ \sum_{j} \opro{\hat{\alpha}_j^{11}}{\hat{\alpha}_j^{11}}_{\regX,\regZ},\\
    &\Pi_{in, mid} := \sum_{j: p_j \in (\gamma-2\delta,\gamma)}\opro{\hat{\alpha}_j}{\hat{\alpha}_j}_{\regX,\regZ}.
\end{align*}

We let $\ket{\psi_{\leq \gamma-2\delta}}_{\regX,\regZ}:=\Pi_{in, \leq \gamma-2\delta}\ket{\psi}_{\regX,\regZ}$,  $\ket{\psi_{\geq \gamma}}_{\regX,\regZ}:=\Pi_{in, \geq \gamma}\ket{\psi}_{\regX,\regZ}$, and $\ket{\psi_{mid}}_{\regX,\regZ}:=\Pi_{in, mid}\ket{\psi}_{\regX,\regZ}$.
Then we have 
\begin{align}
\ket{\psi}_{\regX,\regZ}=\ket{\psi_{\leq \gamma-2\delta}}_{\regX,\regZ}+\ket{\psi_{\geq\gamma}}_{\regX,\regZ}+\ket{\psi_{mid}}_{\regX,\regZ}. \label{eq:psi}
\end{align}
Roughly speaking, $\ket{\psi_{\leq \gamma-2\delta}}_{\regX,\regZ}$, $\ket{\psi_{\geq\gamma}}_{\regX,\regZ}$, $\ket{\psi_{mid}}_{\regX,\regZ}$ will correspond to $\ket{\psi_0}$, $\ket{\psi_1}$, and $\ket{\psi_{err}}$ with some error terms as explained in the following.

It is easy to see that $E_{\gamma}[\|\ket{\psi_{mid}}\|^2]\leq \frac{1}{T}$ since $\Pi_{in, mid}$ with different choice of $\gamma$ are disjoint. \takashi{Explanation may be needed.}
In the following, we analyze how the first two terms of Eq. \ref{eq:psi} develops by $G_{i,\gamma}$.

$\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}$ is a superposition of states $\{\ket{\hat{\alpha}_j}_{\regX,\regZ}\}_{j:p_j\leq \gamma-2\delta}$ and $\{\ket{\hat{\alpha}_j^{11}}_{\regX,\regZ}\}_{j}$.
By Lemma~\ref{lem:decomposition}, $\ket{\alpha_j}_{\regC,\regX,\regZ}=\ket{0^m}_{\regC}\ot \ket{\hat{\alpha}_j}_{\regX,\regZ}$ can be written as $\ket{\alpha_j}_{\regC,\regX,\regZ}=\frac{1}{\sqrt{2}}(\ket{\phi_j^+}_{\regC,\regX,\regZ}+\ket{\phi_j^-}_{\regC,\regX,\regZ})$ where $\ket{\phi_j^\pm}_{\regC,\regX,\regZ}$ is an eigenvector of $Q$ with eigenvalue $e^{\pm i\theta_j}$ where $\theta_j=2\arccos(\sqrt{p_j})\geq 2\arccos (\sqrt{\gamma-2\delta})$. 
Moreover,  $\ket{\alpha_j^{(10)}}_{\regC,\regX,\regZ}=\ket{0^m}_{\regC}\ot \ket{\hat{\alpha}_j^{(10)}}_{\regX,\regZ}$ is an eigenvector of $Q$ with eigenvalue $-1=e^{i\pi}$. 
Here, we remark that $\pi\geq 2\arccos x$ for any $0\leq x \leq 1$.
Thus, after applying $U_{est}$ to  $\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}$, $(1-2^{-\secpar})$-fraction of the state contains $\theta$ in the register $ph$ such that $|\theta|\geq 2\arccos(\sqrt{\gamma-2\delta}) -2^{-\tau}$. which implies $\cos^2(\theta/2)\leq \gamma-\frac{3}{2}\delta<\gamma-\delta$ by our choice of $\tau$.
For this fraction of the state, $U_{th}$ does nothing.
 Thus, we have 
 \begin{align*}
 \TD(U_{est}\ket{0^m}_{\regC}\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in},U_{th}U_{est}\ket{0^m}_{\regC}\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in})\leq 2^{-n}
 \end{align*}
  and thus
  \begin{align*}
  \TD(\ket{0^m}_{\regC}\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in},U_{est}^\dag U_{th}U_{est}\ket{0^m}_{\regC}\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in})\leq 2^{-n}
  \end{align*}
   where $\TD$ denotes the trace distance. 
 \takashi{The explanation here makes sense? If not, we may need to write some expressions as in the previous manuscript.}

Therefore we can write
\begin{align}
 G_{i,\gamma}\ket{0^m}_{\regC}\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in}=z_{\leq \gamma-2\delta}\ket{0^m}_{\regC}\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+\ket{\psi'_{err,\leq \gamma-2\delta}} \label{eq:leq}
\end{align}

by using $z_{\leq \gamma-2\delta}$ such that $|z_{\leq \gamma-2\delta}|^2\geq 1-2^{-\secpar}$ and a state  $\ket{\psi'_{err,\leq \gamma-2\delta}}$ that is orthogonal to $\ket{0^m}_{\regC}\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}$ such that $\|\ket{\psi'_{err,\leq \gamma-2\delta}}\|^2 \leq 2^{-n}$.

\begin{comment}
$\ket{\psi_{\geq\gamma}}_{\regX,\regZ}$ is a superposition of $\ket{\hat{\alpha}_j}_{\regX,\regZ}$ such that $p_j\geq \gamma$ and $\ket{\hat{\alpha}_j^{11}}_{\regX,\regZ}$.
By Lemma~??? $\ket{\alpha_j}_{\regC,\regX,\regZ}=\ket{0^m}_{\regC}\ot \ket{\hat{\alpha}_j}_{\regX,\regZ}$ can be written as $\ket{\alpha_j}_{\regC,\regX,\regZ}=\frac{1}{\sqrt{2}}(\ket{\phi_j^+}_{\regC,\regX,\regZ}+\ket{\phi_j^-}_{\regC,\regX,\regZ})$ where $\ket{\phi_j^\pm}_{\regC,\regX,\regZ}$ is an eigenvector of $Q$ with eigenvalue $e^{-i\theta_j}$. 
Moreover,  $\ket{\alpha_j^{(11)}}_{\regC,\regX,\regZ}=\ket{0^m}_{\regC}\ot \ket{\hat{\alpha}_j^{(11)}}_{\regX,\regZ}$ is an eigenvector of $Q$ with eigenvalue $1=e^{0}$. 
Thus, after applying $U_{est}$ to  $\ket{\psi_{\geq\gamma}}_{\regX,\regZ}$, $(1-2^{-\secpar})$-fraction of the state contains $\theta$ in the register $ph$ such that $\theta\leq 2\arccos(\sqrt{\gamma}) +2^{-t}$. which implies $\cos^2(\theta/2)\geq \gamma-\delta$ by our choice of $t$.
%For this fraction of the state, $U_{th}$ does nothing, and then $U_{\est}^\dag$ returns the state to the original state.  
 Thus, we have $\TD(U_{est}\ket{0^m}_{\regC}\ket{\psi_{\geq\gamma}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in},U_{th}U_{est}\ket{0^m}_{\regC}\ket{\psi_{\geq\gamma}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in})\leq 2^{-n}$ and thus$\TD(\ket{0^m}_{\regC}\ket{\psi_{\geq\gamma}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in},U_{est}^\dag U_{th}U_{est}\ket{0^m}_{\regC}\ket{\psi_{\geq\gamma}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in})\leq 2^{-n}$ where $\TD$ denotes the trace distance. 
 \takashi{The explanation here makes sense? If not, we may need to write some expressions as in the previous manuscript.}

Therefore we can write
\end{comment}

By a similar analysis, we can write 
\begin{align}
 G_{i,\gamma}\ket{0^m}_{\regC}\ket{\psi_{\geq\gamma}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in}=z_{\geq \gamma}\ket{0^m}_{\regC}\ket{\psi_{\geq\gamma}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in}+\ket{\psi'_{err,\geq \gamma}} \label{eq:geq}
\end{align}

by using $z_{\geq \gamma}$ such that $|z_{\geq \gamma}|^2\geq 1-2^{-\secpar}$ and a state  $\ket{\psi'_{err,\geq \gamma}}$ that is orthogonal to $\ket{0^m}_{\regC}\ket{\psi_{\geq\gamma}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}$ such that $\|\ket{\psi'_{err,\geq \gamma}}\|^2 \leq 2^{-n}$.

Combining Eq. \ref{eq:psi}, \ref{eq:leq}, and \ref{eq:geq}, we have
%we have 
%\begin{align*}
 %   G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = \ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+ \ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}.
%\end{align*}
%where 
%\begin{align*}
%\ket{\psi_{0}}_{\regX,\regZ}=z_{\geq \gamma}\ket{\psi_{\geq\gamma}}_{\regX,\regZ}+
%\end{align*}
\begin{align}
\begin{split}
& G_{i,\gamma}\ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t00}_{ph,th,in} \\
&=\ket{0^m}_{\regC}(z_{\geq \gamma}\ket{\psi_{\geq\gamma}}_{\regX,\regZ}+\ket{\eta_{mid,0}}_{\regX,\regZ}+\ket{\eta_{other,0}}_{\regX,\regZ})\ket{0^t01}_{ph,th,in} \\
&+\ket{0^m}_{\regC}(z_{\leq \gamma-2\delta}\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}+\ket{\eta_{mid,1}}_{\regX,\regZ}+\ket{\eta_{other,1}}_{\regX,\regZ})\ket{0^t11}_{ph,th,in} \\
&+ \ket{\psi'_{err}}. 
\end{split} \label{eq:resulting_state}
\end{align}

where $\ket{\eta_{mid,0}}_{\regX,\regZ}$, $\ket{\eta_{other,0}}_{\regX,\regZ}$, $\ket{\eta_{mid,1}}_{\regX,\regZ}$, and $\ket{\eta_{other,1}}_{\regX,\regZ}$ are defined so that
\begin{align}
& I_{\regC,\regX,\regZ} \ot \opro{0^t01}{0^t01}_{ph,th,in}G_{i,\gamma}\ket{0^m}_{\regC}\ket{\psi_{mid}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in}=\ket{0^m}_{\regC}{\ket{\eta_{mid,0}}_{\regX,\regZ}}\ket{0^t01}_{ph,th,in}, \label{eq:etamid} \\
&I_{\regC,\regX,\regZ} \ot \opro{0^t11}{0^t11}_{ph,th,in}G_{i,\gamma}\ket{0^m}_{\regC}\ket{\psi_{mid}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in}=\ket{0^m}_{\regC}{\ket{\eta_{mid,1}}_{\regX,\regZ}}\ket{0^t11}_{ph,th,in}, \label{eq:etamidprime} \\
&I_{\regC,\regX,\regZ} \ot \opro{0^t01}{0^t01}_{ph,th,in}(\ket{\psi'_{err,\leq \gamma-2\delta}}+\ket{\psi'_{err,\geq \gamma}})=\ket{0^m}_{\regC}{\ket{\eta_{other,0}}_{\regX,\regZ}}\ket{0^t01}_{ph,th,in}, \label{eq:etaother} \\
&I_{\regC,\regX,\regZ} \ot \opro{0^t11}{0^t11}_{ph,th,in}(\ket{\psi'_{err,\leq \gamma-2\delta}}+\ket{\psi'_{err,\geq \gamma}})=\ket{0^m}_{\regC}{\ket{\eta_{other,1}}_{\regX,\regZ}}\ket{0^t11}_{ph,th,in}. \label{eq:etaotherprime} 
\end{align}
and $\ket{\psi'_{err}}$  is defined by 
\begin{align}
%\begin{split}
\ket{\psi'_{err}}&:=
\sum_{s\notin \{0^t01,0^t11\}} I_{\regC,\regX,\regZ} \ot \opro{s}{s}_{ph,th,in}(G_{i,\gamma}\ket{0^m}_{\regC}\ket{\psi_{mid}}_{\regX,\regZ}\ket{0^t00}_{ph,th,in}+\ket{\psi'_{err,\leq \gamma-2\delta}}+\ket{\psi'_{err,\geq \gamma}}) \label{eq:psierrprime}
%&-\ket{0^m}_{\regC}(\ket{\eta_{mid,0}}_{\regX,\regZ}+\ket{\eta_{other,0}}_{\regX,\regZ})\ket{0^t01}_{ph,th,in} \\
%&-\ket{0^m}_{\regC}(\ket{\eta_{mid,1}}_{\regX,\regZ}+\ket{\eta_{other,1}}_{\regX,\regZ})\ket{0^t11}_{ph,th,in}. 
%\end{split} 
\end{align}

We remark that $\ket{\eta_{mid,0}}_{\regX,\regZ}$, $\ket{\eta_{other,0}}_{\regX,\regZ}$, $\ket{\eta_{mid,1}}_{\regX,\regZ}$, and $\ket{\eta_{other,1}}_{\regX,\regZ}$ are well-defined since after applying $G_{i,\gamma}$, the value in the register $in$ is $1$ if and only if the value in the register $\regC$ is $0^m$.

We let $z_0:=\frac{z_{\leq \gamma-2\delta}}{|z_{\leq \gamma-2\delta}|}$, $z_1:=\frac{z_{\geq \gamma}}{|z_{\geq \gamma}|}$, and 
\begin{align}
&\ket{\psi_0}_{\regX,\regZ}:=|z_{\leq \gamma-2\delta}|\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}+ \overline{z}_0(\ket{\eta_{mid,0}}_{\regX,\regZ}+\ket{\eta_{other,0}}_{\regX,\regZ}), \label{eq:psizero} \\
&\ket{\psi_1}_{\regX,\regZ}:=|z_{\geq \gamma}|\ket{\psi_{\geq\gamma}}_{\regX,\regZ}+ \overline{z}_1(\ket{\eta_{mid,1}}_{\regX,\regZ}+\ket{\eta_{other,1}}_{\regX,\regZ}), \label{eq:psione}
\end{align}
where $\overline{z}_0$ and $\overline{z}_1$ denotes complex conjugates of $z_0$ and $z_1$. By Eq~\ref{eq:resulting_state}, \ref{eq:psizero}, and \ref{eq:psione}, we have
\begin{align*}
    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+ z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}.
\end{align*}

Now, we are ready to prove the five claims in Lemma~\ref{lem:partition}.

\paragraph{Proof of the first claim.}
By Eq.~\ref{eq:psi}, \ref{eq:psizero}, and \ref{eq:psione}, we have
\begin{align*}
\ket{\psi_{err}}_{\regX,\regZ}&=\ket{\psi}_{\regX,\regZ}-\ket{\psi_0}_{\regX,\regZ}-\ket{\psi_1}_{\regX,\regZ}\\
&=(1-|z_{\leq \gamma-2\delta}|)\ket{\psi_{\leq\gamma-2\delta}}_{\regX,\regZ}+(1-|z_{\geq \gamma}|)\ket{\psi_{\geq\gamma}}_{\regX,\regZ}+\ket{\psi_{mid}}_{\regX,\regZ}\\
&-\overline{z}_0(\ket{\eta_{mid,0}}_{\regX,\regZ}+\ket{\eta_{other,0}}_{\regX,\regZ})
-\overline{z}_1(\ket{\eta_{mid,1}}_{\regX,\regZ}+\ket{\eta_{other,1}}_{\regX,\regZ}),
\end{align*}

Since $|z_{\leq \gamma-2\delta}|$ and $|z_{\geq \gamma}|$ are $1-\negl(\secpar)$, the norms of the first two terms are negligible.
By Eq.~\ref{eq:etaother} and \ref{eq:etaotherprime}, we have $\|\ket{\eta_{other,0}}_{\regX,\regZ}\|^2 + \|\ket{\eta_{other,1}}_{\regX,\regZ}\|^2\leq \|\ket{\psi'_{err,\leq \gamma-2\delta}}+\ket{\psi'_{err,\geq \gamma}}\|^2 \leq \negl(\secpar)$.
Therefore we have
\begin{align*}
\|\ket{\psi_{err}}_{\regX,\regZ}\|^2 &\leq \|\ket{\psi_{mid}}_{\regX,\regZ}-\overline{z}_0\ket{\eta_{mid,0}}_{\regX,\regZ}-\overline{z}_1\ket{\eta_{mid,1}}_{\regX,\regZ}\|^2+\negl(\secpar)\\
&\leq 3(\|\ket{\psi_{mid}}_{\regX,\regZ}\|^2+\|\ket{\eta_{mid,0}}_{\regX,\regZ}\|^2 + \|\ket{\eta_{mid,1}}_{\regX,\regZ}\|^2)+\negl(\secpar)
\end{align*}
where the latter inequality follows from the Cauchy-Schwarz inequality.
As already noted, we have $E_{\gamma}[\|\ket{\psi_{mid}}_{\regX,\regZ}\|^2]\leq \frac{1}{T}$.
By Eq.~\ref{eq:etamid} and \ref{eq:etamidprime}, we have $E_{\gamma}[\|\ket{\eta_{mid,0}}_{\regX,\regZ}\|^2 + \|\ket{\eta_{mid,1}}_{\regX,\regZ}\|^2]\leq E_{\gamma}[\|\ket{\psi_{mid}}_{\regX,\regZ}\|^2]\leq \frac{1}{T}$.
Therefore, we have $E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(\secpar)$ and the first claim is proven.
\takashi{The constant $6$ is somewhat ugly. Is there a better analysis?}

\paragraph{Proof of the second claim.}
By Eq~\ref{eq:psierrprime}, we can see that 
\begin{align*}
I_{\regC,\regX,\regZ} \ot (\opro{001}{001}_{ph,th,in}+ \opro{011}{011}_{ph,th,in})\ket{\psi'_{err}}=0.
\end{align*}
This immediately implies the second claim.
%
\paragraph{Proof of the third claim.}
By the second claim,  $\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}$,  $\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in}$, and $\ket{\psi'_{err}}$ are orthogonal with one another.
Therefore we have 
\begin{align*}
&\|G_{i,\gamma}\ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t00}_{ph,th,in}\|^2\\
=&\|z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}\|^2+\|z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in}\|^2+\|\ket{\psi'_{err}}\|^2.
\end{align*}
Since we have 
$\|G_{i,\gamma}\ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t00}_{ph,th,in}\|^2=\|\ket{\psi}_{\regX,\regZ}\|^2$ and $\|z_b\ket{0^m}_{\regC}\ket{\psi_{b}}_{\regX,\regZ}\ket{0^tb1}_{ph,th,in}\|^2=\|\ket{\psi_{b}}_{\regX,\regZ}\|^2$, the above implies $\|\ket{\psi_{0}}_{\regX,\regZ}\|^2+\|\ket{\psi_{1}}_{\regX,\regZ}\|^2\leq \|\ket{\psi}_{\regX,\regZ}\|^2$, which implies the third claim.
%
\paragraph{Proof of the forth claim.}
By the definition of $\ket{\psi_{mid}}_{\regX,\regZ}$, the state $\ket{0^m}_{\regC}\ket{\psi_{mid}}_{\regX,\regZ}$ is in the subspace $S_{mid}$, which is the subspace spanned by $\{S_j\}_{j:p_j\in (\gamma-2\delta,\gamma)}$.
We define $\ket{\psi''_{mid,s}}_{\regC,\regX,\regZ}$ so that 
\begin{align*}
G_{i,\gamma}\ket{0^m}_{\regC}\ket{\psi_{mid}}\ket{0^t00}_{ph,th,in}=\sum_{s\in \bit^{t+2}} \ket{\psi''_{mid,s}}_{\regC,\regX,\regZ}\ket{s}_{ph,th,in}.
\end{align*}
Since each subspace $S_j$ is invariant under the projections $\Pi_{in}$ and $\Pi_{i,out}$, each $\ket{\psi''_{mid,s}}_{\regC,\regX,\regZ}$ is also in the subspace $S_{mid}$. \takashi{More explanation needed?}
In particular, $\ket{0^m}_{\regC}\ket{\eta_{mid,0}}_{\regX,\regZ}=\ket{\psi''_{mid,0^t01}}_{\regC,\regX,\regZ}$ is in the subspace $S_{mid}$.
%Then by Eq~\ref{eq:etamid} and that $\Pi_{in}S_{mid}$ is spanned by $\{\hat{\alpha}_j\}_{j: p_j\in (\gamma-2\delta,\gamma)}$, we can express $\ket{\eta_{mid,0}}_{\regX,\regZ}$ as a superposition of states $\{\hat{\alpha}_j\}_{j: p_j\in (\gamma-2\delta,\gamma)}$,
%\begin{align*}
%\ket{\eta_{mid,0}}_{\regX,\regZ}=\sum_{j: p_j\in (\gamma-2\delta,\gamma)} d_j \ket{\hat{\alpha}_j}. 
%\end{align*}
Therefore, by Eq. \ref{eq:psizero}, we can write 
\begin{align}
\ket{0^m}_{\regC}\ket{\psi_0}_{\regX,\regZ}=\sum_{j:p_j<\gamma} d_j \ket{\alpha_j}_{\regC,\regX,\regZ}+\sum_{j} d_j^{(10)} \ket{\alpha_j^{(10)}}_{\regC,\regX,\regZ}+\ket{\psi''_{err,0}}_{\regC,\regX,\regZ}  \label{eq:psizero_decompose} 
\end{align}
where $\ket{\psi''_{err,0}}_{\regC,\regX,\regZ}:=\overline{z}_0 \ket{0^m}_{\regC}\ket{\eta_{other,0}}_{\regX,\regZ}$.
We remark that $\|\ket{\psi''_{err,0}}_{\regC,\regX,\regZ}\|=\negl(\secpar)$ since we have $\|\ket{\psi''_{err,0}}_{\regC,\regX,\regZ}\|=\|\ket{\eta_{other,0}}_{\regX,\regZ}\|\leq \|\ket{\psi_{err,\leq \gamma-2\delta}}+\ket{\psi_{err,\geq \gamma}})\|=\negl(\secpar)$ by Eq. \ref{eq:etamid}.

By the definition of $\Pi_{i,out}$, we have 
\begin{align}
 \Pr_{c_{-i}}\left[M_{\regX_i}\circ U\frac{\ket{c_1...c_{i-1}0c_{i+1}...c_m}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]=\frac{\bra{0^m}_{\regC}\bra{\psi_0}_{\regX,\regZ} \Pi_{i,out} \ket{0^m}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|^2} \label{eq:accept_probability}
\end{align}
where $c_{-i}$ denotes $c_1...c_{i-1}c_{i+1}...c_{m}$.

By Lemma~\ref{lem:decomposition}, we can see that $\bra{\alpha_j}\Pi_{i,out} \ket{\alpha_{j'}}=0$ for all $j\neq j'$ and $\Pi_{i,out} \ket{\alpha_{j}^{(10)}}=0$ for all $j$.
By substituting Eq. \ref{eq:psizero_decompose} for Eq. \ref{eq:accept_probability}, we have
\begin{align*}
&~~~\Pr_{c_{-i}}\left[M_{\regX_i}\circ U\frac{\ket{c_1...c_{i-1}0c_{i+1}...c_m}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\\
%&=(\sum_{j:p_j<\gamma} \overline{a}_j \bra{\alpha_j}_{\regC,\regX,\regZ}+\bra{\psi''_{err,0}}_{\regC,\regX,\regZ}) \Pi_{i,out} (\sum_{j:p_j<\gamma} a_j \ket{\alpha_j}_{\regC,\regX,\regZ}+\ket{\psi''_{err,0}}_{\regC,\regX,\regZ})\\
&=\frac{1}{\|\ket{\psi_0}_{\regX,\regZ}\|^2}\left(\sum_{j:p_j<\gamma} |d_j|^2 \bra{\alpha_j} \Pi_{i,out} \ket{\alpha_j}+ \sum_{j:p_j<\gamma} (\overline{d}_j \bra{\alpha_j}\Pi_{i,out} \ket{\psi''_{err,0}} + d_j \bra{\psi''_{err,0}}\Pi_{i,out} \ket{\alpha_j})\right)\\
%&\leq \sum_{j:p_j<\gamma} |a_j|^2 \gamma + \negl(\secpar)\\
&\leq \gamma+\negl(\secpar)
\end{align*}
where the last inequality follows from $\sum_{j:p_j<\gamma}|d_j|^2\leq \|\ket{\psi_0}_{\regX,\regZ}\|^2$ and $\|\ket{\psi''_{err,0}}_{\regC,\regX,\regZ}\|=\negl(\secpar)$. 
This immediately implies the forth claim considering that the number of possible $c_{-i}$ is $2^{m-1}$ and $m=O(\log \secpar)$.
%
\paragraph{Proof of the fifth claim.}
By a similar argument to the one in the proof of the forth claim, we can write  
\begin{align}
\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}=\sum_{j:p_j>\gamma-2\delta} d_j \ket{\alpha_j}_{\regC,\regX,\regZ}+\sum_{j} `d_j^{(11)} \ket{\alpha_j^{(11)}}_{\regC,\regX,\regZ}+\ket{\psi''_{err,1}}_{\regC,\regX,\regZ}  \label{eq:psione_decompose} 
\end{align}
where $\ket{\psi''_{err,1}}_{\regC,\regX,\regZ}$ is a state such that $\|\ket{\psi''_{err,1}}_{\regC,\regX,\regZ}\|=\negl(\secpar)$.

The algorithm $\ext_{i}$ is described below:

\begin{description}
\item[$\ext_{i}\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$:]
Given $\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}$ as input, $\ext_{i}$ works as follows:
\begin{itemize}
%\item Append $\ket{0^m}_{\regC}$ to prepare $\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}$.
\item Repeat the following procedure $N=\poly(\secpar)$ times where $N$ is specified later:
\begin{enumerate}
\item Perform a measurement $\{\Pi_{i,out},I_{\regC,\regX,\regZ}-\Pi_{i,out}\}$. If the outcome is $0$, i,e, $\Pi_{i,out}$ is applied, then measure the register $\regX_i$ in computational basis to obtain $a_i$, outputs $a_i$, and immediately halts.
\item  Perform a measurement $\{\Pi_{in},I_{\regC,\regX,\regZ}-\Pi_{in}\}$.
\end{enumerate}
\item If it does not halts within $N$ trials in the previous step, output $\bot$.
\end{itemize}
\end{description}

By the definition of $\Pi_{i,out}$, it is clear that $\ext_{i}$ succeeds, (i.e., returns $a_i\in \Acc_{k_i,y_i}$) if it does not output $\bot$.
Since the algorithm $\ext_{i}$ just alternately applies measurements $\{\Pi_{i,out},I_{\regC,\regX,\regZ}-\Pi_{i,out}\}$ and $\{\Pi_{in},I_{\regC,\regX,\regZ}-\Pi_{in}\}$ and each subspaces $S_j$ and $T_j^{(11)}$ are invariant under $\Pi_{in}$ and $\Pi_{i,out}$, we can analyze the success probability of the algorithm separately on each subspace.
Therefore, it suffices to show that $\ext_{i}$ succeeds with probability $1-\negl(\secpar)$ on any input $\ket{\alpha_j}_{\regX,\regZ}$ such that  $p_j> \gamma-2\delta$ or $\ket{\alpha_j^{(11)}}$ for any $j$.
First, it is easy to see that on input $\ket{\alpha_j^{(11)}}$, $\ext_{i}$ returns $a_i\in \Acc_{k_i,y_i}$ at the first trial with probability $1$ since we have $\bra{\alpha_{j}^{(11)}} \Pi_{i,out} \ket{\alpha_{j}^{11}}=1$.
What is left is to prove that $\ext_{i}$ succeeds with probability $1-\negl(\secpar)$ on any input $\ket{\alpha_j}_{\regX,\regZ}$ such that  $p_j> \gamma-2\delta$.

By Lemma~\ref{lem:decomposition}, it is easy to see that we have
\begin{align*}
&\ket{\alpha_j}_{\regX,\regZ}=\sqrt{p_j}\ket{\beta_j}_{\regX,\regZ}+\sqrt{1-p_j}\ket{\beta_j^\bot}_{\regX,\regZ},\\
&\ket{\beta_j}_{\regX,\regZ}=\sqrt{p_j}\ket{\alpha_j}_{\regX,\regZ}+\sqrt{1-p_j}\ket{\alpha_j^\bot}_{\regX,\regZ}.
\end{align*}

Let  $P_k$ and $P_k^\bot$ be the probability that $\ext_i$ succeeds within $k$ trials starting from the initial state $\ket{\alpha_j}_{\regX,\regZ}$   and $\ket{\alpha_j^\bot}_{\regX,\regZ}$, respectively.
Then by the above equations, it is easy to see that we have $P_0=P_0^\bot=0$ and
\begin{align*}
&P_{k+1}=p_j+(1-p_j)^2 P_{k}+ (1-p_j)p_j P_{k}^\bot, \\
&P_{k+1}^\bot=(1-p_j)+ p_j(1-p_j) P_{k}+ p_j^2 P_{k}^\bot.
\end{align*}

Solving this, we have 
\begin{align*}
P_N=1-(1-2p_j+2p_j^2)^{N-1}(1-p_j).
\end{align*}
\takashi{Just a back-of-envelope calculation and not super confident. Should double check. Or is there any better way of analysis?}

Since we assume $p_j> \gamma-2\delta>\frac{\gamma_0}{3T}=1/\poly(\secpar)$, we have $1-2p_j+2p_j^2=1-1/\poly(\secpar)$.
Therefore if we take $N=\poly(\secpar)$ sufficiently large, then $P_N=1-\negl(\secpar)$.
This means that $\ext_i$ succeeds within $N$ steps with probability $1-\negl(\secpar)$ starting from the initial state $\ket{\alpha_j}_{\regX,\regZ}$.
This completes the proof of the fifth claim and the proof of Lemma~\ref{lem:partition}. 
%\end{align*}
\end{proof}

%\begin{remark}\label{remark:one_half}
%Note that $\ket{\psi_0}$ and $\ket{\psi_1}$ may not be orthogonal. However, $\|\ket{\psi_0}\|^2+ \|\ket{\psi_1}\|^2\leq 1$ since $\|\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{001}+ \ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{011} + \ket{\psi_{err}}\|^2 =1$ and  $\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{001}$ and $ \ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{011}$ are orthogonal. This implies that 
%\begin{align*}
%    E_{c_i}[ \|\ket{\psi_{c_i}}\|^2 ] \leq 1/2
%\end{align*}
%\end{remark}

In Lemma~\ref{lem:partition}, we showed that by fixing any $i\in [m]$, we can partition any prover's state $\ket{\psi}_{\regX,\regZ}$ into $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ with certain properties. %such that $\ket{\psi_0}$ and $\ket{\psi_1}$ will be rejected and accepted in the test round with high probability.
%In the following, we show another procedure that further decompose the prover's state according to any given $c\in \{0,1\}^n$. 
In the following, we sequentially apply Lemma~\ref{lem:partition} for each $i\in[m]$ to further decompose the prover's state.

\begin{lemma}\label{lem:partition_further}
%Fix $c\in \{0,1\}^m$. 
Let $m$, $\gamma_0$, $T$ be as in Lemma~\ref{lem:partition}, and let $\gamma_i\sample [\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}]$ for each $i\in [m]$.
For any $c\in \bit^m$, a state $\ket{\psi}_{\regX,\regZ}$ can be partitioned as follows.% by using Procedure~\ref{fig:process_H}. 
\begin{align*}
    & \ket{\psi}_{\regX,\regZ} = \ket{\psi_{c_1}}_{\regX,\regZ} + \ket{\psi_{\bar{c}_1,c_2}}_{\regX,\regZ} + \cdots +\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{m-1},c_m}}_{\regX,\regZ} + \ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}_{\regX,\regZ}+ \ket{\psi_{err}}_{\regX,\regZ}
\end{align*}
where the way of partition may depend on the choice of $\hat{\gamma}=\gamma_1...\gamma_m$.
Further, the following properties are satisfied. 
\begin{enumerate}
    \item For any fixed $\hat{\gamma}$ and any $c$, $i\in [m]$ such that $c_i=0$, we have 
    \begin{align*}
    \Pr\left[M_{\regX_i}\circ U \frac{\ket{0^m}_{\regC}\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},0}}_{\regX,\regZ}}{|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},0}}_{\regX,\regZ}|}\in \Acc_{k_i,y_i}\right]\leq 2^{m-1}\gamma_0+ \negl(\secpar).
    \end{align*}

    \item For any fixed $\hat{\gamma}$ and any $c$, $i\in[m]$ such that $c_i=1$, there exists an efficient algorithm $\ext_i$ such that 
    \begin{align*}  
  \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}}{\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
  \end{align*}   
  \item For any fixed $\hat{\gamma}$, we have $E_c[\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}_{\regX,\regZ}\|^2] \leq 2^{-m}$.
\item For any fixed $c$, we have $E_{\hat{\gamma}}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6m^2}{T}+\negl(\secpar)$.
    \item For any fixed $\hat{\gamma}$ and $c$ there exists an efficient quantum algorithm $H_{\hat{\gamma},c}$ that is given $\ket{\psi}_{\regX,\regZ}$ as input and produces  $\frac{\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}_{\regX,\regZ}}{\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}_{\regX,\regZ}\|}$ with probability $\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}_{\regX,\regZ}\|^2$ ignoring a global phase factor.
%    \item Measuring the register $(ph_1,th_1,in_1),\dots,(ph_i,th_i,in_i)$ gives error (i.e., $\exists i$, such that $(ph_i,th_i,in_i)\neq (0^t,0,1)$ or $(0^t,1,1)$) with probability at most $\frac{m}{T}$. 
 %   \item For any fixed $\gamma$, $E_c[\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}\|^2] \leq 2^{-m}$.
\end{enumerate}
\end{lemma}
\begin{proof}
We inductively define $\ket{\psi_{c_1}}_{\regX,\regZ}$,...,$\ket{\psi_{\bar{c}_1,...,\bar{c}_m}}_{\regX,\regZ}$ as follows.

First, we apply Lemma \ref{lem:partition} for the state $\ket{\psi}_{\regX,\regZ}$ with $\gamma=\gamma_1$ to give a decomposition
\begin{align*}
\ket{\psi}_{\regX,\regZ}=\ket{\psi_0}_{\regX,\regZ}+\ket{\psi_1}_{\regX,\regZ} + \ket{\psi_{err,1}}_{\regX,\regZ} 
\end{align*}
where $\ket{\psi_{err,1}}_{\regX,\regZ}$ corresponds to $\ket{\psi_{err}}_{\regX,\regZ}$ in Lemma \ref{lem:partition}.

For each $i=2,...,m$, we apply  Lemma \ref{lem:partition} for the state $\ket{\psi_{\bar{c}_1,...,\bar{c}_{i-1}}}_{\regX,\regZ}$ with $\gamma=\gamma_i$ to give a decomposition 
\begin{align*}
\ket{\psi_{\bar{c}_1,...,\bar{c}_{i-1}}}_{\regX,\regZ}=\ket{\psi_{\bar{c}_1,...,\bar{c}_{i-1},0}}_{\regX,\regZ}+\ket{\psi_{\bar{c}_1,...,\bar{c}_{i-1},1}}_{\regX,\regZ} + \ket{\psi_{err,i}}_{\regX,\regZ} 
\end{align*}  
where 
$\ket{\psi_{\bar{c}_1,...,\bar{c}_{i-1},0}}_{\regX,\regZ}$, $\ket{\psi_{\bar{c}_1,...,\bar{c}_{i-1},1}}_{\regX,\regZ}$, and $\ket{\psi_{err,i}}_{\regX,\regZ}$ corresponds to $\ket{\psi_{0}}_{\regX,\regZ}$, $\ket{\psi_{1}}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ in Lemma \ref{lem:partition}, respectively.

 Then it is easy to see that we have
 \begin{align*}
    & \ket{\psi}_{\regX,\regZ} = \ket{\psi_{c_1}}_{\regX,\regZ} + \ket{\psi_{\bar{c}_1,c_2}}_{\regX,\regZ} + \cdots +\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{m-1},c_m}}_{\regX,\regZ} + \ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}_{\regX,\regZ}+ \ket{\psi_{err}}_{\regX,\regZ}
\end{align*}
where we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \sum_{i=1}^{m}\ket{\psi_{err,i}}_{\regX,\regZ}$.

The first and second claims immediately follow from the forth and fifth claims of Lemma~\ref{lem:partition} and $\gamma_i\leq \gamma_0$ for each $i\in[m]$.

By the third claim of  Lemma~\ref{lem:partition}, we have $E_{c_1...c_{i}}[\|\ket{\psi_{\bar{c}_1,...,\bar{c}_{i}}}_{\regX,\regZ}\|]\leq \frac{1}{2}E_{c_1...c_{i-1}}[\|\ket{\psi_{\bar{c}_1,...,\bar{c}_{i-1}}}_{\regX,\regZ}\|]$.
Ths implies the third claim.

By the first claim of  Lemma~\ref{lem:partition}, we have $E_{\gamma_i}[\|\ket{\psi_{err,i}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(\secpar)$.
The forth claim follows from this and the Cauchy-Schwarz inequality.

Finally, for proving the fifth claim, we define the procedure $H_{\hat{\gamma},c}$ as described in Procedure~\ref{fig:process_H}
We can easily see that $H_{\hat{\gamma},c}$ satisfies the desired property by the second claim of  Lemma~\ref{lem:partition}.

\floatname{algorithm}{Procedure}
\begin{algorithm}[h]
    \begin{mdframed}[style=figstyle,innerleftmargin=10pt,innerrightmargin=10pt]
   On input $\ket{\psi}_{\regX,\regZ}$, it works as follows:

   For each $i=1,...,m$, it applies 
    \begin{enumerate}
    \item Prepare registers $\regC$, $(ph_1,th_1,in_1)$,..., $(ph_m,th_m,in_m)$ all of which are initialized to be $\ket{0}$.
    \item For each $i=1,...,m$, do the following: 
      \begin{enumerate}
      \item Apply $G_{i,\gamma_i}$ on the quantum state in the registers $(\regC,\regX,\regZ,ph_i,th_i,in_i)$.
      \item Measure the registers $(ph_i,th_i,in_i)$ in the computational basis.
      \item If the outcome is $0^tc_{i}1$, then it halts and returns the state in the register $(\regX,\regZ)$. If the outcome is $0^t\bar{c}_{i}1$, continue to run. Otherwise, immediately halt and abort.
      \end{enumerate}   
    \end{enumerate}

    \caption{$H_{\hat{\gamma},c}$}
    \label{fig:process_H}
    \end{mdframed}
\end{algorithm}
\end{proof}

Given Lemma~\ref{lem:partition_further}, we can start proving Theorem~\ref{thm:rep_soundness}.

\begin{proof}[Proof of Theorem~\ref{thm:rep_soundness}]

%According to Lemma~\ref{lem:Mah_soundness}, we know that
%\begin{align*}
 %   \Pr_{k,y}[U_{0}\ket{\psi(k,y)}\mbox{ wins test round}]\geq 1-\negl(n) \Rightarrow \Pr_{k,y}[U_{0}\ket{\psi(k,y)}\mbox{ wins Hadamard round}]\leq \negl(n),   
%\end{align*}
%Here,  
First, we recall how a cheating prover characterized by $(U_0,U)$ works.
When the first message $k$ is given, it first applies 
\begin{align*}
    &U_0\ket{0}_{\regX,\regZ}\ket{0}_{\regY}\ket{k}_{\regK} \xrightarrow{\mbox{measure }\regY} \ket{\psi(k,y)}_{\regX,\regZ}\ket{k}_{\regK}.
\end{align*}
to generate the second message $y$ and $\ket{\psi(k,y)}_{\regX,\regZ}$.
Then after receiving the third message $c$, it applies $U$ on $\ket{c}_{\regC}\ket{\psi(k,y)}_{\regX,\regZ}$ and measures the register $\regX$ in the computational basis to obtain the forth message $a$.
In the following, we just write $\ket{\psi}_{\regX,\regZ}$ to mean $\ket{\psi(k,y)}_{\regX,\regZ}$ for notational simplicity.
%let $V_{i,b}$ be a unitary over $\hil_{\regC,\regX,\regZ}$ that runs the verification procedure for $c_i=b$ on the $i$-th coordinate and write the verification result in a designated register (say, $i$-th qubit of $\regZ$), and $M_i$ be the measurement on the designated register that contains the verification result on the $i$-th coordinate.
%Note that $V_{i,1}$ cannot be applied publicly without knowing the trapdoor,  but this does not affect our analysis below.
Let $M_{i,k_i,\td_i,y_i,c_i}$ be the measurement that outputs the verification result of the value in the register $\regX_i$ w.r.t.  $k_i,\td_i,y_i,c_i$, and let $M_{k,\td,y,c}$ be the measurement that returns $\top$ if and only if $M_{i,k_i,\td_i,y_i,c_i}$ returns $\top$ for all $i\in[m]$ where $k=(k_1,...,k_m)$, $\td=(\td_1,...,\td_m)$, $y=(y_1,...,y_m)$ and $c=(c_1,...,c_m)$.
%For any state $\ket{\phi}_{\regC,\regX,\regZ}$, we denote $M\circ \ket{\phi}_{\regC,\regX,\regZ}=\top$ to mean $M_i\circ \ket{\phi}_{\regC,\regX,\regZ}=\top$ for all $i\in[m]$ for notational simplicity. 
With this notation, a cheating prover's success probability can be written as 
\begin{align*}
    \Pr_{k,\td,y,c}[M_{k,\td,y,c}U\ket{c}_{\regC}\ket{\psi}_{\regX,\regZ} = \top].
\end{align*}

Let $\gamma_0$, $\hat{\gamma}$, and $T$ be as in Lemma~\ref{lem:partition_further}.
According to Lemma~\ref{lem:partition_further}, for any fixed $\hat{\gamma}$ and $c\in \bit^{m}$, we can decompose $\ket{\psi}_{\regX,\regZ}$ as 
\begin{align*}
    \ket{\psi}_{\regX,\regZ} =  \ket{\psi_{c_1}}_{\regX,\regZ}+ \ket{\psi_{\bar{c}_1,c_2}}_{\regX,\regZ} + \cdots + \ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},c_{m}}}_{\regX,\regZ} + \ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},\bar{c}_{m}}}_{\regX,\regZ}+ \ket{\psi_{err}}_{\regX,\regZ}.
\end{align*}

To prove the theorem, we show the following two inequalities.
First,  for any  fixed $\hat{\gamma}$, $i\in[m]$, $c\in \bit^{m}$ such that $c_i=0$, $k_i$, $\td_i$, and $y_i$, we have
\begin{align}
 \Pr\left[M_{i,k_i,\td_i,y_i,0} \circ \frac{U\ket{c}_{\regC}\ket{\psi_{\bar{c}_1,\ldots,\bar{c}_{i-1},0}}_{\regX,\regZ}}{\|\ket{\psi_{\bar{c}_1,\ldots,\bar{c}_{i-1},0}}_{\regX,\regZ}\|}=\top\right]\leq 2^{m-1}\gamma_0+\negl(\secpar). \label{eq:Test}
\end{align}
This easily follows from the first claim of Lemma~\ref{lem:partition_further}

Second, for any  fixed $\hat{\gamma}$, $i\in[m]$, and $c\in \bit^{m}$ such that $c_i=1$,
\begin{align}
    \underset{k,\td,y}{E}\left[\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}\|^2\Pr\left[M_{i,k_i,\td_i,y_i,1}\circ U\frac{\ket{c}_{\regC}\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}}{\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}\|} = \top\right]\right] = \negl(n) \label{eq:Hada}
\end{align}
assuming the quantum hardness of LWE problem.

For proving Eq.~\ref{eq:Hada}, we consider a cheating prover against the original Mahadev's protocol on the $i$-th corrdinate described below:

\begin{enumerate}
    \item Given $k_i$, it picks $k_{-i}=k_1...k_{i-1},k_{i+1},...,k_{m}$ as in the protocol and computes $U_0\ket{0}_{\regX,\regZ}\ket{0}_{\regY}\ket{k}_{\regK}$ and measure the register $\regY$ to obtain $y=(y_1,...,y_m)$ along with the corresponding state $\ket{\psi}_{\regX,\regZ}=\ket{\psi(k,y)}_{\regX,\regZ}$.
    \item Apply $H_{\hat{\gamma},c}$ to generate the state $\frac{\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}}{\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}\|}$, which succeeds with probability $\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}\|^2$ (ignoring a global phase factor).
    We denote by $\Succ$ the event that it succeeds in generating the state.
    If it fails to generate the state, then it overrides $y_i$ by picking it in a way such that it can pass the test round with probability $1$, which can be done according to Fact~\ref{fact:perfectly_pass_test}.
    Then it sends $y_i$ to the verifier.
    \item Given a challenge $c'_i$, it works as follows:
    \begin{itemize}
     \item When $c'_i=0$ (i.e., Test round), if $\Succ$ occurred, then it runs $\ext_i$ in the second claim of Lemma~\ref{lem:partition_further} on input $\frac{\ket{0^m}_{\regC}\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}}{\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}\|}$ to generate a forth message accepted with probability $1-\negl(\secpar)$. 
     If $\Succ$ did not occur, then it returns a forth message accepted with probability $1$, which is possible by Fact~\ref{fact:perfectly_pass_test}.
    \item When $c'_i=1$ (i.e., Hadamard round), if $\Succ$ occurred, then it computes  $U\frac{\ket{c}_{\regC}\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}}{\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}_{\regX,\regZ}\|}$ and measure the register $\regX_i$ to obtain the forth message $a_i$.
    If $\Succ$ did not occur, it just aborts.
    \end{itemize}
\end{enumerate}
Then we can see that this cheating adversary passes the test round with overwhelming probability and passes the Hadamard round with the probability equal to the LHS of Eq.~\ref{eq:Hada}.
Therefore, Eq.~\ref{eq:Hada} follows from Lemma~\ref{lem:Mah_soundness} assuming the quantum hardness of LWE problem.

Now, we are ready to prove the theorem. 
As remarked at the beginning of Sec. \ref{sec:proof_of_soundness}, it suffices to show that for any $\mu=1/\poly(n)$, there exists $m=O(\log(n))$ such that the success probability of the cheating prover is at most $\mu$.
Here we set $m = \log \frac{1}{\mu^2}$, $\gamma_0 = 2^{-2m}$, and $T=2^{m}$. 
Note that this parameter setting satisfies the requirement for Lemma~\ref{lem:partition_further} since
$m=\log \frac{1}{\mu^2}=\log (\poly(\secpar))=O(\log \secpar)$ and
$\frac{\gamma_0}{T}=2^{-3m}=\mu^{6}=1/\poly(\secpar)$.
Then we have
\begin{align*}
    &\Pr_{k,\td,y,c}\left[M_{k,\td,y,c}\circ U\ket{c}_{\regC}\ket{\psi}_{\regX,\regZ}= \top\right] \\
     &=\Pr_{k,\td,y,c,\hat{\gamma}}\left[M_{k,\td,y,c}\circ U\ket{c}_{\regC}\left(\sum_{i=1}^{m}\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}_{\regX,\regZ} + \ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}_{\regX,\regZ}+ \ket{\psi_{err}}_{\regX,\regZ}\right) = \top\right] \\
    &\leq (m+2) \underset{k,\td,y,c,\hat{\gamma}}{E}\Biggl[\sum_{i=1}^{m} \|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}_{\regX,\regZ}\|^2\Pr\left[M_{k,\td,y,c}\circ U\frac{\ket{c}_{\regC}\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}_{\regX,\regZ}}{\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}_{\regX,\regZ}\|}=\top\right]\\
   &+\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}_{\regX,\regZ}\|^2\Pr\left[M_{k,\td,y,c}\circ U\frac{\ket{c}_{\regC}\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}_{\regX,\regZ}}{\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}_{\regX,\regZ}} =\top\right]\\
    &+ \|\ket{\psi_{err}}_{\regX,\regZ}\|^2\Pr\left[M_{k,\td,y,c}\circ U\frac{\ket{c}_{\regC} \ket{\psi_{err}}_{\regX,\regZ}}{\|\ket{\psi_{err}}_{\regX,\regZ}\|}=\top\right]\Biggr]\\
        &\leq (m+2) \underset{k,\td,y,c,\hat{\gamma}}{E}\Biggl[\sum_{i=1}^{m} \|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}_{\regX,\regZ}\|^2\Pr\left[M_{i,k_i,\td_i,y_i,c_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}_{\regX,\regZ}}{\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}_{\regX,\regZ}\|}=\top\right]\\
   &+\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}_{\regX,\regZ}\|^2+ \|\ket{\psi_{err}}_{\regX,\regZ}\|^2 \Biggr]\\
    &\leq (m+2)(m(2^{m-1}\gamma_0 +\negl(n))+ 2^{-m} + \frac{m^2}{T}+\negl(\secpar)) \\
    & \leq \mathsf{poly}(\log \mu^{-1}) \mu^{2}+\negl(\secpar). 
\end{align*}
The first equation follows from Lemma \ref{lem:partition_further}. The first inequality follows from the Cauchy-Schwarz inequality.
\takashi{More explanation may be useful.}
 The second inequality holds since considering the verification on a particular coordinate just increases the acceptance probability and probabilities are at most $1$.
The third inequality follows from Eq.~\ref{eq:Test} and \ref{eq:Hada}, which give an upper bound of the first term and Lemma~\ref{lem:partition_further}, which gives upper bounds of the second and third terms.
The last inequality follows from our choices of $\gamma_0$, $T$, and $m$.
For sufficiently large $\secpar$,  this can be upper bounded by $\mu$.
\end{proof}

%---------------------Older  Proof--------------------------------
\begin{comment}
According to Lemma~\ref{lem:partition_further}, we can decompose any state $\ket{\psi}$ above as 
\begin{align*}
    &\ket{\psi} = \ket{\psi_{c_1}} + \ket{\psi_{\bar{c}_1,c_2}} + \cdots +\ket{\psi_{\bar{c}_1,\dots,c_m}} + \ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}+ \ket{\psi_{err}}.
\end{align*}
To prove the theorem, we need to show that 
\begin{align*}
    \Pr[M\circ(V_{i,H}U_c\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}) = accept] = \negl(n), 
\end{align*}
where $V_{i,H}$ is the verification procedure in the $i$th round and $M$ is the measurement to check whether the prover wins the Hadamard round.

When $i=0$, $\ket{\psi} = \ket{\psi_0}+ \ket{\psi_1}+\ket{\psi_{err_1}}$, and $\ket{\psi_1}$ wins the test round with high probability. We prove that the prover with internal state $\ket{\psi_1}$ wins the Hadamard round with only negligible probability by contradiction. Suppose $\ket{\psi_1}$ wins the Hadamard round with noticeable probability. Then, we can construct the following attack for $\ket{\psi}$ such that Lemma~\ref{lem:Mah_soundness} fails. Without loss of generality, we can assume $\|\ket{\psi_1}\|^2\geq 1/poly(n)$. The prover first applies the corresponding $G_{1,\gamma,\delta}$ and measure the register $ph,th,in$ to obtain $\ket{\psi_1}$ with noticeable probability, which implies that the prover can win the test round with noticeable probability by Lemma~\ref{lem:partition}. Then, consider the Hadamard round, if the prover does not obtain $\ket{\psi_1}$ from $G_{1,\gamma,\delta}$, it just randomly outputs $u,d$ to the verifier; otherwise, if the prover obtains $\ket{\psi_1}$, based on our hypothesis, it can win with noticeable probability. Overall, the prover can win the Hadamard round with noticeable probability, which violates Lemma~\ref{lem:Mah_soundness}. Therefore, the prover with internal state $\ket{\psi_1}$ wins the Hadamard round with only negligible probability.

We can decompose $\ket{\psi}$ by using Procedure~\ref{fig:process_H}
\begin{align*}
    \ket{\psi} =  \ket{\psi_{c_1}}+ \ket{\psi_{\bar{c}_1,c_2}} + \cdots + \ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},c_{m}}} + \ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},\bar{c}_{m}}}+ \ket{\psi_{err}}.
\end{align*}
Similar to the case with only one trial, we can show that the prover with internal state $\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},1}}$ wins the Hadamard round with negligible probability by contradiction.
Suppose the prover with $\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},0}}$ can win the Hadamard round with noticeable probability. Without loss of generality, $\|\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},1}}\|^2>1/\poly(n)$. This implies that the prover has noticeable probability to obtain $\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},1}}$ and thus it can win the test round with high probability. Then, in the Hadamard round, the prover can again use $H_c$ to obtain $\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},1}}$ and win the Hadamard round with noticeable probability, which fails Lemma~\ref{lem:Mah_soundness}. Hence, the prover with $\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},1}}$ can only win the Hadamard wound with negligible probability.

Now, we are ready to prove the theorem by using contradiction. Let $m' = \log^2n$. We suppose that there exists a prover can win with probability $\mu=1/\poly(n)$. We choose $m = \log \frac{1}{\mu^2}$, $\gamma_0 = 2^{-2m}$, and $T=2^{-m}$. Then, we choose the first $m$ trials to do parallel repetition and show that by our choices of parameters, the prover can only succeed with probability less than $\mu$. Note that the verifier has $c_1,\dots,c_m$ be chosen uniformly independently. Hence, $c_{m+1},\dots,c_{m'}$ can be viewed as some redundant information uncorrelated to $c_1,\dots,c_m$ given to the prover, which does not change our analysis in Lemma~\ref{lem:Mah_soundness}, Lemma~\ref{lem:partition}, and Lemma~\ref{lem:partition_further}. Let the verifier's verification be $V_{1,c_1},\dots,V_{m,c_m}$, where $V_{i,0}$ is doing the test round in the $i$th trial and $V_{i,1}$ is doing the Hadamard round. Then, 
\begin{align}
    &\Pr[M\circ\left(U_c\ket{\psi}\right) = accept] \\
    &\leq (m+2)(\Pr[M\circ\left(U_c\ket{\psi_{c_1}}\right)=accept] \\
    &+ \Pr[M\circ\left(U_c\ket{\psi_{\bar{c}_1,c_2}}\right)=accept]\\
    &+\cdots+\Pr[M\circ\left(U_c\ket{\psi_{\bar{c}_1,\dots,c_m}}\right)=accept]\label{eq:last_1}\\
    &+\Pr[M\circ\left(U_c\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}\right)=accept] \label{eq:last_2}\\
    &+ \Pr[M\circ\left(U_c\ket{\psi_{err}}\right)=accept])\\
    &\leq (m2^m\gamma_0 + 2^{-m} + \frac{m}{T})(m+2) \leq \mu. 
\end{align}
The first inequality follows from the Cauchy-Schwarz inequality. The second inequality follows from the fact that $V_1,\dots,V_m$ commute, and thus we can choose $V_{i,c_i}$ to be the first operator operating on $\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_{i}}}$; then, by our analysis, the probability that the prover can win is at most $2^m\gamma_0$. The states considered in Eq.~\ref{eq:last_1} and Eq.~\ref{eq:last_2} have norm at most $1/2^m$ and $m/T$ according to Lemma~\ref{lem:partition_further}. The last inequality follows from our choices of $\gamma_0$, $T$, and $m$.

For all noticeable $\mu$, we can find corresponding $m$, $\gamma_0$, and $T$ such that the prover can only win with probability less than $\mu$. Therefore, the probability the prover can win the test can only be negligible when $m=\poly(n)$.  
\end{comment}

### 2020-01-21 parallel/preliminaries.tex

\section{Preliminaries}
\paragraph{Notations.}
For a bit $b\in\bit$, $\bar{b}$ denotes $1-b$.
For a finite set $\calX$, $x\sample \calX$ means that $x$ is uniformly chosen from $\calX$.
For finite sets $\calX$ and $\calY$, $\func(\calX,\calY)$ denotes the set of all functions with domain $\calX$ and range $\calY$.
A function $f:\mathbb{N}\ra [0,1]$ is said to be negligible if for all polynomial $p$ and sufficiently large $\secpar \in \mathbb{N}$, we have $f(\secpar)< 1/p(\secpar)$ and said to be overwhelming if $1-f$ is negligible.
We denote by $\poly$ an unspecified polynomial and by $\negl$ an unspecified negligible function.
We say that a classical (resp. quantum) algorithm is efficient if it runs in probabilistic polynomial-time (resp. quantum polynominal time).
For a quantum or randomized algorithm $\A$, $y\sample \A(x)$ means that $\A$ is run on input $x$ and outputs $y$ and $y \defeq \A(x;r)$  means that $\A$ is run on input $x$ and randomness $r$ and outputs $y$. 
For an interactive protocol between a ``prover" $P$ and ``verifier" $V$, $y\sample \langle P(x_P),V(x_V)) \rangle(x_P)$ means an interaction between them with prover's private input $x_P$ verifier's private input $x_V$, and common input $x$ outputs $y$.
For a quantum state $\ket{\psi}$, $M_{\regX}\circ \ket{\psi}$ means a measurement in the computational basis on the register $\regX$ of $\ket{\psi}$.
We denote by $\QTIME(T)$ a class of languages decided by a quantum algorithm whose running time is at most $T$.
We use $\secpar$ to denote the security parameter throughout the paper.

\subsection{Learning with Error Problem}
Roughly speaking, the learning with error (LWE) is a problem to solve system of noisy linear equations.
Regev \cite{JACM:Regev09} proved that the hardness of LWE can be reduced to hardness of certain worst-case lattice problems via quantum reductions.
We do not give a definition of LWE in this paper since we use the hardness of LWE only for ensuring the soundness of the Mahadev's protocol (Lemma~\ref{lem:Mah_soundness}), which is used as a black-box manner in the rest of the paper.
Therefore, we use exactly the same assumption as that used in \cite{FOCS:Mahadev18a}, to which we refer for detailed definitions and parameter settings for LWE.

\subsection{Quantum Random Oracle Model}
The quantum random oracle model (QROM) \cite{AC:BDFLSZ11} is an idealized model where a real-world hash function is modeled as a quantum oracle that computes a random function.
More precisely, in the QROM, a random function $H:\calX \ra \cal Y$ of a certain domain $\calX$ and range $\calY$ is uniformly chosen from $\func(\calX,\calY)$ at the beginning, and every party (including an adversary) can access to a quantum oracle $O_H$ that maps $\ket{x}\ket{y}$ to $\ket{x}\ket{y\oplus H(x)}$.
We often abuse notation to denote $\A^{H}$ to mean a quantum algorithm $\A$ is given oracle $O_H$.

\subsection{Cryptographic Primitives}
Here, we give definitions of cryptographic primitives that are used in this paper.
We note that they are only used in Sec~\ref{sec:efficient} where we construct an efficient verifier variant.

\subsubsection{Pseudorandom Generator}
A post-quantum pseudorandom generator (PRG) is an efficient deterministic classical algorithm $\PRG:\bit^{\ell} \ra \bit^{m}$ such that for any efficient quantum algorithm $\A$, we have
\begin{align*}
    \left|\Pr_{s\sample \bit^{\ell}}[\A(\PRG(s))]-\Pr_{y\sample \bit^{m}}[\A(y)]\right|\leq \negl(\secpar).
\end{align*}

It is known that there exists a post-quantum PRG for any $\ell=\Omega(\secpar)$ and $m=\poly(\secpar)$ assuming post-quantum one-way function \cite{SIAM:HILL99,FOCS:Zhandry12}.
Especially, a post-quantum PRG exists assuming the quantum hardness of LWE.

%\subsubsection{Collision Resistant Hash}
%A family $\famCRH$ of post-quantum collision resistant hash functions (CRH) is a set of functions $\CRH:\bit^{*}\ra \bit^{m}$ such that for any efficient quantum algorithm $\A$, we have 
%\begin{align*}
%    \Pr_{\CRH\sample \famCRH}[\CRH(x)=\CRH(x')\land x\neq x'): (x,x')\sample \A(\CRH)]\leq \negl(\secpar).
%\end{align*}

%It is known that a post-quantum CRH for any $m=\Omega(\secpar)$ assuming quantum hardness of LWE \cite{STOC:Ajtai96}.\footnote{In fact, a weaker assumption which is quantum hardness of the short integer solution (SIS) problem suffices.}

\subsubsection{Fully Homomorphic Encryption}
A post-quantum fully homomorphic encryption consists of four efficient classical algorithm $\Pi_\FHE=\allowbreak (\fhekeygen,\fheenc,\fheeval,\fhedec)$.
\begin{description}
\item[$\fhekeygen(1^\secpar)$:] The key generation algorithm takes the security parameter $1^\secpar$ as input and outputs a public key $\pk$ and a secret key $\sk$.
\item[$\fheenc(\pk,m)$:] The encryption algorithm takes a public key $\pk$ and a message $m$ as input, and outputs a ciphertext $\ct$.
\item[$\fheeval(\pk,C,\ct)$:] The evaluation algorithm takes a public key $\pk$, a classical circuit $C$, and a ciphertext $\ct$, and outputs a evaluated ciphertext $\ct'$.
\item[$\fhedec(\sk,\ct)$:] The decryption algorithm takes secret key $\sk$ and a ciphertext $\ct$ as input and outputs a message $m$ or $\bot$. 
\end{description}
\paragraph{Correctness.}
For all $\secpar\in \mathbb{N}$, $(\pk,\sk)\sample \fhekeygen(1^\secpar)$, $m$ and $C$, we have
\begin{align*}
    \Pr[\fhedec(\sk,\fheenc(\pk,m))=m]=1
\end{align*}
and
\begin{align*}
    \Pr[\fhedec(\sk,\fheeval(\pk,C,\fheenc(\pk,m)))=C(m)]=1.
\end{align*}
\paragraph{Post-Quantum CPA-Security.}
For any efficient quantum adversary $\A=(\A_1,\A_2)$, we have  
\begin{align*}
    &|\Pr[1\sample  \A_2(\ket{\st_{\A}},\ct):(\pk,\sk)\sample \fhekeygen(1^\secpar),(m_0,m_1,\ket{\st_{\A}})\sample \A_1(\pk), \ct\sample \fheenc(\pk,m_0)]\\
    &-\Pr[1\sample  \A_2(\ket{\st_{\A}},\ct):(\pk,\sk)\sample \fhekeygen(1^\secpar),(m_0,m_1,\ket{\st_{\A}})\sample \A_1(\pk), \ct\sample \fheenc(\pk,m_1)]|\\
&\leq \negl(\secpar).
\end{align*}

FHE is usually constructed by first constructing \textit{leveled} FHE, where we have to upper bound the depth of a circuit to evaluate at the setup, and then converting it to FHE by the technique called bootstrapping~\cite{STOC:Gentry09}. 
There have been many constructions of leveled FHE whose (post-quantum) security can be reduced to the (quantum) hardness of LWE \cite{FOCS:BraVai11,ITCS:BraGenVai12,C:Brakerski12,C:GenSahWat13}.
FHE can be obtained assuming that any of these schemes is \textit{circular secure} \cite{EC:CamLys01} so that it can be upgraded into FHE via bootstrapping.
%which requires that the scheme remains secure even if an adversary sees an encryption of the secret key.
We note that Canetti et al. \cite{TCC:CLTV15} gave an alternative transformation from leveled FHE to FHE based on subexponentially secure iO.

\subsubsection{Strong Output-Compressing Randomized Encoding}
A strong output-compressing randomized encoding \cite{AC:BFKSW19} consists of three efficient classical  algorithms $(\rsetup,\renc,\rdec)$.
\begin{description}
\item[$\rsetup(1^\secpar,1^\ell,\crs)$]: It takes the security parameter $1^\secpar$, output-bound $\ell$, and a common reference string $\crs\in\bit^{\ell}$ and outputs a encoding key $\ek$. 
\item[$\renc(\ek,M,\inp,T)$:] It takes an encoding key $\ek$, Turing machine $M$, an input $\inp\in \bit^*$, and a time-bound $T\leq 2^{\secpar}$ (in binary) as input and outputs an encoding $\Menc$.
\item[$\rdec(\crs,\Menc)$:] It takes a common reference string $\crs$ and an encoding $\Menc$ as input and outputs $\out \in \bit^* \cup \{\bot\}$.
\end{description}

\paragraph{Correctness.}
For any $\secpar\in\mathbb{N}$, $\ell,T\in \mathbb{N}$, $\crs\in \bit^{\ell}$, Turing machine $M$ and input $\inp\in \bit^*$ such that $M(\inp)$ halts in at most $T$ steps and returns a string whose length is at most $\ell$, we have 
\begin{align*}
    \Pr\left[\rdec(\Menc,\crs)=M(\inp): \ek\sample\rsetup(1^\secpar,1^\ell,\crs), \Menc\sample\renc(\ek,M,\inp,T)\right]=1.
\end{align*}

\paragraph{Efficiency.}
There exists polynomials $p_1,p_2,p_3$ such that for all $\secpar\in \mathbb{N}$, $\ell\in \mathbb{N}$, $\crs\sample \bit^{\ell}$:
\begin{itemize}
    \item If $\ek\sample \rsetup(1^\secpar,1^\ell,\crs)$, $|\ek|\leq p_1(\secpar, \log \ell)$.
    \item For every Turing machine $M$, time bound $T$, input $\inp\in \bit^{*}$, if  $\Menc\sample\renc(\ek,M,\inp,T)$, then $|\Menc|\leq p_2(|M|,|\inp|,\log T, \log \ell, \secpar)$,
    \item The running time of $\rdec(\crs,\Menc)$ is at most $\min(T,\Time(M,x))\cdot p_3(\secpar,\log T)$
\end{itemize}

\paragraph{Post-Quantum Security.}
%For any efficient classical adversary $\A=(\A_1,\A_2)$, there exists a simulator $\calS$ such that for all efficient quantum distinguisher $\calD$ such that...

There exists a simulator $\calS$ such that for any $M$ and $\inp$ such that $M(\inp)$ halts in $T^*\leq T$ steps and $|M(\inp)|\leq \ell$ and efficient quantum adversary $\A$,
\begin{align*}
    &|\Pr[1 \sample \A(\crs,\ek,\Menc):\crs\sample \bit^{\ell},\ek\sample\rsetup(1^\secpar,1^\ell,\crs),\Menc\sample\renc(\ek,M,\inp,T)]\\
    &-\Pr[1 \sample \A(\crs,\ek,\Menc):(\crs,\Menc)\sample \calS(1^{\secpar},1^{|M|},1^{|\inp|},M(\inp),T^*),\ek\sample\rsetup(1^\secpar,1^\ell,\crs)]|\leq \negl(\secpar).
\end{align*}

Badrinarayanan et al.~\cite{AC:BFKSW19} gave a construction of strong output-compressing randomized encoding based on iO and the LWE assumption.

\subsubsection{SNARK in the QROM}
Let $H:\bit^{2\secpar}\ra \bit^{\secpar}$ be a quantum random oracle.
A SNARK for an $\NP$ language $\lang$ associated with a relation $\rela$ in the QROM consists of two efficient oracle-aided classical algorithms $\pro_\snark^H$ and $\ver_\snark^H$.
\begin{description}
\item[$\pro_\snark^H$:] It is an instance $x$ and a witness $w$ as input and outputs a proof $\pi$.
\item[$\ver_\snark^H$:] It is an instance $x$ and a proof $\pi$ as input and outputs $\top$ indicating acceptance or $\bot$ indicating rejection.
\end{description}
We require SNARK to satisfy the following properties:

\noindent\textbf{Completeness.}
For any $(x,w)\in\rela$, we have 
\begin{align*}
    \Pr_{H}[\ver_\snark^H(x,\pi)=\top:\pi\sample \pro_\snark^H(x,w)]=1.
\end{align*}

\noindent\textbf{Extractability.}
There exists an efficient quantum extractor $\ext$ such that
for any $x$ and a malicious quantum prover $\tilde{\pro}_\snark^{H}$ making at most $q=\poly(\secpar)$ queries, if 
\begin{align*}
    \Pr_H[\ver_\snark^H(x,\pi):\pi \sample \tilde{\pro}_\snark^H(x)]
\end{align*}
is non-negligible in $\secpar$, then 
\begin{align*}
    \Pr_H[(x,w)\in \rela: w\sample \ext^{\tilde{\pro}_\snark}(x,1^q,1^\secpar)]
\end{align*}
is non-negligible in $\secpar$.\\

\noindent\textbf{Efficient Verification.}
If we can verify that $(x,w)\in \rela$ in classical time $T$, then for any $\pi \sample \tilde{\pro}_\snark^H(x)$, $\ver_\snark^H(x,\pi)$ runs in classical time $\poly(\secpar,|x|,\log T)$.

Chiesa et al.~\cite{TCC:ChiManSpo19} showed that there exists SNARK in the QROM that satisfies the above properties.

### 2020-01-21 parallel/FiatShamir.tex

\section{Two-Round Protocol via Fiat-Shamir Transform}\label{sec:tworound}
In this section, we show that if we apply the Fiat-Shamir transform to $m$-parallel version of the Mahadev's protocol, then we obtain two-round protocol in the QROM. 
That is, we prove the following theorem.
\begin{theorem}\label{thm:MahFS}
Assuming LWE assumption, there exists a two-round CVQC protocol with overwhelming completeness and negligible soundness error in the QROM.
\end{theorem}

\begin{proof}%(of Theorem~\ref{thm:MahFS})
Let $m>\secpar$ be a sufficiently large integer so that $m$-parallel version of the Mahadev's protocol has negligible soundness.
For notational simplicity, we abuse the notation to simply use $\ver_{i}$, $\pro_{i}$, and $\ver_{\out}$ to mean the $m$-parallel repetitions of them. 
Let $H:\calY\ra \bit^{m}$ be a hash function idealized as a quantum random oracle where $\calX$ is the space of the second message $y$ and $\calY=\bit^{m}$.
Our two-round protocol is described below:
\begin{description}
\item[First Message:] The verifier runs $\ver_1$ to generate $(k,\td)$. Then it sends $k$ to the prover and keeps $\td$ as its state.
\item[Second Message:] The prover runs $\pro_2$ on input $k$ to generate $y$ along with the prover's state $\ket{\st_\pro}$. Then set $c\defeq H(y)$, and runs $\pro_4$ on input $\ket{\st_\pro}$ and $y$ to generate $a$. Finally, it returns $(y,a)$ to the verifier.
\item[Verification:] The verifier computes $c=H(y)$, runs $\ver_{\out}(k,\td,y,c,a)$, and outputs as $\ver_{\out}$ outputs.
\end{description}

It is clear that the completeness is preserved given that $H$ is a random oracle.
We reduce the soundness of this protocol to the soundness of $m$-parallel version of the Mahadev's protocol.
For proving this, we borrow the following lemma shown in \cite{C:DFMS19}.

%\begin{lemma}[\cite{C:DFMS19}]\label{lem:FS}
%Let $\calY$ be finite non-empty sets. There exists a black-box polynomial-time two-stage quantum algorithm $\calS$ with the following property. Let $\A$ be an arbitrary oracle quantum algorithm that makes $q$ queries to a uniformly random $H:\calY\ra \bit^{m}$ and that outputs some $y\in \calY$ and output $a$. 
%Then, the two-stage algorithm $\calS^{\A}$ outputs $y\in\calY$ in the first stage
%and, upon a random $c^*\in \bit^{m}$ as input to the second stage, output $a$ so that for any $x_\circ\in \calX$ and any predicate $V$:
%\begin{align*}
%    \Pr_{c^*}\left[y=y_\circ \land V(y,c^*,a):(y,a)\sample \langle\calS^{\A},c^* \rangle \right]\lapprox \frac{1}{O(q^2)}\Pr_{H}\left[y=y_{\circ}\land V(y,H(y),a):(y,a)\sample \A^H\right],
%\end{align*}
%where 
%$(y,a)\sample \langle\calS^{\A},c^* \rangle$ means that $\calS^{\A}$ outputs $y$ and $a$ in the first and second stages respectively on the second stage input $c^*$, and  $\lapprox$ hides a term that is bounded by $\frac{1}{2^{m+1}q}$ when summed over all $y_{\circ}\in \calY$.
%\end{lemma}

\begin{lemma}[{\cite[Theorem 2]{C:DFMS19}}]\label{lem:FS}
Let $\calY$ be finite non-empty sets. There exists a black-box polynomial-time two-stage quantum algorithm $\calS$ with the following property. Let $\A$ be an arbitrary oracle quantum algorithm that makes $q$ queries to a uniformly random $H:\calY\ra \bit^{m}$ and that outputs some $y\in \calY$ and output $a$. 
Then, the two-stage algorithm $\calS^{\A}$ outputs $y\in\calY$ in the first stage
and, upon a random $c\in \bit^{m}$ as input to the second stage, output $a$ so that for any $x_\circ\in \calX$ and any predicate $V$:
\begin{align*}
    \Pr_{c}\left[V(y,c,a):(y,a)\sample \langle\calS^{\A},c \rangle \right]\leq \frac{1}{O(q^2)}\Pr_{H}\left[V(y,H(y),a):(y,a)\sample \A^H\right]-\frac{1}{2^{m+1}q},
\end{align*}
where 
$(y,a)\sample \langle\calS^{\A},c \rangle$ means that $\calS^{\A}$ outputs $y$ and $a$ in the first and second stages respectively on the second stage input $c$.
\end{lemma}

We assume that there exists an efficient adversary $\A$ that breaks the soundness of the above two-round protocol.
We fix $x\notin \lang$ on which $\A$ succeeds in cheating.
We fix $(k,\td)$ that is in the support of the verifier's first message.
We apply Lemma~\ref{lem:FS} for $\A=\A(k)$ and $V=\ver_\out(k,\td,\cdot,\cdot,\cdot)$, to obtain an algorithm $\calS^{\A(k)}$ that satisfies
\begin{align*}
    &\Pr_{c}\left[V_{\out}(k,\td,y,c,a):(y,a)\sample \langle\calS^{\A(k)},c \rangle \right]\\
    \leq &\frac{1}{O(q^2)}\Pr_{H}\left[V_{\out}(k,\td,y,H(y),a):(y,a)\sample \A^H(k)\right]-\frac{1}{2^{m+1}q}.
\end{align*}
Averaging over all possible $(k,\td)$, we have
\begin{align*}
    &\Pr_{k,\td,c}\left[V_{\out}(k,\td,y,c,a):(y,a)\sample \langle\calS^{\A(k)},c \rangle \right]\\
    \leq &\frac{1}{O(q^2)}\Pr_{k,\td,H}\left[V_{\out}(k,\td,y,H(y),a):(y,a)\sample \A^H(k)\right]-\frac{1}{2^{m+1}q}.
\end{align*}
Since we assume that $\A$ breaks the soundness of the above two-round protocol,
\[
\Pr_{k,\td,H}\left[V_{\out}(k,\td,y,H(y),a):(y,a)\sample \A^H(k)\right]
\]
is non-negligible in $\secpar$.
Therefore, as long as $q=\poly(\secpar)$, 
\[
\Pr_{k,\td,c^*}\left[V_{\out}(k,\td,y,c^*,a):(y,a)\sample \langle\calS^{\A(k)},c^* \rangle \right]\]
is also non-negligible in $\secpar$.
Then, we construct an adversary $\B$ that breaks the soundness of parallel version of Mahadev's protocol as follows:
\begin{description}
\item[Second Message:] Given the first message $k$, $\B$ runs the first stage of $\calS^{\A(k)}$ to obtain $y$. It sends $y$ to the verifier.
\item[Forth Message:] Given the third message $c$, $\B$ gives $c$ to $\calS^{\A(k)}$ as the second stage input, and let $a$ be the output of it.
Then $\B$ sends $a$ to the verifier.
\end{description}
Clearly, the probability that $\B$ succeeds in cheating is 
\[
\Pr_{k,\td,c^*}\left[V_{\out}(k,\td,y,c^*,a):(y,a)\sample \langle\calS^{\A(k)},c^* \rangle \right],\]
which is non-negligible in $\secpar$.
This contradicts the soundness of $m$-parallel version of Mahadev's protocol (Theorem~\ref{thm:rep_soundness}).
Therefore we conclude that there does not exists an adversary that succeeds in the two-round protocol with non-negligible probability assuming LWE in the QROM.
\end{proof}

### 2020-01-21 parallel/parallel_2.tex

\section{Parallel Repetition of Mahadev's Protocol}

\subsection{Overview of Mahadev's Protocol}\label{sec:mahadev_overview}
Here, we recall the Mahadev's protocol \cite{FOCS:Mahadev18a}. We only give a high-level description of the protocol and properties of it and omit the details since they are not needed to show our result.

The protocol is run between a quantum prover $\pro$ and a classical verifier $\ver$ on a common input $x$. The aim of the protocol is to enable a verifier to classically verify $x\in \lang$ for a BQP language $\lang$ with the help of interactions with a quantum prover.
The protocol is a 4-round protocol where the first message is sent from $\ver$ to $\pro$. 
We denote the $i$-th message generation algorithm by $\ver_i$ for $i\in\{1,3\}$ or $\pro_i$ for $i\in \{2,4\}$ and denote the verifier's final decision algorithm by $\ver_\out$.
Then a high-level description of the protocol is given below.
\begin{description}
\item[$\ver_1$:] On input the security parameter $1^\secpar$ and $x$, it generates a pair $(\key,\td)$ of a``key" and ``trapdoor", sends $\key$ to $\pro$, and keeps $\td$ as its internal state.
\item[$\pro_2$:] On input $x$ and $\key$, it generates a classical ``commitment" $\comy$ along with a quantum state $\ket{\st_\pro}$, sends $\comy$ to $\pro$, and keeps $\ket{\st_\pro}$ as its internal state.
\item[$\ver_3$:] It randomly picks $c\sample \bit$ and sends $c$ to $\pro$.\footnote{The third message is just a public-coin, and does not depend on the transcript so far or $x$.}
For a knowledgeable reader, the case of $c=0$ corresponds to the ``test round" and the case of $c=1$ corresponds to the ``Hadamard round" in the terminology in \cite{FOCS:Mahadev18a}.
\item[$\pro_4$:] On input $\ket{\st_\pro}$ and $c$, it generates a classical string $\ans$ and sends $\ans$ to $\pro$.
\item[$\ver_\out$:] On input $\key$, $\td$, $y$, $c$, and $\ans$, it returns $\top$ indicating acceptance or $\bot$ indicating rejection.
In case $c=0$, the verification can be done publicly, that is, $\ver_\out$ need not take $\td$ as input.
\end{description}

For the protocol, we have the following properties:\\
\noindent\textbf{Completeness:}
For all $x\in \lang$, we have $\Pr[\langle \pro,\ver \rangle(x)]=\bot]= \negl(\secpar)$.\\
\noindent\textbf{Soundness:}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$, we have  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot]\leq 3/4$.

We need a slightly different form of soundness implicitly shown in \cite{FOCS:Mahadev18a}, which roughly says that if a cheating prover can pass the ``test round" (i.e., the case of $c=0$) with overwhelming probability, then it can pass the ``Hadamard round" (i.e., the case of $c=1$) only with a negligible probability. 
\begin{lemma}[implicit in \cite{FOCS:Mahadev18a}]\label{lem:Mah_soundness}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$ such that  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot\mid c=0]=\negl(\secpar)$, we have $\Pr[\langle \pro^*,\ver \rangle(x)]=\top\mid c=1]=\negl(\secpar)$.
\end{lemma}

We will also use the following simple fact:
\begin{fact}\label{fact:perfectly_pass_test}
There exists an efficient prover that passes the test round with probability $1$ (but passes the Hadamard round with probability $0$) even if $x\notin \lang$. 
\end{fact}

\subsection{Parallel Repetition}
Here, we prove that the parallel repetition of the Mahadev's protocol decrease the soundness bound to be negligible.
Let $\pro^m$ and $\ver^m$ be $m$-parallel repetitions of the honest prover $\pro$ and verifier $\ver$ in the Mahadev's protocol. Then we have the following:
\begin{theorem}[Completeness]\label{thm:rep_completeness}
For all $m= \Omega(\log^2(\secpar))$, for all $x\in \lang$, we have $\Pr[\langle \pro^m,\ver^m \rangle(x)]=\bot]= \negl(\secpar)$.\\
\end{theorem}
\begin{theorem}[Soundness]\label{thm:rep_soundness}
For all $m= \Omega(\log^2(\secpar))$, if the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$, we have  $\Pr[\langle \pro^*,\ver^m \rangle(x)]=\top]\leq \negl(\secpar)$.
\end{theorem}
The completeness (Theorem~\ref{thm:rep_completeness}) easily follows from the completeness of the Mahadev's protocol.
In the next subsection, we prove the soundness (Theorem~\ref{thm:rep_soundness}).

\subsection{Proof of Soundness}

We prove the soundness by showing that for all noticeable error $\epsilon$, there exists a number $m$ such that by parallelly repeating the protocol $m$ times, the error can be reduced to less than $\epsilon$.

\noindent\textbf{Characterization of cheating prover.}
Any cheating prover can be characterized by a tuple $(U_0,\{U_c\}_{c\in \bit^m})$ of unitaries over Hilbert space $\hil_{\regX}\otimes \hil_{\regZ} \otimes \hil_{\regY}  \otimes \hil_{\regK}\otimes \hil_{\regC} $. 
A prover characterized by $(U_0,\{U_{\bfc}\}_{\bfc\in \bit^m})$ works as follows.\footnote{Here, we hardwire into the cheating prover the instance $x\notin \lang$ on which it will cheat instead of giving it as an input.}
\begin{description}
\item[Second Message:] Upon receiving $k=(\key_1,...,\key_m)$, it applies $U_0$ to the state $\ket{0}_{\regX}\otimes\ket{0}_{\regZ}\otimes\ket{0}_{\regY}\otimes  \ket{k}_{\regK}$, and then measures the $Y$ register to obtain $y=(\comy_1,...,\comy_m)$. Then it sends $\bfy$ to $\ver$ and keeps the resulting state $\ket{\psi(k,y)}$ over  $\hil_{\regX,\regZ}$.
\item [Forth Message:] Upon receiving $c\in \bit^{m}$, it applies $U_c$ to $\ket{\psi(k,y)}_{\regX,\regZ}\ket{0}_{\regC}$ and then measures the $\regX$ register in computational basis to obtain $a=(a_1,...,a_m)$. We denote the designated register for $a_i$ by $\regX_i$. Then, we can view the verifier's verification procedure on $i$th trial as a unitary $V_i$. 
\end{description}

%\begin{lemma}[{\cite[Theorem 3]{NWZ09}}]
%Let $\Pi_0$ and $\Pi_1$ be projectors on a Hilbert space $\hil$ and let $R_0:= 2\Pi_0-I$, $R_1:= 2\Pi_1-I$, and $Q:=R_1R_0$. $\hil$ can be decomposed into two-dimensional subspaces $S_1,...,S_\ell$ and one-dimensional subspaces $T_1,...,T_{\ell'}$ invariant under $\Pi_0$ and $\Pi_1$.
%For each $i\in[\ell]$, we can choose a basis $\{\ket{v_i},\ket{v_i}^\bot\}$ of $S_i$ such that $Q$ is a rotation with eigenvalues $e^{\pm i2\theta_i}$ in $S_i$ where $\theta_i=\arccos\sqrt{\bra{v_i}\Pi_1\ket{v_i}}$.
%For $j\in[\ell']$, $Q$ has eigenvalues $\pm 1$ in $T_j$. 
%corresponding to eigenvectors
%\begin{align*}
%    \ket{\phi_i^+}=\frac{1}{\sqrt{2}}(\ket{v_i}+i\ket{v_i^\bot}),~~~\ket{\phi_i^-}=\frac{1}{\sqrt{2}}(\ket{v_i}-i\ket{v_i^\bot})
%\end{align*}
%\end{lemma}

In the following, we first introduced the Jordan's lemma, which we will use to prove Lemma~\ref{lem:partition}. 
\begin{lemma}[Jordan's lemma]~\label{lemma:Jordan}
Given any two projectors $\Pi_1$ and $\Pi_2$. There exists a decomposition of the Hilbert space into one-dimensional and two-dimensional subspaces, which satisfy the following properties: 
\begin{itemize}
    \item All subspaces are orthogonal to each other.
    \item For any two-dimensional subspace $S$, for all $\ket{s}\in S$, $\Pi_1 \ket{s} \in S$ and $\Pi_2 \ket{s} \in S$.
    \item For any two-dimensional subspace $S$, $\Pi_1$ and $\Pi_2$ are rank-one projectors, i.e., there exist two vectors $\ket{v_1}$ and $\ket{v_2}$ in $S$ such that for all $ \ket{s}\in S$,  $\Pi_1 \ket{s} = \ipro{v_1}{s}\ket{v_1}$ and $\Pi_2 |s\rangle =\ipro{v_2}{s}\ket{v_2}$. 
\end{itemize}
\end{lemma}

Fix $k,y$ and the function $f$. Let $i\in [m]$, we consider two projectors 
\begin{align*}
    &\Pi_{in}:= \opro{0}{0}_{\regC}\otimes I_{\regX,\regZ}\\
    %&\Pi_{i,out} := (UH_{\regC_{-i}})^{\dag}(\sum_{b,x: f_{k}(b,x)=y}\opro{b,x}{b,x}_{\regX_i})\otimes I_{\regC,\regX_{-i},\regZ} (UH_{\regC_{-i}}),
   & \Pi_{i,out} := (UH_{\regC_{-i}})^{\dag}(\sum_{a_i\in \Acc_{k_i,y_i}}\opro{a_i}{a_i}_{\regX_i}\otimes I_{\regC,\regX_{-i},\regZ}) (UH_{\regC_{-i}}),
\end{align*}
where $U$ can be any prover's strategy and $\Acc_{k_i,y_i}$ denotes the set of $a_i$ such that the verifier accepts $a_i$ in the test round on the $i$-th coordinate when the first and second messages are $k_i$ and $y_i$, respectively. 
Note that one can efficiently check if $a_i\in \Acc_{k_i,y_i}$ without knowing the trapdoor behind $k_i$ since verification in the test round can be done publicly as explained in Sec. \ref{sec:mahadev_overview}.

$\regX_{-i}:= \regX_1,\dots,\regX_{i-1}, \regX_{i+1},\dots, \regX_{m}$, and $H_{\regC_{-i}}$ means applying Hadamard operators to registers $\regC_1,\dots,\regC_{i-1}, \regC_{i+1},\dots, \regC_{m}$. By using Jordan's lemma, we can decompose the space $\hil_{\regC,\regX,\regZ}$ in the two-dimensional subspaces $S_1,\dots,S_{\ell}$ and one-dimensional subspaces $S_{\ell+1},\dots,S_{p'}$ which are vectors on either $\Pi_{in}$ or $\Pi_{i,out}$. Furthermore, $\Pi_{in}$ and $\Pi_{i,out}$ on $S_1,\dots,S_{p'}$ are rank-one projectors $\opro{\alpha_1}{\alpha_1},\dots,\opro{\alpha_{p'}}{\alpha_{p'}}$ and $\opro{\beta_1}{\beta_1},\dots,\opro{\beta_{p'}}{\beta_{p'}}$. 
For $j\in [p']$, we let the angles between $\ket{\alpha_j}$ and $\ket{\beta_j}$ as $\theta_j$.  Then, we define projectors 
\begin{align*}
    &\Pi_{in, \geq\gamma} := I_{\regC}\otimes(\sum_{j: \theta_j\geq \gamma}\opro{\alpha_j}{\alpha_j}_{\regX,\regZ})\\
    &\Pi_{in, \leq\gamma} := I_{\regC}\otimes(\sum_{j: \theta_j\leq \gamma}\opro{\alpha_j}{\alpha_j}_{\regX,\regZ}).
\end{align*}

\begin{lemma}\label{lem:partition}
Let $(U_0,U)$ be any prover's strategy. Let $i\in[m]$. Let $\gamma_0,\delta\in [0,1]$ where $2^m\gamma_0<<1$. Let $T\in \mathbb{N}$, where $\gamma_0/T>> \delta$ and $\gamma_0/T = 1/\poly(n)$. Let $\gamma$ be sampled uniformly randomly from $[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}]$ and $2^{m-1}<< \frac{\gamma_0}{T}$. Then, there exists an efficient quantum algorithm $G_{i,\gamma,\delta}$ such that for any efficiently generated \takashi{"efficiently generated" may not be needed here.} quantum state $\ket{\psi}_{\regX,\regZ}$, 
\begin{align*}
    G_{i,\gamma,\delta} \ket{0}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0}_{ph}\ket{0}_{th}\ket{0}_{in} = \ket{0}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{001}+ \ket{0}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{011} + \ket{\psi'_{err}}.
\end{align*}
Furthermore, the following properties are satisfied. 
\begin{enumerate}
    \item If we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$, then we have  $E_{\gamma}[\|\ket{\psi_{err}}\|^2]\leq \frac{1}{T}+\negl(n)$.
    \item $\Pr_{\gamma}[M_{ph,th,in}\circ (G_{i,\gamma,\delta} \ket{0}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0}_{ph}\ket{0}_{th}\ket{0}_{in})\notin \{0^t01,0^t11\}] \leq \frac{1}{T}+\negl(n)$, where $M_{ph,th,in}$ is the standard-basis measurement in the register $(ph,th,in)$, and $t$ is the number of qubits in $ph$.   
    \item $E_{c\in \{0,1\}} [\|\ket{\psi_c}\|^2]\leq 1/2$. 
    \item $\|\Pi_{in,\geq\gamma-2\delta} \ket{\psi_1}\|^2 \geq (1-\negl(n))\|\ket{\psi_1}\|^2$. This implies that there exists an polynomial-time cheating prover with $\ket{\psi_1}$ that can be accepted in the test round with $1-\negl(n)$ probability. 
    \takashi{How about saying as follows: There exists an efficient unitary $U'$ such that $\Pr[M_{\regX_i}\circ U'\ket{\psi_1}\in \Acc_{k_i,y_i}]=1-\negl(\secpar)$. Especially, we need not talk about $\Pi_{in,\geq\gamma-2\delta}$ in the statement.}
    \item $\|\Pi_{in,\leq\gamma} \ket{\psi_0}\|^2 \geq (1-\negl(n))\|\ket{\psi_0}\|^2$. %This implies that $\ket{\psi_0}$ will be accepted in the test round with probability at most $2^{m}\gamma$. 
    \takashi{Similarly, we can say as follow: $\Pr[M_{\regX_i}\circ U'\ket{\psi_0}\in \Acc_{k_i,y_i}]\leq 2^{m}\gamma+\negl(\secpar)$}
\end{enumerate}
\end{lemma}

\begin{remark}
To prove Theorem~\ref{thm:rep_soundness}, we only need $m$ to be at most $\log(n)$. Hence, $\gamma_0$ and $T$ can be $1/\poly(n)$. 
\end{remark}

\begin{proof}[Proof of Lemma~\ref{lem:partition}]
We can consider $U_c$ as a unitary $U$ operating on registers $\regC$, $\regX$, and $\regZ$. Procedure~\ref{fig:process_G} defines an efficient process $G_{i,\gamma,\delta}$, which decomposes $\ket{0}_{\regC}\ket{\psi}_{\regX,\regZ}$ into states described in Lemma~\ref{lem:partition}.

\floatname{algorithm}{Procedure}
\begin{algorithm}[h]
    \begin{mdframed}[style=figstyle,innerleftmargin=10pt,innerrightmargin=10pt]
    We define $R_1:= I-2\Pi_{i,out} $, $R_2:= 2\Pi_{in}-I$, and $Q:= R_2R_1$. 
    \begin{enumerate}
    \item Do quantum phase estimation $U_{est}$ on $Q$ with input state $\ket{\psi}$ and $t$-bit precision for parameter $t$ which will be specified later, i.e.,  
    \begin{align*}
        U_{est}\ket{u}\ket{0} \rightarrow \sum_{\theta} \alpha_{\theta} \ket{u}\ket{\theta},
    \end{align*}
    such that $\sum_{\theta\notin \hat{\theta}\pm \epsilon/2}|\alpha_{\theta}|^2\leq 2^{-n}$.
    \item Sample $\gamma$ from $\{\gamma_0/T,\dots,\gamma_0\}$ and then apply $U_{th}:\ket{u}\ket{\theta}\ket{0}_{th} \xrightarrow{U_{th}} \ket{u}\ket{\theta}\ket{b}_{th} $, 
    where $b=1$ if $\theta\in [\gamma-\delta/2, 2\pi - \gamma + \delta/2]$. 
    \item Apply $U^{\dag}_{est}$. 
    \item Apply $U_{in}: \ket{c}_{\regC}\ket{0}_{in} \xrightarrow{U_{in}}  \ket{c}_{\regC}\ket{b'}_{in}$,
    where $b'=1$ if $c\neq 0$. 
    %\item Measure the single-qubit registers $th$ and $err$. 
\end{enumerate}
    \caption{$G_{i,\gamma,\delta}$}
    \label{fig:process_G}
    \end{mdframed}
\end{algorithm}

Here, $G_{i,\gamma,\delta} := U_{in}U^{\dag}_{est}U_{th}U_{est}$ operates on register $\regC$, $\regX$, $\regZ$, and additional registers $ph$, $th$, and $in$.

We let $\ket{u^+_{j}} := \frac{1}{\sqrt{2}}(\ket{\beta_j}+ i\ket{\beta^{\bot}_j})$ and $\ket{u^-_{j}} := \frac{1}{\sqrt{2}}(\ket{\beta_j}- i\ket{\beta^{\bot}_j})$ for $j\in [\ell]$, which are eigenvectors of $Q$. For each one-dimensional subspace, it is either a vector in $\Pi_{in}$ or $\Pi_{i,out}$. We only consider vectors in $\Pi_{in}$, and denote them as $\ket{\alpha_{\ell+1}},\dots,\ket{\alpha_{p}}$. Obviously, they are also eigenvectors of $Q$ (with eigenvalues equal to zero). The eigenvalues corresponding to $\ket{u^+_j}$ are $e^{i\theta_j}$ and $\ket{u^-_j}$ are $e^{i(2\pi-\theta_j)}$.

Now, we can decompose any input state as 
\begin{align*}
    \ket{0}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0}_{ph}\ket{0}_{th}\ket{0}_{in}:= \sum_{j=1}^p d_j \ket{0}_{\regC}\ket{\alpha_j}_{\regX,\regZ}\ket{0}_{ph}\ket{0}_{th}\ket{0}_{in}. 
\end{align*}

We suppose that $\ket{\psi}$ are on the two-dimensional subspaces without loss of generality. Then, since each $\ket{\alpha_j}$ for $j\in [\ell]$ can be represented as $a^+_j\ket{u^+_j} + a^-_{j}\ket{u^-_{j}}$, we rewrite the state in the basis of eigenvectors as 
\begin{align}
    \ket{0}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0}_{ph}\ket{0}_{th}\ket{0}_{in}:= \sum_{j=1}^{\ell} (e^+_j \ket{u^+_j}_{\regC,\regX,\regZ} +e^-_j \ket{u^-_j}_{\regC,\regX,\regZ} )\ket{0}_{ph}\ket{0}_{th}\ket{0}_{in},  \label{eq:input_state}
\end{align}
where $e^+_j = a^+_jd_j$ and $e^-_j = a^-_jd_j$.

We define a function 
\begin{align*}
    \Delta(a;b) = \left\{\begin{matrix} 1 & \mbox{if } a\in [b,2\pi-b]\\
    0 & \mbox{otherwise}\end{matrix}\right.
\end{align*}

In the following, we apply $U_{est}$ and $U_{th}$ to the state in Eq.~\ref{eq:input_state} to estimate the eigenvalues of each $\ket{u_j}$. 
\begin{align}
    &U_{th}U_{est} \ket{0}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0}_{ph}\ket{0}_{th}\ket{0}_{in} \\
    &= U_{th}\sum_{j=1}^{\ell} \left(e^+_j \ket{u^+_j}(\sum_{\tilde{\theta}^+_j} w_{\tilde{\theta}^+_j}\ket{\tilde{\theta}^+_j}_{ph}) + e^-_j \ket{u^-_j}(\sum_{\tilde{\theta}^-_j} w_{\tilde{\theta}^-_j}\ket{\tilde{\theta}^-_j}_{ph})\right) \ket{0}_{th}\ket{0}_{in}\\
    &= \sum_{j: \theta_j\in [\gamma,2\pi-\gamma]} e^+_j \ket{u^+_j}\left(\sum_{\tilde{\theta}^+_j}\ket{\tilde{\theta}^+_j} \ket{\Delta(\tilde{\theta}^+_j,\gamma-\delta)}\ket{0}\right) + e^-_j \ket{u^-_j} \left(\sum_{\tilde{\theta}^-_j}\ket{\tilde{\theta}^-_j} \ket{\Delta(\tilde{\theta}^-_j,\gamma-\delta)}\ket{0}\right)
    \label{eq:correct_1}\\
    &+ \sum_{j: \theta_j\notin [\gamma-2\delta,2\pi-\gamma+2\delta]} e^+_j \ket{u^+_j}\left(\sum_{\tilde{\theta}^+_j}\ket{\tilde{\theta}^+_j} \ket{\Delta(\tilde{\theta}^+_j,\gamma-\delta)}\ket{0}\right) + e^-_j \ket{u^-_j} \left(\sum_{\tilde{\theta}^-_j}\ket{\tilde{\theta}^-_j} \ket{\Delta(\tilde{\theta}^-_j,\gamma-\delta)}\ket{0}\right)\label{eq:correct_2}\\
    &+ \sum_{j: \theta_j \in [\gamma-2\delta,\gamma]\vee[2\pi - \gamma,2\pi - \gamma+\delta]} \left(e^+_j\ket{u^+_j}\ket{\phi_j^+}_{ph,th} + e^-_j\ket{u^-_j}\ket{\phi_j^-}_{ph,th}\right) \ket{0}_{in}. 
    \label{eq:grey_part}
\end{align}
Here, $w_{\tilde{\theta_j^+}} = \frac{1}{2^t}\left( \frac{1-e^{2\pi i(2^t\theta_j^{+}-(b_j^+ + \tilde{\theta}_j^+))}}{1-e^{2\pi i(\theta_j^{+}-(b_j^+ + \tilde{\theta}_j^+)/2^t)}}\right)$ and $w_{\tilde{\theta_j^-}} = \frac{1}{2^t}\left( \frac{1-e^{2\pi i(2^t\theta_j^{-}-(b_j^- + \tilde{\theta}_j^-))}}{1-e^{2\pi i(\theta_j^{-}-(b_j^- + \tilde{\theta}_j^-)/2^t)}}\right)$ for $b_j^{\pm}$ the best $t$ bit approximation to $\theta_j^{\pm}$ which is less than $\theta_j^{\pm}$ for $j\in [\ell]$.

To successfully obtain $\theta_j$ with accuracy $\delta$ with probability $1-\epsilon$ for $\epsilon$ be negligible, we can choose $t=O(\log n)$. Note that simply applying phase estimation with $O(\log n)$-bit precision can not guarantee $\epsilon$ to be negligible. However, by parallelly applying phase estimation polynomially times and taking the most commonly occurring outcome, one can reduce $\epsilon$ to be negligible as shown by Watrous in~\cite{Watrous06}.

By applying $U_{est}^{\dag}$, the state above will be 
\begin{align}
    &\sum_{j: \theta_j\in [\gamma,2\pi-\gamma]} \left[e^+_j \ket{u^+_j} \left( z^+_j\ket{0}_{ph}\ket{1}_{th} + \sqrt{1-|z^+_j|^2} (\sum_{i\neq 0^t1} h^+_{i}\ket{i}_{ph,th}) \right)\ket{0}\right. \\
    &\left. +e^-_j \ket{u^-_j} \left( z^-_j\ket{0}_{ph}\ket{1}_{th} + \sqrt{1-|z^-_j|^2} (\sum_{i\neq 0^t1} h^-_{i}\ket{i}_{ph,th}) \right)\ket{0}\right]\\
    &+\sum_{j: \theta_j\notin [\gamma-2\delta,2\pi-\gamma+2\delta]} \left[e^+_j \ket{u^+_j} \left( z^+_j\ket{0}_{ph}\ket{1}_{th} + \sqrt{1-|z^+_j|^2} (\sum_{i\neq 0^t0} h^+_{i}\ket{i}_{ph,th}) \right)\ket{0}\right.\\
    &\left. +e^-_j \ket{u^-_j} \left( z^-_j\ket{0}_{ph}\ket{1}_{th} + \sqrt{1-|z^-_j|^2} (\sum_{i\neq 0^t0} h^-_{i}\ket{i}_{ph,th}) \right)\ket{0}\right]\\
    &+  \sum_{j: \theta_j \in [\gamma-2\delta,\gamma]\vee[2\pi - \gamma,2\pi - \gamma+\delta]} \left(e^+_j\ket{u^+_j}\ket{\phi_j^+}_{ph,th} + e^-_j\ket{u^-_j}\ket{\phi_j^-}_{ph,th}\right) \ket{0}_{in}.
\end{align}
Here, $z_j^+ = z_j^-$ for all $j$. Let $z_j = z_j^+ = z_j^-$, then
$|z_j|^2 \geq 1-\epsilon$ if $\theta_j\in [\gamma,2\pi-\gamma]$ or $\theta_j\notin [\gamma-2\delta,2\pi-\gamma+2\delta]$. We can rewrite the state above in the basis of $\ket{\alpha_1},\dots,\ket{\alpha_{p}}$. 
\begin{align}
    &\sum_{j: \theta_j\in [\gamma,2\pi-\gamma]} z_jd_j \ket{0}_{\regC}\ket{\alpha_j}_{\regX,\regZ} \ket{0}_{ph}\ket{1}_{th}\ket{0}_{in}\label{eq:correct1}\\
    &+ \sum_{j: \theta_j\notin [\gamma-2\delta,2\pi-\gamma+2\delta]} z_jd_j \ket{0}_{\regC}\ket{\alpha_j}_{\regX,\regZ} \ket{0}_{ph}\ket{0}_{th}\ket{0}_{in}\label{eq:correct2}\\
    &+ \sum_{j: \theta_j\in [\gamma,2\pi-\gamma]} \sqrt{1-|z_j|^2} \left(e^+_j  \ket{u^+_j}(\sum_{i\neq 01} h^+_{i}\ket{i}_{ph,th})\ket{0}+e^-_j \ket{u^-_j}(\sum_{i\neq 01} h^-_{i}\ket{i}_{ph,th})\right)\ket{0}\label{eq:error_1}\\
    &+ \sum_{j: \theta_j\notin [\gamma-2\delta,2\pi-\gamma+2\delta]}\sqrt{1-|z_j|^2} \left(e^+_j  \ket{u^+_j}(\sum_{i\neq 00} h^+_{i}\ket{i}_{ph,th})\ket{0}+e^-_j \ket{u^-_j}(\sum_{i\neq 00} h^-_{i}\ket{i}_{ph,th})\right)\ket{0}\label{eq:error_2}\\
    &+  \sum_{j: \theta_j \in [\gamma-2\delta,\gamma]\vee[2\pi - \gamma,2\pi - \gamma+2\delta]} \left(e^+_j\ket{u^+_j}\ket{\phi_j^+}_{ph,th} + e^-_j\ket{u^-_j}\ket{\phi_j^-}_{ph,th}\right) \ket{0}_{in}\label{eq:grey}.
\end{align}
Notably, the state Eq.~\ref{eq:grey} can only have expected norm $1/T$ over the choice of $\gamma\in \{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\gamma_0\}$. Moreover, the norms of states in Eq.~\ref{eq:error_1} and Eq.~\ref{eq:error_2} can only be negligible since the phase estimation has success probability at least $1-\negl(n)$.

By applying $U_{in}$, we can write the output state of $G_{i,\gamma,\delta}$ as
\begin{align}
    &\left(\sum_{j: \theta_j\in [\gamma-2\delta,2\pi-\gamma+2\delta]} z_jd_j \ket{0}_{\regC}\ket{\alpha_j}_{\regX,\regZ}+\ket{\eta}\right) \ket{0}_{ph}\ket{1}_{th}\ket{1}_{in} \label{eq:output_1}\\
    &+ \left(\sum_{j: \theta_j\notin [\gamma,2\pi-\gamma]} z_jd_j \ket{0}_{\regC}\ket{\alpha_j}_{\regX,\regZ}+\ket{\eta'}\right) \ket{0}_{ph}\ket{0}_{th}\ket{1}_{in}\label{eq:output_2}\\
    &+\sum_{s\in \{0,1\}^{t+2}\setminus \{0^t11,0^{t+1}1\}}\ket{\psi'_{s}}_{\regC,\regX,\regZ}\ket{s}_{ph,th,in}\label{eq:output_err}.
\end{align}
Here, $\ket{\eta}$ and $\ket{\eta'}$ are errors from the states in Eq.~\ref{eq:error_2} and Eq.~\ref{eq:error_1} after applying $U_{in}$. Furthermore, the range of $\theta_j$ has been changed from $[\gamma,2\pi-\gamma]$ to $[\gamma-2\delta, 2\pi-\gamma+2\delta]$ in Eq.~\ref{eq:correct1} and from $[\gamma-2\delta,2\pi-\gamma+2\delta]$ to $[\gamma,2\pi-\gamma]$ in Eq.~\ref{eq:output_1} and Eq.~\ref{eq:output_2}. This follows from the fact that there can be additional state from the state in Eq.~\ref{eq:grey} after applying $U_{in}$. Therefore, $\|\ket{\eta}\|$ and $\|\ket{\eta'}\|$ can only be negligible, and the probability that measuring the register $ph,th,in$ of the state gives neither $0^t11$ nor $0^{t+1}1$ is at most $1/T+\negl(n)$.

We then define
\begin{align*}
&\ket{\psi_1}:=\sum_{j: \theta_j\in [\gamma-2\delta,2\pi-\gamma+2\delta]} z_jd_j \ket{\alpha_j}_{\regX,\regZ}+\ket{\eta}\\
&\ket{\psi_0}:=\sum_{j: \theta_j\notin [\gamma,2\pi-\gamma]} z_jd_j \ket{\alpha_j}_{\regX,\regZ}+\ket{\eta'}.\\
&\ket{\psi_{err}}:= \ket{\psi}-\ket{\psi_0}-\ket{\psi_1}. 
\end{align*}
It is worth noting that 
\begin{align*}
    \ket{0}_{\regC}\ket{\psi}_{\regX,\regZ} &=  \ket{0}_{\regC}\ket{\psi_0}_{\regX,\regZ} + \ket{0}_{\regC}\ket{\psi_1}_{\regX,\regZ} + 
    \sum_{s\in \{0,1\}^{t+2}\setminus \{0^t11,0^{t+1}1\}}\ket{\psi'_{s}}_{\regC,\regX,\regZ}\\
    &= \ket{0}_{\regC}(\ket{\psi_0}+\ket{\psi_1}+\ket{\psi_{err}}).
\end{align*}

Now, we are going to prove that the five properties of the lemma are correct. First, it is obvious that $\ket{\psi} = \ket{\psi_0}+\ket{\psi_1}+\ket{\psi_{err}}$. Then, as we have explained in the previous paragraph, the probability that measuring the register $ph,th,in$ of the state gives neither $0^t11$ nor $0^{t+1}1$ is at most $1/T+\negl(n)$. Then, we prove that $E_{\gamma}[\|\ket{\psi_{err}}\|^2]$ is at most $1/T+\negl(n)$. The errors come from the state in Eq.~\ref{eq:grey_part} are on the eigenvectors with eigenvalues in $[\gamma-2\delta,\gamma]\vee[2\pi - \gamma,2\pi - \gamma+2\delta]$, therefore, the error can be at most $\sum_{j:\theta_j \in [\gamma-2\delta,\gamma]\vee[2\pi - \gamma,2\pi - \gamma+2\delta]}| |e_j^+|^2+|e_j^-|^2$, which expected value is at most $1/T$ over the choice of $\gamma$. The errors from the states in Eq.~\ref{eq:error_2} and Eq.~\ref{eq:error_1} are at most negligible. This proves the second property.  Then, $\ket{\psi_0}$ and $\ket{\psi_1}$ may not be orthogonal. However, $\|\ket{\psi_0}\|^2+ \|\ket{\psi_1}\|^2\leq 1$ since $\|\ket{0}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{001}+ \ket{0}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{011}\|^2 \leq1$ and  $\ket{0}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{001}$ and $ \ket{0}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{011}$ are orthogonal. This also implies that 
\begin{align*}
    E_{c\in \{0,1\}}[ \|\ket{\psi_{c}}\|^2 ] \leq 1/2. 
\end{align*}
Finally, fix $k_i,y_i$, and let $b_i,x_i$ satisfy that $f_{k_i}(b_i,x_i) = y_i$. 
\takashi{Here, we also need to replace $f_{k_i}(b_i,x_i) = y_i$ with $a_i\in \Acc_{k_i,y_i}$.}
Then, given any $c_{-i}$, there exists a unitary $U_c$ such that
\begin{align*}
    & \Pr[M_{\regX}\circ(U_{c} \ket{\psi_0}) = b_i,x_i] \leq 2^m \gamma\\ 
    &\Pr[M_{\regX}\circ(U_{c} \ket{\psi_1}) = b_i,x_i] \geq 1-\negl(n).
\end{align*}
This follow from the fact that on average over $c_{-i}$,  $\Pr[M_{\regX}\circ(UH_{-i} \ket{0}_{\regC}\ket{\psi_0}) = b_i,x_i] \leq \gamma$ and $\Pr[M_{\regX}\circ(UH_{-i} \ket{0}_{\regC}\ket{\psi_1}) = b_i,x_i] \geq 1-\negl(n)$. We can show that $\Pr[M_{\regX}\circ(UH_{-i} \ket{0}_{\regC}\ket{\psi_0}) = b_i,x_i] \leq \gamma$ and $\Pr[M_{\regX}\circ(UH_{-i} \ket{0}_{\regC}\ket{\psi_1}) = b_i,x_i] \geq 1-\negl(n)$ by using the error reduction procedure by Marriott and Watrous in~\cite{MW05}. This completes the proof.

%Consider a linear map $N_{est}: \ket{\phi}_{\regF} \rightarrow \ket{0}_{\regF}$ for all $\ket{\phi}$. Obviously, $N_{est}U_{est} = N_{est}U_{est}^{\dag}= N_{est}$ and $N_{est}$ commutes with $U_{in}$ and $U_{th}$. Similarly, we can define $N_{th}$ and $N_{err}$ that map qubits $th$ and $err$ to $\ket{0}$. Similarly, $N_{th}$ commutes with $U_{in}$ and $U_{est}$ as well as $N_{err}$ commutes with $U_{th}$ and $U_{est}$. Then, 
%\begin{align*}
%    N_eN_{th} N_e N_{err} G_{i,\gamma,\delta}\ket{\psi}\ket{0} =  \ket{\psi}\ket{0}.
%\end{align*}
%Therefore, 
%\begin{align*}
%    \ket{0}_{\regC}\ket{\psi}_{\regX,\regZ}=\ket{0}_{\regC}\ket{\psi_{00}}_{\regX,\regZ}+\ket{0}_{\regC}\ket{\psi_{01}}_{\regX,\regZ}+\ket{\psi_{10}}_{\regC,\regX,\regZ}+ \ket{\psi_{11}}_{\regC,\regX,\regZ}.
%\end{align*}

\end{proof}

%\begin{remark}\label{remark:one_half}
%Note that $\ket{\psi_0}$ and $\ket{\psi_1}$ may not be orthogonal. However, $\|\ket{\psi_0}\|^2+ \|\ket{\psi_1}\|^2\leq 1$ since $\|\ket{0}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{001}+ \ket{0}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{011} + \ket{\psi_{err}}\|^2 =1$ and  $\ket{0}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{001}$ and $ \ket{0}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{011}$ are orthogonal. This implies that 
%\begin{align*}
%    E_{c_i}[ \|\ket{\psi_{c_i}}\|^2 ] \leq 1/2
%\end{align*}
%\end{remark}

In Lemma~\ref{lem:partition}, we show that by fixing any $i\in [m]$, we can partition any prover's state into $\ket{\psi_0}$, $\ket{\psi_1}$, and $\ket{\psi_{err}}$ such that $\ket{\psi_0}$ and $\ket{\psi_1}$ will be rejected and accepted in the test round with high probability.

In the following, we show another procedure that further decompose the prover's state according to any given $c\in \{0,1\}^n$. 
\floatname{algorithm}{Procedure}
\begin{algorithm}[h]
    \begin{mdframed}[style=figstyle,innerleftmargin=10pt,innerrightmargin=10pt]
    Let $(ph_1,th_1,in_1),\dots,(ph_m,th_m,in_m)$ be additional registers that $H_c$ will use. 
    \begin{enumerate}
        \item Sample $\gamma_1$ from $\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\gamma_0\}$. Apply $G_{1,\gamma_1,\delta}$ on $\ket{\psi}\ket{0}_{ph_1,th_1,in_1}$ to obtain
    \begin{align*}
        \ket{\psi_0}\ket{0^t01}+ \ket{\psi_1}\ket{0^t11} + \sum_{s_1\in \{0,1\}^{t+2}\setminus \{0^t01,0^t11\}}\ket{\psi'_{s_1}}\ket{s_1}. 
    \end{align*}
    \item For $i=2,\dots,m$, 
    \begin{enumerate}
        \item Sample $\gamma_i$ from $\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\gamma_0\}$. 
        \item Apply $G_{i,\gamma_i,\delta}$ on $\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1}}}\ket{0}_{ph_i,th_i,in_i}$ to decompose the state into
        \begin{align*}
            \ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},0}}\ket{0^t01}+ \ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}\ket{0^t11} + \sum_{s_i\in \{0,1\}^{t+2}\setminus \{0^t01,0^t11\}}\ket{\psi'_{s_i}}\ket{s_i}.  
        \end{align*}
    \end{enumerate}
    \end{enumerate}

    \caption{$H_c$}
    \label{fig:process_H}
    \end{mdframed}
\end{algorithm}

\begin{lemma}\label{lem:partition_further}
%Fix $c\in \{0,1\}^m$. 
For any $c\in \bit^m$, the state $\ket{\psi}$ can be partitioned as follows by using Procedure~\ref{fig:process_H}. 
\takashi{More precisely, shouldn't we explicitly say that there is an efficient procedure to generate $\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}$ with probability $\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}\|^2$?}
\begin{align*}
    & \ket{\psi} = \ket{\psi_{c_1}} + \ket{\psi_{\bar{c}_1,c_2}} + \cdots +\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{m-1},c_m}} + \ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}+ \ket{\psi_{err}}.
\end{align*}
Further, the following properties are satisfied. 
For any $c\in\bit^{m}$, we have 
\begin{enumerate}
    \item For any $i\in [m]$,
    $\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},0}}$ is rejected in the $i$th test round with probability at most $2^m\gamma$.
    \takashi{$\Pr[M_{\regX_i}\circ U_c \ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},0}}\in \Acc_{k_i,y_i}]\leq 2^{m}\gamma+ \negl(\secpar)$.}

    \takashi{minor comment: $\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},0}}$ is not defined when $c_i=1$. We may need to slightly change the way of the statement.}
    \item There exists an polynomial-time cheating prover with $\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}$ that can be accepted in the test round with $1-\negl(n)$ probability. 
    \takashi{There exists an efficient unitary $U'$ such that $\Pr[M_{\regX_i}\circ U' \ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}\in \Acc_{k_i,y_i}]= 1-\negl(\secpar)$.}
\item $E_{\gamma_1,...,\gamma_m}[\|\ket{\psi_{err}}\|^2]\leq \frac{m^2}{T}+\negl(\secpar)$.
%    \item Measuring the register $(ph_1,th_1,in_1),\dots,(ph_i,th_i,in_i)$ gives error (i.e., $\exists i$, such that $(ph_i,th_i,in_i)\neq (0^t,0,1)$ or $(0^t,1,1)$) with probability at most $\frac{m}{T}$. 
 %   \item For any fixed $\gamma$, $E_c[\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}\|^2] \leq 2^{-m}$.
\end{enumerate}
 Moreover, for any fixed $\gamma$, we have $E_c[\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}\|^2] \leq 2^{-m}$.
\end{lemma}
\begin{proof}
We prove this lemma by induction on $i\in [m]$. 
When $i=1$, 
\begin{align*}
    \ket{\psi} =  \ket{\psi_0} + \ket{\psi_1} + \ket{\psi_{err_1}}, 
\end{align*}
where $\ket{\psi_0}$, $\ket{\psi_1}$, and $\ket{\psi_{err_1}}$ satisfy all the properties of Lemma~\ref{lem:partition_further} according to Lemma~\ref{lem:partition}.

We suppose the hypothesis is true when $i=k$. Then, when $i=k+1$, we can decompose the state $\ket{\psi}$ as follows
\begin{align*}
    \ket{\psi} =  \ket{\psi_{c_1}}+ \ket{\psi_{\bar{c}_1,c_2}} + \cdots + \ket{\psi_{\bar{c}_1,\dots, \bar{c}_k,c_{k+1}}} + \ket{\psi_{\bar{c}_1,\dots, \bar{c}_k,\bar{c}_{k+1}}}+ \sum_{j=1}^{k+1}\ket{\psi_{err_j}}.
\end{align*}
$\ket{\psi_{\bar{c}_1,\dots, \bar{c}_k,c_k}}$ also satisfies the first two properties according to Lemma~\ref{lem:partition}, and the third property follows from the Cauchy-Schwarz inequality. Finally, as $E[\ket{\psi_{\bar{c}_1,\dots, \bar{c}_k}}]\leq 2^{-k}$, it is obvious that $E[\ket{\psi_{\bar{c}_1,\dots, \bar{c}_k,\bar{c}_{k=1}}}]\leq 2^{-(k+1)}$ according to Lemma~\ref{lem:partition}. 
\end{proof}

Given Lemma~\ref{lem:partition_further}, we can start proving Theorem~\ref{thm:rep_soundness}.

\begin{proof}[Proof of Theorem~\ref{thm:rep_soundness}]

According to Lemma~\ref{lem:Mah_soundness}, we know that
\begin{align*}
    \Pr_{k,y}[U_{0}\ket{\psi(k,y)}\mbox{ wins test round}]\geq 1-\negl(n) \Rightarrow \Pr_{k,y}[U_{0}\ket{\psi(k,y)}\mbox{ wins Hadamard round}]\leq \negl(n),   
\end{align*}
Here,  
\begin{align*}
    &U_0\ket{0}_{\regY}\ket{0}_{\regX,\regZ}\ket{k}_{\regK} \xrightarrow{\mbox{measure }\regY} \ket{\psi(k,y)}_{\regX,\regZ}\ket{k}_{\regK}.
\end{align*}
In the following, we just write $\ket{\psi}$ to mean $\ket{\psi(k,y)}$.

For each $i\in [m]$, let $V_{i,0}$ and $V_{i,1}$ be unitaries that run the verification procedure in the test and Hadamard round on the $i$-th coordinate and write the verification result in a designated register and $M_i$ be the measurement on the designated register on the $i$-th coordinate.
For any state $\ket{\phi}$, we denote $M\circ \ket{\phi}=\top$ to mean $M_i\circ \ket{\phi}=\top$ for all $i\in[m]$ for notational simplicity. 
With this notation, a cheating prover's success probability can be written as 
\begin{align*}
    \Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi}\right) = \top].
\end{align*}

According to Lemma~\ref{lem:partition_further}, for any fixed $c\in \bit^{m}$, we can decompose $\ket{\psi}$ as 
\begin{align*}
    \ket{\psi} =  \ket{\psi_{c_1}}+ \ket{\psi_{\bar{c}_1,c_2}} + \cdots + \ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},c_{m}}} + \ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},\bar{c}_{m}}}+ \ket{\psi_{err}}.
\end{align*}

To prove the theorem, we first show the following two inequalities holds for any $i\in[m]$ and fixed $c\in \bit^{m}$:
\begin{align}
    \Pr[M_i\circ(V_{i,0}U_c\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},0}}) = \top] \leq 2^{m}\gamma_{0}. \label{eq:Test}
\end{align}
\begin{align}
    \|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}\|^2\Pr[M_i\circ(V_{i,1}U_c\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}) = \top] = \negl(n). \label{eq:Hada}
\end{align}

Eq.~\ref{eq:Test} easily follows from the first claim of Lemma~\ref{lem:partition_further} and $\gamma\leq \gamma_0$.

For proving Eq.~\ref{eq:Hada}, we consider a modified cheating adversary described below:

\begin{enumerate}
    \item Given $k$, it runs the first stage of the adversary to obtain $y$ along with the corresponding state $\ket{\psi}=\ket{\psi(k,y)}$.
    \item Apply $G_{1,\gamma,\delta}$,....,$G_{i-1,\gamma,\delta}$ sequentially to obtain the state $\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}$, which succeeds in non-negligible probability since we assume the LHS of Eq.~\ref{eq:Hada} is non-negligible. 
    We denote by $\Succ$ the event that it succeeds in generating the state.
    If it fails to generate the state, then it overrides $y$ by picking it in a way such that it can pass the test round with probability $1$, which can be done according to Fact~\ref{fact:perfectly_pass_test}.
    Then it sends $y$ to the verifier.
    \item Given a challenge $c_i$, it works as follows:
    \begin{itemize}
     \item When $c_i=0$ (i.e., Test round), if $\Succ$ occurred, then it runs the cheating prover that is assumed to exist in the second claim of Lemma~\ref{lem:partition_further} to generate an forth message accepted with overwhelming probability. 
     If $\Succ$ did not occur, then it returns a forth message accepted with probability $1$, which is possible by Fact~\ref{fact:perfectly_pass_test}.
    \item When $c_i=0$ (i.e., Hadamard round), if $\Succ$ occurred, then it runs the second stage of the adversary with the internal state  $\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}$ to generate the forth message $a$. If $\Succ$ did not occur, it just aborts.
    \end{itemize}
\end{enumerate}
Then we can see that this cheating adversary passes the test round with overwhelming probability and passes the Hadamard round with the probability equal to the LHS of Eq.~\ref{eq:Hada}.
Therefore, Eq.~\ref{eq:Hada} follows from Lemma~\ref{lem:Mah_soundness}.

Now, we are ready to prove the theorem. 
First, we remark that it suffices to show that for any $\mu=1/\poly(n)$, there exists $m=O(\log(n))$ such that the success probability of the cheating prover is at most $\mu$.
This is because we are considering $\omega(\log(n))$-parallel repetition, in which case the number of trials is larger than   any $m=O(\log(n))$ for sufficiently large $n$, and thus we can do the same analyses focusing on  the first $m$ trials and ignoring the rest of the trials.  
Specifically, we set $m = \log \frac{1}{\mu^2}$, $\gamma_0 = 2^{-2m}$, and $T=2^{m}$. Then we have
\begin{align*}
    &\Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi}\right) = \top] \\
    &\leq (m+2)(\sum_{i=1}^{m} \|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}\|^2\Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}\right)=\top]\\
    &+\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}\|^2\Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}\right)=\top]\\
    &+ \|\ket{\psi_{err}}\|^2\Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi_{err}}\right)=\top]))\\
    &\leq (m+2)(\sum_{i=1}^{m} \|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}\|^2\Pr[M_i\circ\left(V_{i,c_i}U_c\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_i}}\right)=\top]\\
    &+\|\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}\|^2+\|\ket{\psi_{err}}\|^2)\\
    &\leq (m+2)(m(2^m\gamma_0 +\negl(n))+ 2^{-m} + \frac{m^2}{T}+\negl(\secpar)) \leq \mu. 
\end{align*}
The first inequality follows from the Cauchy-Schwarz inequality. The second inequality follows from the fact that $V_1,\dots,V_m$ commute, and thus we can choose $V_{i,c_i}$ to be the first operator operating on $\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_{i}}}$.
The third inequality follows from Eq.~\ref{eq:Test} and \ref{eq:Hada}, which give an upper bound of the first term and Lemma~\ref{lem:partition_further}, which give upper bounds of the second and third terms.
The last inequality follows from our choices of $\gamma_0$, $T$, and $m$.
\end{proof}

%---------------------Older  Proof--------------------------------
\begin{comment}
According to Lemma~\ref{lem:partition_further}, we can decompose any state $\ket{\psi}$ above as 
\begin{align*}
    &\ket{\psi} = \ket{\psi_{c_1}} + \ket{\psi_{\bar{c}_1,c_2}} + \cdots +\ket{\psi_{\bar{c}_1,\dots,c_m}} + \ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}+ \ket{\psi_{err}}.
\end{align*}
To prove the theorem, we need to show that 
\begin{align*}
    \Pr[M\circ(V_{i,H}U_c\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},1}}) = accept] = \negl(n), 
\end{align*}
where $V_{i,H}$ is the verification procedure in the $i$th round and $M$ is the measurement to check whether the prover wins the Hadamard round.

When $i=0$, $\ket{\psi} = \ket{\psi_0}+ \ket{\psi_1}+\ket{\psi_{err_1}}$, and $\ket{\psi_1}$ wins the test round with high probability. We prove that the prover with internal state $\ket{\psi_1}$ wins the Hadamard round with only negligible probability by contradiction. Suppose $\ket{\psi_1}$ wins the Hadamard round with noticeable probability. Then, we can construct the following attack for $\ket{\psi}$ such that Lemma~\ref{lem:Mah_soundness} fails. Without loss of generality, we can assume $\|\ket{\psi_1}\|^2\geq 1/poly(n)$. The prover first applies the corresponding $G_{1,\gamma,\delta}$ and measure the register $ph,th,in$ to obtain $\ket{\psi_1}$ with noticeable probability, which implies that the prover can win the test round with noticeable probability by Lemma~\ref{lem:partition}. Then, consider the Hadamard round, if the prover does not obtain $\ket{\psi_1}$ from $G_{1,\gamma,\delta}$, it just randomly outputs $u,d$ to the verifier; otherwise, if the prover obtains $\ket{\psi_1}$, based on our hypothesis, it can win with noticeable probability. Overall, the prover can win the Hadamard round with noticeable probability, which violates Lemma~\ref{lem:Mah_soundness}. Therefore, the prover with internal state $\ket{\psi_1}$ wins the Hadamard round with only negligible probability.

We can decompose $\ket{\psi}$ by using Procedure~\ref{fig:process_H}
\begin{align*}
    \ket{\psi} =  \ket{\psi_{c_1}}+ \ket{\psi_{\bar{c}_1,c_2}} + \cdots + \ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},c_{m}}} + \ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},\bar{c}_{m}}}+ \ket{\psi_{err}}.
\end{align*}
Similar to the case with only one trial, we can show that the prover with internal state $\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},1}}$ wins the Hadamard round with negligible probability by contradiction.
Suppose the prover with $\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},0}}$ can win the Hadamard round with noticeable probability. Without loss of generality, $\|\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},1}}\|^2>1/\poly(n)$. This implies that the prover has noticeable probability to obtain $\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},1}}$ and thus it can win the test round with high probability. Then, in the Hadamard round, the prover can again use $H_c$ to obtain $\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},1}}$ and win the Hadamard round with noticeable probability, which fails Lemma~\ref{lem:Mah_soundness}. Hence, the prover with $\ket{\psi_{\bar{c}_1,\dots, \bar{c}_{m-1},1}}$ can only win the Hadamard wound with negligible probability.

Now, we are ready to prove the theorem by using contradiction. Let $m' = \log^2n$. We suppose that there exists a prover can win with probability $\mu=1/\poly(n)$. We choose $m = \log \frac{1}{\mu^2}$, $\gamma_0 = 2^{-2m}$, and $T=2^{-m}$. Then, we choose the first $m$ trials to do parallel repetition and show that by our choices of parameters, the prover can only succeed with probability less than $\mu$. Note that the verifier has $c_1,\dots,c_m$ be chosen uniformly independently. Hence, $c_{m+1},\dots,c_{m'}$ can be viewed as some redundant information uncorrelated to $c_1,\dots,c_m$ given to the prover, which does not change our analysis in Lemma~\ref{lem:Mah_soundness}, Lemma~\ref{lem:partition}, and Lemma~\ref{lem:partition_further}. Let the verifier's verification be $V_{1,c_1},\dots,V_{m,c_m}$, where $V_{i,0}$ is doing the test round in the $i$th trial and $V_{i,1}$ is doing the Hadamard round. Then, 
\begin{align}
    &\Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi}\right) = accept] \\
    &\leq (m+2)(\Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi_{c_1}}\right)=accept] \\
    &+ \Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi_{\bar{c}_1,c_2}}\right)=accept]\\
    &+\cdots+\Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi_{\bar{c}_1,\dots,c_m}}\right)=accept]\label{eq:last_1}\\
    &+\Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi_{\bar{c}_1,\dots,\bar{c}_m}}\right)=accept] \label{eq:last_2}\\
    &+ \Pr[M\circ\left((V_{1,c_1}\cdots V_{m,c_m})U_c\ket{\psi_{err}}\right)=accept])\\
    &\leq (m2^m\gamma_0 + 2^{-m} + \frac{m}{T})(m+2) \leq \mu. 
\end{align}
The first inequality follows from the Cauchy-Schwarz inequality. The second inequality follows from the fact that $V_1,\dots,V_m$ commute, and thus we can choose $V_{i,c_i}$ to be the first operator operating on $\ket{\psi_{\bar{c}_1,\dots,\bar{c}_{i-1},c_{i}}}$; then, by our analysis, the probability that the prover can win is at most $2^m\gamma_0$. The states considered in Eq.~\ref{eq:last_1} and Eq.~\ref{eq:last_2} have norm at most $1/2^m$ and $m/T$ according to Lemma~\ref{lem:partition_further}. The last inequality follows from our choices of $\gamma_0$, $T$, and $m$.

For all noticeable $\mu$, we can find corresponding $m$, $\gamma_0$, and $T$ such that the prover can only win with probability less than $\mu$. Therefore, the probability the prover can win the test can only be negligible when $m=\poly(n)$.  
\end{comment}

### 2020-01-21 preliminaries.tex
Make some progress on QPIP0 protocol

@@
 
-Lastly, we recall the definition of a verifiable quantum FHE scheme:
+Lastly, we generalize the above security definition to interactive schemes.
+
 \begin{dfn}
-	TODO
+	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$. Then it is IND-CPA secure if, for any $x_1, x_2$, any polynomial time adversary $\cA$,
+	$$\abs{\Pr\left[TODO\right]}-TODO$$
+
 \end{dfn}

### 2020-01-21 privacy.tex
Make some progress on QPIP0 protocol

@@
 \Ethan{TODO Do some kinda intro to the section}
+
+First we give a definition of CPA security for delegation schemes... TODO
+
+\begin{dfn}
+	A $\QPIP_\tau$ protocol is IND-CPA secure if, for any polynomial time prover $\cA$,
+	$$\abs{\Pr[\cA]}$$
+	where $x$ is the input of the verifier.
+\end{dfn}
 
@@
 
-\floatname{algorithm}{Protocol}
+\Ethan{TODO intro}
+
+Here's what the client should do.
+
 \begin{algorithm}
@@
 		\Procedure{Delegation}{C, x}
-			\State $\mathsf{QHE.Keygen}\rightarrow(pk, evk, sk)$
-			\State Let $\tilde{x}=\mathsf{Enc}_{pk}(x)$
-			\State Let $\tilde{C}$ to the circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{Eval}_{evk}(C, \tilde{x})$
-			\State The client delegates $\tilde{C}(\tilde{x})$ to the server using our $\QPIP_0$ protocol.
+			\State Compute $\mathsf{QHE.Keygen}\rightarrow(pk, evk, sk)$
+			\State Compute $\tilde{x}=\mathsf{Enc}_{pk}(x)$
+			\State Let $\tilde{C}$ be the quantum circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{Eval}_{evk}(C, \tilde{x})$
+			\State Delegate $\tilde{C}(\tilde{x})$ to the server using our $\QPIP_0$ protocol.
+			\State Get $y$ from the server
+			\State \Return $\mathsf{QHE.Dec}(y)$
 		\EndProcedure
@@
 \end{algorithm}
-
-\begin{thm}
-	\autoref{ProtoPrivateDelegation} is IND-CPA secure.
-\end{thm}
-\begin{proof}
-	This is... not so trivial.
-\end{proof}
 
@@
 \end{proof}
+
+\begin{thm}
+	\autoref{ProtoPrivateDelegation} is IND-CPA secure.
+\end{thm}
+\begin{proof}
+	This is... not so trivial?
+\end{proof}

### 2020-01-21 preliminaries.tex
Add first draft definition of CPA for protocols

@@
 \begin{dfn}
-	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$. Then it is IND-CPA secure if, for any $x_1, x_2$, any polynomial time adversary $\cA$,
-	$$\abs{\Pr\left[TODO\right]}-TODO$$
+	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$.
+Then it is IND-CPA secure if any polynomial time adversary $\cA$ can't win \protoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$ \Ethan{Check if it's actually lambda}
+\end{dfn}
 
-\end{dfn}
+\floatname{algorithm}{Protocol}
+\begin{algorithm}
+	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
+	\label{ProtoQPIP1}
+	\begin{algorithmic}[1]
+		\State \Ethan{Do we need some kinda generalization of Keygen here...?}
+		\State $\cA$ picks strings $c_1$ and $c_2$ and sends them to the challenger
+		\State The challenger picks $c_b$ at random where $b\in\set{0,1}$
+		\State The challenger runs the protocol with the adversary, acting as the verifier with input $c_b$
+		\State $\cA$ attempts to guess $b$
+	\end{algorithmic}
+\end{algorithm}
+\floatname{algorithm}{Algorithm}

### 2020-01-21 privacy.tex
Make IND-CPA first draft proof

@@
 \begin{proof}
-	This is... not so trivial?
+	The verifier's first message is encrypted into $\tilde{x}$ in an IND-CPA way as a ciphertext.
+	The verifier's second message is the basis choice of Hadamard or test rounds, which can be done using public coins.
+
+	The verifier only sends the prover these two messages, so it follows \Ethan{hopefully?} easily that the protocol itself is also IND-CPA. \Ethan{Maybe not rigorous enough?}
 \end{proof}

### 2020-01-22 privacy.tex
Add proof sketch of QFHE correctness

@@
 	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
-	\item $\mathsf{QHE.Dec}$ commutes with standard basis measurement. If the ciphertext is a measurement result, it can also be done classically.
+	\item $\mathsf{QHE.Dec}$ ``commutes" with measurements.
+\Ethan{Need to elaborate just a bit more here; i.e.
+need to mention X/Z only} If the ciphertext is a measurement result, it can also be done classically.
 \end{itemize}
@@
 \begin{thm}
-	\autoref{ProtoPrivateDelegation} is a $\QPIP$ scheme for... (TODO) \Ethan{Just copy from earlier and hope I don't need to rewrite too much}
+    \label{QPIP1thm}
+	\protoref{ProtoPrivateDelegation} can evaluate any $L\in\SampBQP$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
 \end{thm}
 \begin{proof}
-	TODO
+	The client will receive a sample from $\mathsf{Eval}_{evk}(C, \tilde{x})$. \Ethan{Errors terms?}
+
+	Which by the properties of homomoprhic encryption should decode to $\rho$ that is $\varepsilon$-indistinguishable to $C(x)$ \Ethan{Fill in error terms}
+
+	As decoding commutes with measurements, the verifier requests its desired measurements of $\rho$ and decode it.
 \end{proof}

### 2020-01-22 blind.tex
Change "private" to "blind"
Clarify how decryption commutes with measurement

--- 2020-01-22 privacy.tex
@@
-\section{Private Delegation}
+\section{Constant-Round, Blind, and Verifiable Delegation}
 
@@
 
-First we give a definition of CPA security for delegation schemes... TODO
+We now present a constant-round, blind, and verifiable delegation scheme for $\SampBQP$ as an application of our $\QPIP_0$ construction for $\SampBQP$,
+which we achieve by using the homomorphic encryption scheme from \cite{mahadev_qfhe} together with our construction.
 
-\begin{dfn}
-	A $\QPIP_\tau$ protocol is IND-CPA secure if, for any polynomial time prover $\cA$,
-	$$\abs{\Pr[\cA]}$$
-	where $x$ is the input of the verifier.
-\end{dfn}
-
-\subsection{Quantum homomorphic encryption scheme}
+\subsection{Homomorphic Encryption with Classical Client}
 
@@
 
-We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe}.
-We use this particular QFHE because it allows the use of a classical client.
+We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe} which allows the use of a classical client.
 Specifically, it has the following extra properties:
@@
 	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
-	\item $\mathsf{QHE.Dec}$ ``commutes" with measurements.
-\Ethan{Need to elaborate just a bit more here; i.e.
-need to mention X/Z only} If the ciphertext is a measurement result, it can also be done classically.
+	\item Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
+		$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
 \end{itemize}

### 2020-01-23 blind.tex
Write first draft for blind delegation proof

@@
 	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
-	\item Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
+\end{itemize}
+
+Furthermore, one could either decode or measure first, in the following sense:
+\begin{lemma}
+	\label{decodeMeasureOrder}
+	Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
 		$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
-\end{itemize}
+\end{lemma}
 
@@
 	\caption{Verifiable, secure, and constant round delegation}
-	\label{ProtoPrivateDelegation}
+	\label{ProtoPriv}
 	\begin{algorithmic}[1]
@@
 			\State Compute $\tilde{x}=\mathsf{Enc}_{pk}(x)$
-			\State Let $\tilde{C}$ be the quantum circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{Eval}_{evk}(C, \tilde{x})$
+			\State Let $\tilde{C}$ be the quantum circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{QHE.Eval}_{evk}(C, \tilde{x})$
 			\State Delegate $\tilde{C}(\tilde{x})$ to the server using our $\QPIP_0$ protocol.
-			\State Get $y$ from the server
-			\State \Return $\mathsf{QHE.Dec}(y)$
+			\State Request $\Lambda'$ based on \autoref{decodeMeasureOrder}, where $\Lambda$ is the basis choice if $C(x)$ were delegated.
+			\State Let $y$ be the measurement results from the server
+			\State \Return $\widehat{\mathsf{QHE.Dec}_{sk}}(y)$
 		\EndProcedure
@@
     \label{QPIP1thm}
-	\protoref{ProtoPrivateDelegation} can evaluate any $L\in\SampBQP$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
+	\myprotoref{ProtoPriv} can evaluate any $L\in\SampBQP$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
 \end{thm}
 \begin{proof}
-	The client will receive a sample from $\mathsf{Eval}_{evk}(C, \tilde{x})$. \Ethan{Errors terms?}
+	Suppose $\bbV$ accepts $\bbP'$ at least $\delta$ of the time.
 
-	Which by the properties of homomoprhic encryption should decode to $\rho$ that is $\varepsilon$-indistinguishable to $C(x)$ \Ethan{Fill in error terms}
+	Then the $\QPIP_0$ delegation must accept at least that often too,
+	so the client will receive a sample from $\mathsf{Eval}_{evk}(C, \tilde{x})$ with at most inverse poly error. \Ethan{security param?}
 
-	As decoding commutes with measurements, the verifier requests its desired measurements of $\rho$ and decode it.
+	The verifier ends up with a state within inverse poly distance to
+		$$\widehat{\mathsf{QHE.Dec}_{sk}}\circ\Lambda'(\tilde{C}(\tilde{x}))$$
+		$$=\Lambda\circ\mathsf{QHE.Dec}_{sk}(\tilde{C}(\tilde{x}))$$
+		$$=\Lambda\circ\mathsf{QHE.Dec}_{sk}(\mathsf{QHE.Eval}_{evk}(C, \tilde{x}))$$
+
+	By the properties of homomoprhic encryption, with overwhelming probability this is indistinguishable to \Ethan{Check if it's true} $\Lambda(C(x))$
 \end{proof}
@@
 \begin{thm}
-	\autoref{ProtoPrivateDelegation} is IND-CPA secure.
+	\myprotoref{ProtoPriv} is IND-CPA secure.
 \end{thm}

### 2020-01-23 blind.tex
Make editorial changes

@@
 \section{Constant-Round, Blind, and Verifiable Delegation}
-
-\Ethan{TODO Do some kinda intro to the section}
 
@@
 
-\Ethan{This subsection is copied and pasted directly from the other QMPC paper and is kinda a mess}
-
-We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe} which allows the use of a classical client.
+We first present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe} which allows the use of a classical client.
 Specifically, it has the following extra properties:
@@
 
-\subsection{Generalizing our delegation protocol using QFHE}
+\subsection{Our Delegation Protocol}
 
-\Ethan{TODO intro}
-
-Here's what the client should do.
+Now we're ready to construct our delegation protocol.
 

### 2020-01-23 preliminaries.tex
Fix typo

@@
 \begin{dfn}
-	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
+	A quantum homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
 	\begin{itemize}

### 2020-01-23 preliminaries.tex
Remove unused code

@@
 $\Lambda^2_{1, 2}(X_3)$ would be a Toffoli (CCNOT) gate.
-
-\iffalse
-\begin{definition}
-	Let $H\geq0$ denote $H$ is positive semidefinite.
-\end{definition}
-
-\begin{definition}
-	Let $\lambda(H)$ as the least eigenvalue of $H$.
-\end{definition}
-
-\begin{definition}
-	Let the \emph{ground state} of $H$ be the eigenvector corresponding to $\lambda(H)$.
-\end{definition}
-
-\begin{definition}
-	Let $H\big|_S=\prod_SH\prod_S$, where $\prod_S$ is the projection onto the subspace $S$.
-\end{definition}
-
-\begin{definition}
-	Let $\ket{\widehat{t}}=\ket{11\ldots1} \ket{00\ldots0}$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
-\end{definition}
-
-\begin{definition}
-	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
-I.e.
-$\Lambda^2_{1, 2}(X_3)$ would be a Toffoli (CCNOT) gate.
-\end{definition}
-\fi
 

### 2020-01-23 preliminaries.tex
Make a pass at preliminary

@@
 
-\begin{rmk}
-\hannote{sampling generalize decision blah}
-\end{rmk}
+\hannote{sampling generalize decision blah} \Ethan{That doesn't sound right}
 
@@
 		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
-			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
 		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
@@
 
-As this is a homomorphic encryption scheme, it satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$
+$\mathsf{HE}$ also satisfies, with all but negligible probability in $\lambda$, that
+$$\mathsf{HE.Dec}_{sk}(\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
 
@@
 
-Lastly, we generalize the above security definition to interactive schemes.
+\subsection{Security definition for interactive protocols}
 
 \begin{dfn}
+	Let $\lambda$ be a security parameter.
 	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$.
-Then it is IND-CPA secure if any polynomial time adversary $\cA$ can't win \protoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$ \Ethan{Check if it's actually lambda}
+	Then it is IND-CPA secure if any polynomial time adversary $\cA$ can't win \myprotoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$ \Ethan{Check if it's actually lambda}
 \end{dfn}
@@
 	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
-	\label{ProtoQPIP1}
+	\label{ProtoIndCPA}
 	\begin{algorithmic}[1]
-		\State \Ethan{Do we need some kinda generalization of Keygen here...?}
 		\State $\cA$ picks strings $c_1$ and $c_2$ and sends them to the challenger
@@
 \floatname{algorithm}{Algorithm}
+
+\begin{rmk}
+	\Ethan{Maybe something about this being (hopefully) equivalent to simulator-based security?}
+\end{rmk}

### 2020-01-23 preliminaries.tex
Updates from Overleaf

--- 2020-01-23 preliminaries.tex
@@
 		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
-		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$ outputs a distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
+		\item (Soundness) For all $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$ outputs a distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
 	\end{itemize}
@@
 \begin{dfn}
-	A quantum homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
+	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
 	\begin{itemize}
@@
 \begin{dfn}
-	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$.
-Then it is IND-CPA secure if any polynomial time adversary $\cA$ can't win \protoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$ \Ethan{Check if it's actually lambda}
+	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$. Then it is IND-CPA secure if, for any $x_1, x_2$, any polynomial time adversary $\cA$,
+	$$\abs{\Pr\left[TODO\right]}-TODO$$
+
 \end{dfn}
-
-\floatname{algorithm}{Protocol}
-\begin{algorithm}
-	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
-	\label{ProtoQPIP1}
-	\begin{algorithmic}[1]
-		\State \Ethan{Do we need some kinda generalization of Keygen here...?}
-		\State $\cA$ picks strings $c_1$ and $c_2$ and sends them to the challenger
-		\State The challenger picks $c_b$ at random where $b\in\set{0,1}$
-		\State The challenger runs the protocol with the adversary, acting as the verifier with input $c_b$
-		\State $\cA$ attempts to guess $b$
-	\end{algorithmic}
-\end{algorithm}
-\floatname{algorithm}{Algorithm}

### 2020-01-23 qpip0.tex
Updates from Overleaf

@@
 \subsection{Subprotocol for Quantum Measurements}
-%\hannote{what is this for?}
+\hannote{Ethan old description before parallel rep.}
 As a warm-up, we  restate the construction in \cite{mahadev_delegation}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.
@@
 	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
-	    \item (completeness) $\forall n\in\mathcal{B}^{\otimes n}, h\in\bbN$ and $h$, there is a prover with negligible reject probability.
-Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_\rho, h$
+	    \item (completeness) $\forall\rho\in\mathcal{B}^{\otimes n}$ and $h\in\set{0,1}^n$, there is a prover with negligible reject probability.
+Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_{\rho, h}$
 	    \item (soundness) Fix $\bbP'$ and $h$.
@@
 \end{theorem}
+
+\hannote{import urmila protocol description.. up}
+Here, we recall the Mahadev's protocol \cite{FOCS:Mahadev18a}.
+We only give a high-level description of the protocol and properties of it and omit the details since they are not needed to show our result.
+
+The protocol is run between a quantum prover $\pro$ and a classical verifier $\ver$ on a common input $x$.
+The aim of the protocol is to enable a verifier to classically verify $x\in \lang$ for a BQP language $\lang$ with the help of interactions with a quantum prover.
+The protocol is a 4-round protocol where the first message is sent from $\ver$ to $\pro$. 
+We denote the $i$-th message generation algorithm by $\ver_i$ for $i\in\{1,3\}$ or $\pro_i$ for $i\in \{2,4\}$ and denote the verifier's final decision algorithm by $\ver_\out$.
+Then a high-level description of the protocol is given below.
+\begin{description}
+\item[$\ver_1$:] On input the security parameter $1^\secpar$ and $x$, it generates a pair $(\key,\td)$ of a``key" and ``trapdoor", sends $\key$ to $\pro$, and keeps $\td$ as its internal state.
+\item[$\pro_2$:] On input $x$ and $\key$, it generates a classical ``commitment" $\comy$ along with a quantum state $\ket{\st_\pro}$, sends $\comy$ to $\pro$, and keeps $\ket{\st_\pro}$ as its internal state.
+\item[$\ver_3$:] It randomly picks $c\sample \bit$ and sends $c$ to $\pro$.\footnote{The third message is just a public-coin, and does not depend on the transcript so far or $x$.}
+Following the terminology in \cite{FOCS:Mahadev18a}, we call the case of $c=0$ the ``test round" and the case of $c=1$ the ``Hadamard round".
+\item[$\pro_4$:] On input $\ket{\st_\pro}$ and $c$, it generates a classical string $\ans$ and sends $\ans$ to $\pro$.
+\item[$\ver_\out$:] On input $\key$, $\td$, $y$, $c$, and $\ans$, it returns $\top$ indicating acceptance or $\bot$ indicating rejection.
+In case $c=0$, the verification can be done publicly, that is, $\ver_\out$ need not take $\td$ as input.
+\end{description}
+
+For the protocol, we have the following properties:\\
+\noindent\textbf{Completeness:}
+For all $x\in \lang$, we have $\Pr[\langle \pro,\ver \rangle(x)]=\bot]= \negl(\secpar)$.\\
+\noindent\textbf{Soundness:}
+If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$, we have  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot]\leq 3/4$.
+
+We need a slightly different form of soundness implicitly shown in \cite{FOCS:Mahadev18a}, which roughly says that if a cheating prover can pass the ``test round" (i.e., the case of $c=0$) with overwhelming probability, then it can pass the ``Hadamard round" (i.e., the case of $c=1$) only with a negligible probability.
+\begin{lemma}[implicit in \cite{FOCS:Mahadev18a}]\label{lem:Mah_soundness}
+If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$ such that  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot\mid c=0]=\negl(\secpar)$, we have $\Pr[\langle \pro^*,\ver \rangle(x)]=\top\mid c=1]=\negl(\secpar)$.
+\end{lemma}
+
+We will also use the following simple lemma:
+\begin{lemma}\label{fact:perfectly_pass_test}
+There exists an efficient prover that passes the test round with probability $1$ (but passes the Hadamard round with probability $0$) even if $x\notin \lang$. 
+\end{lemma}
 
@@
 
+\iffalse
 \hannote{duplicate version by ethan..}
@@
 \end{lem}
+\fi
 
@@
 \begin{proof}
-We run Mahadev's 4-round protocol \ref{} and use parallel repetition to reduce the soundness error.
+We run Mahadev's 4-round protocol \ref{} and use parallel repetition to reduce the soundness error. \hannote{describe $N$ time para rep}. 
 \end{proof}
@@
     asdf
-\begin{theorem}
+\begin{cor}
 
@@
 
-\end{theorem}
+\end{cor}

### 2020-01-24 preliminaries.tex
Update IND-CPA for protocols

--- 2020-01-23 preliminaries.tex
@@
 	Let $\lambda$ be a security parameter.
-	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$.
-	Then it is IND-CPA secure if any polynomial time adversary $\cA$ can't win \myprotoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$ \Ethan{Check if it's actually lambda}
+	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
+	Then it is IND-CPA secure if $\forall x\in\set{0,1}^n$ no polynomial time adversary $\cA$ can win \myprotoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$
 \end{dfn}
@@
 	\begin{algorithmic}[1]
-		\State $\cA$ picks strings $c_1$ and $c_2$ and sends them to the challenger
-		\State The challenger picks $c_b$ at random where $b\in\set{0,1}$
-		\State The challenger runs the protocol with the adversary, acting as the verifier with input $c_b$
+		\State The challenge picks $b\in\set{0,1}$ at random
+		\If{b=1}
+			\State The challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
+		\Else
+			\State The challenger runs the protocol with the adversary, acting as the verifier with input $x$
+		\EndIf
 		\State $\cA$ attempts to guess $b$
@@
 \floatname{algorithm}{Algorithm}
-
-\begin{rmk}
-	\Ethan{Maybe something about this being (hopefully) equivalent to simulator-based security?}
-\end{rmk}

### 2020-02-01 bqp.tex
Add blind BQP section

\section{Constant-round blind delegation of BQP}

lol

### 2020-02-01 bqp.tex
Write draft for blind BQP

@@
 
-lol
+\Ethan{Need to define QPIP for both decision and sampling problems and point out the differences then}
+
+We'll define the following protocol for $\BQP$ which we later generalize.
+
+Let $L\in\BQP$, and $x\in\set{0,1}^*$.
+
+There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
+In fact, they have the same certificate, and the certificate can be check using only $X$ and $Z$ measurements, which we'll call $\ket{\psi_x}$. \Ethan{TODO cite textbook for this}
+
+\begin{thm}
+	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
+	Then \protoref{proto:BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
+\end{thm}
+
+\floatname{algorithm}{Protocol}
+\begin{algorithm}
+	\caption{Protocol for $\BQP$}
+	\label{proto:BQP}
+	\begin{algorithmic}[1]
+		\State The verifier sends $x$ to the prover
+		\State The prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
+		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
+	\end{algorithmic}
+\end{algorithm}
+
+Now we generalize the previous construction to achieve blindness.
+We denote the prover's action as $\cF$. That is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.
+
+\begin{algorithm}
+	\caption{Blind Protocol for $\BQP$}
+	\label{proto:BlindBQP}
+	\begin{algorithmic}[1]
+		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$. \Ethan{Security param?}
+		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
+		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ to the prover
+		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
+		\State The verifier decodes qubit-by-qubit \Ethan{hmm?}
+		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
+	\end{algorithmic}
+\end{algorithm}
+
+\begin{thm}
+	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
+	Let $\lambda$ be the security parameter.
+	Then \protoref{proto:BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.
+\end{thm}
+\begin{proof}
+	I promise this is true...
+\end{proof}
+
+Now we can simply apply the following results from \Ethan{TODO cite}...
+
+\begin{thm}
+	compiles $\QPIP_1$ protocol with the following properties:
+	\begin{itemize}
+		\item classical inputs
+		\item only X/Z measurements
+		\item negl. completeness and soundness
+	\end{itemize}
+	into a $\QPIP_0$ protocol with negl. completeness and soundness
+\end{thm}
+
+With this result, we now achieve...
+\begin{thm}
+	There exists...
+\end{thm}
+\begin{proof}
+	Just compile A through B...
+\end{proof}
+
+\floatname{algorithm}{Algorithm}

### 2020-02-01 blind.tex
Move QFHE to preliminary

@@
 which we achieve by using the homomorphic encryption scheme from \cite{mahadev_qfhe} together with our construction.
-
-\subsection{Homomorphic Encryption with Classical Client}
-
-We first present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe} which allows the use of a classical client.
-Specifically, it has the following extra properties:
-\begin{itemize}
-	\item $\mathsf{QHE.Keygen}$ can be done classically.
-	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
-\end{itemize}
-
-Furthermore, one could either decode or measure first, in the following sense:
-\begin{lemma}
-	\label{decodeMeasureOrder}
-	Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
-		$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
-\end{lemma}
 

### 2020-02-01 bqp.tex
Move QFHE to preliminary

@@
-\section{Constant-round blind delegation of BQP}
+\section{Constant-Round Blind Delegation for BQP}
 
@@
 	\begin{algorithmic}[1]
-		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$. \Ethan{Security param?}
+		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$.
 		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
@@
 		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
-		\State The verifier decodes qubit-by-qubit \Ethan{hmm?}
+		\State The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates
+		\State The verifier decodes the measurement results
 		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$

### 2020-02-01 preliminaries.tex
Move QFHE to preliminary

@@
 
+We also use the quantum full homomorphic encryption (QFHE) scheme given in \cite{mahadev_qfhe} which allows the use of a classical client.
+
 \begin{dfn}
-	A quantum homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
+	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
 	\begin{itemize}
@@
 
+The constructions in \cite{mahadev_qfhe}, $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$, has the following extra properties:
+\begin{itemize}
+	\item $\mathsf{QHE.Keygen}$ can be done classically.
+	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
+\end{itemize}
+
+Furthermore, one could either decode or measure first, in the following sense:
+\begin{lemma}
+	\label{decodeMeasureOrder}
+	Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
+		$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
+\end{lemma}
+To the knowledgable reader, this is done simply by storing the so-called quantum-capable ciphertext also as qubits.
+
 \subsection{Security definition for interactive protocols}
@@
 		\State The challenge picks $b\in\set{0,1}$ at random
-		\If{b=1}
+		\If{$b=1$}
 			\State The challenger runs the protocol with the adversary, acting as the verifier with input $0^n$

### 2020-02-01 bqp.tex
Fix typos

@@
 	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
-	Then \protoref{proto:BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
+	Then \protoref{BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
 \end{thm}
@@
 	Let $\lambda$ be the security parameter.
-	Then \protoref{proto:BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.
+	Then \protoref{BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.
 \end{thm}

### 2020-02-01 bqp.tex
Make theorem stubs for BlindBQP

@@
 	\begin{algorithmic}[1]
+		\State Let $\lambda$ be the security parameter.
+		\State Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
 		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$.
@@
 
+As we will see in the theorems below, \protoref{BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.
+
 \begin{thm}
-	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
-	Let $\lambda$ be the security parameter.
-	Then \protoref{BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.
+	\protoref{BlindBQP} has negligible completeness
 \end{thm}
 \begin{proof}
-	I promise this is true...
+	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{Well, we'll pretend it's true...}
+\end{proof}
+
+\begin{thm}
+	\protoref{BlindBQP} has negligible soundness
+\end{thm}
+\begin{proof}
+	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{It sounds good, so it must be true.}
+\end{proof}
+
+\begin{thm}
+	\protoref{BlindBQP} is IND-CPA
+\end{thm}
+\begin{proof}
+	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{I have this gut feeling.}
 \end{proof}
@@
 \begin{thm}
-	compiles $\QPIP_1$ protocol with the following properties:
+	There is a way to compile a $\QPIP_1$ protocol with the following properties:
 	\begin{itemize}

### 2020-02-02 bqp.tex
Write proofs of blind BQP

@@
 		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
-		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ to the prover
+		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
 		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
@@
 \begin{proof}
-	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{Well, we'll pretend it's true...}
+	Based on the correctness of $\mathsf{QHE}$, the verifier would successfully decode $\cF(c)$ with overwhelming probability.
+	The subsequent underlying QMA check also has overwhelming probability of acceptance.
 \end{proof}
@@
 \begin{proof}
-	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{It sounds good, so it must be true.}
+	The verifier's actions is equivalent to first decoding the prover's message then measuring it.
+
+	Suppose the prover's message decodes to some $\rho$. Since it is a quantum state, the soundness of the underlying $\QMA$ instance can be used.
+
+	That is, there doesn't exists a valid certificate $\rho$ that has non-negligible probability of acceptance.
 \end{proof}
@@
 \begin{proof}
-	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{I have this gut feeling.}
+	The only thing the prover learns is $c$ and $pk$, so this follows directly from $\mathsf{QHE}$'s security.
 \end{proof}

### 2020-02-02 qpip0.tex

@@
 
-\subsection{Parallel Repetition of the Measurement Subprotocol}
+\subsection{$\QPIP_0$ protocol for $\SampBQP$}
+%Parallel Repetition of the Measurement Subprotocol
+
+The following protocol is a $\QPIP_0$ protocol for $\SampBQP$
+
+$\forall c\in\bbN$ Soundness = $O(T^{-c})$
+
+Given inverse poly p(T), we can parameterize the protocol to have soundness p(T)
+
+%	\label{ProtoQPIP1}
+
+\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
+\label{proto:QPIP0samp}
+\begin{enumerate}
+    \item Verifier start with description of quantum circuit $C$, input string $x$ 
+    \item Both verifier and prover start with a soundness parameter $\varepsilon$.
+    \item Run $N=O(1/\varepsilon)$ copies of [[urmilla protocol]] of in parallel.
+On the testing round, the verifier uniformly randomly pick one copy and Hadamard round and has all other copies as test round.
+    \item Verified reject if any of the test round result is wrong. Otherwise, decode the Hadamard run desult and run \cref{ProtoQPIP1} on it
+    . 
+\end{enumerate}
+\end{protocol}
 

### 2020-02-02 blind.tex
Start rewriting blind sampbqp
Make flow of blind then fully classical consistent

@@
 
-Now we're ready to construct our delegation protocol.
+Now we compile our $\QPIP_1$ protocol \myprotoref{protoQPIP1} using the quantum homomorphic encryption $\mathsf{QHE}$ \Ethan{TODO maybe wrap this as a def} in a similar way as what we did for our blind $\BQP$ delegation protocol in \cref{sec:BlindQBP}
 
-\begin{algorithm}
-	\caption{Verifiable, secure, and constant round delegation}
-	\label{ProtoPriv}
-	\begin{algorithmic}[1]
-		\Procedure{Delegation}{C, x}
-			\State Compute $\mathsf{QHE.Keygen}\rightarrow(pk, evk, sk)$
-			\State Compute $\tilde{x}=\mathsf{Enc}_{pk}(x)$
-			\State Let $\tilde{C}$ be the quantum circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{QHE.Eval}_{evk}(C, \tilde{x})$
-			\State Delegate $\tilde{C}(\tilde{x})$ to the server using our $\QPIP_0$ protocol.
-			\State Request $\Lambda'$ based on \autoref{decodeMeasureOrder}, where $\Lambda$ is the basis choice if $C(x)$ were delegated.
-			\State Let $y$ be the measurement results from the server
-			\State \Return $\widehat{\mathsf{QHE.Dec}_{sk}}(y)$
-		\EndProcedure
-	\end{algorithmic}
-\end{algorithm}
+The construction is obvious, \Ethan{Maybe still write it out...? Or maybe not?} so we directly go into analysis.
 
 \begin{thm}
-    \label{QPIP1thm}
-	\myprotoref{ProtoPriv} can evaluate any $L\in\SampBQP$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
+	Compiling \cref{proto:QPIP0samp} using $\mathsf{QHE}$ preserves its completeness and soundness.
 \end{thm}
 \begin{proof}
+	A honest prover still gets accepted with overwhelming probability by the correctness of $\mathsf{QHE}$. \Ethan{Not sure if too hand-wavy}
+
+	\Ethan{Check how much of the following still applies before erasing}
 	Suppose $\bbV$ accepts $\bbP'$ at least $\delta$ of the time.

### 2020-02-02 preliminaries.tex
Start rewriting blind sampbqp
Make flow of blind then fully classical consistent

@@
 	\begin{itemize}
-		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
+		\item $\mathsf{Keygen}(1^\lambda, 1^D)\rightarrow(pk, evk, sk)$
 		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
@@
 
-Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.
-
 $\mathsf{HE}$ also satisfies, with all but negligible probability in $\lambda$, that
 $$\mathsf{HE.Dec}_{sk}(\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
+where $f$ is specified by a circuit of depth at most $D$.
 
@@
 
+In general, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then this can be used as a compiler to achieve blindness.
+
 \subsection{Security definition for interactive protocols}

### 2020-02-02 blind.tex
Wrap up blindness first draft

@@
 
-The construction is obvious, \Ethan{Maybe still write it out...? Or maybe not?} so we directly go into analysis.
+The construction is obvious, \Ethan{Maybe still write it out...? Or maybe not?} so we directly go into analysis. \Ethan{Need to remember security param if we write this out}
 
@@
 
-	\Ethan{Check how much of the following still applies before erasing}
-	Suppose $\bbV$ accepts $\bbP'$ at least $\delta$ of the time.
+	As for soundness, a cheating prover cannot do better under this compiliation, since each message still decodes to some plaintext.
 
-	Then the $\QPIP_0$ delegation must accept at least that often too,
-	so the client will receive a sample from $\mathsf{Eval}_{evk}(C, \tilde{x})$ with at most inverse poly error. \Ethan{security param?}
-
-	The verifier ends up with a state within inverse poly distance to
-		$$\widehat{\mathsf{QHE.Dec}_{sk}}\circ\Lambda'(\tilde{C}(\tilde{x}))$$
-		$$=\Lambda\circ\mathsf{QHE.Dec}_{sk}(\tilde{C}(\tilde{x}))$$
-		$$=\Lambda\circ\mathsf{QHE.Dec}_{sk}(\mathsf{QHE.Eval}_{evk}(C, \tilde{x}))$$
-
-	By the properties of homomoprhic encryption, with overwhelming probability this is indistinguishable to \Ethan{Check if it's true} $\Lambda(C(x))$
+	In other words, anything a cheating prover can do after the compiliation, there exists a corresponding strategy in the version before.
+	\Ethan {Ahhhh this is not rigorous at all}
 \end{proof}

### 2020-02-02 bqp.tex
Updates from Overleaf
Make flow of blind then fully classical consistent
Wrap up blindness first draft

@@
 \section{Constant-Round Blind Delegation for BQP}
+\label{sec:BlindBQP}
 
-\Ethan{Need to define QPIP for both decision and sampling problems and point out the differences then}
+In this section we present our constant-round blind delegation protocol for $\BQP$.
+We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.
 
-We'll define the following protocol for $\BQP$ which we later generalize.
+\begin{thm}
+	\Ethan{Main theorem of the section}
+	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
+\end{thm}
+
+We'll construct this protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
 
@@
 There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
-In fact, they have the same certificate, and the certificate can be check using only $X$ and $Z$ measurements, which we'll call $\ket{\psi_x}$. \Ethan{TODO cite textbook for this}
+In fact, they have the same certificate, which we'll call $\ket{\psi_x}$. See the excellent text \cite{kitaev2002classical} for details.
+According to \cite{PhysRevA.93.022326}, the certificate can be check using only $X$ and $Z$ measurements.
+We'll also summarize said proofs in \cref{sec:Hamiltonian} for our $\SampBQP$ construction.
 
@@
 		\State Let $\lambda$ be the security parameter.
+		\State Let $L$ be the depth of the circuit corresponding to $\cF$
 		\State Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
-		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$.
+		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
 		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
@@
 
-Now we can simply apply the following results from \Ethan{TODO cite}...
-
+Now we can simply apply the following results from \cite{parallelrep} to obtain a blind and constant-round for $\QPIP_0$ with negligible completeness and soundness.
 \begin{thm}
-	There is a way to compile a $\QPIP_1$ protocol with the following properties:
+	There is a compiler that takes a $\QPIP_1$ protocol with the following properties:
 	\begin{itemize}
 		\item classical inputs
-		\item only X/Z measurements
+		\item client uses only X/Z measurements
 		\item negl. completeness and soundness
 	\end{itemize}
-	into a $\QPIP_0$ protocol with negl. completeness and soundness
+	and outputs a corresponding $\QPIP_0$ protocol with negl. completeness and soundness \Ethan{same inputs...?}
 \end{thm}
 
-With this result, we now achieve...
-\begin{thm}
-	There exists...
-\end{thm}
-\begin{proof}
-	Just compile A through B...
-\end{proof}
-
 \floatname{algorithm}{Algorithm}

### 2020-02-02 preliminaries.tex
Wrap up blindness first draft

@@
 	\begin{itemize}
-		\item $\mathsf{Keygen}(1^\lambda, 1^D)\rightarrow(pk, evk, sk)$
+		\item $\mathsf{Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
 		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
@@
 
-$\mathsf{HE}$ also satisfies, with all but negligible probability in $\lambda$, that
+\Ethan{TODO Check if Dec has to work all the time or just overwhelming probability (and if so, over what)}
+
+$\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
 $$\mathsf{HE.Dec}_{sk}(\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
-where $f$ is specified by a circuit of depth at most $D$.
+where $f$ is specified by a circuit of depth at most $L$.
 

### 2020-02-02 bqp.tex
Revamp sec:BQP to use protocol env

@@
 \begin{thm}
-	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
-	Then \protoref{BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
+	\protoref{BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
 \end{thm}
 
-\floatname{algorithm}{Protocol}
-\begin{algorithm}
-	\caption{Protocol for $\BQP$}
+\begin{protocol}{Protocol for $\BQP$}
 	\label{proto:BQP}
-	\begin{algorithmic}[1]
-		\State The verifier sends $x$ to the prover
-		\State The prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
-		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
-	\end{algorithmic}
-\end{algorithm}
+	Let $n$ be the number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
+	\begin{enumerate}
+		\item The verifier sends $x$ to the prover
+		\item The prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
+		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
+	\end{enumerate}
+\end{protocol}
 
-Now we generalize the previous construction to achieve blindness.
-We denote the prover's action as $\cF$. That is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.
+Now we compile \cref{proto:BQP} using $\mathsf{QHE}$ in order to achieve blindness.
+We denote the honest prover's action in $\cref{proto:BQP}$ as $\cF$; that is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.
 
-\begin{algorithm}
-	\caption{Blind Protocol for $\BQP$}
+\begin{protocol}{Blind Protocol for $\BQP$}
 	\label{proto:BlindBQP}
-	\begin{algorithmic}[1]
-		\State Let $\lambda$ be the security parameter.
-		\State Let $L$ be the depth of the circuit corresponding to $\cF$
-		\State Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
-		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
-		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
-		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
-		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
-		\State The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates
-		\State The verifier decodes the measurement results
-		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
-	\end{algorithmic}
-\end{algorithm}
+	Let $\lambda$ be the security parameter.
+	Let $L$ be the depth of the circuit corresponding to $\cF$.
+	Let $n$ be number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
+	\begin{enumerate}
+		\item The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
+		\item The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
+		\item The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
+		\item The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
+		\item The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates \Ethan{Not sure if rigorous enough}
+		\item The verifier decodes the measurement results
+		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
+	\end{enumerate}
+\end{protocol}
 

### 2020-02-02 hamiltonian.tex
Fix LaTeX warnings
Wrap up blindness first draft
Make another algorithm env change

@@
 \section{The History XZ Local Hamiltonian}
+\label{sec:Hamiltonian}
 
@@
 		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
-		%The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
 	\end{itemize}
@@
 
-\subsection{Reducing $\SampBQP$ to  local Hamiltonian }
+\subsection{Reducing quantum circuit to  local Hamiltonian }
 
@@
 	\label{AlgGroundStateCheck}
-	\begin{algorithmic}[1]
-		\Require $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$
-		\Procedure{GroundStateCheck}{$\ket\phi$}
-		\State Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
-		\State Set $p_S = \frac{|d_S|}{D}$
-		\State Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
-		\State  Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
-		\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
-		\State Accept
-		\Else
-		\State Reject
-		\EndIf
-		\EndProcedure
-	\end{algorithmic}
+		Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
+		Let $\ket\phi$ be the potential ground state to check
+		\begin{itemize}
+			\item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
+			\item Set $p_S = \frac{|d_S|}{D}$
+			\item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
+			\item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
+			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept. Otherwise, reject.
+		\end{itemize}
 \end{algorithm}

### 2020-02-02 qpip.tex
Remove extra empty section
Make flow of blind then fully classical consistent
Use protocol env for QPIP1 SampBQP

@@
-\section{Our Delegation Protocols}
+\section{Delegation Protocol for Hybrid Client}
 
-\section{Delegation Protocol for Hybrid Client}
+\Ethan{Remark on amplification and doing this qubit-by-qubit by last section. Do some general story-telling.}
 
@@
 
-\floatname{algorithm}{Protocol}
-\begin{algorithm}
-	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
+\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
 	\label{ProtoQPIP1}
-	\begin{algorithmic}[1]
-		\Procedure{QPIP1}{$C, x, c$}
-		\State Let $\varepsilon=T^{-c}$
-		\State Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
-		\State Let $n$ be large enough so both $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ and $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ are negligible in $\varepsilon$ by Chernoff bound
-		\State Let $N$ be large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
-
-		\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
-		\State The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
-		\State $c\gets0$
-		\State $y\gets\bot$
-		\For{$i\gets1, N$}
-			\If{Copy is for checking}
-			\State The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
-			\If{Test passes}
-				$c\gets c+1$
-			\EndIf
-			\ElsIf{Copy is for outputting}
-			\State The verifier measures the copy in standard basis
-			\If{measurement result of the clock register $\geq\frac{T}{2}$}
-				\If{$y=\bot$}
-					\State $y\gets$ measurement result of the data register
-				\EndIf
-			\EndIf
-			\Else
-			\State The verifier measures the entire register in standard basis
-			\EndIf
-		\EndFor
-		\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
-		\If{$y\ne\bot$}
-		\State output $y$
-		\Else
-		\State Reject
-		\EndIf
-		\Else
-		\State Reject
-		\EndIf
-		\EndProcedure
-	\end{algorithmic}
-\end{algorithm}
+	Let $\varepsilon=T^{-c}$. \Ethan{Try setting up this $\varepsilon$ more intuitively}
+	Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
+	Let $n$ be large enough so both $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ and $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ are negligible in $\varepsilon$ by Chernoff bound
+	Let $N$ be large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
+	\begin{enumerate}
+		\item The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
+		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
+		\item $c\gets0$
+		\item $y\gets\bot$
+		\item For $i$ from $1$ to $N$:
+		\begin{enumerate}
+			\item If the $i$-th register is for checking:
+			\begin{enumerate}
+				\item The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
+				\item If the test passes, increment counter $c$.
+			\end{enumerate}
+			\item If the register is for outputting:
+			\begin{enumerate}
+				\item The verifier measures the copy in standard basis
+				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then set $y$ as the measurement result of the data register.
+			\end{enumerate}
+			\item Otherwise, just measure the entire register in standard basis and discard it.
+		\end{enumerate}
+		\item If $\frac{c}{n}\geq\frac{1}{2}-\varepsilon$:
+		\begin{enumerate}
+			\item If $y\ne\bot$ then output $y$
+			\item Otherwise, reject.
+		\end{enumerate}
+		\item Otherwise, reject.
+	\end{enumerate}
+\end{protocol}
 

### 2020-02-02 qpip.tex
Make editorial changes

@@
 	\label{ProtoQPIP1}
-	Let $\varepsilon=T^{-c}$. \Ethan{Try setting up this $\varepsilon$ more intuitively}
+	Take $\varepsilon>0$
 	Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
@@
 		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
-		\item $c\gets0$
-		\item $y\gets\bot$
+		\item Set up a counter $c=0$
+		\item Set $y=\bot$
 		\item For $i$ from $1$ to $N$:
@@
 				\item The verifier measures the copy in standard basis
-				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then set $y$ as the measurement result of the data register.
+				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then update $y$ as the measurement result of the data register.
 			\end{enumerate}
@@
     \label{QPIP1thm}
-	For any $L\in\SampBQP$, \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} is a protocol for $L$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
+	For any $L\in\SampBQP$, \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} is a protocol for $L$ with negligible completeness.
+$\forall c\in\bbN$, it achieves soundness $(\varepsilon, \varepsilon)$ where $\varepsilon=T^{-c}$.
 Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.

### 2020-02-05 bqp.tex
Specify dependence on security param
Make editorial changes

@@
-\section{Constant-Round Blind Delegation for BQP}
+\section{Delegation for BQP}
 \label{sec:BlindBQP}
@@
 	\Ethan{Main theorem of the section}
-	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
+	There exists a constant-round and blind $\QPIP_0$ protocol with a classical client for $\BQP$ with negligible completeness and soundness.
 \end{thm}
@@
 There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
-In fact, they have the same certificate, which we'll call $\ket{\psi_x}$. See the excellent text \cite{kitaev2002classical} for details.
+In fact, they have the same certificate $\ket{\psi_x}$ with some inverse polynomial gap between the completeness and soundness parameters.
+See the excellent text \cite{kitaev2002classical} for details.
 According to \cite{PhysRevA.93.022326}, the certificate can be check using only $X$ and $Z$ measurements.
-We'll also summarize said proofs in \cref{sec:Hamiltonian} for our $\SampBQP$ construction.
+We'll also summarize said proofs in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.
 
@@
 		\item The verifier sends $x$ to the prover
-		\item The prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
+		\item The honest prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
 		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
@@
 \begin{thm}
-	\protoref{BlindBQP} has negligible completeness
+	\protoref{BlindBQP} has negligible completeness in both $T$ and $\lambda$
 \end{thm}
@@
 \begin{thm}
-	\protoref{BlindBQP} has negligible soundness
+	\protoref{BlindBQP} has negligible soundness in both $T$ and $\lambda$
 \end{thm}
@@
 
-\floatname{algorithm}{Algorithm}
+\begin{rmk}
+	The same construction works for $\FBQP$ too. \Ethan{maybe say more?}
+\end{rmk}

### 2020-02-05 preliminaries.tex
Make editorial changes

--- 2020-02-01 preliminaries.tex
@@
 \begin{definition}
-	A sampling problem $S=(D_x)$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms \hannote{ protocols?} $(\bbP, \bbV)$ with the following properties with input $x$:
+	A sampling problem $S=(D_x)$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a protocol $(\bbP, \bbV)$ with the following properties with input $x$:
 	\begin{itemize}
@@
 The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
-		 \item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially\hannote{poly in what} many bits to either direction. 
-		 \item The protocol\hannote{?} is run by steps.
-At any given step, either the verifier or the prover performs computations on their registers and send bits and qubits through the relevant channels to the other party.	\hannote{redundant?}
+		\item There is also a classical communication channel between the prover and the verifier, which can transmit $\poly(\abs{x})$ many bits to either direction. 
 		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
@@
 	\begin{itemize}
-		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
-		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
-		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
-		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
+		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
+		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
+		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
+		\item $\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
 	\end{itemize}
@@
 
-Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.
+$\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
+$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
+where $f$ is specified by a circuit of depth at most $L$.
 
-$\mathsf{HE}$ also satisfies, with all but negligible probability in $\lambda$, that
-$$\mathsf{HE.Dec}_{sk}(\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
+\Ethan{To be pedantic, the above doesn't imply Dec undoes Enc even if we sub in $f=\id$.}
 
@@
 	where $(pk, evk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
-	\Ethan{Urmila didn't specify quantum adversary here? Also dropped the $1^L$.}
 \end{dfn}
 
-The constructions in \cite{mahadev_qfhe}, $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$, has the following extra properties:
+Now we present the quantum homomorphic encryption scheme in \cite{mahadev_qfhe}.
+It admits a classical client; one could do the encryption classically, and the decryption is compatible with $X$ and $Z$ measurements.
+In general, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then it can be used as a compiler to achieve blindness.
+
+\begin{thm}
+	\label{decodeMeasureOrder}
+	There exists a QFHE $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ with the following extra properties:
 	\begin{itemize}
@@
 		\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
+		\item \Ethan{I think this point is obvious?} Let $\Lambda$ be a product of $X$ and $Z$ measurements.
+Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
+			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
 	\end{itemize}
-
-Furthermore, one could either decode or measure first, in the following sense:
-\begin{lemma}
-	\label{decodeMeasureOrder}
-	Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
-		$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
-\end{lemma}
-To the knowledgable reader, this is done simply by storing the so-called quantum-capable ciphertext also as qubits.
+\end{thm}
 

### 2020-02-05 hamiltonian.tex
Change thm env

@@
 \hannote{citation}
-\begin{theorem}
+\begin{thm}
 	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to another circuit $C'$ and classical input $x'$, where $C'$ contains only Hadamard and Toffoli gates.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 	Let $C$ be a circuit consisting of $T$ Hadamard or Toffoli gates. For any input string $x$,  there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
@@
 	Furthermore, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 	Given a circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x$, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
-\end{theorem}
+\end{thm}
 \fi
 
-\begin{theorem}
+\begin{thm}
 	Given circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
@@
 Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 	Let $C$ be a circuit that:
@@
 	\end{itemize}
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 	Let $C=U_T\ldots U_1$ be a circuit consisting of Hadamard and Toffoli gates, and let $x\in\set{0, 1}^n$.
@@
 
-\begin{theorem}\label{ThmXZCheck}
+\begin{thm}\label{ThmXZCheck}
 	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
 	Then \autoref{AlgGroundStateCheck} accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
-\end{theorem}
+\end{thm}
 \begin{proof}

### 2020-02-05 qpip0.tex
Updates from Overleaf

--- 2020-01-23 qpip0.tex
@@
 
-\subsection{Subprotocol for Quantum Measurements}
+%Subprotocol for Quantum Measurements
+\subsection{$\QPIP_0$ for BQP?}
 \hannote{Ethan old description before parallel rep.}
@@
 
-\subsection{Parallel Repetition of the Measurement Subprotocol}
+\subsection{Mahadev's classical "commitment" of $XZ$ measurement}
+
+In her groundbreaking work, Mahadev~\cite{mahadev_delegation} gave the following 4-round interactive protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine.
+
+\begin{protocol}{Mahadev's 4 round commitment}
+\label{proto:urmila4}
+\begin{enumerate}
+    \item Verifier $\bbV$ is a classical machine. Prover $\bbP$ is a $\BQP$ machine. 
+%    \item Both the verifier and the prover know a $\BQP$ circuit $C$ and an input string $x$.
+    \item Both party know the number of qubits $n$ and a security parameter $\lambda=o(n)$.
+    \item Verifier has a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit.
+If $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.
+    \item In the first round, the verifier generate a secret key and  public key pair $(sk,pk)$ from $h$ and $\lambda$ and sent $pk$ to the prover.
+    \item In the second round, the prover pick some $n$-qubit quantum state $\rho$ and generate a "commitment" $y$ from $pk$ and $\rho$.
+He send $y$ to the verifier and keep the leftover quantum state $\sigma$.
+    \item In the third round, the verifier send a uniformly random challenge bit $c\in \{0,1\}$. The prover needs to do a "Testing round" if $c=0$. The prover needs to do a "Hadamard round" if $c=1$.
+    \item In the fourth round. The prover generates a classical string $a$ from $c$ and $\sigma$ and send to back to the prover.
+    \item If $c=0$, the verifier decides whether he is going to reject from $(pk,a,y)$. If $c=1$ the verifier computes an $n$-bit string $z$ from $(sk,h,y,a)$.
+\end{enumerate}
+\end{protocol}
+
+\begin{lemma}[binding property of  Protocol~\ref{proto:urmila4}\cite{mahadev_delegation}]
+If a prover's strategy result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
+\end{lemma}
+
+\begin{rmk}
+Note that even a honest prover has complete freedom in choosing $\rho$, so protocol~\ref{proto:urmila4} didn't make the prover commit to a particular state.
+What it actually does is let the prover commit to a particular $XZ$ measurement on $\rho$.
+This is good enough for our application, since we will feed the $XZ$ measurement results into the verification of $\QPIP_1$ protocol to ensure that the prover pick the history state as $\rho$.
+\end{rmk}
+
+\subsection{$\QPIP_0$ protocol for $\SampBQP$}
+%Parallel Repetition of the Measurement Subprotocol
+
+The following protocol is a $\QPIP_0$ protocol for $\SampBQP$
+
+$\forall c\in\bbN$ Soundness = $O(T^{-c})$
+
+Given inverse poly p(T), we can parameterize the protocol to have soundness p(T)
+
+%	\label{ProtoQPIP1}
+
+\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
+\label{proto:QPIP0samp}
+\begin{enumerate}
+%    \item Verifier start with description of quantum circuit $C$, input string $x$ 
+    \item Both verifier and prover start with the description of number of qubits $n$, quantum circuit $C$, input string $x$, and  a soundness parameter $\varepsilon$.
+    \item Run $N=O(1/\varepsilon)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications.
+On the second round, for each copy, the prover choose the state specified by Protocol~\ref{ProtoQPIP1} as $\rho$.
+On the third round, the verifier uniformly randomly pick an $i\in [N]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies.
+    \item \label{step:multi-testing}Verifier rejects if the results on any of the test rounds is wrong. 
+    \item Verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
+\end{enumerate}
+\end{protocol}
+
+\begin{theorem}\label{thm:urmila-binding}
+    Protocol~\ref{proto:QPIP0samp} is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and $\eps$ computational soundness error\hannote{definition}. 
+\end{theorem}
+
+\begin{proof}
+
+ [[partition lemma -> Parallel repetition]], except for probability $\eps$, either the verifier reject at step~\ref{step:multi-testing} or $z$ has binding property of Theorem~\ref{thm:urmila-binding}.
+
+\end{proof}
+===========
 

### 2020-02-05 preliminaries.tex
Change thm env
Use right env for def proto ind-cpa

@@
 \hannote{original text?}
-\begin{theorem}
+\begin{thm}
 	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$.
@@
 	$$\lambda(H_1+JH_2)\geq\lambda(H_1\big|_K)-\frac{1}{8}$$
-\end{theorem}
+\end{thm}
 
@@
 There are many formulations of quantum de Finetti theorems. We use the one from \cite{Brandão2017} because we need logarithmic dependence on $|A|$.
-\begin{theorem}
+\begin{thm}
 	\label{deFinetti}
@@
 	$$\max_{\Lambda_1,\ldots,\Lambda_l}\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
-\end{theorem}
+\end{thm}
 
@@
 		\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
-		\item \Ethan{I think this point is obvious?} Let $\Lambda$ be a product of $X$ and $Z$ measurements.
+		\item \Ethan{Is this obvious from the construction or do we need proof here?} Let $\Lambda$ be a product of $X$ and $Z$ measurements.
 Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
@@
 
-\floatname{algorithm}{Protocol}
-\begin{algorithm}
-	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
+\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
 	\label{ProtoIndCPA}
-	\begin{algorithmic}[1]
-		\State The challenge picks $b\in\set{0,1}$ at random
-		\If{$b=1$}
-			\State The challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
-		\Else
-			\State The challenger runs the protocol with the adversary, acting as the verifier with input $x$
-		\EndIf
-		\State $\cA$ attempts to guess $b$
-	\end{algorithmic}
-\end{algorithm}
-\floatname{algorithm}{Algorithm}
+	\begin{enumerate}
+		\item The challenge picks $b\in\set{0,1}$ at random
+		\item If $b=0$, the challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
+		\item Otherwise, the challenger runs the protocol with the adversary, acting as the verifier with input $x$
+		\item $\cA$ attempts to guess $b$
+	\end{enumerate}
+\end{protocol}

### 2020-02-05 preliminaries.tex
Add original proj lemma

@@
 
-We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which projects the ground state of the Hamiltonian $H_1$ to the ground space of a Hamiltonian $H_2$ with a large gap.
+We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which relates the ground state of Hamiltonians $H_1 + H_2$ with the ground state of $H_1\big|_{\ker H_2}$.
 
-\hannote{original text?}
 \begin{thm}
-	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$.
-	$$\exists J=\frac{\poly(\norm{H_1})}{\lambda(H_2|_{K^\bot})}$$
-	$$\lambda(H_1+JH_2)\geq\lambda(H_1\big|_K)-\frac{1}{8}$$
+	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on some Hilbert space $\cH=\cS+\cS^\bot$.
+	The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
+	$$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}^2}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
+\end{thm}
+
+We will instead use the following formulation, which can be obtained by relabeling variables from above.
+
+\begin{thm}
+	\label{thm:projection}
+	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$. Then,
+	$$\exists J=\frac{\poly(\norm{H_1})}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
+	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
 \end{thm}
@@
 
-We also use the quantum full homomorphic encryption (QFHE) scheme given in \cite{mahadev_qfhe} which allows the use of a classical client.
+We also use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
 
 \begin{dfn}
-	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
+	A leveled homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
 	\begin{itemize}
@@
 		\item \Ethan{Is this obvious from the construction or do we need proof here?} Let $\Lambda$ be a product of $X$ and $Z$ measurements.
-Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
+Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ so that
 			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
@@
 	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
-	Then it is IND-CPA secure if $\forall x\in\set{0,1}^n$ no polynomial time adversary $\cA$ can win \myprotoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$
+	Then it is IND-CPA secure if $\forall x\in\set{0,1}^n$ no polynomial time adversary $\cA$ can win \protoref{indcpa} with probability better than $\frac{1}{2}+\negl(\lambda)$
 \end{dfn}
@@
 \begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
-	\label{ProtoIndCPA}
+	\label{proto:indcpa}
 	\begin{enumerate}

### 2020-02-05 preliminaries.tex
properly introduce proj lemma

@@
 
-We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which relates the ground state of Hamiltonians $H_1 + H_2$ with the ground state of $H_1\big|_{\ker H_2}$.
+We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which states the condition under which one can estimate the ground state energy of $H_1 + H_2$ with that of $H_1\big|_{\ker H_2}$.
 

### 2020-02-05 preliminaries.tex
Move dfn proto IND-CPA

--- 2020-02-05 preliminaries.tex
@@
 
+\subsection{Semantic security for interactive protocols}
+
+We present the security definition for interactive protocols:
+
+\begin{dfn}
+	Let $\lambda$ be a security parameter.
+	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
+	Then it is IND-CPA secure if $\forall x\in\set{0,1}^n$ no polynomial time adversary $\cA$ can win \protoref{indcpa} with probability better than $\frac{1}{2}+\negl(\lambda)$
+\end{dfn}
+
+\begin{protocol}{Attack against semantic security}
+	\label{proto:indcpa}
+	\begin{enumerate}
+		\item The challenge picks $b\in\set{0,1}$ at random
+		\item If $b=0$, the challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
+		\item Otherwise, the challenger runs the protocol with the adversary, acting as the verifier with input $x$
+		\item $\cA$ attempts to guess $b$
+	\end{enumerate}
+\end{protocol}
+
 \subsection{Projection Lemma}
 
-We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which relates the ground state of Hamiltonians $H_1 + H_2$ with the ground state of $H_1\big|_{\ker H_2}$.
+We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which describes the conditions under which we can estimate the ground state energy of $H_1 + H_2$ with that of $H_1\big|_{\ker H_2}$.
 
@@
 
-We also use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
+We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
+We start by presenting the interface of a homomorphic encryption scheme:
 
@@
 
-Now we present the quantum homomorphic encryption scheme in \cite{mahadev_qfhe}.
-It admits a classical client; one could do the encryption classically, and the decryption is compatible with $X$ and $Z$ measurements.
-In general, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then it can be used as a compiler to achieve blindness.
+The quantum homomorphic encryption scheme in \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients as below:
 
@@
 
-\subsection{Security definition for interactive protocols}
-
-\begin{dfn}
-	Let $\lambda$ be a security parameter.
-	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
-	Then it is IND-CPA secure if $\forall x\in\set{0,1}^n$ no polynomial time adversary $\cA$ can win \protoref{indcpa} with probability better than $\frac{1}{2}+\negl(\lambda)$
-\end{dfn}
-
-\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
-	\label{proto:indcpa}
-	\begin{enumerate}
-		\item The challenge picks $b\in\set{0,1}$ at random
-		\item If $b=0$, the challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
-		\item Otherwise, the challenger runs the protocol with the adversary, acting as the verifier with input $x$
-		\item $\cA$ attempts to guess $b$
-	\end{enumerate}
-\end{protocol}
+As we will see, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then $\mathsf{QHE}$ can be used as a compiler to achieve blindness.

### 2020-02-05 bqp.tex
Break nested lemma/proof

@@
 \begin{thm}
-	\Ethan{Main theorem of the section}
 	There exists a constant-round and blind $\QPIP_0$ protocol with a classical client for $\BQP$ with negligible completeness and soundness.
@@
 
-We'll construct this protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
+We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
 
@@
 \begin{rmk}
-	The same construction works for $\FBQP$ too. \Ethan{maybe say more?}
+	The same construction works for $\FBQP$ too.
+	\Ethan{Maybe say more? Where should I define $\FBQP$?}
 \end{rmk}

### 2020-02-05 hamiltonian.tex
Break nested lemma/proof

@@
 
-\subsection{Reducing quantum circuit to  local Hamiltonian }
+\subsection{Reducing quantum circuit to local Hamiltonian}
 
@@
 
-	To properly combine the three Hamiltonians defined, we consider the kernels of the Hamiltonians we defined.
+	To properly combine the three Hamiltonians defined and analyze it using the projection lemma (\cref{thm:projection}), we consider the kernels of the Hamiltonians we defined.
 	$$K_{clock}=\ker H_{clock}$$
@@
 	$$K_{prop}=\ker H_{prop}$$
-	It is clear that $K_{clock}$ consists of the states with time registers of the form $\ket{\hat{t}}$.
 
-	\begin{lemma} \hannote{throw outside? or just merge}
-		$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
-	\end{lemma}
+	Clearly,
+	$$K_{clock}=\set{\sum_{t=1}^T \ket{\phi_t}\otimes\ket{\hat{t}}:\ket{\phi_t}\in\cB^{\otimes n}}$$
+	Let $\ket\phi\in K_{clock}\cap K_{prop}$.
+	Consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$.
+	As $\ket\phi\in K_{prop}$, we can then do induction using $\widetilde{t}$ as base case to get the relations between the $\ket{\phi_t}$s and conclude that $\ket\phi$ must have the form:
+	$$\ket\phi=\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}$$
+	$$\Rightarrow K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
 
-	\begin{proof}
-		Let $\ket\phi\in K_{clock}\cap K_{prop}$.
-As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations.
-Now consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$.
-As $\ket\phi\in K_{prop}$, we can then say that $\bra{\widetilde{t+1}}\ket\phi=\bra{\widetilde{t}}U_{t+1}\ket\phi$ for $t\ne T$, and $\bra{\widetilde{t}}\ket\phi=U_t\bra{\widetilde{t-1}}\ket\phi$ for $t\ne0$.
-So we can obtain the required statement by induction.
-	\end{proof}
-
-	\begin{corollary}
-		$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$
-	\end{corollary}
+	As a direct result, we get
+	$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$$
 

### 2020-02-05 bqp.tex
Editorial and macros change

@@
 Now we compile \cref{proto:BQP} using $\mathsf{QHE}$ in order to achieve blindness.
-We denote the honest prover's action in $\cref{proto:BQP}$ as $\cF$; that is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.
+We denote the honest prover's action in \cref{proto:BQP} as $\cF$; that is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.
 
@@
 		\item The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
-		\item The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates \Ethan{Not sure if rigorous enough}
+		\item The verifier measures the incoming ciphertext according to \cref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates \Ethan{Not sure if rigorous enough}
 		\item The verifier decodes the measurement results

### 2020-02-05 hamiltonian.tex
Editorial and macros change

@@
 \Ethan{Adiabatic and spectral gap ref = \cite{adiabatic}}
-
-%Here we lay our theoretical foundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper.
-\hannote{?} Here we'll only state the theorems, and prove them later in the subsections.
 
@@
 
-%We want to define and construct an instance of Local Hamiltonian that encodes the history of the computation.
-
  We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$.% and define the following that implicitly depends on $L$.
@@
 \end{definition}
-
-%We fix $L=5$ for this paper.For any $L\in\bbN$,
 
@@
 \end{thm}
-
-\iffalse
-\begin{definition}
-	We call the first registers of $\ket{\psi_{C(x)}}$ the data register, and the later registers of $\psi_{C(x)}$ the time register.
-\end{definition}
-
-\begin{thm}
-	Given a circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x$, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
-\end{thm}
-\fi
 
@@
 Because of this result, we cam assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates.
-
- %After this subsection, we'll be able to assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates.
-%After doing that, we make a further observation that we'll use later.
 
@@
 
-%Now we put the above results in term of measurement outputs.\hannote{???}
-
 We present an algorithm that checks whether a given state is the ground state of some fixed $H_{C(x)}$ following~\cite{PhysRevA.93.022326}.

### 2020-02-05 hamiltonian.tex
Make editorial changes and add TODO on writing

@@
 
-In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian problem. \hannote{put proofs back. Adiabatic ref?}
+In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian problem.
 
-\Ethan{Adiabatic and spectral gap ref = \cite{adiabatic}}
+\Ethan{TODO Give a bit of overview on what is this (I.e. QMA-completeness and whatnot)}
 
-First note that $\set{H, T}$ is a universal gate set.
+This section will mostly be a summarization of known results related to adiabatic quantum computation found in sources such as \cite{adiabatic}.
+\Ethan{This source was given to us by Yu-Ching; I haven't read it}
 
-\hannote{citation}
-\begin{thm}
-	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to another circuit $C'$ and classical input $x'$, where $C'$ contains only Hadamard and Toffoli gates.
-\end{thm}
+\Ethan{TODO Say something about wanting to do more with $\QMA$ certificates than just check yes/no-instances}
 
- We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$.% and define the following that implicitly depends on $L$.
+Recall the following form that $\QMA$ certificates take:
 
-\begin{definition}
+\begin{dfn}
+	\label{dfn:groundstate}	
+	Let $C=U_T\ldots U_1$ be a quantum circuit consisting of $T$ gates, and let $x\in\set{0,1}^n$. Then we denote
+	$$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$$
+	We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
+\end{dfn}
+
+\begin{rmk}
+	\label{idpadding}
+	One can first pad $C$ with identity gates at the end, doubling its number of gates and obtaining another circuit $C'$.
+	Then by measuring the time register of $\ket{\psi_{C'(x)}}$ one obtains with probability $\frac{1}{2}$ the state $C(x)$.
+\end{rmk}
+
+\Ethan{Now say something about QMA here...}
+
+We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$. \Ethan{mention it's the basis for 5-local Hamiltonians?}
+
+\begin{dfn}
 	$$\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \abs{\set{i: U_i\ne I}}\leq 5}$$
-\end{definition}
-
-\hannote{something?}
+\end{dfn}
 
 \begin{thm}
-	Let $C$ be a circuit consisting of $T$ Hadamard or Toffoli gates. For any input string $x$,  there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
+	Let $C$ be a circuit of size $T$. For any input string $x$,  there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
 	\begin{itemize}
 		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
-		\item $H_{C(x)}$ has a unique ground state  $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
-We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
+		\item $H_{C(x)}$ has $\ket{\psi_{C(x)}}$ as the unique ground state with eigenvalue $0$.
 		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
+		\item Its descriptions can be constructed by a $\BPP$ machine in polynomial time.
 	\end{itemize}
-
-	Furthermore, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
 \end{thm}
@@
 \begin{thm}
-	Given circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
+	Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
 In particular, it accepts the $\ket{psi_{C(x)}}$ with probability $\fot$.
@@
 \end{thm}
-
-Lastly, before we present proofs for the above theorems, we make an observation.
-
-\begin{observation}
-	\label{idpadding}
-	Given a circuit $C$ and an input string $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtaining another circuit $C'$.
-One can then measure the time register of $\ket{\psi_{C'(x)}}$ and obtain with probability $\frac{1}{2}$ the state $C(x)$.
-\end{observation}
 
@@
 Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
-Because of this result, we cam assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates.
+Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
 
@@
 	\begin{itemize}
-		\item consists of either $H$ or $\Lambda(P(i))$, and the number of gates is $T$.\hannote{confusing?}
+		\item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
 		\item uses $n$ qubits
@@
 \begin{proof}
-	We need to ensure the excited states of $H_{C(x)}$ have high eigenvalues.
-The base construction comes from \cite{kitaev2002classical}.
-The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.
+	The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.
 
 	Let $x_i$ denote the $i$-th bit of $x$, and let $n$ be the number of qubits in $C$.
+
+	We need to ensure the excited states of $H_{C(x)}$ have high eigenvalues.
 
@@
 
-	Next, we check that $H_{prop}\geq0$ by the following transform.
+	We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least nonzero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
 
-	$$W=\sum_{j=0}^L U_j\ldots U_1\otimes\ket{j}\bra{j}$$
-	$$W^\dagger\phi=\sum_{t=0}^T\ket{x}\otimes\ket{\hat{t}}$$
-	$$W^\dagger H_{prop} W=
-	\begin{pmatrix}
-		\frac{1}{2} & -\frac{1}{2} & & & &  \\
-		-\frac{1}{2} & 1 & -\frac{1}{2} & & & \\
-		& -\frac{1}{2} & 1 & \ddots & & \\
-		& & \ddots & \ddots & -\frac{1}{2} & \\
-		& & & -\frac{1}{2} & 1 & -\frac{1}{2} \\
-		& & & & -\frac{1}{2} & \frac{1}{2}
-	\end{pmatrix}$$
-
-	According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks.
-Furthermore, the last nonzero eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.
-
-	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$.
-Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli.
-Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$.
-$\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
+	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since our gates are either Hadamard or Toffoli.
+	Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
 	$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$

### 2020-02-05 preliminaries.tex
Make editorial changes and add TODO on writing

@@
 		\item \Ethan{Is this obvious from the construction or do we need proof here?} Let $\Lambda$ be a product of $X$ and $Z$ measurements.
-Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ so that
+Then there exists product of $X$ and $Z$ measurements $\Lambda'$ and $\BPP$ algorithm $\widehat{\mathsf{QHE.Dec}}$ such that
 			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$

### 2020-02-05 blind.tex
Update sec 6 title
Make editorial pass

@@
-\section{Constant-Round, Blind, and Verifiable Delegation}
+\section{Constant-Round and Blind $\QPIP_1$ protocol for $\SampBQP$}
 
@@
 
-Now we compile our $\QPIP_1$ protocol \myprotoref{protoQPIP1} using the quantum homomorphic encryption $\mathsf{QHE}$ \Ethan{TODO maybe wrap this as a def} in a similar way as what we did for our blind $\BQP$ delegation protocol in \cref{sec:BlindQBP}
+Now we compile our $\QPIP_1$ protocol (\cref{ProtoQPIP1}) using the quantum homomorphic encryption $\mathsf{QHE}$ from \cref{decodeMeasureOrder} in the same way as what we did for our blind $\BQP$ delegation protocol (\cref{proto:BlindBQP}) in \cref{sec:BlindBQP}.
 
-The construction is obvious, \Ethan{Maybe still write it out...? Or maybe not?} so we directly go into analysis. \Ethan{Need to remember security param if we write this out}
+\begin{protocol}{\cref{ProtoQPIP1} compiled using \cref{decodeMeasureOrder}}
+	\label{proto:QPIP1Samp}
+	\begin{enumerate}
+		\item The verifier runs $\mathsf{QHE.keygen}(1^\lambda, 1^L)$ where $L$ is the depth of circuit corresponding to the honest prover's action in \cref{ProtoQPIP1}
+		\item The verifier encrypts its input and runs \cref{ProtoQPIP1} with the prover homomorphically
+		\item The verifier measures the incoming ciphertext according to \cref{decodeMeasureOrder}
+		\item The verifier decodes the measurement results to get its output
+	\end{enumerate}
+\end{protocol}
 
 \begin{thm}
-	Compiling \cref{proto:QPIP0samp} using $\mathsf{QHE}$ preserves its completeness and soundness.
+	\cref{proto:QPIP1Samp} has the same completeness and soundness guarantees as \cref{ProtoQPIP1}
 \end{thm}
@@
 \begin{thm}
-	\myprotoref{ProtoPriv} is IND-CPA secure.
+	\cref{proto:QPIP1Samp} is IND-CPA secure.
 \end{thm}
 \begin{proof}
-	The verifier's first message is encrypted into $\tilde{x}$ in an IND-CPA way as a ciphertext.
-	The verifier's second message is the basis choice of Hadamard or test rounds, which can be done using public coins.
-
-	The verifier only sends the prover these two messages, so it follows \Ethan{hopefully?} easily that the protocol itself is also IND-CPA. \Ethan{Maybe not rigorous enough?}
+	\Ethan{TODO after nailing down protocol}
 \end{proof}

### 2020-02-05 hamiltonian.tex
Make editorial pass

@@
 
-In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian problem.
+In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian instance.
 
-\Ethan{TODO Give a bit of overview on what is this (I.e. QMA-completeness and whatnot)}
+The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
+Protocols to delegate $\BQP$ computations such as \cite{mahadev_delegation} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
+We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.
+Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
+\Ethan{This source was given to us by Yu-Ching; I haven't read it.
+Also I probably should cite more sources here.}
 
-This section will mostly be a summarization of known results related to adiabatic quantum computation found in sources such as \cite{adiabatic}.
-\Ethan{This source was given to us by Yu-Ching; I haven't read it}
-
-\Ethan{TODO Say something about wanting to do more with $\QMA$ certificates than just check yes/no-instances}
-
-Recall the following form that $\QMA$ certificates take:
+We begin by recalling the form that local Hamiltonian certificates:
 
@@
 
-\Ethan{Now say something about QMA here...}
-
-We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$. \Ethan{mention it's the basis for 5-local Hamiltonians?}
-
+We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$ as below; note that this spans a subspace of $5$-local Hamiltonians.
 \begin{dfn}
@@
 
+Now we state the main theorems that we'll work towards in this section.
+The first one is the reduction from $\SampBQP$ to a local Hamiltonian instance, with some additional properties that will be convenient for us:
 \begin{thm}
+	\label{thm:LHReduction}
 	Let $C$ be a circuit of size $T$. For any input string $x$, there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
@@
 
+The second one is a way to verify ground states of local Hamiltonians, again with some extra properties:
 \begin{thm}
-	Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
-In particular, it accepts the $\ket{psi_{C(x)}}$ with probability $\fot$.
-Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
+	\label{ThmXZCheck}
+	Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists a $\BQP$ algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
+(In particular, it accepts the $\ket{\psi_{C(x)}}$ with probability $\fot$.) Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
 \end{thm}
@@
 
-\hannote{throw this into appendix?}
 Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
 Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
+Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
+\begin{thm}
+	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
+\end{thm}
+\begin{proof}
+	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
+	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
+	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
+\end{proof}
 
-\hannote{theorem?} We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
-$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
-	$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-
-Now we present the construction from \cite{quant-ph/0301040}.
-
+Now we present the proof that $\set{H, \Lambda^2(X)}$ is indeed a universal gate set from \cite{quant-ph/0301040}: \Ethan{This definitely belongs in the appendix instead...}
 \begin{thm}
@@
 \end{thm}
+\begin{proof}
+	We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
+	$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
+		$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
 
-\begin{proof}
-	Consider the transform on quantum states
+	Now consider the transform on quantum states
 	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
@@
 
-Note that our new gate set can be written as linear combinations of $X$ and $Z$ matrices.
-
-\begin{thm}
-	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
-\end{thm}
-
-\begin{proof}
-	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
-	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
-	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
-\end{proof}
-
 \subsection{Reducing quantum circuit to local Hamiltonian}
 
-In this section, we show how to reduce a $\SampBQP$ circuit to a local-$XZ$-Hamiltonian.
+In this subsection, we prove \cref{thm:LHReduction} by showing how to reduce a $\SampBQP$ circuit to a local-$XZ$-Hamiltonian.
 
-\begin{thm}
-	Let $C=U_T\ldots U_1$ be a circuit consisting of Hadamard and Toffoli gates, and let $x\in\set{0, 1}^n$.
-Then there exists a $\BPP$  machine which generates the  description of a $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
-	\begin{itemize}
-		\item its unique ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
-		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
-		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
-		\item $H_{C(x)}$ has $O(T)$ nonzero terms whose coefficients are  at most $O(T^3)$.
-	\end{itemize}
-\end{thm}
-
-\begin{proof}
 	The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.
@@
 So we set $H_{C(x)}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
-\end{proof}
 
@@
 
-We present an algorithm that checks whether a given state is the ground state of some fixed $H_{C(x)}$ following~\cite{PhysRevA.93.022326}.
+In this subsection, we prove \cref{ThmXZCheck}.
+That is, we present and analyze an algorithm that checks whether a given state is the ground state of some fixed $H_{C(x)}$, following~\cite{PhysRevA.93.022326}.
 
@@
 		Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
-		Let $\ket\phi$ be the potential ground state to check
+		Let $\ket\phi$ be the potential ground state to check.
 		\begin{itemize}
@@
 
-\begin{thm}\label{ThmXZCheck}
-	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
-	Then \autoref{AlgGroundStateCheck} accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
+\begin{thm}
+	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients at most $O(\poly(T))$.
+	Then \cref{AlgGroundStateCheck} accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
 \end{thm}
 \begin{proof}
-
 	Here we follow \cite{PhysRevA.93.022326}.
@@
 	\end{align*}
-
 \end{proof}

### 2020-02-05 bqp.tex
Make editorial changes and add more TODOs

@@
 \begin{thm}
-	\protoref{BlindBQP} is IND-CPA
+	\protoref{BlindBQP} is IND-CPA secure.
 \end{thm}
@@
 	\begin{itemize}
-		\item classical inputs
-		\item client uses only X/Z measurements
-		\item negl. completeness and soundness
+		\item client's inputs are classical
+		\item client doesn't applies any quantum gates, and uses only $X$ and $Z$ measurements
+		\item completeness and soundness parameters are both negligible
 	\end{itemize}
-	and outputs a corresponding $\QPIP_0$ protocol with negl. completeness and soundness \Ethan{same inputs...?}
+	and outputs a corresponding $\QPIP_0$ protocol with negligible completeness and soundness.
 \end{thm}
@@
 	The same construction works for $\FBQP$ too.
-	\Ethan{Maybe say more? Where should I define $\FBQP$?}
+	\Ethan{Need to say more about amplification and doing this bit-by-bit. Also, where should I define $\FBQP$?}
 \end{rmk}

### 2020-02-05 qpip.tex
Change thm env
Make editorial changes and add TODO on writing
Fix proto Samp QPIP1 formatting

@@
 \section{Delegation Protocol for Hybrid Client}
-
-\Ethan{Remark on amplification and doing this qubit-by-qubit by last section. Do some general story-telling.}
 
@@
 	\label{ProtoQPIP1}
-	Take $\varepsilon>0$
-	Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
-	Let $n$ be large enough so both $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ and $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ are negligible in $\varepsilon$ by Chernoff bound
-	Let $N$ be large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
+	\begin{itemize}
+		\item Let $\varepsilon>0$
+		\item Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
+		\item Let $n$ be large enough so both
+			$$P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$$
+			and
+			$$P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$$ are negligible in $\varepsilon$ by Chernoff bound
+		\item Let $N$ be large enough so that $$\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$$
+			where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$
+	\end{itemize}
 	\begin{enumerate}
@@
 		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
-		\item Set up a counter $c=0$
+		\item Set counter $c=0$
 		\item Set $y=\bot$
@@
 
-\begin{theorem}
+\begin{thm}
     \label{QPIP1thm}
@@
 Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
-\end{theorem}
+\end{thm}
 \begin{proof}

### 2020-02-05 blind.tex
Fill in a TODO
Remove old and misleading paragraph

@@
 \section{Constant-Round and Blind $\QPIP_1$ protocol for $\SampBQP$}
-
-We now present a constant-round, blind, and verifiable delegation scheme for $\SampBQP$ as an application of our $\QPIP_0$ construction for $\SampBQP$,
-which we achieve by using the homomorphic encryption scheme from \cite{mahadev_qfhe} together with our construction.
-
-\subsection{Our Delegation Protocol}
 
@@
 
-\begin{protocol}{\cref{ProtoQPIP1} compiled using \cref{decodeMeasureOrder}}
+\begin{protocol}{Compiling \cref{ProtoQPIP1} using $\mathsf{QHE}$}
 	\label{proto:QPIP1Samp}
@@
 \begin{proof}
-	\Ethan{TODO after nailing down protocol}
+	The only thing the prover gets is $\mathsf{QHE.Enc}_{pk}(x)$, $pk$, and $evk$. So this follows directly from the security of $\mathsf{QHE}$.
 \end{proof}

### 2020-02-06 preliminaries.tex
Make editorial pass
Make editorial changes and add more TODOs
Add TODO to define complexity classes
Fix missing dfns

@@
 
+\subsection{Relevant complexity classes}
+
+We define a few relevant complexity classes. \Ethan{Do we need to define $\BPP$ and $\BQP$ too?}
+
+\begin{dfn}
+	$\QMA$ is the quantum analogue of the class $\MA$. The verifier in $\QMA$ is now a $\BQP$ machine.
+\end{dfn}
+
+\begin{dfn}
+	$\FBQP$ is the functional analogue of the class $\BQP$.
+That is, every instance corresponds to a string rather than a yes/no bit.
+The error probability is still bounded above away from $\fot$ for some uniform quantum circuit family.
+\end{dfn}
+
 We define a sampling version of $\BQP$, $\SampBQP$, based on \cite{aaronson_2013}.
@@
 \end{definition}
-
-\hannote{sampling generalize decision blah} \Ethan{That doesn't sound right}
 
@@
 
-There are many formulations of quantum de Finetti theorems. We use the one from \cite{Brandão2017} because we need logarithmic dependence on $|A|$.
+De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
+There are many formulations; we use the one from \cite{Brandão2017} because we need logarithmic dependence on $|A|$.
 \begin{thm}
@@
 We start by presenting the interface of a homomorphic encryption scheme:
-
 \begin{dfn}

### 2020-02-06 qpip0.tex

@@
     \item Run $N=O(1/\varepsilon)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications.
-On the second round, for each copy, the prover choose the state specified by Protocol~\ref{ProtoQPIP1} as $\rho$.
+On the second round, for each copy, the prover choose the state specified by Protocol~\ref{ProtoQPIP1}  (with error $\eps$) as $\rho$.
 On the third round, the verifier uniformly randomly pick an $i\in [N]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies.
-    \item \label{step:multi-testing}Verifier rejects if the results on any of the test rounds is wrong. 
-    \item Verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
+    \item \label{step:multi-testing}Verifier rejects if the results on any of the test rounds is rejected. 
+    \item If all testing rounds are accepted, verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
 \end{enumerate}
@@
 
+\begin{definition}[computationally indistinguishable]
+\hannote{move later}
+Let  $D_1$ and $D_2$ be distributions over $n$-bit string.
+We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes a sample from $D_1$ as part of its input.
+\end{definition}
+%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.
+
+\begin{rmk}
+If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
+\end{rmk}
+
 \begin{proof}
 
- [[partition lemma -> Parallel repetition]], except for probability $\eps$, either the verifier reject at step~\ref{step:multi-testing} or $z$ has binding property of Theorem~\ref{thm:urmila-binding}.
+By Lemma~\label{lem:partition}
+
+ [[Partition lemma -> Parallel repetition]], except for probability $\eps$, either the verifier reject at step~\ref{step:multi-testing} or $z$ is $\negl(n)$-computationally indistinguishable to $M_{XZ}(\rho,h)$ by Theorem~\ref{thm:urmila-binding}.
+
+ By theorem~\ref{QPIP1thm}, $M_{XZ}(\rho,h)$  $\eps$-close to $C(x)$.
+Therefore\hannote{?}, $M_{XZ}(\rho,h)$  and  $C(x)$ $z$ are $\eps$-Q-computationally indistinguishable, and thus $z$ and $C(x)$ are  $2\eps$-Q-computationally indistinguishable.
 
@@
 
-\begin{lemma}[Lemma 3.5 of \cite{parallelrep}]\label{lem:partition}
-Let $(U_0,U)$ be any prover's strategy. Let $m=O(\log \secpar)$, $i\in[m]$, 
+\begin{lemma}[Slight adaption from Lemma 3.5 of \cite{parallelrep}]\label{lem:partition}
+Let $(U_0,U)$ be any prover's strategy in Protocol~\ref{proto:QPIP0samp}. Let $m=O(\log \secpar)$, $i\in[m]$, 
 $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\frac{\gamma_0}{T}=1/\poly(\secpar)$.

### 2020-02-06 bqp.tex
Write rmk for FBQP
Add notes from Skype discussion

@@
 \begin{thm}
-	There exists a constant-round and blind $\QPIP_0$ protocol with a classical client for $\BQP$ with negligible completeness and soundness.
+	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
 \end{thm}
@@
 
-Let $L\in\BQP$, and $x\in\set{0,1}^*$.
+Let $L\in\BQP$, and $x\in\set{0,1}^n$.
 
+\Ethan{TODO cite MF instead}
 There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
@@
 
+\Ethan{Consider citing Mahadev protocol 8.3 or theorem 8.4 instead}
+\Ethan{Rewrite according to definition of $\BQP$ and yes/no instances}
 \begin{thm}
-	\protoref{BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
+	\protoref{BQP} is a $\QPIP_1$ protocol for $\BQP$ with negligible completeness and soundness.
 \end{thm}
@@
 		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
+		\Ethan{No need; $\BQP$ is one-sided}
 	\end{enumerate}
@@
 	\protoref{BlindBQP} has negligible completeness in both $T$ and $\lambda$
+	\Ethan{$\lambda$ and $T$ are poly. related, so keep $\lambda$ only.}
 \end{thm}
@@
 Now we can simply apply the following results from \cite{parallelrep} to obtain a blind and constant-round for $\QPIP_0$ with negligible completeness and soundness.
+\Ethan{Drop the theorem and explain in words.
+Mahadev's protocol compiles QPIP1 to QPIP0 but deteriorates soundness, and \cite{parallelrep} says parallel repetition works to recover good soundness guarantees.}
 \begin{thm}
+    \Ethan{TODO Not rigorous enough}
 	There is a compiler that takes a $\QPIP_1$ protocol with the following properties:
@@
 \begin{rmk}
-	The same construction works for $\FBQP$ too.
-	\Ethan{Need to say more about amplification and doing this bit-by-bit. Also, where should I define $\FBQP$?}
+	Everything in this section easily generalizes to $\FBQP$. One simply repeats the process for every output bit.
+	\Ethan{actually need 2 copies per bit now}
 \end{rmk}

### 2020-02-06 bqp.tex
Begin implementing changes from the Skype meeting

--- 2020-02-05 bqp.tex
@@
 
-In this section we present our constant-round blind delegation protocol for $\BQP$.
+In this section we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
+\begin{thm}
+	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
+\end{thm}
+We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
 We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.
 
-\begin{thm}
-	There exists a constant-round and blind $\QPIP_0$ protocol with a classical client for $\BQP$ with negligible completeness and soundness.
-\end{thm}
+Let $L\in\BQP$, and $x\in\set{0,1}^n$.
+We start with an overview of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.
+We'll summarize some more relevant details of this construction in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.
 
-We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
-
-Let $L\in\BQP$, and $x\in\set{0,1}^*$.
-
-There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
-In fact, they have the same certificate $\ket{\psi_x}$ with some inverse polynomial gap between the completeness and soundness parameters.
-See the excellent text \cite{kitaev2002classical} for details.
-According to \cite{PhysRevA.93.022326}, the certificate can be check using only $X$ and $Z$ measurements.
-We'll also summarize said proofs in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.
-
-\begin{thm}
-	\protoref{BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
-\end{thm}
-
-\begin{protocol}{Protocol for $\BQP$}
+\begin{protocol}{Verifying yes-instances for $\BQP$}
 	\label{proto:BQP}
-	Let $n$ be the number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
 	\begin{enumerate}
-		\item The verifier sends $x$ to the prover
-		\item The honest prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
-		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
+		\item The verifier chooses some tensor product of $X$ and $Z$ measurements $\Lambda$
+		\item The prover sends the verifier some state $\rho\in\cB^{\otimes m}$ qubit-by-qubit.
+		\item The verifier measures $\rho$ according to $S$
+		\item The verifier decides whether to accept based on the measurement results.
 	\end{enumerate}
@@
 
+\cref{proto:BQP} has negligible completeness and soundness. \Ethan{Elaborate or no?}
+
 Now we compile \cref{proto:BQP} using $\mathsf{QHE}$ in order to achieve blindness.
-We denote the honest prover's action in \cref{proto:BQP} as $\cF$; that is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.
+We denote the honest prover's action in \cref{proto:BQP} as $\cF$.
 
@@
 	\label{proto:BlindBQP}
-	Let $\lambda$ be the security parameter.
-	Let $L$ be the depth of the circuit corresponding to $\cF$.
-	Let $n$ be number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
+	Let $d$ be the depth of the circuit corresponding to $\cF$.
 	\begin{enumerate}
-		\item The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
-		\item The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
-		\item The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
-		\item The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
-		\item The verifier measures the incoming ciphertext according to \cref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates \Ethan{Not sure if rigorous enough}
-		\item The verifier decodes the measurement results
-		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
+		\item The verifier chooses $\Lambda$ and computes $\Lambda'$ using \cref{decodeMeasureOrder}
+		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
+		\item The verifier computes $c=\mathsf{QHE.Enc}_{pk}(x)$
+		\item The verifier sends $c$ and $evk$ to the prover
+		\item The prover computes $\mathsf{QHE.Eval}(\cF, c)$ and sends it to the verifier qubit-by-qubit.
+		\item The verifier measures the incoming ciphertext according to $\Lambda'$
+		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to the measurement results
+		\item The verifier decides whether to accept based on \cref{proto:BQP}
 	\end{enumerate}
@@
 \begin{thm}
-	\protoref{BlindBQP} has negligible completeness in both $T$ and $\lambda$
+	\cref{proto:BlindBQP} preserves the completeness and soundness of \cref{proto:BQP}
 \end{thm}
 \begin{proof}
-	Based on the correctness of $\mathsf{QHE}$, the verifier would successfully decode $\cF(c)$ with overwhelming probability.
-	The subsequent underlying QMA check also has overwhelming probability of acceptance.
+	Based on the correctness of $\mathsf{QHE}$, any prover strategy in \cref{proto:BlindBQP} has a corresponding strategy in \cref{proto:BQP}.
 \end{proof}
@@
 \begin{thm}
-	\protoref{BlindBQP} has negligible soundness in both $T$ and $\lambda$
+	\cref{proto:BlindBQP} is IND-CPA secure.
 \end{thm}
 \begin{proof}
-	The verifier's actions is equivalent to first decoding the prover's message then measuring it.
-
-	Suppose the prover's message decodes to some $\rho$. Since it is a quantum state, the soundness of the underlying $\QMA$ instance can be used.
-
-	That is, there doesn't exists a valid certificate $\rho$ that has non-negligible probability of acceptance.
+	The only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
 \end{proof}
 
-\begin{thm}
-	\protoref{BlindBQP} is IND-CPA
-\end{thm}
-\begin{proof}
-	The only thing the prover learns is $c$ and $pk$, so this follows directly from $\mathsf{QHE}$'s security.
-\end{proof}
-
-Now we can simply apply the following results from \cite{parallelrep} to obtain a blind and constant-round for $\QPIP_0$ with negligible completeness and soundness.
-\begin{thm}
-	There is a compiler that takes a $\QPIP_1$ protocol with the following properties:
-	\begin{itemize}
-		\item classical inputs
-		\item client uses only X/Z measurements
-		\item negl. completeness and soundness
-	\end{itemize}
-	and outputs a corresponding $\QPIP_0$ protocol with negl. completeness and soundness \Ethan{same inputs...?}
-\end{thm}
+Mahadev's protocol compiles QPIP1 to QPIP0 but deteriorates soundness, and \cite{parallelrep} says parallel repetition works to recover good soundness guarantees.
+\Ethan{TODO elaborate}
 
 \begin{rmk}
-	The same construction works for $\FBQP$ too.
-	\Ethan{Maybe say more? Where should I define $\FBQP$?}
+	Our protocol for $\BQP$ can easily be generalized to $\FBQP$ too in the following way:
+	\Ethan{TODO actually need 2 copies per bit now}
 \end{rmk}

### 2020-02-06 bqp.tex
Work some more on Skype meeting results

@@
 We start with an overview of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.
-We'll summarize some more relevant details of this construction in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.
 
@@
 	\label{proto:BQP}
+	We give only a high-level description here.
 	\begin{enumerate}
@@
 	\end{enumerate}
+	More details are given later in \cref{AlgGroundStateCheck} where we generalize this protocol for $\SampBQP$.
+	\Ethan{TODO clear up details regarding amplification}
 \end{protocol}
@@
 
-Mahadev's protocol compiles QPIP1 to QPIP0 but deteriorates soundness, and \cite{parallelrep} says parallel repetition works to recover good soundness guarantees.
-\Ethan{TODO elaborate}
+Mahadev's protocol compiles $\QPIP_1$ protocols of the form in \cref{proto:BQP} to $\QPIP_0$ but deteriorates soundness.
+Note that \cref{proto:BlindBQP} can also be written in the four-step form, so the compiler can also be applied to it.
+\cite{parallelrep} says parallel repetition works to recover the soundness guarantees.
+
+So we get...
 

### 2020-02-07 bqp.tex
Write protocol for FBQP

--- 2020-02-06 bqp.tex
@@
 \begin{thm}
+	\label{thm:QPIP0BQP}
 	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
@@
 	\label{proto:BQP}
+	We give only a high-level description here.
+	For more details, see \cref{AlgGroundStateCheck} where we generalize this for $\SampBQP$.
 	\begin{enumerate}
@@
 
-\cref{proto:BQP} has negligible completeness and soundness. \Ethan{Elaborate or no?}
-
-Now we compile \cref{proto:BQP} using $\mathsf{QHE}$ in order to achieve blindness.
+Differently from \cref{AlgGroundStateCheck}, \cref{proto:BQP} has negligible completeness and soundness, due to parallel repetition.
 We denote the honest prover's action in \cref{proto:BQP} as $\cF$.
+Now we compile it using $\mathsf{QHE}$ in order to also achieve blindness:
 
@@
 
-Mahadev's protocol compiles QPIP1 to QPIP0 but deteriorates soundness, and \cite{parallelrep} says parallel repetition works to recover good soundness guarantees.
-\Ethan{TODO elaborate}
+\cite{mahadev_delegation} gives a compiler from $\QPIP_1$ protocols of the form in \cref{proto:BQP} to $\QPIP_0$ but deteriorates soundness.
+Note that \cref{proto:BlindBQP} can also be collapsed into the same form, so the same compiler can also be applied to it to obtain a $\QPIP_0$ protocol.
 
-\begin{rmk}
-	Our protocol for $\BQP$ can easily be generalized to $\FBQP$ too in the following way:
-	\Ethan{TODO actually need 2 copies per bit now}
-\end{rmk}
+We can then use results from \cite{parallelrep} to apply parallel repetition and recover the negligible soundness.
+
+Our results for $\BQP$ can also be generalized to $\FBQP$ by applying $2n$ copies of \cref{thm:QPIP0BQP} in parallel.
+
+\begin{protocol}{Blind and verifiable $\QPIP_0$ delegation for $\FBQP$}
+	\label{QPIP0FBQP}
+	Suppose $y\in\set{0,1}^m$ is the output of our $\FBQP$ instance.
+	\begin{enumerate}
+		\item Apply \cref{thm:QPIP0BQP} to every $y_i=0$ and $y_i=1$ case in parallel, resulting in a total of $2m$ cases.
+		\item Output $y$ if for each $i$ precisely one of the $y_i=0$ and $y=i=1$ cases accepts.
+	\end{enumerate}
+\end{protocol}
+
+\Ethan{TODO prove that \cref{QPIP0FBQP} actually works as expected}

### 2020-02-07 qpip0.tex

@@
     \item Both verifier and prover start with the description of number of qubits $n$, quantum circuit $C$, input string $x$, and  a soundness parameter $\varepsilon$.
-    \item Run $N=O(1/\varepsilon)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications.
+    \item Run $m=O(1/\varepsilon)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications.
 On the second round, for each copy, the prover choose the state specified by Protocol~\ref{ProtoQPIP1}  (with error $\eps$) as $\rho$.
-On the third round, the verifier uniformly randomly pick an $i\in [N]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies.
+On the third round, the verifier uniformly randomly pick an $i\in [m]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies.
     \item \label{step:multi-testing}Verifier rejects if the results on any of the test rounds is rejected. 
@@
 
-By Lemma~\label{lem:partition}
+Choose the $T$ in Lemma~\ref{lem:partition} to be $\Theta(m^3)$ \hannote{$\gamma_0$?}. By Property~\ref{partition-property-1} of Lemma~\ref{lem:partition}, 
+$$\forall i, \L(1- 1/m^2\R)\text{fraction of }\gamma$$ 
+satisfies that 
+$$\norm{\ket{\psi_{err}}}^2 \leq 1/m+\negl(n). $$
+Therefore, there exist an $\gamma$ such that 
+$$\forall i,\, \norm{\ket{\psi_{err}}}^2 \leq 1/m+\negl(n). $$
+
+Denote $G_{i,\gamma}$ with  $\gamma$ found above as $G_i$.
 
@@
 \begin{lemma}[Slight adaption from Lemma 3.5 of \cite{parallelrep}]\label{lem:partition}
-Let $(U_0,U)$ be any prover's strategy in Protocol~\ref{proto:QPIP0samp}. Let $m=O(\log \secpar)$, $i\in[m]$, 
+Let $(U_0,U)$ be any prover's strategy in Protocol~\ref{proto:QPIP0samp}.  $i\in[m]$, 
 $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\frac{\gamma_0}{T}=1/\poly(\secpar)$.
@@
 %\item There exist (sub-normalized) states $\ket{\psi_0}_{\regX,\regZ}$ and $\ket{\psi_1}_{\regX,\regZ}$ such that when $G_{i,\gamma}$ runs on input $\ket{\psi}_{\regX,\regZ}$, the output is  $(0,\ket{\psi_0}_{\regX,\regZ}/\|\ket{\psi_0}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_0}_{\regX,\regZ}\|^2$, $(1,\ket{\psi_1}_{\regX,\regZ}/\|\ket{\psi_1}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_1}_{\regX,\regZ}\|^2$, and $\bot$ with probability  $1-\|\ket{\psi_0}_{\regX,\regZ}\|^2- \|\ket{\psi_1}_{\regX,\regZ}\|^2$,
-    \item If we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$, then we have  $E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$.
+    \item \label{partition-property-1} If we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$, then we have  $E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$.
 \item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$.

### 2020-02-07 bqp.tex
Add Skype discussion feedbacks

@@
 \label{sec:BlindBQP}
+
+\Ethan{More feedback notes go here to be implemented later}
+
+\Ethan{Read other papers and see if I can copy their tones and phrasing}
+
+\Ethan{Important lemmas such as 2.4 should be emphasized more and especially this one shouldn't be in prelim.}
+
+\Ethan{2.4 should be a key obsv.}
+
+\Ethan{protocol 2 should say 1 message QPIP1 for BQP}
+
+\Ethan{``choose some tensor"? need distribution info and some basis choice}
+
+\Ethan{Try copying from https://arxiv.org/pdf/1911.08101.pdf pg 11?}
+
+\Ethan{Or parallel rep with efficient ver.}
+
+\Ethan{If the original is wordy, just keep it the way it is. Don't try to simplify existing dfns.}
+
+\Ethan{Two main problems; 1. not professional enough, 2. flow}
+
+\Ethan{Just syntax of QFHE in the preliminary; move the theorem here}
+
+\Ethan{end of notes}
 
@@
 
+\Ethan{Take out the following and take from google docs}
+
 Let $L\in\BQP$, and $x\in\set{0,1}^n$.
@@
 	We give only a high-level description here.
+	\Ethan{Don't say this}
 	For more details, see \cref{AlgGroundStateCheck} where we generalize this for $\SampBQP$.
+	\Ethan{Reference something else; referencing $\SampBQP$ is a bad idea here}
 	\begin{enumerate}
+	    \Ethan{Phrase like ``for some input x, generate y"}
 		\item The verifier chooses some tensor product of $X$ and $Z$ measurements $\Lambda$
-		\item The prover sends the verifier some state $\rho\in\cB^{\otimes m}$ qubit-by-qubit.
-		\item The verifier measures $\rho$ according to $S$
-		\item The verifier decides whether to accept based on the measurement results.
+		\Ethan{just say there's some certain distribution that $\Lambda$ was sampled from}
+		\item The prover sends the verifier some state $\rho\in\cB^{\otimes m}$ qubit-by-qubit. \Ethan{quantify m?}
+		\item The verifier measures $\rho$ according to $S$ \Ethan{give measurement outcome notation}
+		\item The verifier decides whether to accept based on the measurement results. \Ethan{``Takes measurement outcome and generates acc/rej"}
 	\end{enumerate}
@@
 	\label{proto:BlindBQP}
+	\Ethan{Define/quantify $x$ and whatnot}
 	Let $d$ be the depth of the circuit corresponding to $\cF$.
@@
 		\item The verifier chooses $\Lambda$ and computes $\Lambda'$ using \cref{decodeMeasureOrder}
+		\Ethan{Reference to particular steps of the last protocol}
 		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
@@
 \begin{proof}
+    \Ethan{Completeness is trivial, but soundness isn't as trivial as this makes it look like}
 	Based on the correctness of $\mathsf{QHE}$, any prover strategy in \cref{proto:BlindBQP} has a corresponding strategy in \cref{proto:BQP}.
@@
 \begin{thm}
+    \Ethan{Use ``blind", not IND-CPA for protocols}
 	\cref{proto:BlindBQP} is IND-CPA secure.

### 2020-02-07 bqp.tex
Make the project compile properly
Make BQP protos more rigorous

@@
 \label{sec:BlindBQP}
-
-\Ethan{More feedback notes go here to be implemented later}
 
@@
 
-\Ethan{protocol 2 should say 1 message QPIP1 for BQP}
-
-\Ethan{``choose some tensor"? need distribution info and some basis choice}
-
-\Ethan{Try copying from https://arxiv.org/pdf/1911.08101.pdf pg 11?}
-
-\Ethan{Or parallel rep with efficient ver.}
-
 \Ethan{If the original is wordy, just keep it the way it is. Don't try to simplify existing dfns.}
@@
 \Ethan{Just syntax of QFHE in the preliminary; move the theorem here}
-
-\Ethan{end of notes}
 
@@
 
-\Ethan{Take out the following and take from google docs}
+We start with a high-level description of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.
 
-Let $L\in\BQP$, and $x\in\set{0,1}^n$.
-We start with an overview of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.
+\Ethan{below is copied and pasted from google docs and might need a bit of rephrasing}
+Thm 8.4 in Urmila's paper gives a one-message $\QPIP_1$ protocol with XZ measurement for deciding BQP language L.
+Roughly, on input $x \in\set{0,1}^n$,  P will send a m = poly(n) qubit certificate state $\rho$ to V qubit by qubit.
+V will sample a measurement setting $h \in \set{0,1}^m$ according to certain distribution $\pi_x$, and use h to determine how to measure $\rho$.
+Specifically, if $h_i = 0$ (resp., 1), then V will measure the i-th qubit using  X (resp., Z) measurement, and verify the measurement outcome.
 
@@
 	\label{proto:BQP}
-	We give only a high-level description here.
-	\Ethan{Don't say this}
-	For more details, see \cref{AlgGroundStateCheck} where we generalize this for $\SampBQP$.
-	\Ethan{Reference something else; referencing $\SampBQP$ is a bad idea here}
+	Let $L\in\BQP$, and $x\in\set{0,1}^n$. Let $m=\poly(n)$
 	\begin{enumerate}
-	    \Ethan{Phrase like ``for some input x, generate y"}
-		\item The verifier chooses some tensor product of $X$ and $Z$ measurements $\Lambda$
-		\Ethan{just say there's some certain distribution that $\Lambda$ was sampled from}
-		\item The prover sends the verifier some state $\rho\in\cB^{\otimes m}$ qubit-by-qubit. \Ethan{quantify m?}
-		\item The verifier measures $\rho$ according to $S$ \Ethan{give measurement outcome notation}
-		\item The verifier decides whether to accept based on the measurement results. \Ethan{``Takes measurement outcome and generates acc/rej"}
+		\item On input $L$ and $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_{L, x}$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is single-qubit $X$ or $Z$ measurements.
+		\item The verifier sends $x$ to the prover.
+		\item The prover applies a certain CPTP $\cF$ on $x$ to generate $\rho\in\cB^{\otimes m}$.
+			\Ethan{Now we need to define CPTP in prelim...}
+		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
+		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $c$.
+		\item The verifier runs some $\BPP$ algorithm $\cV$ on input $c$ and outputs either accept or reject.
 	\end{enumerate}
@@
 
-Differently from \cref{AlgGroundStateCheck}, \cref{proto:BQP} has negligible completeness and soundness, due to parallel repetition.
-We denote the honest prover's action in \cref{proto:BQP} as $\cF$.
+\Ethan{below is copied from google docs and need rephrasing}
+
+compile this protocol using QFHE to obtain a blind one message $\QPIP_1$ protocol for BQP with XZ measurement.
+High level idea:  run the protocol under Urmila’s QFHE.
+Namely, $\tilde{V}$ sends $ct = Enc(x)$ to $\tilde{P}$, then $\tilde{P}$ homomorphically evaluate $P_1$ on ct to produce $\tilde{rho} = Enc(\rho)$ and send the encrypted certificate state to $\tilde{V}$.
+Discussion: Now $\tilde{V}$ need to obtain the measurement outcome w from the encrypted state $\tilde{rho}$ using qubit-by-qubit XZ measurements. This may not be possible in general. 
+Key observation: Our key observation is that Urmila’s QFHE scheme allows this. 
+Explain why: Urmila’s QFHE ciphertext has the form of  QOTP on quantum msg + classical FHE ciphertext.
+So $\tilde{V}$ can do blah blah XZ measurement on $\tilde{rho}$, and recover w from the measurement outcome.
+We state this as the following fact/key observation: ...
+
+\cref{proto:BQP} has negligible completeness and soundness.
 Now we compile it using $\mathsf{QHE}$ in order to also achieve blindness:
@@
 	Let $d$ be the depth of the circuit corresponding to $\cF$.
+	Take $\pi_{L, x}$, $\cF$, and $\cV$ to be the same as in \cref{proto:BQP}
 	\begin{enumerate}
-		\item The verifier chooses $\Lambda$ and computes $\Lambda'$ using \cref{decodeMeasureOrder}
-		\Ethan{Reference to particular steps of the last protocol}
+		\item The verifier samples $\Lambda$ from $\pi_{L, x}$
+		\item The verifier computes $\Lambda'$ using \cref{decodeMeasureOrder}
 		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
@@
 		\item The verifier sends $c$ and $evk$ to the prover
-		\item The prover computes $\mathsf{QHE.Eval}(\cF, c)$ and sends it to the verifier qubit-by-qubit.
-		\item The verifier measures the incoming ciphertext according to $\Lambda'$
-		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to the measurement results
-		\item The verifier decides whether to accept based on \cref{proto:BQP}
+		\item The prover computes $\sigma=\mathsf{QHE.Eval}(\cF, c)$
+		\item The prover sends $\sigma$ to the verifier qubit-by-qubit.
+		\item The verifier measures the incoming ciphertext according to $\Lambda'$, getting $ct$
+		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $c$.
+		\item The verifier applies $\cV$ to $c$ and outputs its result.
 	\end{enumerate}
@@
 \begin{thm}
-	\cref{proto:BlindBQP} preserves the completeness and soundness of \cref{proto:BQP}
+	\cref{proto:BlindBQP} has negligible completeness and soundness.
 \end{thm}
@@
 \begin{thm}
-    \Ethan{Use ``blind", not IND-CPA for protocols}
-	\cref{proto:BlindBQP} is IND-CPA secure.
+	\cref{proto:BlindBQP} is blind.
 \end{thm}

### 2020-02-07 bqp.tex
Write theorem on BQP key obsv

@@
 \Ethan{Two main problems; 1. not professional enough, 2. flow}
-
-\Ethan{Just syntax of QFHE in the preliminary; move the theorem here}
 
@@
 We state this as the following fact/key observation: ...
+
+\begin{thm}
+	\label{decodeMeasureOrder}
+	Let $sk$ be some secret key of $\mathsf{QHE}$.
+	Let $n\in\bbN$.
+	Let $m\in\bbN$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$.
+	Let $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$, where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
+
+	There exists $\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$ where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and $\BPP$ algorithm $\widehat{\mathsf{QHE.Dec}}$ such that:
+	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
+\end{thm}
+\begin{proof}
+	This is a proof by construction.
+	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
+	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$
+
+	Clearly,
+	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\Lambda(\rho)$$
+
+	Let $\Lambda'$ applies $\Lambda$ to the first register, getting $ct=\Lambda(X^xZ^z\rho Z^zX^x)$, and applies computational basis measurement to the second register, getting $c_{x, z}$.
+
+	Note that the Pauli one-time pad on $ct$ commutes with $X$ and $Z$ measurements.
+	So let $\widehat{\mathsf{QHE.Dec}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $ct$ to get $\Lambda(\rho)$.
+\end{proof}
 

### 2020-02-07 preliminaries.tex
Add notes from Skype discussion
Add another note from Skype discussion
Write theorem on BQP key obsv

@@
 
-We define a few relevant complexity classes. \Ethan{Do we need to define $\BPP$ and $\BQP$ too?}
+We define a few relevant complexity classes.
+
+\Ethan{TODO Dfn $\BQP$}
+\Ethan{TODO Negligible errors}
 
@@
 \begin{dfn}
+    \Ethan{TODO Negligible errors}
 	$\FBQP$ is the functional analogue of the class $\BQP$.
@@
 \subsection{Semantic security for interactive protocols}
+\Ethan{Just call this blindness and put this under interactive protocols}
 
@@
 
-The quantum homomorphic encryption scheme in \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients as below:
-
-\begin{thm}
-	\label{decodeMeasureOrder}
-	There exists a QFHE $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ with the following extra properties:
+The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients:
 \begin{itemize}
@@
 	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
-		\item \Ethan{Is this obvious from the construction or do we need proof here?} Let $\Lambda$ be a product of $X$ and $Z$ measurements.
-Then there exists product of $X$ and $Z$ measurements $\Lambda'$ and $\BPP$ algorithm $\widehat{\mathsf{QHE.Dec}}$ such that
-			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
+	\item Its ciphertext takes the form $(X^xZ^z\ket\rho Z^zX^x, c_{x, z})$, where $\rho$ is the plaintext and $c_{x, z}$ is a ciphertext that decodes to $(x, z)$ under a certain classical homomorphic encryption scheme.
+	We assume without loss of generality that the length of $c_{x, z}$ is only dependent on the length of $\ket\phi$ by padding $0$s if necessary.
 \end{itemize}
-\end{thm}
 

### 2020-02-07 bqp.tex
Rephrase discussions and write BlindBQP proof

@@
 
-\Ethan{Read other papers and see if I can copy their tones and phrasing}
+\Ethan{TODO Read other papers and see if I can copy their tones and phrasing}
 
-\Ethan{Important lemmas such as 2.4 should be emphasized more and especially this one shouldn't be in prelim.}
-
-\Ethan{2.4 should be a key obsv.}
-
-\Ethan{If the original is wordy, just keep it the way it is. Don't try to simplify existing dfns.}
-
-\Ethan{Two main problems; 1. not professional enough, 2. flow}
+\Ethan{Note to self: If the original is wordy, just keep it the way it is. Don't try to simplify existing dfns.}
 
@@
 
-We start with a high-level description of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.
+We start with a high-level description of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which is in turn taken from \cite{mf16}.
 
-\Ethan{below is copied and pasted from google docs and might need a bit of rephrasing}
-Thm 8.4 in Urmila's paper gives a one-message $\QPIP_1$ protocol with XZ measurement for deciding BQP language L.
-Roughly, on input $x \in\set{0,1}^n$,  P will send a m = poly(n) qubit certificate state $\rho$ to V qubit by qubit.
-V will sample a measurement setting $h \in \set{0,1}^m$ according to certain distribution $\pi_x$, and use h to determine how to measure $\rho$.
-Specifically, if $h_i = 0$ (resp., 1), then V will measure the i-th qubit using  X (resp., Z) measurement, and verify the measurement outcome.
+This is a one-message $\QPIP_1$ protocol with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
+Roughly, on input $x\in\set{0,1}^n$, the prover sends a $m$-qubit certificate state $\rho$ to the verifier qubit-by-qubit.
+The verifier samples a product measurement $\Lambda$ of $X$ and $Z$s according to certain distribution to apply to $\rho$
+The verifier then, using the measurement results, decides whether to accept or reject.
 
-\begin{protocol}{Verifying yes-instances for $\BQP$}
+\begin{protocol}{1-message $\QPIP_1$ protocol for $\BQP$}
 	\label{proto:BQP}
@@
 		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
-		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $c$.
-		\item The verifier runs some $\BPP$ algorithm $\cV$ on input $c$ and outputs either accept or reject.
+		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $w$.
+		\item The verifier runs some $\BPP$ algorithm $\cV$ on input $w$ and outputs either accept or reject.
 	\end{enumerate}
@@
 
-\Ethan{below is copied from google docs and need rephrasing}
+We compile this protocol using $\mathsf{QHE}$ to obtain a blind 1-message $\QPIP_1$ protocol for $\BQP$, again with only $X$ and $Z$ measurements.
+The high level idea is to run \cref{proto:BQP} under $\mathsf{QHE}$.
+Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
+The prover then homomorphically evaluate $\cF$ on $y$ to produce $\sigma=\mathsf{QHE.Enc}(\rho)$ \Ethan{Is this actually ok?
+$\sigma$ is a ciphertext corresponding to $\rho$, but it wasn't encrypted.
+In fact it's deteriorated due to homomorphic eval} and send it back to the verifier.
 
-compile this protocol using QFHE to obtain a blind one message $\QPIP_1$ protocol for BQP with XZ measurement.
-High level idea:  run the protocol under Urmila’s QFHE.
-Namely, $\tilde{V}$ sends $ct = Enc(x)$ to $\tilde{P}$, then $\tilde{P}$ homomorphically evaluate $P_1$ on ct to produce $\tilde{rho} = Enc(\rho)$ and send the encrypted certificate state to $\tilde{V}$.
-Discussion: Now $\tilde{V}$ need to obtain the measurement outcome w from the encrypted state $\tilde{rho}$ using qubit-by-qubit XZ measurements. This may not be possible in general. 
-Key observation: Our key observation is that Urmila’s QFHE scheme allows this. 
-Explain why: Urmila’s QFHE ciphertext has the form of  QOTP on quantum msg + classical FHE ciphertext.
-So $\tilde{V}$ can do blah blah XZ measurement on $\tilde{rho}$, and recover w from the measurement outcome.
-We state this as the following fact/key observation: ...
+Now the verifier needs to obtain the measurement outcome $w$ from the encrypted state $\sigma$ using qubit-by-qubit $X$ and $Z$ measurements.
+This may not be possible in general, but we observe that $\mathsf{QHE}$ allows this. 
+Its ciphertexts consists of a Pauli one-time-padded plaintext and classically encrypted Pauli keys.
+Pauli one-time-pads commute with $X$ and $Z$ measurements, so the verifier can measure the one-time-padded state as usual then correct the measurement results using the Pauli keys.
+We state this observation as the following theorem:
 
@@
 	\label{proto:BlindBQP}
-	\Ethan{Define/quantify $x$ and whatnot}
-	Let $d$ be the depth of the circuit corresponding to $\cF$.
+	Let $x\in\set{0,1}^n$.
+	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cF$.
 	Take $\pi_{L, x}$, $\cF$, and $\cV$ to be the same as in \cref{proto:BQP}
@@
 		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
-		\item The verifier computes $c=\mathsf{QHE.Enc}_{pk}(x)$
-		\item The verifier sends $c$ and $evk$ to the prover
-		\item The prover computes $\sigma=\mathsf{QHE.Eval}(\cF, c)$
+		\item The verifier computes $y=\mathsf{QHE.Enc}_{pk}(x)$
+		\item The verifier sends $y$ and $evk$ to the prover
+		\item The prover computes $\sigma=\mathsf{QHE.Eval}(\cF, y)$
 		\item The prover sends $\sigma$ to the verifier qubit-by-qubit.
 		\item The verifier measures the incoming ciphertext according to $\Lambda'$, getting $ct$
-		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $c$.
-		\item The verifier applies $\cV$ to $c$ and outputs its result.
+		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $w$.
+		\item The verifier applies $\cV$ to $w$ and outputs its result.
 	\end{enumerate}
@@
 \begin{proof}
-    \Ethan{Completeness is trivial, but soundness isn't as trivial as this makes it look like}
-	Based on the correctness of $\mathsf{QHE}$, any prover strategy in \cref{proto:BlindBQP} has a corresponding strategy in \cref{proto:BQP}.
+	The completeness follows by inspection.
+
+	For soundness, suppose the prover sends $\sigma$.
+
+	The verifier's actions, by \cref{decodeMeasureOrder}, is $\negl(n)$-close to to decoding $\sigma$ to get some $\rho$ then applying $\Lambda$ to get $w$.
+	In other words, the verifier's outputs is $\negl(n)$-close to the verifer of \cref{proto:BQP} under the same input and receiving $\rho$ from the prover.
+	So the conclusion follows from the negligible soundness of \cref{proto:BQP}.
 \end{proof}

### 2020-02-07 bqp.tex
Add more Skype discussion notes

@@
 \Ethan{Note to self: If the original is wordy, just keep it the way it is. Don't try to simplify existing dfns.}
+
+\Ethan{Cut into two subsections, one for BQP and one for FBQP}
 
@@
 
-\begin{protocol}{1-message $\QPIP_1$ protocol for $\BQP$}
+\begin{protocol}{1-message $\QPIP_1$ protocol for $\BQP$ language $L$}
 	\label{proto:BQP}
-	Let $L\in\BQP$, and $x\in\set{0,1}^n$. Let $m=\poly(n)$
+	Input: $x\in\set{0,1}^n$.
+	\Ethan{Consider more notation $V_1$, $P_2$... See parallel rep paper. Numbering like this works better for compilers}
+	\Ethan{Use terms like ``generate" or arrows; see google docs}
 	\begin{enumerate}
-		\item On input $L$ and $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_{L, x}$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is single-qubit $X$ or $Z$ measurements.
+		\item On input $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_x$, where $m=\poly(n)$, $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
 		\item The verifier sends $x$ to the prover.
-		\item The prover applies a certain CPTP $\cF$ on $x$ to generate $\rho\in\cB^{\otimes m}$.
-			\Ethan{Now we need to define CPTP in prelim...}
+		\item The prover applies an algorithm $\cF$ \Ethan{Probably P3 or maybe a ``meaningful" name} on $x$ to generate $\rho\in\cB^{\otimes m}$.
 		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
 		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $w$.
-		\item The verifier runs some $\BPP$ algorithm $\cV$ on input $w$ and outputs either accept or reject.
+		\item The verifier runs some polynomial-time algorithm $\cV$ on input $w$ and outputs either accept or reject.
 	\end{enumerate}
@@
 
-We compile this protocol using $\mathsf{QHE}$ to obtain a blind 1-message $\QPIP_1$ protocol for $\BQP$, again with only $X$ and $Z$ measurements.
+We compile this protocol using Mahadev's $\mathsf{QHE}$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol for $\BQP$, again with only $X$ and $Z$ measurements.
 The high level idea is to run \cref{proto:BQP} under $\mathsf{QHE}$.
@@
 
-	There exists $\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$ where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and $\BPP$ algorithm $\widehat{\mathsf{QHE.Dec}}$ such that:
+	There exists $\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$ where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and polynomial-time algorithm $\widehat{\mathsf{QHE.Dec}}$ such that:
 	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
@@
 
-	Let $\Lambda'$ applies $\Lambda$ to the first register, getting $ct=\Lambda(X^xZ^z\rho Z^zX^x)$, and applies computational basis measurement to the second register, getting $c_{x, z}$.
+	Let $\Lambda'$ applies $\Lambda$ to the first register, getting $u=\Lambda(X^xZ^z\rho Z^zX^x)$, and applies computational basis measurement to the second register, getting $c_{x, z}$.
 
-	Note that the Pauli one-time pad on $ct$ commutes with $X$ and $Z$ measurements.
-	So let $\widehat{\mathsf{QHE.Dec}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $ct$ to get $\Lambda(\rho)$.
+	Note that the Pauli one-time pad on $u$ commutes with $X$ and $Z$ measurements.
+	So let $\widehat{\mathsf{QHE.Dec}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $u$ to get $\Lambda(\rho)$.
 \end{proof}
@@
 		\item The verifier computes $\Lambda'$ using \cref{decodeMeasureOrder}
-		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
+		\item The verifier computes $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$.
 		\item The verifier computes $y=\mathsf{QHE.Enc}_{pk}(x)$
@@
 
+\Ethan{Combine the following two theorems}
+
 \begin{thm}
@@
 	For soundness, suppose the prover sends $\sigma$.
+
+    \Ethan{rewrite the following as a reduction. If exists adversary $P*$ that breaks soundness of this protocol, it breaks the other one...}
 
@@
 
+\Ethan{Use google docs to replace below}
+
 \cite{mahadev_delegation} gives a compiler from $\QPIP_1$ protocols of the form in \cref{proto:BQP} to $\QPIP_0$ but deteriorates soundness.
-Note that \cref{proto:BlindBQP} can also be collapsed into the same form, so the same compiler can also be applied to it to obtain a $\QPIP_0$ protocol.
+Note that \cref{proto:BlindBQP} can also be collapsed into the same form \Ethan{Actually specify QPIP1 one-message use only XZ measurements}, so the same compiler can also be applied to it to obtain a $\QPIP_0$ protocol.
 
 We can then use results from \cite{parallelrep} to apply parallel repetition and recover the negligible soundness.
+
+\Ethan{Need more notation}
 

### 2020-02-07 preliminaries.tex
Add more Skype discussion notes

@@
 \end{dfn}
+
+\begin{definition} [$\FBQP$]
+	TODO copy from https://www.csa.iisc.ac.in/~chandan/courses/complexity15/notes/lec23.pdf and add in overwhelming prob.
+\end{definition}
 
@@
 	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
-	\item Its ciphertext takes the form $(X^xZ^z\ket\rho Z^zX^x, c_{x, z})$, where $\rho$ is the plaintext and $c_{x, z}$ is a ciphertext that decodes to $(x, z)$ under a certain classical homomorphic encryption scheme.
-	We assume without loss of generality that the length of $c_{x, z}$ is only dependent on the length of $\ket\phi$ by padding $0$s if necessary.
+	\item Its ciphertext takes the form $(X^xZ^z\rho Z^zX^x, c_{x, z})$, where $\rho$ is the plaintext and $c_{x, z}$ is a ciphertext that decodes to $(x, z)$ under a certain classical homomorphic encryption scheme.
 \end{itemize}

### 2020-02-07 bqp.tex
Start writing FBQP

@@
-\section{Delegation for BQP}
+\section{Blind Delegation for BQP and FBQP}
 \label{sec:BlindBQP}
@@
 
-\Ethan{Cut into two subsections, one for BQP and one for FBQP}
+\Ethan{TODO Intro this section}
 
-In this section we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
+\subsection{Blind Delegation for BQP}
+\label{subsec:BlindBQP}
+
+In this subsection we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
 \begin{thm}
@@
 \end{thm}
-\begin{proof}
+\begin{prf}
 	This is a proof by construction.
@@
 	So let $\widehat{\mathsf{QHE.Dec}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $u$ to get $\Lambda(\rho)$.
-\end{proof}
+\end{prf}
 
@@
 \end{thm}
-\begin{proof}
+\begin{prf}
 	The completeness follows by inspection.
@@
 
-    \Ethan{rewrite the following as a reduction. If exists adversary $P*$ that breaks soundness of this protocol, it breaks the other one...}
+    \Ethan{rewrite the following as a reduction. If exists adversary $P*$ that breaks soundness of this protocol, construct $P**$ that breaks the other one...}
 
@@
 	So the conclusion follows from the negligible soundness of \cref{proto:BQP}.
-\end{proof}
+\end{prf}
 
@@
 \end{thm}
-\begin{proof}
+\begin{prf}
 	The only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
-\end{proof}
+\end{prf}
 
-\Ethan{Use google docs to replace below}
+\Ethan{Below is copied from google docs}
 
-\cite{mahadev_delegation} gives a compiler from $\QPIP_1$ protocols of the form in \cref{proto:BQP} to $\QPIP_0$ but deteriorates soundness.
-Note that \cref{proto:BlindBQP} can also be collapsed into the same form \Ethan{Actually specify QPIP1 one-message use only XZ measurements}, so the same compiler can also be applied to it to obtain a $\QPIP_0$ protocol.
+Finally, we prove Thm 3.1 by applying Mahadev's measurement protocol~\cite{mahadev_delegation} to Protocol 3 to compile it into a $\QPIP_0$ protocol $(P', V')$ \Ethan{fix name}.
+Note that Mahadev's measurement protocol can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol, and Protocol 3 is a $\QPIP_1$ protocol with X, Z measurement and negligible soundness.
+Thus the resulting protocol $(P', V')$ is a O(1)-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl$ \Ethan{Write what is it negl in}. (preserve blindness)
 
-We can then use results from \cite{parallelrep} to apply parallel repetition and recover the negligible soundness.
+\Ethan{State compiled protocol and prove soundness that way}
+
+\begin{protocol}{\Cref{proto:BlindBQP} compiled using Mahadev's measurement protocol}
+	\label{proto:QPIP0BQP}
+	TODO
+
+\end{protocol}
+
+We then apply the recent result parallel repetition to reduce soundness error...
+
+\Ethan{cite both parallel rep papers}
+
+\begin{protocol}{Parallel repetition of}
+	\label{proto:repQPIP0BQP}
+	Run $n$ copies of \cref{proto:QPIP0BQP} in parallel. Accept if...? TODO some kind of standard procedure here.
+
+\end{protocol}
+
+\subsection{Blind delegation of FBQP}
 
@@
 
+Let $f\in\FBQP$.
+
+Define the language $L_{f, i, b}$ s.t. $x\in L_{f, i, b}$ if the $i$th bit of $f(x)$ is $b$.
+
 \begin{protocol}{Blind and verifiable $\QPIP_0$ delegation for $\FBQP$}
 	\label{QPIP0FBQP}
-	Suppose $y\in\set{0,1}^m$ is the output of our $\FBQP$ instance.
+	Input: $x\in\set{0, 1}^n$
+
+	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how}
+	Let $\cL = \set{L_{f, i, b}: i\in[m], b\in\set{0, 1}}$
 	\begin{enumerate}
-		\item Apply \cref{thm:QPIP0BQP} to every $y_i=0$ and $y_i=1$ case in parallel, resulting in a total of $2m$ cases.
-		\item Output $y$ if for each $i$ precisely one of the $y_i=0$ and $y=i=1$ cases accepts.
+		\item Run \cref{proto:repQPIP0BQP} for all languages $L\in\cL$ in parallel
+		\item If $\exists i$ s.t. $x\in L_{f, i, 0}$ and $x\in L_{f, i, 1}$ gives the same output, reject.
+		\item Otherwise, define $y_i = b$ where $x\in L_{f, i, b}$. This gives $y\in\set{0,1}^m$
+		\item Verifier outputs $y$
 	\end{enumerate}
@@
 
-\Ethan{TODO prove that \cref{QPIP0FBQP} actually works as expected}
+\begin{theorem}
+	\cref{QPIP0FBQP} has negligible completeness and soundness, and is blind.
+\end{theorem}
+\begin{prf}
+	TODO
+\end{prf}

### 2020-02-07 preliminaries.tex
Start writing FBQP

@@
 
-\Ethan{TODO Dfn $\BQP$}
-\Ethan{TODO Negligible errors}
-
-\begin{dfn}
-	$\QMA$ is the quantum analogue of the class $\MA$. The verifier in $\QMA$ is now a $\BQP$ machine.
-\end{dfn}
+\begin{definition} [$\BQP$]
+	\Ethan{TODO: Replace this with something that makes more sense}
+	A language $L$ is in $\BQP$ if it can be decided by some uniform quantum circuit family.
+\end{definition}
 
 \begin{definition} [$\FBQP$]
-	TODO copy from https://www.csa.iisc.ac.in/~chandan/courses/complexity15/notes/lec23.pdf and add in overwhelming prob.
+	A function $f:\set{0,1}^*\rightarrow\set{0,1}^*$ is in $\FBQP$ if there is a $\BQP$ machine that, $\forall x$, outputs $f(x)$ with overwhelming probability.
 \end{definition}
-
-\begin{dfn}
-    \Ethan{TODO Negligible errors}
-	$\FBQP$ is the functional analogue of the class $\BQP$.
-That is, every instance corresponds to a string rather than a yes/no bit.
-The error probability is still bounded above away from $\fot$ for some uniform quantum circuit family.
-\end{dfn}
 

### 2020-02-07 blind.tex
Fix QED symbols (temp fix)

@@
 \end{thm}
-\begin{proof}
+\begin{prf}
 	A honest prover still gets accepted with overwhelming probability by the correctness of $\mathsf{QHE}$. \Ethan{Not sure if too hand-wavy}
@@
 	\Ethan {Ahhhh this is not rigorous at all}
-\end{proof}
+\end{prf}
 
@@
 \end{thm}
-\begin{proof}
+\begin{prf}
 	The only thing the prover gets is $\mathsf{QHE.Enc}_{pk}(x)$, $pk$, and $evk$. So this follows directly from the security of $\mathsf{QHE}$.
-\end{proof}
+\end{prf}

### 2020-02-07 hamiltonian.tex
Fix missing dfns
Fix QED symbols (temp fix)

@@
 Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
-\Ethan{This source was given to us by Yu-Ching; I haven't read it.
-Also I probably should cite more sources here.}
+\Ethan{This source was given to us by Yu-Ching; I haven't read it. Also I probably should cite more sources here.}
 
@@
 \end{thm}
-\begin{proof}
+\begin{prf}
 	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
@@
 	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
-\end{proof}
+\end{prf}
 
@@
 \end{thm}
-\begin{proof}
+\begin{prf}
 	We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
@@
 	\end{itemize}
-\end{proof}
+\end{prf}
 
@@
 \end{thm}
-\begin{proof}
+\begin{prf}
 	Here we follow \cite{PhysRevA.93.022326}.
@@
 	\end{align*}
-\end{proof}
+\end{prf}

### 2020-02-07 qpip.tex
Get lncs to compile
Fix QED symbols (temp fix)

@@
 
-\begin{observation}
+\begin{lemma}
 	\label{ProtoGroundStateCheck}
 	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
-\end{observation}
-\begin{proof}
+\end{lemma}
+\begin{prf}
 	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
-\end{proof}
+\end{prf}
 
@@
 \end{thm}
-\begin{proof}
+\begin{prf}
 	It clearly has completeness negligibly close to $1$.
@@
 	All errors up to this point is $O(\varepsilon)$.
-\end{proof}
+\end{prf}

### 2020-02-07 bqp.tex
Fix another TODO

@@
 
-As we will see in the theorems below, \protoref{BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.
-
-\Ethan{Combine the following two theorems}
+As we will see in the theorems below, \protoref{BlindBQP} is a $\QPIP_1$, constant round, and blind protocol for $\BQP$ with negligible completeness and soundness.
 
 \begin{thm}
-	\cref{proto:BlindBQP} has negligible completeness and soundness.
+	\cref{proto:BlindBQP} has negligible completeness and soundness, and is blind.
 \end{thm}
@@
 	The completeness follows by inspection.
+	For blindness, the only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
+
+    \Ethan{rewrite the following as a reduction. If exists adversary $P*$ that breaks soundness of this protocol, construct $P**$ that breaks the other one...}
 
 	For soundness, suppose the prover sends $\sigma$.
-
-    \Ethan{rewrite the following as a reduction. If exists adversary $P*$ that breaks soundness of this protocol, construct $P**$ that breaks the other one...}
 
@@
 	So the conclusion follows from the negligible soundness of \cref{proto:BQP}.
-\end{prf}
-
-\begin{thm}
-	\cref{proto:BlindBQP} is blind.
-\end{thm}
-\begin{prf}
-	The only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
 \end{prf}

### 2020-02-07 bqp.tex
Work a bit more on FBQP

@@
 
-Define the language $L_{f, i, b}$ s.t. $x\in L_{f, i, b}$ if the $i$th bit of $f(x)$ is $b$.
+For any input $x\in\set{0, 1}^*$, define $f_i(x)$ to be the $i$-th bit of $f(x)$.
+
+Define the language $L_{i, b}=\set{x:f_i(x)=b}$.
 
@@
 	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how}
-	Let $\cL = \set{L_{f, i, b}: i\in[m], b\in\set{0, 1}}$
+	Let $\cL = \set{L_{i, b}: i\in[m], b\in\set{0, 1}}$
 	\begin{enumerate}
 		\item Run \cref{proto:repQPIP0BQP} for all languages $L\in\cL$ in parallel
-		\item If $\exists i$ s.t. $x\in L_{f, i, 0}$ and $x\in L_{f, i, 1}$ gives the same output, reject.
-		\item Otherwise, define $y_i = b$ where $x\in L_{f, i, b}$. This gives $y\in\set{0,1}^m$
+		\item If $\exists i$ s.t. $x\in L_{f, i, 0}$ and $x\in L_{i, 1}$ gives the same output, reject.
+		\item Otherwise, define $y_i = b$ where $x\in L_{i, b}$. This gives $y\in\set{0,1}^m$
 		\item Verifier outputs $y$
@@
 \begin{prf}
-	TODO
+	Completeness is follows by inspection.
+	Blindness follows because the executions of \cref{proto:repQPIP0BQP} are blind.
+
+	Soundness... TODO
 \end{prf}

### 2020-02-08 bqp.tex
Make next draft of FBQP

@@
 
+\Ethan{TODO PROOFREAD ME}
+
 \begin{protocol}{1-message $\QPIP_1$ protocol for $\BQP$ language $L$}
@@
 	Input: $x\in\set{0,1}^n$.
-	\Ethan{Consider more notation $V_1$, $P_2$... See parallel rep paper. Numbering like this works better for compilers}
-	\Ethan{Use terms like ``generate" or arrows; see google docs}
 	\begin{enumerate}
-		\item On input $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_x$, where $m=\poly(n)$, $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
+		\item $\cV_1$:
+			On input $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_x$, where $m=\poly(n)$, $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
+
+			\Ethan{How does this $\cV_1$ thing work?}
 		\item The verifier sends $x$ to the prover.
-		\item The prover applies an algorithm $\cF$ \Ethan{Probably P3 or maybe a ``meaningful" name} on $x$ to generate $\rho\in\cB^{\otimes m}$.
+		\item $\cP_2$:
+			On input $x$, the prover applies an algorithm to generate $\rho\in\cB^{\otimes m}$.
 		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
 		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $w$.
-		\item The verifier runs some polynomial-time algorithm $\cV$ on input $w$ and outputs either accept or reject.
+		\item $\cV_3$:
+			On input $w$, the verifier generates and outputs either accept or reject using a classical polynomial-time algorithm.
 	\end{enumerate}
@@
 
+\Ethan{TODO PROOFREAD ME}
+
 \begin{protocol}{Blind Protocol for $\BQP$}
@@
 	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cF$.
-	Take $\pi_{L, x}$, $\cF$, and $\cV$ to be the same as in \cref{proto:BQP}
 	\begin{enumerate}
-		\item The verifier samples $\Lambda$ from $\pi_{L, x}$
-		\item The verifier computes $\Lambda'$ using \cref{decodeMeasureOrder}
-		\item The verifier computes $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$.
-		\item The verifier computes $y=\mathsf{QHE.Enc}_{pk}(x)$
-		\item The verifier sends $y$ and $evk$ to the prover
-		\item The prover computes $\sigma=\mathsf{QHE.Eval}(\cF, y)$
-		\item The prover sends $\sigma$ to the verifier qubit-by-qubit.
-		\item The verifier measures the incoming ciphertext according to $\Lambda'$, getting $ct$
-		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $w$.
-		\item The verifier applies $\cV$ to $w$ and outputs its result.
+		\item The verifier, on input $x$ generates $\Lambda$ using $\cV_1$ of \cref{proto:BQP}.
+			On input $\Lambda$, it computes $\Lambda'$ using \cref{decodeMeasureOrder}.
+			It computes $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, and $y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
+			Finally, it sends $y$ and $evk$ to the prover
+		\item The prover homomorphically evaluates $\cP_2$ of \cref{proto:BQP} on input $y$, generating $\sigma=\mathsf{QHE.Eval}(\cP_2, y)$.
+			The prover sends $\sigma$ to the verifier qubit-by-qubit.
+		\item The verifier measures the incoming ciphertext $\sigma$ according to $\Lambda'$, getting $ct$
+			It applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $w$.
+			On input $w$, it applies $\cV_3$ of \cref{proto:BQP} and outputs its result.
 	\end{enumerate}
@@
 
-    \Ethan{rewrite the following as a reduction. If exists adversary $P*$ that breaks soundness of this protocol, construct $P**$ that breaks the other one...}
+	\Ethan{TODO PROOFREAD ME}
+	Suppose for the sake of contradiction that some prover $\bbP'$ breaks the soundness of \cref{proto:BlindBQP}.
 
-	For soundness, suppose the prover sends $\sigma$.
+	We construct $\tilde\bbP$ a prover against the soundness guarantees in \cref{proto:BQP} as $(\bbV, \tilde\bbP)$.
 
-	The verifier's actions, by \cref{decodeMeasureOrder}, is $\negl(n)$-close to to decoding $\sigma$ to get some $\rho$ then applying $\Lambda$ to get $w$.
-	In other words, the verifier's outputs is $\negl(n)$-close to the verifer of \cref{proto:BQP} under the same input and receiving $\rho$ from the prover.
-	So the conclusion follows from the negligible soundness of \cref{proto:BQP}.
+	$\tilde\bbP$ simulates \cref{proto:BlindBQP} as $(\bbV', \bbP')$.
+
+	When $\bbP'$ sends $\sigma$, $\tilde\bbP$ computes and sends $\rho=\mathsf{QHE.Dec}_{sk}(\sigma)$ to $\bbV$.
+
+	$\bbV'$ has a non-negligible chance to accept after receiving $\sigma$.
+	When that happens, $\cV(w)=\cV(\Lambda(\rho))=Acc$, so $\bbV$ would also accept after receiving $\rho$.
 \end{prf}
 
-\Ethan{Below is copied from google docs}
+\Ethan{TODO Below is copied from google docs; fix phrasing later}
 
@@
 Note that Mahadev's measurement protocol can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol, and Protocol 3 is a $\QPIP_1$ protocol with X, Z measurement and negligible soundness.
-Thus the resulting protocol $(P', V')$ is a O(1)-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl$ \Ethan{Write what is it negl in}. (preserve blindness)
+Thus the resulting protocol $(P', V')$ is a O(1)-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$
 
-\Ethan{State compiled protocol and prove soundness that way}
+\Ethan{TODO PROOFREAD ME}
+We give a high-level overview of the compiliation results.
 
@@
 	\label{proto:QPIP0BQP}
-	TODO
+	\begin{enumerate}
+		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, y$ the same way as in \cref{proto:BlindBQP}.
+			On input $\Lambda'$, it generates $k, td$.
+			It sends $k, evk, y$ to the prover.
+		\item The prover, on inputs $k, evk, y$, generates classical ``commitment" $m$ and internal state $\ket{st}$.
+			It sends $m$ to the verifier.
+		\item The verifier sends the prover a public fair coin $c\in{0,1}$.
+		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
+		\item The verifier, on inputs $k, td, m, c, a, sk$, generates and outputs either $acc$ or $rej$.
+	\end{enumerate}
+\end{protocol}
+
+$k$ has the additional properties to not leak information on $\Lambda'$, so the compliation preserves blindness. \Ethan{How to make this more rigorous?}
+
+We then apply the recent result parallel repetition get negligible soundness again:
+
+\begin{protocol}{Parallel repetition of \cref{proto:QPIP0BQP}}
+	\label{proto:repQPIP0BQP}
+	\Ethan{TODO PROOFREAD ME}
+	Run $m=\poly(n)$ copies of \cref{proto:QPIP0BQP} in parallel. Accept if the proportion of accepted copies is over some certain threshold $p(n)\in(0, 1)$.
 
@@
 
-We then apply the recent result parallel repetition to reduce soundness error...
-
-\Ethan{cite both parallel rep papers}
-
-\begin{protocol}{Parallel repetition of}
-	\label{proto:repQPIP0BQP}
-	Run $n$ copies of \cref{proto:QPIP0BQP} in parallel. Accept if...? TODO some kind of standard procedure here.
-
-\end{protocol}
+\begin{thm}
+	\cref{proto:repQPIP0BQP} has negligible completeness and soundness
+\end{thm}
+\begin{prf}
+	See \cite{parallelrep} \Ethan{TODO FIND AND CITE the other parallel rep. paper}
+\end{prf}
 
@@
 
-\Ethan{Need more notation}
+\Ethan{TODO PROOFREAD ME}
 
-Our results for $\BQP$ can also be generalized to $\FBQP$ by applying $2n$ copies of \cref{thm:QPIP0BQP} in parallel.
+Our results for $\BQP$ can be generalized to $\FBQP$.
 
 Let $f\in\FBQP$.
-
 For any input $x\in\set{0, 1}^*$, define $f_i(x)$ to be the $i$-th bit of $f(x)$.
-
-Define the language $L_{i, b}=\set{x:f_i(x)=b}$.
+For $i\in\bbN, b\in\set{0,1}$, define the language $L_{i, b}=\set{x:f_i(x)=b}$.
+Define $\cL$ to be the collection of these languages: $\cL = \set{L_{i, b}: i\in[m], b\in\set{0, 1}}$.
 
 \begin{protocol}{Blind and verifiable $\QPIP_0$ delegation for $\FBQP$}
-	\label{QPIP0FBQP}
+	\label{proto:QPIP0FBQP}
 	Input: $x\in\set{0, 1}^n$
 
-	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how}
-	Let $\cL = \set{L_{i, b}: i\in[m], b\in\set{0, 1}}$
+	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how?}
 	\begin{enumerate}
-		\item Run \cref{proto:repQPIP0BQP} for all languages $L\in\cL$ in parallel
-		\item If $\exists i$ s.t. $x\in L_{f, i, 0}$ and $x\in L_{i, 1}$ gives the same output, reject.
-		\item Otherwise, define $y_i = b$ where $x\in L_{i, b}$. This gives $y\in\set{0,1}^m$
+		\item Run \cref{proto:repQPIP0BQP} for all $L\in\cL$ in parallel using input $x$. The verifier gets outputs $v_{i, b}\in\set{Acc, Rej}$.
+		\item If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.
+		\item Otherwise, define $y_i = b$ where $v_{i, b}=Acc$. This gives $y\in\set{0,1}^m$
 		\item Verifier outputs $y$
@@
 \begin{theorem}
-	\cref{QPIP0FBQP} has negligible completeness and soundness, and is blind.
+	\Cref{proto:QPIP0FBQP} has negligible completeness and soundness, and is blind.
 \end{theorem}
@@
 
-	Soundness... TODO
+	Based on the soundness of \cref{proto:BlindBQP}, $v_{i, b}=Acc$ implies that $x\in L_{i, b}\Rightarrow f_i(x)=b$ with overwhelming probability.
+	In other words, $y_i$ is correct with probability $1-\varepsilon_i$ where $\varepsilon_i=\negl(n)$.
+
+	By union bound over all output bits, the soundness of \cref{proto:QPIP0FBQP} is then
+	$\sum_{i=1}^m \varepsilon_i$
+	which is clearly negligible.
 \end{prf}

### 2020-02-08 qpip0.tex

@@
 \begin{lemma}[binding property of  Protocol~\ref{proto:urmila4}\cite{mahadev_delegation}]
-If a prover's strategy result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
+If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
 \end{lemma}
@@
 
-Choose the $T$ in Lemma~\ref{lem:partition} to be $\Theta(m^3)$ \hannote{$\gamma_0$?}. By Property~\ref{partition-property-1} of Lemma~\ref{lem:partition}, 
-$$\forall i, \L(1- 1/m^2\R)\text{fraction of }\gamma$$ 
-satisfies that 
-$$\norm{\ket{\psi_{err}}}^2 \leq 1/m+\negl(n). $$
-Therefore, there exist an $\gamma$ such that 
-$$\forall i,\, \norm{\ket{\psi_{err}}}^2 \leq 1/m+\negl(n). $$
-
-Denote $G_{i,\gamma}$ with  $\gamma$ found above as $G_i$.
-
  [[Partition lemma -> Parallel repetition]], except for probability $\eps$, either the verifier reject at step~\ref{step:multi-testing} or $z$ is $\negl(n)$-computationally indistinguishable to $M_{XZ}(\rho,h)$ by Theorem~\ref{thm:urmila-binding}.
@@
 
-Here we follow \cite{parallelrep}.
-
-We characterize a prover by two unitaries $(U_0, U)$ acting on the space $\cH_C\otimes\cH_X\otimes\cH_Z\otimes\cH_Y\otimes\cH_K$.
-
-\Ethan{I'll elaborate on above later, after figuring out exactly what I need or don't need}
-
-Each coordinate can be accepted and rejected separately, and the entire protocol accepts only if all coordinates accept.
-
-Let $A_{k_i, y_i}$ be the set of $a_i$s accepted by the verifier in the test round when the first and second messages are $k_i$ and $y_i$, respectively.
-
-\Ethan{Do we even need this lemma 3.5, or can we just use 3.6...}
-
 \hannote{import 3.5. didn't import the proof, too long.}
 
-First, We present a lemma from \cite{parallelrep}  that gives a decomposition of a cheating prover's state. We omit the proof here.
+First, We present a slight adaption of Lemma 3.5 of \cite{parallelrep}  that partitions the prover's internal state. We omit the proof here.
 
-\begin{lemma}[Slight adaption from Lemma 3.5 of \cite{parallelrep}]\label{lem:partition}
-Let $(U_0,U)$ be any prover's strategy in Protocol~\ref{proto:QPIP0samp}.  $i\in[m]$, 
-$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\frac{\gamma_0}{T}=1/\poly(\secpar)$.
-Let $\gamma$ be sampled uniformly randomly from $[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}]$.
-Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{\regX,\regZ}$,
+%$\frac{\gamma_0}{T}=1/\poly(\secpar)$
+\begin{lemma}[partition lemma]\label{lem:partition}
+Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}.  Let $i\in[m]$, 
+$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.
+Let $\gamma$ be a random number sampled uniformly from $\L[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R]$.
+
+There exists an $\poly(n)$-sized quantum circuit $G_{i,\gamma}$ such that for all (possibly sub-normalized) \hannote{$n$-qubit?} quantum state $\ket{\psi}_{\regX,\regZ}$,  
 \begin{align*}
-    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+ z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
+    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = \\ z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+  z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
 \end{align*}
-where $t$ is the number of qubits in the register $ph$, $z_0,z_1\in \mathbb{C}$ such that $|z_0|=|z_1|=1$, and 
-$z_0$, $z_1$, $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ may depend on $\gamma$.
+\hannote{what's wrong with all these registers} where $t$ is the number of qubits in the register $ph$, $z_0,z_1\in \mathbb{C}$ such that $|z_0|=|z_1|=1$, and 
+$z_0$, $z_1$, \hannote{$Z$ just phase factor?}$\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ may depend on $\gamma$.
 
@@
 \begin{enumerate}
-%\item There exist (sub-normalized) states $\ket{\psi_0}_{\regX,\regZ}$ and $\ket{\psi_1}_{\regX,\regZ}$ such that when $G_{i,\gamma}$ runs on input $\ket{\psi}_{\regX,\regZ}$, the output is  $(0,\ket{\psi_0}_{\regX,\regZ}/\|\ket{\psi_0}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_0}_{\regX,\regZ}\|^2$, $(1,\ket{\psi_1}_{\regX,\regZ}/\|\ket{\psi_1}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_1}_{\regX,\regZ}\|^2$, and $\bot$ with probability  $1-\|\ket{\psi_0}_{\regX,\regZ}\|^2- \|\ket{\psi_1}_{\regX,\regZ}\|^2$,
-    \item \label{partition-property-1} If we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$, then we have  $E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$.
+    \item \label{partition-property-1}  Define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$.\hannote{?} We have  $$E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$$.
+    $$E_{\gamma}[\|\ket{\psi}_{\regX,\regZ}\|^2 -\|\ket{\psi_0}_{\regX,\regZ}\|^2 -\|\ket{\psi_1}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$$
 \item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$.
@@
 This implies that if we apply the measurement $M_{ph,th,in}$ on $\frac{G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in}}{\|\ket{\psi}_{\regX,\regZ}\|}$, then the outcome is $0^tb1$ with probability $\|\ket{\psi_b}_{\regX,\regZ}\|^2$ and the resulting state in the register $(\regX,\regZ)$  is $\frac{\ket{\psi_b}_{\regX,\regZ}}{\|\ket{\psi_b}_{\regX,\regZ}\|}$ ignoring a global phase factor.
-    \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. 
+
+    % \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. \hannote{redundant?}
+
         \item 
-For any fixed $\gamma$ and $c\in \bit^m$ such that $c_i=0$, we have 
+For any fixed $\gamma$ and $c\in [m]$ such that $c\neq i$\hannote{check}\hannote{for all k, y}, we have 
 \begin{align*}
-\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq 2^{m-1}\gamma+\negl(\secpar).
+\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
 \end{align*}
@@
   \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
-  \end{align*}   
+  \end{align*}   \hannote{$M_x?$}
 \end{enumerate}
@@
 \end{lem}
-\fi
-
-\Ethan{Below is 3.6. Looks kinda useful but I need to think through this $c$ thing to make sure it'll be fine even if it's not randomly generated.}
-\hannote{How about include 3.6 in the theorem}
 
@@
 \end{theorem}
-\begin{proof}
-We run Mahadev's 4-round protocol \ref{} and use parallel repetition to reduce the soundness error. \hannote{describe $N$ time para rep}. 
-\end{proof}
+
+\fi
+==========
+
+Choose the $T$ in Lemma~\ref{lem:partition} to be $\Theta(m^3)$ \hannote{$\gamma_0$?}. By Property~\ref{partition-property-1} of Lemma~\ref{lem:partition}, 
+$$\forall i, \L(1- 1/m^2\R)\text{fraction of }\gamma$$ 
+satisfies that 
+$$\norm{\ket{\psi_{err}}}^2 \leq 1/m+\negl(n). $$
+Therefore, there exist an $\gamma$ such that 
+$$\forall i,\, \norm{\ket{\psi_{err}}}^2 \leq 1/m+\negl(n). $$
+
+Denote $G_{i,\gamma}$ with  $\gamma$ found above as $G_i$. \hannote{finding $\gamma$ is not computationally efficient.}
+
+====
+
+\Ethan{Below is 3.6. Looks kinda useful but I need to think through this $c$ thing to make sure it'll be fine even if it's not randomly generated.}
+\hannote{How about include 3.6 in the theorem}
+
+Here we follow \cite{parallelrep}.
+
+We characterize a prover by two unitaries $(U_0, U)$ acting on the space $\cH_C\otimes\cH_X\otimes\cH_Z\otimes\cH_Y\otimes\cH_K$.
+
+\Ethan{I'll elaborate on above later, after figuring out exactly what I need or don't need}
+
+Each coordinate can be accepted and rejected separately, and the entire protocol accepts only if all coordinates accept.
+
+Let $A_{k_i, y_i}$ be the set of $a_i$s accepted by the verifier in the test round when the first and second messages are $k_i$ and $y_i$, respectively.
+
+\Ethan{Do we even need this lemma 3.5, or can we just use 3.6...}
 
@@
     asdf
+
 \begin{cor}

### 2020-02-08 bqp.tex
Add notes from Skype discussion

@@
 \Ethan{TODO Intro this section}
+
+\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf for conventions. Mal. parties have stars, protos use Pi. Stuff like $r[(P(w), V )(1n ,(M, x, t))$ }
+
+\Ethan{More notation, fix interfaces}
+
+\Ethan{Fix up to proto 3 and proofs}
 
@@
 
-\Ethan{TODO PROOFREAD ME}
-
-\begin{protocol}{1-message $\QPIP_1$ protocol for $\BQP$ language $L$}
+\begin{protocol}{1-message $\QPIP_1$ protocol $\Pi_{MF} = (P_{MF}, V_{MF})$ for $\BQP$ language $L$ \Ethan{TODO use macros}}
 	\label{proto:BQP}
-	Input: $x\in\set{0,1}^n$.
+	Common input: $x\in\set{0,1}^n$. 
 	\begin{enumerate}
-		\item $\cV_1$:
-			On input $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_x$, where $m=\poly(n)$, $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
-
-			\Ethan{How does this $\cV_1$ thing work?}
-		\item The verifier sends $x$ to the prover.
-		\item $\cP_2$:
-			On input $x$, the prover applies an algorithm to generate $\rho\in\cB^{\otimes m}$.
-		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
-		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $w$.
-		\item $\cV_3$:
-			On input $w$, the verifier generates and outputs either accept or reject using a classical polynomial-time algorithm.
+		\item The verifier generates $\Lambda \leftarrow \cV_1(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
+		\Ethan{change $\cV_1$ to $\cV_{MF, 1}$}
+		\item The prover generates a certificate state $\rho\leftarrow\cP_2(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
+		\item The verifier applies the measurement $\Lambda$ to $\rho$ qubit-by-qubit.
+Let $w \in \set{0,1}^n$ denote the measurement outcome.
+It verifies the measurement outcome and produces a decision  $o\leftarrow\cV_3(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cV_3$ is a classical polynomial-time algorithm.
 	\end{enumerate}
@@
 
-\begin{protocol}{Blind Protocol for $\BQP$}
+\begin{protocol}{Blind Protocol $\Pi_{blind} = (P_{blind}, V_{blind}$) for $\BQP$ \Ethan{Define and use macros later}}
 	\label{proto:BlindBQP}
@@
 	\Ethan{TODO PROOFREAD ME}
-	Suppose for the sake of contradiction that some prover $\bbP'$ breaks the soundness of \cref{proto:BlindBQP}.
+	\Ethan{Convention: malicious parties have stars}
 
-	We construct $\tilde\bbP$ a prover against the soundness guarantees in \cref{proto:BQP} as $(\bbV, \tilde\bbP)$.
+	\Ethan{Don't use blackboard bold for provers/verifiers}
 
-	$\tilde\bbP$ simulates \cref{proto:BlindBQP} as $(\bbV', \bbP')$.
+	Suppose for the sake of contradiction that some prover $\bbP_{blind}^*$ breaks the soundness of \cref{proto:BlindBQP}.
 
-	When $\bbP'$ sends $\sigma$, $\tilde\bbP$ computes and sends $\rho=\mathsf{QHE.Dec}_{sk}(\sigma)$ to $\bbV$.
+	Then we use it to construct a prover $\bbP_{MF}^*$ against the soundness guarantees in \cref{proto:BQP}.
 
-	$\bbV'$ has a non-negligible chance to accept after receiving $\sigma$.
-	When that happens, $\cV(w)=\cV(\Lambda(\rho))=Acc$, so $\bbV$ would also accept after receiving $\rho$.
+	$\bbP_{MF}^*$ simulates \cref{proto:BlindBQP} as $(V_{blind}(x), P_{blind}^*)()$
+
+	\Ethan{Fix interface; $P_{blind}^*$ expects some message from $V$}
+
+	When $\bbP_{blind}^*$ sends $\sigma$, $\bbP_{MF}^*$ computes and sends $\rho=\mathsf{QHE.Dec}_{sk}(\sigma)$ to the verifier. \Ethan{Make observation that $P_{blind}^*$ has $sk$
+
+	By assumption, $\bbV_{Blind}$ has a non-negligible chance to accept after receiving $\sigma$.
+	When that happens, $\cV(w)=\cV(\Lambda(\rho))=Acc$.
+	So $\bbV_{MF}$ has the same probability to accept after receiving $\rho$.
 \end{prf}

### 2020-02-08 bqp.tex
Make compiliation pass
Implement some suggestions from Skype call

@@
 \label{sec:BlindBQP}
+
+\def\MF{\mathsf{MF}}
+\nc{\PiMF}{\ensuremath{\Pi_\MF}}
+\nc{\VMF}{\ensuremath{V_\MF}}
+\nc{\PMF}{\ensuremath{P_\MF}}
+\nc{\PMFstar}{\ensuremath{P_\MF^*}}
+\nc{\cVMF}[1]{\ensuremath{\cV_{\MF,#1}}}
+\nc{\cPMF}[1]{\ensuremath{\cP_{\MF,#1}}}
+
+\def\blind{\mathsf{blind}}
+\nc{\Piblind}{\ensuremath{\Pi_\blind}}
+\nc{\Vblind}{\ensuremath{V_\blind}}
+\nc{\Pblind}{\ensuremath{P_\blind}}
+\nc{\Pblindstar}{\ensuremath{P_\blind^*}}
+\nc{\cVblind}[1]{\ensuremath{\cV_{\blind,#1}}}
+\nc{\cPblind}[1]{\ensuremath{\cP_{\MF,#1}}}
 
@@
 
-\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf for conventions. Mal. parties have stars, protos use Pi. Stuff like $r[(P(w), V )(1n ,(M, x, t))$ }
+\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf for conventions. Mal. parties have stars, protos use Pi. Stuff like $r(P(w), V )(1n ,(M, x, t))$ }
 
@@
 
-\begin{protocol}{1-message $\QPIP_1$ protocol $\Pi_{MF} = (P_{MF}, V_{MF})$ for $\BQP$ language $L$ \Ethan{TODO use macros}}
+\begin{protocol}{1-message $\QPIP_1$ protocol $\PiMF = (\PMF, \VMF)$ for $\BQP$ language $L$}
 	\label{proto:BQP}
@@
 	\begin{enumerate}
-		\item The verifier generates $\Lambda \leftarrow \cV_1(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
-		\Ethan{change $\cV_1$ to $\cV_{MF, 1}$}
-		\item The prover generates a certificate state $\rho\leftarrow\cP_2(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
+		\item The verifier generates $\Lambda \leftarrow \cVMF{1}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
+		\item The prover generates a certificate state $\rho\leftarrow\cPMF{2}(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
 		\item The verifier applies the measurement $\Lambda$ to $\rho$ qubit-by-qubit.
 			Let $w \in \set{0,1}^n$ denote the measurement outcome.
-It verifies the measurement outcome and produces a decision  $o\leftarrow\cV_3(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cV_3$ is a classical polynomial-time algorithm.
+			It verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
 	\end{enumerate}
@@
 
-\Ethan{TODO PROOFREAD ME}
-
-\begin{protocol}{Blind Protocol $\Pi_{blind} = (P_{blind}, V_{blind}$) for $\BQP$ \Ethan{Define and use macros later}}
+\begin{protocol}{Blind protocol $\Piblind = (\Pblind, \Vblind)$ for $\BQP$}
 	\label{proto:BlindBQP}
-	Let $x\in\set{0,1}^n$.
-	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cF$.
+	Let $x\in\set{0,1}^n$ be an input for $\Vblind$.
+	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPMF{2}$.
 	\begin{enumerate}
-		\item The verifier, on input $x$ generates $\Lambda$ using $\cV_1$ of \cref{proto:BQP}.
+		\item The verifier generates $\Lambda\leftarrow\cVMF{1}(x)$.
 			On input $\Lambda$, it computes $\Lambda'$ using \cref{decodeMeasureOrder}.
-			It computes $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, and $y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
-			Finally, it sends $y$ and $evk$ to the prover
-		\item The prover homomorphically evaluates $\cP_2$ of \cref{proto:BQP} on input $y$, generating $\sigma=\mathsf{QHE.Eval}(\cP_2, y)$.
-			The prover sends $\sigma$ to the verifier qubit-by-qubit.
-		\item The verifier measures the incoming ciphertext $\sigma$ according to $\Lambda'$, getting $ct$
-			It applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $w$.
-			On input $w$, it applies $\cV_3$ of \cref{proto:BQP} and outputs its result.
+			Then it generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$ and $y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
+			It sends $y$ and $evk$ to the prover.
+		\item The prover homomorphically evaluates $\cPMF{2}$ on input $y$, generating $\sigma\leftarrow\mathsf{QHE.Eval}(\cPMF{2}, y)$.
+			It sends $\sigma$ to the verifier qubit-by-qubit.
+		\item The verifier generates $ct\leftarrow\Lambda'(\sigma)$,
+			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct)$,
+			and then $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
+			It outputs $o$.
 	\end{enumerate}
@@
 
-As we will see in the theorems below, \protoref{BlindBQP} is a $\QPIP_1$, constant round, and blind protocol for $\BQP$ with negligible completeness and soundness.
+As we will prove, $\Piblind$ is a $\QPIP_1$, constant round, and blind protocol for $\BQP$ with negligible completeness and soundness.
 
 \begin{thm}
-	\cref{proto:BlindBQP} has negligible completeness and soundness, and is blind.
+	$\Piblind$ has negligible completeness and soundness, and is blind.
 \end{thm}
@@
 
-	\Ethan{TODO PROOFREAD ME}
-	\Ethan{Convention: malicious parties have stars}
+	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ violating the soundness guarantees of $\Piblind$,
+	then we can use it to construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$.
 
-	\Ethan{Don't use blackboard bold for provers/verifiers}
+	\Ethan{This construction is too small for a separate box but maybe still be too big to just write it like this?}
 
-	Suppose for the sake of contradiction that some prover $\bbP_{blind}^*$ breaks the soundness of \cref{proto:BlindBQP}.
+	We define $\PMFstar$ to first generate
+	$$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}$$
+	and
+	$$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$$
+	It then sends $y$ and $evk$ to $\Pblindstar$ and gets $\sigma$ back.
+	Finally, it generates
+	$$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$$
+	and sends it to $\VMF$ qubit-by-qubit.
 
-	Then we use it to construct a prover $\bbP_{MF}^*$ against the soundness guarantees in \cref{proto:BQP}.
+	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
 
-	$\bbP_{MF}^*$ simulates \cref{proto:BlindBQP} as $(V_{blind}(x), P_{blind}^*)()$
-
-	\Ethan{Fix interface; $P_{blind}^*$ expects some message from $V$}
-
-	When $\bbP_{blind}^*$ sends $\sigma$, $\bbP_{MF}^*$ computes and sends $\rho=\mathsf{QHE.Dec}_{sk}(\sigma)$ to the verifier. \Ethan{Make observation that $P_{blind}^*$ has $sk$
-
-	By assumption, $\bbV_{Blind}$ has a non-negligible chance to accept after receiving $\sigma$.
-	When that happens, $\cV(w)=\cV(\Lambda(\rho))=Acc$.
-	So $\bbV_{MF}$ has the same probability to accept after receiving $\rho$.
+	By assumption, $\Vblind$ has a non-negligible probability to accept after receiving $\sigma$.
+	In other words, let $\Lambda\leftarrow\cVMF{1}$, and define $\Lambda'$ by \cref{decodeMeasureOrder},
+	then with non-negligible probability
+	$$\cVMF{3}(x, \Lambda, \widehat{\mathsf{QHE.Dec}_{sk}}(\Lambda'(\sigma))=acc$$
+	which is equivalent to
+	$$\cVMF{3}(x, \Lambda, \Lambda(\rho))=acc$$
+	That is, $\PMFstar$ violates the soundness of $\PiMF$.
 \end{prf}
@@
 
-\Ethan{TODO PROOFREAD ME}
 We give a high-level overview of the compiliation results.
 
-\begin{protocol}{\Cref{proto:BlindBQP} compiled using Mahadev's measurement protocol}
+\begin{protocol}{\Cref{proto:BlindBQP} compiled using Mahadev's measurement protocol \Ethan{Give this a name}}
 	\label{proto:QPIP0BQP}
 	\begin{enumerate}
-		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, y$ the same way as in \cref{proto:BlindBQP}.
+		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, y$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
 			On input $\Lambda'$, it generates $k, td$.

### 2020-02-08 bqp.tex
Add Skype discussion notes

@@
 		\item The verifier generates $\Lambda \leftarrow \cVMF{1}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
+\Ethan{Switch steps 1 and 2}
 		\item The prover generates a certificate state $\rho\leftarrow\cPMF{2}(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
 		\item The verifier applies the measurement $\Lambda$ to $\rho$ qubit-by-qubit.
-			Let $w \in \set{0,1}^n$ denote the measurement outcome.
+			Let $w \in \set{0,1}^m$ denote the measurement outcome.
 			It verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
@@
 
-\cref{proto:BQP} has negligible completeness and soundness.
+\Ethan{Give the theorem above a corresponding algorithm}
+
+\Cref{proto:BQP} has negligible completeness and soundness.
 Now we compile it using $\mathsf{QHE}$ in order to also achieve blindness:
 
-\begin{protocol}{Blind protocol $\Piblind = (\Pblind, \Vblind)$ for $\BQP$}
+\begin{protocol}{Blind $\QPIP_1$ 1-message protocol $\Piblind = (\Pblind, \Vblind)$ for $\BQP$ language $L$}
 	\label{proto:BlindBQP}
-	Let $x\in\set{0,1}^n$ be an input for $\Vblind$.
+	Verifier's input: $x\in\set{0,1}^n$.
+
 	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPMF{2}$.
@@
 			It sends $y$ and $evk$ to the prover.
+			\Ethan{Do two steps. Keygens first, lambda next. For keygen step, say more in words and describe $d$. Remember to specify $x$ when talking about $d$ and $\cPMF{2}$}
 		\item The prover homomorphically evaluates $\cPMF{2}$ on input $y$, generating $\sigma\leftarrow\mathsf{QHE.Eval}(\cPMF{2}, y)$.
@@
 \end{protocol}
+
+\Ethan{Change steps orders above. 1. verifier enc and send y 2. prover sends something back 3. verifier sample lambda}
 
@@
 
-	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ violating the soundness guarantees of $\Piblind$,
+	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ violating the soundness guarantees of $\Piblind$ 
+	\Ethan{Define some $\epsilon$ here. Also ``non-negligible" = ``noticeable"},
 	then we can use it to construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$.
@@
 
+	\Ethan{Add the ``simulate" thing back}
+
 	We define $\PMFstar$ to first generate
-	$$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}$$
+	$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}$
 	and
-	$$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$$
+	$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
 	It then sends $y$ and $evk$ to $\Pblindstar$ and gets $\sigma$ back.
-	Finally, it generates
-	$$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$$
+	Finally, it decrypts
+	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
 	and sends it to $\VMF$ qubit-by-qubit.
 
+    \Ethan{Rewrite the following proof again; write in terms of interactions this time. See google docs. Same success probability. Compare interactions}
+
 	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
-
     By assumption, $\Vblind$ has a non-negligible probability to accept after receiving $\sigma$.
 	In other words, let $\Lambda\leftarrow\cVMF{1}$, and define $\Lambda'$ by \cref{decodeMeasureOrder},
+    \Ethan{Give theorem 3.2 an algorithm}
 	then with non-negligible probability
@@
 
-We give a high-level overview of the compiliation results.
+We give a high-level overview of the compiliation results. \Ethan{Maybe just delete it and give name only}
 
@@
 		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, y$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
-			On input $\Lambda'$, it generates $k, td$.
+			Then, using $\Lambda'$, it generates $k, td$.
 			It sends $k, evk, y$ to the prover.
@@
 			It sends $m$ to the verifier.
-		\item The verifier sends the prover a public fair coin $c\in{0,1}$.
+		\item The verifier sends the prover a public coin $c\in\set{0,1}$.
 		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
@@
 \end{protocol}
+
+\Ethan{
+    Need to say more about step 5.
+    It's a compiler here.
+    Need to say stuff about interface
+    see protocol 5.1; protocol is the most important
+    interface uses only lambda
+    if hadamard round, get measurement outcome corresponding to sigma
+    how to decode
+
+    Describe in words what's 5.1
+    Leave author note for theorem for now
+}
 

### 2020-02-09 bqp.tex
Restructure BQP protocols and rewrite proof

@@
 	\begin{enumerate}
-		\item The verifier generates $\Lambda \leftarrow \cVMF{1}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
-\Ethan{Switch steps 1 and 2}
-		\item The prover generates a certificate state $\rho\leftarrow\cPMF{2}(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
-		\item The verifier applies the measurement $\Lambda$ to $\rho$ qubit-by-qubit.
+		\item The prover generates a certificate state $\rho\leftarrow\cPMF{1}(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
+		\item The verifier generates $\Lambda \leftarrow \cVMF{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
+			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
+			It applies $\Lambda$ to $\rho$ qubit-by-qubit.
 			Let $w \in \set{0,1}^m$ denote the measurement outcome.
@@
 
-We compile this protocol using Mahadev's $\mathsf{QHE}$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol for $\BQP$, again with only $X$ and $Z$ measurements.
-The high level idea is to run \cref{proto:BQP} under $\mathsf{QHE}$.
+$\PiMF$ has negligible completeness and soundness.
+
+We compile this protocol using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol for $\BQP$, again with only $X$ and $Z$ measurements.
+The high level idea is to run $\PiMF$ under $\mathsf{QHE}$.
 Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
-The prover then homomorphically evaluate $\cF$ on $y$ to produce $\sigma=\mathsf{QHE.Enc}(\rho)$ \Ethan{Is this actually ok?
-$\sigma$ is a ciphertext corresponding to $\rho$, but it wasn't encrypted.
-In fact it's deteriorated due to homomorphic eval} and send it back to the verifier.
+The prover then homomorphically evaluate $\cF$ on $y$ to produce $\sigma$ which is a ciphertext corresponding to $\rho$, and sends $\sigma$ to the verifier.
 
@@
 
+\Ethan{TODO PROOFREAD ME}
 \begin{thm}
 	\label{decodeMeasureOrder}
-	Let $sk$ be some secret key of $\mathsf{QHE}$.
 	Let $n\in\bbN$.
 	Let $m\in\bbN$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$.
-	Let $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$, where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
 
-	There exists $\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$ where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and polynomial-time algorithm $\widehat{\mathsf{QHE.Dec}}$ such that:
+	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\mathsf{QHE.Dec}}$ s.t.
+	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement:
+	\Ethan{How to specify the existence of $sk$?}
+	$$\cM_\QHE(\Lambda)=\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$$
+	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and
 	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
@@
 	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$
-
 	Clearly,
@@
 
-\Ethan{Give the theorem above a corresponding algorithm}
-
-\Cref{proto:BQP} has negligible completeness and soundness.
-Now we compile it using $\mathsf{QHE}$ in order to also achieve blindness:
+Now we state our construction to compile $\PiMF$ using $\mathsf{QHE}$:
 
@@
 
-	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPMF{2}$.
+	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPMF{1}$.
 	\begin{enumerate}
-		\item The verifier generates $\Lambda\leftarrow\cVMF{1}(x)$.
-			On input $\Lambda$, it computes $\Lambda'$ using \cref{decodeMeasureOrder}.
-			Then it generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$ and $y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
-			It sends $y$ and $evk$ to the prover.
-			\Ethan{Do two steps. Keygens first, lambda next. For keygen step, say more in words and describe $d$. Remember to specify $x$ when talking about $d$ and $\cPMF{2}$}
-		\item The prover homomorphically evaluates $\cPMF{2}$ on input $y$, generating $\sigma\leftarrow\mathsf{QHE.Eval}(\cPMF{2}, y)$.
+		\item The verifier generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$.
+			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
+			It also sends $evk$ to the prover.
+		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\mathsf{QHE.Eval}_{evk}(\cPMF{1}, ct_x)$.
 			It sends $\sigma$ to the verifier qubit-by-qubit.
-		\item The verifier generates $ct\leftarrow\Lambda'(\sigma)$,
-			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct)$,
-			and then $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
+		\item The verifier generates $\Lambda\leftarrow\cVMF{2}(x)$,
+			$\Lambda'\leftarrow\cM_\QHE$,
+			$ct_w\leftarrow\Lambda'(\sigma)$,
+			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
+			and $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
 			It outputs $o$.
@@
 \end{protocol}
-
-\Ethan{Change steps orders above. 1. verifier enc and send y 2. prover sends something back 3. verifier sample lambda}
 
@@
 	The completeness follows by inspection.
-	For blindness, the only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
+	For blindness, the only thing the prover sees is $c$ and $evk$, so it follows directly from $\mathsf{QHE}$'s security.
 
-	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ violating the soundness guarantees of $\Piblind$ 
-	\Ethan{Define some $\epsilon$ here. Also ``non-negligible" = ``noticeable"},
-	then we can use it to construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$.
+	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ with some noticeable acceptance probability $\varepsilon$.
 
-	\Ethan{This construction is too small for a separate box but maybe still be too big to just write it like this?}
-
-	\Ethan{Add the ``simulate" thing back}
+	Then we can construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$ by simulating $(\Vblind(x), \Pblindstar)$ as below:
 
 	We define $\PMFstar$ to first generate
-	$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}$
+	$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
 	and
@@
 
-    \Ethan{Rewrite the following proof again; write in terms of interactions this time. See google docs. Same success probability. Compare interactions}
+	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
+	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
+	Consider the experiment corresponding to $\Piblind$:
+	$$(pk, sk, evk)\leftarrow\QGen(1^n, 1^d)$$
+	$$ct_x\leftarrow\QEnc_{pk}(x)$$
+	$$\sigma\leftarrow\cP_\blind^*(ct_x, evk)$$
+	$$\Lambda\leftarrow\cVMF{2}(x)$$
+	$$\Lambda'\leftarrow\cM_\QHE(\Lambda)$$
+	$$ct_w\leftarrow\Lambda'(\sigma)$$
+	$$w\leftarrow\widehat{\QDec_{sk}}(ct_w)$$
+	$$o\leftarrow\cVMF(x, \Lambda, w)$$
 
-	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
-    By assumption, $\Vblind$ has a non-negligible probability to accept after receiving $\sigma$.
-	In other words, let $\Lambda\leftarrow\cVMF{1}$, and define $\Lambda'$ by \cref{decodeMeasureOrder},
-    \Ethan{Give theorem 3.2 an algorithm}
-	then with non-negligible probability
-	$$\cVMF{3}(x, \Lambda, \widehat{\mathsf{QHE.Dec}_{sk}}(\Lambda'(\sigma))=acc$$
-	which is equivalent to
-	$$\cVMF{3}(x, \Lambda, \Lambda(\rho))=acc$$
-	That is, $\PMFstar$ violates the soundness of $\PiMF$.
+	Compare it with the experiment corresponding to $\PMFstar$:
+	$$(pk, sk, evk)\leftarrow\QGen(1^n, 1^d)$$
+	$$ct_x\leftarrow\QEnc_{pk}(x)$$
+	$$\sigma\leftarrow\cP_\blind^*(ct_x, evk)$$
+	$$\Lambda\leftarrow\cVMF{2}(x)$$
+	$$\rho\leftarrow\QDec_{sk}(\sigma)$$
+	$$w\leftarrow\Lambda(\rho)$$
+	$$o\leftarrow\cVMF(x, \Lambda, w)$$
+
+	By inspection, the only difference between the experiments is how $w$ is obtained from $\sigma$.
+	By \cref{decodeMeasureOrder}, the two ways are equivalent.
 \end{prf}
@@
 Note that Mahadev's measurement protocol can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol, and Protocol 3 is a $\QPIP_1$ protocol with X, Z measurement and negligible soundness.
-Thus the resulting protocol $(P', V')$ is a O(1)-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$
+Thus the resulting protocol $(P', V')$ \Ethan{name?} is a O(1)-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$
 
@@
 	\begin{enumerate}
-		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, y$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
+		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, ct_x$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
 			Then, using $\Lambda'$, it generates $k, td$.
-			It sends $k, evk, y$ to the prover.
-		\item The prover, on inputs $k, evk, y$, generates classical ``commitment" $m$ and internal state $\ket{st}$.
-			It sends $m$ to the verifier.
+			It sends $k, evk, ct_x$ to the prover.
+		\item The prover, on inputs $k, evk, ct_x$, generates classical ``commitment" $y$ and internal state $\ket{st}$.
+			It sends $y$ to the verifier.
 		\item The verifier sends the prover a public coin $c\in\set{0,1}$.
 		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
-		\item The verifier, on inputs $k, td, m, c, a, sk$, generates and outputs either $acc$ or $rej$.
+		\item The verifier, on inputs $k, td, y, c, a, sk$, generates and outputs either $acc$ or $rej$.
 	\end{enumerate}

### 2020-02-09 bqp.tex
Add the other parallel rep paper
Give more protocols names

@@
 \nc{\cPblind}[1]{\ensuremath{\cP_{\MF,#1}}}
+
+\def\bz{\mathsf{blind, 0}}
+\nc{\Pibz}{\ensuremath{\Pi_\bz}}
+\nc{\Vbz}{\ensuremath{V_\bz}}
+\nc{\Pbz}{\ensuremath{P_\bz}}
+
+\def\bzrep{\mathsf{blind, 0, rep}}
+\nc{\Pibzrep}{\ensuremath{\Pi_\bzrep}}
 
@@
 
-We give a high-level overview of the compiliation results. \Ethan{Maybe just delete it and give name only}
+We give a high-level overview of the compiliation results.
 
-\begin{protocol}{\Cref{proto:BlindBQP} compiled using Mahadev's measurement protocol \Ethan{Give this a name}}
+\begin{protocol}{Blind $\QPIP_0$ protocol $\Pibz$ for $BQP$ language $L$}
 	\label{proto:QPIP0BQP}
@@
 \begin{prf}
-	See \cite{parallelrep} \Ethan{TODO FIND AND CITE the other parallel rep. paper}
+	See \cite{parallelrep, alagic2019twomessage}
 \end{prf}
@@
 	\begin{enumerate}
-		\item Run \cref{proto:repQPIP0BQP} for all $L\in\cL$ in parallel using input $x$. The verifier gets outputs $v_{i, b}\in\set{Acc, Rej}$.
+		\item Run $\Pibzrep$ for all $L\in\cL$ in parallel using input $x$. The verifier gets outputs $v_{i, b}\in\set{Acc, Rej}$.
 		\item If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.

### 2020-02-09 bqp.tex
Make another editorial pass at BQP section

@@
 
-\Ethan{TODO Read other papers and see if I can copy their tones and phrasing}
-
-\Ethan{Note to self: If the original is wordy, just keep it the way it is. Don't try to simplify existing dfns.}
-
 \Ethan{TODO Intro this section}
-
-\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf for conventions. Mal. parties have stars, protos use Pi. Stuff like $r(P(w), V )(1n ,(M, x, t))$ }
-
-\Ethan{More notation, fix interfaces}
-
-\Ethan{Fix up to proto 3 and proofs}
 
@@
 
-We start with a high-level description of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which is in turn taken from \cite{mf16}.
+We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{mahadev_delegation}, which is in turn taken from \cite{mf16}.
 
@@
 Roughly, on input $x\in\set{0,1}^n$, the prover sends a $m$-qubit certificate state $\rho$ to the verifier qubit-by-qubit.
-The verifier samples a product measurement $\Lambda$ of $X$ and $Z$s according to certain distribution to apply to $\rho$
+The verifier samples a product measurement $\Lambda$ of $X$ and $Z$s according to a certain distribution, and applies it to $\rho$.
 The verifier then, using the measurement results, decides whether to accept or reject.
@@
 
-We compile this protocol using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol for $\BQP$, again with only $X$ and $Z$ measurements.
+We compile $\PiMF$ using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol $\Piblind$ for $\BQP$, again with only $X$ and $Z$ measurements.
 The high level idea is to run $\PiMF$ under $\mathsf{QHE}$.
 Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
-The prover then homomorphically evaluate $\cF$ on $y$ to produce $\sigma$ which is a ciphertext corresponding to $\rho$, and sends $\sigma$ to the verifier.
+The prover then homomorphically evaluates $\cF$ on $y$ to produce $\sigma$ and sends it to the verifier.
 
@@
 Its ciphertexts consists of a Pauli one-time-padded plaintext and classically encrypted Pauli keys.
-Pauli one-time-pads commute with $X$ and $Z$ measurements, so the verifier can measure the one-time-padded state as usual then correct the measurement results using the Pauli keys.
-We state this observation as the following theorem:
+Pauli one-time-pads commute with $X$ and $Z$ measurements, so the verifier can measure the one-time-padded state as usual, then correct the measurement results using the Pauli keys.
+Now we state and prove this observation in more precise terms.
 
@@
 	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement:
-	\Ethan{How to specify the existence of $sk$?}
 	$$\cM_\QHE(\Lambda)=\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$$
@@
 
-Now we state our construction to compile $\PiMF$ using $\mathsf{QHE}$:
+Now we state our results of compiling $\PiMF$ using $\mathsf{QHE}$:
 
@@
 \end{protocol}
-
-As we will prove, $\Piblind$ is a $\QPIP_1$, constant round, and blind protocol for $\BQP$ with negligible completeness and soundness.
 
@@
 
-Finally, we prove Thm 3.1 by applying Mahadev's measurement protocol~\cite{mahadev_delegation} to Protocol 3 to compile it into a $\QPIP_0$ protocol $(P', V')$ \Ethan{fix name}.
-Note that Mahadev's measurement protocol can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol, and Protocol 3 is a $\QPIP_1$ protocol with X, Z measurement and negligible soundness.
-Thus the resulting protocol $(P', V')$ \Ethan{name?} is a O(1)-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$
+Finally, we prove \cref{thm:QPIP0BQP}.
+We use Mahadev's measurement protocol from \cite{mahadev_delegation} which can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol.
+The resulting protocol $\Pibz$ is a constant-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$ and negligible completeness.
 
-We give a high-level overview of the compiliation results.
+In order to prove blindness, we give a high-level overview of the compiliation results.
+\Ethan{Need to discuss about this}
 
@@
 For $i\in\bbN, b\in\set{0,1}$, define the language $L_{i, b}=\set{x:f_i(x)=b}$.
-Define $\cL$ to be the collection of these languages: $\cL = \set{L_{i, b}: i\in[m], b\in\set{0, 1}}$.
+Furthermore, define $\cL$ to be the collection of these languages: $\cL = \set{L_{i, b}: i\in[m], b\in\set{0, 1}}$.
 
-\begin{protocol}{Blind and verifiable $\QPIP_0$ delegation for $\FBQP$}
+\begin{protocol}{Blind and verifiable $\QPIP_0$ protocol $\Pi_{\FBQP}$ for $\FBQP$ language $L$}
 	\label{proto:QPIP0FBQP}
@@
 	\begin{enumerate}
-		\item Run $\Pibzrep$ for all $L\in\cL$ in parallel using input $x$. The verifier gets outputs $v_{i, b}\in\set{Acc, Rej}$.
-		\item If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.
-		\item Otherwise, define $y_i = b$ where $v_{i, b}=Acc$. This gives $y\in\set{0,1}^m$
-		\item Verifier outputs $y$
+		\item Run $\Pibzrep$ for all $L\in\cL$ in parallel using input $x$.
+		\item The verifier gets outputs $v_{i, b}\in\set{acc, rej}$.
+			If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.
+			Otherwise, define $y_i = b$ where $v_{i, b}=acc$. This gives $y\in\set{0,1}^m$.
+			The verifier accepts and outputs $y$.
 	\end{enumerate}
@@
 \begin{theorem}
-	\Cref{proto:QPIP0FBQP} has negligible completeness and soundness, and is blind.
+	$\Pi_{\FBQP}$ has negligible completeness and soundness, and is blind.
 \end{theorem}
@@
 
-	Based on the soundness of \cref{proto:BlindBQP}, $v_{i, b}=Acc$ implies that $x\in L_{i, b}\Rightarrow f_i(x)=b$ with overwhelming probability.
+	By the soundness of $\Pibzrep$, $v_{i, b}=acc$ implies that $x\in L_{i, b}\Rightarrow f_i(x)=b$ with overwhelming probability.
 	In other words, $y_i$ is correct with probability $1-\varepsilon_i$ where $\varepsilon_i=\negl(n)$.

### 2020-02-09 blind.tex
Rewrite blind sampbqp section

@@
 \section{Constant-Round and Blind $\QPIP_1$ protocol for $\SampBQP$}
+
+\def\Samp{\mathsf{Samp}}
+\nc{\PiSamp}{\ensuremath{\Pi_\Samp}}
+\nc{\VSamp}{\ensuremath{V_\Samp}}
+\nc{\PSamp}{\ensuremath{P_\Samp}}
+\nc{\PSampstar}{\ensuremath{P_\Samp^*}}
+\nc{\cVSamp}[1]{\ensuremath{\cV_{\Samp,#1}}}
+\nc{\cPSamp}[1]{\ensuremath{\cP_{\Samp,#1}}}
+
+\def\SampB{\mathsf{Samp, blind}}
+\nc{\PiSampB}{\ensuremath{\Pi_\SampB}}
 
@@
 
-\begin{protocol}{Compiling \cref{ProtoQPIP1} using $\mathsf{QHE}$}
-	\label{proto:QPIP1Samp}
+First we restate \cref{ProtoQPIP1} in more convenient terms.
+
+\begin{protocol}{Our 1-message $\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ language $L$}
+	Common input: $x\in\set{0,1}^n$. 
 	\begin{enumerate}
-		\item The verifier runs $\mathsf{QHE.keygen}(1^\lambda, 1^L)$ where $L$ is the depth of circuit corresponding to the honest prover's action in \cref{ProtoQPIP1}
-		\item The verifier encrypts its input and runs \cref{ProtoQPIP1} with the prover homomorphically
-		\item The verifier measures the incoming ciphertext according to \cref{decodeMeasureOrder}
-		\item The verifier decodes the measurement results to get its output
+		\item The prover generates a certificate state $\rho\leftarrow\cPSamp{1}(x)$ and sends it to the verifier qubit-by-qubit.
+		\item The verifier generates $\Lambda \leftarrow \cVSamp{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
+			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
+			It applies $\Lambda$ to $\rho$ qubit-by-qubit.
+			Let $w \in \set{0,1}^m$ denote the measurement outcome.
+			It verifies the measurement outcome and produces a decision $o\leftarrow\cVSamp{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVSamp{3}$ is a classical polynomial-time algorithm.
+	\end{enumerate}
+\end{protocol}
+
+Note that it is of the same form as its $\BQP$ counterpart $\PiSamp$ found in \cref{subsec:BlindBQP}.
+
+So we can compile it into $\PiSampB$ to achieve blindness in the same way:
+
+\begin{protocol}{Blind $\QPIP_1$ 1-message protocol $\Piblind = (\Pblind, \Vblind)$ for $\SampBQP$ language $L$}
+	\label{proto:BlindBQP}
+	Verifier's input: $x\in\set{0,1}^n$.
+
+	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPSamp{1}$.
+	\begin{enumerate}
+		\item The verifier generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPSamp{1}(x)$.
+			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
+			It also sends $evk$ to the prover.
+		\item The prover homomorphically evaluates $\cPSamp{1}$ on input $ct_x$, generating $\sigma\leftarrow\mathsf{QHE.Eval}_{evk}(\cPSamp{1}, ct_x)$.
+			It sends $\sigma$ to the verifier qubit-by-qubit.
+		\item The verifier generates $\Lambda\leftarrow\cVSamp{2}(x)$,
+			$\Lambda'\leftarrow\cM_\QHE$,
+			$ct_w\leftarrow\Lambda'(\sigma)$,
+			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
+			and $o\leftarrow\cVSamp{3}(x, \Lambda, w)$.
+			It outputs $o$.
 	\end{enumerate}
@@
 \begin{thm}
-	\cref{proto:QPIP1Samp} has the same completeness and soundness guarantees as \cref{ProtoQPIP1}
+	$\PiSampB$ has the same completeness and soundness guarantees as $\PiSamp$ and is blind.
 \end{thm}
 \begin{prf}
-	A honest prover still gets accepted with overwhelming probability by the correctness of $\mathsf{QHE}$. \Ethan{Not sure if too hand-wavy}
-
-	As for soundness, a cheating prover cannot do better under this compiliation, since each message still decodes to some plaintext.
-
-	In other words, anything a cheating prover can do after the compiliation, there exists a corresponding strategy in the version before.
-	\Ethan {Ahhhh this is not rigorous at all}
+	The proof of \cref{thm:BlindBQP} works, up to changing some labels.
+	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either.
+	The proof only shows that the compiliation preserves soundness.
 \end{prf}
-
-\begin{thm}
-	\cref{proto:QPIP1Samp} is IND-CPA secure.
-\end{thm}
-\begin{prf}
-	The only thing the prover gets is $\mathsf{QHE.Enc}_{pk}(x)$, $pk$, and $evk$. So this follows directly from the security of $\mathsf{QHE}$.
-\end{prf}

### 2020-02-09 bqp.tex
Rewrite blind sampbqp section
Fix some labels and references

@@
 
-We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{mahadev_delegation}, which is in turn taken from \cite{mf16}.
+We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{FOCS:Mahadev18a}, which is in turn taken from \cite{mf16}.
 
@@
 \begin{thm}
+	\label{thm:BlindBQP}
 	$\Piblind$ has negligible completeness and soundness, and is blind.
@@
 Finally, we prove \cref{thm:QPIP0BQP}.
-We use Mahadev's measurement protocol from \cite{mahadev_delegation} which can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol.
+We use Mahadev's measurement protocol from \cite{FOCS:Mahadev18a} which can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol.
 The resulting protocol $\Pibz$ is a constant-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$ and negligible completeness.

### 2020-02-09 hamiltonian.tex
Fix some labels and references

@@
 The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
-Protocols to delegate $\BQP$ computations such as \cite{mahadev_delegation} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
+Protocols to delegate $\BQP$ computations such as \cite{FOCS:Mahadev18a} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
 We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.

### 2020-02-09 preliminaries.tex
Restructure BQP protocols and rewrite proof
Fix some labels and references

@@
 \subsection{Quantum Prover Interactive Protocol (QPIP)}
-We classify the interaction between a (almost classical) client and a quantum server for sampling problems, extending the classification by \cite{mahadev_delegation}.
+We classify the interaction between a (almost classical) client and a quantum server for sampling problems, extending the classification by \cite{FOCS:Mahadev18a}.
 
@@
 As we will see, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then $\mathsf{QHE}$ can be used as a compiler to achieve blindness.
+
+\def\QHE{\mathsf{QHE}}
+\def\QGen{\mathsf{QHE.Keygen}}
+\def\QEnc{\mathsf{QHE.Enc}}
+\def\QEval{\mathsf{QHE.Eval}}
+\def\QDec{\mathsf{QHE.Dec}}

### 2020-02-09 qpip0.tex
Updates from Overleaf
Fix some labels and references

@@
 
-\hannote{In this section, we modify the construction of \cite{mahadev_delegation} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}
+\hannote{In this section, we modify the construction of \cite{FOCS:Mahadev18a} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}
 
-We then extend our scheme for $\QPIP_0$ using results from \cite{mahadev_delegation}.
+We then extend our scheme for $\QPIP_0$ using results from \cite{FOCS:Mahadev18a}.
 
-Here we combine \autoref{QPIP1thm} with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients.
+Here we combine \autoref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients.
 Combining them will cost polynomially rounds, so we use results from \cite{parallelrep} that allows parallel repetition to construct a constant-round protocol.
@@
 \hannote{Ethan old description before parallel rep.}
-As a warm-up, we  restate the construction in \cite{mahadev_delegation}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.
+As a warm-up, we  restate the construction in \cite{FOCS:Mahadev18a}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.
 
@@
 
-In her groundbreaking work, Mahadev~\cite{mahadev_delegation} gave the following 4-round interactive protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine.
+In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave the following 4-round interactive protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine.
 
@@
 
-\begin{lemma}[binding property of  Protocol~\ref{proto:urmila4}\cite{mahadev_delegation}]
+\begin{lemma}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
 If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
@@
 \begin{align*}  
-  \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
+  \Pr\left[\ext_i\left(\frac{\ket{i}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
   \end{align*}   \hannote{$M_x?$}

### 2020-02-09 qpip.tex
Change autoref to cref

@@
 	\label{ProtoGroundStateCheck}
-	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
+	There is a $\QPIP_1$ protocol for \cref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
 \end{lemma}
@@
 			\begin{enumerate}
-				\item The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
+				\item The verifier runs \cref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
 				\item If the test passes, increment counter $c$.
@@
 
-	So we can apply \autoref{deFinetti}. $\exists\set{w_i, \rho_i}$ such that:
+	So we can apply \cref{deFinetti}. $\exists\set{w_i, \rho_i}$ such that:
 	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+n}(\sigma'-\sum_i w_i\rho_i^{\otimes n+m})}=O(\varepsilon)$$
@@
 
-	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
+	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \cref{AlgGroundStateCheck}.
 	So the accept chance of this prover is $\sum_j w_j p_j>\delta$
@@
 
-	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ where $\rho_i$ has over probability $1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck} is overwhelming.
+	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ where $\rho_i$ has over probability $1-2\varepsilon$ to be accepted by \cref{AlgGroundStateCheck} is overwhelming.
 
-	Such $\rho_i$ is $O(\negl(\varepsilon))$-close to $\ket{\psi_{C'(x)}}$, by applying a Chernoff bound to \autoref{ThmXZCheck}.
+	Such $\rho_i$ is $O(\negl(\varepsilon))$-close to $\ket{\psi_{C'(x)}}$, by applying a Chernoff bound to \cref{ThmXZCheck}.
 

### 2020-02-09 blind.tex
Fix some labels and references
Fix wording

@@
 \nc{\PiSampB}{\ensuremath{\Pi_\SampB}}
+\nc{\VSampB}{\ensuremath{V_\SampB}}
+\nc{\PSampB}{\ensuremath{P_\SampB}}
 
@@
 
-\begin{protocol}{Blind $\QPIP_1$ 1-message protocol $\Piblind = (\Pblind, \Vblind)$ for $\SampBQP$ language $L$}
-	\label{proto:BlindBQP}
+\begin{protocol}{Blind $\QPIP_1$ 1-message protocol $\PiSampB = (\PSampB, \VSampB)$ for $\SampBQP$ language $L$}
+	\label{proto:BlindSampBQP}
 	Verifier's input: $x\in\set{0,1}^n$.
@@
 \begin{prf}
-	The proof of \cref{thm:BlindBQP} works, up to changing some labels.
-	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either.
-	The proof only shows that the compiliation preserves soundness.
+	The proof is identical to that of \cref{thm:BlindBQP} up to relabeling.
+	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either; the proof only shows that the compiliation preserves soundness.
 \end{prf}

### 2020-02-09 bqp.tex
Make another editorial pass

@@
 
-We then apply the recent result parallel repetition get negligible soundness again:
+We use the recent results \cite{parallelrep, alagic2019twomessage} to apply parallel repetition to $\Pibz$ to get $\Pibzrep$ which has negligible soundness.
+
+\Ethan{Is the following even necessary?}
 
@@
 	Run $m=\poly(n)$ copies of \cref{proto:QPIP0BQP} in parallel. Accept if the proportion of accepted copies is over some certain threshold $p(n)\in(0, 1)$.
-
 \end{protocol}
@@
 \begin{thm}
-	\cref{proto:repQPIP0BQP} has negligible completeness and soundness
+	\cref{proto:repQPIP0BQP} has negligible completeness and soundness and is blind.
 \end{thm}
@@
 
-	By the soundness of $\Pibzrep$, $v_{i, b}=acc$ implies that $x\in L_{i, b}\Rightarrow f_i(x)=b$ with overwhelming probability.
+	By the soundness of $\Pibzrep$, $v_{i, b}=acc$ implies that $x\in L_{i, b}$ with overwhelming probability.
 	In other words, $y_i$ is correct with probability $1-\varepsilon_i$ where $\varepsilon_i=\negl(n)$.

### 2020-02-09 blind.tex
Add notes from Skype discussion

@@
 	The proof is identical to that of \cref{thm:BlindBQP} up to relabeling.
+	\Ethan{too hand-wavy still, can still say ``identically simulates"}
 	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either; the proof only shows that the compiliation preserves soundness.
+	\Ethan{Soundness def. is different}
 \end{prf}

### 2020-02-09 bqp.tex
Add notes from Skype discussion

--- 2020-02-09 bqp.tex
@@
 \nc{\cVblind}[1]{\ensuremath{\cV_{\blind,#1}}}
-\nc{\cPblind}[1]{\ensuremath{\cP_{\MF,#1}}}
+\nc{\cPblind}[1]{\ensuremath{\cP_{\blind,#1}}}
 
@@
 
+\Ethan{Use only pk, sk and combine evk into pk}
+
 \subsection{Blind Delegation for BQP}
@@
 We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
+\Ethan{Write outline here; highlight key ideas/steps}
 We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.
-
 We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{FOCS:Mahadev18a}, which is in turn taken from \cite{mf16}.
 
-This is a one-message $\QPIP_1$ protocol with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
+This is a one-message $\QPIP_1$ protocol $\PiMF$ with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
 Roughly, on input $x\in\set{0,1}^n$, the prover sends a $m$-qubit certificate state $\rho$ to the verifier qubit-by-qubit.
-The verifier samples a product measurement $\Lambda$ of $X$ and $Z$s according to a certain distribution, and applies it to $\rho$.
+The verifier samples a product measurement \Ethan{for consistency, ``measurement basis choice"} $\Lambda$ of $X$ and $Z$s according to a certain distribution, and applies it to $\rho$.
 The verifier then, using the measurement results, decides whether to accept or reject.
@@
 	\begin{enumerate}
-		\item The prover generates a certificate state $\rho\leftarrow\cPMF{1}(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
+		\item The prover generates a certificate state $\rho\leftarrow\cPMF{1}(x)$ and sends $\rho$ to the verifier qubit-by-qubit. \Ethan{Say it's $m$ qubits}
 		\item The verifier generates $\Lambda \leftarrow \cVMF{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
-			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
+			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
 			It applies $\Lambda$ to $\rho$ qubit-by-qubit.
@@
 \end{protocol}
-
+\begin{thm}
+    \Ethan{Add reference}
     $\PiMF$ has negligible completeness and soundness.
+\end{thm}
 
@@
 Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
-The prover then homomorphically evaluates $\cF$ on $y$ to produce $\sigma$ and sends it to the verifier.
+The prover then homomorphically evaluates $\cPMF{3}$ on $ct_x$ to produce $\sigma$ and sends it to the verifier.
 
 Now the verifier needs to obtain the measurement outcome $w$ from the encrypted state $\sigma$ using qubit-by-qubit $X$ and $Z$ measurements.
-This may not be possible in general, but we observe that $\mathsf{QHE}$ allows this. 
+This may not be possible in general, but we observe that Mahadev's $\mathsf{QHE}$ allows this. 
 Its ciphertexts consists of a Pauli one-time-padded plaintext and classically encrypted Pauli keys.
@@
 	Let $n\in\bbN$.
-	Let $m\in\bbN$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$.
+	Let $m\in\bbN$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$. \Ethan{$m$ isn't well-defined this way; missing security param. and depth param.}
+
+	\Ethan{Keygen here}
 
@@
 Now we state our results of compiling $\PiMF$ using $\mathsf{QHE}$:
+\Ethan{We state our construction of blind QPIP 1 for BQP by compiling...}
 
@@
 
-	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPMF{1}$.
 	\begin{enumerate}
@@
 			It also sends $evk$ to the prover.
-		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\mathsf{QHE.Eval}_{evk}(\cPMF{1}, ct_x)$.
+		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\cPblind{1}(evk, ct_x)=\mathsf{QHE.Eval}_{evk}(\cPMF{1}, ct_x)$.
 			It sends $\sigma$ to the verifier qubit-by-qubit.
 		\item The verifier generates $\Lambda\leftarrow\cVMF{2}(x)$,
-			$\Lambda'\leftarrow\cM_\QHE$,
+			$\Lambda'\leftarrow\cM_\QHE(\Lambda)$,
 			$ct_w\leftarrow\Lambda'(\sigma)$,
@@
 
-	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ with some noticeable acceptance probability $\varepsilon$.
-
+	Suppose for the sake of contradiction \Ethan{First specify this is for soundness proof} that there exists some cheating prover $\Pblindstar$ with some noticeable acceptance probability $\varepsilon$.
 	Then we can construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$ by simulating $(\Vblind(x), \Pblindstar)$ as below:
@@
 	$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
-	It then sends $y$ and $evk$ to $\Pblindstar$ and gets $\sigma$ back.
+	It then sends $ct_x$ and $evk$ to $\Pblindstar$ \Ethan{Just run it, don't send it} and gets $\sigma$ back.
 	Finally, it decrypts
@@
 	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
-	Consider the experiment corresponding to $\Piblind$:
+	Consider the experiment corresponding to $(\Vblind, \Pblindstar)$:
 	$$(pk, sk, evk)\leftarrow\QGen(1^n, 1^d)$$
@@
 
+    \Ethan{See google docs; remove the displayed math above and say in words}
 	By inspection, the only difference between the experiments is how $w$ is obtained from $\sigma$.
 	By \cref{decodeMeasureOrder}, the two ways are equivalent.
+	\Ethan{Here finish the proof by contradiction. Something about epsilon.}
 \end{prf}

### 2020-02-09 blind.tex
Combine evk into pk and resolve other simple notes

@@
 	\begin{enumerate}
-		\item The verifier generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPSamp{1}(x)$.
+		\item The verifier generates $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPSamp{1}(x)$.
 			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
-			It also sends $evk$ to the prover.
-		\item The prover homomorphically evaluates $\cPSamp{1}$ on input $ct_x$, generating $\sigma\leftarrow\mathsf{QHE.Eval}_{evk}(\cPSamp{1}, ct_x)$.
+			It also sends $pk$ to the prover.
+		\item The prover homomorphically evaluates $\cPSamp{1}$ on input $ct_x$, generating $\sigma\leftarrow\QEval_{pk}(\cPSamp{1}, ct_x)$.
 			It sends $\sigma$ to the verifier qubit-by-qubit.

### 2020-02-09 bqp.tex
Combine evk into pk and resolve other simple notes

@@
 This is a one-message $\QPIP_1$ protocol $\PiMF$ with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
-Roughly, on input $x\in\set{0,1}^n$, the prover sends a $m$-qubit certificate state $\rho$ to the verifier qubit-by-qubit.
-The verifier samples a product measurement \Ethan{for consistency, ``measurement basis choice"} $\Lambda$ of $X$ and $Z$s according to a certain distribution, and applies it to $\rho$.
+Roughly, on input $x\in\set{0,1}^n$, the prover sends a certificate state $\rho$ to the verifier qubit-by-qubit.
+The verifier samples a measurement basis choice $\Lambda$ according to a certain distribution, and applies it to $\rho$.
 The verifier then, using the measurement results, decides whether to accept or reject.
@@
 	\begin{enumerate}
-		\item The prover generates a certificate state $\rho\leftarrow\cPMF{1}(x)$ and sends $\rho$ to the verifier qubit-by-qubit. \Ethan{Say it's $m$ qubits}
+		\item The prover generates a $m$-qubit certificate state $\rho\leftarrow\cPMF{1}(x)$ and sends $\rho$ to the verifier qubit-by-qubit.
 		\item The verifier generates $\Lambda \leftarrow \cVMF{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
@@
 \end{protocol}
-\begin{thm}
-    \Ethan{Add reference}
+\begin{thm}[from \cite{FOCS:Mahadev18a, mf16}]
     $\PiMF$ has negligible completeness and soundness.
@@
 
-\Ethan{TODO PROOFREAD ME}
 \begin{thm}
 	\label{decodeMeasureOrder}
-	Let $n\in\bbN$.
-	Let $m\in\bbN$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$. \Ethan{$m$ isn't well-defined this way; missing security param. and depth param.}
+	Let $n, L\in\bbN$.
+	Let $(pk, sk)\leftarrow\QGen(1^n, 1^L)$
+	Let $m=\poly(n)$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$.
 
-	\Ethan{Keygen here}
-
-	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\mathsf{QHE.Dec}}$ s.t.
+	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\QDec_{sk}}$ s.t.
 	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement:
@@
 	\begin{enumerate}
-		\item The verifier generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$.
+		\item The verifier generates $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$.
 			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
-			It also sends $evk$ to the prover.
-		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\cPblind{1}(evk, ct_x)=\mathsf{QHE.Eval}_{evk}(\cPMF{1}, ct_x)$.
+			It also sends $pk$ to the prover.
+		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\cPblind{1}(pk, ct_x)=\QEval_{pk}(\cPMF{1}, ct_x)$.
 			It sends $\sigma$ to the verifier qubit-by-qubit.
@@
 	The completeness follows by inspection.
-	For blindness, the only thing the prover sees is $c$ and $evk$, so it follows directly from $\mathsf{QHE}$'s security.
+	For blindness, the only thing the prover sees is $c$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.
 
@@
 	We define $\PMFstar$ to first generate
-	$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
+	$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
 	and
 	$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
-	It then sends $ct_x$ and $evk$ to $\Pblindstar$ \Ethan{Just run it, don't send it} and gets $\sigma$ back.
+	It then sends $ct_x$ and $pk$ to $\Pblindstar$ \Ethan{Just run it, don't send it} and gets $\sigma$ back.
 	Finally, it decrypts
@@
 	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
-	Consider the experiment corresponding to $(\Vblind, \Pblindstar)$:
-	$$(pk, sk, evk)\leftarrow\QGen(1^n, 1^d)$$
-	$$ct_x\leftarrow\QEnc_{pk}(x)$$
-	$$\sigma\leftarrow\cP_\blind^*(ct_x, evk)$$
-	$$\Lambda\leftarrow\cVMF{2}(x)$$
-	$$\Lambda'\leftarrow\cM_\QHE(\Lambda)$$
-	$$ct_w\leftarrow\Lambda'(\sigma)$$
-	$$w\leftarrow\widehat{\QDec_{sk}}(ct_w)$$
-	$$o\leftarrow\cVMF(x, \Lambda, w)$$
 
-	Compare it with the experiment corresponding to $\PMFstar$:
-	$$(pk, sk, evk)\leftarrow\QGen(1^n, 1^d)$$
-	$$ct_x\leftarrow\QEnc_{pk}(x)$$
-	$$\sigma\leftarrow\cP_\blind^*(ct_x, evk)$$
-	$$\Lambda\leftarrow\cVMF{2}(x)$$
-	$$\rho\leftarrow\QDec_{sk}(\sigma)$$
-	$$w\leftarrow\Lambda(\rho)$$
-	$$o\leftarrow\cVMF(x, \Lambda, w)$$
+	Observe the experiments $A$ and $B$ \Ethan{TODO} are identical except...
 
@@
 	\begin{enumerate}
-		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, ct_x$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
+		\item The verifier generates $\Lambda, \Lambda', pk, sk, ct_x$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
 			Then, using $\Lambda'$, it generates $k, td$.
-			It sends $k, evk, ct_x$ to the prover.
-		\item The prover, on inputs $k, evk, ct_x$, generates classical ``commitment" $y$ and internal state $\ket{st}$.
+			It sends $k, pk, ct_x$ to the prover.
+		\item The prover, on inputs $k, pk, ct_x$, generates classical ``commitment" $y$ and internal state $\ket{st}$.
 			It sends $y$ to the verifier.

### 2020-02-09 preliminaries.tex
Combine evk into pk and resolve other simple notes

@@
 
+\def\QHE{\mathsf{QHE}}
+\def\QGen{\mathsf{QHE.Keygen}}
+\def\QEnc{\mathsf{QHE.Enc}}
+\def\QEval{\mathsf{QHE.Eval}}
+\def\QDec{\mathsf{QHE.Dec}}
+
 We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
@@
 	\begin{itemize}
-		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
+		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, sk)$
 		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
 		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
-		\item $\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
+		\item $\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l)\rightarrow c_f$
 	\end{itemize}
@@
 $\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
-$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
+$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
 where $f$ is specified by a circuit of depth at most $L$.
@@
 	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
-	$$\abs{Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
-	where $(pk, evk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
+	$$\abs{Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
+	where $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
 \end{dfn}
@@
 \begin{itemize}
-	\item $\mathsf{QHE.Keygen}$ can be done classically.
-	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
+	\item $\QGen$ can be done classically.
+	\item In the case where the plaintext is classical, $\QEnc$ can be done classically.
 	\item Its ciphertext takes the form $(X^xZ^z\rho Z^zX^x, c_{x, z})$, where $\rho$ is the plaintext and $c_{x, z}$ is a ciphertext that decodes to $(x, z)$ under a certain classical homomorphic encryption scheme.
@@
 
-As we will see, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then $\mathsf{QHE}$ can be used as a compiler to achieve blindness.
-
-\def\QHE{\mathsf{QHE}}
-\def\QGen{\mathsf{QHE.Keygen}}
-\def\QEnc{\mathsf{QHE.Enc}}
-\def\QEval{\mathsf{QHE.Eval}}
-\def\QDec{\mathsf{QHE.Dec}}
+As we will see, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then $\QHE$ can be used as a compiler to achieve blindness.

### 2020-02-10 bqp.tex
Implement more Skype call comments

@@
 \Ethan{TODO Intro this section}
-
-\Ethan{Use only pk, sk and combine evk into pk}
 
@@
 
-Now we state our results of compiling $\PiMF$ using $\mathsf{QHE}$:
-\Ethan{We state our construction of blind QPIP 1 for BQP by compiling...}
+Now we state our construction of blind QPIP 1 for BQP by compiling $\PiMF$ using $\QHE$:
 
@@
 			It also sends $pk$ to the prover.
-		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\cPblind{1}(pk, ct_x)=\QEval_{pk}(\cPMF{1}, ct_x)$.
+		\item The prover computes $\sigma\leftarrow\cPblind{1}$ by homomorphically evaluating $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\QEval_{pk}(\cPMF{1}, ct_x)$.
 			It sends $\sigma$ to the verifier qubit-by-qubit.
@@
 	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
-
-	Observe the experiments $A$ and $B$ \Ethan{TODO} are identical except...
-
-    \Ethan{See google docs; remove the displayed math above and say in words}
-	By inspection, the only difference between the experiments is how $w$ is obtained from $\sigma$.
+	Observe the experiments $A$ and $B$ \Ethan{TODO} are identical except how $w$ is obtained from $\sigma$.
+	\Ethan{TODO Make more precise}
 	By \cref{decodeMeasureOrder}, the two ways are equivalent.
@@
 
-$k$ has the additional properties to not leak information on $\Lambda'$, so the compliation preserves blindness. \Ethan{How to make this more rigorous?}
+For blindness, recall that the prover receives $ct_x = Enc(x), evk, k, c$ from the verifier.
+Blindness follows by the semantic security of QFHE and the fact that k computationally hides the basis choice $\Lambda$.
+\Ethan{This sentence is from google docs so keep it around}
 
@@
 \begin{thm}
-	\cref{proto:repQPIP0BQP} has negligible completeness and soundness and is blind.
+	\cref{proto:repQPIP0BQP} has negligible completeness and soundness.
 \end{thm}
 \begin{prf}
+	\Ethan{Don't open separate proof env}
 	See \cite{parallelrep, alagic2019twomessage}

### 2020-02-17 bqp.tex
Resolve a couple action items

@@
 			It also sends $pk$ to the prover.
-		\item The prover computes $\sigma\leftarrow\cPblind{1}$ by homomorphically evaluating $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\QEval_{pk}(\cPMF{1}, ct_x)$.
+		\item The prover computes $\sigma\leftarrow\cPblind{1}(pk, ct_x)$ by homomorphically evaluating $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\QEval_{pk}(\cPMF{1}, ct_x)$.
 			It sends $\sigma$ to the verifier qubit-by-qubit.
@@
 
-	Suppose for the sake of contradiction \Ethan{First specify this is for soundness proof} that there exists some cheating prover $\Pblindstar$ with some noticeable acceptance probability $\varepsilon$.
+	Now we prove the soundness of $\Piblind$.
+	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ with some noticeable acceptance probability $\varepsilon$.
 	Then we can construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$ by simulating $(\Vblind(x), \Pblindstar)$ as below:
@@
 	and
-	$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
-	It then sends $ct_x$ and $pk$ to $\Pblindstar$ \Ethan{Just run it, don't send it} and gets $\sigma$ back.
+	$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
+	It then runs $\sigma\leftarrow\cPblind{1}(pk, ct_x)$
 	Finally, it decrypts
@@
 	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
-	Observe the experiments $A$ and $B$ \Ethan{TODO} are identical except how $w$ is obtained from $\sigma$.
-	\Ethan{TODO Make more precise}
-	By \cref{decodeMeasureOrder}, the two ways are equivalent.
-	\Ethan{Here finish the proof by contradiction. Something about epsilon.}
+	Observe that the experiments $(\PMFstar, \VMF)(x)$ and $(\Pblindstar, \Vblind(x))$ are identical except for how $w$ is obtained from $\sigma$.
+	so by \cref{decodeMeasureOrder} they are equivalent.
+	Hence we have $\PMFstar$ with noticeable acceptance probability $\varepsilon$, which is a contradiction.
 \end{prf}
@@
 	Run $m=\poly(n)$ copies of \cref{proto:QPIP0BQP} in parallel. Accept if the proportion of accepted copies is over some certain threshold $p(n)\in(0, 1)$.
+
 \end{protocol}

### 2020-02-22 stateprep.tex
Add RSP section

\section{Remote State Preparation}

\Ethan{TODO work on the writing}

\def\QV{\mathsf{QV}}
\nc{\PiQV}{\ensuremath{\Pi_\QV}}
\nc{\VQV}{\ensuremath{V_\QV}}
\nc{\PQV}{\ensuremath{P_\QV}}
\nc{\PQVstar}{\ensuremath{P_\QV^*}}
\nc{\cVQV}[1]{\ensuremath{\cV_{\QV,#1}}}
\nc{\cPQV}[1]{\ensuremath{\cP_{\QV,#1}}}

\def\QVAuth{\mathsf{QVAuth}}
\nc{\PiQVAuth}{\ensuremath{\Pi_\QVAuth}}
\nc{\VQVAuth}{\ensuremath{V_\QVAuth}}
\nc{\PQVAuth}{\ensuremath{P_\QVAuth}}
\nc{\PQVAuthstar}{\ensuremath{P_\QVAuth^*}}
\nc{\cVQVAuth}[1]{\ensuremath{\cV_{\QVAuth,#1}}}
\nc{\cPQVAuth}[1]{\ensuremath{\cP_{\QVAuth,#1}}}

\def\samp{\mathsf{samp}}
\nc{\Pisamp}{\ensuremath{\Pi_\samp}}
\nc{\Vsamp}{\ensuremath{V_\samp}}
\nc{\Psamp}{\ensuremath{P_\samp}}
\nc{\Psampstar}{\ensuremath{P_\samp^*}}
\nc{\cVsamp}[1]{\ensuremath{\cV_{\samp,#1}}}
\nc{\cPsamp}[1]{\ensuremath{\cP_{\samp,#1}}}

\def\sampblind{\mathsf{samp, blind}}
\nc{\Pisampblind}{\ensuremath{\Pi_\sampblind}}
\nc{\Vsampblind}{\ensuremath{V_\sampblind}}
\nc{\Psampblind}{\ensuremath{P_\sampblind}}
\nc{\Psampblindstar}{\ensuremath{P_\sampblind^*}}
\nc{\cVsampblind}[1]{\ensuremath{\cV_{\sampblind,#1}}}
\nc{\cPsampblind}[1]{\ensuremath{\cP_{\sampblind,#1}}}

We generalize our blind $\QPIP_1$ protocol for $\SampBQP$ by allowing fully quantum verifier and quantum output as follows:

\begin{protocol}{Blind and verifiable delegation protocol $\PiQV$ between two quantum computers}
	Verifier's input: $x$

	Pick $m, n, N$ appropriately in term of $\varepsilon$
	\Ethan{TODO fix me; this gets the point across for now}
	\begin{enumerate}
		\item The verifier generates $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$ where $d$ is the depth of the circuit corresponding to $\cPsampblind{1}(x)$.
			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
			It also sends $pk$ to the prover.
		\item The prover computes $\sigma\leftarrow\cPsampblind{1}(pk, ct_x)$ by homomorphically evaluating $\cPsamp{1}$ on input $ct_x$, generating $\sigma\leftarrow\QEval_{pk}(\cPsamp{1}, ct_x)$.
			It sends $\sigma$ to the verifier.
		\item The verifier computes output $o\leftarrow\cVQV(pk, \sigma)$ by (TODO summarize).
			Specifically, it decodes $\sigma$ to get $\rho^N$.
			It randomly picks and uses $n$ copies to check ground state energy using \cref{AlgGroundStateCheck}. If more than $\frac{1}{2}-\Delta$ \Ethan{TODO: define $\Delta$} reject, output $\bot$.
			Otherwise, it measures other copies in random order, stopping and outputting \Ethan{Be more specific later} when it measures $t\geq T$.

			\Ethan{Extremely handwavy but hopefully gets the point across for now}
	\end{enumerate}
\end{protocol}

This has the same soundness guarantee as in \cref{QPIP1thm}.
\Ethan{Or at least I hope it does}
Namely, for all $\PQVstar$ there exists some $\delta\in(0, 1)$ s.t. the output $(\PQVstar, \VQV(x))$ is inverse-poly close to $(1-\delta)C(x) + \delta\ket{\bot}\bra{\bot}$

Now we use $\PiQV$ to delegate $\tilde{C}(k, x)=A_k(C(x))$, where $A$ corresponds to some QAS.
By the guarantee above, the output is inverse-poly close to $(1-\delta)A_k(C(x)) + \delta\ket{\bot}\bra{\bot}$
Assuming it doesn't just...

### 2020-02-22 qpip0.tex
Change autoref to cref

@@
 
-Here we combine \autoref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients.
+Here we combine \cref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients.
 Combining them will cost polynomially rounds, so we use results from \cite{parallelrep} that allows parallel repetition to construct a constant-round protocol.
@@
 %    \item Both the verifier and the prover know a $\BQP$ circuit $C$ and an input string $x$.
-    \item Both party know the number of qubits $n$ and a security parameter $\lambda=o(n)$.
+    \item Both party know the number of qubits $n$ and a security parameter $\lambda=1^{\poly(n)}$.
     \item Verifier has a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit.
@@
     \item In the fourth round. The prover generates a classical string $a$ from $c$ and $\sigma$ and send to back to the prover.
-    \item If $c=0$, the verifier decides whether he is going to reject from $(pk,a,y)$. If $c=1$ the verifier computes an $n$-bit string $z$ from $(sk,h,y,a)$.
+    \item If $c=0$, the verifier decides whether he is going to reject from $(pk,a,y)$. If $c=1$ the verifier computes an $n$-bit string $z$ from $(sk,h,y,a)$, $z=V_f(sk,h,y,a)$.
 \end{enumerate}
@@
 
-\begin{lemma}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
+\begin{definition}
+With loss of generality,  we can assume that the testing round verification is deterministic.
+We denote the set of strings $a$ accepted by the verifier in the testing round with $(pk,y)$ as $\Acc_{pk,y}$.
+\end{definition}
+
+\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
 If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
@@
     \item Both verifier and prover start with the description of number of qubits $n$, quantum circuit $C$, input string $x$, and  a soundness parameter $\varepsilon$.
-    \item Run $m=O(1/\varepsilon)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications.
-On the second round, for each copy, the prover choose the state specified by Protocol~\ref{ProtoQPIP1}  (with error $\eps$) as $\rho$.
-On the third round, the verifier uniformly randomly pick an $i\in [m]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies.
-    \item \label{step:multi-testing}Verifier rejects if the results on any of the test rounds is rejected. 
+    \item Run $m=O(1/\varepsilon^2)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications.
+The copies share the same $h$ but have separate $\{sk\}$, $\{pk\}$, $\{y\}$, $\{c\}$, and $\{a\}$.
+The prover use $h$ specifier by step~\ref{} of Protocol~\ref{ProtoQPIP1} to generate $\{sk\}$ and $\{pk\}$ for all copies on the first round.
+On the second round, for each copy, the prover choose the state specified by step~\ref{} of Protocol~\ref{ProtoQPIP1}  (with  $(C,x,\eps)$ as input) as $\rho$.
+On the third round, the verifier uniformly randomly pick an $i\in [m]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies, i.e.
+$c_i=1$ and $c_j=0$ for all $j\neq i$.
+    \item \label{step:multi-testing}Verifier rejects if the result on any of the test rounds is rejected. 
     \item If all testing rounds are accepted, verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
@@
 
-\begin{theorem}\label{thm:urmila-binding}
+\begin{theorem}\label{thm:qpip0}
     Protocol~\ref{proto:QPIP0samp} is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and $\eps$ computational soundness error\hannote{definition}. 
@@
 
+%Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
+\begin{lemma}[partition lemma2]\label{lem:partition2}
+Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round.
+Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$.
+Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.
+
+ For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,
+
+\begin{align}
+    G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{0,i,\gamma}}_{\regX,\regZ} \\ G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{1,i,\gamma}}_{\regX,\regZ}  \\
+    \ket{\psi}_{\regX,\regZ} =&   \ket{\psi_{0,i,\gamma}}_{\regX,\regZ}+ \ket{\psi_{1,i,\gamma}}_{\regX,\regZ}+\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}
+\end{align}
+
+% $$ \ket{\psi}_{\regX,\regZ} =  G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ}+ G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ}+\ket{\psi_{err}}_{\regX,\regZ},$$
+
+  Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are  sub-normalized.
+$G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$.
+
+Furthermore, the following properties are satisfied for all $i\in[m]$.
+%
+\begin{enumerate}
+    \item \label{property:partition-err}  $$E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\|^2 \leq \frac{6}{T}+\negl(n),$$
+
+    where the averaged is over uniformly sampled $\gamma$. This also implies
+    \begin{align}
+        E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\| \leq \sqrt{\frac{6}{T}}+\negl(n)
+    \end{align}
+by Cauchy's inequality.
+
+        \item \label{property:partition-testing}
+For all $\{pk\}$, $\{y\}$, fixed $\gamma$, and  $j\neq i$, we have
+
+%      \begin{align*}
+%  \Pr\left[M_{\regX_i}\circ U\frac{\ket{\{c\}}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{pk_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
+%  \end{align*}
+
+%  Define
+%  $$\ket{\widetilde{\psi_{0,i,\gamma}}}\defeq U\frac{\ket{\{c\}}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}.$$
+%  We have
+%  \begin{align}
+%      \vev{\widetilde{\psi_{0,i,\gamma}}|P_{i,pk_i,y_i,acc}|\widetilde{\psi_{0,i,\gamma}}} \leq (m-1)\gamma+\negl(\secpar),
+%  \end{align}
+ \begin{align}
+    \norm{ P_{i,pk_i,y_i,acc} \circ U\frac{\ket{e_j}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}}^2 \leq (m-1)\gamma_0+\negl(\secpar),
+ \end{align}
+
+where $P_{i,pk_i,y_i,acc}$ are projector to the states that $i$-th testing round accepts with $pk_i,y_i$, including the last measurement the prover did before sending $\{a\}$.
+This means that $\ket{\psi_{0,i,\gamma}}$ is rejected by $i$-th testing round with high probability.
+
+    \item \label{property:partition-binding}
+
+    % $\{c\}\in S_m$ such that $c_i = 0$
+For all $\{pk\}$, $\{y\}$, fixed $\gamma$, and $j\neq i$, there exists an efficient quantum algorithm $\ext_i$ such that
+
+\begin{align}
+     \norm{P_{i,pk_i,y_i,acc} \circ \ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)}^2 =1-\negl(\secpar).
+\end{align}
+
+% \begin{align*}  
+%   \Pr\left[M_{\regX_i}\circ \ext_i\left(\frac{\ket{\{c\}}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{pk_i,y_i}\right]=1-\negl(\secpar).
+%   \end{align*}
+This will imply that    $\ket{\psi_{1,i,\gamma}}$ is binding to $i$-th Hadamard round.
+
+\item \label{property-partition-norm-sum}
+  For all $\gamma$, 
+  \begin{align}
+    \norm{\ket{\psi_{0,i,\gamma}}}^2+ \norm{\ket{\psi_{1,i,\gamma}}}^2 \leq  \norm{\ket{\psi}}^2 
+\end{align}
+
+\item \hannote{added by me..not needed?}
+
+$$\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}} = \negl(n)$$
+
+\end{enumerate}
+\end{lemma}
+
+% \begin{proof}
+% Step~\ref{step:sum-ob}: 
+% \begin{align}
+%   ( G_{0,i,\gamma}+G_{1,i,\gamma}) \ket{\psi}_{\regX,\regZ}
+%   &= \ket{\psi_{0,i,\gamma}}_{\regX,\regZ}+\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}
+% \end{align}
+% \end{proof}
+
+We also need the following technical lemma.
+\begin{lemma}\label{lem:samp-tech}
+For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
+$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi} $$
+\end{lemma}
 \begin{proof}
+\begin{align}
+    \sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| \nn \\
+    \leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}}  \nn \\ \leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\norm{ P_z\ket{\phi}}^2}     \nn \\
+    \leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn \\
+    \leq & \norm{\ket{\psi}}\norm{\ket{\phi}},
+\end{align}
+where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
+\end{proof}
 
- [[Partition lemma -> Parallel repetition]], except for probability $\eps$, either the verifier reject at step~\ref{step:multi-testing} or $z$ is $\negl(n)$-computationally indistinguishable to $M_{XZ}(\rho,h)$ by Theorem~\ref{thm:urmila-binding}.
+Now we are ready to prove Theorem~\ref{thm:qpip0}
+\begin{proof}
+We begin by considering the state $\ket{\psi}$ the prover in Protocol~\ref{proto:QPIP0samp} hold before he receives $\{c\}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
+
+For all $k\leq m$, $d\in \zo^k$, and $\ket{\psi} \in H_{\regX,\regZ}$, define
+
+$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}G_{d_{k-1},k-1,\gamma}\cdots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$
+
+By Lemma~\ref{lem:partition2}, we have
+
+\begin{align} \label{eq:partition-string}
+    \ket{\psi} =& \ket{\psi_{0,\gamma}}+\ket{\psi_{1,\gamma}}+\ket{\psi_{err,1,\gamma}} \nn \\
+    =& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{11,\gamma}}+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}} \nn \\
+    =& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{m-1}0,\gamma}}+\ket{\psi_{1^{m-1}1,\gamma}} \nn \\
+    &+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,m,\gamma}}, 
+\end{align}
+
+where we abuse the notation and use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
+
+By Property~\ref{property-partition-norm-sum} of Lemma~\ref{lem:partition2}, we have
+\begin{align} \label{eq:bad-term-sum}
+    \norm{\ket{\psi}}^2 \geq& \norm{\ket{\psi_{0,\gamma}}}^2+\norm{\ket{\psi_{1,\gamma}}}^2 \nn \\
+    \geq& \norm{\ket{\psi_{0,\gamma}}}^2+
+    \norm{\ket{\psi_{10,\gamma}}}^2+ \norm{\ket{\psi_{11,\gamma}}}^2 \nn \\
+    \geq& \norm{\ket{\psi_{0,\gamma}}}^2+
+    \norm{\ket{\psi_{10,\gamma}}}^2+ \norm{\ket{\psi_{110,\gamma}}}^2 +\cdots  \nn \\
+    &+ \norm{\ket{\psi_{1^{m-1}0,\gamma}}}^2+ \norm{\ket{\psi_{1^{m-1}1,\gamma}}}^2
+\end{align}
+
+Denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as
+
+$$P_{acc,i,z}.$$
+Note that $P_{acc,i,z}$ also depends on $\{\pk\},\,\{y\}$ and  $(sk_i,h_i,y_i)$ since it includes the measurement the prover did before sending $a$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
+
+Since the verifier only accepts if all $(m-1)$ copies of testing rounds accepts, for all $j\neq i$,
+
+$$P_{acc,i,z}=P_{acc,i,z}P_{j,pk_j,y_j,acc}.$$
+
+And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$\hannote{problem with $e_j$ or $e_i$}
+
+\begin{align} \label{eq:rejected-d}
+    \norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2
+    =& \norm{P_{acc,i,z}P_{j,pk_j,y_j,acc} U \ket{e_i}\, G_{0,j+1,\gamma}\ket{\psi_{1^j,\gamma}}  }^2 \nn \\
+    \leq& \norm{P_{j,pk_j,y_j,acc} U \ket{e_i}\, G_{0,j+1,\gamma}\ket{\psi_{1^j,\gamma}}  }^2 \nn \\
+    \leq& (m-1)\gamma_0+\negl(n) 
+\end{align}
+
+Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$. The output string corresponding to $\ket{\psi} \in H_{\regX,\regZ}$ when $c=e_i$ is then
+
+$$z_i\defeq \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
+where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round.
+
+Since $\{c\}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have 
+$$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$ 
+where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin probabilities.
+Note that $z$ is "sub-normalized", i.e.
+$\tr (z)= \text{probability of getting accepted} \leq 1$.
+
+Define
+
+\begin{align}
+    z_{good,i}=E_\gamma \sum_z \proj{z} \cdot \vev{e_i,\psi_{1^{i-1}1,\gamma}|U^\dag P_{acc,i,z} U|e_i,\psi_{1^{i-1}1,\gamma}}
+\end{align}
+
+Splitting $\ket{\psi}$ with Equation~\ref{eq:partition-string}, 
+%\hannote{gamma..}
+
+\begin{align}
+    \ket{\psi}=& \L. \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{i-1}0,\gamma}}+
+    \ket{\psi_{1^{i-1}1,\gamma}} \R. \nn \\
+     +& \L.\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,i,\gamma}}\R. \nn \\
+     =& \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
+\end{align}
+
+we have
+
+\begin{align}
+    z_i =& \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi} \nn \\
+    =& \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}} +\bra{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} \R]U^\dag  P_{acc,i,z} U\nn \\
+    &\L[ \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}\R]  \nn \\
+    =& E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}} +\bra{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} \R]U^\dag  P_{acc,i,z} U\nn \\
+    &\L[ \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}\R]  \nn \\
+    =& z_{good,i}+ E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
+    \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \nn \\
+      +&  \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
+    +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
+    +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
+    +& \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} 
+    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \nn \\
+    +&\L.\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] , \nn     
+    %=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err ) 
+\end{align}
+
+%  U^\dag  P_{acc,i,z}U
+
+% \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} 
+% \ket{\psi_{1^i,\gamma}} 
+% \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
+
+ where we omitted writing out $e_i$ starting the second line.  We have
+\begin{align} \label{eq:zi-zgoodi}
+    &\tr|z_i-z_{good,i}|   \nn \\
+    \leq&  \sum_z  \L| E_\gamma \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
+    \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \R. \nn \\
+      +&  \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
+    +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
+    +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
+    +& \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} 
+    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \nn \\
+    +&\L.\L.\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R]\R| \nn \\  %%%%%%%%%%%
+    \leq&  \sum_z   E_\gamma \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^j0,\gamma}} \R|+
+    2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R.  \nn \\
+      +&  2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R|    
+    +2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \nn \\
+    +&\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \nn \\ %%%%%%%%%
+      \leq&  \sum_z   \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{e_i,\psi_{1^j0,\gamma}} \R|+
+    2 \sum_{k=0}^{i-1} \L|\bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{e_i,\psi_{1^i,\gamma}} \R|  \R]    +O\L(\frac{m^2}{\sqrt T}\R)\nn \\ %%%%%%%%%
+    \leq&  \sum_z   \L[\L| \bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^{i-1}0,\gamma}} \R|+
+    2  \L|\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R]    \nn \\ +&O\L(\frac{m^2}{\sqrt T}+m^2{(m-1)\gamma_0}+m\sqrt{(m-1)\gamma_0}\R)\nn \\ %%%%%%%%% 
+    \leq& \norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R),
+\end{align}
+where on the second inequality we used triangle inequality, on the third inequality we used  Lemma~\ref{lem:samp-tech} and property~\ref{property:partition-err} of Lemma~\ref{lem:partition2}, on the fourth inequality we used Lemma~\ref{lem:samp-tech} and Equation~\ref{eq:rejected-d}, and on the last inequality we used Lemma~\ref{lem:samp-tech}.
+Once again, we omit $e_i$ when it is not relevant.
+
+% \begin{align}
+%     &\vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi} \nn \\
+%     =& \bra{e_i, \psi_{1^{i-1}1,\gamma}} U^\dag P_{acc,i,z} U \ket{e_i\psi_{1^{i-1}1,\gamma}} +\hannote{poly terms?}+ \negl(n)
+% \end{align}
+
+Now we try to  put together all $i\in [m]$. Define
+$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}.$$
+
+We have 
+\begin{align}
+    \tr|z-z_{good}| =& \tr\L|\frac{1}{m}\sum_i (z_i-z_{good,i})\R| \nn \\
+    \leq&  \frac{1}{m}\sum_i\tr| (z_i-z_{good,i})| \nn \\
+    \leq&  \frac{1}{m}\sum_i\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
+    \leq&  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%
+    =&O\L( \frac{1}{\sqrt m}+\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)
+\end{align}
+
+where we used triangle inequality on the second line, Equation~\ref{eq:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
+
+===
+
+%Prove that $z_{good}$ is binding.
+We now proceeds to prove that $z_{good}$ is binding.
+I.e.
+there exist a $n$-qubit quantum state $\rho$ such that $z_{good}$ is $\eps$-Q-computationally indistinguishable to $\sum_z \proj{z} \tr\L(\rho \sigma_h \R)$.
+\hannote{add notation for pauli matrix $\sigma_h$.}
+
+===
+
+ [[Partition lemma ->  Parallel repetition]], except for probability $\eps$\hannote{$\frac{1}{poly}$?}, either the verifier reject at step~\ref{step:multi-testing} or $z$ is $\negl(n)$-computationally indistinguishable to $M_{XZ}(\rho,h)$ by Lemma~\ref{lem:urmila-binding}.
 
  By theorem~\ref{QPIP1thm}, $M_{XZ}(\rho,h)$  $\eps$-close to $C(x)$.
-Therefore\hannote{?}, $M_{XZ}(\rho,h)$  and  $C(x)$ $z$ are $\eps$-Q-computationally indistinguishable, and thus $z$ and $C(x)$ are  $2\eps$-Q-computationally indistinguishable.
+Therefore, $M_{XZ}(\rho,h)$  and  $C(x)$ $z$ are $\eps$-Q-computationally indistinguishable, and thus $z$ and $C(x)$ are  $2\eps$-Q-computationally indistinguishable.
 
 \end{proof}
+
+===========
+
+\hannote{below are unused old fragments}
+
 ===========
@@
 \begin{lemma}[partition lemma]\label{lem:partition}
-Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}.  Let $i\in[m]$, 
-$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.
-Let $\gamma$ be a random number sampled uniformly from $\L[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R]$.
+Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round.
+Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
+Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.
 
-There exists an $\poly(n)$-sized quantum circuit $G_{i,\gamma}$ such that for all (possibly sub-normalized) \hannote{$n$-qubit?} quantum state $\ket{\psi}_{\regX,\regZ}$,  
+ For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exists an $\poly(n)$-sized quantum circuit $G_{i,\gamma}$ such that for all (possibly sub-normalized) \hannote{$n$-qubit?} quantum state $\ket{\psi}_{\regX,\regZ}$,
 \begin{align*}
-    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = \\ z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+  z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
+    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = \\ \ket{0^m}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+  \ket{0^m}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
 \end{align*}
-\hannote{what's wrong with all these registers} where $t$ is the number of qubits in the register $ph$, $z_0,z_1\in \mathbb{C}$ such that $|z_0|=|z_1|=1$, and 
-$z_0$, $z_1$, \hannote{$Z$ just phase factor?}$\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ may depend on $\gamma$.
+ where $t$ is the number of qubits in the register $ph$, $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ are sub-normalized states that may depend on $\gamma$.
 
-Furthermore, the following properties are satisfied.
+Furthermore, the following properties are satisfied for all $i\in[m]$.
 %
@@
     \item \label{partition-property-1}  Define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$.\hannote{?} We have  $$E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$$.
-    $$E_{\gamma}[\|\ket{\psi}_{\regX,\regZ}\|^2 -\|\ket{\psi_0}_{\regX,\regZ}\|^2 -\|\ket{\psi_1}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$$
+    $$\|\ket{\psi}_{\regX,\regZ}\|^2 -E_{\gamma}\L[\|\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}\|^2 +\|\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}\|^2\R]\leq \frac{6}{T}+\negl(n),$$
+
+    where the averaged is over uniformly sampled $\gamma$.
 \item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$.
@@
 
+%     \begin{align*}
+% \Pr\left[M_{\regX_i}\circ U\frac{\ket{\{c\}}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
+% \end{align*}
+
+%   \begin{align*}
+% \Pr\left[V_{f,i}\L(sk_i,h,y_i, U\frac{\ket{\{c\}}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\R) \in \Acc \right]\leq (m-1)\gamma+\negl(\secpar).
+% \end{align*}
+
         \item 
-For any fixed $\gamma$ and $c\in [m]$ such that $c\neq i$\hannote{check}\hannote{for all k, y}, we have 
+For all $\{pk\}$, $\{y\}$, fixed $\gamma$, and $\{c\}\in S_m$ such that $c_i = 0$, we have
+
      \begin{align*}
-\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
+ \Pr\left[M_{\regX_i}\circ U\frac{\ket{\{c\}}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{pk_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
  \end{align*}
+
     \item 
-For any fixed $\gamma$, there exists an efficient quantum algorithm $\ext_i$ such that 
+For all $\{pk\}$, $\{y\}$, fixed $\gamma$, and $\{c\}\in S_m$ such that $c_i = 0$, there exists an efficient quantum algorithm $\ext_i$ such that
+
 \begin{align*}  
-  \Pr\left[\ext_i\left(\frac{\ket{i}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
-  \end{align*}   \hannote{$M_x?$}
+  \Pr\left[M_{\regX_i}\circ \ext_i\left(\frac{\ket{\{c\}}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{pk_i,y_i}\right]=1-\negl(\secpar).
+  \end{align*}
+
+\item \hannote{added by me..}
+$$\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}} = \negl(n)$$
 \end{enumerate}
 \end{lemma}
+\begin{rmk}\label{rmk:partition-projector}
+\hannote{should be corollary with proof?} By applying $G_{i,\gamma}$ then measuring the $ph,th,in$ register, we can get two efficient quantum algorithms $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that
+
+\begin{enumerate}
+    \item $$G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ}=\ket{\psi_{0,i,\gamma}}_{\regX,\regZ} $$
+\item  $$G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ}=\ket{\psi_{1,i,\gamma}}_{\regX,\regZ} $$
+%  \item ~\label{step:sum-ob} For all $i$ and $\gamma$,
+%   $$G_{0,i,\gamma}+G_{1,i,\gamma} \leq (1+\negl(n))Id_{\regX,\regZ} $$ \hannote{actually wrong.. the fuck?}
+%  \item ~\label{step:sum-lb}
+%   $$E_\gamma(G_{0,i,\gamma}+G_{1,i,\gamma}) \geq (1-\negl(n))Id_{\regX,\regZ} $$
+\end{enumerate}
+
+Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are not normalized.
+\hannote{we overload a quantum algorithm with the corresponding unitary.}
+
+Also note that 
+\begin{align}
+   &\norm{( G_{0,i,\gamma}+G_{1,i,\gamma}) \ket{\psi}}^2 \nn \\
+   =& \norm{\ket{\psi_{0,i,\gamma}}+\ket{\psi_{1,i,\gamma}}}^2 \nn \\
+   =& \norm{\ket{\psi_{0,i,\gamma}}}^2+\norm{\ket{\psi_{1,i,\gamma}}}^2+\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}}+\vev{\psi_{1,i,\gamma}|\psi_{0,i,\gamma}} \nn \\
+    \leq& \norm{\ket{\psi}}^2 +\negl(n)
+\end{align}
+and 
+\begin{align}
+   &E_\gamma \norm{( G_{0,i,\gamma}+G_{1,i,\gamma}) \ket{\psi}}^2 \nn \\
+   =& E_\gamma\norm{\ket{\psi_{0,i,\gamma}}+\ket{\psi_{1,i,\gamma}}}^2 \nn \\
+   =& E_\gamma\L[\norm{\ket{\psi_{0,i,\gamma}}}^2+\norm{\ket{\psi_{1,i,\gamma}}}^2+\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}}+\vev{\psi_{1,i,\gamma}|\psi_{0,i,\gamma}}\R] \nn \\
+    \geq& \norm{\ket{\psi}}^2 -\frac{6}{T}-\negl(n)
+\end{align}
+
+% \begin{align}
+%   &E_\gamma \norm{( G_{0,i,\gamma}+G_{1,i,\gamma}) \ket{\psi}}^2 \nn \\
+%   =& E_\gamma\norm{\ket{\psi_{0,i,\gamma}}+\ket{\psi_{1,i,\gamma}}}^2 \nn \\
+%   =& E_\gamma\norm{\ket{\psi}-\ket{\psi_{err}}}^2 \nn \\
+%     =& E_\gamma\L[\norm{\ket{\psi}}^2+\norm{\ket{\psi_{err}}}^2-2Re(\vev{\psi|\psi_{err}})\R] \nn \\
+%     \geq& \norm{\ket{\psi}}^2 -\frac{6}{T}-\negl(n)
+% \end{align}
+\end{rmk}
+
+\begin{lemma} \hannote{urmila talks about protocol not state.}
+For all $h$, $i\in [m]$ and $\{c\}\in S_m$ such that $c_i = 1$, $a_i \equiv  M_{\regX_i}\circ U\L(\frac{\ket{\{c\}}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\R)$ is binding.
+I.e.
+there exist a $\rho$ such that $V_f(sk,h,y,a)$ is $\negl(n)$-Q-computationally indistinguishable to $M_{XZ}(\rho,h)$, unless LEW can be efficiently solved by a quantum computer.
+\end{lemma}
+\begin{proof}
+We construct an  strategy $\tilde{U}$ for the fourth round of Protocol~\ref{proto:QPIP0samp}, which is "amplified" from $U$ .
+$\tilde{U}$ start by measuring the $\regC$ register.
+Since the $\regC$ register only has classical-valued inputs, this initial measurement does not decohere anything.
+Denote the measured input as $\{\tilde{c}\}$.
+If $\tilde{c}_i=0$, run $U$.
+If $\tilde{c}_i=1$, run $\ext_i$.
+By Lemma~\ref{lem:partition}, ???
+
+%without loss of generality we can assume $U$ measures $\regC$ first and run 
+\end{proof}
+
+====
+
+==============
 

### 2020-02-28 bqp.tex
Add next TODO items for BQP
Attempt to write blind QPIP0 for BQP

@@
 \label{sec:BlindBQP}
+
+\def\Mah{\mathsf{Mah}}
+\nc{\PiMah}{\ensuremath{\Pi_\Mah}}
+\nc{\VMah}{\ensuremath{V_\Mah}}
+\nc{\PMah}{\ensuremath{P_\Mah}}
+\nc{\PMahstar}{\ensuremath{P_\Mah^*}}
+\nc{\cVMah}[1]{\ensuremath{\cV_{\Mah,#1}}}
+\nc{\cPMah}[1]{\ensuremath{\cP_{\Mah,#1}}}
 
@@
 
+\Ethan{TODO Rewrite this}
+
 \begin{protocol}{Blind $\QPIP_1$ 1-message protocol $\Piblind = (\Pblind, \Vblind)$ for $\BQP$ language $L$}
@@
 	\begin{enumerate}
-		\item The verifier generates $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$.
-			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
-			It also sends $pk$ to the prover.
+		\item The verifier generates $(pk, sk, ct_x)\leftarrow\cVblind{1}(x)$ by encrypting $x$, generating
+			$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$ where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$, then
+			$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
+			It sends $pk$ and $ct_x$ to the prover.
 		\item The prover computes $\sigma\leftarrow\cPblind{1}(pk, ct_x)$ by homomorphically evaluating $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\QEval_{pk}(\cPMF{1}, ct_x)$.
 			It sends $\sigma$ to the verifier qubit-by-qubit.
-		\item The verifier generates $\Lambda\leftarrow\cVMF{2}(x)$,
-			$\Lambda'\leftarrow\cM_\QHE(\Lambda)$,
-			$ct_w\leftarrow\Lambda'(\sigma)$,
+		\item The verifier generates $\Lambda'\leftarrow\cVblind{2}(x)$ by computing
+			$\Lambda\leftarrow\cVMF{2}(x)$,
+			$\Lambda'\leftarrow\cM_\QHE(\Lambda)$.
+			It measures the incoming state from the verifier, obtaining $ct_w\leftarrow\Lambda'(\sigma)$.
+			Lastly, it generates and outputs $o\leftarrow\cVblind{3}(ct_w, sk, x, \Lambda')$ by
 			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
 			and $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
-			It outputs $o$.
 	\end{enumerate}
@@
 
+\Ethan{Just move \protoref{urmila4} here; that's Urmila's 4 rounds protocol.
+Or just move that entire subsection here really.}
+
 \Ethan{TODO Below is copied from google docs; fix phrasing later}
@@
 	\label{proto:QPIP0BQP}
+	\Ethan{Sync notations on \PiMah}
 	\begin{enumerate}
-		\item The verifier generates $\Lambda, \Lambda', pk, sk, ct_x$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
-			Then, using $\Lambda'$, it generates $k, td$.
+		\item The verifier generates $(pk, sk, ct_x)\leftarrow\cVblind{1}$,
+			$\Lambda'\leftarrow\cVblind{2}(x)$,
+			and $(k, td)\leftarrow\cVMah{1}(\Lambda')$.
 			It sends $k, pk, ct_x$ to the prover.
-		\item The prover, on inputs $k, pk, ct_x$, generates classical ``commitment" $y$ and internal state $\ket{st}$.
+		\item The prover generates $\sigma\leftarrow\cPblind{1}(pk, ct_x)$ and
+			$(y, st)\leftarrow\cPMah{2}(\sigma)$.
 			It sends $y$ to the verifier.
-		\item The verifier sends the prover a public coin $c\in\set{0,1}$.
-		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
-		\item The verifier, on inputs $k, td, y, c, a, sk$, generates and outputs either $acc$ or $rej$.
+		\item The verifier samples public coin $c\leftarrow\set{0, 1}$ and sends it to the prover.
+		\item The prover generates and sends $a\leftarrow\cPMah{3}(c, st)$ to the verifier.
+		\item If $c=0$, then the verifier generates and outputs $o\leftarrow\cVMah{T}(k, y, a, sk)$.
+			Otherwise, it runs $ct_w\leftarrow\cVMah{H}(k, td, y, a, sk)$,
+			then generates and outputs $o\leftarrow\cVblind{3}(ct_w, sk, x, \Lambda')$.
 	\end{enumerate}
@@
 
-\Ethan{
-    Need to say more about step 5.
-    It's a compiler here.
-    Need to say stuff about interface
-    see protocol 5.1; protocol is the most important
-    interface uses only lambda
-    if hadamard round, get measurement outcome corresponding to sigma
-    how to decode
+\begin{thm}
+	$\Pibz$ has negligible completeness error. Its soundness error is negligibly close to $\frac{3}{4}$.
+\end{thm}
+\begin{proof}
+	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into a $\QPIP_0$ in a similar way and obtains this completeness and soundness.
+	The proof uses that $\PiMF$ is one-round $\QPIP_1$ with only $X$ and $Z$ measurements on the verifier's side, with negligible completeness and soundness errors.
+	$\Piblind$ is two-rounds, but we can treat the verifier's first message as additional classical public inputs, and apply the same logic to the second round.
 
-    Describe in words what's 5.1
-    Leave author note for theorem for now
-}
-
-For blindness, recall that the prover receives $ct_x = Enc(x), evk, k, c$ from the verifier.
-Blindness follows by the semantic security of QFHE and the fact that k computationally hides the basis choice $\Lambda$.
-\Ethan{This sentence is from google docs so keep it around}
+	For blindness, recall that the prover receives $ct_x, pk, k, c$ from the verifier.
+Blindness follows by the semantic security of $\QHE$ and the fact that $k$ computationally hides the basis choice $\Lambda'$.
+\end{proof}
 
@@
 
-\Ethan{Is the following even necessary?}
-
-\begin{protocol}{Parallel repetition of \cref{proto:QPIP0BQP}}
-	\label{proto:repQPIP0BQP}
-	\Ethan{TODO PROOFREAD ME}
-	Run $m=\poly(n)$ copies of \cref{proto:QPIP0BQP} in parallel. Accept if the proportion of accepted copies is over some certain threshold $p(n)\in(0, 1)$.
-
-\end{protocol}
-
-\begin{thm}
-	\cref{proto:repQPIP0BQP} has negligible completeness and soundness.
+\begin{thm}[from \cite{parallelrep, alagic2019twomessage}]
+	One can repeat $\PiMah$ in parallel to obtain negligible completeness and soundness errors. \Ethan{Something doesn't seem right...}
 \end{thm}
-\begin{prf}
-	\Ethan{Don't open separate proof env}
-	See \cite{parallelrep, alagic2019twomessage}
-\end{prf}
 

### 2020-02-28 bqp.tex
Make editorial pass at BQP

@@
 
+\def\MFZ{\mathsf{MFZ}}
+\nc{\PiMFZ}{\ensuremath{\Pi_\MFZ}}
+\def\MFZrep{\mathsf{MFZrep}}
+\nc{\PiMFZrep}{\ensuremath{\Pi_\MFZrep}}
+
 \def\blind{\mathsf{blind}}
@@
 \nc{\Pibzrep}{\ensuremath{\Pi_\bzrep}}
+\nc{\Vbzrep}{\ensuremath{V_\bzrep}}
+\nc{\Pbzrep}{\ensuremath{P_\bzrep}}
 
@@
 
-In this subsection we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
-\begin{thm}
-	\label{thm:QPIP0BQP}
-	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
-\end{thm}
-We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
-\Ethan{Write outline here; highlight key ideas/steps}
-We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.
-We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{FOCS:Mahadev18a}, which is in turn taken from \cite{mf16}.
+In this subsection we present our constant-round blind delegation protocol for $\BQP$.
+We'll construct said protocol piece by piece, starting with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16}.
+\Ethan{TODO finish outline and highlights}
 
@@
 
-Now we state our construction of blind QPIP 1 for BQP by compiling $\PiMF$ using $\QHE$:
-
-\Ethan{TODO Rewrite this}
+Now we state our construction of blind $\QPIP_1$ for $\BQP$:
 
@@
 	$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
-	It then runs $\sigma\leftarrow\cPblind{1}(pk, ct_x)$
+	It then runs $\sigma\leftarrow\cPblind{1}(pk, ct_x)$.
 	Finally, it decrypts
@@
 
-\Ethan{Just move \protoref{urmila4} here; that's Urmila's 4 rounds protocol.
-Or just move that entire subsection here really.}
+\Ethan{Formally introduce \protoref{urmila4} (measurement protocol) earlier?}
 
-\Ethan{TODO Below is copied from google docs; fix phrasing later}
+Next, we make the verifier completely classical by using \protoref{urmila4} from \cite{FOCS:Mahadev18a}.
+It was originally used to compile $\PiMF$ into $\PiMFZ$ that is $\QPIP_0$. \Ethan{Say a bit more?}
+It can however be applied to any $\QPIP_1$ protocol with $X$ and $Z$ measurement and negligible completeness and soundness errors.
 
-Finally, we prove \cref{thm:QPIP0BQP}.
-We use Mahadev's measurement protocol from \cite{FOCS:Mahadev18a} which can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol.
-The resulting protocol $\Pibz$ is a constant-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$ and negligible completeness.
-
-In order to prove blindness, we give a high-level overview of the compiliation results.
-\Ethan{Need to discuss about this}
+We give a high-level overview of the compiliation results.
 
@@
 	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into a $\QPIP_0$ in a similar way and obtains this completeness and soundness.
-	The proof uses that $\PiMF$ is one-round $\QPIP_1$ with only $X$ and $Z$ measurements on the verifier's side, with negligible completeness and soundness errors.
-	$\Piblind$ is two-rounds, but we can treat the verifier's first message as additional classical public inputs, and apply the same logic to the second round.
+	Its proof uses only that $\PiMF$ is $\QPIP_1$ with only $X$ and $Z$ measurements on the verifier's side, with negligible completeness and soundness errors.
+	So the same logic applies here.
 
@@
 \begin{thm}[from \cite{parallelrep, alagic2019twomessage}]
-	One can repeat $\PiMah$ in parallel to obtain negligible completeness and soundness errors. \Ethan{Something doesn't seem right...}
+	\label{thm:MFZrep}
+	$\PiMFZ$ can be repeat in parallel, obtaining $\PiMFZrep$ that has negligible completeness and soundness errors.
+\end{thm}
+
+Again, the same proof logic in \cref{thm:MFZrep} applies here. We simply repeat $\Pibz$ in parallel to get $\Pibzrep$ that is what we wanted in \cref{thm:QPIP0BQP}.
+
+\begin{thm}
+	\label{thm:QPIP0BQP}
+	$\Pibzrep$ is a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
 \end{thm}
@@
 
-\Ethan{TODO PROOFREAD ME}
+Our results for $\BQP$ can be generalized to $\FBQP$ as follows:
 
-Our results for $\BQP$ can be generalized to $\FBQP$.
+\begin{protocol}{Blind and verifiable $\QPIP_0$ protocol $\Pi_{\FBQP}$ for $f\in\FBQP$}
+	\label{proto:QPIP0FBQP}
+	Verifier's input: $x\in\set{0, 1}^n$
 
-Let $f\in\FBQP$.
-For any input $x\in\set{0, 1}^*$, define $f_i(x)$ to be the $i$-th bit of $f(x)$.
-For $i\in\bbN, b\in\set{0,1}$, define the language $L_{i, b}=\set{x:f_i(x)=b}$.
-Furthermore, define $\cL$ to be the collection of these languages: $\cL = \set{L_{i, b}: i\in[m], b\in\set{0, 1}}$.
+	Public input: $f$
 
-\begin{protocol}{Blind and verifiable $\QPIP_0$ protocol $\Pi_{\FBQP}$ for $\FBQP$ language $L$}
-	\label{proto:QPIP0FBQP}
-	Input: $x\in\set{0, 1}^n$
-
-	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how?}
+	Let $m=\abs{f(x)}$; we assume without loss of generality that it depends only on $n$ and can be efficiently computed classically.
+	Denote the $i$-th bit of $f(x)$ as $f_i(x)$.
+	For $i\in\bbN, b\in\set{0,1}$, define the $\BQP$ language $L_{i, b}=\set{s\in\set{0,1}^* : f_i(s)=b}$.
 	\begin{enumerate}
-		\item Run $\Pibzrep$ for all $L\in\cL$ in parallel using input $x$.
+		\item For all $i\in[m], b\in\set{0, 1}$ in parallel, the verifier and the prover run $(\Pbzrep, \Vbzrep(x))$ for $L_{i, b}$.
 		\item The verifier gets outputs $v_{i, b}\in\set{acc, rej}$.
 			If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.
-			Otherwise, define $y_i = b$ where $v_{i, b}=acc$. This gives $y\in\set{0,1}^m$.
+			Otherwise, define $y\in\set{0,1}^m$ s.t. $y_i = b$ where $v_{i, b}=acc$,
 			The verifier accepts and outputs $y$.
@@
 \begin{prf}
-	Completeness is follows by inspection.
-	Blindness follows because the executions of \cref{proto:repQPIP0BQP} are blind.
+	Completeness follows by inspection.
+	Blindness follows because the executions of $\Pibzrep$ are blind.
 
@@
 
-	By union bound over all output bits, the soundness of \cref{proto:QPIP0FBQP} is then
+	By union bound over all output bits, the soundness of $\Pi_{\FBQP}$ is then
 	$\sum_{i=1}^m \varepsilon_i$

### 2020-02-28 bqp.tex
Fix QED symbols in BQP
Add blindness in BQP blind0 theorem statement
Make another BQP editorial pass

@@
 			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
-			It applies $\Lambda$ to $\rho$ qubit-by-qubit.
-			Let $w \in \set{0,1}^m$ denote the measurement outcome.
-			It verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
+			It then applies $\Lambda$ to $\rho$ qubit-by-qubit, obtaining $w\leftarrow\Lambda(\rho)$.
+			Finally, it verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
 	\end{enumerate}
@@
 
-We compile $\PiMF$ using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol $\Piblind$ for $\BQP$, again with only $X$ and $Z$ measurements.
+We first compile $\PiMF$ using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol $\Piblind$ for $\BQP$.
 The high level idea is to run $\PiMF$ under $\mathsf{QHE}$.
-Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
+Namely, the verifier encrypts its original input $x$ and sends $ct_x=\mathsf{QHE.Enc}(x)$ to the prover.
 The prover then homomorphically evaluates $\cPMF{3}$ on $ct_x$ to produce $\sigma$ and sends it to the verifier.
 
-Now the verifier needs to obtain the measurement outcome $w$ from the encrypted state $\sigma$ using qubit-by-qubit $X$ and $Z$ measurements.
+Now the verifier needs to obtain the measurement outcome $w$ from the encrypted state $\sigma$ using qubit-by-qubit measurements.
 This may not be possible in general, but we observe that Mahadev's $\mathsf{QHE}$ allows this. 
@@
 	Let $n, L\in\bbN$.
-	Let $(pk, sk)\leftarrow\QGen(1^n, 1^L)$
-	Let $m=\poly(n)$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$.
+	Let $(pk, sk)\leftarrow\QGen(1^n, 1^L)$.
+	Let $m=\poly(n)$ be the length of the ciphertexts corresponding to plaintexts of length $n$ encrypted using $pk$ under $\mathsf{QHE}$.
 
@@
 	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and
-	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
+	$$\widehat{\mathsf{QHE.Dec}_{sk}}\circ\Lambda'=\Lambda\circ\mathsf{QHE.Dec_{sk}}$$
 \end{thm}
 \begin{prf}
-	This is a proof by construction.
-	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
-	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$
-	Clearly,
-	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\Lambda(\rho)$$
+	This proof is by construction.
+
+	We require $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
+	$$\widehat{\QDec_{sk}}\circ\Lambda'(\sigma)=\Lambda\circ\QDec_{sk}(\sigma)=\Lambda(\rho)$$
 
@@
 	Note that the Pauli one-time pad on $u$ commutes with $X$ and $Z$ measurements.
-	So let $\widehat{\mathsf{QHE.Dec}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $u$ to get $\Lambda(\rho)$.
+	So let $\widehat{\QDec_{sk}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $u$ to get $\Lambda(\rho)$.
 \end{prf}
@@
 	\begin{enumerate}
-		\item The verifier generates $(pk, sk, ct_x)\leftarrow\cVblind{1}(x)$ by encrypting $x$, generating
-			$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$ where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$, then
+		\item The verifier generates $(pk, sk, ct_x)\leftarrow\cVblind{1}(x)$ by encrypting $x$ under $\QHE$.
+			More precisely, it generates
+			$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$ where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$, and
 			$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
@@
 			$\Lambda'\leftarrow\cM_\QHE(\Lambda)$.
-			It measures the incoming state from the verifier, obtaining $ct_w\leftarrow\Lambda'(\sigma)$.
+			It measures the incoming state $\sigma$ qubit-by-qubit, obtaining $ct_w\leftarrow\Lambda'(\sigma)$.
 			Lastly, it generates and outputs $o\leftarrow\cVblind{3}(ct_w, sk, x, \Lambda')$ by
@@
 	The completeness follows by inspection.
-	For blindness, the only thing the prover sees is $c$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.
+	For blindness, the only thing the prover receives is $c$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.
 
@@
 	and
-	$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
-	It then runs $\sigma\leftarrow\cPblind{1}(pk, ct_x)$.
+	$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$,
+	then runs $\sigma\leftarrow\cPblind{1}(pk, ct_x)$.
 	Finally, it decrypts
@@
 \begin{thm}
-	$\Pibz$ has negligible completeness error. Its soundness error is negligibly close to $\frac{3}{4}$.
+	$\Pibz$ has negligible completeness error. Its soundness error is negligibly close to $\frac{3}{4}$. It is blind.
 \end{thm}
-\begin{proof}
+\begin{prf}
 	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into a $\QPIP_0$ in a similar way and obtains this completeness and soundness.
 	Its proof uses only that $\PiMF$ is $\QPIP_1$ with only $X$ and $Z$ measurements on the verifier's side, with negligible completeness and soundness errors.
-	So the same logic applies here.
+	So the same argument applies here. \Ethan{TODO proofread me}
 
 	For blindness, recall that the prover receives $ct_x, pk, k, c$ from the verifier.
-	Blindness follows by the semantic security of $\QHE$ and the fact that $k$ computationally hides the basis choice $\Lambda'$.
-\end{proof}
+	Blindness follows by the semantic security of $\QHE$ and the fact that $k$ computationally hides the measurement basis choice $\Lambda'$.
+\end{prf}
 
@@
 
-Again, the same proof logic in \cref{thm:MFZrep} applies here. We simply repeat $\Pibz$ in parallel to get $\Pibzrep$ that is what we wanted in \cref{thm:QPIP0BQP}.
+Again, the same argument from \cref{thm:MFZrep} applies. We simply repeat $\Pibz$ in parallel to get $\Pibzrep$.
 
@@
 
-Our results for $\BQP$ can be generalized to $\FBQP$ as follows:
+Our results for $\BQP$ can be generalized to $\FBQP$.
+We state our protocol for $\FBQP$ by using our $\Pibzrep$ as a blackbox.
+\Ethan{TODO Proofread me}
 
@@
 	By the soundness of $\Pibzrep$, $v_{i, b}=acc$ implies that $x\in L_{i, b}$ with overwhelming probability.
-	In other words, $y_i$ is correct with probability $1-\varepsilon_i$ where $\varepsilon_i=\negl(n)$.
-
+	In other words, $y_i$ has probability $\varepsilon_i=\negl(n)$ to be incorrect.
 	By union bound over all output bits, the soundness of $\Pi_{\FBQP}$ is then
-	$\sum_{i=1}^m \varepsilon_i$
-	which is clearly negligible.
+	$\sum_{i=1}^m \varepsilon_i=\negl(n)$.
 \end{prf}

### 2020-02-28 bqp.tex
Write BQP intros

@@
 
-\Ethan{TODO Intro this section}
+In this section we build our constant-round blind delegation protocols for $\BQP$ and $\FBQP$ with classical clients.
+We first construct our protocol for $\BQP$ in \cref{subsec:BlindBQP}, then use it to construct our protocol for $\FBQP$ in \cref{subsec:BlindFBQP}.
 
@@
 
-In this subsection we present our constant-round blind delegation protocol for $\BQP$.
-We'll construct said protocol piece by piece, starting with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16}.
-\Ethan{TODO finish outline and highlights}
+We build our constant-round blind delegation protocol for $\BQP$ first.
+We start with the protocol for $\BQP$ from \cite{mf16}, where the verifier requires a single-qubit register and is classical otherwise.
+We first obtain blindness by running said protocol under the homomorphic encryption given in \cite{mahadev_qfhe}.
+We then make the verifier fully classical using the same argument as used in \cite{FOCS:Mahadev18a}.
+Lastly, we use analysis from \cite{parallelrep, alagic2019twomessage} to ensure that it has negligible completeness and soundness errors while still being constant-round.
 
-This is a one-message $\QPIP_1$ protocol $\PiMF$ with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
+We start with the one-message $\QPIP_1$ protocol $\PiMF$ given in \cite{mf16} for deciding a $\BQP$ language $L$.
 Roughly, on input $x\in\set{0,1}^n$, the prover sends a certificate state $\rho$ to the verifier qubit-by-qubit.
@@
 		\item The prover generates a $m$-qubit certificate state $\rho\leftarrow\cPMF{1}(x)$ and sends $\rho$ to the verifier qubit-by-qubit.
-		\item The verifier generates $\Lambda \leftarrow \cVMF{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
+		\item The verifier samples $\Lambda \leftarrow \cVMF{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
 			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
@@
 
-We first compile $\PiMF$ using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol $\Piblind$ for $\BQP$.
-The high level idea is to run $\PiMF$ under $\mathsf{QHE}$.
+We now compile $\PiMF$ using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol $\Piblind$ for $\BQP$.
+The high level idea is to run $\PiMF$ under $\QHE$.
 Namely, the verifier encrypts its original input $x$ and sends $ct_x=\mathsf{QHE.Enc}(x)$ to the prover.
@@
 \subsection{Blind delegation of FBQP}
+\label{subsec:BlindFBQP}
 
-Our results for $\BQP$ can be generalized to $\FBQP$.
-We state our protocol for $\FBQP$ by using our $\Pibzrep$ as a blackbox.
-\Ethan{TODO Proofread me}
+Here we construct our delegation protocol for $\FBQP$.
+The idea is to break any $\FBQP$ instance down into $\BQP$ instances by considering the output bit-by-bit,
+so we can apply our results for $\BQP$.
 

### 2020-02-28 blind.tex
Update SampBQP blindness proof

@@
 \nc{\PSampB}{\ensuremath{P_\SampB}}
+\nc{\PSampBstar}{\ensuremath{P_\SampB^*}}
+\nc{\cVSampB}[1]{\ensuremath{\cV_{\SampB,#1}}}
+\nc{\cPSampB}[1]{\ensuremath{\cP_{\SampB,#1}}}
 
@@
 \begin{prf}
-	The proof is identical to that of \cref{thm:BlindBQP} up to relabeling.
-	\Ethan{too hand-wavy still, can still say ``identically simulates"}
-	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either; the proof only shows that the compiliation preserves soundness.
-	\Ethan{Soundness def. is different}
+	The proof is almost identical to that of \cref{thm:BlindBQP}.
+
+	The completeness follows by inspection.
+	For blindness, the prover receives only $ct_x$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.
+
+	Now we prove the soundness of $\PiSampB$.
+	Suppose for the sake of contradiction that there exists some cheating prover $\PSampBstar$ with some acceptance probability $\varepsilon\notin O(\frac{1}{\poly(n)})$.
+	Then we can construct a prover $\PSampstar$ violating the soundness guarantees of $\PiSamp$ by simulating $(\VSampB(x), \PSampBstar)$ as below:
+
+	We define $\PSampstar$ to first generate
+	$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
+	and
+	$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$,
+	then runs $\sigma\leftarrow\cPSampB{1}(pk, ct_x)$.
+	Finally, it decrypts
+	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
+	and sends it to $\VSamp$ qubit-by-qubit.
+
+	We now prove that $\PSampstar$ in fact violates the soundness of $\PiSamp$.
+	Observe that the experiments $(\PSampstar, \VSamp)(x)$ and $(\PSampBstar, \VSampB(x))$ are identical except for how $w$ is obtained from $\sigma$,
+	so by \cref{decodeMeasureOrder} they are equivalent.
+	Hence we have $\PSampstar$ with acceptance probability $\varepsilon$, which is a contradiction.
 \end{prf}

### 2020-02-28 bqp.tex
Work on BQP intros

@@
 
-In this section we build our constant-round blind delegation protocols for $\BQP$ and $\FBQP$ with classical clients.
-We first construct our protocol for $\BQP$ in \cref{subsec:BlindBQP}, then use it to construct our protocol for $\FBQP$ in \cref{subsec:BlindFBQP}.
+In this section we build our constant-round blind delegation \Ethan{Does ``delegation" imply verifiable?} protocols for $\BQP$ and $\FBQP$ with classical clients.
+
+In \cref{subsec:BlindBQP} we start with the protocol for $\BQP$ from \cite{mf16}.
+It has negligible completeness and soundness errors, but is not blind.
+Its verifier requires a single-qubit register and is classical otherwise.
+We first achieve blindness by running said protocol under the homomorphic encryption given in \cite{mahadev_qfhe}.
+We then make the verifier fully classical by using the compiler used in \cite{FOCS:Mahadev18a} even though it deteriorates soundness.
+Finally, we recover soundness while maintaining constant-round by running multiple copies in parallel,
+which we analyze using \cite{parallelrep, alagic2019twomessage}.
+
+In \cref{subsec:BlindFBQP} we then construct our protocol for $\FBQP$.
+The idea is to break any $\FBQP$ instance down into $\BQP$ instances by considering the output bit-by-bit,
+so we can apply our results for $\BQP$.
 
@@
 \label{subsec:BlindBQP}
-
-We build our constant-round blind delegation protocol for $\BQP$ first.
-We start with the protocol for $\BQP$ from \cite{mf16}, where the verifier requires a single-qubit register and is classical otherwise.
-We first obtain blindness by running said protocol under the homomorphic encryption given in \cite{mahadev_qfhe}.
-We then make the verifier fully classical using the same argument as used in \cite{FOCS:Mahadev18a}.
-Lastly, we use analysis from \cite{parallelrep, alagic2019twomessage} to ensure that it has negligible completeness and soundness errors while still being constant-round.
 
@@
 	The completeness follows by inspection.
-	For blindness, the only thing the prover receives is $c$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.
+	For blindness, the prover receives only $ct_x$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.
 
@@
 	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
-	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
-	Observe that the experiments $(\PMFstar, \VMF)(x)$ and $(\Pblindstar, \Vblind(x))$ are identical except for how $w$ is obtained from $\sigma$.
+	Observe that the experiments $(\PMFstar, \VMF)(x)$ and $(\Pblindstar, \Vblind(x))$ are identical except for how $w$ is obtained from $\sigma$,
 	so by \cref{decodeMeasureOrder} they are equivalent.
@@
 
-Next, we make the verifier completely classical by using \protoref{urmila4} from \cite{FOCS:Mahadev18a}.
-It was originally used to compile $\PiMF$ into $\PiMFZ$ that is $\QPIP_0$. \Ethan{Say a bit more?}
-It can however be applied to any $\QPIP_1$ protocol with $X$ and $Z$ measurement and negligible completeness and soundness errors.
+Next, we make the verifier completely classical by compiling $\Piblind$ using \protoref{urmila4} from \cite{FOCS:Mahadev18a}.
+It was originally used to compile $\PiMF$ into $\PiMFZ$,
+but in fact can be applied to any $\QPIP_1$ protocol to achieve similar effects.
 
@@
 \begin{prf}
-	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into a $\QPIP_0$ in a similar way and obtains this completeness and soundness.
-	Its proof uses only that $\PiMF$ is $\QPIP_1$ with only $X$ and $Z$ measurements on the verifier's side, with negligible completeness and soundness errors.
-	So the same argument applies here. \Ethan{TODO proofread me}
+	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into a $\PiMFZ$ which is $\QPIP_0$ in a similar way and obtains this completeness and soundness.
+	Its proof uses only that $\PiMF$ is $\QPIP_1$ with only $X$ and $Z$ measurements \Ethan{phrasing}, with negligible completeness and soundness errors.
+	So the same argument applies here. \Ethan{TODO proofread me? Does 2-round vs 1-round matter?}
 
@@
 
-Again, the same argument from \cref{thm:MFZrep} applies. We simply repeat $\Pibz$ in parallel to get $\Pibzrep$.
+The argument from \cref{thm:MFZrep} applies here too. We simply repeat $\Pibz$ for $\poly(n)$ times in parallel to get $\Pibzrep$.
 
@@
 
-Here we construct our delegation protocol for $\FBQP$.
-The idea is to break any $\FBQP$ instance down into $\BQP$ instances by considering the output bit-by-bit,
-so we can apply our results for $\BQP$.
+Here we state our delegation protocol for $\FBQP$.
+\Ethan{TODO high level overview, and mention one-sided vs two-sided}
 
@@
 	Verifier's input: $x\in\set{0, 1}^n$
-
-	Public input: $f$
 

### 2020-02-29 bqp.tex
Make another BQP editorial pass

@@
 
-\def\MFZ{\mathsf{MFZ}}
+\def\MFZ{\mathsf{MF, 0}}
 \nc{\PiMFZ}{\ensuremath{\Pi_\MFZ}}
@@
 
-In this section we build our constant-round blind delegation \Ethan{Does ``delegation" imply verifiable?} protocols for $\BQP$ and $\FBQP$ with classical clients.
+In this section we build our constant-round blind delegation schemes for $\BQP$ and $\FBQP$ with classical clients.
 
-In \cref{subsec:BlindBQP} we start with the protocol for $\BQP$ from \cite{mf16}.
-It has negligible completeness and soundness errors, but is not blind.
-Its verifier requires a single-qubit register and is classical otherwise.
+In \cref{subsec:BlindBQP} we start with the protocol for $\BQP$ from \cite{mf16} which has negligible completeness and soundness errors, but is not blind;
+its verifier requires a single-qubit register and is classical otherwise.
 We first achieve blindness by running said protocol under the homomorphic encryption given in \cite{mahadev_qfhe}.
 We then make the verifier fully classical by using the compiler used in \cite{FOCS:Mahadev18a} even though it deteriorates soundness.
-Finally, we recover soundness while maintaining constant-round by running multiple copies in parallel,
-which we analyze using \cite{parallelrep, alagic2019twomessage}.
+Finally, we recover soundness while maintaining constant-round by running multiple copies of the protocol in parallel,
+which we analyze using results from \cite{parallelrep, alagic2019twomessage}.
 
 In \cref{subsec:BlindFBQP} we then construct our protocol for $\FBQP$.
-The idea is to break any $\FBQP$ instance down into $\BQP$ instances by considering the output bit-by-bit,
+The idea is to break an $\FBQP$ instance down into $\BQP$ instances by considering the output bit-by-bit,
 so we can apply our results for $\BQP$.
@@
 Namely, the verifier encrypts its original input $x$ and sends $ct_x=\mathsf{QHE.Enc}(x)$ to the prover.
-The prover then homomorphically evaluates $\cPMF{3}$ on $ct_x$ to produce $\sigma$ and sends it to the verifier.
+The prover then homomorphically evaluates $\cPMF{1}$ on $ct_x$ to produce $\sigma$ and sends it to the verifier.
 
@@
 Pauli one-time-pads commute with $X$ and $Z$ measurements, so the verifier can measure the one-time-padded state as usual, then correct the measurement results using the Pauli keys.
-Now we state and prove this observation in more precise terms.
+We state and prove this observation in more precise terms.
 
@@
 
-Now we state our construction of blind $\QPIP_1$ for $\BQP$:
+Now we're ready to state our blind $\QPIP_1$ construction for $\BQP$.
 
@@
 Next, we make the verifier completely classical by compiling $\Piblind$ using \protoref{urmila4} from \cite{FOCS:Mahadev18a}.
-It was originally used to compile $\PiMF$ into $\PiMFZ$,
-but in fact can be applied to any $\QPIP_1$ protocol to achieve similar effects.
-
-We give a high-level overview of the compiliation results.
+It was originally used to compile $\PiMF$ into $\PiMFZ$ to allow a purely classical client,
+but it can be applied to other $\QPIP_1$ protocols such as our $\Piblind$.
+We give a high-level overview of our compiliation results.
 
@@
 \begin{thm}
-	$\Pibz$ has negligible completeness error. Its soundness error is negligibly close to $\frac{3}{4}$. It is blind.
+	$\Pibz$ has negligible completeness error and is blind. Its soundness error is negligibly close to $\frac{3}{4}$.
 \end{thm}
 \begin{prf}
-	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into a $\PiMFZ$ which is $\QPIP_0$ in a similar way and obtains this completeness and soundness.
-	Its proof uses only that $\PiMF$ is $\QPIP_1$ with only $X$ and $Z$ measurements \Ethan{phrasing}, with negligible completeness and soundness errors.
-	So the same argument applies here. \Ethan{TODO proofread me? Does 2-round vs 1-round matter?}
+	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into $\PiMFZ$ similarly and obtains this completeness and soundness.
+	It uses that $\PiMF$ is $\QPIP_1$ with negligible completeness and soundness errors,
+	and that its verifier only performs $X$ and $Z$ measurements in addition to classical operations.
+	As $\Piblind$ fulfills all these requirements, the same arguments can also be used for the completeness and soundness of $\Pibz$.
 
-	For blindness, recall that the prover receives $ct_x, pk, k, c$ from the verifier.
-	Blindness follows by the semantic security of $\QHE$ and the fact that $k$ computationally hides the measurement basis choice $\Lambda'$.
+	For blindness, recall that the prover receives $ct_x, pk, k, c$ from the verifier,
+	so it follows by the semantic security of $\QHE$ and the fact that $k$ computationally hides the measurement basis choice $\Lambda'$.
 \end{prf}
 
-We use the recent results \cite{parallelrep, alagic2019twomessage} to apply parallel repetition to $\Pibz$ to get $\Pibzrep$ which has negligible soundness.
+Finally, we use the recent results \cite{parallelrep, alagic2019twomessage} to recover soundness by means of parallel repetition.
+We first summarize said results.
 
@@
 	\label{thm:MFZrep}
-	$\PiMFZ$ can be repeat in parallel, obtaining $\PiMFZrep$ that has negligible completeness and soundness errors.
+	$\PiMFZ$ can be repeated in parallel, obtaining $\PiMFZrep$ that has negligible completeness and soundness errors.
 \end{thm}
 
-The argument from \cref{thm:MFZrep} applies here too. We simply repeat $\Pibz$ for $\poly(n)$ times in parallel to get $\Pibzrep$.
-
+We can now finish building our delegation scheme for $\BQP$.
 \begin{thm}
 	\label{thm:QPIP0BQP}
-	$\Pibzrep$ is a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
+	By repeating $\Pibz$ for $\poly(n)$ times in parallel,
+	we obtain $\Pibzrep$ which is a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
 \end{thm}
+\begin{prf}
+	The same argument from \cref{thm:MFZrep} applies.
+	\Ethan{How to make this more rigorous?}
+\end{prf}
 
@@
 Here we state our delegation protocol for $\FBQP$.
-\Ethan{TODO high level overview, and mention one-sided vs two-sided}
+We do so by breaking an $\FBQP$ instance down into $\BQP$ instances.
+Note that our $\BQP$ scheme is one-sided; the prover is allowed to cause the verifier to reject a yes-instance.
+As a result, we run two copies of $\Pbzrep$ for every output bit as below:
 
@@
 
-	Let $m=\abs{f(x)}$; we assume without loss of generality that it depends only on $n$ and can be efficiently computed classically.
 	Denote the $i$-th bit of $f(x)$ as $f_i(x)$.
 	For $i\in\bbN, b\in\set{0,1}$, define the $\BQP$ language $L_{i, b}=\set{s\in\set{0,1}^* : f_i(s)=b}$.
+	Let $m=\abs{f(x)}$; we assume without loss of generality that it depends only on $n$ and can be efficiently computed classically.
 	\begin{enumerate}
@@
 	In other words, $y_i$ has probability $\varepsilon_i=\negl(n)$ to be incorrect.
-	By union bound over all output bits, the soundness of $\Pi_{\FBQP}$ is then
+	By union bound over all output bits, the soundness of $\Pi_{\FBQP}$ is
 	$\sum_{i=1}^m \varepsilon_i=\negl(n)$.

### 2020-02-29 bqp.tex
Fix grammar

@@
 It was originally used to compile $\PiMF$ into $\PiMFZ$ to allow a purely classical client,
-but it can be applied to other $\QPIP_1$ protocols such as our $\Piblind$.
+but in fact can be applied to other $\QPIP_1$ protocols such as our $\Piblind$.
 We give a high-level overview of our compiliation results.

### 2020-02-29 preliminaries.tex
Implement more Skype call comments
Define soundness of QPIP with one param

@@
 		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
-		\item (Soundness) For all $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$ outputs a distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
+		\item (Soundness) Define the ideal output distribution $D_{x, \alpha}$ as first flipping a weighted coin with head probability $\alpha$.
+On head, output $\bot$.
+On tail, sample and output from $D_x$.
+			Then the protocol is sound if for all cheating prover $\bbP^*$, there exists $\alpha$ so that the output distribution of $(\bbP^*, \bbV)$ is negligibly close to $D_{x, \alpha}$.
 	\end{itemize}

### 2020-02-29 preliminaries.tex
Remove BQP definition
Fix BQP definition

@@
 I.e.
-$\Lambda^2_{1, 2}(X_3)$ would be a Toffoli (CCNOT) gate.
+$\Lambda^2_{1, 2}(X_3)$ would be a Toffoli gate.
 
@@
 \begin{definition} [$\BQP$]
-	\Ethan{TODO: Replace this with something that makes more sense}
-	A language $L$ is in $\BQP$ if it can be decided by some uniform quantum circuit family.
+	$\BQP$ is the class of languages $L$ for which for all $n\in\bbN$ there exists a quantum circuit constructible in time $\poly(n)$ that, given any $x\in\set{0, 1}^n$ as input, correctly decides whether $x\in L$ at least $\frac{2}{3}$ of the time.
 \end{definition}

### 2020-02-29 preliminaries.tex
Fix BQP definition

--- 2020-02-29 preliminaries.tex
@@
 	\Ethan{TODO: Replace this with something that makes more sense}
-	A language $L$ is in $\BQP$ if it can be decided by some uniform quantum circuit family.
+	$\SampBQP$ is the class of languages $L$ for which for all $n\in\bbN$ there exists a quantum circuit constructible in time $\poly(n)$ that, given any $x\in\set{0, 1}^n$ as input, correctly decides whether $x\in L$ at least $\frac{2}{3}$ of the time.
 \end{definition}

### 2020-02-29 preliminaries.tex
Make editorial changes in prelim

--- 2020-02-29 preliminaries.tex
@@
 	$\BQP$ is the class of languages $L$ for which for all $n\in\bbN$ there exists a quantum circuit constructible in time $\poly(n)$ that, given any $x\in\set{0, 1}^n$ as input, correctly decides whether $x\in L$ at least $\frac{2}{3}$ of the time.
-\end{definition}
 
@@
 
-The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients:
+The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitates the use of classical clients:
 \begin{itemize}
@@
 \end{itemize}
-
-As we will see, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then $\QHE$ can be used as a compiler to achieve blindness.

### 2020-03-04 bqp.tex
Fix typo
Add Skype discussion results

@@
 	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\QDec_{sk}}$ s.t.
-	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement:
+	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement: \Ethan{Just use basis choice string instead}
 	$$\cM_\QHE(\Lambda)=\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$$
-	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and
+	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and \Ethan{Function compositions feels weird}
 	$$\widehat{\mathsf{QHE.Dec}_{sk}}\circ\Lambda'=\Lambda\circ\mathsf{QHE.Dec_{sk}}$$
@@
 	so by \cref{decodeMeasureOrder} they are equivalent.
-	Hence we have $\PMFstar$ with noticeable acceptance probability $\varepsilon$, which is a contradiction.
+	Hence we have $\PMFstar$ with noticeable acceptance probability $\varepsilon$, which is a contradiction. \Ethan {Write more details; more formula}
 \end{prf}
@@
 
-\begin{protocol}{Blind $\QPIP_0$ protocol $\Pibz$ for $BQP$ language $L$}
+\begin{protocol}{Blind $\QPIP_0$ protocol $\Pibz$ for $\BQP$ language $L$}
 	\label{proto:QPIP0BQP}
@@
 	\label{thm:MFZrep}
-	$\PiMFZ$ can be repeated in parallel, obtaining $\PiMFZrep$ that has negligible completeness and soundness errors.
+	$\PiMFZ$ can be repeated in parallel, obtaining $\PiMFZrep$ that has negligible completeness and soundness errors. \Ethan{Just remove this}
 \end{thm}
+
+\Ethan{Just define parallel repetition in words}
 
@@
 Note that our $\BQP$ scheme is one-sided; the prover is allowed to cause the verifier to reject a yes-instance.
-As a result, we run two copies of $\Pbzrep$ for every output bit as below:
+\Ethan{Explain this better...
+Write more intuitions.
+Decision vs function problems; exists vs for all}
+As a result, we run two copies of $\Pibzrep$ for every output bit as below:
 

### 2020-03-04 qpip0.tex
Add Skype discussion results

@@
 
+\begin{definition}[computationally indistinguishable]
+\hannote{move later}
+Let  $D_1$ and $D_2$ be distributions over $n$-bit string.
+We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes a sample from $D_1$ as part of its input.
+\end{definition}
+%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.
+
+\begin{rmk}
+If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
+\end{rmk}
+
+\hannote{comp. indistinguish for subnormalized state?}
+\hannote{triangle inequality}
+
 \begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
+If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
 \end{lemma}
@@
 \end{theorem}
-
-\begin{definition}[computationally indistinguishable]
-\hannote{move later}
-Let  $D_1$ and $D_2$ be distributions over $n$-bit string.
-We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes a sample from $D_1$ as part of its input.
-\end{definition}
-%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.
-
-\begin{rmk}
-If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
-\end{rmk}
 
@@
 
+\hannote{$\rho$ is sub normalized}
+
+\hannote{need to simulate one copy?}
+
+For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp} and $i\in [m]$, consider the following prover strategy for Protocol~\ref{proto:urmila4}: on the first round, try to create $\ket{\psi_{???}}$ \hannote{which $i$ do i use?}
+
 ===

### 2020-03-04 bqp-rewrite.tex
Add BQP Rewrite section

\section{REWRITE - Blind Delegation for BQP and FBQP}
\label{sec:BlindBQP2}

Let $\Pi$ be...
then there exists $\Pi$

### 2020-03-05 qpip0.tex

@@
 
+\begin{lem}~\label{lem:trivial-4-round-strategy}
+    For any input, there exist a prover strategy for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{n}$ in the testing round and \hannote{binding?}.
+\end{lem}
+
 \begin{definition}[computationally indistinguishable]
@@
     \item Run $m=O(1/\varepsilon^2)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications.
-The copies share the same $h$ but have separate $\{sk\}$, $\{pk\}$, $\{y\}$, $\{c\}$, and $\{a\}$.
-The prover use $h$ specifier by step~\ref{} of Protocol~\ref{ProtoQPIP1} to generate $\{sk\}$ and $\{pk\}$ for all copies on the first round.
+The copies have separate $\{h\}$, $\{sk\}$, $\{pk\}$, $\{y\}$, $\{c\}$, and $\{a\}$.
+The verifier draws $\{h\}$ independently from the distribution specifier by step~\ref{} of Protocol~\ref{ProtoQPIP1} to generate $\{sk\}$ and $\{pk\}$ for all copies on the first round.
 On the second round, for each copy, the prover choose the state specified by step~\ref{} of Protocol~\ref{ProtoQPIP1}  (with  $(C,x,\eps)$ as input) as $\rho$.
@@
 
-For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp} and $i\in [m]$, consider the following prover strategy for Protocol~\ref{proto:urmila4}: on the first round, try to create $\ket{\psi_{???}}$ \hannote{which $i$ do i use?}
+For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp} and $i\in [m]$, consider the following prover strategy for Protocol~\ref{proto:urmila4}: on the second round, the prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
+The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
+If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  fact ???
+instead.
+On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$.
+otherwise he run $U_{trivial}$    described  in  fact ???.
+
+By
 

### 2020-03-06 bqp-rewrite.tex
add blind QPIP0 compiler

@@
 
-Let $\Pi$ be...
-then there exists $\Pi$
+In this section we show that there's a relatively simple way to create a blind and constant-round $\QPIP_0$ delegation protocol.
+We create our protocol by running the constant-round $\QPIP_0$ protocol from \cite{FOCS:Mahadev18a} under $\QHE$ from \cite{mahadev_qfhe}.
+This is possible due to certain additional properties of $\QHE$ that facilitates the use of a classical client.
+Roughly speaking, measuring the ciphertext in standard basis converts the ciphertext into a ciphertext under some certain other classical homomorphic encryption.
+
+\def\HE{\mathsf{HE}}
+\def\HGen{\mathsf{HE.Keygen}}
+\def\HEnc{\mathsf{HE.Enc}}
+\def\HEval{\mathsf{HE.Eval}}
+\def\HDec{\mathsf{HE.Dec}}
+
+\begin{protocol}{Compiling $\QPIP_0$ protocol $(P, V)(x)$ into $(\Pblind, \Vblind(x))$}
+	Suppose the protocol $(P, V)$ is $2T$-rounds with the following description:
+
+	Public input: $x$
+	\begin{enumerate}
+		\item $P$ generates initial state $st_{P, 0}\leftarrow\cP_0$
+		\item $V$ generates initial states $st_{V, 0}\leftarrow\cV_0$
+		\item for $t=1,\ldots,T$:
+		\begin{enumerate}
+			\item $V$ generates $v_t\leftarrow\cV_t(st_{V, t-1})$ and sends it to the prover.
+			\item $P$ generates $(p_t, st_{P, t})\leftarrow\cP_t(v_t, st_{P, t-1})$ and sends $p_t$ to the verifier.
+			\item $V$ updates its state as $st_{V, t}\leftarrow\cV_t'(p_t, v_t, st_{V, t-1})$
+		\end{enumerate}
+		\item $V$ computes its output $o\leftarrow\cV_{out}(st_{V, T})$
+	\end{enumerate}
+
+	Then define the protocol $\Piblind$ with security parameter $\lambda$ as below:
+
+	Verifier's input: $x$
+	\begin{enumerate}
+		\item $\Vblind$ generates $(pk, sk)\leftarrow\QGen(1^\lambda, 1^L)$ for sufficiently large depth $L$ and sends $pk$ to $\Pblind$.
+		\item $\Pblind$ generates $q_{st_{P, 0}}\leftarrow\QEval_{pk}(\cP_0)$
+		\item $\Vblind$ generates $h_{st_{V, 0}}\leftarrow\HEval_{pk}(\cV_0)$
+		\item for $t=1,\ldots,T$:
+		\begin{enumerate}
+			\item $\Vblind$ generates $h_{v_t}\leftarrow\HEval_{pk}(\cV_t(st_{V, t-1}))$.
+				Then it uniformly samples $r_t\xleftarrow{\$}\set{0,1}^{\abs{v_t}}$,
+				and computes $h_{r_t}\leftarrow\HEnc_{pk}(r_t)$.
+				It sends $q_{v_t}\leftarrow(r_t, h_{r_t}\oplus_{H, pk} h_{v_t})$ to the server.
+			\item $\Pblind$ generates $(q_{p_t}, st_{P, t})\leftarrow\cP_t(q_{v_t}, st_{P, r-1})$ and sends $q_{p_t}=(p_t\oplus s_t, h_{s_t})$ to the verifier.
+			\item $\Vblind$ encrypts the first part of $q_{p_t}$ under $\HE$ in order to homomorphically compute $p_t$ by $h_{p_t}\leftarrow\HEnc_{pk}(p_t\oplus s_t)\oplus_{H, pk} h_{s_t}$.
+				It updates its state as $c_{st_{V, t}}\leftarrow\HEval_{pk}(\cV_t', (h_{p_t}, h_{v_t}, c_{st_{V, t-1}}))$
+		\end{enumerate}
+		\item $\Vblind$ generates $c_o\leftarrow\HEval_{pk}(\cV_{out}, c_{st_{V, T}})$ and outputs $\HDec_{sk}(c_o)$.
+	\end{enumerate}
+
+\end{protocol}
+
+\begin{theorem}
+	For all cheating prover $\Pblind^*$ of $\Piblind$, there exists a cheating prover $P^*$ of $\Pi$ s.t.
+for all input $x$, the output distributions of $(\Pblind, \Vblind(x))$ and $(P, V)(x)$ are negligibly close.
+\end{theorem}
+\begin{proof}
+	TODO
+\end{proof}

### 2020-03-09 bqp-rewrite.tex
Rewrite blindness compiler

--- 2020-03-04 bqp-rewrite.tex
@@
 
-Let $\Pi$ be...
-then there exists $\Pi$
+In this section we show that there's a relatively simple way to create a blind and constant-round $\QPIP_0$ delegation protocol.
+We create our protocol by running the constant-round $\QPIP_0$ protocol from \cite{FOCS:Mahadev18a} under $\QHE$ from \cite{mahadev_qfhe}.
+This is possible due to certain additional properties of $\QHE$ that facilitates the use of a classical client.
+Roughly speaking, measuring the ciphertext in standard basis converts the ciphertext into a ciphertext under some certain other classical homomorphic encryption.
+
+\def\HE{\mathsf{HE}}
+\def\HGen{\mathsf{HE.Keygen}}
+\def\HEnc{\mathsf{HE.Enc}}
+\def\HEval{\mathsf{HE.Eval}}
+\def\HDec{\mathsf{HE.Dec}}
+
+\nc{\ctx}[2]{\ensuremath{{{#1}^{(#2)}}}}
+
+Due to some properties (TODO) of $\QHE$, we can abuse the notation and write a collection of registers encrypted under $\QHE$ as $(x_1, x_2)'=(x_1', x_2')$ for $\QHE$...
+So suppose $f$ outputs a tuple of registers, when it is evaluated homomorphically we can split its output into corresponding encrypted registers too.
+
+\begin{protocol}{Compiling $\QPIP_0$ protocol $(P, V)(x)$ into $(\Pblind, \Vblind(x))$}
+	Suppose the protocol $(P, V)$ is a $\QPIP_0$ protocol where only the verifier receives outputs, with the following general form:
+
+	Public input: $x$
+	\begin{enumerate}
+		\item $V$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$ and sends $v_1$ to the prover.
+		\item $P$ generates $(p_1, st_{P, 1})\leftarrow\cP_1(v_1, x)$ and sends $p_1$ to the verifier.
+		\item for $t=2,\ldots,T$:
+		\begin{enumerate}
+			\item $V$ generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$ and sends $v_t$ to the prover.
+			\item $P$ generates $(p_t, st_{P, t})\leftarrow\cP_t(v_t, st_{P, t-1})$ and sends $p_t$ to the verifier.
+		\end{enumerate}
+		\item $V$ computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$
+	\end{enumerate}
+
+	Using $\Pi=(P, V)(x)$ from above, we now define the protocol $\Piblind=(P, V(x))$ as follows:
+
+	Let $L_t$ be the circuit depth of $\cP_t$.
+	Let $\lambda=\abs{x}$.
+
+	Verifier's input: $x$
+	\begin{enumerate}
+		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
+			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$,
+			and encrypts $\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
+			It sends $pk_1$, $\ctx{x}{1}$, and $\ctx{v_1}{1}$ to the prover.
+		\item $\Pblind$ generates $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\QEval_{pk}(\cP_0, \ctx{v_1}{1}, \ctx{x}{1})$.
+			It sends $\ctx{p_1}{1}$ to the verifier.
+		\item for $t=2,\ldots,T$:
+		\begin{enumerate}
+			\item $\Vblind$ decrypts the prover's message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p_{t-1}}{t-1})$,
+				and generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
+				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$,
+				and produces encryptions $\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t)$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
+				It sends $pk_t$, $\ctx{v_t}{t}$, and $\ctx{sk_{t-1}}{t}$ to the prover.
+			\item $\Pblind$ updates its state to use the new $\QHE$ key by
+				first encrypting it under the new key by $\ctx{st_{P, t-1}}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st_{P, t-1}}{t-1}))$,
+				then homomorphically decrypting the old encryption by
+				$\ctx{st_{P, t-1}}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1, t})$.
+				It then applies the next-message function of $\Pi$, generating
+				$(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\QEval_{pk_t}(\cP_t, \ctx{v_t}{t}, \ctx{st_{P, t-1}}{t})$.
+				It sends $\ctx{p_t}{t}$ back to the verifier.
+		\end{enumerate}
+		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec_{sk_T}(\ctx{p_T}{T})$.
+			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
+	\end{enumerate}
+\end{protocol}
+
+By the correctness of $\QHE$, the completeness error of $\Piblind$ is negligibly close to that of $\Pi$.
+We show the soundness of $\Piblind$ in the following theorem.
+
+\begin{theorem}
+	For all cheating prover $\Pblind^*$ of $\Piblind$, there exists a cheating prover $P^*$ of $\Pi$ s.t.
+for all input $x$, the output distributions of $(\Pblind, \Vblind(x))$ and $(P, V)(x)$ are negligibly close.
+\end{theorem}
+\begin{proof}
+	TODO
+\end{proof}
+
+Finally, we show the blindness of $\Piblind$ through a standard hybrid argument as below:
+\begin{theorem}
+	$\Piblind$ is blind.
+\end{theorem}
+\begin{proof}
+	Consider $T$ hybrids...
+\end{proof}

### 2020-03-09 bqp-rewrite.tex
Write proof draft for blindness compiler soundness

@@
 
-	Using $\Pi=(P, V)(x)$ from above, we now define the protocol $\Piblind=(P, V(x))$ as follows:
+	Using $\Pi=(P, V)(x)$ from above, we define the protocol $\Piblind=(P, V(x))$ as follows:
+
+	Verifier's input: $x$
 
@@
 
-	Verifier's input: $x$
 	\begin{enumerate}
@@
 			It sends $pk_1$, $\ctx{x}{1}$, and $\ctx{v_1}{1}$ to the prover.
-		\item $\Pblind$ generates $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\QEval_{pk}(\cP_0, \ctx{v_1}{1}, \ctx{x}{1})$.
+		\item $\Pblind$ generates $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\cPblind{1}(\ctx{v_1}{1}, \ctx{x}{1})$
+			by evaluating $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\QEval_{pk}(\cP_1, \ctx{v_1}{1}, \ctx{x}{1})$.
 			It sends $\ctx{p_1}{1}$ to the verifier.
@@
 		\begin{enumerate}
-			\item $\Vblind$ decrypts the prover's message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p_{t-1}}{t-1})$,
-				and generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
+			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p_{t-1}}{t-1})$,
+				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
 				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$,
@@
 				It sends $pk_t$, $\ctx{v_t}{t}$, and $\ctx{sk_{t-1}}{t}$ to the prover.
-			\item $\Pblind$ updates its state to use the new $\QHE$ key by
+			\item $\Pblind$ generates $(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\cPblind{t}(\ctx{v_t}{t}, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1})$
+				by first refreshing the $\QHE$ key that encrypts its states by
 				first encrypting it under the new key by $\ctx{st_{P, t-1}}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st_{P, t-1}}{t-1}))$,
-				then homomorphically decrypting the old encryption by
+				then homomorphically decrypting the old encryption under the new key by
 				$\ctx{st_{P, t-1}}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1, t})$.
@@
 
+\def\Pstar{P^*}
+\nc{\cPstar}[1]{\ensuremath{\cP^*_{#1}}}
+
 \begin{theorem}
-	For all cheating prover $\Pblind^*$ of $\Piblind$, there exists a cheating prover $P^*$ of $\Pi$ s.t.
-for all input $x$, the output distributions of $(\Pblind, \Vblind(x))$ and $(P, V)(x)$ are negligibly close.
+	For all cheating prover $\Pblindstar$, there exists a cheating prover $\Pstar$ s.t. for all input $x$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
 \end{theorem}
 \begin{proof}
-	TODO
+	We define $\Pstar$ so that on $\cPstar{1}$ it generates
+	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$, then produces the encryptions
+	$\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
+	It then runs $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\cPblind{1}(\ctx{v_1}{1}, \ctx{x}{1})$.
+	Finally, it decrypts $p_1\leftarrow\QDec_{sk_1}(\ctx{p_1}{1})$ and sends it back to the verifier,
+	and keeps $\ctx{st_{P, 1}}{1}$ and $sk_1$.
+	Then, on the rest of the $\cPstar{t}$ rounds, $\Pstar$ generates
+	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$, and produces ciphertexts
+	$\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
+	It then runs $(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\cPblind{t}(\ctx{v_t}{t}, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1})$.
+	Finally, it decrypts $p_t\leftarrow\QDec_{sk_t}(\ctx{p_t}{1})$ and sends it back to the verifier,
+	and keeps $\ctx{st_{P, t}}{t}$ and $sk_t$.
+
+	By construction, the experiments $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
 \end{proof}
 
-Finally, we show the blindness of $\Piblind$ through a standard hybrid argument as below:
+Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
 \begin{theorem}

### 2020-03-09 bqp-rewrite.tex
Write first draft of how Piblind is blind

@@
 \begin{proof}
-	Consider $T$ hybrids...
+	Consider $T+1$ hybrids experiments, from $\Hyb_1$ to $\Hyb_{T+1}$.
+	In $\Hyb_i$, we modify $(\Pblind, \Vblind(x))$ s.t.
+	for all rounds associated with $\cV{t}$ where $t\geq i$, the verifier replaces the $\ctx{sk_{t-1}}{t}$ in its message with encryption of $0$.
+	Then, for all $t$, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
+	Since computational indistinguishability is transitive \Ethan{really?}, $\Hyb_1$ is indistinguishable with $\Hyb_{T+1}$.
+	Note that $\Hyb_{T+1}$ is precisely $\Piblind$, and $\Hyb_1$ is clearly blind. So $\Hyb_{T+1}$ is also blind.
 \end{proof}

### 2020-03-10 bqp-rewrite.tex
Attempt to intro blind compiler

@@
-\section{REWRITE - Blind Delegation for BQP and FBQP}
-\label{sec:BlindBQP2}
-
-In this section we show that there's a relatively simple way to create a blind and constant-round $\QPIP_0$ delegation protocol.
-We create our protocol by running the constant-round $\QPIP_0$ protocol from \cite{FOCS:Mahadev18a} under $\QHE$ from \cite{mahadev_qfhe}.
-This is possible due to certain additional properties of $\QHE$ that facilitates the use of a classical client.
-Roughly speaking, measuring the ciphertext in standard basis converts the ciphertext into a ciphertext under some certain other classical homomorphic encryption.
-
 \def\HE{\mathsf{HE}}
@@
 
+\section{REWRITE - Blind Delegation for BQP and FBQP}
+\label{sec:BlindBQP2}
+
 \nc{\ctx}[2]{\ensuremath{{{#1}^{(#2)}}}}
 
-Due to some properties (TODO) of $\QHE$, we can abuse the notation and write a collection of registers encrypted under $\QHE$ as $(x_1, x_2)'=(x_1', x_2')$ for $\QHE$...
-So suppose $f$ outputs a tuple of registers, when it is evaluated homomorphically we can split its output into corresponding encrypted registers too.
+In this section we show a relatively simple way to create a blind and constant-round $\QPIP_0$ delegation protocol for $\BQP$.
+We create our protocol by running the constant-round $\QPIP_0$ protocol from \cite{FOCS:Mahadev18a} under $\QHE$ from \cite{mahadev_qfhe}.
+This is possible due to additional properties of $\QHE$ that facilitates the use of a classical client. Its encryption can be performed classically.
+Then, after the homomorphic evaluation, the server could homomorphically measure the ciphertexts and send the results for the classical client to decrypt.
+In fact, this approach is powerful enough to give blindness to any $\QPIP_0$ protocol.
+
+We start with a summarization of $\QHE$ and notations.
+First, when there are many sets of $\QHE$ keys in play at the same time,
+we use $\ctx{x}{i}$ to denote $x$ encrypted under $pk_i$.
+Otherwise, we write $x'$ for a ciphertext corresponding to plaintext $x$.
+Moreover, the encryption is done on a qubit-by-qubit basis,
+so we can write $(x_1, x_2)'=(x_1', x_2')$.
 
@@
 		\end{enumerate}
-		\item $V$ computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$
+		\item $V$ computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
+			\Ethan{Prover can get outputs too}
 	\end{enumerate}
@@
 			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
+			\Ethan{Prover can get outputs too}
 	\end{enumerate}

### 2020-03-12 bqp-rewrite.tex
Work on blindness compiler intro

@@
 
-In this section we show a relatively simple way to create a blind and constant-round $\QPIP_0$ delegation protocol for $\BQP$.
-We create our protocol by running the constant-round $\QPIP_0$ protocol from \cite{FOCS:Mahadev18a} under $\QHE$ from \cite{mahadev_qfhe}.
-This is possible due to additional properties of $\QHE$ that facilitates the use of a classical client. Its encryption can be performed classically.
-Then, after the homomorphic evaluation, the server could homomorphically measure the ciphertexts and send the results for the classical client to decrypt.
-In fact, this approach is powerful enough to give blindness to any $\QPIP_0$ protocol.
+In this section we show a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
+We start with the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
+Generally one can obtain blindness by running a protocol under homomorphic encryption.
+\Ethan{Maybe cite?} In our case, we have a classical client and a quantum server, so we choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.
 
-We start with a summarization of $\QHE$ and notations.
-First, when there are many sets of $\QHE$ keys in play at the same time,
+We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.
+First, when the plaintext is classical, the encryption can be performed classically.
+Moreover, a quantum ciphertext can be measured homomorphically, in which case the measurement outcomes can then be decrypted classically.
+Lastly, the encryption is done qubit-by-qubit, so one can split a ciphertext into registers as one would with the corresponding plaintext.
+
+We now state our compiler that gives any $\QPIP_0$ protocol blindness.
+For notation, when there are many sets of $\QHE$ keys in play at the same time,
 we use $\ctx{x}{i}$ to denote $x$ encrypted under $pk_i$.
 Otherwise, we write $x'$ for a ciphertext corresponding to plaintext $x$.
-Moreover, the encryption is done on a qubit-by-qubit basis,
+Moreover, the encryption is qubit-by-qubit,
 so we can write $(x_1, x_2)'=(x_1', x_2')$.
@@
 	Then, for all $t$, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
-	Since computational indistinguishability is transitive \Ethan{really?}, $\Hyb_1$ is indistinguishable with $\Hyb_{T+1}$.
-	Note that $\Hyb_{T+1}$ is precisely $\Piblind$, and $\Hyb_1$ is clearly blind. So $\Hyb_{T+1}$ is also blind.
+	Since computational indistinguishability is transitive \Ethan{Really? Definitely need to write down some inequalities here...}, $\Hyb_1$ is indistinguishable with $\Hyb_{T+1}$.
+	Since $\Hyb_{T+1}$ is precisely $\Piblind$, and $\Hyb_1$ is clearly blind, we can conclude that $\Piblind$ is blind.
 \end{proof}

### 2020-03-12 qpip.tex
Work on blindness compiler intro

@@
 Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state.
+\Ethan{Properly intro and point out the difference between BQP and SampBQP and the challenge here.}
 In the case of decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}.
@@
 
+\def\GS{\mathsf{GS}}
+\nc{\PiGS}{\ensuremath{\Pi_\GS}}
+\nc{\VGS}{\ensuremath{V_\GS}}
+\nc{\PGS}{\ensuremath{P_\GS}}
+\nc{\PGSstar}{\ensuremath{P_\GS^*}}
+\nc{\cVGS}[1]{\ensuremath{\cV_{\GS,#1}}}
+\nc{\cPGS}[1]{\ensuremath{\cP_{\GS,#1}}}
+
 \begin{lemma}
 	\label{ProtoGroundStateCheck}
-	There is a $\QPIP_1$ protocol for \cref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
+	There is a $\QPIP_1$ protocol $\PiGS$ for \cref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
 \end{lemma}

### 2020-03-12 qpip0.tex
Work on blindness compiler intro

@@
 
-\begin{definition}[computationally indistinguishable]
+\begin{definition}[quantum computationally indistinguishable]
 \hannote{move later}
 Let  $D_1$ and $D_2$ be distributions over $n$-bit string.
-We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes a sample from $D_1$ as part of its input.
+We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes \emph{one} sample from $D_1$ as part of its input.
+We also denote this as
+$$ D_1 \approx_{q,\eps} D_2$$
 \end{definition}
@@
 \begin{rmk}
+We extend the definition of computational distance to a subnormalized distribution  $D$  by assuming $A(D)=0$ when $A$ fail to draw a sample from $D$.
+\end{rmk}
+
+\begin{rmk}
 If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
 \end{rmk}
+
+\begin{lem}[triangle inequality for computational distance]
+Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.
+
+If 
+\begin{align}
+    D_1 &\approx_{q,\eps} D_2 \\
+    D_4 &\approx_{q,\eps'} D_6, 
+\end{align}
+then 
+\begin{align}
+    D_3 \approx_{q,\eps+\eps'} D_5
+\end{align}
+\end{lem}
+\begin{proof}
+
+\end{proof}
 

### 2020-03-15 bqp-rewrite.tex
Write down feedbacks from meeting

@@
 
-\nc{\ctx}[2]{\ensuremath{{{#1}^{(#2)}}}}
-
 In this section we show a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
+\Ethan{Talk about the compiler first, and BQP after.}
 We start with the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
@@
 \Ethan{Maybe cite?} In our case, we have a classical client and a quantum server, so we choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.
+\Ethan{Talk about FBQP too}
 
+\nc{\ctx}[2]{\ensuremath{{{\widehat{#1}}^{(#2)}}}}
+
+\Ethan{General comment: Make story more interesting. Clearly claim our own contributions.}
+
+\Ethan{Too bottom-up. Need to tell more story.}
 We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.
@@
 
+\Ethan{More story here. Talk about stuff like why switch keys.}
+
 We now state our compiler that gives any $\QPIP_0$ protocol blindness.
@@
 we use $\ctx{x}{i}$ to denote $x$ encrypted under $pk_i$.
-Otherwise, we write $x'$ for a ciphertext corresponding to plaintext $x$.
-Moreover, the encryption is qubit-by-qubit,
-so we can write $(x_1, x_2)'=(x_1', x_2')$.
 
@@
 \begin{proof}
-	We define $\Pstar$ so that on $\cPstar{1}$ it generates
+	We define $\Pstar$ so that \Ethan{Fix wording here} on $\cPstar{1}$ it generates
 	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$, then produces the encryptions
@@
 	and keeps $\ctx{st_{P, 1}}{1}$ and $sk_1$.
+
 	Then, on the rest of the $\cPstar{t}$ rounds, $\Pstar$ generates

### 2020-03-15 qpip.tex
Start rewriting SampBQP part

@@
 
-Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state.
-\Ethan{Properly intro and point out the difference between BQP and SampBQP and the challenge here.}
-In the case of decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}.
-A prover, honest or not, couldn't do better than sending $n$ identical copies of some state.
-The same reasoning does not work in our case, so we give the following construction instead.
-
-First, we make an observation.
+In this section, we construct a $\QPIP_1$ delegation protocol for $\SampBQP$.
+The high level idea is cut-and-choose; that is,
+the server constructs multiple copies of the ground state as certificates,
+the client then randomly chooses a copy to output and checks the rest.
+There are two main challenges to this approach.
+First, the client needs to reliably extract the circuit's output from its corresponding ground state,
+which can be accomplished by padding the circuit with identity gates at the end.
+Then, the clock register measures into after the last gate with high probability,
+which implies that the data register is in the circuit's final state.
+The other challenge is that a cheating prover could create arbitrary entanglements between its certificates.
+This challenge isn't present in the protocol for $\BQP$ because its soundness is one-sided.
+That is, we allow a cheating server to cause the client to reject a yes-instance;
+it just can't convince the client to accept a no-instance.
+Because of this asymmetry, it turns out that any prover, honest or not, can't do better than sending $n$ identical copies of some state,
+which allows the use of Chernoff bound.
+Here we use de Finetti's theorem to approximate our measurement results with unentangled states,
+which comes with a cost of inverse polynomial errors,
+to also allow the use of Chernoff bounds.
 
@@
 \nc{\cPGS}[1]{\ensuremath{\cP_{\GS,#1}}}
+
+\def\Samp{\mathsf{Samp}}
+\nc{\PiSamp}{\ensuremath{\Pi_\Samp}}
+\nc{\VSamp}{\ensuremath{V_\Samp}}
+\nc{\PSamp}{\ensuremath{P_\Samp}}
+\nc{\PSampstar}{\ensuremath{P_\Samp^*}}
+\nc{\cVSamp}[1]{\ensuremath{\cV_{\Samp,#1}}}
+\nc{\cPSamp}[1]{\ensuremath{\cP_{\Samp,#1}}}
+
+\def\GS{\mathsf{GS}}
 
@@
 
-\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
+\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ with soundness error $O(\varepsilon)$}
 	\label{ProtoQPIP1}
-	\begin{itemize}
-		\item Let $\varepsilon>0$
-		\item Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
-		\item Let $n$ be large enough so both
-			$$P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$$
-			and
-			$$P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$$ are negligible in $\varepsilon$ by Chernoff bound
-		\item Let $N$ be large enough so that $$\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$$
+	Let $C'$ be $C$ padding with enough identity gates so that...
+	Let $n$ be large enough so by Chernoff bound
+		$$P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]<\varepsilon$$
+		$$P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]<\varepsilon$$
+	Let $N$ be large enough so that by de Finetti's theorem...
+		That is,
+		$$\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$$
 		where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$
-	\end{itemize}
 	\begin{enumerate}
-		\item The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
-		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
-		\item Set counter $c=0$
-		\item Set $y=\bot$
+		\item The honest prover prepares $N$ copies of $\ket{\psi_{C'(x)}}$
+		\item The verifier privately samples $I\subset[N]$ s.t. $\abs{I}=n$. It then privately samples $k\in[N]\setminus I$.
 		\item For $i$ from $1$ to $N$:
 		\begin{enumerate}
-			\item If the $i$-th register is for checking:
-			\begin{enumerate}
-				\item The verifier runs \cref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
-				\item If the test passes, increment counter $c$.
+			\item The prover sends the $i$-th copy of $\ket{\psi_{C'(x)}}$, $\rho_i$, qubit-by-qubit.
+			\item If $i\in I$, the verifier runs $\cA_{\GS}$ on $\rho_i$.
+Otherwise, if $i=k$, the verifier measures the data register of $\rho_i$ and save the outcome as $y$.
+Otherwise the verifier discards $\rho_i$.
 		\end{enumerate}
-			\item If the register is for outputting:
-			\begin{enumerate}
-				\item The verifier measures the copy in standard basis
-				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then update $y$ as the measurement result of the data register.
-			\end{enumerate}
-			\item Otherwise, just measure the entire register in standard basis and discard it.
-		\end{enumerate}
-		\item If $\frac{c}{n}\geq\frac{1}{2}-\varepsilon$:
-		\begin{enumerate}
-			\item If $y\ne\bot$ then output $y$
-			\item Otherwise, reject.
-		\end{enumerate}
-		\item Otherwise, reject.
+		\item If the proportion of copies accepted by $\cA_{\GS}$ is greater than $\frac{1}{2}-\varepsilon$ then the client accepts and outputs $y$. Otherwise, it rejects.
 	\end{enumerate}

### 2020-03-18 qpip0.tex
Updates from Overleaf

@@
 We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes \emph{one} sample from $D_1$ as part of its input.
-We also denote this as
-$$ D_1 \approx_{q,\eps} D_2$$
+We also denote "$D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable" as
+$$ \norm{D_1 - D_2}_q \leq \eps.$$
+And "$D_1$ and $D_2$  are not $\eps$-Q-computationally indistinguishable" as 
+$$ \norm{D_1 - D_2}_q > \eps.$$
 \end{definition}
@@
 
-\begin{rmk}
+\begin{rmk}\label{rmk:trace-to-comp}
 If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
@@
 
-\begin{lem}[triangle inequality for computational distance]
+\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
+    Let $D_1$, $D_2$, and $D_3$ be three distributions such that 
+    \begin{align}
+        \norm{D_1 -D_2}_q &\leq \eps \\ 
+        \norm{D_2 -D_3}_q &\leq \eps'. 
+    \end{align}
+    We have 
+    \begin{align}
+        \norm{D_1 -D_3}_q &\leq \eps+\eps'
+    \end{align}
+\end{lem}
+\begin{proof}
+For all quantum circuits $A$ with size $\poly(n)$, we have 
+\begin{align}
+    \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} \leq& \eps \\
+    \norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \leq& \eps',  
+\end{align}
+so 
+\begin{align}
+    &\norm{\Pr[A({D_1})=1]-\Pr[A({D_3})=1]} \nn \\
+    =& \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]+\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
+    \leq&  \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} +\norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
+    =& \eps +\eps' \nn
+\end{align}
+
+\end{proof}
+
+\begin{lem}[another triangle inequality for computational distance]\label{lem:computational-triangle}
 Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.
@@
 \begin{align}
-    D_1 &\approx_{q,\eps} D_2 \\
-    D_4 &\approx_{q,\eps'} D_6, 
+    &\norm{D_1 - D_2}_q \leq \eps   \\ 
+    &\norm{D_4 - D_6}_q \leq \eps',  
 \end{align}
@@
 \begin{align}
-    D_3 \approx_{q,\eps+\eps'} D_5
+   \norm{ D_3 - D_5}_q \leq \eps+\eps' 
 \end{align}
 \end{lem}
+% \begin{align}
+%     D_1 &\approx_{q,\eps} D_2 \\
+%     D_4 &\approx_{q,\eps'} D_6, 
+% \end{align}
+% then 
+% \begin{align}
+%     D_3 \approx_{q,\eps+\eps'} D_5
+% \end{align}
 \begin{proof}
+% Since
+% $$\norm{D_4 - D_6}_q \leq \eps',$$
+% there exist
 
+We prove by contradiction. Suppose that
+$$\norm{ D_3 - D_5}_q > \eps+\eps',$$
+then there exist a quantum circuit $A$ of size $poly(n)$ such that 
+$$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
+Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that 
+$$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
+Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
+$$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$ 
+$$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$ 
+So 
+\begin{align}
+    &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
+    =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
+    \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
+     > &\eps 
+\end{align}
+This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
 \end{proof}
@@
 \begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
+If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
 \end{lemma}
@@
 We have 
-\begin{align}
+\begin{align} \label{eq:z-z-good}
     \tr|z-z_{good}| =& \tr\L|\frac{1}{m}\sum_i (z_i-z_{good,i})\R| \nn \\
@@
 
-For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp} and $i\in [m]$, consider the following prover strategy for Protocol~\ref{proto:urmila4}: on the second round, the prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
+For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for Protocol~\ref{proto:urmila4}: on the second round, the prover start with picking a uniformaly random $i\in [m]$.
+The prover then tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
 The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
-If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  fact ???
-instead.
-On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$.
-otherwise he run $U_{trivial}$    described  in  fact ???.
+If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead.
+This is possible because all the inputs are classical.
+On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}.
+otherwise he continues to run the strategy of Lemma~\ref{lem:trivial-4-round-strategy}.
+We denote the random variable the verifier would get on the testing round as $z_{construct}$.
 
-By
+By Lemma~\ref{lem:trivial-4-round-strategy} and property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$.
+Therefore by Lemma~\ref{lem:urmila-binding}, there exist a $\rho_{composite}$ such that
 
+\begin{align}
+    \norm{z_{composite} - M_{XZ}(\rho_{composite},h) }_q \leq \negl(n) 
+\end{align}
+
+By Lemma~\ref{lem:trivial-4-round-strategy} and Lemma~\ref{lem:urmila-binding}, there exist a $\rho_{trivial}$ such that
+
+\begin{align}
+    \norm{z_{trivial} - M_{XZ}(\rho_{trivial},h) }_q \leq \negl(n), 
+\end{align}
+where $z_{trivial}$ is the random variable one get by running the strategy of Lemma~\ref{lem:trivial-4-round-strategy}, normalized by the probability that the trivial strategy is chosen in the composite strategy.
+$\rho_{trivial}$ is normalized by the same probability.
+
+Note that when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good}$.
+Therefore $z_{composite}=z_{good}+z_{trivial}$, and by Lemma~\ref{lem:computational-triangle},
+
+\begin{align} \label{eq:z-good-rho}
+    \norm{z_{good} - M_{XZ}(\rho_{good},h) }_q \leq \negl(n), 
+\end{align}
+where $\rho_{good} \defeq \rho_{composite}-\rho_{trivial}$.
+
+Recall that by Eq~\ref{eq:z-z-good} we have
+\begin{align} \label{eq:z-z-good2}
+    \norm{z-z_{good}}_1 \leq \eps
+\end{align}
+if we pick $m,T,\gamma_0=???$ \hannote{tune eps}
+
+Also note that by theorem~\ref{QPIP1thm}, 
+\begin{align} \label{eq:rho-c}
+    \norm{M_{XZ}(\rho_{good},h) -p_{good} C(x)}_1 \leq \eps, 
+\end{align}
+where $p_{good} = \tr \rho_{good}$.
+
+Putting together Equation~\ref{eq:z-z-good2}\ref{eq:z-good-rho}\ref{eq:rho-c}, and Remark~\ref{rmk:trace-to-comp} and Lemma~\ref{lem:computational-triangle0}, we have  
+\begin{align}
+    \norm{z- p_{good}C(x)}_q \leq 2\eps +\negl{n}
+\end{align}
+
+\end{proof}
+
+===========
+
+\hannote{below are unused old fragments}
 ===
@@
 Therefore, $M_{XZ}(\rho,h)$  and  $C(x)$ $z$ are $\eps$-Q-computationally indistinguishable, and thus $z$ and $C(x)$ are  $2\eps$-Q-computationally indistinguishable.
-
-\end{proof}
-
-===========
-
-\hannote{below are unused old fragments}
 

### 2020-03-18 qpip.tex
Make editorial changes on QPIP1 SampBQP

--- 2020-03-12 qpip.tex
@@
 
-Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state.
-\Ethan{Properly intro and point out the difference between BQP and SampBQP and the challenge here.}
-In the case of decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}.
-A prover, honest or not, couldn't do better than sending $n$ identical copies of some state.
-The same reasoning does not work in our case, so we give the following construction instead.
+In this section, we construct a one-message $\QPIP_1$ delegation protocol for $\SampBQP$.
+It is statistically secure with negligible completeness errors and inverse polynomial soundness errors.
+At a high level idea, it is a cut-and-choose protocol.
+The server constructs multiple copies of the ground state as certificates,
+then the client randomly chooses a copy to output and checks the rest.
 
-First, we make an observation.
+There are two main challenges to this cut-and-choose approach.
+First, the client needs to reliably extract the circuit output from its corresponding ground state.
+We accomplish this by padding the circuit with identity gates at the end.
+By doing so, the clock register collapses to after the last non-identity gate with high probability.
+
+The other challenge is that a cheating prover's copies of certificates can be arbitrarily entangled,
+so the usual techniques such as Chernoff bounds cannot be applied as-is.
+This isn't a challenge for our $\Piblind$ for $\BQP$ earlier because its soundness is one-sided:
+we only guarantee that a client cannot accept a no-instance;
+a cheating server is allowed to cause the client to reject a yes-instance.
+Because of this asymmetry, a cheating prover's for $\Piblind$ optimal strategy is to maximize its acceptance probability,
+which corresponds to sending $n$ identical copies of some state.
+In our case with $\SampBQP$, we overcome this challenge by using de Finetti's theorem
+to approximate our measurement results with that of measurement results on some unentangled copies.
 
@@
 
-\begin{lemma}
-	\label{ProtoGroundStateCheck}
-	There is a $\QPIP_1$ protocol $\PiGS$ for \cref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
-\end{lemma}
-\begin{prf}
-	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
-\end{prf}
+\def\Samp{\mathsf{Samp}}
+\nc{\PiSamp}{\ensuremath{\Pi_\Samp}}
+\nc{\VSamp}{\ensuremath{V_\Samp}}
+\nc{\PSamp}{\ensuremath{P_\Samp}}
+\nc{\PSampstar}{\ensuremath{P_\Samp^*}}
+\nc{\cVSamp}[1]{\ensuremath{\cV_{\Samp,#1}}}
+\nc{\cPSamp}[1]{\ensuremath{\cP_{\Samp,#1}}}
 
-Now we present \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}}, a $\QPIP_1$ protocol for any $\SampBQP$ problem with inverse polynomial error in circuit size.
+\def\GS{\mathsf{GS}}
 
-\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
+Now we present our $\QPIP_1$ protocol. It is parametrized by $\lambda$, the degree of its inverse polynomial soundness.
+
+\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$}
 	\label{ProtoQPIP1}
-	\begin{itemize}
-		\item Let $\varepsilon>0$
-		\item Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
-		\item Let $n$ be large enough so both
-			$$P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$$
-			and
-			$$P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$$ are negligible in $\varepsilon$ by Chernoff bound
-		\item Let $N$ be large enough so that $$\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$$
-			where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$
-	\end{itemize}
+	Let $\varepsilon=\frac{1}{T^\lambda}$.
+	Let $C'$ be $C$ padded with $T^{\lambda + 1}$ identity gates at the end.
+	Let $n$ be large enough so by Chernoff bound:
+		$$P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]<\varepsilon$$
+		$$P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]<\varepsilon$$
+	Let $N$ be large enough so that de Finetti's theorem can be applied at the cost of $\varepsilon$ errors if one randomly picks $n+1$ subsystems out of $N$ permutation-invariant subsystems.
+		That is,
+		$$\sqrt{\frac{2(n+1)^2\ln\abs{A}}{N-(n+1)}}<\varepsilon$$
+		where $\abs{A}$ is the number of qubits in $\ket{\psi_{C'(x)}}$
 	\begin{enumerate}
-		\item The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
-		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
-		\item Set counter $c=0$
-		\item Set $y=\bot$
-		\item For $i$ from $1$ to $N$:
+		\item The verifier privately samples $I\subset[N]$ s.t. $\abs{I}=n$, and $k\xleftarrow{\$}[N]\setminus I$.
+		\item The honest prover prepares $N$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item For $i$ from $1$ to $N$, the verifier chooses what to do to $\rho_i$ as follows:
 		\begin{enumerate}
-			\item If the $i$-th register is for checking:
-			\begin{enumerate}
-				\item The verifier runs \cref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
-				\item If the test passes, increment counter $c$.
+			\item If $i\in I$, run $\cA_{\GS}(\rho_i)$.
+			\item Otherwise, if $i=k$, measure the data register of $\rho_i$ and save the outcome as $y$.
+			\item Otherwise, discard $\rho_i$.
 		\end{enumerate}
-			\item If the register is for outputting:
-			\begin{enumerate}
-				\item The verifier measures the copy in standard basis
-				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then update $y$ as the measurement result of the data register.
-			\end{enumerate}
-			\item Otherwise, just measure the entire register in standard basis and discard it.
-		\end{enumerate}
-		\item If $\frac{c}{n}\geq\frac{1}{2}-\varepsilon$:
-		\begin{enumerate}
-			\item If $y\ne\bot$ then output $y$
-			\item Otherwise, reject.
-		\end{enumerate}
-		\item Otherwise, reject.
+		\item If the proportion of copies accepted by $\cA_{\GS}$ is greater than $\frac{1}{2}-\varepsilon$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
 	\end{enumerate}
@@
 
+Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise. $\PiSamp$ has negligible completeness errors by construction. We now show its soundness.
+
 \begin{thm}
     \label{QPIP1thm}
-	For any $L\in\SampBQP$, \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} is a protocol for $L$ with negligible completeness.
-$\forall c\in\bbN$, it achieves soundness $(\varepsilon, \varepsilon)$ where $\varepsilon=T^{-c}$.
-Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
+	$\PiSamp$ has $O(\frac{1}{T^\lambda})$ soundness error.
 \end{thm}
 \begin{prf}
-	It clearly has completeness negligibly close to $1$.
-Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted.
-Let $\sigma$ be the state the prover sends to the verifier.
+	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier.
 
-	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers.
-	A random permutation is equivalent to a classical mix over all possible permutations of $\sigma$:
+	We first show that de Finetti's theorem can be used here.
+
+	Randomly picking $n+1$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+1$ registers.
+	A random permutation, in turn, is equivalent to a classical mix over all possible permutations of $\sigma$:
 
@@
 
-	So we can apply \cref{deFinetti}. $\exists\set{w_i, \rho_i}$ such that:
+	Now we apply \cref{deFinetti}. $\exists\set{w_i, \rho_i}$ such that:
 	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+n}(\sigma'-\sum_i w_i\rho_i^{\otimes n+m})}=O(\varepsilon)$$
@@
 	So the accept chance of this prover is $\sum_j w_j p_j>\delta$
-	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.
+	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+1}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.
 
@@
 
-	The probability of measuring $t\geq T$ on the clock register of $\ket{\psi_{C'(x)}}$ is $\frac{1}{2}$, so the probability of failing to do so after $m$ attempts is negligible.
-	Once we do measure $t\geq T$, the data register is $C(x)$.
+	The probability of measuring $t<T$ on the clock register of $\ket{\psi_{C'(x)}}$ is $\frac{T}{T+T^{\lambda+1}}<\frac{1}{T^\lambda}=\varepsilon$,
+	so the data register has $1-\varepsilon$ probability to be $C(x)$ at this point.
 

### 2020-03-18 qpip.tex
Rewrite QPIP1 SampBQP proof

@@
 In this section, we construct a one-message $\QPIP_1$ delegation protocol for $\SampBQP$.
-It is statistically secure with negligible completeness errors and inverse polynomial soundness errors.
-At a high level idea, it is a cut-and-choose protocol.
+At a high level, it is a cut-and-choose protocol.
 The server constructs multiple copies of the ground state as certificates,
 then the client randomly chooses a copy to output and checks the rest.
+Unfortunately we have inverse polynomial soundness errors here.
 
@@
 
-The other challenge is that a cheating prover's copies of certificates can be arbitrarily entangled,
-so the usual techniques such as Chernoff bounds cannot be applied as-is.
-This isn't a challenge for our $\Piblind$ for $\BQP$ earlier because its soundness is one-sided:
+The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
+so common techniques such as Chernoff bounds can't be applied as-is.
+This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because its soundness is one-sided:
 we only guarantee that a client cannot accept a no-instance;
@@
 
-\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$}
-	\label{ProtoQPIP1}
-	Let $\varepsilon=\frac{1}{T^\lambda}$.
+\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$}\label{ProtoQPIP1}
 	Let $C'$ be $C$ padded with $T^{\lambda + 1}$ identity gates at the end.
-	Let $n$ be large enough so by Chernoff bound:
-		$$P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]<\varepsilon$$
-		$$P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]<\varepsilon$$
-	Let $N$ be large enough so that de Finetti's theorem can be applied at the cost of $\varepsilon$ errors if one randomly picks $n+1$ subsystems out of $N$ permutation-invariant subsystems.
+
+	Pick $\varepsilon$ small enough so it holds for all $\phi$ that:
+	\begin{equation}
+		\label{QPIP1eps}
+		P[\cA_\GS(\phi)=acc]>\frac{1}{2}-2\varepsilon\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\frac{1}{T^\lambda}
+	\end{equation}
+
+	Pick $n$ large enough so by Chernoff bound:
+	\begin{equation}
+		\label{QPIP1Chernoff1}
+		P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]<2^{-\lambda}
+	\end{equation}
+	\begin{equation}
+		\label{QPIP1Chernoff2}
+		P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]<2^{-\lambda}
+	\end{equation}
+
+	Let $N$ be large enough so that de Finetti's theorem can be applied at the cost of $T^{-\lambda}$ errors if one randomly picks $n+1$ subsystems out of $N$ permutation-invariant subsystems.
 		That is,
-		$$\sqrt{\frac{2(n+1)^2\ln\abs{A}}{N-(n+1)}}<\varepsilon$$
+		$$\sqrt{\frac{2(n+1)^2\ln\abs{A}}{N-(n+1)}}<T^{-\lambda}$$
 		where $\abs{A}$ is the number of qubits in $\ket{\psi_{C'(x)}}$
+
 	\begin{enumerate}
@@
 
-Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise. $\PiSamp$ has negligible completeness errors by construction. We now show its soundness.
+Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise. We now show the completeness and soundness of $\PiSamp$.
 
@@
     \label{QPIP1thm}
-	$\PiSamp$ has $O(\frac{1}{T^\lambda})$ soundness error.
+	$\PiSamp$ has negligible completeness error and $O(T^-\lambda)$ soundness error.
 \end{thm}
 \begin{prf}
+	The completeness follows from \cref{QPIP1Chernoff2} and inspection.
+
+	Now we show soundness.
 	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier.
 
-	We first show that de Finetti's theorem can be used here.
+	We first show that de Finetti's theorem can indeed be used here to achieve independence.
+	Randomly picking $n+1$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+1$ registers.
+	A random permutation, in turn, is a classical mix over all possible permutations:
+	$$\sigma'=\frac{1}{\abs{\Sym(N)}}\sum_{\Pi\in\Sym(N)}\Pi\sigma\Pi^\dagger$$
+	We then verify that $\sigma'$ is permutation-invariant.
+	Fix $\tilde{\Pi}\in\Sym(N)$, then
+	$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger
+	=\frac{1}{\abs{\Sym(N)}}\sum_{\Pi\in\Sym(N)}\tilde{\Pi}\Pi\sigma\Pi^\dagger\tilde{\Pi}^\dagger
+	=\frac{1}{\abs{\Sym(N)}}\sum_{\hat{\Pi}\in\Sym(N)}\hat{\Pi}\sigma\hat{\Pi}^\dagger
+	=\sigma'$$
+	where the second equality is by relabeling $\tilde{\Pi}\Pi=\hat{\Pi}$, which is allowed since $\Sym(N)$ is a group.
 
-	Randomly picking $n+1$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+1$ registers.
-	A random permutation, in turn, is equivalent to a classical mix over all possible permutations of $\sigma$:
+	Now we apply \cref{deFinetti} to approximate $\sigma'$ with a classical mix over tensors of independent states.
+	That is, $\exists\rho=\sum_i w_i\rho_i^{\otimes n+1}$ such that:
+	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{n+1}(\sigma'-\rho)}=O(\varepsilon)$$
 
-	$$\sigma'=\frac{1}{\abs{\Sym(N)}}\sum_{\Pi\in\Sym(N)}\Pi\sigma\Pi^\dagger$$
+	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under $\cA_{\GS}$.
+	We now partition the terms $\rho_i$ into two categories according to the Chernoff bound in \cref{QPIP1Chernoff1}:
+	$$I=\set{i:p_i\geq 2^{-\lambda}}$$
 
-	Now we verify that $\sigma'$ is permutation-invariant.
-	Let $\tilde{\Pi}$ be some fixed permutation, then clearly:
-	$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger=\sigma'$$
+	For $i\notin I$ we have
+	$$\sum_{i\in I} w_i p_i<2^{-\lambda}=\negl(\lambda)$$
 
-	Now we apply \cref{deFinetti}. $\exists\set{w_i, \rho_i}$ such that:
-	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+n}(\sigma'-\sum_i w_i\rho_i^{\otimes n+m})}=O(\varepsilon)$$
+	For $i\in I$ we have
+	$$P[\cA_\GS(\rho_i)=acc]>\frac{1}{2}-2\varepsilon$$
+	and hence
+	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\frac{1}{T^\lambda}$$
+	by \cref{QPIP1eps}.
+	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{at least I think we do. Need theorem.}
+	$$\braket{\rho_i|\phi_{C'(x)}}>1-O(T^{-\lambda})$$
+	\Ethan{Now we need some kinda standard fidelity argument to show that the measurement results will be close too. I'm not familiar with them at the moment.}
 
-	Note that $\tilde\sigma=\sum_i w_i\rho_i^{\otimes n+m}$ is a classical mix over $\rho_i^{\otimes n+m}$ with weights $w_i$.
-
-	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \cref{AlgGroundStateCheck}.
-	So the accept chance of this prover is $\sum_j w_j p_j>\delta$
-	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+1}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.
-
-	Let
-	$$J=\set{j:q_j\leq P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]}$$
-
-	Recall that then each $q_j$ must be negligible by how we picked $n$. Hence the following is clearly negligible:
-	$$\sum_{j\in J} w_j q_j$$
-
-	And so is
-	$$\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}=\frac{\sum_{j\in J} w_j q_j}{\delta}$$
-
-	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ where $\rho_i$ has over probability $1-2\varepsilon$ to be accepted by \cref{AlgGroundStateCheck} is overwhelming.
-
-	Such $\rho_i$ is $O(\negl(\varepsilon))$-close to $\ket{\psi_{C'(x)}}$, by applying a Chernoff bound to \cref{ThmXZCheck}.
-
-	The probability of measuring $t<T$ on the clock register of $\ket{\psi_{C'(x)}}$ is $\frac{T}{T+T^{\lambda+1}}<\frac{1}{T^\lambda}=\varepsilon$,
+	The probability of measuring $t<T$ on the clock register of $\ket{\psi_{C'(x)}}$ is $\frac{T}{T+T^{\lambda+1}}<T^{-\lambda}$,
 	so the data register has $1-\varepsilon$ probability to be $C(x)$ at this point.
 
-	All errors up to this point is $O(\varepsilon)$.
+	The soundness errors incurred at each step is at most $O(T^{-\lambda})$, so the conclusion follows.
 \end{prf}

### 2020-03-19 qpip.tex
Fix typos

@@
 then the client randomly chooses a copy to output and checks the rest.
-Unfortunately we have inverse polynomial soundness errors here.
+Unfortunately our approach incurs inverse polynomial soundness errors.
 
@@
 so common techniques such as Chernoff bounds can't be applied as-is.
-This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because its soundness is one-sided:
-we only guarantee that a client cannot accept a no-instance;
-a cheating server is allowed to cause the client to reject a yes-instance.
-Because of this asymmetry, a cheating prover's for $\Piblind$ optimal strategy is to maximize its acceptance probability,
-which corresponds to sending $n$ identical copies of some state.
-In our case with $\SampBQP$, we overcome this challenge by using de Finetti's theorem
-to approximate our measurement results with that of measurement results on some unentangled copies.
+This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...
+\Ethan{TODO; need brief and intuitive explanation}
+In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem
+to approximate our measurement results with that of some unentangled copies,
+within inverse polynomial errors.
 
@@
 
-	Pick $\varepsilon$ small enough so it holds for all $\phi$ that:
+	Pick $\varepsilon$ small enough so it holds for all $\ket\phi$ that:
 	\begin{equation}
 		\label{QPIP1eps}
-		P[\cA_\GS(\phi)=acc]>\frac{1}{2}-2\varepsilon\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\frac{1}{T^\lambda}
+		P[\cA_\GS(\ket{\phi})=acc]>\frac{1}{2}-2\varepsilon\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\frac{1}{T^\lambda}
 	\end{equation}
@@
 	\begin{enumerate}
-		\item The verifier privately samples $I\subset[N]$ s.t. $\abs{I}=n$, and $k\xleftarrow{\$}[N]\setminus I$.
-		\item The honest prover prepares $N$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
-		\item For $i$ from $1$ to $N$, the verifier chooses what to do to $\rho_i$ as follows:
+		\item The verifier privately samples $I\subset[N]$ s.t. $\abs{I}=n$.
+			It then privately samples $k\xleftarrow{\$}[N]\setminus I$.
+		\item The honest prover prepares $N$ copies of $\ket{\psi_{C'(x)}}$ and sends all of them to the verifier qubit-by-qubit.
+		\item For $i$ from $1$ to $N$, the verifier chooses what to do to the $i$-th copy, $\rho_i$, as follows:
 		\begin{enumerate}
@@
 	$$\sum_{i\in I} w_i p_i<2^{-\lambda}=\negl(\lambda)$$
+	so we can approximate with negligible error that all $\rho_i$ where $i\notin I$ are rejected.
 
@@
 	by \cref{QPIP1eps}.
-	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{at least I think we do. Need theorem.}
+	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain... \Ethan{TODO not done yet. Probably some squares or square roots missing here.}
 	$$\braket{\rho_i|\phi_{C'(x)}}>1-O(T^{-\lambda})$$
-	\Ethan{Now we need some kinda standard fidelity argument to show that the measurement results will be close too. I'm not familiar with them at the moment.}
+	\Ethan{Now we need some kinda standard fidelity argument to show that the measurement results will be close to as if the ground state is measured.}
 

### 2020-03-21 qpip.tex
Reparametrize QPIP1 SampBQP

--- 2020-03-18 qpip.tex
@@
 
-Now we present our $\QPIP_1$ protocol. It is parametrized by $\lambda$, the degree of its inverse polynomial soundness.
-
 \begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$}\label{ProtoQPIP1}
-	Let $C'$ be $C$ padded with $T^{\lambda + 1}$ identity gates at the end.
-
-	Pick $\varepsilon$ small enough so it holds for all $\phi$ that:
-	\begin{equation}
-		\label{QPIP1eps}
-		P[\cA_\GS(\phi)=acc]>\frac{1}{2}-2\varepsilon\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\frac{1}{T^\lambda}
-	\end{equation}
-
-	Pick $n$ large enough so by Chernoff bound:
-	\begin{equation}
-		\label{QPIP1Chernoff1}
-		P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]<2^{-\lambda}
-	\end{equation}
-	\begin{equation}
-		\label{QPIP1Chernoff2}
-		P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]<2^{-\lambda}
-	\end{equation}
-
-	Let $N$ be large enough so that de Finetti's theorem can be applied at the cost of $T^{-\lambda}$ errors if one randomly picks $n+1$ subsystems out of $N$ permutation-invariant subsystems.
-		That is,
-		$$\sqrt{\frac{2(n+1)^2\ln\abs{A}}{N-(n+1)}}<T^{-\lambda}$$
-		where $\abs{A}$ is the number of qubits in $\ket{\psi_{C'(x)}}$
+	Pick $\varepsilon=\poly(T^{-1})$
+	Let $C'$ be $C$ padded with $\poly(\varepsilon^{-1})$ identity gates at the end.
+	Pick $h=\poly(\varepsilon)$, $m=O(h^{-3})$, $M=\poly(m)$.
 
 	\begin{enumerate}
-		\item The verifier privately samples $I\subset[N]$ s.t. $\abs{I}=n$, and $k\xleftarrow{\$}[N]\setminus I$.
-		\item The honest prover prepares $N$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
-		\item For $i$ from $1$ to $N$, the verifier chooses what to do to $\rho_i$ as follows:
+		\item The honest prover prepares $M$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$, and $k\xleftarrow{\$}[M]\setminus I$.
+			For $i$ from $1$ to $N$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
 		\begin{enumerate}
-			\item If $i\in I$, run $\cA_{\GS}(\rho_i)$.
+			\item If $i\in I$, run $z_i\leftarrow\cA_{\GS}(\rho_i)$.
 			\item Otherwise, if $i=k$, measure the data register of $\rho_i$ and save the outcome as $y$.
@@
 		\end{enumerate}
-		\item If the proportion of copies accepted by $\cA_{\GS}$ is greater than $\frac{1}{2}-\varepsilon$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
+			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-hm$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
 	\end{enumerate}
@@
 \begin{prf}
-	The completeness follows from \cref{QPIP1Chernoff2} and inspection.
+	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
+	So we can apply the Chernoff bound \cref{thm:Chernoff} with $\mu=\frac{m}{2}$, $\delta=2h$ to get
+	$$\Prob{\frac{m}{2}-Z\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
 
@@
 	We first show that de Finetti's theorem can indeed be used here to achieve independence.
-	Randomly picking $n+1$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+1$ registers.
+	Randomly picking $m+1$ out of $M$ registers is equivalent to first applying a random permutation to get some $\sigma'$ then taking the first $m+1$ registers.
 	A random permutation, in turn, is a classical mix over all possible permutations:
-	$$\sigma'=\frac{1}{\abs{\Sym(N)}}\sum_{\Pi\in\Sym(N)}\Pi\sigma\Pi^\dagger$$
-	We then verify that $\sigma'$ is permutation-invariant.
-	Fix $\tilde{\Pi}\in\Sym(N)$, then
+	$$\sigma'=\frac{1}{\abs{\Sym(M)}}\sum_{\Pi\in\Sym(M)}\Pi\sigma\Pi^\dagger$$
+	It is simple to check that $\sigma'$ is permutation-invariant.
+	Fix $\tilde{\Pi}\in\Sym(M)$, then
 	$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger
-	=\frac{1}{\abs{\Sym(N)}}\sum_{\Pi\in\Sym(N)}\tilde{\Pi}\Pi\sigma\Pi^\dagger\tilde{\Pi}^\dagger
-	=\frac{1}{\abs{\Sym(N)}}\sum_{\hat{\Pi}\in\Sym(N)}\hat{\Pi}\sigma\hat{\Pi}^\dagger
+	=\frac{1}{\abs{\Sym(M)}}\sum_{\Pi\in\Sym(M)}\tilde{\Pi}\Pi\sigma\Pi^\dagger\tilde{\Pi}^\dagger
+	=\frac{1}{\abs{\Sym(M)}}\sum_{\hat{\Pi}\in\Sym(M)}\hat{\Pi}\sigma\hat{\Pi}^\dagger
 	=\sigma'$$
-	where the second equality is by relabeling $\tilde{\Pi}\Pi=\hat{\Pi}$, which is allowed since $\Sym(N)$ is a group.
+	where the second equality is by relabeling $\tilde{\Pi}\Pi=\hat{\Pi}$, which is allowed since $\Sym(M)$ is a group.
 
 	Now we apply \cref{deFinetti} to approximate $\sigma'$ with a classical mix over tensors of independent states.
-	That is, $\exists\rho=\sum_i w_i\rho_i^{\otimes n+1}$ such that:
-	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{n+1}(\sigma'-\rho)}=O(\varepsilon)$$
+	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ such that:
+	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}=O(\varepsilon)$$
 
-	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under $\cA_{\GS}$.
-	We now partition the terms $\rho_i$ into two categories according to the Chernoff bound in \cref{QPIP1Chernoff1}:
-	$$I=\set{i:p_i\geq 2^{-\lambda}}$$
+	Now we separate the $\rho_j$ into two categories: $J=\set{j\in I:p_j=\cA_\GS(\rho_j)<\frac{1}{2}-2h}$ and its complement. \Ethan{TODO import and use the right ``given" command.}
 
-	For $i\notin I$ we have
-	$$\sum_{i\in I} w_i p_i<2^{-\lambda}=\negl(\lambda)$$
+	First suppose $j\in J$
+	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2h$,
+	then clearly $\Prob{Z>\frac{m}{2}-hm}<\Prob{Y>\frac{m}{2}-hm}$.
+	By Chernoff bound, we have
+	$$\Prob{Y-(\frac{1}{2}-2\varepsilon)m\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
+	where $\mu_y=mp_y$ and $\delta=\frac{2h}{1-4h}$.
 
-	For $i\in I$ we have
-	$$P[\cA_\GS(\rho_i)=acc]>\frac{1}{2}-2\varepsilon$$
-	and hence
-	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\frac{1}{T^\lambda}$$
-	by \cref{QPIP1eps}.
+	Summing up all these terms, we get
+	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda)$$
+	So this case doesn't get accepted often enough to matter.
+
+	Now, for the other case, $j\notin J$.
+	$$P[\cA_\GS(\phi)=acc]>\frac{1}{2}-2\varepsilon\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\frac{1}{T^\lambda}$$
+	we then have
+	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\frac{1}{T^\lambda}.$$
+
 	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{at least I think we do. Need theorem.}
@@
 
-	The probability of measuring $t<T$ on the clock register of $\ket{\psi_{C'(x)}}$ is $\frac{T}{T+T^{\lambda+1}}<T^{-\lambda}$,
+	The probability of measuring $t<T$ on the clock register of $\ket{\psi_{C'(x)}}$ is $\varepsilon$,
 	so the data register has $1-\varepsilon$ probability to be $C(x)$ at this point.

### 2020-03-21 qpip.tex

@@
 	$$\braket{\rho_i|\phi_{C'(x)}}>1-O(T^{-\lambda})$$
-	\Ethan{Now we need some kinda standard fidelity argument to show that the measurement results will be close too. I'm not familiar with them at the moment.}
+	\Ethan{Now we need some kinda standard fidelity argument to show that the measurement results will be close to as if the ground state is measured.}
 

### 2020-03-22 qpip.tex
Rename VHam
Reparametrize QPIP1 SampBQP proof

@@
 
-\def\GS{\mathsf{GS}}
+\def\GS{\mathsf{Ham}}
 \nc{\PiGS}{\ensuremath{\Pi_\GS}}
@@
 
-\def\GS{\mathsf{GS}}
-
 \begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$}\label{ProtoQPIP1}
@@
 		\begin{enumerate}
-			\item If $i\in I$, run $z_i\leftarrow\cA_{\GS}(\rho_i)$.
+			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
 			\item Otherwise, if $i=k$, measure the data register of $\rho_i$ and save the outcome as $y$.
@@
 
-	Now we separate the $\rho_j$ into two categories: $J=\set{j\in I:p_j=\cA_\GS(\rho_j)<\frac{1}{2}-2h}$ and its complement. \Ethan{TODO import and use the right ``given" command.}
+	Now we separate the $\rho_j$ into two categories: $J=\set{j\in I|p_j=\cV_\GS(\rho_j)<\frac{1}{2}-2h}$ and its complement.
 
-	First suppose $j\in J$
+	First suppose $j\in J$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
+	hence incurs negligible soundness errors.
 	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2h$,
-	then clearly $\Prob{Z>\frac{m}{2}-hm}<\Prob{Y>\frac{m}{2}-hm}$.
+	then clearly $\Prob{Z\geq\frac{m}{2}-hm}<\Prob{Y\geq\frac{m}{2}-hm}$.
 	By Chernoff bound, we have
-	$$\Prob{Y-(\frac{1}{2}-2\varepsilon)m\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
-	where $\mu_y=mp_y$ and $\delta=\frac{2h}{1-4h}$.
-
-	Summing up all these terms, we get
+	$$\Prob{Y\geq\frac{m}{2}-hm}=\Prob{Y-\mu\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
+	where $\mu=mp_y=\frac{m}{2}-2hm$ and $\delta=\frac{2h}{1-4h}$.
+	Summing up all the $\rho_j$ terms in $J$, we have
 	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda)$$
-	So this case doesn't get accepted often enough to matter.
 
 	Now, for the other case, $j\notin J$.
-	$$P[\cA_\GS(\phi)=acc]>\frac{1}{2}-2\varepsilon\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\frac{1}{T^\lambda}$$
+	$$\Prob{\cV_\GS(\phi)=acc}>\frac{1}{2}-2h\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\poly(\varepsilon)$$
 	we then have
-	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\frac{1}{T^\lambda}.$$
+	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\poly(\varepsilon).$$
+	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain
+	$$\braket{\rho_i|\phi_{C'(x)}}>1-\poly(\varepsilon).$$
+	By a standard fidelity argument, the measurement results on $\rho_i$ is $\poly(\varepsilon)$-close to that on $\ket{\phi_{C'(x)}}$.
 
-	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{at least I think we do. Need theorem.}
-	$$\braket{\rho_i|\phi_{C'(x)}}>1-O(T^{-\lambda})$$
-	\Ethan{Now we need some kinda standard fidelity argument to show that the measurement results will be close to as if the ground state is measured.}
+	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $\poly(\varepsilon)$ due to the padding,
+	so the data register has $1-\poly(\varepsilon)$ probability to be $C(x)$ at this point.
 
-	The probability of measuring $t<T$ on the clock register of $\ket{\psi_{C'(x)}}$ is $\varepsilon$,
-	so the data register has $1-\varepsilon$ probability to be $C(x)$ at this point.
-
-	The soundness errors incurred at each step is at most $O(T^{-\lambda})$, so the conclusion follows.
+	The soundness errors incurred at each step is at most $\poly(\varepsilon)$, so the conclusion follows.
 \end{prf}

### 2020-03-22 blind.tex
Start rewriting SampBQP part
Update sections structure

--- 2020-02-09 blind.tex
@@
-\section{Constant-Round and Blind $\QPIP_1$ protocol for $\SampBQP$}
+\def\HE{\mathsf{HE}}
+\def\HGen{\mathsf{HE.Keygen}}
+\def\HEnc{\mathsf{HE.Enc}}
+\def\HEval{\mathsf{HE.Eval}}
+\def\HDec{\mathsf{HE.Dec}}
 
-\def\Samp{\mathsf{Samp}}
-\nc{\PiSamp}{\ensuremath{\Pi_\Samp}}
-\nc{\VSamp}{\ensuremath{V_\Samp}}
-\nc{\PSamp}{\ensuremath{P_\Samp}}
-\nc{\PSampstar}{\ensuremath{P_\Samp^*}}
-\nc{\cVSamp}[1]{\ensuremath{\cV_{\Samp,#1}}}
-\nc{\cPSamp}[1]{\ensuremath{\cP_{\Samp,#1}}}
+\section{Blindness for $\QPIP_0$ protocols}
+\label{sec:BlindBQP2}
 
-\def\SampB{\mathsf{Samp, blind}}
-\nc{\PiSampB}{\ensuremath{\Pi_\SampB}}
-\nc{\VSampB}{\ensuremath{V_\SampB}}
-\nc{\PSampB}{\ensuremath{P_\SampB}}
+In this section we show a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
+\Ethan{Talk about the compiler first, and BQP after.}
+We start with the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
+Generally one can obtain blindness by running a protocol under homomorphic encryption.
+\Ethan{Maybe cite?} In our case, we have a classical client and a quantum server, so we choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.
+\Ethan{Talk about FBQP too}
 
-Now we compile our $\QPIP_1$ protocol (\cref{ProtoQPIP1}) using the quantum homomorphic encryption $\mathsf{QHE}$ from \cref{decodeMeasureOrder} in the same way as what we did for our blind $\BQP$ delegation protocol (\cref{proto:BlindBQP}) in \cref{sec:BlindBQP}.
+\nc{\ctx}[2]{\ensuremath{{{\widehat{#1}}^{(#2)}}}}
 
-First we restate \cref{ProtoQPIP1} in more convenient terms.
+\Ethan{General comment: Make story more interesting. Clearly claim our own contributions.}
 
-\begin{protocol}{Our 1-message $\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ language $L$}
-	Common input: $x\in\set{0,1}^n$. 
+\Ethan{Too bottom-up. Need to tell more story.}
+We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.
+First, when the plaintext is classical, the encryption can be performed classically.
+Moreover, a quantum ciphertext can be measured homomorphically, in which case the measurement outcomes can then be decrypted classically.
+Lastly, the encryption is done qubit-by-qubit, so one can split a ciphertext into registers as one would with the corresponding plaintext.
+
+\Ethan{More story here. Talk about stuff like why switch keys.}
+
+We now state our compiler that gives any $\QPIP_0$ protocol blindness.
+For notation, when there are many sets of $\QHE$ keys in play at the same time,
+we use $\ctx{x}{i}$ to denote $x$ encrypted under $pk_i$.
+
+\begin{protocol}{Compiling $\QPIP_0$ protocol $(P, V)(x)$ into $(\Pblind, \Vblind(x))$}
+	Suppose the protocol $(P, V)$ is a $\QPIP_0$ protocol where only the verifier receives outputs, with the following general form:
+
+	Public input: $x$
 	\begin{enumerate}
-		\item The prover generates a certificate state $\rho\leftarrow\cPSamp{1}(x)$ and sends it to the verifier qubit-by-qubit.
-		\item The verifier generates $\Lambda \leftarrow \cVSamp{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
-			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
-			It applies $\Lambda$ to $\rho$ qubit-by-qubit.
-			Let $w \in \set{0,1}^m$ denote the measurement outcome.
-			It verifies the measurement outcome and produces a decision $o\leftarrow\cVSamp{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVSamp{3}$ is a classical polynomial-time algorithm.
+		\item $V$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$ and sends $v_1$ to the prover.
+		\item $P$ generates $(p_1, st_{P, 1})\leftarrow\cP_1(v_1, x)$ and sends $p_1$ to the verifier.
+		\item for $t=2,\ldots,T$:
+		\begin{enumerate}
+			\item $V$ generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$ and sends $v_t$ to the prover.
+			\item $P$ generates $(p_t, st_{P, t})\leftarrow\cP_t(v_t, st_{P, t-1})$ and sends $p_t$ to the verifier.
+		\end{enumerate}
+		\item $V$ computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
+			\Ethan{Prover can get outputs too}
+	\end{enumerate}
+
+	Using $\Pi=(P, V)(x)$ from above, we define the protocol $\Piblind=(P, V(x))$ as follows:
+
+	Verifier's input: $x$
+
+	Let $L_t$ be the circuit depth of $\cP_t$.
+	Let $\lambda=\abs{x}$.
+
+	\begin{enumerate}
+		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
+			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$,
+			and encrypts $\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
+			It sends $pk_1$, $\ctx{x}{1}$, and $\ctx{v_1}{1}$ to the prover.
+		\item $\Pblind$ generates $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\cPblind{1}(\ctx{v_1}{1}, \ctx{x}{1})$
+			by evaluating $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\QEval_{pk}(\cP_1, \ctx{v_1}{1}, \ctx{x}{1})$.
+			It sends $\ctx{p_1}{1}$ to the verifier.
+		\item for $t=2,\ldots,T$:
+		\begin{enumerate}
+			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p_{t-1}}{t-1})$,
+				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
+				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$,
+				and produces encryptions $\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t)$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
+				It sends $pk_t$, $\ctx{v_t}{t}$, and $\ctx{sk_{t-1}}{t}$ to the prover.
+			\item $\Pblind$ generates $(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\cPblind{t}(\ctx{v_t}{t}, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1})$
+				by first refreshing the $\QHE$ key that encrypts its states by
+				first encrypting it under the new key by $\ctx{st_{P, t-1}}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st_{P, t-1}}{t-1}))$,
+				then homomorphically decrypting the old encryption under the new key by
+				$\ctx{st_{P, t-1}}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1, t})$.
+				It then applies the next-message function of $\Pi$, generating
+				$(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\QEval_{pk_t}(\cP_t, \ctx{v_t}{t}, \ctx{st_{P, t-1}}{t})$.
+				It sends $\ctx{p_t}{t}$ back to the verifier.
+		\end{enumerate}
+		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec_{sk_T}(\ctx{p_T}{T})$.
+			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
+			\Ethan{Prover can get outputs too}
 	\end{enumerate}
@@
 
-Note that it is of the same form as its $\BQP$ counterpart $\PiSamp$ found in \cref{subsec:BlindBQP}.
+By the correctness of $\QHE$, the completeness error of $\Piblind$ is negligibly close to that of $\Pi$.
+We show the soundness of $\Piblind$ in the following theorem.
 
-So we can compile it into $\PiSampB$ to achieve blindness in the same way:
+\def\Pstar{P^*}
+\nc{\cPstar}[1]{\ensuremath{\cP^*_{#1}}}
 
-\begin{protocol}{Blind $\QPIP_1$ 1-message protocol $\PiSampB = (\PSampB, \VSampB)$ for $\SampBQP$ language $L$}
-	\label{proto:BlindSampBQP}
-	Verifier's input: $x\in\set{0,1}^n$.
+\begin{theorem}
+	For all cheating prover $\Pblindstar$, there exists a cheating prover $\Pstar$ s.t. for all input $x$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
+\end{theorem}
+\begin{proof}
+	We define $\Pstar$ so that \Ethan{Fix wording here} on $\cPstar{1}$ it generates
+	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$, then produces the encryptions
+	$\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
+	It then runs $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\cPblind{1}(\ctx{v_1}{1}, \ctx{x}{1})$.
+	Finally, it decrypts $p_1\leftarrow\QDec_{sk_1}(\ctx{p_1}{1})$ and sends it back to the verifier,
+	and keeps $\ctx{st_{P, 1}}{1}$ and $sk_1$.
 
-	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPSamp{1}$.
-	\begin{enumerate}
-		\item The verifier generates $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPSamp{1}(x)$.
-			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
-			It also sends $pk$ to the prover.
-		\item The prover homomorphically evaluates $\cPSamp{1}$ on input $ct_x$, generating $\sigma\leftarrow\QEval_{pk}(\cPSamp{1}, ct_x)$.
-			It sends $\sigma$ to the verifier qubit-by-qubit.
-		\item The verifier generates $\Lambda\leftarrow\cVSamp{2}(x)$,
-			$\Lambda'\leftarrow\cM_\QHE$,
-			$ct_w\leftarrow\Lambda'(\sigma)$,
-			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
-			and $o\leftarrow\cVSamp{3}(x, \Lambda, w)$.
-			It outputs $o$.
-	\end{enumerate}
-\end{protocol}
+	Then, on the rest of the $\cPstar{t}$ rounds, $\Pstar$ generates
+	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$, and produces ciphertexts
+	$\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
+	It then runs $(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\cPblind{t}(\ctx{v_t}{t}, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1})$.
+	Finally, it decrypts $p_t\leftarrow\QDec_{sk_t}(\ctx{p_t}{1})$ and sends it back to the verifier,
+	and keeps $\ctx{st_{P, t}}{t}$ and $sk_t$.
 
-\begin{thm}
-	$\PiSampB$ has the same completeness and soundness guarantees as $\PiSamp$ and is blind.
-\end{thm}
-\begin{prf}
-	The proof is identical to that of \cref{thm:BlindBQP} up to relabeling.
-	\Ethan{too hand-wavy still, can still say ``identically simulates"}
-	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either; the proof only shows that the compiliation preserves soundness.
-	\Ethan{Soundness def. is different}
-\end{prf}
+	By construction, the experiments $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
+\end{proof}
+
+Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
+\begin{theorem}
+	$\Piblind$ is blind.
+\end{theorem}
+\begin{proof}
+	Consider $T+1$ hybrids experiments, from $\Hyb_1$ to $\Hyb_{T+1}$.
+	In $\Hyb_i$, we modify $(\Pblind, \Vblind(x))$ s.t.
+	for all rounds associated with $\cV{t}$ where $t\geq i$, the verifier replaces the $\ctx{sk_{t-1}}{t}$ in its message with encryption of $0$.
+	Then, for all $t$, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
+	Since computational indistinguishability is transitive \Ethan{Really? Definitely need to write down some inequalities here...}, $\Hyb_1$ is indistinguishable with $\Hyb_{T+1}$.
+	Since $\Hyb_{T+1}$ is precisely $\Piblind$, and $\Hyb_1$ is clearly blind, we can conclude that $\Piblind$ is blind.
+\end{proof}

### 2020-03-22 fbqp.tex
Update sections structure
Prune blind QPIP1 BQP

--- 2020-02-29 bqp.tex
@@
-\section{Blind Delegation for BQP and FBQP}
-\label{sec:BlindBQP}
-
-\def\Mah{\mathsf{Mah}}
-\nc{\PiMah}{\ensuremath{\Pi_\Mah}}
-\nc{\VMah}{\ensuremath{V_\Mah}}
-\nc{\PMah}{\ensuremath{P_\Mah}}
-\nc{\PMahstar}{\ensuremath{P_\Mah^*}}
-\nc{\cVMah}[1]{\ensuremath{\cV_{\Mah,#1}}}
-\nc{\cPMah}[1]{\ensuremath{\cP_{\Mah,#1}}}
+\section{Delegation for FBQP}
+\label{sec:FBQP}
 
@@
 \nc{\cPMF}[1]{\ensuremath{\cP_{\MF,#1}}}
-
-\def\MFZ{\mathsf{MF, 0}}
-\nc{\PiMFZ}{\ensuremath{\Pi_\MFZ}}
-\def\MFZrep{\mathsf{MFZrep}}
-\nc{\PiMFZrep}{\ensuremath{\Pi_\MFZrep}}
-
-\def\blind{\mathsf{blind}}
-\nc{\Piblind}{\ensuremath{\Pi_\blind}}
-\nc{\Vblind}{\ensuremath{V_\blind}}
-\nc{\Pblind}{\ensuremath{P_\blind}}
-\nc{\Pblindstar}{\ensuremath{P_\blind^*}}
-\nc{\cVblind}[1]{\ensuremath{\cV_{\blind,#1}}}
-\nc{\cPblind}[1]{\ensuremath{\cP_{\blind,#1}}}
-
-\def\bz{\mathsf{blind, 0}}
-\nc{\Pibz}{\ensuremath{\Pi_\bz}}
-\nc{\Vbz}{\ensuremath{V_\bz}}
-\nc{\Pbz}{\ensuremath{P_\bz}}
-
-\def\bzrep{\mathsf{blind, 0, rep}}
-\nc{\Pibzrep}{\ensuremath{\Pi_\bzrep}}
-\nc{\Vbzrep}{\ensuremath{V_\bzrep}}
-\nc{\Pbzrep}{\ensuremath{P_\bzrep}}
-
-In this section we build our constant-round blind delegation schemes for $\BQP$ and $\FBQP$ with classical clients.
-
-In \cref{subsec:BlindBQP} we start with the protocol for $\BQP$ from \cite{mf16} which has negligible completeness and soundness errors, but is not blind;
-its verifier requires a single-qubit register and is classical otherwise.
-We first achieve blindness by running said protocol under the homomorphic encryption given in \cite{mahadev_qfhe}.
-We then make the verifier fully classical by using the compiler used in \cite{FOCS:Mahadev18a} even though it deteriorates soundness.
-Finally, we recover soundness while maintaining constant-round by running multiple copies of the protocol in parallel,
-which we analyze using results from \cite{parallelrep, alagic2019twomessage}.
-
-In \cref{subsec:BlindFBQP} we then construct our protocol for $\FBQP$.
-The idea is to break an $\FBQP$ instance down into $\BQP$ instances by considering the output bit-by-bit,
-so we can apply our results for $\BQP$.
-
-\subsection{Blind Delegation for BQP}
-\label{subsec:BlindBQP}
 
@@
 
-We now compile $\PiMF$ using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol $\Piblind$ for $\BQP$.
-The high level idea is to run $\PiMF$ under $\QHE$.
-Namely, the verifier encrypts its original input $x$ and sends $ct_x=\mathsf{QHE.Enc}(x)$ to the prover.
-The prover then homomorphically evaluates $\cPMF{1}$ on $ct_x$ to produce $\sigma$ and sends it to the verifier.
-
-Now the verifier needs to obtain the measurement outcome $w$ from the encrypted state $\sigma$ using qubit-by-qubit measurements.
-This may not be possible in general, but we observe that Mahadev's $\mathsf{QHE}$ allows this. 
-Its ciphertexts consists of a Pauli one-time-padded plaintext and classically encrypted Pauli keys.
-Pauli one-time-pads commute with $X$ and $Z$ measurements, so the verifier can measure the one-time-padded state as usual, then correct the measurement results using the Pauli keys.
-We state and prove this observation in more precise terms.
-
-\begin{thm}
-	\label{decodeMeasureOrder}
-	Let $n, L\in\bbN$.
-	Let $(pk, sk)\leftarrow\QGen(1^n, 1^L)$.
-	Let $m=\poly(n)$ be the length of the ciphertexts corresponding to plaintexts of length $n$ encrypted using $pk$ under $\mathsf{QHE}$.
-
-	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\QDec_{sk}}$ s.t.
-	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement:
-	$$\cM_\QHE(\Lambda)=\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$$
-	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and
-	$$\widehat{\mathsf{QHE.Dec}_{sk}}\circ\Lambda'=\Lambda\circ\mathsf{QHE.Dec_{sk}}$$
-\end{thm}
-\begin{prf}
-	This proof is by construction.
-
-	We require $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
-	$$\widehat{\QDec_{sk}}\circ\Lambda'(\sigma)=\Lambda\circ\QDec_{sk}(\sigma)=\Lambda(\rho)$$
-
-	Let $\Lambda'$ applies $\Lambda$ to the first register, getting $u=\Lambda(X^xZ^z\rho Z^zX^x)$, and applies computational basis measurement to the second register, getting $c_{x, z}$.
-
-	Note that the Pauli one-time pad on $u$ commutes with $X$ and $Z$ measurements.
-	So let $\widehat{\QDec_{sk}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $u$ to get $\Lambda(\rho)$.
-\end{prf}
-
-Now we're ready to state our blind $\QPIP_1$ construction for $\BQP$.
-
-\begin{protocol}{Blind $\QPIP_1$ 1-message protocol $\Piblind = (\Pblind, \Vblind)$ for $\BQP$ language $L$}
-	\label{proto:BlindBQP}
-	Verifier's input: $x\in\set{0,1}^n$.
-
-	\begin{enumerate}
-		\item The verifier generates $(pk, sk, ct_x)\leftarrow\cVblind{1}(x)$ by encrypting $x$ under $\QHE$.
-			More precisely, it generates
-			$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$ where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$, and
-			$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
-			It sends $pk$ and $ct_x$ to the prover.
-		\item The prover computes $\sigma\leftarrow\cPblind{1}(pk, ct_x)$ by homomorphically evaluating $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\QEval_{pk}(\cPMF{1}, ct_x)$.
-			It sends $\sigma$ to the verifier qubit-by-qubit.
-		\item The verifier generates $\Lambda'\leftarrow\cVblind{2}(x)$ by computing
-			$\Lambda\leftarrow\cVMF{2}(x)$,
-			$\Lambda'\leftarrow\cM_\QHE(\Lambda)$.
-			It measures the incoming state $\sigma$ qubit-by-qubit, obtaining $ct_w\leftarrow\Lambda'(\sigma)$.
-			Lastly, it generates and outputs $o\leftarrow\cVblind{3}(ct_w, sk, x, \Lambda')$ by
-			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
-			and $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
-	\end{enumerate}
-\end{protocol}
-
-\begin{thm}
-	\label{thm:BlindBQP}
-	$\Piblind$ has negligible completeness and soundness, and is blind.
-\end{thm}
-\begin{prf}
-	The completeness follows by inspection.
-	For blindness, the prover receives only $ct_x$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.
-
-	Now we prove the soundness of $\Piblind$.
-	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ with some noticeable acceptance probability $\varepsilon$.
-	Then we can construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$ by simulating $(\Vblind(x), \Pblindstar)$ as below:
-
-	We define $\PMFstar$ to first generate
-	$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
-	and
-	$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$,
-	then runs $\sigma\leftarrow\cPblind{1}(pk, ct_x)$.
-	Finally, it decrypts
-	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
-	and sends it to $\VMF$ qubit-by-qubit.
-
-	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
-	Observe that the experiments $(\PMFstar, \VMF)(x)$ and $(\Pblindstar, \Vblind(x))$ are identical except for how $w$ is obtained from $\sigma$,
-	so by \cref{decodeMeasureOrder} they are equivalent.
-	Hence we have $\PMFstar$ with noticeable acceptance probability $\varepsilon$, which is a contradiction.
-\end{prf}
-
-\Ethan{Formally introduce \protoref{urmila4} (measurement protocol) earlier?}
-
-Next, we make the verifier completely classical by compiling $\Piblind$ using \protoref{urmila4} from \cite{FOCS:Mahadev18a}.
-It was originally used to compile $\PiMF$ into $\PiMFZ$ to allow a purely classical client,
-but it can be applied to other $\QPIP_1$ protocols such as our $\Piblind$.
-We give a high-level overview of our compiliation results.
-
-\begin{protocol}{Blind $\QPIP_0$ protocol $\Pibz$ for $BQP$ language $L$}
-	\label{proto:QPIP0BQP}
-	\Ethan{Sync notations on \PiMah}
-	\begin{enumerate}
-		\item The verifier generates $(pk, sk, ct_x)\leftarrow\cVblind{1}$,
-			$\Lambda'\leftarrow\cVblind{2}(x)$,
-			and $(k, td)\leftarrow\cVMah{1}(\Lambda')$.
-			It sends $k, pk, ct_x$ to the prover.
-		\item The prover generates $\sigma\leftarrow\cPblind{1}(pk, ct_x)$ and
-			$(y, st)\leftarrow\cPMah{2}(\sigma)$.
-			It sends $y$ to the verifier.
-		\item The verifier samples public coin $c\leftarrow\set{0, 1}$ and sends it to the prover.
-		\item The prover generates and sends $a\leftarrow\cPMah{3}(c, st)$ to the verifier.
-		\item If $c=0$, then the verifier generates and outputs $o\leftarrow\cVMah{T}(k, y, a, sk)$.
-			Otherwise, it runs $ct_w\leftarrow\cVMah{H}(k, td, y, a, sk)$,
-			then generates and outputs $o\leftarrow\cVblind{3}(ct_w, sk, x, \Lambda')$.
-	\end{enumerate}
-\end{protocol}
-
-\begin{thm}
-	$\Pibz$ has negligible completeness error and is blind. Its soundness error is negligibly close to $\frac{3}{4}$.
-\end{thm}
-\begin{prf}
-	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into $\PiMFZ$ similarly and obtains this completeness and soundness.
-	It uses that $\PiMF$ is $\QPIP_1$ with negligible completeness and soundness errors,
-	and that its verifier only performs $X$ and $Z$ measurements in addition to classical operations.
-	As $\Piblind$ fulfills all these requirements, the same arguments can also be used for the completeness and soundness of $\Pibz$.
-
-	For blindness, recall that the prover receives $ct_x, pk, k, c$ from the verifier,
-	so it follows by the semantic security of $\QHE$ and the fact that $k$ computationally hides the measurement basis choice $\Lambda'$.
-\end{prf}
-
-Finally, we use the recent results \cite{parallelrep, alagic2019twomessage} to recover soundness by means of parallel repetition.
-We first summarize said results.
-
-\begin{thm}[from \cite{parallelrep, alagic2019twomessage}]
-	\label{thm:MFZrep}
-	$\PiMFZ$ can be repeated in parallel, obtaining $\PiMFZrep$ that has negligible completeness and soundness errors.
-\end{thm}
-
-We can now finish building our delegation scheme for $\BQP$.
-\begin{thm}
-	\label{thm:QPIP0BQP}
-	By repeating $\Pibz$ for $\poly(n)$ times in parallel,
-	we obtain $\Pibzrep$ which is a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
-\end{thm}
-\begin{prf}
-	The same argument from \cref{thm:MFZrep} applies.
-	\Ethan{How to make this more rigorous?}
-\end{prf}
-
-\subsection{Blind delegation of FBQP}
-\label{subsec:BlindFBQP}
-
 Here we state our delegation protocol for $\FBQP$.
@@
 Note that our $\BQP$ scheme is one-sided; the prover is allowed to cause the verifier to reject a yes-instance.
-As a result, we run two copies of $\Pbzrep$ for every output bit as below:
+\Ethan{Explain this better...
+Write more intuitions.
+Decision vs function problems; exists vs for all}
+As a result, we run two copies of $\PiMF$ for every output bit as below:
 
-\begin{protocol}{Blind and verifiable $\QPIP_0$ protocol $\Pi_{\FBQP}$ for $f\in\FBQP$}
+\begin{protocol}{$\QPIP_1$ protocol $\Pi_{\FBQP}$ for $f\in\FBQP$}
 	\label{proto:QPIP0FBQP}
@@
 	Let $m=\abs{f(x)}$; we assume without loss of generality that it depends only on $n$ and can be efficiently computed classically.
+	\Ethan{Move this assumption to the definition and make a remark there}
 	\begin{enumerate}
-		\item For all $i\in[m], b\in\set{0, 1}$ in parallel, the verifier and the prover run $(\Pbzrep, \Vbzrep(x))$ for $L_{i, b}$.
+		\item For all $i\in[m], b\in\set{0, 1}$ in parallel, the verifier and the prover run $\PiMF(x)$ for $L_{i, b}$.
 		\item The verifier gets outputs $v_{i, b}\in\set{acc, rej}$.
@@
 \begin{theorem}
-	$\Pi_{\FBQP}$ has negligible completeness and soundness, and is blind.
+	$\Pi_{\FBQP}$ has negligible completeness and soundness errors.
 \end{theorem}
@@
 	Completeness follows by inspection.
-	Blindness follows because the executions of $\Pibzrep$ are blind.
 
-	By the soundness of $\Pibzrep$, $v_{i, b}=acc$ implies that $x\in L_{i, b}$ with overwhelming probability.
+	By the soundness of $\PiMF$, $v_{i, b}=acc$ implies that $x\in L_{i, b}$ with overwhelming probability.
 	In other words, $y_i$ has probability $\varepsilon_i=\negl(n)$ to be incorrect.

### 2020-03-22 qpip.tex
Fix typo

@@
 \begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$}\label{ProtoQPIP1}
-	Pick $\varepsilon=\poly(T^{-1})$
+	Pick $\varepsilon=\poly(T^{-1})$.
 	Let $C'$ be $C$ padded with $\poly(\varepsilon^{-1})$ identity gates at the end.
@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and $O(T^-\lambda)$ soundness error.
+	$\PiSamp$ has negligible completeness error and $O(\poly(\varepsilon))$ soundness error.
 \end{thm}

### 2020-03-22 qpip.tex
Fix typos and add TODOs

@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and $O(\poly(\varepsilon))$ soundness error.
+	$\PiSamp$ has negligible completeness error and $\poly(\varepsilon)$ soundness error.
 \end{thm}
@@
 	Summing up all the $\rho_j$ terms in $J$, we have
-	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda)$$
+	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda).$$
 
@@
 	we then have
-	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\poly(\varepsilon).$$
+	\Ethan{$\rho_j$ isn't a pure state, so need to rewrite this using traces and such}
+	$$\braket{\rho_j|H_{C'(x)}|\rho_j}<\poly(\varepsilon).$$
 	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain
-	$$\braket{\rho_i|\phi_{C'(x)}}>1-\poly(\varepsilon).$$
-	By a standard fidelity argument, the measurement results on $\rho_i$ is $\poly(\varepsilon)$-close to that on $\ket{\phi_{C'(x)}}$.
+	$$\braket{\rho_j|\phi_{C'(x)}}>1-\poly(\varepsilon).$$
+	By a standard fidelity argument, the measurement results on $\rho_j$ is $\poly(\varepsilon)$-close to that on $\ket{\phi_{C'(x)}}$.
 
@@
 
-	The soundness errors incurred at each step is at most $\poly(\varepsilon)$, so the conclusion follows.
+	The soundness errors at each step is $\poly(\varepsilon)$, so the conclusion follows.
 \end{prf}

### 2020-03-22 preliminaries.tex
Add Skype discussion results
Reparametrize QPIP1 SampBQP
Fix copied dfns

@@
 	$\BQP$ is the class of languages $L$ for which for all $n\in\bbN$ there exists a quantum circuit constructible in time $\poly(n)$ that, given any $x\in\set{0, 1}^n$ as input, correctly decides whether $x\in L$ at least $\frac{2}{3}$ of the time.
+\end{definition}
 
@@
 \begin{definition} [sampling problem]
-	A sampling problem $S$ is a collection of probability distributions $(D_x)$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{p(n)}$ for some fixed polynomial $p$.
+	A sampling problem $S$ is a collection of probability distributions $(D_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{p(n)}$ for some fixed polynomial $p$.
 \end{definition}
@@
 \begin{definition} [$\SampBQP$]
-	$\SampBQP$ is the class of sampling problems $S=(D_x)$ for which for all $\varepsilon$ there exists a quantum circuit constructible in time $\poly(|x|, \frac{1}{\varepsilon})$ that, given $x$ as input, samples from from a probability distribution $\tilde{D}_x$ such that $\norm{\tilde{D}_x-D_x}<\varepsilon$.
+	$\SampBQP$ is the class of sampling problems $S=\left(D_x\right)_{x\in\set{0, 1}^*}$ for which there exists a polynomial-time quantum algorithm $B$ that, given $(x, 0^{1/\varepsilon})$ as input, samples from a probability distribution $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
 \end{definition}
@@
 \end{protocol}
+
+\subsection{Chernoff bound}
+
+Taken from \href{http://math.mit.edu/~goemans/18310S15/chernoff-notes.pdf}{here}.
+
+\begin{theorem}
+\label{thm:Chernoff}
+Let $X=\sum_{i=1}^n X_i$ where $X_i$ are i.i.d. Bernoulli trials, and $\mu=\E[X]$.
+Then for all $0<\delta<1$,
+$$P[\abs{X-\mu}\geq\delta\mu]\leq2e^{-\frac{\mu\delta^2}{3}}$$
+\end{theorem}
 

### 2020-03-23 preliminaries.tex
Encounter problem in dfn FBQP

@@
 
-We define a sampling version of $\BQP$, $\SampBQP$, based on \cite{aaronson_2013}.
+We define search and sampling versions of $\BQP$ based on \cite{aaronson_2013}.
+
+\begin{definition} [search problem]
+	A search problem $R$ is a collection of nonempty sets $(A_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0, 1}^*$, where $A_x$... \Ethan{Great, interface doesn't line up correctly}
+\end{definition}
 

### 2020-03-23 blind.tex
Prune blind QPIP1 BQP
Fix typos and add TODOs
Fix typos and wording

@@
+\section{Blindness for $\QPIP_0$ protocols}
+\label{sec:BlindBQP2}
+
 \def\HE{\mathsf{HE}}
@@
 
-\section{Blindness for $\QPIP_0$ protocols}
-\label{sec:BlindBQP2}
+\def\blind{\mathsf{blind}}
+\nc{\Piblind}{\ensuremath{\Pi_\blind}}
+\nc{\Vblind}{\ensuremath{V_\blind}}
+\nc{\Pblind}{\ensuremath{P_\blind}}
+\nc{\Pblindstar}{\ensuremath{P_\blind^*}}
+\nc{\cVblind}[1]{\ensuremath{\cV_{\blind,#1}}}
+\nc{\cPblind}[1]{\ensuremath{\cP_{\blind,#1}}}
 
@@
 
+\Ethan{TODO: break the following into two boxes}
+
 \begin{protocol}{Compiling $\QPIP_0$ protocol $(P, V)(x)$ into $(\Pblind, \Vblind(x))$}
@@
 	Let $\lambda=\abs{x}$.
+
+	\Ethan{TODO Somehow make the hat not go over subscript}
 
@@
 \begin{proof}
-	We define $\Pstar$ so that \Ethan{Fix wording here} on $\cPstar{1}$ it generates
+	We define $\Pstar$ as follows.
+
+	On $\cPstar{1}$ it generates
 	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$, then produces the encryptions
@@
 
-	Then, on the rest of the $\cPstar{t}$ rounds, $\Pstar$ generates
+	Then, on the rest of the $\cPstar{t}$ rounds, it generates
 	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$, and produces ciphertexts
@@
 	Then, for all $t$, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
-	Since computational indistinguishability is transitive \Ethan{Really? Definitely need to write down some inequalities here...}, $\Hyb_1$ is indistinguishable with $\Hyb_{T+1}$.
-	Since $\Hyb_{T+1}$ is precisely $\Piblind$, and $\Hyb_1$ is clearly blind, we can conclude that $\Piblind$ is blind.
+	By applying triangle inequality iteratively\Ethan{Is this enough or do we need equations?}, we obtain that $\Hyb_1$ is indistinguishable with $\Hyb_{T+1}$.
+	Since $\Hyb_{T+1}$ is precisely $\Piblind$, and $\Hyb_1$ is clearly blind, we conclude that $\Piblind$ is blind.
 \end{proof}

### 2020-03-23 blind.tex
Implement suggestions on blind compiler

@@
 \nc{\cPblind}[1]{\ensuremath{\cP_{\blind,#1}}}
+\def\Pstar{P^*}
+\nc{\cPstar}[1]{\ensuremath{\cP^*_{#1}}}
 
@@
 
-\nc{\ctx}[2]{\ensuremath{{{\widehat{#1}}^{(#2)}}}}
+\nc{\ctx}[3]{\ensuremath{{{\widehat{#1}}_{#2}^{(#3)}}}}
 
@@
 For notation, when there are many sets of $\QHE$ keys in play at the same time,
-we use $\ctx{x}{i}$ to denote $x$ encrypted under $pk_i$.
+we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
 
-\Ethan{TODO: break the following into two boxes}
+We start with a general form of the protocols that we'll compile.
 
-\begin{protocol}{Compiling $\QPIP_0$ protocol $(P, V)(x)$ into $(\Pblind, \Vblind(x))$}
-	Suppose the protocol $(P, V)$ is a $\QPIP_0$ protocol where only the verifier receives outputs, with the following general form:
+\begin{protocol}{$\QPIP_0$ protocol $\Pi_0=(P, V)(x)$ where only the verifier receives outputs}
 
@@
 		\item $V$ computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
-			\Ethan{Prover can get outputs too}
 	\end{enumerate}
 
-	Using $\Pi=(P, V)(x)$ from above, we define the protocol $\Piblind=(P, V(x))$ as follows:
+\end{protocol}
+
+We compile the above protocol to achieve blindness as follows.
+
+\begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ correponding to $\Pi_0$}
 
@@
 
-	\Ethan{TODO Somehow make the hat not go over subscript}
-
 	\begin{enumerate}
@@
 			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$,
-			and encrypts $\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
-			It sends $pk_1$, $\ctx{x}{1}$, and $\ctx{v_1}{1}$ to the prover.
-		\item $\Pblind$ generates $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\cPblind{1}(\ctx{v_1}{1}, \ctx{x}{1})$
-			by evaluating $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\QEval_{pk}(\cP_1, \ctx{v_1}{1}, \ctx{x}{1})$.
-			It sends $\ctx{p_1}{1}$ to the verifier.
+			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
+			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
+		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
+			by evaluating $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval_{pk}(\cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
+			It sends $\ctx{p}{1}{1}$ to the verifier.
 		\item for $t=2,\ldots,T$:
 		\begin{enumerate}
-			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p_{t-1}}{t-1})$,
+			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p}{t-1}{t-1})$,
 				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
 				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$,
-				and produces encryptions $\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t)$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
-				It sends $pk_t$, $\ctx{v_t}{t}$, and $\ctx{sk_{t-1}}{t}$ to the prover.
-			\item $\Pblind$ generates $(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\cPblind{t}(\ctx{v_t}{t}, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1})$
-				by first refreshing the $\QHE$ key that encrypts its states by
-				first encrypting it under the new key by $\ctx{st_{P, t-1}}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st_{P, t-1}}{t-1}))$,
+				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc_{pk_t}(v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
+				It sends $pk_t$, $\ctx{v}{t}{t}$, and $\ctx{sk}{t-1}{t}$ to the prover.
+			\item $\Pblind$ generates $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$
+				by first switching the $\QHE$ key that its states is encrypted under;
+				that is, it first encrypts it under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st}{P, t-1}{t-1}))$,
 				then homomorphically decrypting the old encryption under the new key by
-				$\ctx{st_{P, t-1}}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1, t})$.
-				It then applies the next-message function of $\Pi$, generating
-				$(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\QEval_{pk_t}(\cP_t, \ctx{v_t}{t}, \ctx{st_{P, t-1}}{t})$.
-				It sends $\ctx{p_t}{t}$ back to the verifier.
+				$\ctx{st}{P, t-1}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
+				It then applies the next-message function of $\Pi$ homomorphically, generating
+				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval_{pk_t}(\cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
+				It sends $\ctx{p}{t}{t}$ back to the verifier.
 		\end{enumerate}
-		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec_{sk_T}(\ctx{p_T}{T})$.
+		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec_{sk_T}(\ctx{p}{T}{T})$.
 			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
-			\Ethan{Prover can get outputs too}
 	\end{enumerate}
@@
 We show the soundness of $\Piblind$ in the following theorem.
-
-\def\Pstar{P^*}
-\nc{\cPstar}[1]{\ensuremath{\cP^*_{#1}}}
 
@@
 	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$, then produces the encryptions
-	$\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
-	It then runs $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\cPblind{1}(\ctx{v_1}{1}, \ctx{x}{1})$.
-	Finally, it decrypts $p_1\leftarrow\QDec_{sk_1}(\ctx{p_1}{1})$ and sends it back to the verifier,
-	and keeps $\ctx{st_{P, 1}}{1}$ and $sk_1$.
+	$\ctx{x}{}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
+	It then runs $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$.
+	Finally, it decrypts $p_1\leftarrow\QDec_{sk_1}(\ctx{p}{1}{1})$ and sends it back to the verifier,
+	and keeps $\ctx{st}{P, 1}{1}$ and $sk_1$.
 
@@
 	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$, and produces ciphertexts
-	$\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
-	It then runs $(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\cPblind{t}(\ctx{v_t}{t}, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1})$.
-	Finally, it decrypts $p_t\leftarrow\QDec_{sk_t}(\ctx{p_t}{1})$ and sends it back to the verifier,
-	and keeps $\ctx{st_{P, t}}{t}$ and $sk_t$.
+	$\ctx{v}{t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
+	It then runs $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$.
+	Finally, it decrypts $p_t\leftarrow\QDec_{sk_t}(\ctx{p}{t}{1})$ and sends it back to the verifier,
+	and keeps $\ctx{st}{P, t}{t}$ and $sk_t$.
 
@@
 	In $\Hyb_i$, we modify $(\Pblind, \Vblind(x))$ s.t.
-	for all rounds associated with $\cV{t}$ where $t\geq i$, the verifier replaces the $\ctx{sk_{t-1}}{t}$ in its message with encryption of $0$.
+	for all rounds associated with $\cV{t}$ where $t\geq i$, the verifier replaces the $\ctx{sk}{t-1}{t}$ in its message with encryption of $0$.
 	Then, for all $t$, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.

### 2020-03-23 blind.tex
Simplify blindness compiler

@@
 
-	Let $L_t$ be the circuit depth of $\cP_t$.
-	Let $\lambda=\abs{x}$.
+	Let $L=\poly(x)$, $\lambda=\poly(x)$.
 
@@
 		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
-			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$,
+			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$,
 			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
@@
 				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
-				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$,
+				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$,
 				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc_{pk_t}(v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
@@
 			\item $\Pblind$ generates $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$
-				by first switching the $\QHE$ key that its states is encrypted under;
-				that is, it first encrypts it under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st}{P, t-1}{t-1}))$,
-				then homomorphically decrypting the old encryption under the new key by
+				by first switching its encryption key;
+				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st}{P, t-1}{t-1}))$,
+				then homomorphically decrypts the old encryption by
 				$\ctx{st}{P, t-1}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
-				It then applies the next-message function of $\Pi$ homomorphically, generating
+				Then it applies the next-message function of $\Pi$ homomorphically, generating
 				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval_{pk_t}(\cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
@@
 	On $\cPstar{1}$ it generates
-	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$, then produces the encryptions
+	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$, then produces the encryptions
 	$\ctx{x}{}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
@@
 	Then, on the rest of the $\cPstar{t}$ rounds, it generates
-	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$, and produces ciphertexts
+	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$, and produces ciphertexts
 	$\ctx{v}{t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.

### 2020-03-23 blind.tex
Try introing blind compiler

@@
-\section{Blindness for $\QPIP_0$ protocols}
+\section{Achieving Blindness on $\QPIP_0$ protocols}
 \label{sec:BlindBQP2}
@@
 \nc{\cPstar}[1]{\ensuremath{\cP^*_{#1}}}
+\nc{\ctx}[3]{\ensuremath{{{\widehat{#1}}_{#2}^{(#3)}}}}
 
-In this section we show a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
-\Ethan{Talk about the compiler first, and BQP after.}
-We start with the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
-Generally one can obtain blindness by running a protocol under homomorphic encryption.
-\Ethan{Maybe cite?} In our case, we have a classical client and a quantum server, so we choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.
-\Ethan{Talk about FBQP too}
+Here we present our compiler on $\QPIP_0$ protocols that can be used to achieves blindness.
+The high level idea is to run the protocol under homomorphic encryption.
+Similar idea has happened in
+\Ethan{TODO cite thesis} \Ethan{TODO maybe find out more about that ``simulate-able" thing in that thesis and explain the difference in the contexts}.
+As we have the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
+Compiling it would be a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
+Similarly, the compiler can be applied to our $\FBQP$ and $\SampBQP$ protocols \Ethan{TODO name} too.
 
-\nc{\ctx}[3]{\ensuremath{{{\widehat{#1}}_{#2}^{(#3)}}}}
+We have a classical client and a quantum server.
+We choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.
+More precisely, when the corresponding plaintext is classical, encryption and decryption can be performed classically.
+Furthermore, we notice that a ciphertext can be split into registers as with the corresponding plaintext.
+
+A naive approach is to encrypt the initial input,
+evaluate the entire protocol homomorphically,
+then decode the output at the very end.
+However, it is difficult to prove the soundness because... \Ethan{TODO why?}
+So instead we let the verifier decrypt every round.
+Then, in order the preserve blindness, the verifier generates a new set of keys for every message it sends to the prover...
+Which results in the following protocol.
 
@@
 We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.
-First, when the plaintext is classical, the encryption can be performed classically.
-Moreover, a quantum ciphertext can be measured homomorphically, in which case the measurement outcomes can then be decrypted classically.
-Lastly, the encryption is done qubit-by-qubit, so one can split a ciphertext into registers as one would with the corresponding plaintext.
 
@@
 we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
-
-We start with a general form of the protocols that we'll compile.
 

### 2020-03-23 blind.tex
Make QHE keys into params instead of subscripts

@@
 			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$,
-			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
+			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc(pk_1, x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc(pk_1, v_1)$.
 			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
 		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
-			by evaluating $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval_{pk}(\cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
+			by evaluating $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval(pk, \cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
 			It sends $\ctx{p}{1}{1}$ to the verifier.
@@
 		\begin{enumerate}
-			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p}{t-1}{t-1})$,
+			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec(sk_{t-1}, \ctx{p}{t-1}{t-1})$,
 				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
 				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$,
-				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc_{pk_t}(v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
+				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc(pk_t, v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc(pk_t, sk_{t-1})$.
 				It sends $pk_t$, $\ctx{v}{t}{t}$, and $\ctx{sk}{t-1}{t}$ to the prover.
@@
 				by first switching its encryption key;
-				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st}{P, t-1}{t-1}))$,
+				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc(pk_t, \ctx{st}{P, t-1}{t-1}))$,
 				then homomorphically decrypts the old encryption by
-				$\ctx{st}{P, t-1}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
+				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
 				Then it applies the next-message function of $\Pi$ homomorphically, generating
-				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval_{pk_t}(\cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
+				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval(pk_t, \cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
 				It sends $\ctx{p}{t}{t}$ back to the verifier.
 		\end{enumerate}
-		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec_{sk_T}(\ctx{p}{T}{T})$.
+		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec(sk_T, \ctx{p}{T}{T})$.
 			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
@@
 	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$, then produces the encryptions
-	$\ctx{x}{}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
+	$\ctx{x}{}{1}\leftarrow\QEnc(pk_1, x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc(pk_1, v_1)$.
 	It then runs $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$.
-	Finally, it decrypts $p_1\leftarrow\QDec_{sk_1}(\ctx{p}{1}{1})$ and sends it back to the verifier,
+	Finally, it decrypts $p_1\leftarrow\QDec(sk_1, \ctx{p}{1}{1})$ and sends it back to the verifier,
 	and keeps $\ctx{st}{P, 1}{1}$ and $sk_1$.
@@
 	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$, and produces ciphertexts
-	$\ctx{v}{t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
+	$\ctx{v}{t}{t}\leftarrow\QEnc(pk_t, v_t))$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc(pk_t, sk_{t-1})$.
 	It then runs $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$.
-	Finally, it decrypts $p_t\leftarrow\QDec_{sk_t}(\ctx{p}{t}{1})$ and sends it back to the verifier,
+	Finally, it decrypts $p_t\leftarrow\QDec(sk_t, \ctx{p}{t}{1})$ and sends it back to the verifier,
 	and keeps $\ctx{st}{P, t}{t}$ and $sk_t$.

### 2020-03-23 blind.tex
Fix typo

@@
 				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
-				Then it applies the next-message function of $\Pi$ homomorphically, generating
+				Then it applies the next-message function homomorphically, generating
 				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval(pk_t, \cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.

### 2020-03-23 qpip.tex
Handle mixed states in QPIP1 SampBQP

@@
 	Now, for the other case, $j\notin J$.
-	$$\Prob{\cV_\GS(\phi)=acc}>\frac{1}{2}-2h\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\poly(\varepsilon)$$
-	we then have
-	\Ethan{$\rho_j$ isn't a pure state, so need to rewrite this using traces and such}
-	$$\braket{\rho_j|H_{C'(x)}|\rho_j}<\poly(\varepsilon).$$
-	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain
-	$$\braket{\rho_j|\phi_{C'(x)}}>1-\poly(\varepsilon).$$
-	By a standard fidelity argument, the measurement results on $\rho_j$ is $\poly(\varepsilon)$-close to that on $\ket{\phi_{C'(x)}}$.
+	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2h\Rightarrow\tr\left(H_{C'(x)}\rho_j\right)<\poly(\varepsilon)$$
+	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{Need notation for fidelity}
+	$$D(\rho_j, \ket{\phi_{C'(x)}})<\poly(\varepsilon)$$
 

### 2020-03-23 qpip.tex
Fix wording

@@
 	So we can apply the Chernoff bound \cref{thm:Chernoff} with $\mu=\frac{m}{2}$, $\delta=2h$ to get
-	$$\Prob{\frac{m}{2}-Z\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
+	$$\Prob{\frac{m}{2}-Z\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T).$$
 
@@
 	A random permutation, in turn, is a classical mix over all possible permutations:
-	$$\sigma'=\frac{1}{\abs{\Sym(M)}}\sum_{\Pi\in\Sym(M)}\Pi\sigma\Pi^\dagger$$
+	$$\sigma'=\frac{1}{\abs{\Sym(M)}}\sum_{\Pi\in\Sym(M)}\Pi\sigma\Pi^\dagger.$$
 	It is simple to check that $\sigma'$ is permutation-invariant.
@@
 	=\sigma'$$
-	where the second equality is by relabeling $\tilde{\Pi}\Pi=\hat{\Pi}$, which is allowed since $\Sym(M)$ is a group.
+	where the second equality is by relabeling $\tilde{\Pi}\Pi=\hat{\Pi}$.
 
@@
 	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ such that:
-	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}=O(\varepsilon)$$
+	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}=O(\varepsilon).$$
 
@@
 
-	Now, for the other case, $j\notin J$.
-	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2h\Rightarrow\tr\left(H_{C'(x)}\rho_j\right)<\poly(\varepsilon)$$
+	Now, for the other case, $j\notin J$, we have
+	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2h\Rightarrow\tr\left(H_{C'(x)}\rho_j\right)<\poly(\varepsilon).$$
 	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{Need notation for fidelity}

### 2020-03-23 blind.tex
Cite KMThesis
Editorial changes on blindness compiler intro

@@
 The high level idea is to run the protocol under homomorphic encryption.
-Similar idea has happened in
-\Ethan{TODO cite thesis} \Ethan{TODO maybe find out more about that ``simulate-able" thing in that thesis and explain the difference in the contexts}.
-As we have the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
-Compiling it would be a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
-Similarly, the compiler can be applied to our $\FBQP$ and $\SampBQP$ protocols \Ethan{TODO name} too.
-
+A classical version of this compiler appears in \cite{KMThesis}, where it is used to make protocols computationally simulatable.
 We have a classical client and a quantum server.
-We choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.
+So we choose the quantum homomorphic encryption from \cite{mahadev_qfhe} that's compatible with classical clients.
 More precisely, when the corresponding plaintext is classical, encryption and decryption can be performed classically.
-Furthermore, we notice that a ciphertext can be split into registers as with the corresponding plaintext.
+Furthermore, we notice that the ciphertexts can be split into registers as with the corresponding plaintext.
 
 A naive approach is to encrypt the initial input,
-evaluate the entire protocol homomorphically,
+run the entire protocol homomorphically,
 then decode the output at the very end.
-However, it is difficult to prove the soundness because... \Ethan{TODO why?}
+However, it is difficult to prove the soundness this way because homomorphic encryption schemes doesn't guarantee circuit privacy;
+the server could learn about ther client's coins.
+Furthermore, the prover would also be allowed to send invalid ciphertexts...?
+\Ethan{Can't we assume all ciphertexts are valid, and ``invalid" ones just decodes to $\bot$?}
 So instead we let the verifier decrypt every round.
@@
 \Ethan{General comment: Make story more interesting. Clearly claim our own contributions.}
-
-\Ethan{Too bottom-up. Need to tell more story.}
-We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.
-
-\Ethan{More story here. Talk about stuff like why switch keys.}
 
@@
 \end{proof}
+
+This compiler implies a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
+To do so, apply it to the protocol from \cite{parallelrep, alagic2019twomessage}.
+Similarly, the compiler can be applied to our $\FBQP$ and $\SampBQP$ protocols \Ethan{TODO name} too.

### 2020-03-25 qpip.tex
Add notes from discussion

@@
-\section{Delegation Protocol for Hybrid Client}
+\section{Delegation Protocol for $\QPIP_1$ Client}
 
@@
 
+\Ethan{Again, look at other papers...}
+
+\Ethan{TODO Recall variables from the last section}
+
 \begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$}\label{ProtoQPIP1}
+    \Ethan{Two action items; define T. Don't set eps this early.}
 	Pick $\varepsilon=\poly(T^{-1})$.
+
 	Let $C'$ be $C$ padded with $\poly(\varepsilon^{-1})$ identity gates at the end.
 	Pick $h=\poly(\varepsilon)$, $m=O(h^{-3})$, $M=\poly(m)$.
+	\Ethan{Solve instead of using ``poly"; ``order" is fine.
+	For running time, poly is fine though.}
+	\Ethan{get style from pg 22 on other paper}
+
+	\Ethan{Also see 102, p2, 5}
+
+	\Ethan{201 p12 p23 two different styles of protocol-writing}
+
+	\Ethan{106 p31}
+
+	\Ethan{Specify size of h, m, M when they appear instead of at the top}
+
+	\Ethan{Use gamma or whatever Greek letter instead of h for threshold}
 
@@
 		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$, and $k\xleftarrow{\$}[M]\setminus I$.
-			For $i$ from $1$ to $N$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
+			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
 		\begin{enumerate}
 			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
-			\item Otherwise, if $i=k$, measure the data register of $\rho_i$ and save the outcome as $y$.
-			\item Otherwise, discard $\rho_i$.
+			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ and save the outcome as $y$.
+			\item Else, discard $\rho_i$.
 		\end{enumerate}
@@
 	$$\Prob{\frac{m}{2}-Z\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T).$$
+	\Ethan{Just match the protocol above; write $Z>m/2-hm$.
+	This is Chernoff bound; nobody will get confused over it not matching the theorem statement precisely.}
 
@@
 	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier.
+
+    \Ethan{``First step of our analysis is to use..."; use common sense?}
 
@@
 	$$\sigma'=\frac{1}{\abs{\Sym(M)}}\sum_{\Pi\in\Sym(M)}\Pi\sigma\Pi^\dagger.$$
-	It is simple to check that $\sigma'$ is permutation-invariant.
-	Fix $\tilde{\Pi}\in\Sym(M)$, then
+	It is simple to check that $\sigma'$ is permutation-invariant:
+	fix $\tilde{\Pi}\in\Sym(M)$, then
 	$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger
@@
 
-	Now we apply \cref{deFinetti} to approximate $\sigma'$ with a classical mix over tensors of independent states.
-	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ such that:
+	Now we apply \cref{deFinetti} \Ethan{Theorem is always uppercase. Same with Lemma.} to approximate $\sigma'$ with a classical mix over tensors of independent states.
+	\Ethan{Say this is measurement results, and state typeof(Lambda) while at it. Define specific Lambdas instead of max over; or actually, use for all}
+	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ \Ethan{Double check that registers of rhos are all identical} such that:
 	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}=O(\varepsilon).$$

### 2020-03-27 hamiltonian.tex
Implement some comments from the discussion

@@
-\section{The History XZ Local Hamiltonian}
+\section{Construction of the XZ Local Hamiltonian}
 \label{sec:Hamiltonian}
+
+\XW{highlight the different requirement from the normal Local Hamiltonian reduction; and highlight a bit about the solution idea}
 
@@
 \subsection{Circuits of Toffoli and Hadamard gates}
+
+Old notation: Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
+I.e.
+$\Lambda^2_{1, 2}(X_3)$ would be a Toffoli gate.
+\Ethan{TODO: replace with something that looks better and doesn't conflict with the use of $\Lambda$ as measurement.}
 
@@
 \end{prf}
+
+%%%%
+%%%% Keep the old version here for the record. 
+%%%%
+
+% \section{The History XZ Local Hamiltonian}
+% \label{sec:Hamiltonian}
+
+% In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian instance.
+
+% The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
+% Protocols to delegate $\BQP$ computations such as \cite{FOCS:Mahadev18a} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
+% We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.
+% Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
+% \Ethan{This source was given to us by Yu-Ching; I haven't read it. Also I probably should cite more sources here.}
+
+% We begin by recalling the form that local Hamiltonian certificates:
+
+% \begin{dfn}
+% 	\label{dfn:groundstate}	
+% 	Let $C=U_T\ldots U_1$ be a quantum circuit consisting of $T$ gates, and let $x\in\set{0,1}^n$. Then we denote
+% 	$$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$$
+% 	We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
+% \end{dfn}
+
+% \begin{rmk}
+% 	\label{idpadding}
+% 	One can first pad $C$ with identity gates at the end, doubling its number of gates and obtaining another circuit $C'$.
+% 	Then by measuring the time register of $\ket{\psi_{C'(x)}}$ one obtains with probability $\frac{1}{2}$ the state $C(x)$.
+% \end{rmk}
+
+% We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$ as below; note that this spans a subspace of $5$-local Hamiltonians.
+% \begin{dfn}
+% 	$$\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \abs{\set{i: U_i\ne I}}\leq 5}$$
+% \end{dfn}
+
+% Now we state the main theorems that we'll work towards in this section.
+% The first one is the reduction from $\SampBQP$ to a local Hamiltonian instance, with some additional properties that will be convenient for us:
+% \begin{thm}
+% 	\label{thm:LHReduction}
+% 	Let $C$ be a circuit of size $T$. For any input string $x$, there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
+% 	\begin{itemize}
+% 		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
+% 		\item $H_{C(x)}$ has $\ket{\psi_{C(x)}}$ as the unique ground state with eigenvalue $0$.
+% 		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
+% 		\item Its descriptions can be constructed by a $\BPP$ machine in polynomial time.
+% 	\end{itemize}
+% \end{thm}
+
+% The second one is a way to verify ground states of local Hamiltonians, again with some extra properties:
+% \begin{thm}
+% 	\label{ThmXZCheck}
+% 	Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists a $\BQP$ algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
+(In particular, it accepts the $\ket{\psi_{C(x)}}$ with probability $\fot$.) Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
+% \end{thm}
+
+% \subsection{Circuits of Toffoli and Hadamard gates}
+
+% Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
+% Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
+% Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
+% \begin{thm}
+% 	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
+% \end{thm}
+% \begin{prf}
+% 	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
+% 	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
+% 	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
+% \end{prf}
+
+% Now we present the proof that $\set{H, \Lambda^2(X)}$ is indeed a universal gate set from \cite{quant-ph/0301040}: \Ethan{This definitely belongs in the appendix instead...}
+% \begin{thm}
+% 	Let $C$ be a circuit that:
+% 	\begin{itemize}
+% 		\item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
+% 		\item uses $n$ qubits
+% 	\end{itemize}
+% 	Then a classical machine given $C$ can compute a circuit $C'$ that:
+% 	\begin{itemize}
+% 		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
+% 		\item uses $n+1$ qubits
+% 		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
+% 		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
+% 	\end{itemize}
+% \end{thm}
+% \begin{prf}
+% 	We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
+% 	$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
+% 		$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
+
+% 	Now consider the transform on quantum states
+% 	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
+% 	where $\Re$ and $\Im$ denote real and imaginary parts respectively.
+
+% 	This transform commutes with Hadamard gates on the respective qubit.
+On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turn it into a combination of Hadamard and Toffoli gates.
+Mathematically,
+% 	$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
+% 	$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
+
+% 	We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
+% 	\begin{itemize}
+% 		\item $C'$ uses only Hadamard and Toffoli gates.
+% 		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
+% 		\item When $x$ is classical, $\mathcal{F}(x)=x||0$.
+So $F\circ C(x)=C'(x||0)$.
+It is simple \hannote{need a little more work?}to verify that $\mathcal{F}$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
+% 	\end{itemize}
+% \end{prf}
+
+% \subsection{Reducing quantum circuit to local Hamiltonian}
+
+% In this subsection, we prove \cref{thm:LHReduction} by showing how to reduce a $\SampBQP$ circuit to a local-$XZ$-Hamiltonian.
+
+% 	The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.
+
+% 	Let $x_i$ denote the $i$-th bit of $x$, and let $n$ be the number of qubits in $C$.
+
+% 	We need to ensure the excited states of $H_{C(x)}$ have high eigenvalues.
+
+% 	First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
+% 	$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
+% 	As a sum of projections, clearly $H_{clock}\geq 0$. We shall also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
+% 	$$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
+% 	This can be checked by fixing the first and last qubit, then doing induction on the number of switches.
+
+% 	Then, we ensure that the initial condition is set up correctly.
+% 	$$H_{in}=\sum_{i=1}^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
+% 	The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
+% 	$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$
+
+% 	Then, we ensure that the gates are applied correctly.
+% 	$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
+% 	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
+% 	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+% 	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
+% 	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
+
+% 	We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least nonzero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
+
+% 	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since our gates are either Hadamard or Toffoli.
+% 	Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
+% 	$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
+% 	Extra care must be taken for boundary cases.
+% 	$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
+% 	$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
+
+% 	To properly combine the three Hamiltonians defined and analyze it using the projection lemma (\cref{thm:projection}), we consider the kernels of the Hamiltonians we defined.
+% 	$$K_{clock}=\ker H_{clock}$$
+% 	$$K_{in}=\ker H_{in}$$
+% 	$$K_{prop}=\ker H_{prop}$$
+
+% 	Clearly,
+% 	$$K_{clock}=\set{\sum_{t=1}^T \ket{\phi_t}\otimes\ket{\hat{t}}:\ket{\phi_t}\in\cB^{\otimes n}}$$
+% 	Let $\ket\phi\in K_{clock}\cap K_{prop}$.
+% 	Consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$.
+% 	As $\ket\phi\in K_{prop}$, we can then do induction using $\widetilde{t}$ as base case to get the relations between the $\ket{\phi_t}$s and conclude that $\ket\phi$ must have the form:
+% 	$$\ket\phi=\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}$$
+% 	$$\Rightarrow K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
+
+% 	As a direct result, we get
+% 	$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$$
+
+% We now consider the space outside the desired state.
+% $$S=(\spn\set{\ket{\psi_{C(x)}}})^\bot$$
+% $$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
+% To combine the Hamiltonians, we apply the projection lemma twice.
+% $$\exists J_{clock}
+% =\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
+% =O(n)=O(T)$$
+% $$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
+% \lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
+% $$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
+% =\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
+% $$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
+% \lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
+% \begin{align*}
+% 	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
+% 	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{C(x)}|y}=0}
+% \end{align*}
+% $$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
+% So we set $H_{C(x)}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
+
+% \subsection{Checking the ground state of the local Hamiltonian}
+
+% In this subsection, we prove \cref{ThmXZCheck}.
+% That is, we present and analyze an algorithm that checks whether a given state is the ground state of some fixed $H_{C(x)}$, following~\cite{PhysRevA.93.022326}.
+
+% \begin{algorithm}
+% 	\caption{Check for ground state}
+% 	\label{AlgGroundStateCheck}
+% 		Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
+% 		Let $\ket\phi$ be the potential ground state to check.
+% 		\begin{itemize}
+% 			\item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
+% 			\item Set $p_S = \frac{|d_S|}{D}$
+% 			\item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
+% 			\item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
+% 			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept. Otherwise, reject.
+% 		\end{itemize}
+% \end{algorithm}
+
+% \begin{thm}
+% 	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients at most $O(\poly(T))$.
+% 	Then \cref{AlgGroundStateCheck} accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
+% \end{thm}
+% \begin{prf}
+% 	Here we follow \cite{PhysRevA.93.022326}.
+% 	\begin{align*}
+% 		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
+% 		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
+% 		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
+% 		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
+% 	\end{align*}
+
+% 	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
+% 	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
+% 	\begin{align*}
+% 		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
+% 		&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
+% 	\end{align*}
+% \end{prf}

### 2020-03-27 preliminaries.tex
Add notes from discussion
Implement some comments from the discussion

@@
 For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
-Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
-I.e.
-$\Lambda^2_{1, 2}(X_3)$ would be a Toffoli gate.
+
+\begin{definition} [quantum-classical channels]
+	\label{def:QCChannel}
+	A quantum measurement is given by a set of matrices $\set{M_k}$ such that $M_k\geq0$ and $\sum_k M_k=\id$.
+	We associate to any measurement a map $\Lambda(\rho)=\sum_k \tr(M_k\rho)\ket{k}\bra{k}$
+	with $\set{\ket{k}}$ an orthonormal basis.
+	This map is also called a \emph{quantum-classical channel}.
+\end{definition}
 
@@
 \end{definition}
+
+TODO Define fidelity
 
@@
 \begin{definition}
-	A sampling problem $S=(D_x)$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a protocol $(\bbP, \bbV)$ with the following properties with input $x$:
+	A sampling problem $S=(D_x)_{x\in\set{0, 1}^*}$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a protocol $(\bbP, \bbV)$ with the following properties with input $x$:
 	\begin{itemize}
@@
 	$$\max_{\Lambda_1,\ldots,\Lambda_l}\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
+	where $\Lambda_i$ are quantum-classical channels.
 \end{thm}

### 2020-03-27 qpip.tex
Implement some comments from the discussion

@@
 \def\GS{\mathsf{Ham}}
-\nc{\PiGS}{\ensuremath{\Pi_\GS}}
-\nc{\VGS}{\ensuremath{V_\GS}}
-\nc{\PGS}{\ensuremath{P_\GS}}
-\nc{\PGSstar}{\ensuremath{P_\GS^*}}
-\nc{\cVGS}[1]{\ensuremath{\cV_{\GS,#1}}}
-\nc{\cPGS}[1]{\ensuremath{\cP_{\GS,#1}}}
+\nc{\cVGS}{\ensuremath{\cV_\GS}}
 
@@
 
-\Ethan{TODO Recall variables from the last section}
+We start with a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$ and an input $x$,
+then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy.
+We assume without loss of generality that $C$ comprises of only Hadamard and Toffoli gates.
+We now present our $\QPIP_1$ protocol that allows a client to verifiably obtain the measurement outcome of $C(x)$.
 
-\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$}\label{ProtoQPIP1}
-    \Ethan{Two action items; define T. Don't set eps this early.}
-	Pick $\varepsilon=\poly(T^{-1})$.
+\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for computation of $C(x)$ and error parameter $\varepsilon$}\label{ProtoQPIP1}
 
-	Let $C'$ be $C$ padded with $\poly(\varepsilon^{-1})$ identity gates at the end.
-	Pick $h=\poly(\varepsilon)$, $m=O(h^{-3})$, $M=\poly(m)$.
-	\Ethan{Solve instead of using ``poly"; ``order" is fine.
-	For running time, poly is fine though.}
+	Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
+	Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}, and
+	$\cVGS$ be the way to check this ground state as defined in \Cref{AlgGroundStateCheck}.
+
 	\Ethan{get style from pg 22 on other paper}
@@
 
-	\Ethan{Specify size of h, m, M when they appear instead of at the top}
-
-	\Ethan{Use gamma or whatever Greek letter instead of h for threshold}
-
 	\begin{enumerate}
-		\item The honest prover prepares $M$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
-		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$, and $k\xleftarrow{\$}[M]\setminus I$.
+		\item The honest prover prepares $M=\varepsilon^{-8}\ln(\frac{T}{\varepsilon})$ copies \Ethan{That isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\varepsilon^{-3}$, and $k\xleftarrow{\$}[M]\setminus I$.
 			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
@@
 		\end{enumerate}
-			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-hm$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
+			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\varepsilon m$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
 	\end{enumerate}
@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and $\poly(\varepsilon)$ soundness error.
+	$\PiSamp$ has negligible completeness error and $\poly(\varepsilon^{-1})$ soundness error.
 \end{thm}
@@
 	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
-	So we can apply the Chernoff bound \cref{thm:Chernoff} with $\mu=\frac{m}{2}$, $\delta=2h$ to get
-	$$\Prob{\frac{m}{2}-Z\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T).$$
-	\Ethan{Just match the protocol above; write $Z>m/2-hm$.
-	This is Chernoff bound; nobody will get confused over it not matching the theorem statement precisely.}
+	So we can apply the Chernoff bound \cref{thm:Chernoff} with $\mu=\frac{m}{2}$ and $\delta=2\varepsilon$ to get
+	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$
 
@@
 
-    \Ethan{``First step of our analysis is to use..."; use common sense?}
-
-	We first show that de Finetti's theorem can indeed be used here to achieve independence.
+	The first step of our analysis is to use de Finetti's theorem.
 	Randomly picking $m+1$ out of $M$ registers is equivalent to first applying a random permutation to get some $\sigma'$ then taking the first $m+1$ registers.
@@
 
-	Now we apply \cref{deFinetti} \Ethan{Theorem is always uppercase. Same with Lemma.} to approximate $\sigma'$ with a classical mix over tensors of independent states.
-	\Ethan{Say this is measurement results, and state typeof(Lambda) while at it. Define specific Lambdas instead of max over; or actually, use for all}
-	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ \Ethan{Double check that registers of rhos are all identical} such that:
-	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}=O(\varepsilon).$$
+	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
+	Note that the ground state has $\abs{A}=n+T+\frac{T}{e}$ qubits.
+	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ such that for all quantum-classical channels $\Lambda_i$ on $\abs{A}$ qubits:
+	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}=\frac{todo}{todo}=O(\varepsilon).$$
 
-	Now we separate the $\rho_j$ into two categories: $J=\set{j\in I|p_j=\cV_\GS(\rho_j)<\frac{1}{2}-2h}$ and its complement.
+	Now we separate the $\rho_j$ into two categories: $J=\set{j\in I|p_j=\cV_\GS(\rho_j)<\frac{1}{2}-2\varepsilon}$ and its complement.
 
@@
 	Now, for the other case, $j\notin J$, we have
-	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2h\Rightarrow\tr\left(H_{C'(x)}\rho_j\right)<\poly(\varepsilon).$$
+	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2\varepsilon\Rightarrow\sqrt{\tr\left(H_{C'(x)}\rho_j}\right)<\varepsilon.$$
 	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{Need notation for fidelity}

### 2020-03-29 hamiltonian.tex
Relate V_Ham p_acc with fidelity to ground state

@@
 	\begin{itemize}
-		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
+		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms and $d_S\in O(T^4)$.
 		\item $H_{C(x)}$ has $\ket{\psi_{C(x)}}$ as the unique ground state with eigenvalue $0$.
@@
 \begin{algorithm}
-	\caption{Check for ground state}
+	\caption{Check for ground state $\cVGS$}
 	\label{AlgGroundStateCheck}
@@
 \begin{thm}
-	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients at most $O(\poly(T))$.
-	Then \cref{AlgGroundStateCheck} accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
+	\label{thm:HamCheck}
+	Let $H$ have $O(T)$ nonzero terms whose coefficients are at most $O(T^4)$.
+	\Ethan{Missing a bunch of other assumptions... Should just state $H$ as local Hamiltonian instance from earlier}
+	Then $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{O(1)}{T^5}\braket{\phi|H_{C(x)}|\phi}$.
 \end{thm}
@@
 		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
-		&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
+		&=\frac{1}{2}-\frac{O(1)}{T^5}\braket{\phi|H|\phi}
 	\end{align*}
+\end{prf}
+
+\begin{cor}
+	\Ethan{Consider merging this with theorem above}
+
+	\label{cor:HamCheck}
+	There exists some $c\in\bbR$ s.t.
+	let $H_{C(x)}$ be as above and
+	$\varepsilon\in\bbR$, then
+	if $\cVGS$ accepts $\rho$ with probability at least $\frac{1}{2}-\frac{c\varepsilon}{T^5}$
+	then $F(\rho, \psi_{C(x)})\geq1-\varepsilon$
+\end{cor}
+\begin{prf}
+	Define $c$ so that $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{c}{T^5}\braket{\phi|H_{C(x)}|\phi}$.
+
+	Break $\ket{\phi}$ above into what's in the kernel of $H$ and what isn't.
+	$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
+	We can then see $\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\psi_{C(x)}, \phi)$.
+
+	Now we have
+	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\psi_{C(x)}, \phi))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
+	which easily implies our claim for pure state inputs $\phi$.
+
+	The argument generalizes easily to mixed state inputs $\rho$.
 \end{prf}

### 2020-03-29 preliminaries.tex
Define fidelity
Relate V_Ham p_acc with fidelity to ground state

@@
 For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
+We write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.
 
@@
 \end{definition}
-
-TODO Define fidelity
 
@@
 	\label{thm:projection}
-	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$. Then,
-	$$\exists J=\frac{\poly(\norm{H_1})}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
+	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
+	$$J=\frac{10\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
+	then we have
 	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$

### 2020-03-29 qpip.tex
Relate V_Ham p_acc with fidelity to ground state

@@
 
-\def\GS{\mathsf{Ham}}
-\nc{\cVGS}{\ensuremath{\cV_\GS}}
-
-\def\Samp{\mathsf{Samp}}
-\nc{\PiSamp}{\ensuremath{\Pi_\Samp}}
-\nc{\VSamp}{\ensuremath{V_\Samp}}
-\nc{\PSamp}{\ensuremath{P_\Samp}}
-\nc{\PSampstar}{\ensuremath{P_\Samp^*}}
-\nc{\cVSamp}[1]{\ensuremath{\cV_{\Samp,#1}}}
-\nc{\cPSamp}[1]{\ensuremath{\cP_{\Samp,#1}}}
-
 \Ethan{Again, look at other papers...}
@@
 	Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
-	Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}, and
-	$\cVGS$ be the way to check this ground state as defined in \Cref{AlgGroundStateCheck}.
+	Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction},
+	and $\cVGS$ be the way to check this ground state as defined in \Cref{AlgGroundStateCheck}.
+	Recall that by \Cref{thm:HamCheck} there exists some $c\in\bbN$
+	\Ethan{Maybe figure out the exact value of $c$ later? It's really messy due to multiple uses of projection lemma among other things}
+	so that if $\cVGS$ accepts $\rho$ with probability at least $\frac{1}{2}-\kappa$ where $\kappa=\frac{\varepsilon}{(T+\frac{T}{\varepsilon})^c}$ then $F(\rho, \ket{\psi_{C'(x)}})\geq1-\varepsilon^2$
+	\Ethan{TODO: That theorem currently doesn't even say that. At least write a corollary for it.}
 
@@
 	\begin{enumerate}
-		\item The honest prover prepares $M=\varepsilon^{-8}\ln(\frac{T}{\varepsilon})$ copies \Ethan{That isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
-		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\varepsilon^{-3}$, and $k\xleftarrow{\$}[M]\setminus I$.
+		\item The honest prover prepares $M=\kappa^{-4}\varepsilon^{-4}\ln(\frac{T}{\varepsilon})$ copies \Ethan{That isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\kappa^{-2}\varepsilon^{-1}$, and $k\xleftarrow{\$}[M]\setminus I$.
 			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
@@
 	Now, for the other case, $j\notin J$, we have
-	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2\varepsilon\Rightarrow\sqrt{\tr\left(H_{C'(x)}\rho_j}\right)<\varepsilon.$$
+	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2\varepsilon\Rightarrow\sqrt{\tr H_{C'(x)}\rho_j}<\varepsilon.$$
 	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{Need notation for fidelity}

### 2020-03-29 qpip.tex
Get ready for next round of feedbacks

--- 2020-03-27 qpip.tex
@@
 
-\def\GS{\mathsf{Ham}}
-\nc{\cVGS}{\ensuremath{\cV_\GS}}
-
-\def\Samp{\mathsf{Samp}}
-\nc{\PiSamp}{\ensuremath{\Pi_\Samp}}
-\nc{\VSamp}{\ensuremath{V_\Samp}}
-\nc{\PSamp}{\ensuremath{P_\Samp}}
-\nc{\PSampstar}{\ensuremath{P_\Samp^*}}
-\nc{\cVSamp}[1]{\ensuremath{\cV_{\Samp,#1}}}
-\nc{\cPSamp}[1]{\ensuremath{\cP_{\Samp,#1}}}
-
 \Ethan{Again, look at other papers...}
-
-We start with a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$ and an input $x$,
-then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy.
-We assume without loss of generality that $C$ comprises of only Hadamard and Toffoli gates.
-We now present our $\QPIP_1$ protocol that allows a client to verifiably obtain the measurement outcome of $C(x)$.
-
-\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for computation of $C(x)$ and error parameter $\varepsilon$}\label{ProtoQPIP1}
-
-	Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
-	Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}, and
-	$\cVGS$ be the way to check this ground state as defined in \Cref{AlgGroundStateCheck}.
 
@@
 
+We start with a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$ and an input $x$,
+then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy.
+We assume without loss of generality that $C$ comprises of only Hadamard and Toffoli gates.
+We present our protocol that allows a client to verifiably obtain the measurement outcome of $C(x)$.
+
+\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for the computation $C(x)$ with error parameter $\varepsilon$}
+	\label{ProtoQPIP1}
+
+	Inputs:
+	\begin{itemize}
+		\item Error parameter $\varepsilon\in(0, 1)$
+		\item Input string $x\in\set{0, 1}^n$
+		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates
+	\end{itemize}
+
+	Ingrediants:
+	\begin{itemize}
+		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
+		\item Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}.
+		\item $\cVGS$ be the way to check said ground state as defined in \Cref{AlgGroundStateCheck}.
+		\item Define $c\in\bbR$ as in \Cref{cor:HamCheck}.
+	\end{itemize}
+
+	Pseudocode:
 	\begin{enumerate}
-		\item The honest prover prepares $M=\varepsilon^{-8}\ln(\frac{T}{\varepsilon})$ copies \Ethan{That isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
-		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\varepsilon^{-3}$, and $k\xleftarrow{\$}[M]\setminus I$.
+		\item The honest prover prepares $M=\frac{T^{20}}{\varepsilon^{32}}\ln(\frac{T}{\varepsilon})$ copies \Ethan{This isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
 			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
@@
 		\end{enumerate}
-			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\varepsilon m$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
+			Let $Z=\sum_{i\in I} z_i$.
+If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ then the verifier accepts and outputs $y$.
+Otherwise, it rejects.
 	\end{enumerate}
@@
 
-Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise. We now show the completeness and soundness of $\PiSamp$.
+Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
+It is easy to see $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
+We now show its completeness and soundness.
 
@@
 	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
-	So we can apply the Chernoff bound \cref{thm:Chernoff} with $\mu=\frac{m}{2}$ and $\delta=2\varepsilon$ to get
+	So we can apply Chernoff bound (\Cref{thm:Chernoff}) with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
 	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$
@@
 	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ such that for all quantum-classical channels $\Lambda_i$ on $\abs{A}$ qubits:
-	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}=\frac{todo}{todo}=O(\varepsilon).$$
+	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
+	\leq\sqrt{\frac{2m^2\ln\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
+	=O(\varepsilon).$$
 
-	Now we separate the $\rho_j$ into two categories: $J=\set{j\in I|p_j=\cV_\GS(\rho_j)<\frac{1}{2}-2\varepsilon}$ and its complement.
+	Now we separate the $\rho_j$ into two categories base on $p_j$, the accept probability of $\cVGS(\rho_j)$:
+	$$J=\set{j\in I|p_j<\frac{1}{2}-2\kappa}$$
 
@@
 	hence incurs negligible soundness errors.
-	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2h$,
-	then clearly $\Prob{Z\geq\frac{m}{2}-hm}<\Prob{Y\geq\frac{m}{2}-hm}$.
+	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2\kappa$,
+	then clearly $\Prob{Z\geq\frac{m}{2}-\kappa m}<\Prob{Y\geq\frac{m}{2}-\kappa m}$.
 	By Chernoff bound, we have
-	$$\Prob{Y\geq\frac{m}{2}-hm}=\Prob{Y-\mu\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
-	where $\mu=mp_y=\frac{m}{2}-2hm$ and $\delta=\frac{2h}{1-4h}$.
+	$$\Prob{Y\geq\frac{m}{2}-\kappa m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1})$$
+	where $\mu=mp_y=\frac{m}{2}-2\kappa m$ and $\delta=\frac{2\kappa}{1-4\kappa}$.
 	Summing up all the $\rho_j$ terms in $J$, we have
@@
 
-	Now, for the other case, $j\notin J$, we have
-	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2\varepsilon\Rightarrow\sqrt{\tr\left(H_{C'(x)}\rho_j}\right)<\varepsilon.$$
-	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{Need notation for fidelity}
-	$$D(\rho_j, \ket{\phi_{C'(x)}})<\poly(\varepsilon)$$
+	Now, for the other case, $j\notin J$, by \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
+	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq\varepsilon^2.$$
+	which in turn implies a lower bound on the respective trace distance:
+	$$T(\rho_j, \ket{\psi_{C'(x)}})<\varepsilon.$$
 
@@
 
-	The soundness errors at each step is $\poly(\varepsilon)$, so the conclusion follows.
+	The soundness errors at each step is $O(\varepsilon)$, so the conclusion follows.
 \end{prf}

### 2020-03-29 hamiltonian.tex
Get ready for next round of feedbacks
Make V_Ham fidelity lemma work for mixed states

@@
 			\item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
-			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept. Otherwise, reject.
+			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept by outputting $1$. Otherwise, reject by outputting $0$.
 		\end{itemize}
@@
 	$\varepsilon\in\bbR$, then
-	if $\cVGS$ accepts $\rho$ with probability at least $\frac{1}{2}-\frac{c\varepsilon}{T^5}$
-	then $F(\rho, \psi_{C(x)})\geq1-\varepsilon$
+	if $\cVGS(\rho)$ accepts with probability at least $\frac{1}{2}-\frac{c\varepsilon}{T^5}$
+	then $F(\rho, \ket{\psi_{C(x)}})\geq1-\varepsilon$
 \end{cor}
 \begin{prf}
+	We first argue this with pure state input $\ket\phi$.
+
 	Define $c$ so that $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{c}{T^5}\braket{\phi|H_{C(x)}|\phi}$.
-
-	Break $\ket{\phi}$ above into what's in the kernel of $H$ and what isn't.
+	Break $\ket{\phi}$ above into what's in the kernel of $H$ and what isn't:
 	$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
-	We can then see $\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\psi_{C(x)}, \phi)$.
-
+	We can then see $\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$.
+	This argument above can be generalized for mixed states since we have for all $\sigma$ that
+	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \sigma)=\sum_i p_i F(\ket{\phi_i}, \sigma)$$
 	Now we have
-	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\psi_{C(x)}, \phi))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
-	which easily implies our claim for pure state inputs $\phi$.
-
-	The argument generalizes easily to mixed state inputs $\rho$.
+	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
+	which implies our claim.
 \end{prf}

### 2020-03-29 hamiltonian.tex
Fix bug

@@
 	We can then see $\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$.
-	This argument above can be generalized for mixed states since we have for all $\sigma$ that
-	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \sigma)=\sum_i p_i F(\ket{\phi_i}, \sigma)$$
+	This argument above can be generalized for mixed states since we have for all $\ket\psi$ that
+	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \ket\psi)=\sum_i p_i F(\ket{\phi_i}, \ket\psi)$$
 	Now we have

### 2020-03-30 hamiltonian.tex
Clarify wording

--- 2020-03-29 hamiltonian.tex
@@
 	$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
-	We can then see $\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$.
-	This argument above can be generalized for mixed states since we have for all $\sigma$ that
-	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \sigma)=\sum_i p_i F(\ket{\phi_i}, \sigma)$$
-	Now we have
+	We can then see
+	$$\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$$
+	which can be generalized for mixed states since we have for all $\ket\psi$ that
+	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \ket\psi)=\sum_i p_i F(\ket{\phi_i}, \ket\psi).$$
+	As a result, we have
 	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$

### 2020-03-30 qpip.tex
Add discussion notes

@@
 We start with a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$ and an input $x$,
-then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy.
+then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy. \Ethan{Define some kinda $\varepsilon_0$ for this}
 We assume without loss of generality that $C$ comprises of only Hadamard and Toffoli gates.
@@
 		\item Input string $x\in\set{0, 1}^n$
-		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates
+		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates \Ethan{move this into ingredients and put SampBQP instance as inputs}
 	\end{itemize}
@@
 		\item Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}.
-		\item $\cVGS$ be the way to check said ground state as defined in \Cref{AlgGroundStateCheck}.
-		\item Define $c\in\bbR$ as in \Cref{cor:HamCheck}.
+\Ethan{Also bring $H_C$ in.
+More descriptions.
+Make it more intuitive.}
+		\item $\cVGS$ be the way to check said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix}
+		\item Define $c\in\bbR$ as in \Cref{cor:HamCheck}. \Ethan{Just make sure it's less than 10 and write 10. Also it shouldn't be an ingredient if it's $c$}
 	\end{itemize}
 
-	Pseudocode:
+	Protocol:
 	\begin{enumerate}
-		\item The honest prover prepares $M=\frac{T^{20}}{\varepsilon^{32}}\ln(\frac{T}{\varepsilon})$ copies \Ethan{This isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item The honest prover prepares $M=\frac{T^{20}}{\varepsilon^{32}}\ln(\frac{T}{\varepsilon})$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
 		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
@@
 			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
-			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ and save the outcome as $y$.
+			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $y$.
 			\item Else, discard $\rho_i$.
@@
 
-Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
+Note that $\VSamp$ \Ethan{TODO Define this} only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
 It is easy to see $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and $\poly(\varepsilon^{-1})$ soundness error.
+	$\PiSamp$ has negligible completeness error and $O(\varepsilon)$ soundness error.
 \end{thm}
@@
 	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
-	So we can apply Chernoff bound (\Cref{thm:Chernoff}) with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
+	So we can apply Chernoff bound (\Cref{thm:Chernoff}) \Ethan{Theorem numbering needs fix} with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
 	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$
@@
 	The first step of our analysis is to use de Finetti's theorem.
-	Randomly picking $m+1$ out of $M$ registers is equivalent to first applying a random permutation to get some $\sigma'$ then taking the first $m+1$ registers.
+	Randomly picking $m+1$ out of $M$ registers is equivalent to first applying a random permutation then taking the first $m+1$ registers.
 	A random permutation, in turn, is a classical mix over all possible permutations:
@@
 	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
-	Note that the ground state has $\abs{A}=n+T+\frac{T}{e}$ qubits.
-	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ such that for all quantum-classical channels $\Lambda_i$ on $\abs{A}$ qubits:
+	Note that the ground state has $\abs{A}=n+T+\frac{T}{\varepsilon}$ qubits.
+	\Ethan{Think about notation... maybe $s$? typeof($A$) is strange. Also an error here.}
+	That is, \Ethan{type out ``there exists" if in sentence} $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$
+	\Ethan{multiple copies to one copy? Say in words that rho j is one component of iids}
+	such that for all quantum-classical channels $\Lambda_i$ on $\abs{A}$ qubits:
 	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
@@
 
-	Now we separate the $\rho_j$ into two categories base on $p_j$, the accept probability of $\cVGS(\rho_j)$:
-	$$J=\set{j\in I|p_j<\frac{1}{2}-2\kappa}$$
+	\Ethan{In our context, lambda i is ground state check... etc. and rho 1 rho 2 are...}
+
+	Now we separate the $\rho_j$ into two categories base on $p_j$, the accept probability of $\cVGS(\rho_j)$: \Ethan{Wording issue; make it obvious I'm defining $p_j$}
+	$$J=\set{j\in\bbN|p_j<\frac{1}{2}-2\kappa}$$
+
+	\Ethan{Definition of $J$ is extraneous; just cut into two cases.}
 
@@
 	hence incurs negligible soundness errors.
+	\Ethan{Delete the following and just say it's standard application of Chernoff bound}
 	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2\kappa$,
@@
 
+    \Ethan{Fix the kets}
+
 	Now, for the other case, $j\notin J$, by \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
-	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq\varepsilon^2.$$
+	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq1-\varepsilon^2.$$
 	which in turn implies a lower bound on the respective trace distance:
 	$$T(\rho_j, \ket{\psi_{C'(x)}})<\varepsilon.$$
+	\Ethan{Trace distance notation}
 
 	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $\poly(\varepsilon)$ due to the padding,
-	so the data register has $1-\poly(\varepsilon)$ probability to be $C(x)$ at this point.
+	so the data register has $1-\poly(\varepsilon)$ probability to be $C(x)$ at this point. \Ethan{get rid of the remaining polys}
 
 	The soundness errors at each step is $O(\varepsilon)$, so the conclusion follows.
+	\Ethan{Be more careful here. Actually sum up errors.}
 \end{prf}

### 2020-03-31 preliminaries.tex
Get ready for next round of feedbacks
Start implementing suggestions from discussion

@@
 We write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.
+We write $T(\rho_1, \rho_2)=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$.
+$\forall \rho_1, \rho_2\in\cB^{\otimes N}$ we have $T(\rho_1, \rho_2)\leq\sqrt{1-F(\rho_1, \rho_2)}$.
 
@@
 De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
-There are many formulations; we use the one from \cite{Brandão2017} because we need logarithmic dependence on $|A|$.
+There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on number of qubits in each subsystem.
 \begin{thm}
 	\label{deFinetti}
-	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
-	$$\max_{\Lambda_1,\ldots,\Lambda_l}\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
+	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state on registers $A_1,\ldots,A_k$ where each register is $s$ qubits,
+	then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
+	$$\max_{\Lambda_1,\ldots,\Lambda_l}
+	\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1
+	\leq\sqrt{\frac{2l^2s}{k-l}}$$
 	where $\Lambda_i$ are quantum-classical channels.

### 2020-03-31 qpip.tex
Start implementing suggestions from discussion

@@
 
-\Ethan{Again, look at other papers...}
-
-\Ethan{get style from pg 22 on other paper}
-
-\Ethan{Also see 102, p2, 5}
-
-\Ethan{201 p12 p23 two different styles of protocol-writing}
-
-\Ethan{106 p31}
+\Ethan{Actual technical part starts here}
 
@@
 
-\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for the computation $C(x)$ with error parameter $\varepsilon$}
+\begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for the computation $C(x)$ with error parameter $\varepsilon$}
 	\label{ProtoQPIP1}
@@
 	\begin{enumerate}
-		\item The honest prover prepares $M=\frac{T^{20}}{\varepsilon^{32}}\ln(\frac{T}{\varepsilon})$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item The honest prover prepares $M=\frac{T^{21}}{\varepsilon^{33}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
 		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
@@
 
-Note that $\VSamp$ \Ethan{TODO Define this} only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
-It is easy to see $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
+Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
+It is simple to check that $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
 We now show its completeness and soundness.
@@
 	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
-	Note that the ground state has $\abs{A}=n+T+\frac{T}{\varepsilon}$ qubits.
 	\Ethan{Think about notation... maybe $s$? typeof($A$) is strange. Also an error here.}
-	That is, \Ethan{type out ``there exists" if in sentence} $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$
+	That is, there exists some $\rho=\sum_j w_j\rho_j^{\otimes m+1}$
 	\Ethan{multiple copies to one copy? Say in words that rho j is one component of iids}
-	such that for all quantum-classical channels $\Lambda_i$ on $\abs{A}$ qubits:
+	such that for all quantum-classical channels $\Lambda_i$ on $n+T+\frac{T}{\varepsilon}$ qubits:
 	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
-	\leq\sqrt{\frac{2m^2\ln\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
+	\leq\sqrt{\frac{2m^2\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
 	=O(\varepsilon).$$
@@
 
-	Now we separate the $\rho_j$ into two categories base on $p_j$, the accept probability of $\cVGS(\rho_j)$: \Ethan{Wording issue; make it obvious I'm defining $p_j$}
-	$$J=\set{j\in\bbN|p_j<\frac{1}{2}-2\kappa}$$
+	Let $p_j$ be the probability that $\cVGS(\rho_j)=acc$. Now we seperate the $\rho_j$ terms into two categories based on $p_j$.
 
-	\Ethan{Definition of $J$ is extraneous; just cut into two cases.}
-
-	First suppose $j\in J$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
+	First suppose $p_j<\frac{1}{2}-2\kappa$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
 	hence incurs negligible soundness errors.

### 2020-03-31 qpip0.tex
Flag typo

@@
 where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
+\Ethan{Typo on line 3?}
 \end{proof}
@@
 $$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$ 
-where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin probabilities.
+	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin \Ethan{Typo} probabilities.
 Note that $z$ is "sub-normalized", i.e.
@@
 
- where we omitted writing out $e_i$ starting the second line.  We have
+ where we omitted writing out $e_i$ starting the second line.  We have \Ethan{$\ket{z}\bra{z}$?}
 \begin{align} \label{eq:zi-zgoodi}

### 2020-04-03 qpip.tex
Fix bug

@@
 	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
-	\Ethan{Think about notation... maybe $s$? typeof($A$) is strange. Also an error here.}
 	That is, there exists some $\rho=\sum_j w_j\rho_j^{\otimes m+1}$
@@
 
-	First suppose $p_j<\frac{1}{2}-2\kappa$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
+	First suppose $p_j<\frac{1}{2}-2\kappa$,
+	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities,
 	hence incurs negligible soundness errors.
-	\Ethan{Delete the following and just say it's standard application of Chernoff bound}
-	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2\kappa$,
-	then clearly $\Prob{Z\geq\frac{m}{2}-\kappa m}<\Prob{Y\geq\frac{m}{2}-\kappa m}$.
-	By Chernoff bound, we have
-	$$\Prob{Y\geq\frac{m}{2}-\kappa m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1})$$
-	where $\mu=mp_y=\frac{m}{2}-2\kappa m$ and $\delta=\frac{2\kappa}{1-4\kappa}$.
-	Summing up all the $\rho_j$ terms in $J$, we have
-	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda).$$
 
@@
 
-	Now, for the other case, $j\notin J$, by \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
+	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
+	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
 	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq1-\varepsilon^2.$$
@@
 
-	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $\poly(\varepsilon)$ due to the padding,
-	so the data register has $1-\poly(\varepsilon)$ probability to be $C(x)$ at this point. \Ethan{get rid of the remaining polys}
+	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $O(\varepsilon)$ due to the padding,
+	so the data register has $1-O(\varepsilon)$ probability to be $C(x)$ at this point.
 

### 2020-04-03 qpip0.tex
Flag typo
Updates from Overleaf

--- 2020-03-18 qpip0.tex
@@
 
-For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for Protocol~\ref{proto:urmila4}: on the second round, the prover start with picking a uniformaly random $i\in [m]$.
+For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for Protocol~\ref{proto:urmila4}: on the first round the verifier pick $h$ from distribution specified by ????
+of Protocol~\ref{ProtoQPIP1}.
+On the second round, the prover start with picking a uniformaly random $i\in [m]$.
 The prover then tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
@@
 
-Putting together Equation~\ref{eq:z-z-good2}\ref{eq:z-good-rho}\ref{eq:rho-c}, and Remark~\ref{rmk:trace-to-comp} and Lemma~\ref{lem:computational-triangle0}, we have  
+Putting together Equation~\ref{eq:z-z-good2} \ref{eq:z-good-rho} \ref{eq:rho-c},  Remark~\ref{rmk:trace-to-comp}, and Lemma~\ref{lem:computational-triangle0}, we have  
 \begin{align}

### 2020-04-04 qpip.tex
Change notation for trace distance

@@
 	which in turn implies a lower bound on the respective trace distance:
-	$$T(\rho_j, \ket{\psi_{C'(x)}})<\varepsilon.$$
+	$$\frac{1}{2}\norm{\rho_j - \ket{\psi_{C'(x)}}}_1<\varepsilon.$$
 	\Ethan{Trace distance notation}

### 2020-04-05 qpip.tex
Implement a couple more suggestions

@@
 
-We start with a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$ and an input $x$,
-then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy. \Ethan{Define some kinda $\varepsilon_0$ for this}
-We assume without loss of generality that $C$ comprises of only Hadamard and Toffoli gates.
-We present our protocol that allows a client to verifiably obtain the measurement outcome of $C(x)$.
-
-\begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for the computation $C(x)$ with error parameter $\varepsilon$}
+\begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for $\SampBQP$}
 	\label{ProtoQPIP1}
@@
 	\begin{itemize}
+		\item $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$
+		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
 		\item Error parameter $\varepsilon\in(0, 1)$
-		\item Input string $x\in\set{0, 1}^n$
-		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates \Ethan{move this into ingredients and put SampBQP instance as inputs}
 	\end{itemize}
@@
 	\begin{itemize}
+		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates \Ethan{Something about $\varepsilon_0$?}
 		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
@@
 		\item $\cVGS$ be the way to check said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix}
-		\item Define $c\in\bbR$ as in \Cref{cor:HamCheck}. \Ethan{Just make sure it's less than 10 and write 10. Also it shouldn't be an ingredient if it's $c$}
 	\end{itemize}
@@
 			Let $Z=\sum_{i\in I} z_i$.
-If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ then the verifier accepts and outputs $y$.
+If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ as in \Cref{cor:HamCheck} then the verifier accepts and outputs $y$.
 Otherwise, it rejects.
@@
 \end{prf}
+\begin{cor}
+	By choosing $\tilde{\varepsilon}=O(\varepsilon)$ accordingly, $\PiSamp$ has $\tilde\varepsilon$ soundness error.
+In which case, it runs in $\poly(T, \tilde\varepsilon^{-1})$ time, and has negligible completeness errors.
+\end{cor}

### 2020-04-05 preliminaries.tex
Fix bug
Change notation for trace distance
Fix definition of protocols for sampling problems

@@
 We write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.
-We write $T(\rho_1, \rho_2)=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$.
-$\forall \rho_1, \rho_2\in\cB^{\otimes N}$ we have $T(\rho_1, \rho_2)\leq\sqrt{1-F(\rho_1, \rho_2)}$.
+We write $\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$.
+$\forall \rho_1, \rho_2\in\cB^{\otimes N}$ we have $\frac{1}{2}\norm{\rho_1-\rho_2}_1\leq\sqrt{1-F(\rho_1, \rho_2)}$.
 
@@
 
+\begin{definition}
+	We say $\Pi=(P, V)(x)$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and soundness error $s$ if
+	\begin{itemize}
+		\item Let $(d, z)\leftarrow(P, V)(x)$. Then $d=rej$ with probability at most $c$.
+		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$. Let $z_{ideal}\leftarrow D_x$ if $d=acc$, else $z_{ideal}=\bot$. Then $\norm{(d, z) - (d, z_{ideal})} \leq s$.
+	\end{itemize}
+\end{definition}
+
 \subsection{Quantum Prover Interactive Protocol (QPIP)}
@@
 \begin{definition}
-	A sampling problem $S=(D_x)_{x\in\set{0, 1}^*}$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a protocol $(\bbP, \bbV)$ with the following properties with input $x$:
+	A sampling problem $S=(D_x)_{x\in\set{0, 1}^*}$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $s$ if there exists a protocol $(\bbP, \bbV)(x)$ for $S$ with the following properties:
 	\begin{itemize}
@@
 		\item There is also a classical communication channel between the prover and the verifier, which can transmit $\poly(\abs{x})$ many bits to either direction. 
-		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
-		\item (Soundness) Define the ideal output distribution $D_{x, \alpha}$ as first flipping a weighted coin with head probability $\alpha$.
-On head, output $\bot$.
-On tail, sample and output from $D_x$.
-			Then the protocol is sound if for all cheating prover $\bbP^*$, there exists $\alpha$ so that the output distribution of $(\bbP^*, \bbV)$ is negligibly close to $D_{x, \alpha}$.
 	\end{itemize}
@@
 
-\begin{theorem}
+\begin{thm}
 \label{thm:Chernoff}
@@
 $$P[\abs{X-\mu}\geq\delta\mu]\leq2e^{-\frac{\mu\delta^2}{3}}$$
-\end{theorem}
+\end{thm}
 

### 2020-04-05 qpip.tex
Implement a couple more suggestions

@@
 
-\begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for $\SampBQP$}
+\begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for the $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$}
 	\label{ProtoQPIP1}
 
-	Inputs:
+	Inputs: \Ethan{Should the $\SampBQP$ instance be an input?}
 	\begin{itemize}
-		\item $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$
 		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
@@
 	\begin{itemize}
-		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates \Ethan{Something about $\varepsilon_0$?}
+		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
 		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
-		\item Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}.
-\Ethan{Also bring $H_C$ in.
-More descriptions.
-Make it more intuitive.}
-		\item $\cVGS$ be the way to check said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix}
+		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
+		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
+		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
 	\end{itemize}
@@
 
-    \Ethan{Fix the kets}
+    \Ethan{TODO Fix the kets}
 
@@
 	$$\frac{1}{2}\norm{\rho_j - \ket{\psi_{C'(x)}}}_1<\varepsilon.$$
-	\Ethan{Trace distance notation}
 
@@
 \end{prf}
-\begin{cor}
-	By choosing $\tilde{\varepsilon}=O(\varepsilon)$ accordingly, $\PiSamp$ has $\tilde\varepsilon$ soundness error.
-In which case, it runs in $\poly(T, \tilde\varepsilon^{-1})$ time, and has negligible completeness errors.
-\end{cor}

### 2020-04-05 preliminaries.tex
Fix definition environment

@@
 
-\begin{dfn}
+\begin{definition}
 	Let $\lambda$ be a security parameter.
@@
 	Then it is IND-CPA secure if $\forall x\in\set{0,1}^n$ no polynomial time adversary $\cA$ can win \protoref{indcpa} with probability better than $\frac{1}{2}+\negl(\lambda)$
-\end{dfn}
+\end{definition}
 
@@
 We start by presenting the interface of a homomorphic encryption scheme:
-\begin{dfn}
+\begin{definition}
 	A leveled homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
@@
 	\end{itemize}
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn}
+\begin{definition}
 	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
@@
 	where $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
-\end{dfn}
+\end{definition}
 

### 2020-04-05 qpip.tex
Remove another done author note

@@
 	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
-	So we can apply Chernoff bound (\Cref{thm:Chernoff}) \Ethan{Theorem numbering needs fix} with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
+	So we can apply Chernoff bound (\Cref{thm:Chernoff}) with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
 	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$

### 2020-04-06 qpip.tex
Add Overleaf Changes
Fix bug

@@
 			Let $Z=\sum_{i\in I} z_i$.
-If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ as in \Cref{cor:HamCheck} then the verifier accepts and outputs $y$.
-Otherwise, it rejects.
+If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ as in \Cref{cor:HamCheck} then the verifier outputs $(acc, y)$.
+Else, it outputs $(rej, \bot)$.
 	\end{enumerate}
@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and $O(\varepsilon)$ soundness error.
+	$\PiSamp$ has negligible completeness error and $O(\varepsilon)$ soundness error. \hannote{remind completeness and soundness with a footnote.}
 \end{thm}

### 2020-04-07 qpip.tex
Add clarification
Add details for SampBQP soundness proof

@@
 We now show its completeness and soundness.
+Particularly, we prove that it has $O(\varepsilon)$ soundness errors
+with the understanding that by relabelling $\varepsilon'=O(\varepsilon)$ and modifying $\PiSamp$ accordingly,
+one can achieve $\varepsilon'$ soundness errors while maintaining completeness and running time properties.
 
@@
 	Now we show soundness.
+
 	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier.
@@
 
-	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
-	That is, there exists some $\rho=\sum_j w_j\rho_j^{\otimes m+1}$
-	\Ethan{multiple copies to one copy? Say in words that rho j is one component of iids}
-	such that for all quantum-classical channels $\Lambda_i$ on $n+T+\frac{T}{\varepsilon}$ qubits:
+	\Ethan{Trace out discarded copy on $\sigma'$? Or add copies on $\tau$?}
+
+	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $M$-fold tensor products of identical copies of some states $\tau_j$.
+	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes M}$
+	such that for all quantum-classical channels $\Lambda_i$ acting on registers with size of $\ket{\psi_{C'(x)}}$:
 	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
@@
 	=O(\varepsilon).$$
+	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
+	$\Lambda_{m+1}$ is measurement on the data register of $\rho_k$.
 
-	\Ethan{In our context, lambda i is ground state check... etc. and rho 1 rho 2 are...}
-
-	Let $p_j$ be the probability that $\cVGS(\rho_j)=acc$. Now we seperate the $\rho_j$ terms into two categories based on $p_j$.
+	Now we claim that for each component $\tau_j$,
+	if $\PSampstar$ had sent $\tau_j^{\otimes M}$ instead then the soundness error is $O(\varepsilon)$.
+	Let $p_j$ be the probability that $\cVGS(\tau_j)=acc$, we seperate $\tau_j$ terms into two cases.
 
 	First suppose $p_j<\frac{1}{2}-2\kappa$,
-	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities,
-	hence incurs negligible soundness errors.
-
-    \Ethan{TODO Fix the kets}
+	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities.
+	That is, it outputs $(rej, \bot)$ with overwhelming probability, hence has negligible soundness errors.
 
 	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
-	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
-	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq1-\varepsilon^2.$$
+	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\tau_j$ and $\ket{\psi_{C'(x)}}$:
+	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\tau_j, \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}})\geq1-\varepsilon^2.$$
 	which in turn implies a lower bound on the respective trace distance:
-	$$\frac{1}{2}\norm{\rho_j - \ket{\psi_{C'(x)}}}_1<\varepsilon.$$
+	$$\frac{1}{2}\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_1<\varepsilon.$$
+	Let $(d, y)$ be $\VSamp$'s output. Suppose $d=acc$, then $y$ would be the measurement on $\tau_j$'s data register,
+	which is $\varepsilon$-close to that on $\ket{\psi_{C'(x)}}$.
+	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has $1-\varepsilon$ probability to contain $C(x)$ due to the padding.
+	So $y$ is $O(\varepsilon)$-close to $y_{ideal}$ when $d=acc$.
+	Which implies that $(d, y)$ is $O(\varepsilon)$-close to $(d, y_{ideal})$.
 
-	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $O(\varepsilon)$ due to the padding,
-	so the data register has $1-O(\varepsilon)$ probability to be $C(x)$ at this point.
-
-	The soundness errors at each step is $O(\varepsilon)$, so the conclusion follows.
-	\Ethan{Be more careful here. Actually sum up errors.}
+	The cheating prover's strategies corresponding to $\tau_j$ all have $O(\varepsilon)$ soundness errors.
+	As $\rho$ is a convex combination of these strategies, we conclude the same about it.
+	Finally, as the outputs corresponding to $\sigma$ is $\varepsilon$-close to that of some $\rho$,
+	by data processing inequality we conclude that $\PiSamp$ has $O(\varepsilon)$ soundness errors.
 \end{prf}

### 2020-04-07 blind.tex
Move blindness compiler to the end
Add discussion notes

@@
 \label{sec:BlindBQP2}
-
-\def\HE{\mathsf{HE}}
-\def\HGen{\mathsf{HE.Keygen}}
-\def\HEnc{\mathsf{HE.Enc}}
-\def\HEval{\mathsf{HE.Eval}}
-\def\HDec{\mathsf{HE.Dec}}
-
-\def\blind{\mathsf{blind}}
-\nc{\Piblind}{\ensuremath{\Pi_\blind}}
-\nc{\Vblind}{\ensuremath{V_\blind}}
-\nc{\Pblind}{\ensuremath{P_\blind}}
-\nc{\Pblindstar}{\ensuremath{P_\blind^*}}
-\nc{\cVblind}[1]{\ensuremath{\cV_{\blind,#1}}}
-\nc{\cPblind}[1]{\ensuremath{\cP_{\blind,#1}}}
-\def\Pstar{P^*}
-\nc{\cPstar}[1]{\ensuremath{\cP^*_{#1}}}
-\nc{\ctx}[3]{\ensuremath{{{\widehat{#1}}_{#2}^{(#3)}}}}
 
@@
 				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc(pk_t, \ctx{st}{P, t-1}{t-1}))$,
-				then homomorphically decrypts the old encryption by
-				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
+				then homomorphically decrypts the old encryption by \linebreak
+				$$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t}).$$
 				Then it applies the next-message function homomorphically, generating

### 2020-04-07 preliminaries.tex
Add discussion notes

@@
 Let $\mathcal{B}$ be the Hilbert space corresponding to one qubit.
-Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian matrices.
+Let $H:\mathcal{B}^{\otimes n}\rightarrow\mathcal{B}^{\otimes n}$ be Hermitian matrices.
 We use $H\geq0$ to denote $H$ being positive semidefinite.
@@
 We write $\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$.
-$\forall \rho_1, \rho_2\in\cB^{\otimes N}$ we have $\frac{1}{2}\norm{\rho_1-\rho_2}_1\leq\sqrt{1-F(\rho_1, \rho_2)}$.
+For all $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$ we have $\frac{1}{2}\norm{\rho_1-\rho_2}_1\leq\sqrt{1-F(\rho_1, \rho_2)}$.
 
@@
 	$\BQP$ is the class of languages $L$ for which for all $n\in\bbN$ there exists a quantum circuit constructible in time $\poly(n)$ that, given any $x\in\set{0, 1}^n$ as input, correctly decides whether $x\in L$ at least $\frac{2}{3}$ of the time.
+	\Ethan{Just copy this from somewhere}
 \end{definition}
@@
 	A function $f:\set{0,1}^*\rightarrow\set{0,1}^*$ is in $\FBQP$ if there is a $\BQP$ machine that, $\forall x$, outputs $f(x)$ with overwhelming probability.
+	\Ethan{Need to be more formal. Also should be efficient verifiable}
 \end{definition}
@@
 
-\begin{definition}
-	We say $\Pi=(P, V)(x)$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and soundness error $s$ if
-	\begin{itemize}
-		\item Let $(d, z)\leftarrow(P, V)(x)$. Then $d=rej$ with probability at most $c$.
-		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$. Let $z_{ideal}\leftarrow D_x$ if $d=acc$, else $z_{ideal}=\bot$. Then $\norm{(d, z) - (d, z_{ideal})} \leq s$.
-	\end{itemize}
-\end{definition}
-
 \subsection{Quantum Prover Interactive Protocol (QPIP)}
@@
 \begin{definition}
-	A sampling problem $S=(D_x)_{x\in\set{0, 1}^*}$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $s$ if there exists a protocol $(\bbP, \bbV)(x)$ for $S$ with the following properties:
+	We say $\Pi=(P, V)(x)$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and soundness error $s$ \Ethan{Might need these to be functions of $\abs{x}$} if
+	\Ethan{Look up ``interactive protocols for BQP". Right now it's missing quantifier for all x. Also need to mention d is decision bit; maybe do that in next definition and swap locations}
+	\begin{itemize}
+		\item Let $(d, z)\leftarrow(P, V)(x)$. Then $d=rej$ with probability at most $c$.
+		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.
+Let \Ethan{Use display math to make it obvious I'm defining this} $z_{ideal}\leftarrow D_x$ if $d=acc$, else $z_{ideal}=\bot$.
+Then $\norm{(d, z) - (d, z_{ideal})} \leq s$ \Ethan{make stat.
+distance notation consistent}.
+	\end{itemize}
+\end{definition}
+
+\Ethan{Acc, rej, P, V fonts}
+
+\Ethan{Might need to write our own def. here}
+
+\Ethan{Look at thesis for this}
+
+\begin{definition}
+	A sampling problem $S=(D_x)_{x\in\set{0, 1}^*}$ is said to be \Ethan{Try to make this more general; remove mentions of sampling/decision problems} in $\QPIP_\tau$ with completeness $c$ and soundness $s$ \Ethan{Don't tie this with completeness and soundness yet} if there exists a protocol $(\bbP, \bbV)(x)$ for $S$ with the following properties:
 	\begin{itemize}
@@
 
+\Ethan{Two separate definitions for comp and soundness}
+
+\Ethan{Soundness?}
+
 \subsection{Semantic security for interactive protocols}
 \Ethan{Just call this blindness and put this under interactive protocols}
+
+\Ethan{See Thomas' paper if he defined this}
 
@@
 \begin{definition}
-	A leveled homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
+	A leveled homomophic encryption scheme is tuple of algorithms \linebreak $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
 	\begin{itemize}

### 2020-04-08 preliminaries.tex
Add BQP alternative dfn

@@
 \begin{definition} [$\BQP$]
+	Definition from Kitaev:
+	A \emph{quantum algorithm} for the computation of a function $F:\zo^*\rightarrow\zo^*$ is a classical algorithm (i.e., a Turing machine) that computes a function of the form $x\mapstochar\rightarrow Z(x)$, where $Z(x)$ is a description of a quantum circuit which computes $F(x)$ on empty input.
+The function $F$ is said to belong to class $\BQP$ if there is a quantum algorithm that computes $F$ in time $\poly(n)$.
+
+	Definition from Complexity Zoo:
 	$\BQP$ is the class of languages $L$ for which for all $n\in\bbN$ there exists a quantum circuit constructible in time $\poly(n)$ that, given any $x\in\set{0, 1}^n$ as input, correctly decides whether $x\in L$ at least $\frac{2}{3}$ of the time.
-	\Ethan{Just copy this from somewhere}
+	\Ethan{Just copy this from somewhere... Does anyone even define this?}
 \end{definition}

### 2020-04-09 paper.tex
Change TODOs to note macros
Fix affliation
Work on new definitions
Add QPIP section
Remove delegation section
Dark mode
Implement some suggestions from Dr. Chung
Use dark mode again
Add section on privacy
Add discussion results
Split protocol into two sections
Change "private" to "blind"
Add blind BQP section
Updates from Overleaf
Make flow of blind then fully classical consistent
Make editorial changes
Editorial and macros change
Get lncs to compile
Fix lncs theorem numbering
Fix lncs page numbering
Add more Skype discussion notes
Start writing FBQP
Change autoref to cref
Fix amsmath warning

@@
-\documentclass{article}
+\documentclass[11pt]{article}
 \usepackage{authblk}
+%\pagestyle{plain}
+
 \usepackage{amsmath, amssymb, amsthm}
@@
 \usepackage{algpseudocode}
+\usepackage[margin=1in]{geometry}
 \newcommand{\sgn}{\operatorname{sgn}}
@@
 \usepackage{hyperref}
-\newcommand{\algorithmautorefname}{Algorithm}
 \apptocmd{\thebibliography}{\raggedright}{}{}
 \usepackage{cite,color,float}
+\usepackage{mdframed} 
+\usepackage{cleveref}
+\crefname{protocol}{protocol}{protocols}
+\Crefname{protocol}{Protocol}{Protocols}
+\crefname{thm}{theorem}{theorems}
+\Crefname{thm}{Theorem}{Theorems}
+\crefname{rmk}{remark}{remarks}
+\Crefname{rmk}{Remark}{Remarks}
+\crefname{lem}{lemma}{lemmata}
+\Crefname{lem}{Lemma}{Lemmata}
+
+%*************************************page layout****************************
+\setlength{\textheight}{9in}
+\setlength{\columnsep}{2.0pc}
+\setlength{\textwidth}{6.5in}
+\setlength{\topmargin}{0in}
+\setlength{\headheight}{0ex}
+\setlength{\hoffset}{0in}
+\setlength{\headsep}{0.0in}
+\setlength{\oddsidemargin}{0ex}
+\setlength{\evensidemargin}{0ex}
+\setlength{\parindent}{1pc}
+
+%\pagecolor{black}
+%\color{white}
+
+\newcounter{protocol}
+\newcommand{\linefill}{\rule{\linewidth}{0.8pt}}
+
+\newenvironment{protocol}[1]{\begingroup\setlength\parindent{0pt}\medskip\noindent\linefill\\
+\refstepcounter{protocol}\textbf{Protocol \theprotocol} #1\\\noindent\linefill}
+{\vspace{-\topsep}\noindent\linefill\endgroup}
 
 \newcommand{\KM}[1]{{\footnotesize\color{cyan}[KM: #1]}}
+\newcommand{\Ethan}[1]{{\footnotesize\color{magenta}[Ethan: #1]}}
+\newcommand{\XW}[1]{{\footnotesize\color{red}[XW: #1]}}
 
-\newtheorem{theorem}{Theorem}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{observation}[theorem]{Observation}
+\title{Constant-round Blind Classical Verification of Quantum Sampling}
 
-\title{Placeholder Title... Something About Delegating Quantum Computations}
-
-\author[1]{Kai-Min Chung}
-\author[2]{Yi Lee}
-\author[3]{Han-Hsuan Lin}
-\author[4]{Xiaodi Wu}
-\affil[1]{Institute of Information Science, Academia Sinica, Taiwan}
-\affil[2]{Department of Physics, National Taiwan University, Taiwan}
+%\iffalse
+\author[1]{Kai-Min Chung\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}.
+Partially supported by the 2019 Academia Sinica Career Development Award under Grant no.
+23-17, and MOST QC project under Grant no.
+MOST 108-2627-E-002-001.}}
+\author[2]{Yi Lee\thanks{\href{mailto:ethanlee515@gmail.com}{ethanlee515@gmail.com}.}}
+\author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.utexas.edu}{linhh@cs.utexas.edu}.}}
+\author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837(CAREER).}}
+\affil[1, 2]{Institute of Information Science, Academia Sinica, Taiwan}
 \affil[3]{Department of Computer Science, University of Texas at Austin, USA}
@@
 }
+%\fi
+%\author{}
+%\institute{}
+
 \input{macros.tex}
+\input{./parallel/macros.tex}
 \begin{document}
@@
 \maketitle
+%\thispagestyle{plain}
 
@@
 
-This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
+In a recent breakthrough, Mahadev constructed a classical verification of quantum computation (CVQC) protocol for a  classical client to delegate decision problems in $\BQP$ to an untrusted quantum prover under computational assumptions.
+In this work, we explore further the feasibility of CVQC with the more general \emph{sampling} problems in BQP and with the desirable \emph{blindness} property.
+We contribute affirmative solutions to both as follows.
+\begin{itemize}
+\item Motivated by the sampling nature of many quantum applications (e.g., quantum algorithms for machine learning and quantum supremacy tasks), we initiate the study of  CVQC for \emph{quantum sampling problems} (denoted by $\SampBQP$).
+Precisely, given an input $x\in \zo^n$ and a quantum circuit $C$, the goal of a classical client is to learn a sample of output $z \leftarrow C(x)$ over $\zo^m$ with the correct distribution up to a small error from an untrusted prover.
+We demonstrate its feasibility by constructing a four-message CVQC protocol for $\SampBQP$ based on the quantum \emph{Learning With Error} assumption.
+\item
+The \emph{blindness} of CVQC protocols refers to a property of the protocol where the prover learns nothing, and hence is blind, about the client's input.
+It is a highly desirable property that has been intensively studied for the delegation of quantum computation.
+Somewhat surprisingly, we provide a simple yet powerful \emph{generic} compiler that transforms any CVQC protocol to a blind one while preserving completeness and soundness errors.  
+\end{itemize}
+Applying our compiler to (a parallel repetition of) Mahadev's protocol for $\BQP$ and our CVQC protocol for $\SampBQP$ yields the first \emph{constant-round} blind CVQC protocol for $\BQP$ and $\SampBQP$ respectively, with negligible completeness and soundness errors.
+
+\vspace{1mm}
+\noindent \textbf{Keywords:} classical delegation of quantum computation, blind quantum computation, quantum sampling problems
+
+\iffalse
+
+\KM{version 2}
+
+In a recent breakthrough, Mahadev constructed a classical verification of quantum computation (CVQC) protocol for a  classical client to delegate \emph{decision problems} in $\BQP$ to an untrusted quantum prover.
+In this work, motivated by the fact that many applications of quantum computations (e.g., in quantum machine learning) are sampling problems, we initiate the study of CVQC for \emph{quantum sampling problems} (denoted by $\SampBQP$), where given an input $x\in \zo^n$, the goal is to learn a sample an output $z \leftarrow C(x)$ over  $\zo^m$ for a quantum circuit $C$ from an untrusted prover with a correct distribution (up to a small error $\eps$).
+
+As our main result, we construct a four-message CVQC protocol for $\SampBQP$ with an arbitrarily small inverse polynomial error $\eps$ based on the quantum learning with error assumption.
+
+\fi
+
+%Following the recent breakthrough of Mahadev, we explore the feasibility of classical verification of quantum computation (CVQC) for a broader class of quantum computation with blindness property.
+
+%This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
 
 \end{abstract}
+
+\newpage
 
@@
 
-\input{delegations}
+% \input{fbqp}
 
-\input{longoutput}
+\input{hamiltonian}
 
-\input{conclusion}
+\input{qpip}
+
+\input{qpip0}
+
+\input{blind}
 

### 2020-04-09 preliminaries.tex
Updates from Overleaf

--- 2020-04-07 preliminaries.tex
@@
 \section{Preliminaries}
+
+\Ethan{Check that the quantifiers are all there}
 
@@
 
+\iffalse
+
 \begin{definition} [$\FBQP$]
@@
 
+\fi
+
 We define search and sampling versions of $\BQP$ based on \cite{aaronson_2013}.
+
+\iffalse
 
@@
 \end{definition}
+
+\fi
 
@@
 \begin{definition}
-	We say $\Pi=(P, V)(x)$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and soundness error $s$ \Ethan{Might need these to be functions of $\abs{x}$} if
+	We say $\Pi=(P, V)$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and soundness error $s$ \Ethan{Might need these to be functions of $\abs{x}$} if
 	\Ethan{Look up ``interactive protocols for BQP". Right now it's missing quantifier for all x. Also need to mention d is decision bit; maybe do that in next definition and swap locations}
@@
 distance notation consistent}.
-	\end{itemize}
+	\end{itemize} \hannote{need computational?}
 \end{definition}
@@
 
-\subsection{Semantic security for interactive protocols}
 \Ethan{Just call this blindness and put this under interactive protocols}
 
-\Ethan{See Thomas' paper if he defined this}
+\Ethan{See Thomas' paper if he defined this. Or actually, see https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf}
 
@@
 \begin{definition}
+    \Ethan{Define this in terms of views instead; see paper linked on Skype}
+
 	Let $\lambda$ be a security parameter.
@@
 \label{thm:Chernoff}
-Let $X=\sum_{i=1}^n X_i$ where $X_i$ are i.i.d. Bernoulli trials, and $\mu=\E[X]$.
+Let $X=\sum_{i=1}^n X_i$ where $X_i$ are i.i.d. \Ethan{Ind. is enough} Bernoulli trials, and $\mu=\E[X]$.
 Then for all $0<\delta<1$,
-$$P[\abs{X-\mu}\geq\delta\mu]\leq2e^{-\frac{\mu\delta^2}{3}}$$
+$$P[\abs{X-\mu}\geq\delta\mu]\leq2e^{-\frac{\mu\delta^2}{3}}.$$
 \end{thm}
@@
 We will instead use the following formulation, which can be obtained by relabeling variables from above.
+
+\Ethan{State 2.3; prove from 2.2 in appendix}
 
@@
 
+\Ethan{Everything gets security param.}
+
 \def\QHE{\mathsf{QHE}}
@@
 $\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
-$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
+$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l))=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
 where $f$ is specified by a circuit of depth at most $L$.
@@
 
-The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitates the use of classical clients:
+The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitate the use of classical clients:
 \begin{itemize}
@@
 \end{itemize}
+
+\Ethan{Reword the above? How? 3rd point can be weakened to can be decrypted classically? Maybe call this ``classical friendly". Mention LWE. There exists a classical friendly... etc.}

### 2020-04-09 qpip.tex
Updates from Overleaf

@@
 		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
-		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
+		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end. \hannote{$T?$}
 		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
@@
 	\begin{enumerate}
-		\item The honest prover prepares $M=\frac{T^{21}}{\varepsilon^{33}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
-		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
+		\item\label{step:qpip1-state-gen} The honest prover prepares $M=\frac{T^{21}}{\varepsilon^{33}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item\label{step:qpip1-verify} The verifier privately samples $I\subset[M]$ s.t.
+$\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
+\hannote{$\xleftarrow{\$}$ ?}
 			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and $O(\varepsilon)$ soundness error. \hannote{remind completeness and soundness with a footnote.}
+	$\PiSamp$ has negligible completeness error and $O(\varepsilon)$ soundness error.
 \end{thm}
@@
 	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$
+
+	\Ethan{Should be negl lambda}
 
@@
 
-	\Ethan{Trace out discarded copy on $\sigma'$? Or add copies on $\tau$?}
+	\Ethan{$\sigma'_{\leq m+1}$ Maybe this notation for traced out state}
 
@@
 	$\Lambda_{m+1}$ is measurement on the data register of $\rho_k$.
+
+	\Ethan{TODO special font for acc/rej}
+
+	\Ethan{Just say what would happen if V accs this instead}
 
@@
 	$$\frac{1}{2}\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_1<\varepsilon.$$
-	Let $(d, y)$ be $\VSamp$'s output. Suppose $d=acc$, then $y$ would be the measurement on $\tau_j$'s data register,
+	Let $(d, y)$ be $\VSamp$'s output \Ethan{on input tau j}. Suppose $d=acc$, then $y$ would be the measurement on $\tau_j$'s data register,
 	which is $\varepsilon$-close to that on $\ket{\psi_{C'(x)}}$.
 	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has $1-\varepsilon$ probability to contain $C(x)$ due to the padding.
-	So $y$ is $O(\varepsilon)$-close to $y_{ideal}$ when $d=acc$.
-	Which implies that $(d, y)$ is $O(\varepsilon)$-close to $(d, y_{ideal})$.
+	So $y$ is $O(\varepsilon)$-close to $y_{ideal}$ when $d=acc$,
+	which implies that $(d, y)$ is $O(\varepsilon)$-close to $(d, y_{ideal})$.
 
 	The cheating prover's strategies corresponding to $\tau_j$ all have $O(\varepsilon)$ soundness errors.
-	As $\rho$ is a convex combination of these strategies, we conclude the same about it.
+	As $\rho$ is a convex combination \Ethan{More equations...} of these strategies, we conclude the same about it.
 	Finally, as the outputs corresponding to $\sigma$ is $\varepsilon$-close to that of some $\rho$,
@@
 \end{prf}
+
+\Ethan{Switch y and z}

### 2020-04-09 qpip0.tex

@@
 \begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
+If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
 \end{lemma}
 
-\begin{rmk}
 Note that even a honest prover has complete freedom in choosing $\rho$, so protocol~\ref{proto:urmila4} didn't make the prover commit to a particular state.
 What it actually does is let the prover commit to a particular $XZ$ measurement on $\rho$.
-This is good enough for our application, since we will feed the $XZ$ measurement results into the verification of $\QPIP_1$ protocol to ensure that the prover pick the history state as $\rho$.
-\end{rmk}
+This is good enough for our application, since we will feed the $XZ$ measurement results into the verification of $\QPIP_1$ protocol to ensure that the prover pick the history state as $\rho$ as we will show next.
+
+We combine the commitment Protocol, Protocol~\ref{proto:urmila4}, and the $\QPIP_1$ Protocol, Protocol~\ref{ProtoQPIP1}, to get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.
+
+\begin{protocol}{naive $\QPIP_0$ protocol  for the $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$}
+	\label{proto:qpip0_naive}
+
+	Inputs: \Ethan{Should the $\SampBQP$ instance be an input?}
+	\begin{itemize}
+		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
+		\item Error parameter $\varepsilon\in(0, 1)$
+	\end{itemize}
+
+ 	Ingrediants:
+ 	\begin{itemize}
+ 		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
+ 		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
+ 		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
+		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
+%  		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
+ 	\end{itemize}
+
+	Protocol:
+	\begin{enumerate}
+	\item The verifier choose a $XZ$-measurement $h$ over  $M=\frac{T^{21}}{\varepsilon^{33}}$  copies of $\ket{\psi_{C'(x)}}$ from the distribution emergent from by Step~\ref{step:qpip1-verify} of Protocol~\ref{ProtoQPIP1}.
+
+	\item The verifier and prover run Protocol~\ref{proto:urmila4}, with the following parameters: $h$ is chosen from previous step, $n_{commit}=M \times$ (number of qubits in $\ket{\psi_{C'(x)}}$), where $n_{commit}$ is the $n$ for Protocol~\ref{proto:urmila4}, and the honest prover choose $M$ copies of $\ket{\psi_{C'(x)}}$ as $\rho$.
+
+	\item If $c=1$, the verifier finished the verification step of Protocol~\ref{ProtoQPIP1} by using $z$ from Protocol~\ref{proto:urmila4} as the measurement result he would get and outputs $(d,z_{naive})$
+
+	\end{enumerate}
+\end{protocol}
+
+\begin{lemma}\label{lem:naive-qpip0-binding}[binding property of  Protocol~\ref{proto:qpip0_naive} ]
+If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen, $\norm{(d,z_{naive})-(d,z_{ideal})}_q \leq O(\eps)$.
+
+, unless LWE can be efficiently solved by a quantum computer. 
+\end{lemma}
 

### 2020-04-10 preliminaries.tex
Fix easier action items

--- 2020-04-09 preliminaries.tex
@@
 We write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.
-We write $\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$.
-For all $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$ we have $\frac{1}{2}\norm{\rho_1-\rho_2}_1\leq\sqrt{1-F(\rho_1, \rho_2)}$.
+We write $\norm{\rho_1-\rho_2}_{tr}$ for the trace distance between $\rho_1$ and $\rho_2$.
+For all $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$ we have $\norm{\rho_1-\rho_2}_{tr}\leq\sqrt{1-F(\rho_1, \rho_2)}$.
 
@@
 
-\subsection{Relevant complexity classes}
-
-We define a few relevant complexity classes.
-
-\begin{definition} [$\BQP$]
-	$\BQP$ is the class of languages $L$ for which for all $n\in\bbN$ there exists a quantum circuit constructible in time $\poly(n)$ that, given any $x\in\set{0, 1}^n$ as input, correctly decides whether $x\in L$ at least $\frac{2}{3}$ of the time.
-	\Ethan{Just copy this from somewhere}
-\end{definition}
-
-\iffalse
-
-\begin{definition} [$\FBQP$]
-	A function $f:\set{0,1}^*\rightarrow\set{0,1}^*$ is in $\FBQP$ if there is a $\BQP$ machine that, $\forall x$, outputs $f(x)$ with overwhelming probability.
-	\Ethan{Need to be more formal. Also should be efficient verifiable}
-\end{definition}
-
-\fi
+\Ethan{I removed the definition of $\BQP$ since nobody else defines it in their papers anyways}
 
 We define search and sampling versions of $\BQP$ based on \cite{aaronson_2013}.
-
-\iffalse
-
-\begin{definition} [search problem]
-	A search problem $R$ is a collection of nonempty sets $(A_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0, 1}^*$, where $A_x$... \Ethan{Great, interface doesn't line up correctly}
-\end{definition}
-
-\fi
 
@@
 \subsection{Quantum Prover Interactive Protocol (QPIP)}
-We classify the interaction between a (almost classical) client and a quantum server for sampling problems, extending the classification by \cite{FOCS:Mahadev18a}.
+We model the interaction between a (almost classical) client and a quantum server following \cite{FOCS:Mahadev18a}.
 
 \begin{definition}
-	We say $\Pi=(P, V)$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and soundness error $s$ \Ethan{Might need these to be functions of $\abs{x}$} if
-	\Ethan{Look up ``interactive protocols for BQP". Right now it's missing quantifier for all x. Also need to mention d is decision bit; maybe do that in next definition and swap locations}
+	A protocol $\Pi=(P, V)$ is said to be in $\QPIP_\tau$ if it satisfies the following properties:
 	\begin{itemize}
-		\item Let $(d, z)\leftarrow(P, V)(x)$. Then $d=rej$ with probability at most $c$.
-		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.
-Let \Ethan{Use display math to make it obvious I'm defining this} $z_{ideal}\leftarrow D_x$ if $d=acc$, else $z_{ideal}=\bot$.
-Then $\norm{(d, z) - (d, z_{ideal})} \leq s$ \Ethan{make stat.
-distance notation consistent}.
-	\end{itemize} \hannote{need computational?}
-\end{definition}
-
-\Ethan{Acc, rej, P, V fonts}
-
-\Ethan{Might need to write our own def. here}
-
-\Ethan{Look at thesis for this}
-
-\begin{definition}
-	A sampling problem $S=(D_x)_{x\in\set{0, 1}^*}$ is said to be \Ethan{Try to make this more general; remove mentions of sampling/decision problems} in $\QPIP_\tau$ with completeness $c$ and soundness $s$ \Ethan{Don't tie this with completeness and soundness yet} if there exists a protocol $(\bbP, \bbV)(x)$ for $S$ with the following properties:
-	\begin{itemize}
-		\item $\bbP$ is run by the prover, a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
-		\item $\bbV$ is run by the verifier, which is a hybrid machine of a classical part and a limited quantum part.
+		\item $P$ is run by the prover, a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
+		\item $V$ is run by the verifier, which is a hybrid machine of a classical part and a limited quantum part.
 The classical part is a $\BPP$ machine.
@@
 The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
-		\item There is also a classical communication channel between the prover and the verifier, which can transmit $\poly(\abs{x})$ many bits to either direction. 
+		\item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially many bits to either direction. 
 	\end{itemize}
@@
 
-\Ethan{Two separate definitions for comp and soundness}
-
-\Ethan{Soundness?}
-
-\Ethan{Just call this blindness and put this under interactive protocols}
-
-\Ethan{See Thomas' paper if he defined this. Or actually, see https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf}
-
-We present the security definition for interactive protocols:
+\Ethan{Look up ``interactive protocols for BQP"}
+\begin{definition}
+	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ if for all $x\in\zo^*$: TODO
+\end{definition}
 
 \begin{definition}
-    \Ethan{Define this in terms of views instead; see paper linked on Skype}
+	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
+	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
+	\begin{itemize}
+		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
+		\item Let $(d, z)\leftarrow(P, V)(x)$. Then $d=rej$ with probability at most $c(\lambda)$.
+		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.
+			Define $z_{ideal}$ by
+			$$\begin{cases}
+				z_{ideal}=\bot & \text{if } d=\Acc\\
+				z_{ideal}\leftarrow D_x & \text{if } d=\Rej
+			\end{cases}$$
+			then $\norm{(d, z) - (d, z_{ideal})} \leq \varepsilon$ \Ethan{make stat. distance notation consistent}.
+	\end{itemize} \hannote{need computational?} \Ethan{The norm at the end? Nah it's statistical distance}
+\end{definition}
 
+We also define blindness of a protocol.
+
+\begin{definition}
 	Let $\lambda$ be a security parameter.
 	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
-	Then it is IND-CPA secure if $\forall x\in\set{0,1}^n$ no polynomial time adversary $\cA$ can win \protoref{indcpa} with probability better than $\frac{1}{2}+\negl(\lambda)$
+	Then it is \emph{blind} if...
+
+	\Ethan{TODO something about views}
+
+	\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf}
 \end{definition}
-
-\begin{protocol}{Attack against semantic security}
-	\label{proto:indcpa}
-	\begin{enumerate}
-		\item The challenge picks $b\in\set{0,1}$ at random
-		\item If $b=0$, the challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
-		\item Otherwise, the challenger runs the protocol with the adversary, acting as the verifier with input $x$
-		\item $\cA$ attempts to guess $b$
-	\end{enumerate}
-\end{protocol}
 
@@
 
-Taken from \href{http://math.mit.edu/~goemans/18310S15/chernoff-notes.pdf}{here}.
-
 \begin{thm}
 \label{thm:Chernoff}
-Let $X=\sum_{i=1}^n X_i$ where $X_i$ are i.i.d. \Ethan{Ind. is enough} Bernoulli trials, and $\mu=\E[X]$.
+Let $X=\sum_{i=1}^n X_i$ where $X_i$ are independent Bernoulli trials, and $\mu=\E[X]$.
 Then for all $0<\delta<1$,
@@
 
-\Ethan{State 2.3; prove from 2.2 in appendix}
+\Ethan{State the one below; prove the one above in appendix}
 
@@
 $\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
-$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l))=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
+$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l))=f(\mathsf{HE.Dec}_{sk}(c_1),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
 where $f$ is specified by a circuit of depth at most $L$.
@@
 
-The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitate the use of classical clients:
+The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitate the use of classical clients.
+
+\begin{definition}
+	we call a quantum homomorphic encryption scheme \emph{classical-friendly} if it has the following properties:
 	\begin{itemize}
@@
 		\item In the case where the plaintext is classical, $\QEnc$ can be done classically.
-	\item Its ciphertext takes the form $(X^xZ^z\rho Z^zX^x, c_{x, z})$, where $\rho$ is the plaintext and $c_{x, z}$ is a ciphertext that decodes to $(x, z)$ under a certain classical homomorphic encryption scheme.
+		\item Its ciphertext can be homomorphically measured, after which $\QDec$ can also be done classically.
 	\end{itemize}
+\end{definition}
 
-\Ethan{Reword the above? How? 3rd point can be weakened to can be decrypted classically? Maybe call this ``classical friendly". Mention LWE. There exists a classical friendly... etc.}
+\begin{theorem} [from \cite{mahadev_qfhe}]
+	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine,
+	there exists a classical-friendly quantum homomorphic encryption scheme.
+\end{theorem}

### 2020-04-10 qpip0.tex

@@
 \begin{lemma}\label{lem:naive-qpip0-binding}[binding property of  Protocol~\ref{proto:qpip0_naive} ]
-If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen, $\norm{(d,z_{naive})-(d,z_{ideal})}_q \leq O(\eps)$.
+If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen, $\norm{(d,z_{naive})-(d,z_{ideal})}_q \leq O(\eps)$, unless LWE can be efficiently solved by a quantum computer.
+\end{lemma}
 
-, unless LWE can be efficiently solved by a quantum computer. 
-\end{lemma}
+\begin{proof}
+By Lemma~\ref{lem:urmila-binding}, if the prover passes the testing round with probability $1-\negl(n)$, there exist a $\rho$ such that $\norm{z_{commit}- M_{XZ}(\rho,h)}_q \leq \negl(n)$.
+Let $Ver$ be the verification operation run by Protocol~\ref{ProtoQPIP1} on the measurement outcome.
+\hannote{describe better} Since $Ver$ is an efficient process and $Ver(z_{commmit})=(d,z_{naive})$, we have that
+
+\begin{equation} \label{eq:z=verM}
+    \norm{(d,z_{naive})-Ver( M_{XZ}(\rho,h))}_q \leq \negl(n).
+\end{equation}
+\hannote{actually true with subnormalize shit?}
+ By Theorem~\ref{QPIP1thm}, for all $\rho$, 
+ \begin{equation}
+     \norm{Ver(M_{XZ}(\rho,h))-(d,z_{ideal})}\leq O(\eps).
+ \end{equation}
+   Combined with Equation~\ref{eq:z=verM} and Lemma~\ref{lem:computational-triangle0}, we have that
+   \begin{equation}
+       \norm{(d,z_{naive})-(d,z_{ideal})}_q\leq O(\eps)
+   \end{equation}
+\end{proof}
 

### 2020-04-10 preliminaries.tex
Update working progress

@@
 For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
-We write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.
-We write $\norm{\rho_1-\rho_2}_{tr}$ for the trace distance between $\rho_1$ and $\rho_2$.
-For all $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$ we have $\norm{\rho_1-\rho_2}_{tr}\leq\sqrt{1-F(\rho_1, \rho_2)}$.
+For $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$,
+we write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.
+We write $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$.
+We have $\norm{\rho_1-\rho_2}_{tr}\leq\sqrt{1-F(\rho_1, \rho_2)}$.
+For two densities $f_1$ and $f_2$ over the same finite domain $X$, we write $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ for their total variation distance.
 
@@
 \begin{definition}
-	$P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$, $X=\begin{pmatrix}0&1\\1&0\end{pmatrix}$,
+	$P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$,
+	$X=\begin{pmatrix}0&1\\1&0\end{pmatrix}$,
 	$Y=\begin{pmatrix}0&-i\\i&0\end{pmatrix}$,
@@
 \begin{definition}
-	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ if for all $x\in\zo^*$: TODO
+	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ with completeness error $c$ and soundness error $s$ if for all $x\in\zo^*$:
+	\Ethan{TODO: errors are functions of input length}
+	\begin{itemize}
+		\item If $x\in L$
+			$\Pr\left[(P, V)(x)=(1^n, x)\right]$
+		\item TODO SOUNDNESS
+	\end{itemize}
 \end{definition}
@@
 		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
-		\item Let $(d, z)\leftarrow(P, V)(x)$. Then $d=rej$ with probability at most $c(\lambda)$.
+		\item Let $(d, z)\leftarrow(P, V)(x)$. \Ethan{Same problem as last definition...} Then $d=rej$ with probability at most $c(\lambda)$.
 		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.
@@
 			\end{cases}$$
-			then $\norm{(d, z) - (d, z_{ideal})} \leq \varepsilon$ \Ethan{make stat. distance notation consistent}.
-	\end{itemize} \hannote{need computational?} \Ethan{The norm at the end? Nah it's statistical distance}
+			then $\norm{(d, z) - (d, z_{ideal})}_{TV} \leq \varepsilon$.
+	\end{itemize} \hannote{need computational?} \Ethan{Yeah. Will fix.}
 \end{definition}
@@
 	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
-	Then it is \emph{blind} if...
-
-	\Ethan{TODO something about views}
+	Then it is \emph{blind} if the following ensembles are computationally indistinguishable over $\lambda$:
+	\begin{itemize}
+		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda)}_{\lambda\in\bbN, x\in\zo^n}$
+		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda)}_{\lambda\in\bbN, x\in\zo^n}$
+	\end{itemize}
+	\Ethan{Do I need to write out unrelated inputs to be fully general?}
 

### 2020-04-10 preliminaries.tex
Updates from Overleaf

--- 2020-04-10 preliminaries.tex
@@
 
-The phase gate and Pauli matrices are denoted as follows.
+The phase gate and Pauli matrices are the following matrices.
 
@@
 				z_{ideal}\leftarrow D_x & \text{if } d=\Rej
-			\end{cases}$$
+			\end{cases}$$\hannote{swap rej and acc}
 			then $\norm{(d, z) - (d, z_{ideal})} \leq \varepsilon$ \Ethan{make stat. distance notation consistent}.
-	\end{itemize} \hannote{need computational?} \Ethan{The norm at the end? Nah it's statistical distance}
+	\end{itemize} \hannote{need computational version of soundness?} \Ethan{The norm at the end? Nah it's statistical distance}
 \end{definition}

### 2020-04-10 preliminaries.tex

--- 2020-04-10 preliminaries.tex
@@
 			$$\begin{cases}
-				z_{ideal}=\bot & \text{if } d=\Acc\\
-				z_{ideal}\leftarrow D_x & \text{if } d=\Rej
+				z_{ideal}=\bot & \text{if } d=\Rej\\
+				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
 			\end{cases}$$
 			then $\norm{(d, z) - (d, z_{ideal})}_{TV} \leq \varepsilon$.
-	\end{itemize} \hannote{need computational?} \Ethan{Yeah. Will fix.}
+	\end{itemize} \hannote{need computational version of soundness?} \Ethan{Yeah. Will fix.}
 \end{definition}

### 2020-04-10 preliminaries.tex
Fix typos

@@
 	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ with completeness error $c$ and soundness error $s$ if for all $x\in\zo^*$:
-	\Ethan{TODO: errors are functions of input length}
 	\begin{itemize}
-		\item If $x\in L$
-			$\Pr\left[(P, V)(x)=(1^n, x)\right]$
-		\item TODO SOUNDNESS
+		\item If $x\in L$, then $\Pr\left[(P, V)(x)=\Rej\right]<c(\abs{x})$.
+		\item If $x\notin L$, then for all cheating prover $P^*$, $\Pr\left[(P^*, V)(x)=\Acc\right]<s(\abs{x})$.
 	\end{itemize}
@@
 		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
-		\item Let $(d, z)\leftarrow(P, V)(x)$. \Ethan{Same problem as last definition...} Then $d=rej$ with probability at most $c(\lambda)$.
+		\item Let $(d, z)\leftarrow(P, V)(x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
 		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.

### 2020-04-11 preliminaries.tex
Upload for discussion

--- 2020-04-10 preliminaries.tex
@@
 \begin{definition}
-	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ with completeness error $c$ and soundness error $s$ if for all $x\in\zo^*$:
-	\Ethan{TODO: errors are functions of input length}
+	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ with completeness error $c$ and soundness error $s$ if for all $x\in\zo^*$ and security parameter $1^\lambda$:
 	\begin{itemize}
-		\item If $x\in L$
-			$\Pr\left[(P, V)(x)=(1^n, x)\right]$
-		\item TODO SOUNDNESS
+		\item If $x\in L$, then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
+		\item If $x\notin L$, then for all cheating prover $P^*$, $\Pr\left[(P^*, V)(x, 1^\lambda)=\Acc\right]<s(\lambda)$.
 	\end{itemize}
@@
 	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
-	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
+	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and computational soundness \Ethan{Specify it's computational or no?} if for all $x\in\zo^*$:
 	\begin{itemize}
 		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
-		\item Let $(d, z)\leftarrow(P, V)(x)$. \Ethan{Same problem as last definition...} Then $d=rej$ with probability at most $c(\lambda)$.
-		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.
+		\item Let $(d, z)\leftarrow(P, V)(x, 1^{1/\varepsilon}, 1^\lambda)$, then $d=\Rej$ with probability at most $c(\lambda)$.
+		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
 			Define $z_{ideal}$ by
@@
 			\end{cases}$$
-			then $\norm{(d, z) - (d, z_{ideal})}_{TV} \leq \varepsilon$.
+			then for all adversary, its probability to distinguish a sample of $(d, z)$ from that of $(d, z_{ideal})$ is less than $\varepsilon$.
 	\end{itemize} \hannote{need computational version of soundness?} \Ethan{Yeah. Will fix.}
@@
 	\end{itemize}
-	\Ethan{Do I need to write out unrelated inputs to be fully general?}
-
-	\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf}
+	\Ethan{See \url{https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf}}
 \end{definition}

### 2020-04-11 qpip.tex
Fix bug
Upload for discussion

--- 2020-04-07 qpip.tex
@@
 
+\Ethan{New changes: Re-parametrize so final error is eps. Write more details for soundness about the classical mix.}
+
 \begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for the $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$}
@@
 
-	Inputs: \Ethan{Should the $\SampBQP$ instance be an input?}
+	Inputs:
 	\begin{itemize}
 		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
-		\item Error parameter $\varepsilon\in(0, 1)$
+		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
+		\item Accuracy parameter $1^{1/\varepsilon}$ where $\varepsilon=\frac{1}{\poly(\lambda)}$ \Ethan{This feels strange... Neither $\forall\poly$ nor $\exists\poly$ feels right.}
 	\end{itemize}
@@
 		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
-		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
+		\item Let $T$ be the number of gates in $C$.
+		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
 		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
@@
 	\begin{enumerate}
-		\item The honest prover prepares $M=\frac{T^{21}}{\varepsilon^{33}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
-		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
+		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{21}\lambda^2}{\varepsilon^{31}}$ \Ethan{I think?
+Double check later} copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item\label{step:qpip1-verify} The verifier privately samples $I\subset[M]$ s.t.
+$\abs{I}=m$ where $m=\frac{T^{10}\lambda}{\varepsilon^{14}}$, and $k\xleftarrow{\$}[M]\setminus I$.
+\hannote{$\xleftarrow{\$}$ ?} \Ethan{Sample randomly from.
+I thought it's standard notation}
 			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
 		\begin{enumerate}
-			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
-			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $y$.
+			\item If $i\in I$, run $y_i\leftarrow\cV_{\GS}(\rho_i)$.
+			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $z$.
 			\item Else, discard $\rho_i$.
 		\end{enumerate}
-			Let $Z=\sum_{i\in I} z_i$.
-If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ as in \Cref{cor:HamCheck} then the verifier outputs $(acc, y)$.
-Else, it outputs $(rej, \bot)$.
+			Let $Y=\sum_{i\in I} y_i$.
+If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{72\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ as in \Cref{cor:HamCheck} then the verifier outputs $(\Acc, z)$.
+			Else, it outputs $(\Rej, \bot)$.
 	\end{enumerate}
@@
 Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
-It is simple to check that $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
+It is simple to check that $\PiSamp$ runs in $\poly(n, \lambda)$ time. \Ethan{Right? Or just $\poly(\lambda)$?}
 We now show its completeness and soundness.
-Particularly, we prove that it has $O(\varepsilon)$ soundness errors
-with the understanding that by relabelling $\varepsilon'=O(\varepsilon)$ and modifying $\PiSamp$ accordingly,
-one can achieve $\varepsilon'$ soundness errors while maintaining completeness and running time properties.
 
@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and $O(\varepsilon)$ soundness error. \hannote{remind completeness and soundness with a footnote.}
+	$\PiSamp$ has negligible completeness error and is computationally sound.
 \end{thm}
@@
 	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
-	So we can apply Chernoff bound (\Cref{thm:Chernoff}) with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
-	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$
+	So we can apply Chernoff bound (\Cref{thm:Chernoff}) to get
+	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq\negl(\lambda).$$
 
@@
 
-	\Ethan{Trace out discarded copy on $\sigma'$? Or add copies on $\tau$?}
-
 	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $M$-fold tensor products of identical copies of some states $\tau_j$.
-	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes M}$
+	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes m+1}$
 	such that for all quantum-classical channels $\Lambda_i$ acting on registers with size of $\ket{\psi_{C'(x)}}$:
-	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
+	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}
 	\leq\sqrt{\frac{2m^2\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
-	=O(\varepsilon).$$
+	\leq\frac{\varepsilon}{6}$$
+	where $\sigma'_{\leq m+1}$ is the first $m+1$ registers of $\sigma'$.
 	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
@@
 
-	Now we claim that for each component $\tau_j$,
-	if $\PSampstar$ had sent $\tau_j^{\otimes M}$ instead then the soundness error is $O(\varepsilon)$.
-	Let $p_j$ be the probability that $\cVGS(\tau_j)=acc$, we seperate $\tau_j$ terms into two cases.
+	For each $\tau_j$, we define the distribution $(d_j, z_j)$ to correspond to $\VSamp$'s output if it were to receive $\tau_j^{\otimes M}$ from $\PSampstar$, and define $z_{j, ideal}$ accordingly.
+	We claim that $(d_j, z_j)$ is $\frac{2\varepsilon}{6}$-close to $(d_j, z_{j, ideal})$.
+	Let $p_j$ be the probability that $\cVGS(\tau_j)=\Acc$, and consider two cases as follows.
 
@@
 	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities.
-	That is, it outputs $(rej, \bot)$ with overwhelming probability, hence has negligible soundness errors.
+	That is, $(d_j, z_j)$ is $\negl(\lambda)$-close to $(\Rej, \bot)$.
 
@@
 	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\tau_j$ and $\ket{\psi_{C'(x)}}$:
-	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\tau_j, \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}})\geq1-\varepsilon^2.$$
+	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\tau_j, \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}})\geq1-\frac{\varepsilon^2}{36}.$$
 	which in turn implies a lower bound on the respective trace distance:
-	$$\frac{1}{2}\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_1<\varepsilon.$$
-	Let $(d, y)$ be $\VSamp$'s output. Suppose $d=acc$, then $y$ would be the measurement on $\tau_j$'s data register,
-	which is $\varepsilon$-close to that on $\ket{\psi_{C'(x)}}$.
+	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}<\frac{\varepsilon}{6}.$$
+	Suppose $d_j=\Acc$, then $z_j$ would be $\negl(\lambda)$-close to the measurement on $\tau_j$'s data register,
+	which is $\frac{\varepsilon}{6}$-close to that on $\ket{\psi_{C'(x)}}$.
 	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has $1-\varepsilon$ probability to contain $C(x)$ due to the padding.
-	So $y$ is $O(\varepsilon)$-close to $y_{ideal}$ when $d=acc$.
-	Which implies that $(d, y)$ is $O(\varepsilon)$-close to $(d, y_{ideal})$.
+	So $z_j$ is $\frac{2\varepsilon}{6}$-close to $z_{ideal}$ when $d=\Acc$,
+	which implies that $(d_j, z_j)$ is $\frac{2\varepsilon}{6}$-close to $(d_j, z_{j, ideal})$.
 
-	The cheating prover's strategies corresponding to $\tau_j$ all have $O(\varepsilon)$ soundness errors.
-	As $\rho$ is a convex combination of these strategies, we conclude the same about it.
-	Finally, as the outputs corresponding to $\sigma$ is $\varepsilon$-close to that of some $\rho$,
-	by data processing inequality we conclude that $\PiSamp$ has $O(\varepsilon)$ soundness errors.
+	Define $z_\rho$ to be the output distribution corresponding to if $\VSamp$ were to receive $\rho=\sum_j w_j\tau_j^{\otimes M}$ instead of $\sigma$ from the server,
+	and define $z_{\rho, ideal}$ accordingly.
+	We have $\norm{(d_\rho, z_\rho) - (d', z'_{\rho, ideal})}_{TV} < \frac{2\varepsilon}{6}$ since the same is true for all components $\tau_j$.
+
+	As $(d, z)$ is $\frac{\varepsilon}{6}$-close to $(d_\rho, z_\rho)$ for some $\rho$ by de Finetti's theorem and data processing inequality,
+	using triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
+	Hence we have $\norm{d - d_\rho}_{TV}\leq\frac{\varepsilon}{2}$, which implies $\norm{(d_\rho, z'_{\rho, ideal}) - (d, z_{ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
+	The conclusion then follows from triangle inequality.
 \end{prf}

### 2020-04-11 qpip.tex
Fix typos and minor bugs

@@
 	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}
-	\leq\sqrt{\frac{2m^2\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
+	\leq\sqrt{\frac{2m^2\left(n+T+\frac{6T}{\varepsilon}\right)}{M-m}}
 	\leq\frac{\varepsilon}{6}$$
@@
 	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
-	$\Lambda_{m+1}$ is measurement on the data register of $\rho_k$.
+	$\Lambda_{m+1}$ measures the data register of $\rho_k$.
 
@@
 	We claim that $(d_j, z_j)$ is $\frac{2\varepsilon}{6}$-close to $(d_j, z_{j, ideal})$.
-	Let $p_j$ be the probability that $\cVGS(\tau_j)=\Acc$, and consider two cases as follows.
+	Let $p_j$ be the probability that $\cVGS(\tau_j)=\Acc$, and consider the following two cases.
 
@@
 	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities.
-	That is, $(d_j, z_j)$ is $\negl(\lambda)$-close to $(\Rej, \bot)$.
+	As a result, $\norm{(d_j, z_j)-(d_j, z_{j, ideal})}_{TV}=\negl(\lambda)$.
 
@@
 	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}<\frac{\varepsilon}{6}.$$
-	Suppose $d_j=\Acc$, then $z_j$ would be $\negl(\lambda)$-close to the measurement on $\tau_j$'s data register,
+	Suppose $d_j=\Acc$, then $z_j$ would be the measurement on $\tau_j$'s data register,
 	which is $\frac{\varepsilon}{6}$-close to that on $\ket{\psi_{C'(x)}}$.
-	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has $1-\varepsilon$ probability to contain $C(x)$ due to the padding.
+	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has at least $1-\frac{\varepsilon}{6}$ probability to contain $C(x)$ due to the padding.
 	So $z_j$ is $\frac{2\varepsilon}{6}$-close to $z_{ideal}$ when $d=\Acc$,
@@
 	and define $z_{\rho, ideal}$ accordingly.
-	We have $\norm{(d_\rho, z_\rho) - (d', z'_{\rho, ideal})}_{TV} < \frac{2\varepsilon}{6}$ since the same is true for all components $\tau_j$.
+	We have $\norm{(d_\rho, z_\rho) - (d, z_{\rho, ideal})}_{TV} < \frac{2\varepsilon}{6}$ since the same is true for all components $\tau_j$.
 
@@
 	using triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
-	Hence we have $\norm{d - d_\rho}_{TV}\leq\frac{\varepsilon}{2}$, which implies $\norm{(d_\rho, z'_{\rho, ideal}) - (d, z_{ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
+	Hence we have $\norm{d - d_\rho}_{TV}\leq\frac{\varepsilon}{2}$, which implies $\norm{(d_\rho, z_{\rho, ideal}) - (d, z_{ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
 	The conclusion then follows from triangle inequality.

### 2020-04-11 preliminaries.tex
Deal with another couple action items

@@
 \begin{definition} [$\SampBQP$]
-	$\SampBQP$ is the class of sampling problems $S=\left(D_x\right)_{x\in\set{0, 1}^*}$ for which there exists a polynomial-time quantum algorithm $B$ that, given $(x, 0^{1/\varepsilon})$ as input, samples from a probability distribution $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
+	$\SampBQP$ is the class of sampling problems $S=\left(D_x\right)_{x\in\set{0, 1}^*}$ for which there exists a polynomial-time quantum algorithm $B$ that, given $(x, 1^{1/\varepsilon})$ as input, samples from a probability distribution $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
 \end{definition}
@@
 	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
-	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and computational soundness \Ethan{Specify it's computational or no?} if for all $x\in\zo^*$:
+	We say $\Pi$ is a computationally sound protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
 	\begin{itemize}
@@
 			\end{cases}$$
-			then for all adversary, its probability to distinguish a sample of $(d, z)$ from that of $(d, z_{ideal})$ is less than $\varepsilon$.
-	\end{itemize} \hannote{need computational version of soundness?} \Ethan{Yeah. Will fix.}
+			then for all adversary, its probability to successfully distinguish a sample of $(d, z)$ from that of $(d, z_{ideal})$ is less than $\frac{1}{2}+\frac{\varepsilon}{2}$
+			\Ethan{Something like this? Or need protocol or specify prior probability is 1/2 each?}
+	\end{itemize}
 \end{definition}
@@
 \begin{thm}
+	\label{thm:proj1}
 	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on some Hilbert space $\cH=\cS+\cS^\bot$.
@@
 
-\Ethan{State the one below; prove the one above in appendix}
-
 \begin{thm}
@@
 	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
-	$$J=\frac{10\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
+	$$J=\frac{11\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
 	then we have
@@
 \end{thm}
+\begin{proof}
+	Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least nonzero eigenvalue of $JH_2$ is greater than $10\norm{H_1}$.
+\end{proof}
 

### 2020-04-11 hamiltonian.tex
Add discussion notes

@@
-\section{Construction of the XZ Local Hamiltonian}
+\section{Construction of the X-Z Local Hamiltonian for $\SampBQP$}
 \label{sec:Hamiltonian}
 
-\XW{highlight the different requirement from the normal Local Hamiltonian reduction; and highlight a bit about the solution idea}
+\def \Hin {H_{\mathrm{in}}}
+\def \Hout {H_{\mathrm{out}}}
+\def \Hprop {H_{\mathrm{prop}}}
+\newcommand{\histpsi}[1]{\ket{\psi_{#1}^{\mathrm{hist}}}}
 
-In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian instance.
+As we mentioned in this introduction, we will employ the circuit \emph{history} state in the original construction of the Local Hamiltonian problem~\cite{kitaev2002classical} to encode the circuit information for $\SampBQP$.
+However, there are distinct requirements between certifying the computation for $\BQP$ and $\SampBQP$ based on the history state.
+For any quantum circuit $C$ on input $x$, the original construction for certifying $\BQP$\footnote{The original construction is for the purpose of certifying problems in QMA.
+We consider its simple restriction to problems inside BQP.} consists of three parts of local Hamiltonian $\Hin, \Hprop$, $\Hout$ where $\Hin$ is used to certify the initial input $x$, $\Hprop$ to certify the gate-by-gate evolution according to the circuit description, and $\Hout$ to certify the final output.
+In particular, the history state referring to quantum circuit $C$ on input $x$ is in the ground space of $\Hin$ and $\Hprop$.
+Note that $\BQP$ is a decision problem and its outcome (0/1) can be easily encoded into the energy $\Hout$ on the single output qubit.
+As a result, the outcome of $\BQP$ can simply be encoded by the \emph{ground energy} of $\Hin + \Hprop + \Hout$.
 
-The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
-Protocols to delegate $\BQP$ computations such as \cite{FOCS:Mahadev18a} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
-We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.
-Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
-\Ethan{This source was given to us by Yu-Ching; I haven't read it. Also I probably should cite more sources here.}
+To deal with $\SampBQP$, we will still employ $\Hin$ and $\Hprop$ to certify the circuit's input and gate-by-gate evolution.
+However, in this case, we care about the entire final state of the circuit, rather than the energy on the output qubit.
+The history state is still in the ground space of $\Hin + \Hprop$.
+One approach to certify the entire final state encoded inside the history state is to make sure that the history state is the unique ground state of $\Hin + \Hprop$ and all other orthogonal states will have much higher energies.
+Namely, we need to construct some $\Hin'+ \Hprop'$ with the history state as the unique ground state and with a large \emph{spectral} gap between the ground energy and excited energies. 
+This guarantees that any state with close-to-ground energy must also be close to the history state. 
+We remark that this is a much stronger and different requirement from most local Hamiltonian constructions where the focus is on the ground energy. 
+However, we show it can indeed be achieved by using the \emph{perturbation} technique 
+developed in the local Hamiltonian literature (e.g.~\cite{kempe_kitaev_regev_2006}) for a different purpose.
+
+%\XW{highlight the different requirement from the normal Local Hamiltonian reduction; and highlight a bit about the solution idea}
+
+% In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian instance.
+% The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
+% Protocols to delegate $\BQP$ computations such as \cite{FOCS:Mahadev18a} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
+% We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.
+% Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
+% \Ethan{This source was given to us by Yu-Ching; I haven't read it. Also I probably should cite more sources here.}
 

### 2020-04-11 qpip.tex
Add discussion notes

@@
 		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
-		\item Accuracy parameter $1^{1/\varepsilon}$ where $\varepsilon=\frac{1}{\poly(\lambda)}$ \Ethan{This feels strange... Neither $\forall\poly$ nor $\exists\poly$ feels right.}
+		\item Accuracy parameter $1^{1/\varepsilon}$ where $\varepsilon=\frac{1}{\poly(\lambda)}$ \Ethan{Just say between 0 and 1; specify poly lambda in thm statement}
 	\end{itemize}
@@
 		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
-		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
+		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$. \Ethan{Cite previous theorem}
 		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
-		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
+		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
 	\end{itemize}
@@
 	\begin{enumerate}
-		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{21}\lambda^2}{\varepsilon^{31}}$ \Ethan{I think?
-Double check later} copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
-		\item\label{step:qpip1-verify} The verifier privately samples $I\subset[M]$ s.t.
+		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{21}\lambda^2}{\varepsilon^{31}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t.
 $\abs{I}=m$ where $m=\frac{T^{10}\lambda}{\varepsilon^{14}}$, and $k\xleftarrow{\$}[M]\setminus I$.
 \hannote{$\xleftarrow{\$}$ ?} \Ethan{Sample randomly from.
-I thought it's standard notation}
+Will add it to preliminary section.}
 			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
@@
 			Let $Y=\sum_{i\in I} y_i$.
-If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{72\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ as in \Cref{cor:HamCheck} then the verifier outputs $(\Acc, z)$.
+If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{72\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ is the constant specified in \Cref{cor:HamCheck}, then the verifier outputs $(\Acc, z)$.
 			Else, it outputs $(\Rej, \bot)$.
@@
 Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
-It is simple to check that $\PiSamp$ runs in $\poly(n, \lambda)$ time. \Ethan{Right? Or just $\poly(\lambda)$?}
+It is simple to check that $\VSamp$ runs in $\poly(n, \lambda, \frac{1}{\epsilon})$ time.
 We now show its completeness and soundness.
@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and is computationally sound.
+	$\PiSamp$ has negligible completeness error and is statistically sound.
+	\Ethan{Should also say $\lambda$ and $\varepsilon$ are inverse poly related. Or actually, maybe specify that in soundness dfn.}
+
+	\Ethan{Might want to define verifier being efficient (poly-time) there too}
 \end{thm}
 \begin{prf}
-	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
+	For completeness, notice $y_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
 	So we can apply Chernoff bound (\Cref{thm:Chernoff}) to get
-	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq\negl(\lambda).$$
+	$$\Prob{Y>\frac{m}{2}-\varepsilon m}\leq\negl(\lambda).$$
+	\Ethan{So its rejection chance is...}
 
 	Now we show soundness.
-
-	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier.
+	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier. \Ethan{on inputs x, eps, lambda...}
 
@@
 
-	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $M$-fold tensor products of identical copies of some states $\tau_j$.
+	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $m+1$-fold tensor products of identical copies of some states $\tau_j$.
 	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes m+1}$
-	such that for all quantum-classical channels $\Lambda_i$ acting on registers with size of $\ket{\psi_{C'(x)}}$:
+	such that for all quantum-classical channels $\Lambda_i$ acting on registers with size of $\ket{\psi_{C'(x)}}$ \Ethan{Make that size another variable}:
 	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}
@@
 	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
-	$\Lambda_{m+1}$ measures the data register of $\rho_k$.
+	$\Lambda_{m+1}$ measures the data register under the standard basis.
 
-	For each $\tau_j$, we define the distribution $(d_j, z_j)$ to correspond to $\VSamp$'s output if it were to receive $\tau_j^{\otimes M}$ from $\PSampstar$, and define $z_{j, ideal}$ accordingly.
-	We claim that $(d_j, z_j)$ is $\frac{2\varepsilon}{6}$-close to $(d_j, z_{j, ideal})$.
+	We now analyze the verifier's output for each $\tau_j$ in $\rho=\sum_j w_j\tau_j^{\otimes m+1}$.
+Let $(d_j, z_j)$ be the verifier's output corresponding to $\tau_j$, and define $z_{j, ideal}$ accordingly.
+	We claim that $\norm{(d_j, z_j)-(d_j, z_{j, ideal})}_{TV}<\frac{2\varepsilon}{6}$.
 	Let $p_j$ be the probability that $\cVGS(\tau_j)=\Acc$, and consider the following two cases.
@@
 	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}<\frac{\varepsilon}{6}.$$
-	Suppose $d_j=\Acc$, then $z_j$ would be the measurement on $\tau_j$'s data register,
-	which is $\frac{\varepsilon}{6}$-close to that on $\ket{\psi_{C'(x)}}$.
+	Observe that when $d_j=\Acc$, $z_j$ is the measurement results on $\tau_j$'s data register,
+	which is $\frac{\varepsilon}{6}$-close to that of $\ket{\psi_{C'(x)}}$.
 	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has at least $1-\frac{\varepsilon}{6}$ probability to contain $C(x)$ due to the padding.
@@
 
-	Define $z_\rho$ to be the output distribution corresponding to if $\VSamp$ were to receive $\rho=\sum_j w_j\tau_j^{\otimes M}$ instead of $\sigma$ from the server,
+    Finally, let $(d_\rho, z_\rho)$ denote the verifier's output distribution corresponding to $\rho=\sum_j w_j\tau_j^{\otimes m+1}$,
 	and define $z_{\rho, ideal}$ accordingly.
@@
 
-	As $(d, z)$ is $\frac{\varepsilon}{6}$-close to $(d_\rho, z_\rho)$ for some $\rho$ by de Finetti's theorem and data processing inequality,
+	As $(d, z)$ is $\frac{\varepsilon}{6}$-close to $(d_\rho, z_\rho)$ by the data processing inequality,
 	using triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{TV}\leq\frac{\varepsilon}{2}$.

### 2020-04-11 qpip0.tex
Add discussion notes

@@
 \label{proto:QPIP0samp}
+Inputs: 
+ Both verifier and prover start with the description of number of qubits $n$,  input string $x$ to the $\SampBQP$ Instance, and a soundness parameter $\varepsilon$.
+
+Protocol:
 \begin{enumerate}
 %    \item Verifier start with description of quantum circuit $C$, input string $x$
-    \item Both verifier and prover start with the description of number of qubits $n$, quantum circuit $C$, input string $x$, and  a soundness parameter $\varepsilon$.
+
     \item Run $m=O(1/\varepsilon^2)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications.
 The copies have separate $\{h\}$, $\{sk\}$, $\{pk\}$, $\{y\}$, $\{c\}$, and $\{a\}$.
-The verifier draws $\{h\}$ independently from the distribution specifier by step~\ref{} of Protocol~\ref{ProtoQPIP1} to generate $\{sk\}$ and $\{pk\}$ for all copies on the first round.
-On the second round, for each copy, the prover choose the state specified by step~\ref{} of Protocol~\ref{ProtoQPIP1}  (with  $(C,x,\eps)$ as input) as $\rho$.
+The verifier draws $\{h\}$ independently from the distribution specifier by step~\ref{step:qpip1-verify} of Protocol~\ref{ProtoQPIP1} to generate $\{sk\}$ and $\{pk\}$ for all copies on the first round.
+On the second round, for each copy, the prover choose the state specified by step~\ref{step:qpip1-state-gen} of Protocol~\ref{ProtoQPIP1}  (with  $(C,x,\eps)$ as input) as $\rho$.
 On the third round, the verifier uniformly randomly pick an $i\in [m]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies, i.e.
@@
 
+\hannote{Intuitions about the partition lemma. }
+
 %Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
@@
 
- For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,
+ For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,  \hannote{$\psi$ should not be pure state?} \hannote{actually need to fix a $pk$ for everything here.}
 
@@
 \begin{proof}
-We begin by considering the state $\ket{\psi}$ the prover in Protocol~\ref{proto:QPIP0samp} hold before he receives $\{c\}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
+Completeness is trivial.
+
+For soundness, We begin by considering the state $\ket{\psi}$ the prover in Protocol~\ref{proto:QPIP0samp} hold before he receives $\{c\}$.
+We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
 
@@
 where we abuse the notation and use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
+%\hannote{Note that the prover's state is actually a mixed state.
+In particular, $\ket{\psi}$ depends on $pk$ and we are considering the mixed state averaged over verifier's choice of $pk$.}
 
@@
 I.e.
-there exist a $n$-qubit quantum state $\rho$ such that $z_{good}$ is $\eps$-Q-computationally indistinguishable to $\sum_z \proj{z} \tr\L(\rho \sigma_h \R)$.
+there exist a subnormalized $n$-qubit quantum state $\rho_{good}$ such that $z_{good}$ is $\eps$-Q-computationally indistinguishable to $M_{XZ}(\rho_{good},h)$.
+
+\hannote{$M_{XZ}(\rho_{good},h)=\sum_z \proj{z} \tr\L(\rho \sigma_{h,z} \R)?$}.
 \hannote{add notation for pauli matrix $\sigma_h$.}
 
-\hannote{$\rho$ is sub normalized}
+\hannote{need to simulate one copy?}
 
-\hannote{need to simulate one copy?}
+For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}: The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
+The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
+If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead.
+This is possible because all the inputs are classical.
+On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}.
+otherwise he continues to run the strategy of Lemma~\ref{lem:trivial-4-round-strategy}.
+We denote the random variable the verifier would get on the testing round as $z_{construct}$.
+
+==== old ===
 

### 2020-04-12 blind.tex
Start action items on blindness compiler

@@
 we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
+
+\Ethan{How to work the security parameter into the following? It's annoying if everything takes that.
+Also, where do I write that footnote about extra uncompiled inputs such as accuracy param.?}
 
@@
 		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
-			by evaluating $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval(pk, \cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
+			by evaluating \linebreak
+			$(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval(pk, \cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
 			It sends $\ctx{p}{1}{1}$ to the verifier.
@@
 				then homomorphically decrypts the old encryption by \linebreak
-				$$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t}).$$
+				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t}).$
 				Then it applies the next-message function homomorphically, generating
@@
 	Consider $T+1$ hybrids experiments, from $\Hyb_1$ to $\Hyb_{T+1}$.
-	In $\Hyb_i$, we modify $(\Pblind, \Vblind(x))$ s.t.
-	for all rounds associated with $\cV{t}$ where $t\geq i$, the verifier replaces the $\ctx{sk}{t-1}{t}$ in its message with encryption of $0$.
-	Then, for all $t$, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
-	By applying triangle inequality iteratively\Ethan{Is this enough or do we need equations?}, we obtain that $\Hyb_1$ is indistinguishable with $\Hyb_{T+1}$.
-	Since $\Hyb_{T+1}$ is precisely $\Piblind$, and $\Hyb_1$ is clearly blind, we conclude that $\Piblind$ is blind.
+	We define $\Hyb_{T+1}$ to be $\Piblind$.
+	For $t<T+1$, we define $\Hyb_{t}$ to be the same as $\Hyb_{t+1}$,
+	except when $\Vblind$ should send $\ctx{sk}{t}{t}$, it instead sends $\ctx{0}{}{t}$ which is encryption of $0$ under $pk_t$.
+	Then, for all $t$, from the perspective of the prover, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
+	By applying triangle inequality iteratively \Ethan{good enough?}, we observe that $\Hyb_1$ is computationally indistinguishable with $\Hyb_{T+1}$.
+	Furthermore, $\Hyb_1$ is blind since the prover isn't provided any information about any secret keys.
+	So we conclude that $\Piblind$ is blind.
 \end{proof}
 
-This compiler implies a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
-To do so, apply it to the protocol from \cite{parallelrep, alagic2019twomessage}.
-Similarly, the compiler can be applied to our $\FBQP$ and $\SampBQP$ protocols \Ethan{TODO name} too.
+Our compiler is a straightforward way of achievement blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
+In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage},
+as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.
+
+\begin{theorem}
+	There exists a blind, constant-round $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness errors.
+\end{theorem}
+
+\begin{theorem}
+	There exists a computationally sound, blind, and constant-round $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness errors.
+\end{theorem}

### 2020-04-12 preliminaries.tex
Add discussion notes
Ready prelim. for next round of feedbacks

@@
 \begin{definition} [sampling problem]
-	A sampling problem $S$ is a collection of probability distributions $(D_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{p(n)}$ for some fixed polynomial $p$.
+	A \emph{sampling problem} is a collection of probability distributions $(D_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{p(n)}$ for some fixed polynomial $p$.
 \end{definition}
@@
 \begin{definition} [$\SampBQP$]
-	$\SampBQP$ is the class of sampling problems $S=\left(D_x\right)_{x\in\set{0, 1}^*}$ for which there exists a polynomial-time quantum algorithm $B$ that, given $(x, 1^{1/\varepsilon})$ as input, samples from a probability distribution $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
+	$\SampBQP$ is the class of sampling problems $\left(D_x\right)_{x\in\set{0, 1}^*}$ for which there exists an efficient $\BPP$ machine that, on input $(n, 1^{1/\varepsilon})$, outputs a quantum circuit (that is, a sequence of unitary gates) $C$ such that for all $x\in\zo^n$, the standard basis measurement outcome on some designated output register \Ethan{Feels incredibly wordy.
+Not sure if the word ``register" here feels right either.} of $C(x)$ is $\varepsilon$-close to $D_x$.
 \end{definition}
@@
 The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
-		\item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially many bits to either direction. 
+		\item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially \Ethan{Is this good enough, or should I try to say poly in input length?
+Input isn't defined yet.} many bits to either direction.
 	\end{itemize}
@@
 
-\Ethan{Look up ``interactive protocols for BQP"}
 \begin{definition}
@@
 \end{definition}
+
+For $\SampBQP$ protocols, the accuracy error is encoded in the $\SampBQP$ instance itself, so there are no soundness parameters.
+
+\begin{definition}
+	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
+	We say $\Pi$ is a statistically sound protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
+	\begin{itemize}
+		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
+		\item Let $(d, z)\leftarrow(P, V)(x, 1^{1/\varepsilon}, 1^\lambda)$, then $d=\Rej$ with probability at most $c(\lambda)$.
+		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
+			Define $z_{ideal}$ by
+			$$\begin{cases}
+				z_{ideal}=\bot & \text{if } d=\Rej\\
+				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
+			\end{cases}$$
+			then $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$.
+	\end{itemize}
+\end{definition}
+
+As sometimes one only achieves computational guarantees instead of statistical ones;
+we also model the corresponding situation for $\SampBQP$ protocols.
 
@@
 
-We also define blindness of a protocol.
+We define blindness of a protocol as follows.
 
@@
 	\end{itemize}
-	\Ethan{See \url{https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf}}
 \end{definition}
@@
 
-\Ethan{Everything gets security param.}
-
 \def\QHE{\mathsf{QHE}}

### 2020-04-12 hamiltonian.tex
Updates from Overleaf

@@
 However, in this case, we care about the entire final state of the circuit, rather than the energy on the output qubit.
-The history state is still in the ground space of $\Hin + \Hprop$.
-One approach to certify the entire final state encoded inside the history state is to make sure that the history state is the unique ground state of $\Hin + \Hprop$ and all other orthogonal states will have much higher energies.
+The history state remains in the ground space of $\Hin + \Hprop$.
+Our approach to certify the entire final state (which is encoded inside the history state) is to make sure that the history state is the unique ground state of $\Hin + \Hprop$ and all other orthogonal states will have much higher energies.
 Namely, we need to construct some $\Hin'+ \Hprop'$ with the history state as the unique ground state and with a large \emph{spectral} gap between the ground energy and excited energies. 
-This guarantees that any state with close-to-ground energy must also be close to the history state. 
-We remark that this is a much stronger and different requirement from most local Hamiltonian constructions where the focus is on the ground energy. 
-However, we show it can indeed be achieved by using the \emph{perturbation} technique 
+It is guaranteed that any state with close-to-ground energy must also be close to the history state. 
+We remark that this is an additional strong requirement, whereas most local Hamiltonian constructions focus on the ground energy. 
+We show it can indeed be achieved by using the \emph{perturbation} technique 
 developed in the local Hamiltonian literature (e.g.~\cite{kempe_kitaev_regev_2006}) for a different purpose. 
+Another example of local Hamiltonian construction focusing on the spectral gap can be found in~\cite{adiabatic} where the purpose is to simulate quantum circuits by adiabatic quantum computation.
+
+We need, however, two more further twists to serve our purpose. 
+First, as we will eventually measure the final state in order to obtain classical samples, we need that the final state occupies a large fraction of the history state.
+We can simply add dummy identity gates for that purpose.
+Second, as we are only able to perform $X$ or $Z$ measurement by techniques from~\cite{FOCS:Mahadev18a},
+we need to construct X-Z only local Hamiltonians. 
+\XW{TOADD: some old references}
+We achieve this by choosing one particular universal gate set and will include our construction for the sake of completeness.
+
+\XW{TOADD: some orgainization}
 
@@
 
-We begin by recalling the form that local Hamiltonian certificates:
+\subsection{Specific Construction}
 
-\begin{dfn}
+Recall the definition of the history state which serves as a transcript of the circuit evolution~\cite{kitaev2002classical}:
+
+\begin{dfn}[History-state]
 	\label{dfn:groundstate}	
-	Let $C=U_T\ldots U_1$ be a quantum circuit consisting of $T$ gates, and let $x\in\set{0,1}^n$. Then we denote
-	$$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$$
-	We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
+    Given any quantum circuit $C=U_T\ldots U_1$ of $T$ elementary gates and input $x\in\{0,1\}^n$, the \emph{history}-state $\histpsi{C(x)}$ is defined by
+    \begin{equation}
+        \histpsi{C(x)} \equiv \frac{1}{\sqrt{T}}\sum_{t=0}^TU_t\ldots U_1\ket{x,0}\otimes\ket{\hat{t}},
+    \end{equation}
+    where the first register refers to the input, the second refers to the work space which is initialized to $\ket{0}$, and the last refers to the clock space which encodes the time information.
+Note that $\hat{t}$ could be some representation of $t$=0,..., $T$ up to design choice.
 \end{dfn}
 
-\begin{rmk}
-	\label{idpadding}
-	One can first pad $C$ with identity gates at the end, doubling its number of gates and obtaining another circuit $C'$.
-	Then by measuring the time register of $\ket{\psi_{C'(x)}}$ one obtains with probability $\frac{1}{2}$ the state $C(x)$.
-\end{rmk}
+% \begin{rmk}
+% 	\label{idpadding}
+% 	One can first pad $C$ with identity gates at the end, doubling its number of gates and obtaining another circuit $C'$.
+% 	Then by measuring the time register of $\ket{\psi_{C'(x)}}$ one obtains with probability $\frac{1}{2}$ the state $C(x)$.
+% \end{rmk}
+
+\XW{define $k$-local XZ Hamiltonian}
 
@@
 \end{dfn}
+
+\XW{cite the results that Toffoli and Hadamard gates
+and add the fact}
+
+Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
+Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
+Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
+\begin{thm}
+	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
+\end{thm}
+\begin{prf}
+	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
+	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
+	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
+\end{prf}
+
+\XW{main construction and proofs}
 
@@
 
-The second one is a way to verify ground states of local Hamiltonians, again with some extra properties:
-\begin{thm}
-	\label{ThmXZCheck}
-	Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists a $\BQP$ algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
+% The second one is a way to verify ground states of local Hamiltonians, again with some extra properties:
+% \begin{thm}
+% 	\label{ThmXZCheck}
+% 	Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists a $\BQP$ algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
 (In particular, it accepts the $\ket{\psi_{C(x)}}$ with probability $\fot$.) Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
-\end{thm}
+% \end{thm}
 
-\subsection{Circuits of Toffoli and Hadamard gates}
+%\subsection{Circuits of Toffoli and Hadamard gates}
 
-Old notation: Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
+% Old notation: Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
 I.e.
 $\Lambda^2_{1, 2}(X_3)$ would be a Toffoli gate.
-\Ethan{TODO: replace with something that looks better and doesn't conflict with the use of $\Lambda$ as measurement.}
+% \Ethan{TODO: replace with something that looks better and doesn't conflict with the use of $\Lambda$ as measurement.}
 
-Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
-Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
-Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
-\begin{thm}
-	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
-\end{thm}
-\begin{prf}
-	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
-	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
-	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
-\end{prf}
+% Now we present the proof that $\set{H, \Lambda^2(X)}$ is indeed a universal gate set from \cite{quant-ph/0301040}: \Ethan{This definitely belongs in the appendix instead...}
+% \begin{thm}
+% 	Let $C$ be a circuit that:
+% 	\begin{itemize}
+% 		\item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
+% 		\item uses $n$ qubits
+% 	\end{itemize}
+% 	Then a classical machine given $C$ can compute a circuit $C'$ that:
+% 	\begin{itemize}
+% 		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
+% 		\item uses $n+1$ qubits
+% 		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
+% 		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
+% 	\end{itemize}
+% \end{thm}
+% \begin{prf}
+% 	We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
+% 	$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
+% 		$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
 
-Now we present the proof that $\set{H, \Lambda^2(X)}$ is indeed a universal gate set from \cite{quant-ph/0301040}: \Ethan{This definitely belongs in the appendix instead...}
-\begin{thm}
-	Let $C$ be a circuit that:
-	\begin{itemize}
-		\item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
-		\item uses $n$ qubits
-	\end{itemize}
-	Then a classical machine given $C$ can compute a circuit $C'$ that:
-	\begin{itemize}
-		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
-		\item uses $n+1$ qubits
-		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
-		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
-	\end{itemize}
-\end{thm}
-\begin{prf}
-	We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
-	$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
-		$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
+% 	Now consider the transform on quantum states
+% 	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
+% 	where $\Re$ and $\Im$ denote real and imaginary parts respectively.
 
-	Now consider the transform on quantum states
-	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
-	where $\Re$ and $\Im$ denote real and imaginary parts respectively.
-
-	This transform commutes with Hadamard gates on the respective qubit.
+% 	This transform commutes with Hadamard gates on the respective qubit.
 On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turn it into a combination of Hadamard and Toffoli gates.
 Mathematically,
-	$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
-	$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
+% 	$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
+% 	$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
 
-	We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
-	\begin{itemize}
-		\item $C'$ uses only Hadamard and Toffoli gates.
-		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
-		\item When $x$ is classical, $\mathcal{F}(x)=x||0$.
+% 	We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
+% 	\begin{itemize}
+% 		\item $C'$ uses only Hadamard and Toffoli gates.
+% 		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
+% 		\item When $x$ is classical, $\mathcal{F}(x)=x||0$.
 So $F\circ C(x)=C'(x||0)$.
 It is simple \hannote{need a little more work?}to verify that $\mathcal{F}$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
-	\end{itemize}
-\end{prf}
-
-\subsection{Reducing quantum circuit to local Hamiltonian}
+% 	\end{itemize}
+% \end{prf}
 
@@
 
-\subsection{Checking the ground state of the local Hamiltonian}
+\subsection{TBA}
 

### 2020-04-12 qpip0.tex
Updates from Overleaf

@@
 
-In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave the following 4-round interactive protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine.
+In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave a 4-round interactive protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine, which we describe below while omitting the implementation details.
 
@@
 
-\begin{lem}~\label{lem:trivial-4-round-strategy}
+\begin{lem}[\hannote{ref}\hannote{unused}]~\label{lem:trivial-4-round-strategy}
     For any input, there exist a prover strategy for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{n}$ in the testing round and \hannote{binding?}.
@@
 
-\begin{lem}[another triangle inequality for computational distance]\label{lem:computational-triangle}
+\begin{lem}[another triangle inequality for computational distance \hannote{unused}]\label{lem:computational-triangle}
 Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.
@@
 	\item The verifier and prover run Protocol~\ref{proto:urmila4}, with the following parameters: $h$ is chosen from previous step, $n_{commit}=M \times$ (number of qubits in $\ket{\psi_{C'(x)}}$), where $n_{commit}$ is the $n$ for Protocol~\ref{proto:urmila4}, and the honest prover choose $M$ copies of $\ket{\psi_{C'(x)}}$ as $\rho$.
+We also allow a cheating prover to send $\bot$ in the second round of Protocol~\ref{proto:urmila4} to abort the process.\footnote{This is useless for the cheating prover but useful for proving our theorem.} If the verifier receives $\bot$ in the second round, he outputs $(\Rej,\bot)$ and terminates the protocol.
 
@@
 $$z_i\defeq \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
-where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round.
+where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round. \hannote{need to average $pk$ here.}
 
@@
 
-For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}: The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
+For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}: The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of Protocol~\ref{proto:urmila4} in Protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
 The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.

### 2020-04-12 preliminaries.tex
Add thm # from Mahadev QFHE

@@
 
-\begin{theorem} [from \cite{mahadev_qfhe}]
+\begin{theorem} [Theorem 1.1 in \cite{mahadev_qfhe}]
 	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine,

### 2020-04-12 preliminaries.tex
Handle more action items

@@
 For two densities $f_1$ and $f_2$ over the same finite domain $X$, we write $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ for their total variation distance.
+We write $x\xleftarrow{\$}X$ when $x$ is sampled uniformly at random from the set $X$.
 
@@
 \begin{definition}
+	\label{dfn:stats-secure-proto-sampbqp}
 	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
+\Ethan{Or, where to put this poly dependence?
+And is this $\exists\poly$ or $\forall\poly$?
+Both sounds strange.}
 	We say $\Pi$ is a statistically sound protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
@@
 \begin{definition}
-	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
-	We say $\Pi$ is a computationally sound protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
-	\begin{itemize}
-		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
-		\item Let $(d, z)\leftarrow(P, V)(x, 1^{1/\varepsilon}, 1^\lambda)$, then $d=\Rej$ with probability at most $c(\lambda)$.
-		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
-			Define $z_{ideal}$ by
-			$$\begin{cases}
-				z_{ideal}=\bot & \text{if } d=\Rej\\
-				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
-			\end{cases}$$
-			then for all adversary, its probability to successfully distinguish a sample of $(d, z)$ from that of $(d, z_{ideal})$ is less than $\frac{1}{2}+\frac{\varepsilon}{2}$
+	Define everything as in \Cref{dfn:stats-secure-proto-sampbqp}.
+	We say $\Pi=(P, V)$ is \emph{computationally sound} instead of statistically if instead of 
+	$\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$,
+	we have that the probability for any adversary to successfully distinguish a sample of $(d, z)$ from that of $(d, z_{ideal})$ is less than $\frac{1}{2}+\frac{\varepsilon}{2}$.
 	\Ethan{Something like this? Or need protocol or specify prior probability is 1/2 each?}
-	\end{itemize}
 \end{definition}

### 2020-04-12 qpip.tex
Handle more action items

@@
 		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
-		\item Accuracy parameter $1^{1/\varepsilon}$ where $\varepsilon=\frac{1}{\poly(\lambda)}$ \Ethan{Just say between 0 and 1; specify poly lambda in thm statement}
+		\item Accuracy parameter $1^{1/\varepsilon}$ where $\varepsilon\in(0, 1)$
 	\end{itemize}
@@
 		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
+		\item Let $s=n+T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$
 		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
@@
 			Let $Y=\sum_{i\in I} y_i$.
-If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{72\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ is the constant specified in \Cref{cor:HamCheck}, then the verifier outputs $(\Acc, z)$.
+If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{72\left(T+\frac{6T}{\varepsilon}\right)^5}$ and $c\in\bbR$ is the constant specified in \Cref{cor:HamCheck}, then the verifier outputs $(\Acc, z)$.
 			Else, it outputs $(\Rej, \bot)$.
@@
 It is simple to check that $\VSamp$ runs in $\poly(n, \lambda, \frac{1}{\epsilon})$ time.
+\Ethan{Maybe this is less work than defining a general ``efficient verifier", since $\BQP$ and $\SampBQP$ have different inputs}
 We now show its completeness and soundness.
@@
 	$\PiSamp$ has negligible completeness error and is statistically sound.
-	\Ethan{Should also say $\lambda$ and $\varepsilon$ are inverse poly related. Or actually, maybe specify that in soundness dfn.}
-
-	\Ethan{Might want to define verifier being efficient (poly-time) there too}
+	\Ethan{TODO Fix this. Figure out where to put the inverse poly dependence between lambda and eps.}
 \end{thm}
@@
 	$$\Prob{Y>\frac{m}{2}-\varepsilon m}\leq\negl(\lambda).$$
-	\Ethan{So its rejection chance is...}
+	So $\VSamp$ has negligible probability to reject.
 
 	Now we show soundness.
-	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier. \Ethan{on inputs x, eps, lambda...}
+	Suppose $\PSampstar$ is a cheating prover that, on inputs $x, 1^{1/\varepsilon}, 1^\lambda$, sends some $\sigma$ to the verifier.
 
@@
 	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes m+1}$
-	such that for all quantum-classical channels $\Lambda_i$ acting on registers with size of $\ket{\psi_{C'(x)}}$ \Ethan{Make that size another variable}:
+	such that for all quantum-classical channels $\Lambda_i$ acting on registers of size $s$:
 	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}

### 2020-04-12 hamiltonian.tex
Add discussion notes

@@
 \label{sec:Hamiltonian}
+
+\XW{merge Section 3 and 4; also easy the discussion}
 
@@
 \newcommand{\histpsi}[1]{\ket{\psi_{#1}^{\mathrm{hist}}}}
+\newcommand{\LHXZ}[1]{\mathrm{LH}_{\mathrm{XZ}}^{#1}}
 
@@
 we need to construct X-Z only local Hamiltonians. 
-\XW{TOADD: some old references}
-We achieve this by choosing one particular universal gate set and will include our construction for the sake of completeness.
+Indeed, this has been shown possible in, e.g.,~\cite{PhysRevA.78.012352}, which serves as the starting point of our construction.
 
-\XW{TOADD: some orgainization}
-
+%\XW{TOADD: some orgainization}
 %\XW{highlight the different requirement from the normal Local Hamiltonian reduction; and highlight a bit about the solution idea}
@@
     \end{equation}
-    where the first register refers to the input, the second refers to the work space which is initialized to $\ket{0}$, and the last refers to the clock space which encodes the time information.
+    where the first register refers to the input, the second refers to the work space ($\mathrm{poly}(n)$ size) which is initialized to $\ket{0}$, and the last refers to the clock space which encodes the time information.
 Note that $\hat{t}$ could be some representation of $t$=0,..., $T$ up to design choice.
@@
 
-\XW{define $k$-local XZ Hamiltonian}
+% \XW{define $k$-local XZ Hamiltonian}
+% We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$ as below; note that this spans a subspace of $5$-local Hamiltonians.
 
-We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$ as below; note that this spans a subspace of $5$-local Hamiltonians.
-\begin{dfn}
-	$$\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \abs{\set{i: U_i\ne I}}\leq 5}$$
+We define the X-Z local Hamiltonian of interest as follows:
+
+\begin{dfn}[$k$-local X-Z Hamiltonian] For any $n$-qubit system, the set of $k$-local X-Z terms, denoted by $\LHXZ{k}$, contains Hermitian matrices that apply non-trivially on at most $k$ qubits as a product of Pauli $X$ and $Z$ terms.
+Namely,
+\begin{equation}
+  \LHXZ{k} = \left\{h_1 \otimes h_2 \otimes \ldots \otimes h_n: \forall i \in [n], h_i \in \{I, X, Z\}, \text{and}, \abs{\set{i: h_i=X \text{ or }Z}} \leq k. \right \}. 
+\end{equation}
+A $k$-local X-Z Hamiltonian $H$ is a linear combination of terms from $\LHXZ{k}$. Namely, 
+\begin{equation}
+  H = \sum_i \alpha_{i} H_i,  \quad \forall i, \alpha_i \in R,  H_i \in \LHXZ{k}.
+\end{equation}
 \end{dfn}
 
-\XW{cite the results that Toffoli and Hadamard gates
-and add the fact}
+As our starting point, we include the existing result of constructing X-Z local Hamitonians for general $\BQP$ computation.
+First, we note the fact Toffoli and Hadamard gates form a universal gate set for quantum computation~\cite{Shi03, quant-ph/0301040}.
+It is easy to see that both Toffoli and Hadamard gates can be represented as linear combinations of terms from $\LHXZ{}$. For example, 
+\begin{equation}
+    \mathrm{(Hadamard)} \quad H \equiv \frac{1}{\sqrt{2}} \begin{pmatrix}1&1\\1&-1\end{pmatrix} = \frac{1}{\sqrt{2}}\left (X+Z\right).
+\end{equation}
+The Toffoli gate maps bits $(a,b,c)$ to $(a,b, c \oplus (a \text{ and } b))$, which can be decomposed as $\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$ where $\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$.
 
-Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
-Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
-Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
-\begin{thm}
-	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
-\end{thm}
-\begin{prf}
-	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
-	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
-	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
-\end{prf}
+% Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
+% Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
+% Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
+% \begin{Fact}
+%     	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
+% \end{Fact}
+% \begin{prf}
+% 	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
+% 	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
+% 	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
+% \end{prf}
+
+Moreover, it is known in~\cite{PhysRevA.78.012352} about how to convert Kitaev's original 5-local Hamiltonian construction~\cite{kitaev2002classical} to a 5-local X-Z Hamiltonian. Precisely,
+
+We will follow the unary clock representation from~\cite{kitaev2002classical}, i.e., valid
 
@@
 	\end{itemize}
+\end{thm}
+
+We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which describes the conditions under which we can estimate the ground state energy of $H_1 + H_2$ with that of $H_1\big|_{\ker H_2}$.
+
+\begin{thm}[\Ethan{TODO thm number from src}]
+	\label{thm:proj1}
+	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on some Hilbert space $\cH=\cS+\cS^\bot$.
+	The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
+	$$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}^2}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
+\end{thm}
+
+We will instead use the following formulation, which can be obtained by relabeling variables from above.
+
+\begin{thm}
+	\label{thm:projection}
+	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
+	$$J=\frac{11\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
+	then we have
+	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
+\end{thm}
+\begin{proof}
+	Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least nonzero eigenvalue of $JH_2$ is greater than $10\norm{H_1}$.
+\end{proof}
+
+De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
+There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on number of qubits in each subsystem.
+\begin{thm}
+	\label{deFinetti}
+	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state on registers $A_1,\ldots,A_k$ where each register is $s$ qubits,
+	then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
+	$$\max_{\Lambda_1,\ldots,\Lambda_l}
+	\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1
+	\leq\sqrt{\frac{2l^2s}{k-l}}$$
+	where $\Lambda_i$ are quantum-classical channels.
 \end{thm}

### 2020-04-12 preliminaries.tex
Add discussion notes

@@
 We have $\norm{\rho_1-\rho_2}_{tr}\leq\sqrt{1-F(\rho_1, \rho_2)}$.
-For two densities $f_1$ and $f_2$ over the same finite domain $X$, we write $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ for their total variation distance.
+For two distributions $f_1$ and $f_2$ over the same finite domain $X$, we write $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ for their total variation distance,
+and we say $f_1$ and $f_2$ are $\varepsilon$-close if $\norm{f_1-f_2}_{TV}\leq\varepsilon$. \Ethan{TODO Copy and paste this for trace dist.}
 We write $x\xleftarrow{\$}X$ when $x$ is sampled uniformly at random from the set $X$.
@@
 
-\Ethan{I removed the definition of $\BQP$ since nobody else defines it in their papers anyways}
+\subsection{Sampling Problems}
 
-We define search and sampling versions of $\BQP$ based on \cite{aaronson_2013}.
+We define the sampling version of $\BQP$ based on \cite{aaronson_2013}.
 
 \begin{definition} [sampling problem]
-	A \emph{sampling problem} is a collection of probability distributions $(D_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{p(n)}$ for some fixed polynomial $p$.
+	A \emph{sampling problem} is a collection of probability distributions $(D_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{m(n)}$ for some fixed polynomial $m$.
 \end{definition}
@@
 \begin{definition} [$\SampBQP$]
-	$\SampBQP$ is the class of sampling problems $\left(D_x\right)_{x\in\set{0, 1}^*}$ for which there exists an efficient $\BPP$ machine that, on input $(n, 1^{1/\varepsilon})$, outputs a quantum circuit (that is, a sequence of unitary gates) $C$ such that for all $x\in\zo^n$, the standard basis measurement outcome on some designated output register \Ethan{Feels incredibly wordy.
-Not sure if the word ``register" here feels right either.} of $C(x)$ is $\varepsilon$-close to $D_x$.
+	$\SampBQP$ is the class of sampling problems $\left(D_x\right)_{x\in\set{0, 1}^*}$ that can be (approximately) sampled by polynomial-size uniform quantum circuits.
+Namely, there exists a Turing machine $M$ such that for every $n \in \bbN$ and $\varepsilon \in (0,1)$, $M(1^n, 1^{1/\eps})$ outputs a quantum circuit $C$ in $\poly(n, 1/\varepsilon)$ time such that for every $x \in \zo^n$, the output of $C(x)$ (measured in standard basis) is $\eps$-close to $D_x$.
 \end{definition}
 
-\subsection{Quantum Prover Interactive Protocol (QPIP)}
+\subsection{Quantum Prover Interactive Protocols (QPIP)}
+
+\Ethan{TODO, lower priority: define protocols}
+
 We model the interaction between a (almost classical) client and a quantum server following \cite{FOCS:Mahadev18a}.
@@
 	\begin{itemize}
-		\item $P$ is run by the prover, a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
-		\item $V$ is run by the verifier, which is a hybrid machine of a classical part and a limited quantum part.
+		\item $P$ is a $\BQP$ \Ethan{wording; quantum poly time?} machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
+		\item $V$ is a hybrid machine of a classical part and a limited quantum part.
 The classical part is a $\BPP$ machine.
@@
 The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
-		\item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially \Ethan{Is this good enough, or should I try to say poly in input length?
-Input isn't defined yet.} many bits to either direction.
+		\item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially many bits to either direction.
+	\end{itemize}
+\end{definition}
+
+\Ethan{Sec. param. should be 1st param}
+
+\begin{definition} \Ethan{Wording at the beginning isn't consistent...}
+	We say \Ethan{quantify this as QPIP proto} $\Pi=(P, V)$ is a protocol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds.
+\begin{itemize}
+	    \item For every... TODO INTERFACE
+		\item (Completeness): For all security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
+		$\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
+		\item (Soundness): For all cheating $\BQP$ prover $P^*$ \Ethan{TODO think about why this has to be quantified first before lambda}, for sufficiently large security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
 	\end{itemize}
@@
 \begin{definition}
-	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ with completeness error $c$ and soundness error $s$ if for all $x\in\zo^*$ and security parameter $1^\lambda$:
+	\label{dfn:stats-secure-proto-sampbqp}
+	Let \Ethan{QPIP proto.} $\Pi=(P, V)$ be a protocol.
+	We say $\Pi$ is a statistically sound protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and statistical (resp., computational) soundness, if for all $x\in\zo^*$ \Ethan{put other params here.
+lambda first, then x and eps in terms of lambda with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$}:
 	\begin{itemize}
-		\item If $x\in L$, then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
-		\item If $x\notin L$, then for all cheating prover $P^*$, $\Pr\left[(P^*, V)(x, 1^\lambda)=\Acc\right]<s(\lambda)$.
+		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$. \Ethan{Mention length of z too. Also mention z is bot if d is rej}
+		\item (Completeness): Let $(d, z)\leftarrow(P, V)(x, 1^{1/\varepsilon}, 1^\lambda)$, then $d=\Rej$ with probability at most $c(\lambda)$.
+		\item (Statistical soundness): For all cheating prover $P^*$,....    Consider the following experiment:
+		\begin{itemize}
+		    \item Let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
+		    \item Define $z_{ideal}$ by
+			$$\begin{cases}
+				z_{ideal}=\bot & \text{if } d=\Rej\\
+				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
+			\end{cases}$$.
 		\end{itemize}
-\end{definition}
+		It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$.
 
-For $\SampBQP$ protocols, the accuracy error is encoded in the $\SampBQP$ instance itself, so there are no soundness parameters.
+		\Ethan{Below is right, not sure what's above}
 
-\begin{definition}
-	\label{dfn:stats-secure-proto-sampbqp}
-	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
-\Ethan{Or, where to put this poly dependence?
-And is this $\exists\poly$ or $\forall\poly$?
-Both sounds strange.}
-	We say $\Pi$ is a statistically sound protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
-	\begin{itemize}
-		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
-		\item Let $(d, z)\leftarrow(P, V)(x, 1^{1/\varepsilon}, 1^\lambda)$, then $d=\Rej$ with probability at most $c(\lambda)$.
-		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
+		let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
 			Define $z_{ideal}$ by
@@
 			then $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$.
+		\item \Ethan{D is BQP}
+		$ \abs{\Pr[D(1^{\lambda}, d,z) = 1] - \Pr[D(1^{\lambda}, d,z_{ideal}) = 1]} \leq \eps $
+
+		TODO Comp. soundness here...?
 	\end{itemize}
@@
 
-We define blindness of a protocol as follows.
+We define blindness of a protocol as follows. \Ethan{Input x is private input now... the rest are still common input... etc.}
 
 \begin{definition}
+	Let $(P, V)$ be an interactive protocol with security parameter $\lambda$. \Ethan{Define the version with eps, say that it's fine without eps for BQP} \Ethan{TODO Quantify cheating prover}
 	Let $\lambda$ be a security parameter.
-	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
 	Then it is \emph{blind} if the following ensembles are computationally indistinguishable over $\lambda$:
@@
 
-\subsection{Projection Lemma}
+% \subsection{Projection Lemma}
 
-We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which describes the conditions under which we can estimate the ground state energy of $H_1 + H_2$ with that of $H_1\big|_{\ker H_2}$.
+% We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which describes the conditions under which we can estimate the ground state energy of $H_1 + H_2$ with that of $H_1\big|_{\ker H_2}$.
 
-\begin{thm}
-	\label{thm:proj1}
-	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on some Hilbert space $\cH=\cS+\cS^\bot$.
-	The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
-	$$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}^2}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
-\end{thm}
+% \begin{thm}[\Ethan{TODO thm number from src}]
+% 	\label{thm:proj1}
+% 	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on some Hilbert space $\cH=\cS+\cS^\bot$.
+% 	The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
+% 	$$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}^2}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
+% \end{thm}
 
-We will instead use the following formulation, which can be obtained by relabeling variables from above.
+% We will instead use the following formulation, which can be obtained by relabeling variables from above.
 
-\begin{thm}
-	\label{thm:projection}
-	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
-	$$J=\frac{11\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
-	then we have
-	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
-\end{thm}
-\begin{proof}
-	Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least nonzero eigenvalue of $JH_2$ is greater than $10\norm{H_1}$.
-\end{proof}
+% \begin{thm}
+% 	\label{thm:projection}
+% 	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
+% 	$$J=\frac{11\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
+% 	then we have
+% 	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
+% \end{thm}
+% \begin{proof}
+% 	Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least nonzero eigenvalue of $JH_2$ is greater than $10\norm{H_1}$.
+% \end{proof}
 
-\subsection{Quantum de Finetti Theorem under Local Measurements}
+% \subsection{Quantum de Finetti Theorem under Local Measurements}
 
-De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
-There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on number of qubits in each subsystem.
-\begin{thm}
-	\label{deFinetti}
-	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state on registers $A_1,\ldots,A_k$ where each register is $s$ qubits,
-	then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
-	$$\max_{\Lambda_1,\ldots,\Lambda_l}
-	\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1
-	\leq\sqrt{\frac{2l^2s}{k-l}}$$
-	where $\Lambda_i$ are quantum-classical channels.
-\end{thm}
+% De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
+% There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on number of qubits in each subsystem.
+% \begin{thm}
+% 	\label{deFinetti}
+% 	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state on registers $A_1,\ldots,A_k$ where each register is $s$ qubits,
+% 	then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
+% 	$$\max_{\Lambda_1,\ldots,\Lambda_l}
+% 	\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1
+% 	\leq\sqrt{\frac{2l^2s}{k-l}}$$
+% 	where $\Lambda_i$ are quantum-classical channels.
+% \end{thm}
 
 \subsection{Quantum Homomorphic Encryption Schemes}
+
+\Ethan{Just define QHE}
 
@@
 We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
-We start by presenting the interface of a homomorphic encryption scheme:
+We start by presenting the definition of a homomorphic encryption scheme:
 \begin{definition}
+    \Ethan{Do more copying}
 	A leveled homomophic encryption scheme is tuple of algorithms \linebreak $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
@@
 
+\Ethan{Maybe add correctness}
+
 We also recall the security definition for a FHE scheme.
@@
 	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
-	$$\abs{Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
+	$$\abs{Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(1))=1]}\leq\mu(\lambda)$$
 	where $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
@@
 	\begin{itemize}
-		\item $\QGen$ can be done classically.
+		\item $\QGen$ produces classical keys
 		\item In the case where the plaintext is classical, $\QEnc$ can be done classically.
-		\item Its ciphertext can be homomorphically measured, after which $\QDec$ can also be done classically.
+		\item Its ciphertext can be homomorphically measured, after which $\QDec$ can also be done classically. \Ethan{Underlying msg is classical = ct is classical = can be classical decrypted}
 	\end{itemize}

### 2020-04-12 qpip.tex
Add discussion notes

@@
 
-\Ethan{Actual technical part starts here}
-
-\Ethan{New changes: Re-parametrize so final error is eps. Write more details for soundness about the classical mix.}
-
 \begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for the $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$}
@@
 		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
-		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$. \Ethan{Cite previous theorem}
+		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$. \Ethan{Refer to the appropriate previous theorem}
 		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
@@
 		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{21}\lambda^2}{\varepsilon^{31}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
-		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t.
-$\abs{I}=m$ where $m=\frac{T^{10}\lambda}{\varepsilon^{14}}$, and $k\xleftarrow{\$}[M]\setminus I$.
-\hannote{$\xleftarrow{\$}$ ?} \Ethan{Sample randomly from.
-Will add it to preliminary section.}
+		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}\lambda}{\varepsilon^{14}}$, and $k\xleftarrow{\$}[M]\setminus I$.
 			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
@@
 			\item If $i\in I$, run $y_i\leftarrow\cV_{\GS}(\rho_i)$.
-			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $z$.
+			\item Else if $i=k$, measure the data register \Ethan{Revisit this name. Nobody has defined/used this register before.} of $\rho_i$ under the standard basis and save the outcome as $z$.
 			\item Else, discard $\rho_i$.
@@
 It is simple to check that $\VSamp$ runs in $\poly(n, \lambda, \frac{1}{\epsilon})$ time.
-\Ethan{Maybe this is less work than defining a general ``efficient verifier", since $\BQP$ and $\SampBQP$ have different inputs}
 We now show its completeness and soundness.
@@
 	$\PiSamp$ has negligible completeness error and is statistically sound.
-	\Ethan{TODO Fix this. Figure out where to put the inverse poly dependence between lambda and eps.}
 \end{thm}

### 2020-04-12 qpip0.tex
Add discussion notes

@@
 
-\begin{lem}[\hannote{ref}\hannote{unused}]~\label{lem:trivial-4-round-strategy}
-    For any input, there exist a prover strategy for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{n}$ in the testing round and \hannote{binding?}.
+\begin{lem}[\hannote{ref}]~\label{lem:trivial-4-round-strategy}
+    For any input, there exist a prover strategy $(U_{trivial,0},U_{trivial})$ for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{n}$ in the testing round and \hannote{binding?}.
 \end{lem}
@@
 
-	\item The verifier and prover run Protocol~\ref{proto:urmila4}, with the following parameters: $h$ is chosen from previous step, $n_{commit}=M \times$ (number of qubits in $\ket{\psi_{C'(x)}}$), where $n_{commit}$ is the $n$ for Protocol~\ref{proto:urmila4}, and the honest prover choose $M$ copies of $\ket{\psi_{C'(x)}}$ as $\rho$.
-We also allow a cheating prover to send $\bot$ in the second round of Protocol~\ref{proto:urmila4} to abort the process.\footnote{This is useless for the cheating prover but useful for proving our theorem.} If the verifier receives $\bot$ in the second round, he outputs $(\Rej,\bot)$ and terminates the protocol.
+	\item \label{step:urmila-in-naive} The verifier and prover run Protocol~\ref{proto:urmila4}, with the following parameters: $h$ is chosen from previous step, $n_{commit}=M \times$ (number of qubits in $\ket{\psi_{C'(x)}}$), where $n_{commit}$ is the $n$ for Protocol~\ref{proto:urmila4}, and the honest prover choose $M$ copies of $\ket{\psi_{C'(x)}}$ as $\rho$.
+We also allow a cheating prover to send $\bot$ in the fourth round of Protocol~\ref{proto:urmila4} if $c=1$ to abort the process.\footnote{This is useless for the cheating prover but useful for proving one of our theorems.} If the verifier receives $\bot$ in the fourth round, he outputs $(\Rej,\bot)$ and terminates this protocol.
 
-	\item If $c=1$, the verifier finished the verification step of Protocol~\ref{ProtoQPIP1} by using $z$ from Protocol~\ref{proto:urmila4} as the measurement result he would get and outputs $(d,z_{naive})$
+	\item If $c=1$, the verifier finished the verification step of Protocol~\ref{ProtoQPIP1} by using $z_{commit}$ from Protocol~\ref{proto:urmila4} as the measurement result he would get and outputs $(d,z_{naive})$.
 
@@
 \begin{lemma}\label{lem:naive-qpip0-binding}[binding property of  Protocol~\ref{proto:qpip0_naive} ]
-If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen, $\norm{(d,z_{naive})-(d,z_{ideal})}_q \leq O(\eps)$, unless LWE can be efficiently solved by a quantum computer.
+If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen,
+
+$$\norm{(d,z_{naive})-(d,z_{ideal})}_q \leq O(\eps),$$
+
+unless LWE can be efficiently solved by a quantum computer. 
 \end{lemma}
@@
 By Lemma~\ref{lem:urmila-binding}, if the prover passes the testing round with probability $1-\negl(n)$, there exist a $\rho$ such that $\norm{z_{commit}- M_{XZ}(\rho,h)}_q \leq \negl(n)$.
+Note that the prover can choose to abort, so $z_{commit}$ and $\rho$ are subnormalized.
 Let $Ver$ be the verification operation run by Protocol~\ref{ProtoQPIP1} on the measurement outcome.
-\hannote{describe better} Since $Ver$ is an efficient process and $Ver(z_{commmit})=(d,z_{naive})$, we have that
+\hannote{describe better} Since $Ver$ is an efficient process and $Ver(z_{commmit})+p_{abort}(\Rej,\bot)=(d,z_{naive})$, we have that
 
 \begin{equation} \label{eq:z=verM}
-    \norm{(d,z_{naive})-Ver( M_{XZ}(\rho,h))}_q \leq \negl(n).
+    \norm{(d,z_{naive})-(Ver( M_{XZ}(\rho,h))+p_{abort}(\Rej,\bot))}_q \leq \negl(n).
 \end{equation}
@@
  \end{equation}
-   Combined with Equation~\ref{eq:z=verM} and Lemma~\ref{lem:computational-triangle0}, we have that
+   Combined with Equation~\ref{eq:z=verM} and Lemma~\ref{lem:computational-triangle0}, and note that $\norm{(\Rej,\bot)-(d,z_{ideal})}=0$, we have that
    \begin{equation}
@@
 \begin{theorem}\label{thm:qpip0}
-    Protocol~\ref{proto:QPIP0samp} is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and $\eps$ computational soundness error\hannote{definition}. 
+    Protocol~\ref{proto:QPIP0samp} is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and $O(\eps)$ computational soundness error\hannote{definition}. 
 \end{theorem}
@@
 
-For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}: The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of Protocol~\ref{proto:urmila4} in Protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
-The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
+For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}.
+Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of Protocol~\ref{proto:qpip0_naive} where Protocol~\ref{proto:urmila4} is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.
+
+The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of Protocol~\ref{proto:urmila4} in Protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
+The prover then picks a uniformly random $\gamma$ and  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
 If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead.
 This is possible because all the inputs are classical.
-On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}.
-otherwise he continues to run the strategy of Lemma~\ref{lem:trivial-4-round-strategy}.
-We denote the random variable the verifier would get on the testing round as $z_{construct}$.
+On the fourth round, there are four possibilities depending on $c$ and whether the prover generated $\ket{\psi_{1^{i-1}1,\gamma}}$.
+If $c=0$ and the prover generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}.
+If $c=1$ and the prover generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he runs $U$ and check whether every copy except the $i$-th copy would be accepted.
+If all $m-1$ copies acceptes, he reply with the $i$-th copy, otherwise reply $\bot$.
+If $c-0$ and the prover failed to generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he runs $U_{trivial}$ and repies.
+If $c=1$ and the prover failed to generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he replies with $\bot$.
+\footnote{Recall that $c=0$ is the testing round and $c=1$ is the Hadamard round.}
 
-==== old ===
+%We denote the random variable the verifier would get on the Hadamard round as $z_{composite}$.
+Also define $(d,z_{composite}) \defeq (\Acc, z_{composite}) + (1-|z_{composite}|)(\Rej,\bot)$ \hannote{correct notation?}
 
-For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for Protocol~\ref{proto:urmila4}: on the first round the verifier pick $h$ from distribution specified by ????
-of Protocol~\ref{ProtoQPIP1}.
-On the second round, the prover start with picking a uniformaly random $i\in [m]$.
-The prover then tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
-The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
-If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead.
-This is possible because all the inputs are classical.
-On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}.
-otherwise he continues to run the strategy of Lemma~\ref{lem:trivial-4-round-strategy}.
-We denote the random variable the verifier would get on the testing round as $z_{construct}$.
+Denote the result we would get when $c=1$ by $(d,z_{composite,i})$.
+
+By Lemma~\ref{lem:trivial-4-round-strategy} and property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when $c=0$.
+Therefore by Lemma~\ref{lem:naive-qpip0-binding},
+\begin{align}
+    \norm{(d,z_{composite,i})-(d,z_{ideal,i})}_q \leq O(\eps)
+\end{align}
+
+By construction, when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$.
+Also note that this is the only case where the verifier won't reject, so $(d,z_{composite,i})=(d,z_{good,i})$, where  $(d,z_{good,i}) \defeq (\Acc, z_{good,i}) + (1-|z_{good,i}|)(\Rej,\bot)$ \hannote{correct notation?} .
+Therefore
+
+\begin{align}
+    \norm{(d,z_{good,i})-(d,z_{ideal,i})}_q \leq O(\eps).
+\end{align}
+
+Average over $i\in[m]$ we get
+
+\begin{align}
+    \norm{(d,z_{good})-(d,z_{ideal})}_q \leq O(\eps).
+\end{align}
+\hannote{do we lose a factor of $m$?}
+Recall that by Eq~\ref{eq:z-z-good} we have $\norm{z-z_{good}}_1 \leq \eps$ if we pick $m,T,\gamma_0=???$ \hannote{tune eps}, which implies 
+\begin{align} 
+    \norm{(d,z)-(d,z_{good})}_1 \leq \eps
+\end{align}
+
+Therefore by Lemma~\ref{lem:computational-triangle0}, we have  
+\begin{align}
+     \norm{(d,z)-(d,z_{ideal})}_q \leq O(\eps)
+\end{align}
+\hannote{the composition of z ideal and triangle ineq is sketchy lol.}
+
+\end{proof}
+
+===========
+
+\hannote{below are unused old fragments}
+
+========= old
 
@@
 
-\end{proof}
+==== old ===
 
-===========
+For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for Protocol~\ref{proto:urmila4}: on the first round the verifier pick $h$ from distribution specified by ????
+of Protocol~\ref{ProtoQPIP1}.
+On the second round, the prover start with picking a uniformaly random $i\in [m]$.
+The prover then tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
+The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
+If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead.
+This is possible because all the inputs are classical.
+On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}.
+otherwise he continues to run the strategy of Lemma~\ref{lem:trivial-4-round-strategy}.
+We denote the random variable the verifier would get on the testing round as $z_{construct}$.
 
-\hannote{below are unused old fragments}
 ===

### 2020-04-13 hamiltonian.tex
Add proj lemma #
Updates from Overleaf

@@
 \def \Hprop {H_{\mathrm{prop}}}
+\def \Hclock {H_{\mathrm{clock}}}
 \newcommand{\histpsi}[1]{\ket{\psi_{#1}^{\mathrm{hist}}}}
@@
     \end{equation}
-    where the first register refers to the input, the second refers to the work space ($\mathrm{poly}(n)$ size) which is initialized to $\ket{0}$, and the last refers to the clock space which encodes the time information.
+    where the first register of $n$-qubit refers to the input, the second of $m$-qubit refers to the work space ($\mathrm{poly}(n)$ size) which is initialized to $\ket{0}$, and the last refers to the clock space which encodes the time information.
 Note that $\hat{t}$ could be some representation of $t$=0,..., $T$ up to design choice.
@@
 
-As our starting point, we include the existing result of constructing X-Z local Hamitonians for general $\BQP$ computation.
+As our starting point, we will include the existing result of constructing X-Z local Hamitonians for general $\BQP$ computation.
 First, we note the fact Toffoli and Hadamard gates form a universal gate set for quantum computation~\cite{Shi03, quant-ph/0301040}.
@@
 The Toffoli gate maps bits $(a,b,c)$ to $(a,b, c \oplus (a \text{ and } b))$, which can be decomposed as $\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$ where $\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$.
-
 % Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
@@
 % \end{prf}
+
+We will follow the unary clock register design from Kitaev's original 5-local Hamiltonian construction~\cite{kitaev2002classical}.
+Namely, valid unary clock states ($T$-qubit) are $\ket{00\ldots0}$, $\ket{10\dots0}$, $\ket{110\ldots0}$, etc, which span the ground energy space of the following local Hamiltonian:
+\begin{equation}
+    \Hclock= \sum_{t=1}^{T-1}\proj{01}_{t,t+1},
+\end{equation}
+where $\proj{01}_{t,t+1}$ stands for a projection on the $t$th and $(t+1)$th qubit in the clock register. 
+It is observed in~\cite{PhysRevA.78.012352} that $\Hclock$ can be reformulated as a linear combination of terms from $\LHXZ{}$ as follows, 
+\begin{equation}
+   \Hclock= \frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_t\otimes Z_{t+1}),
+\end{equation}
+where $Z_t$ refers to Pauli $Z$ operated on the $t$th qubit in the clock register.
+
+One can achieve so similarly for $\Hin$ and $\Hprop$.
+For the input condition, we want to make sure $x=(x_1, \ldots, x_n) \in \{0,1\}^n$ is in the input space and the workspace is initialized to $\ket{0}$ for all qubits at the time $0$.
+Namely, one can set $\Hin$ to be
+\begin{equation}
+    \Hin = \sum_{i=1}^n(I- \proj{x_i}_i)\otimes \proj{0}_1 + \sum_{i=1}^m \proj{0}_{n+i} \otimes \proj{0}_1, 
+\end{equation}
+where the last part $\proj{0}_1$ applies on to the first qubit in the clock register. One can rewrite $\Hin$ as 
+\begin{equation}
+ \Hin=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1) + \frac{1}{4} \sum_{i=1}^m (I - Z_{n+i}) \otimes (I + Z_1). 
+\end{equation}
+\XW{todo here}
+% Then, we ensure that the initial condition is set up correctly.
+% 	$$H_{in}=\sum_{i=1}^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
+% 	The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
+
+	Then, we ensure that the gates are applied correctly.
+	$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
+	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
+	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
+	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
+
+	We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least nonzero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
+
+	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since our gates are either Hadamard or Toffoli.
+	Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
+	$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
+	Extra care must be taken for boundary cases.
+	$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
+	$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
 
@@
 	We need to ensure the excited states of $H_{C(x)}$ have high eigenvalues.
-
-	First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
-	$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
-	As a sum of projections, clearly $H_{clock}\geq 0$. We shall also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
-	$$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
-	This can be checked by fixing the first and last qubit, then doing induction on the number of switches.
-
-	Then, we ensure that the initial condition is set up correctly.
-	$$H_{in}=\sum_{i=1}^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
-	The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
-	$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$
-
-	Then, we ensure that the gates are applied correctly.
-	$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
-	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
-	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
-	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-
-	We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least nonzero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
-
-	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since our gates are either Hadamard or Toffoli.
-	Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
-	$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
-	Extra care must be taken for boundary cases.
-	$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
-	$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
 

### 2020-04-13 preliminaries.tex
Updates from Overleaf

@@
 \end{definition}
+
+\subsection{Computational Indistinguishability}
+
+\begin{definition}[quantum computationally indistinguishable]\label{def:comp-indis}
+\hannote{move later}
+Let  $D_1$ and $D_2$ be distributions over $n$-bit string.
+We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes \emph{one} sample from $D_1$ as part of its input.
+We also denote "$D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable" as
+$$ \norm{D_1 - D_2}_q \leq \eps.$$
+And "$D_1$ and $D_2$  are not $\eps$-Q-computationally indistinguishable" as 
+$$ \norm{D_1 - D_2}_q > \eps.$$
+\end{definition}
+%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.
+
+\begin{rmk}
+We extend the definition of computational distance to a subnormalized distribution  $D$  by assuming $A(D)=0$ when $A$ fail to draw a sample from $D$.
+\end{rmk}
+
+\begin{rmk}\label{rmk:trace-to-comp}
+If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
+\end{rmk}
+
+\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
+    Let $D_1$, $D_2$, and $D_3$ be three distributions such that 
+    \begin{align}
+        \norm{D_1 -D_2}_q &\leq \eps \\ 
+        \norm{D_2 -D_3}_q &\leq \eps'. 
+    \end{align}
+    We have 
+    \begin{align}
+        \norm{D_1 -D_3}_q &\leq \eps+\eps'
+    \end{align}
+\end{lem}
+\begin{proof}
+For all quantum circuits $A$ with size $\poly(n)$, we have 
+\begin{align}
+    \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} \leq& \eps \\
+    \norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \leq& \eps',  
+\end{align}
+so 
+\begin{align}
+    &\norm{\Pr[A({D_1})=1]-\Pr[A({D_3})=1]} \nn \\
+    =& \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]+\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
+    \leq&  \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} +\norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
+    =& \eps +\eps' \nn
+\end{align}
+
+\end{proof}
 

### 2020-04-13 preliminaries.tex
Handle action items

--- 2020-04-12 preliminaries.tex
@@
 we write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.
-We write $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$.
+We write $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$,
 We have $\norm{\rho_1-\rho_2}_{tr}\leq\sqrt{1-F(\rho_1, \rho_2)}$.
+We say $\rho_1$ and $\rho_2$ are $\varepsilon$-close if $F(\rho_1, \rho_2)\leq\varepsilon$.
 For two distributions $f_1$ and $f_2$ over the same finite domain $X$, we write $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ for their total variation distance,
-and we say $f_1$ and $f_2$ are $\varepsilon$-close if $\norm{f_1-f_2}_{TV}\leq\varepsilon$. \Ethan{TODO Copy and paste this for trace dist.}
+and we say $f_1$ and $f_2$ are $\varepsilon$-close if $\norm{f_1-f_2}_{TV}\leq\varepsilon$.
 We write $x\xleftarrow{\$}X$ when $x$ is sampled uniformly at random from the set $X$.
@@
 
-\begin{definition} \Ethan{Wording at the beginning isn't consistent...}
-	We say \Ethan{quantify this as QPIP proto} $\Pi=(P, V)$ is a protocol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds.
+\begin{definition}
+	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
+	We say it is a prototol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds.
 \begin{itemize}
-	    \item For every... TODO INTERFACE
+		\item On public inputs $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
 		\item (Completeness): For all security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
 		$\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
-		\item (Soundness): For all cheating $\BQP$ prover $P^*$ \Ethan{TODO think about why this has to be quantified first before lambda}, for sufficiently large security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
+		\item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
 	\end{itemize}
@@
 	\label{dfn:stats-secure-proto-sampbqp}
-	Let \Ethan{QPIP proto.} $\Pi=(P, V)$ be a protocol.
-	We say $\Pi$ is a statistically sound protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and statistical (resp., computational) soundness, if for all $x\in\zo^*$ \Ethan{put other params here.
-lambda first, then x and eps in terms of lambda with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$}:
+	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
+	We say it is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and statistical (resp., computational) soundness if the following holds.
 	\begin{itemize}
-		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$. \Ethan{Mention length of z too. Also mention z is bot if d is rej}
-		\item (Completeness): Let $(d, z)\leftarrow(P, V)(x, 1^{1/\varepsilon}, 1^\lambda)$, then $d=\Rej$ with probability at most $c(\lambda)$.
-		\item (Statistical soundness): For all cheating prover $P^*$,....    Consider the following experiment:
+		\item On public inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x\in\zo^n$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$. If $d=\Acc$ then $z\in\zo^{m(n)}$, otherwise $z=\bot$.
+		\item (Completeness):
+			For all security parameter $\lambda\in\bbN$, accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$, and $x\in\zo^{\poly(\lambda)}$, 
+			Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\varepsilon}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
+		\item (Statistical soundness): For all cheating prover $P^*$,
+			sufficiently large $\lambda\in\bbN$, accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$, and $x\in\zo^{\poly(\lambda)}$, 
+			consider the following experiment:
 			\begin{itemize}
@@
 			It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$. 
-
-		\Ethan{Below is right, not sure what's above}
-
-		let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
-			Define $z_{ideal}$ by
-			$$\begin{cases}
-				z_{ideal}=\bot & \text{if } d=\Rej\\
-				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
-			\end{cases}$$
-			then $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$.
-		\item \Ethan{D is BQP}
-		$ \abs{\Pr[D(1^{\lambda}, d,z) = 1] - \Pr[D(1^{\lambda}, d,z_{ideal}) = 1]} \leq \eps $
-
-		TODO Comp. soundness here...?
+		\item (Computational soundness): Define $d, z, z_{ideal}$ same as above.
+			It holds that for all $\BQP$ distinguisher $D$,
+			$\abs{\Pr[D(1^{\lambda}, d,z) = 1] - \Pr[D(1^{\lambda}, d,z_{ideal}) = 1]} \leq \varepsilon $
 	\end{itemize}
-\end{definition}
-
-As sometimes one only achieves computational guarantees instead of statistical ones;
-we also model the corresponding situation for $\SampBQP$ protocols.
-
-\begin{definition}
-	Define everything as in \Cref{dfn:stats-secure-proto-sampbqp}.
-	We say $\Pi=(P, V)$ is \emph{computationally sound} instead of statistically if instead of 
-	$\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$,
-	we have that the probability for any adversary to successfully distinguish a sample of $(d, z)$ from that of $(d, z_{ideal})$ is less than $\frac{1}{2}+\frac{\varepsilon}{2}$.
-	\Ethan{Something like this? Or need protocol or specify prior probability is 1/2 each?}
 \end{definition}
@@
 
-% \subsection{Projection Lemma}
-
-% We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which describes the conditions under which we can estimate the ground state energy of $H_1 + H_2$ with that of $H_1\big|_{\ker H_2}$.
-
-% \begin{thm}[\Ethan{TODO thm number from src}]
-% 	\label{thm:proj1}
-% 	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on some Hilbert space $\cH=\cS+\cS^\bot$.
-% 	The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
-% 	$$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}^2}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
-% \end{thm}
-
-% We will instead use the following formulation, which can be obtained by relabeling variables from above.
-
-% \begin{thm}
-% 	\label{thm:projection}
-% 	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
-% 	$$J=\frac{11\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
-% 	then we have
-% 	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
-% \end{thm}
-% \begin{proof}
-% 	Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least nonzero eigenvalue of $JH_2$ is greater than $10\norm{H_1}$.
-% \end{proof}
-
-% \subsection{Quantum de Finetti Theorem under Local Measurements}
-
-% De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
-% There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on number of qubits in each subsystem.
-% \begin{thm}
-% 	\label{deFinetti}
-% 	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state on registers $A_1,\ldots,A_k$ where each register is $s$ qubits,
-% 	then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
-% 	$$\max_{\Lambda_1,\ldots,\Lambda_l}
-% 	\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1
-% 	\leq\sqrt{\frac{2l^2s}{k-l}}$$
-% 	where $\Lambda_i$ are quantum-classical channels.
-% \end{thm}
+\Ethan{Proj. lemma and de Finetti thm. were moved}
 

### 2020-04-13 qpip0.tex

@@
 
-\hannote{In this section, we modify the construction of \cite{FOCS:Mahadev18a} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}
+%\hannote{In this section, we modify the construction of \cite{FOCS:Mahadev18a} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}
 
-We then extend our scheme for $\QPIP_0$ using results from \cite{FOCS:Mahadev18a}.
+% We then extend our scheme for $\QPIP_0$ using results from \cite{FOCS:Mahadev18a}.
 
-Here we combine \cref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients.
-Combining them will cost polynomially rounds, so we use results from \cite{parallelrep} that allows parallel repetition to construct a constant-round protocol.
+In this section, we combine \cref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients.
+To boost the soundness, we need  polynomial rounds, so we use results from \cite{parallelrep} to run polynomially many copies in parallel and get a constant-round protocol.
 
@@
 Let $D_{\rho, h}$ be the distribution of the corresponding measurement results.
-
-\begin{theorem}
-    \label{Mahadev_QPIP0_Protocol_Interface}
-	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
-	\begin{itemize}
-	    \item The protocol runs either a ``Hadamard round" or a ``test round".
-	    \item With a test round, the verifier outputs nothing other than accept/reject
-	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
-	    \item (completeness) $\forall\rho\in\mathcal{B}^{\otimes n}$ and $h\in\set{0,1}^n$, there is a prover with negligible reject probability.
-Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_{\rho, h}$
-	    \item (soundness) Fix $\bbP'$ and $h$.
-Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round.
-Then $\exists\tilde\bbP$ s.t.
-$\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t.
-$D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
-		\item This is a 4-round protocol. The prover does not know whether it is a test or Hadamard round until the end of 3rd round.
-		\begin{enumerate}
-			\item The verifier generates $(k, td)$, ``key" and ``trapdoor". It sends the key to the prover.
-			\item The prover computes a classical ``commitment" $y$ and sends it to the verifier.
-			\item The verifier sends $c\in\set{0, 1}$, where $c=0$ corresponds to test round and $c=1$ corresponds to Hadamard round.
-			\item The prover computes and sends a classical string $a$
-		\end{enumerate}
-	\end{itemize}
-\end{theorem}
-
-\hannote{import urmila protocol description.. up}
-Here, we recall the Mahadev's protocol \cite{FOCS:Mahadev18a}.
-We only give a high-level description of the protocol and properties of it and omit the details since they are not needed to show our result.
-
-The protocol is run between a quantum prover $\pro$ and a classical verifier $\ver$ on a common input $x$.
-The aim of the protocol is to enable a verifier to classically verify $x\in \lang$ for a BQP language $\lang$ with the help of interactions with a quantum prover.
-The protocol is a 4-round protocol where the first message is sent from $\ver$ to $\pro$. 
-We denote the $i$-th message generation algorithm by $\ver_i$ for $i\in\{1,3\}$ or $\pro_i$ for $i\in \{2,4\}$ and denote the verifier's final decision algorithm by $\ver_\out$.
-Then a high-level description of the protocol is given below.
-\begin{description}
-\item[$\ver_1$:] On input the security parameter $1^\secpar$ and $x$, it generates a pair $(\key,\td)$ of a``key" and ``trapdoor", sends $\key$ to $\pro$, and keeps $\td$ as its internal state.
-\item[$\pro_2$:] On input $x$ and $\key$, it generates a classical ``commitment" $\comy$ along with a quantum state $\ket{\st_\pro}$, sends $\comy$ to $\pro$, and keeps $\ket{\st_\pro}$ as its internal state.
-\item[$\ver_3$:] It randomly picks $c\sample \bit$ and sends $c$ to $\pro$.\footnote{The third message is just a public-coin, and does not depend on the transcript so far or $x$.}
-Following the terminology in \cite{FOCS:Mahadev18a}, we call the case of $c=0$ the ``test round" and the case of $c=1$ the ``Hadamard round".
-\item[$\pro_4$:] On input $\ket{\st_\pro}$ and $c$, it generates a classical string $\ans$ and sends $\ans$ to $\pro$.
-\item[$\ver_\out$:] On input $\key$, $\td$, $y$, $c$, and $\ans$, it returns $\top$ indicating acceptance or $\bot$ indicating rejection.
-In case $c=0$, the verification can be done publicly, that is, $\ver_\out$ need not take $\td$ as input.
-\end{description}
-
-For the protocol, we have the following properties:\\
-\noindent\textbf{Completeness:}
-For all $x\in \lang$, we have $\Pr[\langle \pro,\ver \rangle(x)]=\bot]= \negl(\secpar)$.\\
-\noindent\textbf{Soundness:}
-If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$, we have  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot]\leq 3/4$.
-
-We need a slightly different form of soundness implicitly shown in \cite{FOCS:Mahadev18a}, which roughly says that if a cheating prover can pass the ``test round" (i.e., the case of $c=0$) with overwhelming probability, then it can pass the ``Hadamard round" (i.e., the case of $c=1$) only with a negligible probability.
-\begin{lemma}[implicit in \cite{FOCS:Mahadev18a}]\label{lem:Mah_soundness}
-If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$ such that  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot\mid c=0]=\negl(\secpar)$, we have $\Pr[\langle \pro^*,\ver \rangle(x)]=\top\mid c=1]=\negl(\secpar)$.
-\end{lemma}
-
-We will also use the following simple lemma:
-\begin{lemma}\label{fact:perfectly_pass_test}
-There exists an efficient prover that passes the test round with probability $1$ (but passes the Hadamard round with probability $0$) even if $x\notin \lang$. 
-\end{lemma}
 
@@
 \begin{lem}[\hannote{ref}]~\label{lem:trivial-4-round-strategy}
-    For any input, there exist a prover strategy $(U_{trivial,0},U_{trivial})$ for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{n}$ in the testing round and \hannote{binding?}.
+    For any input, there exist a prover strategy $(U_{trivial,0},U_{trivial})$ for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{n}$ in the testing.
 \end{lem}
 
-\begin{definition}[quantum computationally indistinguishable]
-\hannote{move later}
-Let  $D_1$ and $D_2$ be distributions over $n$-bit string.
-We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes \emph{one} sample from $D_1$ as part of its input.
-We also denote "$D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable" as
-$$ \norm{D_1 - D_2}_q \leq \eps.$$
-And "$D_1$ and $D_2$  are not $\eps$-Q-computationally indistinguishable" as 
-$$ \norm{D_1 - D_2}_q > \eps.$$
-\end{definition}
-%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.
+% \begin{lem}[another triangle inequality for computational distance \hannote{unused}]\label{lem:computational-triangle}
+% Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.
 
-\begin{rmk}
-We extend the definition of computational distance to a subnormalized distribution  $D$  by assuming $A(D)=0$ when $A$ fail to draw a sample from $D$.
-\end{rmk}
-
-\begin{rmk}\label{rmk:trace-to-comp}
-If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
-\end{rmk}
-
-\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
-    Let $D_1$, $D_2$, and $D_3$ be three distributions such that 
-    \begin{align}
-        \norm{D_1 -D_2}_q &\leq \eps \\ 
-        \norm{D_2 -D_3}_q &\leq \eps'. 
-    \end{align}
-    We have 
-    \begin{align}
-        \norm{D_1 -D_3}_q &\leq \eps+\eps'
-    \end{align}
-\end{lem}
-\begin{proof}
-For all quantum circuits $A$ with size $\poly(n)$, we have 
-\begin{align}
-    \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} \leq& \eps \\
-    \norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \leq& \eps',  
-\end{align}
-so 
-\begin{align}
-    &\norm{\Pr[A({D_1})=1]-\Pr[A({D_3})=1]} \nn \\
-    =& \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]+\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
-    \leq&  \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} +\norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
-    =& \eps +\eps' \nn
-\end{align}
-
-\end{proof}
-
-\begin{lem}[another triangle inequality for computational distance \hannote{unused}]\label{lem:computational-triangle}
-Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.
-
-If 
-\begin{align}
-    &\norm{D_1 - D_2}_q \leq \eps   \\ 
-    &\norm{D_4 - D_6}_q \leq \eps',  
-\end{align}
-then 
-\begin{align}
-   \norm{ D_3 - D_5}_q \leq \eps+\eps' 
-\end{align}
-\end{lem}
+% If 
 % \begin{align}
-%     D_1 &\approx_{q,\eps} D_2 \\
-%     D_4 &\approx_{q,\eps'} D_6, 
+%     &\norm{D_1 - D_2}_q \leq \eps   \\ 
+%     &\norm{D_4 - D_6}_q \leq \eps',  
 % \end{align}
@@
 % \begin{align}
-%     D_3 \approx_{q,\eps+\eps'} D_5
+%   \norm{ D_3 - D_5}_q \leq \eps+\eps' 
 % \end{align}
-\begin{proof}
-% Since
-% $$\norm{D_4 - D_6}_q \leq \eps',$$
-% there exist
+% \end{lem}
+% % \begin{align}
+% %     D_1 &\approx_{q,\eps} D_2 \\
+% %     D_4 &\approx_{q,\eps'} D_6, 
+% % \end{align}
+% % then 
+% % \begin{align}
+% %     D_3 \approx_{q,\eps+\eps'} D_5
+% % \end{align}
+% \begin{proof}
+% % Since
+% % $$\norm{D_4 - D_6}_q \leq \eps',$$
+% % there exist
 
-We prove by contradiction. Suppose that
-$$\norm{ D_3 - D_5}_q > \eps+\eps',$$
-then there exist a quantum circuit $A$ of size $poly(n)$ such that 
-$$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
-Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that 
-$$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
-Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
-$$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$ 
-$$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$ 
-So 
-\begin{align}
-    &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
-    =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
-    \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
-     > &\eps 
-\end{align}
-This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
-\end{proof}
+% We prove by contradiction. Suppose that
+% $$\norm{ D_3 - D_5}_q > \eps+\eps',$$
+% then there exist a quantum circuit $A$ of size $poly(n)$ such that 
+% $$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
+% Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that 
+% $$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
+% Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
+% $$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$ 
+% $$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$ 
+% So 
+% \begin{align}
+%     &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
+%     =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
+%     \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
+%      > &\eps 
+% \end{align}
+% This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
+% \end{proof}
 
-\hannote{comp. indistinguish for subnormalized state?}
-\hannote{triangle inequality}
+Mahadev's 4-round protocol has the following binding property.
 
 \begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
+If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
 \end{lemma}
@@
 
-We combine the commitment Protocol, Protocol~\ref{proto:urmila4}, and the $\QPIP_1$ Protocol, Protocol~\ref{ProtoQPIP1}, to get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.
+By combining the commitment Protocol, Protocol~\ref{proto:urmila4}, and the $\QPIP_1$ Protocol, Protocol~\ref{ProtoQPIP1}, we get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.
 
@@
  		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
- 		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
+ 		\item Let $T$ be the number of gates in $C$.
+		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
  		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
 		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
+		\item Let $s=n+T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$
 %  		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
@@
 
-	\item \label{step:urmila-in-naive} The verifier and prover run Protocol~\ref{proto:urmila4}, with the following parameters: $h$ is chosen from previous step, $n_{commit}=M \times$ (number of qubits in $\ket{\psi_{C'(x)}}$), where $n_{commit}$ is the $n$ for Protocol~\ref{proto:urmila4}, and the honest prover choose $M$ copies of $\ket{\psi_{C'(x)}}$ as $\rho$.
+	\item \label{step:urmila-in-naive} The verifier and prover run Protocol~\ref{proto:urmila4}, with the following parameters: $h$ is chosen from previous step, $n_{commit}=M \, s$ , where $n_{commit}$ is the $n$ for Protocol~\ref{proto:urmila4}, and the honest prover choose $M$ copies of $\ket{\psi_{C'(x)}}$ as $\rho$.
 We also allow a cheating prover to send $\bot$ in the fourth round of Protocol~\ref{proto:urmila4} if $c=1$ to abort the process.\footnote{This is useless for the cheating prover but useful for proving one of our theorems.} If the verifier receives $\bot$ in the fourth round, he outputs $(\Rej,\bot)$ and terminates this protocol.
@@
 \end{protocol}
+
+ Protocol~\ref{proto:qpip0_naive} has no soundness guarantee, but it has the following binding property that would be useful in proving the soundness of the actual protocol in Section~\ref{sec:qpip0}.
 
@@
 
-\subsection{$\QPIP_0$ protocol for $\SampBQP$}
+\subsection{$\QPIP_0$ protocol for $\SampBQP$} \label{sec:qpip0}
 %Parallel Repetition of the Measurement Subprotocol
@@
 \label{proto:QPIP0samp}
+
+\hannote{fix inputs}
 Inputs: 
@@
 %Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
-\begin{lemma}[partition lemma2]\label{lem:partition2}
+\begin{lemma}[partition lemma]\label{lem:partition2}
 Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round.
@@
 
- For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,  \hannote{$\psi$ should not be pure state?} \hannote{actually need to fix a $pk$ for everything here.}
+ For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,
 
@@
   Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are  sub-normalized.
-$G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$.
+$G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$ and $pk,sk,y$.
+\hannote{check}
 
@@
 
-\item \hannote{added by me..not needed?}
+% \item \hannote{added by me..not needed?}
 
-$$\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}} = \negl(n)$$
+% $$\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}} = \negl(n)$$
 
@@
 
-$$z_i\defeq \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
-where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round. \hannote{need to average $pk$ here.}
+$$z_i\defeq \E_{pk,y} \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
+where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round. \hannote{add description about  averaging $pk$ here.}
 
@@
 
-===
-
-%Prove that $z_{good}$ is binding.
-We now proceeds to prove that $z_{good}$ is binding.
-I.e.
-there exist a subnormalized $n$-qubit quantum state $\rho_{good}$ such that $z_{good}$ is $\eps$-Q-computationally indistinguishable to $M_{XZ}(\rho_{good},h)$.
-
-\hannote{$M_{XZ}(\rho_{good},h)=\sum_z \proj{z} \tr\L(\rho \sigma_{h,z} \R)?$}.
-\hannote{add notation for pauli matrix $\sigma_h$.}
-
-\hannote{need to simulate one copy?}
+We now proceeds to prove that $z_{good}$ is close to the ideal distribution.
 
@@
 \end{align}
-\hannote{the composition of z ideal and triangle ineq is sketchy lol.}
+\hannote{the composition of z ideal and triangle ineq is sketchy lol. Also need to specify different z ideal}
 
 \end{proof}
-
-===========
-
-\hannote{below are unused old fragments}
-
-========= old
-
-By Lemma~\ref{lem:trivial-4-round-strategy} and property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$.
-Therefore by Lemma~\ref{lem:urmila-binding}, there exist a $\rho_{composite}$ such that
-
-\begin{align}
-    \norm{z_{composite} - M_{XZ}(\rho_{composite},h) }_q \leq \negl(n) 
-\end{align}
-
-By Lemma~\ref{lem:trivial-4-round-strategy} and Lemma~\ref{lem:urmila-binding}, there exist a $\rho_{trivial}$ such that
-
-\begin{align}
-    \norm{z_{trivial} - M_{XZ}(\rho_{trivial},h) }_q \leq \negl(n), 
-\end{align}
-where $z_{trivial}$ is the random variable one get by running the strategy of Lemma~\ref{lem:trivial-4-round-strategy}, normalized by the probability that the trivial strategy is chosen in the composite strategy.
-$\rho_{trivial}$ is normalized by the same probability.
-
-Note that when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good}$.
-Therefore $z_{composite}=z_{good}+z_{trivial}$, and by Lemma~\ref{lem:computational-triangle},
-
-\begin{align} \label{eq:z-good-rho}
-    \norm{z_{good} - M_{XZ}(\rho_{good},h) }_q \leq \negl(n), 
-\end{align}
-where $\rho_{good} \defeq \rho_{composite}-\rho_{trivial}$.
-
-Recall that by Eq~\ref{eq:z-z-good} we have
-\begin{align} \label{eq:z-z-good2}
-    \norm{z-z_{good}}_1 \leq \eps
-\end{align}
-if we pick $m,T,\gamma_0=???$ \hannote{tune eps}
-
-Also note that by theorem~\ref{QPIP1thm}, 
-\begin{align} \label{eq:rho-c}
-    \norm{M_{XZ}(\rho_{good},h) -p_{good} C(x)}_1 \leq \eps, 
-\end{align}
-where $p_{good} = \tr \rho_{good}$.
-
-Putting together Equation~\ref{eq:z-z-good2} \ref{eq:z-good-rho} \ref{eq:rho-c},  Remark~\ref{rmk:trace-to-comp}, and Lemma~\ref{lem:computational-triangle0}, we have  
-\begin{align}
-    \norm{z- p_{good}C(x)}_q \leq 2\eps +\negl{n}
-\end{align}
-
-==== old ===
-
-For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for Protocol~\ref{proto:urmila4}: on the first round the verifier pick $h$ from distribution specified by ????
-of Protocol~\ref{ProtoQPIP1}.
-On the second round, the prover start with picking a uniformaly random $i\in [m]$.
-The prover then tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
-The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
-If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead.
-This is possible because all the inputs are classical.
-On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}.
-otherwise he continues to run the strategy of Lemma~\ref{lem:trivial-4-round-strategy}.
-We denote the random variable the verifier would get on the testing round as $z_{construct}$.
-
-===
-
- [[Partition lemma ->  Parallel repetition]], except for probability $\eps$\hannote{$\frac{1}{poly}$?}, either the verifier reject at step~\ref{step:multi-testing} or $z$ is $\negl(n)$-computationally indistinguishable to $M_{XZ}(\rho,h)$ by Lemma~\ref{lem:urmila-binding}.
-
- By theorem~\ref{QPIP1thm}, $M_{XZ}(\rho,h)$  $\eps$-close to $C(x)$.
-Therefore, $M_{XZ}(\rho,h)$  and  $C(x)$ $z$ are $\eps$-Q-computationally indistinguishable, and thus $z$ and $C(x)$ are  $2\eps$-Q-computationally indistinguishable.
-
-===========
-
-\hannote{import 3.5. didn't import the proof, too long.}
-
-First, We present a slight adaption of Lemma 3.5 of \cite{parallelrep}  that partitions the prover's internal state. We omit the proof here.
-
-%$\frac{\gamma_0}{T}=1/\poly(\secpar)$
-\begin{lemma}[partition lemma]\label{lem:partition}
-Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round.
-Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
-Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.
-
- For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exists an $\poly(n)$-sized quantum circuit $G_{i,\gamma}$ such that for all (possibly sub-normalized) \hannote{$n$-qubit?} quantum state $\ket{\psi}_{\regX,\regZ}$,
-\begin{align*}
-    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = \\ \ket{0^m}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+  \ket{0^m}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
-\end{align*}
- where $t$ is the number of qubits in the register $ph$, $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ are sub-normalized states that may depend on $\gamma$.
-
-Furthermore, the following properties are satisfied for all $i\in[m]$.
-%
-\begin{enumerate}
-    \item \label{partition-property-1}  Define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$.\hannote{?} We have  $$E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$$.
-    $$\|\ket{\psi}_{\regX,\regZ}\|^2 -E_{\gamma}\L[\|\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}\|^2 +\|\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}\|^2\R]\leq \frac{6}{T}+\negl(n),$$
-
-    where the averaged is over uniformly sampled $\gamma$.
-\item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$.
-%where $M_{ph,th,in}$ is the computational-basis measurement in the register $(ph,th,in)$.
-%and $t$ is the number of qubits in $ph$.
-This implies that if we apply the measurement $M_{ph,th,in}$ on $\frac{G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in}}{\|\ket{\psi}_{\regX,\regZ}\|}$, then the outcome is $0^tb1$ with probability $\|\ket{\psi_b}_{\regX,\regZ}\|^2$ and the resulting state in the register $(\regX,\regZ)$  is $\frac{\ket{\psi_b}_{\regX,\regZ}}{\|\ket{\psi_b}_{\regX,\regZ}\|}$ ignoring a global phase factor.
-
-    % \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. \hannote{redundant?}
-
-%     \begin{align*}
-% \Pr\left[M_{\regX_i}\circ U\frac{\ket{\{c\}}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
-% \end{align*}
-
-%   \begin{align*}
-% \Pr\left[V_{f,i}\L(sk_i,h,y_i, U\frac{\ket{\{c\}}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\R) \in \Acc \right]\leq (m-1)\gamma+\negl(\secpar).
-% \end{align*}
-
-        \item 
-For all $\{pk\}$, $\{y\}$, fixed $\gamma$, and $\{c\}\in S_m$ such that $c_i = 0$, we have
-
-     \begin{align*}
- \Pr\left[M_{\regX_i}\circ U\frac{\ket{\{c\}}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{pk_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
- \end{align*}
-
-    \item 
-For all $\{pk\}$, $\{y\}$, fixed $\gamma$, and $\{c\}\in S_m$ such that $c_i = 0$, there exists an efficient quantum algorithm $\ext_i$ such that
-
-\begin{align*}  
-  \Pr\left[M_{\regX_i}\circ \ext_i\left(\frac{\ket{\{c\}}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{pk_i,y_i}\right]=1-\negl(\secpar).
-  \end{align*}
-
-\item \hannote{added by me..}
-$$\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}} = \negl(n)$$
-\end{enumerate}
-\end{lemma}
-\begin{rmk}\label{rmk:partition-projector}
-\hannote{should be corollary with proof?} By applying $G_{i,\gamma}$ then measuring the $ph,th,in$ register, we can get two efficient quantum algorithms $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that
-
-\begin{enumerate}
-    \item $$G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ}=\ket{\psi_{0,i,\gamma}}_{\regX,\regZ} $$
-\item  $$G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ}=\ket{\psi_{1,i,\gamma}}_{\regX,\regZ} $$
-%  \item ~\label{step:sum-ob} For all $i$ and $\gamma$,
-%   $$G_{0,i,\gamma}+G_{1,i,\gamma} \leq (1+\negl(n))Id_{\regX,\regZ} $$ \hannote{actually wrong.. the fuck?}
-%  \item ~\label{step:sum-lb}
-%   $$E_\gamma(G_{0,i,\gamma}+G_{1,i,\gamma}) \geq (1-\negl(n))Id_{\regX,\regZ} $$
-\end{enumerate}
-
-Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are not normalized.
-\hannote{we overload a quantum algorithm with the corresponding unitary.}
-
-Also note that 
-\begin{align}
-   &\norm{( G_{0,i,\gamma}+G_{1,i,\gamma}) \ket{\psi}}^2 \nn \\
-   =& \norm{\ket{\psi_{0,i,\gamma}}+\ket{\psi_{1,i,\gamma}}}^2 \nn \\
-   =& \norm{\ket{\psi_{0,i,\gamma}}}^2+\norm{\ket{\psi_{1,i,\gamma}}}^2+\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}}+\vev{\psi_{1,i,\gamma}|\psi_{0,i,\gamma}} \nn \\
-    \leq& \norm{\ket{\psi}}^2 +\negl(n)
-\end{align}
-and 
-\begin{align}
-   &E_\gamma \norm{( G_{0,i,\gamma}+G_{1,i,\gamma}) \ket{\psi}}^2 \nn \\
-   =& E_\gamma\norm{\ket{\psi_{0,i,\gamma}}+\ket{\psi_{1,i,\gamma}}}^2 \nn \\
-   =& E_\gamma\L[\norm{\ket{\psi_{0,i,\gamma}}}^2+\norm{\ket{\psi_{1,i,\gamma}}}^2+\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}}+\vev{\psi_{1,i,\gamma}|\psi_{0,i,\gamma}}\R] \nn \\
-    \geq& \norm{\ket{\psi}}^2 -\frac{6}{T}-\negl(n)
-\end{align}
-
-% \begin{align}
-%   &E_\gamma \norm{( G_{0,i,\gamma}+G_{1,i,\gamma}) \ket{\psi}}^2 \nn \\
-%   =& E_\gamma\norm{\ket{\psi_{0,i,\gamma}}+\ket{\psi_{1,i,\gamma}}}^2 \nn \\
-%   =& E_\gamma\norm{\ket{\psi}-\ket{\psi_{err}}}^2 \nn \\
-%     =& E_\gamma\L[\norm{\ket{\psi}}^2+\norm{\ket{\psi_{err}}}^2-2Re(\vev{\psi|\psi_{err}})\R] \nn \\
-%     \geq& \norm{\ket{\psi}}^2 -\frac{6}{T}-\negl(n)
-% \end{align}
-\end{rmk}
-
-\begin{lemma} \hannote{urmila talks about protocol not state.}
-For all $h$, $i\in [m]$ and $\{c\}\in S_m$ such that $c_i = 1$, $a_i \equiv  M_{\regX_i}\circ U\L(\frac{\ket{\{c\}}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\R)$ is binding.
-I.e.
-there exist a $\rho$ such that $V_f(sk,h,y,a)$ is $\negl(n)$-Q-computationally indistinguishable to $M_{XZ}(\rho,h)$, unless LEW can be efficiently solved by a quantum computer.
-\end{lemma}
-\begin{proof}
-We construct an  strategy $\tilde{U}$ for the fourth round of Protocol~\ref{proto:QPIP0samp}, which is "amplified" from $U$ .
-$\tilde{U}$ start by measuring the $\regC$ register.
-Since the $\regC$ register only has classical-valued inputs, this initial measurement does not decohere anything.
-Denote the measured input as $\{\tilde{c}\}$.
-If $\tilde{c}_i=0$, run $U$.
-If $\tilde{c}_i=1$, run $\ext_i$.
-By Lemma~\ref{lem:partition}, ???
-
-%without loss of generality we can assume $U$ measures $\regC$ first and run 
-\end{proof}
-
-====
-
-==============
-
-\iffalse
-\hannote{duplicate version by ethan..}
-\begin{lem}
-	Let $(U_0, U)$ be some prover's strategy.
-	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $i\in[m]$, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
-	Let $\gamma$ be sampled uniformly from $\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document}.
-	Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{X, Z}$,
-
-	$$TODO-LONG-EQ$$
-
-	where $t$ is the number of qubits in the register $ph$ \Ethan{Where is this register defined?},
-	$z_0, z_1\in\bbC$ such that $\abs{z_0}=\abs{z_1}=1$, and $z_0$, $z_1$, $\ket{\psi_0}_{X, Z}$, $\ket{\psi_1}_{X, Z}$, $\ket{\psi_{err}}_{X, Z}$ may depend on $\gamma$.
-	Furthermore, the following properties are satisfied.
-	\begin{enumerate}
-		\item Let $\ket{\psi_{err}}=\ket{\psi}-\ket{\psi_0}-\ket{\psi_1}$, then
-			$$\E_\gamma[\norm{\ket{\psi_{err}}}^2]\leq\frac{1}{T}+\negl(n)$$
-		\item TODO Some long property
-		\item For any fixed $\gamma$,
-			$$\E_{b\in\set{0, 1}}\left[\norm{\ket{\psi_{b}}_{X, Z}}^2\right]\leq\frac{1}{2}\norm{\ket{\psi}_{X, Z}}^2$$
-		\item For any fixed $\gamma$ and $c\in\set{0, 1}^m$ such that $c_i=0$, \Ethan{Where's this $M_{X_i}$ defined?}
-			$$\Pr\left[M_{X_i}\circ U\frac{\ket{c}_C\ket{\psi_0}_{X,Z}}{\norm{\psi_0}_{X,Z}}\in A_{k_i, y_i}\right]\leq2^{m-1}\gamma+\negl(n)$$
-		\item For any fixed $\gamma$, there exists an efficient quantum algorithm $\cE_i$ such that
-			$$\Pr\left[\cE_i\left(\frac{\ket{0^m}_C\ket{\psi_1}_{X,Z}}{\norm{\psi_1}_{X,Z}}\in A_{k_i, y_i}\right)\right]\leq1-\negl(n)$$
-	\end{enumerate}
-\end{lem}
-
-\begin{theorem}
-
- If there exists a $\QPIP_1$ protocol $(\bbV, \bbP)$ for $\SampBQP$ with soundness blah and completeness blah there exists a $\QPIP_0$ protocol $(\bbV', \bbP')$ for $\SampBQP$ with soundness blah' and completeness blah'
-
-\end{theorem}
-
-\fi
-==========
-
-Choose the $T$ in Lemma~\ref{lem:partition} to be $\Theta(m^3)$ \hannote{$\gamma_0$?}. By Property~\ref{partition-property-1} of Lemma~\ref{lem:partition}, 
-$$\forall i, \L(1- 1/m^2\R)\text{fraction of }\gamma$$ 
-satisfies that 
-$$\norm{\ket{\psi_{err}}}^2 \leq 1/m+\negl(n). $$
-Therefore, there exist an $\gamma$ such that 
-$$\forall i,\, \norm{\ket{\psi_{err}}}^2 \leq 1/m+\negl(n). $$
-
-Denote $G_{i,\gamma}$ with  $\gamma$ found above as $G_i$. \hannote{finding $\gamma$ is not computationally efficient.}
-
-====
-
-\Ethan{Below is 3.6. Looks kinda useful but I need to think through this $c$ thing to make sure it'll be fine even if it's not randomly generated.}
-\hannote{How about include 3.6 in the theorem}
-
-Here we follow \cite{parallelrep}.
-
-We characterize a prover by two unitaries $(U_0, U)$ acting on the space $\cH_C\otimes\cH_X\otimes\cH_Z\otimes\cH_Y\otimes\cH_K$.
-
-\Ethan{I'll elaborate on above later, after figuring out exactly what I need or don't need}
-
-Each coordinate can be accepted and rejected separately, and the entire protocol accepts only if all coordinates accept.
-
-Let $A_{k_i, y_i}$ be the set of $a_i$s accepted by the verifier in the test round when the first and second messages are $k_i$ and $y_i$, respectively.
-
-\Ethan{Do we even need this lemma 3.5, or can we just use 3.6...}
-
-\begin{lem}
-	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
-	Let $\gamma_i\xleftarrow{\$}\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document} for each $i\in[m]$.
-	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
-	$$\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ket{\psi_{110}}+\ldots+\ket{\psi_{11\ldots10}}+\ket{\psi_{11\ldots11}}+\ket{\psi_{err}}$$
-	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
-	Furthermore, the following properties are satisfied. \Ethan{Takes a bit of parsing to see how is our case different here since $c$ might be defined differently for us}
-	\begin{enumerate}
-		\item stuff
-		\item For any fixed $\hat\gamma$... 
-		\item For any fixed $\hat\gamma$...
-		\item For any fixed $c$,
-			$$\E_{\hat\gamma}\left[\norm{\ket{\psi_{err}}_{X,Z}}^2\right]\leq\frac{6m^2}{T}+\negl(n)$$
-		\item stuff
-	\end{enumerate}
-\end{lem}
-    asdf
-
-\begin{cor}
-
-	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ for $\SampBQP$ with soundness blah and completeness blah
-
-\end{cor}

### 2020-04-13 blind.tex
Add discussion notes
Handle action items

@@
 We now state our compiler that gives any $\QPIP_0$ protocol blindness.
+For the sake of simplicity, we omit the security and accuracy parameters. \Ethan{The previous sentence is newly added}
 For notation, when there are many sets of $\QHE$ keys in play at the same time,
 we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
-
-\Ethan{How to work the security parameter into the following? It's annoying if everything takes that.
-Also, where do I write that footnote about extra uncompiled inputs such as accuracy param.?}
 
@@
 		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
-			by evaluating \linebreak
-			$(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval(pk, \cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
+			by evaluating %\linebreak
+			$(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow  \QEval(pk, \cP_1,$ \  $\ctx{v}{1}{1}, \ctx{x}{}{1})$.
 			It sends $\ctx{p}{1}{1}$ to the verifier.
@@
 				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc(pk_t, \ctx{st}{P, t-1}{t-1}))$,
-				then homomorphically decrypts the old encryption by \linebreak
-				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t}).$
+				then homomorphically decrypts the old encryption by
+				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec,$ \ $\ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
 				Then it applies the next-message function homomorphically, generating

### 2020-04-13 preliminaries.tex
Handle action items

@@
 
-\Ethan{Sec. param. should be 1st param}
-
 \begin{definition}
 	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
-	We say it is a prototol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds.
+	We say it is a prototol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds:
 \begin{itemize}
@@
 	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
-	We say it is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and statistical (resp., computational) soundness if the following holds.
+	We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c$ and statistical (resp., computational) soundness if the following holds:
 	\begin{itemize}
@@
 
-We define blindness of a protocol as follows. \Ethan{Input x is private input now... the rest are still common input... etc.}
+We now define blindness of a protocol.
+In the context of blind protocols, the above definitions should be modified so that $x$ is the verifier's private input.
+We define blindness with an accuracy parameter $\varepsilon$, which exists in protocols for $\SampBQP$ instances;
+one can leave it out where appropriate, such as in protocols for $\BQP$ languages.
 
 \begin{definition}
-	Let $(P, V)$ be an interactive protocol with security parameter $\lambda$. \Ethan{Define the version with eps, say that it's fine without eps for BQP} \Ethan{TODO Quantify cheating prover}
-	Let $\lambda$ be a security parameter.
-	Then it is \emph{blind} if the following ensembles are computationally indistinguishable over $\lambda$:
+	Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ and $1^{1/\varepsilon}$, and verifier's private input $x\in\zo^*$.
+	We say $\Pi$ is \emph{blind} if for all cheating prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
 	\begin{itemize}
-		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda)}_{\lambda\in\bbN, x\in\zo^n}$
-		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda)}_{\lambda\in\bbN, x\in\zo^n}$
+		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda, 1^{1/\varepsilon})}_{\lambda\in\bbN, \varepsilon\in(0,1), x\in\zo^*}$
+		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda, 1^{1/\varepsilon})}_{\lambda\in\bbN, \varepsilon\in(0,1), x\in\zo^*}$
 	\end{itemize}
@@
 
-\Ethan{Just define QHE}
-
 \def\QHE{\mathsf{QHE}}
@@
 We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
-We start by presenting the definition of a homomorphic encryption scheme:
 \begin{definition}
-    \Ethan{Do more copying}
-	A leveled homomophic encryption scheme is tuple of algorithms \linebreak $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
+	A quantum homomophic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
+	$\QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:
 	\begin{itemize}
-		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, sk)$
-		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
-		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
-		\item $\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l)\rightarrow c_f$
+		\item \emph{Key generation.}
+			The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda)$ takes a unary representation of the security parameter and outputs a public key encryption key $pk$ and a secret decryption key $sk$.
+		\item \emph{Encryption.}
+			The algorithm $c\leftarrow\QEnc(pk, \mu)$ takes the public key $pk$ and a single bit message $\mu\in\zo$ and outputs a ciphertext $c$.
+		\item \emph{Decryption.}
+			The algorithm $\mu^*\leftarrow\QDec(sk, c)$ takes the secret key $sk$ and a ciphertext $c$ and outputs a message $\mu^*\in\zo$.
+			It must be the case that
+				$$\QDec(sk, \QEnc(pk, \mu))=\mu$$
+			with overwhelming probability in $\lambda$.
+		\item \emph{Homomorphic Evaluation.}
+			The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit \Ethan{?} $f$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ and outputs a ciphertext $c_f$.
+			It must be the case that
+				$$\QDec(sk, \QEval(pk, f, c_1, \ldots, c_l))=f(\QDec(sk, c_1),\ldots,\QDec(sk, c_l))$$
+			with overwhelming probability in $\lambda$.
 	\end{itemize}
@@
 
-$\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
-$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l))=f(\mathsf{HE.Dec}_{sk}(c_1),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
-where $f$ is specified by a circuit of depth at most $L$.
+\begin{definition}[Compactness and Full Homomorphism]
+	\Ethan{This is copied from Mahadev. Not sure how much of this we need. We need at least how leveled HE is defined.}
 
-\Ethan{To be pedantic, the above doesn't imply Dec undoes Enc even if we sub in $f=\id$.}
-
-\Ethan{Maybe add correctness}
+	A quantum homomorphic encryption scheme $\QHE$ is compact if
+	there exists a polynomial $s$ in $\lambda$ such that the output length of $\QEval$ is at most $s$ bits long (regardless of $f$ or
+	the number of inputs). A compact scheme is (pure) fully homomorphic if it can evaluate any efficiently computable
+	boolean function. A compact scheme is leveled fully homomorphic if it takes $1^L$ as additional input in key generation,
+	and can only evaluate depth $L$ Boolean circuits where $L$ is polynomial in $\lambda$. A scheme is quantum pure or
+	leveled fully homomorphic if we refer to quantum circuits rather than boolean circuits.
+\end{definition}
 
@@
 \begin{definition}
-	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
+	\Ethan{This was copied from Mahadev. Not sure where $L$ (level) goes.}
+	A scheme $\QHE$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
 	$$\abs{Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(1))=1]}\leq\mu(\lambda)$$
-	where $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
+	where $(pk, sk)\leftarrow\QGen(1^\lambda)$
 \end{definition}
@@
 		\item In the case where the plaintext is classical, $\QEnc$ can be done classically.
-		\item Its ciphertext can be homomorphically measured, after which $\QDec$ can also be done classically. \Ethan{Underlying msg is classical = ct is classical = can be classical decrypted}
+		\item When the underlying message is classical, the corresponding ciphertext is also classical and can be decrypted classically.
 	\end{itemize}

### 2020-04-14 blind.tex
Add notes and others' updates

@@
 We now state our compiler that gives any $\QPIP_0$ protocol blindness.
-For the sake of simplicity, we omit the security and accuracy parameters. \Ethan{The previous sentence is newly added}
+For the sake of simplicity, we omit the security and accuracy parameters.
 For notation, when there are many sets of $\QHE$ keys in play at the same time,
@@
 
+\Ethan{Say in words I'm going to compile proto 5 (which is a general form of...) to proto 6}
+
+\Ethan{Add lambda back}
+
 \begin{protocol}{$\QPIP_0$ protocol $\Pi_0=(P, V)(x)$ where only the verifier receives outputs}
 
-	Public input: $x$
+	Public input: $x$ \Ethan{Add footnote here about eps}
 	\begin{enumerate}
@@
 \begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ correponding to $\Pi_0$}
-
+    \Ethan{Sync common or public inputs wording. Prefer common.}
 	Verifier's input: $x$
 
-	Let $L=\poly(x)$, $\lambda=\poly(x)$.
+	Let $L=\poly(x)$ \Ethan{Quantify/define L more clearly}, $\lambda=\poly(x)$.
 
@@
 \begin{theorem}
-	For all cheating prover $\Pblindstar$, there exists a cheating prover $\Pstar$ s.t. for all input $x$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
+	For all cheating $\BQP$ prover $\Pblindstar$, there exists a cheating $\BQP$ prover $\Pstar$ s.t.
+for all $\lambda$ and input $x\in\zo^{\poly(\lambda)}$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
 \end{theorem}
@@
 
-	On $\cPstar{1}$ it generates
+	For the first rounds, it generates
 	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$, then produces the encryptions
@@
 
-	Then, on the rest of the $\cPstar{t}$ rounds, it generates
+	For the other rounds, it generates
 	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$, and produces ciphertexts
 	$\ctx{v}{t}{t}\leftarrow\QEnc(pk_t, v_t))$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc(pk_t, sk_{t-1})$.
-	It then runs $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$.
+	It then runs $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t},$ \ $\ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$.
 	Finally, it decrypts $p_t\leftarrow\QDec(sk_t, \ctx{p}{t}{1})$ and sends it back to the verifier,
@@
 	Then, for all $t$, from the perspective of the prover, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
-	By applying triangle inequality iteratively \Ethan{good enough?}, we observe that $\Hyb_1$ is computationally indistinguishable with $\Hyb_{T+1}$.
+	By a standard hybrid argument, we observe that $\Hyb_1$ is computationally indistinguishable with $\Hyb_{T+1}$.
 	Furthermore, $\Hyb_1$ is blind since the prover isn't provided any information about any secret keys.
+	\Ethan{do hybrid on 0 too and make sure it fits the dfns. Also should mention why hybriding works}
 	So we conclude that $\Piblind$ is blind.
@@
 as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.
+
+\Ethan{``preserves soundness" needs just a bit more discussion, since all we've proven are two experiments being identical.}
 

### 2020-04-14 hamiltonian.tex
Add notes and others' updates

@@
-\section{Construction of the X-Z Local Hamiltonian for $\SampBQP$}
-\label{sec:Hamiltonian}
-
-\XW{merge Section 3 and 4; also easy the discussion}
+\section{$\SampBQP$ Delegation Protocol for $\QPIP_1$ Client}
+\label{sec:sampbqp}
 
@@
 \def \Hclock {H_{\mathrm{clock}}}
+\def \Jclock {J_{\mathrm{clock}}}
+\def \Jprop {J_{\mathrm{prop}}}
+\def \Kin {K_{\mathrm{in}}}
+\def \Kclock {K_{\mathrm{clock}}}
+\def \Kprop {K_{\mathrm{prop}}}
+
 \newcommand{\histpsi}[1]{\ket{\psi_{#1}^{\mathrm{hist}}}}
 \newcommand{\LHXZ}[1]{\mathrm{LH}_{\mathrm{XZ}}^{#1}}
+\newcommand{\ground}[1]{{\lambda \left (#1 \right)}}
 
+\XW{merge Section 3 and 4; also easy the discussion;}
+
+\subsection{Construction of the X-Z Local Hamiltonian for $\SampBQP$} \label{sec:LHXZ}
 As we mentioned in this introduction, we will employ the circuit \emph{history} state in the original construction of the Local Hamiltonian problem~\cite{kitaev2002classical} to encode the circuit information for $\SampBQP$.
@@
 For any quantum circuit $C$ on input $x$, the original construction for certifying $\BQP$\footnote{The original construction is for the purpose of certifying problems in QMA.
-We consider its simple restriction to problems inside BQP.} consists of three parts of local Hamiltonian $\Hin, \Hprop$, $\Hout$ where $\Hin$ is used to certify the initial input $x$, $\Hprop$ to certify the gate-by-gate evolution according to the circuit description, and $\Hout$ to certify the final output.
-In particular, the history state referring to quantum circuit $C$ on input $x$ is in the ground space of $\Hin$ and $\Hprop$.
+We consider its simple restriction to problems inside BQP.} consists of local Hamiltonian $\Hin, \Hclock, \Hprop$, $\Hout$ where $\Hin$ is used to certify the initial input $x$, $\Hclock$ to certify the validness of the clock register,  $\Hprop$ to certify the gate-by-gate evolution according to the circuit description, and $\Hout$ to certify the final output.
+In particular, the corresponding history state is in the ground space of $\Hin$, $\Hclock$, and $\Hprop$.
 Note that $\BQP$ is a decision problem and its outcome (0/1) can be easily encoded into the energy $\Hout$ on the single output qubit.
-As a result, the outcome of $\BQP$ can simply be encoded by the \emph{ground energy} of $\Hin + \Hprop + \Hout$.
+As a result, the outcome of $\BQP$ can simply be encoded by the \emph{ground energy} of $\Hin + \Hclock+\Hprop + \Hout$.
 
-To deal with $\SampBQP$, we will still employ $\Hin$ and $\Hprop$ to certify the circuit's input and gate-by-gate evolution.
-However, in this case, we care about the entire final state of the circuit, rather than the energy on the output qubit.
-The history state remains in the ground space of $\Hin + \Hprop$.
-Our approach to certify the entire final state (which is encoded inside the history state) is to make sure that the history state is the unique ground state of $\Hin + \Hprop$ and all other orthogonal states will have much higher energies.
-Namely, we need to construct some $\Hin'+ \Hprop'$ with the history state as the unique ground state and with a large \emph{spectral} gap between the ground energy and excited energies. 
-It is guaranteed that any state with close-to-ground energy must also be close to the history state. 
-We remark that this is an additional strong requirement, whereas most local Hamiltonian constructions focus on the ground energy. 
-We show it can indeed be achieved by using the \emph{perturbation} technique 
-developed in the local Hamiltonian literature (e.g.~\cite{kempe_kitaev_regev_2006}) for a different purpose. 
-Another example of local Hamiltonian construction focusing on the spectral gap can be found in~\cite{adiabatic} where the purpose is to simulate quantum circuits by adiabatic quantum computation.
+To deal with $\SampBQP$, we will still employ $\Hin, \Hclock$, and $\Hprop$ to certify the circuit's input, the clock register, and gate-by-gate evolution.
+However, in $\SampBQP$, we care about the entire final state of the circuit, rather than the energy on the output qubit.
+%The history state remains in the ground space of $\Hin + \Hprop$.  
+Our approach to certify the entire final state (which is encoded inside the history state) is to make sure that the history state is the unique ground state of $\Hin + \Hclock+ \Hprop$ and all other orthogonal states will have much higher energies.
+Namely, we need to construct some $\Hin'+ \Hclock'+ \Hprop'$ with the history state as the unique ground state and with a large \emph{spectral} gap between the ground energy and excited energies. 
+It is hence guaranteed that any state with close-to-ground energy must also be close to the history state. 
+We remark that this is a different requirement from most local Hamiltonian constructions that focus on the ground energy. 
+We achieve so by using the \emph{perturbation} technique developed in~\cite{kempe_kitaev_regev_2006} for reducing the locality of Hamiltonian. 
+Another example of local Hamiltonian construction with a focus on the spectral gap can be found in~\cite{adiabatic}, where the purpose is to simulate quantum circuits by adiabatic quantum computation.
 
-We need, however, two more further twists to serve our purpose. 
+We need two more twists for our purpose. 
 First, as we will eventually measure the final state in order to obtain classical samples, we need that the final state occupies a large fraction of the history state.
-We can simply add dummy identity gates for that purpose.
+We can simply add dummy identity gates.
 Second, as we are only able to perform $X$ or $Z$ measurement by techniques from~\cite{FOCS:Mahadev18a},
@@
 
-\subsection{Specific Construction}
-
 Recall the definition of the history state which serves as a transcript of the circuit evolution~\cite{kitaev2002classical}:
@@
     \end{equation}
-    where the first register of $n$-qubit refers to the input, the second of $m$-qubit refers to the work space ($\mathrm{poly}(n)$ size) which is initialized to $\ket{0}$, and the last refers to the clock space which encodes the time information.
-Note that $\hat{t}$ could be some representation of $t$=0,..., $T$ up to design choice.
+    where the first register of $n$-qubit refers to the input, the second of $m$-qubit refers to the work space ($\mathrm{poly}(n)$, w.l.o.g, $\leq T$ size) which is initialized to $\ket{0}$, and the last refers to the clock space which encodes the time information.
+Note that $\hat{t}$ could be some representation of $t$=0,..., $T$.
 \end{dfn}
@@
  The Toffoli gate maps bits $(a,b,c)$ to $(a,b, c \oplus (a \text{ and } b))$, which can be decomposed as $\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$ where $\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$.
-% Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
-% Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
+ %Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
+ %Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
 % Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
@@
 It is observed in~\cite{PhysRevA.78.012352} that $\Hclock$ can be reformulated as a linear combination of terms from $\LHXZ{}$ as follows, 
-\begin{equation}
+\begin{equation} \label{eqn:Hclock}
    \Hclock= \frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_t\otimes Z_{t+1}),
@@
 \begin{equation} 
-    \Hin = \sum_{i=1}^n(I- \proj{x_i}_i)\otimes \proj{0}_1 + \sum_{i=1}^m \proj{0}_{n+i} \otimes \proj{0}_1, 
+    \Hin = \sum_{i=1}^n(I- \proj{x_i}_i)\otimes \proj{0}_1 + \sum_{i=1}^m \proj{1}_{n+i} \otimes \proj{0}_1, 
 \end{equation}
 where the last part $\proj{0}_1$ applies on to the first qubit in the clock register. One can rewrite $\Hin$ as 
-\begin{equation}
+\begin{equation}\label{eqn:Hin}
  \Hin=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1) + \frac{1}{4} \sum_{i=1}^m (I - Z_{n+i}) \otimes (I + Z_1). 
 \end{equation}
-\XW{todo here}
 % Then, we ensure that the initial condition is set up correctly.
@@
 
-	Then, we ensure that the gates are applied correctly.
-	$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
-	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
-	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
-	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
+For the propagation of the quantum state through the circuit, one uses the $\Hprop$ as follows: 
+\begin{equation*} \label{eqn:Hprop}
+    \Hprop=\sum_{t=1}^T \Hprop^t, 
+\end{equation*}
+where 
+\begin{equation}
+    \Hprop^t=\frac{1}{2}I\otimes\proj{\widehat{t}}
+	+\frac{1}{2}I\otimes\proj{\widehat{t-1}}
+	-\frac{1}{2} U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
+	-\frac{1}{2}U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}.
+\end{equation}
+Note that $\ket{\widehat{t}}\bra{\widehat{t-1}}=\ket{110}\bra{100}_{(t-1,t,t+1)}$ and similarly for $\ket{\widehat{t-1}}\bra{\widehat{t}}$.
+% 	Then, we ensure that the gates are applied correctly.
+% 	$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
+% 	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
+% 	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
+% 	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
+% 	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
+% 	We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least nonzero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
+%One can similarly rewrite $\Hprop$ in terms of elements from $\LHXZ{}$. 
+Note that $U_t^\dagger=U_t$, since our gates are either Hadamard or Toffoli. It is observed in~\cite{PhysRevA.78.012352} that 
+\begin{equation}
+   \Hprop^t=\frac{I}{4}\otimes(I-Z_{t-1})\otimes (I+Z_{t+1})-\frac{U_t}{4}\otimes(I-Z_{t-1})\otimes X_t\otimes (I+Z_{t+1}), \forall t=2, \ldots, T-1,
+\end{equation}
+and 
+\begin{eqnarray}
+  \Hprop^1 &= & \frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1\otimes Z_2) \\
+  \Hprop^T &= & \frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}\otimes X_T).
+\end{eqnarray}
+% 	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$.
+% 	Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
+% 	
+% $$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
+% 	Extra care must be taken for boundary cases.
+% 	$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
+% 	$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
+Combining with the fact that each $U_t$ can be written as a linear combination of terms from $\LHXZ{}$, we conclude that $\Hclock$, $\Hin$, $\Hprop$ are 6-local X-Z Hamiltonian.
 
-	We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least nonzero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
+We will employ the perturbation technique to amplify the spectral gap of $\Hclock + \Hin + \Hprop$. 
+Let $\ground{H}$ denote the ground energy of any Hamiltonian $H$. 
+The projection lemma from \cite{kempe_kitaev_regev_2006} approximates $\ground{H_1 + H_2}$ in terms of $\ground{H_1\big|_{\ker H_2}}$, where $\ker H_2$ denotes the \emph{kernel} space of $H_2$.
 
-	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since our gates are either Hadamard or Toffoli.
-	Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
-	$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
-	Extra care must be taken for boundary cases.
-	$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
-	$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
+\begin{lem}[Lemma 1 in \cite{kempe_kitaev_regev_2006}]
+	\label{thm:proj1}
+	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on Hilbert space $\cH=\cS+\cS^\bot$.
+	The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
+	$$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
+\end{lem}
 
-Moreover, it is known in~\cite{PhysRevA.78.012352} about how to convert Kitaev's original 5-local Hamiltonian construction~\cite{kitaev2002classical} to a 5-local X-Z Hamiltonian. Precisely,
+We will use the following simple reformulation instead. 
+%We will instead use the following formulation, which can be obtained by relabeling variables from above.
 
-We will follow the unary clock representation from~\cite{kitaev2002classical}, i.e., valid
+\begin{lem}
+	\label{lem:projection}
+	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
+	$$J=\frac{8\norm{H_1}^2+ 2\norm{H_1}}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
+	then we have
+	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
+\end{lem}
+\begin{proof}
+	Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least nonzero eigenvalue of $JH_2$ is greater than $2\norm{H_1}$.
+\end{proof}
 
-\XW{main construction and proofs}
-
-Now we state the main theorems that we'll work towards in this section.
-The first one is the reduction from $\SampBQP$ to a local Hamiltonian instance, with some additional properties that will be convenient for us:
 \begin{thm}
 	\label{thm:LHReduction}
-	Let $C$ be a circuit of size $T$. For any input string $x$, there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
-	\begin{itemize}
-		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms and $d_S\in O(T^4)$.
-		\item $H_{C(x)}$ has $\ket{\psi_{C(x)}}$ as the unique ground state with eigenvalue $0$.
-		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
-		\item Its descriptions can be constructed by a $\BPP$ machine in polynomial time.
-	\end{itemize}
+	Given any quantum circuit $C = U_T \ldots U_1$ of  $T$ elementary gates and input $x \in \{0,1\}^n$, one can construct a 6-local X-Z Hamiltonian $H_{C(x)}$ in polynomial time such that 
+	\begin{enumerate}
+		\item[(1)] $H_{C(x)} = \sum_i \alpha_i H_i$ where 
+		each $H_i \in \LHXZ{6}$ and $|\alpha_i| \in O(T^4)$. Moreover, there are at most $O(T)$ non-zero terms. 
+		\item[(2)] $H_{C(x)}$ has $\histpsi{C(x)}$ as the unique ground state with eigenvalue $0$ and has a spectral gap at least $\frac{3}{4}$.
+Namely,  for any state $\ket\phi$ that is orthogonal to $\histpsi{C(x)}$, we have $\braket{\phi|H_{C(x)}|\phi}\geq \frac{3}{4}$.
+	\end{enumerate}
 \end{thm}
 
-We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which describes the conditions under which we can estimate the ground state energy of $H_1 + H_2$ with that of $H_1\big|_{\ker H_2}$.
+\begin{proof}
+We will use the above construction $\Hclock$ (\cref{eqn:Hclock}), $\Hin$ (\cref{eqn:Hin}), $\Hprop$ (\cref{eqn:Hprop}) as our starting point, which are already 6-local X-Z Hamiltonian constructable in polynomial time.
+However, $H_{\mathrm{old}}=\Hin + \Hclock + \Hprop$ does not have the desired spectral gap.
+To that end, our construction will be a weighted sum of $\Hin$, $\Hclock$, and $\Hprop$ as follows,
+\begin{equation}
+    H_{\mathrm{new}}= \Hin + \Jclock \Hclock + \Jprop \Hprop,
+\end{equation}
+where $\Jclock$ and $\Jprop$ will be obtained using \Cref{lem:projection}.
 
-\begin{thm}[\Ethan{TODO thm number from src}]
-	\label{thm:proj1}
-	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on some Hilbert space $\cH=\cS+\cS^\bot$.
-	The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
-	$$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}^2}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
-\end{thm}
+Let $\Kin=\ker \Hin$, $\Kclock=\ker \Hclock$, and $\Kprop=\ker \Hprop$. It is known from e.g.,~\cite{kitaev2002classical}, that 
+\[
+   \Kin \cap \Kclock \cap \Kprop = \spn\set{\histpsi{C(x)}}.
+\]
+Thus $\histpsi{C(x)}$ remains in the ground space of $H_{\mathrm{new}}$. Let $S$ denote its orthogonal space. Namely, $S=(\spn\set{\ket{\psi_{C(x)}}})^\bot$. 
+Denote by $\Hin\big|_S$ the restriction of $\Hin$ on space $S$ and similarly for others.
 
-We will instead use the following formulation, which can be obtained by relabeling variables from above.
+\XW{need to check the following calculation and modify the theorem statement respectively.}
+%We will apply \Cref{lem:projection} twice to obtain $\Jclock$ and $\Jprop$ respectively. 
+Consider $\Hin + \Jclock\Hclock$ first. According to \cref{lem:projection}, by choosing 
+\[
+  \Jclock = \frac{8\norm{\Hin\big|_S}^2 + 2 \norm{\Hin\big|_S}}{\ground{\Hclock\big|_{S\cap \Kclock^\bot}}} = O(T^2),
+\]
+where we use the fact $\norm{\Hin|_S}\leq T$ and $\ground{\Hclock\big|_{S\cap \Kclock^\bot}}\geq \ground{\Hclock\big|_{\Kclock^\bot}}=1$, 
+we have 
+\[
+ \ground{\Hin\big|_S + \Jclock\Hclock\big|_S}\geq \ground{\Hin\big|_{S\cap \Kclock}} - \frac{1}{8}. 
+\]
+Consider further adding $\Jprop\Hprop$ term.  By choosing 
+\[
+ \Jprop= \frac{O(\norm{\Hin\big|_S + \Jclock\Hclock\big|_S}^2)}{\ground{\Hprop\big|_{S \cap \Kprop^\bot}}}= O(T^6),
+\]
+where we use the fact $\ground{\Hprop\big|_{S\cap \Kprop^\bot}}\geq \ground{\Hprop\big|_{\Kprop^\bot}}=\Omega(T^{-2})$~\cite{kitaev2002classical}, we have  
+% $$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
+% =\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
+% $$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
+% \lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
+\[
+ \ground{\Hin\big|_S + \Jclock\Hclock\big|_S + \Jprop\Hprop\big|_S} \geq \ground{\Hin\big|_{S \cap \Kclock \cap \Kprop}} - \frac{1}{4}. 
+\]
+A simple observation here is that $S \cap \Kclock \cap \Kprop$ is the span of history states with different inputs or different initialization of the work space.
+Namely, $\ground{\Hin\big|_{S \cap \Kclock \cap \Kprop}} \geq 1$.
+Thus,
+\[
+  \ground{(\Hin + \Jclock\Hclock + \Jprop\Hprop)\big|_S} \geq 1- \frac{1}{4}=\frac{3}{4}. 
+\]
+Given that $\histpsi{C(x)}$ is the ground state of $H_{\mathrm{new}}$ with eigenvalue 0, and any orthogonal state to $\histpsi{C(x)}$ has eigenvalue at least $\ground{H_{\mathrm{new}}}\geq 3/4$, the spectral gap of $H_{\mathrm{new}}$ at at least $3/4$.
 
-\begin{thm}
-	\label{thm:projection}
-	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
-	$$J=\frac{11\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
-	then we have
-	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
-\end{thm}
-\begin{proof}
-	Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least nonzero eigenvalue of $JH_2$ is greater than $10\norm{H_1}$.
+Note that $H_{\mathrm{new}}$ is a 6-local X-Z Hamiltonian by construction.
+It suffices to check the bound of $\abs{\alpha_i}$ and the number of terms.
+The former is determined by $\Jclock$ and $\Jprop$.
+The latter is by counting the number of terms from $\Hin, \Hclock, \Hprop$, each of which is bounded by $O(T)$.
 \end{proof}
+% 	To properly combine the three Hamiltonians defined and analyze it using the projection lemma (\cref{thm:projection}), we consider the kernels of the Hamiltonians we defined.
+% 	$$K_{clock}=\ker H_{clock}$$
+% 	$$K_{in}=\ker H_{in}$$
+% 	$$K_{prop}=\ker H_{prop}$$
+
+% 	Clearly,
+% 	$$K_{clock}=\set{\sum_{t=1}^T \ket{\phi_t}\otimes\ket{\hat{t}}:\ket{\phi_t}\in\cB^{\otimes n}}$$
+% 	Let $\ket\phi\in K_{clock}\cap K_{prop}$.
+% 	Consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$.
+% 	As $\ket\phi\in K_{prop}$, we can then do induction using $\widetilde{t}$ as base case to get the relations between the $\ket{\phi_t}$s and conclude that $\ket\phi$ must have the form:
+% 	$$\ket\phi=\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}$$
+% 	$$\Rightarrow K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
+% 	As a direct result, we get
+% 	$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$$
+% \begin{align*}
+% 	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
+% 	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{C(x)}|y}=0}
+% \end{align*}
+% $$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
+% So we set $H_{C(x)}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
+
+\subsection{Delegation Protocol for $\QPIP_1$ client}
+\label{sec:qpip1}
+In this subsection, we construct a one-message $\QPIP_1$ delegation protocol for $\SampBQP$.
+By definition of $\QPIP_1$, we assume the client has limited quantum power, e.g., performing single qubit $X$ or $Z$ measurement one by one.
+Intuitively, one should expect the one-message from the server to the client is something like the history state so that the client can measure to sample.
+
+At a high-level, the design of such protocol should consist of at least two components: (1) the first component should test whether the message is indeed a valid history state; (2) the second component should simulate the last step of a $\SampBQP$ computation by measuring the final state in the computational basis.
+Our construction of X-Z local Hamiltonian $H$ from \Cref{thm:LHReduction} will help serve the first purpose. 
+In particular, we adopt a variant of the energy verification protocol for local Hamiltonian (e.g., ~\cite{mf16, PhysRevA.93.022326}) to certify the energy of $H$ with only $X$ or $Z$ measurements.
+Moreover, because of the large spectral gap, when the energy is small, the underlying state must also be close to the history state. 
+Precisely, consider the following protocol $\cVGS$:
+
+\begin{protocol}{Energy verification for X-Z local Hamiltonian $\cVGS$} \label{AlgGroundStateCheck}
+Given a $k$-local X-Z Hamiltonian 
+$H=\sum_i \alpha_{i} H_i$ (i.e., $\forall i, H_i \in \LHXZ{k}$) and any state $\ket{\phi}$.
+%Let $\ket\phi$ be the potential ground state to check.
+
+\begin{itemize}
+\item Let $p_i= \abs{\alpha_i}/\sum_i \abs{\alpha_i}$ for each $i$. Sample $i^*$ according to $p_{i^*}$. 
+\item Pick $H_{i^*}$ which acts non-trivially on at most $k$ qubits of $\ket{\phi}$. Measure the corresponding single-qubit Pauli X or Z operator. 
+Record the list of the resutls $x_j=\pm 1$ for $j=1, \ldots k$. 
+\item Let $r=x_1x_2\cdots x_k$. The protocol \emph{accepts} if $r$ and $\alpha_{i^*}$ have different signs, i.e., $\sgn(\alpha_{i^*})r=-1$. Otherwise, the protocol \emph{rejects}. 
+\end{itemize}
+\end{protocol}
+% In this subsection, we prove \cref{ThmXZCheck}.
+% That is, we present and analyze an algorithm that checks whether a given state is the ground state of some fixed $H_{C(x)}$, following~\cite{PhysRevA.93.022326}.
+
+\begin{lem}[\cite{PhysRevA.93.022326}]
+	\label{thm:HamCheck}
+	For any $k$-local X-Z Hamiltonian $H=\sum_i \alpha_{i} H_i$ and any state $\ket{\phi}$, 
+	the protocol $\cVGS$ in Protocol~\ref{AlgGroundStateCheck} accepts with 
+	probability
+\begin{equation}
+ \mathrm{Prob}[ \cVGS \text{ accepts } \ket{\psi}] = \frac{1}{2} - \frac{1}{2 \sum_i \abs{\alpha_i}}\braket{\phi|H|\phi}.
+\end{equation}
+\end{lem}
+
+\begin{theorem} \label{thm:HamCheckClose}
+Given any quantum circuit $C$ and input $x$, consider using $H_{C(x)}$ from \Cref{thm:LHReduction} in Protocol~\ref{AlgGroundStateCheck} ($\cVGS$). 
+For any state $\rho$, and $0< \epsilon < 1$, if $\cVGS$ accepts $\rho$ with probability, 
+\[
+ \mathrm{Prob}[\cVGS \text{ accepts } \rho] \geq \frac{1}{2} - \frac{\epsilon}{2 \sum_i \abs{\alpha_i}},
+\]
+then the fidelity between $\rho$ and $\histpsi{C(x)}$ is at least $1-\epsilon$. 
+\end{theorem}
+
+\begin{prf} Consider the pure state case $\rho=\proj{\phi}$ first. By \Cref{thm:HamCheck} and our assumption, we have $\braket{\phi|H|\phi} \leq \epsilon$. 
+Decompose $\ket{\phi}= \alpha \histpsi{C(x)} + \beta \histpsi{C(x)}^\bot$.
+Note that $\histpsi{C(x)}$ is a eigenvector $H_{C(x)}$ of eigenvalue 0 and all other eigenvalues are at least $3/4$.
+Thus, we have $\abs{\beta}^2 \leq \frac{4}{3}\epsilon$.
+Thus,
+\[
+  \mathrm{F}(\histpsi{C(x)}, \ket{\phi}) =
+\] 
+\XW{todo from here; might need to change the theorem statement as well}
+$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
+	We can then see
+	$$\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$$
+	which can be generalized for mixed states since we have for all $\ket\psi$ that
+	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \ket\psi)=\sum_i p_i F(\ket{\phi_i}, \ket\psi).$$
+	As a result, we have
+	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
+	which implies our claim.
+\end{prf}
+
+% \begin{algorithm}
+% 	\caption{Check for ground state $\cVGS$}
+% 	\label{AlgGroundStateCheck}
+% 		Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
+% 		Let $\ket\phi$ be the potential ground state to check.
+% 		\begin{itemize}
+% 			\item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
+% 			\item Set $p_S = \frac{|d_S|}{D}$
+% 			\item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
+% 			\item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
+% 			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept by outputting $1$. Otherwise, reject by outputting $0$.
+% 		\end{itemize}
+% \end{algorithm}
+% \begin{prf}
+% 	Here we follow \cite{PhysRevA.93.022326}.
+% 	\begin{align*}
+% 		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
+% 		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
+% 		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
+% 		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
+% 	\end{align*}
+
+% 	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
+% 	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
+% 	\begin{align*}
+% 		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
+% 		&=\frac{1}{2}-\frac{O(1)}{T^5}\braket{\phi|H|\phi}
+% 	\end{align*}
+% \end{prf}
+
+\XW{rewrite this part of the introduction}
+At a high level, it is a cut-and-choose protocol.
+The server constructs multiple copies of the ground state as certificates,
+then the client randomly chooses a copy to output and checks the rest.
+Unfortunately our approach incurs inverse polynomial soundness errors.
+
+There are two main challenges to this cut-and-choose approach.
+First, the client needs to reliably extract the circuit output from its corresponding ground state.
+We accomplish this by padding the circuit with identity gates at the end.
+By doing so, the clock register collapses to after the last non-identity gate with high probability.
+
+The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
+so common techniques such as Chernoff bounds can't be applied as-is.
+This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...
+\Ethan{TODO; need brief and intuitive explanation}
+In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem
+to approximate our measurement results with that of some unentangled copies,
+within inverse polynomial errors.
 
@@
 
-% The second one is a way to verify ground states of local Hamiltonians, again with some extra properties:
-% \begin{thm}
-% 	\label{ThmXZCheck}
-% 	Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists a $\BQP$ algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
-(In particular, it accepts the $\ket{\psi_{C(x)}}$ with probability $\fot$.) Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
-% \end{thm}
-
-%\subsection{Circuits of Toffoli and Hadamard gates}
-
-% Old notation: Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
-I.e.
-$\Lambda^2_{1, 2}(X_3)$ would be a Toffoli gate.
-% \Ethan{TODO: replace with something that looks better and doesn't conflict with the use of $\Lambda$ as measurement.}
-
-% Now we present the proof that $\set{H, \Lambda^2(X)}$ is indeed a universal gate set from \cite{quant-ph/0301040}: \Ethan{This definitely belongs in the appendix instead...}
-% \begin{thm}
-% 	Let $C$ be a circuit that:
-% 	\begin{itemize}
-% 		\item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
-% 		\item uses $n$ qubits
-% 	\end{itemize}
-% 	Then a classical machine given $C$ can compute a circuit $C'$ that:
-% 	\begin{itemize}
-% 		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
-% 		\item uses $n+1$ qubits
-% 		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
-% 		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
-% 	\end{itemize}
-% \end{thm}
-% \begin{prf}
-% 	We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
-% 	$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
-% 		$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-
-% 	Now consider the transform on quantum states
-% 	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
-% 	where $\Re$ and $\Im$ denote real and imaginary parts respectively.
-
-% 	This transform commutes with Hadamard gates on the respective qubit.
-On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turn it into a combination of Hadamard and Toffoli gates.
-Mathematically,
-% 	$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
-% 	$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
-
-% 	We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
-% 	\begin{itemize}
-% 		\item $C'$ uses only Hadamard and Toffoli gates.
-% 		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
-% 		\item When $x$ is classical, $\mathcal{F}(x)=x||0$.
-So $F\circ C(x)=C'(x||0)$.
-It is simple \hannote{need a little more work?}to verify that $\mathcal{F}$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
-% 	\end{itemize}
-% \end{prf}
-
-In this subsection, we prove \cref{thm:LHReduction} by showing how to reduce a $\SampBQP$ circuit to a local-$XZ$-Hamiltonian.
-
-	The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.
-
-	Let $x_i$ denote the $i$-th bit of $x$, and let $n$ be the number of qubits in $C$.
-
-	We need to ensure the excited states of $H_{C(x)}$ have high eigenvalues.
-
-	To properly combine the three Hamiltonians defined and analyze it using the projection lemma (\cref{thm:projection}), we consider the kernels of the Hamiltonians we defined.
-	$$K_{clock}=\ker H_{clock}$$
-	$$K_{in}=\ker H_{in}$$
-	$$K_{prop}=\ker H_{prop}$$
-
-	Clearly,
-	$$K_{clock}=\set{\sum_{t=1}^T \ket{\phi_t}\otimes\ket{\hat{t}}:\ket{\phi_t}\in\cB^{\otimes n}}$$
-	Let $\ket\phi\in K_{clock}\cap K_{prop}$.
-	Consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$.
-	As $\ket\phi\in K_{prop}$, we can then do induction using $\widetilde{t}$ as base case to get the relations between the $\ket{\phi_t}$s and conclude that $\ket\phi$ must have the form:
-	$$\ket\phi=\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}$$
-	$$\Rightarrow K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
-
-	As a direct result, we get
-	$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$$
-
-We now consider the space outside the desired state.
-$$S=(\spn\set{\ket{\psi_{C(x)}}})^\bot$$
-$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
-To combine the Hamiltonians, we apply the projection lemma twice.
-$$\exists J_{clock}
-=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
-=O(n)=O(T)$$
-$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
-\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
-$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
-=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
-$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
-\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
-\begin{align*}
-	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
-	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{C(x)}|y}=0}
-\end{align*}
-$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
-So we set $H_{C(x)}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
-
-\subsection{TBA}
-
-In this subsection, we prove \cref{ThmXZCheck}.
-That is, we present and analyze an algorithm that checks whether a given state is the ground state of some fixed $H_{C(x)}$, following~\cite{PhysRevA.93.022326}.
-
-\begin{algorithm}
-	\caption{Check for ground state $\cVGS$}
-	\label{AlgGroundStateCheck}
-		Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
-		Let $\ket\phi$ be the potential ground state to check.
-		\begin{itemize}
-			\item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
-			\item Set $p_S = \frac{|d_S|}{D}$
-			\item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
-			\item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
-			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept by outputting $1$. Otherwise, reject by outputting $0$.
-		\end{itemize}
-\end{algorithm}
-
-\begin{thm}
-	\label{thm:HamCheck}
-	Let $H$ have $O(T)$ nonzero terms whose coefficients are at most $O(T^4)$.
-	\Ethan{Missing a bunch of other assumptions... Should just state $H$ as local Hamiltonian instance from earlier}
-	Then $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{O(1)}{T^5}\braket{\phi|H_{C(x)}|\phi}$.
-\end{thm}
-\begin{prf}
-	Here we follow \cite{PhysRevA.93.022326}.
-	\begin{align*}
-		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
-		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
-		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
-		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
-	\end{align*}
-
-	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
-	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
-	\begin{align*}
-		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
-		&=\frac{1}{2}-\frac{O(1)}{T^5}\braket{\phi|H|\phi}
-	\end{align*}
-\end{prf}
-
-\begin{cor}
-	\Ethan{Consider merging this with theorem above}
-
-	\label{cor:HamCheck}
-	There exists some $c\in\bbR$ s.t.
-	let $H_{C(x)}$ be as above and
-	$\varepsilon\in\bbR$, then
-	if $\cVGS(\rho)$ accepts with probability at least $\frac{1}{2}-\frac{c\varepsilon}{T^5}$
-	then $F(\rho, \ket{\psi_{C(x)}})\geq1-\varepsilon$
-\end{cor}
-\begin{prf}
-	We first argue this with pure state input $\ket\phi$.
-
-	Define $c$ so that $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{c}{T^5}\braket{\phi|H_{C(x)}|\phi}$.
-	Break $\ket{\phi}$ above into what's in the kernel of $H$ and what isn't:
-	$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
-	We can then see
-	$$\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$$
-	which can be generalized for mixed states since we have for all $\ket\psi$ that
-	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \ket\psi)=\sum_i p_i F(\ket{\phi_i}, \ket\psi).$$
-	As a result, we have
-	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
-	which implies our claim.
-\end{prf}
+\input{qpip}
 
@@
 % \end{prf}
+
+% The second one is a way to verify ground states of local Hamiltonians, again with some extra properties:
+% \begin{thm}
+% 	\label{ThmXZCheck}
+% 	Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists a $\BQP$ algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
+(In particular, it accepts the $\ket{\psi_{C(x)}}$ with probability $\fot$.) Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
+% \end{thm}
+
+%\subsection{Circuits of Toffoli and Hadamard gates}
+
+% Old notation: Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
+I.e.
+$\Lambda^2_{1, 2}(X_3)$ would be a Toffoli gate.
+% \Ethan{TODO: replace with something that looks better and doesn't conflict with the use of $\Lambda$ as measurement.}
+
+% Now we present the proof that $\set{H, \Lambda^2(X)}$ is indeed a universal gate set from \cite{quant-ph/0301040}: \Ethan{This definitely belongs in the appendix instead...}
+% \begin{thm}
+% 	Let $C$ be a circuit that:
+% 	\begin{itemize}
+% 		\item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
+% 		\item uses $n$ qubits
+% 	\end{itemize}
+% 	Then a classical machine given $C$ can compute a circuit $C'$ that:
+% 	\begin{itemize}
+% 		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
+% 		\item uses $n+1$ qubits
+% 		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
+% 		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
+% 	\end{itemize}
+% \end{thm}
+% \begin{prf}
+% 	We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
+% 	$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
+% 		$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
+
+% 	Now consider the transform on quantum states
+% 	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
+% 	where $\Re$ and $\Im$ denote real and imaginary parts respectively.
+
+% 	This transform commutes with Hadamard gates on the respective qubit.
+On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turn it into a combination of Hadamard and Toffoli gates.
+Mathematically,
+% 	$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
+% 	$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
+
+% 	We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
+% 	\begin{itemize}
+% 		\item $C'$ uses only Hadamard and Toffoli gates.
+% 		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
+% 		\item When $x$ is classical, $\mathcal{F}(x)=x||0$.
+So $F\circ C(x)=C'(x||0)$.
+It is simple \hannote{need a little more work?}to verify that $\mathcal{F}$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
+% 	\end{itemize}
+% \end{prf}

### 2020-04-14 preliminaries.tex
Add notes and others' updates

@@
 We have $\norm{\rho_1-\rho_2}_{tr}\leq\sqrt{1-F(\rho_1, \rho_2)}$.
-We say $\rho_1$ and $\rho_2$ are $\varepsilon$-close if $F(\rho_1, \rho_2)\leq\varepsilon$.
+We say $\rho_1$ and $\rho_2$ are $\varepsilon$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\varepsilon$.
 For two distributions $f_1$ and $f_2$ over the same finite domain $X$, we write $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ for their total variation distance,
@@
 	$\SampBQP$ is the class of sampling problems $\left(D_x\right)_{x\in\set{0, 1}^*}$ that can be (approximately) sampled by polynomial-size uniform quantum circuits.
-Namely, there exists a Turing machine $M$ such that for every $n \in \bbN$ and $\varepsilon \in (0,1)$, $M(1^n, 1^{1/\eps})$ outputs a quantum circuit $C$ in $\poly(n, 1/\varepsilon)$ time such that for every $x \in \zo^n$, the output of $C(x)$ (measured in standard basis) is $\eps$-close to $D_x$.
+Namely, there exists a Turing machine $M$ such that for every $n \in \bbN$ and $\varepsilon \in (0,1)$, $M(1^n, 1^{1/\varepsilon})$ outputs a quantum circuit $C$ in $\poly(n, 1/\varepsilon)$ time such that for every $x \in \zo^n$, the output of $C(x)$ (measured in standard basis) is $\varepsilon$-close to $D_x$.
 \end{definition}
@@
 \subsection{Computational Indistinguishability}
+
+\Ethan{Use Mahadev's definitions, but add eps param
+
+change to subnormalized states
+
+Need to define what it means to apply algorithm to subnormalized states
+
+Two families of (potentially sub-normalized) states... leave author note for applying algorithms to subnormalized states; might be ok
+
+change ``attacker" to ``distinguisher"
+
+sec. param change from n to lambda}
+
+\Ethan{Comment out entire section including triangle ineq.; just leave what's said above}
 
@@
 	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
-	We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c$ and statistical (resp., computational) soundness if the following holds:
+	We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c(\cdot)$ and statistical (resp., computational) soundness if the following holds:
 	\begin{itemize}
-		\item On public inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x\in\zo^n$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$. If $d=\Acc$ then $z\in\zo^{m(n)}$, otherwise $z=\bot$.
+		\item On public inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
+If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$, \footnote{$m$ is the length of...
+TODO} otherwise $z=\bot$.
 		\item (Completeness):
-			For all security parameter $\lambda\in\bbN$, accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$, and $x\in\zo^{\poly(\lambda)}$, 
+			For all accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
+			security parameter $\lambda\in\bbN$,
+			and $x\in\zo^{\poly(\lambda)}$, 
 			Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\varepsilon}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
 		\item (Statistical soundness): For all cheating prover $P^*$,
-			sufficiently large $\lambda\in\bbN$, accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$, and $x\in\zo^{\poly(\lambda)}$, 
+		    accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
+			sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, 
 			consider the following experiment:
 			\begin{itemize}
-				\item Let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
+				\item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\varepsilon}, x)$.
 				\item Define $z_{ideal}$ by
@@
 			It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$. 
-		\item (Computational soundness): Define $d, z, z_{ideal}$ same as above.
-			It holds that for all $\BQP$ distinguisher $D$,
-			$\abs{\Pr[D(1^{\lambda}, d,z) = 1] - \Pr[D(1^{\lambda}, d,z_{ideal}) = 1]} \leq \varepsilon $
+		\item (Computational soundness):
+		For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
+			sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$, 
+			define $d, z, z_{ideal}$ by the same experiment as above.
+			It holds that
+			$$\abs{\Pr[\mathsf{D}(1^{\lambda}, d,z) = 1] - \Pr[\mathsf{D}(1^{\lambda}, d,z_{ideal}) = 1]} \leq \varepsilon $$
 	\end{itemize}
@@
 We now define blindness of a protocol.
-In the context of blind protocols, the above definitions should be modified so that $x$ is the verifier's private input.
-We define blindness with an accuracy parameter $\varepsilon$, which exists in protocols for $\SampBQP$ instances;
-one can leave it out where appropriate, such as in protocols for $\BQP$ languages.
+In the context of blind protocols, we consider $x$ as the verifier's private input instead of a common input.  
+%the above definitions should be modified so that $x$ is the verifier's private input.
+%We define blindness with an accuracy parameter $\varepsilon$, which exists in protocols for $\SampBQP$ instances;
+%one can leave it out where appropriate, such as in protocols for $\BQP$ languages.
 
 \begin{definition}
-	Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ and $1^{1/\varepsilon}$, and verifier's private input $x\in\zo^*$.
-	We say $\Pi$ is \emph{blind} if for all cheating prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
+	Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ (and $1^{1/\varepsilon}$ for the case of $\SampBQP$ problem), and verifier's private input $x\in\zo^*$.
+	We say $\Pi$ is \emph{blind} if for all cheating $\BQP$ prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
 	\begin{itemize}
@@
 
-\Ethan{Proj. lemma and de Finetti thm. were moved}
-
 \subsection{Quantum Homomorphic Encryption Schemes}
@@
 		\item \emph{Key generation.}
-			The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda)$ takes a unary representation of the security parameter and outputs a public key encryption key $pk$ and a secret decryption key $sk$.
+			The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda)$ takes a unary representation of the security parameter as input and outputs a public key $pk$ and a secret key $sk$.
 		\item \emph{Encryption.}
-			The algorithm $c\leftarrow\QEnc(pk, \mu)$ takes the public key $pk$ and a single bit message $\mu\in\zo$ and outputs a ciphertext $c$.
+			The algorithm $c\leftarrow\QEnc(pk, \mu)$ takes the public key $pk$ and a single bit message $\mu\in\zo$ as inputs and outputs a ciphertext $c$.
 		\item \emph{Decryption.}
-			The algorithm $\mu^*\leftarrow\QDec(sk, c)$ takes the secret key $sk$ and a ciphertext $c$ and outputs a message $\mu^*\in\zo$.
+			The algorithm $\mu^*\leftarrow\QDec(sk, c)$ takes the secret key $sk$ and a ciphertext $c$ as inputs and outputs a message $\mu^*\in\zo$.
 			It must be the case that
@@
 		\item \emph{Homomorphic Evaluation.}
-			The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit \Ethan{?} $f$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ and outputs a ciphertext $c_f$.
+			The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit $f$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ as inputs and outputs a ciphertext $c_f$.
 			It must be the case that
@@
 \begin{definition}[Compactness and Full Homomorphism]
-	\Ethan{This is copied from Mahadev. Not sure how much of this we need. We need at least how leveled HE is defined.}
-
 	A quantum homomorphic encryption scheme $\QHE$ is compact if
@@
 	boolean function. A compact scheme is leveled fully homomorphic if it takes $1^L$ as additional input in key generation,
-	and can only evaluate depth $L$ Boolean circuits where $L$ is polynomial in $\lambda$. A scheme is quantum pure or
-	leveled fully homomorphic if we refer to quantum circuits rather than boolean circuits.
+	and can only evaluate depth $L$ Boolean circuits where $L$ is polynomial in $\lambda$.
 \end{definition}
+
+\Ethan{Combine leveled dfn. with QFHE; keep compactness here}
 
@@
 \begin{definition}
-	\Ethan{This was copied from Mahadev. Not sure where $L$ (level) goes.}
 	A scheme $\QHE$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
@@
 	\begin{itemize}
-		\item $\QGen$ produces classical keys
+		\item $\QGen$ is a classical algorithm
 		\item In the case where the plaintext is classical, $\QEnc$ can be done classically.
@@
 	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine,
-	there exists a classical-friendly quantum homomorphic encryption scheme.
+	there exists a classical-friendly compact quantum leveled homomorphic encryption scheme.
 \end{theorem}

### 2020-04-14 qpip.tex
Add notes and others' updates

@@
-\section{Delegation Protocol for $\QPIP_1$ Client}
+%\section{Delegation Protocol for $\QPIP_1$ Client}
 
-In this section, we construct a one-message $\QPIP_1$ delegation protocol for $\SampBQP$.
-At a high level, it is a cut-and-choose protocol.
-The server constructs multiple copies of the ground state as certificates,
-then the client randomly chooses a copy to output and checks the rest.
-Unfortunately our approach incurs inverse polynomial soundness errors.
+% In this section, we construct a one-message $\QPIP_1$ delegation protocol for $\SampBQP$.
+% At a high level, it is a cut-and-choose protocol.
+% The server constructs multiple copies of the ground state as certificates,
+% then the client randomly chooses a copy to output and checks the rest.
+% Unfortunately our approach incurs inverse polynomial soundness errors.
 
-There are two main challenges to this cut-and-choose approach.
-First, the client needs to reliably extract the circuit output from its corresponding ground state.
-We accomplish this by padding the circuit with identity gates at the end.
-By doing so, the clock register collapses to after the last non-identity gate with high probability.
+% There are two main challenges to this cut-and-choose approach.
+% First, the client needs to reliably extract the circuit output from its corresponding ground state.
+% We accomplish this by padding the circuit with identity gates at the end.
+% By doing so, the clock register collapses to after the last non-identity gate with high probability.
 
-The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
-so common techniques such as Chernoff bounds can't be applied as-is.
-This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...
-\Ethan{TODO; need brief and intuitive explanation}
-In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem
-to approximate our measurement results with that of some unentangled copies,
-within inverse polynomial errors.
+% The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
+% so common techniques such as Chernoff bounds can't be applied as-is.
+% This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...
+% \Ethan{TODO; need brief and intuitive explanation}
+% In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem
+% to approximate our measurement results with that of some unentangled copies,
+% within inverse polynomial errors.
 
@@
 
-	Ingrediants:
+	Ingredients:
 	\begin{itemize}

### 2020-04-14 qpip0.tex
Add notes and others' updates

@@
 %Subprotocol for Quantum Measurements
-\subsection{$\QPIP_0$ for BQP?}
-\hannote{Ethan old description before parallel rep.}
-As a warm-up, we  restate the construction in \cite{FOCS:Mahadev18a}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.
+% \subsection{$\QPIP_0$ for BQP?}
+% \hannote{Ethan old description before parallel rep.}
+% As a warm-up, we  restate the construction in \cite{FOCS:Mahadev18a}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.
 
-Let $\rho$ be an $n$-qubit state.
+% Let $\rho$ be an $n$-qubit state.
 Let $h$ be an n-bits string called the \emph{basis choice}.
@@
 \label{proto:urmila4}
+\Ethan{TODO Make notation consistent with protocols in other sections}
+
 \begin{enumerate}
+
     \item Verifier $\bbV$ is a classical machine. Prover $\bbP$ is a $\BQP$ machine. 
@@
 With loss of generality,  we can assume that the testing round verification is deterministic.
-We denote the set of strings $a$ accepted by the verifier in the testing round with $(pk,y)$ as $\Acc_{pk,y}$.
+We denote the set of strings $a$ \Ethan{Font makes this $a$ look screwy} accepted by the verifier in the testing round with $(pk,y)$ as $\Acc_{pk,y}$.
 \end{definition}
@@
 \end{lem}
+
+\Ethan{Again change all n to lambda for sec. param.}
 
@@
 \begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
+If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ \Ethan{Prover will produce isn't right, the one producing z should be verifier} on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
 \end{lemma}
@@
 
+\Ethan{Probably can omit details from below}
+
 \begin{protocol}{naive $\QPIP_0$ protocol  for the $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$}
@@
 
-	Inputs: \Ethan{Should the $\SampBQP$ instance be an input?}
+	Inputs: \Ethan{Just assume PiSamp has the properties I need including non-adaptive measurements. Maybe make author note for now if needed and add it back later}
 	\begin{itemize}
@@
 We also allow a cheating prover to send $\bot$ in the fourth round of Protocol~\ref{proto:urmila4} if $c=1$ to abort the process.\footnote{This is useless for the cheating prover but useful for proving one of our theorems.} If the verifier receives $\bot$ in the fourth round, he outputs $(\Rej,\bot)$ and terminates this protocol.
+Let $z_{commit}$ be the output of the called Protocol~\ref{proto:urmila4}.
 
-	\item If $c=1$, the verifier finished the verification step of Protocol~\ref{ProtoQPIP1} by using $z_{commit}$ from Protocol~\ref{proto:urmila4} as the measurement result he would get and outputs $(d,z_{naive})$.
+	\item If $c=1$, the verifier finished the verification step of Protocol~\ref{ProtoQPIP1} by using $z_{commit}$  as the measurement result he would get and outputs $(d,z_{naive})$.
 
@@
 
+\Ethan{Might need to fix the following. Note that it's not a standard parallel rep, so we can't just say it's N-fold parallel rep without saying anything else}
+
 \begin{protocol}{$\QPIP_0$ for $\SampBQP$}
@@
 
-    \item Run $m=O(1/\varepsilon^2)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications.
+    \item Run $m=O(1/\varepsilon^2)$ copies of protocol~\ref{proto:urmila4} in parallel \Ethan{proto 2?
+Or 3?}, with following modifications.
 The copies have separate $\{h\}$, $\{sk\}$, $\{pk\}$, $\{y\}$, $\{c\}$, and $\{a\}$.
@@
 
-\hannote{Intuitions about the partition lemma. }
+\hannote{intuition about proof}
+
+\hannote{Intuitions about the partition lemma. efficient projectors into passing testing part and not passing testing part.}
+
+\hannote{related notation back to 3.5}
 
 %Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
-\begin{lemma}[partition lemma]\label{lem:partition2}
+\begin{lemma}[partition lemma \hannote{ref}\Ethan{Lemma number?}]\label{lem:partition2}
 Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round.
@@
 
- For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,
+ For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ \Ethan{Not consistent with the cited paper; typeof(G0, G1) aren't q circuits} such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,
 
@@
   Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are  sub-normalized.
-$G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$ and $pk,sk,y$.
+$G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$ and $pk,y$.
 \hannote{check}
@@
 \begin{enumerate}
-    \item \label{property:partition-err}  $$E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\|^2 \leq \frac{6}{T}+\negl(n),$$
+    \item \label{property:partition-err}  $$\E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\|^2 \leq \frac{6}{T}+\negl(n),$$
 
@@
     \begin{align}
-        E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\| \leq \sqrt{\frac{6}{T}}+\negl(n)
+        \E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\| \leq \sqrt{\frac{6}{T}}+\negl(n)
     \end{align}
@@
 $$z_i\defeq \E_{pk,y} \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
-where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round. \hannote{add description about  averaging $pk$ here.}
+where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round.
+Note that we have averaged over $pk, y$ where as previously everything has fixed $pk$ and $y$.
+\hannote{add description about  averaging $pk$ here.}
 
@@
 \begin{align}
-    z_{good,i}=E_\gamma \sum_z \proj{z} \cdot \vev{e_i,\psi_{1^{i-1}1,\gamma}|U^\dag P_{acc,i,z} U|e_i,\psi_{1^{i-1}1,\gamma}}
+    z_{good,i}=\E_\gamma \sum_z \proj{z} \cdot \vev{e_i,\psi_{1^{i-1}1,\gamma}|U^\dag P_{acc,i,z} U|e_i,\psi_{1^{i-1}1,\gamma}}
 \end{align}
@@
     &\L[ \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}\R]  \nn \\
-    =& E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}} +\bra{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} \R]U^\dag  P_{acc,i,z} U\nn \\
+    =& \E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}} +\bra{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} \R]U^\dag  P_{acc,i,z} U\nn \\
     &\L[ \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}\R]  \nn \\
-    =& z_{good,i}+ E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
+    =& z_{good,i}+ \E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
     \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \nn \\
@@
 
- where we omitted writing out $e_i$ starting the second line.  We have \Ethan{$\ket{z}\bra{z}$?}
+ where we omitted writing out $e_i$ starting the second line. We have
 \begin{align} \label{eq:zi-zgoodi}
     &\tr|z_i-z_{good,i}|   \nn \\
-    \leq&  \sum_z  \L| E_\gamma \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
+    \leq&  \sum_z  \L| \E_\gamma \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
     \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \R. \nn \\
@@
     +&\L.\L.\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R]\R| \nn \\  %%%%%%%%%%%
-    \leq&  \sum_z   E_\gamma \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^j0,\gamma}} \R|+
+    \leq&  \sum_z   \E_\gamma \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^j0,\gamma}} \R|+
     2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R.  \nn \\
@@
 By construction, when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$.
-Also note that this is the only case where the verifier won't reject, so $(d,z_{composite,i})=(d,z_{good,i})$, where  $(d,z_{good,i}) \defeq (\Acc, z_{good,i}) + (1-|z_{good,i}|)(\Rej,\bot)$ \hannote{correct notation?} .
+Also note that this is the only case where the verifier won't reject, so $(d,z_{composite,i})=(d,z_{good,i})$, where  $(d,z)_{good,i} \defeq (\Acc, z_{good,i}) + (1-|z_{good,i}|)(\Rej,\bot)$ \hannote{correct notation?
+operational def?} .
 Therefore

### 2020-04-14 blind.tex
Add lambda in blindness compiler

@@
 
-	Public input: $x$ \Ethan{Add footnote here about eps}
+	Common inputs\footnote{TODO something about eps}:
+	\begin{itemize}
+		\item $x\in\zo^*$
+		\item $1^\lambda$
+	\end{itemize}
+
 	\begin{enumerate}
-		\item $V$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$ and sends $v_1$ to the prover.
-		\item $P$ generates $(p_1, st_{P, 1})\leftarrow\cP_1(v_1, x)$ and sends $p_1$ to the verifier.
+		\item $V$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(1^\lambda, x)$ and sends $v_1$ to the prover.
+		\item $P$ generates $(p_1, st_{P, 1})\leftarrow\cP_1(1^\lambda, v_1, x)$ and sends $p_1$ to the verifier.
 		\item for $t=2,\ldots,T$:
@@
 \begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ correponding to $\Pi_0$}
-    \Ethan{Sync common or public inputs wording. Prefer common.}
-	Verifier's input: $x$
+	Common input: $\lambda$
+
+	Verifier's input: $x\in\zo^*$
 
@@
 			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
-		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
-			by evaluating %\linebreak
-			$(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow  \QEval(pk, \cP_1,$ \  $\ctx{v}{1}{1}, \ctx{x}{}{1})$.
+		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(1^\lambda, \ctx{v}{1}{1}, \ctx{x}{}{1})$
+			by evaluating
+			$(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow  \QEval(pk, \cP_1,$ \  $\QEnc(pk_1, 1^\lambda), \ctx{v}{1}{1}, \ctx{x}{}{1})$.
 			It sends $\ctx{p}{1}{1}$ to the verifier.
@@
 	$\ctx{x}{}{1}\leftarrow\QEnc(pk_1, x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc(pk_1, v_1)$.
-	It then runs $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$.
+	It then runs $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(1^\lambda, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
 	Finally, it decrypts $p_1\leftarrow\QDec(sk_1, \ctx{p}{1}{1})$ and sends it back to the verifier,

### 2020-04-14 blind.tex
Attempt to wrap up my own sections

@@
 We now state our compiler that gives any $\QPIP_0$ protocol blindness.
-For the sake of simplicity, we omit the security and accuracy parameters.
 For notation, when there are many sets of $\QHE$ keys in play at the same time,
 we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
-
-\Ethan{Say in words I'm going to compile proto 5 (which is a general form of...) to proto 6}
-
-\Ethan{Add lambda back}
+We start with a general form of a $\QPIP_0$ protocol that we'll be compiling.
 
@@
 
-	Common inputs\footnote{TODO something about eps}:
+	Common inputs\footnote{For the sake of simplicity, we omit accuracy parameter $\varepsilon$ where it exists}:
 	\begin{itemize}
-		\item $x\in\zo^*$
-		\item $1^\lambda$
+		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
+		\item Some classical input $x\in\zo^*$ \Ethan{Or should this be $\zo^n$? Or $\zo^{\poly(\lambda)}$?}
 	\end{itemize}
@@
 \begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ correponding to $\Pi_0$}
-	Common input: $\lambda$
+	Inputs:
+	\begin{itemize}
+		\item Common input: Security parameter $1^\lambda$ where $\lambda\in\bbN$
+		\item Verifier's input: $x\in\zo^n$
+	\end{itemize}
 
-	Verifier's input: $x\in\zo^*$
-
-	Let $L=\poly(x)$ \Ethan{Quantify/define L more clearly}, $\lambda=\poly(x)$.
+	Ingrediants:
+	\begin{itemize}
+		\item Let $L$ be the maximum circuit depth of $\cP_t$.
+	\end{itemize}
 
 	\begin{enumerate}
-		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
+		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(1^\lambda, x)$.
 			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$,
@@
 \begin{proof}
-	Consider $T+1$ hybrids experiments, from $\Hyb_1$ to $\Hyb_{T+1}$.
-	We define $\Hyb_{T+1}$ to be $\Piblind$.
-	For $t<T+1$, we define $\Hyb_{t}$ to be the same as $\Hyb_{t+1}$,
-	except when $\Vblind$ should send $\ctx{sk}{t}{t}$, it instead sends $\ctx{0}{}{t}$ which is encryption of $0$ under $pk_t$.
-	Then, for all $t$, from the perspective of the prover, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
-	By a standard hybrid argument, we observe that $\Hyb_1$ is computationally indistinguishable with $\Hyb_{T+1}$.
-	Furthermore, $\Hyb_1$ is blind since the prover isn't provided any information about any secret keys.
-	\Ethan{do hybrid on 0 too and make sure it fits the dfns. Also should mention why hybriding works}
-	So we conclude that $\Piblind$ is blind.
+	We show that for all cheating prover $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
+	$P^*$ cannot distinguish $(P^*, \Vblind(x))(\lambda)$ from $(P^*, \Vblind(0^n))(\lambda)$ with noticeable probability in $\lambda$.
+	We use a hybrid argument; let $\Hyb_{T+1}^x=(P^*, \Vblind(x))(\lambda)$ and $\Hyb_{T+1}^0=(P^*, \Vblind(0^n))(\lambda)$.
+	For $2\leq t<T+1$, define $\Hyb_t^x$ to be the same as $\Hyb_{t+1}^x$,
+	except when $\Vblind$ should send $\ctx{v}{t}{t}$ and $\ctx{sk}{t-1}{t}$, it instead sends encryptions of $0$ under $pk_t$.
+	We define $\Hyb_1^x$ to be the same as $\Hyb_2^x$ except the verifier sends encryptions of $0$ in place of $\ctx{x}{}{1}$ and $\ctx{v}{1}{1}$.
+	We define $\Hyb_t^0$ similarly. Note that $\Hyb_1^x$ and $\Hyb_1^0$ are identical.
+
+	For all $t$, from the perspective of the prover,
+	as it receives no information on $sk_t$,
+	$\Hyb_{t+1}^x$ is computationally indistinguishable from $\Hyb_t^x$ due to the CPA security of $\QHE$ under $pk_t$.
+	By a standard hybrid argument, we observe that $\Hyb_1^x$ is computationally indistinguishable with $\Hyb_{T+1}^x$.
+	We use the the same argument for the computational indistinguishability between $\Hyb_1^0$ and $\Hyb_{T+1}^0$.
+	We conclude that $P^*$ cannot distinguish between $\Hyb_{T+1}^x$ and $\Hyb_{T+1}^0$,
+	therefore $\Piblind$ is blind.
 \end{proof}

### 2020-04-14 preliminaries.tex
Attempt to wrap up my own sections

@@
 	\begin{itemize}
-		\item $P$ is a $\BQP$ \Ethan{wording; quantum poly time?} machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
+		\item $P$ is a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
 		\item $V$ is a hybrid machine of a classical part and a limited quantum part.
@@
 		\item On public inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
-If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$, \footnote{$m$ is the length of...
-TODO} otherwise $z=\bot$.
+If $d=\Acc$ then $z$ is in the domain \Ethan{?} of $D_x$, otherwise $z=\bot$.
 		\item (Completeness):
@@
 \begin{definition}
-	A quantum homomophic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
+	A quantum leveled homomophic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
 	$\QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:
@@
 		\item \emph{Key generation.}
-			The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda)$ takes a unary representation of the security parameter as input and outputs a public key $pk$ and a secret key $sk$.
+			The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda, 1^L)$ takes a unary representation of the security parameter and a unary representation of the level parameter as inputs and outputs a public key $pk$ and a secret key $sk$.
 		\item \emph{Encryption.}
@@
 		\item \emph{Homomorphic Evaluation.}
-			The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit $f$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ as inputs and outputs a ciphertext $c_f$.
+			The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit $f$ of depth at most $L$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ as inputs and outputs a ciphertext $c_f$.
 			It must be the case that
@@
 	the number of inputs). A compact scheme is (pure) fully homomorphic if it can evaluate any efficiently computable
-	boolean function. A compact scheme is leveled fully homomorphic if it takes $1^L$ as additional input in key generation,
-	and can only evaluate depth $L$ Boolean circuits where $L$ is polynomial in $\lambda$.
+	boolean function.
 \end{definition}
-
-\Ethan{Combine leveled dfn. with QFHE; keep compactness here}
 

### 2020-04-14 preliminaries.tex
Clean up comp. indistinguishability dfn

@@
 
+\begin{definition}
+	Let $\rho_1,\rho_2\in\cB^n$.
+	We write $\rho_1\approx_{c,\varepsilon}\rho_2$ if $\rho_1$ and $\rho_2$ are \emph{$\varepsilon$-computationally indistinguishable}.
+	That is, for all quantum polynomial-time distinguishers $\mathsf{D}$,
+	$$\abs{\Pr\left[\mathsf(D)(\rho_1)=1\right]-\Pr\left[\mathsf(D)(\rho_2)=1\right]}\leq\varepsilon.$$
+\end{definition}
+
+We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized outputs on subnormalized inputs.
+We also extend it to distributions, which can be treated as mixed states.
+
+\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
+    Let $D_1$, $D_2$, and $D_3$ be three distributions such that 
+    \begin{align}
+		D_1\approx_{c, \varepsilon}D_2\\
+		D_2\approx_{c, \varepsilon'}D_3.
+    \end{align}
+    We have 
+    \begin{align}
+		D_1\approx_{c, \varepsilon+\varepsilon'}D_3.
+    \end{align}
+\end{lem}
+
 \subsection{Sampling Problems}
@@
 \end{definition}
-
-\subsection{Computational Indistinguishability}
-
-\Ethan{Use Mahadev's definitions, but add eps param
-
-change to subnormalized states
-
-Need to define what it means to apply algorithm to subnormalized states
-
-Two families of (potentially sub-normalized) states... leave author note for applying algorithms to subnormalized states; might be ok
-
-change ``attacker" to ``distinguisher"
-
-sec. param change from n to lambda}
-
-\Ethan{Comment out entire section including triangle ineq.; just leave what's said above}
-
-\begin{definition}[quantum computationally indistinguishable]\label{def:comp-indis}
-\hannote{move later}
-Let  $D_1$ and $D_2$ be distributions over $n$-bit string.
-We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes \emph{one} sample from $D_1$ as part of its input.
-We also denote "$D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable" as
-$$ \norm{D_1 - D_2}_q \leq \eps.$$
-And "$D_1$ and $D_2$  are not $\eps$-Q-computationally indistinguishable" as 
-$$ \norm{D_1 - D_2}_q > \eps.$$
-\end{definition}
-%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.
-
-\begin{rmk}
-We extend the definition of computational distance to a subnormalized distribution  $D$  by assuming $A(D)=0$ when $A$ fail to draw a sample from $D$.
-\end{rmk}
-
-\begin{rmk}\label{rmk:trace-to-comp}
-If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
-\end{rmk}
-
-\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
-    Let $D_1$, $D_2$, and $D_3$ be three distributions such that 
-    \begin{align}
-        \norm{D_1 -D_2}_q &\leq \eps \\ 
-        \norm{D_2 -D_3}_q &\leq \eps'. 
-    \end{align}
-    We have 
-    \begin{align}
-        \norm{D_1 -D_3}_q &\leq \eps+\eps'
-    \end{align}
-\end{lem}
-\begin{proof}
-For all quantum circuits $A$ with size $\poly(n)$, we have 
-\begin{align}
-    \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} \leq& \eps \\
-    \norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \leq& \eps',  
-\end{align}
-so 
-\begin{align}
-    &\norm{\Pr[A({D_1})=1]-\Pr[A({D_3})=1]} \nn \\
-    =& \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]+\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
-    \leq&  \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} +\norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
-    =& \eps +\eps' \nn
-\end{align}
-
-\end{proof}
 

### 2020-04-14 qpip0.tex
Fix protocols

@@
 
-In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave a 4-round interactive protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine, which we describe below while omitting the implementation details.
+In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave a 4-round $\QPIP_0$ protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine, which we describe below while omitting the implementation details.
 
-\begin{protocol}{Mahadev's 4 round commitment}
+\begin{protocol}{Mahadev's 4 round commitment protocol $\PiMeasure$}
 \label{proto:urmila4}
-\Ethan{TODO Make notation consistent with protocols in other sections}
+\Ethan{Still rooms for improvements, but it's not as bad as before}
 
+Inputs:
+\begin{itemize}
+	\item Common input: Security parameter $1^\lambda$ where $\lambda\in\bbN$.
+	\item Prover's input: a state $\rho\in\cB^{\otimes n}$ for the verifier to measure.
+	\item Verifier's inputs:
+		\begin{itemize}
+			\item a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit. If $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.  
+			\item a challenge bit $c\in\zo$. The prover needs to do a ``Testing round" if $c=0$. The prover needs to do a ``Hadamard round" if $c=1$.
+		\end{itemize}
+\end{itemize}
+
+The protocol:
 \begin{enumerate}
-
-    \item Verifier $\bbV$ is a classical machine. Prover $\bbP$ is a $\BQP$ machine. 
-%    \item Both the verifier and the prover know a $\BQP$ circuit $C$ and an input string $x$.
-    \item Both party know the number of qubits $n$ and a security parameter $\lambda=1^{\poly(n)}$.
-    \item Verifier has a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit.
-If $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.
-    \item In the first round, the verifier generate a secret key and  public key pair $(sk,pk)$ from $h$ and $\lambda$ and sent $pk$ to the prover.
-    \item In the second round, the prover pick some $n$-qubit quantum state $\rho$ and generate a "commitment" $y$ from $pk$ and $\rho$.
-He send $y$ to the verifier and keep the leftover quantum state $\sigma$.
-    \item In the third round, the verifier send a uniformly random challenge bit $c\in \{0,1\}$. The prover needs to do a "Testing round" if $c=0$. The prover needs to do a "Hadamard round" if $c=1$.
-    \item In the fourth round. The prover generates a classical string $a$ from $c$ and $\sigma$ and send to back to the prover.
-    \item If $c=0$, the verifier decides whether he is going to reject from $(pk,a,y)$. If $c=1$ the verifier computes an $n$-bit string $z$ from $(sk,h,y,a)$, $z=V_f(sk,h,y,a)$.
+    \item The verifier generates a public and secret key pair $(pk, sk)$ on inputs $h$ and $1^\lambda$. It sends $pk$ to the prover.
+    \item The prover generates a classical ``commitment" $y$ and internal state $\sigma$ on inputs $pk$ and $\rho$. He send $y$ to the verifier.
+	\item The verifier sends $c$ to the prover.
+    \item The prover generates a classical string $a$ on inputs $c$ and $\sigma$, and sends it to back to the verifier.
+    \item If $c=0$, the verifier decides whether he is going to reject on inputs $(pk,a,y)$.
+		If $c=1$, the verifier computes an $n$-bit string $z=V_f(sk,h,y,a)$ on inputs $(sk,h,y,a)$.
 \end{enumerate}
 \end{protocol}
+
+\Ethan{The following modifications are mine}
+Two modification have been made from the original protocol.
+\begin{itemize}
+	\item On the protocol's third message. Instead of randomly picking whether to run what's called a ``testing round" or a ``Hadamard round", we let the verifier decide as one of its inputs.
+	\item On the protocol's fourth message, the prover can choose to abort by sending $a=\bot$. This is useless for the cheating prover but useful for proving one of our theorems.
+\end{itemize}
 
@@
 
-% \begin{lem}[another triangle inequality for computational distance \hannote{unused}]\label{lem:computational-triangle}
-% Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.
+Mahadev's 4-round protocol has the following binding property.
 
-% If 
-% \begin{align}
-%     &\norm{D_1 - D_2}_q \leq \eps   \\ 
-%     &\norm{D_4 - D_6}_q \leq \eps',  
-% \end{align}
-% then 
-% \begin{align}
-%   \norm{ D_3 - D_5}_q \leq \eps+\eps' 
-% \end{align}
-% \end{lem}
-% % \begin{align}
-% %     D_1 &\approx_{q,\eps} D_2 \\
-% %     D_4 &\approx_{q,\eps'} D_6, 
-% % \end{align}
-% % then 
-% % \begin{align}
-% %     D_3 \approx_{q,\eps+\eps'} D_5
-% % \end{align}
-% \begin{proof}
-% % Since
-% % $$\norm{D_4 - D_6}_q \leq \eps',$$
-% % there exist
-
-% We prove by contradiction. Suppose that
-% $$\norm{ D_3 - D_5}_q > \eps+\eps',$$
-% then there exist a quantum circuit $A$ of size $poly(n)$ such that 
-% $$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
-% Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that 
-% $$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
-% Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
-% $$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$ 
-% $$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$ 
-% So 
-% \begin{align}
-%     &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
-%     =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
-%     \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
-%      > &\eps 
-% \end{align}
-% This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
-% \end{proof}
-
-Mahadev's 4-round protocol has the following binding property.
+\Ethan{TODO fix variable labels and whatnot here}
 
@@
 
-By combining the commitment Protocol, Protocol~\ref{proto:urmila4}, and the $\QPIP_1$ Protocol, Protocol~\ref{ProtoQPIP1}, we get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.
+By combining the commitment Protocol, $\PiMeasure$, and our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, we get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.
+In particular, we combine them by replacing the verifier's measurements with a call to $\PiMeasure$. It is possible because $\VSamp$ applies only $X$ and $Z$ measurements.
+Furthermore, its measurements are not adaptive, meaning measurement results do not change later measurement basis choices.
 
@@
 
-\begin{protocol}{naive $\QPIP_0$ protocol  for the $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$}
+\begin{protocol}{naive $\QPIP_0$ protocol $\PiNaive$ for the $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$}
 	\label{proto:qpip0_naive}
 
-	Inputs: \Ethan{Just assume PiSamp has the properties I need including non-adaptive measurements. Maybe make author note for now if needed and add it back later}
+	Inputs:
 	\begin{itemize}
+		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
+		\item Error parameter $\varepsilon\in(0, 1)$
 		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
-		\item Error parameter $\varepsilon\in(0, 1)$
+		\item Verifier's input: challenge bit $c\in\zo$ as in $\PiMeasure$
 	\end{itemize}
 
- 	Ingrediants:
- 	\begin{itemize}
- 		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
- 		\item Let $T$ be the number of gates in $C$.
-		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
- 		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
-		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
-		\item Let $s=n+T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$
-%  		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
- 	\end{itemize}
+	% Ingrediant: Let $\varepsilon'=0.99\varepsilon$
 
@@
 	\begin{enumerate}
-	\item The verifier choose a $XZ$-measurement $h$ over  $M=\frac{T^{21}}{\varepsilon^{33}}$  copies of $\ket{\psi_{C'(x)}}$ from the distribution emergent from by Step~\ref{step:qpip1-verify} of Protocol~\ref{ProtoQPIP1}.
-
-	\item \label{step:urmila-in-naive} The verifier and prover run Protocol~\ref{proto:urmila4}, with the following parameters: $h$ is chosen from previous step, $n_{commit}=M \, s$ , where $n_{commit}$ is the $n$ for Protocol~\ref{proto:urmila4}, and the honest prover choose $M$ copies of $\ket{\psi_{C'(x)}}$ as $\rho$.
-We also allow a cheating prover to send $\bot$ in the fourth round of Protocol~\ref{proto:urmila4} if $c=1$ to abort the process.\footnote{This is useless for the cheating prover but useful for proving one of our theorems.} If the verifier receives $\bot$ in the fourth round, he outputs $(\Rej,\bot)$ and terminates this protocol.
-Let $z_{commit}$ be the output of the called Protocol~\ref{proto:urmila4}.
-
-	\item If $c=1$, the verifier finished the verification step of Protocol~\ref{ProtoQPIP1} by using $z_{commit}$  as the measurement result he would get and outputs $(d,z_{naive})$.
-
+		\item The verifier choose a $XZ$-measurement $h$ from the distribution emergent from by Step~\ref{step:qpip1-verify} of $\PiSamp$. \Ethan{I didn't change the wording here}
+			It samples $c\xleftarrow{\$}\zo$ uniformly at random.
+		\item The prover prepares $\sigma$ by running Step~\ref{step:qpip1-state-gen} of $\PiSamp$.
+		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\sigma), \VMeasure(h))(1^\lambda, 1^{1/\varepsilon}, x)$.
+			If $c=1$, the verifier obtains $z_{commit}$.
+		\item If $c=1$, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by using $z_{commit}$ as the measurement result he would get and outputs $(d,z_{naive})$.
 	\end{enumerate}
@@
 \begin{lemma}\label{lem:naive-qpip0-binding}[binding property of  Protocol~\ref{proto:qpip0_naive} ]
+	\Ethan{I haven't done anything with this lemma yet. Might need to fix or make consistent later.}
 If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen,
@@
 
-\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
+\begin{protocol}{$\QPIP_0$ protocol $\PiSampZ$ for $\SampBQP$}
 \label{proto:QPIP0samp}
 
-\hannote{fix inputs}
 Inputs:
- Both verifier and prover start with the description of number of qubits $n$,  input string $x$ to the $\SampBQP$ Instance, and a soundness parameter $\varepsilon$.
+	\begin{itemize}
+		\item Security parameter $1^\lambda$ for $\lambda\in\bbN$.
+		\item Accuracy paramter $1^\varepsilon$ for the $\SampBQP$ instance
+		\item Input $x\in\zo^n$ \Ethan{Or $\zo^*$?} for the $\SampBQP$ instance
+	\end{itemize}
+
+Ingrediant: Let $m=O(1/\varepsilon^2)$ be the number of parallel repetitions to run.
 
@@
 %    \item Verifier start with description of quantum circuit $C$, input string $x$ 
-
-    \item Run $m=O(1/\varepsilon^2)$ copies of protocol~\ref{proto:urmila4} in parallel \Ethan{proto 2?
-Or 3?}, with following modifications.
-The copies have separate $\{h\}$, $\{sk\}$, $\{pk\}$, $\{y\}$, $\{c\}$, and $\{a\}$.
-The verifier draws $\{h\}$ independently from the distribution specifier by step~\ref{step:qpip1-verify} of Protocol~\ref{ProtoQPIP1} to generate $\{sk\}$ and $\{pk\}$ for all copies on the first round.
-On the second round, for each copy, the prover choose the state specified by step~\ref{step:qpip1-state-gen} of Protocol~\ref{ProtoQPIP1}  (with  $(C,x,\eps)$ as input) as $\rho$.
-On the third round, the verifier uniformly randomly pick an $i\in [m]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies, i.e.
-$c_i=1$ and $c_j=0$ for all $j\neq i$.
-    \item \label{step:multi-testing}Verifier rejects if the result on any of the test rounds is rejected. 
-    \item If all testing rounds are accepted, verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
+	\item The verifier samples $r\xleftarrow{\$}[m]$. For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
+	\item The prover and verifier runs $m$-fold parallel repetion of $\PiNaive$.
+		That is, for $1\leq i\leq m$, run $(\PNaive, \VNaive(c_i))(1^\lambda, 1^\varepsilon, x)$.
+	\item \label{step:multi-testing} If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
+		Else it outputs the result from the Hadamard round copy.
 \end{enumerate}

### 2020-04-14 qpip0.tex
Add discussion TODOs

@@
 By combining the commitment Protocol, $\PiMeasure$, and our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, we get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.
+\Ethan{The following discussion is mine}
 In particular, we combine them by replacing the verifier's measurements with a call to $\PiMeasure$. It is possible because $\VSamp$ applies only $X$ and $Z$ measurements.
 Furthermore, its measurements are not adaptive, meaning measurement results do not change later measurement basis choices.
-
-\Ethan{Probably can omit details from below}
 
@@
 
-\Ethan{Might need to fix the following. Note that it's not a standard parallel rep, so we can't just say it's N-fold parallel rep without saying anything else}
+\Ethan{TODO add discussion about parallel rep}
 

### 2020-04-14 hamiltonian.tex
Updates from Overleaf

@@
 \]
-then the fidelity between $\rho$ and $\histpsi{C(x)}$ is at least $1-\epsilon$. 
+then the trace distance between $\rho$ and $\histpsi{C(x)}$ is at most $\frac{2}{\sqrt{3}}\sqrt{\epsilon}$. 
 \end{theorem}
@@
 Note that $\histpsi{C(x)}$ is a eigenvector $H_{C(x)}$ of eigenvalue 0 and all other eigenvalues are at least $3/4$.
-Thus, we have $\abs{\beta}^2 \leq \frac{4}{3}\epsilon$.
+Thus, we have $\abs{\alpha}^2 \geq 1-\frac{4}{3}\epsilon$.
 Thus,
 \[
-  \mathrm{F}(\histpsi{C(x)}, \ket{\phi}) =
+   \norm{\proj{\psi^{\mathrm{hist}}_{C(x)}}- \proj{\phi}}_{tr} = \sqrt{1- |\braket{\psi^{\mathrm{hist}}_{C(x)}|\phi}|^2}
+   \leq \frac{2}{\sqrt{3}}\sqrt{\epsilon}.
 \]
-\XW{todo from here; might need to change the theorem statement as well}
-$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
-	We can then see
-	$$\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$$
-	which can be generalized for mixed states since we have for all $\ket\psi$ that
-	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \ket\psi)=\sum_i p_i F(\ket{\phi_i}, \ket\psi).$$
-	As a result, we have
-	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
-	which implies our claim.
+For any mixed state $\rho=\sum_i p_i \proj{\phi_i}$, by the triangle inequality, we have 
+\[
+    \norm{\proj{\psi^{\mathrm{hist}}_{C(x)}}- \rho}_{tr} \leq \sum_i p_i    \norm{\proj{\psi^{\mathrm{hist}}_{C(x)}}- \proj{\phi_i}}_{tr} \leq \sum_i p_i \frac{2}{\sqrt{3}} \sqrt{\epsilon} =\frac{2}{\sqrt{3}}\sqrt{\epsilon}.
+\]
+% $$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
+% 	We can then see
+% 	$$\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$$
+% 	which can be generalized for mixed states since we have for all $\ket\psi$ that
+% 	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \ket\psi)=\sum_i p_i F(\ket{\phi_i}, \ket\psi).$$
+% 	As a result, we have
+% 	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
+% 	which implies our claim.
 \end{prf}
@@
 
-\XW{rewrite this part of the introduction}
 At a high level, it is a cut-and-choose protocol.

### 2020-04-14 hamiltonian.tex
Change fidelity to trace dist

@@
 		\item[(1)] $H_{C(x)} = \sum_i \alpha_i H_i$ where 
-		each $H_i \in \LHXZ{6}$ and $|\alpha_i| \in O(T^4)$. Moreover, there are at most $O(T)$ non-zero terms. 
+		each $H_i \in \LHXZ{6}$ and $|\alpha_i| \in O(T^6)$. Moreover, there are at most $O(T)$ non-zero terms. 
 		\item[(2)] $H_{C(x)}$ has $\histpsi{C(x)}$ as the unique ground state with eigenvalue $0$ and has a spectral gap at least $\frac{3}{4}$.
@@
 
-\XW{need to check the following calculation and modify the theorem statement respectively.}
+%\XW{need to check the following calculation and modify the theorem statement respectively.}
 %We will apply \Cref{lem:projection} twice to obtain $\Jclock$ and $\Jprop$ respectively. 
@@
 At a high-level, the design of such protocol should consist of at least two components: (1) the first component should test whether the message is indeed a valid history state; (2) the second component should simulate the last step of a $\SampBQP$ computation by measuring the final state in the computational basis.
+
 Our construction of X-Z local Hamiltonian $H$ from \Cref{thm:LHReduction} will help serve the first purpose. 
@@
 
-At a high level, it is a cut-and-choose protocol.
-The server constructs multiple copies of the ground state as certificates,
-then the client randomly chooses a copy to output and checks the rest.
-Unfortunately our approach incurs inverse polynomial soundness errors.
-
-There are two main challenges to this cut-and-choose approach.
-First, the client needs to reliably extract the circuit output from its corresponding ground state.
-We accomplish this by padding the circuit with identity gates at the end.
-By doing so, the clock register collapses to after the last non-identity gate with high probability.
+One, however, needs to combine the test and the output on multiple copies of the history states for our second purpose, where we construct the following cut-and-choose protocol.  
+% At a high level, it is a cut-and-choose protocol.
+% The server constructs multiple copies of the ground state as certificates,
+% then the client randomly chooses a copy to output and checks the rest.
+% Unfortunately our approach incurs inverse polynomial soundness errors.
+% There are two main challenges to this cut-and-choose approach.
+% First, the client needs to reliably extract the circuit output from its corresponding ground state.
+% We accomplish this by padding the circuit with identity gates at the end.
+% By doing so, the clock register collapses to after the last non-identity gate with high probability.
 

### 2020-04-14 hamiltonian.tex
Fix minor bug

--- 2020-04-14 hamiltonian.tex
@@
 		\item[(1)] $H_{C(x)} = \sum_i \alpha_i H_i$ where 
-		each $H_i \in \LHXZ{6}$ and $|\alpha_i| \in O(T^4)$. Moreover, there are at most $O(T)$ non-zero terms. 
+		each $H_i \in \LHXZ{6}$ and $|\alpha_i| \in O(T^9)$. Moreover, there are at most $O(T)$ non-zero terms. 
 		\item[(2)] $H_{C(x)}$ has $\histpsi{C(x)}$ as the unique ground state with eigenvalue $0$ and has a spectral gap at least $\frac{3}{4}$.
@@
 \[
- \Jprop= \frac{O(\norm{\Hin\big|_S + \Jclock\Hclock\big|_S}^2)}{\ground{\Hprop\big|_{S \cap \Kprop^\bot}}}= O(T^6),
+ \Jprop= \frac{O(\norm{\Hin\big|_S + \Jclock\Hclock\big|_S}^2)}{\ground{\Hprop\big|_{S \cap \Kprop^\bot}}}= O(T^8),
 \]
@@
 It suffices to check the bound of $\abs{\alpha_i}$ and the number of terms.
-The former is determined by $\Jclock$ and $\Jprop$.
+The former is one more than the order of $\Jprop$ since each $\Hprop^t$ contributes $\frac{1}{4}$ to the $I$ term, creating an extra factor of $T$.
 The latter is by counting the number of terms from $\Hin, \Hclock, \Hprop$, each of which is bounded by $O(T)$.
@@
 \item Pick $H_{i^*}$ which acts non-trivially on at most $k$ qubits of $\ket{\phi}$. Measure the corresponding single-qubit Pauli X or Z operator. 
-Record the list of the resutls $x_j=\pm 1$ for $j=1, \ldots k$. 
+Record the list of the results $x_j=\pm 1$ for $j=1, \ldots k$. 
 \item Let $r=x_1x_2\cdots x_k$. The protocol \emph{accepts} if $r$ and $\alpha_{i^*}$ have different signs, i.e., $\sgn(\alpha_{i^*})r=-1$. Otherwise, the protocol \emph{rejects}. 

### 2020-04-14 hamiltonian.tex

--- 2020-04-14 hamiltonian.tex
@@
 		\item[(1)] $H_{C(x)} = \sum_i \alpha_i H_i$ where 
-		each $H_i \in \LHXZ{6}$ and $|\alpha_i| \in O(T^6)$. Moreover, there are at most $O(T)$ non-zero terms. 
+		each $H_i \in \LHXZ{6}$ and $|\alpha_i| \in O(T^9)$. Moreover, there are at most $O(T)$ non-zero terms. 
 		\item[(2)] $H_{C(x)}$ has $\histpsi{C(x)}$ as the unique ground state with eigenvalue $0$ and has a spectral gap at least $\frac{3}{4}$.

### 2020-04-14 qpip.tex
Attempt to wrap up my own sections
Fix QPIP1 params

@@
 	\begin{itemize}
-		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
 		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
 		\item Accuracy parameter $1^{1/\varepsilon}$ where $\varepsilon\in(0, 1)$
+		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
+			\Ethan{I switched the order of the inputs for consistency}
 	\end{itemize}
@@
 		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
-		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$. \Ethan{Refer to the appropriate previous theorem}
+		\item Let $H_{C'(x)}=\sum_i \alpha_i H_i$ be the local Hamiltonian instance associated with the computation of $C'(x)$. \Ethan{Refer to the appropriate previous theorem}
 		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
@@
 	\begin{enumerate}
-		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{21}\lambda^2}{\varepsilon^{31}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
-		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}\lambda}{\varepsilon^{14}}$, and $k\xleftarrow{\$}[M]\setminus I$.
+		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{40}\lambda^2}{\varepsilon^{48}}$ copies \Ethan{$505=2\times 7\times 6\times 6+1$} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{20}\lambda}{\varepsilon^{24}}$, and $k\xleftarrow{\$}[M]\setminus I$.
 			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
@@
 		\end{enumerate}
-			Let $Y=\sum_{i\in I} y_i$.
-If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{72\left(T+\frac{6T}{\varepsilon}\right)^5}$ and $c\in\bbR$ is the constant specified in \Cref{cor:HamCheck}, then the verifier outputs $(\Acc, z)$.
+			Let $Y=\sum_{i\in I} y_i$. If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{1}{192}\frac{\varepsilon^2}{\sum_i\abs{\alpha_i}}$, then the verifier outputs $(\Acc, z)$.
 			Else, it outputs $(\Rej, \bot)$.
@@
 	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
+	\iffalse
 	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\tau_j$ and $\ket{\psi_{C'(x)}}$:
@@
 	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}<\frac{\varepsilon}{6}.$$
+	\fi
+	By \Cref{HamCheckClose} we have
+	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}\leq\frac{2}{\sqrt{3}}\sqrt{2\kappa\cdot2\sum_i\abs{\alpha_i}}=\frac{\varepsilon}{6}.$$
 	Observe that when $d_j=\Acc$, $z_j$ is the measurement results on $\tau_j$'s data register,

### 2020-04-14 qpip0.tex
Updates from Overleaf

@@
 \begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ \Ethan{Prover will produce isn't right, the one producing z should be verifier} on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
+If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the verifier will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
 \end{lemma}

### 2020-04-14 hamiltonian.tex

@@
 
-One, however, needs to combine the test and the output on multiple copies of the history states for our second purpose, where we construct the following cut-and-choose protocol.  
+To serve the second purpose, one needs to combine the test and the output on multiple copies of the history states, where we construct the following cut-and-choose protocol.  
 % At a high level, it is a cut-and-choose protocol.
@@
 % By doing so, the clock register collapses to after the last non-identity gate with high probability.
+The challenge comes from the fact that a cheating prover might send something rather than copies of the history state. 
+In particular, the prover can entangle between different copies in order to cheat. 
+In the case of certifying a $\BQP$ computation, the goal is to verify the ground energy of any local Hamiltonian. 
+A cheating strategy with potential entanglement won't create any witness state with energy lower than the actual ground energy. 
+Thus, this kind of attack won't work for $B$
+
+one always needs to send the best certificate state (i.e., the perfect history state) in order to pass the local Hamiltonian ground energy test.
 
@@
 so common techniques such as Chernoff bounds can't be applied as-is.
-This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...
-\Ethan{TODO; need brief and intuitive explanation}
+
+%This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...
+
 In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem
+
 to approximate our measurement results with that of some unentangled copies,

### 2020-04-14 hamiltonian.tex
Fix typos

@@
 In the case of certifying a $\BQP$ computation, the goal is to verify the ground energy of any local Hamiltonian. 
-A cheating strategy with potential entanglement won't create any witness state with energy lower than the actual ground energy. 
-Thus, this kind of attack won't work for $B$
+A cheating strategy with potential entanglement won't create any witness state with an energy lower than the actual ground energy. 
+Thus, this kind of attack won't work for $\BQP$ computation.
+
+However, in the context of $\SampBQP$, one needs to both certify both the energy and output a good copy. statistical information cannot rule out a bad copy.
 

### 2020-04-14 preliminaries.tex
Fix typos

@@
 For $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$,
-we write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.
-We write $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$,
-We have $\norm{\rho_1-\rho_2}_{tr}\leq\sqrt{1-F(\rho_1, \rho_2)}$.
+we write $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$.
 We say $\rho_1$ and $\rho_2$ are $\varepsilon$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\varepsilon$.

### 2020-04-14 qpip.tex
Fix typos

@@
 	\fi
-	By \Cref{HamCheckClose} we have
-	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}\leq\frac{2}{\sqrt{3}}\sqrt{2\kappa\cdot2\sum_i\abs{\alpha_i}}=\frac{\varepsilon}{6}.$$
+	By \Cref{thm:HamCheckClose} we have
+	$$\norm{\tau_j - \ket{\psi^{\mathrm{hist}}_{C'(x)}}\bra{\psi^{\mathrm{hist}}_{C'(x)}}}_{tr}\leq\frac{2}{\sqrt{3}}\sqrt{2\kappa\cdot2\sum_i\abs{\alpha_i}}=\frac{\varepsilon}{6}.$$
 	Observe that when $d_j=\Acc$, $z_j$ is the measurement results on $\tau_j$'s data register,

### 2020-04-14 preliminaries.tex
Fix wording

@@
 	That is, for all quantum polynomial-time distinguishers $\mathsf{D}$,
-	$$\abs{\Pr\left[\mathsf(D)(\rho_1)=1\right]-\Pr\left[\mathsf(D)(\rho_2)=1\right]}\leq\varepsilon.$$
+	$$\abs{\Pr\left[\mathsf{D}(\rho_1)=1\right]-\Pr\left[\mathsf{D}(\rho_2)=1\right]}\leq\varepsilon.$$
 \end{definition}
-
-We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized outputs on subnormalized inputs.
-We also extend it to distributions, which can be treated as mixed states.
+We extend the notion of computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized outputs as appropriate.
+We also extend it to distributions by treating them as mixed states.
 
 \begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
-    Let $D_1$, $D_2$, and $D_3$ be three distributions such that 
+    Let $\rho_1, \rho_2, \rho_3\in\cB^{\otimes n}$ such that 
     \begin{align}
-		D_1\approx_{c, \varepsilon}D_2\\
-		D_2\approx_{c, \varepsilon'}D_3.
+		\rho_1\approx_{c, \varepsilon}\rho_2\\
+		\rho_2\approx_{c, \varepsilon'}\rho_3.
     \end{align}
@@
     \begin{align}
-		D_1\approx_{c, \varepsilon+\varepsilon'}D_3.
+		\rho_1\approx_{c, \varepsilon+\varepsilon'}\rho_3.
     \end{align}

### 2020-04-15 blind.tex
Add action items on QPIP0 section

@@
 		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
-		\item Some classical input $x\in\zo^*$ \Ethan{Or should this be $\zo^n$? Or $\zo^{\poly(\lambda)}$?}
+		\item A classical input $x\in\zo^{\poly(\lambda)}$
 	\end{itemize}
 
+    Protocol:
 	\begin{enumerate}
@@
 
+    Protocol:
 	\begin{enumerate}
@@
 \begin{proof}
-	We show that for all cheating prover $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
-	$P^*$ cannot distinguish $(P^*, \Vblind(x))(\lambda)$ from $(P^*, \Vblind(0^n))(\lambda)$ with noticeable probability in $\lambda$.
-	We use a hybrid argument; let $\Hyb_{T+1}^x=(P^*, \Vblind(x))(\lambda)$ and $\Hyb_{T+1}^0=(P^*, \Vblind(0^n))(\lambda)$.
+	We show that for all cheating $\BQP$ prover $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
+	$P^*$ cannot distinguish $(P^*, \Vblind(x))(1^\lambda)$ from $(P^*, \Vblind(0^n))(1^\lambda)$ with noticeable probability in $\lambda$.
+	We use a hybrid argument; let $\Hyb_{T+1}^x=(P^*, \Vblind(x))(1^\lambda)$ and $\Hyb_{T+1}^0=(P^*, \Vblind(0^n))(1^\lambda)$.
 	For $2\leq t<T+1$, define $\Hyb_t^x$ to be the same as $\Hyb_{t+1}^x$,
 	except when $\Vblind$ should send $\ctx{v}{t}{t}$ and $\ctx{sk}{t-1}{t}$, it instead sends encryptions of $0$ under $pk_t$.
-	We define $\Hyb_1^x$ to be the same as $\Hyb_2^x$ except the verifier sends encryptions of $0$ in place of $\ctx{x}{}{1}$ and $\ctx{v}{1}{1}$.
+	We define $\Hyb_1^x$ to be the same as $\Hyb_2^x$ except the verifier sends encryptions of $0$ under $pk_1$ in place of $\ctx{x}{}{1}$ and $\ctx{v}{1}{1}$.
 	We define $\Hyb_t^0$ similarly. Note that $\Hyb_1^x$ and $\Hyb_1^0$ are identical.

### 2020-04-15 hamiltonian.tex
Add action items on QPIP0 section

@@
 
-However, in the context of $\SampBQP$, one needs to both certify both the energy and output a good copy. statistical information cannot rule out a bad copy.
-
-one always needs to send the best certificate state (i.e., the perfect history state) in order to pass the local Hamiltonian ground energy test.
-
-The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
-so common techniques such as Chernoff bounds can't be applied as-is.
-
+However, in the context of $\SampBQP$, one needs to certify the ground energy (known to be zero in this case) and to output a good copy. 
+%%% not sure about this high-level argument. 
+While the statistical test as before can be used to certify the ground energy, 
+it has less control on the shape of the output copy.
+In fact, the prover can always prepare a bad copy among with many good copies as a plain attack. 
+This attack will succeed when the bad copy is chosen to output, the probability of which is non-negligible in terms of the total number of copies assuming some symmetry of the protocol. 
+The potential entanglement among different copies could further complicate the analysis. 
+We employ the quantum \emph{de Finetti}'s theorem to address this technical challenge. 
+Specifically, given any permutation-invariant $k$-register state, it is known that the reduced state on many subsets of $k$-register will be close to a separable state. 
+This helps establish some sort of independence between different copies in the analysis. 
+To serve our purpose, we adopt the following version of quantum de Finetti's theorem from~\cite{Brandão2017} where the error depends nicely  on the number of qubits, rather than the dimension of quantum systems.
+% one always needs to send the best certificate state (i.e., the perfect history state) in order to pass the local Hamiltonian ground energy test. 
+% The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
+% so common techniques such as Chernoff bounds can't be applied as-is.
 %This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...
-
-In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem
-
-to approximate our measurement results with that of some unentangled copies,
-within inverse polynomial errors.
-
-De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
-There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on number of qubits in each subsystem.
-\begin{thm}
+% In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem
+% to approximate our measurement results with that of some unentangled copies,
+% within inverse polynomial errors.
+% De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
+% There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on number of qubits in each subsystem.
+\begin{thm}[\cite{Brandão2017}]
 	\label{deFinetti}
-	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state on registers $A_1,\ldots,A_k$ where each register is $s$ qubits,
-	then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
+	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state on registers $A_1,\ldots,A_k$ where each register contains $s$ qubits. 
+	For any $0\leq l\leq k$,  there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
 	$$\max_{\Lambda_1,\ldots,\Lambda_l}
@@
 \end{thm}
+
+\XW{comment on saturating the error bound?}
 

### 2020-04-15 introduction.tex
Start combining with QFHE
Add action items on QPIP0 section

--- 2019-09-10 introduction.tex
@@
 \section{Introduction}
+% \XW{ 
+% \begin{itemize}
+%     \item add a lot of references. 
+%     \item comparison with the most relevant results:
+%       \begin{itemize}
+%           \item Sampling, the only paper; how about classical sampling?
+%           \item the following for BQP  
+%           \item blind and verifiable ~\cite{GV19}; we  constant round; technique-wise very different. 
+%           \item there is a table in~\cite{Grilo19}. Safe to say ~\cite{GV19} only existing blind protocol in the computational setting? 
+%           \item all previous either quantum clients, or at least 2 provers. 
+%           \item the following for blindess
+%           \item Mahadev in her thesis~\cite{mahadev_2018} discussed a bit about the relation between verifiability and blindness.
+She hoped to get verifiability out of blindness by designing some non-malleable QFHE but failed.
+%           \item what's the high-level message we can say here?
+Use QFHE in a different way?
+It is correct that not much work in the classical setting either.
+Maybe existing classical work employs the principle but with different implementation.
+%           \item old approach, first get blindness  (measurement-based, self-testing), and then try to make it verifiable; our approach, first have a verifiable protocol, and upgrade by a QFHE. 
+%           \item directly QFHE (blindness) won't give verifiability. some thoughts from Mahadev. 
+%           \item 
+%       \end{itemize}
+% \end{itemize}
+% }
+Can quantum computation, with potential computational advantages that are intractable for classical computers,
+be efficiently verified by classical human being? 
+This seemingly paradox has been one of the central problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}. 
+From a philosophical point of view, this question is also known to have a fascinating connection to the \emph{falsifiability} of quantum mechanics in the potential high complexity regime~\cite{survey:AV12}.
 
-Below is some intro of it copied from my SoP.
-This is unpolished and mostly a placeholder at the moment though.
+A complexity theoretic reformulation of this problem by Gottesman~\cite{web:Aaronson}
 
-It was proven that BQP=BQIP.
+\begin{itemize}
+    \item Add some of the very original motivation of delegation (at some philosophical level) to motivate that sampling problem is important and has been sought after from the very beginning. 
+    \item quickly survey the topic (Add references and surveys) to Mahadev's results. 
+    \item \XW{What're important post-Mahadev's result to discuss here? use subsequentially 3 papers}
+\end{itemize}
+
+Sampling Part
+\begin{itemize}
+    \item Motivating Sampling.  and a little bit why sampling could be different and hard. (Aaronson's paper?) 
+    \item To ADD
+    \item 2nd de finetti have independence; but latter, the analysis, computational parallel repetition. 
+    \item emphasize the feasibility. 
+\end{itemize}
+
+Blindness Part 
+\begin{itemize}
+    \item Motivating Blindness
+    \item To ADD
+    \item Combine both for the results. 
+\end{itemize}
+
+Related work
+\begin{itemize}
+    \item Comparison with related works here?
+\end{itemize}
+
+Technical Contribution
+\begin{itemize}
+    \item Technical contribution. 
+    \item TO ADD for both parts. 
+\end{itemize}
+
+Open Questions
+\begin{itemize}
+    \item Open questions, and also explain for some associated high-cost. specifically 
+    \item T dependence. In general, improve the efficiency.  
+    \item negligible soundness error.  compare with classical? what's the state-of-the art. 
+\end{itemize}
+
+Organization
+
+% \Ethan{This section is currently all rough draft. We'll probably rewrite almost all of it.}
+
+% \Ethan{application: verifiable private constant round delegation}
+
+% \Ethan{Below is my attempt to talk about it in my SoP}
+
+% It was proven that BQP=BQIP\hannote{who  when and cite}.
 That is, if a quantum computer can efficiently solve a given decision problem, then it can also efficiently convince a classical machine of its solution.
@@
 I've been trying to get a grasp on the particular structure of the local Hamiltonian reduction in order to better analyze it.
+
+% \Ethan{Below is my attempt to talk about it in my research proposal}
+
+% We are interested in delegating quantum computations from a classical client to an untrusted quantum server.
+Under this setting, the client would send the server a quantum circuit and an initial state.
+Then, through interaction with the honest server, the client obtains a measurement result as if he measured the true output of the circuit.
+If the server attempts to deceive the client, the client should reject it.
+The case where the circuit encodes a decision problem has been well-studied, and we're now trying to generalize those results to circuits with possibly many bits of output.
+
+% If the circuit encodes a decision problem, then by considering adiabatic quantum computation, there exists a reduction to local Hamiltonian.
+Local Hamiltonian is QMA-complete, so there's a certificate for every yes-instance, and no valid certificates for any no-instances.
+An introduction can be found in Kitaev, Shen, and Vyalyi's "Classical and Quantum Computation".
+Furthermore, Biamonte and Love's "Realizable Hamiltonians for Universal Adiabatic Quantum Computers" states that these local Hamiltonians have very simple forms, which in turn implies that in order to check such certificates one only requires abilities to receive qubits and perform X/Z measurements.
+Based on this observation, Mahadev constructed a protocol in "Classical Verification of Quantum Computations" which, under the LWE assumption (a widely believed conjecture in quantum cryptography), allows the prover to commit qubits and act as the verfier's trusted X/Z measurement device.
+This solves the delegation of decision problem from a fully classical client to a quantum server.
+
+% To generalize delegation of quantum computations to allow long output, simply repeating the known protocol for every output qubit doesn't work.
+The joint probability distribution between qubits would be incorrect due to entanglements.
+In fact, generally the output qubits encode sampling problems rather than decision problems.
+Furthermore, for decision problems one can argue that the prover's optimal strategy is to send identical copies of a certificate, so Chernoff bound can be applied, but said argument doesn't generalize to sampling problems either.
+To overcome these challenges, we start by modifying the local Hamiltonian construction so it is compatible with long output.
+We then analyze our protocol's soundness more carefully, before using Mahadev's result as a black box to solve the long output case too for fully classical clients.
+
+% A possible application for our long output protocol is to make the computation not only verifiable, but also private in the sense of homomorphic encryptions.
+That is, the input is encrypted before being sent to the server.
+The server computes on the encrypted input, obtaining an encrypted output.
+The client then receives and decrypts the output.
+Here we can combine results from Mahadev's "Classical Homomorphic Encryption for Quantum Circuits" with our long output scheme.
+The client can simply send the homomorphic evaluation circuit to the server with the encrypted input.

### 2020-04-15 preliminaries.tex
Add action items on QPIP0 section

@@
 \end{definition}
-
-\begin{definition}
-	Let $\rho_1,\rho_2\in\cB^n$.
-	We write $\rho_1\approx_{c,\varepsilon}\rho_2$ if $\rho_1$ and $\rho_2$ are \emph{$\varepsilon$-computationally indistinguishable}.
-	That is, for all quantum polynomial-time distinguishers $\mathsf{D}$,
-	$$\abs{\Pr\left[\mathsf{D}(\rho_1)=1\right]-\Pr\left[\mathsf{D}(\rho_2)=1\right]}\leq\varepsilon.$$
-\end{definition}
-We extend the notion of computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized outputs as appropriate.
-We also extend it to distributions by treating them as mixed states.
-
-\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
-    Let $\rho_1, \rho_2, \rho_3\in\cB^{\otimes n}$ such that 
-    \begin{align}
-		\rho_1\approx_{c, \varepsilon}\rho_2\\
-		\rho_2\approx_{c, \varepsilon'}\rho_3.
-    \end{align}
-    We have 
-    \begin{align}
-		\rho_1\approx_{c, \varepsilon+\varepsilon'}\rho_3.
-    \end{align}
-\end{lem}
 
@@
 
+\begin{definition}
+\label{def:comp-indis}
+    \Ethan{TODO Mention asymptotic/ensemble. Things should be in terms of $\lambda$. Should also move to other subsections instead, since this is computatational. Maybe move to end of 2.3.}
+	Let $\rho_1,\rho_2\in\cB^n$.
+	We write $\rho_1\approx_{c,\varepsilon}\rho_2$ if $\rho_1$ and $\rho_2$ are \emph{$\varepsilon$-computationally indistinguishable}.
+	That is, for all quantum polynomial-time \hannote{formalize} distinguishers $\mathsf{D}$,
+	$$\abs{\Pr\left[\mathsf{D}(\rho_1)=1\right]-\Pr\left[\mathsf{D}(\rho_2)=1\right]}\leq\varepsilon.$$
+\end{definition}
+We extend the notion of computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized outputs as appropriate.
+We also extend it to distributions by treating them as mixed states.
+
+\iffalse
+
+Probably not necessary
+
+\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
+    Let $\rho_1, \rho_2, \rho_3\in\cB^{\otimes n}$ such that 
+    \begin{align}
+		\rho_1\approx_{c, \varepsilon}\rho_2\\
+		\rho_2\approx_{c, \varepsilon'}\rho_3.
+    \end{align}
+    We have 
+    \begin{align}
+		\rho_1\approx_{c, \varepsilon+\varepsilon'}\rho_3.
+    \end{align}
+\end{lem}
+
+\fi
+
 \subsection{Chernoff bound}

### 2020-04-15 qpip.tex
Add action items on QPIP0 section

@@
 		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
-			\Ethan{I switched the order of the inputs for consistency}
+		%	\Ethan{I switched the order of the inputs for consistency}
 	\end{itemize}
@@
 		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
-		\item Let $H_{C'(x)}=\sum_i \alpha_i H_i$ be the local Hamiltonian instance associated with the computation of $C'(x)$. \Ethan{Refer to the appropriate previous theorem}
-		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
-		\item Let $s=n+T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$
+		\item Let $H_{C'(x)}=\sum_i \alpha_i H_i$ be the X-Z local Hamiltonian instance associated with the computation of $C'(x)$ from \Cref{thm:LHReduction}.
+		\item Let $\histpsi{{C'(x)}}$ be the ground state of $H_{C'(x)}$.
+		\item \XW{Let $s=n+T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This number is used in de Finetti theorem.
+But I forgot to count ancilla, so this currently isn't correct.}
 		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
@@
 	\begin{enumerate}
-		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{40}\lambda^2}{\varepsilon^{48}}$ copies \Ethan{$505=2\times 7\times 6\times 6+1$} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
+		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{41}\lambda^2}{\varepsilon^{51}}$ copies \Ethan{$505=2\times 7\times 6\times 6+1$} of $\histpsi{C'(x)}$ and sends all of it to the verifier qubit-by-qubit.
 		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{20}\lambda}{\varepsilon^{24}}$, and $k\xleftarrow{\$}[M]\setminus I$.
@@
 			\item If $i\in I$, run $y_i\leftarrow\cV_{\GS}(\rho_i)$.
-			\item Else if $i=k$, measure the data register \Ethan{Revisit this name. Nobody has defined/used this register before.} of $\rho_i$ under the standard basis and save the outcome as $z$.
+			\item Else if $i=k$, measure the data register \Ethan{Revisit this name.
+Nobody has defined/used this register before.} \XW{this is the Z measurement?} \Ethan{Yeah} of $\rho_i$ under the standard basis and save the outcome as $z$.
 			\item Else, discard $\rho_i$.
@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and is statistically sound.
+	$\PiSamp$ has negligible completeness error and is statistically sound. \XW{do we want precise error bound?}
 \end{thm}
@@
 	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}
-	\leq\sqrt{\frac{2m^2\left(n+T+\frac{6T}{\varepsilon}\right)}{M-m}}
+	\leq\sqrt{\frac{2m^2s}{M-m}}
 	\leq\frac{\varepsilon}{6}$$
@@
 	using triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
-	Hence we have $\norm{d - d_\rho}_{TV}\leq\frac{\varepsilon}{2}$, which implies $\norm{(d_\rho, z_{\rho, ideal}) - (d, z_{ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
+	Hence $\norm{d - d_\rho}_{TV}\leq\frac{\varepsilon}{2}$, which implies $\norm{(d_\rho, z_{\rho, ideal}) - (d, z_{ideal})}_{TV}$ $\leq$ $\frac{\varepsilon}{2}$.
 	The conclusion then follows from triangle inequality.

### 2020-04-15 qpip0.tex
Add action items on QPIP0 section

@@
 In this section, we combine \cref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients.
-To boost the soundness, we need  polynomial rounds, so we use results from \cite{parallelrep} to run polynomially many copies in parallel and get a constant-round protocol.
+To boost the soundness, we need  polynomial \Ethan{Wording is strange/misleading} rounds, so we use results from \cite{parallelrep} to run polynomially many copies in parallel and get a constant-round protocol.
 
@@
 
-\subsection{Mahadev's classical "commitment" of $XZ$ measurement}
+\subsection{Mahadev's measurement protocol}
 
@@
 
-\begin{protocol}{Mahadev's 4 round commitment protocol $\PiMeasure$}
+\Ethan{Write a bit of technical intro. allows prover commit a state and verifier chooses h allows verifier to learn... MXZ introduce here}
+
+\Ethan{Discussion: Intuitively the purpose of this protocol is to let the verifier learn a measurement outcome. Define MXZ rho h notation here.}
+
+\Ethan{Check tone, this is intro/interface}
+
+\begin{protocol}{Mahadev's measurement protocol $\PiMeasure=(\PMeasure, \VMeasure)$}
 \label{proto:urmila4}
@@
 			\item a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit. If $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.  
-			\item a challenge bit $c\in\zo$. The prover needs to do a ``Testing round" if $c=0$. The prover needs to do a ``Hadamard round" if $c=1$.
+			\item a challenge bit $c\in\zo$. The prover needs to do a ``Testing round" if $c=0$. The prover needs to do a ``Hadamard round" if $c=1$. \Ethan{TODO rephrase. c indicates testing vs Hadamard...}
 			\end{itemize}
@@
 
-The protocol:
+The protocol: \Ethan{Bring back V1 P1 notations}
 \begin{enumerate}
@@
     \item The prover generates a classical string $a$ on inputs $c$ and $\sigma$, and sends it to back to the verifier.
-    \item If $c=0$, the verifier decides whether he is going to reject on inputs $(pk,a,y)$.
-		If $c=1$, the verifier computes an $n$-bit string $z=V_f(sk,h,y,a)$ on inputs $(sk,h,y,a)$.
+    \item \Ethan{Need more discussion about what's testing/Hadamard} If $c=0$, the verifier \Ethan{performs testing and} decides whether he is going to reject on inputs $(pk,y,a)$.
+	If $c=1$, the verifier \Ethan{performs Hadamard round and generates} computes an $n$-bit string $z=V_f(sk,h,y,a)$ on inputs $(sk,h,y,a)$.
+
+	\Ethan{Switch to the following wording:
+
+	If it's a testing round (c=0), then the verifier...
+	If it's a Hadamard round (c=1), then the verifier...}
 \end{enumerate}
@@
 
-\Ethan{The following modifications are mine}
+\Ethan{Discussion: Notice that testing round has no outputs, then binding property. Then fact.}
+
 Two modification have been made from the original protocol.
 \begin{itemize}
-	\item On the protocol's third message. Instead of randomly picking whether to run what's called a ``testing round" or a ``Hadamard round", we let the verifier decide as one of its inputs.
-	\item On the protocol's fourth message, the prover can choose to abort by sending $a=\bot$. This is useless for the cheating prover but useful for proving one of our theorems.
+	\item On the protocol's third message.
+Instead of randomly picking whether to run what's called a ``testing round" or a ``Hadamard round", we let the verifier decide as one of its inputs.
+\Ethan{Remove this and make $c$ random.
+Instead of this, say that we do parallel repetition but we change the distribution of $c$}
+	\item On the protocol's fourth message, the prover can choose to abort by sending $a=\bot$.
+This is useless for the cheating prover but useful for proving one of our theorems.
+\Ethan{Move to later when it's used}
 \end{itemize}
 
-\begin{definition}
-With loss of generality,  we can assume that the testing round verification is deterministic.
+% \begin{definition}
+% With loss of generality,  we can assume that the testing round verification is deterministic.
 We denote the set of strings $a$ \Ethan{Font makes this $a$ look screwy} accepted by the verifier in the testing round with $(pk,y)$ as $\Acc_{pk,y}$.
-\end{definition}
+\hannote{do  i actually use this}
+% \end{definition}
 
-\begin{lem}[\hannote{ref}]~\label{lem:trivial-4-round-strategy}
-    For any input, there exist a prover strategy $(U_{trivial,0},U_{trivial})$ for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{n}$ in the testing.
+\begin{lem}[\cite{FOCS:Mahadev18a}\hannote{change to fact?} \Ethan{Ok I'll do that later}]~\label{lem:trivial-4-round-strategy}
+    For any input, there exist a prover strategy $(U_{trivial,0},U_{trivial})$ \Ethan{Consider delay introducing the particular notation; just write this name when it's used later} for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{\lambda}$ \Ethan{Changed n to lambda here, see what does it affect} in the testing.
 \end{lem}
@@
 \begin{lemma}\label{lem:urmila-binding}[binding property of Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the verifier will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
+If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the verifier will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally \Ethan{Remove Q} indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
 \end{lemma}
@@
 \Ethan{The following discussion is mine}
-In particular, we combine them by replacing the verifier's measurements with a call to $\PiMeasure$. It is possible because $\VSamp$ applies only $X$ and $Z$ measurements.
-Furthermore, its measurements are not adaptive, meaning measurement results do not change later measurement basis choices.
+In particular, we combine them by replacing \Ethan{Still a bit ambiguous.
+More discussion than just ``replace".
+Mention it's QPIP1 and whatnot.} the verifier's measurements with a call to $\PiMeasure$.
+It is possible because $\VSamp$ applies only $X$ and $Z$ measurements non-adaptively.
 
-\begin{protocol}{naive $\QPIP_0$ protocol $\PiNaive$ for the $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$}
+\begin{protocol}{Intermediate $\QPIP_0$ protocol $\PiNaive$ for a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$}
 	\label{proto:qpip0_naive}
@@
 		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
-		\item Verifier's input: challenge bit $c\in\zo$ as in $\PiMeasure$
 	\end{itemize}
@@
 	\begin{enumerate}
-		\item The verifier choose a $XZ$-measurement $h$ from the distribution emergent from by Step~\ref{step:qpip1-verify} of $\PiSamp$. \Ethan{I didn't change the wording here}
+		\item The verifier choose a $XZ$-measurement $h$ from the distribution specified in Step~\ref{step:qpip1-verify} of $\PiSamp$. \Ethan{I didn't change the wording here}
 		It samples $c\xleftarrow{\$}\zo$ uniformly at random.
@@
 		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\sigma), \VMeasure(h))(1^\lambda, 1^{1/\varepsilon}, x)$.
-			If $c=1$, the verifier obtains $z_{commit}$.
-		\item If $c=1$, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by using $z_{commit}$ as the measurement result he would get and outputs $(d,z_{naive})$.
+		\Ethan{Let z be the verifier output when it's a Hadamard round}
+		If $c=1$, the verifier obtains $z_{commit}$ \Ethan{measure/commit... so many notations. Confusing. Just do v}.
+		\item If $c=1$, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by using $z_{commit}$ as the measurement result he would get and outputs $(d,z_{naive})$ \Ethan{Just do z here}.
 	\end{enumerate}
 \end{protocol}
+
+\Ethan{Try to update notation:
+Use something else for measurement outcome for proto 3. Maybe v or w.
+Let z be sampbqp results.}
 
@@
  \begin{equation}
-     \norm{Ver(M_{XZ}(\rho,h))-(d,z_{ideal})}\leq O(\eps).
+     \norm{Ver(M_{XZ}(\rho,h))-(d,z_{ideal})} \leq O(\eps).
  \end{equation}
@@
 
-\hannote{intuition about proof}
-
-\hannote{Intuitions about the partition lemma. efficient projectors into passing testing part and not passing testing part.}
-
-\hannote{related notation back to 3.5}
+The intuition behind this theorem is that the we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
+Therefore if the prover want to cheat, i.e.
+send something not binding in the Hadamard round copy, he would be caught with probability $1-1/m$.
+However, the prover is quantum, so he might create quantum correlations that let him cheat with probability more than $1/m$.
+To prove that such kind of cheating is impossible, we use the following partition lemma from \cite{parallelrep}, which intuitively says that there exist efficient projectors $G_{0,i}$ and $G_{1,i}$ which splits a quantum state in the prover's   internal space into a part that is rejected with high probability in the testing round of $i$-th copy and a part that is accepted with high probability.
+$G_{0,i}$ and $G_{1,i}$ need to be efficient because Protocol~\ref{proto:urmila4} only gives computational indistinguishability.
+Once we have $G_{0,i}$ and $G_{1,i}$, we can split up the prover's internal state $\ket{\psi}$ like conditional probabilistic events.
+For example, $G_{0,3} G_{1,5} \ket{\psi}$ corresponds to the events of passing the testing round on fifth copy then fails the the testing round on the third copy.
+We split the state sub-normalized states corresponding to the prover cheating on different copies and show that the sum of probabilities corresponding to bad states can't be more than $1/m$.
+{The actual proof is more complicated than this sketch because the $G$'s don't commute with each other, so we need to handle the splitting carefully.}
 
 %Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
-\begin{lemma}[partition lemma \hannote{ref}\Ethan{Lemma number?}]\label{lem:partition2}
+\begin{lemma}[partition lemma (revision of Lemma 3.5 of \cite{parallelrep}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{parallelrep} and post-select on the $th$ register being $0$ or $1$ then discard $ph,th,in$.
+Property~\ref{property:partition-err} corresponds to Property~1.
+Property~\ref{property:partition-testing}corresponds to Property~4, with $2^{m-1}$ changes to $m-1$ because we only have $m$ possible choices of $\{c\}$.
+Property~\ref{property:partition-binding} corresponds to Property~5.
+Property~\ref{property-partition-norm-sum} comes from the fact that $G_0$ and $G_1$ are post-selections of orthogonal results of the same $G$.})]\label{lem:partition2}
 Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round.
@@
 By Lemma~\ref{lem:trivial-4-round-strategy} and property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when $c=0$.
-Therefore by Lemma~\ref{lem:naive-qpip0-binding},
+Since the prover's strartegy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
 \begin{align}

### 2020-04-15 qpip.tex
Fix minor bug

@@
 		\item Let $\histpsi{{C'(x)}}$ be the ground state of $H_{C'(x)}$.
-		\item \XW{Let $s=n+T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This number is used in de Finetti theorem.
-But I forgot to count ancilla, so this currently isn't correct.}
+		\item \XW{Let $s\leq n+2T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This number is used in de Finetti theorem.
+But I forgot to count ancilla, so it wasn't correct.}
 		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
@@
 	\begin{enumerate}
-		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{41}\lambda^2}{\varepsilon^{51}}$ copies \Ethan{$505=2\times 7\times 6\times 6+1$} of $\histpsi{C'(x)}$ and sends all of it to the verifier qubit-by-qubit.
+		\item\label{step:qpip1-state-gen} The honest prover prepares $M=649\frac{T^{41}\lambda^2}{\varepsilon^{51}}$ copies \Ethan{$649=2\times 9\times 6\times 6+1$} of $\histpsi{C'(x)}$ and sends all of it to the verifier qubit-by-qubit.
 		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{20}\lambda}{\varepsilon^{24}}$, and $k\xleftarrow{\$}[M]\setminus I$.

### 2020-04-15 qpip.tex
Fix wording

@@
 		\item Let $\histpsi{{C'(x)}}$ be the ground state of $H_{C'(x)}$.
-		\item \XW{Let $s\leq n+2T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This number is used in de Finetti theorem.
-But I forgot to count ancilla, so it wasn't correct.}
+		\item \XW{Let $s\leq 3T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This is used in de Finetti theorem.
+But I forgot to count ancilla, so it wasn't correct before.}
 		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.

### 2020-04-15 qpip0.tex
Handle action items

@@
 
-In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave a 4-round $\QPIP_0$ protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine, which we describe below while omitting the implementation details.
-
-\Ethan{Write a bit of technical intro. allows prover commit a state and verifier chooses h allows verifier to learn... MXZ introduce here}
-
-\Ethan{Discussion: Intuitively the purpose of this protocol is to let the verifier learn a measurement outcome. Define MXZ rho h notation here.}
+In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave a 4-round $\QPIP_0$ protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine.
+Intuitively, the protocol allows the prover to commit to a state $\rho$ and the verifier to choose a measurement basis $h$ and learn a corresponding measurement outcome $M_{XZ}(\rho, h)$.
+\Ethan{The following discussion is from Han-Hsuan}
+Note that even a honest prover has complete freedom in choosing $\rho$;
+what this protocol actually does is let the prover commit to a particular measurement on $\rho$.
+This is good enough for our application, since we will feed the $XZ$ measurement results into the verification of $\QPIP_1$ protocol to ensure that the prover pick the history state as $\rho$ as we will show next.
+We now describe the protocol while omitting the implementation details.
 
@@
 \label{proto:urmila4}
-\Ethan{Still rooms for improvements, but it's not as bad as before}
 
@@
 	\item Prover's input: a state $\rho\in\cB^{\otimes n}$ for the verifier to measure.
-	\item Verifier's inputs:
-		\begin{itemize}
-			\item a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit. If $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.  
-			\item a challenge bit $c\in\zo$. The prover needs to do a ``Testing round" if $c=0$. The prover needs to do a ``Hadamard round" if $c=1$. \Ethan{TODO rephrase. c indicates testing vs Hadamard...}
-			\end{itemize}
+	\item Verifier's input:
+			a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit. If $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.  
 \end{itemize}
 
-The protocol: \Ethan{Bring back V1 P1 notations}
+Protocol:
 \begin{enumerate}
-    \item The verifier generates a public and secret key pair $(pk, sk)$ on inputs $h$ and $1^\lambda$. It sends $pk$ to the prover.
-    \item The prover generates a classical ``commitment" $y$ and internal state $\sigma$ on inputs $pk$ and $\rho$. He send $y$ to the verifier.
-	\item The verifier sends $c$ to the prover.
-    \item The prover generates a classical string $a$ on inputs $c$ and $\sigma$, and sends it to back to the verifier.
-    \item \Ethan{Need more discussion about what's testing/Hadamard} If $c=0$, the verifier \Ethan{performs testing and} decides whether he is going to reject on inputs $(pk,y,a)$.
-	If $c=1$, the verifier \Ethan{performs Hadamard round and generates} computes an $n$-bit string $z=V_f(sk,h,y,a)$ on inputs $(sk,h,y,a)$.
-
-	\Ethan{Switch to the following wording:
-
-	If it's a testing round (c=0), then the verifier...
-	If it's a Hadamard round (c=1), then the verifier...}
+	\item The verifier generates a public and secret key pair $(pk, sk)\leftarrow\cVMeasure{1}(1^\lambda, h)$. It sends $pk$ to the prover.
+	\item The prover generates $(y, \sigma)\leftarrow\cPMeasure{2}(pk, \rho)$.
+		$y$ is a classical ``commitment", and $\sigma$ is some internal state.
+		He sends $y$ to the verifier.
+	\item The verifier samples $c\xleftarrow{\$}\zo$ uniformly at random and sends it to the prover. $c=0$ indicates what's called a ``testing round", and $c=1$ indicates a ``Hadamard round".
+	\item The prover generates a classical string $a\leftarrow\cPMeasure{4}(c, \sigma)$ and sends it to back to the verifier.
+	\item If it's a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$, where $o\in\set{\Acc, \Rej}$.
+		If it's a Hadamard round ($c=1$), then the verifier computes $M_{XZ}(\rho, h)$ by $v\leftarrow\cVMeasure{H}(sk, h, y, a)$. It outputs $v$.
 \end{enumerate}
@@
 
-\Ethan{Discussion: Notice that testing round has no outputs, then binding property. Then fact.}
-
-Two modification have been made from the original protocol.
-\begin{itemize}
-	\item On the protocol's third message.
-Instead of randomly picking whether to run what's called a ``testing round" or a ``Hadamard round", we let the verifier decide as one of its inputs.
-\Ethan{Remove this and make $c$ random.
-Instead of this, say that we do parallel repetition but we change the distribution of $c$}
-	\item On the protocol's fourth message, the prover can choose to abort by sending $a=\bot$.
-This is useless for the cheating prover but useful for proving one of our theorems.
-\Ethan{Move to later when it's used}
-\end{itemize}
+Notice that the verifier doesn't in fact receive a measurement result on a testing round.
+Instead, it exists to achieve a ``binding" property that gives certain guarantees against cheating provers.
 
@@
 
-\begin{lem}[\cite{FOCS:Mahadev18a}\hannote{change to fact?} \Ethan{Ok I'll do that later}]~\label{lem:trivial-4-round-strategy}
-    For any input, there exist a prover strategy $(U_{trivial,0},U_{trivial})$ \Ethan{Consider delay introducing the particular notation; just write this name when it's used later} for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{\lambda}$ \Ethan{Changed n to lambda here, see what does it affect} in the testing.
-\end{lem}
-
-\Ethan{Again change all n to lambda for sec. param.}
-
-Mahadev's 4-round protocol has the following binding property.
-
-\Ethan{TODO fix variable labels and whatnot here}
+\Ethan{Again change all n to lambda for sec. param. and fix variable labels}
 
 \begin{lemma}\label{lem:urmila-binding}[binding property of Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the verifier will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally \Ethan{Remove Q} indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer.
+If a prover's strategy in $\PiMeasure$ \hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the verifier will produce a $z$ on the Hadamard round that is $\negl(n)$-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$, unless LWE can be efficiently solved by a quantum computer.
 \end{lemma}
 
-Note that even a honest prover has complete freedom in choosing $\rho$, so protocol~\ref{proto:urmila4} didn't make the prover commit to a particular state.
-What it actually does is let the prover commit to a particular $XZ$ measurement on $\rho$.
-This is good enough for our application, since we will feed the $XZ$ measurement results into the verification of $\QPIP_1$ protocol to ensure that the prover pick the history state as $\rho$ as we will show next.
+We also mention a fact that intuitively captures the completeness of $\PiMeasure$.
 
-By combining the commitment Protocol, $\PiMeasure$, and our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, we get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.
-\Ethan{The following discussion is mine}
-In particular, we combine them by replacing \Ethan{Still a bit ambiguous.
-More discussion than just ``replace".
-Mention it's QPIP1 and whatnot.} the verifier's measurements with a call to $\PiMeasure$.
-It is possible because $\VSamp$ applies only $X$ and $Z$ measurements non-adaptively.
+\begin{fact}[\cite{FOCS:Mahadev18a}]~\label{lem:trivial-4-round-strategy}
+   There exist a prover strategy for $\PiMeasure$ that is accepted with probability $1-\negl{\lambda}$ \Ethan{Changed n to lambda here, see what does it affect} in the testing.
+\end{fact}
+
+\Ethan{Introduce $(U_{trivial,0},U_{trivial})$ later corresponding to the ``honest" prover}
+
+We now use $\PiMeasure$ to modify our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, to achieve a corresponding $\QPIP_0$ protocol $\PiNaive$.
+Recall that $\PiSamp$ is a one-message protocol, where $\VSamp$ applies $X$ and $Z$ measurements non-adaptively to the incoming message.
+We modify $\VSamp$ to pick all its measurement ahead of time, and measure the incoming message from $\PSamp$ through $\PiMeasure$ instead as below.
 
@@
 
-	% Ingrediant: Let $\varepsilon'=0.99\varepsilon$
-
 	Protocol:
 	\begin{enumerate}
-		\item The verifier choose a $XZ$-measurement $h$ from the distribution specified in Step~\ref{step:qpip1-verify} of $\PiSamp$. \Ethan{I didn't change the wording here}
-		It samples $c\xleftarrow{\$}\zo$ uniformly at random.
-		\item The prover prepares $\sigma$ by running Step~\ref{step:qpip1-state-gen} of $\PiSamp$.
+		\item The verifier choose a $XZ$-measurement $h\leftarrow\cVNaive{1}(1^\lambda, 1^\varepsilon, x)$ from the distribution specified in Step~\ref{step:qpip1-verify} of $\PiSamp$.
+		It picks between testing and Hadamard round by sampling $c\xleftarrow{\$}\zo$ uniformly at random.
+	\item The prover prepares $\sigma\leftarrow\cPNaive{2}(1^\lambda, 1^\varepsilon, x)$ by running Step~\ref{step:qpip1-state-gen} of $\PiSamp$.
 		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\sigma), \VMeasure(h))(1^\lambda, 1^{1/\varepsilon}, x)$.
-		\Ethan{Let z be the verifier output when it's a Hadamard round}
-		If $c=1$, the verifier obtains $z_{commit}$ \Ethan{measure/commit... so many notations. Confusing. Just do v}.
-		\item If $c=1$, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by using $z_{commit}$ as the measurement result he would get and outputs $(d,z_{naive})$ \Ethan{Just do z here}.
+	\item If it's a testing round, the verifier accepts or rejects based on the outputs of $\PiMeasure$.
+		If it's a Hadamard round, the verifier obtains $v$. It finishes the verification step of Protocol~\ref{ProtoQPIP1} by using $v$ as the measurement result he would get and outputs $(d, z)$.
 	\end{enumerate}
@@
 
-\Ethan{Try to update notation:
-Use something else for measurement outcome for proto 3. Maybe v or w.
-Let z be sampbqp results.}
-
- Protocol~\ref{proto:qpip0_naive} has no soundness guarantee, but it has the following binding property that would be useful in proving the soundness of the actual protocol in Section~\ref{sec:qpip0}.
+$\PiNaive$ has no soundness guarantee, but it has the following binding property that would be useful in proving the soundness of the actual protocol in Section~\ref{sec:qpip0}.
 
@@
 %Parallel Repetition of the Measurement Subprotocol
+
+\Ethan{Find a good place for this:
+
+On the protocol's fourth message, the prover can choose to abort by sending $a=\bot$. This is useless for the cheating prover but useful for proving one of our theorems.}
 

### 2020-04-15 introduction.tex
Updates from Overleaf

@@
 
-A complexity theoretic reformulation of this problem by Gottesman~\cite{web:Aaronson}
-
-\begin{itemize}
-    \item Add some of the very original motivation of delegation (at some philosophical level) to motivate that sampling problem is important and has been sought after from the very beginning. 
-    \item quickly survey the topic (Add references and surveys) to Mahadev's results. 
-    \item \XW{What're important post-Mahadev's result to discuss here? use subsequentially 3 papers}
-\end{itemize}
+A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
+efficient quantum prover (a $\BQP$ machine).
+In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations. 
+The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,PR:FitKas17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
+The second type of feasibility results (e.g,~\cite{Nat:RUV13} \XW{add more reference})
+considers a $\BPP$ verifier interacting with at least two entangled, non communicating quantum provers. 
+\XW{state the Mahadev's result + post Mahadev's development (3 papers)}.
 

### 2020-04-15 qpip0.tex
Add action items on 8.2

@@
 
-In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave a 4-round $\QPIP_0$ protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine.
-Intuitively, the protocol allows the prover to commit to a state $\rho$ and the verifier to choose a measurement basis $h$ and learn a corresponding measurement outcome $M_{XZ}(\rho, h)$.
-\Ethan{The following discussion is from Han-Hsuan}
+\Ethan{Half of this discussion is from Han-Hsuan}
+
+In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave a 4-round $\QPIP_0$ protocol to let a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
+\Ethan{Mahadev's end result is QPIP0 BQP.
+Two steps. One is measurement proto.
+The other is combine with MF.
+Break the previous sentence into two sentences accordingly. Something like the following:
+
+Mahadev's end results in groundbreaking work 4 round protocol for BQP. At the core it is a 4 round protocol to let BQP prover commit XZ measurement to a classical machine.
+}
+Intuitively, the protocol allows the prover to commit to a state $\rho$ and the verifier to choose a measurement basis $h$ and learn a corresponding measurement outcome $M_{XZ}(\rho, h)$ \Ethan{Actually define this notation by cutting-pasting $h$ from verifier's input}.
+\Ethan{Remove the next sentences or move to later}
 Note that even a honest prover has complete freedom in choosing $\rho$;
 what this protocol actually does is let the prover commit to a particular measurement on $\rho$.
-This is good enough for our application, since we will feed the $XZ$ measurement results into the verification of $\QPIP_1$ protocol to ensure that the prover pick the history state as $\rho$ as we will show next.
+This is good enough for our application, since we will feed the measurement results into the verification of $\QPIP_1$ protocol to ensure that the prover pick the history state as $\rho$ as we will show next.
 We now describe the protocol while omitting the implementation details.
@@
 	\item The verifier samples $c\xleftarrow{\$}\zo$ uniformly at random and sends it to the prover. $c=0$ indicates what's called a ``testing round", and $c=1$ indicates a ``Hadamard round".
-	\item The prover generates a classical string $a\leftarrow\cPMeasure{4}(c, \sigma)$ and sends it to back to the verifier.
-	\item If it's a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$, where $o\in\set{\Acc, \Rej}$.
-		If it's a Hadamard round ($c=1$), then the verifier computes $M_{XZ}(\rho, h)$ by $v\leftarrow\cVMeasure{H}(sk, h, y, a)$. It outputs $v$.
+	\item The prover generates a classical string $a\leftarrow\cPMeasure{4}(pk, c, \sigma)$ and sends it to back to the verifier.
+	\item If it's a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$, where $o\in\set{\Acc, \Rej}$. \Ethan{Just say testing and acc/rej}
+		If it's \Ethan{No abbreviations} a Hadamard round ($c=1$), then the verifier generates and outputs $v\leftarrow\cVMeasure{H}(sk, h, y, a)$.
 \end{enumerate}
@@
 
-Notice that the verifier doesn't in fact receive a measurement result on a testing round.
-Instead, it exists to achieve a ``binding" property that gives certain guarantees against cheating provers.
+The verifier only learns the measurement outcome on a Hadamard round.
+The protocol achieves a ``binding" property that gives guarantees against cheating provers.
 
@@
 
-\Ethan{Again change all n to lambda for sec. param. and fix variable labels}
-
 \begin{lemma}\label{lem:urmila-binding}[binding property of Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-If a prover's strategy in $\PiMeasure$ \hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the verifier will produce a $z$ on the Hadamard round that is $\negl(n)$-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$, unless LWE can be efficiently solved by a quantum computer.
+\Ethan{Need to be more formal. BQP adversaries... etc. Look at the two parallel rep papers}
+\Ethan{Changed $n$ to $\lambda$, TODO sync later uses of this lemma}
+If a prover's strategy in $\PiMeasure$ \hannote{need clarification} results in passing the testing round with probability $1-\negl(\lambda)$, then there must exist a $\rho$ such that for all $h$, the verifier will produce a $v$ on the Hadamard round that is $\negl(\lambda)$-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$, unless LWE can be efficiently solved by a quantum computer.
 \end{lemma}
 
-We also mention a fact that intuitively captures the completeness of $\PiMeasure$.
-
-\begin{fact}[\cite{FOCS:Mahadev18a}]~\label{lem:trivial-4-round-strategy}
+We also mention a fact that will be useful later.
+\begin{fact}
+\label{lem:trivial-4-round-strategy}
    There exist a prover strategy for $\PiMeasure$ that is accepted with probability $1-\negl{\lambda}$ \Ethan{Changed n to lambda here, see what does it affect} in the testing.
@@
 
-We now use $\PiMeasure$ to modify our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, to achieve a corresponding $\QPIP_0$ protocol $\PiNaive$.
-Recall that $\PiSamp$ is a one-message protocol, where $\VSamp$ applies $X$ and $Z$ measurements non-adaptively to the incoming message.
-We modify $\VSamp$ to pick all its measurement ahead of time, and measure the incoming message from $\PSamp$ through $\PiMeasure$ instead as below.
+We now use $\PiMeasure$ to transform our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, to a corresponding $\QPIP_0$ protocol $\PiNaive$ in a natural way.
+Recall that in $\PiSamp$ the verifier learns the XZ measurement outcome of the prover's message.
+In PiInt We let the verifier use $\PiMeasure$ to learn...
 
@@
 	\begin{enumerate}
-		\item The verifier choose a $XZ$-measurement $h\leftarrow\cVNaive{1}(1^\lambda, 1^\varepsilon, x)$ from the distribution specified in Step~\ref{step:qpip1-verify} of $\PiSamp$.
-		It picks between testing and Hadamard round by sampling $c\xleftarrow{\$}\zo$ uniformly at random.
-	\item The prover prepares $\sigma\leftarrow\cPNaive{2}(1^\lambda, 1^\varepsilon, x)$ by running Step~\ref{step:qpip1-state-gen} of $\PiSamp$.
-		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\sigma), \VMeasure(h))(1^\lambda, 1^{1/\varepsilon}, x)$.
-	\item If it's a testing round, the verifier accepts or rejects based on the outputs of $\PiMeasure$.
-		If it's a Hadamard round, the verifier obtains $v$. It finishes the verification step of Protocol~\ref{ProtoQPIP1} by using $v$ as the measurement result he would get and outputs $(d, z)$.
+		\item The verifier choose a $XZ$-measurement $h\leftarrow\cVNaive{1}(1^\lambda, 1^{1/\varepsilon}, x)$ \Ethan{Just don't give names for now} from the distribution specified in Step~\ref{step:qpip1-verify} of $\PiSamp$.
+	\item The prover prepares $\rho\leftarrow\cPNaive{2}(1^\lambda, 1^{1/\varepsilon}, x)$ by running Step~\ref{step:qpip1-state-gen} of $\PiSamp$.
+		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
+		If it's a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
+		If it's a Hadamard round, the verifier obtains $v$.
+	\item 
+		If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)\leftarrow\cVNaive{4}(1^\lambda, 1^{1/\varepsilon}, x, h, v)$.
 	\end{enumerate}
@@
 
-$\PiNaive$ has no soundness guarantee, but it has the following binding property that would be useful in proving the soundness of the actual protocol in Section~\ref{sec:qpip0}.
+$\PiNaive$ has no soundness guarantee \Ethan{Sounds strange}, but it has the following binding property that would be useful in proving the soundness of the actual protocol in Section~\ref{sec:qpip0}.
 
-\begin{lemma}\label{lem:naive-qpip0-binding}[binding property of  Protocol~\ref{proto:qpip0_naive} ]
-	\Ethan{I haven't done anything with this lemma yet. Might need to fix or make consistent later.}
+\Ethan{
+Note that in PiInt the verifier only learns the output in H round
+So PiInt is not QPIP0 with good completeness or soundness.
+On the other hand, it has the following binding property (maybe refer that it does because PiMeasure does)
+}
+
+\begin{lemma}\label{lem:naive-qpip0-binding}[binding property of $\PiNaive$]
+\Ethan{Statement needs to be more rigorous}
 If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen,
 
-$$\norm{(d,z_{naive})-(d,z_{ideal})}_q \leq O(\eps),$$
+\Ethan{Instead of using conditioning, just say the verifier's output in the Hadamard round satisfies this}
+
+$$(d, z)\approx_{c, \varepsilon}(d, z_{ideal})$$
 
 unless LWE can be efficiently solved by a quantum computer.
+\Ethan{under the QLWE assumption}
 \end{lemma}
@@
 \begin{proof}
+\Ethan{I haven't looked at this yet}
 By Lemma~\ref{lem:urmila-binding}, if the prover passes the testing round with probability $1-\negl(n)$, there exist a $\rho$ such that $\norm{z_{commit}- M_{XZ}(\rho,h)}_q \leq \negl(n)$.
@@
 \Ethan{TODO add discussion about parallel rep}
+
+\Ethan{Define in words first, and use the protocol box to introduce notations
+
+unfold for the sake of convenience in analysis
+
+verifier h1 to hm, prover generates whatever it should generate (tensor of whatever),
+pki ski expand all, use vec.
+
+}
 

### 2020-04-15 qpip0.tex
Rewrite parallel rep proto

@@
 
+We now introduce our $\QPIP_0$ protocol $\PiSampZ$ for $\SampBQP$.
+It is essentially a $m$-fold parallel repetition of $\PiNaive$.
+However, instead of choosing whether to run test or Hadamard round randomly each round,
+we run $m-1$ test rounds and only one Hadamard round.
+
 \begin{protocol}{$\QPIP_0$ protocol $\PiSampZ$ for $\SampBQP$}
@@
 		\item Security parameter $1^\lambda$ for $\lambda\in\bbN$.
-		\item Accuracy paramter $1^\varepsilon$ for the $\SampBQP$ instance
-		\item Input $x\in\zo^n$ \Ethan{Or $\zo^*$?} for the $\SampBQP$ instance
+		\item Accuracy paramter $1^{1/\varepsilon}$ for the $\SampBQP$ instance
+		\item Input $x\in\zo^{\poly(\lambda)}$ for the $\SampBQP$ instance
 	\end{itemize}
@@
 \begin{enumerate}
-%    \item Verifier start with description of quantum circuit $C$, input string $x$ 
-	\item The verifier samples $r\xleftarrow{\$}[m]$. For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
-	\item The prover and verifier runs $m$-fold parallel repetion of $\PiNaive$.
-		That is, for $1\leq i\leq m$, run $(\PNaive, \VNaive(c_i))(1^\lambda, 1^\varepsilon, x)$.
-	\item \label{step:multi-testing} If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
-		Else it outputs the result from the Hadamard round copy.
+	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ on inputs $1^\lambda, 1^{1/\varepsilon}, x$.
+	\item The prover prepares $\rho^{\otimes m}$.
+	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}={sk_1,\ldots,sk_m}$, on inputs $1^\lambda$ and $\vec{h}$. It sends $\vec{pk}$ to the prover.
+	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$, and sends it to the verifier.
+	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
+		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$. It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
+	\item The prover generates $\vec{a}$ on inputs $pk, c, \sigma$ and sends it back to the verifier.
+	\item \label{step:multi-testing}
+		The verifier computes the outcome for each round.
+		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
+		Else, it outputs the result from the Hadamard round copy.
 \end{enumerate}
@@
 \begin{theorem}\label{thm:qpip0}
-    Protocol~\ref{proto:QPIP0samp} is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and $O(\eps)$ computational soundness error\hannote{definition}. 
+	$\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and computational soundness. 
+	\Ethan{Its proof currently only shows $O(\varepsilon)$ accuracy.}
 \end{theorem}

### 2020-04-15 qpip0.tex
Fix typos

@@
 \begin{enumerate}
-	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ on inputs $1^\lambda, 1^{1/\varepsilon}, x$.
-	\item The prover prepares $\rho^{\otimes m}$.
-	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}={sk_1,\ldots,sk_m}$, on inputs $1^\lambda$ and $\vec{h}$. It sends $\vec{pk}$ to the prover.
+	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ on inputs $1^\lambda, 1^{1/\varepsilon}, x$. \Ethan{As in step A of proto B...}
+	\item The prover prepares $\rho^{\otimes m}$. \Ethan{Same as last pt.}
+	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$. It sends $\vec{pk}$ to the prover.
 	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$, and sends it to the verifier.
@@
 		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$. It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
-	\item The prover generates $\vec{a}$ on inputs $pk, c, \sigma$ and sends it back to the verifier.
+	\item The prover generates $\vec{a}$ on inputs $\vec{pk}, \vec{c}, \sigma$ and sends it back to the verifier.
 	\item \label{step:multi-testing}
@@
 \end{protocol}
+
+\Ethan{TODO Fix proof notations. Like U0, U notations might've been undefined; see parallel rep paper}
 
@@
 $$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$ 
-	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin \Ethan{Typo} probabilities.
+	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin probabilities.
 Note that $z$ is "sub-normalized", i.e.

### 2020-04-15 preliminaries.tex
Fix typos
Deal with a couple action items

@@
 \begin{definition} [sampling problem]
+	\label{dfn:sampling-problem}
 	A \emph{sampling problem} is a collection of probability distributions $(D_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{m(n)}$ for some fixed polynomial $m$.
@@
 		\item On public inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
-If $d=\Acc$ then $z$ is in the domain \Ethan{?} of $D_x$, otherwise $z=\bot$.
+			If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$ where $m$ is given in \Cref{dfn:sampling-problem} \Ethan{Like this, right?}, otherwise $z=\bot$.
 		\item (Completeness):

### 2020-04-15 qpip0.tex
Deal with a couple action items

@@
 \begin{enumerate}
-	\item The verifier generates a public and secret key pair $(pk, sk)\leftarrow\cVMeasure{1}(1^\lambda, h)$. It sends $pk$ to the prover.
-	\item The prover generates $(y, \sigma)\leftarrow\cPMeasure{2}(pk, \rho)$.
+	\item \label{step:measure1} The verifier generates a public and secret key pair $(pk, sk)\leftarrow\cVMeasure{1}(1^\lambda, h)$. It sends $pk$ to the prover.
+	\item \label{step:measure2} The prover generates $(y, \sigma)\leftarrow\cPMeasure{2}(pk, \rho)$.
 		$y$ is a classical ``commitment", and $\sigma$ is some internal state.
 		He sends $y$ to the verifier.
-	\item The verifier samples $c\xleftarrow{\$}\zo$ uniformly at random and sends it to the prover. $c=0$ indicates what's called a ``testing round", and $c=1$ indicates a ``Hadamard round".
-	\item The prover generates a classical string $a\leftarrow\cPMeasure{4}(pk, c, \sigma)$ and sends it to back to the verifier.
-	\item If it's a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$, where $o\in\set{\Acc, \Rej}$. \Ethan{Just say testing and acc/rej}
+	\item \label{step:measure3} The verifier samples $c\xleftarrow{\$}\zo$ uniformly at random and sends it to the prover.
+$c=0$ indicates what's called a ``testing round", and $c=1$ indicates a ``Hadamard round".
+	\item \label{step:measure4} The prover generates a classical string $a\leftarrow\cPMeasure{4}(pk, c, \sigma)$ and sends it to back to the verifier.
+	\item \label{step:output} If it's a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$, where $o\in\set{\Acc, \Rej}$.
+\Ethan{Just say testing and acc/rej}
 		If it's \Ethan{No abbreviations} a Hadamard round ($c=1$), then the verifier generates and outputs $v\leftarrow\cVMeasure{H}(sk, h, y, a)$.
@@
 \begin{lemma}\label{lem:urmila-binding}[binding property of Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-\Ethan{Need to be more formal. BQP adversaries... etc. Look at the two parallel rep papers}
-\Ethan{Changed $n$ to $\lambda$, TODO sync later uses of this lemma}
-If a prover's strategy in $\PiMeasure$ \hannote{need clarification} results in passing the testing round with probability $1-\negl(\lambda)$, then there must exist a $\rho$ such that for all $h$, the verifier will produce a $v$ on the Hadamard round that is $\negl(\lambda)$-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$, unless LWE can be efficiently solved by a quantum computer.
+	Let $\PMeasureStar$ be a cheating $\BQP$ prover for $\PiMeasure$.
+	Suppose that for all $\lambda\in\bbN$ and $h\in\zo^*$ \Ethan{or $\zo^n$?},
+	$\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$.
+	Then, under the QLWE assumption, there exists some $\rho$ so that for all $h$,
+	the verifier's outputs on the Hadamard round is $\negl(\lambda)$-computationally indistinguishable from $M_{XZ}(\rho, h)$.
 \end{lemma}
@@
 	\begin{enumerate}
-		\item The verifier choose a $XZ$-measurement $h\leftarrow\cVNaive{1}(1^\lambda, 1^{1/\varepsilon}, x)$ \Ethan{Just don't give names for now} from the distribution specified in Step~\ref{step:qpip1-verify} of $\PiSamp$.
-	\item The prover prepares $\rho\leftarrow\cPNaive{2}(1^\lambda, 1^{1/\varepsilon}, x)$ by running Step~\ref{step:qpip1-state-gen} of $\PiSamp$.
+		\item \label{step:naive1} The verifier choose a $XZ$-measurement $h$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
+		\item \label{step:naive2} The prover prepares $\rho$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
 		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
@@
 		If it's a Hadamard round, the verifier obtains $v$.
-	\item 
-		If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)\leftarrow\cVNaive{4}(1^\lambda, 1^{1/\varepsilon}, x, h, v)$.
+		\item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$
+			on inputs $1^\lambda$, $1^{1/\varepsilon}$, $x$, $h$, and $v$. \Ethan{So many inputs... Should the verifier keep internal states instead?}
 	\end{enumerate}
@@
 
-$\PiNaive$ has no soundness guarantee \Ethan{Sounds strange}, but it has the following binding property that would be useful in proving the soundness of the actual protocol in Section~\ref{sec:qpip0}.
-
-\Ethan{
-Note that in PiInt the verifier only learns the output in H round
-So PiInt is not QPIP0 with good completeness or soundness.
-On the other hand, it has the following binding property (maybe refer that it does because PiMeasure does)
-}
+Note that in $\PiNaive$ the verifier only learns the output in Hadamard round.
+So $\PiNaive$ is not a $\QPIP_0$ with good completeness or soundness.
+On the other hand, it also has a binding property, which we will use to achieve completeness and soundness in \Cref{sec:qpip0}.
 
 \begin{lemma}\label{lem:naive-qpip0-binding}[binding property of $\PiNaive$]
-\Ethan{Statement needs to be more rigorous}
-If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen,
-
-\Ethan{Instead of using conditioning, just say the verifier's output in the Hadamard round satisfies this}
-
-$$(d, z)\approx_{c, \varepsilon}(d, z_{ideal})$$
-
-unless LWE can be efficiently solved by a quantum computer.
-\Ethan{under the QLWE assumption}
+	Let $\Pstar$ be a cheating $\BQP$ prover for $\PiNaive$ which passes the testing round with probability $1-\negl(\lambda)$.
+	Then, under the QLWE assumption, the verifier's output in the Hadamard round satisfies
+		$$(d, z)\approx_{c, \varepsilon}(d, z_{ideal}).$$
 \end{lemma}
@@
 \begin{enumerate}
-	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ on inputs $1^\lambda, 1^{1/\varepsilon}, x$. \Ethan{As in step A of proto B...}
-	\item The prover prepares $\rho^{\otimes m}$. \Ethan{Same as last pt.}
-	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$. It sends $\vec{pk}$ to the prover.
-	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$, and sends it to the verifier.
+	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ on inputs $1^\lambda, 1^{1/\varepsilon}, x$ as in \stepref{naive1} of $\PiNaive$
+	\item The prover prepares $\rho^{\otimes m}$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$. Each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$
+	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$, as in \stepref{measure1} of $\PiMeasure$.
+		It sends $\vec{pk}$ to the prover.
+	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$ as in \stepref{measure2} of $\PiMeasure$.
+		It sends $\vec{y}$ to the verifier.
 	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
-		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$. It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
-	\item The prover generates $\vec{a}$ on inputs $\vec{pk}, \vec{c}, \sigma$ and sends it back to the verifier.
+		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
+		It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
+	\item The prover generates $\vec{a}$ on inputs $\vec{pk}, \vec{c}, \sigma$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
 	\item \label{step:multi-testing}
-		The verifier computes the outcome for each round.
+		The verifier computes the outcome for each round as in \stepref{output} of $\PiMeasure$.
 		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.

### 2020-04-15 qpip0.tex
Fix binding dfn for PiMeasure

@@
 \begin{lemma}\label{lem:urmila-binding}[binding property of Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
-	Let $\PMeasureStar$ be a cheating $\BQP$ prover for $\PiMeasure$.
+	Let $\PMeasureStar$ be a $\BQP$ cheating  prover for $\PiMeasure$ and $\lambda$ be the security parameter.
+Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
+\iffalse	
 	Suppose that for all $\lambda\in\bbN$ and $h\in\zo^*$ \Ethan{or $\zo^n$?},
@@
 	the verifier's outputs on the Hadamard round is $\negl(\lambda)$-computationally indistinguishable from $M_{XZ}(\rho, h)$.
+\fi
 \end{lemma}
@@
 	\begin{enumerate}
-		\item \label{step:naive1} The verifier choose a $XZ$-measurement $h$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
-		\item \label{step:naive2} The prover prepares $\rho$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
+		\item \label{step:naive1} The verifier chooses a $XZ$-measurement $h$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
+		\item \label{step:naive2} The prover prepares $\rho$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
 		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
@@
 		\item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$
-			on inputs $1^\lambda$, $1^{1/\varepsilon}$, $x$, $h$, and $v$. \Ethan{So many inputs... Should the verifier keep internal states instead?}
+
 	\end{enumerate}
@@
 \begin{enumerate}
-	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ on inputs $1^\lambda, 1^{1/\varepsilon}, x$ as in \stepref{naive1} of $\PiNaive$
+	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ as in \stepref{naive1} of $\PiNaive$
 	\item The prover prepares $\rho^{\otimes m}$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$. Each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$

### 2020-04-15 qpip0.tex
Rewrite PiInt binding proof

@@
 		\item \label{step:naive2} The prover prepares $\rho$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
-		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
+		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$,
+			where on $\PiMeasure$'s fourth message, the prover can instead choose to abort by sending $a=\bot$.
+			This is useless for the cheating prover but useful for proving one of our theorems later. \Ethan{Where/how to say this?}
 			If it's a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
@@
 \begin{lemma}\label{lem:naive-qpip0-binding}[binding property of $\PiNaive$]
-	Let $\Pstar$ be a cheating $\BQP$ prover for $\PiNaive$ which passes the testing round with probability $1-\negl(\lambda)$.
-	Then, under the QLWE assumption, the verifier's output in the Hadamard round satisfies
-		$$(d, z)\approx_{c, \varepsilon}(d, z_{ideal}).$$
+	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
+	Under the QLWE assumption, if $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
+	then the verifier's output in the Hadamard round is $(\varepsilon+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
 \end{lemma}
@@
 \begin{proof}
-\Ethan{I haven't looked at this yet}
-By Lemma~\ref{lem:urmila-binding}, if the prover passes the testing round with probability $1-\negl(n)$, there exist a $\rho$ such that $\norm{z_{commit}- M_{XZ}(\rho,h)}_q \leq \negl(n)$.
-Note that the prover can choose to abort, so $z_{commit}$ and $\rho$ are subnormalized.
-Let $Ver$ be the verification operation run by Protocol~\ref{ProtoQPIP1} on the measurement outcome.
-\hannote{describe better} Since $Ver$ is an efficient process and $Ver(z_{commmit})+p_{abort}(\Rej,\bot)=(d,z_{naive})$, we have that
-
-\begin{equation} \label{eq:z=verM}
-    \norm{(d,z_{naive})-(Ver( M_{XZ}(\rho,h))+p_{abort}(\Rej,\bot))}_q \leq \negl(n).
-\end{equation}
-\hannote{actually true with subnormalize shit?}
- By Theorem~\ref{QPIP1thm}, for all $\rho$, 
- \begin{equation}
-     \norm{Ver(M_{XZ}(\rho,h))-(d,z_{ideal})} \leq O(\eps).
- \end{equation}
-   Combined with Equation~\ref{eq:z=verM} and Lemma~\ref{lem:computational-triangle0}, and note that $\norm{(\Rej,\bot)-(d,z_{ideal})}=0$, we have that
-   \begin{equation}
-       \norm{(d,z_{naive})-(d,z_{ideal})}_q\leq O(\eps)
-   \end{equation}
+	By \Cref{lem:urmila-binding},
+	there exist some $\rho$ such that
+	$v\approx_{c,\negl(\lambda)}M_{XZ}(\rho,h)$.
+	Let $\cVVer$ be the verification operation in \stepref{qpip1-verify} of $\PiSamp$.
+	Since $\cVVer$ is efficient, we have
+	$(d,z)\approx_{c, \negl(\lambda)}\cVVer(M_{XZ}(\rho, h))$.
+	\Ethan{There were some shenanigans involving subnormalized states for which I'm not quite sure what's going on.}
+	By \Cref{QPIP1thm}, for all $\rho$, 
+	$\cVVer(M_{XZ}(\rho, h))\approx_{c, \varepsilon}(d, z_{ideal})$.
+	So we conclude that
+	$(d, z)\approx_{c, \varepsilon+\negl(\lambda)}(d, z_{ideal})$.
 \end{proof}
@@
 %Parallel Repetition of the Measurement Subprotocol
-
-\Ethan{Find a good place for this:
-
-On the protocol's fourth message, the prover can choose to abort by sending $a=\bot$. This is useless for the cheating prover but useful for proving one of our theorems.}
 

### 2020-04-15 qpip0.tex
Add action item on Pi_int binding proof

@@
 		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$,
-			where on $\PiMeasure$'s fourth message, the prover can instead choose to abort by sending $a=\bot$.
+			where on $\PiMeasure$'s second message, the prover can instead choose to abort by sending $a=\bot$.
 			This is useless for the cheating prover but useful for proving one of our theorems later. \Ethan{Where/how to say this?}
@@
 	Under the QLWE assumption, if $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
+	\Ethan{Wrong assumption. The ``perfect prover" notion here is generalized and allows giving up.}
 	then the verifier's output in the Hadamard round is $(\varepsilon+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
@@
 \begin{proof}
+	\Ethan{TODO this is currently wrong and I'm not sure how to fix it.
+	The version before this which had subnormalized states seems strange too.
+	The correct proof should involve an alternative prover strategy that ``fixes" the abort case
+	by re-running with perfect prover strategy,
+	in order to connect the dots with \Cref{lem:urmila-binding}}
 	By \Cref{lem:urmila-binding},

### 2020-04-15 qpip0.tex
Add/clarify some action items

@@
 Intuitively, the protocol allows the prover to commit to a state $\rho$ and the verifier to choose a measurement basis $h$ and learn a corresponding measurement outcome $M_{XZ}(\rho, h)$ \Ethan{Actually define this notation by cutting-pasting $h$ from verifier's input}.
-\Ethan{Remove the next sentences or move to later}
-Note that even a honest prover has complete freedom in choosing $\rho$;
-what this protocol actually does is let the prover commit to a particular measurement on $\rho$.
-This is good enough for our application, since we will feed the measurement results into the verification of $\QPIP_1$ protocol to ensure that the prover pick the history state as $\rho$ as we will show next.
 We now describe the protocol while omitting the implementation details.
@@
 	\item \label{step:measure4} The prover generates a classical string $a\leftarrow\cPMeasure{4}(pk, c, \sigma)$ and sends it to back to the verifier.
-	\item \label{step:output} If it's a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$, where $o\in\set{\Acc, \Rej}$.
-\Ethan{Just say testing and acc/rej}
-		If it's \Ethan{No abbreviations} a Hadamard round ($c=1$), then the verifier generates and outputs $v\leftarrow\cVMeasure{H}(sk, h, y, a)$.
+	\item \label{step:output} If it is a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$, where $o\in\set{\Acc, \Rej}$.
+\Ethan{Just say it's a test that can acc or rej}
+		If it is a Hadamard round ($c=1$), then the verifier generates and outputs $v\leftarrow\cVMeasure{H}(sk, h, y, a)$.
 \end{enumerate}
@@
 
-\begin{lemma}\label{lem:urmila-binding}[binding property of Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
+\begin{lemma}[binding property of $\PiMeasure$]
+\label{lem:urmila-binding}
 	Let $\PMeasureStar$ be a $\BQP$ cheating  prover for $\PiMeasure$ and $\lambda$ be the security parameter.
@@
 
-We now use $\PiMeasure$ to transform our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, to a corresponding $\QPIP_0$ protocol $\PiNaive$ in a natural way.
-Recall that in $\PiSamp$ the verifier learns the XZ measurement outcome of the prover's message.
-In PiInt We let the verifier use $\PiMeasure$ to learn...
+We now use $\PiMeasure$ to transform our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, to a corresponding $\QPIP_0$ protocol $\PiNaive$.
+Recall that in $\PiSamp$ the verifier takes $X$ and $Z$ measurements on the prover's message.
+In $\PiNaive$ we let the verifier use $\PiMeasure$ to learn those measurement outcomes instead.
 
@@
 		\item \label{step:naive2} The prover prepares $\rho$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
-		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$,
-			where on $\PiMeasure$'s second message, the prover can instead choose to abort by sending $a=\bot$.
-			This is useless for the cheating prover but useful for proving one of our theorems later. \Ethan{Where/how to say this?}
+		\item \label{step:urmila-in-naive}
+		    The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
+On $\PiMeasure$'s second message, we allow the prover to abort by sending $a=\bot$, which does not benefit cheating provers but is useful for analysis.
+
 			If it's a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
@@
 
-\begin{lemma}\label{lem:naive-qpip0-binding}[binding property of $\PiNaive$]
+\begin{lemma}[binding property of $\PiNaive$]
+\label{lem:naive-qpip0-binding}
 	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
@@
 	$(d, z)\approx_{c, \varepsilon+\negl(\lambda)}(d, z_{ideal})$.
+
+	\Ethan{Original proof below.}
+
+	By Lemma~\ref{lem:urmila-binding}, if the prover passes the testing round with probability $1-\negl(n)$, there exist a $\rho$ such that $\norm{z_{commit}- M_{XZ}(\rho,h)}_q \leq \negl(n)$.
+Note that the prover can choose to abort, so $z_{commit}$ and $\rho$ are subnormalized.
+Let $Ver$ be the verification operation run by Protocol~\ref{ProtoQPIP1} on the measurement outcome.
+\hannote{describe better} Since $Ver$ is an efficient process and $Ver(z_{commmit})+p_{abort}(\Rej,\bot)=(d,z_{naive})$, we have that
+
+\begin{equation} \label{eq:z=verM}
+    \norm{(d,z_{naive})-(Ver( M_{XZ}(\rho,h))+p_{abort}(\Rej,\bot))}_q \leq \negl(n).
+\end{equation}
+\hannote{actually true with subnormalize shit?}
+ By Theorem~\ref{QPIP1thm}, for all $\rho$,
+ \begin{equation}
+     \norm{Ver(M_{XZ}(\rho,h))-(d,z_{ideal})} \leq O(\eps).
+ \end{equation}
+   Combined with Equation~\ref{eq:z=verM} and Lemma~\ref{lem:computational-triangle0}, and note that $\norm{(\Rej,\bot)-(d,z_{ideal})}=0$, we have that
+   \begin{equation}
+       \norm{(d,z_{naive})-(d,z_{ideal})}_q\leq O(\eps)
+   \end{equation}
 \end{proof}
@@
 
+\iffalse
 The following protocol is a $\QPIP_0$ protocol for $\SampBQP$
@@
 Given inverse poly p(T), we can parameterize the protocol to have soundness p(T)
+\fi
 
 %	\label{ProtoQPIP1}
-
-\Ethan{TODO add discussion about parallel rep}
-
-\Ethan{Define in words first, and use the protocol box to introduce notations
-
-unfold for the sake of convenience in analysis
-
-verifier h1 to hm, prover generates whatever it should generate (tensor of whatever),
-pki ski expand all, use vec.
-
-}
 
@@
 we run $m-1$ test rounds and only one Hadamard round.
+In the description of our protocol below, we expand out the uses of $\PiNaive$ and $\PiMeasure$ in order to introduce notations that we need in our analysis.
 
@@
 
-\Ethan{TODO Fix proof notations. Like U0, U notations might've been undefined; see parallel rep paper}
+\Ethan{TODO Fix proof notations. Like U0, U notations might've been undefined; copy from parallel rep paper if needed}
 
@@
 	$\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and computational soundness. 
-	\Ethan{Its proof currently only shows $O(\varepsilon)$ accuracy.}
 \end{theorem}
@@
 Property~\ref{property:partition-err} corresponds to Property~1.
-Property~\ref{property:partition-testing}corresponds to Property~4, with $2^{m-1}$ changes to $m-1$ because we only have $m$ possible choices of $\{c\}$.
+Property~\ref{property:partition-testing} corresponds to Property~4, with $2^{m-1}$ changes to $m-1$ because we only have $m$ possible choices of $\{c\}$.
 Property~\ref{property:partition-binding} corresponds to Property~5.
@@
 
- For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ \Ethan{Not consistent with the cited paper; typeof(G0, G1) aren't q circuits} such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,
+ For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,
 
@@
         \item \label{property:partition-testing}
-For all $\{pk\}$, $\{y\}$, fixed $\gamma$, and  $j\neq i$, we have
+For all $\vec{pk}$, $\vec{y}$, fixed $\gamma$, and  $j\neq i$, we have
 
@@
     % $\{c\}\in S_m$ such that $c_i = 0$
-For all $\{pk\}$, $\{y\}$, fixed $\gamma$, and $j\neq i$, there exists an efficient quantum algorithm $\ext_i$ such that
+For all $\vec{pk}$, $\vec{y}$, fixed $\gamma$, and $j\neq i$, there exists an efficient quantum algorithm $\ext_i$ such that
 
@@
 \begin{proof}
+
+\Ethan{This proof currently only shows $O(\varepsilon)$ accuracy, which doesn't perfectly match up with the definition. Hopefully doesn't matter way too much though?}
+
 Completeness is trivial.
@@
 $$P_{acc,i,z}.$$
-Note that $P_{acc,i,z}$ also depends on $\{\pk\},\,\{y\}$ and  $(sk_i,h_i,y_i)$ since it includes the measurement the prover did before sending $a$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
+Note that $P_{acc,i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $a$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
 

### 2020-04-15 preliminaries.tex
Fix binding dfn for PiMeasure
Change epsilon font

@@
 we write $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$.
-We say $\rho_1$ and $\rho_2$ are $\varepsilon$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\varepsilon$.
+We say $\rho_1$ and $\rho_2$ are $\eps$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\eps$.
 For two distributions $f_1$ and $f_2$ over the same finite domain $X$, we write $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ for their total variation distance,
-and we say $f_1$ and $f_2$ are $\varepsilon$-close if $\norm{f_1-f_2}_{TV}\leq\varepsilon$.
+and we say $f_1$ and $f_2$ are $\eps$-close if $\norm{f_1-f_2}_{TV}\leq\eps$.
 We write $x\xleftarrow{\$}X$ when $x$ is sampled uniformly at random from the set $X$.
@@
 	$\SampBQP$ is the class of sampling problems $\left(D_x\right)_{x\in\set{0, 1}^*}$ that can be (approximately) sampled by polynomial-size uniform quantum circuits.
-Namely, there exists a Turing machine $M$ such that for every $n \in \bbN$ and $\varepsilon \in (0,1)$, $M(1^n, 1^{1/\varepsilon})$ outputs a quantum circuit $C$ in $\poly(n, 1/\varepsilon)$ time such that for every $x \in \zo^n$, the output of $C(x)$ (measured in standard basis) is $\varepsilon$-close to $D_x$.
+Namely, there exists a Turing machine $M$ such that for every $n \in \bbN$ and $\eps \in (0,1)$, $M(1^n, 1^{1/\eps})$ outputs a quantum circuit $C$ in $\poly(n, 1/\eps)$ time such that for every $x \in \zo^n$, the output of $C(x)$ (measured in standard basis) is $\eps$-close to $D_x$.
 \end{definition}
@@
 	\begin{itemize}
-		\item On public inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
-			If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$ where $m$ is given in \Cref{dfn:sampling-problem} \Ethan{Like this, right?}, otherwise $z=\bot$.
+		\item On public inputs $1^\lambda$, $1^{1/\eps}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
+			If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$ where $m$ is given in \Cref{dfn:sampling-problem}, otherwise $z=\bot$.
 		\item (Completeness):
-			For all accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
+			For all accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
 			security parameter $\lambda\in\bbN$,
 			and $x\in\zo^{\poly(\lambda)}$, 
-			Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\varepsilon}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
+			Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
 		\item (Statistical soundness): For all cheating prover $P^*$,
-		    accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
+		    accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
 			sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, 
@@
 			\begin{itemize}
-				\item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\varepsilon}, x)$.
+				\item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\eps}, x)$.
 				\item Define $z_{ideal}$ by
@@
 			\end{itemize}
-			It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$. 
+			It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\eps$. 
 		\item (Computational soundness):
-		For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
+		For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
 			sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$, 
@@
 			It holds that
-			$$\abs{\Pr[\mathsf{D}(1^{\lambda}, d,z) = 1] - \Pr[\mathsf{D}(1^{\lambda}, d,z_{ideal}) = 1]} \leq \varepsilon $$
+			$$\abs{\Pr[\mathsf{D}(1^{\lambda}, d,z) = 1] - \Pr[\mathsf{D}(1^{\lambda}, d,z_{ideal}) = 1]} \leq \eps $$
 	\end{itemize}
@@
 %the above definitions should be modified so that $x$ is the verifier's private input.
-%We define blindness with an accuracy parameter $\varepsilon$, which exists in protocols for $\SampBQP$ instances;
+%We define blindness with an accuracy parameter $\eps$, which exists in protocols for $\SampBQP$ instances;
 %one can leave it out where appropriate, such as in protocols for $\BQP$ languages.
@@
 \begin{definition}
-	Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ (and $1^{1/\varepsilon}$ for the case of $\SampBQP$ problem), and verifier's private input $x\in\zo^*$.
+	Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ (and $1^{1/\eps}$ for the case of $\SampBQP$ problem), and verifier's private input $x\in\zo^*$.
 	We say $\Pi$ is \emph{blind} if for all cheating $\BQP$ prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
 	\begin{itemize}
-		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda, 1^{1/\varepsilon})}_{\lambda\in\bbN, \varepsilon\in(0,1), x\in\zo^*}$
-		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda, 1^{1/\varepsilon})}_{\lambda\in\bbN, \varepsilon\in(0,1), x\in\zo^*}$
+		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda, 1^{1/\eps})}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
+		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda, 1^{1/\eps})}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
 	\end{itemize}
@@
 	Let $\rho_1,\rho_2\in\cB^n$.
-	We write $\rho_1\approx_{c,\varepsilon}\rho_2$ if $\rho_1$ and $\rho_2$ are \emph{$\varepsilon$-computationally indistinguishable}.
+	We write $\rho_1\approx_{c,\eps}\rho_2$ if $\rho_1$ and $\rho_2$ are \emph{$\eps$-computationally indistinguishable}.
 	That is, for all quantum polynomial-time \hannote{formalize} distinguishers $\mathsf{D}$,
-	$$\abs{\Pr\left[\mathsf{D}(\rho_1)=1\right]-\Pr\left[\mathsf{D}(\rho_2)=1\right]}\leq\varepsilon.$$
+	$$\abs{\Pr\left[\mathsf{D}(\rho_1)=1\right]-\Pr\left[\mathsf{D}(\rho_2)=1\right]}\leq\eps.$$
 \end{definition}
@@
     \begin{align}
-		\rho_1\approx_{c, \varepsilon}\rho_2\\
-		\rho_2\approx_{c, \varepsilon'}\rho_3.
+		\rho_1\approx_{c, \eps}\rho_2\\
+		\rho_2\approx_{c, \eps'}\rho_3.
     \end{align}
@@
     \begin{align}
-		\rho_1\approx_{c, \varepsilon+\varepsilon'}\rho_3.
+		\rho_1\approx_{c, \eps+\eps'}\rho_3.
     \end{align}

### 2020-04-15 qpip.tex
Fix binding dfn for PiMeasure
Change epsilon font

@@
 		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
-		\item Accuracy parameter $1^{1/\varepsilon}$ where $\varepsilon\in(0, 1)$
+		\item Accuracy parameter $1^{1/\eps}$ where $\eps\in(0, 1)$
 		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
@@
 	\begin{itemize}
-		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
+		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\eps$.
 		\item Let $T$ be the number of gates in $C$.
-		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
+		\item Let $C'$ be $C$ padded with $\frac{6T}{\eps}$ identity gates at the end.
 		\item Let $H_{C'(x)}=\sum_i \alpha_i H_i$ be the X-Z local Hamiltonian instance associated with the computation of $C'(x)$ from \Cref{thm:LHReduction}.
 		\item Let $\histpsi{{C'(x)}}$ be the ground state of $H_{C'(x)}$.
-		\item \XW{Let $s\leq 3T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This is used in de Finetti theorem.
-But I forgot to count ancilla, so it wasn't correct before.}
+		\item \XW{Let $s\leq 3T+\frac{6T}{\eps}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This is used in de Finetti theorem.
+Btw I forgot to count ancilla, so it wasn't correct before.}
 		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
@@
 	\begin{enumerate}
-		\item\label{step:qpip1-state-gen} The honest prover prepares $M=649\frac{T^{41}\lambda^2}{\varepsilon^{51}}$ copies \Ethan{$649=2\times 9\times 6\times 6+1$} of $\histpsi{C'(x)}$ and sends all of it to the verifier qubit-by-qubit.
-		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{20}\lambda}{\varepsilon^{24}}$, and $k\xleftarrow{\$}[M]\setminus I$.
+		\item\label{step:qpip1-state-gen} The honest prover prepares $M=649\frac{T^{41}\lambda^2}{\eps^{51}}$ copies \Ethan{$649=2\times 9\times 6\times 6+1$} of $\histpsi{C'(x)}$ and sends all of it to the verifier qubit-by-qubit.
+		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{20}\lambda}{\eps^{24}}$, and $k\xleftarrow{\$}[M]\setminus I$.
 			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
@@
 		\end{enumerate}
-			Let $Y=\sum_{i\in I} y_i$. If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{1}{192}\frac{\varepsilon^2}{\sum_i\abs{\alpha_i}}$, then the verifier outputs $(\Acc, z)$.
+			Let $Y=\sum_{i\in I} y_i$. If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{1}{192}\frac{\eps^2}{\sum_i\abs{\alpha_i}}$, then the verifier outputs $(\Acc, z)$.
 			Else, it outputs $(\Rej, \bot)$.
@@
 	So we can apply Chernoff bound (\Cref{thm:Chernoff}) to get
-	$$\Prob{Y>\frac{m}{2}-\varepsilon m}\leq\negl(\lambda).$$
+	$$\Prob{Y>\frac{m}{2}-\eps m}\leq\negl(\lambda).$$
 	So $\VSamp$ has negligible probability to reject.
@@
 	Now we show soundness.
-	Suppose $\PSampstar$ is a cheating prover that, on inputs $x, 1^{1/\varepsilon}, 1^\lambda$, sends some $\sigma$ to the verifier.
+	Suppose $\PSampstar$ is a cheating prover that, on inputs $x, 1^{1/\eps}, 1^\lambda$, sends some $\sigma$ to the verifier.
 
@@
 	\leq\sqrt{\frac{2m^2s}{M-m}}
-	\leq\frac{\varepsilon}{6}$$
+	\leq\frac{\eps}{6}$$
 	where $\sigma'_{\leq m+1}$ is the first $m+1$ registers of $\sigma'$.
@@
 Let $(d_j, z_j)$ be the verifier's output corresponding to $\tau_j$, and define $z_{j, ideal}$ accordingly.
-	We claim that $\norm{(d_j, z_j)-(d_j, z_{j, ideal})}_{TV}<\frac{2\varepsilon}{6}$.
+	We claim that $\norm{(d_j, z_j)-(d_j, z_{j, ideal})}_{TV}<\frac{2\eps}{6}$.
 	Let $p_j$ be the probability that $\cVGS(\tau_j)=\Acc$, and consider the following two cases.
@@
 	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\tau_j$ and $\ket{\psi_{C'(x)}}$:
-	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\tau_j, \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}})\geq1-\frac{\varepsilon^2}{36}.$$
+	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\tau_j, \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}})\geq1-\frac{\eps^2}{36}.$$
 	which in turn implies a lower bound on the respective trace distance:
-	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}<\frac{\varepsilon}{6}.$$
+	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}<\frac{\eps}{6}.$$
 	\fi
 	By \Cref{thm:HamCheckClose} we have
-	$$\norm{\tau_j - \ket{\psi^{\mathrm{hist}}_{C'(x)}}\bra{\psi^{\mathrm{hist}}_{C'(x)}}}_{tr}\leq\frac{2}{\sqrt{3}}\sqrt{2\kappa\cdot2\sum_i\abs{\alpha_i}}=\frac{\varepsilon}{6}.$$
+	$$\norm{\tau_j - \ket{\psi^{\mathrm{hist}}_{C'(x)}}\bra{\psi^{\mathrm{hist}}_{C'(x)}}}_{tr}\leq\frac{2}{\sqrt{3}}\sqrt{2\kappa\cdot2\sum_i\abs{\alpha_i}}=\frac{\eps}{6}.$$
 	Observe that when $d_j=\Acc$, $z_j$ is the measurement results on $\tau_j$'s data register,
-	which is $\frac{\varepsilon}{6}$-close to that of $\ket{\psi_{C'(x)}}$.
-	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has at least $1-\frac{\varepsilon}{6}$ probability to contain $C(x)$ due to the padding.
-	So $z_j$ is $\frac{2\varepsilon}{6}$-close to $z_{ideal}$ when $d=\Acc$,
-	which implies that $(d_j, z_j)$ is $\frac{2\varepsilon}{6}$-close to $(d_j, z_{j, ideal})$.
+	which is $\frac{\eps}{6}$-close to that of $\ket{\psi_{C'(x)}}$.
+	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has at least $1-\frac{\eps}{6}$ probability to contain $C(x)$ due to the padding.
+	So $z_j$ is $\frac{2\eps}{6}$-close to $z_{ideal}$ when $d=\Acc$,
+	which implies that $(d_j, z_j)$ is $\frac{2\eps}{6}$-close to $(d_j, z_{j, ideal})$.
 
@@
 	and define $z_{\rho, ideal}$ accordingly.
-	We have $\norm{(d_\rho, z_\rho) - (d, z_{\rho, ideal})}_{TV} < \frac{2\varepsilon}{6}$ since the same is true for all components $\tau_j$.
+	We have $\norm{(d_\rho, z_\rho) - (d, z_{\rho, ideal})}_{TV} < \frac{2\eps}{6}$ since the same is true for all components $\tau_j$.
 
-	As $(d, z)$ is $\frac{\varepsilon}{6}$-close to $(d_\rho, z_\rho)$ by the data processing inequality,
-	using triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
-	Hence $\norm{d - d_\rho}_{TV}\leq\frac{\varepsilon}{2}$, which implies $\norm{(d_\rho, z_{\rho, ideal}) - (d, z_{ideal})}_{TV}$ $\leq$ $\frac{\varepsilon}{2}$.
+	As $(d, z)$ is $\frac{\eps}{6}$-close to $(d_\rho, z_\rho)$ by the data processing inequality,
+	using triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{TV}\leq\frac{\eps}{2}$.
+	Hence $\norm{d - d_\rho}_{TV}\leq\frac{\eps}{2}$, which implies $\norm{(d_\rho, z_{\rho, ideal}) - (d, z_{ideal})}_{TV}$ $\leq$ $\frac{\eps}{2}$.
 	The conclusion then follows from triangle inequality.

### 2020-04-15 qpip0.tex
Change epsilon font

@@
 		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
-		\item Error parameter $\varepsilon\in(0, 1)$
+		\item Error parameter $\eps\in(0, 1)$
 		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
@@
 	\Ethan{Wrong assumption. The ``perfect prover" notion here is generalized and allows giving up.}
-	then the verifier's output in the Hadamard round is $(\varepsilon+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
+	then the verifier's output in the Hadamard round is $(\eps+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
 \end{lemma}
@@
 	By \Cref{QPIP1thm}, for all $\rho$, 
-	$\cVVer(M_{XZ}(\rho, h))\approx_{c, \varepsilon}(d, z_{ideal})$.
+	$\cVVer(M_{XZ}(\rho, h))\approx_{c, \eps}(d, z_{ideal})$.
 	So we conclude that
-	$(d, z)\approx_{c, \varepsilon+\negl(\lambda)}(d, z_{ideal})$.
+	$(d, z)\approx_{c, \eps+\negl(\lambda)}(d, z_{ideal})$.
 
@@
 		\item Security parameter $1^\lambda$ for $\lambda\in\bbN$.
-		\item Accuracy paramter $1^{1/\varepsilon}$ for the $\SampBQP$ instance
+		\item Accuracy paramter $1^{1/\eps}$ for the $\SampBQP$ instance
 		\item Input $x\in\zo^{\poly(\lambda)}$ for the $\SampBQP$ instance
@@
 
-Ingrediant: Let $m=O(1/\varepsilon^2)$ be the number of parallel repetitions to run.
+Ingrediant: Let $m=O(1/\eps^2)$ be the number of parallel repetitions to run.
 
@@
 	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ as in \stepref{naive1} of $\PiNaive$
-	\item The prover prepares $\rho^{\otimes m}$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$. Each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$
+	\item The prover prepares $\rho^{\otimes m}$ on inputs $1^\lambda$, $1^{1/\eps}$, and $x$. Each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$
 	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$, as in \stepref{measure1} of $\PiMeasure$.
@@
 
-\Ethan{This proof currently only shows $O(\varepsilon)$ accuracy, which doesn't perfectly match up with the definition. Hopefully doesn't matter way too much though?}
+\Ethan{This proof currently only shows $O(\eps)$ accuracy, which doesn't perfectly match up with the definition. Hopefully doesn't matter way too much though?}
 

### 2020-04-15 introduction.tex
Move to local copy

@@
 The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,PR:FitKas17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
-The second type of feasibility results (e.g,~\cite{Nat:RUV13} \XW{add more reference})
+The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
 considers a $\BPP$ verifier interacting with at least two entangled, non communicating quantum provers. 
-\XW{state the Mahadev's result + post Mahadev's development (3 papers)}.
+In a recent breakthrough, Mahadev~\cite{mahadev_2018} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
+The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
+We refer curious readers to the survey~\cite{survey:GKK19} for details.
+
+With the newly developed techniques, we revisit the verification of quantum computation problem from both a philosophical and a practical point of view. 
+Our first observation is that the sampling version of $\BQP$ (e.g., as formulated in Aaronson~\cite
+
+\XW{motivation: say with the development, a first question is to revisit the BQP formulation; emphasize that SampBQP is a more important question; and poses some technique difficulty. }
+
+\XW{Another feature one hope is the blindness}
+
+\vspace{1mm} \noindent \textbf{Contribution.}
+
+\XW{list the main results; + comparison with all related works}
 
@@
 \end{itemize}
+
+\XW{then the technical contribution}
 

### 2020-04-15 qpip0.tex
Move to local copy

@@
 
-\Ethan{Half of this discussion is from Han-Hsuan}
-
-In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave a 4-round $\QPIP_0$ protocol to let a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
-\Ethan{Mahadev's end result is QPIP0 BQP.
-Two steps. One is measurement proto.
-The other is combine with MF.
-Break the previous sentence into two sentences accordingly. Something like the following:
-
-Mahadev's end results in groundbreaking work 4 round protocol for BQP. At the core it is a 4 round protocol to let BQP prover commit XZ measurement to a classical machine.
-}
-Intuitively, the protocol allows the prover to commit to a state $\rho$ and the verifier to choose a measurement basis $h$ and learn a corresponding measurement outcome $M_{XZ}(\rho, h)$ \Ethan{Actually define this notation by cutting-pasting $h$ from verifier's input}.
-We now describe the protocol while omitting the implementation details.
-
-\Ethan{Check tone, this is intro/interface}
+In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gives a $\QPIP_0$ protocol for $\BQP$ languages.
+The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that lets a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
+Intuitively, the prover commits to a state $\rho$, while
+the verifier chooses a string $h$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit; if $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.
+At the end of $\PiMeasure$, the verifier learns a measurement outcome $M_{XZ}(\rho, h)$.
+We now describe the interface of $\PiMeasure$ while omitting the implementation details.
 
@@
 \label{proto:urmila4}
+
+\Ethan{Make sure this has the right tone as an intro/interface and isn't confusing to the uninitiated.}
 
@@
 	\item Verifier's input:
-			a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit. If $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.  
+	    the measurement basis choice $h \in \{0,1\}^n$ 
 \end{itemize}
@@
 \label{lem:trivial-4-round-strategy}
-   There exist a prover strategy for $\PiMeasure$ that is accepted with probability $1-\negl{\lambda}$ \Ethan{Changed n to lambda here, see what does it affect} in the testing.
+   There exist a prover strategy for $\PiMeasure$ that is accepted with probability $1-\negl(\lambda)$ \Ethan{Changed n to lambda here, see what does it affect} in the testing.
 \end{fact}
@@
 On the other hand, it also has a binding property, which we will use to achieve completeness and soundness in \Cref{sec:qpip0}.
+
+\Ethan{TODO move the following}
+
+\begin{lem}[another triangle inequality for computational distance]\label{lem:computational-triangle}
+Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.
+
+If
+\begin{align}
+    &\norm{D_1 - D_2}_q \leq \eps   \\
+    &\norm{D_4 - D_6}_q \leq \eps',
+\end{align}
+then
+\begin{align}
+   \norm{ D_3 - D_5}_q \leq \eps+\eps'
+\end{align}
+\end{lem}
+% \begin{align}
+%     D_1 &\approx_{q,\eps} D_2 \\
+%     D_4 &\approx_{q,\eps'} D_6,
+% \end{align}
+% then
+% \begin{align}
+%     D_3 \approx_{q,\eps+\eps'} D_5
+% \end{align}
+\begin{proof}
+% Since
+% $$\norm{D_4 - D_6}_q \leq \eps',$$
+% there exist
+
+We prove by contradiction. Suppose that
+$$\norm{ D_3 - D_5}_q > \eps+\eps',$$
+$$D_3\not\approx_{c, \eps+\eps'} D_5,$$
+then there exist a quantum circuit $A$ of size $poly(n)$ such that
+$$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
+Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that
+$$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
+Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
+$$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$
+$$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$
+So
+\begin{align}
+    &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
+    =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
+    \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
+     > &\eps
+\end{align}
+This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
+\end{proof}
+
+\hannote{comp. indistinguish for subnormalized state?}
+\hannote{triangle inequality}
 
@@
 
+\begin{proof}
+For every cheating prover $\PNaiveStar$ which aborts, consider an alternative prover $P_{alt}$ which is $\PNaiveStar$ with the following modification: on the second round of Protocol~\ref{proto:urmila4}, if $\PNaiveStar$ would abort, $P_{alt}$ switch to run the trivial strategy specified by Fact~\ref{fact:perfectly_pass_test} instead.
+This is possible because the message send by the verifier on the first round is classical, so the prover can recalculate everything.
+
+By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda)$ probability.
+\end{proof}
+
 \subsection{$\QPIP_0$ protocol for $\SampBQP$} \label{sec:qpip0}
@@
 \begin{enumerate}
-	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ as in \stepref{naive1} of $\PiNaive$
-	\item The prover prepares $\rho^{\otimes m}$ on inputs $1^\lambda$, $1^{1/\eps}$, and $x$. Each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$
-	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$, as in \stepref{measure1} of $\PiMeasure$.
+	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ as in \stepref{naive1} of $\PiNaive$.
+	\item The prover prepares $\rho^{\otimes m}$; each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$.
+	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, as in \stepref{measure1} of $\PiMeasure$.
 		It sends $\vec{pk}$ to the prover.
-	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$ as in \stepref{measure2} of $\PiMeasure$.
+	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ as in \stepref{measure2} of $\PiMeasure$.
 		It sends $\vec{y}$ to the verifier.
@@
 		It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
-	\item The prover generates $\vec{a}$ on inputs $\vec{pk}, \vec{c}, \sigma$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
+	\item The prover generates $\vec{a}$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
 	\item \label{step:multi-testing}
@@
 \begin{theorem}\label{thm:qpip0}
-	$\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and computational soundness. 
+	$\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(\lambda)$ completeness error and computational soundness. 
 \end{theorem}
@@
 To prove that such kind of cheating is impossible, we use the following partition lemma from \cite{parallelrep}, which intuitively says that there exist efficient projectors $G_{0,i}$ and $G_{1,i}$ which splits a quantum state in the prover's   internal space into a part that is rejected with high probability in the testing round of $i$-th copy and a part that is accepted with high probability.
-$G_{0,i}$ and $G_{1,i}$ need to be efficient because Protocol~\ref{proto:urmila4} only gives computational indistinguishability.
+$G_{0,i}$ and $G_{1,i}$ need to be efficient because $\PiMeasure$ only gives computational indistinguishability.
 Once we have $G_{0,i}$ and $G_{1,i}$, we can split up the prover's internal state $\ket{\psi}$ like conditional probabilistic events.
@@
 %Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
-\begin{lemma}[partition lemma (revision of Lemma 3.5 of \cite{parallelrep}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{parallelrep} and post-select on the $th$ register being $0$ or $1$ then discard $ph,th,in$.
+\begin{lemma}[partition lemma; revision of Lemma 3.5 of \cite{parallelrep}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{parallelrep} and post-select on the $th$ register being $0$ or $1$ then discard $ph,th,in$.
 Property~\ref{property:partition-err} corresponds to Property~1.
@@
 Property~\ref{property:partition-binding} corresponds to Property~5.
-Property~\ref{property-partition-norm-sum} comes from the fact that $G_0$ and $G_1$ are post-selections of orthogonal results of the same $G$.})]\label{lem:partition2}
-Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round.
-Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$.
+Property~\ref{property-partition-norm-sum} comes from the fact that $G_0$ and $G_1$ are post-selections of orthogonal results of the same $G$.}]\label{lem:partition2}
+Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message.
+Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$, which corresponds to Hadamard round on the $i$-th copy and testing round on all others.
 Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.
+\Ethan{These $n$ probably should be $\lambda$}
 
@@
 \hannote{check}
+  \Ethan{check whether this should be some single pk and y or the entire tuple}
 
@@
 where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
-\Ethan{Typo on line 3?}
+\Ethan{TODO There are typos in the proof}
 \end{proof}
@@
 
-For soundness, We begin by considering the state $\ket{\psi}$ the prover in Protocol~\ref{proto:QPIP0samp} hold before he receives $\{c\}$.
-We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
+For soundness, We begin by considering the state $\ket{\psi}$ the prover in $\PiSampZ$ holds before he receives $\vec{c}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
 
@@
 $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}G_{d_{k-1},k-1,\gamma}\cdots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$
+
+\Ethan{ew.}
 
@@
 \begin{align}
-    \norm{(d,z_{composite,i})-(d,z_{ideal,i})}_q \leq O(\eps)
+    (d,z_{composite,i})\approx_{c, O(\eps)}(d,z_{ideal,i})
 \end{align}
@@
 \begin{align}
-    \norm{(d,z_{good,i})-(d,z_{ideal,i})}_q \leq O(\eps).
+    (d,z_{good,i})\approx_{c, O(\eps)}(d,z_{ideal,i}).
 \end{align}
@@
 \begin{align}
-    \norm{(d,z_{good})-(d,z_{ideal})}_q \leq O(\eps).
+    (d,z_{good})\approx_{c, O(\eps)}(d,z_{ideal}).
 \end{align}
@@
 \begin{align}
-    \norm{(d,z)-(d,z_{good})}_1 \leq \eps
+    (d,z)\approx_{c, O(\eps)}(d,z_{good}).
 \end{align}
@@
 \begin{align}
-     \norm{(d,z)-(d,z_{ideal})}_q \leq O(\eps)
+     (d,z)\approx_{c, O(\eps)}(d,z_{ideal}).
 \end{align}

### 2020-04-15 introduction.tex
Try to push a working version

@@
 
-With the newly developed techniques, we revisit the verification of quantum computation problem from both a philosophical and a practical point of view. 
-Our first observation is that the sampling version of $\BQP$ (e.g., as formulated in Aaronson~\cite
+With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
+Our first observation is that the sampling version of $\BQP$ (e.g., as formulated by Aaronson~\cite{aaronson_2013})
 

### 2020-04-15 qpip0.tex
Try to push a working version
Update triangle ineq. to not use q norm

@@
 \begin{align}
-    &\norm{D_1 - D_2}_q \leq \eps   \\
-    &\norm{D_4 - D_6}_q \leq \eps',
+	D_1\approx_{c,\eps} D_2 \\
+	D_4\approx_{c,\eps'} D_6,
 \end{align}
@@
 \begin{align}
-   \norm{ D_3 - D_5}_q \leq \eps+\eps'
+	D_3\approx_{c,\eps+\eps'} D_5
 \end{align}
@@
 We prove by contradiction. Suppose that
-$$\norm{ D_3 - D_5}_q > \eps+\eps',$$
 $$D_3\not\approx_{c, \eps+\eps'} D_5,$$
@@
 \end{align}
-This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
+	This contradicts with the assumption that $D_1\approx_{c,\eps}D_2$.
 \end{proof}
@@
 By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda)$ probability.
+Therefore by Lemma~\ref{lem:urmila-binding}, there exist a state $\rho_{alt}$ such that
+
 \end{proof}

### 2020-04-15 introduction.tex
Updates from Overleaf

@@
 With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
-Our first observation is that the sampling version of $\BQP$ (e.g., as formulated by Aaronson~\cite{aaronson_2013})
+Our first observation is that the sampling version of $\BQP$ (e.g., as formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem. 
+Philosophically, experiments of quantum mechanics usually generate samples and statistical information, which is well demonstrated in the famous double-split
 

### 2020-04-15 qpip0.tex
Updates from Overleaf

--- 2020-04-15 qpip0.tex
@@
 	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
-	Under the QLWE assumption, if $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
+	Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting, $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
 	\Ethan{Wrong assumption. The ``perfect prover" notion here is generalized and allows giving up.}
@@
 
-By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda)$ probability.
+By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda))$ probability.
+Therefore by Lemma~\ref{lem:urmila-binding}, there exist a state $\rho_{alt}$ such that
+\begin{align}
+    z_{commit,alt} \approx~{c,\eps} M_{XZ}(\rho_{alt},h)
+\end{align}
+
 \end{proof}

### 2020-04-15 qpip0.tex

--- 2020-04-15 qpip0.tex
@@
 
-By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda)$ probability.
+By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda))$ probability.
 Therefore by Lemma~\ref{lem:urmila-binding}, there exist a state $\rho_{alt}$ such that
+\begin{align}
+    z_{commit,alt} \approx~{c,\eps} M_{XZ}(\rho_{alt},h)
+\end{align}
 

### 2020-04-15 introduction.tex
Move to local

--- 2020-04-15 introduction.tex
@@
 considers a $\BPP$ verifier interacting with at least two entangled, non communicating quantum provers. 
-In a recent breakthrough, Mahadev~\cite{mahadev_2018} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
+In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
 The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
@@
 With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
-Our first observation is that the sampling version of $\BQP$ (e.g., as formulated by Aaronson~\cite{aaronson_2013})
+Our first observation is that the sampling version of $\BQP$ (e.g., the $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
+Philosophically, experiments of quantum mechanics usually generate samples and statistical information, which is well demonstrated in the famous double-slit experiment. 
+Moreover, a lot of quantum algorithms from the famous Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component.
+The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones strengthens the importance of $\SampBQP$. 
+Even though the relation between $\BQP$ and $\SampBQP$ is relatively understood in the plain model, what are the potential technical challenges raised by their subtle differences in the context of CVQC and how to resolve them is however far from clear.
+In particular, it is a prior unclear whether it is feasible to develop a CVQC protocol for $\SampBQP$ based on Mahadev's technique~\cite{FOCS:Mahadev18a}.
 

### 2020-04-15 qpip0.tex
Move to local

@@
 
-In this section, we combine \cref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients.
-To boost the soundness, we need  polynomial \Ethan{Wording is strange/misleading} rounds, so we use results from \cite{parallelrep} to run polynomially many copies in parallel and get a constant-round protocol.
+In this section, we combine \Cref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients.
+To boost its soundness, we need  polynomially many repetitions, so we use results from \cite{parallelrep} to run polynomially many copies in parallel and get a constant-round protocol.
 
@@
 $$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
-Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that
+Since $$D_4\approx_{c, \eps'}D_6,$$ we know that
 $$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
@@
 \begin{proof}
-For every cheating prover $\PNaiveStar$ which aborts, consider an alternative prover $P_{alt}$ which is $\PNaiveStar$ with the following modification: on the second round of Protocol~\ref{proto:urmila4}, if $\PNaiveStar$ would abort, $P_{alt}$ switch to run the trivial strategy specified by Fact~\ref{fact:perfectly_pass_test} instead.
+For every cheating prover $\PNaiveStar$ which aborts, consider an alternative prover $P_{alt}$ which is $\PNaiveStar$ with the following modification: on the second round of $\PiMeasure$, if $\PNaiveStar$ would abort, $P_{alt}$ switch to run the trivial strategy specified by Fact~\ref{fact:perfectly_pass_test} instead.
 This is possible because the message send by the verifier on the first round is classical, so the prover can recalculate everything.
 
-By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda))$ probability.
+By \Cref{lem:trivial-4-round-strategy} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda))$ probability.
 Therefore by Lemma~\ref{lem:urmila-binding}, there exist a state $\rho_{alt}$ such that
-\begin{align}
-    z_{commit,alt} \approx~{c,\eps} M_{XZ}(\rho_{alt},h)
+\begin{align} \label{eq:z-alt-rho}
+    z_{commit,alt} \approx_{c,\negl(\lambda)} M_{XZ}(\rho_{alt},h).
 \end{align}
+
+Note that $z_{commit,alt} = z_{commit}+z_{trivial}$, where $z_{commit}$ and $z_{trivial}$ are sub-normalized states correspond to whether $p_{alt}$ follows $\PNaiveStar$ or the trivial strategy.
+
+By Fact~\ref{lem:trivial-4-round-strategy} and Lemma~\ref{lem:urmila-binding}, there exist a sub-normalized state $\rho_{trivial}$ such that
+
+\begin{align} \label{eq:z-triv-rho}
+    z_{trivial} \approx_{c,\negl(\lambda)} M_{XZ}(\rho_{trivial},h).
+\end{align}
+
+By Equation~\ref{eq:z-alt-rho}, Equation~\ref{eq:z-triv-rho}, and Lemma~\ref{lem:computational-triangle}, we have
+
+\begin{align} \label{eq:z-triv-rho}
+    z_{commit} \approx_{c,\negl(\lambda)} M_{XZ}(\rho_{commit},h),
+\end{align}
+
+where $\rho_{commit} \defeq \rho_{alt}-\rho_{trivial}$.\hannote{wrong, not a state.} Note that
 
@@
   Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are  sub-normalized.
-$G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$ and $pk,y$.
+$G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$ and $\vec{pk},\vec{y}$.
 \hannote{check}
-  \Ethan{check whether this should be some single pk and y or the entire tuple}
 
@@
     \sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| \nn \\
-    \leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}}  \nn \\ \leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\norm{ P_z\ket{\phi}}^2}     \nn \\
+    \leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}} \nn \\
+    \leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\sum_z\norm{P_z\ket{\phi}}^2} \nn \\
     \leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn \\
@@
 where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
-\Ethan{TODO There are typos in the proof}
 \end{proof}
@@
 where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round.
-Note that we have averaged over $pk, y$ where as previously everything has fixed $pk$ and $y$.
-\hannote{add description about  averaging $pk$ here.}
+Note that we have averaged over $\vec{pk}, \vec{y}$ where as previously everything has fixed $\vec{pk}$ and $\vec{y}$.
 
-Since $\{c\}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have 
+Since $\vec{c}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have 
 $$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$ 
 	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin probabilities.
-Note that $z$ is "sub-normalized", i.e.
+Note that $z$ is ``sub-normalized", i.e.
 $\tr (z)= \text{probability of getting accepted} \leq 1$.
@@
 If $c=1$ and the prover generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he runs $U$ and check whether every copy except the $i$-th copy would be accepted.
-If all $m-1$ copies acceptes, he reply with the $i$-th copy, otherwise reply $\bot$.
-If $c-0$ and the prover failed to generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he runs $U_{trivial}$ and repies.
+If all $m-1$ copies accepts, he reply with the $i$-th copy, otherwise reply $\bot$.
+If $c=0$ and the prover failed to generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he runs $U_{trivial}$ and repies.
 If $c=1$ and the prover failed to generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he replies with $\bot$.
@@
 \end{align}
-\hannote{do we lose a factor of $m$?}
-Recall that by Eq~\ref{eq:z-z-good} we have $\norm{z-z_{good}}_1 \leq \eps$ if we pick $m,T,\gamma_0=???$ \hannote{tune eps}, which implies 
+% \hannote{do we lose a factor of $m$?}
+Recall that by Eq~\ref{eq:z-z-good} we have $\norm{z-z_{good}}_1 \leq \eps$ if we pick $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$, which implies 
 \begin{align}
@@
 
-Therefore by Lemma~\ref{lem:computational-triangle0}, we have  
+Therefore  we have  
 \begin{align}
@@
 \end{align}
-\hannote{the composition of z ideal and triangle ineq is sketchy lol. Also need to specify different z ideal}
+%\hannote{the composition of z ideal and triangle ineq is sketchy lol. Also need to specify different z ideal}
 

### 2020-04-15 qpip0.tex
Write proof first draft for Pi_Int binding

@@
 		    The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
-On $\PiMeasure$'s second message, we allow the prover to abort by sending $a=\bot$, which does not benefit cheating provers but is useful for analysis.
-
-			If it's a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
-			If it's a Hadamard round, the verifier obtains $v$.
+			\begin{enumerate}
+				\item The verifier samples $(pk, sk)\leftarrow\cVNaive{1}(1^\lambda, h)$ and sends $pk$ to the prover.
+				\item The prover runs $(y, \sigma)\leftarrow\cPNaive{2}(pk, \rho)$.
+					Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but is useful for analysis.
+				\item The verifier samples $c\leftarrow\cVNaive{3}$
+				\item The prover replies $a\leftarrow\cPNaive{4}(pk, c, \sigma)$.
+				\item 
+					If it is a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
+					If it is a Hadamard round, the verifier obtains $v$.
+			\end{enumerate}
 		\item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$
-
 	\end{enumerate}
@@
 
-\Ethan{TODO move the following}
-
-\begin{lem}[another triangle inequality for computational distance]\label{lem:computational-triangle}
-Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.
-
-If
-\begin{align}
-	D_1\approx_{c,\eps} D_2 \\
-	D_4\approx_{c,\eps'} D_6,
-\end{align}
-then
-\begin{align}
-	D_3\approx_{c,\eps+\eps'} D_5
-\end{align}
-\end{lem}
-% \begin{align}
-%     D_1 &\approx_{q,\eps} D_2 \\
-%     D_4 &\approx_{q,\eps'} D_6,
-% \end{align}
-% then
-% \begin{align}
-%     D_3 \approx_{q,\eps+\eps'} D_5
-% \end{align}
-\begin{proof}
-% Since
-% $$\norm{D_4 - D_6}_q \leq \eps',$$
-% there exist
-
-We prove by contradiction. Suppose that
-$$D_3\not\approx_{c, \eps+\eps'} D_5,$$
-then there exist a quantum circuit $A$ of size $poly(n)$ such that
-$$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
-Since $$D_4\approx_{c, \eps'}D_6,$$ we know that
-$$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
-Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
-$$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$
-$$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$
-So
-\begin{align}
-    &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
-    =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
-    \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
-     > &\eps
-\end{align}
-	This contradicts with the assumption that $D_1\approx_{c,\eps}D_2$.
-\end{proof}
-
-\hannote{comp. indistinguish for subnormalized state?}
-\hannote{triangle inequality}
-
 \begin{lemma}[binding property of $\PiNaive$]
@@
 	Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting, $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
-	\Ethan{Wrong assumption. The ``perfect prover" notion here is generalized and allows giving up.}
 	then the verifier's output in the Hadamard round is $(\eps+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
 \end{lemma}
+\begin{proof}
+	Consider the following reduction to another cheating $\BQP$ prover for $\PiNaive$ that is perfect and non-aborting.
 
-\begin{proof}
-	\Ethan{TODO this is currently wrong and I'm not sure how to fix it.
-	The version before this which had subnormalized states seems strange too.
-	The correct proof should involve an alternative prover strategy that ``fixes" the abort case
-	by re-running with perfect prover strategy,
-	in order to connect the dots with \Cref{lem:urmila-binding}}
-	By \Cref{lem:urmila-binding},
-	there exist some $\rho$ such that
-	$v\approx_{c,\negl(\lambda)}M_{XZ}(\rho,h)$.
-	Let $\cVVer$ be the verification operation in \stepref{qpip1-verify} of $\PiSamp$.
-	Since $\cVVer$ is efficient, we have
-	$(d,z)\approx_{c, \negl(\lambda)}\cVVer(M_{XZ}(\rho, h))$.
-	\Ethan{There were some shenanigans involving subnormalized states for which I'm not quite sure what's going on.}
-	By \Cref{QPIP1thm}, for all $\rho$, 
-	$\cVVer(M_{XZ}(\rho, h))\approx_{c, \eps}(d, z_{ideal})$.
-	So we conclude that
-	$(d, z)\approx_{c, \eps+\negl(\lambda)}(d, z_{ideal})$.
+	We define $\Pstar$ as follows.
+	For the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
+	If $y\ne\bot$, then reply $y$.
+	Else run the corresponding step of the dummy strategy as in \Cref{lem:trivial-4-round-strategy} and reply with its results.
+	For the fourth message, if $y\ne\bot$, run and reply with $a\leftarrow\cPNaiveStar{4}(pk, c, \sigma)$.
+	If $y=\bot$ and $c=0$, continue the dummy strategy.
 
-	\Ethan{Original proof below.}
+	Observe that this $\Pstar$ indeed passes testing round with overwhelming probability by construction.
+	So we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property.
+	Combining it with $\PiSamp$'s soundness,
+	we see that the verifier's outputs corresponding $\Pstar$, $(d', z')$ is computationally indistinguishable to some $(d', z_{ideal}')$
 
-	By Lemma~\ref{lem:urmila-binding}, if the prover passes the testing round with probability $1-\negl(n)$, there exist a $\rho$ such that $\norm{z_{commit}- M_{XZ}(\rho,h)}_q \leq \negl(n)$.
-Note that the prover can choose to abort, so $z_{commit}$ and $\rho$ are subnormalized.
-Let $Ver$ be the verification operation run by Protocol~\ref{ProtoQPIP1} on the measurement outcome.
-\hannote{describe better} Since $Ver$ is an efficient process and $Ver(z_{commmit})+p_{abort}(\Rej,\bot)=(d,z_{naive})$, we have that
+	Conditioned on $\PNaiveStar$ accept, clearly $(d, z)=(d', z')$.
+	On $\PNaiveStar$ reject, since dummy strategy will be rejected with overwhelming probability in Hadamard round, \Ethan{kinda obvious but we never explicitly explained why}
+	we also have $(d, z)=(\Rej, \bot)\approx_{c, \negl(\lambda)}(d', z')$
 
-\begin{equation} \label{eq:z=verM}
-    \norm{(d,z_{naive})-(Ver( M_{XZ}(\rho,h))+p_{abort}(\Rej,\bot))}_q \leq \negl(n).
-\end{equation}
-\hannote{actually true with subnormalize shit?}
- By Theorem~\ref{QPIP1thm}, for all $\rho$,
- \begin{equation}
-     \norm{Ver(M_{XZ}(\rho,h))-(d,z_{ideal})} \leq O(\eps).
- \end{equation}
-   Combined with Equation~\ref{eq:z=verM} and Lemma~\ref{lem:computational-triangle0}, and note that $\norm{(\Rej,\bot)-(d,z_{ideal})}=0$, we have that
-   \begin{equation}
-       \norm{(d,z_{naive})-(d,z_{ideal})}_q\leq O(\eps)
-   \end{equation}
-\end{proof}
-
-\begin{proof}
-For every cheating prover $\PNaiveStar$ which aborts, consider an alternative prover $P_{alt}$ which is $\PNaiveStar$ with the following modification: on the second round of $\PiMeasure$, if $\PNaiveStar$ would abort, $P_{alt}$ switch to run the trivial strategy specified by Fact~\ref{fact:perfectly_pass_test} instead.
-This is possible because the message send by the verifier on the first round is classical, so the prover can recalculate everything.
-
-By \Cref{lem:trivial-4-round-strategy} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda))$ probability.
-Therefore by Lemma~\ref{lem:urmila-binding}, there exist a state $\rho_{alt}$ such that
-\begin{align} \label{eq:z-alt-rho}
-    z_{commit,alt} \approx_{c,\negl(\lambda)} M_{XZ}(\rho_{alt},h).
-\end{align}
-
-Note that $z_{commit,alt} = z_{commit}+z_{trivial}$, where $z_{commit}$ and $z_{trivial}$ are sub-normalized states correspond to whether $p_{alt}$ follows $\PNaiveStar$ or the trivial strategy.
-
-By Fact~\ref{lem:trivial-4-round-strategy} and Lemma~\ref{lem:urmila-binding}, there exist a sub-normalized state $\rho_{trivial}$ such that
-
-\begin{align} \label{eq:z-triv-rho}
-    z_{trivial} \approx_{c,\negl(\lambda)} M_{XZ}(\rho_{trivial},h).
-\end{align}
-
-By Equation~\ref{eq:z-alt-rho}, Equation~\ref{eq:z-triv-rho}, and Lemma~\ref{lem:computational-triangle}, we have
-
-\begin{align} \label{eq:z-triv-rho}
-    z_{commit} \approx_{c,\negl(\lambda)} M_{XZ}(\rho_{commit},h),
-\end{align}
-
-where $\rho_{commit} \defeq \rho_{alt}-\rho_{trivial}$.\hannote{wrong, not a state.} Note that
-
+	The conclusion follows from a simple hybrid argument.
 \end{proof}

### 2020-04-15 qpip0.tex
Updates from Overleaf

--- 2020-04-15 qpip0.tex
@@
 Property~\ref{property-partition-norm-sum} comes from the fact that $G_0$ and $G_1$ are post-selections of orthogonal results of the same $G$.}]\label{lem:partition2}
+Let $\lambda$ be the security parameter and  $\eps$ be the accuracy parameter.
 Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message.
 Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$, which corresponds to Hadamard round on the $i$-th copy and testing round on all others.
-Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.
+Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=\poly(\eps)$ and $T=1/\poly(\eps)$.
 \Ethan{These $n$ probably should be $\lambda$}
 
- For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,
+ For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized) $\poly(\lambda)$-qubits quantum state $\ket{\psi}_{\regX,\regZ}$,
 
@@
 $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$ and $\vec{pk},\vec{y}$.
-\hannote{check}
 
@@
 \begin{enumerate}
-    \item \label{property:partition-err}  $$\E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\|^2 \leq \frac{6}{T}+\negl(n),$$
+    \item \label{property:partition-err}  $$\E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\|^2 \leq \frac{6}{T}+\negl(\lambda),$$
 
@@
     \begin{align}
-        \E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\| \leq \sqrt{\frac{6}{T}}+\negl(n)
+        \E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\| \leq \sqrt{\frac{6}{T}}+\negl(\lambda)
     \end{align}
@@
  \begin{align}
-    \norm{ P_{i,pk_i,y_i,acc} \circ U\frac{\ket{e_j}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}}^2 \leq (m-1)\gamma_0+\negl(\secpar),
+    \norm{ P_{i,pk_i,y_i,acc} \circ U\frac{\ket{e_j}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}}^2 \leq (m-1)\gamma_0+\negl(\lambda),
  \end{align}
@@
 \begin{align}
-     \norm{P_{i,pk_i,y_i,acc} \circ \ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)}^2 =1-\negl(\secpar).
+     \norm{P_{i,pk_i,y_i,acc} \circ \ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)}^2 =1-\negl(\lambda).
 \end{align}
@@
 
-And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$\hannote{problem with $e_j$ or $e_i$}
+And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$   %\hannote{problem with $e_j$ or $e_i$}
 
@@
 By construction, when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$.
-Also note that this is the only case where the verifier won't reject, so $(d,z_{composite,i})=(d,z_{good,i})$, where  $(d,z)_{good,i} \defeq (\Acc, z_{good,i}) + (1-|z_{good,i}|)(\Rej,\bot)$ \hannote{correct notation?
-operational def?} .
+Also note that this is the only case where the verifier won't reject, so $(d,z_{composite,i})=(d,z_{good,i})$, where $(d,z_{good,i})$ is defined as:
+
+$$\begin{cases}
+					 (d,z_{good,i}) \la (\Acc, z_{good,i}/|z_{good,i}|) & \text{with probability } |z_{good,i}|\\
+					(d,z_{good,i}) = (\Rej,\bot)  & \text{otherwise } 
+				\end{cases}$$.
+
+% where  $(d,z)_{good,i} \defeq (\Acc, z_{good,i}) + (1-|z_{good,i}|)(\Rej,\bot)$ \hannote{correct notation? operational def?} .
+
 Therefore

### 2020-04-15 blind.tex
Change epsilon font

@@
 \label{sec:BlindBQP2}
+
+In this section, we present a generic protocol compiler that compiles any $\QPIP_0$ protocol $\Pi_0 = (P_0,V_0)$ to a protocol $\Pi = (P,V)$ that achieve blindness while preserving the completeness, soundness, and round complexity.
+At a high-level, the idea is simple: we simply run the original protocol under a quantum homomorphic encryption $\QHE$ with the verifier's key.
+Intuitively, this allows the prover to compute his next message under encryption without learning the underlying verifier's message, and hence achieves blindness while preserving the property of the original protocol.
+
+However, several issues need to be taken care to make the idea work.
+First, since the verifier is classical, we need the quantum homomorphic encryption scheme $\QHE$ to be \emph{classical friendly} as defined in Definition~\ref{def:classical-friendly}.
+Namely, the key generation algorithm and the encryption algorithm for classical messages should be classical, and when the underlying message is classical, the ciphertext (potentially from homomorphic evaluation) and the decryption algorithm should be classical as well.
+Fortunately, the quantum homomorphic encryption scheme of Mahadev~\cite{mahadev_qfhe} is classical friendly
+
+and the encryption algorithm for classical messages should be classical, and
+
+The idea of running the protocol under homomorphic encryptions is used in~\cite{KMThesis} in a classical setting, but for a different purpose of making the protocol ``computationally simulatable'' in their context.
 
@@
 
-	Common inputs\footnote{For the sake of simplicity, we omit accuracy parameter $\varepsilon$ where it exists}:
+	Common inputs\footnote{For the sake of simplicity, we omit accuracy parameter $\eps$ where it exists}:
 	\begin{itemize}

### 2020-04-15 introduction.tex

@@
 
-A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
+A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier/client (a $\BPP$ machine) to verify the output of an
 efficient quantum prover (a $\BQP$ machine).
@@
 With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
-Our first observation is that the sampling version of $\BQP$ (e.g., the $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
-Philosophically, experiments of quantum mechanics usually generate samples and statistical information, which is well demonstrated in the famous double-slit experiment. 
-Moreover, a lot of quantum algorithms from the famous Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component.
+We observe that the \emph{sampling} version of $\BQP$ (e.g., the $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
+Philosophically, the outcomes of quantum mechanical experiments are usually samples or statistical information, which is well demonstrated in the famous double-slit experiment. 
+Moreover, a lot of quantum algorithms from Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component.
 The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones strengthens the importance of $\SampBQP$. 
@@
 
-\XW{motivation: say with the development, a first question is to revisit the BQP formulation; emphasize that SampBQP is a more important question; and poses some technique difficulty. }
+Another desirable property of CVQC protocols is the \emph{blindness} where the prover cannot distinguish the particular computation in the protocol from another one of the same size, and hence is blind about the client's input.
+Historically, blindness has been achieved in the weaker formulations of CVQC based on various techniques: e.g., the measurement-based quantum computation exploited in~\cite{BFK09}, the quantum authentication scheme exploited in~\cite{arXiv:ABOEM17}, and the self-testing technique exploited in~\cite{Nat:RUV13}.
+Moreover, the blindness property is known to be helpful to establish the verifiability of CVQC protocols. However, this is never an easy task. 
+See for example the significant amount of efforts to add verifiability to blind CVQC protocols in~\cite{FK17}. 
+Achieving both blindness and verifiability on top of Mahadev's technique~\cite{FOCS:Mahadev18a} is a conceivably much more challenging task. 
+The only successful attempt~\cite{FOCS:GheVid19} so far applies Mahadev's technique to the measurement-based quantum computation, 
+whereas the analysis is still very specific to the construction. 
+Could there be a \emph{generic} way to achieve blindness and verifiability for CVQC protocols at the same time?
 
-\XW{Another feature one hope is the blindness}
+\vspace{2mm} \noindent \textbf{Contribution.} We provide \emph{affirmative} solutions to both of our questions. 
+In particular, we demonstrate the feasibility of the classical verification of quantum sampling by 
+constructing a constant-round CVQC protocol for $\SampBQP$. 
+Our protocol leverages the Hamiltonian model and the computational X-Z measurement from~\cite{FOCS:Mahadev18a}.
+However, a significant amount of new techniques have been developed to deal with the difference between $\SampBQP$ and $\BQP$, which will be highlighted in the technical contribution below. Precisely,
 
-\vspace{1mm} \noindent \textbf{Contribution.}
-
-\XW{list the main results; + comparison with all related works}
-
-Sampling Part
-\begin{itemize}
-    \item Motivating Sampling.  and a little bit why sampling could be different and hard. (Aaronson's paper?) 
-    \item To ADD
-    \item 2nd de finetti have independence; but latter, the analysis, computational parallel repetition. 
-    \item emphasize the feasibility. 
-\end{itemize}
+\XW{Insert the theorem statement for the first result here!}
 
@@
 
-\XW{then the technical contribution}
+%       \begin{itemize}
+%           \item Sampling, the only paper; how about classical sampling?
+%           \item the following for BQP  
+%           \item blind and verifiable ~\cite{GV19}; we  constant round; technique-wise very different. 
+%           \item there is a table in~\cite{Grilo19}. Safe to say ~\cite{GV19} only existing blind protocol in the computational setting? 
+%           \item all previous either quantum clients, or at least 2 provers. 
+%           \item the following for blindess
+%           \item Mahadev in her thesis~\cite{mahadev_2018} discussed a bit about the relation between verifiability and blindness.
+She hoped to get verifiability out of blindness by designing some non-malleable QFHE but failed.
+%           \item what's the high-level message we can say here?
+Use QFHE in a different way?
+It is correct that not much work in the classical setting either.
+Maybe existing classical work employs the principle but with different implementation.
+%           \item old approach, first get blindness  (measurement-based, self-testing), and then try to make it verifiable; our approach, first have a verifiable protocol, and upgrade by a QFHE. 
+%           \item directly QFHE (blindness) won't give verifiability. some thoughts from Mahadev. 
+%
+%           technical comparison with the past parallel % reptiton. 
+%           \item
+
+\vspace{2mm} \noindent \textbf{Techniques.}
 
@@
     \item Technical contribution. 
+    \item 2nd de finetti have independence; but latter, the analysis, computational parallel repetition. 
     \item TO ADD for both parts. 
@@
 
-Open Questions
+\vspace{2mm} \noindent \textbf{Open Questions.}
 \begin{itemize}
@@
 \end{itemize}
-
-Organization
 

### 2020-04-16 blind.tex
Sync with local for macro changes

--- 2020-04-15 blind.tex
@@
 \label{sec:BlindBQP2}
+
+In this section, we present a generic protocol compiler that compiles any $\QPIP_0$ protocol $\Pi = (P, V)$ (with an arbitrarily number of rounds) to a protocol $\Piblind = (\Pblind, \Vblind)$ that achieve blindness while preserving the completeness, soundness, and round complexity.
+At a high-level, the idea is simple: we simply run the original protocol under a quantum homomorphic encryption $\QHE$ with the verifier's key.
+Intuitively, this allows the prover to compute his next message under encryption without learning the underlying verifier's message, and hence achieves blindness while preserving the properties of the original protocol.
+
+However, several issues need to be taking care to make the idea work.
+First, since the verifier is classical, we need the quantum homomorphic encryption scheme $\QHE$ to be \emph{classical friendly} as defined in Definition~\ref{def:classical-friendly}.
+Namely, the key generation algorithm and the encryption algorithm for classical messages should be classical, and when the underlying message is classical, the ciphertext (potentially from homomorphic evaluation) and the decryption algorithm should be classical as well.
+Fortunately, the quantum homomorphic encryption scheme of Mahadev~\cite{mahadev_qfhe} is classical friendly.
+
+A more subtle issue is to preserve the soundness.
+Intuitively, the soundness holds since the execution of $\Piblind$ simulates the execution of $\Pi$, and hence the soundness of $\Pi$ implies the soundness of $\Piblind$.
+However, to see the subtle issue, let us consider the following naive compiler that uses a single key: In $\Piblind$,  the verifier $V$ initially generates a pair $\QHE$ key $(pk, sk)$, sends $pk$ and encrypted input $\QEnc(pk,x)$ to $P$.
+Then they run $\Pi$ under encryption with this key, where both of them use homomorphic evaluation to compute their next message.
+
+There are two reasons that the compiled protocol $\Piblind$ may not be sound (or even not blind).
+First, in general, the $\QHE$ scheme may not have \emph{circuit privacy}; namely, the homomorphic evaluation may leak information about the circuit being evaluated.
+Since the verifier computes his next message using homomorphic evaluation, a cheating prover $\Pblindstar$ seeing the homomorphically evaluated ciphertext of the verifier's message may learn information about the verifier's next message circuit, which may contain information about the secret input $x$ or help $\Pblindstar$ to break the soundness.
+Second, $\Pblindstar$ may send invalid ciphertexts to $V$, so the execution of $\Piblind$ may not simulate a valid execution of $\Pi$.
+\Ethan{Either ways, we need $\QHE$ to never fail on decryption, in both this naive $\Piblind$ and our actual $\Piblind$. So there can't be ``invalid ciphertexts" either ways.}
+
+To resolve the issue, we let the verifier to switch to a fresh new key for each round of the protocol.
+For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext \Ethan{Need to mention somewhere that if $\QDec$ fails, it outputs $\bot$ instead of aborting}, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$.
+Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoid the issue of circuit privacy.
+Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it to $\Pblind$.
+This allows the prover to homomorphically convert ciphertexts under key $pk$ to ciphertexts under key $pk'$.
+By doing so, we show that for any cheating prover $\Pblindstar$, the interaction $(\Pblindstar, \Vblind)$ indeed simulates a valid interaction of $(\Pstar, V)$ for some cheating $\Pstar$, and hence the soundness of $\Pi$ implies the soundness of the compiled protocol.
+
+We note that the idea of running the protocol under homomorphic encryptions is used in~\cite{KMThesis} in a classical setting, but for a different purpose of making the protocol ``computationally simulatable'' in their context.
+
+\iffalse
 
@@
 
-\Ethan{General comment: Make story more interesting. Clearly claim our own contributions.}
+\fi
 
-We now state our compiler that gives any $\QPIP_0$ protocol blindness.
-For notation, when there are many sets of $\QHE$ keys in play at the same time,
-we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
-We start with a general form of a $\QPIP_0$ protocol that we'll be compiling.
+%\Ethan{General comment: Make story more interesting. Clearly claim our own contributions.}
 
-\begin{protocol}{$\QPIP_0$ protocol $\Pi_0=(P, V)(x)$ where only the verifier receives outputs}
+\KM{notation inconsistency...}
 
-	Common inputs\footnote{For the sake of simplicity, we omit accuracy parameter $\varepsilon$ where it exists}:
+We proceeds to present our compiler. We start by introducing the notation of a $\QPIP_0$ protocol $\Pi$ as follows.
+% We now state our compiler that gives any $\QPIP_0$ protocol blindness.
+
+\begin{protocol}{$\QPIP_0$ protocol $\Pi=(P, V)(x)$ where only the verifier receives outputs}
+
+	Common inputs\footnote{For the sake of simplicity, we omit accuracy parameter $\eps$ where it exists}:
 	\begin{itemize}
@@
 We compile the above protocol to achieve blindness as follows.
+For notation, when there are many sets of $\QHE$ keys in play at the same time,
+we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
+%We start with a general form of a $\QPIP_0$ protocol that we'll be compiling.
 
@@
 By the correctness of $\QHE$, the completeness error of $\Piblind$ is negligibly close to that of $\Pi$.
-We show the soundness of $\Piblind$ in the following theorem.
+For the soundness property, we show the following lemma, which implies that $\Piblind$ preserves the soundness of $\Pi_0$.
 
-\begin{theorem}
+%soundness of $\Piblind$ in the following theorem.
+
+\begin{thm} \label{thm:compiler-errors}
 	For all cheating $\BQP$ prover $\Pblindstar$, there exists a cheating $\BQP$ prover $\Pstar$ s.t.
 for all $\lambda$ and input $x\in\zo^{\poly(\lambda)}$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
-\end{theorem}
+\end{thm}
 \begin{proof}
@@
 Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
-\begin{theorem}
-	$\Piblind$ is blind.
-\end{theorem}
+\begin{thm} \label{thm:compiler-blindness}
+	Assuming the QLWE assumption, $\Piblind$ is blind.
+\end{thm}
 \begin{proof}
@@
 
-Our compiler is a straightforward way of achievement blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
-In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage},
-as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.
+Applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage} and our $\QPIP_0$ protocol $\PiSampZ$ from \Cref{proto:QPIP0samp} for $\SampBQP$ yields the first constant-round blind $\QPIP_0$ protocol for $\BQP$ and $\SampBQP$, respectively.
+
+%Our compiler is a straightforward way of achievement blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
+%In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage},
+%as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.
 
@@
 
-\begin{theorem}
-	There exists a blind, constant-round $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness errors.
-\end{theorem}
+\XW{is this formal enough?}
 
-\begin{theorem}
-	There exists a computationally sound, blind, and constant-round $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness errors.
-\end{theorem}
+\begin{cor}
+	Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
+\end{cor}
+
+\begin{cor}
+		Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
+		%There exists a computationally sound, blind, and constant-round $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness errors under the QLWE assumption.
+\end{cor}

### 2020-04-16 introduction.tex
Sync with local for macro changes

@@
 be efficiently verified by classical human being? 
-This seemingly paradox has been one of the central problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}. 
+This seeming paradox has been one of the central problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}. 
 From a philosophical point of view, this question is also known to have a fascinating connection to the \emph{falsifiability} of quantum mechanics in the potential high complexity regime~\cite{survey:AV12}.
@@
 In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations. 
-The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,PR:FitKas17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
+The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,FK17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
 The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
@@
 With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
-We observe that the \emph{sampling} version of $\BQP$ (e.g., the $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
+We first observe that the \emph{sampling} version of $\BQP$ (e.g., the class $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
 Philosophically, the outcomes of quantum mechanical experiments are usually samples or statistical information, which is well demonstrated in the famous double-slit experiment. 
 Moreover, a lot of quantum algorithms from Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component.
-The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones strengthens the importance of $\SampBQP$. 
-Even though the relation between $\BQP$ and $\SampBQP$ is relatively understood in the plain model, what are the potential technical challenges raised by their subtle differences in the context of CVQC and how to resolve them is however far from clear.
-In particular, it is a prior unclear whether it is feasible to develop a CVQC protocol for $\SampBQP$ based on Mahadev's technique~\cite{FOCS:Mahadev18a}.
+The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones strengthens the importance of delegation for quantum sampling problems. 
+ %Even though the relation between $\BQP$ and $\SampBQP$ is relatively understood in the plain model, 
+However, it is far from clear whether the subtle difference between $\BQP$ and its sampling version could lead to 
+technical barrier in the context of CVQC, or 
+ %what are the potential technical challenges raised by their subtle differences in the context of CVQC and how to resolve them is however far from clear. 
+whether one can develop a CVQC protocol for $\SampBQP$ based on Mahadev's technique~\cite{FOCS:Mahadev18a}.
 
@@
 In particular, we demonstrate the feasibility of the classical verification of quantum sampling by 
-constructing a constant-round CVQC protocol for $\SampBQP$. 
+constructing a constant-round CVQC protocol for $\SampBQP$, the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}.
+Formally, $\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine with an inverse polynomial accurate.
+%Namely, $A(x,1^{1/\eps})$ outputs a sample that is $\eps$-close to the distribution $D_x$ in statistical distance.
+%, where given an input $x \in \zo^n$, the goal  
 Our protocol leverages the Hamiltonian model and the computational X-Z measurement from~\cite{FOCS:Mahadev18a}.
-However, a significant amount of new techniques have been developed to deal with the difference between $\SampBQP$ and $\BQP$, which will be highlighted in the technical contribution below. Precisely,
+However, a significant amount of new techniques have been developed to deal with the difference between $\SampBQP$ and $\BQP$, which will be highlighted in the technical contribution section.
+Precisely,
+\begin{theorem}[informal]
+Assuming the QLWE assumption, there exists a four-message CVQC protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
+\end{theorem}
+%\XW{Insert the theorem statement for the first result here! and a pointer!}
 
-\XW{Insert the theorem statement for the first result here!}
+Somewhat surprisingly, our second contribution is a simple yet powerful generic compiler that transforms any CVQC protocol to a blind one while preserving completeness and soundness errors.
+Our construction builds upon another important primitive called the Quantum Fully Homomorphic Encryption (QFHE)~\cite{BJ15, DSS16, LC18, NS18, OTF18, mahadev_qfhe}.
+Intuitively, QFHE allows fully homomorphic operations on encrypted quantum data and thus could be an ideal technical candidate for achieving blindness.
+Indeed, in another paper~\cite{mahadev_qfhe}, Mahadev constructed the first leveled QFHE based on similar techniques and computational assumptions from~\cite{FOCS:Mahadev18a}. 
+The constructed QFHE automatically implies a blind CVQC protocol, however, without verifiability. 
+Extending this protocol with verifiability seems challenging as hinted by failed attempts in~\cite{mahadev_2018}.
+In fact, most existing blind and verifiable CVQC protocols requires a notable amount of efforts in achieving each property respectively.
 
-Blindness Part 
-\begin{itemize}
-    \item Motivating Blindness
-    \item To ADD
-    \item Combine both for the results. 
-\end{itemize}
+We observe that QFHE, especially the one from~\cite{mahadev_qfhe}, can be used to transform any CVQC protocol to a blind one with the same number of round communication, while preserving completeness and soundness error.
+As a result, one can \emph{upgrade} every verifiable CVQC protocol with blindness almost for free with the help of QFHE. 
+Conceptually, we take a very different approach from previous results (e.g.,~\cite{FK17}) which use the blindness as the start point and then work to extend it with verifiability. 
+At a high level, our strategy is to simulate the original CVQC protocol under QFHE per each message. 
+To that end, we do require a special property of QFHE that the classical part of the ciphertext can be operated on separately from the quantum part, which is satisfied by the construction from~\cite{mahadev_qfhe}.
+Our construction makes a modular use of QFHE and only requires a minor technicality in the analysis, which will be explained below. As a result, we obtain
+\begin{theorem}[informal]
+Assuming the QLWE assumption, there exists a protocol compiler that transforms any CVQC protocol $\Pi$ to a CVQC protocol $\Piblind$ that achieve blindness while preserves its round complexity, completeness, and soundness.
+\end{theorem}
 
-Related work
-\begin{itemize}
-    \item Comparison with related works here?
-\end{itemize}
+\XW{theorem statement for the second contribution and pointer}
 
+As a simple corollary of combining both results above, we achieve a constant-round blind CVQC protocol for $\SampBQP$. %with negligible completeness error and statistical soundness.  
+\begin{theorem}[informal]
+		Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
+\end{theorem}
+
+We can also the first blind and constant-round CVQC protocol for $\BQP$ by applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage}.
+
+\begin{theorem}[informal]
+	Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
+\end{theorem}
+
+\XW{here for both $\BQP$ and $\SampBQP$}
+\XW{check the para/terminology here; consider adding a theorem statement,or a pointer to the later section}
+
+To the authors' best knowledge, we are the first to study CVQC protocols for $\SampBQP$ and establish a generic compiler to upgrade CVQC protocols with blindness. 
+Our result also entails a \emph{constant-round} blind and verifiable CVQC protocol for $\BQP$. 
+The closet result to ours is by Gheorghiu and Vidick~\cite{FOCS:GheVid19} which shows such a CVQC protocol for $\BQP$, however, with a polynomial number of rounds. 
+Their protocol was obtained by first constructing a remote state preparation primitive and then combining it with an existing blind and verifiable protocol~\cite{FK17} where the verifier has some limited quantum power.
+Our technical approach is quite different and seems incomparable.
+
+% \XW{any more to say about parameters, techniques?}
+% \XW{anything we want to say about composability?}
+% \Ethan{Last time we checked, Vidick might have better composability since he's got some kind of ideal box and simulator-based proof}
+
+% Related work
+% \begin{itemize}
+%     \item Comparison with related works here?
+% \end{itemize}
 %       \begin{itemize}
@@
 
-\vspace{2mm} \noindent \textbf{Techniques.}
+\vspace{2mm} \noindent \textbf{Techniques.} Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of quantum register in the possession of the classical verifier, or equivalently, the limited quantum computation power of the verifier.
+It is known that $\BQP$ can be efficiently verified by a classical verifier that can perform a single qubit X or Z measurement~\cite{PhysRevA.93.022326, mf16}. 
+Namely, there is a $\QPIP_1$ protocol for $\BQP$. 
+The main contribution of Mahadev~\cite{FOCS:Mahadev18a} can hence be deemed as a way to compile this $\QPIP_1$ protocol into a $\QPIP_0$ protocol (i.e., with a fully classical verifier).
 
-Technical Contribution
-\begin{itemize}
-    \item Technical contribution. 
-    \item 2nd de finetti have independence; but latter, the analysis, computational parallel repetition. 
-    \item TO ADD for both parts. 
-\end{itemize}
+\vspace{2mm} \noindent \textbf{(1) Construction of a $\QPIP_0$ protocol for $\SampBQP$}. 
+We will follow the same road map above (i.e., from $\QPIP_1$ to $\QPIP_0$) for $\SampBQP$.
+However, since there is no existing $\QPIP_1$ protocol for $\SampBQP$, we make original contributions to both steps as follows:
+
+\vspace{2mm} \noindent \emph{$\diamond \, \QPIP_1$ protocol for $\SampBQP$}: We will employ the local Hamiltonian technique~\cite{kitaev2002classical} and its ground state (known as the history state) as a key technical ingredient to certify the $\SampBQP$ circuits.
+However, there are important differences between the cases for $\BQP$ and $\SampBQP$. 
+Recall that the original construction of local Hamiltonian $H$ for $\BQP$ (or $\QMA$) contains two parts $H=H_{\mathrm{circuit}}+ H_{\mathrm{out}}$. 
+Roughly speaking, $H_{\mathrm{circuit}}$ helps guarantee its ground space only contains \emph{valid} history states with correct input and circuit evolution, while $H_{\mathrm{out}}$'s energy encodes the 0/1 output for $\BQP$ circuits.
+Thus, its outcome can be encoded by the \emph{ground energy} of $H$. 
+For $\SampBQP$, one still uses $H_{\mathrm{circuit}}$ to certify the validness of the history state. 
+However, in this case, one needs to measure on the entire final state of the circuit, rather than a single output qubit, 
+which can no longer be encoded solely by the ground energy. 
+Our approach is to have the valid history state lie in the ground space of a different local Hamiltonian different $H'_{\mathrm{circuit}}$ that has a large \emph{spectral} gap between its ground energy and excited ones.
+It is hence guaranteed that any state with close-to-ground energy must also be close to the history state. 
+In other words, a certification of the energy $H'_{\mathrm{circuit}}$ could lead to a certification of the history state. 
+We construct such $H'_{\mathrm{circuit}}$ from $H_{\mathrm{circuit}}$ by using the \emph{perturbation} technique (e.g.,~\cite{kempe_kitaev_regev_2006}) with further restriction to X/Z terms.
+(\Cref{sec:LHXZ}.)
+
+Another high-level difficulty in constructing a $\QPIP_1$ protocol for $\SampBQP$ is due to the distinction between the test part and the output part. 
+Specifically, we will certify the energy of $H'_{\mathrm{circuit}}$ to guarantee the underling state is close to the valid history state. 
+However, this procedure could be vastly different from outputting a sample by measuring the final state of $\SampBQP$ circuits. 
+We design a \emph{cut-and-choose} protocol on multiple copies of the history state for both testing and outputting. 
+We also employ a variant of quantum \emph{de Finetti} theorem~\cite{Brandão2017}
+to prevent potential cheating strategies by entangling different copies of history states. 
+(\Cref{sec:qpip1}.)
+
+\vspace{2mm} \noindent  \emph{$\diamond$ Compile $\QPIP_1$ into $\QPIP_0$}: 
+A naive attempt is to directly apply Mahadev's protocol on the aforementioned $\QPIP_1$ protocol. 
+Unfortunately, the plain version of Mahadev's protocol does not yield favorable parameters by itself. 
+In fact, there are some recent results~\cite{arXiv:AlaChiHun19, arXiv:ChiaChungYam19} that provide a parallel repetition of Mahadev's original protocol for $\BQP$ with 
+much more favorable parameters.
+
+However, we cannot directly make use of these parallel repetition results due to the subtle difference between protocols for $\BQP$ and $\SampBQP$. 
+One of the major difficulties here is still to deal with both the test part and the output part in $\SampBQP$ protocols. 
+However, because we are now in the computational setting, there is no longer any available quantum de Finetti theorem that is usually derived in the information-theoretic setting. 
+We end up of developing a weaker version of parallel repetition result of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}. 
+Due to the nature of parallel repetition in the computational setting, our analysis is much less modular and significantly involved for this part.  
+More intuitions and detailed analysis are given in \Cref{sec:qpip0_all}.
+
+\vspace{2mm} \noindent \textbf{(2) A generic compiler to upgrade $\QPIP_0$ protocols with blindness}.
+At a high-level, the idea is simple: we run the original protocol under a QFHE with the verifier's key.
+Intuitively, this allows the prover to compute his next message under encryption without learning the underlying verifier's message, and hence achieves blindness while preserving the properties of the original protocol.
+One subtlety with this approach is due to the fact that the verifer is classical while the QFHE cipher text could depend on both quantum and classical data. 
+In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm needs to be classical when the underlying message is classical, which is fortunately satisfied by~\cite{mahadev_qfhe}.
+
+A more subtle issue is to preserve the soundness. 
+In particular, compiled protocols with only one-time use of QFHE might (1) leak information about the circuit being evaluated during the homomorphic evaluation of QFHE ciphertexts (i.e., no \emph{circuit privacy});
+or (2) fail to simulate original protocols upon receiving invalid ciphertexts. 
+We address these issues by letting the verifier to switch to a fresh new key for each round of the protocol. 
+Details are given in \Cref{sec:BlindBQP2}.
 
 \vspace{2mm} \noindent \textbf{Open Questions.}
+
 \begin{itemize}

### 2020-04-16 preliminaries.tex
Updates from Overleaf
Sync with local for macro changes

@@
 \section{Preliminaries}
-
-\Ethan{Check that the quantifiers are all there}
 
@@
 For matrix $H$ and subspace $S$, let $H\big|_S=\Pi_S H \Pi_S$, where $\Pi_S$ is the projector onto the subspace $S$.
-For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
+%For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
+
 For $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$,
-we write $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ for the trace distance between $\rho_1$ and $\rho_2$.
+let $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ denote the trace distance between $\rho_1$ and $\rho_2$.
 We say $\rho_1$ and $\rho_2$ are $\eps$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\eps$.
-For two distributions $f_1$ and $f_2$ over the same finite domain $X$, we write $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ for their total variation distance,
+For two distributions $f_1$ and $f_2$ over the same finite domain $X$, let $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ denote their total variation distance,
 and we say $f_1$ and $f_2$ are $\eps$-close if $\norm{f_1-f_2}_{TV}\leq\eps$.
@@
 	A quantum measurement is given by a set of matrices $\set{M_k}$ such that $M_k\geq0$ and $\sum_k M_k=\id$.
-	We associate to any measurement a map $\Lambda(\rho)=\sum_k \tr(M_k\rho)\ket{k}\bra{k}$
-	with $\set{\ket{k}}$ an orthonormal basis.
+	We associate to any measurement a map $\Lambda(\rho)=\sum_k \tr(M_k\rho)\proj{k}$
+	with $\{\ket{k}\}$ an orthonormal basis.
 	This map is also called a \emph{quantum-classical channel}.
@@
 	$Y=\begin{pmatrix}0&-i\\i&0\end{pmatrix}$,
-	$Z=\begin{pmatrix}1&0\\0&-1\end{pmatrix}$
+	$Z=\begin{pmatrix}1&0\\0&-1\end{pmatrix}$.
 \end{definition}
@@
 \subsection{Quantum Prover Interactive Protocols (QPIP)}
-
-\Ethan{TODO, lower priority: define protocols}
 
@@
 \label{def:comp-indis}
-    \Ethan{TODO Mention asymptotic/ensemble. Things should be in terms of $\lambda$. Should also move to other subsections instead, since this is computatational. Maybe move to end of 2.3.}
-	Let $\rho_1,\rho_2\in\cB^n$.
-	We write $\rho_1\approx_{c,\eps}\rho_2$ if $\rho_1$ and $\rho_2$ are \emph{$\eps$-computationally indistinguishable}.
-	That is, for all quantum polynomial-time \hannote{formalize} distinguishers $\mathsf{D}$,
-	$$\abs{\Pr\left[\mathsf{D}(\rho_1)=1\right]-\Pr\left[\mathsf{D}(\rho_2)=1\right]}\leq\eps.$$
+    \Ethan{TODO PROOFREAD ME}
+    Two families of states $\set{\rho_{1,\lambda}}_{\lambda\in\bbN}$ and $\set{\rho_{2,\lambda}}_{\lambda\in\bbN}$ are \emph{$\eps$-computationally indistinguishable} if for all $\BQP$ distinguishers $\mathsf{D}$ and $\lambda\in\bbN$,
+	$$\abs{\Pr\left[\mathsf{D}(\rho_{1,\lambda})=1\right]-\Pr\left[\mathsf{D}(\rho_{2,\lambda})=1\right]}\leq\eps(\lambda).$$
+	We also denote $\eps$-computational indistinguishability by $\rho_{1,\lambda}\approx_{c, \eps}\rho_{2,\lambda}$.
+    We drop the $\eps$ parameter when it is negligible.
+    We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized states as appropriate.
+    We also extend it to distributions by treating them as mixed states.
 \end{definition}
-We extend the notion of computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized outputs as appropriate.
-We also extend it to distributions by treating them as mixed states.
 
@@
 \subsection{Quantum Homomorphic Encryption Schemes}
-
-\def\QHE{\mathsf{QHE}}
-\def\QGen{\mathsf{QHE.Keygen}}
-\def\QEnc{\mathsf{QHE.Enc}}
-\def\QEval{\mathsf{QHE.Eval}}
-\def\QDec{\mathsf{QHE.Dec}}
 
@@
 
-\begin{definition}
+\begin{definition} \label{def:classical-friendly}
 	we call a quantum homomorphic encryption scheme \emph{classical-friendly} if it has the following properties:

### 2020-04-16 qpip.tex
Sync with local for macro changes

@@
 		\item Let $\histpsi{{C'(x)}}$ be the ground state of $H_{C'(x)}$.
-		\item \XW{Let $s\leq 3T+\frac{6T}{\eps}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This is used in de Finetti theorem.
-Btw I forgot to count ancilla, so it wasn't correct before.}
+		\item Let $s\leq 3T+\frac{6T}{\eps}$ be the number of qubits in $\histpsi{C'(x)}$.
+		%Why this number?} \Ethan{This is used in de Finetti theorem. Btw I forgot to count ancilla, so it wasn't correct before.}
 		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
@@
 	\begin{enumerate}
-		\item\label{step:qpip1-state-gen} The honest prover prepares $M=649\frac{T^{41}\lambda^2}{\eps^{51}}$ copies \Ethan{$649=2\times 9\times 6\times 6+1$} of $\histpsi{C'(x)}$ and sends all of it to the verifier qubit-by-qubit.
+		\item\label{step:qpip1-state-gen} The honest prover prepares $M=649\frac{T^{41}\lambda^2}{\eps^{51}}$ copies of $\histpsi{C'(x)}$ and sends all of it to the verifier qubit-by-qubit.
 		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{20}\lambda}{\eps^{24}}$, and $k\xleftarrow{\$}[M]\setminus I$.
@@
 			\item If $i\in I$, run $y_i\leftarrow\cV_{\GS}(\rho_i)$.
-			\item Else if $i=k$, measure the data register \Ethan{Revisit this name.
-Nobody has defined/used this register before.} \XW{this is the Z measurement?} \Ethan{Yeah} of $\rho_i$ under the standard basis and save the outcome as $z$.
+			\item Else if $i=k$, measure the data register 
+			%\Ethan{Revisit this name. Nobody has defined/used this register before.} \XW{this is the Z measurement?} \Ethan{Yeah} 
+			of $\rho_i$ under the computational (i.e., $Z$) basis and save the outcome as $z$.
 			\item Else, discard $\rho_i$.
@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and is statistically sound. \XW{do we want precise error bound?}
+	$\PiSamp$ has negligible completeness error and is statistically sound. 
+	%\XW{do we want precise error bound?}
 \end{thm}
@@
 	Hence $\norm{d - d_\rho}_{TV}\leq\frac{\eps}{2}$, which implies $\norm{(d_\rho, z_{\rho, ideal}) - (d, z_{ideal})}_{TV}$ $\leq$ $\frac{\eps}{2}$.
-	The conclusion then follows from triangle inequality.
+	It then follows from triangle inequality that
+	$\norm{(d, z) - (d, z_{ideal})}_{TV}\leq\eps$.
 \end{prf}

### 2020-04-16 qpip0.tex
Sync with local for macro changes

@@
-\section{Delegation Protocol for Fully Classical Client}
+\section{$\SampBQP$ Delegation Protocol for Fully Classical Client}
+\label{sec:qpip0_all}
 
@@
 
-In this section, we combine \Cref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients.
-To boost its soundness, we need  polynomially many repetitions, so we use results from \cite{parallelrep} to run polynomially many copies in parallel and get a constant-round protocol.
+In this section, we combine the core protocol from \cite{FOCS:Mahadev18a}, which we restate as Protocol~\ref{proto:urmila4}, with \Cref{QPIP1thm} to create a delegation protocol for $\SampBQP$ for fully classical clients.
+A direct composition results in Protocol~\ref{proto:qpip0_naive}.
+However, as we will see in \Cref{sec:urmila4}, Protocol~\ref{proto:urmila4} has a peculiar and weak guarantee, so \Cref{proto:qpip0_naive} don't have any reasonable completeness and soundness.
+To boost the soundness of Protocol~\ref{proto:qpip0_naive}, we run $m=\poly(\lambda)$ copies of Protocol~\ref{proto:qpip0_naive} in parallel and test on $m-1$ copies of them, resulting in Protocol~\ref{proto:QPIP0samp}.
+We use techniques from \cite{parallelrep} to prove that Protocol~\ref{proto:QPIP0samp} has soundness error $1/\sqrt{m}$ in \Cref{thm:qpip0}.
+
+% since Protocol~\ref{proto:urmila4} has a constant soundness error\hannote{too imprecise}\footnote{Protocol~\ref{proto:urmila4} doesn't have a formally defined soundness error.
+But intuitively, the verifier would accept a non-binding result will constant probability.}, Protocol~\ref{proto:qpip0_naive}  also has a constant soundness error, which means the outputted samples have constant computational distance to the ideal distribution, making the result not very useful.
 
@@
 
-\subsection{Mahadev's measurement protocol}
+\subsection{Mahadev's measurement protocol}\label{sec:urmila4}
+
+Before introducing Mahadev's protocol, we introduce a notation.
+
+\begin{definition}[$M_{XZ}(\rho,h)$]
+
+For any natural number $n$, $n$-bit string $h$, and $n$-qubit quantum state $\rho$, consider the following measurement procedure: measure the first qubit of $\rho$ in $X$ basis if $h_1=0$; measure the first qubit of $\rho$ in $Z$ basis if $h_1=1$.
+Measure the second qubit of $\rho$ in $X$ basis if $h_2=0$; measure the second qubit of $\rho$ in $Z$ basis if $h_2=1$.
+Continue qubit-by-qubit until all $n$-qubits of $\rho$ are measured, where $i$-th qubit is measured in $X$ basis if $h_i=0$ and  $i$-th qubit is measured in the $Z$ basis if $h_i=1$.
+
+We denote the $n$-bit random variable corresponding to the measurement results as $M_{XZ}(\rho,h)$.
+
+\end{definition}
 
@@
 The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that lets a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
-Intuitively, the prover commits to a state $\rho$, while
-the verifier chooses a string $h$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit; if $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.
-At the end of $\PiMeasure$, the verifier learns a measurement outcome $M_{XZ}(\rho, h)$.
-We now describe the interface of $\PiMeasure$ while omitting the implementation details.
+Intuitively, the verifier chooses a string $h$ specifying  the measurement he wants to make, and send encoded $h$ to the prover.
+The prover ``commits" to a state $\rho$ with the encoded $h$ and replies.
+The verifier then uniformly chose between have two options: do a \emph{testing round} or do a \emph{Hadamard round}.
+He send his choice between the two to the prover have the  prover reply.
+If the verifier chose testing, he checks the prover's two replies and rejects if he see a inconsistency.
+If the verifier chose the Hadamard round, he calculate $M_{XZ}(\rho,h)$ based on the replies.
+Mahadev~\cite{FOCS:Mahadev18a} proves a ``binding" property of the above protocol: if a prover's strategy would always succeeds on the testing round, then that strategy must binds to a $\rho$, meaning that no matter what $h$ the verifier has picked at the beginning, the verifier can get $M_{XZ}(\rho,h)$  with the same $\rho$ if he had chosen the Hadamard round.
+
+We now formally describe the interface of $\PiMeasure$ while omitting the implementation details.
+
+%  that : if $h_i=0$, he wants a $X$ measurement on $i$-th qubit; if $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.
+% At the end of $\PiMeasure$, the verifier learns a measurement outcome $M_{XZ}(\rho, h)$.
 
@@
 \label{proto:urmila4}
-
-\Ethan{Make sure this has the right tone as an intro/interface and isn't confusing to the uninitiated.}
 
@@
 	\item \label{step:measure3} The verifier samples $c\xleftarrow{\$}\zo$ uniformly at random and sends it to the prover.
-$c=0$ indicates what's called a ``testing round", and $c=1$ indicates a ``Hadamard round".
+$c=0$ indicates a \emph{testing round}, while $c=1$ indicates a \emph{Hadamard round}.
 	\item \label{step:measure4} The prover generates a classical string $a\leftarrow\cPMeasure{4}(pk, c, \sigma)$ and sends it to back to the verifier.
-	\item \label{step:output} If it is a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$, where $o\in\set{\Acc, \Rej}$.
-\Ethan{Just say it's a test that can acc or rej}
+	\item \label{step:output} If it is a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$ where $o\in\set{\Acc, \Rej}$.
 		If it is a Hadamard round ($c=1$), then the verifier generates and outputs $v\leftarrow\cVMeasure{H}(sk, h, y, a)$.
@@
 \label{lem:trivial-4-round-strategy}
-   There exist a prover strategy for $\PiMeasure$ that is accepted with probability $1-\negl(\lambda)$ \Ethan{Changed n to lambda here, see what does it affect} in the testing.
+   There exist a prover strategy for $\PiMeasure$ that is accepted with probability $1-\negl(\lambda)$
 \end{fact}
-
-\Ethan{Introduce $(U_{trivial,0},U_{trivial})$ later corresponding to the ``honest" prover}
 
@@
 				\item The verifier samples $(pk, sk)\leftarrow\cVNaive{1}(1^\lambda, h)$ and sends $pk$ to the prover.
-				\item The prover runs $(y, \sigma)\leftarrow\cPNaive{2}(pk, \rho)$.
+				\item The prover runs $(y, \sigma)\leftarrow\cPNaive{2}(pk, \rho)$ and sends $y$ to the verifier.
 	    			Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but is useful for analysis.
-				\item The verifier samples $c\leftarrow\cVNaive{3}$
+				\item\label{step:c-urmila-in-naive} The verifier samples $c\leftarrow\cVNaive{3}()$  and sends it to the prover.
 				\item The prover replies $a\leftarrow\cPNaive{4}(pk, c, \sigma)$.
@@
 
-Note that in $\PiNaive$ the verifier only learns the output in Hadamard round.
-So $\PiNaive$ is not a $\QPIP_0$ with good completeness or soundness.
-On the other hand, it also has a binding property, which we will use to achieve completeness and soundness in \Cref{sec:qpip0}.
+There are several problems with using $\PiNaive$ as a $\SampBQP$ protocol.
+first, since the verifier don't get a sample if he had chosen the testing round in Step~\ref{step:c-urmila-in-naive}, so the protocol has  completeness error at least $1/2$.
+And since Protocol~\ref{proto:urmila4} does not check anything on the Hadamard round, a cheating prover can give up passing the testing round and breaks the commitment on the Hadamard round.
+Such cheating prover only has constant $1/2$ probability of being caught, resulting in constant soundness error.
+
+% Note that in $\PiNaive$ the verifier only learns the output in Hadamard round.
+% So $\PiNaive$ is not a $\QPIP_0$ with good completeness or soundness.
+
+On the other hand, \Cref{proto:qpip0_naive} has a binding property like \Cref{proto:urmila4}, which we will use to achieve completeness and soundness in \Cref{sec:qpip0}.
 
@@
 	For the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
-	If $y\ne\bot$, then reply $y$.
-	Else run the corresponding step of the dummy strategy as in \Cref{lem:trivial-4-round-strategy} and reply with its results.
-	For the fourth message, if $y\ne\bot$, run and reply with $a\leftarrow\cPNaiveStar{4}(pk, c, \sigma)$.
-	If $y=\bot$ and $c=0$, continue the dummy strategy.
+	If $y\ne\bot$, then reply $y$;
+	else, run the corresponding step of the dummy strategy as in \Cref{lem:trivial-4-round-strategy} and reply with its results.
+	For the fourth message, if $y\ne\bot$, run and reply with $a\leftarrow\cPNaiveStar{4}(pk, c, \sigma)$;
+	else, continue the dummy strategy.
 
-	Observe that this $\Pstar$ indeed passes testing round with overwhelming probability by construction.
-	So we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property.
-	Combining it with $\PiSamp$'s soundness,
-	we see that the verifier's outputs corresponding $\Pstar$, $(d', z')$ is computationally indistinguishable to some $(d', z_{ideal}')$
+	Observe that this $\Pstar$ passes testing round with overwhelming probability by construction,
+	so we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property (\Cref{lem:urmila-binding}).
+	That is, there exists some $\rho$ such that $v=M_{XZ}(\rho, h)$.
+	Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}),
+	we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\varepsilon}, x)$ is computationally indistinguishable to $(d', z_{ideal}')$.
 
+    Now we relate $(d', z')$ back to $(d, z)$.
 	Conditioned on $\PNaiveStar$ accept, clearly $(d, z)=(d', z')$.
-	On $\PNaiveStar$ reject, since dummy strategy will be rejected with overwhelming probability in Hadamard round, \Ethan{kinda obvious but we never explicitly explained why}
-	we also have $(d, z)=(\Rej, \bot)\approx_{c, \negl(\lambda)}(d', z')$
-
-	The conclusion follows from a simple hybrid argument.
+	Conditioned on $\PNaiveStar$ reject, since dummy strategy will be rejected with high probability in Hadamard round, \Ethan{kinda obvious but we never explicitly explained why}
+	we have $(d', z')\approx_{c, O(\eps)}(\Rej, \bot)=(d, z)$.
+	So we have $(d, z)\approx_{c, O(\varepsilon)}(d', z')\approx_{c, \negl(\lambda)}(d', z_{ideal}')$,
+	which in turn implies $\abs{d-d'}\leq O(\eps)$
+    and $(d, z_{ideal})\approx_{c, O(\eps)}(d', z_{ideal}')$.
+    Combining everything, we conclude that $(d, z)\approx_{c, O(\eps)}(d, z_{ideal})$.
 \end{proof}
@@
 It is essentially a $m$-fold parallel repetition of $\PiNaive$.
-However, instead of choosing whether to run test or Hadamard round randomly each round,
-we run $m-1$ test rounds and only one Hadamard round.
-In the description of our protocol below, we expand out the uses of $\PiNaive$ and $\PiMeasure$ in order to introduce notations that we need in our analysis.
+Instead of having each copies running testing round or Hadamard round uniformly at random, we randomly pick one copy to run Hadamard round to get our samples, and run testing round on all other $m-1$ copies.
+In the description of our protocol below, we describe $\PiNaive$ and $\PiMeasure$ in details  in order to introduce notations that we need in our analysis.
 
@@
 	\item \label{step:multi-testing}
-		The verifier computes the outcome for each round as in \stepref{output} of $\PiMeasure$.
+		The verifier computes the outcome for each round as in \stepref{naive-output} of $\PiNaive$.
 		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
@@
 
-\Ethan{TODO Fix proof notations. Like U0, U notations might've been undefined; copy from parallel rep paper if needed}
-
 \begin{theorem}\label{thm:qpip0}
-	$\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(\lambda)$ completeness error and computational soundness. 
+	Assuming the QLWE assumption, $\PiSampZ$ is a $\QPIP_0$ protocol for all problems in $\SampBQP$ with negligible  completeness error and computational soundness. 
 \end{theorem}
@@
 send something not binding in the Hadamard round copy, he would be caught with probability $1-1/m$.
-However, the prover is quantum, so he might create quantum correlations that let him cheat with probability more than $1/m$.
-To prove that such kind of cheating is impossible, we use the following partition lemma from \cite{parallelrep}, which intuitively says that there exist efficient projectors $G_{0,i}$ and $G_{1,i}$ which splits a quantum state in the prover's   internal space into a part that is rejected with high probability in the testing round of $i$-th copy and a part that is accepted with high probability.
-$G_{0,i}$ and $G_{1,i}$ need to be efficient because $\PiMeasure$ only gives computational indistinguishability.
+However, the prover might create correlations between copies that let him cheat with probability much higher than $1/m$.
+This is a common problem in trying to create parallel repetition protocols.
+We are able to bound the soundness error as $O(1/\sqrt{m})$.
+To prove that, we use the following partition lemma from \cite{parallelrep}, which intuitively says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
+$G_{0,i}$ represents the subspace that are rejected with high probability in the testing round of $i$-th copy; $G_{1,i}$  represents the subspace accepted with ``high probability"\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
+$G_{0,i}$ and $G_{1,i}$ need to be efficient because $\PiMeasure$ only gives computational security.
 Once we have $G_{0,i}$ and $G_{1,i}$, we can split up the prover's internal state $\ket{\psi}$ like conditional probabilistic events.
-For example, $G_{0,3} G_{1,5} \ket{\psi}$ corresponds to the events of passing the testing round on fifth copy then fails the the testing round on the third copy.
-We split the state sub-normalized states corresponding to the prover cheating on different copies and show that the sum of probabilities corresponding to bad states can't be more than $1/m$.
+We  split up  $\ket{\psi}$ into $G_{0,1}\ket{\psi}+ G_{0,2}G_{1,1}\ket{\psi} + G_{0,3}G_{1,2}G_{1,1}\ket{\psi} + \dots +  G_{0,m} G_{1,m-1}\dots G_{1,2}G_{1,1}\ket{\psi} + G_{1,m} G_{1,m-1}\dots G_{1,2}G_{1,1}\ket{\psi}$, where for example, $G_{0,2}G_{1,1}\ket{\psi}$ intuitively corresponds to passing the testing round of the first copy then getting rejected on the testing round of the second copy.
+Since each of the  substates in  $\{G_{0,1}\ket{\psi}, G_{0,2}G_{1,1}\ket{\psi} , G_{0,3}G_{1,2}G_{1,1}\ket{\psi} , \dots ,  G_{0,m} G_{1,m-1}\dots G_{1,2}G_{1,1}\ket{\psi} \}$ all have  probability $1-1/m$ of being caught by one of the $m-1$ testing rounds, they have well-bounded
+ probability of being accepted in Step~\ref{step:multi-testing} of Protocol~\ref{proto:QPIP0samp}, so the output in  Step~\ref{step:multi-testing} would mostly corresponds to $G_{1,m} G_{1,m-1}\dots G_{1,2}G_{1,1}\ket{\psi}$.
+However, since $G_{1,i}$ don't commute with $G_{1,j}$, $G_{1,m} G_{1,m-1}\dots G_{1,2}G_{1,1}\ket{\psi}$ is only binding for the $m$-th copy, so this simplified strategy is not quite correct.
+We were able to fix this issue with a more careful split up of $\ket{\psi}$.
+Also as a careful reader might have noticed, the prover's space don't happen to split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
+In \cite{parallelrep} this is solved by doing eigenvalue estimation to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
+However, states with accept probability really close to the threshold $\gamma$ can not be classified, so we need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.
+
+ %but there will always be some states  herefore we introduce  an extra parameter $\gamma$ that corresponds to the probability cut-off line that to distinguish the accepted and rejected part, and we need to average over $\gamma$.
+
+% We split the state sub-normalized states corresponding to the prover cheating on different copies and show that the sum of probabilities corresponding to bad states can't be more than $1/m$.
 {The actual proof is more complicated than this sketch because the $G$'s don't commute with each other, so we need to handle the splitting carefully.}
+
+%For example, $G_{0,3} G_{1,5} \ket{\psi}$ corresponds to the events of passing the testing round on fifth copy then fails the the testing round on the third copy.
 
@@
 Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=\poly(\eps)$ and $T=1/\poly(\eps)$.
-\Ethan{These $n$ probably should be $\lambda$}
 
@@
 
-where $P_{i,pk_i,y_i,acc}$ are projector to the states that $i$-th testing round accepts with $pk_i,y_i$, including the last measurement the prover did before sending $\{a\}$.
+where $P_{i,pk_i,y_i,acc}$ are projector to the states that $i$-th testing round accepts with $pk_i,y_i$, including the last measurement the prover did before sending $\vec{a}$.
 This means that $\ket{\psi_{0,i,\gamma}}$ is rejected by $i$-th testing round with high probability.
@@
 
-\Ethan{This proof currently only shows $O(\eps)$ accuracy, which doesn't perfectly match up with the definition. Hopefully doesn't matter way too much though?}
-
 Completeness is trivial.
@@
 $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}G_{d_{k-1},k-1,\gamma}\cdots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$
-
-\Ethan{ew.}
 
@@
 $$P_{acc,i,z}.$$
-Note that $P_{acc,i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $a$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
+Note that $P_{acc,i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $\vec{a}$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
 
@@
 The prover then picks a uniformly random $\gamma$ and  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
+If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything aborts by sending $\bot$ back.
+On the fourth round,  If it's a testing round the prover reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}.
+If it's the Hadamard round  the prover  runs $U$ and check whether every copy except the $i$-th copy would be accepted.
+If all $m-1$ copies accepts, he reply with the $i$-th copy, otherwise reply $\bot$.
+
+%old protocol when jerection on 4-th round
+% The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of Protocol~\ref{proto:urmila4} in Protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
+The prover then picks a uniformly random $\gamma$ and  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
 If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead.
@@
 
-By Lemma~\ref{lem:trivial-4-round-strategy} and property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when $c=0$.
+By  property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort.
 Since the prover's strartegy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
@@
 % \hannote{do we lose a factor of $m$?}
-Recall that by Eq~\ref{eq:z-z-good} we have $\norm{z-z_{good}}_1 \leq \eps$ if we pick $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$, which implies 
+Recall that by Eq~\ref{eq:z-z-good} we have $\norm{z-z_{good}}_1 \leq O(\eps)$ if we pick $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$, which implies 
 \begin{align}

### 2020-04-16 qpip0.tex

@@
 The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that lets a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
-Intuitively, the verifier chooses a string $h$ specifying  the measurement he wants to make, and send encoded $h$ to the prover.
+Intuitively, the verifier chooses a string $h$ specifying  the measurement he wants to make, and sends encoded $h$ to the prover.
 The prover ``commits" to a state $\rho$ with the encoded $h$ and replies.
-The verifier then uniformly chose between have two options: do a \emph{testing round} or do a \emph{Hadamard round}.
-He send his choice between the two to the prover have the  prover reply.
-If the verifier chose testing, he checks the prover's two replies and rejects if he see a inconsistency.
-If the verifier chose the Hadamard round, he calculate $M_{XZ}(\rho,h)$ based on the replies.
+The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}.
+He sends his choice between the two to the prover and has the  prover reply.
+If the verifier chose testing, he checks the prover's two replies and rejects if he sees an inconsistency.
+If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho,h)$ based on the replies.
 Mahadev~\cite{FOCS:Mahadev18a} proves a ``binding" property of the above protocol: if a prover's strategy would always succeeds on the testing round, then that strategy must binds to a $\rho$, meaning that no matter what $h$ the verifier has picked at the beginning, the verifier can get $M_{XZ}(\rho,h)$  with the same $\rho$ if he had chosen the Hadamard round.
@@
 $c=0$ indicates a \emph{testing round}, while $c=1$ indicates a \emph{Hadamard round}.
-	\item \label{step:measure4} The prover generates a classical string $a\leftarrow\cPMeasure{4}(pk, c, \sigma)$ and sends it to back to the verifier.
+    \item \label{step:measure4} The prover generates a classical string $a\leftarrow\cPMeasure{4}(pk, c, \sigma)$ and sends it back to the verifier.
     \item \label{step:output} If it is a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$ where $o\in\set{\Acc, \Rej}$.
@@
     Then, under the QLWE assumption, there exists some $\rho$ so that for all $h$,
-	the verifier's outputs on the Hadamard round is $\negl(\lambda)$-computationally indistinguishable from $M_{XZ}(\rho, h)$.
+    The verifier's output on the Hadamard round is $\negl(\lambda)$-computationally indistinguishable from $M_{XZ}(\rho, h)$.
 \fi
@@
 There are several problems with using $\PiNaive$ as a $\SampBQP$ protocol.
-first, since the verifier don't get a sample if he had chosen the testing round in Step~\ref{step:c-urmila-in-naive}, so the protocol has  completeness error at least $1/2$.
+first, since the verifier doesn't get a sample if he had chosen the testing round in Step~\ref{step:c-urmila-in-naive}, so the protocol has  completeness error at least $1/2$.
 And since Protocol~\ref{proto:urmila4} does not check anything on the Hadamard round, a cheating prover can give up passing the testing round and breaks the commitment on the Hadamard round.
-Such cheating prover only has constant $1/2$ probability of being caught, resulting in constant soundness error.
+Such cheating prover only has a constant $1/2$ probability of being caught, resulting in constant soundness error.
 
-% Note that in $\PiNaive$ the verifier only learns the output in Hadamard round.
+% Note that in $\PiNaive$ the verifier only learns the output in the Hadamard round.
 % So $\PiNaive$ is not a $\QPIP_0$ with good completeness or soundness.
@@
 It is essentially a $m$-fold parallel repetition of $\PiNaive$.
-Instead of having each copies running testing round or Hadamard round uniformly at random, we randomly pick one copy to run Hadamard round to get our samples, and run testing round on all other $m-1$ copies.
+Instead of having each copy running testing round or Hadamard round uniformly at random, we randomly pick one copy to run Hadamard round to get our samples, and run testing round on all other $m-1$ copies.
 In the description of our protocol below, we describe $\PiNaive$ and $\PiMeasure$ in details  in order to introduce notations that we need in our analysis.
@@
         \item Security parameter $1^\lambda$ for $\lambda\in\bbN$.
-		\item Accuracy paramter $1^{1/\eps}$ for the $\SampBQP$ instance
+        \item Accuracy parameter $1^{1/\eps}$ for the $\SampBQP$ instance
         \item Input $x\in\zo^{\poly(\lambda)}$ for the $\SampBQP$ instance
@@
 
-Ingrediant: Let $m=O(1/\eps^2)$ be the number of parallel repetitions to run.
+Ingredient: Let $m=O(1/\eps^2)$ be the number of parallel repetitions to run.
 
@@
 
-The intuition behind this theorem is that the we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
-Therefore if the prover want to cheat, i.e.
+The intuition behind this theorem is that we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
+Therefore if the prover wants to cheat, i.e.
 send something not binding in the Hadamard round copy, he would be caught with probability $1-1/m$.
@@
 We were able to fix this issue with a more careful split up of $\ket{\psi}$.
-Also as a careful reader might have noticed, the prover's space don't happen to split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
+Also as a careful reader might have noticed, the prover's space doesn't happen to split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
 In \cite{parallelrep} this is solved by doing eigenvalue estimation to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
@@
 
- %but there will always be some states  herefore we introduce  an extra parameter $\gamma$ that corresponds to the probability cut-off line that to distinguish the accepted and rejected part, and we need to average over $\gamma$.
+ %but there will always be some states  therefore we introduce  an extra parameter $\gamma$ that corresponds to the probability cut-off line that to distinguish the accepted and rejected part, and we need to average over $\gamma$.
 
@@
 
-%For example, $G_{0,3} G_{1,5} \ket{\psi}$ corresponds to the events of passing the testing round on fifth copy then fails the the testing round on the third copy.
+%For example, $G_{0,3} G_{1,5} \ket{\psi}$ corresponds to the events of passing the testing round on the fifth copy then fails the testing round on the third copy.
 
@@
 where $P_{i,pk_i,y_i,acc}$ are projector to the states that $i$-th testing round accepts with $pk_i,y_i$, including the last measurement the prover did before sending $\vec{a}$.
-This means that $\ket{\psi_{0,i,\gamma}}$ is rejected by $i$-th testing round with high probability.
+This means that $\ket{\psi_{0,i,\gamma}}$ is rejected by the $i$-th testing round with high probability.
 
@@
 %   \end{align*}
-This will imply that    $\ket{\psi_{1,i,\gamma}}$ is binding to $i$-th Hadamard round.
+This will imply that    $\ket{\psi_{1,i,\gamma}}$ is binding to the $i$-th Hadamard round.
 
@@
 %\hannote{Note that the prover's state is actually a mixed state.
-In particular, $\ket{\psi}$ depends on $pk$ and we are considering the mixed state averaged over verifier's choice of $pk$.}
+In particular, $\ket{\psi}$ depends on $pk$ and we are considering the mixed state averaged over the verifier's choice of $pk$.}
 
@@
 
-We now proceeds to prove that $z_{good}$ is close to the ideal distribution.
+We now proceed to prove that $z_{good}$ is close to the ideal distribution.
 
@@
 The prover then picks a uniformly random $\gamma$ and  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
-If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything aborts by sending $\bot$ back.
+If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and aborts by sending $\bot$ back.
 On the fourth round,  If it's a testing round the prover reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}.
-If it's the Hadamard round  the prover  runs $U$ and check whether every copy except the $i$-th copy would be accepted.
-If all $m-1$ copies accepts, he reply with the $i$-th copy, otherwise reply $\bot$.
+If it's the Hadamard round  the prover  runs $U$ and checks whether every copy except the $i$-th copy would be accepted.
+If all $m-1$ copies are accepted, he replies with the $i$-th copy, otherwise reply $\bot$.
 
@@
 By  property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort.
-Since the prover's strartegy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
+Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
 \begin{align}

### 2020-04-16 blind.tex
Remove duplicate references

@@
 
-Applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage} and our $\QPIP_0$ protocol $\PiSampZ$ from \Cref{proto:QPIP0samp} for $\SampBQP$ yields the first constant-round blind $\QPIP_0$ protocol for $\BQP$ and $\SampBQP$, respectively.
+Applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19} and our $\QPIP_0$ protocol $\PiSampZ$ from \Cref{proto:QPIP0samp} for $\SampBQP$ yields the first constant-round blind $\QPIP_0$ protocol for $\BQP$ and $\SampBQP$, respectively.
 
 %Our compiler is a straightforward way of achievement blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
-%In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage},
+%In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19},
 %as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.

### 2020-04-16 introduction.tex
Updates from Overleaf
Remove duplicate references

@@
 
-We can also the first blind and constant-round CVQC protocol for $\BQP$ by applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage}.
+We can also the first blind and constant-round CVQC protocol for $\BQP$ by applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19}.
 

### 2020-04-16 qpip0.tex
Remove duplicate references

--- 2020-04-16 qpip0.tex
@@
 To boost the soundness of Protocol~\ref{proto:qpip0_naive}, we run $m=\poly(\lambda)$ copies of Protocol~\ref{proto:qpip0_naive} in parallel and test on $m-1$ copies of them, resulting in Protocol~\ref{proto:QPIP0samp}.
-We use techniques from \cite{parallelrep} to prove that Protocol~\ref{proto:QPIP0samp} has soundness error $1/\sqrt{m}$ in \Cref{thm:qpip0}.
+We use techniques from \cite{arXiv:ChiaChungYam19} to prove that Protocol~\ref{proto:QPIP0samp} has soundness error $1/\sqrt{m}$ in \Cref{thm:qpip0}.
 
@@
 We are able to bound the soundness error as $O(1/\sqrt{m})$.
-To prove that, we use the following partition lemma from \cite{parallelrep}, which intuitively says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
+To prove that, we use the following partition lemma from \cite{arXiv:ChiaChungYam19}, which intuitively says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
 $G_{0,i}$ represents the subspace that are rejected with high probability in the testing round of $i$-th copy; $G_{1,i}$  represents the subspace accepted with ``high probability"\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
@@
 Also as a careful reader might have noticed, the prover's space don't happen to split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
-In \cite{parallelrep} this is solved by doing eigenvalue estimation to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
+In \cite{arXiv:ChiaChungYam19} this is solved by doing eigenvalue estimation to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
 However, states with accept probability really close to the threshold $\gamma$ can not be classified, so we need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.
@@
 %Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
-\begin{lemma}[partition lemma; revision of Lemma 3.5 of \cite{parallelrep}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{parallelrep} and post-select on the $th$ register being $0$ or $1$ then discard $ph,th,in$.
+\begin{lemma}[partition lemma; revision of Lemma 3.5 of \cite{arXiv:ChiaChungYam19}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{arXiv:ChiaChungYam19} and post-select on the $th$ register being $0$ or $1$ then discard $ph,th,in$.
 Property~\ref{property:partition-err} corresponds to Property~1.

### 2020-04-16 qpip0.tex

--- 2020-04-16 qpip0.tex
@@
 
-The intuition behind this theorem is that we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
-Therefore if the prover wants to cheat, i.e.
+The intuition behind this theorem is that the we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
+Therefore if the prover want to cheat, i.e.
 send something not binding in the Hadamard round copy, he would be caught with probability $1-1/m$.
@@
 We were able to fix this issue with a more careful split up of $\ket{\psi}$.
-Also as a careful reader might have noticed, the prover's space doesn't happen to split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
-In \cite{parallelrep} this is solved by doing eigenvalue estimation to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
+Also as a careful reader might have noticed, the prover's space don't happen to split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
+In \cite{arXiv:ChiaChungYam19} this is solved by doing eigenvalue estimation to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
 However, states with accept probability really close to the threshold $\gamma$ can not be classified, so we need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.

### 2020-04-16 blind.tex
Updates from Overleaf

--- 2020-04-16 blind.tex
@@
 
-\XW{is this formal enough?}
+\begin{thm}
+	Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
+\end{thm}
 
-\begin{cor}
-	Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
-\end{cor}
-
-\begin{cor}
+\begin{thm}
 		Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
 		%There exists a computationally sound, blind, and constant-round $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness errors under the QLWE assumption.
-\end{cor}
+\end{thm}

### 2020-04-16 introduction.tex
Updates from Overleaf

--- 2020-04-16 introduction.tex
@@
 %           \item all previous either quantum clients, or at least 2 provers.
-%           \item the following for blindess
+%           \item the following for blindness
 %           \item Mahadev in her thesis~\cite{mahadev_2018} discussed a bit about the relation between verifiability and blindness.
@@
 Can quantum computation, with potential computational advantages that are intractable for classical computers,
-be efficiently verified by classical human being? 
+be efficiently verified by classical human beings?
 This seeming paradox has been one of the central problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}.
@@
 
-With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
+With the newly developed techniques, we revisit the classical verification of quantum computation problems from both a philosophical and a practical point of view.
 We first observe that the \emph{sampling} version of $\BQP$ (e.g., the class $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
@@
 Extending this protocol with verifiability seems challenging as hinted by failed attempts in~\cite{mahadev_2018}.
-In fact, most existing blind and verifiable CVQC protocols requires a notable amount of efforts in achieving each property respectively.
+In fact, most existing blind and verifiable CVQC protocols require a notable amount of effort in achieving each property respectively.
 
@@
 \begin{theorem}[informal]
-Assuming the QLWE assumption, there exists a protocol compiler that transforms any CVQC protocol $\Pi$ to a CVQC protocol $\Piblind$ that achieve blindness while preserves its round complexity, completeness, and soundness.
+Assuming the QLWE assumption, there exists a protocol compiler that transforms any CVQC protocol $\Pi$ to a CVQC protocol $\Piblind$ that achieves blindness while preserves its round complexity, completeness, and soundness.
 \end{theorem}
 
-\XW{theorem statement for the second contribution and pointer}
+%\XW{theorem statement for the second contribution and pointer}
 
@@
 
-\XW{here for both $\BQP$ and $\SampBQP$}
-\XW{check the para/terminology here; consider adding a theorem statement,or a pointer to the later section}
+%\XW{here for both $\BQP$ and $\SampBQP$}
+%\XW{check the para/terminology here; consider adding a theorem statement,or a pointer to the later section}
 
@@
 Our result also entails a \emph{constant-round} blind and verifiable CVQC protocol for $\BQP$.
-The closet result to ours is by Gheorghiu and Vidick~\cite{FOCS:GheVid19} which shows such a CVQC protocol for $\BQP$, however, with a polynomial number of rounds. 
+The closest result to ours is by Gheorghiu and Vidick~\cite{FOCS:GheVid19} which shows such a CVQC protocol for $\BQP$, however, with a polynomial number of rounds.
 Their protocol was obtained by first constructing a remote state preparation primitive and then combining it with an existing blind and verifiable protocol~\cite{FK17} where the verifier has some limited quantum power.
@@
 %
-%           technical comparison with the past parallel % reptiton. 
+%           technical comparison with the past parallel % repetition.
 %           \item
@@
 Thus, its outcome can be encoded by the \emph{ground energy} of $H$.
-For $\SampBQP$, one still uses $H_{\mathrm{circuit}}$ to certify the validness of the history state. 
+For $\SampBQP$, one still uses $H_{\mathrm{circuit}}$ to certify the validity of the history state.
 However, in this case, one needs to measure on the entire final state of the circuit, rather than a single output qubit,
 which can no longer be encoded solely by the ground energy.
-Our approach is to have the valid history state lie in the ground space of a different local Hamiltonian different $H'_{\mathrm{circuit}}$ that has a large \emph{spectral} gap between its ground energy and excited ones.
+Our approach is to have the valid history state lie in the ground space of a different local Hamiltonian $H'_{\mathrm{circuit}}$  that has a large \emph{spectral} gap between its ground energy and excited ones.
 It is hence guaranteed that any state with close-to-ground energy must also be close to the history state.
@@
 Another high-level difficulty in constructing a $\QPIP_1$ protocol for $\SampBQP$ is due to the distinction between the test part and the output part.
-Specifically, we will certify the energy of $H'_{\mathrm{circuit}}$ to guarantee the underling state is close to the valid history state. 
+Specifically, we will certify the energy of $H'_{\mathrm{circuit}}$ to guarantee the underlying state is close to the valid history state.
 However, this procedure could be vastly different from outputting a sample by measuring the final state of $\SampBQP$ circuits.
@@
 However, because we are now in the computational setting, there is no longer any available quantum de Finetti theorem that is usually derived in the information-theoretic setting.
-We end up of developing a weaker version of parallel repetition result of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}. 
+We end up developing a weaker version of parallel repetition result of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}.
 Due to the nature of parallel repetition in the computational setting, our analysis is much less modular and significantly involved for this part.  
@@
 Intuitively, this allows the prover to compute his next message under encryption without learning the underlying verifier's message, and hence achieves blindness while preserving the properties of the original protocol.
-One subtlety with this approach is due to the fact that the verifer is classical while the QFHE cipher text could depend on both quantum and classical data. 
+One subtlety with this approach is due to the fact that the verifier is classical while the QFHE cipher text could depend on both quantum and classical data.
 In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm needs to be classical when the underlying message is classical, which is fortunately satisfied by~\cite{mahadev_qfhe}.
@@
 or (2) fail to simulate original protocols upon receiving invalid ciphertexts.
-We address these issues by letting the verifier to switch to a fresh new key for each round of the protocol. 
+We address these issues by letting the verifier switch to a fresh new key for each round of the protocol.
 Details are given in \Cref{sec:BlindBQP2}.
 
-\vspace{2mm} \noindent \textbf{Open Questions.}
+\vspace{2mm} \noindent \textbf{Open Questions.} Our main focus is on the feasibility of the desired functionality and properties, which nevertheless leaves a big room for the improvement of efficiency.
+Some of our parameter dependence inherits from previous works (e.g.~\cite{FOCS:Mahadev18a}), whereas some is due to our own construction. 
+It will be extremely interesting to improve the parameter dependence with potentially new techniques.
 
-\begin{itemize}
-    \item Open questions, and also explain for some associated high-cost. specifically 
-    \item T dependence. In general, improve the efficiency.  
-    \item negligible soundness error.  compare with classical? what's the state-of-the art. 
-\end{itemize}
+% \begin{itemize}
+%     \item Open questions, and also explain for some associated high-cost. specifically
+%     \item T dependence. In general, improve the efficiency.  
+%     \item negligible soundness error.  compare with classical? what's the state-of-the art.
+% \end{itemize}
 
@@
 Simply measuring the entire output register instead is difficult to analyze.
-For decision problems, it’s not hard to argue that a malicious prover cannot do better than sending identical copies of some pure state unentangled with each others.
+For decision problems, it’s not hard to argue that a malicious prover cannot do better than sending identical copies of some pure state unentangled with each other.
 That same reasoning doesn't apply here a priori.

### 2020-04-16 preliminaries.tex

@@
 
+\begin{remark} Note that we do not parameterize the soundness error in Definition \ref{dfn:stats-secure-proto-sampbqp}.
+This is because the definition of $\SampBQP$ already includes an error parameter $\eps$, where the algorithm is allowed to generate a sample with statistical error up to $\eps$ in time polynomial in $1/\eps$.
+Hence, in our definition of soundness, we allow the verifier's output to have error $\eps$ for any given inverse polynomial $\eps$.
+\end{remark}
+
 We now define blindness of a protocol.
@@
 
-\begin{definition}
+\begin{definition}[Blindness]
 	Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ (and $1^{1/\eps}$ for the case of $\SampBQP$ problem), and verifier's private input $x\in\zo^*$.

### 2020-04-16 blind.tex
Sync with local to fix smart quotes

@@
 
-To resolve the issue, we let the verifier to switch to a fresh new key for each round of the protocol.
+To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol.
 For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext \Ethan{Need to mention somewhere that if $\QDec$ fails, it outputs $\bot$ instead of aborting}, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$.
-Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoid the issue of circuit privacy.
+Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoids the issue of circuit privacy.
 Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it to $\Pblind$.
@@
 By doing so, we show that for any cheating prover $\Pblindstar$, the interaction $(\Pblindstar, \Vblind)$ indeed simulates a valid interaction of $(\Pstar, V)$ for some cheating $\Pstar$, and hence the soundness of $\Pi$ implies the soundness of the compiled protocol.
+Finally, for the issue of the prover sending invalid ciphertext, we can assume without loss of generality that the decryption
 
@@
 
-Here we present our compiler on $\QPIP_0$ protocols that can be used to achieves blindness.
+Here we present our compiler on $\QPIP_0$ protocols that can be used to achieve blindness.
 The high level idea is to run the protocol under homomorphic encryption.
@@
 However, it is difficult to prove the soundness this way because homomorphic encryption schemes doesn't guarantee circuit privacy;
-the server could learn about ther client's coins.
+the server could learn about its client's coins.
 Furthermore, the prover would also be allowed to send invalid ciphertexts...?
@@
 So instead we let the verifier decrypt every round.
-Then, in order the preserve blindness, the verifier generates a new set of keys for every message it sends to the prover...
+Then, in order to preserve blindness, the verifier generates a new set of keys for every message it sends to the prover...
 Which results in the following protocol.
@@
 
-%\Ethan{General comment: Make story more interesting. Clearly claim our own contributions.}
+%\Ethan{General comment: Make the story more interesting. Clearly claim our own contributions.}
 
-\KM{notation inconsistency...}
-
-We proceeds to present our compiler. We start by introducing the notation of a $\QPIP_0$ protocol $\Pi$ as follows.
+We proceed to present our compiler. We start by introducing the notation of a $\QPIP_0$ protocol $\Pi$ as follows.
 % We now state our compiler that gives any $\QPIP_0$ protocol blindness.
@@
 
-\begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ correponding to $\Pi_0$}
+\begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ corresponding to $\Pi_0$}
     Inputs:
@@
 
-	Ingrediants:
+    Ingredients:
     \begin{itemize}
@@
     By a standard hybrid argument, we observe that $\Hyb_1^x$ is computationally indistinguishable with $\Hyb_{T+1}^x$.
-	We use the the same argument for the computational indistinguishability between $\Hyb_1^0$ and $\Hyb_{T+1}^0$.
+    We use the same argument for the computational indistinguishability between $\Hyb_1^0$ and $\Hyb_{T+1}^0$.
     We conclude that $P^*$ cannot distinguish between $\Hyb_{T+1}^x$ and $\Hyb_{T+1}^0$,
@@
 
-%Our compiler is a straightforward way of achievement blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
+%Our compiler is a straightforward way of achieving blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
 %In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19},

### 2020-04-16 hamiltonian.tex
Change epsilon font
Sync with local for macro changes
Sync with local to fix smart quotes

@@
 
-\def \Hin {H_{\mathrm{in}}}
-\def \Hout {H_{\mathrm{out}}}
-\def \Hprop {H_{\mathrm{prop}}}
-\def \Hclock {H_{\mathrm{clock}}}
-\def \Jclock {J_{\mathrm{clock}}}
-\def \Jprop {J_{\mathrm{prop}}}
-\def \Kin {K_{\mathrm{in}}}
-\def \Kclock {K_{\mathrm{clock}}}
-\def \Kprop {K_{\mathrm{prop}}}
-
-\newcommand{\histpsi}[1]{\ket{\psi_{#1}^{\mathrm{hist}}}}
-\newcommand{\LHXZ}[1]{\mathrm{LH}_{\mathrm{XZ}}^{#1}}
-\newcommand{\ground}[1]{{\lambda \left (#1 \right)}}
-
-\XW{merge Section 3 and 4; also easy the discussion;}
+%\XW{merge Section 3 and 4; also easy the discussion;}
 
@@
 
-%\XW{TOADD: some orgainization}
+%\XW{TOADD: some organization}
 %\XW{highlight the different requirement from the normal Local Hamiltonian reduction; and highlight a bit about the solution idea}
@@
  The Toffoli gate maps bits $(a,b,c)$ to $(a,b, c \oplus (a \text{ and } b))$, which can be decomposed as $\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$ where $\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$.
- %Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
- %Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
+ %Here we restate the result from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
+ %Because of this result, we can assume without loss of generality that our quantum circuits consist of only Toffoli and Hadamard gates.
 % Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
@@
 %     -U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-% 	We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least nonzero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
+%     We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least non zero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
 %One can similarly rewrite $\Hprop$ in terms of elements from $\LHXZ{}$.
@@
 \begin{proof}
-	Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least nonzero eigenvalue of $JH_2$ is greater than $2\norm{H_1}$.
+    Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least non zero eigenvalue of $JH_2$ is greater than $2\norm{H_1}$.
 \end{proof}
@@
 Decompose $\ket{\phi}= \alpha \histpsi{C(x)} + \beta \histpsi{C(x)}^\bot$.
-Note that $\histpsi{C(x)}$ is a eigenvector $H_{C(x)}$ of eigenvalue 0 and all other eigenvalues are at least $3/4$.
+Note that $\histpsi{C(x)}$ is an eigenvector $H_{C(x)}$ of eigenvalue 0 and all other eigenvalues are at least $3/4$.
 Thus, we have $\abs{\alpha}^2 \geq 1-\frac{4}{3}\epsilon$.
@@
 %     As a result, we have
-% 	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
+%     $$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\eps}{T^5}$$
 %     which implies our claim.
@@
 % De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
-% There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on number of qubits in each subsystem.
+% There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on the number of qubits in each subsystem.
 \begin{thm}[\cite{Brandão2017}]
@@
 
-\XW{comment on saturating the error bound?}
+%\XW{comment on saturating the error bound?}
 
@@
 
-% Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
-% Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
+% Here we restate the result from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
+% Because of this result, we can assume without loss of generality that our quantum circuits consist of only Toffoli and Hadamard gates.
 % Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
@@
 %     This transform commutes with Hadamard gates on the respective qubit.
-On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turn it into a combination of Hadamard and Toffoli gates.
+On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turns it into a combination of Hadamard and Toffoli gates.
 Mathematically,
@@
 %         \item $C'$ uses only Hadamard and Toffoli gates.
-% 		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
+%         \item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size.
+Exchanging $\mathcal{F}$ with a controlled phase gate turns it into $4$ gates.
+So the final result is at most $4T$ gates.
 %         \item When $x$ is classical, $\mathcal{F}(x)=x||0$.
@@
 
-% 	We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least nonzero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
+%     We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least non zero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
 

### 2020-04-16 preliminaries.tex
Sync with local to fix smart quotes

@@
 This is because the definition of $\SampBQP$ already includes an error parameter $\eps$, where the algorithm is allowed to generate a sample with statistical error up to $\eps$ in time polynomial in $1/\eps$.
-Hence, in our definition of soundness, we allow the verifier's output to have error $\eps$ for any given inverse polynomial $\eps$.
+Hence, we define the soundness to  allow the verifier's output to have an $\eps$ error for any given inverse polynomial $\eps$ without introducing an extra soundness error parameter.
 \end{remark}
@@
 \label{def:comp-indis}
-    \Ethan{TODO PROOFREAD ME}
-    Two families of states $\set{\rho_{1,\lambda}}_{\lambda\in\bbN}$ and $\set{\rho_{2,\lambda}}_{\lambda\in\bbN}$ are \emph{$\eps$-computationally indistinguishable} if for all $\BQP$ distinguishers $\mathsf{D}$ and $\lambda\in\bbN$,
+    %\Ethan{TODO PROOFREAD ME}
+    Two ensemble of states $\set{\rho_{1,\lambda}}_{\lambda\in\bbN}$ and $\set{\rho_{2,\lambda}}_{\lambda\in\bbN}$ are \emph{$\eps$-computationally indistinguishable} if for all $\BQP$ distinguishers $\mathsf{D}$ and $\lambda\in\bbN$,
 	$$\abs{\Pr\left[\mathsf{D}(\rho_{1,\lambda})=1\right]-\Pr\left[\mathsf{D}(\rho_{2,\lambda})=1\right]}\leq\eps(\lambda).$$

### 2020-04-16 qpip0.tex
Sync with local to fix smart quotes

@@
     Conditioned on $\PNaiveStar$ accept, clearly $(d, z)=(d', z')$.
-    Conditioned on $\PNaiveStar$ reject, since dummy strategy will be rejected with high probability in Hadamard round, \Ethan{kinda obvious but we never explicitly explained why}
+    Conditioned on $\PNaiveStar$ reject, since dummy strategy will be rejected with high probability in Hadamard round, %\Ethan{kinda obvious but we never explicitly explained why}
     we have $(d', z')\approx_{c, O(\eps)}(\Rej, \bot)=(d, z)$.
@@
 Note that $z$ is ``sub-normalized", i.e.
-$\tr (z)= \text{probability of getting accepted} \leq 1$.
+$\tr (z) \leq 1 \text{}$, and $\tr(z)$ equals to the probability of getting accepted.
 
@@
     +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-    +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
-    +& \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \nn \\
-    +&\L.\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] , \nn     
+    \nn \\
+    +&  \bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
+    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
+   \nn \\
+    +&\L.
+\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] , \nn
     %=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err )
@@
     +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-    +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
-    +& \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \nn \\
-    +&\L.\L.\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R]\R| \nn \\  %%%%%%%%%%%
+    \nn \\
+    +&  \bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
+    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
+     \nn \\
+    +&\L.\L. \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}
+    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R]\R| \nn \\  %%%%%%%%%%%
     \leq&  \sum_z   \E_\gamma \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^j0,\gamma}} \R|+
@@
       \leq&  \sum_z   \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{e_i,\psi_{1^j0,\gamma}} \R|+
-    2 \sum_{k=0}^{i-1} \L|\bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{e_i,\psi_{1^i,\gamma}} \R|  \R]    +O\L(\frac{m^2}{\sqrt T}\R)\nn \\ %%%%%%%%%
+    2 \sum_{k=0}^{i-1} \L|\bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{e_i,\psi_{1^i,\gamma}} \R|  \R]\nn \\
+    +& O\L(\frac{m^2}{\sqrt T}\R)\nn \\ %%%%%%%%%
     \leq&  \sum_z   \L[\L| \bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^{i-1}0,\gamma}} \R|+
-    2  \L|\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R]    \nn \\ +&O\L(\frac{m^2}{\sqrt T}+m^2{(m-1)\gamma_0}+m\sqrt{(m-1)\gamma_0}\R)\nn \\ %%%%%%%%%
+    2  \L|\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R]    \nn \\ 
+    +&O\L(\frac{m^2}{\sqrt T}+m^2{(m-1)\gamma_0}+m\sqrt{(m-1)\gamma_0}\R)\nn \\ %%%%%%%%%
     \leq& \norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R),

### 2020-04-16 blind.tex
Sync submitted version onto GitHub

@@
-\section{Achieving Blindness on $\QPIP_0$ protocols}
+\section{Generic Blindness Protocol Compiler for $\QPIP_0$}
 \label{sec:BlindBQP2}
@@
 By doing so, we show that for any cheating prover $\Pblindstar$, the interaction $(\Pblindstar, \Vblind)$ indeed simulates a valid interaction of $(\Pstar, V)$ for some cheating $\Pstar$, and hence the soundness of $\Pi$ implies the soundness of the compiled protocol.
-Finally, for the issue of the prover sending invalid ciphertext, we can assume without loss of generality that the decryption
+Finally, for the issue of the prover sending invalid ciphertexts, we note that this is not an issue if the decryption never fails, which can be achieved by simply let the decryption algorithm output a default dummy message (e.g., $0$) when it fails.
 
@@
         \item Common input: Security parameter $1^\lambda$ where $\lambda\in\bbN$
-        \item Verifier's input: $x\in\zo^n$
+        \item Verifier's input: $x\in\zo^{\poly(\lambda)}$
     \end{itemize}

### 2020-04-16 introduction.tex
Sync with local to fix smart quotes
Sync submitted version onto GitHub

@@
 The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
-considers a $\BPP$ verifier interacting with at least two entangled, non communicating quantum provers.
+considers a $\BPP$ verifier interacting with at least two entangled, non-communicating quantum provers.
 In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
@@
 However, because we are now in the computational setting, there is no longer any available quantum de Finetti theorem that is usually derived in the information-theoretic setting.
-We end up developing a weaker version of parallel repetition result of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}.
+We end up developing a weaker version of  parallel repetition of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}.
 Due to the nature of parallel repetition in the computational setting, our analysis is much less modular and significantly involved for this part.  

### 2020-04-16 qpip0.tex
Sync submitted version onto GitHub

@@
     Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting, $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
-    then the verifier's output in the Hadamard round is $(\eps+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
+    then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
 \end{lemma}
@@
     Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}),
-    we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\varepsilon}, x)$ is computationally indistinguishable to $(d', z_{ideal}')$.
+    we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\varepsilon}, x)$ is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.
 
     Now we relate $(d', z')$ back to $(d, z)$.
-    Conditioned on $\PNaiveStar$ accept, clearly $(d, z)=(d', z')$.
-    Conditioned on $\PNaiveStar$ reject, since dummy strategy will be rejected with high probability in Hadamard round, %\Ethan{kinda obvious but we never explicitly explained why}
-    we have $(d', z')\approx_{c, O(\eps)}(\Rej, \bot)=(d, z)$.
+    First, for the case that $\PNaiveStar$ aborts, since dummy strategy will be rejected with high probability in Hadamard round,
+    we have $(d', z')\approx_{c, O(\eps)}(\Rej, \bot)=(d, z)$ conditioned on $\PNaiveStar$ aborts.
+    For the other case, conditioned on $\PNaiveStar$ not aborts, clearly $(d, z)=(d', z')$.
     So we have $(d, z)\approx_{c, O(\varepsilon)}(d', z')\approx_{c, \negl(\lambda)}(d', z_{ideal}')$,

### 2020-04-30 preliminaries.tex
Add revision action items

@@
 
+\Ethan{After this point, add more remarks in this section}
+
 We define the sampling version of $\BQP$ based on \cite{aaronson_2013}.
@@
 \end{definition}
+
+\Ethan{see Scott's paper to see why inverse poly there. Maybe it's just because it's required for his result to work.
+More generally, need discussions on sampling vs non sampling
+Try to claim our definitions is WLOG/general/intuitive
+}
 
@@
 We model the interaction between a (almost classical) client and a quantum server following \cite{FOCS:Mahadev18a}.
+
+\Ethan{``Streaming" model; can send qubits one-by-one to let client measure many qubits this way.
+
+Tone: Review/introduce. It's not new. Use Urmila's use case as example.}
 
@@
 
+\Ethan{Need discussion for dfn. 2.7.
+Currently there's a remark after about not needing soundness error.
+Discuss more.
+
+Difference between SampBQP and BQP definitions.
+In particular, SampBQP has additional output (not 0/1).
+
+Two sources of error. Kinda like ``DI" device independent/QKD?
+Condition on acc...
+Really depends on target audience. If not crypto...
+
+Maybe just remark that there are 2 params but this definition captures both
+
+Again, it's different from BQP so explain why/where.
+Make it more friendly to people who aren't familiar with this approach.
+
+Also discuss whether soundness error needs additional param. besides inherited from SampBQP}
+
 \begin{definition}
     Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
-	We say it is a prototol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds:
+    We say it is a protocol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds:
 \begin{itemize}
@@
 
+\Ethan{The following is more crypto based
+
+Others don't have a fully general definition,
+or it's just statistical/OTP.
+
+Need explanation/discussion for this.
+Nobody else writes it like this,
+but this is the correct way to write it.
+
+Explain what is this saying.}
+
 \begin{definition}[Blindness]
@@
 \end{definition}
+
+\Ethan{Maybe swap 2.9 and 2.8 or move it up even more.
+If it's before 2.7 then we can just write 2.7 in terms of this.
+
+Consider making this its own section.}
 
@@
 
+\Ethan{Chernoff bound looks like it's in the middle of nowhere. Just get rid of it.}
+
+\iffalse
 \subsection{Chernoff bound}
@@
 
+\fi
+
 \subsection{Quantum Homomorphic Encryption Schemes}
+
+\Ethan{This section should be fine; just leave it alone.
+It's just technicalities copied from another paper.}
 
@@
 \begin{definition}
-	A quantum leveled homomophic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
+    A quantum leveled homomorphic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
     $\QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:

### 2020-04-30 qpip0.tex
Add revision action items

@@
 The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that lets a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
-Intuitively, the verifier chooses a string $h$ specifying  the measurement he wants to make, and sends encoded $h$ to the prover.
+Intuitively, the verifier chooses a string $h$ specifying  the measurement he wants to make, and sends encoded $h$ \Ethan{what?} to the prover.
 The prover ``commits" to a state $\rho$ with the encoded $h$ and replies.
@@
                     Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but is useful for analysis.
-                \item\label{step:c-urmila-in-naive} The verifier samples $c\leftarrow\cVNaive{3}()$  and sends it to the prover.
+                \item\label{step:c-urmila-in-naive} The verifier samples $c\leftarrow\cVNaive{3}()$ \Ethan{Just give it sec.
+param even though it's just a public coin.
+Just so it doesn't look strange.} and sends it to the prover.
                 \item The prover replies $a\leftarrow\cPNaive{4}(pk, c, \sigma)$.
@@
 Now we are ready to prove Theorem~\ref{thm:qpip0}
+
+\Ethan{Try to cut the proof into two: point-wise and average arguments. Figure out what does z-good mean intuitively.
+
+Also more comments/remarks/discussions. Subnormalized state and stuff.}
+
 \begin{proof}

### 2020-07-11 paper.tex
Delete FBQP which was commented out
Add notes and others' updates
Sync with local for macro changes
Sync with local to fix smart quotes
Sync Github and Overleaf

@@
+\newif\ifdraft
+%\drafttrue
+\draftfalse
+
 \documentclass[11pt]{article}
@@
 \usepackage{amsmath, amssymb, amsthm}
+\usepackage{stmaryrd}
 \usepackage{braket}
 \usepackage{algorithm}
+\usepackage{enumitem}
 \usepackage{algpseudocode}
@@
 %\color{white}
-
+\numberwithin{equation}{section}
 \newcounter{protocol}
@@
 
+\ifdraft
 \newcommand{\KM}[1]{{\footnotesize\color{cyan}[KM: #1]}}
@@
 \newcommand{\XW}[1]{{\footnotesize\color{red}[XW: #1]}}
+\else
+\newcommand{\KM}[1]{}
+\newcommand{\Ethan}[1]{}
+\newcommand{\XW}[1]{}
+\fi
+
+\def \Hin {H_{\mathrm{in}}}
+\def \Hout {H_{\mathrm{out}}}
+\def \Hprop {H_{\mathrm{prop}}}
+\def \Hclock {H_{\mathrm{clock}}}
+\def \Jclock {J_{\mathrm{clock}}}
+\def \Jprop {J_{\mathrm{prop}}}
+\def \Kin {K_{\mathrm{in}}}
+\def \Kclock {K_{\mathrm{clock}}}
+\def \Kprop {K_{\mathrm{prop}}}
+
+\newcommand{\histpsi}[1]{\ket{\psi_{#1}^{\mathrm{hist}}}}
+\newcommand{\LHXZ}[1]{\mathrm{LH}_{\mathrm{XZ}}^{#1}}
+\newcommand{\ground}[1]{{\lambda \left (#1 \right)}}
 
@@
 MOST 108-2627-E-002-001.}}
-\author[2]{Yi Lee\thanks{\href{mailto:ethanlee515@gmail.com}{ethanlee515@gmail.com}.}}
-\author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.utexas.edu}{linhh@cs.utexas.edu}.}}
+\author[2]{Yi Lee\thanks{\href{mailto:ethanlee515@gmail.com}{ethanlee515@gmail.com}. This work was done in part while the author was affiliated to National Taiwan University.}}
+\author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.utexas.edu}{linhh@cs.utexas.edu}. Supported by Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.}}
 \author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837(CAREER).}}
@@
 
-% \input{fbqp}
-
 \input{hamiltonian}
 
-\input{qpip}
+%\input{qpip}
 

### 2020-07-12 qpip0.tex
Add some comments on qpip0 proof

@@
                     Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but is useful for analysis.
-                \item\label{step:c-urmila-in-naive} The verifier samples $c\leftarrow\cVNaive{3}()$ \Ethan{Just give it sec.
-param even though it's just a public coin.
-Just so it doesn't look strange.} and sends it to the prover.
+				\item\label{step:c-urmila-in-naive} The verifier samples $c\leftarrow\xleftarrow{\$}\zo$ and sends it to the prover.
                 \item The prover replies $a\leftarrow\cPNaive{4}(pk, c, \sigma)$.
@@
 
-For all $k\leq m$, $d\in \zo^k$, and $\ket{\psi} \in H_{\regX,\regZ}$, define
+For all $k\leq m$, $d\in \zo^k$, \Ethan{and for all $\gamma$?} and $\ket{\psi} \in H_{\regX,\regZ}$, define
 
@@
 Note that we have averaged over $\vec{pk}, \vec{y}$ where as previously everything has fixed $\vec{pk}$ and $\vec{y}$.
+\Ethan{Here $\psi$ and $y$ are implicitly dependent on $pk$. Might need to clarify what the expected value over $y$ means.}
 
@@
 $$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
-    where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin probabilities.
+	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin \Ethan{typo?} probabilities.
 Note that $z$ is ``sub-normalized", i.e.

### 2020-07-19 qpip0.tex
Auto-indent qpip0.tex
Add author note about gamma
Add question about parallel rep citation
Add more questions
Start rewriting parallel rep

@@
 \label{sec:qpip0_all}
-
-%\hannote{In this section, we modify the construction of \cite{FOCS:Mahadev18a} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}
-
-% We then extend our scheme for $\QPIP_0$ using results from \cite{FOCS:Mahadev18a}.
 
@@
 We use techniques from \cite{arXiv:ChiaChungYam19} to prove that Protocol~\ref{proto:QPIP0samp} has soundness error $1/\sqrt{m}$ in \Cref{thm:qpip0}.
-
-% since Protocol~\ref{proto:urmila4} has a constant soundness error\hannote{too imprecise}\footnote{Protocol~\ref{proto:urmila4} doesn't have a formally defined soundness error.
-But intuitively, the verifier would accept a non-binding result will constant probability.}, Protocol~\ref{proto:qpip0_naive}  also has a constant soundness error, which means the outputted samples have constant computational distance to the ideal distribution, making the result not very useful.
-
-%Subprotocol for Quantum Measurements
-% \subsection{$\QPIP_0$ for BQP?}
-% \hannote{Ethan old description before parallel rep.}
-% As a warm-up, we  restate the construction in \cite{FOCS:Mahadev18a}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.
-
-% Let $\rho$ be an $n$-qubit state.
-Let $h$ be an n-bits string called the \emph{basis choice}.
-That is, $h_i=0$ indicates that the $i$-th qubit of $\rho$ is to be measured in the standard basis, while $i=1$ indicates Hadamard basis measurement instead.
-Let $D_{\rho, h}$ be the distribution of the corresponding measurement results.
 
@@
 We now formally describe the interface of $\PiMeasure$ while omitting the implementation details.
-
-%  that : if $h_i=0$, he wants a $X$ measurement on $i$-th qubit; if $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.
-% At the end of $\PiMeasure$, the verifier learns a measurement outcome $M_{XZ}(\rho, h)$.
 
@@
 The protocol achieves a ``binding" property that gives guarantees against cheating provers.
-
-% \begin{definition}
-% With loss of generality,  we can assume that the testing round verification is deterministic.
-We denote the set of strings $a$ \Ethan{Font makes this $a$ look screwy} accepted by the verifier in the testing round with $(pk,y)$ as $\Acc_{pk,y}$.
-\hannote{do  i actually use this}
-% \end{definition}
 
@@
 
-% Note that in $\PiNaive$ the verifier only learns the output in the Hadamard round.
-% So $\PiNaive$ is not a $\QPIP_0$ with good completeness or soundness.
-
 On the other hand, \Cref{proto:qpip0_naive} has a binding property like \Cref{proto:urmila4}, which we will use to achieve completeness and soundness in \Cref{sec:qpip0}.
@@
 \subsection{$\QPIP_0$ protocol for $\SampBQP$} \label{sec:qpip0}
-%Parallel Repetition of the Measurement Subprotocol
-
-\iffalse
-The following protocol is a $\QPIP_0$ protocol for $\SampBQP$
-
-$\forall c\in\bbN$ Soundness = $O(T^{-c})$
-
-Given inverse poly p(T), we can parameterize the protocol to have soundness p(T)
-\fi
-
-%    \label{ProtoQPIP1}
 
@@
 	% $$ \ket{\psi}_{\regX,\regZ} =  G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ}+ G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ}+\ket{\psi_{err}}_{\regX,\regZ},$$
+
+	\Ethan{Maybe $G_0$ and $G_1$ need to post-select on $in$ and $ph$ registers too?}
 
@@
 
+\Ethan{Pull the definitions of $z_i$ and $z_{good, i}$ up here}
+
+\begin{theorem}
+	\Ethan{First part of main theorem this section}
+	$z_i\approx z_{good, i}$
+\end{theorem}
+
+\begin{theorem}
+	\Ethan{Second part of main theorem this section}
+	$(d_i, z_{good, i})\approx (d_i, z_{ideal, i})$
+	\Ethan{Need to define $d_i$ here}
+\end{theorem}
+
+\begin{theorem}
+	\Ethan{TODO some kinda average argument}
+\end{theorem}
+
 \begin{proof}
@@
 Splitting $\ket{\psi}$ with Equation~\ref{eq:partition-string},
-%\hannote{gamma..}
+\hannote{gamma..}
+\Ethan{Maybe take expected value over gamma here}
 
@@
 
+\Ethan{Is this particular $z_{ideal, i}$ defined? As in, what's its corresponding accept probability?}
+
 By construction, when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$.

### 2020-07-20 qpip0.tex
Fix on parallel rep G0 G1 post-selection

--- 2020-07-12 qpip0.tex
@@
  %Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
-\begin{lemma}[partition lemma; revision of Lemma 3.5 of \cite{arXiv:ChiaChungYam19}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{arXiv:ChiaChungYam19} and post-select on the $th$ register being $0$ or $1$ then discard $ph,th,in$.
+\begin{lemma}[partition lemma; revision of Lemma 3.5 of \cite{arXiv:ChiaChungYam19}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{arXiv:ChiaChungYam19} and post-select on the $ph,th,in$ register being $0^t01$ or $0^t11$ then discard $ph,th,in$.
 Property~\ref{property:partition-err} corresponds to Property~1.
@@
 	% $$ \ket{\psi}_{\regX,\regZ} =  G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ}+ G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ}+\ket{\psi_{err}}_{\regX,\regZ},$$
+
+	\Ethan{Why the $\ket{\psi_{err,i,\gamma}}$ term? $G_0$ and $G_1$ come from post-selection, right? Do they not post-select on all possible outcomes?}
 

### 2020-07-20 hamiltonian.tex
Add revision action items
Remove non-ascii in label

@@
 %We will apply \Cref{lem:projection} twice to obtain $\Jclock$ and $\Jprop$ respectively.
+
+\Ethan{See if proj. lemma can be applied just once instead of twice. Possibly add prop and clock together first. (lower priority relatively?)
+
+Also a problem with attitude. Don't make it too obvious that there's trivial improvements to be made}
+
 Consider $\Hin + \Jclock\Hclock$ first. According to \cref{lem:projection}, by choosing
@@
 This helps establish some sort of independence between different copies in the analysis.
-To serve our purpose, we adopt the following version of quantum de Finetti's theorem from~\cite{Brandão2017} where the error depends nicely  on the number of qubits, rather than the dimension of quantum systems.
+To serve our purpose, we adopt the following version of quantum de Finetti's theorem from~\cite{Brandao2017} where the error depends nicely  on the number of qubits, rather than the dimension of quantum systems.
 % one always needs to send the best certificate state (i.e., the perfect history state) in order to pass the local Hamiltonian ground energy test.
@@
 % There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on the number of qubits in each subsystem.
-\begin{thm}[\cite{Brandão2017}]
+\begin{thm}[\cite{Brandao2017}]
     \label{deFinetti}

### 2020-07-20 introduction.tex
Add revision action items
Remove non-ascii in label

@@
 The constructed QFHE automatically implies a blind CVQC protocol, however, without verifiability.
-Extending this protocol with verifiability seems challenging as hinted by failed attempts in~\cite{mahadev_2018}.
+Extending this protocol with verifiability seems challenging as hinted by failed attempts in Section 2.2.2 of~\cite{mahadev_2018}.
 In fact, most existing blind and verifiable CVQC protocols require a notable amount of effort in achieving each property respectively.
@@
 We design a \emph{cut-and-choose} protocol on multiple copies of the history state for both testing and outputting.
-We also employ a variant of quantum \emph{de Finetti} theorem~\cite{Brandão2017}
+We also employ a variant of quantum \emph{de Finetti} theorem~\cite{Brandao2017}
 to prevent potential cheating strategies by entangling different copies of history states.
@@
 It will be extremely interesting to improve the parameter dependence with potentially new techniques.
+
+\Ethan{TODO add organization of paper}
 

### 2020-07-23 qpip0.tex
Add comment about lemma in QPIP0

--- 2020-07-19 qpip0.tex
@@
 
-We also need the following technical lemma.
+We also need the following technical lemma. \Ethan{This lemma kinda breaks the flow here. Is it ok to move it somewhere else?}
 \begin{lemma}\label{lem:samp-tech}

### 2020-07-24 qpip0.tex
Remove done action item
Start breaking the proof

@@
 
-\subsection{Mahadev's measurement protocol}\label{sec:urmila4}
+\subsection{Notations and technical lemma}
 
-Before introducing Mahadev's protocol, we introduce a notation.
+We first introduce some tools that we'll use in our analysis.
 
 \begin{definition}[$M_{XZ}(\rho,h)$]
-
 	For any natural number $n$, $n$-bit string $h$, and $n$-qubit quantum state $\rho$, consider the following measurement procedure: measure the first qubit of $\rho$ in $X$ basis if $h_1=0$; measure the first qubit of $\rho$ in $Z$ basis if $h_1=1$.
@@
 	We denote the $n$-bit random variable corresponding to the measurement results as $M_{XZ}(\rho,h)$.
+\end{definition}
 
-\end{definition}
+\Ethan{Moving the lemma up here for now so it doesn't break the flow later; maybe we can move it into preliminary?}
+\begin{lemma}\label{lem:samp-tech}
+	For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
+	$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi} $$
+\end{lemma}
+\begin{proof}
+	\begin{align}
+		\sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| \nn \\
+		\leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}} \nn \\
+		\leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\sum_z\norm{P_z\ket{\phi}}^2} \nn \\
+		\leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn \\
+		\leq & \norm{\ket{\psi}}\norm{\ket{\phi}},
+	\end{align}
+	where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
+\end{proof}
+
+\subsection{Mahadev's measurement protocol}\label{sec:urmila4}
 
@@
 
+\Ethan{Mention that completeness is trivial somewhere up here}
+
 The intuition behind this theorem is that the we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
@@
 	% $$ \ket{\psi}_{\regX,\regZ} =  G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ}+ G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ}+\ket{\psi_{err}}_{\regX,\regZ},$$
-
-	\Ethan{Maybe $G_0$ and $G_1$ need to post-select on $in$ and $ph$ registers too?}
 
@@
 
-We also need the following technical lemma. \Ethan{This lemma kinda breaks the flow here. Is it ok to move it somewhere else?}
-\begin{lemma}\label{lem:samp-tech}
-	For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
-	$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi} $$
-\end{lemma}
-\begin{proof}
-	\begin{align}
-		\sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| \nn \\
-		\leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}} \nn \\
-		\leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\sum_z\norm{P_z\ket{\phi}}^2} \nn \\
-		\leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn \\
-		\leq & \norm{\ket{\psi}}\norm{\ket{\phi}},
-	\end{align}
-	where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
-\end{proof}
-
-Now we are ready to prove Theorem~\ref{thm:qpip0}
-
 \Ethan{Try to cut the proof into two: point-wise and average arguments. Figure out what does z-good mean intuitively.
@@
 
-\begin{proof}
-
-	Completeness is trivial.
+	\Ethan{Mention completeness somewhere}
 
@@
 
-	By Lemma~\ref{lem:partition2}, we have
-
+	By Lemma~\ref{lem:partition2}, we can decompose
 	\begin{align} \label{eq:partition-string}
@@
 \Ethan{Maybe take expected value over gamma here}
+
+\begin{proof}
 

### 2020-07-24 qpip0.tex
Re-indent
Approximately cut qpip0 into 3 theorems

@@
 
-% \begin{proof}
-% Step~\ref{step:sum-ob}:
-% \begin{align}
-%   ( G_{0,i,\gamma}+G_{1,i,\gamma}) \ket{\psi}_{\regX,\regZ}
-%   &= \ket{\psi_{0,i,\gamma}}_{\regX,\regZ}+\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}
-% \end{align}
-% \end{proof}
-
 \Ethan{Try to cut the proof into two: point-wise and average arguments. Figure out what does z-good mean intuitively.
@@
 
-\begin{theorem}
-	\Ethan{First part of main theorem this section}
-	$z_i\approx z_{good, i}$
-\end{theorem}
-
-\begin{theorem}
-	\Ethan{Second part of main theorem this section}
-	$(d_i, z_{good, i})\approx (d_i, z_{ideal, i})$
-	\Ethan{Need to define $d_i$ here}
-\end{theorem}
-
-\begin{theorem}
-	\Ethan{TODO some kinda average argument}
-\end{theorem}
-
 \Ethan{Mention completeness somewhere}
@@
 For soundness, We begin by considering the state $\ket{\psi}$ the prover in $\PiSampZ$ holds before he receives $\vec{c}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
+\Ethan{WLOG $\ket{\psi}$ is pure, or maybe can purify?}
 
-	For all $k\leq m$, $d\in \zo^k$, \Ethan{and for all $\gamma$?} and $\ket{\psi} \in H_{\regX,\regZ}$, define
-
+For all $k\leq m$, $d\in \zo^k$, $\gamma$ \Ethan{domain for $\gamma$?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define
 $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}G_{d_{k-1},k-1,\gamma}\cdots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$
@@
 \end{align}
-
 where we abuse the notation and use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
-%\hannote{Note that the prover's state is actually a mixed state.
-In particular, $\ket{\psi}$ depends on $pk$ and we are considering the mixed state averaged over the verifier's choice of $pk$.}
 
@@
 
-	And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$   %\hannote{problem with $e_j$ or $e_i$}
+And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$
 
@@
 
-	Since $\vec{c}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have
-$$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
-	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin \Ethan{typo?} probabilities.
-Note that $z$ is ``sub-normalized", i.e.
-$\tr (z) \leq 1 \text{}$, and $\tr(z)$ equals to the probability of getting accepted.
-
 Define
-
 \begin{align}
@@
 
+\begin{theorem}
+	\Ethan{First part of main theorem this section}
+	$z_i\approx z_{good, i}$
+\end{theorem}
+\begin{proof}
+
 	Splitting $\ket{\psi}$ with Equation~\ref{eq:partition-string},
@@
 	\Ethan{Maybe take expected value over gamma here}
-
-\begin{proof}
 
@@
 
+\end{proof}
+
+\begin{theorem}
+	\Ethan{Second part of main theorem this section}
+	$(d_i, z_{good, i})\approx (d_i, z_{ideal, i})$
+	\Ethan{Need to define $d_i$ here}
+\end{theorem}
+\begin{proof}
+
 % \begin{align}
@@
 % \end{align}
-
-Now we try to  put together all $i\in [m]$. Define
-$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}.$$
-
-We have
-\begin{align} \label{eq:z-z-good}
-	\tr|z-z_{good}| =& \tr\L|\frac{1}{m}\sum_i (z_i-z_{good,i})\R| \nn \\
-	\leq&  \frac{1}{m}\sum_i\tr| (z_i-z_{good,i})| \nn \\
-	\leq&  \frac{1}{m}\sum_i\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
-	\leq&  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%
-	=&O\L( \frac{1}{\sqrt m}+\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)
-\end{align}
-
-where we used triangle inequality on the second line, Equation~\ref{eq:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
-
-We now proceed to prove that $z_{good}$ is close to the ideal distribution.
 
@@
 If all $m-1$ copies are accepted, he replies with the $i$-th copy, otherwise reply $\bot$.
-
-%old protocol when jerection on 4-th round
-% The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of Protocol~\ref{proto:urmila4} in Protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
-The prover then picks a uniformly random $\gamma$ and  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
-If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead.
-This is possible because all the inputs are classical.
-On the fourth round, there are four possibilities depending on $c$ and whether the prover generated $\ket{\psi_{1^{i-1}1,\gamma}}$.
-If $c=0$ and the prover generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}.
-If $c=1$ and the prover generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he runs $U$ and check whether every copy except the $i$-th copy would be accepted.
-If all $m-1$ copies accepts, he reply with the $i$-th copy, otherwise reply $\bot$.
-If $c=0$ and the prover failed to generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he runs $U_{trivial}$ and repies.
-If $c=1$ and the prover failed to generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he replies with $\bot$.
-\footnote{Recall that $c=0$ is the testing round and $c=1$ is the Hadamard round.}
 
@@
 \end{align}
+\end{proof}
+
+\begin{theorem}
+	\Ethan{TODO some kinda average argument}
+\end{theorem}
+\begin{proof}
+Now we try to put together all $i\in [m]$. Define
+$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}.$$
+
+We have
+\begin{align} \label{eq:z-z-good}
+	\tr|z-z_{good}| =& \tr\L|\frac{1}{m}\sum_i (z_i-z_{good,i})\R| \nn \\
+	\leq&  \frac{1}{m}\sum_i\tr| (z_i-z_{good,i})| \nn \\
+	\leq&  \frac{1}{m}\sum_i\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
+	\leq&  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%
+	=&O\L( \frac{1}{\sqrt m}+\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)
+\end{align}
+
+where we used triangle inequality on the second line, Equation~\ref{eq:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
+
+We now proceed to prove that $z_{good}$ is close to the ideal distribution.
+Since $\vec{c}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have
+$$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
+where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin \Ethan{typo?} probabilities.
+Note that $z$ is ``sub-normalized", i.e.
+$\tr (z) \leq 1 \text{}$, and $\tr(z)$ equals to the probability of getting accepted.
+
+	\Ethan{Here use the 2nd thm}
 
@@
 \end{align}
-%\hannote{the composition of z ideal and triangle ineq is sketchy lol. Also need to specify different z ideal}
-
 \end{proof}

### 2020-07-26 qpip0.tex
Indent proof body
Try to move detail in proof
Move more details
Start rewriting QPIP0

@@
 					Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but is useful for analysis.
-				\item\label{step:c-urmila-in-naive} The verifier samples $c\leftarrow\xleftarrow{\$}\zo$ and sends it to the prover.
+				\item\label{step:c-urmila-in-naive} The verifier samples $c\xleftarrow{\$}\zo$ and sends it to the prover.
 				\item The prover replies $a\leftarrow\cPNaive{4}(pk, c, \sigma)$.
@@
 
-\Ethan{Try to cut the proof into two: point-wise and average arguments. Figure out what does z-good mean intuitively.
-
-Also more comments/remarks/discussions. Subnormalized state and stuff.}
-
-\Ethan{Pull the definitions of $z_i$ and $z_{good, i}$ up here}
-
 \Ethan{Mention completeness somewhere}
@@
 
-For all $k\leq m$, $d\in \zo^k$, $\gamma$ \Ethan{domain for $\gamma$?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define
+For all $k\leq m$, $d\in \zo^k$, $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and $\ket{\psi} \in H_{\regX,\regZ}$, define
 $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}G_{d_{k-1},k-1,\gamma}\cdots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$
@@
 
-By Property~\ref{property-partition-norm-sum} of Lemma~\ref{lem:partition2}, we have
-\begin{align} \label{eq:bad-term-sum}
-	\norm{\ket{\psi}}^2 \geq& \norm{\ket{\psi_{0,\gamma}}}^2+\norm{\ket{\psi_{1,\gamma}}}^2 \nn \\
-	\geq& \norm{\ket{\psi_{0,\gamma}}}^2+
-	\norm{\ket{\psi_{10,\gamma}}}^2+ \norm{\ket{\psi_{11,\gamma}}}^2 \nn \\
-	\geq& \norm{\ket{\psi_{0,\gamma}}}^2+
-	\norm{\ket{\psi_{10,\gamma}}}^2+ \norm{\ket{\psi_{110,\gamma}}}^2 +\cdots  \nn \\
-	&+ \norm{\ket{\psi_{1^{m-1}0,\gamma}}}^2+ \norm{\ket{\psi_{1^{m-1}1,\gamma}}}^2
+We denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as $P_{acc,i,z}$.
+Note that $P_{acc,i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $\vec{a}$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
+
+We denote the string $0^{i-1}10^{m-i} \in \zo^m$ as $e_i$. The output string corresponding to $\ket{\psi} \in H_{\regX,\regZ}$ when $c=e_i$ is then
+\Ethan{Maybe use norm instead of braket for that acc probability?}
+$$z_i\defeq \E_{pk,y} \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
+where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round.
+Note that we have averaged over $\vec{pk}, \vec{y}$ where as previously everything has fixed $\vec{pk}$ and $\vec{y}$.
+\Ethan{Here $\psi$ and $y$ are implicitly dependent on $pk$. Might need to clarify what the expected value over $y$ means?}
+
+Now we define
+\Ethan{Need intuitive high-level description on what this is, maybe the good terms of partition or something?}
+\begin{align}
+	z_{good, i}=\E_\gamma \sum_z \proj{z} \cdot \vev{e_i,\psi_{1^{i-1}1,\gamma}|U^\dag P_{acc,i,z} U|e_i,\psi_{1^{i-1}1,\gamma}}
 \end{align}
+which we can show is close to $z_i$.
 
-Denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as
+\begin{theorem}
+	\Ethan{First part of main theorem this section}
+	$z_i\approx z_{good, i}$
+\end{theorem}
+\begin{proof}
+	We rewrite \Cref{eq:partition-string}.
+	$$\ket{\psi}=\E_{\gamma}\left[
+		\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
+	\right]$$
+	It is then straightforward to see that
+	\begin{align}
+		z_i=& z_{good,i}+ \E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
+		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \nn \\
+		+&  \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
+		+\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
+		\nn \\
+		+&  \bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
+		+\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
+		\nn \\
+		+&\L.
+\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] , \nn
+		%=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err )
+	\end{align}
+	by expanding out \Ethan{TODO Some expression}, where we omitted writing out $e_i$ starting the second line.
+	Therefore we have
+	\begin{align} \label{eq:zi-zgoodi}
+		\tr|z_i-z_{good,i}|\leq&  \sum_z   \E_\gamma \L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|+
+		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R.  \nn \\
+		+& 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R|    
+		+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \nn \\
+		+&\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \nn \\ %%%%%%%%%
+		\leq&  \sum_z   \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{e_i,\psi_{1^j0,\gamma}} \R| \nn \R.\\
+		+&\L.2 \sum_{k=0}^{i-1} \L|\bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{e_i,\psi_{1^i,\gamma}} \R|\R] + O\L(\frac{m^2}{\sqrt T}\R)\nn \\ %%%%%%%%%
+		\leq&  \sum_z   \L[\L| \bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^{i-1}0,\gamma}} \R|+
+		2  \L|\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R]    \nn \\ 
+		+&O\L(\frac{m^2}{\sqrt T}+m^2{(m-1)\gamma_0}+m\sqrt{(m-1)\gamma_0}\R)\nn \\ %%%%%%%%%
+		\leq& \norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R),
+	\end{align}
+	where \Ethan{One of the eqs is deleted so need to correct this later} on the second inequality we used triangle inequality, on the third inequality we used  Lemma~\ref{lem:samp-tech} and property~\ref{property:partition-err} of Lemma~\ref{lem:partition2}, on the fourth inequality we used Lemma~\ref{lem:samp-tech} and Equation~\ref{eq:rejected-d}, and on the last inequality we used Lemma~\ref{lem:samp-tech}.
+Once again, we omit $e_i$ when it is not relevant.
 
-$$P_{acc,i,z}.$$
-Note that $P_{acc,i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $\vec{a}$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
+	\Ethan{Connect the dots with below}
 
@@
 	\end{align}
-
-Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$. The output string corresponding to $\ket{\psi} \in H_{\regX,\regZ}$ when $c=e_i$ is then
-
-$$z_i\defeq \E_{pk,y} \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
-where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round.
-Note that we have averaged over $\vec{pk}, \vec{y}$ where as previously everything has fixed $\vec{pk}$ and $\vec{y}$.
-\Ethan{Here $\psi$ and $y$ are implicitly dependent on $pk$. Might need to clarify what the expected value over $y$ means.}
-
-Define
-\begin{align}
-	z_{good,i}=\E_\gamma \sum_z \proj{z} \cdot \vev{e_i,\psi_{1^{i-1}1,\gamma}|U^\dag P_{acc,i,z} U|e_i,\psi_{1^{i-1}1,\gamma}}
-\end{align}
-
-\begin{theorem}
-	\Ethan{First part of main theorem this section}
-	$z_i\approx z_{good, i}$
-\end{theorem}
-\begin{proof}
-
-	Splitting $\ket{\psi}$ with Equation~\ref{eq:partition-string},
-	\hannote{gamma..}
-	\Ethan{Maybe take expected value over gamma here}
-
-	\begin{align}
-		\ket{\psi}=& \L. \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{i-1}0,\gamma}}+
-		\ket{\psi_{1^{i-1}1,\gamma}} \R. \nn \\
-		+& \L.\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,i,\gamma}}\R. \nn \\
-		=& \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-	\end{align}
-
-	we have
-
-	\begin{align}
-		z_i =& \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi} \nn \\
-		=& \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}} +\bra{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} \R]U^\dag  P_{acc,i,z} U\nn \\
-		&\L[ \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}\R]  \nn \\
-		=& \E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}} +\bra{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} \R]U^\dag  P_{acc,i,z} U\nn \\
-		&\L[ \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}\R]  \nn \\
-		=& z_{good,i}+ \E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
-		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \nn \\
-		+&  \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-		+\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-		\nn \\
-		+&  \bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-		+\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-		\nn \\
-		+&\L.
-\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] , \nn
-		%=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err )
-	\end{align}
-
-	%  U^\dag  P_{acc,i,z}U
-
-	% \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-	% \ket{\psi_{1^i,\gamma}}
-	% \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-
-	where we omitted writing out $e_i$ starting the second line. We have
-	\begin{align} \label{eq:zi-zgoodi}
-		&\tr|z_i-z_{good,i}|   \nn \\
-		\leq&  \sum_z  \L| \E_\gamma \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
-		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \R. \nn \\
-		+&  \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-		+\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-		\nn \\
-		+&  \bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-		+\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-		\nn \\
-		+&\L.\L. \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}
-		+\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R]\R| \nn \\  %%%%%%%%%%%
-		\leq&  \sum_z   \E_\gamma \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^j0,\gamma}} \R|+
-		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R.  \nn \\
-		+&  2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R|    
-		+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \nn \\
-		+&\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \nn \\ %%%%%%%%%
-		\leq&  \sum_z   \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{e_i,\psi_{1^j0,\gamma}} \R|+
-		2 \sum_{k=0}^{i-1} \L|\bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{e_i,\psi_{1^i,\gamma}} \R|  \R]\nn \\
-		+& O\L(\frac{m^2}{\sqrt T}\R)\nn \\ %%%%%%%%%
-		\leq&  \sum_z   \L[\L| \bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^{i-1}0,\gamma}} \R|+
-		2  \L|\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R]    \nn \\ 
-		+&O\L(\frac{m^2}{\sqrt T}+m^2{(m-1)\gamma_0}+m\sqrt{(m-1)\gamma_0}\R)\nn \\ %%%%%%%%%
-		\leq& \norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R),
-	\end{align}
-where on the second inequality we used triangle inequality, on the third inequality we used  Lemma~\ref{lem:samp-tech} and property~\ref{property:partition-err} of Lemma~\ref{lem:partition2}, on the fourth inequality we used Lemma~\ref{lem:samp-tech} and Equation~\ref{eq:rejected-d}, and on the last inequality we used Lemma~\ref{lem:samp-tech}.
-Once again, we omit $e_i$ when it is not relevant.
-
 \end{proof}
@@
 
+Now we try to put together all $i\in [m]$. Define
+$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}.$$
+
 \begin{theorem}
@@
 \begin{proof}
-Now we try to put together all $i\in [m]$. Define
-$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}.$$
+
+	By Property~\ref{property-partition-norm-sum} of Lemma~\ref{lem:partition2}, we have
+	\begin{align} \label{eq:bad-term-sum}
+		\norm{\ket{\psi}}^2 \geq& \norm{\ket{\psi_{0,\gamma}}}^2+\norm{\ket{\psi_{1,\gamma}}}^2 \nn \\
+		\geq& \norm{\ket{\psi_{0,\gamma}}}^2+
+		\norm{\ket{\psi_{10,\gamma}}}^2+ \norm{\ket{\psi_{11,\gamma}}}^2 \nn \\
+		\geq& \norm{\ket{\psi_{0,\gamma}}}^2+
+		\norm{\ket{\psi_{10,\gamma}}}^2+ \norm{\ket{\psi_{110,\gamma}}}^2 +\cdots  \nn \\
+		&+ \norm{\ket{\psi_{1^{m-1}0,\gamma}}}^2+ \norm{\ket{\psi_{1^{m-1}1,\gamma}}}^2
+	\end{align}
 

### 2020-07-26 qpip0.tex
Redefine zideal to be subnormalized too

@@
 
+Now define $z_{true}$ to be sampled from $D_x$... \Ethan{Or something like that},
+and define $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
+
 \begin{theorem}
 	\Ethan{Second part of main theorem this section}
-	$(d_i, z_{good, i})\approx (d_i, z_{ideal, i})$
-	\Ethan{Need to define $d_i$ here}
+	$z_{good, i}\approx z_{ideal, i}$
 \end{theorem}

### 2020-07-26 qpip0.tex
Rewrite first thm of parallel rep

@@
 
-\subsection{Notations and technical lemma}
-
-We first introduce some tools that we'll use in our analysis.
-
+We first introduce a notation that we'll use throughout this chapter.
 \begin{definition}[$M_{XZ}(\rho,h)$]
@@
 \end{definition}
-
-\Ethan{Moving the lemma up here for now so it doesn't break the flow later; maybe we can move it into preliminary?}
-\begin{lemma}\label{lem:samp-tech}
-	For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
-	$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi} $$
-\end{lemma}
-\begin{proof}
-	\begin{align}
-		\sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| \nn \\
-		\leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}} \nn \\
-		\leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\sum_z\norm{P_z\ket{\phi}}^2} \nn \\
-		\leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn \\
-		\leq & \norm{\ket{\psi}}\norm{\ket{\phi}},
-	\end{align}
-	where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
-\end{proof}
 
@@
 which we can show is close to $z_i$.
+However, before doing so, we first present a couple lemmas that we will need.
+\begin{lemma}\label{lem:samp-tech}
+	For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
+	$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi} $$
+\end{lemma}
+\begin{proof}
+	\begin{align}
+		\sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| \nn \\
+		\leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}} \nn \\
+		\leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\sum_z\norm{P_z\ket{\phi}}^2} \nn \\
+		\leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn \\
+		\leq & \norm{\ket{\psi}}\norm{\ket{\phi}},
+	\end{align}
+	where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
+\end{proof}
+\begin{lemma}
+	\label{lem:partition-testing}
+	$\forall\gamma$,
+	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2
+		\leq (m-1)\gamma_0+\negl(n)$$
+\end{lemma}
+\begin{proof}
+	Since the verifier only accepts if all $(m-1)$ copies of testing rounds accepts, for all $j\neq i$,
+	$$P_{acc,i,z}=P_{acc,i,z}P_{j,pk_j,y_j,acc}.$$
+	And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$
+	\begin{align} \label{eq:rejected-d}
+		\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2
+		=& \norm{P_{acc,i,z}P_{j,pk_j,y_j,acc} U \ket{e_i}\, G_{0,j+1,\gamma}\ket{\psi_{1^j,\gamma}}  }^2 \nn \\
+		\leq& \norm{P_{j,pk_j,y_j,acc} U \ket{e_i}\, G_{0,j+1,\gamma}\ket{\psi_{1^j,\gamma}}  }^2 \nn \\
+		\leq& (m-1)\gamma_0+\negl(n)
+	\end{align}
+\end{proof}
+
+Now we're ready to show that $z_{i, good}$ is close to $z_i$.
 
 \begin{theorem}
-	\Ethan{First part of main theorem this section}
-	$z_i\approx z_{good, i}$
+	$$\tr\abs{z_i-z_{i, good}}\leq\E_\gamma\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)$$
 \end{theorem}
@@
 	\right]$$
-	It is then straightforward to see that
+	Then we expand $z_i$ as
 	\begin{align}
-		z_i=& z_{good,i}+ \E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
+		z_i=& z_{good,i}+ \E_\gamma \sum_z \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
 		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \nn \\
@@
 		+&\L.
-\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] , \nn
+\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] \proj{z} , \nn
 		%=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err )
 	\end{align}
-	by expanding out \Ethan{TODO Some expression}, where we omitted writing out $e_i$ starting the second line.
+	where we omitted writing out $e_i$.
 	Therefore we have
-	\begin{align} \label{eq:zi-zgoodi}
-		\tr|z_i-z_{good,i}|\leq&  \sum_z   \E_\gamma \L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|+
-		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R.  \nn \\
+	\begin{align*}
+		\tr|z_i-z_{good,i}|\leq& \E_\gamma \sum_z \L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|+
+		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R. \\
 		+& 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R|    
-		+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \nn \\
-		+&\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \nn \\ %%%%%%%%%
-		\leq&  \sum_z   \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{e_i,\psi_{1^j0,\gamma}} \R| \nn \R.\\
-		+&\L.2 \sum_{k=0}^{i-1} \L|\bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{e_i,\psi_{1^i,\gamma}} \R|\R] + O\L(\frac{m^2}{\sqrt T}\R)\nn \\ %%%%%%%%%
-		\leq&  \sum_z   \L[\L| \bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^{i-1}0,\gamma}} \R|+
-		2  \L|\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R]    \nn \\ 
-		+&O\L(\frac{m^2}{\sqrt T}+m^2{(m-1)\gamma_0}+m\sqrt{(m-1)\gamma_0}\R)\nn \\ %%%%%%%%%
-		\leq& \norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R),
-	\end{align}
-	where \Ethan{One of the eqs is deleted so need to correct this later} on the second inequality we used triangle inequality, on the third inequality we used  Lemma~\ref{lem:samp-tech} and property~\ref{property:partition-err} of Lemma~\ref{lem:partition2}, on the fourth inequality we used Lemma~\ref{lem:samp-tech} and Equation~\ref{eq:rejected-d}, and on the last inequality we used Lemma~\ref{lem:samp-tech}.
-Once again, we omit $e_i$ when it is not relevant.
+		+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \\
+		+&\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
+	\end{align*}
+	by the triangle inequality.
+	The last three error terms sum to $O\L(\frac{m^2}{\sqrt{T}}\R)$ by \Cref{lem:samp-tech} and \Cref{property:partition-err} of \Cref{lem:partition2}.
 
-	\Ethan{Connect the dots with below}
-
-	Since the verifier only accepts if all $(m-1)$ copies of testing rounds accepts, for all $j\neq i$,
-
-	$$P_{acc,i,z}=P_{acc,i,z}P_{j,pk_j,y_j,acc}.$$
-
-	And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$
-
-	\begin{align} \label{eq:rejected-d}
-		\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2
-		=& \norm{P_{acc,i,z}P_{j,pk_j,y_j,acc} U \ket{e_i}\, G_{0,j+1,\gamma}\ket{\psi_{1^j,\gamma}}  }^2 \nn \\
-		\leq& \norm{P_{j,pk_j,y_j,acc} U \ket{e_i}\, G_{0,j+1,\gamma}\ket{\psi_{1^j,\gamma}}  }^2 \nn \\
-		\leq& (m-1)\gamma_0+\negl(n)
-	\end{align}
+	Now by \Cref{lem:samp-tech} and \Cref{lem:partition-testing}, we see that
+	\begin{align*}
+		\sum_z \sum_{k=0}^{i-1}\sum_{j=0}^{i-1}
+		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}}} \\
+		&\leq\sum_z \abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^{i-1}0,\gamma}}} + O\L(m^2(m-1)\gamma_0\R) \\
+		&\leq\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2 + O\L(m^2(m-1)\gamma_0\R)
+	\end{align*}
+	and similarly
+	\begin{align*}
+		\sum_z\sum_{k=0}^{i-1}
+		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}\\
+		&\leq\sum_z\abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R)\\
+		&\leq\norm{\ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R)
+	\end{align*}
 \end{proof}
@@
 
-	where we used triangle inequality on the second line, Equation~\ref{eq:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
+	where we used triangle inequality on the second line, \Ethan{thm 1 this section} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
 

### 2020-07-26 qpip0.tex
Polish parallel rep

@@
 \Ethan{WLOG $\ket{\psi}$ is pure, or maybe can purify?}
-
 For all $k\leq m$, $d\in \zo^k$, $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and $\ket{\psi} \in H_{\regX,\regZ}$, define
 $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}G_{d_{k-1},k-1,\gamma}\cdots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$
-
 By Lemma~\ref{lem:partition2}, we can decompose
@@
 We denote the string $0^{i-1}10^{m-i} \in \zo^m$ as $e_i$. The output string corresponding to $\ket{\psi} \in H_{\regX,\regZ}$ when $c=e_i$ is then
-\Ethan{Maybe use norm instead of braket for that acc probability?}
-$$z_i\defeq \E_{pk,y} \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
+$$z_i\defeq \E_{pk,y} \sum_z \norm{P_{acc,i,z} U\ket{e_i,\psi}}^2\proj{z},$$
 where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round.
 Note that we have averaged over $\vec{pk}, \vec{y}$ where as previously everything has fixed $\vec{pk}$ and $\vec{y}$.
-\Ethan{Here $\psi$ and $y$ are implicitly dependent on $pk$. Might need to clarify what the expected value over $y$ means?}
-
+\Ethan{Here $y$ is implicitly dependent on $pk$. Might need to clarify what the expected value over $y$ means?}
 Now we define
-\Ethan{Need intuitive high-level description on what this is, maybe the good terms of partition or something?}
 \begin{align}
-	z_{good, i}=\E_\gamma \sum_z \proj{z} \cdot \vev{e_i,\psi_{1^{i-1}1,\gamma}|U^\dag P_{acc,i,z} U|e_i,\psi_{1^{i-1}1,\gamma}}
+	z_{good, i}=\E_{\gamma, pk, y} \sum_z \norm{P_{acc,i,z} U\ket{e_i,\psi_{1^{i-1}1,\gamma}}}^2\proj{z}
 \end{align}
@@
 	\label{lem:partition-testing}
-	$\forall\gamma$,
+	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$,
 	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2
@@
 
-Now define $z_{true}$ to be sampled from $D_x$... \Ethan{Or something like that},
-and define $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
-
+Now let $z_{true}$, as a mixed state, be correctly sampled from the $\SampBQP$ instance $D_x$,
+and let $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
+We show that $z_{ideal, i}$ is close to $z_{good, i}$.
 \begin{theorem}
-	\Ethan{Second part of main theorem this section}
-	$z_{good, i}\approx z_{ideal, i}$
+	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$ \Ethan{Check thm statement again later}
 \end{theorem}
@@
 
-	Denote the result we would get when $c=1$ by $(d,z_{composite,i})$.
+	Denote the result we would get when $c=1$ by $z_{composite,i}$.
 

### 2020-07-26 qpip0.tex
Rewrite parallelrep avg argument

@@
 \begin{theorem}
+	\label{thm:zi-zgoodi}
 	$$\tr\abs{z_i-z_{i, good}}\leq\E_\gamma\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)$$
@@
 
-Now we try to put together all $i\in [m]$. Define
-$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}.$$
+Now we try to put together all $i\in [m]$. Define the following quantities:
+$$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi}$$
+$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}$$
+$$z_{ideal}\defeq \frac{1}{m}\sum_i z_{ideal,i}$$
+Notice that $z_{ideal}=pz_{true}$ for some probability $p\in[0, 1]$.
 
 \begin{theorem}
-	\Ethan{TODO some kinda average argument}
+	$\PiSampZ$ is a computationally sound protocol for $\SampBQP$.
 \end{theorem}
 \begin{proof}
-
 	By Property~\ref{property-partition-norm-sum} of Lemma~\ref{lem:partition2}, we have
@@
 
-	where we used triangle inequality on the second line, \Ethan{thm 1 this section} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
-
-	We now proceed to prove that $z_{good}$ is close to the ideal distribution.
-	Since $\vec{c}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have
-	$$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
-	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin \Ethan{typo?} probabilities.
-Note that $z$ is ``sub-normalized", i.e.
-$\tr (z) \leq 1 \text{}$, and $\tr(z)$ equals to the probability of getting accepted.
-
-	\Ethan{Here use the 2nd thm}
-
-	Average over $i\in[m]$ we get
-
-	\begin{align}
-		(d,z_{good})\approx_{c, O(\eps)}(d,z_{ideal}).
-	\end{align}
-	% \hannote{do we lose a factor of $m$?}
-	Recall that by Eq~\ref{eq:z-z-good} we have $\norm{z-z_{good}}_1 \leq O(\eps)$ if we pick $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$, which implies
-	\begin{align}
-		(d,z)\approx_{c, O(\eps)}(d,z_{good}).
-	\end{align}
-
-	Therefore  we have  
-	\begin{align}
-		(d,z)\approx_{c, O(\eps)}(d,z_{ideal}).
-	\end{align}
+	where we used triangle inequality on the second line, \Cref{thm:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
+	Let $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$ and by triangle inequality we have $\tr\abs{z-z_{ideal}}=O(\varepsilon)$.
+	Since $z$ is close to some ideal output distribution $z_{ideal}$, it must be close to the ideal output distribution with its accept probability too.
 \end{proof}

### 2020-07-26 qpip0.tex
Redo z_ideal proof for parallelrep

@@
 \begin{theorem}
+	\label{thm:zgood-zideal}
 	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$ \Ethan{Check thm statement again later}
@@
 \begin{proof}
-
-	% \begin{align}
-	%     &\vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi} \nn \\
-	%     =& \bra{e_i, \psi_{1^{i-1}1,\gamma}} U^\dag P_{acc,i,z} U \ket{e_i\psi_{1^{i-1}1,\gamma}} +\hannote{poly terms?}+ \negl(n)
-	% \end{align}
-
 	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}.
@@
 	Denote the result we would get when $c=1$ by $z_{composite,i}$.
+By construction, when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$.
+Also note that this is the only case where the verifier won't reject, so $z_{composite,i}=z_{good,i}$.
 
@@
 Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
-	\begin{align}
-		(d,z_{composite,i})\approx_{c, O(\eps)}(d,z_{ideal,i})
-	\end{align}
-
-	\Ethan{Is this particular $z_{ideal, i}$ defined? As in, what's its corresponding accept probability?}
-
-	By construction, when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$.
-Also note that this is the only case where the verifier won't reject, so $(d,z_{composite,i})=(d,z_{good,i})$, where $(d,z_{good,i})$ is defined as:
-
-	$$\begin{cases}
-		(d,z_{good,i}) \la (\Acc, z_{good,i}/|z_{good,i}|) & \text{with probability } |z_{good,i}|\\
-						(d,z_{good,i}) = (\Rej,\bot)  & \text{otherwise }
-	\end{cases}$$.
-
-	% where  $(d,z)_{good,i} \defeq (\Acc, z_{good,i}) + (1-|z_{good,i}|)(\Rej,\bot)$ \hannote{correct notation? operational def?} .
-
-	Therefore
-
-	\begin{align}
-		(d,z_{good,i})\approx_{c, O(\eps)}(d,z_{ideal,i}).
-	\end{align}
+	$\tr\abs{z_{composite,i}-z_{ideal,i}}=O(\eps)$.
 \end{proof}

### 2020-07-27 qpip0.tex
Remove done author note
More polish

@@
 	\label{thm:zgood-zideal}
-	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$ \Ethan{Check thm statement again later}
+	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$
 \end{theorem}
@@
 
-Now we try to put together all $i\in [m]$. Define the following quantities:
+Now we try to put together all $i\in [m]$. First let
 $$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi}$$
+which is the output distribution of $\PiSampZ$.
+We also define the following accordingly:
 $$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}$$
 $$z_{ideal}\defeq \frac{1}{m}\sum_i z_{ideal,i}$$
-Notice that $z_{ideal}=pz_{true}$ for some probability $p\in[0, 1]$.
+Notice that $z_{ideal}$ is some ideal output distribution, which (a priori) might not have the same accept probability as $z$.
 

### 2020-07-28 preliminaries.tex
Polish and move MXZ to prelim

@@
     $Z=\begin{pmatrix}1&0\\0&-1\end{pmatrix}$.
+\end{definition}
+
+\Ethan{Quantum measurements...}
+
+\begin{definition}[$M_{XZ}(\rho,h)$]
+	For any natural number $n$, $n$-bit string $h$, and $n$-qubit quantum state $\rho$, consider the following measurement procedure: measure the first qubit of $\rho$ in $X$ basis if $h_1=0$; measure the first qubit of $\rho$ in $Z$ basis if $h_1=1$.
+Measure the second qubit of $\rho$ in $X$ basis if $h_2=0$; measure the second qubit of $\rho$ in $Z$ basis if $h_2=1$.
+Continue qubit-by-qubit until all $n$-qubits of $\rho$ are measured, where $i$-th qubit is measured in $X$ basis if $h_i=0$ and  $i$-th qubit is measured in the $Z$ basis if $h_i=1$.
+
+	We denote the $n$-bit random variable corresponding to the measurement results as $M_{XZ}(\rho,h)$.
 \end{definition}

### 2020-07-28 qpip0.tex
Polish and move MXZ to prelim

@@
 However, as we will see in \Cref{sec:urmila4}, Protocol~\ref{proto:urmila4} has a peculiar and weak guarantee, so \Cref{proto:qpip0_naive} don't have any reasonable completeness and soundness.
-To boost the soundness of Protocol~\ref{proto:qpip0_naive}, we run $m=\poly(\lambda)$ copies of Protocol~\ref{proto:qpip0_naive} in parallel and test on $m-1$ copies of them, resulting in Protocol~\ref{proto:QPIP0samp}.
-We use techniques from \cite{arXiv:ChiaChungYam19} to prove that Protocol~\ref{proto:QPIP0samp} has soundness error $1/\sqrt{m}$ in \Cref{thm:qpip0}.
-
-We first introduce a notation that we'll use throughout this chapter.
-\begin{definition}[$M_{XZ}(\rho,h)$]
-	For any natural number $n$, $n$-bit string $h$, and $n$-qubit quantum state $\rho$, consider the following measurement procedure: measure the first qubit of $\rho$ in $X$ basis if $h_1=0$; measure the first qubit of $\rho$ in $Z$ basis if $h_1=1$.
-Measure the second qubit of $\rho$ in $X$ basis if $h_2=0$; measure the second qubit of $\rho$ in $Z$ basis if $h_2=1$.
-Continue qubit-by-qubit until all $n$-qubits of $\rho$ are measured, where $i$-th qubit is measured in $X$ basis if $h_i=0$ and  $i$-th qubit is measured in the $Z$ basis if $h_i=1$.
-
-	We denote the $n$-bit random variable corresponding to the measurement results as $M_{XZ}(\rho,h)$.
-\end{definition}
+To boost its soundness, we run $m=\poly(\lambda)$ copies in parallel and test on $m-1$ copies of them, resulting in Protocol~\ref{proto:QPIP0samp}.
+We use techniques from \cite{arXiv:ChiaChungYam19} to prove that Protocol~\ref{proto:QPIP0samp} has soundness error $1/\sqrt{m}$.
 
@@
 
-\begin{theorem}\label{thm:qpip0}
-	Assuming the QLWE assumption, $\PiSampZ$ is a $\QPIP_0$ protocol for all problems in $\SampBQP$ with negligible completeness error and computational soundness.
-\end{theorem}
-
-\Ethan{Mention that completeness is trivial somewhere up here}
-
-The intuition behind this theorem is that the we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
+It is trivial to see that $\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness error.
+We now show that it is computationally sound.
+The intuition is that the we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
 Therefore if the prover want to cheat, i.e.
@@
 
-\Ethan{Mention completeness somewhere}
-
-For soundness, We begin by considering the state $\ket{\psi}$ the prover in $\PiSampZ$ holds before he receives $\vec{c}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
+We begin by considering the state $\ket{\psi}$ the prover in $\PiSampZ$ holds before he receives $\vec{c}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
 \Ethan{WLOG $\ket{\psi}$ is pure, or maybe can purify?}
@@
 \begin{theorem}
-	$\PiSampZ$ is a computationally sound protocol for $\SampBQP$.
+	Under the QLWE assumption, $\PiSampZ$ is a computationally sound protocol for $\SampBQP$.
 \end{theorem}

### 2020-07-28 qpip0.tex
Polish qpip0

@@
 The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that lets a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
-Intuitively, the verifier chooses a string $h$ specifying  the measurement he wants to make, and sends encoded $h$ \Ethan{what?} to the prover.
-The prover ``commits" to a state $\rho$ with the encoded $h$ and replies.
+Intuitively, the verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$, before sending $pk$ to the prover.
+The prover commits to a state $\rho$ of its choice using $pk$ and replies with its commitment.
 The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}.
-He sends his choice between the two to the prover and has the  prover reply.
-If the verifier chose testing, he checks the prover's two replies and rejects if he sees an inconsistency.
-If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho,h)$ based on the replies.
-Mahadev~\cite{FOCS:Mahadev18a} proves a ``binding" property of the above protocol: if a prover's strategy would always succeeds on the testing round, then that strategy must binds to a $\rho$, meaning that no matter what $h$ the verifier has picked at the beginning, the verifier can get $M_{XZ}(\rho,h)$  with the same $\rho$ if he had chosen the Hadamard round.
+He sends his choice to the prover, and prover replies accordingly.
+If the verifier chose testing, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency.
+If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply.
+\cite{FOCS:Mahadev18a} shows a ``binding" property of $\PiMeasure$: if a prover would always succeed on the testing round, then there exists some $\rho$ so that the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round, no matter what $h$ the verifier has picked at the beginning.
 
@@
 		\item Prover's input: a state $\rho\in\cB^{\otimes n}$ for the verifier to measure.
-		\item Verifier's input:
-			the measurement basis choice $h \in \{0,1\}^n$
+		\item Verifier's input: the measurement basis choice $h \in \zo^n$
 	\end{itemize}
@@
 
-The verifier only learns the measurement outcome on a Hadamard round.
-The protocol achieves a ``binding" property that gives guarantees against cheating provers.
+$\PiMeasure$ has negligible completeness errors.
+On the other hand, as the verifier learns the measurement outcome only on Hadamard round, the protocol offers no standard soundness guarantees;
+instead, it achieves the following \emph{binding property} that gives weaker guarantees against cheating provers.
 
@@
 \end{lemma}
-
-We also mention a fact that will be useful later.
-\begin{fact}
-	\label{lem:trivial-4-round-strategy}
-	There exist a prover strategy for $\PiMeasure$ that is accepted with probability $1-\negl(\lambda)$
-\end{fact}
 
@@
 There are several problems with using $\PiNaive$ as a $\SampBQP$ protocol.
-first, since the verifier doesn't get a sample if he had chosen the testing round in Step~\ref{step:c-urmila-in-naive}, so the protocol has  completeness error at least $1/2$.
-And since Protocol~\ref{proto:urmila4} does not check anything on the Hadamard round, a cheating prover can give up passing the testing round and breaks the commitment on the Hadamard round.
-Such cheating prover only has a constant $1/2$ probability of being caught, resulting in constant soundness error.
+First, since the verifier doesn't get a sample if he had chosen the testing round in Step~\ref{step:c-urmila-in-naive}, the protocol has completeness error at least $1/2$.
+Moreover, since Protocol~\ref{proto:urmila4} does not check anything on the Hadamard round, a cheating prover can give up passing the testing round and breaks the commitment on the Hadamard round, with only a constant $1/2$ probability of being caught.
+However, we can show that \Cref{proto:qpip0_naive} has a binding property similar to \Cref{proto:urmila4}.
 
-On the other hand, \Cref{proto:qpip0_naive} has a binding property like \Cref{proto:urmila4}, which we will use to achieve completeness and soundness in \Cref{sec:qpip0}.
-
-\begin{lemma}[binding property of $\PiNaive$]
+\begin{theorem}[binding property of $\PiNaive$]
 	\label{lem:naive-qpip0-binding}
 	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
-	Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting, $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
+	Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting (ie. $y\ne\bot$), $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
 	then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
-\end{lemma}
+\end{theorem}
 \begin{proof}
+	There's a \emph{dummy strategy} for $\PiNaive$'s prover, who chooses $\rho$ as maximally mixed state instead, and executes the rest of the protocol honestly.
+	It is accepted in the testing round with probability $1-\negl(\lambda)$,
+	but has negligible probability passing the verification after the Hadamard round.
+
+	\Ethan{Smooth this out}
+
 	Consider the following reduction to another cheating $\BQP$ prover for $\PiNaive$ that is perfect and non-aborting.
@@
 	Now we relate $(d', z')$ back to $(d, z)$.
-	First, for the case that $\PNaiveStar$ aborts, since dummy strategy will be rejected with high probability in Hadamard round,
+	First, for the case that $\PNaiveStar$ aborts, since dummy strategy will be rejected with overwhelming probability in Hadamard round,
 	we have $(d', z')\approx_{c, O(\eps)}(\Rej, \bot)=(d, z)$ conditioned on $\PNaiveStar$ aborts.
@@
 
-It is trivial to see that $\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness error.
+Clearly $\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness error.
 We now show that it is computationally sound.

### 2020-07-28 qpip0.tex
Leave more action items

@@
 To prove that, we use the following partition lemma from \cite{arXiv:ChiaChungYam19}, which intuitively says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
-$G_{0,i}$ represents the subspace that are rejected with high probability in the testing round of $i$-th copy; $G_{1,i}$  represents the subspace accepted with ``high probability"\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
+$G_{0,i}$ represents the subspace that are rejected with high probability in the testing round of $i$-th copy, while $G_{1,i}$  represents the subspace accepted with high probability\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
+\Ethan{Next sentence feels like a technical detail that fits better in a proof?}
 $G_{0,i}$ and $G_{1,i}$ need to be efficient because $\PiMeasure$ only gives computational security.
+\Ethan{There's gotta be a better way to describe the following...}
 Once we have $G_{0,i}$ and $G_{1,i}$, we can split up the prover's internal state $\ket{\psi}$ like conditional probabilistic events.
@@
 We were able to fix this issue with a more careful split up of $\ket{\psi}$.
+\Ethan{Maybe move the above chunk below the lemma and just explain by doing} 
 Also as a careful reader might have noticed, the prover's space don't happen to split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
@@
 
- %but there will always be some states  therefore we introduce  an extra parameter $\gamma$ that corresponds to the probability cut-off line that to distinguish the accepted and rejected part, and we need to average over $\gamma$.
-
- % We split the state sub-normalized states corresponding to the prover cheating on different copies and show that the sum of probabilities corresponding to bad states can't be more than $1/m$.
-{The actual proof is more complicated than this sketch because the $G$'s don't commute with each other, so we need to handle the splitting carefully.}
-
- %For example, $G_{0,3} G_{1,5} \ket{\psi}$ corresponds to the events of passing the testing round on the fifth copy then fails the testing round on the third copy.
-
- %Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
 \begin{lemma}[partition lemma; revision of Lemma 3.5 of \cite{arXiv:ChiaChungYam19}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{arXiv:ChiaChungYam19} and post-select on the $ph,th,in$ register being $0^t01$ or $0^t11$ then discard $ph,th,in$.
@@
 			\end{align}
-
 			where $P_{i,pk_i,y_i,acc}$ are projector to the states that $i$-th testing round accepts with $pk_i,y_i$, including the last measurement the prover did before sending $\vec{a}$.
 This means that $\ket{\psi_{0,i,\gamma}}$ is rejected by the $i$-th testing round with high probability.
-
 		\item \label{property:partition-binding}
-
-			% $\{c\}\in S_m$ such that $c_i = 0$
 			For all $\vec{pk}$, $\vec{y}$, fixed $\gamma$, and $j\neq i$, there exists an efficient quantum algorithm $\ext_i$ such that
-
 			\begin{align}
@@
 			\end{align}
-
-			% \item \hannote{added by me..not needed?}
-
-			% $$\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}} = \negl(n)$$
-
 	\end{enumerate}
@@
 	Denote the result we would get when $c=1$ by $z_{composite,i}$.
-By construction, when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$.
+By construction, when $G_{i,1,\gamma}\ldots G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$.
 Also note that this is the only case where the verifier won't reject, so $z_{composite,i}=z_{good,i}$.
@@
 $$z_{ideal}\defeq \frac{1}{m}\sum_i z_{ideal,i}$$
-Notice that $z_{ideal}$ is some ideal output distribution, which (a priori) might not have the same accept probability as $z$.
+Notice that $z_{ideal}$ is some ideal output distribution, which might not have the same accept probability as $z$.
 

### 2020-07-28 qpip0.tex
Try to discuss QPIP0 decomp

@@
 $G_{0,i}$ represents the subspace that are rejected with high probability in the testing round of $i$-th copy, while $G_{1,i}$  represents the subspace accepted with high probability\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
-\Ethan{Next sentence feels like a technical detail that fits better in a proof?}
-$G_{0,i}$ and $G_{1,i}$ need to be efficient because $\PiMeasure$ only gives computational security.
-\Ethan{There's gotta be a better way to describe the following...}
-Once we have $G_{0,i}$ and $G_{1,i}$, we can split up the prover's internal state $\ket{\psi}$ like conditional probabilistic events.
-We split up $\ket{\psi}$ into $G_{0,1}\ket{\psi}+ G_{0,2}G_{1,1}\ket{\psi} + G_{0,3}G_{1,2}G_{1,1}\ket{\psi} + \dots +  G_{0,m} G_{1,m-1}\dots G_{1,2}G_{1,1}\ket{\psi} + G_{1,m} G_{1,m-1}\dots G_{1,2}G_{1,1}\ket{\psi}$, where for example, $G_{0,2}G_{1,1}\ket{\psi}$ intuitively corresponds to passing the testing round of the first copy then getting rejected on the testing round of the second copy.
-Since each of the  substates in  $\{G_{0,1}\ket{\psi}, G_{0,2}G_{1,1}\ket{\psi} , G_{0,3}G_{1,2}G_{1,1}\ket{\psi} , \dots ,  G_{0,m} G_{1,m-1}\dots G_{1,2}G_{1,1}\ket{\psi} \}$ all have  probability $1-1/m$ of being caught by one of the $m-1$ testing rounds, they have well-bounded
- probability of being accepted in Step~\ref{step:multi-testing} of Protocol~\ref{proto:QPIP0samp}, so the output in  Step~\ref{step:multi-testing} would mostly corresponds to $G_{1,m} G_{1,m-1}\dots G_{1,2}G_{1,1}\ket{\psi}$.
-However, since $G_{1,i}$ don't commute with $G_{1,j}$, $G_{1,m} G_{1,m-1}\dots G_{1,2}G_{1,1}\ket{\psi}$ is only binding for the $m$-th copy, so this simplified strategy is not quite correct.
-We were able to fix this issue with a more careful split up of $\ket{\psi}$.
-\Ethan{Maybe move the above chunk below the lemma and just explain by doing} 
 Also as a careful reader might have noticed, the prover's space don't happen to split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
@@
 
-We begin by considering the state $\ket{\psi}$ the prover in $\PiSampZ$ holds before he receives $\vec{c}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
+\Ethan{The following discussion is under construction}
+
+By using \Cref{lem:partition2} iteratively, we can decompose the prover's internal state.
+Let $\ket{\psi}$ be the state the prover holds before he receives $\vec{c}$;
 \Ethan{WLOG $\ket{\psi}$ is pure, or maybe can purify?}
+we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
 For all $k\leq m$, $d\in \zo^k$, $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and $\ket{\psi} \in H_{\regX,\regZ}$, define
-$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}G_{d_{k-1},k-1,\gamma}\cdots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$
-By Lemma~\ref{lem:partition2}, we can decompose
+$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}\ldots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}.$$
+For example, $\ket{\psi_{110, \gamma}}$ intuitively corresponds to the component that would pass the first two copies' testing rounds and fail the third one.
+At this point it is tempting to decompose $\ket{\psi}$ into $\ket{\psi_{s, \gamma}}$ where $s\in\zo^m$ and say that $\ket{\psi_{1^m, \gamma}}$ is the only component that is not rejected with high ($1-1/m$) probability;
+however, $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m, \gamma}}$ is only binding for the $m$-th copy.
+Instead, we must make a point-wise argument for each $i\in[m]$, then... \Ethan{TODO}
+
+For all $i\in[m]$, we define
 \begin{align} \label{eq:partition-string}
@@
 	=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{m-1}0,\gamma}}+\ket{\psi_{1^{m-1}1,\gamma}} \nn \\
-	&+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,m,\gamma}},
+	&+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,m,\gamma}} \nn\\
+	=&\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
 \end{align}

### 2020-07-28 qpip0.tex
Polish further

@@
 We now show that it is computationally sound.
-The intuition is that the we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
+\Ethan{Try to word the following a bit better}
+The intuition is that the we run $m$ copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
 Therefore if the prover want to cheat, i.e.
@@
 However, the prover might create correlations between copies that let him cheat with probability much higher than $1/m$.
-This is a common problem in trying to create parallel repetition protocols.
 We are able to bound the soundness error as $O(1/\sqrt{m})$.
@@
 
-	% $$ \ket{\psi}_{\regX,\regZ} =  G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ}+ G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ}+\ket{\psi_{err}}_{\regX,\regZ},$$
-
 	Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are  sub-normalized.
@@
 	Furthermore, the following properties are satisfied for all $i\in[m]$.
-	%
 	\begin{enumerate}
@@
 	\label{lem:partition-testing}
-	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$,
-	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2
-		\leq (m-1)\gamma_0+\negl(n)$$
+	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and all $i,j\in[m]$ such that $j<i-1$, we have
+	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
 \end{lemma}

### 2020-07-30 qpip0.tex
Smooth out binding property proof

@@
 \begin{proof}
-	There's a \emph{dummy strategy} for $\PiNaive$'s prover, who chooses $\rho$ as maximally mixed state instead, and executes the rest of the protocol honestly.
-	It is accepted in the testing round with probability $1-\negl(\lambda)$,
+	If the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly,
+	it would be accepted in the testing round with probability $1-\negl(\lambda)$,
 	but has negligible probability passing the verification after the Hadamard round.
+	We call this the \emph{dummy strategy}.
 
-	\Ethan{Smooth this out}
-
-	Consider the following reduction to another cheating $\BQP$ prover for $\PiNaive$ that is perfect and non-aborting.
-
-	We define $\Pstar$ as follows.
+	Now we construct another cheating $\BQP$ prover $\Pstar$ that is perfect and non-aborting as follows.
 	For the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
 	If $y\ne\bot$, then reply $y$;
-	else, run the corresponding step of the dummy strategy as in \Cref{lem:trivial-4-round-strategy} and reply with its results.
+	else, run the corresponding step of the dummy strategy and reply with its results.
 	For the fourth message, if $y\ne\bot$, run and reply with $a\leftarrow\cPNaiveStar{4}(pk, c, \sigma)$;
@@
 	Now we relate $(d', z')$ back to $(d, z)$.
-	First, for the case that $\PNaiveStar$ aborts, since dummy strategy will be rejected with overwhelming probability in Hadamard round,
-	we have $(d', z')\approx_{c, O(\eps)}(\Rej, \bot)=(d, z)$ conditioned on $\PNaiveStar$ aborts.
-	For the other case, conditioned on $\PNaiveStar$ not aborts, clearly $(d, z)=(d', z')$.
-	So we have $(d, z)\approx_{c, O(\varepsilon)}(d', z')\approx_{c, \negl(\lambda)}(d', z_{ideal}')$,
-	which in turn implies $\abs{d-d'}\leq O(\eps)$
-	and $(d, z_{ideal})\approx_{c, O(\eps)}(d', z_{ideal}')$.
-	Combining everything, we conclude that $(d, z)\approx_{c, O(\eps)}(d, z_{ideal})$.
+	First, conditioned on that $\PNaiveStar$ aborts, since dummy strategy will be rejected with overwhelming probability in Hadamard round,
+	we have $(d', z')$ is $O(\varepsilon)$-computationally indistinguishable to $(\Rej, \bot)=(d, z)$.
+	On the other hand, conditioned on $\PNaiveStar$ not aborting, clearly $(d, z)=(d', z')$.
+	So $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d', z')$,
+	which in turn is $\negl(\lambda)$-computationally indistinguishable to $d', z_{ideal}')$.
+	So $\abs{d-d'}\leq O(\eps)$,
+	and $(d, z_{ideal})$ is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
+	Combining everything, we conclude that $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d, z_{ideal})$.
 \end{proof}
@@
 	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$
+	\Ethan{This doesn't seem true; I think we get computational guarantees here at best?}
 \end{theorem}

### 2020-07-30 qpip0.tex
Fix bug

@@
 	\label{thm:zgood-zideal}
-	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$
-	\Ethan{This doesn't seem true; I think we get computational guarantees here at best?}
+	$z_{good, i}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
 \end{theorem}
@@
 	Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
-	$\tr\abs{z_{composite,i}-z_{ideal,i}}=O(\eps)$.
+	$z_{composite,}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
 \end{proof}

### 2020-07-30 qpip0.tex
Smooth out discussions of Mahadev's PiMeasure

@@
 
-In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gives a $\QPIP_0$ protocol for $\BQP$ languages.
-The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that lets a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
-Intuitively, the verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$, before sending $pk$ to the prover.
+In her groundbreaking work, Mahadev gives a $\QPIP_0$ protocol for $\BQP$ languages.
+The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that allow a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
+Specifically, the verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$, before sending $pk$ to the prover.
 The prover commits to a state $\rho$ of its choice using $pk$ and replies with its commitment.
@@
 He sends his choice to the prover, and prover replies accordingly.
-If the verifier chose testing, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency.
+If the verifier chose testing round, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency.
 If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply.

### 2020-07-31 qpip0.tex
Attempt to clean up discussions

@@
 We now show that it is computationally sound.
-\Ethan{Try to word the following a bit better}
-The intuition is that the we run $m$ copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy.
-Therefore if the prover want to cheat, i.e.
-send something not binding in the Hadamard round copy, he would be caught with probability $1-1/m$.
-However, the prover might create correlations between copies that let him cheat with probability much higher than $1/m$.
-We are able to bound the soundness error as $O(1/\sqrt{m})$.
-To prove that, we use the following partition lemma from \cite{arXiv:ChiaChungYam19}, which intuitively says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
+We first use the following partition lemma from \cite{arXiv:ChiaChungYam19}, which intuitively says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
 $G_{0,i}$ represents the subspace that are rejected with high probability in the testing round of $i$-th copy, while $G_{1,i}$  represents the subspace accepted with high probability\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
-Also as a careful reader might have noticed, the prover's space don't happen to split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
-In \cite{arXiv:ChiaChungYam19} this is solved by doing eigenvalue estimation to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
+Also as a careful reader might have noticed, the prover's space don't split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
+In \cite{arXiv:ChiaChungYam19} this is solved by doing eigenvalue estimation \Ethan{Any better ways to describe this...?} to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
 However, states with accept probability really close to the threshold $\gamma$ can not be classified, so we need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.
@@
 
-\Ethan{The following discussion is under construction}
-
 By using \Cref{lem:partition2} iteratively, we can decompose the prover's internal state.
 Let $\ket{\psi}$ be the state the prover holds before he receives $\vec{c}$;
-\Ethan{WLOG $\ket{\psi}$ is pure, or maybe can purify?}
 we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
@@
 For example, $\ket{\psi_{110, \gamma}}$ intuitively corresponds to the component that would pass the first two copies' testing rounds and fail the third one.
-At this point it is tempting to decompose $\ket{\psi}$ into $\ket{\psi_{s, \gamma}}$ where $s\in\zo^m$ and say that $\ket{\psi_{1^m, \gamma}}$ is the only component that is not rejected with high ($1-1/m$) probability;
-however, $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m, \gamma}}$ is only binding for the $m$-th copy.
-Instead, we must make a point-wise argument for each $i\in[m]$, then... \Ethan{TODO}
-
-For all $i\in[m]$, we define
+At this point it is tempting to decompose $\ket{\psi}$ into $\ket{\psi_{s, \gamma}}$ where $s\in\zo^m$,
+and say that $\ket{\psi_{1^m, \gamma}}$ is the only component that is not rejected with high probability.
+This doesn't work, however, as $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m, \gamma}}$ is only binding for the $m$-th copy.
+Instead, we start with a pointwise argument and fix the Hadamard round on the $i$-th copy,
+and show that the corresponding output is $O(\norm{\ket{\psi_{1^{i-1}0}}})$-close to ideal.
+We can later average out this error over the different choices of $i$, since not all $\norm{\ket{\psi_{1^{i-1}0}}}$ can be large at the same time.
+To begin, for all $i\in[m]$, we decompose $\ket{\psi}$ as follows:
 \begin{align} \label{eq:partition-string}
@@
 \end{align}
-where we abuse the notation and use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
+where we use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
 

### 2020-08-01 preliminaries.tex
Reorganize prelim

@@
 %For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
-
-For $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$,
-let $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ denote the trace distance between $\rho_1$ and $\rho_2$.
-We say $\rho_1$ and $\rho_2$ are $\eps$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\eps$.
-For two distributions $f_1$ and $f_2$ over the same finite domain $X$, let $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ denote their total variation distance,
-and we say $f_1$ and $f_2$ are $\eps$-close if $\norm{f_1-f_2}_{TV}\leq\eps$.
 We write $x\xleftarrow{\$}X$ when $x$ is sampled uniformly at random from the set $X$.
-
-\begin{definition} [quantum-classical channels]
-    \label{def:QCChannel}
-    A quantum measurement is given by a set of matrices $\set{M_k}$ such that $M_k\geq0$ and $\sum_k M_k=\id$.
-    We associate to any measurement a map $\Lambda(\rho)=\sum_k \tr(M_k\rho)\proj{k}$
-    with $\{\ket{k}\}$ an orthonormal basis.
-    This map is also called a \emph{quantum-classical channel}.
-\end{definition}
 
@@
 
-\Ethan{Quantum measurements...}
+For $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$,
+let $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ denote the trace distance between $\rho_1$ and $\rho_2$.
+We say $\rho_1$ and $\rho_2$ are $\eps$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\eps$.
+For two distributions $f_1$ and $f_2$ over the same finite domain $X$, let $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ denote their total variation distance,
+and we say $f_1$ and $f_2$ are $\eps$-close if $\norm{f_1-f_2}_{TV}\leq\eps$.
+We additionally denote the following for states that are only computationally indistinguishable (but might be statistically far):
+\begin{definition}
+\label{def:comp-indis}
+    Two ensemble of states $\set{\rho_{1,\lambda}}_{\lambda\in\bbN}$ and $\set{\rho_{2,\lambda}}_{\lambda\in\bbN}$ are \emph{$\eps$-computationally indistinguishable} if for all $\BQP$ distinguishers $\mathsf{D}$ and $\lambda\in\bbN$,
+    $$\abs{\Pr\left[\mathsf{D}(\rho_{1,\lambda})=1\right]-\Pr\left[\mathsf{D}(\rho_{2,\lambda})=1\right]}\leq\eps(\lambda).$$
+    We also denote $\eps$-computational indistinguishability by $\rho_{1,\lambda}\approx_{c, \eps}\rho_{2,\lambda}$.
+    We drop the $\eps$ parameter when it is negligible.
+    We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized states as appropriate.
+    We also extend it to distributions by treating them as mixed states.
+\end{definition}
 
+We denote measurement as follows:
+\begin{definition} [quantum-classical channels]
+    \label{def:QCChannel}
+    A quantum measurement is given by a set of matrices $\set{M_k}$ such that $M_k\geq0$ and $\sum_k M_k=\id$.
+    We associate to any measurement a map $\Lambda(\rho)=\sum_k \tr(M_k\rho)\proj{k}$
+    with $\{\ket{k}\}$ an orthonormal basis.
+    This map is also called a \emph{quantum-classical channel}.
+\end{definition}
+Furthermore, we associate measurement outcomes in $X$ or $Z$ basis with a corresponding random variable as follows:
 \begin{definition}[$M_{XZ}(\rho,h)$]
@@
             It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\eps$.
-        \item (Computational soundness):
+		\item (Computational soundness): \Ethan{TODO write in terms of comp. indistinguishability?}
         For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
@@
 In the context of blind protocols, we consider $x$ as the verifier's private input instead of a common input.
-%the above definitions should be modified so that $x$ is the verifier's private input.
-%We define blindness with an accuracy parameter $\eps$, which exists in protocols for $\SampBQP$ instances;
-%one can leave it out where appropriate, such as in protocols for $\BQP$ languages.
 
-\Ethan{The following is more crypto based
-
-Others don't have a fully general definition,
-or it's just statistical/OTP.
-
-Need explanation/discussion for this.
-Nobody else writes it like this,
-but this is the correct way to write it.
-
-Explain what is this saying.}
+\Ethan{The following blindness definition is more crypto-based, but since we're submitting it to Eurocrypt maybe this is fine as-is?}
 
@@
     \end{itemize}
-\end{definition}
-
-\Ethan{Maybe swap 2.9 and 2.8 or move it up even more.
-If it's before 2.7 then we can just write 2.7 in terms of this.
-
-Consider making this its own section.}
-
-\begin{definition}
-\label{def:comp-indis}
-    %\Ethan{TODO PROOFREAD ME}
-    Two ensemble of states $\set{\rho_{1,\lambda}}_{\lambda\in\bbN}$ and $\set{\rho_{2,\lambda}}_{\lambda\in\bbN}$ are \emph{$\eps$-computationally indistinguishable} if for all $\BQP$ distinguishers $\mathsf{D}$ and $\lambda\in\bbN$,
-    $$\abs{\Pr\left[\mathsf{D}(\rho_{1,\lambda})=1\right]-\Pr\left[\mathsf{D}(\rho_{2,\lambda})=1\right]}\leq\eps(\lambda).$$
-    We also denote $\eps$-computational indistinguishability by $\rho_{1,\lambda}\approx_{c, \eps}\rho_{2,\lambda}$.
-    We drop the $\eps$ parameter when it is negligible.
-    We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized states as appropriate.
-    We also extend it to distributions by treating them as mixed states.
 \end{definition}
@@
 \end{lem}
-
-\fi
-
-\Ethan{Chernoff bound looks like it's in the middle of nowhere. Just get rid of it.}
-
-\iffalse
-\subsection{Chernoff bound}
-
-\begin{thm}
-\label{thm:Chernoff}
-Let $X=\sum_{i=1}^n X_i$ where $X_i$ are independent Bernoulli trials, and $\mu=\E[X]$.
-Then for all $0<\delta<1$,
-$$P[\abs{X-\mu}\geq\delta\mu]\leq2e^{-\frac{\mu\delta^2}{3}}.$$
-\end{thm}
 

### 2020-08-02 preliminaries.tex
Add QPIP streaming model discussion in preliminary

@@
 We model the interaction between a (almost classical) client and a quantum server following \cite{FOCS:Mahadev18a}.
-
-\Ethan{``Streaming" model; can send qubits one-by-one to let client measure many qubits this way.
-
-Tone: Review/introduce. It's not new. Use Urmila's use case as example.}
+When the client has limited quantum capabilities, this is a ``streaming" model.
+That is, the server can send qubits one-by-one to let client measure them sequentially.
+even if the client cannot hold the entire quantum message,
+We do not care about rounds-complexity unless the client is fully classical,
+in which case this model specializes to the standard rounds-based model.
 

### 2020-08-02 preliminaries.tex
Redo some comp. indis. notations

@@
     $$\abs{\Pr\left[\mathsf{D}(\rho_{1,\lambda})=1\right]-\Pr\left[\mathsf{D}(\rho_{2,\lambda})=1\right]}\leq\eps(\lambda).$$
-    We also denote $\eps$-computational indistinguishability by $\rho_{1,\lambda}\approx_{c, \eps}\rho_{2,\lambda}$.
+    % We also denote $\eps$-computational indistinguishability by $\rho_{1,\lambda}\approx_{c, \eps}\rho_{2,\lambda}$.
     We drop the $\eps$ parameter when it is negligible.
@@
             It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\eps$.
-		\item (Computational soundness): \Ethan{TODO write in terms of comp. indistinguishability?}
+		\item (Computational soundness):
+			\Ethan{tried to write in terms of indistinguishability}
         For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
@@
             define $d, z, z_{ideal}$ by the same experiment as above.
-            It holds that
-            $$\abs{\Pr[\mathsf{D}(1^{\lambda}, d,z) = 1] - \Pr[\mathsf{D}(1^{\lambda}, d,z_{ideal}) = 1]} \leq \eps $$
+            It holds that $(d, z)$ is $\eps$-computationally indistinguishable to $(d, z_{ideal})$ over $\lambda$.
+            % $$\abs{\Pr[\mathsf{D}(1^{\lambda}, d,z) = 1] - \Pr[\mathsf{D}(1^{\lambda}, d,z_{ideal}) = 1]} \leq \eps $$
     \end{itemize}

### 2020-08-04 qpip0.tex
Add discussion feedbacks

@@
 
-In this section, we combine the core protocol from \cite{FOCS:Mahadev18a}, which we restate as Protocol~\ref{proto:urmila4}, with \Cref{QPIP1thm} to create a delegation protocol for $\SampBQP$ for fully classical clients.
+In this section, we combine the core protocol from \cite{FOCS:Mahadev18a}, which we restate as Protocol~\ref{proto:urmila4} \Ethan{Just say $\PiMeasure$}, with \Cref{QPIP1thm} to create a delegation protocol for $\SampBQP$ for fully classical clients.
 A direct composition results in Protocol~\ref{proto:qpip0_naive}.
@@
 To boost its soundness, we run $m=\poly(\lambda)$ copies in parallel and test on $m-1$ copies of them, resulting in Protocol~\ref{proto:QPIP0samp}.
-We use techniques from \cite{arXiv:ChiaChungYam19} to prove that Protocol~\ref{proto:QPIP0samp} has soundness error $1/\sqrt{m}$.
+We use techniques from \cite{arXiv:ChiaChungYam19} to prove that Protocol~\ref{proto:QPIP0samp} has soundness error \Ethan{Phrase in terms of accuracy param instead} $1/\sqrt{m}$.
+
+\Ethan{Go even more high level. This roadmap is confusing to people who aren't familiar with the relevant literature}
 
@@
 The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that allow a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
-Specifically, the verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$, before sending $pk$ to the prover.
-The prover commits to a state $\rho$ of its choice using $pk$ and replies with its commitment.
+\Ethan{Talk about how $\PiMeasure$ + $\cVGS$ gives $\QPIP_0$ protocol for $\BQP$}
+
+Specifically, the verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$, before \Ethan{bad choice of word?} sending $pk$ to the prover.
+The prover ``commits" to a state $\rho$ of its choice using $pk$ and replies with its commitment.
 The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}.
@@
 	Let $\PMeasureStar$ be a $\BQP$ cheating prover for $\PiMeasure$ and $\lambda$ be the security parameter.
-Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
+Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability \Ethan{Not precise enough - probability over what?
+For all $h$ or $pk$?} $1-\negl(\lambda)$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
 	\iffalse    
@@
 	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
-	Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting (ie. $y\ne\bot$), $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
-	then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
+	Under the QLWE assumption, \Ethan{Add ``if P satisfies that..."} if conditioned on $\PNaiveStar$ not aborting (ie.
+$y\ne\bot$) \Ethan{Make even more explicit ie.
+say not aborting on round 2}, $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
+	then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$. \Ethan{Check if this notation is defined; give reminder even if it is}
 \end{theorem}
 \begin{proof}
+	\Ethan{We first introduce the \emph{dummy strategy} that we will use...}
 	If the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly,
@@
 We can later average out this error over the different choices of $i$, since not all $\norm{\ket{\psi_{1^{i-1}0}}}$ can be large at the same time.
-To begin, for all $i\in[m]$, we decompose $\ket{\psi}$ as follows:
+To begin, for all $i\in[m]$, we decompose $\ket{\psi}$ as follows: \Ethan{Paragraph break before this; should define everything earlier again}
 \begin{align} \label{eq:partition-string}
@@
 
+\Ethan{TODO explain more pointwise vs average argument w.r.t. $pk, y$}
+
 We denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as $P_{acc,i,z}$.
@@
 Note that we have averaged over $\vec{pk}, \vec{y}$ where as previously everything has fixed $\vec{pk}$ and $\vec{y}$.
-\Ethan{Here $y$ is implicitly dependent on $pk$. Might need to clarify what the expected value over $y$ means?}
 Now we define
+\Ethan{TODO what is this? Need intuitive idea.}
 \begin{align}
@@
 Now we're ready to show that $z_{i, good}$ is close to $z_i$.
+\Ethan{Not really ``close to" though. Could use a lot more discussion here anyways.}
 
@@
 	$$\tr\abs{z_i-z_{i, good}}\leq\E_\gamma\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)$$
+	\Ethan{This should've been a lemma. Same for the next theorem.}
 \end{theorem}

### 2020-08-05 qpip0.tex
Start working on meeting feedbacks

@@
 The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that allow a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
-\Ethan{Talk about how $\PiMeasure$ + $\cVGS$ gives $\QPIP_0$ protocol for $\BQP$}
+One can see $\cVGS$ as a $\QPIP_1$ protocol where the prover sends copies of ground state to the verifier to measure;
+which can then be transformed to a $\QPIP_0$ protocol by replacing the verifier's measurement with calls to $\PiMeasure$.
 
-Specifically, the verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$, before \Ethan{bad choice of word?} sending $pk$ to the prover.
+The details of $\PiMeasure$ is as follows.
+The verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$.
+It sends $pk$ to the prover.
 The prover ``commits" to a state $\rho$ of its choice using $pk$ and replies with its commitment.
-The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}.
+\Ethan{Need more intuition} The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}.
 He sends his choice to the prover, and prover replies accordingly.
@@
 However, we can show that \Cref{proto:qpip0_naive} has a binding property similar to \Cref{proto:urmila4}.
+Namely, if a cheating prover passes the testing round with overwhelming probability conditioned on it doesn't ``give up" on the 2nd message, then... \Ethan{Word this better}
+The intuition of the proof is to construct another $\BQP$ prover $\Pstar$ which, intuitively, uses $\PNaiveStar$'s strategy when it doesn't abort,
+otherwise commits with the maximally mixed states.\Ethan{Finish this high level proof sketch}
+...in order to use \Cref{lem:urmila-binding}.
+We state the theorem and proof in full technical details as below.
 
@@
 \begin{proof}
-	\Ethan{We first introduce the \emph{dummy strategy} that we will use...}
-	If the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly,
-	it would be accepted in the testing round with probability $1-\negl(\lambda)$,
+	We first introduce the \emph{dummy strategy} where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
+	It is straightforward to verify that this prover would be accepted in the testing round with probability $1-\negl(\lambda)$,
 	but has negligible probability passing the verification after the Hadamard round.
-	We call this the \emph{dummy strategy}.
 
@@
 		\item The prover generates $\vec{a}$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
-		\item \label{step:multi-testing}
-			The verifier computes the outcome for each round as in \stepref{naive-output} of $\PiNaive$.
+		\item The verifier computes the outcome for each round as in \stepref{naive-output} of $\PiNaive$.
 			If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
@@
 
-Now we're ready to show that $z_{i, good}$ is close to $z_i$.
-\Ethan{Not really ``close to" though. Could use a lot more discussion here anyways.}
+Now we can estimate $z_i$ using $z_{i, good}$, with errors on the orders of $\norm{\ket{\psi_{1^{i-1}0}}}$.
+This error might not be small in general,
+but we can average it out later by considering uniformly random $i\in[m]$.
+The analysis is tedious but straightforward;
+we simply expand $z_i$ and bound the terms other than $z_{i, good}$.
 
-\begin{theorem}
+\begin{lemma}
 	\label{thm:zi-zgoodi}
 	$$\tr\abs{z_i-z_{i, good}}\leq\E_\gamma\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)$$
-	\Ethan{This should've been a lemma. Same for the next theorem.}
-\end{theorem}
+\end{lemma}
 \begin{proof}
@@
 We show that $z_{ideal, i}$ is close to $z_{good, i}$.
-\begin{theorem}
+\begin{lemma}
 	\label{thm:zgood-zideal}
 	$z_{good, i}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
-\end{theorem}
+\end{lemma}
 \begin{proof}

### 2020-08-05 blind.tex
Remove outdated author notes

@@
 Second, $\Pblindstar$ may send invalid ciphertexts to $V$, so the execution of $\Piblind$ may not simulate a valid execution of $\Pi$.
-\Ethan{Either ways, we need $\QHE$ to never fail on decryption, in both this naive $\Piblind$ and our actual $\Piblind$. So there can't be ``invalid ciphertexts" either ways.}
 
 To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol.
-For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext \Ethan{Need to mention somewhere that if $\QDec$ fails, it outputs $\bot$ instead of aborting}, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$.
+For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$.
 Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoids the issue of circuit privacy.

### 2020-08-16 qpip0.tex
Make QPIP0 intro easier to understand

@@
 
-In this section, we combine the core protocol from \cite{FOCS:Mahadev18a}, which we restate as Protocol~\ref{proto:urmila4} \Ethan{Just say $\PiMeasure$}, with \Cref{QPIP1thm} to create a delegation protocol for $\SampBQP$ for fully classical clients.
-A direct composition results in Protocol~\ref{proto:qpip0_naive}.
-However, as we will see in \Cref{sec:urmila4}, Protocol~\ref{proto:urmila4} has a peculiar and weak guarantee, so \Cref{proto:qpip0_naive} don't have any reasonable completeness and soundness.
-To boost its soundness, we run $m=\poly(\lambda)$ copies in parallel and test on $m-1$ copies of them, resulting in Protocol~\ref{proto:QPIP0samp}.
-We use techniques from \cite{arXiv:ChiaChungYam19} to prove that Protocol~\ref{proto:QPIP0samp} has soundness error \Ethan{Phrase in terms of accuracy param instead} $1/\sqrt{m}$.
+\Ethan{The following two paragraphs have been rewritten to be more high-level}
 
-\Ethan{Go even more high level. This roadmap is confusing to people who aren't familiar with the relevant literature}
+In this section, we create a delegation protocol for $\SampBQP$ with fully classical clients following the approach taken in \cite{FOCS:Mahadev18a}.
+The core protocol, $\PiMeasure$, allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
+By asking the prover to prepare and commit copies of a certificate for the client to verify, one obtains a $\QPIP_0$ protocol for $\BQP$.
+
+Composing our $\PiSamp$ with $\PiMeasure$ directly, however, results in $\PiNaive$ which does not provide reasonable completeness or accuracy guarantees.
+This is due to $\PiMeasure$ itself having peculiar and weak guarantees:
+particularly, the client doesn't always obtain measurement outcomes even if the server were honest.
+To overcome this challenge, we run $m=\poly(\lambda)$-copies of $\PiNaive$ in parallel to produce a constant-round $\PiSampZ$.
+Using techniques from \cite{arXiv:ChiaChungYam19}, we prove that $\PiSampZ$ has accuracy error $O(1/\sqrt{m})$.
 
@@
 
-In her groundbreaking work, Mahadev gives a $\QPIP_0$ protocol for $\BQP$ languages.
-The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that allow a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
-One can see $\cVGS$ as a $\QPIP_1$ protocol where the prover sends copies of ground state to the verifier to measure;
-which can then be transformed to a $\QPIP_0$ protocol by replacing the verifier's measurement with calls to $\PiMeasure$.
-
-The details of $\PiMeasure$ is as follows.
+$\PiMeasure$ is a 4-round protocol played between a verifier (which corresponds to our client) and a prover (which corresponds to our server).
+The first two rounds are similar to the typical commit phase.
 The verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$.
 It sends $pk$ to the prover.
-The prover ``commits" to a state $\rho$ of its choice using $pk$ and replies with its commitment.
-\Ethan{Need more intuition} The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}.
+The prover ``commits" to a state $\rho$ of its choice using $pk$ and replies with its commitment $y$.
+\Ethan{Fix the following...}
+The verifier at this point chooses between the ability to catch cheating provers and generate outputs.
+If it suspects a prover is cheating, it runs a \emph{testing round},
+which catches cheating provers at the cost of obtaining outputs.
+Otherwise it runs a \emph{Hadamard round},
+where it obtains a potentially incorrect output depending on whether the prover cheats.
+
+The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}.
 He sends his choice to the prover, and prover replies accordingly.
@@
 If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply.
-\cite{FOCS:Mahadev18a} shows a ``binding" property of $\PiMeasure$: if a prover would always succeed on the testing round, then there exists some $\rho$ so that the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round, no matter what $h$ the verifier has picked at the beginning.
 
@@
 $\PiMeasure$ has negligible completeness errors.
-On the other hand, as the verifier learns the measurement outcome only on Hadamard round, the protocol offers no standard soundness guarantees;
-instead, it achieves the following \emph{binding property} that gives weaker guarantees against cheating provers.
+It also gives the following \emph{binding property} against cheating provers:
+if a prover would always succeed on the testing round, then there exists some $\rho$ so that the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round, no matter what $h$ was chosen at the beginning.
+\Ethan{Say somewhere that a ``prover" is fully described by two unitaries}
 

### 2020-08-17 qpip0.tex
Fix intro for measurement protocol

@@
 
-$\PiMeasure$ is a 4-round protocol played between a verifier (which corresponds to our client) and a prover (which corresponds to our server).
-The first two rounds are similar to the typical commit phase.
+$\PiMeasure$ is a 4-round protocol between a verifier (which corresponds to our client) and a prover (which corresponds to our server).
 The verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$.
@@
 The prover ``commits" to a state $\rho$ of its choice using $pk$ and replies with its commitment $y$.
-\Ethan{Fix the following...}
-The verifier at this point chooses between the ability to catch cheating provers and generate outputs.
-If it suspects a prover is cheating, it runs a \emph{testing round},
-which catches cheating provers at the cost of obtaining outputs.
-Otherwise it runs a \emph{Hadamard round},
-where it obtains a potentially incorrect output depending on whether the prover cheats.
-
-The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}.
+The verifier must then choose between two options: do a \emph{testing round} or do a \emph{Hadamard round}.
+In a testing round, the verifier can catch cheating provers, but generates no outputs;
+on the other hand, in a Hadamard round the verifier loses the opportunity to catch cheating provers.
 He sends his choice to the prover, and prover replies accordingly.
@@
 If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply.
-
 We now formally describe the interface of $\PiMeasure$ while omitting the implementation details.
@@
 $\PiMeasure$ has negligible completeness errors.
-It also gives the following \emph{binding property} against cheating provers:
+It gives the following \emph{binding property} against cheating provers:
 if a prover would always succeed on the testing round, then there exists some $\rho$ so that the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round, no matter what $h$ was chosen at the beginning.

### 2020-08-20 qpip0.tex
Fix grammar

@@
 The prover ``commits" to a state $\rho$ of its choice using $pk$ and replies with its commitment $y$.
-The verifier must then choose between two options: do a \emph{testing round} or do a \emph{Hadamard round}.
-In a testing round, the verifier can catch cheating provers, but generates no outputs;
+The verifier must then choose between two options: do a \emph{testing round} or a \emph{Hadamard round}.
+In a testing round the verifier can catch cheating provers, but generates no outputs;
 on the other hand, in a Hadamard round the verifier loses the opportunity to catch cheating provers.
@@
 If the verifier chose testing round, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency.
-If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply.
+If the verifier chose Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply.
 We now formally describe the interface of $\PiMeasure$ while omitting the implementation details.

### 2020-08-22 qpip0.tex
Handle more QPIP0 author notes

@@
 	Let $\PMeasureStar$ be a $\BQP$ cheating prover for $\PiMeasure$ and $\lambda$ be the security parameter.
-Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability \Ethan{Not precise enough - probability over what?
-For all $h$ or $pk$?} $1-\negl(\lambda)$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
+Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
 	\iffalse    
@@
 First, since the verifier doesn't get a sample if he had chosen the testing round in Step~\ref{step:c-urmila-in-naive}, the protocol has completeness error at least $1/2$.
-Moreover, since Protocol~\ref{proto:urmila4} does not check anything on the Hadamard round, a cheating prover can give up passing the testing round and breaks the commitment on the Hadamard round, with only a constant $1/2$ probability of being caught.
-However, we can show that \Cref{proto:qpip0_naive} has a binding property similar to \Cref{proto:urmila4}.
-Namely, if a cheating prover passes the testing round with overwhelming probability conditioned on it doesn't ``give up" on the 2nd message, then... \Ethan{Word this better}
-The intuition of the proof is to construct another $\BQP$ prover $\Pstar$ which, intuitively, uses $\PNaiveStar$'s strategy when it doesn't abort,
-otherwise commits with the maximally mixed states.\Ethan{Finish this high level proof sketch}
-...in order to use \Cref{lem:urmila-binding}.
-We state the theorem and proof in full technical details as below.
+Moreover, since $\PiMeasure$ does not check anything on the Hadamard round, a cheating prover can give up passing the testing round and breaks the commitment on the Hadamard round, with only a constant $1/2$ probability of being caught.
+However, we can show that $\PiNaive$ has a binding property similar to $\PiMeasure$:
+if a cheating prover $\PNaiveStar$, conditioned on it doesn't ``give up" on the second message, passes the testing round with overwhelming probability,
+then the output $(d, z)\leftarrow(\PNaiveStar, \VNaive)$ is close to $(d, z_{ideal})$.
+Recall the ideal output
+$$\begin{cases}
+	z_{ideal}=\bot & \text{if } d=\Rej\\
+	z_{ideal}\leftarrow D_x & \text{if } d=\Acc
+\end{cases}$$
+is drawn from the true distribution instead when $\PNaiveStar$ is accepted.
+The intuition of the proof is to reduce to \Cref{lem:urmila-binding} by constructing another $\BQP$ prover $\Pstar$ for $\PiMeasure$.
+Specifically, $\Pstar$ uses $\PNaiveStar$'s strategy when it doesn't abort, otherwise honestly inputs some default state for the verifier to measure.
+We now state the theorem and proof.
 
@@
 	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
-	Under the QLWE assumption, \Ethan{Add ``if P satisfies that..."} if conditioned on $\PNaiveStar$ not aborting (ie.
-$y\ne\bot$) \Ethan{Make even more explicit ie.
-say not aborting on round 2}, $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
-	then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$. \Ethan{Check if this notation is defined; give reminder even if it is}
+	Suppose that conditioned on $\PNaiveStar$ not aborting on the second round (ie. $y\ne\bot$), it passes the testing round with overwhelming probability.
+	Under the QLWE assumption, then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
 \end{theorem}

### 2020-08-22 qpip0.tex
Remove unnecessary action item
Handle another QPIP0 action item

@@
 if a prover would always succeed on the testing round, then there exists some $\rho$ so that the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round, no matter what $h$ was chosen at the beginning.
-\Ethan{Say somewhere that a ``prover" is fully described by two unitaries}
 
@@
 Also as a careful reader might have noticed, the prover's space don't split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
-In \cite{arXiv:ChiaChungYam19} this is solved by doing eigenvalue estimation \Ethan{Any better ways to describe this...?} to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
+In \cite{arXiv:ChiaChungYam19} this is solved by splitting the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
 However, states with accept probability really close to the threshold $\gamma$ can not be classified, so we need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.

### 2020-08-22 qpip0.tex
cite measurement protocol binding property

@@
 
-\begin{lemma}[binding property of $\PiMeasure$]
+\begin{lemma}[binding property of $\PiMeasure$; special case of Claim 7.1 in \cite{FOCS:Mahadev18a}]
 	\label{lem:urmila-binding}
@@
 Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
-	\iffalse    
-	Suppose that for all $\lambda\in\bbN$ and $h\in\zo^*$ \Ethan{or $\zo^n$?},
-	$\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$.
-	Then, under the QLWE assumption, there exists some $\rho$ so that for all $h$,
-	The verifier's output on the Hadamard round is $\negl(\lambda)$-computationally indistinguishable from $M_{XZ}(\rho, h)$.
-	\fi
 \end{lemma}

### 2020-08-22 qpip0.tex
Handle more QPIP0 action items

@@
 We can later average out this error over the different choices of $i$, since not all $\norm{\ket{\psi_{1^{i-1}0}}}$ can be large at the same time.
-To begin, for all $i\in[m]$, we decompose $\ket{\psi}$ as follows: \Ethan{Paragraph break before this; should define everything earlier again}
+
+To begin, let $\ket{\psi}$ be the state the prover holds before he receives $\vec{c}$.
+For all $i\in[m]$, we decompose $\ket{\psi}$ as
 \begin{align} \label{eq:partition-string}
@@
 \end{align}
-where we use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
-
-\Ethan{TODO explain more pointwise vs average argument w.r.t. $pk, y$}
+where
+$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}\ldots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$
+and $\ket{\psi_{err,i,\gamma}}$ denotes the error state from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
 
@@
 Now we define
-\Ethan{TODO what is this? Need intuitive idea.}
 \begin{align}
@@
 \end{align}
-which we can show is close to $z_i$.
-However, before doing so, we first present a couple lemmas that we will need.
+as the output corresponding to the component that would pass all $i$ testing rounds.
+We will show that it is $O(\norm{\ket{\psi_{1^{i-1}0}}})$-close to $z_i$.
+Before doing so, we first present a couple technical lemma.
 \begin{lemma}\label{lem:samp-tech}
@@
 
-Now we can estimate $z_i$ using $z_{i, good}$, with errors on the orders of $\norm{\ket{\psi_{1^{i-1}0}}}$.
+Now we can estimate $z_i$ using $z_{good, i}$, with errors on the orders of $\norm{\ket{\psi_{1^{i-1}0}}}$.
 This error might not be small in general,
@@
 we simply expand $z_i$ and bound the terms other than $z_{i, good}$.
+\Ethan{Analysis missing expected value over $pk, y$?}
 
@@
 \begin{proof}
-	We rewrite \Cref{eq:partition-string}.
+	We rewrite \Cref{eq:partition-string}
 	$$\ket{\psi}=\E_{\gamma}\left[
@@
 	\right]$$
-	Then we expand $z_i$ as
+	and expand $z_i$ as
 	\begin{align}

### 2020-08-23 qpip0.tex
Remove unnecessary author note
Handle another QPIP0 action item
Polish wording
Polish qpip0

@@
 \label{sec:qpip0_all}
-
-\Ethan{The following two paragraphs have been rewritten to be more high-level}
 
@@
 We will show that it is $O(\norm{\ket{\psi_{1^{i-1}0}}})$-close to $z_i$.
-Before doing so, we first present a couple technical lemma.
+Before doing so, we present a couple technical lemma.
 \begin{lemma}\label{lem:samp-tech}
@@
 we simply expand $z_i$ and bound the terms other than $z_{i, good}$.
-\Ethan{Analysis missing expected value over $pk, y$?}
 
@@
 	\label{thm:zi-zgoodi}
-	$$\tr\abs{z_i-z_{i, good}}\leq\E_\gamma\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)$$
+	$$\tr\abs{z_i-z_{i, good}}\leq\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)$$
 \end{lemma}
@@
 	\begin{align}
-		z_i=& z_{good,i}+ \E_\gamma \sum_z \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
+		z_i=& z_{good,i}+ \E_{pk, y, \gamma} \sum_z \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
 		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \nn \\
@@
 	\begin{align*}
-		\tr|z_i-z_{good,i}|\leq& \E_\gamma \sum_z \L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|+
+		\tr|z_i-z_{good,i}|\leq& \E_{pk, y, \gamma} \sum_z \L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|+
 		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R. \\
@@
 \begin{proof}
-	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}.
-Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of Protocol~\ref{proto:qpip0_naive} where Protocol~\ref{proto:urmila4} is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.
+	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for $\PiSampZ$, consider the following composite strategy of the prover for $\PiNaive$.
+Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of $\PiNaive$ where $\PiMeasure$ is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.
 
-	The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of Protocol~\ref{proto:urmila4} in Protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself.
+	The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of $\PiMeasure$ in $\PiSampZ$ and simulating other $m-1$ copies by himself.
 The prover then picks a uniformly random $\gamma$ and  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
@@
 		\leq&  \frac{1}{m}\sum_i\tr| (z_i-z_{good,i})| \nn \\
-		\leq&  \frac{1}{m}\sum_i\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
+		\leq&  \frac{1}{m}\sum_i\L[\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
 		\leq&  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%

### 2020-08-23 qpip0.tex
Fix typo

@@
 	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for $\PiSampZ$, consider the following composite strategy of the prover for $\PiNaive$.
-Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of $\PiNaive$ where $\PiMeasure$ is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.
+Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of $\PiNaive$ where $\PiMeasure$ is run, so we describe the prover's action in terms of the four rounds of communication in $\PiMeasure$.
 

### 2020-08-23 qpip0.tex
Fix another typo

@@
 	Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
-	$z_{composite,}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
+	$z_{composite}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
 \end{proof}

### 2020-08-29 preliminaries.tex
Add discussion feedbacks
Remove another unnecessary action item
Polish

@@
 
-\Ethan{After this point, add more remarks in this section}
-
 We define the sampling version of $\BQP$ based on \cite{aaronson_2013}.
@@
 We model the interaction between a (almost classical) client and a quantum server following \cite{FOCS:Mahadev18a}.
-When the client has limited quantum capabilities, this is a ``streaming" model.
-That is, the server can send qubits one-by-one to let client measure them sequentially.
-even if the client cannot hold the entire quantum message,
-We do not care about rounds-complexity unless the client is fully classical,
-in which case this model specializes to the standard rounds-based model.
+When the client has limited quantum memories, this is a ``streaming" model.
+That is, the server can send qubits one-by-one to let client measure them sequentially,
+even if the client cannot hold the entire quantum message.
+When the client is fully classical,
+this model specializes to the standard rounds-based model.
 
@@
 
-\Ethan{Need discussion for dfn. 2.7.
-Currently there's a remark after about not needing soundness error.
-Discuss more.
-
-Difference between SampBQP and BQP definitions.
-In particular, SampBQP has additional output (not 0/1).
-
-Two sources of error. Kinda like ``DI" device independent/QKD?
-Condition on acc...
-Really depends on target audience. If not crypto...
-
-Maybe just remark that there are 2 params but this definition captures both
-
-Again, it's different from BQP so explain why/where.
-Make it more friendly to people who aren't familiar with this approach.
-
-Also discuss whether soundness error needs additional param. besides inherited from SampBQP}
+It is straightforward to write down what it means for a $\QPIP_\tau$ protocol to recognize a $\BQP$ language.
 
@@
 \end{definition}
+
+It is less simple to state what it means for a $\QPIP_\tau$ protocol to solve a $\SampBQP$ instance.
+We cannot hope for the protocol's output distribution to be close to the true distribution,
+since a cheating prover can abort to force the verifier output $\bot$ with arbitrary probability.
+The natural relaxation is to first condition on acceptance, then require the same of the output distribution.
+By doing so, we arrive at the following definition.
 
@@
             It holds that $(d, z)$ is $\eps$-computationally indistinguishable to $(d, z_{ideal})$ over $\lambda$.
-            % $$\abs{\Pr[\mathsf{D}(1^{\lambda}, d,z) = 1] - \Pr[\mathsf{D}(1^{\lambda}, d,z_{ideal}) = 1]} \leq \eps $$
     \end{itemize}
@@
 \subsection{Quantum Homomorphic Encryption Schemes}
-
-\Ethan{This section should be fine; just leave it alone.
-It's just technicalities copied from another paper.}
 

### 2020-09-02 qpip0.tex
Add discussion notes

@@
 Using techniques from \cite{arXiv:ChiaChungYam19}, we prove that $\PiSampZ$ has accuracy error $O(1/\sqrt{m})$.
+
+\Ethan{Above is too concise; might be difficult to read. Either just add ``as we will see..." or expand.}
+
+\Ethan{Maybe explain technical stuff here?}
 
@@
 However, we can show that $\PiNaive$ has a binding property similar to $\PiMeasure$:
-if a cheating prover $\PNaiveStar$, conditioned on it doesn't ``give up" on the second message, passes the testing round with overwhelming probability,
+if a cheating prover $\PNaiveStar$, conditioned on it doesn't ``give up" \Ethan{Ambiguous.
+also need to associate this with $y=\bot$ if we haven't yet.} on the second message \Ethan{Move this clause to the end and say ``whenever it doesn't abort"}, passes the testing round with overwhelming probability,
 then the output $(d, z)\leftarrow(\PNaiveStar, \VNaive)$ is close to $(d, z_{ideal})$.
@@
 The intuition of the proof is to reduce to \Cref{lem:urmila-binding} by constructing another $\BQP$ prover $\Pstar$ for $\PiMeasure$.
-Specifically, $\Pstar$ uses $\PNaiveStar$'s strategy when it doesn't abort, otherwise honestly inputs some default state for the verifier to measure.
+Specifically, $\Pstar$ uses $\PNaiveStar$'s strategy when it doesn't abort, otherwise honestly chooses some default state for the verifier to measure.
 We now state the theorem and proof.
@@
 	Under the QLWE assumption, then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
+	\Ethan{Write the conditional probability in terms of equations}
 \end{theorem}
@@
 
-	Now we construct another cheating $\BQP$ prover $\Pstar$ that is perfect and non-aborting as follows.
+	Now we construct another cheating $\BQP$ prover $\Pstar$ that is perfect \Ethan{``almost perfect"?} and non-aborting as follows.
 	For the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
@@
 	So $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d', z')$,
-	which in turn is $\negl(\lambda)$-computationally indistinguishable to $d', z_{ideal}')$.
+	which in turn is $\negl(\lambda)$-computationally indistinguishable to $(d', z_{ideal}')$.
 	So $\abs{d-d'}\leq O(\eps)$,
@@
 We now introduce our $\QPIP_0$ protocol $\PiSampZ$ for $\SampBQP$.
-It is essentially a $m$-fold parallel repetition of $\PiNaive$.
-Instead of having each copy running testing round or Hadamard round uniformly at random, we randomly pick one copy to run Hadamard round to get our samples, and run testing round on all other $m-1$ copies.
+It is essentially a $m$-fold parallel repetition of $\PiNaive$,
+but instead of having each copy running testing round or Hadamard round uniformly at random, we randomly pick one copy to run Hadamard round to get our samples and run testing round on all other $m-1$ copies.
+\Ethan{Maybe say the $1/m$ thing here?}
 In the description of our protocol below, we describe $\PiNaive$ and $\PiMeasure$ in details in order to introduce notations that we need in our analysis.
@@
 
-Clearly $\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness error.
-We now show that it is computationally sound.
+Clearly \Ethan{If it's clear then just say why. Or say ``by inspection..."} $\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness error.
+We now show that it is computationally sound. \Ethan{Lacking intuition currently...}
 We first use the following partition lemma from \cite{arXiv:ChiaChungYam19}, which intuitively says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
-$G_{0,i}$ represents the subspace that are rejected with high probability in the testing round of $i$-th copy, while $G_{1,i}$  represents the subspace accepted with high probability\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
+$G_{0,i}$ represents the subspace that are rejected with high probability \Ethan{change the characterization to whether the prover ``knows"...} in the testing round of $i$-th copy, while $G_{1,i}$  represents the subspace accepted with high probability\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
+\Ethan{Maybe technical overview goes here. That ``tree or something"...}
+\Ethan{TODO then talk about why other naive approaches don't work: stuff doesn't commute and whatnot}
 Also as a careful reader might have noticed, the prover's space don't split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
@@
 Property~\ref{property-partition-norm-sum} comes from the fact that $G_0$ and $G_1$ are post-selections of orthogonal results of the same $G$.}]\label{lem:partition2}
-	Let $\lambda$ be the security parameter and  $\eps$ be the accuracy parameter.
+	Let $\lambda$ be the security parameter and  $\eps$ be the accuracy parameter \Ethan{Is this the global one?}.
 Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message.
@@
 By using \Cref{lem:partition2} iteratively, we can decompose the prover's internal state.
+\Ethan{The following is still too quick. Don't use all properties up front in short succession.}
 Let $\ket{\psi}$ be the state the prover holds before he receives $\vec{c}$;
 we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
-For all $k\leq m$, $d\in \zo^k$, $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and $\ket{\psi} \in H_{\regX,\regZ}$, define
+For all $k\leq m$, $d\in \zo^k$, $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and $\ket{\psi} \in H_{\regX,\regZ}$, define \Ethan{This isn't correct; $\gamma$ should be independent for each copy}
 $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}\ldots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}.$$
-For example, $\ket{\psi_{110, \gamma}}$ intuitively corresponds to the component that would pass the first two copies' testing rounds and fail the third one.
+For example \Ethan{``take $k=3$"...}, $\ket{\psi_{110, \gamma}}$ intuitively corresponds to the component that would pass the first two copies' testing rounds and fail the third one.
+\Ethan{Comment about $\ket{\psi_{good}}$ or whatever it is}
 At this point it is tempting to decompose $\ket{\psi}$ into $\ket{\psi_{s, \gamma}}$ where $s\in\zo^m$,

### 2020-09-02 introduction.tex
Add discussion feedbacks

@@
  %Even though the relation between $\BQP$ and $\SampBQP$ is relatively understood in the plain model,
+ \Ethan{Maybe replace the following sentence with the actual challenges? Ie. unclear how to run many copies to reduce errors; classical approach with PRG seed doesn't work either}
 However, it is far from clear whether the subtle difference between $\BQP$ and its sampling version could lead to
@@
 % \Ethan{application: verifiable private constant round delegation}
-
-% \Ethan{Below is my attempt to talk about it in my SoP}
-
-% It was proven that BQP=BQIP\hannote{who  when and cite}.
-That is, if a quantum computer can efficiently solve a given decision problem, then it can also efficiently convince a classical machine of its solution.
-I'm generalizing this to arbitrary efficient quantum computations.
-The proof for decision problems involves the classical verifier reducing the problem to a local Hamiltonian instance; the quantum prover would then commit its certificate and act as the verifier’s trusted measurement device as put forth in ``Classical Verification of Quantum Computations" by Mahadev.
-It isn't as trivial as it may seem.
-Repeating the scheme for each qubit loses the information carried by entanglements and throws off the joint distribution between qubits.
-Simply measuring the entire output register instead is difficult to analyze.
-For decision problems, it’s not hard to argue that a malicious prover cannot do better than sending identical copies of some pure state unentangled with each other.
-That same reasoning doesn't apply here a priori.
-I've been trying to get a grasp on the particular structure of the local Hamiltonian reduction in order to better analyze it.
-
-% \Ethan{Below is my attempt to talk about it in my research proposal}
-
-% We are interested in delegating quantum computations from a classical client to an untrusted quantum server.
-Under this setting, the client would send the server a quantum circuit and an initial state.
-Then, through interaction with the honest server, the client obtains a measurement result as if he measured the true output of the circuit.
-If the server attempts to deceive the client, the client should reject it.
-The case where the circuit encodes a decision problem has been well-studied, and we're now trying to generalize those results to circuits with possibly many bits of output.
-
-% If the circuit encodes a decision problem, then by considering adiabatic quantum computation, there exists a reduction to local Hamiltonian.
-Local Hamiltonian is QMA-complete, so there's a certificate for every yes-instance, and no valid certificates for any no-instances.
-An introduction can be found in Kitaev, Shen, and Vyalyi's "Classical and Quantum Computation".
-Furthermore, Biamonte and Love's "Realizable Hamiltonians for Universal Adiabatic Quantum Computers" states that these local Hamiltonians have very simple forms, which in turn implies that in order to check such certificates one only requires abilities to receive qubits and perform X/Z measurements.
-Based on this observation, Mahadev constructed a protocol in "Classical Verification of Quantum Computations" which, under the LWE assumption (a widely believed conjecture in quantum cryptography), allows the prover to commit qubits and act as the verfier's trusted X/Z measurement device.
-This solves the delegation of decision problem from a fully classical client to a quantum server.
-
-% To generalize delegation of quantum computations to allow long output, simply repeating the known protocol for every output qubit doesn't work.
-The joint probability distribution between qubits would be incorrect due to entanglements.
-In fact, generally the output qubits encode sampling problems rather than decision problems.
-Furthermore, for decision problems one can argue that the prover's optimal strategy is to send identical copies of a certificate, so Chernoff bound can be applied, but said argument doesn't generalize to sampling problems either.
-To overcome these challenges, we start by modifying the local Hamiltonian construction so it is compatible with long output.
-We then analyze our protocol's soundness more carefully, before using Mahadev's result as a black box to solve the long output case too for fully classical clients.
-
-% A possible application for our long output protocol is to make the computation not only verifiable, but also private in the sense of homomorphic encryptions.
-That is, the input is encrypted before being sent to the server.
-The server computes on the encrypted input, obtaining an encrypted output.
-The client then receives and decrypts the output.
-Here we can combine results from Mahadev's "Classical Homomorphic Encryption for Quantum Circuits" with our long output scheme.
-The client can simply send the homomorphic evaluation circuit to the server with the encrypted input.

### 2020-09-03 qpip0.tex
Attempt to rewrite intro for QPIP0

@@
 The core protocol, $\PiMeasure$, allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
-By asking the prover to prepare and commit copies of a certificate for the client to verify, one obtains a $\QPIP_0$ protocol for $\BQP$.
+Composing it with $\QPIP_1$ protocol for $\BQP$ in \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
+Now we try to compose $\PiMeasure$ similarly with our $\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$
 
-Composing our $\PiSamp$ with $\PiMeasure$ directly, however, results in $\PiNaive$ which does not provide reasonable completeness or accuracy guarantees.
-This is due to $\PiMeasure$ itself having peculiar and weak guarantees:
-particularly, the client doesn't always obtain measurement outcomes even if the server were honest.
-To overcome this challenge, we run $m=\poly(\lambda)$-copies of $\PiNaive$ in parallel to produce a constant-round $\PiSampZ$.
-Using techniques from \cite{arXiv:ChiaChungYam19}, we prove that $\PiSampZ$ has accuracy error $O(1/\sqrt{m})$.
-
-\Ethan{Above is too concise; might be difficult to read. Either just add ``as we will see..." or expand.}
-
-\Ethan{Maybe explain technical stuff here?}
+A direct composition $\PiSamp$ with $\PiMeasure$, however, results in $\PiNaive$ which does not provide reasonable completeness or accuracy guarantees.
+As we will see, this is due to $\PiMeasure$ itself having peculiar and weak guarantees:
+the client doesn't always obtain measurement outcomes even if the server were honest.
+To overcome this challenge, we run many copies of $\PiNaive$ in parallel so the verifier can generate its outputs from some copy.
+We spend the majority of this section showing the soundness of this parallel repetition.
 
@@
 In a testing round the verifier can catch cheating provers, but generates no outputs;
-on the other hand, in a Hadamard round the verifier loses the opportunity to catch cheating provers.
+on the other hand, in a Hadamard round the verifier loses the opportunity \Ethan{focus on what the round can do, not what they can't} to catch cheating provers.
 He sends his choice to the prover, and prover replies accordingly.

### 2020-09-03 preliminaries.tex
Implement suggestions from meeting

@@
 }
+This version has an inverse-polynomial error because...
+\Ethan{TODO cite the other paper and something about near-term quantum computers}
 
@@
 The natural relaxation is to first condition on acceptance, then require the same of the output distribution.
-By doing so, we arrive at the following definition.
+We must also add that the acceptance probability is at least noticeable.
+By combining these two conditions, we arrive at the following definition.
 

### 2020-09-03 qpip0.tex
Implement suggestions from meeting

@@
 The core protocol, $\PiMeasure$, allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
-Composing it with $\QPIP_1$ protocol for $\BQP$ in \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
-Now we try to compose $\PiMeasure$ similarly with our $\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$
+Composing it with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
+We now try to compose $\PiMeasure$ similarly with our $\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$
 
-A direct composition $\PiSamp$ with $\PiMeasure$, however, results in $\PiNaive$ which does not provide reasonable completeness or accuracy guarantees.
+A direct composition between $\PiSamp$ and $\PiMeasure$, however, results in $\PiNaive$ which does not provide reasonable completeness or accuracy guarantees.
 As we will see, this is due to $\PiMeasure$ itself having peculiar and weak guarantees:
@@
 The verifier must then choose between two options: do a \emph{testing round} or a \emph{Hadamard round}.
-In a testing round the verifier can catch cheating provers, but generates no outputs;
-on the other hand, in a Hadamard round the verifier loses the opportunity \Ethan{focus on what the round can do, not what they can't} to catch cheating provers.
+In a testing round the verifier can catch cheating provers,
+and in a Hadamard round the verifier receives some measurement outcome.
 He sends his choice to the prover, and prover replies accordingly.
@@
 It gives the following \emph{binding property} against cheating provers:
-if a prover would always succeed on the testing round, then there exists some $\rho$ so that the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round, no matter what $h$ was chosen at the beginning.
+if a prover would always succeed on the testing round, then there exists some $\rho$ so that for any $h$ the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round.
 
@@
 However, we can show that $\PiNaive$ has a binding property similar to $\PiMeasure$:
-if a cheating prover $\PNaiveStar$, conditioned on it doesn't ``give up" \Ethan{Ambiguous.
-also need to associate this with $y=\bot$ if we haven't yet.} on the second message \Ethan{Move this clause to the end and say ``whenever it doesn't abort"}, passes the testing round with overwhelming probability,
-then the output $(d, z)\leftarrow(\PNaiveStar, \VNaive)$ is close to $(d, z_{ideal})$.
+if a cheating prover $\PNaiveStar$ passes the testing round with overwhelming probability whenever it doesn't abort on the second message,
+then the corresponding output $(d, z)\leftarrow(\PNaiveStar, \VNaive)$ is close to $(d, z_{ideal})$.
 Recall the ideal output
@@
 
-	Now we construct another cheating $\BQP$ prover $\Pstar$ that is perfect \Ethan{``almost perfect"?} and non-aborting as follows.
+	Now we construct another cheating $\BQP$ prover $\Pstar$ that is non-aborting and almost perfect as follows.
 	For the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
@@
 but instead of having each copy running testing round or Hadamard round uniformly at random, we randomly pick one copy to run Hadamard round to get our samples and run testing round on all other $m-1$ copies.
-\Ethan{Maybe say the $1/m$ thing here?}
+Intuitively, if the server wants to cheat by sending something not binding on some copy,
+he will be caught when that copy is a testing round, which is with probability $1-1/m$.
+This over-simplified analysis does not take into account that the server might create entanglements between the copies, however, so the correct analysis is more technically involved.
+
 In the description of our protocol below, we describe $\PiNaive$ and $\PiMeasure$ in details in order to introduce notations that we need in our analysis.
@@
 \end{protocol}
+By inspection, $\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness error.
+To show that it is computationally sound, we first use the partition lemma from \cite{arXiv:ChiaChungYam19}.
+It says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
+$G_{0,i}$ represents the subspace where the server knows the answer to the testing round on the $i$-th copy, while $G_{1,i}$ represents the subspace where the server doesn't.
+By using this partition lemma iteratively, we can split the prover's internal state $\ket{\psi}$ by the first copy a component will fail on a testing round. 
+That is, $\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ldots+\ket{\psi_{1^{m-1}0}}+\ket{\psi_{1^m}}$, where $\ket{\psi_{1^i0}}$ represents the component that would pass the first $i$ testing rounds then gets rejected by the next one, and $\ket{\psi_{1^m}}$ represents the ``good" component where the prover knows the answer to every testing round.
+% As each $\ket{\psi_{1^i0}}$ survives only when the Hadamard round choice is $c=e_{i+1}$, that is with low probability, the output corresponding to $\ket{\psi}$ would be close to that of the subnormalized state $\ket{\psi_{1^m}}$.
 
-Clearly \Ethan{If it's clear then just say why. Or say ``by inspection..."} $\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness error.
-We now show that it is computationally sound. \Ethan{Lacking intuition currently...}
-We first use the following partition lemma from \cite{arXiv:ChiaChungYam19}, which intuitively says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
-$G_{0,i}$ represents the subspace that are rejected with high probability \Ethan{change the characterization to whether the prover ``knows"...} in the testing round of $i$-th copy, while $G_{1,i}$  represents the subspace accepted with high probability\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
-\Ethan{Maybe technical overview goes here. That ``tree or something"...}
-\Ethan{TODO then talk about why other naive approaches don't work: stuff doesn't commute and whatnot}
-Also as a careful reader might have noticed, the prover's space don't split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle.
+\Ethan{This paragraph needs more work}
+There is an additional issue, however, as $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m, \gamma}}$ is only binding for the $m$-th copy.
+To solve this problem, we start with a pointwise argument and fix the Hadamard round on the $i$-th copy,
+and show that the corresponding output is $O(\norm{\ket{\psi_{1^{i-1}0}}})$-close to ideal.
+We can later average out this error over the different choices of $i$, since not all $\norm{\ket{\psi_{1^{i-1}0}}}$ can be large at the same time.
+
+Also as a careful reader might have noticed, in fact the prover's space don't always decompose cleanly.
 In \cite{arXiv:ChiaChungYam19} this is solved by splitting the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
-However, states with accept probability really close to the threshold $\gamma$ can not be classified, so we need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.
+However, states with accept probability really close to the threshold $\gamma$ can not be classified, so they need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.
+Now we give a formal description of the partition lemma.
 
@@
 
-By using \Cref{lem:partition2} iteratively, we can decompose the prover's internal state.
-\Ethan{The following is still too quick. Don't use all properties up front in short succession.}
+We now decompose the prover's internal state by using \Cref{lem:partition2} iteratively.
 Let $\ket{\psi}$ be the state the prover holds before he receives $\vec{c}$;
@@
 $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}\ldots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}.$$
-For example \Ethan{``take $k=3$"...}, $\ket{\psi_{110, \gamma}}$ intuitively corresponds to the component that would pass the first two copies' testing rounds and fail the third one.
-\Ethan{Comment about $\ket{\psi_{good}}$ or whatever it is}
-At this point it is tempting to decompose $\ket{\psi}$ into $\ket{\psi_{s, \gamma}}$ where $s\in\zo^m$,
-and say that $\ket{\psi_{1^m, \gamma}}$ is the only component that is not rejected with high probability.
-This doesn't work, however, as $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m, \gamma}}$ is only binding for the $m$-th copy.
-Instead, we start with a pointwise argument and fix the Hadamard round on the $i$-th copy,
-and show that the corresponding output is $O(\norm{\ket{\psi_{1^{i-1}0}}})$-close to ideal.
-We can later average out this error over the different choices of $i$, since not all $\norm{\ket{\psi_{1^{i-1}0}}}$ can be large at the same time.
 
-To begin, let $\ket{\psi}$ be the state the prover holds before he receives $\vec{c}$.
 For all $i\in[m]$, we decompose $\ket{\psi}$ as
+\Ethan{Maybe we can delete a couple of the following equations now, since the intuitive idea was presented earlier?}
 \begin{align} \label{eq:partition-string}
@@
 \end{align}
-where
-$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}\ldots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$
-and $\ket{\psi_{err,i,\gamma}}$ denotes the error state from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
+where $\ket{\psi_{err,i,\gamma}}$ denotes the error state from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
 
@@
 	Since the verifier only accepts if all $(m-1)$ copies of testing rounds accepts, for all $j\neq i$,
+	\Ethan{Is this really true?}
 	$$P_{acc,i,z}=P_{acc,i,z}P_{j,pk_j,y_j,acc}.$$

### 2020-09-04 qpip0.tex
Add extra info on QPIP0 intro

@@
 the client doesn't always obtain measurement outcomes even if the server were honest.
-To overcome this challenge, we run many copies of $\PiNaive$ in parallel so the verifier can generate its outputs from some copy.
-We spend the majority of this section showing the soundness of this parallel repetition.
+When that happens under the $\BQP$ context, the verifier can simply accept the prover at the cost of some soundness error;
+under our $\SampBQP$ context, however, we must run many copies of $\PiNaive$ in parallel so the verifier can generate its outputs from some copy.
+We spend the majority of this section analyzing the soundness of this parallel repetition.
 

### 2020-09-04 qpip0.tex
Write binding property as equation

@@
 	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
-	Suppose that conditioned on $\PNaiveStar$ not aborting on the second round (ie. $y\ne\bot$), it passes the testing round with overwhelming probability.
-	Under the QLWE assumption, then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
-	\Ethan{Write the conditional probability in terms of equations}
+	Suppose that $\Prob{d=\Acc\mid y\ne\bot, c=0}$ is overwhelming, \Ethan{This good?}
+	under the QLWE assumption, then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
 \end{theorem}
@@
 
-\Ethan{This paragraph needs more work}
 There is an additional issue, however, as $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m, \gamma}}$ is only binding for the $m$-th copy.
-To solve this problem, we start with a pointwise argument and fix the Hadamard round on the $i$-th copy,
+To solve this problem, we start with a pointwise argument and fix the Hadamard round on the $i$-th copy where $\ket{\psi_{1^i}}$ is binding,
 and show that the corresponding output is $O(\norm{\ket{\psi_{1^{i-1}0}}})$-close to ideal.

### 2020-09-04 qpip0.tex
Remove unnecessary author note

@@
 	Since the verifier only accepts if all $(m-1)$ copies of testing rounds accepts, for all $j\neq i$,
-	\Ethan{Is this really true?}
 	$$P_{acc,i,z}=P_{acc,i,z}P_{j,pk_j,y_j,acc}.$$

### 2020-09-04 qpip0.tex
Write gamma as vector

@@
 we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
-For all $k\leq m$, $d\in \zo^k$, $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and $\ket{\psi} \in H_{\regX,\regZ}$, define \Ethan{This isn't correct; $\gamma$ should be independent for each copy}
-$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}\ldots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}.$$
+For all $k\leq m$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$ \Ethan{This ok?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define
+$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.$$
 
-For all $i\in[m]$, we decompose $\ket{\psi}$ as
-\Ethan{Maybe we can delete a couple of the following equations now, since the intuitive idea was presented earlier?}
-\begin{align} \label{eq:partition-string}
-	\ket{\psi} =& \ket{\psi_{0,\gamma}}+\ket{\psi_{1,\gamma}}+\ket{\psi_{err,1,\gamma}} \nn \\
-	=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{11,\gamma}}+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}} \nn \\
-	=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{m-1}0,\gamma}}+\ket{\psi_{1^{m-1}1,\gamma}} \nn \\
-	&+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,m,\gamma}} \nn\\
-	=&\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-\end{align}
+For all $i\in[m]$, we decompose
+	$$\ket{\psi}=\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}$$
 where $\ket{\psi_{err,i,\gamma}}$ denotes the error state from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.

### 2020-09-04 qpip0.tex
Fix labelling bug

@@
 For all $k\leq m$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$ \Ethan{This ok?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define
-$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.$$
+\begin{equation}
+	\Cref{eq:partition-string}
+	\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.
+\end{equation}
 
@@
 \begin{proof}
-	We rewrite \Cref{eq:partition-string}
+	We take expectation of \Cref{eq:partition-string} over $\gamma$
 	$$\ket{\psi}=\E_{\gamma}\left[

### 2020-09-04 qpip0.tex
Fix typo

@@
 we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
-For all $k\leq m$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$ \Ethan{This ok?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define
+For all $k\leq m$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$ \Ethan{This ok?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.$$
+For all $i\in[m]$, we then decompose
 \begin{equation}
-	\Cref{eq:partition-string}
-	\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.
+	\label{eq:partition-string}
+	\ket{\psi}=\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
 \end{equation}
-
-For all $i\in[m]$, we decompose
-	$$\ket{\psi}=\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}$$
 where $\ket{\psi_{err,i,\gamma}}$ denotes the error state from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.

### 2020-09-04 qpip0.tex
Make readability improvement

@@
 We denote the string $0^{i-1}10^{m-i} \in \zo^m$ as $e_i$. The output string corresponding to $\ket{\psi} \in H_{\regX,\regZ}$ when $c=e_i$ is then
-$$z_i\defeq \E_{pk,y} \sum_z \norm{P_{acc,i,z} U\ket{e_i,\psi}}^2\proj{z},$$
+\begin{equation}
+	\label{eq:zi-def}
+	z_i\defeq \E_{pk,y} \sum_z \norm{P_{acc,i,z} U\ket{e_i,\psi}}^2\proj{z},
+\end{equation}
 where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round.
@@
 Now we define
-\begin{align}
+\begin{equation}
+	\label{eq:zgoodi-def}
 	z_{good, i}=\E_{\gamma, pk, y} \sum_z \norm{P_{acc,i,z} U\ket{e_i,\psi_{1^{i-1}1,\gamma}}}^2\proj{z}
-\end{align}
+\end{equation}
 as the output corresponding to the component that would pass all $i$ testing rounds.
@@
 	\right]$$
-	and expand $z_i$ as
+	and expand $z_i$ from \Cref{eq:zi-def} as
 	\begin{align}
@@
 	The last three error terms sum to $O\L(\frac{m^2}{\sqrt{T}}\R)$ by \Cref{lem:samp-tech} and \Cref{property:partition-err} of \Cref{lem:partition2}.
-
-	Now by \Cref{lem:samp-tech} and \Cref{lem:partition-testing}, we see that
+	As for the first two terms, by \Cref{lem:samp-tech} and \Cref{lem:partition-testing}, we see that
 	\begin{align*}

### 2020-09-04 preliminaries.tex
Add the other aaronson's paper on SampBQP
Talk about SampBQP inverse poly error

@@
 
-We define the sampling version of $\BQP$ based on \cite{aaronson_2013}.
+We define the sampling version of $\BQP$ based on \cite{aaronson_2013, aaronson_arkhipov_2011}.
+The definition of $\SampBQP$ allows inverse-polynomial error in order to capture some characteristics of optics-based quantum computing implementations.
 
@@
 \end{definition}
-
-\Ethan{see Scott's paper to see why inverse poly there. Maybe it's just because it's required for his result to work.
-More generally, need discussions on sampling vs non sampling
-Try to claim our definitions is WLOG/general/intuitive
-}
-This version has an inverse-polynomial error because...
-\Ethan{TODO cite the other paper and something about near-term quantum computers}
 

### 2020-09-04 preliminaries.tex
Fix some wording

@@
 since a cheating prover can abort to force the verifier output $\bot$ with arbitrary probability.
-The natural relaxation is to first condition on acceptance, then require the same of the output distribution.
-We must also add that the acceptance probability is at least noticeable.
-By combining these two conditions, we arrive at the following definition.
+On the other hand, we can ask that the output distribution to be close to the true one whenever the protocol does not abort.
 

### 2020-09-04 introduction.tex
Add reasons why quantum sampling is hard

@@
 The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones strengthens the importance of delegation for quantum sampling problems.
- %Even though the relation between $\BQP$ and $\SampBQP$ is relatively understood in the plain model,
- \Ethan{Maybe replace the following sentence with the actual challenges? Ie. unclear how to run many copies to reduce errors; classical approach with PRG seed doesn't work either}
-However, it is far from clear whether the subtle difference between $\BQP$ and its sampling version could lead to
-technical barrier in the context of CVQC, or
- %what are the potential technical challenges raised by their subtle differences in the context of CVQC and how to resolve them is however far from clear.
-whether one can develop a CVQC protocol for $\SampBQP$ based on Mahadev's technique~\cite{FOCS:Mahadev18a}.
+
+\Ethan{This paragraph is new and has to be checked}
+Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however,
+it is still unclear how to construct a CVQC protocol for $\SampBQP$.
+A protocol for classical sampling problems is usually obtained from one for decision problems,
+by fixing a seed for pseudorandomness then computing the output bit-by-bit.
+This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements,
+where the outcome is generally different from one execution to the next.
+Furthermore, it is unclear how to even amplify the soundness of a sampling protocol by means of repetitions,
+especially considering the outputs from different executions might be correlated to begin with.
 
@@
 whereas the analysis is still very specific to the construction.
+\Ethan{And it has inverse-poly errors, which makes it not constant-round to achieve negligible errors for $\BQP$, right?}
 Could there be a \emph{generic} way to achieve blindness and verifiability for CVQC protocols at the same time?

### 2020-09-10 introduction.tex
Fix wording

@@
 it is still unclear how to construct a CVQC protocol for $\SampBQP$.
-A protocol for classical sampling problems is usually obtained from one for decision problems,
+A protocol for classical sampling problems is usually obtained from that of decision problems,
 by fixing a seed for pseudorandomness then computing the output bit-by-bit.

### 2020-09-11 introduction.tex
Make phrasing more concise
Make editorial changes

@@
 by fixing a seed for pseudorandomness then computing the output bit-by-bit.
-This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements,
-where the outcome is generally different from one execution to the next.
-Furthermore, it is unclear how to even amplify the soundness of a sampling protocol by means of repetitions,
-especially considering the outputs from different executions might be correlated to begin with.
+This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements.
+Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
+since it is unclear how to use the usual trick of running many copies of the protocol then applying the Chernoff bound.
 

### 2020-09-11 qpip0.tex
Make editorial changes

@@
 	Let $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$ and by triangle inequality we have $\tr\abs{z-z_{ideal}}=O(\varepsilon)$.
-	Since $z$ is close to some ideal output distribution $z_{ideal}$, it must be close to the ideal output distribution with its accept probability too.
+	Since $z$ is close to some ideal output distribution $z_{ideal}$, it must be close to the ideal output distribution with its own accept probability too.
 \end{proof}

### 2020-09-11 introduction.tex
Fix wording

@@
 Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
-since it is unclear how to use the usual trick of running many copies of the protocol then applying the Chernoff bound.
+since it is unclear how to apply the usual trick of running many copies of the protocol then applying the Chernoff bound.
 

### 2020-10-03 preliminaries.tex
Fix typo

@@
 
-We define the sampling version of $\BQP$ based on \cite{aaronson_2013, aaronson_arkhipov_2011}.
-The definition of $\SampBQP$ allows inverse-polynomial error in order to capture some characteristics of optics-based quantum computing implementations.
+We define $\SampBQP$ based on \cite{aaronson_2013, aaronson_arkhipov_2011}.
+\Ethan{Tried to explain better}
+This complexity class is meant to model feasible quantum computations.
+It is worth noting that quantum states live in a Hilbert space which is continuous,
+so it is likely that any physical implementation of quantum computing would naturally involve some sort of errors.
+\cite{aaronson_arkhipov_2011} gives an argument from the physical implementation perspective that this error should be inverse polynomial.
 

### 2020-10-04 qpip0.tex
Fix typo
Move epsilon definition in QPIP0

@@
 Property~\ref{property-partition-norm-sum} comes from the fact that $G_0$ and $G_1$ are post-selections of orthogonal results of the same $G$.}]\label{lem:partition2}
-	Let $\lambda$ be the security parameter and  $\eps$ be the accuracy parameter \Ethan{Is this the global one?}.
+	Let $\lambda$ be the security parameter, and $\gamma_0 \in[0,1]$ and $T\in \mathbb{N}$ be parameters that will relate to the randomly-chosen threshold $\gamma$.
 	Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message.
 Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$, which corresponds to Hadamard round on the $i$-th copy and testing round on all others.
-Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=\poly(\eps)$ and $T=1/\poly(\eps)$.
 
@@
 The analysis is tedious but straightforward;
-we simply expand $z_i$ and bound the terms other than $z_{i, good}$.
+we simply expand $z_i$ and bound the terms other than $z_{good, i}$.
 
@@
 	\label{thm:zi-zgoodi}
-	$$\tr\abs{z_i-z_{i, good}}\leq\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)$$
+	$$\tr\abs{z_i-z_{good, i}}\leq\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)$$
 \end{lemma}
@@
 	\label{thm:zgood-zideal}
-	$z_{good, i}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
+	$z_{good, i}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$,
+	where $\eps\in\bbR$ is the accuracy parameter picked earlier in $\PiSampZ$.
 \end{lemma}

### 2020-10-04 qpip0.tex
Remove unnecessary lemma

@@
 			For all $\vec{pk}$, $\vec{y}$, fixed $\gamma$, and  $j\neq i$, we have
-
-			%      \begin{align*}
-			%  \Pr\left[M_{\regX_i}\circ U\frac{\ket{\{c\}}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{pk_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
-			%  \end{align*}
-
-			%  Define
-			%  $$\ket{\widetilde{\psi_{0,i,\gamma}}}\defeq U\frac{\ket{\{c\}}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}.$$
-			%  We have
-			%  \begin{align}
-			%      \vev{\widetilde{\psi_{0,i,\gamma}}|P_{i,pk_i,y_i,acc}|\widetilde{\psi_{0,i,\gamma}}} \leq (m-1)\gamma+\negl(\secpar),
-			%  \end{align}
 			\begin{align}
-				\norm{ P_{i,pk_i,y_i,acc} \circ U\frac{\ket{e_j}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}}^2 \leq (m-1)\gamma_0+\negl(\lambda),
+				\norm{ P_{acc, i} \circ U\frac{\ket{e_j}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}}^2 \leq (m-1)\gamma_0+\negl(\lambda),
 			\end{align}
-			where $P_{i,pk_i,y_i,acc}$ are projector to the states that $i$-th testing round accepts with $pk_i,y_i$, including the last measurement the prover did before sending $\vec{a}$.
+			where $P_{acc, i}$ are projector to the states that $i$-th testing round accepts with $pk_i,y_i$, including the last measurement the prover did before sending $\vec{a}$.
 This means that $\ket{\psi_{0,i,\gamma}}$ is rejected by the $i$-th testing round with high probability.
@@
 			\begin{align}
-				\norm{P_{i,pk_i,y_i,acc} \circ \ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)}^2 =1-\negl(\lambda).
+				\norm{P_{acc, i} \circ \ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)}^2 =1-\negl(\lambda).
 			\end{align}
@@
 \end{lemma}
+
+By Property~\ref{property:partition-testing} of the partition lemma above,
+it clearly also follows that \Ethan{This ok?}
+\begin{rmk}
+	\label{lem:partition-testing}
+	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and all $i,j\in[m]$ such that $j<i-1$, we have
+	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
+\end{rmk}
 
@@
 We will show that it is $O(\norm{\ket{\psi_{1^{i-1}0}}})$-close to $z_i$.
-Before doing so, we present a couple technical lemma.
+Before doing so, we present a technical lemma.
 \begin{lemma}\label{lem:samp-tech}
@@
 	where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
-\end{proof}
-\begin{lemma}
-	\label{lem:partition-testing}
-	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and all $i,j\in[m]$ such that $j<i-1$, we have
-	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
-\end{lemma}
-\begin{proof}
-	Since the verifier only accepts if all $(m-1)$ copies of testing rounds accepts, for all $j\neq i$,
-	\Ethan{Is this really true?}
-	$$P_{acc,i,z}=P_{acc,i,z}P_{j,pk_j,y_j,acc}.$$
-	And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$
-	\begin{align} \label{eq:rejected-d}
-		\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2
-		=& \norm{P_{acc,i,z}P_{j,pk_j,y_j,acc} U \ket{e_i}\, G_{0,j+1,\gamma}\ket{\psi_{1^j,\gamma}}  }^2 \nn \\
-		\leq& \norm{P_{j,pk_j,y_j,acc} U \ket{e_i}\, G_{0,j+1,\gamma}\ket{\psi_{1^j,\gamma}}  }^2 \nn \\
-		\leq& (m-1)\gamma_0+\negl(n)
-	\end{align}
 \end{proof}

### 2020-10-04 qpip0.tex
Provide more intuition for QPIP0

@@
 To show that it is computationally sound, we first use the partition lemma from \cite{arXiv:ChiaChungYam19}.
-It says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
-$G_{0,i}$ represents the subspace where the server knows the answer to the testing round on the $i$-th copy, while $G_{1,i}$ represents the subspace where the server doesn't.
-By using this partition lemma iteratively, we can split the prover's internal state $\ket{\psi}$ by the first copy a component will fail on a testing round. 
-That is, $\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ldots+\ket{\psi_{1^{m-1}0}}+\ket{\psi_{1^m}}$, where $\ket{\psi_{1^i0}}$ represents the component that would pass the first $i$ testing rounds then gets rejected by the next one, and $\ket{\psi_{1^m}}$ represents the ``good" component where the prover knows the answer to every testing round.
-% As each $\ket{\psi_{1^i0}}$ survives only when the Hadamard round choice is $c=e_{i+1}$, that is with low probability, the output corresponding to $\ket{\psi}$ would be close to that of the subnormalized state $\ket{\psi_{1^m}}$.
+\Ethan{Tried to ``slow down" on this paragraph}
+It says that for each copy $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
+$G_{0,i}$ intuitively represents the subspace where the server does not knows the answer to the testing round on the $i$-th copy, while $G_{1,i}$ represents the subspace where the server does.
+By using this partition lemma iteratively, we can decompose the prover's internal state $\ket{\psi}$.
+First we apply it to the first copy, writing $\ket{\psi}=G_{0,1}\ket{\psi}+G_{1,1}\ket{\psi}=\ket{\psi_0}+\ket{\psi_1}$.
+The component $\ket{\psi_0}$ would then get rejected as long as the first copy is a testing round,
+which occurs with high probability.
+More precisely, the output corresponding to $\ket{\psi_0}$ is $1/m$-close to the ideal distribution that just rejects all the time.
+On the other hand, $\ket{\psi_1}$ is now binding on the first copy;
+we now similarly apply the partition lemma to the second copy of $\ket{\psi_1}$.
+We write $\ket{\psi_1}=G_{0,2}\ket{\psi_1}+G_{1,2}\ket{\psi_1}=\ket{\psi_{10}}+\ket{\psi_{11}}$, and apply the same argument about $\ket{\psi_{10}}$ and $\ket{\psi_{11}}$.
+We then continue to decompose $\ket{\psi_{11}}=\ket{\psi_{110}}+\ket{\psi_{111}}$ and so on, until we reach the last copy and obtain $\ket{\psi_{1^m}}$.
+This $\ket{\psi_{1^m}}$ term represents the ``good" component where the prover knows the answer to every testing round and therefore has high accept probability.
+Intuitively, $\ket{\psi_{1^m}}$ also satisfies some binding property,
+so the verifier should obtain a measurement result of some state on the Hadamard round copy,
+and the analysis from the $\QPIP_1$ protocol $\PiSamp$ follows.
 
-There is an additional issue, however, as $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m, \gamma}}$ is only binding for the $m$-th copy.
+There is an additional issue, however, as $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m}}$ is unfortunately only binding for the $m$-th copy.
 To solve this problem, we start with a pointwise argument and fix the Hadamard round on the $i$-th copy where $\ket{\psi_{1^i}}$ is binding,

### 2020-10-04 introduction.tex
Fix intro/prelim action items

--- 2020-09-11 introduction.tex
@@
 it is still unclear how to construct a CVQC protocol for $\SampBQP$.
-A protocol for classical sampling problems is usually obtained from that of decision problems,
-by fixing a seed for pseudorandomness then computing the output bit-by-bit.
-This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements.
+In the context of delegating \emph{classical} sampling problems,
+there is a simple reduction to that of decision problems.
+Namely, the verifier fixes a seed for pseudorandomness and send it to the prover,
+then the sampling outcome can be computed deterministically bit-by-bit using this pseudorandomness.
+Unfortunately, this de-randomization trick does not work for delegation of $\SampBQP$, as quantum computation is inherently random.
+\Ethan{Next part needs discussion on context Ie. protocol or local computation}
 Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
-since it is unclear how to use the usual trick of running many copies of the protocol then applying the Chernoff bound.
+since it is unclear how to apply the usual trick of running many copies of the protocol then applying the Chernoff bound.
 

### 2020-10-04 preliminaries.tex
Fix intro/prelim action items

@@
 This complexity class is meant to model feasible quantum computations.
-It is worth noting that quantum states live in a Hilbert space which is continuous,
-so it is likely that any physical implementation of quantum computing would naturally involve some sort of errors.
-\cite{aaronson_arkhipov_2011} gives an argument from the physical implementation perspective that this error should be inverse polynomial.
+As quantum states live in a continuous Hilbert space,
+it is likely that any realization of quantum computing would suffer from natural noise and inaccuracies.
+An argument from the physical implementation perspective that this error should be on an inverse polynomial scale is given in \cite{aaronson_arkhipov_2011}.
+As a result, $\SampBQP$ is correspondingly stated to allow inverse-polynomial errors.
 

### 2020-10-26 qpip0.tex
Update from Overleaf version

@@
 
-	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized) $\poly(\lambda)$-qubits quantum state $\ket{\psi}_{\regX,\regZ}$,
+	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit \hannote{precise def.
+With post selection?} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized) $\poly(\lambda)$-qubits quantum state $\ket{\psi}_{\regX,\regZ}$,
 

### 2020-10-27 qpip0.tex
Sync Overleaf with Github

@@
 
-In this section, we create a delegation protocol for $\SampBQP$ with fully classical clients following the approach taken in \cite{FOCS:Mahadev18a}.
-The core protocol, $\PiMeasure$, allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
+%to create a fully classical delegation protocol for $\BQP$
+
+In this section, we create a delegation protocol for $\SampBQP$ with fully classical clients by adapting the approach taken in \cite{FOCS:Mahadev18a}. In \cite{FOCS:Mahadev18a}, 
+Mahadev designed a protocol $\PiMeasure$ (\cref{proto:urmila4}) that allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
 Composing it with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
-We now try to compose $\PiMeasure$ similarly with our $\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$
+In this work, We try to compose $\PiMeasure$ with our $\QPIP_1$ protocol $\PiSamp$ (\cref{ProtoQPIP1}) for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$
 
-A direct composition between $\PiSamp$ and $\PiMeasure$, however, results in $\PiNaive$ which does not provide reasonable completeness or accuracy guarantees.
+A direct composition of $\PiSamp$ and $\PiMeasure$, however, results in $\PiNaive$ (\cref{proto:qpip0_naive}) which does not provide reasonable completeness or accuracy guarantees.
 As we will see, this is due to $\PiMeasure$ itself having peculiar and weak guarantees:
@@
 $\PiMeasure$ is a 4-round protocol between a verifier (which corresponds to our client) and a prover (which corresponds to our server).
-The verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$.
+The verifier (secretly) chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$.
 It sends $pk$ to the prover.
@@
 	\label{lem:urmila-binding}
-	Let $\PMeasureStar$ be a $\BQP$ cheating prover for $\PiMeasure$ and $\lambda$ be the security parameter.
-Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
+	Let $\PMeasureStar$ be a $\BQP$ cheating \hannote{defined?} prover for $\PiMeasure$ and $\lambda$ be the security parameter.
+Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$ \hannote{too weak?}, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
 \end{lemma}

### 2020-10-28 qpip0.tex
Sync overleaf and github

@@
 In this section, we create a delegation protocol for $\SampBQP$ with fully classical clients by adapting the approach taken in \cite{FOCS:Mahadev18a}. In \cite{FOCS:Mahadev18a}, 
-Mahadev designed a protocol $\PiMeasure$ (\cref{proto:urmila4}) that allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
+Mahadev designed a protocol $\PiMeasure$ (\Cref{proto:urmila4}) that allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
 Composing it with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
-In this work, We try to compose $\PiMeasure$ with our $\QPIP_1$ protocol $\PiSamp$ (\cref{ProtoQPIP1}) for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$
+In this work, We try to compose $\PiMeasure$ with our $\QPIP_1$ protocol $\PiSamp$ (\Cref{ProtoQPIP1}) for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$
 
-A direct composition of $\PiSamp$ and $\PiMeasure$, however, results in $\PiNaive$ (\cref{proto:qpip0_naive}) which does not provide reasonable completeness or accuracy guarantees.
+A direct composition of $\PiSamp$ and $\PiMeasure$, however, results in $\PiNaive$ (\Cref{proto:qpip0_naive}) which does not provide reasonable completeness or accuracy guarantees.
 As we will see, this is due to $\PiMeasure$ itself having peculiar and weak guarantees:
@@
 		\item Prover's input: a state $\rho\in\cB^{\otimes n}$ for the verifier to measure.
-		\item Verifier's input: the measurement basis choice $h \in \zo^n$
+		\item Verifier's input: the measurement basis choice $h \in \zo^n$ \hannote{those two parameters are actually called input?}
 	\end{itemize}
@@
 
-We now use $\PiMeasure$ to transform our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, to a corresponding $\QPIP_0$ protocol $\PiNaive$.
+We now combine $\PiMeasure$ with our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$ (\Cref{ProtoQPIP1}), to get a corresponding $\QPIP_0$ protocol $\PiNaive$.
 Recall that in $\PiSamp$ the verifier takes $X$ and $Z$ measurements on the prover's message.
@@
 			\begin{enumerate}
-				\item The verifier samples $(pk, sk)\leftarrow\cVNaive{1}(1^\lambda, h)$ and sends $pk$ to the prover.
+				\item The verifier samples $(pk, sk)\leftarrow\cVNaive{1}(1^\lambda, h)$ and sends $pk$ to the prover. \hannote{shouldn't those be $V_{meas,1}$?}
 				\item The prover runs $(y, \sigma)\leftarrow\cPNaive{2}(pk, \rho)$ and sends $y$ to the verifier.
-					Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but is useful for analysis.
+					Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but simplifies our analysis.
 				\item\label{step:c-urmila-in-naive} The verifier samples $c\xleftarrow{\$}\zo$ and sends it to the prover.
@@
 \end{cases}$$
-is drawn from the true distribution instead when $\PNaiveStar$ is accepted.
-The intuition of the proof is to reduce to \Cref{lem:urmila-binding} by constructing another $\BQP$ prover $\Pstar$ for $\PiMeasure$.
+is drawn from the true distribution instead when $\PNaiveStar$ is accepted. \hannote{?} This binding property is formalized in \Cref{lem:naive-qpip0-binding}.
+The intuition of the proof of \Cref{lem:naive-qpip0-binding} is to reduce\hannote{not quite?} to \Cref{lem:urmila-binding} by constructing another $\BQP$ prover\hannote{this is really confusing..} $\Pstar$ for $\PiMeasure$.
 Specifically, $\Pstar$ uses $\PNaiveStar$'s strategy when it doesn't abort, otherwise honestly chooses some default state for the verifier to measure.
-We now state the theorem and proof.
+%We now state the theorem and proof.
 
@@
 	which in turn is $\negl(\lambda)$-computationally indistinguishable to $(d', z_{ideal}')$.
-	So $\abs{d-d'}\leq O(\eps)$,
+	So $\abs{d-d'}\leq O(\eps)$ \hannote{?},
 	and $(d, z_{ideal})$ is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.

### 2020-11-02 introduction.tex
Sync

@@
 % }
+
 Can quantum computation, with potential computational advantages that are intractable for classical computers,
-be efficiently verified by classical human beings?
+be efficiently verified by classical clients?
 This seeming paradox has been one of the central problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}.
@@
 In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
-The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
-We refer curious readers to the survey~\cite{survey:GKK19} for details.
+The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.,~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
+On the other side, there are known complexity-theoretic limitations on the feasibility of blind CVQC in the information-theoretical setting (e.g.~\cite{aaronson_et_al:LIPIcs:2019:10582}).
+%\XW{here some no-go for information theoretical result.}
+%We refer curious readers to a slightly outdated  survey~\cite{survey:GKK19} for details.
 
@@
 Moreover, a lot of quantum algorithms from Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component.
-The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones strengthens the importance of delegation for quantum sampling problems.
+The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones also suggests the relevance of delegation for quantum sampling problems.
 
-\Ethan{This paragraph is new and has to be checked}
-Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however,
-it is still unclear how to construct a CVQC protocol for $\SampBQP$.
-In the context of delegating \emph{classical} sampling problems,
-there is a simple reduction to that of decision problems.
-Namely, the verifier fixes a seed for pseudorandomness and send it to the prover,
-then the sampling outcome can be computed deterministically bit-by-bit using this pseudorandomness.
-Unfortunately, this de-randomization trick does not work for delegation of $\SampBQP$, as quantum computation is inherently random.
-\Ethan{Next part needs discussion on context Ie. protocol or local computation}
-Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
-since it is unclear how to apply the usual trick of running many copies of the protocol then applying the Chernoff bound.
+It is worthwhile noting that there is a simple reduction of the delegation of \emph{classical} sampling problems to decision ones: for example, the verifier can fix a seed for pseudo-randomness, send it to the prover, and then the sampling outcome can be computed  bit-by-bit under this pseudo-random seed in a deterministic way.
+Unfortunately, it is unclear how to make this de-randomization trick work for the delegation of $\SampBQP$, 
+as randomness in quantum computation inherently comes from quantum mechanics rather than classical probability theory. 
+Thus, the delegation of $\SampBQP$ might need to take a totally different route from classical. 
+One natural starting point is Mahadev's protocol~\cite{FOCS:Mahadev18a} for the decision problem. 
+Indeed, some nice features of Mahadev's protocol (e.g., allowing X-Z measurements on any qubit) suggest the feasibility of generating a multi-bit measurement outcomes with the protocol. 
+However, as highlighted below in the technical introduction section, there are also important drawbacks of Mahadev's protocol in its current form, which makes it hard to allow a CVQC protocol for $\SampBQP$ with desired completeness and soundness.
+Note that such difficulty does not hold for the decision problem, which demonstrates an importance difference between CVQC protocols for the decision and the sampling problems.
+
+% \XW{Adjust the flow; highlight the key questions}
+% \Ethan{This paragraph is new and has to be checked}
+% Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however, 
+%it is still unclear how to construct a CVQC protocol for $\SampBQP$.
+% In the context of delegating \emph{classical} sampling problems,
+% there is a simple reduction to that of decision problems.
+% Namely, the verifier fixes a seed for pseudorandomness and send it to the prover,
+% then the sampling outcome can be computed deterministically bit-by-bit using this pseudorandomness.
 
@@
 See for example the significant amount of efforts to add verifiability to blind CVQC protocols in~\cite{FK17}.
-Achieving both blindness and verifiability on top of Mahadev's technique~\cite{FOCS:Mahadev18a} is a conceivably much more challenging task.
-The only successful attempt~\cite{FOCS:GheVid19} so far applies Mahadev's technique to the measurement-based quantum computation,
-whereas the analysis is still very specific to the construction.
-\Ethan{And it has inverse-poly errors, which makes it not constant-round to achieve negligible errors for $\BQP$, right?}
-Could there be a \emph{generic} way to achieve blindness and verifiability for CVQC protocols at the same time?
+It is also known that another important primitive called the Quantum Fully Homomorphic Encryption (QFHE)~\cite{BJ15, DSS16, LC18, NS18, OTF18, mahadev_qfhe} should be helpful for establishing blindness: this is intuitive since QFHE allows fully homomorphic operations on encrypted quantum data.
+Indeed, in another paper~\cite{mahadev_qfhe}, Mahadev constructed the first leveled QFHE based on similar techniques and computational assumptions from~\cite{FOCS:Mahadev18a}.
+The constructed QFHE automatically implies a blind CVQC protocol, however, without verifiability.
+Extending this protocol with verifiability seems challenging as hinted by failed attempts in Section 2.2.2 of Mahadev's Phd thesis~\cite{mahadev_2018}.
+
+In fact, most existing blind and verifiable CVQC protocols require a notable amount of effort in achieving each property respectively. 
+The only successful attempt~\cite{FOCS:GheVid19} of achieving both so far applies Mahadev's technique~\cite{FOCS:Mahadev18a} to the measurement-based quantum computation, whereas the analysis is still very specific to the construction.
+%\Ethan{And it has inverse-poly errors, which makes it not constant-round to achieve negligible errors for $\BQP$, right?}
+Could there be a \emph{generic} way to achieve blindness and verifiability for CVQC protocols at the same time, say by leveraging the state of the art CVQC~\cite{FOCS:Mahadev18a} and QFHE~\cite{mahadev_qfhe} protocol?
+
+%\XW{Mention QFHE as a natural attempt, and highlight the problem}
 
@@
 In particular, we demonstrate the feasibility of the classical verification of quantum sampling by
-constructing a constant-round CVQC protocol for $\SampBQP$, the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}.
-Formally, $\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine with an inverse polynomial accurate.
+constructing a constant-round CVQC protocol for $\SampBQP$, the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}, based on the quantum LWE (QLWE) assumption that the learning with error problem is hard for BQP machines.
+Formally, $\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine with an inverse polynomial accuracy.
 %Namely, $A(x,1^{1/\eps})$ outputs a sample that is $\eps$-close to the distribution $D_x$ in statistical distance.
 %, where given an input $x \in \zo^n$, the goal  
-Our protocol leverages the Hamiltonian model and the computational X-Z measurement from~\cite{FOCS:Mahadev18a}.
-However, a significant amount of new techniques have been developed to deal with the difference between $\SampBQP$ and $\BQP$, which will be highlighted in the technical contribution section.
 Precisely,
@@
 \end{theorem}
-%\XW{Insert the theorem statement for the first result here! and a pointer!}
 
-Somewhat surprisingly, our second contribution is a simple yet powerful generic compiler that transforms any CVQC protocol to a blind one while preserving completeness and soundness errors.
-Our construction builds upon another important primitive called the Quantum Fully Homomorphic Encryption (QFHE)~\cite{BJ15, DSS16, LC18, NS18, OTF18, mahadev_qfhe}.
-Intuitively, QFHE allows fully homomorphic operations on encrypted quantum data and thus could be an ideal technical candidate for achieving blindness.
-Indeed, in another paper~\cite{mahadev_qfhe}, Mahadev constructed the first leveled QFHE based on similar techniques and computational assumptions from~\cite{FOCS:Mahadev18a}.
-The constructed QFHE automatically implies a blind CVQC protocol, however, without verifiability.
-Extending this protocol with verifiability seems challenging as hinted by failed attempts in Section 2.2.2 of~\cite{mahadev_2018}.
-In fact, most existing blind and verifiable CVQC protocols require a notable amount of effort in achieving each property respectively.
-
-We observe that QFHE, especially the one from~\cite{mahadev_qfhe}, can be used to transform any CVQC protocol to a blind one with the same number of round communication, while preserving completeness and soundness error.
+Our second contribution is a simple yet powerful \emph{generic}  compiler that transforms any CVQC protocol to a blind one while preserving completeness and soundness errors, building on top of QFHE.
+We observe that QFHE, especially the one from~\cite{mahadev_qfhe}, can be used to transform any CVQC protocol to \emph{a blind one with the same number of round communication, while preserving completeness and soundness error}.
 As a result, one can \emph{upgrade} every verifiable CVQC protocol with blindness almost for free with the help of QFHE.
-Conceptually, we take a very different approach from previous results (e.g.,~\cite{FK17}) which use the blindness as the start point and then work to extend it with verifiability.
-At a high level, our strategy is to simulate the original CVQC protocol under QFHE per each message.
+Conceptually, we take a very different approach from previous results (e.g.,~\cite{FK17} as well as failed attempts in~\cite{mahadev_2018}) which use the blindness as the start point and then work to extend it with verifiability.
+Instead, our strategy is to simulate the original CVQC protocol under QFHE per each message.
 To that end, we do require a special property of QFHE that the classical part of the ciphertext can be operated on separately from the quantum part, which is satisfied by the construction from~\cite{mahadev_qfhe}.
-Our construction makes a modular use of QFHE and only requires a minor technicality in the analysis, which will be explained below. As a result, we obtain
+Our construction makes a modular use of QFHE and only requires a minor technicality in the analysis, which will be explained below. 
+%As a result, we obtain
 \begin{theorem}[informal]
@@
 
-We can also the first blind and constant-round CVQC protocol for $\BQP$ by applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19}.
+We also construct the first blind and constant-round CVQC protocol for $\BQP$ by applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19}.
 
@@
 
-\vspace{2mm} \noindent \textbf{Techniques.} Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of quantum register in the possession of the classical verifier, or equivalently, the limited quantum computation power of the verifier.
+\vspace{2mm} \noindent \textbf{Techniques.}
+
+\XW{revisit Mahadev's approach: (a) QPIP0 to QPIP1; QPIP0 requires very good completeness and soundness.
+(can say for examples the use of X-Z Hamiltonian, what's the detailed bound transformation?);  the output protocol has poor soundness errors;   (this is still for the decision problem; inefficiency); cite the recent parallel repetition - motivation and result; efficiency- round ?
+so sequential-repetition is not preferred.}
+
+\XW{the difference between decision and sampling problems. precision definitions are given in where?}
+
+\XW{still say what's good and where are the gaps. (b) this could cause a problem for samp? because in definition, we need to more than Acc/Rej, we also wants to output the distribution when ACC.}
+
+\XW{(1) a basic step for encoding of the history state in the local Hamiltonian problem, and can be tested (so spectral gap). 
+(2) testing the spectral gap and make sure outputing. QPIP0 protocol. (need and how); here also  
+(3) QPIP1 compilation, and also main the efficiency (round?). But this parallel repetition just makes more complicated because of the sampling requirement! 
+}
+
+\Ethan{Next part needs discussion on context Ie. protocol or local computation}
+Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
+since it is unclear how to apply the usual trick of running many copies of the protocol then applying the Chernoff bound. \XW{too vague to be useful?}
+
+Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of quantum register in the possession of the classical verifier, or equivalently, the limited quantum computation power of the verifier.
 It is known that $\BQP$ can be efficiently verified by a classical verifier that can perform a single qubit X or Z measurement~\cite{PhysRevA.93.022326, mf16}.
@@
 However, since there is no existing $\QPIP_1$ protocol for $\SampBQP$, we make original contributions to both steps as follows:
+\XW{use a different labeling in order to highlight contributions}
 
@@
 (\Cref{sec:LHXZ}.)
+
+\XW{anything useful here: Our protocol leverages the Hamiltonian model and the computational X-Z measurement from~\cite{FOCS:Mahadev18a}.
+However, a significant amount of new techniques have been developed to deal with the difference between $\SampBQP$ and $\BQP$, which will be highlighted in the technical contribution section. }
 
@@
 
+\XW{stop here}
+
 \vspace{2mm} \noindent \textbf{(2) A generic compiler to upgrade $\QPIP_0$ protocols with blindness}.
@@
 Details are given in \Cref{sec:BlindBQP2}.
+
+\XW{To KM: expand the above a bit more?}
 

### 2020-11-02 qpip0.tex
Sync

@@
 
-$\PiMeasure$ has negligible completeness errors.
+$\PiMeasure$ has negligible completeness errors, i.e.
+if both the prover and verifier are honest, the verifier's output on Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
+As for soundness,
 It gives the following \emph{binding property} against cheating provers:
@@
 	\label{lem:urmila-binding}
-	Let $\PMeasureStar$ be a $\BQP$ cheating \hannote{defined?} prover for $\PiMeasure$ and $\lambda$ be the security parameter.
-Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$ \hannote{too weak?}, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
+	Let $\PMeasureStar$ be a $\BQP$ cheating  prover for $\PiMeasure$ and $\lambda$ be the security parameter.
+Let $1-p_{h,T}$ be the  probability that the verifier accepts $\PMeasureStar$ in the testing round on basis choice $h$.\footnote{Compared to Claim 7.1 of \cite{FOCS:Mahadev18a}, we don't have a $p_{h,H}$ term here.
+This is because on rejecting a Hadamard round, the verifier can output a uniformly random string, and that is the result of measuring $h$ on the totally mixed state.} Under the QLWE assumption, there exists some $\rho^*$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round has $\sqrt{p_{h,T}}+\negl(n) $ computational distance\footnote{Two distributions has $c$ computational distance if any efficient algorithm can produce at most $c$ bias between them.}  from $M_{XZ}(\rho^*, h)$.
+
 \end{lemma}
+
+% \begin{lemma}[binding property of $\PiMeasure$; special case of Claim 7.1 in \cite{FOCS:Mahadev18a}\hannote{correct ref?}]
+% 	\label{lem:urmila-binding}
+% 	Let $\PMeasureStar$ be a $\BQP$ cheating \hannote{defined?} prover for $\PiMeasure$ and $\lambda$ be the security parameter.
+Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$\footnote{In terms of \cite{FOCS:Mahadev18a}, we are setting $P_{h,T}$ as a negligible function.}, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
+% \end{lemma}
 
@@
 then the corresponding output $(d, z)\leftarrow(\PNaiveStar, \VNaive)$ is close to $(d, z_{ideal})$.
-Recall the ideal output
+Recall the ideal output is
 $$\begin{cases}
 	z_{ideal}=\bot & \text{if } d=\Rej\\
-	z_{ideal}\leftarrow D_x & \text{if } d=\Acc
+	z_{ideal}\leftarrow D_x & \text{if } d=\Acc.
 \end{cases}$$
-is drawn from the true distribution instead when $\PNaiveStar$ is accepted. \hannote{?} This binding property is formalized in \Cref{lem:naive-qpip0-binding}.
+%is drawn from the true distribution instead when $\PNaiveStar$ is accepted. \hannote{?} 
+This binding property is formalized in \Cref{lem:naive-qpip0-binding}.
 The intuition of the proof of \Cref{lem:naive-qpip0-binding} is to reduce\hannote{not quite?} to \Cref{lem:urmila-binding} by constructing another $\BQP$ prover\hannote{this is really confusing..} $\Pstar$ for $\PiMeasure$.
+\hannote{and the binding of $P*$ implies the binding of $P^*_{int}$}
 Specifically, $\Pstar$ uses $\PNaiveStar$'s strategy when it doesn't abort, otherwise honestly chooses some default state for the verifier to measure.
@@
 	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
-	Suppose that $\Prob{d=\Acc\mid y\ne\bot, c=0}$ is overwhelming, \Ethan{This good?}
+	Suppose that $\Prob{d=\Acc\mid y\ne\bot, c=0}$ is overwhelming for all $x$, \Ethan{This good?}
 	under the QLWE assumption, then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
@@
 \begin{proof}
-	We first introduce the \emph{dummy strategy} where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
+	We first introduce the \emph{dummy strategy} for ~\Cref{proto:qpip0_naive}, where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
 	It is straightforward to verify that this prover would be accepted in the testing round with probability $1-\negl(\lambda)$,
@@
 
-	Now we construct another cheating $\BQP$ prover $\Pstar$ that is non-aborting and almost perfect as follows.
+   In the following we fix an $x$.
+
+	Now we construct a cheating $\BQP$ prover for $\PiMeasure$, $\Pstar$, that is almost perfect as follows.
 	For the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
@@
 
-	Observe that this $\Pstar$ passes testing round with overwhelming probability by construction,
-	so we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property (\Cref{lem:urmila-binding}).
-	That is, there exists some $\rho$ such that $v=M_{XZ}(\rho, h)$.
-	Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}),
-	we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\varepsilon}, x)$ is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.
+%	so we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property (\Cref{lem:urmila-binding}).
+%That is, there exists some $\rho$ such that $v=M_{XZ}(\rho, h)$.\hannote{only comp}
+
+	Let the distribution on $h$ specified in Step~\ref{step:naive1} of the protocol be $p_x(h)$.
+By construction $\Pstar$ passes testing round with overwhelming probability over $p_x(h)$, i.e.
+$\sum_h p_x(h) p_{h,T} =\negl{\lambda}$, where $p_{h,T}$ is $\Pstar$'s probability of getting accepted by the prover on the testing round on basis choice $h$.
+By \Cref{lem:urmila-binding} and Cauchy's inequality, there exists some $\rho$ such that  $\sum_h p_x(h) \norm{v_h -M_{XZ}(\rho, h)}_c = \negl(\lambda)$, where $\norm{}_c$ means computational distance.
+\hannote{defined in a footnote ahhhhhhhhh}.
+Therefore $v= \sum_h p_x(h) v_h$ is computationally indistinguishable to $\sum_h p_x(h) M_{XZ}(\rho, h)$.
+
+	Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}), \hannote{computational ok?}
+
+	we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\varepsilon}, x)$ \hannote{fix notation} is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.
 
@@
 	First, conditioned on that $\PNaiveStar$ aborts, since dummy strategy will be rejected with overwhelming probability in Hadamard round,
-	we have $(d', z')$ is $O(\varepsilon)$-computationally indistinguishable to $(\Rej, \bot)=(d, z)$.
+	we have $(d', z')$ is $O(\varepsilon)$-computationally\hannote{negl(lambda)?} indistinguishable to $(\Rej, \bot)=(d, z)$.
 	On the other hand, conditioned on $\PNaiveStar$ not aborting, clearly $(d, z)=(d', z')$.
 	So $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d', z')$,
-	which in turn is $\negl(\lambda)$-computationally indistinguishable to $(d', z_{ideal}')$.
-	So $\abs{d-d'}\leq O(\eps)$ \hannote{?},
-	and $(d, z_{ideal})$ is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
+	which in turn is $\negl(\lambda)$-computationally indistinguishable to $(d', z_{ideal}')$.\hannote{switch errors?}
+	Since $\abs{d-d'}\leq O(\eps)$ \hannote{?},
+	 $(d, z_{ideal})$ is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
 	Combining everything, we conclude that $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d, z_{ideal})$.
@@
 
-	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit \hannote{precise def.
-With post selection?} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized) $\poly(\lambda)$-qubits quantum state $\ket{\psi}_{\regX,\regZ}$,
+	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit with post selection\footnote{A quantum circuit with post selection is composed of unitary gates followed by a post selection on some measurement outcome on ancilla qubits, so it produces a subnormalized state, where the amplitude square of the output state is the probability of post selection.} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized) $\poly(\lambda)$-qubits quantum state $\ket{\psi}_{\regX,\regZ}$,
 
@@
 
-	By property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort.
-	Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
+	By ~\cref{property:partition-binding} of ~\Cref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort.
+	Since the prover's strategy is also efficient, by ~\Cref{lem:naive-qpip0-binding},
 	$z_{composite}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.

### 2020-11-04 introduction.tex
Sync

@@
 It is worthwhile noting that there is a simple reduction of the delegation of \emph{classical} sampling problems to decision ones: for example, the verifier can fix a seed for pseudo-randomness, send it to the prover, and then the sampling outcome can be computed  bit-by-bit under this pseudo-random seed in a deterministic way.
+As such, classical literature of delegation of computation primarily focuses on delegation of decision problems.
+%delegation of classical sampling problem is not explicitly studied in literature.
+
 Unfortunately, it is unclear how to make this de-randomization trick work for the delegation of $\SampBQP$, 
 as randomness in quantum computation inherently comes from quantum mechanics rather than classical probability theory. 
-Thus, the delegation of $\SampBQP$ might need to take a totally different route from classical. 
-One natural starting point is Mahadev's protocol~\cite{FOCS:Mahadev18a} for the decision problem. 
+Thus, we do not know a generic construction from delegation for $\BQP$, and delegation of $\SampBQP$ may require a different construction.
+%delegation of $\SampBQP$ may require a totally different construction from delegation of $\BQP$. 
+%
+One natural starting point is Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} for $\BQP$. 
 Indeed, some nice features of Mahadev's protocol (e.g., allowing X-Z measurements on any qubit) suggest the feasibility of generating a multi-bit measurement outcomes with the protocol. 
 However, as highlighted below in the technical introduction section, there are also important drawbacks of Mahadev's protocol in its current form, which makes it hard to allow a CVQC protocol for $\SampBQP$ with desired completeness and soundness.
-Note that such difficulty does not hold for the decision problem, which demonstrates an importance difference between CVQC protocols for the decision and the sampling problems.
+As we shall see, such difficulties do not hold for the decision problem, which demonstrates an importance difference between CVQC protocols for the decision and the sampling problems.
 
@@
 
-\vspace{2mm} \noindent \textbf{Techniques.}
+\vspace{2mm} \noindent \textbf{Techniques.} Let us revisit Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} first for some technical background. 
+Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of quantum register in the possession of the classical verifier, or equivalently, the limited quantum computation power of the verifier.
+It is known that $\BQP$ can be efficiently verified by a classical verifier that can perform a single qubit $X$ or $Z$ measurement~\cite{PhysRevA.93.022326, mf16}, by reducing any $\BQP$ problem to a local Hamiltonian problem where each term consists of  $X$ and $Z$ only.
+This leads to a $\QPIP_1$ protocol for $\BQP$.
+The main contribution of Mahadev~\cite{FOCS:Mahadev18a} can hence be deemed as a way to compile this $\QPIP_1$ protocol into a $\QPIP_0$ protocol (i.e., with a fully classical verifier).
 
-\XW{revisit Mahadev's approach: (a) QPIP0 to QPIP1; QPIP0 requires very good completeness and soundness.
+Precisely, to leverage Mahadev's construction, one needs to start with a $\QPIP_1$ protocol with very small completeness and soundness errors, which will then be compiled into a $\QPIP_0$ protocol with a small completeness error, but a close-to-$3/4$ soundness error under the QLWE assumption.
+This large soundness error is due to the current structure of Mahadev's protocol that consists of the \emph{testing} round and the \emph{Hadamard} round, each of which happens with a half chance. 
+At a high level, the protocol verifies the behavior of the prover in the test round, while assumes that the prover behaves honestly and all the X-Z measurements are correct in the Hadamard round. 
+The soundness is obtained by observing that the dishonest prover cannot cheat in both rounds, while cheating in one round alone is possible which leads to a large soundness error. 
+This less desirable soundness error, as well as other parameters, has been subsequently improved in \cite{arXiv:AlaChiHun19, arXiv:ChiaChungYam19} by a parallel repetition of Mahadev's original CVQC protocol in the computational setting.
+
+A key difference between $\SampBQP$ and $\BQP$ is that in addition to the single bit $\mathrm{Accept/Reject}$ information, the verifier in any CVQC protocol for $\SampBQP$ needs to always output a sample of the desired distribution when the protocol accepts.
+This fundamentally new requirement of $\SampBQP$ could be, as we will show, fulfilled in the Hadamard round of Mahadev's protocol. 
+However, it is unclear how to generate such a sample when the protocol accepts in the testing round, since the sampling information stored in the quantum state will be disturbed by the testing step.
+
+As a result, in order to construct a $\QPIP_0$ protocol for $\SampBQP$,  one needs to (1) construct a $\QPIP_1$ protocol for $\SampBQP$ with very small completeness and soundness errors, and (2) amend Mahadev's construction so that the protocol will generate the desired sample whenever it accepts.
+Our first contribution is a solution to address the above two technical challenges.
+
+% \XW{revisit Mahadev's approach: (a) QPIP0 to QPIP1; QPIP0 requires very good completeness and soundness.
 (can say for examples the use of X-Z Hamiltonian, what's the detailed bound transformation?);  the output protocol has poor soundness errors;   (this is still for the decision problem; inefficiency); cite the recent parallel repetition - motivation and result; efficiency- round ?
@@
 
-\XW{the difference between decision and sampling problems. precision definitions are given in where?}
+% \XW{the difference between decision and sampling problems. precision definitions are given in where?}
 
-\XW{still say what's good and where are the gaps. (b) this could cause a problem for samp? because in definition, we need to more than Acc/Rej, we also wants to output the distribution when ACC.}
+% \Ethan{Next part needs discussion on context Ie. protocol or local computation}
+% Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
+% since it is unclear how to apply the usual trick of running many copies of the protocol then applying the Chernoff bound. \XW{too vague to be useful?}
 
-\XW{(1) a basic step for encoding of the history state in the local Hamiltonian problem, and can be tested (so spectral gap). 
-(2) testing the spectral gap and make sure outputing. QPIP0 protocol. (need and how); here also  
-(3) QPIP1 compilation, and also main the efficiency (round?). But this parallel repetition just makes more complicated because of the sampling requirement! 
-}
+\vspace{2mm} \noindent \textbf{Construction of a $\QPIP_0$ protocol for $\SampBQP$}. 
+% \XW{stop here} We will follow the same road map above (i.e., from $\QPIP_1$ to $\QPIP_0$) for $\SampBQP$
+% However, since there is no existing $\QPIP_1$ protocol for $\SampBQP$, we make original contributions to both steps as follows:
+% \XW{use a different labeling in order to highlight contributions}
+Following the aforementioned outline, our construction can be divided into three key technical steps.
 
-\Ethan{Next part needs discussion on context Ie. protocol or local computation}
-Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
-since it is unclear how to apply the usual trick of running many copies of the protocol then applying the Chernoff bound. \XW{too vague to be useful?}
+% \XW{(1) a basic step for encoding of the history state in the local Hamiltonian problem, and can be tested (so spectral gap). 
+% (2) testing the spectral gap and make sure outputing. QPIP0 protocol. (need and how); here also  
+% (3) QPIP1 compilation, and also main the efficiency (round?). But this parallel repetition just makes more complicated because of the sampling requirement! 
+% }
 
-Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of quantum register in the possession of the classical verifier, or equivalently, the limited quantum computation power of the verifier.
-It is known that $\BQP$ can be efficiently verified by a classical verifier that can perform a single qubit X or Z measurement~\cite{PhysRevA.93.022326, mf16}.
-Namely, there is a $\QPIP_1$ protocol for $\BQP$.
-The main contribution of Mahadev~\cite{FOCS:Mahadev18a} can hence be deemed as a way to compile this $\QPIP_1$ protocol into a $\QPIP_0$ protocol (i.e., with a fully classical verifier).
+\vspace{2mm} \noindent \emph{$\diamond$ Reducing  $\SampBQP$ to the local Hamiltonian problem}: We will continue to employ the local Hamiltonian technique~\cite{kitaev2002classical} and its ground state (known as the history state) as a key technical ingredient to certify the $\SampBQP$ circuits.
+Recall that the $\QPIP_1$ protocol for $\BQP$ in Mahadev's construction also comes from a reduction of $\BQP$ to a $X$-$Z$-only local Hamiltonian problem.
 
-\vspace{2mm} \noindent \textbf{(1) Construction of a $\QPIP_0$ protocol for $\SampBQP$}.
-We will follow the same road map above (i.e., from $\QPIP_1$ to $\QPIP_0$) for $\SampBQP$.
-However, since there is no existing $\QPIP_1$ protocol for $\SampBQP$, we make original contributions to both steps as follows:
-\XW{use a different labeling in order to highlight contributions}
-
-\vspace{2mm} \noindent \emph{$\diamond \, \QPIP_1$ protocol for $\SampBQP$}: We will employ the local Hamiltonian technique~\cite{kitaev2002classical} and its ground state (known as the history state) as a key technical ingredient to certify the $\SampBQP$ circuits.
 However, there are important differences between the cases for $\BQP$ and $\SampBQP$.
@@
 Roughly speaking, $H_{\mathrm{circuit}}$ helps guarantee its ground space only contains \emph{valid} history states with correct input and circuit evolution, while $H_{\mathrm{out}}$'s energy encodes the 0/1 output for $\BQP$ circuits.
-Thus, its outcome can be encoded by the \emph{ground energy} of $H$.
-For $\SampBQP$, one still uses $H_{\mathrm{circuit}}$ to certify the validity of the history state.
-However, in this case, one needs to measure on the entire final state of the circuit, rather than a single output qubit,
-which can no longer be encoded solely by the ground energy.
-Our approach is to have the valid history state lie in the ground space of a different local Hamiltonian $H'_{\mathrm{circuit}}$  that has a large \emph{spectral} gap between its ground energy and excited ones.
-It is hence guaranteed that any state with close-to-ground energy must also be close to the history state.
-In other words, a certification of the energy $H'_{\mathrm{circuit}}$ could lead to a certification of the history state.
+Thus, the outcome of a $\BQP$ instance can be encoded by the \emph{ground energy} of $H$.
+
+In the case of $\SampBQP$, one needs to output both Accept/Reject information as well as a sample from the desired distribution if the protocol accepts. 
+To that end, one hopes to certify the validity of the entire history state which is the ground state of $H_{\mathrm{circuit}}$, rather than the ground energy of $H_{\mathrm{circuit}}$ only. 
+% one still uses $H_{\mathrm{circuit}}$ to certify the validity of the history state.
+% However, in this case, one needs to measure on the entire final state of the circuit, rather than a single output qubit,
+% which can no longer be encoded solely by the ground energy.
+Namely, we want to rule out the existence of any state that is far from the history state but its energy (respect to $H_{\mathrm{circuit}}$) is very close to the ground one. 
+One nature approach, also ours, is to make the unique valid history state lie in the ground space of a slightly different local Hamiltonian $H'_{\mathrm{circuit}}$ that has a large \emph{spectral} gap between its ground energy and excited ones.
+It is hence guaranteed that any state with a close-to-ground energy must also be close to the history state.
+In other words, a certification of the energy $H'_{\mathrm{circuit}}$ could lead to a certification of the history state, which in turn helps us generate the desired sample. 
 We construct such $H'_{\mathrm{circuit}}$ from $H_{\mathrm{circuit}}$ by using the \emph{perturbation} technique (e.g.,~\cite{kempe_kitaev_regev_2006}) with further restriction to X/Z terms.
@@
 
-\XW{anything useful here: Our protocol leverages the Hamiltonian model and the computational X-Z measurement from~\cite{FOCS:Mahadev18a}.
-However, a significant amount of new techniques have been developed to deal with the difference between $\SampBQP$ and $\BQP$, which will be highlighted in the technical contribution section. }
+%\XW{what's good about Mahadev's protocol; one can measure a lot; but of course, one needs to also test it; for the QPIP1 protocol; to get the QPIP0, the story won't be different.}
+% \XW{anything useful here: Our protocol leverages the Hamiltonian model and the computational X-Z measurement from~\cite{FOCS:Mahadev18a}.
+% However, a significant amount of new techniques have been developed to deal with the difference between $\SampBQP$ and $\BQP$, which will be highlighted in the technical contribution section. }
 
-Another high-level difficulty in constructing a $\QPIP_1$ protocol for $\SampBQP$ is due to the distinction between the test part and the output part.
-Specifically, we will certify the energy of $H'_{\mathrm{circuit}}$ to guarantee the underlying state is close to the valid history state.
-However, this procedure could be vastly different from outputting a sample by measuring the final state of $\SampBQP$ circuits.
-We design a \emph{cut-and-choose} protocol on multiple copies of the history state for both testing and outputting.
-We also employ a variant of quantum \emph{de Finetti} theorem~\cite{Brandao2017}
-to prevent potential cheating strategies by entangling different copies of history states.
-(\Cref{sec:qpip1}.)
+\vspace{2mm} \noindent \emph{$\diamond$ A $\QPIP_1$ protocol for $\SampBQP$:} A certification protocol for the history state, however, is insufficient to imply a $\QPIP_1$ protocol for $\SampBQP$ directly.
+Intuitively, we face a similar dilemma as we described above about Mahadev's protocol: we can either employ the certification protocol on $H'_{\mathrm{circuit}}$ to do the test, or to measure the history state to generate the desired outcome, but not both at the same time since the testing protocol would disturb the measurement outcome.
+% Specifically, we will certify the energy of $H'_{\mathrm{circuit}}$ to guarantee the underlying state is close to the valid history state.
+% However, this procedure could be vastly different from outputting a sample by measuring the final state of $\SampBQP$ circuits.
+To resolve that, we design a \emph{cut-and-choose} protocol on multiple copies of the history state so as to separate the testing and the outputting parts on separate copies of history states.
 
-\vspace{2mm} \noindent  \emph{$\diamond$ Compile $\QPIP_1$ into $\QPIP_0$}:
-A naive attempt is to directly apply Mahadev's protocol on the aforementioned $\QPIP_1$ protocol.
-Unfortunately, the plain version of Mahadev's protocol does not yield favorable parameters by itself.
-In fact, there are some recent results~\cite{arXiv:AlaChiHun19, arXiv:ChiaChungYam19} that provide a parallel repetition of Mahadev's original protocol for $\BQP$ with
-much more favorable parameters.
+The prover in the real protocol, of course, won't necessarily send copies of history states.
+Thus, to leverage the aforementioned intuition, one needs to avoid entanglement among these copies to obtain some sort of independence.
+We employ quantum \emph{de Finetti} theorem to address this technical challenge.
+Specifically, given any permutation-invariant $k$-register state (where each register could contain many qubits), it is known that the reduced state on many subsets of $k$-register will be close to a separable state.
+Typically, for favorable error bounds, the parameter $k$ could be as large as the dimension of a single register, which is exponential in our context and hence undesirable. 
+Fortunately, since there is no entangled operation in the protocol to perform on two copies of history states, one can employ an efficient variant of quantum \emph{de Finetti} theorem~\cite{Brandao2017} whose error bound depends poly-logarithmically on the dimension of the register, which leads to an efficient $\QPIP_1$ protocol for $\SampBQP$.
+Note further that this $\QPIP_1$ protocol is information-theoretically sound without any computational assumption.  (\Cref{sec:qpip1}.)
 
-However, we cannot directly make use of these parallel repetition results due to the subtle difference between protocols for $\BQP$ and $\SampBQP$.
-One of the major difficulties here is still to deal with both the test part and the output part in $\SampBQP$ protocols.
-However, because we are now in the computational setting, there is no longer any available quantum de Finetti theorem that is usually derived in the information-theoretic setting.
-We end up developing a weaker version of  parallel repetition of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}.
-Due to the nature of parallel repetition in the computational setting, our analysis is much less modular and significantly involved for this part.  
-More intuitions and detailed analysis are given in \Cref{sec:qpip0_all}.
+\vspace{2mm} \noindent  \emph{$\diamond$ Compile $\QPIP_1$ into $\QPIP_0$ after parallel repetition}: we are ready to address the aforementioned drawback of Mahadev's protocol.
+First, we will use Mahadev's compilation to obtain a $\QPIP_0$ protocol $\PiNaive$ for the above $\QPIP_1$ protocol.
+As mentioned previously, this protocol $\PiNaive$ will have some trouble outputting the desired sample in the testing round.
+To address this issue, we will separate the testing and the outputting in different runs of the protocol, similarly to what we have done in the design of $\QPIP_1$ protocol. 
+Precisely, we will run again a cut-and-choose protocol $\PiSampZ$ on top of many copies of $\PiNaive$, which are executed in parallel to preserve the number of rounds.
 
-\XW{stop here}
+However, since $\PiNaive$ only has computational soundness, we need to design a parallel repetition of $\PiNaive$ in the computational setting, which also prevents the use of quantum de Finetti theorem that only holds in the information-theoretical setting.
+Fortunately,  some recent results on computational parallel repetitions of Mahadev's original protocol for $\BQP$~\cite{arXiv:AlaChiHun19, arXiv:ChiaChungYam19} provide a technical starting point for us.
+Precisely, these results open the box of the analysis of Mahadev's protocol and analyze the computational soundness under a parallel repetition.
+
+\XW{highlight a bit about the open-the-box partition lemma}
+We end up developing a weaker version of  parallel repetition of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}. \Cref{sec:qpip0_all}.
+
+% A naive attempt is to directly apply Mahadev's protocol on the aforementioned $\QPIP_1$ protocol.
+% Unfortunately, the plain version of Mahadev's protocol does not yield favorable parameters by itself.
+% However, we cannot directly make use of these parallel repetition results due to the subtle difference between protocols for $\BQP$ and $\SampBQP$.
+% One of the major difficulties here is still to deal with both the test part and the output part in $\SampBQP$ protocols.
+% However, because we are now in the computational setting, there is no longer any available quantum de Finetti theorem that is usually derived in the information-theoretic setting.
+% Due to the nature of parallel repetition in the computational setting, our analysis is much less modular and significantly involved for this part.  
+% More intuitions and detailed analysis are given in
+
+\XW{Comment on Aaronson's blog}
 
@@
 Details are given in \Cref{sec:BlindBQP2}.
-
-\XW{To KM: expand the above a bit more?}
+%\XW{To KM: expand the above a bit more?}
 

### 2020-11-04 model.tex
Sync

--- 2020-10-04 preliminaries.tex
@@
-\section{Preliminaries}
+\section{Delegation of Quantum Sampling Problems}
 
-\subsection{Notations}
+In this section, we formally introduce the task of delegation for quantum sampling problem.
+We start by recalling the complexity class $\SampBQP$ defined by Aaronson~\cite{aaronson_2013, aaronson_arkhipov_2011}, which captures the class of sampling problems that
+are approximately solvable by polynomial-time quantum algorithms.
 
-Let $\mathcal{B}$ be the Hilbert space corresponding to one qubit.
-Let $H:\mathcal{B}^{\otimes n}\rightarrow\mathcal{B}^{\otimes n}$ be Hermitian matrices.
-We use $H\geq0$ to denote $H$ being positive semidefinite.
-Let $\lambda(H)$ be the smallest eigenvalue of $H$.
-The ground states of $H$ are the eigenvectors corresponding to $\lambda(H)$.
-For matrix $H$ and subspace $S$, let $H\big|_S=\Pi_S H \Pi_S$, where $\Pi_S$ is the projector onto the subspace $S$.
-%For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
-We write $x\xleftarrow{\$}X$ when $x$ is sampled uniformly at random from the set $X$.
+\begin{definition} [Sampling Problem]
+    \label{dfn:sampling-problem}
+    A \emph{sampling problem} is a collection of probability distributions $(D_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{m(n)}$ for some fixed polynomial $m$.
+\end{definition}
 
-The phase gate and Pauli matrices are the following matrices.
+\begin{definition} [$\SampBQP$]
+    $\SampBQP$ is the class of sampling problems $\left(D_x\right)_{x\in\set{0, 1}^*}$ that can be (approximately) sampled by polynomial-size uniform quantum circuits.
+Namely, there exists a Turing machine $M$ such that for every $n \in \bbN$ and $\eps \in (0,1)$, $M(1^n, 1^{1/\eps})$ outputs a quantum circuit $C$ in $\poly(n, 1/\eps)$ time such that for every $x \in \zo^n$, the output of $C(x)$ (measured in standard basis) is $\eps$-close to $D_x$.
+\end{definition}
+
+Note that in the above definition, there is an accuracy parameter $\eps$ and the quantum sampling algorithm only requires to output a sample that is $\eps$-close to the correct distribution in time $\poly(n,1/\eps)$, instead of the stringent requirement of outputting a perfect sample.
+There are multiple reasons for allowing an inverse polynomial error.
+For example, conceivable physical realizations of quantum computer may consist of inherent noise.
+We refer the readers to~\cite{aaronson_2013, aaronson_arkhipov_2011} for the discussion therein on why this better captures the sampling problem solvable by efficient quantum computers.
+
+We next define what does it mean for a $\QPIP_\tau$ protocol to solve a $\SampBQP$ problem $\left(D_x\right)_{x\in\set{0, 1}^*}$.
+Since sampling problem comes with an accuracy parameter $\eps$, we let the prover $P$ and the verifier $V$ receive the input $x$ and $1^\eps$ as common inputs. 
+Completeness is straightforward to define, which requires that when the prover $P$ is honest, the verifier $V$ should accept with high probability and output a sample $z$ distributed close to $D_x$ on input $x$.
+Defining soundness is more subtle.
+Intuitively, it requires that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interact with a malicious prover.
+We formalize this by a strong simulation-based definition, where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.
+Note that since the protocol receives the accuracy parameter $1^{\eps}$ as input to specify the allowed error, we do not need to introduce an additional soundness error parameter in the definition.
+
+\KM{should be better to add more discussion.}
+
+%\KM{point to discuss: (i) syntax: accuracy parameter $\eps$ (ii) simulation-based soundness (iii) no soundness error (iv) computational soundness
+}
+
+%Intuitively, completeness requires that when the prover $P$ is honest, the verifier $V$ should accept with high probability and output a sample $z$ close to $D_x$ on input $x$.
+Soundness should require that
 
 \begin{definition}
-    $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$,
-    $X=\begin{pmatrix}0&1\\1&0\end{pmatrix}$,
-    $Y=\begin{pmatrix}0&-i\\i&0\end{pmatrix}$,
-    $Z=\begin{pmatrix}1&0\\0&-1\end{pmatrix}$.
+    \label{dfn:stats-secure-proto-sampbqp}
+    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
+    We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c(\cdot)$ and statistical (resp., computational) soundness if the following holds:
+    \begin{itemize}
+        \item On public inputs $1^\lambda$, $1^{1/\eps}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
+            If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$ where $m$ is given in \Cref{dfn:sampling-problem}, otherwise $z=\bot$.
+        \item (Completeness):
+            For all accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
+            security parameter $\lambda\in\bbN$,
+            and $x\in\zo^{\poly(\lambda)}$,
+            Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
+        \item (Statistical soundness): For all cheating prover $P^*$,
+            accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
+            sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$,
+            consider the following experiment:
+            \begin{itemize}
+                \item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\eps}, x)$.
+                \item Define $z_{ideal}$ by
+                $$\begin{cases}
+                    z_{ideal}=\bot & \text{if } d=\Rej\\
+                    z_{ideal}\leftarrow D_x & \text{if } d=\Acc
+                \end{cases}$$.
+            \end{itemize}
+            It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\eps$.
+		\item (Computational soundness):
+			\Ethan{tried to write in terms of indistinguishability}
+        For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
+            sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$,
+            define $d, z, z_{ideal}$ by the same experiment as above.
+            It holds that $(d, z)$ is $\eps$-computationally indistinguishable to $(d, z_{ideal})$ over $\lambda$.
+    \end{itemize}
 \end{definition}
 
-For $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$,
-let $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ denote the trace distance between $\rho_1$ and $\rho_2$.
-We say $\rho_1$ and $\rho_2$ are $\eps$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\eps$.
-For two distributions $f_1$ and $f_2$ over the same finite domain $X$, let $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ denote their total variation distance,
-and we say $f_1$ and $f_2$ are $\eps$-close if $\norm{f_1-f_2}_{TV}\leq\eps$.
-We additionally denote the following for states that are only computationally indistinguishable (but might be statistically far):
-\begin{definition}
-\label{def:comp-indis}
-    Two ensemble of states $\set{\rho_{1,\lambda}}_{\lambda\in\bbN}$ and $\set{\rho_{2,\lambda}}_{\lambda\in\bbN}$ are \emph{$\eps$-computationally indistinguishable} if for all $\BQP$ distinguishers $\mathsf{D}$ and $\lambda\in\bbN$,
-    $$\abs{\Pr\left[\mathsf{D}(\rho_{1,\lambda})=1\right]-\Pr\left[\mathsf{D}(\rho_{2,\lambda})=1\right]}\leq\eps(\lambda).$$
-    % We also denote $\eps$-computational indistinguishability by $\rho_{1,\lambda}\approx_{c, \eps}\rho_{2,\lambda}$.
-    We drop the $\eps$ parameter when it is negligible.
-    We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized states as appropriate.
-    We also extend it to distributions by treating them as mixed states.
-\end{definition}
+As in the case of $\BQP$, we are particularly interested in the case that $\tau = 0$, i.e., when the verifier $V$ is classical.
+In this case, we say that $\Pi$ is a CVQC protocol for the $\SampBQP$ problem $(D_x)_{x\in\zo^*}$.
 
-We denote measurement as follows:
-\begin{definition} [quantum-classical channels]
-    \label{def:QCChannel}
-    A quantum measurement is given by a set of matrices $\set{M_k}$ such that $M_k\geq0$ and $\sum_k M_k=\id$.
-    We associate to any measurement a map $\Lambda(\rho)=\sum_k \tr(M_k\rho)\proj{k}$
-    with $\{\ket{k}\}$ an orthonormal basis.
-    This map is also called a \emph{quantum-classical channel}.
-\end{definition}
-Furthermore, we associate measurement outcomes in $X$ or $Z$ basis with a corresponding random variable as follows:
-\begin{definition}[$M_{XZ}(\rho,h)$]
-	For any natural number $n$, $n$-bit string $h$, and $n$-qubit quantum state $\rho$, consider the following measurement procedure: measure the first qubit of $\rho$ in $X$ basis if $h_1=0$; measure the first qubit of $\rho$ in $Z$ basis if $h_1=1$.
-Measure the second qubit of $\rho$ in $X$ basis if $h_2=0$; measure the second qubit of $\rho$ in $Z$ basis if $h_2=1$.
-Continue qubit-by-qubit until all $n$-qubits of $\rho$ are measured, where $i$-th qubit is measured in $X$ basis if $h_i=0$ and  $i$-th qubit is measured in the $Z$ basis if $h_i=1$.
+To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems.
+We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the soundness property we defined.
+Proving soundness of these constructions for delegating $\SampBQP$ is an interesting open question.
 
-	We denote the $n$-bit random variable corresponding to the measurement results as $M_{XZ}(\rho,h)$.
-\end{definition}
-
+\iffalse
 \subsection{Sampling Problems}
@@
 
-\iffalse
-
-Probably not necessary
-
-\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
-    Let $\rho_1, \rho_2, \rho_3\in\cB^{\otimes n}$ such that
-    \begin{align}
-        \rho_1\approx_{c, \eps}\rho_2\\
-        \rho_2\approx_{c, \eps'}\rho_3.
-    \end{align}
-    We have
-    \begin{align}
-        \rho_1\approx_{c, \eps+\eps'}\rho_3.
-    \end{align}
-\end{lem}
-
 \fi
-
-\subsection{Quantum Homomorphic Encryption Schemes}
-
-We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
-\begin{definition}
-    A quantum leveled homomorphic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
-    $\QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:
-    \begin{itemize}
-        \item \emph{Key generation.}
-            The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda, 1^L)$ takes a unary representation of the security parameter and a unary representation of the level parameter as inputs and outputs a public key $pk$ and a secret key $sk$.
-        \item \emph{Encryption.}
-            The algorithm $c\leftarrow\QEnc(pk, \mu)$ takes the public key $pk$ and a single bit message $\mu\in\zo$ as inputs and outputs a ciphertext $c$.
-        \item \emph{Decryption.}
-            The algorithm $\mu^*\leftarrow\QDec(sk, c)$ takes the secret key $sk$ and a ciphertext $c$ as inputs and outputs a message $\mu^*\in\zo$.
-            It must be the case that
-                $$\QDec(sk, \QEnc(pk, \mu))=\mu$$
-            with overwhelming probability in $\lambda$.
-        \item \emph{Homomorphic Evaluation.}
-            The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit $f$ of depth at most $L$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ as inputs and outputs a ciphertext $c_f$.
-            It must be the case that
-                $$\QDec(sk, \QEval(pk, f, c_1, \ldots, c_l))=f(\QDec(sk, c_1),\ldots,\QDec(sk, c_l))$$
-            with overwhelming probability in $\lambda$.
-    \end{itemize}
-\end{definition}
-
-\begin{definition}[Compactness and Full Homomorphism]
-    A quantum homomorphic encryption scheme $\QHE$ is compact if
-    there exists a polynomial $s$ in $\lambda$ such that the output length of $\QEval$ is at most $s$ bits long (regardless of $f$ or
-    the number of inputs). A compact scheme is (pure) fully homomorphic if it can evaluate any efficiently computable
-    boolean function.
-\end{definition}
-
-We also recall the security definition for a FHE scheme.
-
-\begin{definition}
-    A scheme $\QHE$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
-    $$\abs{Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(1))=1]}\leq\mu(\lambda)$$
-    where $(pk, sk)\leftarrow\QGen(1^\lambda)$
-\end{definition}
-
-The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitate the use of classical clients.
-
-\begin{definition} \label{def:classical-friendly}
-    we call a quantum homomorphic encryption scheme \emph{classical-friendly} if it has the following properties:
-    \begin{itemize}
-        \item $\QGen$ is a classical algorithm
-        \item In the case where the plaintext is classical, $\QEnc$ can be done classically.
-        \item When the underlying message is classical, the corresponding ciphertext is also classical and can be decrypted classically.
-    \end{itemize}
-\end{definition}
-
-\begin{theorem} [Theorem 1.1 in \cite{mahadev_qfhe}]
-    Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine,
-    there exists a classical-friendly compact quantum leveled homomorphic encryption scheme.
-\end{theorem}

### 2020-11-04 preliminaries.tex
Sync

--- 2020-09-04 preliminaries.tex
@@
 
-\subsection{Sampling Problems}
-
-We define the sampling version of $\BQP$ based on \cite{aaronson_2013, aaronson_arkhipov_2011}.
-The definition of $\SampBQP$ allows inverse-polynomial error in order to capture some characteristics of optics-based quantum computing implementations.
-
-\begin{definition} [sampling problem]
-    \label{dfn:sampling-problem}
-    A \emph{sampling problem} is a collection of probability distributions $(D_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{m(n)}$ for some fixed polynomial $m$.
-\end{definition}
-
-\begin{definition} [$\SampBQP$]
-    $\SampBQP$ is the class of sampling problems $\left(D_x\right)_{x\in\set{0, 1}^*}$ that can be (approximately) sampled by polynomial-size uniform quantum circuits.
-Namely, there exists a Turing machine $M$ such that for every $n \in \bbN$ and $\eps \in (0,1)$, $M(1^n, 1^{1/\eps})$ outputs a quantum circuit $C$ in $\poly(n, 1/\eps)$ time such that for every $x \in \zo^n$, the output of $C(x)$ (measured in standard basis) is $\eps$-close to $D_x$.
-\end{definition}
-
 \subsection{Quantum Prover Interactive Protocols (QPIP)}
 
-We model the interaction between a (almost classical) client and a quantum server following \cite{FOCS:Mahadev18a}.
-When the client has limited quantum memories, this is a ``streaming" model.
-That is, the server can send qubits one-by-one to let client measure them sequentially,
-even if the client cannot hold the entire quantum message.
-When the client is fully classical,
-this model specializes to the standard rounds-based model.
+Following \cite{FOCS:Mahadev18a}, we model the interaction between a (almost classical) client and a quantum server in the following definition.
+When the client has limited quantum memories (i.e., $\tau > 0$), this is a ``streaming" model.
+That is, the server can send qubits one-by-one to let client measure them sequentially, even if the client cannot hold the entire quantum message.
+When the client is fully classical (i.e, $\tau = 0$), this model specializes to the standard rounds-based interactive protocols.
 
@@
 
-It is straightforward to write down what it means for a $\QPIP_\tau$ protocol to recognize a $\BQP$ language.
+It is straightforward to define what it means for a $\QPIP_\tau$ protocol to decide a $\BQP$ language.
 
@@
 
-It is less simple to state what it means for a $\QPIP_\tau$ protocol to solve a $\SampBQP$ instance.
-We cannot hope for the protocol's output distribution to be close to the true distribution,
-since a cheating prover can abort to force the verifier output $\bot$ with arbitrary probability.
-On the other hand, we can ask that the output distribution to be close to the true one whenever the protocol does not abort.
+We are particularly interested in the case that $\tau = 0$, i.e., when the verifier $V$ is classical. In this case, we say $\Pi$ is a CVQC protocol for the $\BQP$ language $L$.
 
-\begin{definition}
-    \label{dfn:stats-secure-proto-sampbqp}
-    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
-    We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c(\cdot)$ and statistical (resp., computational) soundness if the following holds:
-    \begin{itemize}
-        \item On public inputs $1^\lambda$, $1^{1/\eps}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
-            If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$ where $m$ is given in \Cref{dfn:sampling-problem}, otherwise $z=\bot$.
-        \item (Completeness):
-            For all accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
-            security parameter $\lambda\in\bbN$,
-            and $x\in\zo^{\poly(\lambda)}$,
-            Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
-        \item (Statistical soundness): For all cheating prover $P^*$,
-            accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
-            sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$,
-            consider the following experiment:
-            \begin{itemize}
-                \item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\eps}, x)$.
-                \item Define $z_{ideal}$ by
-                $$\begin{cases}
-                    z_{ideal}=\bot & \text{if } d=\Rej\\
-                    z_{ideal}\leftarrow D_x & \text{if } d=\Acc
-                \end{cases}$$.
-            \end{itemize}
-            It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\eps$.
-		\item (Computational soundness):
-			\Ethan{tried to write in terms of indistinguishability}
-        For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
-            sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$,
-            define $d, z, z_{ideal}$ by the same experiment as above.
-            It holds that $(d, z)$ is $\eps$-computationally indistinguishable to $(d, z_{ideal})$ over $\lambda$.
-    \end{itemize}
-\end{definition}
-
-\begin{remark} Note that we do not parameterize the soundness error in Definition \ref{dfn:stats-secure-proto-sampbqp}.
-This is because the definition of $\SampBQP$ already includes an error parameter $\eps$, where the algorithm is allowed to generate a sample with statistical error up to $\eps$ in time polynomial in $1/\eps$.
-Hence, we define the soundness to  allow the verifier's output to have an $\eps$ error for any given inverse polynomial $\eps$ without introducing an extra soundness error parameter.
-\end{remark}
-
-We now define blindness of a protocol.
-In the context of blind protocols, we consider $x$ as the verifier's private input instead of a common input.
+We now define blindness, which means that the prover does not learn any information about the verifier's input except for its length.
+As such, in this context, we consider the input $x$ as the verifier's private input instead of a common input.
 
@@
 \begin{definition}[Blindness]
-    Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ (and $1^{1/\eps}$ for the case of $\SampBQP$ problem), and verifier's private input $x\in\zo^*$.
+    Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ 
+    %(and $1^{1/\eps}$ for the case of $\SampBQP$ problem), 
+    and verifier's private input $x\in\zo^*$.
     We say $\Pi$ is \emph{blind} if for all cheating $\BQP$ prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
     \begin{itemize}
-        \item $\set{\View_{P^*}(P^*, V(x))(1^\lambda, 1^{1/\eps})}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
-        \item $\set{\View_{P^*}(P^*, V(0))(1^\lambda, 1^{1/\eps})}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
+        \item $\set{\View_{P^*}(P^*, V(x))(1^\lambda)}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
+        \item $\set{\View_{P^*}(P^*, V(0))(1^\lambda)}_{\lambda\in\bbN, \eps\in(0^{|x|},1), x\in\zo^*}$
     \end{itemize}

### 2020-11-06 introduction.tex
Sync

@@
 
-Unfortunately, it is unclear how to make this de-randomization trick work for the delegation of $\SampBQP$, 
+Unfortunately, it is unclear about how to make this de-randomization trick work for the delegation of $\SampBQP$, 
 as randomness in quantum computation inherently comes from quantum mechanics rather than classical probability theory. 
-Thus, we do not know a generic construction from delegation for $\BQP$, and delegation of $\SampBQP$ may require a different construction.
+Thus, it seems that the delegation of $\SampBQP$ needs to take a different technical route.
 %delegation of $\SampBQP$ may require a totally different construction from delegation of $\BQP$. 
@@
 One natural starting point is Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} for $\BQP$. 
-Indeed, some nice features of Mahadev's protocol (e.g., allowing X-Z measurements on any qubit) suggest the feasibility of generating a multi-bit measurement outcomes with the protocol. 
-However, as highlighted below in the technical introduction section, there are also important drawbacks of Mahadev's protocol in its current form, which makes it hard to allow a CVQC protocol for $\SampBQP$ with desired completeness and soundness.
+Indeed, some nice features of Mahadev's protocol (e.g., allowing X-Z measurements on any qubit) suggest the feasibility of generating  multi-bit measurement outcomes with the protocol. 
+However, as highlighted below in the technical introduction section, there are also important drawbacks of Mahadev's protocol in its current form, which makes it hard to allow a CVQC protocol for $\SampBQP$ with desired performance.
 As we shall see, such difficulties do not hold for the decision problem, which demonstrates an importance difference between CVQC protocols for the decision and the sampling problems.
@@
 
-In fact, most existing blind and verifiable CVQC protocols require a notable amount of effort in achieving each property respectively. 
-The only successful attempt~\cite{FOCS:GheVid19} of achieving both so far applies Mahadev's technique~\cite{FOCS:Mahadev18a} to the measurement-based quantum computation, whereas the analysis is still very specific to the construction.
+In fact, most existing blind and verifiable protocols for delegation of quantum computation require a notable amount of effort in achieving each property respectively. 
+The only successful CVQC protocol~\cite{FOCS:GheVid19} of achieving both so far applies Mahadev's technique~\cite{FOCS:Mahadev18a} to the measurement-based quantum computation, whereas the analysis is still very specific to the construction.
 %\Ethan{And it has inverse-poly errors, which makes it not constant-round to achieve negligible errors for $\BQP$, right?}
-Could there be a \emph{generic} way to achieve blindness and verifiability for CVQC protocols at the same time, say by leveraging the state of the art CVQC~\cite{FOCS:Mahadev18a} and QFHE~\cite{mahadev_qfhe} protocol?
+Could there be a \emph{generic} way to achieve blindness and verifiability for CVQC protocols at the same time, say by leveraging the state-of-the-art CVQC~\cite{FOCS:Mahadev18a} and QFHE~\cite{mahadev_qfhe} protocols?
 
@@
 In particular, we demonstrate the feasibility of the classical verification of quantum sampling by
-constructing a constant-round CVQC protocol for $\SampBQP$, the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}, based on the quantum LWE (QLWE) assumption that the learning with error problem is hard for BQP machines.
+constructing a constant-round CVQC protocol for $\SampBQP$, the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}, based on the quantum LWE (QLWE) assumption that the learning-with-error problem is hard for BQP machines.
 Formally, $\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine with an inverse polynomial accuracy.
-%Namely, $A(x,1^{1/\eps})$ outputs a sample that is $\eps$-close to the distribution $D_x$ in statistical distance.
+\KM{add ref to Sec 3}  %Namely, $A(x,1^{1/\eps})$ outputs a sample that is $\eps$-close to the distribution $D_x$ in statistical distance.
 %, where given an input $x \in \zo^n$, the goal  
@@
 
-Our second contribution is a simple yet powerful \emph{generic}  compiler that transforms any CVQC protocol to a blind one while preserving completeness and soundness errors, building on top of QFHE.
-We observe that QFHE, especially the one from~\cite{mahadev_qfhe}, can be used to transform any CVQC protocol to \emph{a blind one with the same number of round communication, while preserving completeness and soundness error}.
+Our second contribution is a simple yet powerful \emph{generic}  compiler that transforms any CVQC protocol to a blind one while preserving verifiability, building on top of QFHE. 
+Precisely, we leverage QFHE (especially the one from~\cite{mahadev_qfhe}) to transform any CVQC protocol to \emph{a blind one with the same number of round communication, while preserving completeness and soundness properties}.
 As a result, one can \emph{upgrade} every verifiable CVQC protocol with blindness almost for free with the help of QFHE.
-Conceptually, we take a very different approach from previous results (e.g.,~\cite{FK17} as well as failed attempts in~\cite{mahadev_2018}) which use the blindness as the start point and then work to extend it with verifiability.
-Instead, our strategy is to simulate the original CVQC protocol under QFHE per each message.
+Conceptually, we take a very different approach from previous ones  (e.g.,~\cite{FK17} as well as failed attempts in~\cite{mahadev_2018}) which use the blindness as the start point and then work to extend it with verifiability.
+Instead, our strategy is to simulate a (verifiable) CVQC protocol under QFHE per each message.
 To that end, we do require a special property of QFHE that the classical part of the ciphertext can be operated on separately from the quantum part, which is satisfied by the construction from~\cite{mahadev_qfhe}.
@@
 This large soundness error is due to the current structure of Mahadev's protocol that consists of the \emph{testing} round and the \emph{Hadamard} round, each of which happens with a half chance. 
-At a high level, the protocol verifies the behavior of the prover in the test round, while assumes that the prover behaves honestly and all the X-Z measurements are correct in the Hadamard round. 
+At a high level, the protocol verifies the behavior of the prover in the testing round, while assumes that the prover behaves honestly and all the X-Z measurements are correct in the Hadamard round. 
 The soundness is obtained by observing that the dishonest prover cannot cheat in both rounds, while cheating in one round alone is possible which leads to a large soundness error. 
@@
 
-A key difference between $\SampBQP$ and $\BQP$ is that in addition to the single bit $\mathrm{Accept/Reject}$ information, the verifier in any CVQC protocol for $\SampBQP$ needs to always output a sample of the desired distribution when the protocol accepts.
-This fundamentally new requirement of $\SampBQP$ could be, as we will show, fulfilled in the Hadamard round of Mahadev's protocol. 
-However, it is unclear how to generate such a sample when the protocol accepts in the testing round, since the sampling information stored in the quantum state will be disturbed by the testing step.
+The first thing when dealing with $\SampBQP$ is to properly define the requirement of CVQC protocols for $\SampBQP$. 
+In contrast to the single bit $\mathrm{Accept/Reject}$ information for the decision $\BQP$, any $\SampBQP$ problem needs to always output a sample of the desired distribution.
+In the context of CVQC protocols, it means that the protocol should allow the verifier to generate a desired output sample whenever the protocol accepts. 
+(Of course, when the prover cheats, the verifier will reject and no further output is required in that case.)
+We provide a formal definition for CVQC protocols for $\SampBQP$ in Section~\ref{sec:samp_definition} to capture the above intuition. \KM{say the distribution should be correct conditioned on accepts}
+
+\KM{terminology: testing protocol, test round etc.}
+
+This fundamentally new requirement of any CVQC protocol for $\SampBQP$ exposes one drawback of Mahadev's protocol: 
+while it is possible, as we will show, to generate desired output samples in the Hadamard round, 
+it is however unclear about how to generate such a sample when the protocol accepts in the testing round, since the sampling information stored in the quantum state will be disturbed by the testing step.
 
 As a result, in order to construct a $\QPIP_0$ protocol for $\SampBQP$,  one needs to (1) construct a $\QPIP_1$ protocol for $\SampBQP$ with very small completeness and soundness errors, and (2) amend Mahadev's construction so that the protocol will generate the desired sample whenever it accepts.
-Our first contribution is a solution to address the above two technical challenges.
+Our contribution is a solution to address the above two technical challenges.
 
@@
 Fortunately, since there is no entangled operation in the protocol to perform on two copies of history states, one can employ an efficient variant of quantum \emph{de Finetti} theorem~\cite{Brandao2017} whose error bound depends poly-logarithmically on the dimension of the register, which leads to an efficient $\QPIP_1$ protocol for $\SampBQP$.
-Note further that this $\QPIP_1$ protocol is information-theoretically sound without any computational assumption.  (\Cref{sec:qpip1}.)
+We can further achieve very small completeness and soundness errors in this way to satisfy the premise of Mahadev's compilation.  
+Note that the established $\QPIP_1$ protocol is information-theoretically sound without any computational assumption.  (\Cref{sec:qpip1}.)
 
@@
 
-\XW{highlight a bit about the open-the-box partition lemma}
-We end up developing a weaker version of  parallel repetition of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}. \Cref{sec:qpip0_all}.
+\XW{Precisely, comment on the partition lemma~\cite{arXiv:ChiaChungYam19}, and how it is used ...}
+% We end up developing a weaker version of  parallel repetition of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}. 
+\XW{Note that there is also an important difference between us and~\cite{arXiv:ChiaChungYam19}, the difference between decision and sampling problems.}
+\Cref{sec:qpip0_all}.
 
@@
 
-\XW{Comment on Aaronson's blog}
+It is worthwhile mentioning that we came to notice some online discussion\footnote{\url{https://www.scottaaronson.com/blog/?p=3697}, e.g., comment \#25, \#26, \#42, \#48.
+} on the possibility of a CVQC protocol for $\SampBQP$ after we developed our own result.
+These comments suggested a possible reduction of $\SampBQP$ to the local Hamiltonian problem following a similar high-level idea as our solution, however, with no detail and a seemingly different technical route.
+However, they failed to identify other important gaps in the protocol design that we have addressed.
 
-\vspace{2mm} \noindent \textbf{(2) A generic compiler to upgrade $\QPIP_0$ protocols with blindness}.
+\vspace{2mm} \noindent \textbf{A generic compiler to upgrade $\QPIP_0$ protocols with blindness}.
 At a high-level, the idea is simple: we run the original protocol under a QFHE with the verifier's key.

### 2020-11-06 qpip.tex
Add some comments on qpip0 proof
Sync

@@
 
-\begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for the $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$}
+\begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for the $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$}
 	\label{ProtoQPIP1}
@@
     \label{QPIP1thm}
-	$\PiSamp$ has negligible completeness error and is statistically sound. 
+	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}}
 	%\XW{do we want precise error bound?}
@@
 	For completeness, notice $y_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
-	So we can apply Chernoff bound (\Cref{thm:Chernoff}) to get
+	So we can apply Chernoff bound to get
 	$$\Prob{Y>\frac{m}{2}-\eps m}\leq\negl(\lambda).$$

### 2020-11-06 qpip0.tex
Sync

@@
 		\item Prover's input: a state $\rho\in\cB^{\otimes n}$ for the verifier to measure.
-		\item Verifier's input: the measurement basis choice $h \in \zo^n$ \hannote{those two parameters are actually called input?}
+		\item Verifier's input: the measurement basis choice $h \in \zo^n$
 	\end{itemize}
@@
 Let $1-p_{h,T}$ be the  probability that the verifier accepts $\PMeasureStar$ in the testing round on basis choice $h$.\footnote{Compared to Claim 7.1 of \cite{FOCS:Mahadev18a}, we don't have a $p_{h,H}$ term here.
-This is because on rejecting a Hadamard round, the verifier can output a uniformly random string, and that is the result of measuring $h$ on the totally mixed state.} Under the QLWE assumption, there exists some $\rho^*$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round has $\sqrt{p_{h,T}}+\negl(n) $ computational distance\footnote{Two distributions has $c$ computational distance if any efficient algorithm can produce at most $c$ bias between them.}  from $M_{XZ}(\rho^*, h)$.
+This is because on rejecting a Hadamard round, the verifier can output a uniformly random string, and that is same as the result of measuring $h$ on the totally mixed state.} Under the QLWE assumption, there exists some $\rho^*$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is $\sqrt{p_{h,T}}+\negl(n)$-computationally indistinguishable from $M_{XZ}(\rho^*, h)$.
+
+%\footnote{Two distributions has $c$ computational distance if any efficient algorithm can produce at most $c$ bias between them.}
 
@@
 			\begin{enumerate}
-				\item The verifier samples $(pk, sk)\leftarrow\cVNaive{1}(1^\lambda, h)$ and sends $pk$ to the prover. \hannote{shouldn't those be $V_{meas,1}$?}
-				\item The prover runs $(y, \sigma)\leftarrow\cPNaive{2}(pk, \rho)$ and sends $y$ to the verifier.
-					Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but simplifies our analysis.
+				\item The verifier samples $(pk, sk)\leftarrow\cVNaive{1}(1^\lambda, h)$ and sends $pk$ to the prover, where $\cVNaive{1}$ is the same as $\cVMeasure{1}$ of \Cref{proto:urmila4}. 
+				\item The prover runs $(y, \sigma)\leftarrow\cPNaive{2}(pk, \rho)$ and sends $y$ to the verifier, where $\cPNaive{2}$ is the same as $\cPMeasure{2}$.
+					Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but simplifies our analysis of parallel repetition later.
 				\item\label{step:c-urmila-in-naive} The verifier samples $c\xleftarrow{\$}\zo$ and sends it to the prover.
@@
 This binding property is formalized in \Cref{lem:naive-qpip0-binding}.
-The intuition of the proof of \Cref{lem:naive-qpip0-binding} is to reduce\hannote{not quite?} to \Cref{lem:urmila-binding} by constructing another $\BQP$ prover\hannote{this is really confusing..} $\Pstar$ for $\PiMeasure$.
-\hannote{and the binding of $P*$ implies the binding of $P^*_{int}$}
-Specifically, $\Pstar$ uses $\PNaiveStar$'s strategy when it doesn't abort, otherwise honestly chooses some default state for the verifier to measure.
+Intuitively,  the proof of \Cref{lem:naive-qpip0-binding}  combines the binding property of \Cref{proto:qpip0_naive} (\Cref{lem:urmila-binding}) and $\PiSamp$'s soundness (\Cref{QPIP1thm}).
+There is a technical issue that \Cref{proto:qpip0_naive} allows the prover to abort while \Cref{proto:urmila4} doesn't.
+This issue is solved by constructing another $\BQP$ prover $\Pstar$ for every cheating prover $\PNaiveStar$.
+Specifically, $\Pstar$ uses $\PNaiveStar$'s strategy when it doesn't abort, otherwise honestly chooses the totally mixed state for the verifier to measure.
 %We now state the theorem and proof.
+%\hannote{and the binding of $P^*$ implies the binding of $P^*_{int}$}
 
@@
 	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
-	Suppose that $\Prob{d=\Acc\mid y\ne\bot, c=0}$ is overwhelming for all $x$, \Ethan{This good?}
+	Suppose that $\Prob{d=\Acc\mid y\ne\bot, c=0}$ is overwhelming, 
 	under the QLWE assumption, then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
@@
 \begin{proof}
-	We first introduce the \emph{dummy strategy} for ~\Cref{proto:qpip0_naive}, where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
+	We first introduce the \emph{dummy strategy} for ~\Cref{proto:urmila4}, where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
 	It is straightforward to verify that this prover would be accepted in the testing round with probability $1-\negl(\lambda)$,
@@
 
-   In the following we fix an $x$.
-
-	Now we construct a cheating $\BQP$ prover for $\PiMeasure$, $\Pstar$, that is almost perfect as follows.
-	For the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
+   %for $\PiMeasure$ $\Pstarsub$ that is almost perfect as follows. 
+	Now we construct a cheating $\BQP$ prover for \Cref{proto:qpip0_naive}, $\Pstar$, that does the same thing as $\PNaiveStar$ except at Step~\ref{step:urmila-in-naive}, where the prover and verifier runs \Cref{proto:urmila4}.
+$\Pstar$ does the following in Step~\ref{step:urmila-in-naive}:
+	for the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
 	If $y\ne\bot$, then reply $y$;
@@
 
+	 In the following we fix an $x$.
 Let the distribution on $h$ specified in Step~\ref{step:naive1} of the protocol be $p_x(h)$.
-By construction $\Pstar$ passes testing round with overwhelming probability over $p_x(h)$, i.e.
-$\sum_h p_x(h) p_{h,T} =\negl{\lambda}$, where $p_{h,T}$ is $\Pstar$'s probability of getting accepted by the prover on the testing round on basis choice $h$.
-By \Cref{lem:urmila-binding} and Cauchy's inequality, there exists some $\rho$ such that  $\sum_h p_x(h) \norm{v_h -M_{XZ}(\rho, h)}_c = \negl(\lambda)$, where $\norm{}_c$ means computational distance.
-\hannote{defined in a footnote ahhhhhhhhh}.
+Note that we can take $\Pstar$'s responds in Step~\ref{step:urmila-in-naive}, $\Pstarsub(x)$, as a prover strategy for \Cref{proto:urmila4}.
+By construction $\Pstarsub(x)$ passes testing round with overwhelming probability over $p_x(h)$, i.e.
+$\sum_h p_x(h) p_{h,T} =\negl(\lambda)$, where $p_{h,T}$ is $\Pstar$'s probability of getting accepted by the prover on the testing round on basis choice $h$.
+By \Cref{lem:urmila-binding} and Cauchy's inequality, there exists some $\rho$ such that  $\sum_h p_x(h) \norm{v_h -M_{XZ}(\rho, h)}_c = \negl(\lambda)$, where we use $\norm{A-B}_c=\alpha$ to denote that $A$ is $\alpha$-computational indistinguishable to $B$.
 Therefore $v= \sum_h p_x(h) v_h$ is computationally indistinguishable to $\sum_h p_x(h) M_{XZ}(\rho, h)$.
-
-	Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}), \hannote{computational ok?}
-
-	we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\varepsilon}, x)$ \hannote{fix notation} is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.
+Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}),
+	we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\varepsilon}, x)$  is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.
 
@@
 	First, conditioned on that $\PNaiveStar$ aborts, since dummy strategy will be rejected with overwhelming probability in Hadamard round,
-	we have $(d', z')$ is $O(\varepsilon)$-computationally\hannote{negl(lambda)?} indistinguishable to $(\Rej, \bot)=(d, z)$.
+	we have $(d', z')$ is computationally indistinguishable to $(\Rej, \bot)=(d, z)$.
 	On the other hand, conditioned on $\PNaiveStar$ not aborting, clearly $(d, z)=(d', z')$.
-	So $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d', z')$,
-	which in turn is $\negl(\lambda)$-computationally indistinguishable to $(d', z_{ideal}')$.\hannote{switch errors?}
-	Since $\abs{d-d'}\leq O(\eps)$ \hannote{?},
+	So $(d, z)$ is computationally indistinguishable to $(d', z')$,
+	which in turn is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
+	Since $\norm{d-d'}_{tr}= O(\eps)$,
 	 $(d, z_{ideal})$ is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
@@
 It is essentially a $m$-fold parallel repetition of $\PiNaive$,
-but instead of having each copy running testing round or Hadamard round uniformly at random, we randomly pick one copy to run Hadamard round to get our samples and run testing round on all other $m-1$ copies.
+from which we uniformly randomly pick one copy to run Hadamard round to get our samples and run testing round on all other $m-1$ copies.
 Intuitively, if the server wants to cheat by sending something not binding on some copy,
 he will be caught when that copy is a testing round, which is with probability $1-1/m$.
-This over-simplified analysis does not take into account that the server might create entanglements between the copies, however, so the correct analysis is more technically involved.
+This over-simplified analysis does not take into account that the server might create entanglement between the copies. Therefore, a more technically involved analysis is required.
 
@@
 	Ingredient: Let $m=O(1/\eps^2)$ be the number of parallel repetitions to run.
+\bigskip
 
@@
 	\begin{enumerate}
-		\item  The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ as in \stepref{naive1} of $\PiNaive$.
+		\item  The verifier  generates $m$ independent copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$, where each copy is generated as in \stepref{naive1} of $\PiNaive$.
 		\item The prover prepares $\rho^{\otimes m}$; each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$.
@@
 To show that it is computationally sound, we first use the partition lemma from \cite{arXiv:ChiaChungYam19}.
-\Ethan{Tried to ``slow down" on this paragraph}
-It says that for each copy $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
-$G_{0,i}$ intuitively represents the subspace where the server does not knows the answer to the testing round on the $i$-th copy, while $G_{1,i}$ represents the subspace where the server does.
-By using this partition lemma iteratively, we can decompose the prover's internal state $\ket{\psi}$.
-First we apply it to the first copy, writing $\ket{\psi}=G_{0,1}\ket{\psi}+G_{1,1}\ket{\psi}=\ket{\psi_0}+\ket{\psi_1}$.
-The component $\ket{\psi_0}$ would then get rejected as long as the first copy is a testing round,
-which occurs with high probability.
+
+Intuitively, the partition lemma says that for any cheating prover and for each copy $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
+$G_{0,i}$ and $G_{1,i}$ splits up the prover's internal state after sending back his first message.
+$G_{0,i}$ intuitively represents the subspace where the prover does not knows the answer to the testing round on the $i$-th copy, while $G_{1,i}$ represents the subspace where the prover does.
+Note that the prover is using a single internal space for all copies, and every $G_{0,i}$ and every $G_{1,i}$ is acting on this single internal space.
+By using this partition lemma iteratively, we can decompose the prover's internal state $\ket{\psi}$ into sum of subnormalized states.
+First we apply it to the first copy, writing $\ket{\psi}=G_{0,1}\ket{\psi}+G_{1,1}\ket{\psi} \equiv \ket{\psi_0}+\ket{\psi_1}$.
+The component $\ket{\psi_0}$ would then get rejected as long as the first copy is chosen as a testing round,
+which occurs with pretty high probability.
 More precisely, the output corresponding to $\ket{\psi_0}$ is $1/m$-close to the ideal distribution that just rejects all the time.
 On the other hand, $\ket{\psi_1}$ is now binding on the first copy;
-we now similarly apply the partition lemma to the second copy of $\ket{\psi_1}$.
-We write $\ket{\psi_1}=G_{0,2}\ket{\psi_1}+G_{1,2}\ket{\psi_1}=\ket{\psi_{10}}+\ket{\psi_{11}}$, and apply the same argument about $\ket{\psi_{10}}$ and $\ket{\psi_{11}}$.
+we now similarly apply the partition lemma of the second copy to $\ket{\psi_1}$.
+We write $\ket{\psi_1}=G_{0,2}\ket{\psi_1}+G_{1,2}\ket{\psi_1}\equiv \ket{\psi_{10}}+\ket{\psi_{11}}$, and apply the same argument about $\ket{\psi_{10}}$ and $\ket{\psi_{11}}$.
 We then continue to decompose $\ket{\psi_{11}}=\ket{\psi_{110}}+\ket{\psi_{111}}$ and so on, until we reach the last copy and obtain $\ket{\psi_{1^m}}$.
@@
 
-There is an additional issue, however, as $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m}}$ is unfortunately only binding for the $m$-th copy.
+There is an additional issue, however. As $G_{1,i}$ does not commute with $G_{1,j}$, $\ket{\psi_{1^m}}$ is unfortunately only binding for the $m$-th copy.
 To solve this problem, we start with a pointwise argument and fix the Hadamard round on the $i$-th copy where $\ket{\psi_{1^i}}$ is binding,
@@
 
-Also as a careful reader might have noticed, in fact the prover's space don't always decompose cleanly.
+Also as a careful reader might have noticed that the prover's space don't always decompose cleanly.
 In \cite{arXiv:ChiaChungYam19} this is solved by splitting the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
@@
 Property~\ref{property-partition-norm-sum} comes from the fact that $G_0$ and $G_1$ are post-selections of orthogonal results of the same $G$.}]\label{lem:partition2}
-	Let $\lambda$ be the security parameter, and $\gamma_0 \in[0,1]$ and $T\in \mathbb{N}$ be parameters that will relate to the randomly-chosen threshold $\gamma$.
+	Let $\lambda$ be the security parameter, and $\gamma_0 \in[0,1]$ and $T\in \mathbb{N}$ be parameters that will be related to the randomly-chosen threshold $\gamma$.
 	Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message.
-Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$, which corresponds to Hadamard round on the $i$-th copy and testing round on all others.
+\hannote{$H_{XZ}$} Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$, which corresponds to doing Hadamard round on the $i$-th copy and testing round on all others.
 
-	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit with post selection\footnote{A quantum circuit with post selection is composed of unitary gates followed by a post selection on some measurement outcome on ancilla qubits, so it produces a subnormalized state, where the amplitude square of the output state is the probability of post selection.} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized) $\poly(\lambda)$-qubits quantum state $\ket{\psi}_{\regX,\regZ}$,
+	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two $\poly(1/\gamma_0,T,\lambda)$-time quantum circuit with post selection\footnote{A quantum circuit with post selection is composed of unitary gates followed by a post selection on some measurement outcome on ancilla qubits, so it produces a subnormalized state, where the amplitude square of the output state is the probability of post selection.} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized) $\poly(\lambda)$-qubits quantum state $\ket{\psi}_{\regX,\regZ}$,  properties \ref{property:partition-err}~\ref{property:partition-testing}~\ref{property:partition-binding}~\ref{property-partition-norm-sum}, to be described later, are satisfied.
+Before we describe the properties, we introduce the following notations:
 
 	\begin{align}
-		G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{0,i,\gamma}}_{\regX,\regZ} \\ G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{1,i,\gamma}}_{\regX,\regZ}  \\
-		\ket{\psi}_{\regX,\regZ} =&   \ket{\psi_{0,i,\gamma}}_{\regX,\regZ}+ \ket{\psi_{1,i,\gamma}}_{\regX,\regZ}+\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}
+	\label{eq:psi0}	G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{0,i,\gamma}}_{\regX,\regZ} \\ 
+	\label{eq:psi1}	G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{1,i,\gamma}}_{\regX,\regZ}  \\
+	\label{eq:psierr}	\ket{\psi}_{\regX,\regZ} -\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}- \ket{\psi_{1,i,\gamma}}_{\regX,\regZ} \defeq&   \ket{\psi_{err,i,\gamma}}_{\regX,\regZ}
 	\end{align}
@@
 
-	Furthermore, the following properties are satisfied for all $i\in[m]$.
+	The following properties are satisfied for all $i\in[m]$:
 	\begin{enumerate}
@@
 		\item \label{property:partition-testing}
-			For all $\vec{pk}$, $\vec{y}$, fixed $\gamma$, and  $j\neq i$, we have
+			For all $\vec{pk}$, $\vec{y}$, $\gamma$, and  $j\neq i$, we have
 			\begin{align}
@@
 		\item \label{property:partition-binding}
-			For all $\vec{pk}$, $\vec{y}$, fixed $\gamma$, and $j\neq i$, there exists an efficient quantum algorithm $\ext_i$ such that
+			For all $\vec{pk}$, $\vec{y}$, $\gamma$, and $j\neq i$, there exists an efficient quantum algorithm $\ext_i$ such that
 			\begin{align}
@@
 			\begin{align}
-				\norm{\ket{\psi_{0,i,\gamma}}}^2+ \norm{\ket{\psi_{1,i,\gamma}}}^2 \leq  \norm{\ket{\psi}}^2
+				\norm{\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}^2+ \norm{\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}^2 \leq  \norm{\ket{\psi}_{\regX,\regZ}}^2
 			\end{align}
@@
 
-By Property~\ref{property:partition-testing} of the partition lemma above,
-it clearly also follows that \Ethan{This ok?}
-\begin{rmk}
-	\label{lem:partition-testing}
-	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and all $i,j\in[m]$ such that $j<i-1$, we have
-	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
-\end{rmk}
+Note that in property~\ref{property:partition-binding}, we are using $\ext_i$ instead of $U$ because we are doing some amplitude amplification to boost the success probability.
+\hannote{some discussion on why we want $G$ to be efficient.}
 
@@
 we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
-For all $k\leq m$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$ \Ethan{This ok?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.$$
-For all $i\in[m]$, we then decompose
+For all $k \in [m]$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$ \Ethan{This ok?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.$$
+For all $i\in[m]$, we then decompose $\ket{\psi}$ into
 \begin{equation}
@@
 \end{equation}
-where $\ket{\psi_{err,i,\gamma}}$ denotes the error state from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
+by using \Cref{eq:psi0,eq:psi1,eq:psierr} repeatedly,  where $\ket{\psi_{err,i,\gamma}}$ denotes the error state from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
 
@@
 Note that $P_{acc,i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $\vec{a}$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
+$P_{acc,i,z}$ is a projector because it only involves the projective measurements to get $a$ and classical post-processing of the verifiers.
+Also note that  $P_{acc,i,z} P_{acc,i,z'}=0$ for all $z\neq z'$, and $\sum_z P_{acc,i,z} \leq Id$.
 
@@
 Note that we have averaged over $\vec{pk}, \vec{y}$ where as previously everything has fixed $\vec{pk}$ and $\vec{y}$.
+
+By Property~\ref{property:partition-testing} of \Cref{lem:partition2},
+it clearly follows that \Ethan{This ok?}
+\begin{rmk}
+	\label{lem:partition-testing}
+	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and all $i,j\in[m]$ such that $j<i-1$, we have
+	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
+\end{rmk}
+
 Now we define
@@
 \end{equation}
-as the output corresponding to the component that would pass all $i$ testing rounds.
+as the output corresponding to a component that would pass the $i$-th testing rounds.
 We will show that it is $O(\norm{\ket{\psi_{1^{i-1}0}}})$-close to $z_i$.
@@
 The analysis is tedious but straightforward;
-we simply expand $z_i$ and bound the terms other than $z_{good, i}$.
+we simply expand $z_i$ and bound the terms that are not $z_{good, i}$.
 
@@
 	by the triangle inequality.
-	The last three error terms sum to $O\L(\frac{m^2}{\sqrt{T}}\R)$ by \Cref{lem:samp-tech} and \Cref{property:partition-err} of \Cref{lem:partition2}.
+	The last three error terms sum to $O\L(\frac{m^2}{\sqrt{T}}\R)$ by \Cref{lem:samp-tech} and property~\ref{property:partition-err} of \Cref{lem:partition2}.
 	As for the first two terms, by \Cref{lem:samp-tech} and \Cref{lem:partition-testing}, we see that
@@
 
-Now let $z_{true}$, as a mixed state, be correctly sampled from the $\SampBQP$ instance $D_x$,
+Now let $z_{true}$, as a mixed state, be the correct sample of the $\SampBQP$ instance $D_x$,
 and let $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
@@
 \begin{proof}
-	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for $\PiSampZ$, consider the following composite strategy of the prover for $\PiNaive$.
-Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of $\PiNaive$ where $\PiMeasure$ is run, so we describe the prover's action in terms of the four rounds of communication in $\PiMeasure$.
+	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for $\PiSampZ$, consider the following composite strategy, $\Picomp$, as a prover for $\PiNaive$.
+Note that a prover only interacts with the verifier in Step~\ref{step:urmila-in-naive} of $\PiNaive$ where $\PiMeasure$ is run, so we describe a prover's action in terms of the four rounds of communication in $\PiMeasure$.
 
-	The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of $\PiMeasure$ in $\PiSampZ$ and simulating other $m-1$ copies by himself.
+	$\Picomp$ tries to run $U_0$ by taking the verifier's input as the input to the $i$-th copy of $\PiMeasure$ in $\PiSampZ$ and simulating other $m-1$ copies by himself.
 The prover then picks a uniformly random $\gamma$ and  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
+This can be efficiently done because of \Cref{lem:partition2} and our choice of $\gamma_0$ and $T$ in \Cref{thm:qpip0}.
 If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and aborts by sending $\bot$ back.
@@
 
-	Denote the result we would get when $c=1$ by $z_{composite,i}$.
+	Denote the result we would get in the Hadamard round by $z_{composite,i}$.
 By construction, when $G_{i,1,\gamma}\ldots G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$.
@@
 
-	By ~\cref{property:partition-binding} of ~\Cref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort.
+	In the testing round, by property~\ref{property:partition-binding} of ~\Cref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort.
 	Since the prover's strategy is also efficient, by ~\Cref{lem:naive-qpip0-binding},
-	$z_{composite}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
+	$z_{composite,i}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$. \hannote{fix notation difference..}
 \end{proof}
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:qpip0} \hannote{to the form of thm 4.4. call to thm 1.1?}
 	Under the QLWE assumption, $\PiSampZ$ is a computationally sound protocol for $\SampBQP$.
@@
 	where we used triangle inequality on the second line, \Cref{thm:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
-	Let $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$ and by triangle inequality we have $\tr\abs{z-z_{ideal}}=O(\varepsilon)$.
+	Set $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$.
+Combining \Cref{thm:zgood-zideal} and \Cref{eq:z-z-good} by triangle inequality, we have $\tr\abs{z-z_{ideal}}=O(\varepsilon)$.
+\hannote{computational?}
 	Since $z$ is close to some ideal output distribution $z_{ideal}$, it must be close to the ideal output distribution with its own accept probability too.

### 2020-11-06 introduction.tex
Sync

@@
 However, as highlighted below in the technical introduction section, there are also important drawbacks of Mahadev's protocol in its current form, which makes it hard to allow a CVQC protocol for $\SampBQP$ with desired performance.
-As we shall see, such difficulties do not hold for the decision problem, which demonstrates an importance difference between CVQC protocols for the decision and the sampling problems.
+As we shall see, such difficulties do not hold for the decision problem, which demonstrates an important difference between CVQC protocols for the decision and the sampling problems.
 
@@
 Moreover, the blindness property is known to be helpful to establish the verifiability of CVQC protocols. However, this is never an easy task.
-See for example the significant amount of efforts to add verifiability to blind CVQC protocols in~\cite{FK17}.
+See for example the significant amount of efforts to add verifiability to blind computation protocol in~\cite{FK17}.
 It is also known that another important primitive called the Quantum Fully Homomorphic Encryption (QFHE)~\cite{BJ15, DSS16, LC18, NS18, OTF18, mahadev_qfhe} should be helpful for establishing blindness: this is intuitive since QFHE allows fully homomorphic operations on encrypted quantum data.
@@
 The constructed QFHE automatically implies a blind CVQC protocol, however, without verifiability.
-Extending this protocol with verifiability seems challenging as hinted by failed attempts in Section 2.2.2 of Mahadev's Phd thesis~\cite{mahadev_2018}.
+Extending this protocol with verifiability seems challenging as hinted by failed attempts in Section 2.2.2 of Mahadev's PhD thesis~\cite{mahadev_2018}.
 
@@
 \vspace{2mm} \noindent  \emph{$\diamond$ Compile $\QPIP_1$ into $\QPIP_0$ after parallel repetition}: we are ready to address the aforementioned drawback of Mahadev's protocol.
-First, we will use Mahadev's compilation to obtain a $\QPIP_0$ protocol $\PiNaive$ for the above $\QPIP_1$ protocol.
+First, we will use Mahadev's compilation to obtain an ``intermediate" $\QPIP_0$ protocol $\PiNaive$ for the above $\QPIP_1$ protocol.
 As mentioned previously, this protocol $\PiNaive$ will have some trouble outputting the desired sample in the testing round.
@@
 Precisely, we will run again a cut-and-choose protocol $\PiSampZ$ on top of many copies of $\PiNaive$, which are executed in parallel to preserve the number of rounds.
+
+\KM{more precise about the issue and construction; issue: testing round has no output; construction: parallel repetition and use one hadamard + k - 1 testing; partition lemma: know testing answer and not know; know answer $\Rightarrow$ write output distribution; difference to BQP: $2^{-m}$ vs $1/m$; sampling no amplification can't combine samples  }
 
@@
 \XW{Note that there is also an important difference between us and~\cite{arXiv:ChiaChungYam19}, the difference between decision and sampling problems.}
-\Cref{sec:qpip0_all}.
-
 % A naive attempt is to directly apply Mahadev's protocol on the aforementioned $\QPIP_1$ protocol.
@@
 
-It is worthwhile mentioning that we came to notice some online discussion\footnote{\url{https://www.scottaaronson.com/blog/?p=3697}, e.g., comment \#25, \#26, \#42, \#48.
+It is worthwhile to mention that we came to notice some online discussion\footnote{\url{https://www.scottaaronson.com/blog/?p=3697}, e.g., comment \#25, \#26, \#42, \#48.
 } on the possibility of a CVQC protocol for $\SampBQP$ after we developed our own result.

### 2020-11-07 introduction.tex
Sync submitted version

@@
 In particular, we demonstrate the feasibility of the classical verification of quantum sampling by
-constructing a constant-round CVQC protocol for $\SampBQP$, the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}, based on the quantum LWE (QLWE) assumption that the learning-with-error problem is hard for BQP machines.
+constructing a constant-round CVQC protocol for $\SampBQP$, based on the quantum LWE (QLWE) assumption that the learning-with-error problem is hard for BQP machines. 
+$\SampBQP$ is the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}.
+%the class of sampling problem that are approximately solvable by polynomial-time quantum algorithms defined by Aaronson~\cite{aaronson_2013}.
+%the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}
 Formally, $\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine with an inverse polynomial accuracy.
-\KM{add ref to Sec 3}  %Namely, $A(x,1^{1/\eps})$ outputs a sample that is $\eps$-close to the distribution $D_x$ in statistical distance.
+See Section~\ref{sec:samp_definition} for further discussions on $\SampBQP$ and the precise definition of CVQC for $\SampBQP$.
+%Namely, $A(x,1^{1/\eps})$ outputs a sample that is $\eps$-close to the distribution $D_x$ in statistical distance.
 %, where given an input $x \in \zo^n$, the goal  
-Precisely,
-\begin{theorem}[informal]
+%Precisely,
+\begin{theorem}[informal] \label{thm:qpip0-informal}
 Assuming the QLWE assumption, there exists a four-message CVQC protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
@@
 
-Precisely, to leverage Mahadev's construction, one needs to start with a $\QPIP_1$ protocol with very small completeness and soundness errors, which will then be compiled into a $\QPIP_0$ protocol with a small completeness error, but a close-to-$3/4$ soundness error under the QLWE assumption.
+Precisely, to leverage Mahadev's construction, one needs to start with a $\QPIP_1$ protocol with very small completeness and soundness errors, which will then be compiled into a $\QPIP_0$ protocol with a small completeness error, but a close-to-$1/2$ soundness error under the QLWE assumption\footnote{Mahadev only proved soundness error close-to-$3/4$ for her protocol, but it was later proved~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19} that her protocol actually achieves close-to-$1/2$ soundness error}.
 This large soundness error is due to the current structure of Mahadev's protocol that consists of the \emph{testing} round and the \emph{Hadamard} round, each of which happens with a half chance. 
@@
 (Of course, when the prover cheats, the verifier will reject and no further output is required in that case.)
-We provide a formal definition for CVQC protocols for $\SampBQP$ in Section~\ref{sec:samp_definition} to capture the above intuition. \KM{say the distribution should be correct conditioned on accepts}
+Intuitively, the soundness requires that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interact with a malicious prover.
+We formalize this by a strong simulation-based definition (Section~\ref{sec:samp_definition}), where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.
 
-\KM{terminology: testing protocol, test round etc.}
+To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems.
+We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the simulation-based soundness property we defined.
+Proving soundness of these constructions for delegating $\SampBQP$ is an interesting open question.
 
-This fundamentally new requirement of any CVQC protocol for $\SampBQP$ exposes one drawback of Mahadev's protocol: 
+%We provide a formal definition for CVQC protocols for $\SampBQP$ in Section~\ref{sec:samp_definition} to capture the above intuition.
+\KM{say the distribution should be correct conditioned on accepts}
+
+%\KM{terminology: testing protocol, test round etc.}
+
+The requirement that the verifier needs to output a sample when accepts exposes one drawback of Mahadev's protocol: 
 while it is possible, as we will show, to generate desired output samples in the Hadamard round, 
@@
 
-\vspace{2mm} \noindent  \emph{$\diamond$ Compile $\QPIP_1$ into $\QPIP_0$ after parallel repetition}: we are ready to address the aforementioned drawback of Mahadev's protocol.
-First, we will use Mahadev's compilation to obtain an ``intermediate" $\QPIP_0$ protocol $\PiNaive$ for the above $\QPIP_1$ protocol.
-As mentioned previously, this protocol $\PiNaive$ will have some trouble outputting the desired sample in the testing round.
-To address this issue, we will separate the testing and the outputting in different runs of the protocol, similarly to what we have done in the design of $\QPIP_1$ protocol. 
-Precisely, we will run again a cut-and-choose protocol $\PiSampZ$ on top of many copies of $\PiNaive$, which are executed in parallel to preserve the number of rounds.
+\vspace{2mm} \noindent  \emph{$\diamond$ Compile $\QPIP_1$ into $\QPIP_0$ after parallel repetition}: We now discuss how to use Mahadev's measurement protocol to compile the above $\QPIP_1$ protocol for $\SampBQP$ to a $\QPIP_0$ protocol.
+As mentioned, a major issue we need to address is that when the verifier $V$ choose to run a testing round, $V$ does not learn a output sample when it accepts.
+%(which happens with probability $1/2$),
 
-\KM{more precise about the issue and construction; issue: testing round has no output; construction: parallel repetition and use one hadamard + k - 1 testing; partition lemma: know testing answer and not know; know answer $\Rightarrow$ write output distribution; difference to BQP: $2^{-m}$ vs $1/m$; sampling no amplification can't combine samples  }
+Specifically, let $\PiNaive$ be an ``intermediate'' $\QPIP_0$ protocol obtained by applying Mahadev's compilation to the above $\QPIP_1$ protocol.
+Namely, when $V$ chooses to run the Hadamard round, it learns a measurement outcome from the measurement protocol and runs the $\QPIP_1$ verifier to generate a decision and a output sample when accepts.
+However, when  $V$ chooses to run the testing round, it only decides to accept or reject without being able to output a sample.
 
-However, since $\PiNaive$ only has computational soundness, we need to design a parallel repetition of $\PiNaive$ in the computational setting, which also prevents the use of quantum de Finetti theorem that only holds in the information-theoretical setting.
-Fortunately,  some recent results on computational parallel repetitions of Mahadev's original protocol for $\BQP$~\cite{arXiv:AlaChiHun19, arXiv:ChiaChungYam19} provide a technical starting point for us.
-Precisely, these results open the box of the analysis of Mahadev's protocol and analyze the computational soundness under a parallel repetition.
+Similar to the above cut-and-choose idea for $\QPIP_1$, a natural idea to fix the issue is to execute multiple copies of $\PiNaive$ in parallel\footnote{It is also reasonable to consider sequential repetition, but we consider parallel repetition for its advantage of preserving the round complexity.}, and to choose a random copy to run the Hadamard round to generate an output sample and use all the remaining copies to run the testing round.
+The verifier accepts only when all executions accept and outputs the sample from the Hadamard round.
+Let us call this protocol $\PiSampZ$.
 
-\XW{Precisely, comment on the partition lemma~\cite{arXiv:ChiaChungYam19}, and how it is used ...}
+Clearly from the construction, the verifier now can output a sample when it decides to accept, and outputs a correct sample when interacting with an honest prover (completeness).
+The challenge is to show that $\PiSampZ$ is computationally sound.
+Note that now we are in the computational setting, we cannot use quantum de Finetti theorem as above since it only holds in the information-theoretical setting.
+Furthermore, parallel repetition for computationally sound protocols are typically difficult to analyze, and known to not always work for protocols with four or more messages~\cite{BIN97,PW12}.
+
+Fortunately, parallel repetition of Mahadev's protocol for $\BQP$ has been analyzed before in ~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19} with interestingly different proofs.
+Both works showed that $m$-fold parallel repetition reduces the soundness error to $2^{-m}$ by relying on special properties of Mahadev's protocol.
+
+It is worth comparing parallel repetition of Mahadev's protocol for $\BQP$ and $\SampBQP$.
+For $\BQP$, the verifier simply chooses to run the Hadamard and testing rounds independently for each repetition.
+In contrast, our $\PiSampZ$ runs the Hadamard round in one repetition and run the testing round in the rest.
+The reason is that in $\SampBQP$, we do not have a good way to combine two samples learned from two Hadamard-round executions.
+The difference also reflects in the parameters, where the soundness error decreases exponentially for $\BQP$, but as we see below (and also in the above $\QPIP_1$ protocols), for $\SampBQP$, $m$-fold repetition only decreases the error to $\poly(1/m)$.
+The difference stems from the fact that there is no generic error reduction method for the sampling problem, whereas one can just conduct a majority vote for decision problems.
+
+We rely on the technique developed in~\cite{arXiv:ChiaChungYam19} to analyze the soundness of $\PiSampZ$.
+Intuitively, Mahadev's protocol has the property that if a malicious prover $P^*$ knows the answer to pass the testing round, then it must be ``committed'' to a state $\rho$ in the sense that the verifier $V$ learns the $X/Z$ measurement outcome of $\rho$ in the Hadamard round (in a computational sense), and thus, the soundness of the underlying $\QPIP_1$ protocol ensures that $V$ learns a correct sample when it accepts.
+In short, when $P^*$ knows the testing round answer,  $P^*$ cannot ``cheat'' in the Hadamard round.
+The work of~\cite{arXiv:ChiaChungYam19} formalizes this intuition by a \emph{partition lemma}, which roughly says that there is an efficient projection that partitions the prover's internal quantum space into a ``known-answer'' subspace $S_1$ that $P^*$ knows the answer to the testing round, and a ``not-known-answer'' subspace $S_0$ that $P^*$ does not know the answer to the testing round.
+For (efficient) prover's states $\ket{\psi} \in S_1$, the verifier $V$ can produce a sound output in the Hadamard round.
+For (efficient) prover's states $\ket{\psi} \in S_0$, the verifier $V$ rejects in the testing round with high probability.
+The work of \cite{arXiv:ChiaChungYam19} used this partition lemma iteratively to each instance of the repetition to show that for a no instance $x$ for any (efficient) prover's state $\ket{\psi}$, the probability that $V$ accepts is at most roughly $2^{-m}$.
+
+We apply the partition lemma iteratively to the prover's state  similarly as~\cite{arXiv:ChiaChungYam19}, but with significant differences to show the soundness of $\PiSampZ$ for $\SampBQP$.
+In particular, extra cares are required to reason about the computational indistinguishability of the verifier's output sample from the correct distribution $D_x$.
+To gain some intuition, let us apply the partition lemma to the prover's state $\ket{\psi}$ with respect to the first coordinate, which decompose $\ket{\psi} = \ket{\psi_0} + \ket{\psi_1}$ with $\ket{\psi_0} \in S_0$ and  $\ket{\psi_1} \in S_1$, respectively.
+Intuitively, the $\ket{\psi_0}$ component will be rejected whenever the first coordinate runs the testing round, but the verifier may be ``cheated'' to accepted incorrectly when the first coordinate runs the Hadamard round, which happens with probability $1/m$ and is where the error come from.
+For the $\ket{\psi_1}$ component, $V$ will produce a sound output if it runs the Hadamard round at the first coordinate.
+For the case that $V$ chooses to run the testing round at the first coordinate, we can analyze it by further applying the partition lemma to $\ket{\psi_1}$ with respect to the second coordinate to analyze.
+%
+While the analysis outlined above grosses over many technical details, our actual analysis follows this outline closely. 
+(Section~\ref{sec:qpip0_all}.)
+
+%To address this issue, we will separate the testing and the outputting in different runs of the protocol, similarly to what we have done in the design of $\QPIP_1$ protocol. 
+%Precisely, we will run again a cut-and-choose protocol $\PiSampZ$ on top of many copies of $\PiNaive$, which are executed in parallel to preserve the number of rounds.
+
+%\KM{more precise about the issue and construction; issue: testing round has no output; construction: parallel repetition and use one hadamard + k - 1 testing; partition lemma: know testing answer and not know; know answer $\Rightarrow$ write output distribution; difference to BQP: $2^{-m}$ vs $1/m$; sampling no amplification can't combine samples  }
+
+%However, since $\PiNaive$ only has computational soundness, we need to design a parallel repetition of $\PiNaive$ in the computational setting, which also prevents the use of quantum de Finetti theorem that only holds in the information-theoretical setting.
+%Fortunately,  some recent results on computational parallel repetitions of Mahadev's original protocol for $\BQP$~\cite{arXiv:AlaChiHun19, arXiv:ChiaChungYam19} provide a technical starting point for us.
+%Precisely, these results open the box of the analysis of Mahadev's protocol and analyze the computational soundness under a parallel repetition.
+
+%\XW{Precisely, comment on the partition lemma~\cite{arXiv:ChiaChungYam19}, and how it is used ...}
 % We end up developing a weaker version of  parallel repetition of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}. 
-\XW{Note that there is also an important difference between us and~\cite{arXiv:ChiaChungYam19}, the difference between decision and sampling problems.}
+%\XW{Note that there is also an important difference between us and~\cite{arXiv:ChiaChungYam19}, the difference between decision and sampling problems.}
 % A naive attempt is to directly apply Mahadev's protocol on the aforementioned $\QPIP_1$ protocol.
@@
 These comments suggested a possible reduction of $\SampBQP$ to the local Hamiltonian problem following a similar high-level idea as our solution, however, with no detail and a seemingly different technical route.
-However, they failed to identify other important gaps in the protocol design that we have addressed.
+Furthermore, the issue that the verifier does not generate output in the testing round seems to be overlooked and not discussed there.
+%However, they failed to identify other important gaps in the protocol design that we have addressed.
 

### 2020-11-07 paper.tex
Add some comments on qpip0 proof
Sync
Sync submitted version

@@
 %*************************************page layout****************************
+\iffalse
 \setlength{\textheight}{9in}
@@
 
+\fi
 %\pagecolor{black}
@@
 \newcounter{protocol}
-\newcommand{\linefill}{\rule{\linewidth}{0.8pt}}
+%\newcommand{\linefill}{\rule{\linewidth}{0.8pt}}
 
@@
 \author[2]{Yi Lee\thanks{\href{mailto:ethanlee515@gmail.com}{ethanlee515@gmail.com}. This work was done in part while the author was affiliated to National Taiwan University.}}
-\author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.utexas.edu}{linhh@cs.utexas.edu}. Supported by Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.}}
+\author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}.
+Part of this work was done while supported by Scott Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.}}
 \author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837(CAREER).}}
 \affil[1, 2]{Institute of Information Science, Academia Sinica, Taiwan}
-\affil[3]{Department of Computer Science, University of Texas at Austin, USA}
+\affil[3]{Department of Computer Science, National Tsing Hua University, Taiwan}
 \affil[4]{
@@
 \item  Motivated by the sampling nature of many quantum applications (e.g., quantum algorithms for machine learning and quantum supremacy tasks), we initiate the study of  CVQC for \emph{quantum sampling problems} (denoted by $\SampBQP$).
-Precisely, given an input $x\in \zo^n$ and a quantum circuit $C$, the goal of a classical client is to learn a sample of output $z \leftarrow C(x)$ over $\zo^m$ with the correct distribution up to a small error from an untrusted prover.
+More precisely, in a CVQC protocol for a $\SampBQP$ problem, the prover and the verifier are given an input $x\in \zo^n$ and a quantum circuit $C$, and the goal of the classical client is to learn a sample from the output $z \leftarrow C(x)$ up to a small error, from its interation with an untrusted prover.
 We demonstrate its feasibility by constructing a four-message CVQC protocol for $\SampBQP$ based on the quantum \emph{Learning With Error} assumption.
+
 \item
@@
 It is a highly desirable property that has been intensively studied for the delegation of quantum computation.
-Somewhat surprisingly, we provide a simple yet powerful \emph{generic} compiler that transforms any CVQC protocol to a blind one while preserving completeness and soundness errors.  
+Somewhat surprisingly, we provide a simple yet powerful \emph{generic} compiler that transforms any CVQC protocol to a blind one while preserving the completeness and soundness errors.  
 \end{itemize}
-Applying our compiler to (a parallel repetition of) Mahadev's protocol for $\BQP$ and our CVQC protocol for $\SampBQP$ yields the first \emph{constant-round} blind CVQC protocol for $\BQP$ and $\SampBQP$ respectively, with negligible completeness and soundness errors.
+Applying our compiler to (a parallel repetition of) Mahadev's CVQC protocol for $\BQP$ and our CVQC protocol for $\SampBQP$ yields the first \emph{constant-round} blind CVQC protocol for $\BQP$ and $\SampBQP$ respectively, with negligible completeness and soundness errors.
 
@@
 
+\input{model}
+
 \input{hamiltonian}

### 2020-11-07 preliminaries.tex
Sync submitted version

@@
 We write $x\xleftarrow{\$}X$ when $x$ is sampled uniformly at random from the set $X$.
+We use $\BQP$ as an adjective to mean polynomial-time, e.g. a $\BQP$ machine.
 
@@
     We drop the $\eps$ parameter when it is negligible.
-    We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized states as appropriate.
-    We also extend it to distributions by treating them as mixed states.
+    We extend computational indistinguishability to subnormalized states by interpreting a subnormalized state $\rho$ as sending out $\bot$ with probability $1-\tr(\rho)$ and having the distinguisher $\mathsf{D}$ output $\bot$ whenever he receives $\bot$.
+    We also extend it to classical random variable by treating them as mixed states.
 \end{definition}
+
+%   We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output\hannote{?} subnormalized states as appropriate.
 

### 2020-11-07 qpip0.tex
Sync submitted version

@@
 
-\begin{protocol}{Intermediate $\QPIP_0$ protocol $\PiNaive$ for a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$}
+\begin{protocol}{Intermediate $\QPIP_0$ protocol $\PiNaive$ for the $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$}
 	\label{proto:qpip0_naive}
@@
 Intuitively,  the proof of \Cref{lem:naive-qpip0-binding}  combines the binding property of \Cref{proto:qpip0_naive} (\Cref{lem:urmila-binding}) and $\PiSamp$'s soundness (\Cref{QPIP1thm}).
-There is a technical issue that \Cref{proto:qpip0_naive} allows the prover to abort while \Cref{proto:urmila4} doesn't.
+There is a technical issue that \Cref{proto:qpip0_naive} allows the prover to abort while \Cref{proto:urmila4} does not.
 This issue is solved by constructing another $\BQP$ prover $\Pstar$ for every cheating prover $\PNaiveStar$.
@@
 Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}),
-	we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\varepsilon}, x)$  is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.
+	we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\epsilon}, x)$  is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.
 
@@
 
-\begin{protocol}{$\QPIP_0$ protocol $\PiSampZ$ for $\SampBQP$}
+\begin{protocol}{$\QPIP_0$ protocol $\PiSampZ$ for the $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$}
 	\label{proto:QPIP0samp}
@@
 		\item The prover prepares $\rho^{\otimes m}$; each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$.
-		\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, as in \stepref{measure1} of $\PiMeasure$.
+		\item \label{step:urmila-in-qpip0-1} The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, as in \stepref{measure1} of $\PiMeasure$.
 			It sends $\vec{pk}$ to the prover.
-		\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ as in \stepref{measure2} of $\PiMeasure$.
+		\item \label{step:urmila-in-qpip0-2}The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ as in \stepref{measure2} of $\PiMeasure$.
 			It sends $\vec{y}$ to the verifier.
-		\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
+		\item \label{step:urmila-in-qpip0-3}The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
 			For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
 			It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
-		\item The prover generates $\vec{a}$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
+		\item \label{step:urmila-in-qpip0-4}The prover generates $\vec{a}$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
 		\item The verifier computes the outcome for each round as in \stepref{naive-output} of $\PiNaive$.
@@
 Property~\ref{property:partition-err} corresponds to Property~1.
-Property~\ref{property:partition-testing} corresponds to Property~4, with $2^{m-1}$ changes to $m-1$ because we only have $m$ possible choices of $\{c\}$.
+Property~\ref{property:partition-testing} corresponds to Property~4, with $2^{m-1}$ changes to $m-1$ because we only have $m$ possible choices of $\vec{c}$.
 Property~\ref{property:partition-binding} corresponds to Property~5.
@@
 	Let $\lambda$ be the security parameter, and $\gamma_0 \in[0,1]$ and $T\in \mathbb{N}$ be parameters that will be related to the randomly-chosen threshold $\gamma$.
-	Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message.
-\hannote{$H_{XZ}$} Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$, which corresponds to doing Hadamard round on the $i$-th copy and testing round on all others.
+	Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$\footnote{A $m$-fold parallel repetition of $\PiMeasure$ is running step~\ref{step:urmila-in-qpip0-1}~\ref{step:urmila-in-qpip0-2}~\ref{step:urmila-in-qpip0-3}~\ref{step:urmila-in-qpip0-4} of \Cref{proto:QPIP0samp} with verifier input $\vec{h}$ and prover input $\rho^\otimes n$, followed by an output step where the verifier rejects if any of the $m-1$ testing round copies is rejected, otherwise outputs the result of the Hadamard round copy.}, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message.
+Let $H_{\regX,\regZ}$ be the Hilberspace of the prover's internal calculation.
+	Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$, which corresponds to doing Hadamard round on the $i$-th copy and testing round on all others.
 
-	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two $\poly(1/\gamma_0,T,\lambda)$-time quantum circuit with post selection\footnote{A quantum circuit with post selection is composed of unitary gates followed by a post selection on some measurement outcome on ancilla qubits, so it produces a subnormalized state, where the amplitude square of the output state is the probability of post selection.} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized) $\poly(\lambda)$-qubits quantum state $\ket{\psi}_{\regX,\regZ}$,  properties \ref{property:partition-err}~\ref{property:partition-testing}~\ref{property:partition-binding}~\ref{property-partition-norm-sum}, to be described later, are satisfied.
+	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two $\poly(1/\gamma_0,T,\lambda)$-time quantum circuit with post selection\footnote{A quantum circuit with post selection is composed of unitary gates followed by a post selection on some measurement outcome on ancilla qubits, so it produces a subnormalized state, where the amplitude square of the output state is the probability of post selection.} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}\in  H_{\regX,\regZ}$,  properties \ref{property:partition-err}~\ref{property:partition-testing}~\ref{property:partition-binding}~\ref{property-partition-norm-sum}, to be described later, are satisfied.
 Before we describe the properties, we introduce the following notations:
@@
 Note that in property~\ref{property:partition-binding}, we are using $\ext_i$ instead of $U$ because we are doing some amplitude amplification to boost the success probability.
-\hannote{some discussion on why we want $G$ to be efficient.}
 
@@
 By Property~\ref{property:partition-testing} of \Cref{lem:partition2},
-it clearly follows that \Ethan{This ok?}
+it clearly follows that
 \begin{rmk}
@@
 \begin{proof}
-	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for $\PiSampZ$, consider the following composite strategy, $\Picomp$, as a prover for $\PiNaive$.
+	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for $\PiSampZ$, consider the following composite strategy, $\Picomp{i}$, as a prover for $\PiNaive$.
 Note that a prover only interacts with the verifier in Step~\ref{step:urmila-in-naive} of $\PiNaive$ where $\PiMeasure$ is run, so we describe a prover's action in terms of the four rounds of communication in $\PiMeasure$.
 
-	$\Picomp$ tries to run $U_0$ by taking the verifier's input as the input to the $i$-th copy of $\PiMeasure$ in $\PiSampZ$ and simulating other $m-1$ copies by himself.
+	$\Picomp{i}$ tries to run $U_0$ by taking the verifier's input as the input to the $i$-th copy of $\PiMeasure$ in $\PiSampZ$ and simulating other $m-1$ copies by himself.
 The prover then picks a uniformly random $\gamma$ and  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$.
@@
 	Since the prover's strategy is also efficient, by ~\Cref{lem:naive-qpip0-binding},
-	$z_{composite,i}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$. \hannote{fix notation difference..}
+	$z_{composite,i}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$. 
 \end{proof}
@@
 
-\begin{theorem}\label{thm:qpip0} \hannote{to the form of thm 4.4. call to thm 1.1?}
-	Under the QLWE assumption, $\PiSampZ$ is a computationally sound protocol for $\SampBQP$.
+\begin{theorem}\label{thm:qpip0} 
+	Under the QLWE assumption, $\PiSampZ$ is a protocol for the $\SampBQP$ problem $(D_x)_{x\in\set{0,1}^*}$  with negligible completeness error and is statistically sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}}
+
 \end{theorem}
 \begin{proof}
+	Completeness is trivial. In the following we prove the soundness.
+
 	By Property~\ref{property-partition-norm-sum} of Lemma~\ref{lem:partition2}, we have
@@
 	Set $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$.
-Combining \Cref{thm:zgood-zideal} and \Cref{eq:z-z-good} by triangle inequality, we have $\tr\abs{z-z_{ideal}}=O(\varepsilon)$.
-\hannote{computational?}
-	Since $z$ is close to some ideal output distribution $z_{ideal}$, it must be close to the ideal output distribution with its own accept probability too.
+Combining \Cref{thm:zgood-zideal} and \Cref{eq:z-z-good} by triangle inequality, we have $z$ is $O(\epsilon)$-computationally indistinguishable to $z_{ideal}$.
+Therefore, $(d,z)$  $O(\epsilon)$-computationally indistinguishable to $(d,z_{ideal})$.
+
+%	\hannote{?}Since $z$ is close to some ideal output distribution $z_{ideal}$, it must be close to the ideal output distribution with its own accept probability too.
 \end{proof}
+
+~\Cref{thm:qpip0-informal} follows as a corollary.
+
+%$\tr\abs{z-z_{ideal}}=O(\epsilon)$

### 2020-11-14 hamiltonian.tex
Sync

@@
-\section{$\SampBQP$ Delegation Protocol for $\QPIP_1$ Client}
+\section{Construction of the $\QPIP_1$ Protocol for $\SampBQP$}
 \label{sec:sampbqp}
 
-%\XW{merge Section 3 and 4; also easy the discussion;}
-
-\subsection{Construction of the X-Z Local Hamiltonian for $\SampBQP$} \label{sec:LHXZ}
+\subsection{Reducing $\SampBQP$ to the X-Z Local Hamiltonian} \label{sec:LHXZ}
 As we mentioned in this introduction, we will employ the circuit \emph{history} state in the original construction of the Local Hamiltonian problem~\cite{kitaev2002classical} to encode the circuit information for $\SampBQP$.
@@
 
-%\XW{TOADD: some organization}
-%\XW{highlight the different requirement from the normal Local Hamiltonian reduction; and highlight a bit about the solution idea}
-
-% In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian instance.
-% The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
-% Protocols to delegate $\BQP$ computations such as \cite{FOCS:Mahadev18a} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
-% We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.
-% Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
-% \Ethan{This source was given to us by Yu-Ching; I haven't read it. Also I probably should cite more sources here.}
-
 Recall the definition of the history state which serves as a transcript of the circuit evolution~\cite{kitaev2002classical}:
@@
     \begin{equation}
-        \histpsi{C(x)} \equiv \frac{1}{\sqrt{T}}\sum_{t=0}^TU_t\ldots U_1\ket{x,0}\otimes\ket{\hat{t}},
+        \histpsi{C(x)} \equiv \frac{1}{\sqrt{T}}\sum_{t=0}^{T-1}U_t\ldots U_1\ket{x,0}\otimes\ket{\hat{t}},
     \end{equation}
     where the first register of $n$-qubit refers to the input, the second of $m$-qubit refers to the work space ($\mathrm{poly}(n)$, w.l.o.g, $\leq T$ size) which is initialized to $\ket{0}$, and the last refers to the clock space which encodes the time information.
-Note that $\hat{t}$ could be some representation of $t$=0,..., $T$.
+Note that $\hat{t}$ could be some representation of $t$=0,..., $T-1$.
 \end{dfn}
-
-% \begin{rmk}
-%     \label{idpadding}
-%     One can first pad $C$ with identity gates at the end, doubling its number of gates and obtaining another circuit $C'$.
-%     Then by measuring the time register of $\ket{\psi_{C'(x)}}$ one obtains with probability $\frac{1}{2}$ the state $C(x)$.
-% \end{rmk}
-
-% \XW{define $k$-local XZ Hamiltonian}
-% We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$ as below; note that this spans a subspace of $5$-local Hamiltonians.
 
@@
  The Toffoli gate maps bits $(a,b,c)$ to $(a,b, c \oplus (a \text{ and } b))$, which can be decomposed as $\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$ where $\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$.
- %Here we restate the result from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
- %Because of this result, we can assume without loss of generality that our quantum circuits consist of only Toffoli and Hadamard gates.
-% Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
-% \begin{Fact}
-%         $H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
-% \end{Fact}
-% \begin{prf}
-%     $$H=\frac{1}{\sqrt{2}}(X+Z)$$
-%     $$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
-%     $$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
-% \end{prf}
 
@@
 \end{equation}
-% Then, we ensure that the initial condition is set up correctly.
-%     $$H_{in}=\sum_{i=1}^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
-%     The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
 
@@
 Note that $\ket{\widehat{t}}\bra{\widehat{t-1}}=\ket{110}\bra{100}_{(t-1,t,t+1)}$ and similarly for $\ket{\widehat{t-1}}\bra{\widehat{t}}$.
-%     Then, we ensure that the gates are applied correctly.
-%     $$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
-%     $$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
-%     +I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-%     -U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
-%     -U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-%     We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least non zero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
-%One can similarly rewrite $\Hprop$ in terms of elements from $\LHXZ{}$.
 Note that $U_t^\dagger=U_t$, since our gates are either Hadamard or Toffoli. It is observed in~\cite{PhysRevA.78.012352} that
@@
 \end{eqnarray}
-%     We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$.
-%     Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
-%     
-% $$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
-%     Extra care must be taken for boundary cases.
-%     $$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
-%     $$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
 Combining with the fact that each $U_t$ can be written as a linear combination of terms from $\LHXZ{}$, we conclude that $\Hclock$, $\Hin$, $\Hprop$ are 6-local X-Z Hamiltonian.
@@
 We will use the following simple reformulation instead.
-%We will instead use the following formulation, which can be obtained by relabeling variables from above.
 
@@
 
-%\XW{need to check the following calculation and modify the theorem statement respectively.}
-%We will apply \Cref{lem:projection} twice to obtain $\Jclock$ and $\Jprop$ respectively.
-
-\Ethan{See if proj. lemma can be applied just once instead of twice. Possibly add prop and clock together first. (lower priority relatively?)
-
-Also a problem with attitude. Don't make it too obvious that there's trivial improvements to be made}
-
 Consider $\Hin + \Jclock\Hclock$ first. According to \cref{lem:projection}, by choosing
@@
 where we use the fact $\ground{\Hprop\big|_{S\cap \Kprop^\bot}}\geq \ground{\Hprop\big|_{\Kprop^\bot}}=\Omega(T^{-2})$~\cite{kitaev2002classical}, we have  
-% $$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
-% =\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
-% $$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
-% \lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
 \[
@@
 \end{proof}
-%     To properly combine the three Hamiltonians defined and analyze it using the projection lemma (\cref{thm:projection}), we consider the kernels of the Hamiltonians we defined.
-%     $$K_{clock}=\ker H_{clock}$$
-%     $$K_{in}=\ker H_{in}$$
-%     $$K_{prop}=\ker H_{prop}$$
 
-%     Clearly,
-%     $$K_{clock}=\set{\sum_{t=1}^T \ket{\phi_t}\otimes\ket{\hat{t}}:\ket{\phi_t}\in\cB^{\otimes n}}$$
-%     Let $\ket\phi\in K_{clock}\cap K_{prop}$.
-%     Consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$.
-%     As $\ket\phi\in K_{prop}$, we can then do induction using $\widetilde{t}$ as base case to get the relations between the $\ket{\phi_t}$s and conclude that $\ket\phi$ must have the form:
-%     $$\ket\phi=\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}$$
-%     $$\Rightarrow K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
-%     As a direct result, we get
-%     $$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$$
-% \begin{align*}
-%     S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
-%     &=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{C(x)}|y}=0}
-% \end{align*}
-% $$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
-% So we set $H_{C(x)}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
+\noindent \textbf{Remark.} We believe that the specific parameter dependence above can be tightened by a more careful analysis.
+However, as our focus is on the feasibility, we keep the above slightly loose analysis which might be more intuitive.
 
@@
 
-At a high-level, the design of such protocol should consist of at least two components: (1) the first component should test whether the message is indeed a valid history state; (2) the second component should simulate the last step of a $\SampBQP$ computation by measuring the final state in the computational basis.
+At a high-level, the design of such protocols should consist of at least two components: (1) the first component should test whether the message is indeed a valid history state; (2) the second component should simulate the last step of any $\SampBQP$ computation by measuring the final state in the computational basis.
 
@@
 \[
-   \norm{\proj{\psi^{\mathrm{hist}}_{C(x)}}- \proj{\phi}}_{tr} = \sqrt{1- |\braket{\psi^{\mathrm{hist}}_{C(x)}|\phi}|^2}
+   \norm{\proj{\psi^{\mathrm{hist}}_{C(x)}}- \proj{\phi}}_{\tr} = \sqrt{1- |\braket{\psi^{\mathrm{hist}}_{C(x)}|\phi}|^2}
    \leq \frac{2}{\sqrt{3}}\sqrt{\epsilon}.
@@
 \[
-    \norm{\proj{\psi^{\mathrm{hist}}_{C(x)}}- \rho}_{tr} \leq \sum_i p_i    \norm{\proj{\psi^{\mathrm{hist}}_{C(x)}}- \proj{\phi_i}}_{tr} \leq \sum_i p_i \frac{2}{\sqrt{3}} \sqrt{\epsilon} =\frac{2}{\sqrt{3}}\sqrt{\epsilon}.
+    \norm{\proj{\psi^{\mathrm{hist}}_{C(x)}}- \rho}_{\tr} \leq \sum_i p_i    \norm{\proj{\psi^{\mathrm{hist}}_{C(x)}}- \proj{\phi_i}}_{\tr} \leq \sum_i p_i \frac{2}{\sqrt{3}} \sqrt{\epsilon} =\frac{2}{\sqrt{3}}\sqrt{\epsilon}.
 \]
-% $$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
-%     We can then see
-%     $$\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$$
-%     which can be generalized for mixed states since we have for all $\ket\psi$ that
-%     $$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \ket\psi)=\sum_i p_i F(\ket{\phi_i}, \ket\psi).$$
-%     As a result, we have
-%     $$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\eps}{T^5}$$
-%     which implies our claim.
 \end{prf}
 
-% \begin{algorithm}
-%     \caption{Check for ground state $\cVGS$}
-%     \label{AlgGroundStateCheck}
-%         Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
-%         Let $\ket\phi$ be the potential ground state to check.
-%         \begin{itemize}
-%             \item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
-%             \item Set $p_S = \frac{|d_S|}{D}$
-%             \item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
-%             \item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
-%             \item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept by outputting $1$. Otherwise, reject by outputting $0$.
-%         \end{itemize}
-% \end{algorithm}
-% \begin{prf}
-%     Here we follow \cite{PhysRevA.93.022326}.
-%     \begin{align*}
-%         \frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
-%         &=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
-%         &=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
-%         &=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
-%     \end{align*}
-
-%     Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
-%     $$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
-%     \begin{align*}
-%         \Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
-%         &=\frac{1}{2}-\frac{O(1)}{T^5}\braket{\phi|H|\phi}
-%     \end{align*}
-% \end{prf}
-
 To serve the second purpose, one needs to combine the test and the output on multiple copies of the history states, where we construct the following cut-and-choose protocol.  
-% At a high level, it is a cut-and-choose protocol.
-% The server constructs multiple copies of the ground state as certificates,
-% then the client randomly chooses a copy to output and checks the rest.
-% Unfortunately our approach incurs inverse polynomial soundness errors.
-% There are two main challenges to this cut-and-choose approach.
-% First, the client needs to reliably extract the circuit output from its corresponding ground state.
-% We accomplish this by padding the circuit with identity gates at the end.
-% By doing so, the clock register collapses to after the last non-identity gate with high probability.
 The challenge comes from the fact that a cheating prover might send something rather than copies of the history state.
@@
 However, in the context of $\SampBQP$, one needs to certify the ground energy (known to be zero in this case) and to output a good copy.
-%%% not sure about this high-level argument.
 While the statistical test as before can be used to certify the ground energy,
@@
 To serve our purpose, we adopt the following version of quantum de Finetti's theorem from~\cite{Brandao2017} where the error depends nicely  on the number of qubits, rather than the dimension of quantum systems.
-% one always needs to send the best certificate state (i.e., the perfect history state) in order to pass the local Hamiltonian ground energy test.
-% The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
-% so common techniques such as Chernoff bounds can't be applied as-is.
-%This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...
-% In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem
-% to approximate our measurement results with that of some unentangled copies,
-% within inverse polynomial errors.
-% De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
-% There are many formulations; we use the one from \cite{Brandão2017} because we need to avoid exponential dependence on the number of qubits in each subsystem.
+
 \begin{thm}[\cite{Brandao2017}]
@@
 
-%\XW{comment on saturating the error bound?}
-
 \input{qpip}
-
-%%%%
-%%%% Keep the old version here for the record.
-%%%%
-
-% \section{The History XZ Local Hamiltonian}
-% \label{sec:Hamiltonian}
-
-% In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian instance.
-
-% The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
-% Protocols to delegate $\BQP$ computations such as \cite{FOCS:Mahadev18a} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
-% We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.
-% Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
-% \Ethan{This source was given to us by Yu-Ching; I haven't read it. Also I probably should cite more sources here.}
-
-% We begin by recalling the form that local Hamiltonian certificates:
-
-% \begin{dfn}
-%     \label{dfn:groundstate}    
-%     Let $C=U_T\ldots U_1$ be a quantum circuit consisting of $T$ gates, and let $x\in\set{0,1}^n$. Then we denote
-%     $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$$
-%     We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
-% \end{dfn}
-
-% \begin{rmk}
-%     \label{idpadding}
-%     One can first pad $C$ with identity gates at the end, doubling its number of gates and obtaining another circuit $C'$.
-%     Then by measuring the time register of $\ket{\psi_{C'(x)}}$ one obtains with probability $\frac{1}{2}$ the state $C(x)$.
-% \end{rmk}
-
-% We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$ as below; note that this spans a subspace of $5$-local Hamiltonians.
-% \begin{dfn}
-%     $$\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \abs{\set{i: U_i\ne I}}\leq 5}$$
-% \end{dfn}
-
-% Now we state the main theorems that we'll work towards in this section.
-% The first one is the reduction from $\SampBQP$ to a local Hamiltonian instance, with some additional properties that will be convenient for us:
-% \begin{thm}
-%     \label{thm:LHReduction}
-%     Let $C$ be a circuit of size $T$. For any input string $x$, there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
-%     \begin{itemize}
-%         \item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
-%         \item $H_{C(x)}$ has $\ket{\psi_{C(x)}}$ as the unique ground state with eigenvalue $0$.
-%         \item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
-%         \item Its descriptions can be constructed by a $\BPP$ machine in polynomial time.
-%     \end{itemize}
-% \end{thm}
-
-% The second one is a way to verify ground states of local Hamiltonians, again with some extra properties:
-% \begin{thm}
-%     \label{ThmXZCheck}
-%     Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists a $\BQP$ algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
-(In particular, it accepts the $\ket{\psi_{C(x)}}$ with probability $\fot$.) Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
-% \end{thm}
-
-% \subsection{Circuits of Toffoli and Hadamard gates}
-
-% Here we restate the result from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
-% Because of this result, we can assume without loss of generality that our quantum circuits consist of only Toffoli and Hadamard gates.
-% Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
-% \begin{thm}
-%     $H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
-% \end{thm}
-% \begin{prf}
-%     $$H=\frac{1}{\sqrt{2}}(X+Z)$$
-%     $$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
-%     $$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
-% \end{prf}
-
-% Now we present the proof that $\set{H, \Lambda^2(X)}$ is indeed a universal gate set from \cite{quant-ph/0301040}: \Ethan{This definitely belongs in the appendix instead...}
-% \begin{thm}
-%     Let $C$ be a circuit that:
-%     \begin{itemize}
-%         \item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
-%         \item uses $n$ qubits
-%     \end{itemize}
-%     Then a classical machine given $C$ can compute a circuit $C'$ that:
-%     \begin{itemize}
-%         \item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
-%         \item uses $n+1$ qubits
-%         \item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
-%         The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
-%     \end{itemize}
-% \end{thm}
-% \begin{prf}
-%     We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
-%     $$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
-%         $$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-
-%     Now consider the transform on quantum states
-%     $$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
-%     where $\Re$ and $\Im$ denote real and imaginary parts respectively.
-
-%     This transform commutes with Hadamard gates on the respective qubit.
-On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turns it into a combination of Hadamard and Toffoli gates.
-Mathematically,
-%     $$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
-%     $$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
-
-%     We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
-%     \begin{itemize}
-%         \item $C'$ uses only Hadamard and Toffoli gates.
-%         \item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size.
-Exchanging $\mathcal{F}$ with a controlled phase gate turns it into $4$ gates.
-So the final result is at most $4T$ gates.
-%         \item When $x$ is classical, $\mathcal{F}(x)=x||0$.
-So $F\circ C(x)=C'(x||0)$.
-It is simple \hannote{need a little more work?}to verify that $\mathcal{F}$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
-%     \end{itemize}
-% \end{prf}
-
-% \subsection{Reducing quantum circuit to local Hamiltonian}
-
-% In this subsection, we prove \cref{thm:LHReduction} by showing how to reduce a $\SampBQP$ circuit to a local-$XZ$-Hamiltonian.
-
-%     The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.
-
-%     Let $x_i$ denote the $i$-th bit of $x$, and let $n$ be the number of qubits in $C$.
-
-%     We need to ensure the excited states of $H_{C(x)}$ have high eigenvalues.
-
-%     First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
-%     $$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
-%     As a sum of projections, clearly $H_{clock}\geq 0$. We shall also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
-%     $$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
-%     This can be checked by fixing the first and last qubit, then doing induction on the number of switches.
-
-%     Then, we ensure that the initial condition is set up correctly.
-%     $$H_{in}=\sum_{i=1}^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
-%     The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
-%     $$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$
-
-%     Then, we ensure that the gates are applied correctly.
-%     $$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
-%     $$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
-%     +I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
-%     -U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
-%     -U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
-
-%     We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least non zero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.
-
-%     We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since our gates are either Hadamard or Toffoli.
-%     Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
-%     $$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
-%     Extra care must be taken for boundary cases.
-%     $$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
-%     $$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
-
-%     To properly combine the three Hamiltonians defined and analyze it using the projection lemma (\cref{thm:projection}), we consider the kernels of the Hamiltonians we defined.
-%     $$K_{clock}=\ker H_{clock}$$
-%     $$K_{in}=\ker H_{in}$$
-%     $$K_{prop}=\ker H_{prop}$$
-
-%     Clearly,
-%     $$K_{clock}=\set{\sum_{t=1}^T \ket{\phi_t}\otimes\ket{\hat{t}}:\ket{\phi_t}\in\cB^{\otimes n}}$$
-%     Let $\ket\phi\in K_{clock}\cap K_{prop}$.
-%     Consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$.
-%     As $\ket\phi\in K_{prop}$, we can then do induction using $\widetilde{t}$ as base case to get the relations between the $\ket{\phi_t}$s and conclude that $\ket\phi$ must have the form:
-%     $$\ket\phi=\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}$$
-%     $$\Rightarrow K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
-
-%     As a direct result, we get
-%     $$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$$
-
-% We now consider the space outside the desired state.
-% $$S=(\spn\set{\ket{\psi_{C(x)}}})^\bot$$
-% $$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
-% To combine the Hamiltonians, we apply the projection lemma twice.
-% $$\exists J_{clock}
-% =\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
-% =O(n)=O(T)$$
-% $$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
-% \lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
-% $$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
-% =\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
-% $$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
-% \lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
-% \begin{align*}
-%     S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
-%     &=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{C(x)}|y}=0}
-% \end{align*}
-% $$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
-% So we set $H_{C(x)}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
-
-% \subsection{Checking the ground state of the local Hamiltonian}
-
-% In this subsection, we prove \cref{ThmXZCheck}.
-% That is, we present and analyze an algorithm that checks whether a given state is the ground state of some fixed $H_{C(x)}$, following~\cite{PhysRevA.93.022326}.
-
-% \begin{algorithm}
-%     \caption{Check for ground state}
-%     \label{AlgGroundStateCheck}
-%         Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
-%         Let $\ket\phi$ be the potential ground state to check.
-%         \begin{itemize}
-%             \item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
-%             \item Set $p_S = \frac{|d_S|}{D}$
-%             \item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
-%             \item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
-%             \item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept. Otherwise, reject.
-%         \end{itemize}
-% \end{algorithm}
-
-% \begin{thm}
-%     Let $H$ have $O(\poly(T))$ nonzero components whose coefficients at most $O(\poly(T))$.
-%     Then \cref{AlgGroundStateCheck} accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
-% \end{thm}
-% \begin{prf}
-%     Here we follow \cite{PhysRevA.93.022326}.
-%     \begin{align*}
-%         \frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
-%         &=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
-%         &=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
-%         &=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
-%     \end{align*}
-
-%     Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
-%     $$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
-%     \begin{align*}
-%         \Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
-%         &=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
-%     \end{align*}
-% \end{prf}
-
-% The second one is a way to verify ground states of local Hamiltonians, again with some extra properties:
-% \begin{thm}
-%     \label{ThmXZCheck}
-%     Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists a $\BQP$ algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
-(In particular, it accepts the $\ket{\psi_{C(x)}}$ with probability $\fot$.) Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
-% \end{thm}
-
-%\subsection{Circuits of Toffoli and Hadamard gates}
-
-% Old notation: Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$.
-I.e.
-$\Lambda^2_{1, 2}(X_3)$ would be a Toffoli gate.
-% \Ethan{TODO: replace with something that looks better and doesn't conflict with the use of $\Lambda$ as measurement.}
-
-% Now we present the proof that $\set{H, \Lambda^2(X)}$ is indeed a universal gate set from \cite{quant-ph/0301040}: \Ethan{This definitely belongs in the appendix instead...}
-% \begin{thm}
-%     Let $C$ be a circuit that:
-%     \begin{itemize}
-%         \item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
-%         \item uses $n$ qubits
-%     \end{itemize}
-%     Then a classical machine given $C$ can compute a circuit $C'$ that:
-%     \begin{itemize}
-%         \item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
-%         \item uses $n+1$ qubits
-%         \item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
-%         The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
-%     \end{itemize}
-% \end{thm}
-% \begin{prf}
-%     We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
-%     $$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
-%         $$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
-
-%     Now consider the transform on quantum states
-%     $$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
-%     where $\Re$ and $\Im$ denote real and imaginary parts respectively.
-
-%     This transform commutes with Hadamard gates on the respective qubit.
-On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turns it into a combination of Hadamard and Toffoli gates.
-Mathematically,
-%     $$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
-%     $$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
-
-%     We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
-%     \begin{itemize}
-%         \item $C'$ uses only Hadamard and Toffoli gates.
-%         \item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size.
-Exchanging $\mathcal{F}$ with a controlled phase gate turns it into $4$ gates.
-So the final result is at most $4T$ gates.
-%         \item When $x$ is classical, $\mathcal{F}(x)=x||0$.
-So $F\circ C(x)=C'(x||0)$.
-It is simple \hannote{need a little more work?}to verify that $\mathcal{F}$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
-%     \end{itemize}
-% \end{prf}

### 2020-11-14 introduction.tex
Sync

@@
 \section{Introduction}
-% \XW{
-% \begin{itemize}
-%     \item add a lot of references.
-%     \item comparison with the most relevant results:
-%       \begin{itemize}
-%           \item Sampling, the only paper; how about classical sampling?
-%           \item the following for BQP  
-%           \item blind and verifiable ~\cite{GV19}; we  constant round; technique-wise very different.
-%           \item there is a table in~\cite{Grilo19}. Safe to say ~\cite{GV19} only existing blind protocol in the computational setting?
-%           \item all previous either quantum clients, or at least 2 provers.
-%           \item the following for blindness
-%           \item Mahadev in her thesis~\cite{mahadev_2018} discussed a bit about the relation between verifiability and blindness.
-She hoped to get verifiability out of blindness by designing some non-malleable QFHE but failed.
-%           \item what's the high-level message we can say here?
-Use QFHE in a different way?
-It is correct that not much work in the classical setting either.
-Maybe existing classical work employs the principle but with different implementation.
-%           \item old approach, first get blindness  (measurement-based, self-testing), and then try to make it verifiable; our approach, first have a verifiable protocol, and upgrade by a QFHE.
-%           \item directly QFHE (blindness) won't give verifiability. some thoughts from Mahadev.
-%           \item
-%       \end{itemize}
-% \end{itemize}
-% }
+Can quantum computation, with potential computational advantages that are intractable for classical computers,
+be efficiently verified by classical means?
+This seeming paradox has been one of the central problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}.
+From a philosophical point of view, this question is also known to have a fascinating connection to the \emph{falsifiability} of quantum mechanics in the high complexity regime~\cite{survey:AV12}.
 
-Can quantum computation, with potential computational advantages that are intractable for classical computers,
-be efficiently verified by classical clients?
-This seeming paradox has been one of the central problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}.
-From a philosophical point of view, this question is also known to have a fascinating connection to the \emph{falsifiability} of quantum mechanics in the potential high complexity regime~\cite{survey:AV12}.
-
-A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier/client (a $\BPP$ machine) to verify the output of an
+A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks about the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
 efficient quantum prover (a $\BQP$ machine).
@@
 considers a $\BPP$ verifier interacting with at least two entangled, non-communicating quantum provers.
-In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
+In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of Classical Verification of Quantum Computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
 The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.,~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
 On the other side, there are known complexity-theoretic limitations on the feasibility of blind CVQC in the information-theoretical setting (e.g.~\cite{aaronson_et_al:LIPIcs:2019:10582}).
-%\XW{here some no-go for information theoretical result.}
-%We refer curious readers to a slightly outdated  survey~\cite{survey:GKK19} for details.
 
@@
 As such, classical literature of delegation of computation primarily focuses on delegation of decision problems.
-%delegation of classical sampling problem is not explicitly studied in literature.
 
@@
 Thus, it seems that the delegation of $\SampBQP$ needs to take a different technical route.
-%delegation of $\SampBQP$ may require a totally different construction from delegation of $\BQP$. 
-%
 One natural starting point is Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} for $\BQP$. 
@@
 As we shall see, such difficulties do not hold for the decision problem, which demonstrates an important difference between CVQC protocols for the decision and the sampling problems.
-
-% \XW{Adjust the flow; highlight the key questions}
-% \Ethan{This paragraph is new and has to be checked}
-% Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however, 
-%it is still unclear how to construct a CVQC protocol for $\SampBQP$.
-% In the context of delegating \emph{classical} sampling problems,
-% there is a simple reduction to that of decision problems.
-% Namely, the verifier fixes a seed for pseudorandomness and send it to the prover,
-% then the sampling outcome can be computed deterministically bit-by-bit using this pseudorandomness.
 
@@
 
-In fact, most existing blind and verifiable protocols for delegation of quantum computation require a notable amount of effort in achieving each property respectively. 
+In fact, most existing blind and/or verifiable protocols for delegation of quantum computation require a notable amount of effort in achieving each property respectively. 
 The only successful CVQC protocol~\cite{FOCS:GheVid19} of achieving both so far applies Mahadev's technique~\cite{FOCS:Mahadev18a} to the measurement-based quantum computation, whereas the analysis is still very specific to the construction.
-%\Ethan{And it has inverse-poly errors, which makes it not constant-round to achieve negligible errors for $\BQP$, right?}
 Could there be a \emph{generic} way to achieve blindness and verifiability for CVQC protocols at the same time, say by leveraging the state-of-the-art CVQC~\cite{FOCS:Mahadev18a} and QFHE~\cite{mahadev_qfhe} protocols?
-
-%\XW{Mention QFHE as a natural attempt, and highlight the problem}
 
@@
 $\SampBQP$ is the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}.
-%the class of sampling problem that are approximately solvable by polynomial-time quantum algorithms defined by Aaronson~\cite{aaronson_2013}.
-%the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}
 Formally, $\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine with an inverse polynomial accuracy.
 See Section~\ref{sec:samp_definition} for further discussions on $\SampBQP$ and the precise definition of CVQC for $\SampBQP$.
-%Namely, $A(x,1^{1/\eps})$ outputs a sample that is $\eps$-close to the distribution $D_x$ in statistical distance.
-%, where given an input $x \in \zo^n$, the goal  
-%Precisely,
 \begin{theorem}[informal] \label{thm:qpip0-informal}
@@
 
-%\XW{theorem statement for the second contribution and pointer}
-
-As a simple corollary of combining both results above, we achieve a constant-round blind CVQC protocol for $\SampBQP$. %with negligible completeness error and statistical soundness.  
+As a simple corollary of combining both results above, we achieve a constant-round blind CVQC protocol for $\SampBQP$. 
 \begin{theorem}[informal]
@@
 
-%\XW{here for both $\BQP$ and $\SampBQP$}
-%\XW{check the para/terminology here; consider adding a theorem statement,or a pointer to the later section}
-
 To the authors' best knowledge, we are the first to study CVQC protocols for $\SampBQP$ and establish a generic compiler to upgrade CVQC protocols with blindness.
@@
 
-% \XW{any more to say about parameters, techniques?}
-% \XW{anything we want to say about composability?}
-% \Ethan{Last time we checked, Vidick might have better composability since he's got some kind of ideal box and simulator-based proof}
-
-% Related work
-% \begin{itemize}
-%     \item Comparison with related works here?
-% \end{itemize}
-%       \begin{itemize}
-%           \item Sampling, the only paper; how about classical sampling?
-%           \item the following for BQP  
-%           \item blind and verifiable ~\cite{GV19}; we  constant round; technique-wise very different.
-%           \item there is a table in~\cite{Grilo19}. Safe to say ~\cite{GV19} only existing blind protocol in the computational setting?
-%           \item all previous either quantum clients, or at least 2 provers.
-%           \item the following for blindness
-%           \item Mahadev in her thesis~\cite{mahadev_2018} discussed a bit about the relation between verifiability and blindness.
-She hoped to get verifiability out of blindness by designing some non-malleable QFHE but failed.
-%           \item what's the high-level message we can say here?
-Use QFHE in a different way?
-It is correct that not much work in the classical setting either.
-Maybe existing classical work employs the principle but with different implementation.
-%           \item old approach, first get blindness  (measurement-based, self-testing), and then try to make it verifiable; our approach, first have a verifiable protocol, and upgrade by a QFHE.
-%           \item directly QFHE (blindness) won't give verifiability. some thoughts from Mahadev.
-%
-%           technical comparison with the past parallel % repetition.
-%           \item
-
 \vspace{2mm} \noindent \textbf{Techniques.} Let us revisit Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} first for some technical background. 
-Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of quantum register in the possession of the classical verifier, or equivalently, the limited quantum computation power of the verifier.
+Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of (local) quantum memory in the possession of the classical verifier, or equivalently, the limited quantum power of the verifier\footnote{Intuitively, the size of local quantum memory limits the size of qubits that a general (entangled) quantum operation can be operated on at the same time.
+However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the pover and discard some local qubits in the case of overflow.}.
+A precise definition is given in Section~\ref{sec:qpip_def}. 
 It is known that $\BQP$ can be efficiently verified by a classical verifier that can perform a single qubit $X$ or $Z$ measurement~\cite{PhysRevA.93.022326, mf16}, by reducing any $\BQP$ problem to a local Hamiltonian problem where each term consists of  $X$ and $Z$ only.
@@
 
-Precisely, to leverage Mahadev's construction, one needs to start with a $\QPIP_1$ protocol with very small completeness and soundness errors, which will then be compiled into a $\QPIP_0$ protocol with a small completeness error, but a close-to-$1/2$ soundness error under the QLWE assumption\footnote{Mahadev only proved soundness error close-to-$3/4$ for her protocol, but it was later proved~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19} that her protocol actually achieves close-to-$1/2$ soundness error}.
+Precisely, to leverage Mahadev's construction, one needs to start with a $\QPIP_1$ protocol with very small completeness and soundness errors, which will then be compiled into a $\QPIP_0$ protocol with a small completeness error, but a close-to-$1/2$ soundness error under the QLWE assumption\footnote{Mahadev only proved soundness error close-to-$3/4$ for her protocol, but it was later proved~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19} that her protocol actually achieves close-to-$1/2$ soundness error.}.
 This large soundness error is due to the current structure of Mahadev's protocol that consists of the \emph{testing} round and the \emph{Hadamard} round, each of which happens with a half chance. 
@@
 
-The first thing when dealing with $\SampBQP$ is to properly define the requirement of CVQC protocols for $\SampBQP$. 
+The first and important step in the case of $\SampBQP$ is to identify an appropriate definition of corresponding CVQC protocols.
 In contrast to the single bit $\mathrm{Accept/Reject}$ information for the decision $\BQP$, any $\SampBQP$ problem needs to always output a sample of the desired distribution.
@@
 Intuitively, the soundness requires that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interact with a malicious prover.
-We formalize this by a strong simulation-based definition (Section~\ref{sec:samp_definition}), where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.
+We formalize this by a strong \emph{simulation-based} definition (Section~\ref{sec:samp_definition}), where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in the either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.
 
@@
 Proving soundness of these constructions for delegating $\SampBQP$ is an interesting open question.
-
-%We provide a formal definition for CVQC protocols for $\SampBQP$ in Section~\ref{sec:samp_definition} to capture the above intuition.
-\KM{say the distribution should be correct conditioned on accepts}
-
-%\KM{terminology: testing protocol, test round etc.}
 
@@
 
-% \XW{revisit Mahadev's approach: (a) QPIP0 to QPIP1; QPIP0 requires very good completeness and soundness.
-(can say for examples the use of X-Z Hamiltonian, what's the detailed bound transformation?);  the output protocol has poor soundness errors;   (this is still for the decision problem; inefficiency); cite the recent parallel repetition - motivation and result; efficiency- round ?
-so sequential-repetition is not preferred.}
-
-% \XW{the difference between decision and sampling problems. precision definitions are given in where?}
-
-% \Ethan{Next part needs discussion on context Ie. protocol or local computation}
-% Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
-% since it is unclear how to apply the usual trick of running many copies of the protocol then applying the Chernoff bound. \XW{too vague to be useful?}
-
 \vspace{2mm} \noindent \textbf{Construction of a $\QPIP_0$ protocol for $\SampBQP$}. 
-% \XW{stop here} We will follow the same road map above (i.e., from $\QPIP_1$ to $\QPIP_0$) for $\SampBQP$
-% However, since there is no existing $\QPIP_1$ protocol for $\SampBQP$, we make original contributions to both steps as follows:
-% \XW{use a different labeling in order to highlight contributions}
 Following the aforementioned outline, our construction can be divided into three key technical steps.
-
-% \XW{(1) a basic step for encoding of the history state in the local Hamiltonian problem, and can be tested (so spectral gap). 
-% (2) testing the spectral gap and make sure outputing. QPIP0 protocol. (need and how); here also  
-% (3) QPIP1 compilation, and also main the efficiency (round?). But this parallel repetition just makes more complicated because of the sampling requirement! 
-% }
 
@@
 In other words, a certification of the energy $H'_{\mathrm{circuit}}$ could lead to a certification of the history state, which in turn helps us generate the desired sample. 
-We construct such $H'_{\mathrm{circuit}}$ from $H_{\mathrm{circuit}}$ by using the \emph{perturbation} technique (e.g.,~\cite{kempe_kitaev_regev_2006}) with further restriction to X/Z terms.
+We construct such $H'_{\mathrm{circuit}}$ from $H_{\mathrm{circuit}}$ by using the \emph{perturbation} technique (e.g.,~\cite{kempe_kitaev_regev_2006}) with a further restriction to X/Z terms.
 (\Cref{sec:LHXZ}.)
-
-%\XW{what's good about Mahadev's protocol; one can measure a lot; but of course, one needs to also test it; for the QPIP1 protocol; to get the QPIP0, the story won't be different.}
-% \XW{anything useful here: Our protocol leverages the Hamiltonian model and the computational X-Z measurement from~\cite{FOCS:Mahadev18a}.
-% However, a significant amount of new techniques have been developed to deal with the difference between $\SampBQP$ and $\BQP$, which will be highlighted in the technical contribution section. }
 
@@
 Intuitively, we face a similar dilemma as we described above about Mahadev's protocol: we can either employ the certification protocol on $H'_{\mathrm{circuit}}$ to do the test, or to measure the history state to generate the desired outcome, but not both at the same time since the testing protocol would disturb the measurement outcome.
-% Specifically, we will certify the energy of $H'_{\mathrm{circuit}}$ to guarantee the underlying state is close to the valid history state.
-% However, this procedure could be vastly different from outputting a sample by measuring the final state of $\SampBQP$ circuits.
 To resolve that, we design a \emph{cut-and-choose} protocol on multiple copies of the history state so as to separate the testing and the outputting parts on separate copies of history states.
@@
 \vspace{2mm} \noindent  \emph{$\diamond$ Compile $\QPIP_1$ into $\QPIP_0$ after parallel repetition}: We now discuss how to use Mahadev's measurement protocol to compile the above $\QPIP_1$ protocol for $\SampBQP$ to a $\QPIP_0$ protocol.
-As mentioned, a major issue we need to address is that when the verifier $V$ choose to run a testing round, $V$ does not learn a output sample when it accepts.
+As mentioned, a major issue we need to address in Mahadev's original construction is that when the verifier $V$ chooses to run a testing round, $V$ does not learn an output sample when it accepts.
 %(which happens with probability $1/2$),
@@
 Specifically, let $\PiNaive$ be an ``intermediate'' $\QPIP_0$ protocol obtained by applying Mahadev's compilation to the above $\QPIP_1$ protocol.
-Namely, when $V$ chooses to run the Hadamard round, it learns a measurement outcome from the measurement protocol and runs the $\QPIP_1$ verifier to generate a decision and a output sample when accepts.
-However, when  $V$ chooses to run the testing round, it only decides to accept or reject without being able to output a sample.
+Namely, when $V$ chooses to run the Hadamard round, it could learn a measurement outcome from the measurement protocol and be able to run the $\QPIP_1$ verifier to generate a decision and an output sample when accepts.
+However, when  $V$ chooses to run the testing round, it only decides to accept/reject without being able to output a sample.
 
@@
 
-Clearly from the construction, the verifier now can output a sample when it decides to accept, and outputs a correct sample when interacting with an honest prover (completeness).
+Clearly from the construction, the verifier now can output a sample when it decides to accept, and output a correct sample when interacting with an honest prover (completeness).
 The challenge is to show that $\PiSampZ$ is computationally sound.
@@
 Fortunately, parallel repetition of Mahadev's protocol for $\BQP$ has been analyzed before in ~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19} with interestingly different proofs.
-Both works showed that $m$-fold parallel repetition reduces the soundness error to $2^{-m}$ by relying on special properties of Mahadev's protocol.
+Both works showed that $m$-fold parallel repetition reduces the soundness error to $2^{-m}$ for $\BQP$ by relying on special properties of Mahadev's protocol.
 
@@
 In contrast, our $\PiSampZ$ runs the Hadamard round in one repetition and run the testing round in the rest.
-The reason is that in $\SampBQP$, we do not have a good way to combine two samples learned from two Hadamard-round executions.
-The difference also reflects in the parameters, where the soundness error decreases exponentially for $\BQP$, but as we see below (and also in the above $\QPIP_1$ protocols), for $\SampBQP$, $m$-fold repetition only decreases the error to $\poly(1/m)$.
-The difference stems from the fact that there is no generic error reduction method for the sampling problem, whereas one can just conduct a majority vote for decision problems.
+The reason is that in $\SampBQP$, as well as generically in sampling problems, there is no known approach to combine two samples learned from two Hadamard-round executions to generate one sample with much better parameters, i.e., no generic error reduction method for the sampling problem.
+In contrast, the error reduction for decision problems can be done with the majority vote. 
+As a result, while the soundness error decreases exponentially for $\BQP$, as we see below (and also in the above $\QPIP_1$ protocols), for $\SampBQP$, $m$-fold repetition only decreases the error to $\poly(1/m)$.
 
 We rely on the technique developed in~\cite{arXiv:ChiaChungYam19} to analyze the soundness of $\PiSampZ$.
-Intuitively, Mahadev's protocol has the property that if a malicious prover $P^*$ knows the answer to pass the testing round, then it must be ``committed'' to a state $\rho$ in the sense that the verifier $V$ learns the $X/Z$ measurement outcome of $\rho$ in the Hadamard round (in a computational sense), and thus, the soundness of the underlying $\QPIP_1$ protocol ensures that $V$ learns a correct sample when it accepts.
+Intuitively, Mahadev's protocol has the property that if a malicious prover $P^*$ knows the answer to pass the testing round, then it must be ``committed'' to a state $\rho$ in the sense that the verifier $V$ learns the $X/Z$ measurement outcome of $\rho$ in the Hadamard round (in a computational sense).
+Thus, the soundness of the underlying $\QPIP_1$ protocol ensures that $V$ learns a correct sample when it accepts.
 In short, when $P^*$ knows the testing round answer,  $P^*$ cannot ``cheat'' in the Hadamard round.
-The work of~\cite{arXiv:ChiaChungYam19} formalizes this intuition by a \emph{partition lemma}, which roughly says that there is an efficient projection that partitions the prover's internal quantum space into a ``known-answer'' subspace $S_1$ that $P^*$ knows the answer to the testing round, and a ``not-known-answer'' subspace $S_0$ that $P^*$ does not know the answer to the testing round.
+The work of~\cite{arXiv:ChiaChungYam19} formalizes this intuition by a \emph{partition lemma}, which roughly says that there is an efficient projection that partitions the prover's internal quantum space into a ``known-answer'' subspace $S_1$ where $P^*$ knows the answer to the testing round, and a ``not-known-answer'' subspace $S_0$ where $P^*$ does not know the answer to the testing round.
 For (efficient) prover's states $\ket{\psi} \in S_1$, the verifier $V$ can produce a sound output in the Hadamard round.
@@
 For the $\ket{\psi_1}$ component, $V$ will produce a sound output if it runs the Hadamard round at the first coordinate.
-For the case that $V$ chooses to run the testing round at the first coordinate, we can analyze it by further applying the partition lemma to $\ket{\psi_1}$ with respect to the second coordinate to analyze.
+For the case that $V$ chooses to run the testing round at the first coordinate, we can analyze it by further applying the partition lemma to $\ket{\psi_1}$ with respect to the second coordinate, and repeat the analysis, and so on.
 %
-While the analysis outlined above grosses over many technical details, our actual analysis follows this outline closely. 
-(Section~\ref{sec:qpip0_all}.)
+The intuitive analysis outlined above grosses over many technical details, and we substantiate this outline with full details in  
+Section~\ref{sec:qpip0_all}.
 
-%To address this issue, we will separate the testing and the outputting in different runs of the protocol, similarly to what we have done in the design of $\QPIP_1$ protocol. 
-%Precisely, we will run again a cut-and-choose protocol $\PiSampZ$ on top of many copies of $\PiNaive$, which are executed in parallel to preserve the number of rounds.
-
-%\KM{more precise about the issue and construction; issue: testing round has no output; construction: parallel repetition and use one hadamard + k - 1 testing; partition lemma: know testing answer and not know; know answer $\Rightarrow$ write output distribution; difference to BQP: $2^{-m}$ vs $1/m$; sampling no amplification can't combine samples  }
-
-%However, since $\PiNaive$ only has computational soundness, we need to design a parallel repetition of $\PiNaive$ in the computational setting, which also prevents the use of quantum de Finetti theorem that only holds in the information-theoretical setting.
-%Fortunately,  some recent results on computational parallel repetitions of Mahadev's original protocol for $\BQP$~\cite{arXiv:AlaChiHun19, arXiv:ChiaChungYam19} provide a technical starting point for us.
-%Precisely, these results open the box of the analysis of Mahadev's protocol and analyze the computational soundness under a parallel repetition.
-
-%\XW{Precisely, comment on the partition lemma~\cite{arXiv:ChiaChungYam19}, and how it is used ...}
-% We end up developing a weaker version of  parallel repetition of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}. 
-%\XW{Note that there is also an important difference between us and~\cite{arXiv:ChiaChungYam19}, the difference between decision and sampling problems.}
-% A naive attempt is to directly apply Mahadev's protocol on the aforementioned $\QPIP_1$ protocol.
-% Unfortunately, the plain version of Mahadev's protocol does not yield favorable parameters by itself.
-% However, we cannot directly make use of these parallel repetition results due to the subtle difference between protocols for $\BQP$ and $\SampBQP$.
-% One of the major difficulties here is still to deal with both the test part and the output part in $\SampBQP$ protocols.
-% However, because we are now in the computational setting, there is no longer any available quantum de Finetti theorem that is usually derived in the information-theoretic setting.
-% Due to the nature of parallel repetition in the computational setting, our analysis is much less modular and significantly involved for this part.  
-% More intuitions and detailed analysis are given in
-
-It is worthwhile to mention that we came to notice some online discussion\footnote{\url{https://www.scottaaronson.com/blog/?p=3697}, e.g., comment \#25, \#26, \#42, \#48.
+It is worthwhile mentioning that we came to notice some online discussion\footnote{\url{https://www.scottaaronson.com/blog/?p=3697}, e.g., comment \#25, \#26, \#42, \#48.
 } on the possibility of a CVQC protocol for $\SampBQP$ after we developed our own result.
 These comments suggested a possible reduction of $\SampBQP$ to the local Hamiltonian problem following a similar high-level idea as our solution, however, with no detail and a seemingly different technical route.
-Furthermore, the issue that the verifier does not generate output in the testing round seems to be overlooked and not discussed there.
-%However, they failed to identify other important gaps in the protocol design that we have addressed.
+More importantly, the issue that the verifier does not generate outputs in the testing round seems to be overlooked and not discussed there.
 
@@
 One subtlety with this approach is due to the fact that the verifier is classical while the QFHE cipher text could depend on both quantum and classical data.
-In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm needs to be classical when the underlying message is classical, which is fortunately satisfied by~\cite{mahadev_qfhe}.
+In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm need to be classical when the underlying message is classical, which is fortunately satisfied by~\cite{mahadev_qfhe}.
 
@@
 
-\vspace{2mm} \noindent \textbf{Open Questions.} Our main focus is on the feasibility of the desired functionality and properties, which nevertheless leaves a big room for the improvement of efficiency.
-Some of our parameter dependence inherits from previous works (e.g.~\cite{FOCS:Mahadev18a}), whereas some is due to our own construction. 
+\vspace{2mm} \noindent \textbf{Open Questions.} Our main focus is on the feasibility of the desired functionality and properties, which nevertheless leaves room for the improvement of parameter dependence.
+Some of our parameter dependence inherits from previous works (e.g.~\cite{FOCS:Mahadev18a}), whereas some is due to our own construction where we didn't mean to identify the best possible parameter dependence.
 It will be extremely interesting to improve the parameter dependence with potentially new techniques.
 
-\Ethan{TODO add organization of paper}
-
-% \begin{itemize}
-%     \item Open questions, and also explain for some associated high-cost. specifically
-%     \item T dependence. In general, improve the efficiency.  
-%     \item negligible soundness error.  compare with classical? what's the state-of-the art.
-% \end{itemize}
-
-% \Ethan{This section is currently all rough draft. We'll probably rewrite almost all of it.}
-
-% \Ethan{application: verifiable private constant round delegation}
+\vspace{2mm} \noindent \textbf{Organization.} We provide preliminaries on technical background in Section~\ref{sec:prelim}. 
+Our simulation-based definition of CVQC for $\SampBQP$ is discussed in Section~\ref{sec:samp_definition}. 
+Our main technical contributions are explained in details in Section~\ref{sec:sampbqp} (a construction of $\QPIP_1$ protocol for $\SampBQP$), 
+Section~\ref{sec:qpip0_all} (the construction of $\QPIP_0$ protocol for $\SampBQP$ based on the above $\QPIP_1$ protocol), 
+and Section~\ref{sec:BlindBQP2} (a generic compiler to upgrade $\QPIP_0$ protocols with blindness).

### 2020-11-14 model.tex
Sync

@@
-\section{Delegation of Quantum Sampling Problems}
+\section{Delegation of Quantum Sampling Problems} \label{sec:samp_definition}
 
-In this section, we formally introduce the task of delegation for quantum sampling problem.
+In this section, we formally introduce the task of delegation for quantum sampling problems.
 We start by recalling the complexity class $\SampBQP$ defined by Aaronson~\cite{aaronson_2013, aaronson_arkhipov_2011}, which captures the class of sampling problems that
@@
     $\SampBQP$ is the class of sampling problems $\left(D_x\right)_{x\in\set{0, 1}^*}$ that can be (approximately) sampled by polynomial-size uniform quantum circuits.
-Namely, there exists a Turing machine $M$ such that for every $n \in \bbN$ and $\eps \in (0,1)$, $M(1^n, 1^{1/\eps})$ outputs a quantum circuit $C$ in $\poly(n, 1/\eps)$ time such that for every $x \in \zo^n$, the output of $C(x)$ (measured in standard basis) is $\eps$-close to $D_x$.
+Namely, there exists a Turing machine $M$ such that for every $n \in \bbN$ and $\eps \in (0,1)$, $M(1^n, 1^{1/\eps})$ outputs a quantum circuit $C$ in $\poly(n, 1/\eps)$ time such that for every $x \in \zo^n$, the output of $C(x)$ (measured in standard basis) is $\eps$-close to $D_x$ in the total variation distance.
 \end{definition}
@@
 For example, conceivable physical realizations of quantum computer may consist of inherent noise.
-We refer the readers to~\cite{aaronson_2013, aaronson_arkhipov_2011} for the discussion therein on why this better captures the sampling problem solvable by efficient quantum computers.
+We refer the readers to~\cite{aaronson_2013, aaronson_arkhipov_2011} for the discussion therein on why this better captures the sampling problem solvable by realistic quantum computers.
 
-We next define what does it mean for a $\QPIP_\tau$ protocol to solve a $\SampBQP$ problem $\left(D_x\right)_{x\in\set{0, 1}^*}$.
-Since sampling problem comes with an accuracy parameter $\eps$, we let the prover $P$ and the verifier $V$ receive the input $x$ and $1^\eps$ as common inputs. 
+We next define what it means for a $\QPIP_\tau$ protocol to solve a $\SampBQP$ problem $\left(D_x\right)_{x\in\set{0, 1}^*}$.
+Since sampling problems come with an accuracy parameter $\eps$, we let the prover $P$ and the verifier $V$ receive the input $x$ and $1^{1/\eps}$ as common inputs. 
 Completeness is straightforward to define, which requires that when the prover $P$ is honest, the verifier $V$ should accept with high probability and output a sample $z$ distributed close to $D_x$ on input $x$.
 Defining soundness is more subtle.
-Intuitively, it requires that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interact with a malicious prover.
+Intuitively, it requires that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interacting with a malicious prover.
 We formalize this by a strong simulation-based definition, where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.
-Note that since the protocol receives the accuracy parameter $1^{\eps}$ as input to specify the allowed error, we do not need to introduce an additional soundness error parameter in the definition.
-
-\KM{should be better to add more discussion.}
-
-%\KM{point to discuss: (i) syntax: accuracy parameter $\eps$ (ii) simulation-based soundness (iii) no soundness error (iv) computational soundness
-}
-
-%Intuitively, completeness requires that when the prover $P$ is honest, the verifier $V$ should accept with high probability and output a sample $z$ close to $D_x$ on input $x$.
-Soundness should require that
+Since the protocol receives the accuracy parameter $1^{1/\eps}$ as input to specify the allowed error, we do not need to introduce an additional soundness error parameter in the definition.
 
@@
             and $x\in\zo^{\poly(\lambda)}$,
-            Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
+            let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
         \item (Statistical soundness): For all cheating prover $P^*$,
@@
             \end{itemize}
-            It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\eps$.
+            It holds that $\norm{(d,z)-(d,z_{ideal})}_{\mathrm{TV}}\leq\eps$.
 		\item (Computational soundness):
-			\Ethan{tried to write in terms of indistinguishability}
         For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
             sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$,
-            define $d, z, z_{ideal}$ by the same experiment as above.
+            let us define $d, z, z_{ideal}$ by the same experiment as above.
             It holds that $(d, z)$ is $\eps$-computationally indistinguishable to $(d, z_{ideal})$ over $\lambda$.
@@
 To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems.
-We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the soundness property we defined.
-Proving soundness of these constructions for delegating $\SampBQP$ is an interesting open question.
-
-\iffalse
-\subsection{Sampling Problems}
-
-We define $\SampBQP$ based on \cite{aaronson_2013, aaronson_arkhipov_2011}.
-\Ethan{Tried to explain better}
-This complexity class is meant to model feasible quantum computations.
-As quantum states live in a continuous Hilbert space,
-it is likely that any realization of quantum computing would suffer from natural noise and inaccuracies.
-An argument from the physical implementation perspective that this error should be on an inverse polynomial scale is given in \cite{aaronson_arkhipov_2011}.
-As a result, $\SampBQP$ is correspondingly stated to allow inverse-polynomial errors.
-
-\begin{definition} [sampling problem]
-    \label{dfn:sampling-problem}
-    A \emph{sampling problem} is a collection of probability distributions $(D_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{m(n)}$ for some fixed polynomial $m$.
-\end{definition}
-
-\begin{definition} [$\SampBQP$]
-    $\SampBQP$ is the class of sampling problems $\left(D_x\right)_{x\in\set{0, 1}^*}$ that can be (approximately) sampled by polynomial-size uniform quantum circuits.
-Namely, there exists a Turing machine $M$ such that for every $n \in \bbN$ and $\eps \in (0,1)$, $M(1^n, 1^{1/\eps})$ outputs a quantum circuit $C$ in $\poly(n, 1/\eps)$ time such that for every $x \in \zo^n$, the output of $C(x)$ (measured in standard basis) is $\eps$-close to $D_x$.
-\end{definition}
-
-\subsection{Quantum Prover Interactive Protocols (QPIP)}
-
-We model the interaction between a (almost classical) client and a quantum server following \cite{FOCS:Mahadev18a}.
-When the client has limited quantum memories, this is a ``streaming" model.
-That is, the server can send qubits one-by-one to let client measure them sequentially,
-even if the client cannot hold the entire quantum message.
-When the client is fully classical,
-this model specializes to the standard rounds-based model.
-
-\begin{definition}
-    A protocol $\Pi=(P, V)$ is said to be in $\QPIP_\tau$ if it satisfies the following properties:
-    \begin{itemize}
-        \item $P$ is a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
-        \item $V$ is a hybrid machine of a classical part and a limited quantum part.
-The classical part is a $\BPP$ machine.
-The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel which can transmit $\tau$ qubits.
-At any given time, the verifier is not allowed to possess more than $\tau$ qubits.
-The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
-        \item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially many bits to either direction.
-    \end{itemize}
-\end{definition}
-
-It is straightforward to write down what it means for a $\QPIP_\tau$ protocol to recognize a $\BQP$ language.
-
-\begin{definition}
-    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
-    We say it is a protocol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds:
-\begin{itemize}
-        \item On public inputs $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
-        \item (Completeness): For all security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
-        $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
-        \item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
-    \end{itemize}
-\end{definition}
-
-It is less simple to state what it means for a $\QPIP_\tau$ protocol to solve a $\SampBQP$ instance.
-We cannot hope for the protocol's output distribution to be close to the true distribution,
-since a cheating prover can abort to force the verifier output $\bot$ with arbitrary probability.
-On the other hand, we can ask that the output distribution to be close to the true one whenever the protocol does not abort.
-
-\begin{definition}
-    \label{dfn:stats-secure-proto-sampbqp}
-    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
-    We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c(\cdot)$ and statistical (resp., computational) soundness if the following holds:
-    \begin{itemize}
-        \item On public inputs $1^\lambda$, $1^{1/\eps}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
-            If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$ where $m$ is given in \Cref{dfn:sampling-problem}, otherwise $z=\bot$.
-        \item (Completeness):
-            For all accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
-            security parameter $\lambda\in\bbN$,
-            and $x\in\zo^{\poly(\lambda)}$,
-            Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
-        \item (Statistical soundness): For all cheating prover $P^*$,
-            accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
-            sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$,
-            consider the following experiment:
-            \begin{itemize}
-                \item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\eps}, x)$.
-                \item Define $z_{ideal}$ by
-                $$\begin{cases}
-                    z_{ideal}=\bot & \text{if } d=\Rej\\
-                    z_{ideal}\leftarrow D_x & \text{if } d=\Acc
-                \end{cases}$$.
-            \end{itemize}
-            It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\eps$.
-		\item (Computational soundness):
-			\Ethan{tried to write in terms of indistinguishability}
-        For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
-            sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$,
-            define $d, z, z_{ideal}$ by the same experiment as above.
-            It holds that $(d, z)$ is $\eps$-computationally indistinguishable to $(d, z_{ideal})$ over $\lambda$.
-    \end{itemize}
-\end{definition}
-
-\begin{remark} Note that we do not parameterize the soundness error in Definition \ref{dfn:stats-secure-proto-sampbqp}.
-This is because the definition of $\SampBQP$ already includes an error parameter $\eps$, where the algorithm is allowed to generate a sample with statistical error up to $\eps$ in time polynomial in $1/\eps$.
-Hence, we define the soundness to  allow the verifier's output to have an $\eps$ error for any given inverse polynomial $\eps$ without introducing an extra soundness error parameter.
-\end{remark}
-
-We now define blindness of a protocol.
-In the context of blind protocols, we consider $x$ as the verifier's private input instead of a common input.
-
-\Ethan{The following blindness definition is more crypto-based, but since we're submitting it to Eurocrypt maybe this is fine as-is?}
-
-\begin{definition}[Blindness]
-    Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ (and $1^{1/\eps}$ for the case of $\SampBQP$ problem), and verifier's private input $x\in\zo^*$.
-    We say $\Pi$ is \emph{blind} if for all cheating $\BQP$ prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
-    \begin{itemize}
-        \item $\set{\View_{P^*}(P^*, V(x))(1^\lambda, 1^{1/\eps})}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
-        \item $\set{\View_{P^*}(P^*, V(0))(1^\lambda, 1^{1/\eps})}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
-    \end{itemize}
-\end{definition}
-
-\fi
+We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the soundness property we just defined.
+Proving the soundness of these constructions for delegating $\SampBQP$ is an interesting open question.

### 2020-11-14 paper.tex
Sync

@@
 \newif\ifdraft
-%\drafttrue
-\draftfalse
+\drafttrue
+%\draftfalse
 
@@
 \fi
+
 %\pagecolor{black}
@@
 \newcounter{protocol}
-%\newcommand{\linefill}{\rule{\linewidth}{0.8pt}}
+\newcommand{\linefill}{\rule{\linewidth}{0.8pt}}
 
@@
 \def \Kprop {K_{\mathrm{prop}}}
+%\def \tr {\mathrm{tr}}
 
@@
 Part of this work was done while supported by Scott Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.}}
-\author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837(CAREER).}}
+\author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER).}}
 \affil[1, 2]{Institute of Information Science, Academia Sinica, Taiwan}
@@
 \input{macros.tex}
-\input{./parallel/macros.tex}
+\input{macros_1.tex}
 \begin{document}
@@
 It is a highly desirable property that has been intensively studied for the delegation of quantum computation.
-Somewhat surprisingly, we provide a simple yet powerful \emph{generic} compiler that transforms any CVQC protocol to a blind one while preserving the completeness and soundness errors.  
+We provide a simple yet powerful \emph{generic} compiler that transforms any CVQC protocol to a blind one while preserving its completeness and soundness errors as well as the number of rounds.  
 \end{itemize}
@@
 \noindent \textbf{Keywords:} classical delegation of quantum computation, blind quantum computation, quantum sampling problems
-
-\iffalse
-
-\KM{version 2}
-
-In a recent breakthrough, Mahadev constructed a classical verification of quantum computation (CVQC) protocol for a  classical client to delegate \emph{decision problems} in $\BQP$ to an untrusted quantum prover.
-In this work, motivated by the fact that many applications of quantum computations (e.g., in quantum machine learning) are sampling problems, we initiate the study of CVQC for \emph{quantum sampling problems} (denoted by $\SampBQP$), where given an input $x\in \zo^n$, the goal is to learn a sample an output $z \leftarrow C(x)$ over  $\zo^m$ for a quantum circuit $C$ from an untrusted prover with a correct distribution (up to a small error $\eps$).
-
-As our main result, we construct a four-message CVQC protocol for $\SampBQP$ with an arbitrarily small inverse polynomial error $\eps$ based on the quantum learning with error assumption.
-
-\fi
-
-%Following the recent breakthrough of Mahadev, we explore the feasibility of classical verification of quantum computation (CVQC) for a broader class of quantum computation with blindness property.
-
-%This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
 
@@
 
-%\input{qpip}
-
 \input{qpip0}

### 2020-11-14 preliminaries.tex
Sync

@@
-\section{Preliminaries}
+\section{Preliminaries} \label{sec:prelim}
 
@@
 For matrix $H$ and subspace $S$, let $H\big|_S=\Pi_S H \Pi_S$, where $\Pi_S$ is the projector onto the subspace $S$.
-%For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
 We write $x\xleftarrow{\$}X$ when $x$ is sampled uniformly at random from the set $X$.
-We use $\BQP$ as an adjective to mean polynomial-time, e.g. a $\BQP$ machine.
+%We use $\BQP$ as an adjective to mean polynomial-time, e.g. a $\BQP$ machine.
 
@@
 For $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$,
-let $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ denote the trace distance between $\rho_1$ and $\rho_2$.
-We say $\rho_1$ and $\rho_2$ are $\eps$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\eps$.
-For two distributions $f_1$ and $f_2$ over the same finite domain $X$, let $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ denote their total variation distance,
-and we say $f_1$ and $f_2$ are $\eps$-close if $\norm{f_1-f_2}_{TV}\leq\eps$.
+let $\norm{\rho_1-\rho_2}_{\mathrm{tr}}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ denote the trace distance between $\rho_1$ and $\rho_2$.
+We say $\rho_1$ and $\rho_2$ are $\eps$-close if $\norm{\rho_1- \rho_2}_{\mathrm{tr}}\leq\eps$.
+For two distributions $f_1$ and $f_2$ over the same finite domain $X$, let $\norm{f_1-f_2}_{\mathrm{TV}}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ denote their total variation distance,
+and we say $f_1$ and $f_2$ are $\eps$-close if $\norm{f_1-f_2}_{\mathrm{TV}}\leq\eps$.
 We additionally denote the following for states that are only computationally indistinguishable (but might be statistically far):
@@
     $$\abs{\Pr\left[\mathsf{D}(\rho_{1,\lambda})=1\right]-\Pr\left[\mathsf{D}(\rho_{2,\lambda})=1\right]}\leq\eps(\lambda).$$
-    % We also denote $\eps$-computational indistinguishability by $\rho_{1,\lambda}\approx_{c, \eps}\rho_{2,\lambda}$.
     We drop the $\eps$ parameter when it is negligible.
     We extend computational indistinguishability to subnormalized states by interpreting a subnormalized state $\rho$ as sending out $\bot$ with probability $1-\tr(\rho)$ and having the distinguisher $\mathsf{D}$ output $\bot$ whenever he receives $\bot$.
-    We also extend it to classical random variable by treating them as mixed states.
+    We also extend it to classical random variables by treating them as mixed states.
 \end{definition}
-
-%   We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output\hannote{?} subnormalized states as appropriate.
 
@@
 \subsection{Quantum Prover Interactive Protocols (QPIP)} 
+\label{sec:qpip_def}
 
-Following \cite{FOCS:Mahadev18a}, we model the interaction between a (almost classical) client and a quantum server in the following definition.
-When the client has limited quantum memories (i.e., $\tau > 0$), this is a ``streaming" model.
-That is, the server can send qubits one-by-one to let client measure them sequentially, even if the client cannot hold the entire quantum message.
-When the client is fully classical (i.e, $\tau = 0$), this model specializes to the standard rounds-based interactive protocols.
+Following \cite{FOCS:Mahadev18a}, we model the interaction between an almost classical client with quantum memory of size $\tau$ (verifier) and a quantum server (prover) in the following definition.
+When the client has limited quantum memories (i.e., $\tau > 0$), it becomes a ``streaming" model.
+Namely, the server can send qubits one-by-one to let the client measure them sequentially, even if the client cannot hold the entire quantum message.
+When the client is fully classical (i.e., $\tau = 0$), this model specializes to the standard interactive protocols.
 
@@
 The classical part is a $\BPP$ machine.
-The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel which can transmit $\tau$ qubits.
+The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel that can transmit $\tau$ qubits.
 At any given time, the verifier is not allowed to possess more than $\tau$ qubits.
@@
 \begin{itemize}
-        \item On public inputs $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
+        \item On public input $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
         \item (Completeness): For all security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
@@
 
-We now define blindness, which means that the prover does not learn any information about the verifier's input except for its length.
+We now define \emph{blindness} which means that the prover does not learn any information about the verifier's input except for its length.
 As such, in this context, we consider the input $x$ as the verifier's private input instead of a common input.
-
-\Ethan{The following blindness definition is more crypto-based, but since we're submitting it to Eurocrypt maybe this is fine as-is?}
 
@@
     \begin{itemize}
-        \item $\set{\View_{P^*}(P^*, V(x))(1^\lambda)}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
-        \item $\set{\View_{P^*}(P^*, V(0))(1^\lambda)}_{\lambda\in\bbN, \eps\in(0^{|x|},1), x\in\zo^*}$
+        \item $\set{\View_{P^*}(P^*, V(x))(1^\lambda)}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$,
+        \item $\set{\View_{P^*}(P^*, V(0))(1^\lambda)}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$.
     \end{itemize}
@@
 
-\iffalse
+% \iffalse
+% Probably not necessary
 
-Probably not necessary
-
-\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
-    Let $\rho_1, \rho_2, \rho_3\in\cB^{\otimes n}$ such that
-    \begin{align}
-        \rho_1\approx_{c, \eps}\rho_2\\
-        \rho_2\approx_{c, \eps'}\rho_3.
-    \end{align}
-    We have
-    \begin{align}
-        \rho_1\approx_{c, \eps+\eps'}\rho_3.
-    \end{align}
-\end{lem}
-
-\fi
+% \begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
+%     Let $\rho_1, \rho_2, \rho_3\in\cB^{\otimes n}$ such that
+%     \begin{align}
+%         \rho_1\approx_{c, \eps}\rho_2\\
+%         \rho_2\approx_{c, \eps'}\rho_3.
+%     \end{align}
+%     We have
+%     \begin{align}
+%         \rho_1\approx_{c, \eps+\eps'}\rho_3.
+%     \end{align}
+% \end{lem}
+% \fi
 
@@
 \begin{definition}[Compactness and Full Homomorphism]
-    A quantum homomorphic encryption scheme $\QHE$ is compact if
+    A quantum homomorphic encryption scheme $\QHE$ is \emph{compact} if
     there exists a polynomial $s$ in $\lambda$ such that the output length of $\QEval$ is at most $s$ bits long (regardless of $f$ or
-    the number of inputs). A compact scheme is (pure) fully homomorphic if it can evaluate any efficiently computable
-    boolean function.
+    the number of inputs). A compact scheme is (pure) \emph{fully homomorphic} if it can evaluate any efficiently computable
+    Boolean function.
 \end{definition}
@@
     A scheme $\QHE$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
-    $$\abs{Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(1))=1]}\leq\mu(\lambda)$$
-    where $(pk, sk)\leftarrow\QGen(1^\lambda)$
+    $$\abs{Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(1))=1]}\leq\mu(\lambda),$$
+    where $(pk, sk)\leftarrow\QGen(1^\lambda)$.
 \end{definition}

### 2020-11-14 qpip.tex
Sync

@@
 	\begin{itemize}
-		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\eps$.
+		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}_{\mathrm{TV}}\leq\eps$.
 		\item Let $T$ be the number of gates in $C$.
@@
     \label{QPIP1thm}
-	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}}
+	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}.}
 	%\XW{do we want precise error bound?}
@@
 	=\frac{1}{\abs{\Sym(M)}}\sum_{\hat{\Pi}\in\Sym(M)}\hat{\Pi}\sigma\hat{\Pi}^\dagger
-	=\sigma'$$
+	=\sigma',$$
 	where the second equality is by relabeling $\tilde{\Pi}\Pi=\hat{\Pi}$.
 
-	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $m+1$-fold tensor products of identical copies of some states $\tau_j$.
+	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $(m+1)$-fold tensor products of identical copies of some states $\tau_j$.
 	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes m+1}$
 	such that for all quantum-classical channels $\Lambda_i$ acting on registers of size $s$:
-	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}
+	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}_1
 	\leq\sqrt{\frac{2m^2s}{M-m}}
-	\leq\frac{\eps}{6}$$
+	\leq\frac{\eps}{6},$$
 	where $\sigma'_{\leq m+1}$ is the first $m+1$ registers of $\sigma'$.
@@
 Let $(d_j, z_j)$ be the verifier's output corresponding to $\tau_j$, and define $z_{j, ideal}$ accordingly.
-	We claim that $\norm{(d_j, z_j)-(d_j, z_{j, ideal})}_{TV}<\frac{2\eps}{6}$.
+	We claim that $\norm{(d_j, z_j)-(d_j, z_{j, ideal})}_{\mathrm{TV}}<\frac{2\eps}{6}$.
 	Let $p_j$ be the probability that $\cVGS(\tau_j)=\Acc$, and consider the following two cases.
@@
 	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities.
-	As a result, $\norm{(d_j, z_j)-(d_j, z_{j, ideal})}_{TV}=\negl(\lambda)$.
+	As a result, $\norm{(d_j, z_j)-(d_j, z_{j, ideal})}_{\mathrm{TV}}=\negl(\lambda)$.
 
@@
 	which in turn implies a lower bound on the respective trace distance:
-	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}<\frac{\eps}{6}.$$
+	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{\tr}<\frac{\eps}{6}.$$
 	\fi
 	By \Cref{thm:HamCheckClose} we have
-	$$\norm{\tau_j - \ket{\psi^{\mathrm{hist}}_{C'(x)}}\bra{\psi^{\mathrm{hist}}_{C'(x)}}}_{tr}\leq\frac{2}{\sqrt{3}}\sqrt{2\kappa\cdot2\sum_i\abs{\alpha_i}}=\frac{\eps}{6}.$$
+	$$\norm{\tau_j - \ket{\psi^{\mathrm{hist}}_{C'(x)}}\bra{\psi^{\mathrm{hist}}_{C'(x)}}}_{\tr}\leq\frac{2}{\sqrt{3}}\sqrt{2\kappa\cdot2\sum_i\abs{\alpha_i}}=\frac{\eps}{6}.$$
 	Observe that when $d_j=\Acc$, $z_j$ is the measurement results on $\tau_j$'s data register,
@@
 	and define $z_{\rho, ideal}$ accordingly.
-	We have $\norm{(d_\rho, z_\rho) - (d, z_{\rho, ideal})}_{TV} < \frac{2\eps}{6}$ since the same is true for all components $\tau_j$.
+	We have $\norm{(d_\rho, z_\rho) - (d, z_{\rho, ideal})}_{\mathrm{TV}} < \frac{2\eps}{6}$ since the same is true for all components $\tau_j$.
 
 	As $(d, z)$ is $\frac{\eps}{6}$-close to $(d_\rho, z_\rho)$ by the data processing inequality,
-	using triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{TV}\leq\frac{\eps}{2}$.
-	Hence $\norm{d - d_\rho}_{TV}\leq\frac{\eps}{2}$, which implies $\norm{(d_\rho, z_{\rho, ideal}) - (d, z_{ideal})}_{TV}$ $\leq$ $\frac{\eps}{2}$.
-	It then follows from triangle inequality that
-	$\norm{(d, z) - (d, z_{ideal})}_{TV}\leq\eps$.
+	using the triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{\mathrm{TV}}\leq\frac{\eps}{2}$.
+	Hence $\norm{d - d_\rho}_{\mathrm{TV}}\leq\frac{\eps}{2}$, which implies $\norm{(d_\rho, z_{\rho, ideal}) - (d, z_{ideal})}_{\mathrm{TV}}$ $\leq$ $\frac{\eps}{2}$.
+	It then follows from the triangle inequality that
+	$\norm{(d, z) - (d, z_{ideal})}_{\mathrm{TV}}\leq\eps$.
 \end{prf}

### 2020-11-14 qpip0.tex
Sync

@@
 Composing it with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
-In this work, We try to compose $\PiMeasure$ with our $\QPIP_1$ protocol $\PiSamp$ (\Cref{ProtoQPIP1}) for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$
+In this work, We try to compose $\PiMeasure$ with our $\QPIP_1$ protocol $\PiSamp$ (\Cref{ProtoQPIP1}) for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$.
 
@@
 under our $\SampBQP$ context, however, we must run many copies of $\PiNaive$ in parallel so the verifier can generate its outputs from some copy.
-We spend the majority of this section analyzing the soundness of this parallel repetition.
+We will spend the majority of this section analyzing the soundness of this parallel repetition.
 
@@
 It gives the following \emph{binding property} against cheating provers:
-if a prover would always succeed on the testing round, then there exists some $\rho$ so that for any $h$ the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round.
+if a prover would always succeed on the testing round, then there exists some $\rho$ so that for any $h$ the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen the Hadamard round.
 
@@
 we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
-For all $k \in [m]$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$ \Ethan{This ok?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.$$
+For all $k \in [m]$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$,  
+%\Ethan{This ok?}, 
+and $\ket{\psi} \in H_{\regX,\regZ}$, define $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.$$
 For all $i\in[m]$, we then decompose $\ket{\psi}$ into

### 2021-02-19 hamiltonian.tex
Sync Overleaf changes

@@
 \begin{eqnarray}
-  \Hprop^1 &= & \frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1\otimes Z_2) \\
+  \Hprop^1 &= & \frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1\otimes Z_2), \\
   \Hprop^T &= & \frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}\otimes X_T).
@@
     The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
-    $$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
+    $$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right).$$
 \end{lem}
@@
     Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
-    $$J=\frac{8\norm{H_1}^2+ 2\norm{H_1}}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
+    $$J=\frac{8\norm{H_1}^2+ 2\norm{H_1}}{\lambda\left(H_2\big|_{K^\bot}\right)},$$
     then we have
-    $$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
+    $$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}.$$
 \end{lem}

### 2021-02-19 introduction.tex
Sync Overleaf changes

@@
 
-A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks about the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
+A complexity-theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks about the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
 efficient quantum prover (a $\BQP$ machine).
@@
 It is worthwhile noting that there is a simple reduction of the delegation of \emph{classical} sampling problems to decision ones: for example, the verifier can fix a seed for pseudo-randomness, send it to the prover, and then the sampling outcome can be computed  bit-by-bit under this pseudo-random seed in a deterministic way.
-As such, classical literature of delegation of computation primarily focuses on delegation of decision problems.
-
-Unfortunately, it is unclear about how to make this de-randomization trick work for the delegation of $\SampBQP$, 
+As such, classical literature of delegation of computation primarily focuses on the delegation of decision problems.
+Unfortunately, it is unclear how to make this de-randomization trick work for the delegation of $\SampBQP$, 
 as randomness in quantum computation inherently comes from quantum mechanics rather than classical probability theory. 
 Thus, it seems that the delegation of $\SampBQP$ needs to take a different technical route.
-One natural starting point is Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} for $\BQP$. 
-Indeed, some nice features of Mahadev's protocol (e.g., allowing X-Z measurements on any qubit) suggest the feasibility of generating  multi-bit measurement outcomes with the protocol. 
-However, as highlighted below in the technical introduction section, there are also important drawbacks of Mahadev's protocol in its current form, which makes it hard to allow a CVQC protocol for $\SampBQP$ with desired performance.
-As we shall see, such difficulties do not hold for the decision problem, which demonstrates an important difference between CVQC protocols for the decision and the sampling problems.
+
+The first and important step in the case of $\SampBQP$ is to identify an appropriate definition of corresponding CVQC protocols.
+In contrast to the single-bit $\mathrm{Accept/Reject}$ information for the decision $\BQP$, any $\SampBQP$ problem needs to always output a sample of the desired distribution.
+In the context of CVQC protocols, it means that the protocol should allow the verifier to generate the desired output sample whenever the protocol accepts.
+Of course, when the prover cheats, the verifier will reject and no further output is required in that case.
+Intuitively, the soundness should require that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interacting with a malicious prover.
+
+A natural attempt is to directly apply Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} for $\SampBQP$.
+Note that Mahadev's protocol consists of the so-called testing round, where the prover's behavior is tested,  and the Hadamard round, where measurement outcomes are generated.
+Indeed, some nice features of the Hadamard round,  e.g., allowing X-Z measurements on any qubit,  suggest the feasibility of generating  multi-bit measurement outcomes with the protocol. 
+However, the requirement that the verifier needs to output a sample whenever accepting also exposes one drawback of Mahadev's protocol: while it is possible, as we will show, to generate desired output samples in the Hadamard round,
+it is however unclear how to generate such a sample when the protocol accepts in the testing round, since the sampling information stored in the quantum state will be disturbed by the testing step. 
+Note that this difficulty is essentially due to the different requirements between the definitions of CVQC protocols for the decision and the sampling problems.
 
@@
 Moreover, the blindness property is known to be helpful to establish the verifiability of CVQC protocols. However, this is never an easy task.
-See for example the significant amount of efforts to add verifiability to blind computation protocol in~\cite{FK17}.
+See for example the significant amount of effort to add verifiability to blind computation protocol in~\cite{FK17}.
 It is also known that another important primitive called the Quantum Fully Homomorphic Encryption (QFHE)~\cite{BJ15, DSS16, LC18, NS18, OTF18, mahadev_qfhe} should be helpful for establishing blindness: this is intuitive since QFHE allows fully homomorphic operations on encrypted quantum data.
@@
 The constructed QFHE automatically implies a blind CVQC protocol, however, without verifiability.
-Extending this protocol with verifiability seems challenging as hinted by failed attempts in Section 2.2.2 of Mahadev's PhD thesis~\cite{mahadev_2018}.
+Extending this protocol with verifiability seems challenging as hinted by failed attempts in Section 2.2.2 of Mahadev's Ph.D. thesis~\cite{mahadev_2018}.
 
@@
 Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of (local) quantum memory in the possession of the classical verifier, or equivalently, the limited quantum power of the verifier\footnote{Intuitively, the size of local quantum memory limits the size of qubits that a general (entangled) quantum operation can be operated on at the same time.
-However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the pover and discard some local qubits in the case of overflow.}.
+However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the prover and discard some local qubits in the case of overflow.}.
 A precise definition is given in Section~\ref{sec:qpip_def}. 
@@
 
-The first and important step in the case of $\SampBQP$ is to identify an appropriate definition of corresponding CVQC protocols.
-In contrast to the single bit $\mathrm{Accept/Reject}$ information for the decision $\BQP$, any $\SampBQP$ problem needs to always output a sample of the desired distribution.
-In the context of CVQC protocols, it means that the protocol should allow the verifier to generate a desired output sample whenever the protocol accepts. 
-(Of course, when the prover cheats, the verifier will reject and no further output is required in that case.)
-Intuitively, the soundness requires that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interact with a malicious prover.
-We formalize this by a strong \emph{simulation-based} definition (Section~\ref{sec:samp_definition}), where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in the either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.
+As we mentioned earlier that an appropriate definition of CVQC for $\SampBQP$ is needed to capture the intuition that the verifier should always output the desired sample whenever accepts, but should never be "cheated" to accept and output an incorrect sample when interacting with a malicious prover.
+We formalize this by a strong \emph{simulation-based} definition (Section~\ref{sec:samp_definition}), where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.
 
-To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems.
-We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the simulation-based soundness property we defined.
-Proving soundness of these constructions for delegating $\SampBQP$ is an interesting open question.
+To the best of our knowledge, we are the first to formally define the delegation of quantum sampling problems.
+We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problems and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the simulation-based soundness property we defined.
+Proving the soundness of these constructions for delegating $\SampBQP$ is an interesting open question.
 
-The requirement that the verifier needs to output a sample when accepts exposes one drawback of Mahadev's protocol: 
-while it is possible, as we will show, to generate desired output samples in the Hadamard round, 
-it is however unclear about how to generate such a sample when the protocol accepts in the testing round, since the sampling information stored in the quantum state will be disturbed by the testing step.
-
+The requirement that the verifier needs to output a sample when accepts makes a direct application of Mahadev's protocol infeasible for $\SampBQP$.
 As a result, in order to construct a $\QPIP_0$ protocol for $\SampBQP$,  one needs to (1) construct a $\QPIP_1$ protocol for $\SampBQP$ with very small completeness and soundness errors, and (2) amend Mahadev's construction so that the protocol will generate the desired sample whenever it accepts.
@@
 Recall that the original construction of local Hamiltonian $H$ for $\BQP$ (or $\QMA$) contains two parts $H=H_{\mathrm{circuit}}+ H_{\mathrm{out}}$.
-Roughly speaking, $H_{\mathrm{circuit}}$ helps guarantee its ground space only contains \emph{valid} history states with correct input and circuit evolution, while $H_{\mathrm{out}}$'s energy encodes the 0/1 output for $\BQP$ circuits.
+Roughly speaking, $H_{\mathrm{circuit}}$ helps guarantee its ground space only contains \emph{valid} history states with the correct input and circuit evolution, while $H_{\mathrm{out}}$'s energy encodes the 0/1 output for $\BQP$ circuits.
 Thus, the outcome of a $\BQP$ instance can be encoded by the \emph{ground energy} of $H$.
@@
 Thus, to leverage the aforementioned intuition, one needs to avoid entanglement among these copies to obtain some sort of independence.
-We employ quantum \emph{de Finetti} theorem to address this technical challenge.
+We employ the quantum \emph{de Finetti} theorem to address this technical challenge.
 Specifically, given any permutation-invariant $k$-register state (where each register could contain many qubits), it is known that the reduced state on many subsets of $k$-register will be close to a separable state.
 Typically, for favorable error bounds, the parameter $k$ could be as large as the dimension of a single register, which is exponential in our context and hence undesirable. 
-Fortunately, since there is no entangled operation in the protocol to perform on two copies of history states, one can employ an efficient variant of quantum \emph{de Finetti} theorem~\cite{Brandao2017} whose error bound depends poly-logarithmically on the dimension of the register, which leads to an efficient $\QPIP_1$ protocol for $\SampBQP$.
+Fortunately, since there is no entangled operation in the protocol to perform on two copies of history states, one can employ an efficient variant of the quantum \emph{de Finetti} theorem~\cite{Brandao2017} whose error bound depends poly-logarithmically on the dimension of the register, which leads to an efficient $\QPIP_1$ protocol for $\SampBQP$.
 We can further achieve very small completeness and soundness errors in this way to satisfy the premise of Mahadev's compilation.  
@@
 The challenge is to show that $\PiSampZ$ is computationally sound.
-Note that now we are in the computational setting, we cannot use quantum de Finetti theorem as above since it only holds in the information-theoretical setting.
+Note that now we are in the computational setting, we cannot use the quantum de Finetti theorem as above since it only holds in the information-theoretical setting.
 Furthermore, parallel repetition for computationally sound protocols are typically difficult to analyze, and known to not always work for protocols with four or more messages~\cite{BIN97,PW12}.
@@
 
-It is worth comparing parallel repetition of Mahadev's protocol for $\BQP$ and $\SampBQP$.
+It is worth comparing the parallel repetition of Mahadev's protocol for $\BQP$ and $\SampBQP$.
 For $\BQP$, the verifier simply chooses to run the Hadamard and testing rounds independently for each repetition.
@@
 
-We apply the partition lemma iteratively to the prover's state  similarly as~\cite{arXiv:ChiaChungYam19}, but with significant differences to show the soundness of $\PiSampZ$ for $\SampBQP$.
-In particular, extra cares are required to reason about the computational indistinguishability of the verifier's output sample from the correct distribution $D_x$.
+We apply the partition lemma iteratively to the prover's state  similarly to~\cite{arXiv:ChiaChungYam19}, but with significant differences to show the soundness of $\PiSampZ$ for $\SampBQP$.
+In particular, extra care is required to reason about the computational indistinguishability of the verifier's output sample from the correct distribution $D_x$.
 To gain some intuition, let us apply the partition lemma to the prover's state $\ket{\psi}$ with respect to the first coordinate, which decompose $\ket{\psi} = \ket{\psi_0} + \ket{\psi_1}$ with $\ket{\psi_0} \in S_0$ and  $\ket{\psi_1} \in S_1$, respectively.
@@
 Intuitively, this allows the prover to compute his next message under encryption without learning the underlying verifier's message, and hence achieves blindness while preserving the properties of the original protocol.
-One subtlety with this approach is due to the fact that the verifier is classical while the QFHE cipher text could depend on both quantum and classical data.
+One subtlety with this approach is the fact that the verifier is classical while the QFHE cipher text could depend on both quantum and classical data.
 In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm need to be classical when the underlying message is classical, which is fortunately satisfied by~\cite{mahadev_qfhe}.
@@
 A more subtle issue is to preserve the soundness.
-In particular, compiled protocols with only one-time use of QFHE might (1) leak information about the circuit being evaluated during the homomorphic evaluation of QFHE ciphertexts (i.e., no \emph{circuit privacy});
-or (2) fail to simulate original protocols upon receiving invalid ciphertexts.
+In particular, compiled protocols with a single application of QFHE might (1) leak information about the circuit evaluated by the verifier through its outputted QFHE ciphertexts (i.e., no \emph{circuit privacy});
+or (2) fail to simulate original protocols upon receiving invalid ciphertexts from the prover.
 We address these issues by letting the verifier switch to a fresh new key for each round of the protocol. 

### 2021-02-19 model.tex
Sync Overleaf changes

@@
 In this section, we formally introduce the task of delegation for quantum sampling problems.
-We start by recalling the complexity class $\SampBQP$ defined by Aaronson~\cite{aaronson_2013, aaronson_arkhipov_2011}, which captures the class of sampling problems that
+We start by recalling the complexity class $\SampBQP$ defined by Aaronson~\cite{aaronson_2013, Boson}, which captures the class of sampling problems that
 are approximately solvable by polynomial-time quantum algorithms.
@@
 For example, conceivable physical realizations of quantum computer may consist of inherent noise.
-We refer the readers to~\cite{aaronson_2013, aaronson_arkhipov_2011} for the discussion therein on why this better captures the sampling problem solvable by realistic quantum computers.
+We refer the readers to~\cite{aaronson_2013, Boson} for the discussion therein on why this better captures the sampling problem solvable by realistic quantum computers.
 

### 2021-02-19 paper.tex
Sync Overleaf changes

@@
 
+\date{}
 \maketitle
@@
 \item  Motivated by the sampling nature of many quantum applications (e.g., quantum algorithms for machine learning and quantum supremacy tasks), we initiate the study of  CVQC for \emph{quantum sampling problems} (denoted by $\SampBQP$).
-More precisely, in a CVQC protocol for a $\SampBQP$ problem, the prover and the verifier are given an input $x\in \zo^n$ and a quantum circuit $C$, and the goal of the classical client is to learn a sample from the output $z \leftarrow C(x)$ up to a small error, from its interation with an untrusted prover.
+More precisely, in a CVQC protocol for a $\SampBQP$ problem, the prover and the verifier are given an input $x\in \zo^n$ and a quantum circuit $C$, and the goal of the classical client is to learn a sample from the output $z \leftarrow C(x)$ up to a small error, from its interaction with an untrusted prover.
 We demonstrate its feasibility by constructing a four-message CVQC protocol for $\SampBQP$ based on the quantum \emph{Learning With Error} assumption.

### 2021-02-19 qpip0.tex
Sync Overleaf changes

@@
 In this section, we create a delegation protocol for $\SampBQP$ with fully classical clients by adapting the approach taken in \cite{FOCS:Mahadev18a}. In \cite{FOCS:Mahadev18a}, 
-Mahadev designed a protocol $\PiMeasure$ (\Cref{proto:urmila4}) that allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
+Mahadev designed a protocol $\PiMeasure$ (\Cref{proto:urmila4}) that allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a $X$ or $Z$ measurement and obtain corresponding measurement results.
 Composing it with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
-In this work, We try to compose $\PiMeasure$ with our $\QPIP_1$ protocol $\PiSamp$ (\Cref{ProtoQPIP1}) for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$.
+In this work, we will compose $\PiMeasure$ with our $\QPIP_1$ protocol $\PiSamp$ (\Cref{ProtoQPIP1}) for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$.
 
@@
 and in a Hadamard round the verifier receives some measurement outcome.
-He sends his choice to the prover, and prover replies accordingly.
+He sends his choice to the prover, and the prover replies accordingly.
 If the verifier chose testing round, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency.
@@
 $\PiMeasure$ has negligible completeness errors, i.e.
-if both the prover and verifier are honest, the verifier's output on Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
+if both the prover and verifier are honest, the verifier accepts with overwhelming probability and his output on Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
 As for soundness,
-It gives the following \emph{binding property} against cheating provers:
+it gives the following \emph{binding property} against cheating provers:
 if a prover would always succeed on the testing round, then there exists some $\rho$ so that for any $h$ the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen the Hadamard round.
@@
 This is because on rejecting a Hadamard round, the verifier can output a uniformly random string, and that is same as the result of measuring $h$ on the totally mixed state.} Under the QLWE assumption, there exists some $\rho^*$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is $\sqrt{p_{h,T}}+\negl(n)$-computationally indistinguishable from $M_{XZ}(\rho^*, h)$.
-
-%\footnote{Two distributions has $c$ computational distance if any efficient algorithm can produce at most $c$ bias between them.}
-
 \end{lemma}
-
-% \begin{lemma}[binding property of $\PiMeasure$; special case of Claim 7.1 in \cite{FOCS:Mahadev18a}\hannote{correct ref?}]
-% 	\label{lem:urmila-binding}
-% 	Let $\PMeasureStar$ be a $\BQP$ cheating \hannote{defined?} prover for $\PiMeasure$ and $\lambda$ be the security parameter.
-Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$\footnote{In terms of \cite{FOCS:Mahadev18a}, we are setting $P_{h,T}$ as a negligible function.}, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
-% \end{lemma}
 
@@
 Let the distribution on $h$ specified in Step~\ref{step:naive1} of the protocol be $p_x(h)$.
-Note that we can take $\Pstar$'s responds in Step~\ref{step:urmila-in-naive}, $\Pstarsub(x)$, as a prover strategy for \Cref{proto:urmila4}.
+Define $\Pstarsub(x)$ as $\Pstar$'s responds in Step~\ref{step:urmila-in-naive}.
+Note that we can view $\Pstarsub(x)$ as a prover strategy for \Cref{proto:urmila4}.
 By construction $\Pstarsub(x)$ passes testing round with overwhelming probability over $p_x(h)$, i.e.
@@
 		\item Security parameter $1^\lambda$ for $\lambda\in\bbN$.
-		\item Accuracy parameter $1^{1/\eps}$ for the $\SampBQP$ instance
-		\item Input $x\in\zo^{\poly(\lambda)}$ for the $\SampBQP$ instance
+		\item Accuracy parameter $1^{1/\eps}$ for the $\SampBQP$ problem.
+		\item Input $x\in\zo^{\poly(\lambda)}$ for the $\SampBQP$ instance.
 	\end{itemize}
@@
 Intuitively, the partition lemma says that for any cheating prover and for each copy $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
-$G_{0,i}$ and $G_{1,i}$ splits up the prover's internal state after sending back his first message.
+$G_{0,i}$ and $G_{1,i}$ splits up the prover's residual internal state after sending back his first message.
 $G_{0,i}$ intuitively represents the subspace where the prover does not knows the answer to the testing round on the $i$-th copy, while $G_{1,i}$ represents the subspace where the prover does.
@@
 We then continue to decompose $\ket{\psi_{11}}=\ket{\psi_{110}}+\ket{\psi_{111}}$ and so on, until we reach the last copy and obtain $\ket{\psi_{1^m}}$.
-This $\ket{\psi_{1^m}}$ term represents the ``good" component where the prover knows the answer to every testing round and therefore has high accept probability.
-Intuitively, $\ket{\psi_{1^m}}$ also satisfies some binding property,
+Intuitively, the $\ket{\psi_{1^m}}$ term represents the ``good" component where the prover knows the answer to every testing round and therefore has high accept probability.
+Therefore, $\ket{\psi_{1^m}}$ also satisfies some binding property,
 so the verifier should obtain a measurement result of some state on the Hadamard round copy,
@@
 
-There is an additional issue, however. As $G_{1,i}$ does not commute with $G_{1,j}$, $\ket{\psi_{1^m}}$ is unfortunately only binding for the $m$-th copy.
+However, the intuition that $\ket{\psi_{1^m}}$ is binding to every Hadamard round is incorrect.
+As $G_{1,i}$ does not commute with $G_{1,j}$, $\ket{\psi_{1^m}}$ is unfortunately only binding for the $m$-th copy.
 To solve this problem, we start with a pointwise argument and fix the Hadamard round on the $i$-th copy where $\ket{\psi_{1^i}}$ is binding,
@@
 We can later average out this error over the different choices of $i$, since not all $\norm{\ket{\psi_{1^{i-1}0}}}$ can be large at the same time.
+Another way to see this issue is to notice that we are partitioning a quantum state, not probability events, so there are some inconsistencies between our intuition and calculation.
+Indeed, the error we get in the end is $O(\sqrt{1/m})$ instead of the $O(1/m)$ we expected.
 
-Also as a careful reader might have noticed that the prover's space don't always decompose cleanly.
-In \cite{arXiv:ChiaChungYam19} this is solved by splitting the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$.
+Also a careful reader might have noticed that the prover's space don't always decompose cleanly into parts that the verifier either rejects or accepts with high probability, as there might be some states that a accepted with mediocre probability.
+In \cite{arXiv:ChiaChungYam19}, this is solved by splitting the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$ and applying amplitude amplification to boost the accept probability if it is bigger than $\gamma$.
 However, states with accept probability really close to the threshold $\gamma$ can not be classified, so they need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.
@@
 	Let $\lambda$ be the security parameter, and $\gamma_0 \in[0,1]$ and $T\in \mathbb{N}$ be parameters that will be related to the randomly-chosen threshold $\gamma$.
-	Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$\footnote{A $m$-fold parallel repetition of $\PiMeasure$ is running step~\ref{step:urmila-in-qpip0-1}~\ref{step:urmila-in-qpip0-2}~\ref{step:urmila-in-qpip0-3}~\ref{step:urmila-in-qpip0-4} of \Cref{proto:QPIP0samp} with verifier input $\vec{h}$ and prover input $\rho^\otimes n$, followed by an output step where the verifier rejects if any of the $m-1$ testing round copies is rejected, otherwise outputs the result of the Hadamard round copy.}, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message.
+	Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$\footnote{A $m$-fold parallel repetition of $\PiMeasure$ is running step~\ref{step:urmila-in-qpip0-1}~\ref{step:urmila-in-qpip0-2}~\ref{step:urmila-in-qpip0-3}~\ref{step:urmila-in-qpip0-4} of \Cref{proto:QPIP0samp} with verifier input $\vec{h}$ and prover input $\rho^{\otimes n}$, followed by an output step where the verifier rejects if any of the $m-1$ testing round copies is rejected, otherwise outputs the result of the Hadamard round copy.}, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message.
 Let $H_{\regX,\regZ}$ be the Hilberspace of the prover's internal calculation.
@@
 	\begin{align}
-	\label{eq:psi0}	G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{0,i,\gamma}}_{\regX,\regZ} \\ 
-	\label{eq:psi1}	G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{1,i,\gamma}}_{\regX,\regZ}  \\
-	\label{eq:psierr}	\ket{\psi}_{\regX,\regZ} -\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}- \ket{\psi_{1,i,\gamma}}_{\regX,\regZ} \defeq&   \ket{\psi_{err,i,\gamma}}_{\regX,\regZ}
+	\label{eq:psi0}	G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{0,i,\gamma}}_{\regX,\regZ}, \\ 
+	\label{eq:psi1}	G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{1,i,\gamma}}_{\regX,\regZ},  \\
+	\label{eq:psierr}	\ket{\psi}_{\regX,\regZ} -\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}- \ket{\psi_{1,i,\gamma}}_{\regX,\regZ} \defeq&   \ket{\psi_{err,i,\gamma}}_{\regX,\regZ}.
 	\end{align}
@@
 			\begin{align}
-				\norm{\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}^2+ \norm{\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}^2 \leq  \norm{\ket{\psi}_{\regX,\regZ}}^2
+				\norm{\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}^2+ \norm{\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}^2 \leq  \norm{\ket{\psi}_{\regX,\regZ}}^2.
 			\end{align}
@@
 it clearly follows that 
-\begin{rmk}
+\begin{claim}
 	\label{lem:partition-testing}
@@
 	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
-\end{rmk}
+\end{claim}
 
@@
 	For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
-	$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi} $$
+	$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi}. $$
 \end{lemma}
@@
 	\label{thm:zi-zgoodi}
-	$$\tr\abs{z_i-z_{good, i}}\leq\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)$$
+	$$\tr\abs{z_i-z_{good, i}}\leq\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R).$$
 \end{lemma}
@@
 		\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-	\right]$$
+	\right],$$
 	and expand $z_i$ from \Cref{eq:zi-def} as
@@
 		&\leq\sum_z\abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R)\\
-		&\leq\norm{\ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R)
+		&\leq\norm{\ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R).
 	\end{align*}
@@
 
-	%We denote the random variable the verifier would get on the Hadamard round as $z_{composite}$.
-Also define $(d,z_{composite}) \defeq (\Acc, z_{composite}) + (1-|z_{composite}|)(\Rej,\bot)$ \hannote{correct notation?}
-
 	Denote the result we would get in the Hadamard round by $z_{composite,i}$.
@@
 Now we try to put together all $i\in [m]$. First let
-$$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi}$$
+$$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
 which is the output distribution of $\PiSampZ$.
 We also define the following accordingly:
-$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}$$
-$$z_{ideal}\defeq \frac{1}{m}\sum_i z_{ideal,i}$$
+$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i,}$$
+$$z_{ideal}\defeq \frac{1}{m}\sum_i z_{ideal,i}.$$
 Notice that $z_{ideal}$ is some ideal output distribution, which might not have the same accept probability as $z$.
@@
 \begin{theorem}\label{thm:qpip0} 
-	Under the QLWE assumption, $\PiSampZ$ is a protocol for the $\SampBQP$ problem $(D_x)_{x\in\set{0,1}^*}$  with negligible completeness error and is statistically sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}}
+	Under the QLWE assumption, $\PiSampZ$ is a protocol for the $\SampBQP$ problem $(D_x)_{x\in\set{0,1}^*}$  with negligible completeness error and is computationally sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}}
 
@@
 		\norm{\ket{\psi_{10,\gamma}}}^2+ \norm{\ket{\psi_{110,\gamma}}}^2 +\cdots  \nn \\
-		&+ \norm{\ket{\psi_{1^{m-1}0,\gamma}}}^2+ \norm{\ket{\psi_{1^{m-1}1,\gamma}}}^2
+		&+ \norm{\ket{\psi_{1^{m-1}0,\gamma}}}^2+ \norm{\ket{\psi_{1^{m-1}1,\gamma}}}^2.
 	\end{align}
@@
 		\leq&  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%
-		=&O\L( \frac{1}{\sqrt m}+\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) 
+		=&O\L( \frac{1}{\sqrt m}+\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R),  
 	\end{align}
-
 	where we used triangle inequality on the second line, \Cref{thm:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
@@
 Therefore, $(d,z)$  $O(\epsilon)$-computationally indistinguishable to $(d,z_{ideal})$.
-
 %	\hannote{?}Since $z$ is close to some ideal output distribution $z_{ideal}$, it must be close to the ideal output distribution with its own accept probability too.

### 2021-05-31 hamiltonian_short.tex
Sync Overleaf updates with GitHub

\section{Construction of the $\QPIP_1$ Protocol for $\SampBQP$}
\label{sec:sampbqp_short}

See \Cref{sec:sampbqp} for the details of the construction of our $\QPIP_1$ Protocol for $\SampBQP$, \Cref{ProtoQPIP1}. The soundness and completeness of \Cref{ProtoQPIP1} is stated in the following theorem.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem\\ $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}.}
	%\XW{do we want precise error bound?}
\end{thm}

### 2021-05-31 introduction.tex
Sync Overleaf updates with GitHub

@@
 \section{Introduction}
+
 Can quantum computation, with potential computational advantages that are intractable for classical computers,
 be efficiently verified by classical means?
-This seeming paradox has been one of the central problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}.
-From a philosophical point of view, this question is also known to have a fascinating connection to the \emph{falsifiability} of quantum mechanics in the high complexity regime~\cite{survey:AV12}.
-
+This problem has been a major open problems in quantum complexity theory and delegation of quantum computation~\cite{web:Aaronson}.
 A complexity-theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks about the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
@@
 In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations.
-The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,FK17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
+The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,FK17,mf16}) considers the case where the verifier is equipped with limited quantum power.
 The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
 considers a $\BPP$ verifier interacting with at least two entangled, non-communicating quantum provers.
-In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of Classical Verification of Quantum Computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
-The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.,~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
-On the other side, there are known complexity-theoretic limitations on the feasibility of blind CVQC in the information-theoretical setting (e.g.~\cite{aaronson_et_al:LIPIcs:2019:10582}).
 
-With the newly developed techniques, we revisit the classical verification of quantum computation problems from both a philosophical and a practical point of view.
-We first observe that the \emph{sampling} version of $\BQP$ (e.g., the class $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
-Philosophically, the outcomes of quantum mechanical experiments are usually samples or statistical information, which is well demonstrated in the famous double-slit experiment.
-Moreover, a lot of quantum algorithms from Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component.
-The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones also suggests the relevance of delegation for quantum sampling problems.
+Recently, the problem is resolved by a breakthrough result of Mahadev~\cite{FOCS:Mahadev18a}, who constructed the first Classical Verification of Quantum Computation (CVQC) protocol for $\BQP$, where an efficient classical ($\BPP$) verifier can interact with an efficient quantum ($\BQP$) prover to verify any $\BQP$ language.
+Soundness of Mahadev's protocol  is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
+%In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of Classical Verification of Quantum Computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
+The technique invented therein has inspired many subsequent developments of CVQC protocols with improved parameters and functionality.
+For example, Mahadev's protocol has a large constant soundness error.
+The works of ~\cite{arXiv:AlaChiHun19,arXiv:ChiaChungYam19} use parallel repetition to achieve a negligible soundness error.
+As another example, the work of ~\cite{FOCS:GheVid19} extends Mahadev's techniques in an involved way to obtain a CVQC protocol with an additional blindness property.
 
-It is worthwhile noting that there is a simple reduction of the delegation of \emph{classical} sampling problems to decision ones: for example, the verifier can fix a seed for pseudo-randomness, send it to the prover, and then the sampling outcome can be computed  bit-by-bit under this pseudo-random seed in a deterministic way.
-As such, classical literature of delegation of computation primarily focuses on the delegation of decision problems.
-Unfortunately, it is unclear how to make this de-randomization trick work for the delegation of $\SampBQP$, 
-as randomness in quantum computation inherently comes from quantum mechanics rather than classical probability theory. 
-Thus, it seems that the delegation of $\SampBQP$ needs to take a different technical route.
+%For example,~\cite{arXiv:AlaChiHun19,arXiv:ChiaChungYam19}  
+%
+%(e.g.,~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
 
-The first and important step in the case of $\SampBQP$ is to identify an appropriate definition of corresponding CVQC protocols.
-In contrast to the single-bit $\mathrm{Accept/Reject}$ information for the decision $\BQP$, any $\SampBQP$ problem needs to always output a sample of the desired distribution.
-In the context of CVQC protocols, it means that the protocol should allow the verifier to generate the desired output sample whenever the protocol accepts.
+In this work, we make two more contributions to this exciting line of research.
+First, we observe that the literature has mostly restricted the attention to delegation of \emph{decision} problems (i.e., $\BQP$).
+Motivated by the intrinsic randomness of quantum computation and the sampling nature of many quantum applications, we initiate the study of CVQC for quantum \emph{sampling} problems.
+Second, we further investigate the desirable \emph{blindness} property and construct the first \emph{constant-round} blind CVQC protocols.
+We elaborate on our contributions in \Cref{subsection:sampling} and \ref{subsection:blind}, respectively.
+
+% On the other side, there are known complexity-theoretic limitations on the feasibility of blind CVQC in the information-theoretical setting (e.g.~\cite{aaronson_et_al:LIPIcs:2019:10582}).
+
+% With the newly developed techniques, we revisit the classical verification of quantum computation problems from both a philosophical and a practical point of view.
+
+\subsection{CVQC for Quantum Sampling Problems} \label{subsection:sampling}
+
+We initiate the study of CVQC for quantum sampling problem, which we believe is highly desirable and natural for delegation of quantum computation.
+In general, a round of quantum computation can be described as applying a quantum circuit and measuring the output qubits in computational basis.
+Due to its intrinsic randomness, the output is randomized and described by a distribution.
+%To verifiably delegate general quantum computation, it is natural to require that the output is close to the correct distribution when the verifier accepts. 
+Thus, if a classical verifier want to utilize the full power of a quantum machine, the ability to get a verifiable sample from the quantum circuit's output distribution is desirable.
+On a more concrete level, quantum algorithms like Shor's algorithm~\cite{Shor} has a significant quantum sampling component, and the recent quantum supremacy proposals (e.g.,~\cite{Boson, IQP, nature-google}) are built around sampling tasks, suggesting the importance of sampling in quantum computation.
+
+%The previous works following Madadev's construction has been focusing on decision problems.
+In this work, we proposed and constructed a extension of Mahadev's protocol to \emph{sampling} problems, where the classical verifier get a sample from a desired distribution from the quantum prover.
+More formally, we seek a classical verifiable delegation of the class $\SampBQP$ proposed by Aaronson~\cite{aaronson_2013}.
+Such an extension to sampling problems is desirable on a fundamental level; since we can always measure all qubits at the end of a quantum circuit, every quantum circuit naturally gives some distribution to sample from.
+Thus, if a classical verifier want to utilize the full power of a quantum machine, the ability to get a verifiable sample from the quantum circuit's output distribution is desired.
+On a more concrete level, quantum algorithms like Shor's algorithm~\cite{Shor} has a significant quantum sampling component, and the recent quantum supremacy proposals (e.g.,~\cite{Boson, IQP, nature-google}) are built around sampling tasks, suggesting the importance of sampling in quantum computation.
+
+% We first observe that the \emph{sampling} version of $\BQP$ (e.g., the class $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
+
+% Moreover, a lot of quantum algorithms from Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component.
+% The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones also suggests the relevance of delegation for quantum sampling problems.
+
+It is worth noting that the difficulty of extending the delegation of decision problem to the delegation of sampling problems is quantum-specific. This is because 
+there is a simple reduction from the delegation of \emph{classical} sampling problems to decision ones:  the verifier can sample and fix the random seed of the computation, 
+%\footnote{One can use pseudorandomness, e.g., generated by a PRG seed, if verifier's efficiency is required, as typically in the classical delegation of computation literature.}, 
+which makes the computation deterministic.
+Then, the verifier can delegate the output of the computation bit-by-bit as decision problems.
+However, this derandomization trick does not work in the quantum setting due to its intrinsic randomness.
+
+%fix a seed for pseudo-randomness, send it to the prover, and then the sampling outcome can be computed  bit-by-bit under this pseudo-random seed in a deterministic way.
+Therefore, classical literature of delegation of computation primarily focuses on the delegation of decision problems.
+%However, it is unclear how to make this de-randomization trick work for the delegation of $\SampBQP$,  as randomness in quantum computation comes from inherent nature of quantum mechanics rather than some random seeds.
+%Thus, it seems that the delegation of $\SampBQP$ needs to take a different technical route.
+
+% The first and important step in the case of $\SampBQP$ is to identify an appropriate definition of corresponding CVQC protocols.
+
+\vspace{-3pt}
+
+\paragraph{Our Contribution.}
+As the first step to formalize CVQC for quantum sampling problems, we formalize efficiently computable quantum sampling problems with the complexity class $\SampBQP$ introduced by Aaronson~\cite{aaronson_2013}.
+%
+%Formally, 
+$\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine (See Section~\ref{sec:samp_definition} for the formal definition).
+We consider CVQC for a $\SampBQP$ problem $(D_x)_{x\in\zo^*}$ where a classical $\BPP$ verifier delegate the computation of a sample $z\leftarrow D_x$ for some input $x$ to a quantum $\BQP$ prover.
+Completeness requires that when the prover is honest, the verifier should accept with high probability and learn a correct sample $z\leftarrow D_x$.
+For soundness, intuitively, the verifier should not accept and output a sample with incorrect distribution  when interacting with a malicious prover.
+We formalize the soundness by a strong \emph{simulation-based} definition, (\Cref{dfn:stats-secure-proto-sampbqp}),
+where we require that the joint distribution $(d,z)$ of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from the desired distribution $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.\hannote{justify?}
+%
+%To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems.
+
+%and almost never accept and output from an incorrect distribution when interacting with a malicious prover.
+We formalize this by a strong \emph{simulation-based} definition (Section~\ref{sec:samp_definition}), where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from the desired distribution $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.
+
+As our main result, we construct a constant-round CVQC protocol for $\SampBQP$, based on the quantum LWE (QLWE) assumption that the learning-with-error problem is hard for BQP machines. 
+\begin{theorem}[informal] \label{thm:qpip0-informal}
+Assuming the QLWE assumption, there exists a four-message CVQC protocol for all sampling problems in $\SampBQP$ with computational soundness and negligible completeness error.
+\end{theorem}
+
+% To the best of our knowledge, we are the first to formally define the delegation of quantum sampling problems.
+
+% We note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problems and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the simulation-based soundness property we defined.
+Proving the soundness of these constructions for delegating $\SampBQP$ is an interesting open question.
+
+% The requirement that the verifier needs to output a sample when accepts makes a direct application of Mahadev's protocol infeasible for $\SampBQP$.
+As a result, in order to construct a $\QPIP_0$ protocol for $\SampBQP$,  one needs to (1) construct a $\QPIP_1$ protocol for $\SampBQP$ with very small completeness and soundness errors, and (2) amend Mahadev's construction so that the protocol will generate the desired sample whenever it accepts.
+% Our contribution is a solution to address the above two technical challenges.
+
+% In contrast to the single-bit $\mathrm{Accept/Reject}$ information for the decision $\BQP$, any $\SampBQP$ problem needs to always output a sample of the desired distribution.
+% In the context of CVQC protocols, it means that the protocol should allow the verifier to generate the desired output sample whenever the protocol accepts.
 Of course, when the prover cheats, the verifier will reject and no further output is required in that case.
-Intuitively, the soundness should require that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interacting with a malicious prover.
+% Intuitively, the soundness should require that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interacting with a malicious prover.
 
-A natural attempt is to directly apply Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} for $\SampBQP$.
-Note that Mahadev's protocol consists of the so-called testing round, where the prover's behavior is tested,  and the Hadamard round, where measurement outcomes are generated.
-Indeed, some nice features of the Hadamard round,  e.g., allowing X-Z measurements on any qubit,  suggest the feasibility of generating  multi-bit measurement outcomes with the protocol. 
-However, the requirement that the verifier needs to output a sample whenever accepting also exposes one drawback of Mahadev's protocol: while it is possible, as we will show, to generate desired output samples in the Hadamard round,
-it is however unclear how to generate such a sample when the protocol accepts in the testing round, since the sampling information stored in the quantum state will be disturbed by the testing step. 
-Note that this difficulty is essentially due to the different requirements between the definitions of CVQC protocols for the decision and the sampling problems.
+% 
+% Indeed, some nice features of the Hadamard round,  e.g., allowing X-Z measurements on any qubit,  suggest the feasibility of generating  multi-bit measurement outcomes with the protocol.
 
-Another desirable property of CVQC protocols is the \emph{blindness} where the prover cannot distinguish the particular computation in the protocol from another one of the same size, and hence is blind about the client's input.
-Historically, blindness has been achieved in the weaker formulations of CVQC based on various techniques: e.g., the measurement-based quantum computation exploited in~\cite{BFK09}, the quantum authentication scheme exploited in~\cite{arXiv:ABOEM17}, and the self-testing technique exploited in~\cite{Nat:RUV13}.
-Moreover, the blindness property is known to be helpful to establish the verifiability of CVQC protocols. However, this is never an easy task.
-See for example the significant amount of effort to add verifiability to blind computation protocol in~\cite{FK17}.
-It is also known that another important primitive called the Quantum Fully Homomorphic Encryption (QFHE)~\cite{BJ15, DSS16, LC18, NS18, OTF18, mahadev_qfhe} should be helpful for establishing blindness: this is intuitive since QFHE allows fully homomorphic operations on encrypted quantum data.
-Indeed, in another paper~\cite{mahadev_qfhe}, Mahadev constructed the first leveled QFHE based on similar techniques and computational assumptions from~\cite{FOCS:Mahadev18a}.
-The constructed QFHE automatically implies a blind CVQC protocol, however, without verifiability.
-Extending this protocol with verifiability seems challenging as hinted by failed attempts in Section 2.2.2 of Mahadev's Ph.D. thesis~\cite{mahadev_2018}.
+%\paragraph{Techniques.}
 
-In fact, most existing blind and/or verifiable protocols for delegation of quantum computation require a notable amount of effort in achieving each property respectively. 
-The only successful CVQC protocol~\cite{FOCS:GheVid19} of achieving both so far applies Mahadev's technique~\cite{FOCS:Mahadev18a} to the measurement-based quantum computation, whereas the analysis is still very specific to the construction.
-Could there be a \emph{generic} way to achieve blindness and verifiability for CVQC protocols at the same time, say by leveraging the state-of-the-art CVQC~\cite{FOCS:Mahadev18a} and QFHE~\cite{mahadev_qfhe} protocols?
+The construction of our CVQC protocol follows the blueprint of Mahadev's construction~\cite{FOCS:Mahadev18a}.
+However, there are several obstacles we need to overcome along the way.
+To explains the obstacles and our ideas, we first present a high-level overview of Mahadev's protocol.
+
+%Our protocol is constructed by generalizing Mahadev's protocol to ha
+
+\paragraph{Overview of Mahadev's Protocol.}
+%
+Following~\cite{FOCS:Mahadev18a}, we define $\QPIP_{\tau}$ as classes of interactive proof systems between an (almost) classical verifier and a quantum prover, where the classical verifier has limited quantum computational capability, formalized as possessing $\tau$-qubit quantum memory.
+%\footnote{Intuitively, the size of local quantum memory limits the size of qubits that a general (entangled) quantum operation can be operated on at the same time.
+However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the prover and discard some local qubits in the case of overflow.}.
+A formal definition is given in Section~\ref{sec:qpip_def}.
+
+At a high-level, the heart of Mahadev's protocol is a measurement protocol $\PiMeasure$ that can compile an one-round $\QPIP_1$ protocol with special properties to a $\QPIP_0$ protocol.
+Note that in a $\QPIP_1$ protocol, the verifier with one-qubit memory can only measure the prover's quantum message qubit by qubit.
+Informally, the measurement protocol $\PiMeasure$ allows a $\BQP$ prover to ``commit to'' a quantum state $\rho$ and a classical verifier to choose an $X$ or $Z$ measurement to apply to each qubit of $\rho$ such that the verifier can learn the resulting measurement outcome.
+
+Thus, if an (one-round) $\QPIP_1$ verifier only applies $X$ or $Z$ measurement to the prover's quantum message, we can use the measurement protocol $\PiMeasure$ to turn the $\QPIP_1$ protocol into a $\QPIP_0$ protocol in a natural way.
+However, one restriction here is that the verifier's measurement choices need to be determined at the beginning (i.e., cannot depend adaptively on the intermediate measurement outcome).
+
+Furthermore, in $\PiMeasure$, the verifier chooses to run a ``\emph{testing}'' round or a ``\emph{Hadamard}'' round with $1/2$ probability, respectively.
+Informally, the testing round is used to ``test'' the commitment of $\rho$, and the Hadamard round is used to learn the measurement outcome.
+(See \Cref{proto:urmila4} for further details about the measurement protocol $\PiMeasure$.) Another limitation here is that in the testing round, the verifier may accept the test of the commitment without learning any measurement result.
+
+In~\cite{FOCS:Mahadev18a}, Mahadev's CVQC protocol for $\BQP$ is constructed by applying her measurement protocol to the one-round $\QPIP_1$ protocol of~\cite{PhysRevA.93.022326, mf16}, which has the desired property that the verifier only performs non-adaptive $X/Z$ measurement to the prover's quantum message.
+The fact that the verifier does not learn the measurement outcome in the testing round is not an issue here since the verifier can simply accept when the test is passed (at the cost of a constant soundness error).
+
+\paragraph{Overview of Our Construction.}
+As mentioned, our construction of CVQC protocol for $\SampBQP$ follows the blueprint of Mahadev's construction.
+Namely, we proceed in the following two steps: 1.
+construct a $\QPIP_1$ protocol for $\SampBQP$ with required special property, and 2.
+compile the $\QPIP_1$ protocol using $\PiMeasure$ to get the desired $\QPIP_0$ protocol.
+Both steps requires non-trivial works, but it turns out that the second step is the main technical challenge.
+At a high-level, the reason is the above-mentioned issue that the verifier does not learn the measurement outcome in the testing round.
+While this is not a problem for the case of decision problems (where the verifier only needs to decide to accept or reject), for the case of sampling problems, the verifier needs to produce an output sample when accepts, but there seems no way to produce the output for the verifier without learning the measurement outcome.
+%
+We discuss both steps in turn as follows.
+
+%As we shall see, both steps requires non-trivial works, and the second step is the main technical challenge.
+
+\emph{Construct a $\QPIP_1$ protocol for $\SampBQP$ with required special property}: Interestingly, while the notion of delegation for quantum sampling problem is not explicitly formalized in their work, Hayashi and Morimae~\cite{hayashi2015verifiable} constructed an one-round $\QPIP_1$ protocol that can delegate quantum sampling problem and achieve our notion of completeness and soundness\footnote{They did not prove our notion of soundness for their construction, but it is not hard to prove its soundness based on their analysis.}.
+Furthermore, their protocol has information-theoretic security and additionally achieve the blindness property.
+However, in their protocol, the computation is performed by the verifier using measurement-based quantum computation (MBQC)\footnote{In more detail, the prover of their protocol is required to send multiple copies of the graph states to the verifier (qubit by qubit).
+The verifier tests the received supposedly graph states using cut-and-choose and perform the computation using MBQC.}, and hence the verifier needs to perform adaptive measurement choices.
+Therefore, we cannot rely on their $\QPIP_1$ protocol for $\SampBQP$.
+
+Instead, we construct the desired $\QPIP_1$ protocol for $\SampBQP$ by generalizing the approach of local Hamiltonian reduction used in~\cite{PhysRevA.93.022326, mf16} to verify $\SampBQP$.
+Doing so requires the combination of several existing techniques from different context with some new ideas.
+For example, to handle $\SampBQP$, we need to prove lower bound on the spectral gap of the reduced local Hamiltonian instance, which is reminiscent to the simulation of quantum circuits by adiabatic quantum computation~\cite{adiabatic}.
+To achieve soundness, we introduce a cut-and-choose procedure and analyze it using de Finetti theorem in a  way similar to~\cite{takeuchi2018verification,hayashi2015verifiable}.
+See Section~\ref{sec:qpip1} for detailed discussions.
+
+\emph{$\diamond$ Compile the $\QPIP_1$ protocol using $\PiMeasure$}: We now discuss how to use Mahadev's measurement protocol to compile the above $\QPIP_1$ protocol for $\SampBQP$ to a $\QPIP_0$ protocol.
+As mentioned, a major issue we need to address in Mahadev's original construction is that when the verifier $V$ chooses to run a testing round, $V$ does not learn an output sample when it accepts.
+%(which happens with probability $1/2$),
+
+Specifically, let $\PiNaive$ be an ``intermediate'' $\QPIP_0$ protocol obtained by applying Mahadev's compilation to the above $\QPIP_1$ protocol.
+In such a protocol, when the verifier $V$ chooses to run the Hadamard round, it could learn a measurement outcome from the measurement protocol and be able to run the $\QPIP_1$ verifier to generate a decision and an output sample when accepts.
+However, when  $V$ chooses to run the testing round, it only decides to accept/reject without being able to output a sample.
+
+ A natural idea to fix the issue is to execute multiple copies of $\PiNaive$ in parallel\footnote{It is also reasonable to consider sequential repetition, but we consider parallel repetition for its advantage of preserving the round complexity.}, and to choose a random copy to run the Hadamard round to generate an output sample and use all the remaining copies to run the testing round.
+The verifier accepts only when all executions accept and outputs the sample from the Hadamard round.
+We call this protocol $\PiSampZ$.
+
+Clearly from the construction, the verifier now can output a sample when it decides to accept, and output a correct sample when interacting with an honest prover (completeness).
+The challenge is to show that $\PiSampZ$ is computationally sound.
+Note that now we are in the computational setting, we cannot use the quantum de Finetti theorem as above since it only holds in the information-theoretical setting\hannote{really?
+maybe emphasis on constructing adversary}.
+Furthermore, parallel repetition for computationally sound protocols are typically difficult to analyze, and known to not always work for protocols with four or more messages~\cite{BIN97,PW12}.
+
+% Fortunately, parallel repetition of Mahadev's protocol for $\BQP$ has been analyzed before in ~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19} with interestingly different proofs.
+Both works showed that $m$-fold parallel repetition reduces the soundness error to $2^{-m}$ for $\BQP$ by relying on special properties of Mahadev's protocol.
+
+ Parallel repetition of Mahadev's protocol for $\BQP$ has been analyzed before in ~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19}.
+However, the parallel repetitions of Mahadev's protocol for $\BQP$ and $\SampBQP$ is very different.
+For $\BQP$, the verifier simply chooses to run the Hadamard and testing rounds independently for each repetition.
+In contrast, our $\PiSampZ$ runs the Hadamard round in one repetition and run the testing rounds in the rest.
+The reason is that in $\SampBQP$, as well as generically in sampling problems, there is no known approach to combine two samples learned from two Hadamard-round executions to generate one sample with much better parameters, i.e., there is no generic error reduction method for the sampling problem.
+In contrast, the error reduction for decision problems can be done with the majority vote. 
+As a result, while the soundness error decreases exponentially for $\BQP$, as we see below (and also in the above $\QPIP_1$ protocols), for $\SampBQP$, $m$-fold repetition only decreases the error to $\poly(1/m)$.
+
+%Intuitively, Mahadev's protocol has the property that if a malicious prover $P^*$ knows the answer to pass the testing round, then it must be ``committed'' to a state $\rho$ in the sense that the verifier $V$ learns the $X/Z$ measurement outcome of $\rho$ in the Hadamard round (in a computational sense).
+Thus, the soundness of the underlying $\QPIP_1$ protocol ensures that $V$ learns a correct sample when it accepts.
+In short, when $P^*$ knows the testing round answer,  $P^*$ cannot ``cheat'' in the Hadamard round.
+
+%\hannote{copy ch 5 here?}
+To analyze the soundness of $\PiSampZ$, we use the \emph{partition lemma} developed in~\cite{arXiv:ChiaChungYam19} to analyze the prover's behavior while executing copies of $\PiMeasure$.
+Intuitively, the partition lemma says that for any cheating prover and for each copy $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
+$G_{0,i}$ and $G_{1,i}$ splits up the prover's residual internal state after sending back his first message.
+$G_{0,i}$ intuitively represents the subspace where the prover does not knows the answer to the testing round on the $i$-th copy, while $G_{1,i}$ represents the subspace where the prover does.
+Note that the prover is using a single internal space for all copies, and every $G_{0,i}$ and every $G_{1,i}$ is acting on this single internal space.
+By using this partition lemma iteratively, we can decompose the prover's internal state $\ket{\psi}$ into sum of subnormalized states.
+First we apply it to the first copy, writing $\ket{\psi}=G_{0,1}\ket{\psi}+G_{1,1}\ket{\psi} \equiv \ket{\psi_0}+\ket{\psi_1}$.
+The component $\ket{\psi_0}$ would then get rejected as long as the first copy is chosen as a testing round,
+which occurs with pretty high probability.
+More precisely, the output corresponding to $\ket{\psi_0}$ is $1/m$-close to the ideal distribution that just rejects all the time.
+On the other hand, $\ket{\psi_1}$ is now binding on the first copy;
+we now similarly apply the partition lemma of the second copy to $\ket{\psi_1}$.
+We write $\ket{\psi_1}=G_{0,2}\ket{\psi_1}+G_{1,2}\ket{\psi_1}\equiv \ket{\psi_{10}}+\ket{\psi_{11}}$, and apply the same argument about $\ket{\psi_{10}}$ and $\ket{\psi_{11}}$.
+We then continue to decompose $\ket{\psi_{11}}=\ket{\psi_{110}}+\ket{\psi_{111}}$ and so on, until we reach the last copy and obtain $\ket{\psi_{1^m}}$.
+Intuitively, all the $\ket{\psi_{1\dots10}}$ terms will be rejected with high probability, while the $\ket{\psi_{1^m}}$ term represents the ``good" component where the prover knows the answer to every testing round and therefore has high accept probability.
+Therefore, $\ket{\psi_{1^m}}$ also satisfies some binding property,
+so the verifier should obtain a measurement result of some state on the Hadamard round copy,
+and the analysis from the $\QPIP_1$ protocol $\PiSamp$ follows.
+
+However, the intuition that $\ket{\psi_{1^m}}$ is binding to every Hadamard round is incorrect.
+As $G_{1,i}$ does not commute with $G_{1,j}$, $\ket{\psi_{1^m}}$ is unfortunately only binding for the $m$-th copy.
+To solve this problem, we start with a pointwise argument and fix the Hadamard round on the $i$-th copy where $\ket{\psi_{1^i}}$ is binding,
+and show that the corresponding output is $O(\norm{\ket{\psi_{1^{i-1}0}}})$-close to ideal.
+We can later average out this error over the different choices of $i$, since not all $\norm{\ket{\psi_{1^{i-1}0}}}$ can be large at the same time.
+Another way to see this issue is to notice that we are partitioning a quantum state, not probability events, so there are some inconsistencies between our intuition and calculation.
+Indeed, the error we get in the end is $O(\sqrt{1/m})$ instead of the $O(1/m)$ we expected.
+
+% ~\cite{arXiv:ChiaChungYam19}  introduces a \emph{partition lemma}, which roughly says that there is an efficient projection that partitions the prover's internal quantum space into a ``known-answer'' subspace $S_1$ where $P^*$ knows the answer to the testing round, and a ``not-known-answer'' subspace $S_0$ where $P^*$ does not know the answer to the testing round.
+For an (efficient) prover's states $\ket{\psi} \in S_1$, the verifier $V$ can produce a sound output in the Hadamard round.
+For (efficient) prover's states $\ket{\psi} \in S_0$, the verifier $V$ rejects in the testing round with high probability.
+The work of \cite{arXiv:ChiaChungYam19} used this partition lemma iteratively to each instance of the repetition to show that for a no instance $x$ for any (efficient) prover's state $\ket{\psi}$, the probability that $V$ accepts is at most roughly $2^{-m}$.
+
+% We apply the partition lemma iteratively to the prover's state  similarly to~\cite{arXiv:ChiaChungYam19}, but with significant differences to show the soundness of $\PiSampZ$ for $\SampBQP$.
+In particular, extra care is required to reason about the computational indistinguishability of the verifier's output sample from the correct distribution $D_x$.
+To gain some intuition, let us apply the partition lemma to the prover's state $\ket{\psi}$ with respect to the first coordinate, which decompose $\ket{\psi} = \ket{\psi_0} + \ket{\psi_1}$ with $\ket{\psi_0} \in S_0$ and  $\ket{\psi_1} \in S_1$, respectively.
+Intuitively, the $\ket{\psi_0}$ component will be rejected whenever the first coordinate runs the testing round, but the verifier may be ``cheated'' to accepted incorrectly when the first coordinate runs the Hadamard round, which happens with probability $1/m$ and is where the error come from.
+For the $\ket{\psi_1}$ component, $V$ will produce a sound output if it runs the Hadamard round at the first coordinate.
+For the case that $V$ chooses to run the testing round at the first coordinate, we can analyze it by further applying the partition lemma to $\ket{\psi_1}$ with respect to the second coordinate, and repeat the analysis, and so on.
+% %
+The intuitive analysis outlined above grosses over many technical details, and we substantiate this outline with full details in 
+Section~\ref{sec:qpip0_all}.
+
+%\hannote{put this somewhere else?}
+%It is worthwhile mentioning that we came to notice some online discussion\footnote{\url{https://www.scottaaronson.com/blog/?p=3697}, e.g., comment \#25, \#26, \#42, \#48.
+} on the possibility of a CVQC protocol for $\SampBQP$ after we developed our own result.
+These comments suggested a possible reduction of $\SampBQP$ to the local Hamiltonian problem following a similar high-level idea as our solution, however, with no detail and a seemingly different technical route.
+More importantly, the issue that the verifier does not generate outputs in the testing round seems to be overlooked and not discussed there.
+
+%A natural attempt to construct a CVQC protocol for $\SampBQP$ is to directly apply Mahadev's CVQC protocol for $\SampBQP$~\cite{FOCS:Mahadev18a}.
+However, the requirement that the verifier needs to get a sample whenever accepting is not easily fulfilled by Mahadev's protocol.
+Before we explain this issue in details, let us go through a brief review of the construction and notations of Mahadev's protocol.
+%\hannote{something more nature} \hannote{explain mahadev protocol} \hannote{explain how to direct apply} \hannote{qpip1}
+% Let us revisit Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} first for some technical background. 
+%Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$
+
+%Following~\cite{FOCS:Mahadev18a}, we define $\QPIP_{\tau}$ as classes of interactive proof systems between an (almost) classical verifier and a quantum prover, where the classical verifier has limited quantum computational capability, formalized as possessing $\tau$-qubit quantum memory\footnote{Intuitively, the size of local quantum memory limits the size of qubits that a general (entangled) quantum operation can be operated on at the same time.
+However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the prover and discard some local qubits in the case of overflow.}.
+%A formal definition is given in Section~\ref{sec:qpip_def}. 
+%It is known that a solution to a $\BQP$-problem can be efficiently verified by a classical verifier who can perform a single qubit $X$ or $Z$ measurement~\cite{PhysRevA.93.022326, mf16}, by reducing any $\BQP$ problem to a local Hamiltonian problem where each term consists of  $X$ and $Z$ only.
+This leads to a $\QPIP_1$ protocol for $\BQP$.
+%The main contribution of Mahadev~\cite{FOCS:Mahadev18a} is a compiler from a $\QPIP_1$ protocol with $X$ or $Z$ measurements to a $\QPIP_0$ protocol.
+% ====
+% In this section, we create a delegation protocol for $\SampBQP$ with fully classical clients by adapting the approach taken in \cite{FOCS:Mahadev18a}.  
+%The center piece of Mahadev's compiler is the protocol $\PiMeasure$ (See \Cref{proto:urmila4}) that allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a $X$ or $Z$ measurement to measure on.
+% Composing it with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
+%$\PiMeasure$ is a 4-round protocol between a verifier  and a prover.
+%The verifier start by secretly choosing a string $h$ specifying the $X$ or $Z$ measurements it wants to make on each qubit, and generates keys $pk, sk$ from $h$.
+The first round of communication is the verifier sending $pk$ to the prover.
+The prover ``commits" to a state $\rho$ of its choice using $pk$, and the second round of communication is the prover replying with its commitment $y$.
+%The verifier must then choose between two options: a \emph{testing round} or a \emph{Hadamard round}.
+%If the verifier chose the testing round, it can catch cheating provers at the end of the protocol, 
+%and if the verifier chose the Hadamard round, it receives desired $XZ$-measurement outcomes at the end of the protocol.
+%The third round of communication is the verifier sending his 1-bit choice of testing or Hadamard round to the prover.
+Finally, in the fourth round of the communication, the prover replies accord to the verifier's choice in the third round.
+After the last round of the communication, the verifier wrap up the protocol with some extra computation.
+If the testing round was chosen, the verifier checks the prover's fourh-round reply against the previous commitment, and rejects if he sees an inconsistency.
+If the Hadamard round was chosen, the verifier calculates $M_{XZ}(\rho, h)$, the $XZ$-measurement specified by $h$ on $\rho$, basing on the fourth-round reply.
+Using $\PiMeasure$ to delegate the $X$ or $Z$ measurement of the aforementioned $\QPIP_1$ protocol~\cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
+
+% In this work, we will compose $\PiMeasure$ with our $\QPIP_1$ protocol $\PiSamp$ (\Cref{ProtoQPIP1}) for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$.
+
+% A direct composition of $\PiSamp$ and $\PiMeasure$, however, results in a protocol $\PiNaive$ (\Cref{proto:qpip0_naive}) which does not provide reasonable completeness or accuracy guarantees.
+% This is due to $\PiMeasure$ itself having peculiar and weak guarantees:
+% the client doesn't always obtain measurement outcomes even if the server were honest.
+
+% When that happens under the $\BQP$ context, the verifier can simply accept the prover at the cost of some soundness error;
+% under our $\SampBQP$ context, however, we must run many copies of $\PiNaive$ in parallel so the verifier can generate its outputs from some copy.
+% We will spend the majority of this section analyzing the soundness of this parallel repetition.
+
+% \hannote{4 round?} As we described in blah, Mahadev's compiler is a 4-round protocol. 
+% However, the requirement that the verifier needs to get a sample whenever accepting exposes one drawback of Mahadev's protocol.
+
+% Note that Mahadev's protocol consists of the so-called testing round, where the prover's behavior is tested, and the Hadamard round, where measurement outcomes are generated. 
+% Mimicing Mahadev's construction of
+
+%With Mahadev's compiler from $\QPIP_1$ to $\QPIP_0$ for $\BQP$ in mind, a natural approach to construct a $\QPIP_0$ protocol for $\SampBQP$ is the follow step approach: 1.
+construct a $\QPIP_1$ protocol for $\SampBQP$ with $X$ or $Z$ measurements.
+2.
+compile the $\QPIP_1$ protocol with $\PiMeasure$ to get $\QPIP_0$ protocol.
+This indeed is the general outline we follow in this work.
+However, getting our result is not straightforward.
+While it is relatively straightforward to do the first step with techniques in the literature, a naive combination between the resulting $\QPIP_1$ protocol and $\PiMeasure$ does not give a $\QPIP_0$ protocols for $\SampBQP$ with reasonable \emph{completeness}.
+The reason is that while it is possible to generate desired output samples in the Hadamard round of $\PiMeasure$,
+%it is unclear how to generate such a sample when the protocol accepts in the testing round. 
+%Note that this difficulty originates from the nature of sampling problems.
+In a decision problem, the verifier can blindly choose to output accept even if he did not get the measurement details, potential sacrificing some soundness.
+In comparison, in a sampling problem, the verifier always needs to output a good sample.
+
+%\hannote{our solution}
+
+%\hannote{something quick on qpip1, can be put together with available techs. scott blog }
+
+%\hannote{japanese citations : \cite{takeuchi2018verification,hayashi2015verifiable}}
+
+\subsection{Blind CVQC Protocols} \label{subsection:blind}
+
+Another desirable property of CVQC protocols is  \emph{blindness}, which means that the prover does not learn any information about the private input for the delegated computation.\footnote{In literature, the definition of blindness may also require to additionally hide the computation.
+We note the two notions are equivalent from a feasibility point of view by a standard transformation (see Remark~\ref{} in Section~\ref{}\hannote{missing}).
+%The two notions are equivalent from a feasibility point of view by a standard transformation that takes the description of the computation as part of the input and delegate the computation of  universal quantum circuits.
+} In the relaxed setting where the verifier has a limited quantum capability, Hayashi and Morimae~\cite{hayashi2015verifiable} constructed a blind $\QPIP_1$ protocol for delegating quantum computation with information-theoretic security that also handles sampling problems.
+%
+However, for purely classical verifiers, blind CVQC protocols seem much more difficult to construct.
+This goal is recently achieved by the seminal work of Gheorghiu and Vidick~\cite{FOCS:GheVid19}, who constructed the first blind CVQC protocol for $\BQP$ by constructing a composable remote state preparation protocol and combining it with the verifiable blind quantum computation protocol of Fitzsimons and Kashefi~\cite{FK17}.
+However, their protocol has   polynomially many rounds  and requires a rather involved analysis.
+Before our work, it is an open question whether constant-round blind CVQC protocol for $\BQP$ is achievable.
+
+\paragraph{Our Contribution.} Somewhat surprisingly, we provide a simple yet powerful  
+\emph{generic}  compiler that transforms any CVQC protocol to a blind one while preserving completeness, soundness, as well as its round complexity. 
+Our compiler relies on quantum fully homomorphic encryption (QFHE) schemes with certain ``classical-friendly'' properties, which is satisfied by Mahadev's construction~\cite{mahadev_qfhe}.
+%building on top of quantum fully homomorphic encyprtion (QFHE). 
+%Precisely, we leverage QFHE (especially the one from~\cite{mahadev_qfhe}) to transform any CVQC protocol to \emph{a blind one with the same number of round communication, while preserving completeness and soundness properties}.
+%As a result, one can \emph{upgrade} every verifiable CVQC protocol with blindness almost for free with the help of QFHE.
+%
+%Conceptually, we take a very different approach from previous ones  (e.g.,~\cite{FK17} as well as failed attempts in~\cite{mahadev_2018}) which use the blindness as the start point and then work to extend it with verifiability.
+%
+%Instead, our strategy is to simulate a (verifiable) CVQC protocol under QFHE per each message.
+%To that end, we do require a special property of QFHE that the classical part of the ciphertext can be operated on separately from the quantum part, which is satisfied by the construction from~\cite{mahadev_qfhe}.
+%Our construction makes a modular use of QFHE and only requires a minor technicality in the analysis, which will be explained below. 
+%As a result, we obtain
+\begin{theorem}[informal]
+Assuming the QLWE assumption, there exists a protocol compiler that transforms any CVQC protocol $\Pi$ to a CVQC protocol $\Piblind$ that achieves blindness while preserves its round complexity, completeness, and soundness.
+\end{theorem}
+
+Applying our blindness compiler to the parallel repetition of Mahadev's protocol from~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19}, we obtain the first constant-round blind CVQC protocol for $\BQP$ with negligible completeness and soundness error, resolving the aforementioned open question.
+
+\begin{theorem}[informal]
+    Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
+\end{theorem}
+
+We can also apply our compier to our CVQC protocol for $\SampBQP$ to additionally achieve blindness.
+
+%As a simple corollary of combining both results above, we achieve a constant-round blind CVQC protocol for $\SampBQP$. 
+\begin{theorem}[informal]
+        Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all sampling problems in $\SampBQP$ with  computational soundness and negligible completeness error.
+\end{theorem}
+
+\paragraph{Techniques.} At a high-level, the idea is simple: we run the original protocol under a QFHE with the QFHE　key generated by the verifier.
+Intuitively, this allows the prover to compute his next message under encryption without learning verifier's message, and hence achieves blindness while preserving the properties of the original protocol.
+One subtlety with this approach is the fact that the verifier is classical while the QFHE cipher text could contain quantum data.
+In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm need to be classical when the underlying message is classical.
+Fortunately, such  ``classical-friendly'' property is satisfied by the construction of~\cite{mahadev_qfhe}.
+
+A more subtle issue is to preserve the soundness.
+In particular, compiled protocols with a single application of QFHE might (1) leak information about the circuit evaluated by the verifier through its outputted QFHE ciphertexts (i.e., no \emph{circuit privacy});
+or (2) fail to simulate original protocols upon receiving invalid ciphertexts from the prover.
+We address these issues by letting the verifier switch to a fresh new key for each round of the protocol. 
+Details are given in \Cref{sec:BlindBQP2}.
+%\XW{To KM: expand the above a bit more?}
+
+%\hannote{endddddddddddddddd}
+
+\iffalse
 
@@
 
-\vspace{2mm} \noindent \textbf{Open Questions.} Our main focus is on the feasibility of the desired functionality and properties, which nevertheless leaves room for the improvement of parameter dependence.
+\fi
+
+%\vspace{2mm} \noindent \textbf{Open Questions.} 
+%\KM{mention error issue}
+%Our main focus is on the feasibility of the desired functionality and properties, which nevertheless leaves room for the improvement of parameter dependence.
 Some of our parameter dependence inherits from previous works (e.g.~\cite{FOCS:Mahadev18a}), whereas some is due to our own construction where we didn't mean to identify the best possible parameter dependence.
@@
 
-\vspace{2mm} \noindent \textbf{Organization.} We provide preliminaries on technical background in Section~\ref{sec:prelim}. 
+%\vspace{2mm} \noindent \textbf{Organization.} \KM{check if its correct...} \KM{can use here to mention that preliminary is moved to appendix} 
+\paragraph{Organization}
+We provide preliminaries on technical background in Section~\ref{sec:prelim}. 
 Our simulation-based definition of CVQC for $\SampBQP$ is discussed in Section~\ref{sec:samp_definition}. 
-Our main technical contributions are explained in details in Section~\ref{sec:sampbqp} (a construction of $\QPIP_1$ protocol for $\SampBQP$), 
+Our main technical contributions are explained in Section~\ref{sec:sampbqp_short} (a construction of $\QPIP_1$ protocol for $\SampBQP$), 
 Section~\ref{sec:qpip0_all} (the construction of $\QPIP_0$ protocol for $\SampBQP$ based on the above $\QPIP_1$ protocol), 

### 2021-05-31 preliminaries.tex
Sync Overleaf updates with GitHub

@@
 
-\subsection{Quantum Prover Interactive Protocols (QPIP)} 
+\subsection{Quantum Prover Interactive Proof (QPIP)} 
 \label{sec:qpip_def}
@@
 When the client is fully classical (i.e., $\tau = 0$), this model specializes to the standard interactive protocols.
+
+\hannote{different from umila's}
 
@@
         $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
-        \item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
+        \item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large \\security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then \\$\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
     \end{itemize}
@@
 \begin{definition}
-    A quantum leveled homomorphic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
-    $\QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:
+    A quantum leveled homomorphic (public-key) encryption scheme $\QHE=(\QGen, \QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:
     \begin{itemize}
@@
             It must be the case that
-                $$\QDec(sk, \QEval(pk, f, c_1, \ldots, c_l))=f(\QDec(sk, c_1),\ldots,\QDec(sk, c_l))$$
+            \begin{align*}
+                \QDec&(sk, \QEval(pk, f, c_1, \ldots, c_l))
+                \\
+                &=f(\QDec(sk, c_1),\ldots,\QDec(sk, c_l))
+            \end{align*}
             with overwhelming probability in $\lambda$.

### 2021-05-31 qpip.tex
Sync Overleaf updates with GitHub

@@
 
-\begin{thm}
-    \label{QPIP1thm}
-	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}.}
-	%\XW{do we want precise error bound?}
-\end{thm}
-\begin{prf}
+% \begin{thm}
+%     \label{QPIP1thm}
+% 	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}.}
+% 	%\XW{do we want precise error bound?}
+% \end{thm}
+\begin{prf} [\Cref{QPIP1thm}]
 	For completeness, notice $y_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.

### 2021-05-31 qpip0.tex
Updates from Overleaf
Sync Overleaf updates with GitHub

@@
 	\begin{enumerate}
-		\item \label{step:measure1} The verifier generates a public and secret key pair $(pk, sk)\leftarrow\cVMeasure{1}(1^\lambda, h)$. It sends $pk$ to the prover.
+		\item \label{step:measure1} The verifier generates a public and secret key pair $(pk, sk)\leftarrow\cVMeasure{1}($ $1^\lambda, h)$. It sends $pk$ to the prover.
 		\item \label{step:measure2} The prover generates $(y, \sigma)\leftarrow\cPMeasure{2}(pk, \rho)$.
@@
 		\item \label{step:output} If it is a testing round ($c=0$), then the verifier generates and outputs $o\leftarrow\cVMeasure{T}(pk, y, a)$ where $o\in\set{\Acc, \Rej}$.
-			If it is a Hadamard round ($c=1$), then the verifier generates and outputs $v\leftarrow\cVMeasure{H}(sk, h, y, a)$.
+			If it is a Hadamard round ($c=1$), then the verifier generates and outputs $v\leftarrow\cVMeasure{H}($ $sk, h, y, a)$.
 	\end{enumerate}
@@
 Recall that in $\PiSamp$ the verifier takes $X$ and $Z$ measurements on the prover's message.
-In $\PiNaive$ we let the verifier use $\PiMeasure$ to learn those measurement outcomes instead.
+In $\PiNaive$ we let the verifier use $\PiMeasure$ to learn those measurement outcomes instead. \hannote{also need to be non-adaptive?}
 
@@
 \begin{proof}
-	We first introduce the \emph{dummy strategy} for ~\Cref{proto:urmila4}, where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
-	It is straightforward to verify that this prover would be accepted in the testing round with probability $1-\negl(\lambda)$,
-	but has negligible probability passing the verification  after the Hadamard round.
-
-   %for $\PiMeasure$ $\Pstarsub$ that is almost perfect as follows. 
-	Now we construct a cheating $\BQP$ prover for \Cref{proto:qpip0_naive}, $\Pstar$, that does the same thing as $\PNaiveStar$ except at Step~\ref{step:urmila-in-naive}, where the prover and verifier runs \Cref{proto:urmila4}.
-$\Pstar$ does the following in Step~\ref{step:urmila-in-naive}:
-	for the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
-	If $y\ne\bot$, then reply $y$;
-	else, run the corresponding step of the dummy strategy and reply with its results.
-	For the fourth message, if $y\ne\bot$, run and reply with $a\leftarrow\cPNaiveStar{4}(pk, c, \sigma)$;
-	else, continue the dummy strategy.
-
-%	so we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property (\Cref{lem:urmila-binding}).
-%That is, there exists some $\rho$ such that $v=M_{XZ}(\rho, h)$.\hannote{only comp}
-
-	 In the following we fix an $x$.
-Let the distribution on $h$ specified in Step~\ref{step:naive1} of the protocol be $p_x(h)$.
-Define $\Pstarsub(x)$ as $\Pstar$'s responds in Step~\ref{step:urmila-in-naive}.
-Note that we can view $\Pstarsub(x)$ as a prover strategy for \Cref{proto:urmila4}.
-By construction $\Pstarsub(x)$ passes testing round with overwhelming probability over $p_x(h)$, i.e.
-$\sum_h p_x(h) p_{h,T} =\negl(\lambda)$, where $p_{h,T}$ is $\Pstar$'s probability of getting accepted by the prover on the testing round on basis choice $h$.
-By \Cref{lem:urmila-binding} and Cauchy's inequality, there exists some $\rho$ such that  $\sum_h p_x(h) \norm{v_h -M_{XZ}(\rho, h)}_c = \negl(\lambda)$, where we use $\norm{A-B}_c=\alpha$ to denote that $A$ is $\alpha$-computational indistinguishable to $B$.
-Therefore $v= \sum_h p_x(h) v_h$ is computationally indistinguishable to $\sum_h p_x(h) M_{XZ}(\rho, h)$.
-Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}),
-	we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\epsilon}, x)$  is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.
-
-	Now we relate $(d', z')$ back to $(d, z)$.
-	First, conditioned on that $\PNaiveStar$ aborts, since dummy strategy will be rejected with overwhelming probability in Hadamard round,
-	we have $(d', z')$ is computationally indistinguishable to $(\Rej, \bot)=(d, z)$.
-	On the other hand, conditioned on $\PNaiveStar$ not aborting, clearly $(d, z)=(d', z')$.
-	So $(d, z)$ is computationally indistinguishable to $(d', z')$,
-	which in turn is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
-	Since $\norm{d-d'}_{tr}= O(\eps)$,
-	 $(d, z_{ideal})$ is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
-	Combining everything, we conclude that $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d, z_{ideal})$.
+    See \Cref{sec:qpip0_proof}. 
 \end{proof}
@@
 	\label{thm:zi-zgoodi}
-	$$\tr\abs{z_i-z_{good, i}}\leq\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R).$$
+	\begin{align*}
+	\tr\abs{z_i-z_{good, i}}\leq&\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]\\
+	&+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R).
+	\end{align*}
 \end{lemma}
 \begin{proof}
-	We take expectation of \Cref{eq:partition-string} over $\gamma$
-	$$\ket{\psi}=\E_{\gamma}\left[
-		\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-	\right],$$
-	and expand $z_i$ from \Cref{eq:zi-def} as
-	\begin{align}
-		z_i=& z_{good,i}+ \E_{pk, y, \gamma} \sum_z \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
-		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \nn \\
-		+&  \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-		+\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-		\nn \\
-		+&  \bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-		+\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
-		\nn \\
-		+&\L.
-\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] \proj{z} , \nn
-		%=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err )
-	\end{align}
-	where we omitted writing out $e_i$.
-	Therefore we have
-	\begin{align*}
-		\tr|z_i-z_{good,i}|\leq& \E_{pk, y, \gamma} \sum_z \L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|+
-		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R. \\
-		+& 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R|    
-		+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \\
-		+&\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
-	\end{align*}
-	by the triangle inequality.
-	The last three error terms sum to $O\L(\frac{m^2}{\sqrt{T}}\R)$ by \Cref{lem:samp-tech} and property~\ref{property:partition-err} of \Cref{lem:partition2}.
-	As for the first two terms, by \Cref{lem:samp-tech} and \Cref{lem:partition-testing}, we see that
-	\begin{align*}
-		\sum_z \sum_{k=0}^{i-1}\sum_{j=0}^{i-1}
-		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}}} \\
-		&\leq\sum_z \abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^{i-1}0,\gamma}}} + O\L(m^2(m-1)\gamma_0\R) \\
-		&\leq\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2 + O\L(m^2(m-1)\gamma_0\R)
-	\end{align*}
-	and similarly
-	\begin{align*}
-		\sum_z\sum_{k=0}^{i-1}
-		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}\\
-		&\leq\sum_z\abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R)\\
-		&\leq\norm{\ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R).
-	\end{align*}
+    See \Cref{sec:qpip0}.
 \end{proof}
@@
 \end{lemma}
-\begin{proof}
+\begin{proof}[\Cref{thm:zgood-zideal}]
 	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for $\PiSampZ$, consider the following composite strategy, $\Picomp{i}$, as a prover for $\PiNaive$.
@@
 		\leq&  \frac{1}{m}\sum_i\tr| (z_i-z_{good,i})| \nn \\
-		\leq&  \frac{1}{m}\sum_i\L[\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
+		\leq&  \frac{1}{m}\sum_i\L[\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R] \R.\nn \\
+		&+ \L. O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
 		\leq&  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%

### 2021-05-31 qpip0_proofs.tex
Sync Overleaf updates with GitHub

\section{Proofs for \Cref{sec:qpip0_all}}
\label{sec:qpip0_proof}

% \begin{theorem}[binding property of $\PiNaive$]
% 	\label{lem:naive-qpip0-binding}
% 	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
% 	Suppose that $\Prob{d=\Acc\mid y\ne\bot, c=0}$ is overwhelming, 
% 	under the QLWE assumption, then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
% \end{theorem}
\begin{proof}[\Cref{lem:naive-qpip0-binding}]
	We first introduce the \emph{dummy strategy} for ~\Cref{proto:urmila4}, where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
	It is straightforward to verify that this prover would be accepted in the testing round with probability $1-\negl(\lambda)$,
	but has negligible probability passing the verification  after the Hadamard round.

   %for $\PiMeasure$ $\Pstarsub$ that is almost perfect as follows. 
	Now we construct a cheating $\BQP$ prover for \Cref{proto:qpip0_naive}, $\Pstar$, that does the same thing as $\PNaiveStar$ except at Step~\ref{step:urmila-in-naive}, where the prover and verifier runs \Cref{proto:urmila4}. $\Pstar$ does the following in Step~\ref{step:urmila-in-naive}:
	for the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
	If $y\ne\bot$, then reply $y$;
	else, run the corresponding step of the dummy strategy and reply with its results.
	For the fourth message, if $y\ne\bot$, run and reply with $a\leftarrow\cPNaiveStar{4}(pk, c, \sigma)$;
	else, continue the dummy strategy.

%	so we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property (\Cref{lem:urmila-binding}).
%That is, there exists some $\rho$ such that $v=M_{XZ}(\rho, h)$.\hannote{only comp}

	 In the following we fix an $x$. Let the distribution on $h$ specified in Step~\ref{step:naive1} of the protocol be $p_x(h)$. Define $\Pstarsub(x)$ as $\Pstar$'s responds in Step~\ref{step:urmila-in-naive}. Note that we can view $\Pstarsub(x)$ as a prover strategy for \Cref{proto:urmila4}. By construction $\Pstarsub(x)$ passes testing round with overwhelming probability over $p_x(h)$, i.e. $\sum_h p_x(h) p_{h,T} =\negl(\lambda)$, where $p_{h,T}$ is $\Pstar$'s probability of getting accepted by the prover on the testing round on basis choice $h$. By \Cref{lem:urmila-binding} and Cauchy's inequality, there exists some $\rho$ such that  $\sum_h p_x(h) \norm{v_h -M_{XZ}(\rho, h)}_c = \negl(\lambda)$, where we use $\norm{A-B}_c=\alpha$ to denote that $A$ is $\alpha$-computational indistinguishable to $B$. Therefore $v= \sum_h p_x(h) v_h$ is computationally indistinguishable to $\sum_h p_x(h) M_{XZ}(\rho, h)$. Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}), 
	we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\epsilon}, x)$  is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.

	Now we relate $(d', z')$ back to $(d, z)$.
	First, conditioned on that $\PNaiveStar$ aborts, since dummy strategy will be rejected with overwhelming probability in Hadamard round,
	we have $(d', z')$ is computationally indistinguishable to $(\Rej, \bot)=(d, z)$.
	On the other hand, conditioned on $\PNaiveStar$ not aborting, clearly $(d, z)=(d', z')$.
	So $(d, z)$ is computationally indistinguishable to $(d', z')$,
	which in turn is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
	Since $\norm{d-d'}_{tr}= O(\eps)$,
	 $(d, z_{ideal})$ is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
	Combining everything, we conclude that $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d, z_{ideal})$.
\end{proof}

\begin{proof}[\Cref{thm:zi-zgoodi}]
	We take expectation of \Cref{eq:partition-string} over $\gamma$
	$$\ket{\psi}=\E_{\gamma}\left[
		\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
	\right],$$
	and expand $z_i$ from \Cref{eq:zi-def} as
	\begin{align}
		z_i &= z_{good,i}+ \E_{pk, y, \gamma} \sum_z \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} \R. \nn \\
		&+
		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
		&+\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
		\nn \\
		&+ \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} + \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}
		\nn \\
		&\L.    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] \proj{z} , \nn     
		%=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err )
	\end{align}
	where we omitted writing out $e_i$.
	Therefore we have
	\begin{align*}
		\tr|z_i-z_{good,i}|\leq \E_{pk, y, \gamma} \sum_z &\L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|\R.\\
		&+
		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R| \\
		&+ 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R| \\   
		&+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \\
		&+\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
	\end{align*}
	by the triangle inequality.
	The last three error terms sum to $O\L(\frac{m^2}{\sqrt{T}}\R)$ by \Cref{lem:samp-tech} and property~\ref{property:partition-err} of \Cref{lem:partition2}.
	As for the first two terms, by \Cref{lem:samp-tech} and \Cref{lem:partition-testing}, we see that
	\begin{align*}
		\sum_z \sum_{k=0}^{i-1}\sum_{j=0}^{i-1}
		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}}} \\
		&\leq\sum_z \abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^{i-1}0,\gamma}}} + O\L(m^2(m-1)\gamma_0\R) \\
		&\leq\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2 + O\L(m^2(m-1)\gamma_0\R)
	\end{align*}
	and similarly
	\begin{align*}
		\sum_z\sum_{k=0}^{i-1}
		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}\\
		&\leq\sum_z\abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R)\\
		&\leq\norm{\ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R).
	\end{align*}
\end{proof}

### 2021-05-31 blind.tex
Sync Overleaf changes
Sync to GitHub for 1st submission

@@
 
-%Our compiler is a straightforward way of achieving blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
-%In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19},
-%as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.
-
-\Ethan{``preserves soundness" needs just a bit more discussion, since all we've proven are two experiments being identical.}
-
 \begin{thm}
-    Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
+    Assuming the QLWE assumption, \Ethan{wording sounds awkward?
+Maybe ``under the QLWE assumption"...?} there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
 \end{thm}
@@
         Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
-        %There exists a computationally sound, blind, and constant-round $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness errors under the QLWE assumption.
 \end{thm}

### 2021-05-31 introduction.tex
Sync to GitHub for 1st submission

@@
 \end{theorem}
+
+\Ethan{Related QIP review below:
+
+A potential problem I see is that the main theorem (Theorem 1.1) in the paper gives a protocol that achieves only computational soundness.
+Roughly speaking, this means that the protocol can only be used to verify that the ideal distribution is close to some distribution which in turn is computationally indistinguishable from the ideal quantum distribution.
+This guarantee seems not to be enough for any currently established (or conjectured!) hardness argument in quantum supremacy.
+The problem is essentially that quantum hardness of sampling arguments are fundamentally only (potentially) robust to statistical distance and not computational indistinguishability.
+For example, it would be fully compatible with everything we know (and even quite expected) if the output distribution of random quantum circuits are, with high probability over the choice of random circuit, *computationally indistinguishable* from the uniform distribution.
+But clearly the uniform distribution is n!
+ ot hard to sample from.
+
+Said in another way: what is being shown here is the following: consider a new class sampBQP', where the complete problem is to sample from something BQP-indistinguishable from the output distribution of a quantum circuit.
+Here it is shown that this new class sampBQP' can be interactively verified.
+Unfortunately, we don’t know or have evidence that, for example $\SampBQP’ = \SampBPP \implies$ PH collapse, like we do for the standard sampBQP class.
+
+Notably, discussion of this issue is missing entirely from the writeup!
+In conclusion, while I found this paper to be an interesting followup to the Mahadev result, I find that the quantum supremacy motivation, which would a priori have been quite strong, is not obviously correct.}
 

### 2021-05-31 qpip0.tex
Sync to GitHub for 1st submission

@@
 
-Also a careful reader might have noticed that the prover's space don't always decompose cleanly into parts that the verifier either rejects or accepts with high probability, as there might be some states that a accepted with mediocre probability.
+Also a careful reader might have noticed that the prover's space don't always decompose cleanly into parts that the verifier either rejects or accepts with high probability, as there might be some states that is accepted with mediocre probability.
 In \cite{arXiv:ChiaChungYam19}, this is solved by splitting the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$ and applying amplitude amplification to boost the accept probability if it is bigger than $\gamma$.
@@
 it clearly follows that 
-\begin{claim}
+\begin{cor}
 	\label{lem:partition-testing}
@@
 	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
-\end{claim}
+\end{cor}
 
@@
     See \Cref{sec:qpip0}.
+    \Ethan{Double check this ref? This feels off.}
 \end{proof}

### 2021-06-02 introduction.tex
Sync with GitHub

--- 2021-05-31 introduction.tex
@@
 Recently, the problem is resolved by a breakthrough result of Mahadev~\cite{FOCS:Mahadev18a}, who constructed the first Classical Verification of Quantum Computation (CVQC) protocol for $\BQP$, where an efficient classical ($\BPP$) verifier can interact with an efficient quantum ($\BQP$) prover to verify any $\BQP$ language.
-Soundness of Mahadev's protocol  is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
+Soundness of Mahadev's protocol  is based on a widely recognized computational assumption that the learning with errors (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
 %In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of Classical Verification of Quantum Computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
@@
 \paragraph{Our Contribution.}
-As the first step to formalize CVQC for quantum sampling problems, we formalize efficiently computable quantum sampling problems with the complexity class $\SampBQP$ introduced by Aaronson~\cite{aaronson_2013}.
+As the first step to formalize CVQC for quantum sampling problems, we consider the complexity class $\SampBQP$ introduced by Aaronson~\cite{aaronson_2013} as a natural class to capture efficiently computable quantum sampling problems.
+%model
+%formalize efficiently computable quantum sampling problems with the complexity class $\SampBQP$ introduced by Aaronson~\cite{aaronson_2013}.
 %
 %Formally, 
-$\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine (See Section~\ref{sec:samp_definition} for the formal definition).
-We consider CVQC for a $\SampBQP$ problem $(D_x)_{x\in\zo^*}$ where a classical $\BPP$ verifier delegate the computation of a sample $z\leftarrow D_x$ for some input $x$ to a quantum $\BQP$ prover.
+$\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine with a desired inverse polynomial error (See Section~\ref{sec:samp_definition} for the formal definition).
+We consider CVQC for a $\SampBQP$ problem $(D_x)_{x\in\zo^*}$ where a classical $\BPP$ verifier delegates the computation of a sample $z\leftarrow D_x$ for some input $x$ to a quantum $\BQP$ prover.
 Completeness requires that when the prover is honest, the verifier should accept with high probability and learn a correct sample $z\leftarrow D_x$.
@@
 We formalize the soundness by a strong \emph{simulation-based} definition, (\Cref{dfn:stats-secure-proto-sampbqp}),
-where we require that the joint distribution $(d,z)$ of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from the desired distribution $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.\hannote{justify?}
+where we require that the joint distribution $(d,z)$ of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from the desired distribution $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.\footnote{This simulation-based formulation is analogous to the standard composable security definition for QKD.} \hannote{justify?}
 %
@@
 
-As our main result, we construct a constant-round CVQC protocol for $\SampBQP$, based on the quantum LWE (QLWE) assumption that the learning-with-error problem is hard for BQP machines. 
+As our main result, we construct a constant-round CVQC protocol for $\SampBQP$, based on the quantum LWE (QLWE) assumption that the learning-with-errors problem is hard for BQP machines. 
 \begin{theorem}[informal] \label{thm:qpip0-informal}
@@
 \end{theorem}
+
+\KM{mention the inverse poly error and add forward pointer for discussion}
 
@@
 
-At a high-level, the heart of Mahadev's protocol is a measurement protocol $\PiMeasure$ that can compile an one-round $\QPIP_1$ protocol with special properties to a $\QPIP_0$ protocol.
+At a high-level, the heart of Mahadev's protocol is a measurement protocol $\PiMeasure$ that can compile an one-round $\QPIP_1$ protocol (with special properties) to a $\QPIP_0$ protocol.
 Note that in a $\QPIP_1$ protocol, the verifier with one-qubit memory can only measure the prover's quantum message qubit by qubit.
@@
 Thus, if an (one-round) $\QPIP_1$ verifier only applies $X$ or $Z$ measurement to the prover's quantum message, we can use the measurement protocol $\PiMeasure$ to turn the $\QPIP_1$ protocol into a $\QPIP_0$ protocol in a natural way.
-However, one restriction here is that the verifier's measurement choices need to be determined at the beginning (i.e., cannot depend adaptively on the intermediate measurement outcome).
+One additional requirement here is that the verifier's measurement choices need to be determined at the beginning (i.e., cannot depend adaptively on the intermediate measurement outcome).
 
@@
 Informally, the testing round is used to ``test'' the commitment of $\rho$, and the Hadamard round is used to learn the measurement outcome.
-(See \Cref{proto:urmila4} for further details about the measurement protocol $\PiMeasure$.) Another limitation here is that in the testing round, the verifier may accept the test of the commitment without learning any measurement result.
+(See \Cref{proto:urmila4} for further details about the measurement protocol $\PiMeasure$.) Another limitation here is that in the testing round, the verifier only ``test'' the commitment without learning any measurement result.
 
-In~\cite{FOCS:Mahadev18a}, Mahadev's CVQC protocol for $\BQP$ is constructed by applying her measurement protocol to the one-round $\QPIP_1$ protocol of~\cite{PhysRevA.93.022326, mf16}, which has the desired property that the verifier only performs non-adaptive $X/Z$ measurement to the prover's quantum message.
+In~\cite{FOCS:Mahadev18a}, Mahadev's CVQC protocol for $\BQP$ is constructed by applying her measurement protocol to the one-round $\QPIP_1$ protocol of~\cite{PhysRevA.93.022326, mf16}, which has the desired properties that the verifier only performs non-adaptive $X/Z$ measurement to the prover's quantum message.
 The fact that the verifier does not learn the measurement outcome in the testing round is not an issue here since the verifier can simply accept when the test is passed (at the cost of a constant soundness error).
@@
 \paragraph{Overview of Our Construction.}
-As mentioned, our construction of CVQC protocol for $\SampBQP$ follows the blueprint of Mahadev's construction.
-Namely, we proceed in the following two steps: 1.
+%As mentioned, our construction of CVQC protocol for $\SampBQP$ 
+Following the blueprint of Mahadev's construction, our construction proceeds in the following two steps: 1.
 construct a $\QPIP_1$ protocol for $\SampBQP$ with required special property, and 2.
 compile the $\QPIP_1$ protocol using $\PiMeasure$ to get the desired $\QPIP_0$ protocol.
-Both steps requires non-trivial works, but it turns out that the second step is the main technical challenge.
+The first step can be done by combining existing techniques from different contexts, whereas the second step is the main technical challenge.
+%Both steps requires non-trivial works, but it turns out that the second step is the main technical challenge. 
 At a high-level, the reason is the above-mentioned issue that the verifier does not learn the measurement outcome in the testing round.
-While this is not a problem for the case of decision problems (where the verifier only needs to decide to accept or reject), for the case of sampling problems, the verifier needs to produce an output sample when accepts, but there seems no way to produce the output for the verifier without learning the measurement outcome.
+While this is not a problem for decision problems, %(where the verifier only needs to decide to accept or reject),
+for sampling problems, the verifier needs to produce an output sample when accepts, but there seems no way to produce the output for the verifier without learning the measurement outcome.   
 %
@@
 
-\emph{Construct a $\QPIP_1$ protocol for $\SampBQP$ with required special property}: Interestingly, while the notion of delegation for quantum sampling problem is not explicitly formalized in their work, Hayashi and Morimae~\cite{hayashi2015verifiable} constructed an one-round $\QPIP_1$ protocol that can delegate quantum sampling problem and achieve our notion of completeness and soundness\footnote{They did not prove our notion of soundness for their construction, but it is not hard to prove its soundness based on their analysis.}.
+\emph{$\diamond$ Construct a $\QPIP_1$ protocol for $\SampBQP$ with required special property}: Interestingly, while the notion of delegation for quantum sampling problem is not explicitly formalized in their work, Hayashi and Morimae~\cite{hayashi2015verifiable} constructed an one-round $\QPIP_1$ protocol that can delegate quantum sampling problem and achieve our notion of completeness and soundness\footnote{They did not prove our notion of soundness for their construction, but it is not hard to prove its soundness based on their analysis.}.
 Furthermore, their protocol has information-theoretic security and additionally achieve the blindness property.
@@
 For example, to handle $\SampBQP$, we need to prove lower bound on the spectral gap of the reduced local Hamiltonian instance, which is reminiscent to the simulation of quantum circuits by adiabatic quantum computation~\cite{adiabatic}.
-To achieve soundness, we introduce a cut-and-choose procedure and analyze it using de Finetti theorem in a  way similar to~\cite{takeuchi2018verification,hayashi2015verifiable}.
+To achieve soundness, we use cut-and-choose and analyze it using de Finetti theorem in a  way similar to~\cite{takeuchi2018verification,hayashi2015verifiable}.
 See Section~\ref{sec:qpip1} for detailed discussions.
@@
 maybe emphasis on constructing adversary}.
-Furthermore, parallel repetition for computationally sound protocols are typically difficult to analyze, and known to not always work for protocols with four or more messages~\cite{BIN97,PW12}.
+Furthermore, parallel repetition for computationally sound protocols are typically difficult to analyze, and known to not always work for protocols with four or more messages even in the classical setting~\cite{BIN97,PW12}.
 
@@
 
- Parallel repetition of Mahadev's protocol for $\BQP$ has been analyzed before in ~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19}.
-However, the parallel repetitions of Mahadev's protocol for $\BQP$ and $\SampBQP$ is very different.
+ Parallel repetition of Mahadev's protocol for $\BQP$ has been analyzed before in ~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19}. However, the situation here is different. 
+ %the parallel repetitions of Mahadev's protocol for $\BQP$ and $\SampBQP$ is very different. 
  For $\BQP$, the verifier simply chooses to run the Hadamard and testing rounds independently for each repetition.
 In contrast, our $\PiSampZ$ runs the Hadamard round in one repetition and run the testing rounds in the rest.
-The reason is that in $\SampBQP$, as well as generically in sampling problems, there is no known approach to combine two samples learned from two Hadamard-round executions to generate one sample with much better parameters, i.e., there is no generic error reduction method for the sampling problem.
+The reason is that in $\SampBQP$, as well as generically in sampling problems, there is no known approach to combine multiple samples to generate one sample with reduced error, i.e., there is no generic error reduction method for the sampling problem.
 In contrast, the error reduction for decision problems can be done with the majority vote. 
@@
 so the verifier should obtain a measurement result of some state on the Hadamard round copy,
-and the analysis from the $\QPIP_1$ protocol $\PiSamp$ follows.
+and the soundness of the $\QPIP_1$ protocol $\PiSamp$ follows.
 
@@
 \emph{generic}  compiler that transforms any CVQC protocol to a blind one while preserving completeness, soundness, as well as its round complexity. 
-Our compiler relies on quantum fully homomorphic encryption (QFHE) schemes with certain ``classical-friendly'' properties, which is satisfied by Mahadev's construction~\cite{mahadev_qfhe}.
+Our compiler relies on quantum fully homomorphic encryption (QFHE) schemes with certain ``classical-friendly'' properties, which is satisfied by both constructions of Mahadev~\cite{mahadev_qfhe} and Brakerski~\cite{??}.
+
+%Mahadev's construction~\cite{mahadev_qfhe}.
 %building on top of quantum fully homomorphic encyprtion (QFHE). 
@@
 \begin{theorem}[informal]
-Assuming the QLWE assumption, there exists a protocol compiler that transforms any CVQC protocol $\Pi$ to a CVQC protocol $\Piblind$ that achieves blindness while preserves its round complexity, completeness, and soundness.
+Assuming the QLWE assumption\footnote{By using Brakerski's QFHE, we only need to rely on the QLWE assumption with polynomial modulus in thsi theorem.}, there exists a protocol compiler that transforms any CVQC protocol $\Pi$ to a CVQC protocol $\Piblind$ that achieves blindness while preserves its round complexity, completeness, and soundness.
 \end{theorem}
@@
 In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm need to be classical when the underlying message is classical.
-Fortunately, such  ``classical-friendly'' property is satisfied by the construction of~\cite{mahadev_qfhe}.
+Fortunately, such  ``classical-friendly'' property is satisfied by the construction of~\cite{mahadev_qfhe,??}.
 
@@
 %\XW{To KM: expand the above a bit more?}
+
+\paragraph{On the Inverse Polynomial Error in $\SampBQP$.} To be added. \KM{where to add this? Sec 1.3?}
 

### 2021-06-02 model.tex
Sync Overleaf updates with GitHub
Sync with GitHub

@@
 
-Note that in the above definition, there is an accuracy parameter $\eps$ and the quantum sampling algorithm only requires to output a sample that is $\eps$-close to the correct distribution in time $\poly(n,1/\eps)$, instead of the stringent requirement of outputting a perfect sample.
-There are multiple reasons for allowing an inverse polynomial error.
+Note that in the above definition, there is an accuracy parameter $\eps$ and the quantum sampling algorithm only requires to output a sample that is $\eps$-close to the correct distribution in time $\poly(n,1/\eps)$, instead of requiring a perfect or negligibly close sample.
+\cite{aaronson_2013, Boson} discussed multiple reasons for allowing the inverse polynomial error, such as conceivable physical realizations of quantum computer may consist of inherent noise.
+%There are multiple reasons for allowing an inverse polynomial error.
 For example, conceivable physical realizations of quantum computer may consist of inherent noise.
 We refer the readers to~\cite{aaronson_2013, Boson} for the discussion therein on why this better captures the sampling problem solvable by realistic quantum computers.
+However, we note that it is also meaningful to require an exponentially small error instead of an inverse polynomial one. %We follow the definition of~\cite{aaronson_2013}, but note that
 
@@
 Proving the soundness of these constructions for delegating $\SampBQP$ is an interesting open question.
+%We also note that

### 2021-06-02 paper.tex
Change to LNCS format again
Sync Overleaf updates with GitHub
Change format for FOCS submission
Use 11 point fonts
Toggle Han-Hsuan's notes visibility with draft mode
Sync with GitHub

@@
 \documentclass[11pt]{article}
+\pagestyle{plain}
 \usepackage{authblk}
-%\pagestyle{plain}
 
@@
 \newcommand{\XW}[1]{{\footnotesize\color{red}[XW: #1]}}
+\newcommand{\hannote}[1]{\textcolor{blue}{\small {\textbf{(Han:} #1\textbf{) }}}}
+\newcommand{\Knote}[1]{\textcolor{red}{\small {\textbf{(KM:} #1\textbf{) }}}}
 \else
@@
 \newcommand{\XW}[1]{}
+\newcommand{\hannote}[1]{}
+\newcommand{\Knote}[1]{}
 \fi
@@
 
-%\iffalse
 \author[1]{Kai-Min Chung\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}.
@@
 MOST 108-2627-E-002-001.}}
-\author[2]{Yi Lee\thanks{\href{mailto:ethanlee515@gmail.com}{ethanlee515@gmail.com}. This work was done in part while the author was affiliated to National Taiwan University.}}
+\author[2]{Yi Lee\thanks{\href{mailto:ylee1228@umd.edu}{ylee1228@umd.edu}. This work was done while affiliated to Academia Sinica and to National Taiwan University.}}
 \author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}.
@@
 \author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER).}}
-\affil[1, 2]{Institute of Information Science, Academia Sinica, Taiwan}
+\affil[1]{Institute of Information Science, Academia Sinica, Taiwan}
+\affil[2]{Department of Computer Science, University of Maryland, USA}
 \affil[3]{Department of Computer Science, National Tsing Hua University, Taiwan}
@@
 }
-%\fi
-%\author{}
-%\institute{}
 
@@
 More precisely, in a CVQC protocol for a $\SampBQP$ problem, the prover and the verifier are given an input $x\in \zo^n$ and a quantum circuit $C$, and the goal of the classical client is to learn a sample from the output $z \leftarrow C(x)$ up to a small error, from its interaction with an untrusted prover.
-We demonstrate its feasibility by constructing a four-message CVQC protocol for $\SampBQP$ based on the quantum \emph{Learning With Error} assumption.
+We demonstrate its feasibility by constructing a four-message CVQC protocol for $\SampBQP$ based on the quantum \emph{Learning With Errors} assumption.
 
@@
 
-\input{preliminaries}
+%\input{preliminaries}
 
@@
 
-\input{hamiltonian}
+\input{hamiltonian_short}
 
@@
 
+\input{supplementary}
+
 \end{document}

### 2021-06-02 preliminaries.tex
Sync with GitHub

@@
         $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
-        \item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large \\security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then \\$\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
+        \item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large \\security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then \\$\Pr\left[(P, V)(x, 1^\lambda)=\Acc\right]<s(\lambda)$.
     \end{itemize}

### 2021-06-02 acknowledgements.tex
Add acknowledgements section

\section{Acknowledgments}

\Ethan{TODO Acknowledge Morimae}

\Ethan{TODO Acknowledge STOC Reviewer for bringing up Brakerski's QFHE}

### 2021-06-02 introduction.tex
Whitespace?
Updates from Overleaf

@@
 
-\KM{mention the inverse poly error and add forward pointer for discussion}
+We note that since the definition of $\SampBQP$ allows an inverse polynomial error, our CVQC protocol also implicitly allows an arbitrary small inverse polynomial error in  soundness (see Section~\ref{sec:samp_definition} for the formal definition).
+Achieving negligible soundness error for delegating sampling problems is an intriguing open question; see Section~\ref{subsec:discussion} for further discussions.
+
+%, which we discuss  further in Section~\ref{subsec:discussion}.
+
+%\KM{mention the inverse poly error and add forward pointer for discussion}
 
@@
 However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the prover and discard some local qubits in the case of overflow.}.
-A formal definition is given in Section~\ref{sec:qpip_def}.
+A formal definition is given in Appendix~\ref{sec:qpip_def}.
 
@@
 
-\paragraph{On the Inverse Polynomial Error in $\SampBQP$.} To be added. \KM{where to add this? Sec 1.3?}
+\subsection{Related Works and Discussions}  \label{subsec:discussion}
+
+As mentioned, while we are the first to explicitly investigate delegation of quantum sampling problems, Hayashi and Morimae~\cite{hayashi2015verifiable} constructed an one-round blind $\QPIP_1$ protocol that can be used to delegate $\SampBQP$ and achieve our notion of information-theoretical security.
+Like us, for $\SampBQP$, their protocol also does not achieve negligible soundness error, but requires an arbitrarily small inverse polynomial soundness error.
+It is also worth noting that several existing constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be generalized to delegate $\SampBQP$ in a natural way, but it seems challenging to analyze their security.
+Furthermore, these protocols cannot achieve negligible soundness error for $\SampBQP$ as well.
+The reason is that in all these constructions, some form of cut and choose are used to achieve soundness, and for delegating decision problems, negligible soundness can be achieved by taking majority vote of multiple outcomes.
+For sampling problems, as mentioned, there seems to be no generic way to combine multiple samples for error reduction, so the verifier needs to choose one sample to output in the cut and choose.
+In this case, an adversarial prover may choose to cheat on a random copy in the cut and choose and success in cheating with an inverse polynomial probability.
+
+On the other hand, while the definition of
+
+\paragraph{On the Inverse Polynomial Error in $\SampBQP$.}
+To be added. \KM{where to add this? Sec 1.3?}
 

### 2021-06-02 model.tex
Updates from Overleaf

@@
 
-Note that in the above definition, there is an accuracy parameter $\eps$ and the quantum sampling algorithm only requires to output a sample that is $\eps$-close to the correct distribution in time $\poly(n,1/\eps)$, instead of requiring a perfect or negligibly close sample.
-\cite{aaronson_2013, Boson} discussed multiple reasons for allowing the inverse polynomial error, such as conceivable physical realizations of quantum computer may consist of inherent noise.
+Note that in the above definition, there is an accuracy parameter $\eps$ and the quantum sampling algorithm only requires to output a sample that is $\eps$-close to the correct distribution in time $\poly(n,1/\eps)$.
+%, instead of requiring a perfect or negligibly close sample.
+\cite{aaronson_2013, Boson} discussed multiple reasons for allowing the inverse polynomial error, such as to take into account the inherent noise in conceivable physical realizations of quantum computer.
+%may consist of inherent noise.
 %There are multiple reasons for allowing an inverse polynomial error.
@@
 We refer the readers to~\cite{aaronson_2013, Boson} for the discussion therein on why this better captures the sampling problem solvable by realistic quantum computers.
-However, we note that it is also meaningful to require an exponentially small error instead of an inverse polynomial one. %We follow the definition of~\cite{aaronson_2013}, but note that
+On the other hand, it is also meaningful to require negligible error. As discussed, it is an intriguing open question to delegate quantum sampling problem with negligible error.
 
-We next define what it means for a $\QPIP_\tau$ protocol to solve a $\SampBQP$ problem $\left(D_x\right)_{x\in\set{0, 1}^*}$.
+%However, we note that it is also meaningful to require an exponentially small error instead of an inverse polynomial one. %We follow the definition of~\cite{aaronson_2013}, but note that
+
+We next define what it means for a $\QPIP_\tau$ protocol\footnote{See Appendix~\ref{sec:qpip_def} for a formal definition of $\QPIP_\tau$.} to solve a $\SampBQP$ problem $\left(D_x\right)_{x\in\set{0, 1}^*}$.
 Since sampling problems come with an accuracy parameter $\eps$, we let the prover $P$ and the verifier $V$ receive the input $x$ and $1^{1/\eps}$ as common inputs. 
@@
 To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems.
-We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the soundness property we just defined.
+We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) may be generalized naturally to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the soundness property we just defined.
 Proving the soundness of these constructions for delegating $\SampBQP$ is an interesting open question.

### 2021-06-02 acknowledgements.tex
Sync for submission

@@
-\section{Acknowledgments}
+\section*{Acknowledgments}
 
-\Ethan{TODO Acknowledge Morimae}
-
-\Ethan{TODO Acknowledge STOC Reviewer for bringing up Brakerski's QFHE}
+The authors would like to thank Tomoyuki Morimae for valuable feedback that helped improve the paper.
+We are also thankful to the anonymous reviewers from STOC 2021 for various useful comments and mentioning the stronger security guarantees given by Brakerski's encryption scheme in \cite{brakerski_qfhe}.
+\Ethan{check if this is ok}

### 2021-06-02 blind.tex
Sync for submission

@@
 Namely, the key generation algorithm and the encryption algorithm for classical messages should be classical, and when the underlying message is classical, the ciphertext (potentially from homomorphic evaluation) and the decryption algorithm should be classical as well.
-Fortunately, the quantum homomorphic encryption scheme of Mahadev~\cite{mahadev_qfhe} is classical friendly.
+Fortunately, the quantum homomorphic encryption scheme of Mahadev~\cite{mahadev_qfhe} and Brakerski~\cite{brakerski_qfhe} are classical friendly.
+Moreover, Brakerski's scheme requires a weaker QLWE assumption, where the modulus is polynomial instead of super-polynomial.
 
@@
 \begin{thm} \label{thm:compiler-blindness}
-    Assuming the QLWE assumption, $\Piblind$ is blind.
+    Under the QLWE assumption with polynomial modulus, $\Piblind$ is blind.
 \end{thm}
@@
 \begin{thm}
-    Assuming the QLWE assumption, \Ethan{wording sounds awkward?
-Maybe ``under the QLWE assumption"...?} there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
+    Under the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
 \end{thm}
@@
 \begin{thm}
-        Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
+        Under the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
 \end{thm}

### 2021-06-02 hamiltonian.tex
Sync for submission

@@
 \subsection{Reducing $\SampBQP$ to the X-Z Local Hamiltonian} \label{sec:LHXZ}
-As we mentioned in this introduction, we will employ the circuit \emph{history} state in the original construction of the Local Hamiltonian problem~\cite{kitaev2002classical} to encode the circuit information for $\SampBQP$.
-However, there are distinct requirements between certifying the computation for $\BQP$ and $\SampBQP$ based on the history state.
-For any quantum circuit $C$ on input $x$, the original construction for certifying $\BQP$\footnote{The original construction is for the purpose of certifying problems in QMA.
-We consider its simple restriction to problems inside BQP.} consists of local Hamiltonian $\Hin, \Hclock, \Hprop$, $\Hout$ where $\Hin$ is used to certify the initial input $x$, $\Hclock$ to certify the validness of the clock register,  $\Hprop$ to certify the gate-by-gate evolution according to the circuit description, and $\Hout$ to certify the final output.
-In particular, the corresponding history state is in the ground space of $\Hin$, $\Hclock$, and $\Hprop$.
-Note that $\BQP$ is a decision problem and its outcome (0/1) can be easily encoded into the energy $\Hout$ on the single output qubit.
-As a result, the outcome of $\BQP$ can simply be encoded by the \emph{ground energy} of $\Hin + \Hclock+\Hprop + \Hout$.
-
-To deal with $\SampBQP$, we will still employ $\Hin, \Hclock$, and $\Hprop$ to certify the circuit's input, the clock register, and gate-by-gate evolution.
-However, in $\SampBQP$, we care about the entire final state of the circuit, rather than the energy on the output qubit.
-%The history state remains in the ground space of $\Hin + \Hprop$.  
-Our approach to certify the entire final state (which is encoded inside the history state) is to make sure that the history state is the unique ground state of $\Hin + \Hclock+ \Hprop$ and all other orthogonal states will have much higher energies.
-Namely, we need to construct some $\Hin'+ \Hclock'+ \Hprop'$ with the history state as the unique ground state and with a large \emph{spectral} gap between the ground energy and excited energies.
-It is hence guaranteed that any state with close-to-ground energy must also be close to the history state.
-We remark that this is a different requirement from most local Hamiltonian constructions that focus on the ground energy.
-We achieve so by using the \emph{perturbation} technique developed in~\cite{kempe_kitaev_regev_2006} for reducing the locality of Hamiltonian.
-Another example of local Hamiltonian construction with a focus on the spectral gap can be found in~\cite{adiabatic}, where the purpose is to simulate quantum circuits by adiabatic quantum computation.
-
-We need two more twists for our purpose.
-First, as we will eventually measure the final state in order to obtain classical samples, we need that the final state occupies a large fraction of the history state.
-We can simply add dummy identity gates.
-Second, as we are only able to perform $X$ or $Z$ measurement by techniques from~\cite{FOCS:Mahadev18a},
-we need to construct X-Z only local Hamiltonians.
-Indeed, this has been shown possible in, e.g.,~\cite{PhysRevA.78.012352}, which serves as the starting point of our construction.
 

### 2021-06-02 hamiltonian_short.tex
Sync to GitHub for 1st submission
Sync for submission

@@
 
-See \Cref{sec:sampbqp} for the details of the construction of our $\QPIP_1$ Protocol for $\SampBQP$, \Cref{ProtoQPIP1}.
+As we mentioned in this introduction, we will employ the circuit \emph{history} state in the original construction of the Local Hamiltonian problem~\cite{kitaev2002classical} to encode the circuit information for $\SampBQP$.
+However, there are distinct requirements between certifying the computation for $\BQP$ and $\SampBQP$ based on the history state.
+For any quantum circuit $C$ on input $x$, the original construction for certifying $\BQP$\footnote{The original construction is for the purpose of certifying problems in QMA.
+We consider its simple restriction to problems inside BQP.} consists of local Hamiltonian $\Hin, \Hclock, \Hprop$, $\Hout$ where $\Hin$ is used to certify the initial input $x$, $\Hclock$ to certify the validness of the clock register,  $\Hprop$ to certify the gate-by-gate evolution according to the circuit description, and $\Hout$ to certify the final output.
+In particular, the corresponding history state is in the ground space of $\Hin$, $\Hclock$, and $\Hprop$.
+Note that $\BQP$ is a decision problem and its outcome (0/1) can be easily encoded into the energy $\Hout$ on the single output qubit.
+As a result, the outcome of $\BQP$ can simply be encoded by the \emph{ground energy} of $\Hin + \Hclock+\Hprop + \Hout$.
+
+To deal with $\SampBQP$, we will still employ $\Hin, \Hclock$, and $\Hprop$ to certify the circuit's input, the clock register, and gate-by-gate evolution.
+However, in $\SampBQP$, we care about the entire final state of the circuit, rather than the energy on the output qubit.
+%The history state remains in the ground space of $\Hin + \Hprop$.  
+Our approach to certify the entire final state (which is encoded inside the history state) is to make sure that the history state is the unique ground state of $\Hin + \Hclock+ \Hprop$ and all other orthogonal states will have much higher energies.
+Namely, we need to construct some $\Hin'+ \Hclock'+ \Hprop'$ with the history state as the unique ground state and with a large \emph{spectral} gap between the ground energy and excited energies.
+It is hence guaranteed that any state with close-to-ground energy must also be close to the history state.
+We remark that this is a different requirement from most local Hamiltonian constructions that focus on the ground energy.
+We achieve so by using the \emph{perturbation} technique developed in~\cite{kempe_kitaev_regev_2006} for reducing the locality of Hamiltonian.
+Another example of local Hamiltonian construction with a focus on the spectral gap can be found in~\cite{adiabatic}, where the purpose is to simulate quantum circuits by adiabatic quantum computation.
+
+We need two more twists for our purpose.
+First, as we will eventually measure the final state in order to obtain classical samples, we need that the final state occupies a large fraction of the history state.
+We can simply add dummy identity gates.
+Second, as we are only able to perform $X$ or $Z$ measurement by techniques from~\cite{FOCS:Mahadev18a},
+we need to construct X-Z only local Hamiltonians.
+Indeed, this has been shown possible in, e.g.,~\cite{PhysRevA.78.012352}, which serves as the starting point of our construction.
+
+ For more details of the construction of our $\QPIP_1$ Protocol for $\SampBQP$, \Cref{ProtoQPIP1}, see \Cref{sec:sampbqp}.
 The soundness and completeness of \Cref{ProtoQPIP1} is stated in the following theorem.
@@
     \label{QPIP1thm}
-	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem\\ $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}.}
+	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem\\ $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}.} where the verifier only needs to do non-adaptive $X/Z$ measurements.
 	%\XW{do we want precise error bound?}	

### 2021-06-02 introduction.tex
Sync for submission

--- 2021-06-02 introduction.tex
@@
 Another desirable property of CVQC protocols is  \emph{blindness}, which means that the prover does not learn any information about the private input for the delegated computation.\footnote{In literature, the definition of blindness may also require to additionally hide the computation.
-We note the two notions are equivalent from a feasibility point of view by a standard transformation (see Remark~\ref{} in Section~\ref{}\hannote{missing}).
+We note the two notions are equivalent from a feasibility point of view by a standard transformation (see Remark~\ref{rmk:blind-comp} in Section~\ref{sec:qpip_def}).
 %The two notions are equivalent from a feasibility point of view by a standard transformation that takes the description of the computation as part of the input and delegate the computation of  universal quantum circuits.
@@
 \emph{generic}  compiler that transforms any CVQC protocol to a blind one while preserving completeness, soundness, as well as its round complexity. 
-Our compiler relies on quantum fully homomorphic encryption (QFHE) schemes with certain ``classical-friendly'' properties, which is satisfied by both constructions of Mahadev~\cite{mahadev_qfhe} and Brakerski~\cite{??}.
+Our compiler relies on quantum fully homomorphic encryption (QFHE) schemes with certain ``classical-friendly'' properties, which is satisfied by both constructions of Mahadev~\cite{mahadev_qfhe} and Brakerski~\cite{brakerski_qfhe}.
 
@@
 \begin{theorem}[informal]
-    Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
+    Under the QLWE assumption, there exists a blind, four-message CVQC protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
 \end{theorem}
@@
 \begin{theorem}[informal]
-        Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all sampling problems in $\SampBQP$ with  computational soundness and negligible completeness error.
+        Under the QLWE assumption, there exists a blind, four-message CVQC protocol for all sampling problems in $\SampBQP$ with  computational soundness and negligible completeness error.
 \end{theorem}
@@
 In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm need to be classical when the underlying message is classical.
-Fortunately, such  ``classical-friendly'' property is satisfied by the construction of~\cite{mahadev_qfhe,??}.
+Fortunately, such  ``classical-friendly'' property is satisfied by the construction of~\cite{mahadev_qfhe, brakerski_qfhe}.
 
@@
 
-\paragraph{On the Inverse Polynomial Error in $\SampBQP$.} To be added. \KM{where to add this? Sec 1.3?}
+\subsection{Related Works and Discussions}  \label{subsec:discussion}
+
+As mentioned, while we are the first to explicitly investigate delegation of quantum sampling problems, Hayashi and Morimae~\cite{hayashi2015verifiable} constructed an one-round blind $\QPIP_1$ protocol that can be used to delegate $\SampBQP$ and achieve our notion of information-theoretical security.
+Like our $\SampBQP$ protocol, their protocol has an arbitrarily small inverse polynomial soundness error instead of negligible soundness error.
+Also as mentioned,  Gheorghiu and Vidick~\cite{FOCS:GheVid19} extends Mahadev's techniques to obtain a blind CVQC protocol.
+The protocol of \cite{FOCS:GheVid19} has polynomially many rounds, whereas our protocol has 4 rounds.
+
+It is also worth noting that several existing constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be generalized to delegate $\SampBQP$ in a natural way, but it seems challenging to analyze the soundness of the generalized protocol.
+Furthermore, it is highly likely that these generalized protocols cannot achieve negligible soundness error for $\SampBQP$.
+The reason is that in all these constructions, some form of cut and choose are used to achieve soundness.\Ethan{Maybe unnecessary?: , and for delegating decision problems, negligible soundness can be achieved by taking majority vote of multiple outcomes.} For sampling problems, as mentioned, there seems to be no generic way to combine multiple samples for error reduction, so the verifier needs to choose one sample to output in the cut and choose.
+In this case, an adversarial prover may choose to cheat on a random copy in the cut and choose and succeed in cheating with an inverse polynomial probability.
+
+On the other hand, while the definition of $\SampBQP$ in~\cite{aaronson_2013, Boson} allows an inverse polynomial error, there seems to be no fundamental barriers to achieve negligible error.
+It is conceivable that negligible error can be achieved using quantum error correction.
+Negligible error is naturally desirable and achievable in the related setting of secure multi-party quantum computation (MPQC\hannote{ref})\footnote{In MPQC, for the special case where the output is classical, it has the same simulation-based security for the output as our soundness definition.}.
+There, it\hannote{?} is achieved by using either verifiable quantum secret sharing or quantum authentication codes, both of which requires quantum communications.
+An intriguing open problem is whether it is possible to achieve negligible soundness error with classical communication while delegating a quantum sampling problem.
+
+%while a classical verifier is delegating a quantum sampling problem.
+
+%\paragraph{On the Inverse Polynomial Error in $\SampBQP$.}
+%To be added. \KM{where to add this? Sec 1.3?}
 

### 2021-06-02 model.tex
Sync for submission

@@
 
-To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems.
+%To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems.
 We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) may be generalized naturally to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the soundness property we just defined.

### 2021-06-02 paper.tex
Add acknowledgements section
Sync for submission

@@
 \author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}.
-Part of this work was done while supported by Scott Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.}}
-\author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER).}}
+Part of this work was done while supported by Scott Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.
+Partially funded by MOST Grant no.
+110-2222-E-007-002-MY3}}
+\author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER). }}
 \affil[1]{Institute of Information Science, Academia Sinica, Taiwan}
@@
 
+\input{acknowledgements}
+
 \bibliographystyle{plain}

### 2021-06-02 preliminaries.tex
Sync for submission

@@
 
+\begin{remark} \label{rmk:blind-comp}
+In literature, the definition of blindness may also require to additionally hide the computation.
+The two notions are equivalent from a feasibility point of view by a standard transformation (e.g., as in~\cite{GHRW14} in a different context) that takes the description of the computation as part of the input and delegate the computation of  universal quantum circuits.
+\end{remark}
+
 % \iffalse
@@
         \item In the case where the plaintext is classical, $\QEnc$ can be done classically.
-        \item When the underlying message is classical, the corresponding ciphertext is also classical and can be decrypted classically.
+        \item When the underlying message is a classical-quantum state, then the cipher text is composed of a corresponding classical part and a corresponding quantum part.
+Moreover, the classical part has a classical ciphertext and can be decrypted classically.
     \end{itemize}

### 2021-06-02 qpip.tex
Sync for submission

@@
 
-	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $(m+1)$-fold tensor products of identical copies of some states $\tau_j$.
+	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma'$ with the measurement result of a classical mix over $(m+1)$-identical copies of some states $\tau_j$.
 	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes m+1}$
-	such that for all quantum-classical channels $\Lambda_i$ acting on registers of size $s$:
+	such that for all quantum-classical channels $\Lambda_i$ acting on $s$-qubits:
 	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}_1

### 2021-06-03 acknowledgements.tex
Sync submitted version

--- 2021-06-02 acknowledgements.tex
@@
-\section{Acknowledgments}
+\section*{Acknowledgments}
 
-\Ethan{TODO Acknowledge Morimae}
-
-\Ethan{TODO Acknowledge STOC Reviewer for bringing up Brakerski's QFHE}
+The authors would like to thank Tomoyuki Morimae for his valuable feedback that helped improve the paper and for pointing out the related works \cite{takeuchi2018verification, hayashi2015verifiable}.
+We are also thankful to anonymous reviewers for various useful comments. \Ethan{check if this is ok}

### 2021-06-03 hamiltonian_short.tex
Sync submitted version

@@
 
- For more details of the construction of our $\QPIP_1$ Protocol for $\SampBQP$, \Cref{ProtoQPIP1}, see \Cref{sec:sampbqp}.
+We present the formal construction of our $\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ in \Cref{sec:sampbqp}, \Cref{ProtoQPIP1}.
+The soundness and completeness of \Cref{ProtoQPIP1} is stated in the following theorem, whose proof is also deferred to \Cref{sec:sampbqp}.% The proof of
+
+ %For more details of the construction of our $\QPIP_1$ Protocol for $\SampBQP$, \Cref{ProtoQPIP1}, see \Cref{sec:sampbqp}.
 The soundness and completeness of \Cref{ProtoQPIP1} is stated in the following theorem.
@@
     \label{QPIP1thm}
-	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem\\ $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}.} where the verifier only needs to do non-adaptive $X/Z$ measurements.
+	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem  $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}.} where the verifier only needs to do non-adaptive $X/Z$ measurements.
 	%\XW{do we want precise error bound?}	

### 2021-06-03 introduction.tex
Sync submitted version

@@
 \begin{theorem}[informal]
-Assuming the QLWE assumption\footnote{By using Brakerski's QFHE, we only need to rely on the QLWE assumption with polynomial modulus in thsi theorem.}, there exists a protocol compiler that transforms any CVQC protocol $\Pi$ to a CVQC protocol $\Piblind$ that achieves blindness while preserves its round complexity, completeness, and soundness.
+Assuming the QLWE assumption\footnote{By using Brakerski's QFHE, we only need to rely on the QLWE assumption with polynomial modulus in this theorem.}, there exists a protocol compiler that transforms any CVQC protocol $\Pi$ to a CVQC protocol $\Piblind$ that achieves blindness while preserves its round complexity, completeness, and soundness.
 \end{theorem}
@@
 Like our $\SampBQP$ protocol, their protocol has an arbitrarily small inverse polynomial soundness error instead of negligible soundness error.
-Also as mentioned,  Gheorghiu and Vidick~\cite{FOCS:GheVid19} extends Mahadev's techniques to obtain a blind CVQC protocol.
+Also as mentioned,  Gheorghiu and Vidick~\cite{FOCS:GheVid19} constructed the first blind CVQC protocol for $\BQP$ by constructing a composable remote state preparation protocol and combining it with the verifiable blind quantum computation protocol of Fitzsimons and Kashefi~\cite{FK17}.
+However, their protocol has polynomially many rounds  and requires a rather involved analysis.
+
+%Gheorghiu and Vidick~\cite{FOCS:GheVid19} extends Mahadev's techniques to obtain a blind CVQC protocol for $\BQP$.
 The protocol of \cite{FOCS:GheVid19} has polynomially many rounds, whereas our protocol has 4 rounds.
@@
 It is also worth noting that several existing constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be generalized to delegate $\SampBQP$ in a natural way, but it seems challenging to analyze the soundness of the generalized protocol.
-Furthermore, it is highly likely that these generalized protocols cannot achieve negligible soundness error for $\SampBQP$.
-The reason is that in all these constructions, some form of cut and choose are used to achieve soundness.\Ethan{Maybe unnecessary?: , and for delegating decision problems, negligible soundness can be achieved by taking majority vote of multiple outcomes.} For sampling problems, as mentioned, there seems to be no generic way to combine multiple samples for error reduction, so the verifier needs to choose one sample to output in the cut and choose.
+Furthermore, it is unlikely that these generalized protocols can achieve negligible soundness error for $\SampBQP$.
+The reason is that in all these constructions, some form of cut and choose are used to achieve soundness.
+%\Ethan{Maybe unnecessary?: , and for delegating decision problems, negligible soundness can be achieved by taking majority vote of multiple outcomes.} 
+For sampling problems, as mentioned, there seems to be no generic way to combine multiple samples for error reduction, so the verifier needs to choose one sample to output in the cut and choose.
 In this case, an adversarial prover may choose to cheat on a random copy in the cut and choose and succeed in cheating with an inverse polynomial probability.
@@
 It is conceivable that negligible error can be achieved using quantum error correction.
-Negligible error is naturally desirable and achievable in the related setting of secure multi-party quantum computation (MPQC\hannote{ref})\footnote{In MPQC, for the special case where the output is classical, it has the same simulation-based security for the output as our soundness definition.}.
+Negligible security error is also achievable in the related settings of secure multi-party quantum computation (MPQC)~\cite{CGS02,DNS12} and verifiable quantum FHE~\cite{ADSS17} based on verifiable quantum secret sharing or quantum authentication codes\footnote{The security definitions are not comparable, but it seems plausible that the techniques can be used to achieve negligible soundness error for sampling problems.}.
+However, both primitives requires to compute and communicate quantum encodings and are not applicable in the context of CVQC and $\QPIP_1$.
+An intriguing open problem is whether it is possible to achieve negligible soundness error with classical communication while delegating a quantum sampling problem.
+
+%(MPQC\hannote{ref})\footnote{In MPQC, for the special case where the output is classical, it has the same simulation-based security for the output as our soundness definition.}.
 There, it\hannote{?} is achieved by using either verifiable quantum secret sharing or quantum authentication codes, both of which requires quantum communications.

### 2021-06-03 paper.tex
Sync submitted version

@@
 \newif\ifdraft
-\drafttrue
-%\draftfalse
+%\drafttrue
+\draftfalse
 
@@
 \end{itemize}
-Applying our compiler to (a parallel repetition of) Mahadev's CVQC protocol for $\BQP$ and our CVQC protocol for $\SampBQP$ yields the first \emph{constant-round} blind CVQC protocol for $\BQP$ and $\SampBQP$ respectively, with negligible completeness and soundness errors.
+Applying our compiler to (a parallel repetition of) Mahadev's CVQC protocol for $\BQP$ and our CVQC protocol for $\SampBQP$ yields the first \emph{constant-round} blind CVQC protocol for $\BQP$ and $\SampBQP$ respectively, with negligible and inverse polynomial soundness errors respectively, and negligible completeness errors.
 

### 2021-06-03 qpip0.tex
Sync submitted version

--- 2021-02-19 qpip0.tex
@@
 \end{theorem}
-\begin{proof}
-	We first introduce the \emph{dummy strategy} for ~\Cref{proto:urmila4}, where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
+\begin{proof}[\Cref{lem:naive-qpip0-binding}]
+	We first introduce the \emph{dummy strategy} for $\PiMeasure$, where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
 	It is straightforward to verify that this prover would be accepted in the testing round with probability $1-\negl(\lambda)$,
@@
 	\label{thm:zi-zgoodi}
-	$$\tr\abs{z_i-z_{good, i}}\leq\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R).$$
+	\begin{align*}
+	\tr\abs{z_i-z_{good, i}}\leq&\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]\\
+	&+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R).
+	\end{align*}
 \end{lemma}
-\begin{proof}
+
+\begin{proof}[\Cref{thm:zi-zgoodi}]
 	We take expectation of \Cref{eq:partition-string} over $\gamma$
@@
 	\begin{align}
-		z_i=& z_{good,i}+ \E_{pk, y, \gamma} \sum_z \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
-		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \nn \\
-		+&  \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-		+\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
+		z_i &= z_{good,i}+ \E_{pk, y, \gamma} \sum_z \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} \R. \nn \\
+		&+
+		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
+		&+\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
 		\nn \\
-		+&  \bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-		+\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
+		&+ \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} + \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}
 		\nn \\
-		+&\L.
-\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] \proj{z} , \nn
+		&\L.    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] \proj{z} , \nn     
 		%=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err )
@@
 	\begin{align*}
-		\tr|z_i-z_{good,i}|\leq& \E_{pk, y, \gamma} \sum_z \L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|+
-		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R. \\
-		+& 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R|    
-		+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \\
-		+&\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
+		\tr|z_i-z_{good,i}|\leq \E_{pk, y, \gamma} \sum_z &\L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|\R.\\
+		&+
+		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R| \\
+		&+ 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R| \\   
+		&+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \\
+		&+\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
 	\end{align*}

### 2021-06-03 qpip0_proofs.tex
Sync submitted version

@@
-\section{Proofs for \Cref{sec:qpip0_all}}
-\label{sec:qpip0_proof}
-
 % \begin{theorem}[binding property of $\PiNaive$]
@@
 % \end{theorem}
-\begin{proof}[\Cref{lem:naive-qpip0-binding}]
-	We first introduce the \emph{dummy strategy} for ~\Cref{proto:urmila4}, where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
-	It is straightforward to verify that this prover would be accepted in the testing round with probability $1-\negl(\lambda)$,
-	but has negligible probability passing the verification  after the Hadamard round.
-
-   %for $\PiMeasure$ $\Pstarsub$ that is almost perfect as follows. 
-	Now we construct a cheating $\BQP$ prover for \Cref{proto:qpip0_naive}, $\Pstar$, that does the same thing as $\PNaiveStar$ except at Step~\ref{step:urmila-in-naive}, where the prover and verifier runs \Cref{proto:urmila4}.
-$\Pstar$ does the following in Step~\ref{step:urmila-in-naive}:
-	for the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
-	If $y\ne\bot$, then reply $y$;
-	else, run the corresponding step of the dummy strategy and reply with its results.
-	For the fourth message, if $y\ne\bot$, run and reply with $a\leftarrow\cPNaiveStar{4}(pk, c, \sigma)$;
-	else, continue the dummy strategy.
-
-%	so we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property (\Cref{lem:urmila-binding}).
-%That is, there exists some $\rho$ such that $v=M_{XZ}(\rho, h)$.\hannote{only comp}
-
-	 In the following we fix an $x$.
-Let the distribution on $h$ specified in Step~\ref{step:naive1} of the protocol be $p_x(h)$.
-Define $\Pstarsub(x)$ as $\Pstar$'s responds in Step~\ref{step:urmila-in-naive}.
-Note that we can view $\Pstarsub(x)$ as a prover strategy for \Cref{proto:urmila4}.
-By construction $\Pstarsub(x)$ passes testing round with overwhelming probability over $p_x(h)$, i.e.
-$\sum_h p_x(h) p_{h,T} =\negl(\lambda)$, where $p_{h,T}$ is $\Pstar$'s probability of getting accepted by the prover on the testing round on basis choice $h$.
-By \Cref{lem:urmila-binding} and Cauchy's inequality, there exists some $\rho$ such that  $\sum_h p_x(h) \norm{v_h -M_{XZ}(\rho, h)}_c = \negl(\lambda)$, where we use $\norm{A-B}_c=\alpha$ to denote that $A$ is $\alpha$-computational indistinguishable to $B$.
-Therefore $v= \sum_h p_x(h) v_h$ is computationally indistinguishable to $\sum_h p_x(h) M_{XZ}(\rho, h)$.
-Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}),
-	we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\epsilon}, x)$  is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.
-
-	Now we relate $(d', z')$ back to $(d, z)$.
-	First, conditioned on that $\PNaiveStar$ aborts, since dummy strategy will be rejected with overwhelming probability in Hadamard round,
-	we have $(d', z')$ is computationally indistinguishable to $(\Rej, \bot)=(d, z)$.
-	On the other hand, conditioned on $\PNaiveStar$ not aborting, clearly $(d, z)=(d', z')$.
-	So $(d, z)$ is computationally indistinguishable to $(d', z')$,
-	which in turn is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
-	Since $\norm{d-d'}_{tr}= O(\eps)$,
-	 $(d, z_{ideal})$ is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
-	Combining everything, we conclude that $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d, z_{ideal})$.
-\end{proof}
-
-\begin{proof}[\Cref{thm:zi-zgoodi}]
-	We take expectation of \Cref{eq:partition-string} over $\gamma$
-	$$\ket{\psi}=\E_{\gamma}\left[
-		\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-	\right],$$
-	and expand $z_i$ from \Cref{eq:zi-def} as
-	\begin{align}
-		z_i &= z_{good,i}+ \E_{pk, y, \gamma} \sum_z \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} \R. \nn \\
-		&+
-		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
-		&+\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
-		\nn \\
-		&+ \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} + \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}
-		\nn \\
-		&\L.    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] \proj{z} , \nn     
-		%=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err )
-	\end{align}
-	where we omitted writing out $e_i$.
-	Therefore we have
-	\begin{align*}
-		\tr|z_i-z_{good,i}|\leq \E_{pk, y, \gamma} \sum_z &\L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|\R.\\
-		&+
-		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R| \\
-		&+ 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R| \\   
-		&+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \\
-		&+\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
-	\end{align*}
-	by the triangle inequality.
-	The last three error terms sum to $O\L(\frac{m^2}{\sqrt{T}}\R)$ by \Cref{lem:samp-tech} and property~\ref{property:partition-err} of \Cref{lem:partition2}.
-	As for the first two terms, by \Cref{lem:samp-tech} and \Cref{lem:partition-testing}, we see that
-	\begin{align*}
-		\sum_z \sum_{k=0}^{i-1}\sum_{j=0}^{i-1}
-		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}}} \\
-		&\leq\sum_z \abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^{i-1}0,\gamma}}} + O\L(m^2(m-1)\gamma_0\R) \\
-		&\leq\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2 + O\L(m^2(m-1)\gamma_0\R)
-	\end{align*}
-	and similarly
-	\begin{align*}
-		\sum_z\sum_{k=0}^{i-1}
-		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}\\
-		&\leq\sum_z\abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R)\\
-		&\leq\norm{\ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R).
-	\end{align*}
-\end{proof}

### 2021-09-29 qpip0.tex
Updates from Overleaf

@@
 			\begin{align}
-				\norm{ P_{acc, i} \circ U\frac{\ket{e_j}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}}^2 \leq (m-1)\gamma_0+\negl(\lambda),
+				\norm{ P_{acc, i} \circ U\frac{\ket{e_j}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}\|}}^2 \leq (m-1)\gamma_0+\negl(\lambda),
 			\end{align}
@@
 			\begin{align}
-				\norm{P_{acc, i} \circ \ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)}^2 =1-\negl(\lambda).
+				\norm{P_{acc, i} \circ \ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}\|}\right)}^2 =1-\negl(\lambda).
 			\end{align}
@@
 
-We denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as $P_{acc,i,z}$.
-Note that $P_{acc,i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $\vec{a}$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
-$P_{acc,i,z}$ is a projector because it only involves the projective measurements to get $a$ and classical post-processing of the verifiers.
-Also note that  $P_{acc,i,z} P_{acc,i,z'}=0$ for all $z\neq z'$, and $\sum_z P_{acc,i,z} \leq Id$.
+\hannote{maybe some explanation about $P_{acc,i}$ and $P_{acc,j}$ commute.
+maybe just stress that $P_{acc}$'s are in standard basis.stress on the dilation dequantization?} We denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as $P_{acc,-i,z}$.
+Note that $P_{acc,-i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $\vec{a}$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
+$P_{acc,-i,z}$ is a projector because it only involves the projective measurements to get $a$ and classical post-processing of the verifiers.
+Also note that  $P_{acc,-i,z} P_{acc,-i,z'}=0$ for all $z\neq z'$, and $\sum_z P_{acc,-i,z} =\Pi_{j \neq i} P_{acc,j}\leq Id$.
 
@@
 	\label{eq:zi-def}
-	z_i\defeq \E_{pk,y} \sum_z \norm{P_{acc,i,z} U\ket{e_i,\psi}}^2\proj{z},
+	z_i\defeq \E_{pk,y} \sum_z \norm{P_{acc,-i,z} U\ket{e_i,\psi}}^2\proj{z},
 \end{equation}
@@
 	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and all $i,j\in[m]$ such that $j<i-1$, we have
-	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
+	$$\norm{P_{acc,-i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
 \end{cor}
@@
 	\label{eq:zgoodi-def}
-	z_{good, i}=\E_{\gamma, pk, y} \sum_z \norm{P_{acc,i,z} U\ket{e_i,\psi_{1^{i-1}1,\gamma}}}^2\proj{z}
+	z_{good, i}=\E_{\gamma, pk, y} \sum_z \norm{P_{acc,-i,z} U\ket{e_i,\psi_{1^{i-1}1,\gamma}}}^2\proj{z}
 \end{equation}
@@
 	\begin{align}
-		z_i &= z_{good,i}+ \E_{pk, y, \gamma} \sum_z \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} \R. \nn \\
+		z_i &= z_{good,i}+ \E_{pk, y, \gamma} \sum_z \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} \R. \nn \\
 		&+
-		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
-		&+\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
+		\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^i,\gamma}} +\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
+		&+\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,-i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,-i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
 		\nn \\
-		&+ \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} + \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}
+		&+ \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,-i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} + \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,-i,z}U \ket{\psi_{1^i,\gamma}}
 		\nn \\
-		&\L.    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] \proj{z} , \nn     
+		&\L.    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,-i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] \proj{z} , \nn     
 		%=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err )
@@
 	\begin{align*}
-		\tr|z_i-z_{good,i}|\leq \E_{pk, y, \gamma} \sum_z &\L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}} \R|\R.\\
+		\tr|z_i-z_{good,i}|\leq \E_{pk, y, \gamma} \sum_z &\L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^j0,\gamma}} \R|\R.\\
 		&+
-		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R| \\
-		&+ 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R| \\   
-		&+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \\
-		&+\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
+		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^i,\gamma}} \R| \\
+		&+ 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U\ket{\psi_{err,j,\gamma}}\R| \\   
+		&+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,-i,z}U \ket{\psi_{err,j,\gamma}}\R| \\
+		&+\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,-i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
 	\end{align*}
@@
 		\sum_z \sum_{k=0}^{i-1}\sum_{j=0}^{i-1}
-		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^j0,\gamma}}} \\
-		&\leq\sum_z \abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^{i-1}0,\gamma}}} + O\L(m^2(m-1)\gamma_0\R) \\
+		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^j0,\gamma}}} \\
+		&\leq\sum_z \abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^{i-1}0,\gamma}}} + O\L(m^2(m-1)\gamma_0\R) \\
 		&\leq\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2 + O\L(m^2(m-1)\gamma_0\R)
@@
 		\sum_z\sum_{k=0}^{i-1}
-		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}\\
-		&\leq\sum_z\abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R)\\
+		&\abs{\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^i,\gamma}}}\\
+		&\leq\sum_z\abs{\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R)\\
 		&\leq\norm{\ket{\psi_{1^i,\gamma}}}+O\L(m\sqrt{(m-1)\gamma_0}\R).
@@
 Now we try to put together all $i\in [m]$. First let
-$$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
+$$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,-i,z} U|e_i,\psi},$$
 which is the output distribution of $\PiSampZ$.

### 2021-09-29 blind.tex
Fix the simpler typos

@@
 
-In this section, we present a generic protocol compiler that compiles any $\QPIP_0$ protocol $\Pi = (P, V)$ (with an arbitrarily number of rounds) to a protocol $\Piblind = (\Pblind, \Vblind)$ that achieve blindness while preserving the completeness, soundness, and round complexity.
+In this section, we present a generic protocol compiler that compiles any $\QPIP_0$ protocol $\Pi = (P, V)$ (with an arbitrary number of rounds) to a protocol $\Piblind = (\Pblind, \Vblind)$ that achieve blindness while preserving the completeness, soundness, and round complexity.
 At a high-level, the idea is simple: we simply run the original protocol under a quantum homomorphic encryption $\QHE$ with the verifier's key.

### 2021-09-29 hamiltonian.tex
Fix the simpler typos

@@
 Given any quantum circuit $C$ and input $x$, consider using $H_{C(x)}$ from \Cref{thm:LHReduction} in Protocol~\ref{AlgGroundStateCheck} ($\cVGS$).
-For any state $\rho$, and $0< \epsilon < 1$, if $\cVGS$ accepts $\rho$ with probability,
+For any state $\rho$, and $0< \epsilon < 1$, if $\cVGS$ accepts $\rho$ with probability
 \[
@@
 it has less control on the shape of the output copy.
-In fact, the prover can always prepare a bad copy among with many good copies as a plain attack.
+In fact, the prover can always prepare a bad copy along with many good copies as a plain attack.
 This attack will succeed when the bad copy is chosen to output, the probability of which is non-negligible in terms of the total number of copies assuming some symmetry of the protocol.

### 2021-09-29 introduction.tex
Fix the simpler typos

@@
 The challenge is to show that $\PiSampZ$ is computationally sound.
-Note that now we are in the computational setting, we cannot use the quantum de Finetti theorem as above since it only holds in the information-theoretical setting\hannote{really?
+Since we are now in the computational setting, we cannot use the quantum de Finetti theorem as above which only holds in the information-theoretical setting\hannote{really?
 maybe emphasis on constructing adversary}.
@@
  For $\BQP$, the verifier simply chooses to run the Hadamard and testing rounds independently for each repetition.
-In contrast, our $\PiSampZ$ runs the Hadamard round in one repetition and run the testing rounds in the rest.
+In contrast, our $\PiSampZ$ runs the Hadamard round in one repetition and runs the testing rounds in the rest.
 The reason is that in $\SampBQP$, as well as generically in sampling problems, there is no known approach to combine multiple samples to generate one sample with reduced error, i.e., there is no generic error reduction method for the sampling problem.
@@
 % %
-The intuitive analysis outlined above grosses over many technical details, and we substantiate this outline with full details in 
+The intuitive analysis outlined above glosses over many technical details, and we substantiate this outline with full details in 
 Section~\ref{sec:qpip0_all}.
@@
 %
-The intuitive analysis outlined above grosses over many technical details, and we substantiate this outline with full details in  
+The intuitive analysis outlined above glosses over many technical details, and we substantiate this outline with full details in  
 Section~\ref{sec:qpip0_all}.

### 2021-09-29 qpip.tex
Fix the simpler typos

@@
 	\begin{enumerate}
-		\item\label{step:qpip1-state-gen} The honest prover prepares $M=649\frac{T^{41}\lambda^2}{\eps^{51}}$ copies of $\histpsi{C'(x)}$ and sends all of it to the verifier qubit-by-qubit.
+		\item\label{step:qpip1-state-gen} The honest prover prepares $M=649\frac{T^{41}\lambda^2}{\eps^{51}}$ copies of $\histpsi{C'(x)}$ and sends all of them to the verifier qubit-by-qubit.
 		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{20}\lambda}{\eps^{24}}$, and $k\xleftarrow{\$}[M]\setminus I$.

### 2021-09-29 qpip0.tex
Fix the simpler typos

--- 2021-06-03 qpip0.tex
@@
 Let the distribution on $h$ specified in Step~\ref{step:naive1} of the protocol be $p_x(h)$.
-Define $\Pstarsub(x)$ as $\Pstar$'s responds in Step~\ref{step:urmila-in-naive}.
+Define $\Pstarsub(x)$ as $\Pstar$'s response in Step~\ref{step:urmila-in-naive}.
 Note that we can view $\Pstarsub(x)$ as a prover strategy for \Cref{proto:urmila4}.
@@
 
-\begin{lemma}[partition lemma; revision of Lemma 3.5 of \cite{arXiv:ChiaChungYam19}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{arXiv:ChiaChungYam19} and post-select on the $ph,th,in$ register being $0^t01$ or $0^t11$ then discard $ph,th,in$.
+\begin{lemma}[partition lemma; revision of Lemma 3.5 of \cite{arXiv:ChiaChungYam19}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{arXiv:ChiaChungYam19} and post-selecting on the $ph,th,in$ register being $0^t01$ or $0^t11$ then discard $ph,th,in$.
 Property~\ref{property:partition-err} corresponds to Property~1.
@@
 	Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$\footnote{A $m$-fold parallel repetition of $\PiMeasure$ is running step~\ref{step:urmila-in-qpip0-1}~\ref{step:urmila-in-qpip0-2}~\ref{step:urmila-in-qpip0-3}~\ref{step:urmila-in-qpip0-4} of \Cref{proto:QPIP0samp} with verifier input $\vec{h}$ and prover input $\rho^{\otimes n}$, followed by an output step where the verifier rejects if any of the $m-1$ testing round copies is rejected, otherwise outputs the result of the Hadamard round copy.}, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message.
-Let $H_{\regX,\regZ}$ be the Hilberspace of the prover's internal calculation.
+Let $H_{\regX,\regZ}$ be the Hilbert space of the prover's internal calculation.
 	Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$, which corresponds to doing Hadamard round on the $i$-th copy and testing round on all others.

### 2021-09-30 qpip0.tex
Updates from Overleaf

@@
 Note that $P_{acc,-i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $\vec{a}$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
-$P_{acc,-i,z}$ is a projector because it only involves the projective measurements to get $a$ and classical post-processing of the verifiers.
+$P_{acc,-i,z}$ is a projector because it only involves the standard basis measurements to get $a$ and classical post-processing of the verifiers.
 Also note that  $P_{acc,-i,z} P_{acc,-i,z'}=0$ for all $z\neq z'$, and $\sum_z P_{acc,-i,z} =\Pi_{j \neq i} P_{acc,j}\leq Id$.
@@
 	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and all $i,j\in[m]$ such that $j<i-1$, we have
-	$$\norm{P_{acc,-i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
+	$$\sum_z\norm{P_{acc,-i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
 \end{cor}

### 2021-09-30 blind.tex
Take FOCS reviewer comments

@@
 Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoids the issue of circuit privacy.
-Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it to $\Pblind$.
+Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it along with $pk'$ to $\Pblind$.
 This allows the prover to homomorphically convert ciphertexts under key $pk$ to ciphertexts under key $pk'$.

### 2021-09-30 introduction.tex
Take FOCS reviewer comments

@@
 While this is not a problem for decision problems, %(where the verifier only needs to decide to accept or reject),
-for sampling problems, the verifier needs to produce an output sample when accepts, but there seems no way to produce the output for the verifier without learning the measurement outcome.   
+for sampling problems, the verifier needs to produce an output sample when accepts, but there seems to be no way to produce the output for the verifier without learning the measurement outcome.   
 %
@@
 Negligible security error is also achievable in the related settings of secure multi-party quantum computation (MPQC)~\cite{CGS02,DNS12} and verifiable quantum FHE~\cite{ADSS17} based on verifiable quantum secret sharing or quantum authentication codes\footnote{The security definitions are not comparable, but it seems plausible that the techniques can be used to achieve negligible soundness error for sampling problems.}.
-However, both primitives requires to compute and communicate quantum encodings and are not applicable in the context of CVQC and $\QPIP_1$.
+However, both primitives require computing and communicating quantum encodings and are not applicable in the context of CVQC and $\QPIP_1$.
 An intriguing open problem is whether it is possible to achieve negligible soundness error with classical communication while delegating a quantum sampling problem.

### 2021-09-30 qpip0.tex
Take FOCS reviewer comments

@@
 	\begin{align}
-	\label{eq:psi0}	G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{0,i,\gamma}}_{\regX,\regZ}, \\ 
-	\label{eq:psi1}	G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{1,i,\gamma}}_{\regX,\regZ},  \\
-	\label{eq:psierr}	\ket{\psi}_{\regX,\regZ} -\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}- \ket{\psi_{1,i,\gamma}}_{\regX,\regZ} \defeq&   \ket{\psi_{err,i,\gamma}}_{\regX,\regZ}.
+	\label{eq:psi0}
+	\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}
+	\defeq&
+	G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ}, \\ 
+	\label{eq:psi1}	
+	\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}
+	 \defeq&
+	G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ}
+	,  \\
+	\label{eq:psierr}
+	\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}
+	\defeq&
+	\ket{\psi}_{\regX,\regZ} -\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}- \ket{\psi_{1,i,\gamma}}_{\regX,\regZ}
+	.
 	\end{align}
@@
 	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and all $i,j\in[m]$ such that $j<i-1$, we have
-	$$\sum_z\norm{P_{acc,-i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
+	$$\norm{\sum_z P_{acc,-i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
 \end{cor}
@@
 Before doing so, we present a technical lemma.
-\begin{lemma}\label{lem:samp-tech}
-	For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
-	$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi}. $$
+
+\begin{lemma}\label{lem:samp-tech-2}
+	For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $P_z P_{z'} =0 $ for all $z\neq z'$, we have
+	$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 }. $$
 \end{lemma}
@@
 		\leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\sum_z\norm{P_z\ket{\phi}}^2} \nn \\
-		\leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn \\
-		\leq & \norm{\ket{\psi}}\norm{\ket{\phi}},
+		\leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn,
 	\end{align}
@@
 \end{proof}
+
+\begin{cor}\label{lem:samp-tech}
+	For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
+	$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi}. $$
+\end{cor}
 
@@
 	The last three error terms sum to $O\L(\frac{m^2}{\sqrt{T}}\R)$ by \Cref{lem:samp-tech} and property~\ref{property:partition-err} of \Cref{lem:partition2}.
-	As for the first two terms, by \Cref{lem:samp-tech} and \Cref{lem:partition-testing}, we see that
+	As for the first two terms, by \Cref{lem:samp-tech-2} and \Cref{lem:partition-testing}, we see that
 	\begin{align*}

### 2021-09-30 blind.tex
Fix singular/plural "for all" issues

@@
 \begin{thm} \label{thm:compiler-errors}
-    For all cheating $\BQP$ prover $\Pblindstar$, there exists a cheating $\BQP$ prover $\Pstar$ s.t.
-for all $\lambda$ and input $x\in\zo^{\poly(\lambda)}$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
+    For all cheating $\BQP$ provers $\Pblindstar$, there exists a cheating $\BQP$ prover $\Pstar$ s.t.
+for all $\lambda$ and inputs $x\in\zo^{\poly(\lambda)}$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
 \end{thm}
@@
 \begin{proof}
-    We show that for all cheating $\BQP$ prover $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
+    We show that for all cheating $\BQP$ provers $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
     $P^*$ cannot distinguish $(P^*, \Vblind(x))(1^\lambda)$ from $(P^*, \Vblind(0^n))(1^\lambda)$ with noticeable probability in $\lambda$.

### 2021-09-30 model.tex
Fix singular/plural "for all" issues

@@
         \item (Completeness):
-            For all accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
-            security parameter $\lambda\in\bbN$,
+            For all accuracy parameters $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
+            security parameters $\lambda\in\bbN$,
             and $x\in\zo^{\poly(\lambda)}$,
             let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
-        \item (Statistical soundness): For all cheating prover $P^*$,
-            accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
+        \item (Statistical soundness): For all cheating provers $P^*$,
+            accuracy parameters $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
             sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$,
@@
 		\item (Computational soundness):
-        For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
+        For all cheating $\BQP$ provers $P^*$, $\BQP$ distinguishers $\mathsf{D}$, accuracy parameters $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
             sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$,

### 2021-09-30 preliminaries.tex
Fix singular/plural "for all" issues

@@
         \item On public input $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
-        \item (Completeness): For all security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
+        \item (Completeness): For all security parameters $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
         $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
-        \item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large \\security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then \\$\Pr\left[(P, V)(x, 1^\lambda)=\Acc\right]<s(\lambda)$.
+        \item (Soundness): For all cheating $\BQP$ provers $P^*$, sufficiently large \\security parameters $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then \\$\Pr\left[(P, V)(x, 1^\lambda)=\Acc\right]<s(\lambda)$.
     \end{itemize}
@@
     and verifier's private input $x\in\zo^*$.
-    We say $\Pi$ is \emph{blind} if for all cheating $\BQP$ prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
+    We say $\Pi$ is \emph{blind} if for all cheating $\BQP$ provers $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
     \begin{itemize}

### 2021-09-30 qpip0.tex
Fix singular/plural "for all" issues

@@
 
-	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two $\poly(1/\gamma_0,T,\lambda)$-time quantum circuit with post selection\footnote{A quantum circuit with post selection is composed of unitary gates followed by a post selection on some measurement outcome on ancilla qubits, so it produces a subnormalized state, where the amplitude square of the output state is the probability of post selection.} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}\in  H_{\regX,\regZ}$,  properties \ref{property:partition-err}~\ref{property:partition-testing}~\ref{property:partition-binding}~\ref{property-partition-norm-sum}, to be described later, are satisfied.
+	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two $\poly(1/\gamma_0,T,\lambda)$-time quantum circuit with post selection\footnote{A quantum circuit with post selection is composed of unitary gates followed by a post selection on some measurement outcome on ancilla qubits, so it produces a subnormalized state, where the amplitude square of the output state is the probability of post selection.} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum states $\ket{\psi}_{\regX,\regZ}\in  H_{\regX,\regZ}$,  properties \ref{property:partition-err}~\ref{property:partition-testing}~\ref{property:partition-binding}~\ref{property-partition-norm-sum}, to be described later, are satisfied.
 Before we describe the properties, we introduce the following notations:

### 2021-09-30 blind.tex
Implement more FOCS feedback

@@
 By the correctness of $\QHE$, the completeness error of $\Piblind$ is negligibly close to that of $\Pi$.
+In particular, note that the level parameter $L$ is sufficient for the honest prover which has a bounded complexity.
 For the soundness property, we show the following lemma, which implies that $\Piblind$ preserves the soundness of $\Pi_0$.
@@
 
-Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
+Finally, we show the blindness of $\Piblind$ through a standard hybrid argument where the $sk_i$'s are ``erased" one by one, starting from $sk_T$.
+Once $sk_1$ is eventually erased, $\QEnc(pk_1, x)$ and $\QEnc(pk_1, 0)$ become indistinguishable due to the IND-CPA security of $\QEnc$, and we complete the proof.
+We now fill in the mathmatical details of this argument.
+
 \begin{thm} \label{thm:compiler-blindness}

### 2021-09-30 introduction.tex
Updates from Overleaf

@@
 %\hannote{copy ch 5 here?}
-To analyze the soundness of $\PiSampZ$, we use the \emph{partition lemma} developed in~\cite{arXiv:ChiaChungYam19} to analyze the prover's behavior while executing copies of $\PiMeasure$.
-Intuitively, the partition lemma says that for any cheating prover and for each copy $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
+To analyze the soundness of $\PiSampZ$, we use the \emph{partition lemma} developed in~\cite{arXiv:ChiaChungYam19} to analyze the prover's behavior while executing copies of $\PiMeasure$.\footnote{The analysis of \cite{arXiv:AlaChiHun19} is more tailored to the decision problems setting, and it is unclear how to extend it to sampling problems where there are multiple bits of output.} Intuitively, the partition lemma says that for any cheating prover and for each copy $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
 $G_{0,i}$ and $G_{1,i}$ splits up the prover's residual internal state after sending back his first message.
@@
 
-\subsection{Related Works and Discussions}  \label{subsec:discussion}
+\subsection{Related and Followup Works and Discussions}  \label{subsec:discussion}
 
@@
 An intriguing open problem is whether it is possible to achieve negligible soundness error with classical communication while delegating a quantum sampling problem.
+
+As a followup work, Bartusek~\cite{bartuseksecure} constructs maliciously-secure multi-party protocols for $\BQP$  computation using our classical verification protocol for $\SampBQP$.
 

### 2021-10-22 introduction.tex
Sync from Overleaf

@@
 We initiate the study of CVQC for quantum sampling problem, which we believe is highly desirable and natural for delegation of quantum computation.
-In general, a round of quantum computation can be described as applying a quantum circuit and measuring the output qubits in computational basis.
-Due to its intrinsic randomness, the output is randomized and described by a distribution.
+Due to the intrinsic randomness of quantum mechanics, the output from a quantum computation is randomized and described by a distribution.
+% In general, a round of quantum computation can be described as applying a quantum circuit and measuring the output qubits in computational basis.
 %To verifiably delegate general quantum computation, it is natural to require that the output is close to the correct distribution when the verifier accepts. 
@@
 
+\vspace{-3pt}
+
 \subsection{Related and Followup Works and Discussions}  \label{subsec:discussion}
@@
 It is conceivable that negligible error can be achieved using quantum error correction.
-Negligible security error is also achievable in the related settings of secure multi-party quantum computation (MPQC)~\cite{CGS02,DNS12} and verifiable quantum FHE~\cite{ADSS17} based on verifiable quantum secret sharing or quantum authentication codes\footnote{The security definitions are not comparable, but it seems plausible that the techniques can be used to achieve negligible soundness error for sampling problems.}.
+Negligible security error is also achievable in the related settings of secure multi-party quantum computation ~\cite{CGS02,DNS12} and verifiable quantum FHE~\cite{ADSS17} based on verifiable quantum secret sharing or quantum authentication codes\footnote{The security definitions are not comparable, but it seems plausible that the techniques can be used to achieve negligible soundness error for sampling problems.}.
 However, both primitives require computing and communicating quantum encodings and are not applicable in the context of CVQC and $\QPIP_1$.
@@
 
-As a followup work, Bartusek~\cite{bartuseksecure} constructs maliciously-secure multi-party protocols for $\BQP$  computation using our classical verification protocol for $\SampBQP$.
+In a recent work, Bartusek~\cite{bartuseksecure} used the technique we developed for delegation of $\SampBQP$ to construct secure quantum computation protocols with classical communication for pseudo-deterministic quantum functionalities.
+
+%As a followup work, Bartusek~\cite{bartuseksecure} constructs maliciously-secure multi-party protocols for $\BQP$  computation using our classical verification protocol for $\SampBQP$.
 

### 2021-10-22 qpip0.tex
Sync from Overleaf

@@
 Also a careful reader might have noticed that the prover's space don't always decompose cleanly into parts that the verifier either rejects or accepts with high probability, as there might be some states that is accepted with mediocre probability.
-In \cite{arXiv:ChiaChungYam19}, this is solved by splitting the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$ and applying amplitude amplification to boost the accept probability if it is bigger than $\gamma$.
-However, states with accept probability really close to the threshold $\gamma$ can not be classified, so they need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.
+As in \cite{arXiv:ChiaChungYam19}, we solve this by splitting the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$ and applying Marriott-Watrous~\cite{marriott2005quantum} amplification to boost the accept probability if it is bigger than $\gamma$, getting a corresponding amplified prover action $\ext$.
+However, states with accept probability really close to the threshold $\gamma$ can not be classified, so we average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.
 Now we give a formal description of the partition lemma.
+
+%
+
+%Roughly speaking, the idea of the partition lemma is picking a small random probability $\gamma$ and run Marriott-Watrous ~\cite{marriott2005quantum} amplification on the acceptance probability of the testing round.
+This roughly separates the prover's internal space into subspaces with acceptance probability less than $\gamma$ (Corresponds to $G_0$) and subspaces with acceptance probability bigger than $\gamma$ (Corresponds to $G_1$).
+We also get an "amplified" prover protocol $\ext$ which gi.
 
@@
 
-Note that in property~\ref{property:partition-binding}, we are using $\ext_i$ instead of $U$ because we are doing some amplitude amplification to boost the success probability.
+Note that in property~\ref{property:partition-binding}, we are using $\ext_i$ instead of $U$ because we use amplitude amplification to boost the success probability.
 

### 2021-10-22 introduction.tex
Remove comments from intro

@@
 Soundness of Mahadev's protocol  is based on a widely recognized computational assumption that the learning with errors (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
-%In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of Classical Verification of Quantum Computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
 The technique invented therein has inspired many subsequent developments of CVQC protocols with improved parameters and functionality.
@@
 As another example, the work of ~\cite{FOCS:GheVid19} extends Mahadev's techniques in an involved way to obtain a CVQC protocol with an additional blindness property.
-
-%For example,~\cite{arXiv:AlaChiHun19,arXiv:ChiaChungYam19}  
-%
-%(e.g.,~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
 
@@
 
-% On the other side, there are known complexity-theoretic limitations on the feasibility of blind CVQC in the information-theoretical setting (e.g.~\cite{aaronson_et_al:LIPIcs:2019:10582}).
-
-% With the newly developed techniques, we revisit the classical verification of quantum computation problems from both a philosophical and a practical point of view.
-
 \subsection{CVQC for Quantum Sampling Problems} \label{subsection:sampling}
@@
 Due to the intrinsic randomness of quantum mechanics, the output from a quantum computation is randomized and described by a distribution.
-% In general, a round of quantum computation can be described as applying a quantum circuit and measuring the output qubits in computational basis.
-%To verifiably delegate general quantum computation, it is natural to require that the output is close to the correct distribution when the verifier accepts. 
 Thus, if a classical verifier want to utilize the full power of a quantum machine, the ability to get a verifiable sample from the quantum circuit's output distribution is desirable.
@@
 
-%The previous works following Madadev's construction has been focusing on decision problems.
-In this work, we proposed and constructed a extension of Mahadev's protocol to \emph{sampling} problems, where the classical verifier get a sample from a desired distribution from the quantum prover.
-More formally, we seek a classical verifiable delegation of the class $\SampBQP$ proposed by Aaronson~\cite{aaronson_2013}.
-Such an extension to sampling problems is desirable on a fundamental level; since we can always measure all qubits at the end of a quantum circuit, every quantum circuit naturally gives some distribution to sample from.
-Thus, if a classical verifier want to utilize the full power of a quantum machine, the ability to get a verifiable sample from the quantum circuit's output distribution is desired.
-On a more concrete level, quantum algorithms like Shor's algorithm~\cite{Shor} has a significant quantum sampling component, and the recent quantum supremacy proposals (e.g.,~\cite{Boson, IQP, nature-google}) are built around sampling tasks, suggesting the importance of sampling in quantum computation.
-
-% We first observe that the \emph{sampling} version of $\BQP$ (e.g., the class $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
-
-% Moreover, a lot of quantum algorithms from Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component.
-% The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones also suggests the relevance of delegation for quantum sampling problems.
-
 It is worth noting that the difficulty of extending the delegation of decision problem to the delegation of sampling problems is quantum-specific. This is because 
 there is a simple reduction from the delegation of \emph{classical} sampling problems to decision ones:  the verifier can sample and fix the random seed of the computation, 
-%\footnote{One can use pseudorandomness, e.g., generated by a PRG seed, if verifier's efficiency is required, as typically in the classical delegation of computation literature.}, 
 which makes the computation deterministic.
@@
 However, this derandomization trick does not work in the quantum setting due to its intrinsic randomness.
-
-%fix a seed for pseudo-randomness, send it to the prover, and then the sampling outcome can be computed  bit-by-bit under this pseudo-random seed in a deterministic way.
-Therefore, classical literature of delegation of computation primarily focuses on the delegation of decision problems.
-%However, it is unclear how to make this de-randomization trick work for the delegation of $\SampBQP$,  as randomness in quantum computation comes from inherent nature of quantum mechanics rather than some random seeds.
-%Thus, it seems that the delegation of $\SampBQP$ needs to take a different technical route.
-
-% The first and important step in the case of $\SampBQP$ is to identify an appropriate definition of corresponding CVQC protocols.
 
@@
 As the first step to formalize CVQC for quantum sampling problems, we consider the complexity class $\SampBQP$ introduced by Aaronson~\cite{aaronson_2013} as a natural class to capture efficiently computable quantum sampling problems.
-%model
-%formalize efficiently computable quantum sampling problems with the complexity class $\SampBQP$ introduced by Aaronson~\cite{aaronson_2013}.
-%
-%Formally, 
 $\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine with a desired inverse polynomial error (See Section~\ref{sec:samp_definition} for the formal definition).
@@
 We formalize the soundness by a strong \emph{simulation-based} definition, (\Cref{dfn:stats-secure-proto-sampbqp}),
-where we require that the joint distribution $(d,z)$ of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from the desired distribution $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.\footnote{This simulation-based formulation is analogous to the standard composable security definition for QKD.} \hannote{justify?}
-%
-%To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems.
-
-%and almost never accept and output from an incorrect distribution when interacting with a malicious prover.
-We formalize this by a strong \emph{simulation-based} definition (Section~\ref{sec:samp_definition}), where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from the desired distribution $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.
+where we require that the joint distribution $(d,z)$ of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from the desired distribution $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.\footnote{This simulation-based formulation is analogous to the standard composable security definition for QKD.}
 
@@
 
-%, which we discuss  further in Section~\ref{subsec:discussion}.
-
-%\KM{mention the inverse poly error and add forward pointer for discussion}
-
-% To the best of our knowledge, we are the first to formally define the delegation of quantum sampling problems.
-
-% We note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problems and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the simulation-based soundness property we defined.
-Proving the soundness of these constructions for delegating $\SampBQP$ is an interesting open question.
-
-% The requirement that the verifier needs to output a sample when accepts makes a direct application of Mahadev's protocol infeasible for $\SampBQP$.
-As a result, in order to construct a $\QPIP_0$ protocol for $\SampBQP$,  one needs to (1) construct a $\QPIP_1$ protocol for $\SampBQP$ with very small completeness and soundness errors, and (2) amend Mahadev's construction so that the protocol will generate the desired sample whenever it accepts.
-% Our contribution is a solution to address the above two technical challenges.
-
-% In contrast to the single-bit $\mathrm{Accept/Reject}$ information for the decision $\BQP$, any $\SampBQP$ problem needs to always output a sample of the desired distribution.
-% In the context of CVQC protocols, it means that the protocol should allow the verifier to generate the desired output sample whenever the protocol accepts.
-Of course, when the prover cheats, the verifier will reject and no further output is required in that case.
-% Intuitively, the soundness should require that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interacting with a malicious prover.
-
-% 
-% Indeed, some nice features of the Hadamard round,  e.g., allowing X-Z measurements on any qubit,  suggest the feasibility of generating  multi-bit measurement outcomes with the protocol.
-
-%\paragraph{Techniques.}
-
 The construction of our CVQC protocol follows the blueprint of Mahadev's construction~\cite{FOCS:Mahadev18a}.
@@
 
-%Our protocol is constructed by generalizing Mahadev's protocol to ha
-
 \paragraph{Overview of Mahadev's Protocol.}
-%
 Following~\cite{FOCS:Mahadev18a}, we define $\QPIP_{\tau}$ as classes of interactive proof systems between an (almost) classical verifier and a quantum prover, where the classical verifier has limited quantum computational capability, formalized as possessing $\tau$-qubit quantum memory.
-%\footnote{Intuitively, the size of local quantum memory limits the size of qubits that a general (entangled) quantum operation can be operated on at the same time.
-However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the prover and discard some local qubits in the case of overflow.}.
 A formal definition is given in Appendix~\ref{sec:qpip_def}.
@@
 \paragraph{Overview of Our Construction.}
-%As mentioned, our construction of CVQC protocol for $\SampBQP$ 
 Following the blueprint of Mahadev's construction, our construction proceeds in the following two steps: 1.
@@
 The first step can be done by combining existing techniques from different contexts, whereas the second step is the main technical challenge.
-%Both steps requires non-trivial works, but it turns out that the second step is the main technical challenge. 
-At a high-level, the reason is the above-mentioned issue that the verifier does not learn the measurement outcome in the testing round.
-While this is not a problem for decision problems, %(where the verifier only needs to decide to accept or reject),
+At a high-level, the reason is the above-mentioned issue that the verifier does not learn the measurement outcome in the testing round. While this is not a problem for decision problems,
 for sampling problems, the verifier needs to produce an output sample when accepts, but there seems to be no way to produce the output for the verifier without learning the measurement outcome.   
-%
 We discuss both steps in turn as follows.
-
-%As we shall see, both steps requires non-trivial works, and the second step is the main technical challenge.
 
@@
 The challenge is to show that $\PiSampZ$ is computationally sound.
-Since we are now in the computational setting, we cannot use the quantum de Finetti theorem as above which only holds in the information-theoretical setting\hannote{really?
-maybe emphasis on constructing adversary}.
+Since we are now in the computational setting, we cannot use the quantum de Finetti theorem as above which only holds in the information-theoretical setting.
 Furthermore, parallel repetition for computationally sound protocols are typically difficult to analyze, and known to not always work for protocols with four or more messages even in the classical setting~\cite{BIN97,PW12}.
 
-% Fortunately, parallel repetition of Mahadev's protocol for $\BQP$ has been analyzed before in ~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19} with interestingly different proofs.
-Both works showed that $m$-fold parallel repetition reduces the soundness error to $2^{-m}$ for $\BQP$ by relying on special properties of Mahadev's protocol.
-
  Parallel repetition of Mahadev's protocol for $\BQP$ has been analyzed before in ~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19}. However, the situation here is different. 
- %the parallel repetitions of Mahadev's protocol for $\BQP$ and $\SampBQP$ is very different. 
  For $\BQP$, the verifier simply chooses to run the Hadamard and testing rounds independently for each repetition.
@@
 
-%Intuitively, Mahadev's protocol has the property that if a malicious prover $P^*$ knows the answer to pass the testing round, then it must be ``committed'' to a state $\rho$ in the sense that the verifier $V$ learns the $X/Z$ measurement outcome of $\rho$ in the Hadamard round (in a computational sense).
-Thus, the soundness of the underlying $\QPIP_1$ protocol ensures that $V$ learns a correct sample when it accepts.
-In short, when $P^*$ knows the testing round answer,  $P^*$ cannot ``cheat'' in the Hadamard round.
-
-%\hannote{copy ch 5 here?}
 To analyze the soundness of $\PiSampZ$, we use the \emph{partition lemma} developed in~\cite{arXiv:ChiaChungYam19} to analyze the prover's behavior while executing copies of $\PiMeasure$.\footnote{The analysis of \cite{arXiv:AlaChiHun19} is more tailored to the decision problems setting, and it is unclear how to extend it to sampling problems where there are multiple bits of output.} Intuitively, the partition lemma says that for any cheating prover and for each copy $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$.
@@
 
-% ~\cite{arXiv:ChiaChungYam19}  introduces a \emph{partition lemma}, which roughly says that there is an efficient projection that partitions the prover's internal quantum space into a ``known-answer'' subspace $S_1$ where $P^*$ knows the answer to the testing round, and a ``not-known-answer'' subspace $S_0$ where $P^*$ does not know the answer to the testing round.
-For an (efficient) prover's states $\ket{\psi} \in S_1$, the verifier $V$ can produce a sound output in the Hadamard round.
-For (efficient) prover's states $\ket{\psi} \in S_0$, the verifier $V$ rejects in the testing round with high probability.
-The work of \cite{arXiv:ChiaChungYam19} used this partition lemma iteratively to each instance of the repetition to show that for a no instance $x$ for any (efficient) prover's state $\ket{\psi}$, the probability that $V$ accepts is at most roughly $2^{-m}$.
-
-% We apply the partition lemma iteratively to the prover's state  similarly to~\cite{arXiv:ChiaChungYam19}, but with significant differences to show the soundness of $\PiSampZ$ for $\SampBQP$.
-In particular, extra care is required to reason about the computational indistinguishability of the verifier's output sample from the correct distribution $D_x$.
-To gain some intuition, let us apply the partition lemma to the prover's state $\ket{\psi}$ with respect to the first coordinate, which decompose $\ket{\psi} = \ket{\psi_0} + \ket{\psi_1}$ with $\ket{\psi_0} \in S_0$ and  $\ket{\psi_1} \in S_1$, respectively.
-Intuitively, the $\ket{\psi_0}$ component will be rejected whenever the first coordinate runs the testing round, but the verifier may be ``cheated'' to accepted incorrectly when the first coordinate runs the Hadamard round, which happens with probability $1/m$ and is where the error come from.
-For the $\ket{\psi_1}$ component, $V$ will produce a sound output if it runs the Hadamard round at the first coordinate.
-For the case that $V$ chooses to run the testing round at the first coordinate, we can analyze it by further applying the partition lemma to $\ket{\psi_1}$ with respect to the second coordinate, and repeat the analysis, and so on.
-% %
 The intuitive analysis outlined above glosses over many technical details, and we substantiate this outline with full details in 
 Section~\ref{sec:qpip0_all}.
-
-%\hannote{put this somewhere else?}
-%It is worthwhile mentioning that we came to notice some online discussion\footnote{\url{https://www.scottaaronson.com/blog/?p=3697}, e.g., comment \#25, \#26, \#42, \#48.
-} on the possibility of a CVQC protocol for $\SampBQP$ after we developed our own result.
-These comments suggested a possible reduction of $\SampBQP$ to the local Hamiltonian problem following a similar high-level idea as our solution, however, with no detail and a seemingly different technical route.
-More importantly, the issue that the verifier does not generate outputs in the testing round seems to be overlooked and not discussed there.
-
-%A natural attempt to construct a CVQC protocol for $\SampBQP$ is to directly apply Mahadev's CVQC protocol for $\SampBQP$~\cite{FOCS:Mahadev18a}.
-However, the requirement that the verifier needs to get a sample whenever accepting is not easily fulfilled by Mahadev's protocol.
-Before we explain this issue in details, let us go through a brief review of the construction and notations of Mahadev's protocol.
-%\hannote{something more nature} \hannote{explain mahadev protocol} \hannote{explain how to direct apply} \hannote{qpip1}
-% Let us revisit Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} first for some technical background. 
-%Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$
-
-%Following~\cite{FOCS:Mahadev18a}, we define $\QPIP_{\tau}$ as classes of interactive proof systems between an (almost) classical verifier and a quantum prover, where the classical verifier has limited quantum computational capability, formalized as possessing $\tau$-qubit quantum memory\footnote{Intuitively, the size of local quantum memory limits the size of qubits that a general (entangled) quantum operation can be operated on at the same time.
-However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the prover and discard some local qubits in the case of overflow.}.
-%A formal definition is given in Section~\ref{sec:qpip_def}. 
-%It is known that a solution to a $\BQP$-problem can be efficiently verified by a classical verifier who can perform a single qubit $X$ or $Z$ measurement~\cite{PhysRevA.93.022326, mf16}, by reducing any $\BQP$ problem to a local Hamiltonian problem where each term consists of  $X$ and $Z$ only.
-This leads to a $\QPIP_1$ protocol for $\BQP$.
-%The main contribution of Mahadev~\cite{FOCS:Mahadev18a} is a compiler from a $\QPIP_1$ protocol with $X$ or $Z$ measurements to a $\QPIP_0$ protocol.
-% ====
-% In this section, we create a delegation protocol for $\SampBQP$ with fully classical clients by adapting the approach taken in \cite{FOCS:Mahadev18a}.  
-%The center piece of Mahadev's compiler is the protocol $\PiMeasure$ (See \Cref{proto:urmila4}) that allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a $X$ or $Z$ measurement to measure on.
-% Composing it with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
-%$\PiMeasure$ is a 4-round protocol between a verifier  and a prover.
-%The verifier start by secretly choosing a string $h$ specifying the $X$ or $Z$ measurements it wants to make on each qubit, and generates keys $pk, sk$ from $h$.
-The first round of communication is the verifier sending $pk$ to the prover.
-The prover ``commits" to a state $\rho$ of its choice using $pk$, and the second round of communication is the prover replying with its commitment $y$.
-%The verifier must then choose between two options: a \emph{testing round} or a \emph{Hadamard round}.
-%If the verifier chose the testing round, it can catch cheating provers at the end of the protocol, 
-%and if the verifier chose the Hadamard round, it receives desired $XZ$-measurement outcomes at the end of the protocol.
-%The third round of communication is the verifier sending his 1-bit choice of testing or Hadamard round to the prover.
-Finally, in the fourth round of the communication, the prover replies accord to the verifier's choice in the third round.
-After the last round of the communication, the verifier wrap up the protocol with some extra computation.
-If the testing round was chosen, the verifier checks the prover's fourh-round reply against the previous commitment, and rejects if he sees an inconsistency.
-If the Hadamard round was chosen, the verifier calculates $M_{XZ}(\rho, h)$, the $XZ$-measurement specified by $h$ on $\rho$, basing on the fourth-round reply.
-Using $\PiMeasure$ to delegate the $X$ or $Z$ measurement of the aforementioned $\QPIP_1$ protocol~\cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
-
-% In this work, we will compose $\PiMeasure$ with our $\QPIP_1$ protocol $\PiSamp$ (\Cref{ProtoQPIP1}) for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$.
-
-% A direct composition of $\PiSamp$ and $\PiMeasure$, however, results in a protocol $\PiNaive$ (\Cref{proto:qpip0_naive}) which does not provide reasonable completeness or accuracy guarantees.
-% This is due to $\PiMeasure$ itself having peculiar and weak guarantees:
-% the client doesn't always obtain measurement outcomes even if the server were honest.
-
-% When that happens under the $\BQP$ context, the verifier can simply accept the prover at the cost of some soundness error;
-% under our $\SampBQP$ context, however, we must run many copies of $\PiNaive$ in parallel so the verifier can generate its outputs from some copy.
-% We will spend the majority of this section analyzing the soundness of this parallel repetition.
-
-% \hannote{4 round?} As we described in blah, Mahadev's compiler is a 4-round protocol. 
-% However, the requirement that the verifier needs to get a sample whenever accepting exposes one drawback of Mahadev's protocol.
-
-% Note that Mahadev's protocol consists of the so-called testing round, where the prover's behavior is tested, and the Hadamard round, where measurement outcomes are generated. 
-% Mimicing Mahadev's construction of
-
-%With Mahadev's compiler from $\QPIP_1$ to $\QPIP_0$ for $\BQP$ in mind, a natural approach to construct a $\QPIP_0$ protocol for $\SampBQP$ is the follow step approach: 1.
-construct a $\QPIP_1$ protocol for $\SampBQP$ with $X$ or $Z$ measurements.
-2.
-compile the $\QPIP_1$ protocol with $\PiMeasure$ to get $\QPIP_0$ protocol.
-This indeed is the general outline we follow in this work.
-However, getting our result is not straightforward.
-While it is relatively straightforward to do the first step with techniques in the literature, a naive combination between the resulting $\QPIP_1$ protocol and $\PiMeasure$ does not give a $\QPIP_0$ protocols for $\SampBQP$ with reasonable \emph{completeness}.
-The reason is that while it is possible to generate desired output samples in the Hadamard round of $\PiMeasure$,
-%it is unclear how to generate such a sample when the protocol accepts in the testing round. 
-%Note that this difficulty originates from the nature of sampling problems.
-In a decision problem, the verifier can blindly choose to output accept even if he did not get the measurement details, potential sacrificing some soundness.
-In comparison, in a sampling problem, the verifier always needs to output a good sample.
-
-%\hannote{our solution}
-
-%\hannote{something quick on qpip1, can be put together with available techs. scott blog }
-
-%\hannote{japanese citations : \cite{takeuchi2018verification,hayashi2015verifiable}}
 
@@
 We note the two notions are equivalent from a feasibility point of view by a standard transformation (see Remark~\ref{rmk:blind-comp} in Section~\ref{sec:qpip_def}).
-%The two notions are equivalent from a feasibility point of view by a standard transformation that takes the description of the computation as part of the input and delegate the computation of  universal quantum circuits.
 } In the relaxed setting where the verifier has a limited quantum capability, Hayashi and Morimae~\cite{hayashi2015verifiable} constructed a blind $\QPIP_1$ protocol for delegating quantum computation with information-theoretic security that also handles sampling problems.
-%
 However, for purely classical verifiers, blind CVQC protocols seem much more difficult to construct.
@@
 
-%Mahadev's construction~\cite{mahadev_qfhe}.
-%building on top of quantum fully homomorphic encyprtion (QFHE). 
-%Precisely, we leverage QFHE (especially the one from~\cite{mahadev_qfhe}) to transform any CVQC protocol to \emph{a blind one with the same number of round communication, while preserving completeness and soundness properties}.
-%As a result, one can \emph{upgrade} every verifiable CVQC protocol with blindness almost for free with the help of QFHE.
-%
-%Conceptually, we take a very different approach from previous ones  (e.g.,~\cite{FK17} as well as failed attempts in~\cite{mahadev_2018}) which use the blindness as the start point and then work to extend it with verifiability.
-%
-%Instead, our strategy is to simulate a (verifiable) CVQC protocol under QFHE per each message.
-%To that end, we do require a special property of QFHE that the classical part of the ciphertext can be operated on separately from the quantum part, which is satisfied by the construction from~\cite{mahadev_qfhe}.
-%Our construction makes a modular use of QFHE and only requires a minor technicality in the analysis, which will be explained below. 
-%As a result, we obtain
 \begin{theorem}[informal]
@@
 
-%As a simple corollary of combining both results above, we achieve a constant-round blind CVQC protocol for $\SampBQP$. 
 \begin{theorem}[informal]
@@
 Details are given in \Cref{sec:BlindBQP2}.
-%\XW{To KM: expand the above a bit more?}
 
@@
 
-%Gheorghiu and Vidick~\cite{FOCS:GheVid19} extends Mahadev's techniques to obtain a blind CVQC protocol for $\BQP$.
-The protocol of \cite{FOCS:GheVid19} has polynomially many rounds, whereas our protocol has 4 rounds.
-
 It is also worth noting that several existing constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be generalized to delegate $\SampBQP$ in a natural way, but it seems challenging to analyze the soundness of the generalized protocol.
@@
 The reason is that in all these constructions, some form of cut and choose are used to achieve soundness.
-%\Ethan{Maybe unnecessary?: , and for delegating decision problems, negligible soundness can be achieved by taking majority vote of multiple outcomes.} 
 For sampling problems, as mentioned, there seems to be no generic way to combine multiple samples for error reduction, so the verifier needs to choose one sample to output in the cut and choose.
@@
 
-%As a followup work, Bartusek~\cite{bartuseksecure} constructs maliciously-secure multi-party protocols for $\BQP$  computation using our classical verification protocol for $\SampBQP$.
-
-%(MPQC\hannote{ref})\footnote{In MPQC, for the special case where the output is classical, it has the same simulation-based security for the output as our soundness definition.}.
-There, it\hannote{?} is achieved by using either verifiable quantum secret sharing or quantum authentication codes, both of which requires quantum communications.
-An intriguing open problem is whether it is possible to achieve negligible soundness error with classical communication while delegating a quantum sampling problem.
-
-%while a classical verifier is delegating a quantum sampling problem.
-
-%\paragraph{On the Inverse Polynomial Error in $\SampBQP$.}
-%To be added. \KM{where to add this? Sec 1.3?}
-
-%\hannote{endddddddddddddddd}
-
-\iffalse
-
-\vspace{2mm} \noindent \textbf{Contribution.} We provide \emph{affirmative} solutions to both of our questions.
-In particular, we demonstrate the feasibility of the classical verification of quantum sampling by
-constructing a constant-round CVQC protocol for $\SampBQP$, based on the quantum LWE (QLWE) assumption that the learning-with-error problem is hard for BQP machines. 
-$\SampBQP$ is the sampling version of $\BQP$ formulated by Aaronson~\cite{aaronson_2013}.
-Formally, $\SampBQP$ consists of sampling problems $(D_x)_{x\in\zo^*}$ that can be approximately sampled by a $\BQP$ machine with an inverse polynomial accuracy.
-See Section~\ref{sec:samp_definition} for further discussions on $\SampBQP$ and the precise definition of CVQC for $\SampBQP$.
-\begin{theorem}[informal] \label{thm:qpip0-informal}
-Assuming the QLWE assumption, there exists a four-message CVQC protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
-\end{theorem}
-
-Our second contribution is a simple yet powerful \emph{generic}  compiler that transforms any CVQC protocol to a blind one while preserving verifiability, building on top of QFHE. 
-Precisely, we leverage QFHE (especially the one from~\cite{mahadev_qfhe}) to transform any CVQC protocol to \emph{a blind one with the same number of round communication, while preserving completeness and soundness properties}.
-As a result, one can \emph{upgrade} every verifiable CVQC protocol with blindness almost for free with the help of QFHE.
-Conceptually, we take a very different approach from previous ones  (e.g.,~\cite{FK17} as well as failed attempts in~\cite{mahadev_2018}) which use the blindness as the start point and then work to extend it with verifiability.
-Instead, our strategy is to simulate a (verifiable) CVQC protocol under QFHE per each message.
-To that end, we do require a special property of QFHE that the classical part of the ciphertext can be operated on separately from the quantum part, which is satisfied by the construction from~\cite{mahadev_qfhe}.
-Our construction makes a modular use of QFHE and only requires a minor technicality in the analysis, which will be explained below. 
-%As a result, we obtain
-\begin{theorem}[informal]
-Assuming the QLWE assumption, there exists a protocol compiler that transforms any CVQC protocol $\Pi$ to a CVQC protocol $\Piblind$ that achieves blindness while preserves its round complexity, completeness, and soundness.
-\end{theorem}
-
-As a simple corollary of combining both results above, we achieve a constant-round blind CVQC protocol for $\SampBQP$. 
-\begin{theorem}[informal]
-        Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
-\end{theorem}
-
-We also construct the first blind and constant-round CVQC protocol for $\BQP$ by applying our compiler to the parallel repetition of Mahadev's protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19}.
-
-\begin{theorem}[informal]
-    Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
-\end{theorem}
-
-To the authors' best knowledge, we are the first to study CVQC protocols for $\SampBQP$ and establish a generic compiler to upgrade CVQC protocols with blindness.
-Our result also entails a \emph{constant-round} blind and verifiable CVQC protocol for $\BQP$.
-The closest result to ours is by Gheorghiu and Vidick~\cite{FOCS:GheVid19} which shows such a CVQC protocol for $\BQP$, however, with a polynomial number of rounds.
-Their protocol was obtained by first constructing a remote state preparation primitive and then combining it with an existing blind and verifiable protocol~\cite{FK17} where the verifier has some limited quantum power.
-Our technical approach is quite different and seems incomparable.
-
-\vspace{2mm} \noindent \textbf{Techniques.} Let us revisit Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} first for some technical background. 
-Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of (local) quantum memory in the possession of the classical verifier, or equivalently, the limited quantum power of the verifier\footnote{Intuitively, the size of local quantum memory limits the size of qubits that a general (entangled) quantum operation can be operated on at the same time.
-However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the prover and discard some local qubits in the case of overflow.}.
-A precise definition is given in Section~\ref{sec:qpip_def}. 
-It is known that $\BQP$ can be efficiently verified by a classical verifier that can perform a single qubit $X$ or $Z$ measurement~\cite{PhysRevA.93.022326, mf16}, by reducing any $\BQP$ problem to a local Hamiltonian problem where each term consists of  $X$ and $Z$ only.
-This leads to a $\QPIP_1$ protocol for $\BQP$.
-The main contribution of Mahadev~\cite{FOCS:Mahadev18a} can hence be deemed as a way to compile this $\QPIP_1$ protocol into a $\QPIP_0$ protocol (i.e., with a fully classical verifier).
-
-Precisely, to leverage Mahadev's construction, one needs to start with a $\QPIP_1$ protocol with very small completeness and soundness errors, which will then be compiled into a $\QPIP_0$ protocol with a small completeness error, but a close-to-$1/2$ soundness error under the QLWE assumption\footnote{Mahadev only proved soundness error close-to-$3/4$ for her protocol, but it was later proved~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19} that her protocol actually achieves close-to-$1/2$ soundness error.}.
-This large soundness error is due to the current structure of Mahadev's protocol that consists of the \emph{testing} round and the \emph{Hadamard} round, each of which happens with a half chance. 
-At a high level, the protocol verifies the behavior of the prover in the testing round, while assumes that the prover behaves honestly and all the X-Z measurements are correct in the Hadamard round. 
-The soundness is obtained by observing that the dishonest prover cannot cheat in both rounds, while cheating in one round alone is possible which leads to a large soundness error. 
-This less desirable soundness error, as well as other parameters, has been subsequently improved in \cite{arXiv:AlaChiHun19, arXiv:ChiaChungYam19} by a parallel repetition of Mahadev's original CVQC protocol in the computational setting.
-
-As we mentioned earlier that an appropriate definition of CVQC for $\SampBQP$ is needed to capture the intuition that the verifier should always output the desired sample whenever accepts, but should never be "cheated" to accept and output an incorrect sample when interacting with a malicious prover.
-We formalize this by a strong \emph{simulation-based} definition (Section~\ref{sec:samp_definition}), where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.
-
-To the best of our knowledge, we are the first to formally define the delegation of quantum sampling problems.
-We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problems and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the simulation-based soundness property we defined.
-Proving the soundness of these constructions for delegating $\SampBQP$ is an interesting open question.
-
-The requirement that the verifier needs to output a sample when accepts makes a direct application of Mahadev's protocol infeasible for $\SampBQP$.
-As a result, in order to construct a $\QPIP_0$ protocol for $\SampBQP$,  one needs to (1) construct a $\QPIP_1$ protocol for $\SampBQP$ with very small completeness and soundness errors, and (2) amend Mahadev's construction so that the protocol will generate the desired sample whenever it accepts.
-Our contribution is a solution to address the above two technical challenges.
-
-\vspace{2mm} \noindent \textbf{Construction of a $\QPIP_0$ protocol for $\SampBQP$}. 
-Following the aforementioned outline, our construction can be divided into three key technical steps.
-
-\vspace{2mm} \noindent \emph{$\diamond$ Reducing  $\SampBQP$ to the local Hamiltonian problem}: We will continue to employ the local Hamiltonian technique~\cite{kitaev2002classical} and its ground state (known as the history state) as a key technical ingredient to certify the $\SampBQP$ circuits.
-Recall that the $\QPIP_1$ protocol for $\BQP$ in Mahadev's construction also comes from a reduction of $\BQP$ to a $X$-$Z$-only local Hamiltonian problem.
-
-However, there are important differences between the cases for $\BQP$ and $\SampBQP$.
-Recall that the original construction of local Hamiltonian $H$ for $\BQP$ (or $\QMA$) contains two parts $H=H_{\mathrm{circuit}}+ H_{\mathrm{out}}$.
-Roughly speaking, $H_{\mathrm{circuit}}$ helps guarantee its ground space only contains \emph{valid} history states with the correct input and circuit evolution, while $H_{\mathrm{out}}$'s energy encodes the 0/1 output for $\BQP$ circuits.
-Thus, the outcome of a $\BQP$ instance can be encoded by the \emph{ground energy} of $H$.
-
-In the case of $\SampBQP$, one needs to output both Accept/Reject information as well as a sample from the desired distribution if the protocol accepts. 
-To that end, one hopes to certify the validity of the entire history state which is the ground state of $H_{\mathrm{circuit}}$, rather than the ground energy of $H_{\mathrm{circuit}}$ only. 
-% one still uses $H_{\mathrm{circuit}}$ to certify the validity of the history state.
-% However, in this case, one needs to measure on the entire final state of the circuit, rather than a single output qubit,
-% which can no longer be encoded solely by the ground energy.
-Namely, we want to rule out the existence of any state that is far from the history state but its energy (respect to $H_{\mathrm{circuit}}$) is very close to the ground one. 
-One nature approach, also ours, is to make the unique valid history state lie in the ground space of a slightly different local Hamiltonian $H'_{\mathrm{circuit}}$ that has a large \emph{spectral} gap between its ground energy and excited ones.
-It is hence guaranteed that any state with a close-to-ground energy must also be close to the history state.
-In other words, a certification of the energy $H'_{\mathrm{circuit}}$ could lead to a certification of the history state, which in turn helps us generate the desired sample. 
-We construct such $H'_{\mathrm{circuit}}$ from $H_{\mathrm{circuit}}$ by using the \emph{perturbation} technique (e.g.,~\cite{kempe_kitaev_regev_2006}) with a further restriction to X/Z terms.
-(\Cref{sec:LHXZ}.)
-
-\vspace{2mm} \noindent \emph{$\diamond$ A $\QPIP_1$ protocol for $\SampBQP$:} A certification protocol for the history state, however, is insufficient to imply a $\QPIP_1$ protocol for $\SampBQP$ directly.
-Intuitively, we face a similar dilemma as we described above about Mahadev's protocol: we can either employ the certification protocol on $H'_{\mathrm{circuit}}$ to do the test, or to measure the history state to generate the desired outcome, but not both at the same time since the testing protocol would disturb the measurement outcome.
-To resolve that, we design a \emph{cut-and-choose} protocol on multiple copies of the history state so as to separate the testing and the outputting parts on separate copies of history states.
-
-The prover in the real protocol, of course, won't necessarily send copies of history states.
-Thus, to leverage the aforementioned intuition, one needs to avoid entanglement among these copies to obtain some sort of independence.
-We employ the quantum \emph{de Finetti} theorem to address this technical challenge.
-Specifically, given any permutation-invariant $k$-register state (where each register could contain many qubits), it is known that the reduced state on many subsets of $k$-register will be close to a separable state.
-Typically, for favorable error bounds, the parameter $k$ could be as large as the dimension of a single register, which is exponential in our context and hence undesirable. 
-Fortunately, since there is no entangled operation in the protocol to perform on two copies of history states, one can employ an efficient variant of the quantum \emph{de Finetti} theorem~\cite{Brandao2017} whose error bound depends poly-logarithmically on the dimension of the register, which leads to an efficient $\QPIP_1$ protocol for $\SampBQP$.
-We can further achieve very small completeness and soundness errors in this way to satisfy the premise of Mahadev's compilation.  
-Note that the established $\QPIP_1$ protocol is information-theoretically sound without any computational assumption.  (\Cref{sec:qpip1}.)
-
-\vspace{2mm} \noindent  \emph{$\diamond$ Compile $\QPIP_1$ into $\QPIP_0$ after parallel repetition}: We now discuss how to use Mahadev's measurement protocol to compile the above $\QPIP_1$ protocol for $\SampBQP$ to a $\QPIP_0$ protocol.
-As mentioned, a major issue we need to address in Mahadev's original construction is that when the verifier $V$ chooses to run a testing round, $V$ does not learn an output sample when it accepts.
-%(which happens with probability $1/2$),
-
-Specifically, let $\PiNaive$ be an ``intermediate'' $\QPIP_0$ protocol obtained by applying Mahadev's compilation to the above $\QPIP_1$ protocol.
-Namely, when $V$ chooses to run the Hadamard round, it could learn a measurement outcome from the measurement protocol and be able to run the $\QPIP_1$ verifier to generate a decision and an output sample when accepts.
-However, when  $V$ chooses to run the testing round, it only decides to accept/reject without being able to output a sample.
-
-Similar to the above cut-and-choose idea for $\QPIP_1$, a natural idea to fix the issue is to execute multiple copies of $\PiNaive$ in parallel\footnote{It is also reasonable to consider sequential repetition, but we consider parallel repetition for its advantage of preserving the round complexity.}, and to choose a random copy to run the Hadamard round to generate an output sample and use all the remaining copies to run the testing round.
-The verifier accepts only when all executions accept and outputs the sample from the Hadamard round.
-Let us call this protocol $\PiSampZ$.
-
-Clearly from the construction, the verifier now can output a sample when it decides to accept, and output a correct sample when interacting with an honest prover (completeness).
-The challenge is to show that $\PiSampZ$ is computationally sound.
-Note that now we are in the computational setting, we cannot use the quantum de Finetti theorem as above since it only holds in the information-theoretical setting.
-Furthermore, parallel repetition for computationally sound protocols are typically difficult to analyze, and known to not always work for protocols with four or more messages~\cite{BIN97,PW12}.
-
-Fortunately, parallel repetition of Mahadev's protocol for $\BQP$ has been analyzed before in ~\cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19} with interestingly different proofs.
-Both works showed that $m$-fold parallel repetition reduces the soundness error to $2^{-m}$ for $\BQP$ by relying on special properties of Mahadev's protocol.
-
-It is worth comparing the parallel repetition of Mahadev's protocol for $\BQP$ and $\SampBQP$.
-For $\BQP$, the verifier simply chooses to run the Hadamard and testing rounds independently for each repetition.
-In contrast, our $\PiSampZ$ runs the Hadamard round in one repetition and run the testing round in the rest.
-The reason is that in $\SampBQP$, as well as generically in sampling problems, there is no known approach to combine two samples learned from two Hadamard-round executions to generate one sample with much better parameters, i.e., no generic error reduction method for the sampling problem.
-In contrast, the error reduction for decision problems can be done with the majority vote. 
-As a result, while the soundness error decreases exponentially for $\BQP$, as we see below (and also in the above $\QPIP_1$ protocols), for $\SampBQP$, $m$-fold repetition only decreases the error to $\poly(1/m)$.
-
-We rely on the technique developed in~\cite{arXiv:ChiaChungYam19} to analyze the soundness of $\PiSampZ$.
-Intuitively, Mahadev's protocol has the property that if a malicious prover $P^*$ knows the answer to pass the testing round, then it must be ``committed'' to a state $\rho$ in the sense that the verifier $V$ learns the $X/Z$ measurement outcome of $\rho$ in the Hadamard round (in a computational sense).
-Thus, the soundness of the underlying $\QPIP_1$ protocol ensures that $V$ learns a correct sample when it accepts.
-In short, when $P^*$ knows the testing round answer,  $P^*$ cannot ``cheat'' in the Hadamard round.
-The work of~\cite{arXiv:ChiaChungYam19} formalizes this intuition by a \emph{partition lemma}, which roughly says that there is an efficient projection that partitions the prover's internal quantum space into a ``known-answer'' subspace $S_1$ where $P^*$ knows the answer to the testing round, and a ``not-known-answer'' subspace $S_0$ where $P^*$ does not know the answer to the testing round.
-For (efficient) prover's states $\ket{\psi} \in S_1$, the verifier $V$ can produce a sound output in the Hadamard round.
-For (efficient) prover's states $\ket{\psi} \in S_0$, the verifier $V$ rejects in the testing round with high probability.
-The work of \cite{arXiv:ChiaChungYam19} used this partition lemma iteratively to each instance of the repetition to show that for a no instance $x$ for any (efficient) prover's state $\ket{\psi}$, the probability that $V$ accepts is at most roughly $2^{-m}$.
-
-We apply the partition lemma iteratively to the prover's state  similarly to~\cite{arXiv:ChiaChungYam19}, but with significant differences to show the soundness of $\PiSampZ$ for $\SampBQP$.
-In particular, extra care is required to reason about the computational indistinguishability of the verifier's output sample from the correct distribution $D_x$.
-To gain some intuition, let us apply the partition lemma to the prover's state $\ket{\psi}$ with respect to the first coordinate, which decompose $\ket{\psi} = \ket{\psi_0} + \ket{\psi_1}$ with $\ket{\psi_0} \in S_0$ and  $\ket{\psi_1} \in S_1$, respectively.
-Intuitively, the $\ket{\psi_0}$ component will be rejected whenever the first coordinate runs the testing round, but the verifier may be ``cheated'' to accepted incorrectly when the first coordinate runs the Hadamard round, which happens with probability $1/m$ and is where the error come from.
-For the $\ket{\psi_1}$ component, $V$ will produce a sound output if it runs the Hadamard round at the first coordinate.
-For the case that $V$ chooses to run the testing round at the first coordinate, we can analyze it by further applying the partition lemma to $\ket{\psi_1}$ with respect to the second coordinate, and repeat the analysis, and so on.
-%
-The intuitive analysis outlined above glosses over many technical details, and we substantiate this outline with full details in  
-Section~\ref{sec:qpip0_all}.
-
-It is worthwhile mentioning that we came to notice some online discussion\footnote{\url{https://www.scottaaronson.com/blog/?p=3697}, e.g., comment \#25, \#26, \#42, \#48.
-} on the possibility of a CVQC protocol for $\SampBQP$ after we developed our own result.
-These comments suggested a possible reduction of $\SampBQP$ to the local Hamiltonian problem following a similar high-level idea as our solution, however, with no detail and a seemingly different technical route.
-More importantly, the issue that the verifier does not generate outputs in the testing round seems to be overlooked and not discussed there.
-
-\vspace{2mm} \noindent \textbf{A generic compiler to upgrade $\QPIP_0$ protocols with blindness}.
-At a high-level, the idea is simple: we run the original protocol under a QFHE with the verifier's key.
-Intuitively, this allows the prover to compute his next message under encryption without learning the underlying verifier's message, and hence achieves blindness while preserving the properties of the original protocol.
-One subtlety with this approach is the fact that the verifier is classical while the QFHE cipher text could depend on both quantum and classical data.
-In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm need to be classical when the underlying message is classical, which is fortunately satisfied by~\cite{mahadev_qfhe}.
-
-A more subtle issue is to preserve the soundness.
-In particular, compiled protocols with a single application of QFHE might (1) leak information about the circuit evaluated by the verifier through its outputted QFHE ciphertexts (i.e., no \emph{circuit privacy});
-or (2) fail to simulate original protocols upon receiving invalid ciphertexts from the prover.
-We address these issues by letting the verifier switch to a fresh new key for each round of the protocol. 
-Details are given in \Cref{sec:BlindBQP2}.
-%\XW{To KM: expand the above a bit more?}
-
-\fi
-
-%\vspace{2mm} \noindent \textbf{Open Questions.} 
-%\KM{mention error issue}
-%Our main focus is on the feasibility of the desired functionality and properties, which nevertheless leaves room for the improvement of parameter dependence.
-Some of our parameter dependence inherits from previous works (e.g.~\cite{FOCS:Mahadev18a}), whereas some is due to our own construction where we didn't mean to identify the best possible parameter dependence.
-It will be extremely interesting to improve the parameter dependence with potentially new techniques.
-
-%\vspace{2mm} \noindent \textbf{Organization.} \KM{check if its correct...} \KM{can use here to mention that preliminary is moved to appendix} 
 \paragraph{Organization}

### 2021-10-22 qpip0.tex
Do more clean-up

@@
 \label{sec:qpip0_all}
-
-%to create a fully classical delegation protocol for $\BQP$
 
@@
 Recall that in $\PiSamp$ the verifier takes $X$ and $Z$ measurements on the prover's message.
-In $\PiNaive$ we let the verifier use $\PiMeasure$ to learn those measurement outcomes instead. \hannote{also need to be non-adaptive?}
+In $\PiNaive$ we let the verifier use $\PiMeasure$ to learn those measurement outcomes instead.
 
@@
 \end{cases}$$
-%is drawn from the true distribution instead when $\PNaiveStar$ is accepted. \hannote{?} 
 This binding property is formalized in \Cref{lem:naive-qpip0-binding}.
@@
 Specifically, $\Pstar$ uses $\PNaiveStar$'s strategy when it doesn't abort, otherwise honestly chooses the totally mixed state for the verifier to measure.
-%We now state the theorem and proof.
-%\hannote{and the binding of $P^*$ implies the binding of $P^*_{int}$}
 
@@
 
-   %for $\PiMeasure$ $\Pstarsub$ that is almost perfect as follows. 
 	Now we construct a cheating $\BQP$ prover for \Cref{proto:qpip0_naive}, $\Pstar$, that does the same thing as $\PNaiveStar$ except at Step~\ref{step:urmila-in-naive}, where the prover and verifier runs \Cref{proto:urmila4}.
@@
 	else, continue the dummy strategy.
-
-%	so we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property (\Cref{lem:urmila-binding}).
-%That is, there exists some $\rho$ such that $v=M_{XZ}(\rho, h)$.\hannote{only comp}
 
@@
 
-%
-
-%Roughly speaking, the idea of the partition lemma is picking a small random probability $\gamma$ and run Marriott-Watrous ~\cite{marriott2005quantum} amplification on the acceptance probability of the testing round.
-This roughly separates the prover's internal space into subspaces with acceptance probability less than $\gamma$ (Corresponds to $G_0$) and subspaces with acceptance probability bigger than $\gamma$ (Corresponds to $G_1$).
-We also get an "amplified" prover protocol $\ext$ which gi.
-
 \begin{lemma}[partition lemma; revision of Lemma 3.5 of \cite{arXiv:ChiaChungYam19}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{arXiv:ChiaChungYam19} and post-selecting on the $ph,th,in$ register being $0^t01$ or $0^t11$ then discard $ph,th,in$.
@@
 
-			% \begin{align*}  
-			%   \Pr\left[M_{\regX_i}\circ \ext_i\left(\frac{\ket{\{c\}}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{pk_i,y_i}\right]=1-\negl(\secpar).
-			%   \end{align*}
 			This will imply that $\ket{\psi_{1,i,\gamma}}$ is binding to the $i$-th Hadamard round.
@@
 For all $k \in [m]$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$,  
-%\Ethan{This ok?}, 
 and $\ket{\psi} \in H_{\regX,\regZ}$, define $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.$$
@@
 
-\hannote{maybe some explanation about $P_{acc,i}$ and $P_{acc,j}$ commute.
-maybe just stress that $P_{acc}$'s are in standard basis.stress on the dilation dequantization?} We denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as $P_{acc,-i,z}$.
+We denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as $P_{acc,-i,z}$.
 Note that $P_{acc,-i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $\vec{a}$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.
@@
 		&\L.    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,-i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] \proj{z} , \nn     
-		%=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err )
 	\end{align}
@@
 		&+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,-i,z}U \ket{\psi_{err,j,\gamma}}\R| \\
-		&+\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,-i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
+		&+\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,-i,z}U \ket{\psi_{err,j,\gamma}}\R| \R]
 	\end{align*}
@@
 Therefore, $(d,z)$  $O(\epsilon)$-computationally indistinguishable to $(d,z_{ideal})$.
-%	\hannote{?}Since $z$ is close to some ideal output distribution $z_{ideal}$, it must be close to the ideal output distribution with its own accept probability too.
 \end{proof}
@@
 ~\Cref{thm:qpip0-informal} follows as a corollary.
-
-%$\tr\abs{z-z_{ideal}}=O(\epsilon)$

### 2021-10-22 blind.tex
Updates from Overleaf
Do more cleanup

@@
 For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$.
+Note that a fresh key pair is necessary here to ensure blindness, as decrypting uses information from the secret key.
 Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoids the issue of circuit privacy.
@@
 
-\iffalse
-
-Here we present our compiler on $\QPIP_0$ protocols that can be used to achieve blindness.
-The high level idea is to run the protocol under homomorphic encryption.
-A classical version of this compiler appears in \cite{KMThesis}, where it is used to make protocols computationally simulatable.
-We have a classical client and a quantum server.
-So we choose the quantum homomorphic encryption from \cite{mahadev_qfhe} that's compatible with classical clients.
-More precisely, when the corresponding plaintext is classical, encryption and decryption can be performed classically.
-Furthermore, we notice that the ciphertexts can be split into registers as with the corresponding plaintext.
-
-A naive approach is to encrypt the initial input,
-run the entire protocol homomorphically,
-then decode the output at the very end.
-However, it is difficult to prove the soundness this way because homomorphic encryption schemes doesn't guarantee circuit privacy;
-the server could learn about its client's coins.
-Furthermore, the prover would also be allowed to send invalid ciphertexts...?
-\Ethan{Can't we assume all ciphertexts are valid, and ``invalid" ones just decodes to $\bot$?}
-So instead we let the verifier decrypt every round.
-Then, in order to preserve blindness, the verifier generates a new set of keys for every message it sends to the prover...
-Which results in the following protocol.
-
-\fi
-
-%\Ethan{General comment: Make the story more interesting. Clearly claim our own contributions.}
-
 We proceed to present our compiler. We start by introducing the notation of a $\QPIP_0$ protocol $\Pi$ as follows.
-% We now state our compiler that gives any $\QPIP_0$ protocol blindness.
 
@@
 we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
-%We start with a general form of a $\QPIP_0$ protocol that we'll be compiling.
 
@@
 For the soundness property, we show the following lemma, which implies that $\Piblind$ preserves the soundness of $\Pi_0$.
-
-%soundness of $\Piblind$ in the following theorem.
 

### 2022-02-28 blind.tex

@@
 
-To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol.
+To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol.\footnote{
+An alternative strategy is to assume circuit privacy of $\QHE$.
+This turns out to require many additional properties such as \emph{malicious} circuit privacy, efficient simulation and extraction, multi-hop evaluation, and classical $\QEval$ on classical ciphertexts and circuits.
+While existing constructions such as \cite{circuit-private-qfhe} achieves many of these properties, we are not sure if any constructions satisfy all our requirements.}
 For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$.

### 2022-02-28 introduction.tex

--- 2021-10-22 introduction.tex
@@
 We formalize the soundness by a strong \emph{simulation-based} definition, (\Cref{dfn:stats-secure-proto-sampbqp}),
-where we require that the joint distribution $(d,z)$ of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from the desired distribution $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.\footnote{This simulation-based formulation is analogous to the standard composable security definition for QKD.} \hannote{justify?}
+where we require that the joint distribution $(d,z)$ of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from the desired distribution $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.\footnote{This simulation-based formulation is analogous to the standard composable security definition for QKD.}
 %
@@
 The challenge is to show that $\PiSampZ$ is computationally sound.
-Since we are now in the computational setting, we cannot use the quantum de Finetti theorem as above which only holds in the information-theoretical setting\hannote{really?
-maybe emphasis on constructing adversary}.
+Since we are now in the computational setting, we cannot use the quantum de Finetti theorem as above which only holds in the information-theoretical setting.
 Furthermore, parallel repetition for computationally sound protocols are typically difficult to analyze, and known to not always work for protocols with four or more messages even in the classical setting~\cite{BIN97,PW12}.

### 2022-02-28 paper.tex
Change to LNCS format again
Fix font
Do more cleanup

@@
-\newif\ifdraft
-%\drafttrue
-\draftfalse
-
-\documentclass[11pt]{article}
+\documentclass[runningheads,a4paper]{llncs}
 \pagestyle{plain}
-\usepackage{authblk}
-
-\usepackage{amsmath, amssymb, amsthm}
+%\documentclass[11pt]{article}
+%\usepackage[margin=1in]{geometry}
+\usepackage{amsmath, amssymb}
 \usepackage{stmaryrd}
@@
 \usepackage{algpseudocode}
-\usepackage[margin=1in]{geometry}
 \newcommand{\sgn}{\operatorname{sgn}}
@@
 
-%*************************************page layout****************************
-\iffalse
-\setlength{\textheight}{9in}
-\setlength{\columnsep}{2.0pc}
-\setlength{\textwidth}{6.5in}
-\setlength{\topmargin}{0in}
-\setlength{\headheight}{0ex}
-\setlength{\hoffset}{0in}
-\setlength{\headsep}{0.0in}
-\setlength{\oddsidemargin}{0ex}
-\setlength{\evensidemargin}{0ex}
-\setlength{\parindent}{1pc}
-
-\fi
-
-%\pagecolor{black}
-%\color{white}
 \numberwithin{equation}{section}
@@
 {\vspace{-\topsep}\noindent\linefill\endgroup}
-
-\ifdraft
-\newcommand{\KM}[1]{{\footnotesize\color{cyan}[KM: #1]}}
-\newcommand{\Ethan}[1]{{\footnotesize\color{magenta}[Ethan: #1]}}
-\newcommand{\XW}[1]{{\footnotesize\color{red}[XW: #1]}}
-\newcommand{\hannote}[1]{\textcolor{blue}{\small {\textbf{(Han:} #1\textbf{) }}}}
-\newcommand{\Knote}[1]{\textcolor{red}{\small {\textbf{(KM:} #1\textbf{) }}}}
-\else
-\newcommand{\KM}[1]{}
-\newcommand{\Ethan}[1]{}
-\newcommand{\XW}[1]{}
-\newcommand{\hannote}[1]{}
-\newcommand{\Knote}[1]{}
-\fi
 
@@
 \def \Kprop {K_{\mathrm{prop}}}
-%\def \tr {\mathrm{tr}}
 
@@
 
-\author[1]{Kai-Min Chung\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}.
+%\iffalse
+\author{Kai-Min Chung
+\inst{1}\orcidID{0000-0002-3356-369X}
+\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}.
 Partially supported by the 2019 Academia Sinica Career Development Award under Grant no.
 23-17, and MOST QC project under Grant no.
-MOST 108-2627-E-002-001.}}
-\author[2]{Yi Lee\thanks{\href{mailto:ylee1228@umd.edu}{ylee1228@umd.edu}. This work was done while affiliated to Academia Sinica and to National Taiwan University.}}
-\author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}.
+MOST 108-2627-E-002-001.}
+\and
+Yi Lee
+\inst{2}\orcidID{0000-0003-3742-3296}
+\thanks{\href{mailto:ylee1228@umd.edu}{ylee1228@umd.edu}. This work was done while affiliated to Academia Sinica and to National Taiwan University.}
+\and
+Han-Hsuan Lin
+\inst{3}\orcidID{???}
+\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}.
 Part of this work was done while supported by Scott Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.
 Partially funded by MOST Grant no.
-110-2222-E-007-002-MY3}}
-\author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER). }}
-\affil[1]{Institute of Information Science, Academia Sinica, Taiwan}
-\affil[2]{Department of Computer Science, University of Maryland, USA}
-\affil[3]{Department of Computer Science, National Tsing Hua University, Taiwan}
-\affil[4]{
-	Department of Computer Science, Institute for Advanced Computer Studies,
-	and Joint Center for Quantum Information and Computer Science,
-	University of Maryland, USA
+110-2222-E-007-002-MY3}
+\and
+Xiaodi Wu
+\inst{2,4}\orcidID{0000-0001-8877-9802}
+\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER). }}
+
+\index{Chung, Kai-Min}
+\index{Lee, Yi}
+\index{Lin, Han-Hsuan}
+\index{Wu, Xiaodi}
+
+%\fi
+%\author{}
+\institute{
+Institute of Information Science, Academia Sinica, Taiwan
+\and
+Department of Computer Science, University of Maryland, USA
+\and
+Department of Computer Science, National Tsing Hua University, Taiwan
+\and
+Joint Center for Quantum Information and Computer Science, University of Maryland, USA
 }
@@
 
-\date{}
 \maketitle
-%\thispagestyle{plain}
 
@@
 
-%\input{preliminaries}
-
 \input{model}

### 2022-02-28 paper.tex
Fix running heads

@@
 \documentclass[runningheads,a4paper]{llncs}
-\pagestyle{plain}
 %\documentclass[11pt]{article}
@@
 %\iffalse
-\author{Kai-Min Chung
-\inst{1}\orcidID{0000-0002-3356-369X}
-\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}.
+\author{Kai-Min Chung\inst{1}\orcidID{0000-0002-3356-369X}\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}.
 Partially supported by the 2019 Academia Sinica Career Development Award under Grant no.
 23-17, and MOST QC project under Grant no.
-MOST 108-2627-E-002-001.}
-\and
-Yi Lee
-\inst{2}\orcidID{0000-0003-3742-3296}
-\thanks{\href{mailto:ylee1228@umd.edu}{ylee1228@umd.edu}. This work was done while affiliated to Academia Sinica and to National Taiwan University.}
-\and
-Han-Hsuan Lin
-\inst{3}\orcidID{???}
-\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}.
+MOST 108-2627-E-002-001.}\and
+Yi Lee\inst{2}\orcidID{0000-0003-3742-3296}\thanks{\href{mailto:ylee1228@umd.edu}{ylee1228@umd.edu}. This work was done while affiliated to Academia Sinica and to National Taiwan University.}\and
+Han-Hsuan Lin\inst{3}\orcidID{???}\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}.
 Part of this work was done while supported by Scott Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.
 Partially funded by MOST Grant no.
-110-2222-E-007-002-MY3}
-\and
-Xiaodi Wu
-\inst{2,4}\orcidID{0000-0001-8877-9802}
-\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER). }}
+110-2222-E-007-002-MY3}\and
+Xiaodi Wu\inst{2,4}\orcidID{0000-0001-8877-9802}\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}.
+Partially supported by the U.S.
+National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER).}}
 

### 2022-02-28 blind.tex
Fix wording

@@
 This turns out to require many additional properties such as \emph{malicious} circuit privacy, efficient simulation and extraction, multi-hop evaluation, and classical $\QEval$ on classical ciphertexts and circuits.
-While existing constructions such as \cite{circuit-private-qfhe} achieves many of these properties, we are not sure if any constructions satisfy all our requirements.}
+While existing constructions such as \cite{circuit-private-qfhe} achieves many of these properties, we are unsure if any construction satisfies all our requirements.}
 For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$.

### 2022-03-02 paper.tex
Wrap up final conference version

@@
 
-%\iffalse
-\author{Kai-Min Chung\inst{1}\orcidID{0000-0002-3356-369X}\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}.
-Partially supported by the 2019 Academia Sinica Career Development Award under Grant no.
+\iffalse
+\author{Kai-Min Chung\inst{1}\orcidID{0000-0002-3356-369X} Partially supported by the 2019 Academia Sinica Career Development Award under Grant no.
 23-17, and MOST QC project under Grant no.
-MOST 108-2627-E-002-001.}\and
+MOST 108-2627-E-002-001.
+\and
 Yi Lee\inst{2}\orcidID{0000-0003-3742-3296}\thanks{\href{mailto:ylee1228@umd.edu}{ylee1228@umd.edu}. This work was done while affiliated to Academia Sinica and to National Taiwan University.}\and
-Han-Hsuan Lin\inst{3}\orcidID{???}\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}.
+Han-Hsuan Lin\inst{3}\orcidID{0000-0002-5126-0174}\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}.
 Part of this work was done while supported by Scott Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.
@@
 National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER).}}
+\fi
+
+\author{Kai-Min Chung\inst{1}\orcidID{0000-0002-3356-369X}
+\and
+Yi Lee\inst{2}\orcidID{0000-0003-3742-3296}
+\and
+Han-Hsuan Lin\inst{3}\orcidID{0000-0002-5126-0174}\
+\and
+Xiaodi Wu\inst{2,4}\orcidID{0000-0001-8877-9802}}
 
@@
 Institute of Information Science, Academia Sinica, Taiwan
+\email{kmchung@iis.sinica.edu.tw}
 \and
 Department of Computer Science, University of Maryland, USA
+\email{ylee1228@umd.edu, xwu@cs.umd.edu}
 \and
 Department of Computer Science, National Tsing Hua University, Taiwan
+\email{linhh@cs.nthu.edu.tw}
 \and
@@
 
-\vspace{1mm}
-\noindent \textbf{Keywords:} classical delegation of quantum computation, blind quantum computation, quantum sampling problems
+\keywords{classical delegation of quantum computation\and
+blind quantum computation\and
+quantum sampling problems}
 
 \end{abstract}
-
-\newpage
 

### 2022-03-02 qpip0.tex
Wrap up final conference version

@@
 	\begin{align}
-		\sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| \nn \\
-		\leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}} \nn \\
+		\sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| %\nn \\
+		\leq \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}} \nn \\
 		\leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\sum_z\norm{P_z\ket{\phi}}^2} \nn \\
@@
 	\end{align}
-	where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
+	where we used Cauchy's inequality on the first two inequalities and $P_z P_{z'} =0 $ on the last one.
 \end{proof}
@@
 	\begin{align*}
-		\tr|z_i-z_{good,i}|\leq \E_{pk, y, \gamma} \sum_z &\L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^j0,\gamma}} \R|\R.\\
-		&+
-		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^i,\gamma}} \R| \\
-		&+ 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U\ket{\psi_{err,j,\gamma}}\R| \\   
-		&+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,-i,z}U \ket{\psi_{err,j,\gamma}}\R| \\
-		&+\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,-i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
+		&\tr|z_i-z_{good,i}|\leq \E_{pk, y, \gamma} \sum_z \L[ \sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^j0,\gamma}} \R|\R.\\
+		&\quad+
+		2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U \ket{\psi_{1^i,\gamma}} \R| %\\
+		+ 2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,-i,z}U\ket{\psi_{err,j,\gamma}}\R| \\   
+		&\quad+2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,-i,z}U \ket{\psi_{err,j,\gamma}}\R| %\\
+		+\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,-i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \\ %%%%%%%%%
 	\end{align*}
@@
 		\geq& \norm{\ket{\psi_{0,\gamma}}}^2+
-		\norm{\ket{\psi_{10,\gamma}}}^2+ \norm{\ket{\psi_{110,\gamma}}}^2 +\cdots  \nn \\
-		&+ \norm{\ket{\psi_{1^{m-1}0,\gamma}}}^2+ \norm{\ket{\psi_{1^{m-1}1,\gamma}}}^2.
+		\norm{\ket{\psi_{10,\gamma}}}^2
+		%+ \norm{\ket{\psi_{110,\gamma}}}^2
+		+\cdots  %\nn \\
+		+ \norm{\ket{\psi_{1^{m-1}0,\gamma}}}^2+ \norm{\ket{\psi_{1^m,\gamma}}}^2.
 	\end{align}
@@
 	\begin{align} \label{eq:z-z-good}
-		\tr|z-z_{good}| =& \tr\L|\frac{1}{m}\sum_i (z_i-z_{good,i})\R| \nn \\
-		\leq&  \frac{1}{m}\sum_i\tr| (z_i-z_{good,i})| \nn \\
-		\leq&  \frac{1}{m}\sum_i\L[\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R] \R.\nn \\
-		&+ \L. O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
-		\leq&  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%
-		=&O\L( \frac{1}{\sqrt m}+\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R),  
+		&\tr|z-z_{good}| = \tr\L|\frac{1}{m}\sum_i (z_i-z_{good,i})\R| %\nn \\
+		\leq  \frac{1}{m}\sum_i\tr| (z_i-z_{good,i})| \nn \\
+		&\quad\leq  \frac{1}{m}\sum_i\L[\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R] \R.\nn \\
+		&\qquad+ \L. O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
+		&\quad\leq  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%
+		&\quad=O\L( \frac{1}{\sqrt m}+\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R),  
 	\end{align}
-	where we used triangle inequality on the second line, \Cref{thm:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
+	where we used triangle inequality on the first inequality, \Cref{thm:zi-zgoodi} on the next one, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the last one.
 	Set $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$.

### 2022-03-16 acknowledgements.tex
Do more cleanup

@@
-\section*{Acknowledgments}
+\small{\subsubsection{Acknowledgments}
 
 The authors would like to thank Tomoyuki Morimae for his valuable feedback that helped improve the paper and for pointing out the related works \cite{takeuchi2018verification, hayashi2015verifiable}.
-We are also thankful to anonymous reviewers for various useful comments. \Ethan{check if this is ok}
+We are also thankful to anonymous reviewers for various useful comments.
+
+Kai-Min Chung is partially supported by the 2019 Academia Sinica Career Development Award under Grant no. 23-17, and MOST QC project under Grant no. MOST 108-2627-E-002-001.
+This work was done while Yi Lee was affiliated to Academia Sinica and to National Taiwan University.
+Part of this work was done while Han-Hsuan Lin was supported by Scott Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.
+Partially funded by MOST Grant no.
+110-2222-E-007-002-MY3.
+Xiaodi Wu is partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER).
+}

### 2022-03-16 blind.tex

--- 2021-10-22 blind.tex
@@
 
-To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol.
+To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol.\footnote{
+An alternative strategy is to assume circuit privacy of $\QHE$.
+This seems to require many additional properties such as \emph{malicious} circuit privacy with efficient simulation and extraction when $\QGen$ is honest and secret key is available, multi-hop evaluation, and classical $\QEval$ on classical ciphertexts and circuits.
+While existing constructions such as \cite{circuit-private-qfhe} achieves some of these properties, we are unsure if any construction satisfies all of these requirements.}
 For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$.
@@
 Finally, we show the blindness of $\Piblind$ through a standard hybrid argument where the $sk_i$'s are ``erased" one by one, starting from $sk_T$.
-Once $sk_1$ is eventually erased, $\QEnc(pk_1, x)$ and $\QEnc(pk_1, 0)$ become indistinguishable due to the IND-CPA security of $\QEnc$, and we complete the proof.
-We now fill in the mathmatical details of this argument.
+Once $sk_1$ is eventually erased, $\QEnc(pk_1, x)$ and $\QEnc(pk_1, 0)$ become indistinguishable due to the IND-CPA security of $\QEnc$.
+We now fill in the details.
 

### 2022-03-16 hamiltonian_short.tex
Sync from Overleaf
Do more clean-up

@@
 
-We present the formal construction of our $\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ in \Cref{sec:sampbqp}, \Cref{ProtoQPIP1}.
-The soundness and completeness of \Cref{ProtoQPIP1} is stated in the following theorem, whose proof is also deferred to \Cref{sec:sampbqp}.% The proof of
+We present the formal construction of our $\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ in our full version \cite{full-version}.
+The soundness and completeness of \Cref{ProtoQPIP1} is stated in the following theorem, whose proof is also deferred to \cite{full-version}.% The proof of
 
@@
 \end{thm}
+
+\vspace{-3pt}

### 2022-03-16 introduction.tex

@@
 However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the prover and discard some local qubits in the case of overflow.}.
-A formal definition is given in Appendix~\ref{sec:qpip_def}.
+A formal definition is given in our full version \cite{full-version}.
 
@@
 Another desirable property of CVQC protocols is  \emph{blindness}, which means that the prover does not learn any information about the private input for the delegated computation.\footnote{In literature, the definition of blindness may also require to additionally hide the computation.
-We note the two notions are equivalent from a feasibility point of view by a standard transformation (see Remark~\ref{rmk:blind-comp} in Section~\ref{sec:qpip_def}).
+We note the two notions are equivalent from a feasibility point of view by a standard transformation (see our full version \cite{full-version}).
 %The two notions are equivalent from a feasibility point of view by a standard transformation that takes the description of the computation as part of the input and delegate the computation of  universal quantum circuits.
@@
 \paragraph{Organization}
-We provide preliminaries on technical background in Section~\ref{sec:prelim}. 
+For preliminary technical background, see our full version \cite{full-version}. 
 Our simulation-based definition of CVQC for $\SampBQP$ is discussed in Section~\ref{sec:samp_definition}. 

### 2022-03-16 model.tex
Do more clean-up
Re-add accidentally deleted line

@@
 
-We next define what it means for a $\QPIP_\tau$ protocol\footnote{See Appendix~\ref{sec:qpip_def} for a formal definition of $\QPIP_\tau$.} to solve a $\SampBQP$ problem $\left(D_x\right)_{x\in\set{0, 1}^*}$.
+We next define what it means for a $\QPIP_\tau$ protocol\footnote{See our full version \cite{full-version} for a formal definition of $\QPIP_\tau$.} to solve a $\SampBQP$ problem $\left(D_x\right)_{x\in\set{0, 1}^*}$.
 Since sampling problems come with an accuracy parameter $\eps$, we let the prover $P$ and the verifier $V$ receive the input $x$ and $1^{1/\eps}$ as common inputs. 
